\tzpanchor{0025}
\tzpentryheader{0025}{Conservation Law: TZP Topological Charge}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e5df247c-bfcd-5785-9cab-6c030335e166}}\\
\textbf{PiID} & \tzpcode{8327950288419} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{32}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{97.0806 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.1600 rad}\\
\textbf{TZPID} & \tzpcode{ID0025} & \textbf{Node Dependencies}\quad \tzpidref{0017}\\
\textbf{Registry} & \tzpcode{registry\_id\_0025} & \textbf{Scale}\quad topological-current\\
\textbf{LOC Classification} & QA612 conserved topological quantities & QC174 current conservation\\
\textbf{arXiv Classification} & Primary: gr-qc \quad Cross-list: hep-th, math-ph & \\
\textbf{Primary Support} & Charge Integral & Current Conservation\\
\textbf{Closure Support} & Charge-Winding Identity & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The topological charge associated with the Trawin Zero Point is computed by integrating a conserved current over a hypersurface enclosing the anchor. The resulting charge equals the Trawinistic winding number and is therefore conserved under admissible evolution.

\tzpsection{Canonical Equation}
\[
Q
=
\int_{\Sigma} J^{\mu}\, d\Sigma_{\mu}
\]
\[
\nabla^{\mathrm{T}}_{\mu}J^{\mu}=0,
\qquad
Q=w
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $Q$: source equation symbol.
    \item $\mu$: source equation symbol.
    \item $\mathcal{K}_{0025}$: canonical registry object for entry ID 0025.
    \item $\Sigma_{\mu}$: source equation symbol.
    \item $S$: source equation symbol.
    \item $J^{\mu}$: source equation symbol.
    \item $T$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0025 generated source Wolfram model *)
ClearAll[K0025, Cr0025, T, R, A, W, I, N];
eq0025$1 = HoldForm[Q == IntegralSigma*J^mu*dSigmaMu];
eq0025$2 = HoldForm[TZPSequence[Grad^T*_*mu*J^mu == 0, Q == w]];
eq0025$3 = HoldForm[Grad^T*_*mu*J^mu == 0];
eq0025$4 = HoldForm[Q == w];

K0025 = HoldForm[{eq0025$1, eq0025$2, eq0025$3, eq0025$4}];

N = "normalized TRAWIN closure object for Conservation Law: TZP Topological Charge";
I = "Charge-Winding Identity integration/comparison layer";
W = "Current Conservation wave or operator carrier";
A = "Charge Integral admissible action/amplitude condition";
R = "Current Conservation rotation/curl preservation layer";
T = "Charge Integral local source condition";

Cr0025[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0025 = Cr0025[K0025];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Charge Integral local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Current Conservation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Charge Integral admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Current Conservation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Charge-Winding Identity integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Conservation Law: TZP Topological Charge.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0025] Conservation Law: TZP Topological Charge}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
Q
=
\int_{\Sigma}
J^\mu
\,\mathrm{d}\Sigma_\mu .
\end{equation}

\paragraph{Primary Derivation.}
Let $J^\mu$ be a conserved Trawinistic current satisfying:

\begin{equation}
\nabla^T_\mu J^\mu = 0 .
\end{equation}

The total charge enclosed by a spacelike hypersurface $\Sigma$ is obtained by integrating the current flux through that hypersurface:

\begin{equation}
Q
=
\int_{\Sigma}
J^\mu
\,\mathrm{d}\Sigma_\mu .
\end{equation}

Because the current is conserved, deformation of $\Sigma$ does not change $Q$, provided the hypersurface continues to enclose the same TZP winding structure.

\begin{equation}
\frac{\mathrm{d}Q}{\mathrm{d}t}=0 .
\end{equation}

Thus,

\begin{equation}
\boxed{
Q
=
\int_{\Sigma}
J^\mu
\,\mathrm{d}\Sigma_\mu .
}
\end{equation}

\paragraph{Interpretation.}
The TZP topological charge is conserved because it is the flux of a divergence-free current through a hypersurface enclosing the zero-point structure.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Conservation Law: TZP Topological Charge by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Charge Integral}\par
\[
Q
=
\int_{\Sigma} J^{\mu}\, d\Sigma_{\mu}
\]
\noindent This turns a conserved current into a hypersurface-dependent scalar quantity.\par
\noindent\textbf{2. Current Conservation}\par
\[
\nabla^{\mathrm{T}}_{\mu}J^{\mu}=0
\]
\noindent This ensures the charge does not depend on which enclosing hypersurface is chosen.\par
\noindent\textbf{3. Charge-Winding Identity}\par
\[
Q=w
\]
\noindent This closes the progression by identifying the conserved flux quantity with the topological winding count around the anchor.\par

\clearpage
\noindent\textbf{[ID 0025] Conservation Law: TZP Topological Charge}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Conservation Law: TZP Topological Charge is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The topological charge QQQ associated with the TZP is defined by Q=integralSigmaJmu dSigma sub muQ=integral sub Sigma J mu textbackslash, d Sigmatextbackslash sub mu Q=integralSigmaJmudSigma sub mu, where JmuJ mu Jmu is a conserved current satisfying nablaT sub muJmu=0nablatextsuperscript T textbackslash sub mu J mu =0nablaT sub muJmu=0 and SigmaSigmaSigma is a spacelike hypersurface enclosing ppp; QQQ equals the Trawinistic winding number www. \textbackslash{}. \textbf{Contextual meaning:} The entry reads Conservation Law: TZP Topological Charge as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Charge Integral; Current Conservation; Charge-Winding Identity.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP topological charge is conserved because it is the flux of a divergence-free current through a hypersurface enclosing the zero-point structure.

\tzpsection{Equation Grounding}
Equation anchors: The topological charge QQQ associated with the TZP is defined by Q=integralSigmaJmu dSigma muQ=integral Sigma J to the power mu textbackslash, d Sigmatextbackslash mu Q=integralSigmaJmudSigma mu, where JmuJ to the power mu Jmu is a conserved current satisfying ablaT muJmu=0 ablatextsuperscript T textbackslash mu J mu =0 ablaT muJmu=0 and SigmaSigmaSigma is a spacelike hypersurface enclosing ppp; QQQ equals the Trawinistic winding number www. The topological charge QQQ associated with the TZP is defined by Q=integralSigmaJmu dSigma muQ=integral Sigma J to the power mu textbackslash, d Sigmatextbackslash mu Q=integralSigmaJmudSigma mu, where JmuJ to the power mu Jmu is a conserved current satisfying ablaT muJmu=0 ablatextsuperscript T textbackslash mu J mu =0 ablaT muJmu=0 and SigmaSigmaSigma is a spacelike hypersurface enclosing ppp; QQQ equals the Trawinistic winding number www.

\tzpsection{Interpretive Role}
This law ties topological counting to current conservation, which means the winding information can propagate into dynamical statements rather than staying as a static loop invariant.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Conservation Governing Relation Tzp Shape-Preserving Electric Load}: field-energy vocabulary for charge, electromagnetic stress, or covariant flow.
\item \textbf{Governing Relation Shape-Preserving Electric Load Field-Energy Analogue}: field-energy vocabulary for charge, electromagnetic stress, or covariant flow.
\item \textbf{Electric Load Terminology}: field-energy vocabulary for charge, electromagnetic stress, or covariant flow.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0025]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0025_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0025] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Conservation Law: TZP Topological Charge}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the topological charge associated with the Trawin Zero Point is computed by integrating
a conserved current over a hypersurface enclosing the anchor

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Conservation Law: TZP Topological Charge is valid when the total tensorial quantity is
conserved under the stated constraint.''\\
\textbf{Proof:} The source statement identifies a conserved balance law. Reading 0025 as a proposition,
validity follows by requiring the full stress, flux, or current contribution to be
included before the divergence or balance condition is evaluated.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conserved total-structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0025_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
