\section*{ID9223: Definition of πstereo(q)}
\paragraph{Metadata.}
PiID: 8022967807057 | RTEID: RTE:P35814.9572:T2.4634 | UUID: 9f821b65-7400-53d5-9c14-83fb03e6ac77

\paragraph{Canonical Statement.}
onicus 2 TZP CANONICAL REGISTRY – ENTRIES 150–199 Falsifiability / Test Handle: Measure phase shifts in a rotating optical system and verify linear dependence on mmm, golden ratio factor in the Berry phase, and rotational frequency in the Sagnac term. 2.0.156 ID 305: Tesseract Projection and Four-Dimensional Addressing Type: Definition Formal Statement: Given a unit quaternion q=(q0,q1,q2,q3)q=(q\_0,q\_1,q\_2,q\_3)q=(q0,q1,q2,q3) on S3Sˆ3S3, stereographic projection from the south pole maps qqq to \$πstereo(q)=(q0,q1,q2)/(1q3)\textbackslash{}pi \{\textbackslash{}text\{stereo\}\}(q)\$ = (q\_0,q\_1,q\_2)/(1 - \$q\_3)πstereo(q)=(q0,q1,q2)/(1q3).\$ A tesseract’s 16 vertices correspond to normalized binary vectors \{1,+1\}ˆ4; stereographic projection onto R3\textbackslash{}mathbb\{R\}ˆ3R3 preserves circles and angles and is used to bridge fourdimensional hypercube coordinates to threedimensional DAANSphere addresses. Interpretive Meaning: The tesseract projection stage converts binary blobmatrix indices

\paragraph{Canonical Equation.}
\[
πstereo(q)=(q0,q1,q2)/(1q3)\pi {\text{stereo}}(q)
\]

\paragraph{Dictionary.}
Definition of πstereo(q) — πstereo(q)=(q0,q1,q2)/(1q3)π stereo(q)

\paragraph{Encyclopedia.}
Definition of πstereo(q) is an algebraic definition, written πstereo(q)=(q0,q1,q2)/(1q3)π stereo(q). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from π, q, defining πstereo(q). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
