\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathptmx}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,filecolor=black,menucolor=black,anchorcolor=black,pdfauthor={Daniel Alexander Trawin},pdftitle={Algebraic Signal, Geometric Enforcement: The 32/27 Ratio Family},pdfsubject={TZPID Companion Spine Series, Paper C11},pdfkeywords={TZPID, algebraic signal geometric enforcement}]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\title{Algebraic Signal, Geometric Enforcement: The 32/27 Ratio Family\\[0.6em]
\large TZPID Companion Spine Series, Paper C11 of XXVII\\
\normalsize The recurring chi = 1.185185... and its enforcement geometry}
\author{Daniel Alexander Trawin\\
\small ORCID: \href{https://orcid.org/0009-0001-4630-3715}{0009-0001-4630-3715}\\
\small \href{mailto:danielalexandertrawin@gmail.com}{danielalexandertrawin@gmail.com}}
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
This companion studies the recurring ratio family centred on chi = 32/27 = 1.185185..., the Pythagorean minor third, asking why one rational number enforces itself across the program's signal constructions.
The source manuscript's stated thesis: ``This manuscript studies the recurring ratio family centered on chi= 32 = 1.185185 . .'' The paper organizes this thesis as a TZPID gold spine: a curated seven-node registry chain (ID8515, ID8787, ID2142, ID0481, ID8586, ID0949, ID1493) with typed proof-obligation roles, dictionary and encyclopedia anchors for every node, a declared dependency order, and stubs in the program's Isabelle/Wolfram verification pipeline. Within the arc this paper is the biography of the corpus's most persistent number.
\end{abstract}

\section{Introduction}
\label{sec:intro}

Some numbers keep arriving. Across the registry's signal constructions one rational recurs with the insistence of a law: $\chi = 32/27 = 1.185185\ldots$, the Pythagorean minor third, composed entirely of the octave prime 2 and the fifth prime 3 ($2^5/3^3$). It is the bridging frequency ratio of ID0097 and ID0130; the scale-invariant ripple axiom of ID6583; the named ``1.185 Bridge'' of ID1835; and the explicit bridge target of the FlipTwistRamp architecture (companion C12). This companion asks the only question such recurrence permits: what enforces it?

The manuscript's answer is in its title: the signal is algebraic, the enforcement is geometric. Algebraically, $\chi$ is the simplest ratio that bridges without locking---close enough to unity to beat slowly against a carrier, built from the locking primes 2 and 3 yet not itself a unison, octave, or fifth. Geometrically, the enclosure's mode lattice (the rational ladder of core Paper II) makes ratios built from small powers of 2 and 3 the only stable bridge candidates, and among them $\chi$ is selected by the reciprocal-flip structure: $(32/27) \cdot (27/32) = 1$ exactly, the certified bridge-reciprocal identity, placing $\chi$ and its inverse symmetrically about the unison the way the comma pair $\gamma, 1/\gamma$ straddles closure in core Paper III.

The spine below assembles the ratio family's registry chain. Its refinement target is the cymatic prediction inherited from Paper I: successive pattern transitions on driven enclosure analogues at the $32/27$ ratio---the laboratory question that would convert the ratio's recurrence from registry sociology into physics.

\section{The concept-anchored spine methodology}
\label{sec:method}

The companion series applies a uniform method, stated here so that the paper is self-contained. The source manuscript was published with its mathematics rendered as text rather than as machine-readable LaTeX, so its spine is \emph{concept-anchored}: the thesis is taken from the manuscript's abstract, and the spine nodes are the canonical-registry entries most strongly matched to the manuscript's themes, selected by weighted term overlap with foundational nodes ranked first. Each node carries its registry equation, its dictionary definition, its encyclopedia interpretation, and a declared proof-obligation role (Core\_Definition, Core\_Axiom, or Derived\_Theorem\_Obligation). The resulting chain is a starting backbone for refinement---a typed scaffold onto which an exact, equation-by-equation crosswalk with the source manuscript can be progressively attached---rather than a claim of completed formalization.

Three properties make the backbone useful even before refinement completes. First, \emph{addressability}: every claim in the companion paper resolves to a registry identifier whose equation, definition, and verification status are independently inspectable, so disagreement can be localized to a node rather than to the paper as a whole. Second, \emph{pipeline coupling}: each spine is paired with an Isabelle focus-theory stub and a Wolfram check stub, so that as nodes are refined their obligations enter the same machine-checked pipeline that certifies the core series' guardrails. Third, \emph{role discipline}: the obligation roles separate what the spine defines from what it asserts and what it must prove, which keeps the demarcation section of every companion paper honest by construction.

The dependency chain should accordingly be read as a proof-order proposal: upstream nodes supply the vocabulary and axioms that downstream nodes consume, and the refinement pass is free to reorder where the source manuscript's own logic demands it. Where a node's registry equation arrives with rendering artifacts inherited from the source extraction (a known cost of text-rendered mathematics), the equation is quoted as carried by the registry, with the dictionary and encyclopedia entries supplying the authoritative reading.

\section{The registry chain}
\label{sec:chain}

The curated chain, in proof order, is
\begin{equation*}
\begin{gathered}
\text{ID8515} \to \text{ID8787} \to \text{ID2142} \to \text{ID0481} \\
\to \text{ID8586} \to \text{ID0949} \to \text{ID1493}.
\end{gathered}
\end{equation*}
We take the nodes in order; each subsection quotes the registry equation as carried by the canonical master, then gives the dictionary definition and the encyclopedia's interpretive reading.

\subsection{ID8515: GEOMETRIC ENFORCEMENT AXIOM Canonical Statutory Formula: chi\_alg xrightarrowpi... (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}chi\_\{alg\} \textbackslash{}xrightarrow\{\textbackslash{}pi\} \textbackslash{}Psi\_\{geo\}}}\par\medskip
\noindent\textit{Dictionary definition.} GEOMETRIC ENFORCEMENT AXIOM Canonical Statutory Formula: chi\_alg xrightarrowpi Psi\_geo Formal Technical Dissertation: The fundamental law of the Trawin framework.\par\medskip
\noindent\textit{Encyclopedia reading.} GEOMETRIC ENFORCEMENT AXIOM Canonical Statutory Formula: chi\_alg xrightarrowpi... is a symbolic expression, written chi\_alg xrightarrowpi Psi\_geo. It introduces a symbol or relation used elsewhere in the framework. It is built from pi, a, l, g, o. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{algebraic\_signal\_geo\_ID8515\_structure}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID8787: Definition of Det g|\_p (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}det g|\_p = 0}}\par\medskip
\noindent\textit{Dictionary definition.} Definition of Det g|\_p --- det g|\_p = 0\par\medskip
\noindent\textit{Encyclopedia reading.} Definition of Det g|\_p is an algebraic definition, written det g|\_p = 0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{algebraic\_signal\_geo\_ID8787\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID2142: Geometric Enforcement and the Trawin Zero Poin(1) (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{Delta phi( chi) = pi left( frac\{32\}\{27\} - 1 right) = pi left( frac\{5\}\{27\} right) approx 0.5818 text\{ radians\} approx 33.34\textasciicircum{} circ}}\par\medskip
\noindent\textit{Dictionary definition.} Delta phi( chi) = pi left( frac3227 - 1 right) = pi left( frac527 right) approx 0.5818 text radians approx 33.34\textasciicircum{} circ\par\medskip
\noindent\textit{Encyclopedia reading.} Delta phi( chi) = pi left( frac\{32\}\{27\} - 1 right) = pi left( frac\{5\}\{27\} right) approx 0.5818 text\{ radians\} approx 33.34\textasciicircum{} circ
\par\medskip\noindent\textit{Computational guardrail:} \texttt{algebraic\_signal\_geo\_ID2142\_identity}.
\par\medskip\noindent\textit{Obligation reading.} A definitional node: its function is to make later statements well-formed. The guardrail attached to it is correspondingly structural---an identity or well-formedness check rather than a physical claim.

\subsection{ID0481: Natural Three-Qubit Gate Implementation (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}begin\{adjustbox\}\{max width=\textbackslash{}linewidth,center\} \$\textbackslash{}displaystyle \textbackslash{}text\{cents\} = \textbackslash{}cdots \$ \textbackslash{}end\{adjustbox\}}}\par\medskip
\noindent\textit{Dictionary definition.} ID 481 formalizes the inherent multi qubit processing of the Tripartite architecture.\par\medskip
\noindent\textit{Encyclopedia reading.} T: Aggregate Relation is localized within the manifold and metric dynamics arc of the directory. R: Aggregate Relation preserves the operative relation that quantum process tomography (qpt) requires. A: Closure Relation fixes the admissible closure condition for the entry. W: QUANTUM PROCESS TOMOGRAPHY (QPT) is rendered as a reusable operator-level statement. I: The informational content of quantum process tomogra- phy (qpt) is retained rather than flattened. N: QUANTUM PROCESS TOMOGRAPHY (QPT) closes as a distinct normalized TRAWIN object. Interpretive role: This entry specifies the structure within the registry.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{algebraic\_signal\_geo\_ID0481\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID8586: Definition of i<psi|dmupsi> (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{i<psi|dmupsi> ==>}}\par\medskip
\noindent\textit{Dictionary definition.} Definition of i<psi|dmupsi> --- i<psi|dmupsi> ==>\par\medskip
\noindent\textit{Encyclopedia reading.} Definition of i<psi|dmupsi> is an algebraic definition, written i<psi|dmupsi> ==>. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{algebraic\_signal\_geo\_ID8586\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID0949: 12-Node Multi-Phase Transducer Synchronization (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{quad \textbackslash{}text\{and\}\textbackslash{}quad \textbackslash{}chi := \textbackslash{}frac\{32\}\{27\} || define the algebraic surplus \textbackslash{}mathrm\{begin\}\{equation\} \textbackslash{}mathrm\{delta\}(s) : =s-1}}\par\medskip
\noindent\textit{Dictionary definition.} 12-Node Multi-Phase Transducer Synchronization --- quad and chi := (32)/(27) || define the algebraic surplus beginequation delta(s) : =s-1\par\medskip
\noindent\textit{Encyclopedia reading.} frac\textbackslash{}\{16\textbackslash{}\}\textbackslash{}\{15\textbackslash{}\},quad frac\textbackslash{}\{10\textbackslash{}\}\textbackslash{}\{9\textbackslash{}\},quad text\textbackslash{}\{and\textbackslash{}\}quad chi := frac\textbackslash{}\{32\textbackslash{}\}\textbackslash{}\{27\textbackslash{}\}. / ] Individually, these ratios represent small algebraic deviations from exact closure. Taken together, they form a structured ladder that signals the onset of qualitative regime change when embedded in a geometrically curved or topologically nontrivial system. The role of /pi/ in this process is not to define the ratios themselves, but to convert their algebraic excess into a physically meaningful phase surplus. paragraph \textbackslash{}\{Definition (Algebraic Surplus).\textbackslash{}\} For any multiplicative step Ss>0S, define the algebraic surplus begin\textbackslash{}\{equation\textbackslash{}\} delta(s) : =s-1 . end\textbackslash{}\{equation\textbackslash{}\} In particular, begin\textbackslash{}\{equation\textbackslash{}\} delta/!left(frac\textbackslash{}\{16\textbackslash{}\}\textbackslash{}\{15\textbackslash{}\}right)=frac\textbackslash{}\{1\textbackslash{}\}\textbackslash{}\{15\textbackslash{}\},quad delta/!left(frac\textbackslash{}\{10\textbackslash{}\}\textbackslash{}\{9\textbackslash{}\}right)=frac\textbackslash{}\{1\textbackslash{}\}\textbackslash{}\{9\textbackslash{}\},quad delta(chi)=frac\textbackslash{}\{5\textbackslash{}\}\textbackslash{}\{27\textbackslash{}\}. end\textbackslash{}\{equation\textbackslash{}\} paragraph \textbackslash{}\{Definition (/pi/-Weighted Phase Surplu
\par\medskip\noindent\textit{Computational guardrail:} \texttt{algebraic\_signal\_geo\_ID0949\_identity}.
\par\medskip\noindent\textit{Obligation reading.} A definitional node: its function is to make later statements well-formed. The guardrail attached to it is correspondingly structural---an identity or well-formedness check rather than a physical claim.

\subsection{ID1493: Algebraic Signal Geometric Enforcement (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{in ratio can echo through many layers of understanding, suggesting that perhaps nature has its own subtle harmonies in store, waiting at just the right 1.185 interval for those who are listening. Sources:   Mathematical and musical relations of 16:15, 10:9, and 32:27en.wikipedia.orgen.wikipedia.orge ...}}\par\medskip
\noindent\textit{Dictionary definition.} Algebraic Signal Geometric Enforcement --- in ratio can echo through many layers of understanding, suggesting that perhaps nature has its own subtle harmonies in store, waiting at just the righ\par\medskip
\noindent\textit{Encyclopedia reading.} Technically, algebraic signal geometric enforcement is interpreted through the variables and operators present in the canonical relation. The equation support section should preserve these source equations in sequence so later proof and Wolfram passes operate on the same mathematical object.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{algebraic\_signal\_geo\_ID1493\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\section{Dependency structure and obligations}
\label{sec:dep}

Table~\ref{tab:obligations} summarizes the spine's obligation ledger. The chain's proof order runs from the definitional nodes (vocabulary first) through the derived obligations to the spine's closure; the refinement pass may interleave additional registry nodes where the source manuscript's own derivations require them, in which case the table grows monotonically---existing rows are never weakened, only joined.

\begin{table}[ht]
\centering
\small
\caption{Obligation ledger for the algebraic signal geometric enforcement spine.}
\label{tab:obligations}
\begin{tabular}{llp{6.2cm}}
\toprule
ID & Obligation role & Wolfram check \\
\midrule
ID8515 & Core\_Definition & \texttt{algebraic\_signal\_geo\_ID8515\_structure} \\
ID8787 & Core\_Definition & \texttt{algebraic\_signal\_geo\_ID8787\_identity} \\
ID2142 & Core\_Definition & \texttt{algebraic\_signal\_geo\_ID2142\_identity} \\
ID0481 & Core\_Definition & \texttt{algebraic\_signal\_geo\_ID0481\_identity} \\
ID8586 & Core\_Definition & \texttt{algebraic\_signal\_geo\_ID8586\_identity} \\
ID0949 & Core\_Definition & \texttt{algebraic\_signal\_geo\_ID0949\_identity} \\
ID1493 & Derived\_Theorem\_Obligation & \texttt{algebraic\_signal\_geo\_ID1493\_identity} \\
\bottomrule
\end{tabular}
\end{table}

\section{Crosswalk to the core series and companion corpus}
\label{sec:crosswalk}

Because all spines draw on one canonical registry, node sharing is measurable and meaningful: a shared identifier means two papers consume literally the same typed object, so verification work transfers between them without translation. Of this spine's seven nodes, 0 appear in core-series spines and 1 recur elsewhere in the companion corpus. Table~\ref{tab:crosswalk} records the census.

\begin{table}[ht]
\centering
\small
\caption{Node-sharing census for this spine.}
\label{tab:crosswalk}
\begin{tabular}{lp{4.4cm}p{6.6cm}}
\toprule
ID & Core-series appearances & Companion-corpus appearances \\
\midrule
ID8515 & --- & --- \\
ID8787 & --- & --- \\
ID2142 & --- & --- \\
ID0481 & --- & trawin zero point quantum field theory; universal interaction kernel \\
ID8586 & --- & --- \\
ID0949 & --- & --- \\
ID1493 & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

Two readings follow. Nodes shared with the core series are this spine's strongest members: their guardrails are already certified in the core pipeline, and the present paper inherits that status. Nodes unique to this spine are its distinctive contribution---and its refinement priority, since no other paper will discharge them. Nodes recurring across companions mark the corpus's internal seams: the same object consumed by several manuscripts, whose refinements must agree by the duplicate discipline documented in the Einstein Focus companion.

\section{Position in the TZPID arc}
\label{sec:arc}

This companion is the connective tissue of the signal group: it explains why C12's architecture chose $r = 32/27$, why core Paper II's flip-twist bridge carries the same number, and why Paper I's cross-scale ripple pillar had to separate the spatial ripple index from the $32/27$ frequency axis. Behind all of it stands Paper III: $\chi$ lives on the same 2-3 lattice as the comma, and its enforcement geometry is the same enclosure that makes twelve fifths miss seven octaves by exactly $\gamma$.

\section{Verification pathway}
\label{sec:verify}

The spine enters the program's two-engine verification pipeline. The Isabelle focus theory \texttt{TZPID\_Spine\_algebraic\_signal\_geometric\_enforcement.thy} types the seven obligations over the registry's declared vocabulary, in the dependency order of Section~\ref{sec:chain}; the Wolfram check stub \texttt{algebraic\_signal\_geometric\_enforcement\_checks.wl} carries the per-node computational guardrails listed in Table~\ref{tab:obligations}. As with the core series, the division of labor is deliberate: the theorem prover certifies structure (types, roles, dependency soundness), while the computational engine certifies arithmetic and algebraic identities node by node. A check name of the form \texttt{...\_identity} denotes a per-node identity guardrail generated from the registry equation; refined checks replace these as the equation-level crosswalk matures.

Because the companion spines share the registry with the core series, verification is cumulative: any node here that also appears in a core spine (the chain tables record several) inherits the core guardrail's status, and any refinement proved here propagates back. The companion series thus functions as the proof pipeline's breadth dimension---161 distinct registry nodes across the 27 companions---complementing the core series' depth.

The pipeline's two-engine division also fixes what failure means at this layer. A failed Wolfram guardrail localizes an arithmetic or algebraic defect in one node's registered equation: the repair is editorial (correct the registration against the source) or substantive (the source itself errs), and the obligations ledger records which. A failed Isabelle discharge, by contrast, indicts the chain: a type mismatch or unprovable dependency means the proof-order proposal of Section~\\ref{sec:chain} is wrong as stated, and the refinement pass must re-curate. Keeping these failure modes separate is what the stub architecture buys: every companion enters the pipeline with its failure semantics declared in advance, which is the practical meaning of being peer-reviewable by machine.

\section{Refinement worksheet}
\label{sec:worksheet}

The concept-anchored backbone converts into an equation-level formalization through a bounded, node-by-node worksheet. For each node the worksheet item below states the concrete refinement act; completing all seven closes the spine's first formalization pass.

\begin{enumerate}
\item \textbf{ID8515} (\texttt{algebraic\_signal\_geo\_ID8515\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID8787} (\texttt{algebraic\_signal\_geo\_ID8787\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID2142} (\texttt{algebraic\_signal\_geo\_ID2142\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID0481} (\texttt{algebraic\_signal\_geo\_ID0481\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID8586} (\texttt{algebraic\_signal\_geo\_ID8586\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID0949} (\texttt{algebraic\_signal\_geo\_ID0949\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID1493} (\texttt{algebraic\_signal\_geo\_ID1493\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\end{enumerate}

The worksheet's order matters: definitional items unblock derived ones, and a failure at any item halts propagation rather than silently weakening downstream claims. Completed items should update the obligations CSV in place, so that the spine's public ledger always reflects its true refinement state---the same live-ledger discipline the core series applies to its guardrails.

\section{Demarcation and refinement targets}
\label{sec:demarc}

As throughout the program, the demarcation line is drawn explicitly. The established layer comprises the standard mathematics and physics that the chain's nodes quote---definitions, identities, and independently citable results---together with whatever the computational guardrails certify. The framework layer comprises the source manuscript's interpretive claims and the spine's structural assertion that its nodes form the stated dependency chain. The ratio's registry recurrence is fact; the enforcement claim is the framework's surplus, and the Faraday/cymatic transition test at 32/27 is its declared falsifier.

Refinement targets, in pipeline order: (i) replace the concept-anchored node selection with an equation-level crosswalk against the source manuscript; (ii) promote each \texttt{...\_identity} guardrail to a content-bearing check; (iii) discharge the typed obligations in the Isabelle focus theory against the program's shared vocabulary; and (iv) record any node whose refinement fails, since a failed node localizes exactly where the source manuscript and the canonical registry disagree---the information a refinement pass exists to produce.

\section{Conclusion}
\label{sec:conc}

The 32/27 family study converts a recurring registry number into a structured claim: algebra proposes the bridge, geometry enforces it. One bench experiment---pattern transitions at the predicted ratio---decides whether the enforcement is the enclosure's or the registry author's. Few papers in the corpus offer a referee so compact a bargain.

\begin{thebibliography}{9}

\bibitem{registry} Trawin, D. A., \emph{TZPID Canonical Equation Master Registry, Dictionary, and Encyclopedia}, TZPIDProof archive (2026). Registry identifiers as cited in text.

\bibitem{spine} Trawin, D. A., \emph{TZPID Zenodo Individual Spines: algebraic signal geometric enforcement}, TZPIDProof archive, \texttt{zenodo\_individual\_spines/} (2026).

\bibitem{manuscript} Trawin, D. A., \emph{algebraic signal geometric enforcement}, Zenodo manuscript (2026).

\bibitem{core} Trawin, D. A., TZPID Gold Spine Series, Papers I--VIII (2026).

\bibitem{einstein} Trawin, D. A., \emph{The Einstein Focus}, TZPID Gold Spine Series, Paper V-A (2026).

\bibitem{index} Trawin, D. A., \emph{TZPID Zenodo Paper Gold Spines} (aggregate), \texttt{TZPID\_ZENODO\_SPINES.md}, TZPIDProof archive (2026).

\end{thebibliography}

\end{document}
