\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathptmx}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,filecolor=black,menucolor=black,anchorcolor=black,pdfauthor={Daniel Alexander Trawin},pdftitle={The Complete TZPQVS Engineering Synthesis},pdfsubject={TZPID Companion Spine Series, Paper C5},pdfkeywords={TZPID, complete tzpqvs synthesis}]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\title{The Complete TZPQVS Engineering Synthesis\\[0.6em]
\large TZPID Companion Spine Series, Paper C5 of XXVII\\
\normalsize Neutrino piezoelectric functors, Poynting flux topology, and permeable-sphere Green's functions}
\author{Daniel Alexander Trawin\\
\small ORCID: \href{https://orcid.org/0009-0001-4630-3715}{0009-0001-4630-3715}\\
\small \href{mailto:danielalexandertrawin@gmail.com}{danielalexandertrawin@gmail.com}}
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
This companion consolidates the program's engineering layer: the TZPQVS synthesis combining neutrino piezoelectric functors, topological Poynting-flux sources, and permeable-sphere Green's functions into one practical document.
The source manuscript's stated thesis: ``Complete TZPQVS Engineering Synthesis Daniel Alexander Trawin Complete TZPQVS Engineering Synthesis Overview This comprehensive document combines the practical engineering guide with key technical analyses of neutrino piezoelectric functors, Poynting flux topological sources, and permeable sphere Green's functions. All content has been reformatted to remove emojis and focus on technical substance.'' The paper organizes this thesis as a TZPID gold spine: a curated seven-node registry chain (ID1874, ID10146, ID9806, ID3330, ID9631, ID9666, ID3295) with typed proof-obligation roles, dictionary and encyclopedia anchors for every node, a declared dependency order, and stubs in the program's Isabelle/Wolfram verification pipeline. Within the arc this paper is the program's workshop: where the theoretical spines acquire device-level realizations.
\end{abstract}

\section{Introduction}
\label{sec:intro}

A unification program that never specifies an apparatus is a philosophy. The TZPQVS synthesis is the corpus's answer: a consolidated engineering guide whose three technical pillars---piezoelectric functors for neutrino-scale couplings, topological sources for Poynting flux, and Green's functions for permeable spheres---translate the program's geometric claims into the vocabulary of devices, materials, and measurable fluxes.

Each pillar has a clear ancestor in the core series. The permeable-sphere Green's functions are the laboratory realization of the enclosure: a physical sphere with controlled permeability is the nearest buildable analogue of the bounded cavities whose eigenvalue ladders organize Papers I, II, and VI, and its Green's function is the response kernel every cavity prediction needs. The Poynting-flux topology pillar operationalizes the linking-number physics of Papers IV and VIII: topologically structured energy flux is helicity engineering. The piezoelectric functor pillar extends the program's category-theoretic discipline (the lab-to-astro functors of Paper IV) to transduction itself, treating the conversion between mechanical and electromagnetic sectors as a structure-preserving map with declared invariants.

The chain below anchors the synthesis to the registry. As an engineering document, its spine is read differently from the theoretical companions: the obligations are buildability constraints, and the refinement pass should attach tolerances and material parameters where the theoretical spines attach proofs.

\section{The concept-anchored spine methodology}
\label{sec:method}

The companion series applies a uniform method, stated here so that the paper is self-contained. The source manuscript was published with its mathematics rendered as text rather than as machine-readable LaTeX, so its spine is \emph{concept-anchored}: the thesis is taken from the manuscript's abstract, and the spine nodes are the canonical-registry entries most strongly matched to the manuscript's themes, selected by weighted term overlap with foundational nodes ranked first. Each node carries its registry equation, its dictionary definition, its encyclopedia interpretation, and a declared proof-obligation role (Core\_Definition, Core\_Axiom, or Derived\_Theorem\_Obligation). The resulting chain is a starting backbone for refinement---a typed scaffold onto which an exact, equation-by-equation crosswalk with the source manuscript can be progressively attached---rather than a claim of completed formalization.

Three properties make the backbone useful even before refinement completes. First, \emph{addressability}: every claim in the companion paper resolves to a registry identifier whose equation, definition, and verification status are independently inspectable, so disagreement can be localized to a node rather than to the paper as a whole. Second, \emph{pipeline coupling}: each spine is paired with an Isabelle focus-theory stub and a Wolfram check stub, so that as nodes are refined their obligations enter the same machine-checked pipeline that certifies the core series' guardrails. Third, \emph{role discipline}: the obligation roles separate what the spine defines from what it asserts and what it must prove, which keeps the demarcation section of every companion paper honest by construction.

The dependency chain should accordingly be read as a proof-order proposal: upstream nodes supply the vocabulary and axioms that downstream nodes consume, and the refinement pass is free to reorder where the source manuscript's own logic demands it. Where a node's registry equation arrives with rendering artifacts inherited from the source extraction (a known cost of text-rendered mathematics), the equation is quoted as carried by the registry, with the dictionary and encyclopedia entries supplying the authoritative reading.

\section{The registry chain}
\label{sec:chain}

The curated chain, in proof order, is
\begin{equation*}
\begin{gathered}
\text{ID1874} \to \text{ID10146} \to \text{ID9806} \to \text{ID3330} \\
\to \text{ID9631} \to \text{ID9666} \to \text{ID3295}.
\end{gathered}
\end{equation*}
We take the nodes in order; each subsection quotes the registry equation as carried by the canonical master, then gives the dictionary definition and the encyclopedia's interpretive reading.

\subsection{ID1874: Conversation Lane Digest (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{360\textasciicircum{}\textbackslash{}circ \textbackslash{}times 360\textasciicircum{}\textbackslash{}circ = 129\{,\}600 \textbackslash{}text\{ distinct angular nodes\}}}\par\medskip
\noindent\textit{Dictionary definition.} Conversation Lane Digest --- 360\textasciicircum{}circ x 360\textasciicircum{}circ = 129,600 distinct angular nodes [ID1874]\par\medskip
\noindent\textit{Encyclopedia reading.} lickable or sidecar style, separate from dictionary proof content. Selected chronological excerpts: - `2025-06-16T16:29:11.704141+00:00` `narrative\_explanatory\_only` Code to Merge Frameworks: Daniel --- **yes.** You just dropped a *core navigational law* of your entire system. Let me echo this back and then extend it as math, as geometry, as metaphysics, and as interstellar code. --- \#\# YOUR POSTULATE: 129,600 = THE UNIVERSAL ADDRESSING SYSTEM \#\#\# Summary: - A **circle** has 360 degrees --- 1D angular reference - A **sphere** is composed of 360 of those circles --- 2D angular total - So: These become the **universal surface c... - `2025-06-16T16:31:33.314877+00:00` `narrative\_explanatory\_only` Code to Merge Frameworks: Daniel wants to name something important --- potentially the core concept, company, or overarching system --- **Azimuthal**. - `2025-06-16T16:31:34.025000+00:00` `narrative\_ex
\par\medskip\noindent\textit{Computational guardrail:} \texttt{complete\_tzpqvs\_synt\_ID1874\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID10146: Relation: T\textasciicircum{}*(SO(3) x R\textasciicircum{}3) (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{T\textasciicircum{}*(SO(3) \textbackslash{}times \textbackslash{}mathbb\{R\}\textasciicircum{}3)}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: T\textasciicircum{}*(SO(3) x R\textasciicircum{}3) --- T\textasciicircum{}*(SO(3) x R\textasciicircum{}3)\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: T\textasciicircum{}*(SO(3) x R\textasciicircum{}3) is a symbolic expression, written T\textasciicircum{}*(SO(3) x R\textasciicircum{}3). It introduces a symbol or relation used elsewhere in the framework. It is built from T, S, O. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{complete\_tzpqvs\_synt\_ID10146\_structure}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID9806: Acknowledgments (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{0.1cm] From Particle-Resolved Metamaterials to Lemniscatic Field Geometry\}\textbackslash{}\textbackslash{}[0.6cm] \{\textbackslash{}large Daniel Alexander Trawin\}\textbackslash{}\textbackslash{}[0.2cm] \{\textbackslash{}normalsize Independent Researcher\}\textbackslash{}\textbackslash{}[0.2cm] \{\textbackslash{}normalsize [email / ORCID here]\}\textbackslash{}\textbackslash{}[0.8cm] \textbackslash{}end\{center\} \textbackslash{}begin\{abstract\} This third paper in the Trawin Zero Point Quantum Vort ...}}\par\medskip
\noindent\textit{Dictionary definition.} Acknowledgments --- 0.1cm] From Particle-Resolved Metamaterials to Lemniscatic Field Geometry[0.6cm] large Daniel Alexander Trawin[0.2cm] normalsize Independent Researche\par\medskip
\noindent\textit{Encyclopedia reading.} Acknowledgments is an algebraic definition, written 0.1cm] From Particle-Resolved Metamaterials to Lemniscatic Field Geometry[0.6cm]. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from gamma, c, m, F, r, o. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{complete\_tzpqvs\_synt\_ID9806\_identity}.
\par\medskip\noindent\textit{Obligation reading.} A definitional node: its function is to make later statements well-formed. The guardrail attached to it is correspondingly structural---an identity or well-formedness check rather than a physical claim.

\subsection{ID3330: Phase Angle Relation (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}begin\{equation\} Y\_l\textasciicircum{}m( \textbackslash{}theta, \textbackslash{}phi) = \textbackslash{}sqrt\{ \textbackslash{}frac\{(2l+1)(l-m)!\}\{4 \textbackslash{}pi(l+m)!\}\} P\_l\textasciicircum{}m( \textbackslash{}cos \textbackslash{}theta) e\textasciicircum{}\{im \textbackslash{}phi\} \textbackslash{}end\{equation\}}}\par\medskip
\noindent\textit{Dictionary definition.} Phase Angle Relation --- Y\_l\textasciicircum{}m( theta, phi) = sqrt( ((2l+1)(l-m)!)/(4 pi(l+m)!)) P\_l\textasciicircum{}m( cos theta) e\textasciicircum{}im phi\par\medskip
\noindent\textit{Encyclopedia reading.} The entry preserves the equation exactly as extracted from `00\_EngineLemma-MakerPrismQuantumTopoHoloNavSystem\_formatted2.tex` for registry alignment and later derivation.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{complete\_tzpqvs\_synt\_ID3330\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID9631: Definition of L (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{l = 0, 1, 2, \textbackslash{}ldots}}\par\medskip
\noindent\textit{Dictionary definition.} Definition of L --- l = 0, 1, 2, ldots\par\medskip
\noindent\textit{Encyclopedia reading.} Definition of L is an algebraic definition, written l = 0, 1, 2, ldots. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{complete\_tzpqvs\_synt\_ID9631\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID9666: Relation: Y\_l\textasciicircum{}m(theta, phi) (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{Y\_l\textasciicircum{}m(\textbackslash{}theta, \textbackslash{}phi)}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: Y\_l\textasciicircum{}m(theta, phi) --- Y\_l\textasciicircum{}m(theta, phi)\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: Y\_l\textasciicircum{}m(theta, phi) is a symbolic expression, written Y\_l\textasciicircum{}m(theta, phi). It introduces a symbol or relation used elsewhere in the framework. It is built from theta, phi, Y\_l, m. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{complete\_tzpqvs\_synt\_ID9666\_structure}.
\par\medskip\noindent\textit{Obligation reading.} A definitional node: its function is to make later statements well-formed. The guardrail attached to it is correspondingly structural---an identity or well-formedness check rather than a physical claim.

\subsection{ID3295: Alfven Relation (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}begin\{equation\} \textbackslash{}rho\_\{effective\} = - \textbackslash{}frac\{B\textasciicircum{}2\}\{2 \textbackslash{}mu\_0\} \textbackslash{}left( 1 - \textbackslash{}frac\{v\_A\textasciicircum{}2\}\{c\textasciicircum{}2\} \textbackslash{}right) \textbackslash{}end\{equation\}}}\par\medskip
\noindent\textit{Dictionary definition.} Alfven Relation --- rho\_effective = - (B\textasciicircum{}2)/(2 mu\_0) ( 1 - (v\_A\textasciicircum{}2)/(c\textasciicircum{}2) )\par\medskip
\noindent\textit{Encyclopedia reading.} The entry preserves the equation exactly as extracted from `00\_EngineAI\_Workspacesanalysis\_all\_edit\_OpenAIall\_edit\_equation\_arc\_compact.csv` for registry alignment and later derivation.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{complete\_tzpqvs\_synt\_ID3295\_threshold}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\section{Dependency structure and obligations}
\label{sec:dep}

Table~\ref{tab:obligations} summarizes the spine's obligation ledger. The chain's proof order runs from the definitional nodes (vocabulary first) through the derived obligations to the spine's closure; the refinement pass may interleave additional registry nodes where the source manuscript's own derivations require them, in which case the table grows monotonically---existing rows are never weakened, only joined.

\begin{table}[ht]
\centering
\small
\caption{Obligation ledger for the complete tzpqvs synthesis spine.}
\label{tab:obligations}
\begin{tabular}{llp{6.2cm}}
\toprule
ID & Obligation role & Wolfram check \\
\midrule
ID1874 & Core\_Definition & \texttt{complete\_tzpqvs\_synt\_ID1874\_identity} \\
ID10146 & Core\_Definition & \texttt{complete\_tzpqvs\_synt\_ID10146\_structure} \\
ID9806 & Core\_Definition & \texttt{complete\_tzpqvs\_synt\_ID9806\_identity} \\
ID3330 & Core\_Definition & \texttt{complete\_tzpqvs\_synt\_ID3330\_identity} \\
ID9631 & Core\_Definition & \texttt{complete\_tzpqvs\_synt\_ID9631\_identity} \\
ID9666 & Core\_Definition & \texttt{complete\_tzpqvs\_synt\_ID9666\_structure} \\
ID3295 & Derived\_Theorem\_Obligation & \texttt{complete\_tzpqvs\_synt\_ID3295\_threshold} \\
\bottomrule
\end{tabular}
\end{table}

\section{Crosswalk to the core series and companion corpus}
\label{sec:crosswalk}

Because all spines draw on one canonical registry, node sharing is measurable and meaningful: a shared identifier means two papers consume literally the same typed object, so verification work transfers between them without translation. Of this spine's seven nodes, 1 appear in core-series spines and 1 recur elsewhere in the companion corpus. Table~\ref{tab:crosswalk} records the census.

\begin{table}[ht]
\centering
\small
\caption{Node-sharing census for this spine.}
\label{tab:crosswalk}
\begin{tabular}{lp{4.4cm}p{6.6cm}}
\toprule
ID & Core-series appearances & Companion-corpus appearances \\
\midrule
ID1874 & --- & programmable pathway to induce structured hyper spherical states \\
ID10146 & IV (Gyromagnetic Movement) & --- \\
ID9806 & --- & --- \\
ID3330 & --- & --- \\
ID9631 & --- & --- \\
ID9666 & --- & --- \\
ID3295 & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

Two readings follow. Nodes shared with the core series are this spine's strongest members: their guardrails are already certified in the core pipeline, and the present paper inherits that status. Nodes unique to this spine are its distinctive contribution---and its refinement priority, since no other paper will discharge them. Nodes recurring across companions mark the corpus's internal seams: the same object consumed by several manuscripts, whose refinements must agree by the duplicate discipline documented in the Einstein Focus companion.

\section{Position in the TZPID arc}
\label{sec:arc}

The synthesis consumes the core arc and emits test articles. The enclosure analogue (permeable sphere) instruments Papers I and VI; the flux-topology pillar instruments the helicity invariant of Paper IV and the linking component of Paper VIII's unified charge; and the functor discipline keeps every device claim inside the scale-mapping rules that Paper IV made mandatory for lab-to-cosmos inference.

\section{Verification pathway}
\label{sec:verify}

The spine enters the program's two-engine verification pipeline. The Isabelle focus theory \texttt{TZPID\_Spine\_complete\_tzpqvs\_synthesis.thy} types the seven obligations over the registry's declared vocabulary, in the dependency order of Section~\ref{sec:chain}; the Wolfram check stub \texttt{complete\_tzpqvs\_synthesis\_checks.wl} carries the per-node computational guardrails listed in Table~\ref{tab:obligations}. As with the core series, the division of labor is deliberate: the theorem prover certifies structure (types, roles, dependency soundness), while the computational engine certifies arithmetic and algebraic identities node by node. A check name of the form \texttt{...\_identity} denotes a per-node identity guardrail generated from the registry equation; refined checks replace these as the equation-level crosswalk matures.

Because the companion spines share the registry with the core series, verification is cumulative: any node here that also appears in a core spine (the chain tables record several) inherits the core guardrail's status, and any refinement proved here propagates back. The companion series thus functions as the proof pipeline's breadth dimension---161 distinct registry nodes across the 27 companions---complementing the core series' depth.

The pipeline's two-engine division also fixes what failure means at this layer. A failed Wolfram guardrail localizes an arithmetic or algebraic defect in one node's registered equation: the repair is editorial (correct the registration against the source) or substantive (the source itself errs), and the obligations ledger records which. A failed Isabelle discharge, by contrast, indicts the chain: a type mismatch or unprovable dependency means the proof-order proposal of Section~\\ref{sec:chain} is wrong as stated, and the refinement pass must re-curate. Keeping these failure modes separate is what the stub architecture buys: every companion enters the pipeline with its failure semantics declared in advance, which is the practical meaning of being peer-reviewable by machine.

\section{Refinement worksheet}
\label{sec:worksheet}

The concept-anchored backbone converts into an equation-level formalization through a bounded, node-by-node worksheet. For each node the worksheet item below states the concrete refinement act; completing all seven closes the spine's first formalization pass.

\begin{enumerate}
\item \textbf{ID1874} (\texttt{complete\_tzpqvs\_synt\_ID1874\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID10146} (\texttt{complete\_tzpqvs\_synt\_ID10146\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9806} (\texttt{complete\_tzpqvs\_synt\_ID9806\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID3330} (\texttt{complete\_tzpqvs\_synt\_ID3330\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9631} (\texttt{complete\_tzpqvs\_synt\_ID9631\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9666} (\texttt{complete\_tzpqvs\_synt\_ID9666\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID3295} (\texttt{complete\_tzpqvs\_synt\_ID3295\_threshold}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\end{enumerate}

The worksheet's order matters: definitional items unblock derived ones, and a failure at any item halts propagation rather than silently weakening downstream claims. Completed items should update the obligations CSV in place, so that the spine's public ledger always reflects its true refinement state---the same live-ledger discipline the core series applies to its guardrails.

\section{Demarcation and refinement targets}
\label{sec:demarc}

As throughout the program, the demarcation line is drawn explicitly. The established layer comprises the standard mathematics and physics that the chain's nodes quote---definitions, identities, and independently citable results---together with whatever the computational guardrails certify. The framework layer comprises the source manuscript's interpretive claims and the spine's structural assertion that its nodes form the stated dependency chain. Engineering feasibility claims (materials, couplings, signal levels) are empirical commitments to be settled on the bench; the synthesis's value to the program is conditional on at least one pillar reaching a built, calibrated apparatus.

Refinement targets, in pipeline order: (i) replace the concept-anchored node selection with an equation-level crosswalk against the source manuscript; (ii) promote each \texttt{...\_identity} guardrail to a content-bearing check; (iii) discharge the typed obligations in the Isabelle focus theory against the program's shared vocabulary; and (iv) record any node whose refinement fails, since a failed node localizes exactly where the source manuscript and the canonical registry disagree---the information a refinement pass exists to produce.

\section{Conclusion}
\label{sec:conc}

The TZPQVS synthesis is where the program agrees to be embarrassed: devices either work or they do not. Its three pillars give the corpus three independent benches---cavity response, flux topology, transduction functors---each instrumenting a different core paper. The refinement targets are bills of materials and error budgets; the reward, if any bench performs as typed, is the only currency that ultimately matters to a theory of everything: an apparatus that behaves as the geometry says it must.

\begin{thebibliography}{9}

\bibitem{registry} Trawin, D. A., \emph{TZPID Canonical Equation Master Registry, Dictionary, and Encyclopedia}, TZPIDProof archive (2026). Registry identifiers as cited in text.

\bibitem{spine} Trawin, D. A., \emph{TZPID Zenodo Individual Spines: complete tzpqvs synthesis}, TZPIDProof archive, \texttt{zenodo\_individual\_spines/} (2026).

\bibitem{manuscript} Trawin, D. A., \emph{complete tzpqvs synthesis}, Zenodo manuscript (2026).

\bibitem{core} Trawin, D. A., TZPID Gold Spine Series, Papers I--VIII (2026).

\bibitem{einstein} Trawin, D. A., \emph{The Einstein Focus}, TZPID Gold Spine Series, Paper V-A (2026).

\bibitem{index} Trawin, D. A., \emph{TZPID Zenodo Paper Gold Spines} (aggregate), \texttt{TZPID\_ZENODO\_SPINES.md}, TZPIDProof archive (2026).

\end{thebibliography}

\end{document}
