\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathptmx}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,filecolor=black,menucolor=black,anchorcolor=black,pdfauthor={Daniel Alexander Trawin},pdftitle={The Trawin-Enlil Protocol: Emergent Matter from a Hyperspherical Zero-Point Field},pdfsubject={TZPID Companion Spine Series, Paper C24},pdfkeywords={TZPID, trawin enlil protocol}]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\title{The Trawin-Enlil Protocol: Emergent Matter from a Hyperspherical Zero-Point Field\\[0.6em]
\large TZPID Companion Spine Series, Paper C24 of XXVII\\
\normalsize Bessel-resonance validation of the TZP ansatz}
\author{Daniel Alexander Trawin\\
\small ORCID: \href{https://orcid.org/0009-0001-4630-3715}{0009-0001-4630-3715}\\
\small \href{mailto:danielalexandertrawin@gmail.com}{danielalexandertrawin@gmail.com}}
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
This companion presents the Trawin-Enlil protocol: the unified geometric ansatz in which observable matter and spacetime emerge from geometric disharmonies within a synchronized hyperspherical zero-point field, validated through Bessel-resonance analysis.
The source manuscript's stated thesis: ``Emergent Matter from a Hyper-Spherical Zero-Point Field: The Trawin-Enlil Protocol and Bessel-Resonance Validation Daniel Alexander Trawin ORCID: 0009-0001-4630-3715 (Dated: March 15, 2026) We propose a unified geometric framework, the Trawin Zero Point (TZP) Ansatz, which posits that observable matter and spacetime emerge from geometric disharmonies within a synchronized hyperspherical Zero-Point Field (ZPF). By ana\,\ldots'' The paper organizes this thesis as a TZPID gold spine: a curated seven-node registry chain (ID0449, ID3584, ID5092, ID1871, ID6489, ID9859, ID3708) with typed proof-obligation roles, dictionary and encyclopedia anchors for every node, a declared dependency order, and stubs in the program's Isabelle/Wolfram verification pipeline. Within the arc this paper is the matter spine's manuscript ancestor: disharmony-as-matter, with the Bessel ladder as its measuring instrument.
\end{abstract}

\section{Introduction}
\label{sec:intro}

The energy-to-matter logic of core Paper VII has its manuscript root here. The Trawin-Enlil protocol proposes the TZP Ansatz in its most unified form: observable matter and spacetime alike emerge from geometric \emph{disharmonies} within a synchronized hyperspherical zero-point field. The field's default state is synchrony---the phase-locked, ratio-locked condition that core Paper II's mechanism produces on any bounded enclosure. Matter is what a disharmony looks like: a localized failure of the synchronized field to close on itself, persistent because the surrounding synchrony holds it in place.

The reading unifies three core threads in one figure. It is companion C1's deficit ontology with the deficit specified (a phase defect rather than a density hole); it is Paper III's comma made material (the registry names this lineage directly: ID1473, the hyperspherical disharmony model of matter); and it is Paper VII's creation threshold read geometrically---creation as the nucleation of a disharmony when the synchronized field's tension crosses critical.

The protocol's validation instrument is Bessel resonance. Because the hyperspherical field's modes live on the Bessel ladder (the corpus's universal spectrum), disharmonies have computable resonance signatures: which rungs they detune, by how much, with what half-order structure. The manuscript's Bessel-resonance analysis checks the ansatz against exactly these signatures, anticipating the half-Bessel seam physics that core Paper VI sharpened into the 18.01\% fingerprint. The spine below anchors the protocol's chain; refinement targets are the disharmony-defect dictionary (which defect classes map to which particle properties) and the resonance census against the typed ladder.

\section{The concept-anchored spine methodology}
\label{sec:method}

The companion series applies a uniform method, stated here so that the paper is self-contained. The source manuscript was published with its mathematics rendered as text rather than as machine-readable LaTeX, so its spine is \emph{concept-anchored}: the thesis is taken from the manuscript's abstract, and the spine nodes are the canonical-registry entries most strongly matched to the manuscript's themes, selected by weighted term overlap with foundational nodes ranked first. Each node carries its registry equation, its dictionary definition, its encyclopedia interpretation, and a declared proof-obligation role (Core\_Definition, Core\_Axiom, or Derived\_Theorem\_Obligation). The resulting chain is a starting backbone for refinement---a typed scaffold onto which an exact, equation-by-equation crosswalk with the source manuscript can be progressively attached---rather than a claim of completed formalization.

Three properties make the backbone useful even before refinement completes. First, \emph{addressability}: every claim in the companion paper resolves to a registry identifier whose equation, definition, and verification status are independently inspectable, so disagreement can be localized to a node rather than to the paper as a whole. Second, \emph{pipeline coupling}: each spine is paired with an Isabelle focus-theory stub and a Wolfram check stub, so that as nodes are refined their obligations enter the same machine-checked pipeline that certifies the core series' guardrails. Third, \emph{role discipline}: the obligation roles separate what the spine defines from what it asserts and what it must prove, which keeps the demarcation section of every companion paper honest by construction.

The dependency chain should accordingly be read as a proof-order proposal: upstream nodes supply the vocabulary and axioms that downstream nodes consume, and the refinement pass is free to reorder where the source manuscript's own logic demands it. Where a node's registry equation arrives with rendering artifacts inherited from the source extraction (a known cost of text-rendered mathematics), the equation is quoted as carried by the registry, with the dictionary and encyclopedia entries supplying the authoritative reading.

\section{The registry chain}
\label{sec:chain}

The curated chain, in proof order, is
\begin{equation*}
\begin{gathered}
\text{ID0449} \to \text{ID3584} \to \text{ID5092} \to \text{ID1871} \\
\to \text{ID6489} \to \text{ID9859} \to \text{ID3708}.
\end{gathered}
\end{equation*}
We take the nodes in order; each subsection quotes the registry equation as carried by the canonical master, then gives the dictionary definition and the encyclopedia's interpretive reading.

\subsection{ID0449: Industrial Ip \textbackslash{}\& Merl-50 Compliance (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}begin\{adjustbox\}\{max width=\textbackslash{}linewidth,center\} \$\textbackslash{}displaystyle \textbackslash{}text\{Access\} = \textbackslash{}cdots \$ \textbackslash{}end\{adjustbox\}}}\par\medskip
\noindent\textit{Dictionary definition.} ID 449 establishes the legal and ethical framework for the "Trawin Zero Point Opera Omnia." All engineering specifications within this registry are governed by the Modified Educational Research License (MERL 50).\par\medskip
\noindent\textit{Encyclopedia reading.} T: Carrier Map is localized within the manifold and metric dynamics arc of the directory. R: Composable Action preserves the operative relation that cold-start cooldown protocol requires. A: Normalized Output fixes the admissible closure condi- tion for the entry. W: COLD-START COOLDOWN PROTOCOL is ren- dered as a reusable operator-level statement. I: The informational content of cold-start cooldown proto- col is retained rather than flattened. N: COLD-START COOLDOWN PROTOCOL closes as a distinct normalized TRAWIN object. Interpretive role: This entry specifies the structure within the registry.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{trawin\_enlil\_protoco\_ID0449\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID3584: Magnetic Helicity Relation (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}begin\{equation\} \textbackslash{}mathcal\{M\} = \textbackslash{}text\{SO\}(3) \textbackslash{}times \textbackslash{}mathbb\{R\}\textasciicircum{}3 \textbackslash{}times \textbackslash{}mathfrak\{so\}(3)\textasciicircum{}* \textbackslash{}times (\textbackslash{}mathbb\{R\}\textasciicircum{}3)\textasciicircum{}* \textbackslash{}end\{equation\}}}\par\medskip
\noindent\textit{Dictionary definition.} Magnetic Helicity Relation --- M = SO(3) x R\textasciicircum{}3 x mathfrakso(3)\textasciicircum{}* x (R\textasciicircum{}3)\textasciicircum{}*\par\medskip
\noindent\textit{Encyclopedia reading.} The entry preserves the equation exactly as extracted from `D:\textbackslash{}00\_EngineCSVconcept\_units.csv` for registry alignment and later derivation.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{trawin\_enlil\_protoco\_ID3584\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID5092: Coupled Hamiltonian (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\$\$\textbackslash{}\textbackslash{}hat\{H\}\_\{\textbackslash{}\textbackslash{}text\{interaction\}\} = \textbackslash{}\textbackslash{}sum\_\{k,l\} g\_\{kl\} \textbackslash{}\textbackslash{}hat\{a\}\textasciicircum{}\{\textbackslash{}\textbackslash{}dagger\}\_k \textbackslash{}\textbackslash{}hat\{a\}\_l \textbackslash{}\textbackslash{}otimes \textbackslash{}\textbackslash{}hat\{\textbackslash{}\textbackslash{}sigma\}\textasciicircum{}\{(k)\}\_+ \textbackslash{}\textbackslash{}hat\{\textbackslash{}\textbackslash{}sigma\}\textasciicircum{}\{(l)\}\_-\$\$}}\par\medskip
\noindent\textit{Dictionary definition.} Power Consumption: 9. Integration with Trawin Zero Point System The communication protocol integrates with the TZP energy extraction via: Where the interaction Hamiltonian couples zero-point fluctuations to quantum information flow: Critical Innovation This architecture achieves zero-obstruction qu\par\medskip
\noindent\textit{Encyclopedia reading.} \textbackslash{}hat\{H\}\_\{\textbackslash{}text\{interaction\}\} = \textbackslash{}sum\_\{k,l\} g\_\{kl\} \textbackslash{}hat\{a\}\textasciicircum{}\{\textbackslash{}dagger\}\_k \textbackslash{}hat\{a\}\_l \textbackslash{}otimes \textbackslash{}hat\{\textbackslash{}sigma\}\textasciicircum{}\{(k)\}\_+ \textbackslash{}hat\{\textbackslash{}sigma\}\textasciicircum{}\{(l)\}\_- The entry preserves the equation exactly as extracted from `latex\_storyboard\_semantic\_bundle\_exhaustive\_20260307\_002706\textbackslash{}00\_EngineAI\_Workspacesmaster\_candidate\_queue\_exports\_dedup.csv` for registry alignment and later derivation.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{trawin\_enlil\_protoco\_ID5092\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This node carries proof debt by declaration---Derived\_Theorem\_Obligation---and is therefore where the refinement pass should concentrate first: a discharged derivation here strengthens every downstream node simultaneously.

\subsection{ID1871: Academic First Derivation Bridge Sidecar (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}Psi\_\{\textbackslash{}mathrm\{matter\}\}=\textbackslash{}mathcal\{F\}\textasciicircum{}\{-1\}\textbackslash{} !\textbackslash{}left[\textbackslash{}mathcal\{F\}(\textbackslash{}Psi\_\{\textbackslash{}mathrm\{noise\}\} )\textbackslash{},J\_0(k\textbackslash{}cdot e)\textbackslash{}right]}}\par\medskip
\noindent\textit{Dictionary definition.} Status: conditional derivation bridge only. This does not modify source truth, claim proof validity, or claim publication status.\par\medskip
\noindent\textit{Encyclopedia reading.} . This does not modify source truth, claim proof validity, or claim publication status. \#\# Bridge Target - family\_key: `trawin\_enlil\_protocol` - source\_alias: `trawin\_enlil\_protocol.pdf` - selected\_locator: `trawin\_enlil\_protocol.pdf\#page=2` - target: `ID0230` Bessel Interference Pattern of Emergent Matter - bridge\_status: `conditional\_derivation\_bridge\_ready\_for\_review` - promotion\_state: `bridge\_support\_ready\_but\_not\_proof\_or\_submission\_ready` - bridge\_digest\_sha256: `3ea2426d7cf1f81d21733293199c9e890cd02b8bc9bf00388e808f30418d896f` \#\# Derivation Bridge \#\#\# Step 1: Source Filter Form The selected source line applies a Bessel J0 kernel in transform/filter space. \#\#\# Step 2: Radial Projection Assumption Under a two-dimensional radial projection, the filter direction is read as the radial coordinate used by the target entry. \#\#\# Step 3: Background Plus Small Mode A uniform background plus
\par\medskip\noindent\textit{Computational guardrail:} \texttt{trawin\_enlil\_protoco\_ID1871\_threshold}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\subsection{ID6489: \textbackslash{}\{Einstein--Rosen Bridge and Trawin Zero-Point Tunnel:\}\textbackslash{} (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{0.3em] \textbackslash{}textit\{A Theoretical Massless Transit System of Attainable Thermodynamics\textbackslash{}\textbackslash{}Through Wave and Inter-State Topology\} \} \textbackslash{}author\{ Daniel Alexander Trawin\textbackslash{}\textbackslash{}[0.3em] \textbackslash{}small ORCID: \textbackslash{}href\{https://orcid.org/0009-0001-4630-3 715\}\{0009-0001-4630-3715\}\textbackslash{}\textbackslash{}[0.5em] \textbackslash{}small \textbackslash{}texttt\{daniel.alexander.trawin@placeh ...}}\par\medskip
\noindent\textit{Dictionary definition.} \textbackslash{}\{Einstein--Rosen Bridge and Trawin Zero-Point Tunnel:\}\textbackslash{} --- 0.3em] textitA Theoretical Massless Transit System of Attainable ThermodynamicsThrough Wave and Inter-State Topology author Daniel Alexander Trawin[0.\par\medskip
\noindent\textit{Encyclopedia reading.} \textbackslash{}\{Einstein--Rosen Bridge and Trawin Zero-Point Tunnel:\}\textbackslash{} is a tbd, written 0.3em] textitA Theoretical Massless Transit System of Attainable ThermodynamicsT. Its construction method could not be determined from the available material. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{trawin\_enlil\_protoco\_ID6489\_identity}.
\par\medskip\noindent\textit{Obligation reading.} A derived obligation: the spine claims this follows from what precedes it. Until the formal derivation is supplied, the computational guardrail polices at least the node's internal consistency.

\subsection{ID9859: Stress--Energy Tensor Relation (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}int\_\{\textbackslash{}Sigma\} \textbackslash{}sqrt\{|g|\}, R\textasciicircum{}\{\textbackslash{}mu\textbackslash{}nu\} T\_\{\textbackslash{}mu\textbackslash{}nu\}, d\textasciicircum{}4x}}\par\medskip
\noindent\textit{Dictionary definition.} Stress--Energy Tensor Relation --- integral\_Sigma sqrt(|g|), R\textasciicircum{}munu T\_munu, d\textasciicircum{}4x\par\medskip
\noindent\textit{Encyclopedia reading.} Stress--Energy Tensor Relation is an integral expression, written integral\_Sigma sqrt(|g|), R\textasciicircum{}munu T\_munu, d\textasciicircum{}4x. It is obtained by integrating over a domain, accumulating contributions across the region of interest. It is built from Sigma, mu, nu, g, R, T\_. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{trawin\_enlil\_protoco\_ID9859\_structure}.
\par\medskip\noindent\textit{Obligation reading.} This node carries proof debt by declaration---Derived\_Theorem\_Obligation---and is therefore where the refinement pass should concentrate first: a discharged derivation here strengthens every downstream node simultaneously.

\subsection{ID3708: Quantum Density Evolution Equation (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}begin\{equation\} \textbackslash{}rho\_\{\textbackslash{}mathrm\{eff\}\}(r) = -\textbackslash{}frac\{\textbackslash{}hbar c \textbackslash{}pi\textasciicircum{}2\}\{240 \textbackslash{}, d\textasciicircum{}4\} \textbackslash{}bigg[1 - \textbackslash{}frac\{d\textasciicircum{}2\}\{r\textasciicircum{}2\}\textbackslash{}bigg], \textbackslash{}end\{equation\}}}\par\medskip
\noindent\textit{Dictionary definition.} Quantum Density Evolution Equation --- rho\_eff(r) = -( c pi\textasciicircum{}2)/(240 d\textasciicircum{}4) g[1 - (d\textasciicircum{}2)/(r\textasciicircum{}2) g]\par\medskip
\noindent\textit{Encyclopedia reading.} The entry preserves the equation exactly as extracted from `D:\textbackslash{}00\_EngineCSVmath\_blocks\_normalized.csv` for registry alignment and later derivation.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{trawin\_enlil\_protoco\_ID3708\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\section{Dependency structure and obligations}
\label{sec:dep}

Table~\ref{tab:obligations} summarizes the spine's obligation ledger. The chain's proof order runs from the definitional nodes (vocabulary first) through the derived obligations to the spine's closure; the refinement pass may interleave additional registry nodes where the source manuscript's own derivations require them, in which case the table grows monotonically---existing rows are never weakened, only joined.

\begin{table}[ht]
\centering
\small
\caption{Obligation ledger for the trawin enlil protocol spine.}
\label{tab:obligations}
\begin{tabular}{llp{6.2cm}}
\toprule
ID & Obligation role & Wolfram check \\
\midrule
ID0449 & Core\_Definition & \texttt{trawin\_enlil\_protoco\_ID0449\_identity} \\
ID3584 & Core\_Definition & \texttt{trawin\_enlil\_protoco\_ID3584\_identity} \\
ID5092 & Derived\_Theorem\_Obligation & \texttt{trawin\_enlil\_protoco\_ID5092\_identity} \\
ID1871 & Derived\_Theorem\_Obligation & \texttt{trawin\_enlil\_protoco\_ID1871\_threshold} \\
ID6489 & Derived\_Theorem\_Obligation & \texttt{trawin\_enlil\_protoco\_ID6489\_identity} \\
ID9859 & Derived\_Theorem\_Obligation & \texttt{trawin\_enlil\_protoco\_ID9859\_structure} \\
ID3708 & Derived\_Theorem\_Obligation & \texttt{trawin\_enlil\_protoco\_ID3708\_identity} \\
\bottomrule
\end{tabular}
\end{table}

\section{Crosswalk to the core series and companion corpus}
\label{sec:crosswalk}

Because all spines draw on one canonical registry, node sharing is measurable and meaningful: a shared identifier means two papers consume literally the same typed object, so verification work transfers between them without translation. Of this spine's seven nodes, 0 appear in core-series spines and 3 recur elsewhere in the companion corpus. Table~\ref{tab:crosswalk} records the census.

\begin{table}[ht]
\centering
\small
\caption{Node-sharing census for this spine.}
\label{tab:crosswalk}
\begin{tabular}{lp{4.4cm}p{6.6cm}}
\toprule
ID & Core-series appearances & Companion-corpus appearances \\
\midrule
ID0449 & --- & --- \\
ID3584 & --- & --- \\
ID5092 & --- & Gravitational-Emergence-TPZ- \\
ID1871 & --- & --- \\
ID6489 & --- & Gravitational-Emergence-TPZ-; theory of it all trawin topology; tzp type c (+2 more) \\
ID9859 & --- & emergent curvature theory \\
ID3708 & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

Two readings follow. Nodes shared with the core series are this spine's strongest members: their guardrails are already certified in the core pipeline, and the present paper inherits that status. Nodes unique to this spine are its distinctive contribution---and its refinement priority, since no other paper will discharge them. Nodes recurring across companions mark the corpus's internal seams: the same object consumed by several manuscripts, whose refinements must agree by the duplicate discipline documented in the Einstein Focus companion.

\section{Position in the TZPID arc}
\label{sec:arc}

This companion closes the matter group's ancestry: C1 gave matter-as-deficit, this protocol gives matter-as-disharmony with a validation spectrum, and core Papers VI--VII received the inheritance as the half-Bessel seam and the creation threshold. Its synchronized-field premise leans on the whole mechanism arc (Papers I--II), making it the corpus's most integrative manuscript: stage, mechanism, signature, and source in one ansatz.

\section{Verification pathway}
\label{sec:verify}

The spine enters the program's two-engine verification pipeline. The Isabelle focus theory \texttt{TZPID\_Spine\_trawin\_enlil\_protocol.thy} types the seven obligations over the registry's declared vocabulary, in the dependency order of Section~\ref{sec:chain}; the Wolfram check stub \texttt{trawin\_enlil\_protocol\_checks.wl} carries the per-node computational guardrails listed in Table~\ref{tab:obligations}. As with the core series, the division of labor is deliberate: the theorem prover certifies structure (types, roles, dependency soundness), while the computational engine certifies arithmetic and algebraic identities node by node. A check name of the form \texttt{...\_identity} denotes a per-node identity guardrail generated from the registry equation; refined checks replace these as the equation-level crosswalk matures.

Because the companion spines share the registry with the core series, verification is cumulative: any node here that also appears in a core spine (the chain tables record several) inherits the core guardrail's status, and any refinement proved here propagates back. The companion series thus functions as the proof pipeline's breadth dimension---161 distinct registry nodes across the 27 companions---complementing the core series' depth.

The pipeline's two-engine division also fixes what failure means at this layer. A failed Wolfram guardrail localizes an arithmetic or algebraic defect in one node's registered equation: the repair is editorial (correct the registration against the source) or substantive (the source itself errs), and the obligations ledger records which. A failed Isabelle discharge, by contrast, indicts the chain: a type mismatch or unprovable dependency means the proof-order proposal of Section~\\ref{sec:chain} is wrong as stated, and the refinement pass must re-curate. Keeping these failure modes separate is what the stub architecture buys: every companion enters the pipeline with its failure semantics declared in advance, which is the practical meaning of being peer-reviewable by machine.

\section{Refinement worksheet}
\label{sec:worksheet}

The concept-anchored backbone converts into an equation-level formalization through a bounded, node-by-node worksheet. For each node the worksheet item below states the concrete refinement act; completing all seven closes the spine's first formalization pass.

\begin{enumerate}
\item \textbf{ID0449} (\texttt{trawin\_enlil\_protoco\_ID0449\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID3584} (\texttt{trawin\_enlil\_protoco\_ID3584\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID5092} (\texttt{trawin\_enlil\_protoco\_ID5092\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID1871} (\texttt{trawin\_enlil\_protoco\_ID1871\_threshold}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID6489} (\texttt{trawin\_enlil\_protoco\_ID6489\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID9859} (\texttt{trawin\_enlil\_protoco\_ID9859\_structure}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID3708} (\texttt{trawin\_enlil\_protoco\_ID3708\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\end{enumerate}

The worksheet's order matters: definitional items unblock derived ones, and a failure at any item halts propagation rather than silently weakening downstream claims. Completed items should update the obligations CSV in place, so that the spine's public ledger always reflects its true refinement state---the same live-ledger discipline the core series applies to its guardrails.

\section{Demarcation and refinement targets}
\label{sec:demarc}

As throughout the program, the demarcation line is drawn explicitly. The established layer comprises the standard mathematics and physics that the chain's nodes quote---definitions, identities, and independently citable results---together with whatever the computational guardrails certify. The framework layer comprises the source manuscript's interpretive claims and the spine's structural assertion that its nodes form the stated dependency chain. The ansatz is interpretive; the Bessel-resonance signatures are not---defect detunings and half-order structure are computable and comparable against driven-cavity data, which is where the protocol's validation either accrues or fails.

Refinement targets, in pipeline order: (i) replace the concept-anchored node selection with an equation-level crosswalk against the source manuscript; (ii) promote each \texttt{...\_identity} guardrail to a content-bearing check; (iii) discharge the typed obligations in the Isabelle focus theory against the program's shared vocabulary; and (iv) record any node whose refinement fails, since a failed node localizes exactly where the source manuscript and the canonical registry disagree---the information a refinement pass exists to produce.

\section{Conclusion}
\label{sec:conc}

The Trawin-Enlil protocol states the program's ontology at full strength: a synchronized hyperspherical field whose failures to close are the things we call matter, audited by the Bessel ladder those failures detune. Its refinement owes the defect dictionary and the resonance census; its place in the arc is secure either way, as the manuscript where the matter spine's geometry and its measuring instrument first appeared together.

\begin{thebibliography}{9}

\bibitem{registry} Trawin, D. A., \emph{TZPID Canonical Equation Master Registry, Dictionary, and Encyclopedia}, TZPIDProof archive (2026). Registry identifiers as cited in text.

\bibitem{spine} Trawin, D. A., \emph{TZPID Zenodo Individual Spines: trawin enlil protocol}, TZPIDProof archive, \texttt{zenodo\_individual\_spines/} (2026).

\bibitem{manuscript} Trawin, D. A., \emph{trawin enlil protocol}, Zenodo manuscript (2026).

\bibitem{core} Trawin, D. A., TZPID Gold Spine Series, Papers I--VIII (2026).

\bibitem{einstein} Trawin, D. A., \emph{The Einstein Focus}, TZPID Gold Spine Series, Paper V-A (2026).

\bibitem{index} Trawin, D. A., \emph{TZPID Zenodo Paper Gold Spines} (aggregate), \texttt{TZPID\_ZENODO\_SPINES.md}, TZPIDProof archive (2026).

\end{thebibliography}

\end{document}
