\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathptmx}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,filecolor=black,menucolor=black,anchorcolor=black,pdfauthor={Daniel Alexander Trawin},pdftitle={Entrainment and the DAANSsphere Axis},pdfsubject={TZPID Companion Spine Series, Paper C14},pdfkeywords={TZPID, Entrainment and DAANSsphere axis}]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\title{Entrainment and the DAANSsphere Axis\\[0.6em]
\large TZPID Companion Spine Series, Paper C14 of XXVII\\
\normalsize Addressable axes, polarization frames, and fractal boundary modulation}
\author{Daniel Alexander Trawin\\
\small ORCID: \href{https://orcid.org/0009-0001-4630-3715}{0009-0001-4630-3715}\\
\small \href{mailto:danielalexandertrawin@gmail.com}{danielalexandertrawin@gmail.com}}
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
This companion consolidates the DAANSsphere-axis development: the proposal that an addressable axis, a local polarization frame, and fractal boundary modulation jointly provide programmable control over electromagnetic and mechanical standing-wave manifolds.
The source manuscript's stated thesis: ``This manuscript consolidates the DAANSsphere-axis development into a reproducible modeling framework. The core proposal is that an addressable axis, a local polarization frame, and fractal boundary modulation together provide programmable control over electromagnetic and mechanical standing-wave manifolds.'' The paper organizes this thesis as a TZPID gold spine: a curated seven-node registry chain (ID2237, ID9492, ID0483, ID9491, ID9493, ID9494, ID0471) with typed proof-obligation roles, dictionary and encyclopedia anchors for every node, a declared dependency order, and stubs in the program's Isabelle/Wolfram verification pipeline. Within the arc this paper turns the enclosure from an object of study into an instrument with a control panel.
\end{abstract}

\section{Introduction}
\label{sec:intro}

The DAANSsphere of core Paper I was a stage: a golden-angle discretized enclosure on which modes live. This companion installs the controls. Its core proposal is that three structures together make standing-wave manifolds \emph{programmable}: an addressable axis (a distinguished direction on the sphere along which excitations can be targeted), a local polarization frame (the orientation bookkeeping that distinguishes otherwise-degenerate modes), and fractal boundary modulation (structured perturbation of the enclosure wall across nested scales).

Each control has a registry ancestry. The addressable axis realizes the entrainment state space of ID9492---phase, orientation, polarization, and mode amplitudes as the controllable coordinates---with the control law of ID9494 (negative-gradient Lyapunov descent, certified in core Paper II) as its actuation principle. The polarization frame extends the $SO(3) \ltimes U(1)$ symmetry bookkeeping of Paper IV to the enclosure surface. Fractal boundary modulation is the most distinctive control: because the enclosure's spectrum is set by its wall (the program's universal boundary-conditions-first principle), structured multi-scale perturbation of the wall is direct spectral programming---detuning chosen rungs, opening chosen gaps, the engineering inverse of reading the cosmic web as wall acoustics.

The spine below anchors the control architecture. Its refinement direction is a control-theoretic audit: reachability (which manifold states the three controls can reach), bandwidth (how fast), and the Lyapunov certificates that promote the entrainment claims from demonstrations to guarantees.

\section{The concept-anchored spine methodology}
\label{sec:method}

The companion series applies a uniform method, stated here so that the paper is self-contained. The source manuscript was published with its mathematics rendered as text rather than as machine-readable LaTeX, so its spine is \emph{concept-anchored}: the thesis is taken from the manuscript's abstract, and the spine nodes are the canonical-registry entries most strongly matched to the manuscript's themes, selected by weighted term overlap with foundational nodes ranked first. Each node carries its registry equation, its dictionary definition, its encyclopedia interpretation, and a declared proof-obligation role (Core\_Definition, Core\_Axiom, or Derived\_Theorem\_Obligation). The resulting chain is a starting backbone for refinement---a typed scaffold onto which an exact, equation-by-equation crosswalk with the source manuscript can be progressively attached---rather than a claim of completed formalization.

Three properties make the backbone useful even before refinement completes. First, \emph{addressability}: every claim in the companion paper resolves to a registry identifier whose equation, definition, and verification status are independently inspectable, so disagreement can be localized to a node rather than to the paper as a whole. Second, \emph{pipeline coupling}: each spine is paired with an Isabelle focus-theory stub and a Wolfram check stub, so that as nodes are refined their obligations enter the same machine-checked pipeline that certifies the core series' guardrails. Third, \emph{role discipline}: the obligation roles separate what the spine defines from what it asserts and what it must prove, which keeps the demarcation section of every companion paper honest by construction.

The dependency chain should accordingly be read as a proof-order proposal: upstream nodes supply the vocabulary and axioms that downstream nodes consume, and the refinement pass is free to reorder where the source manuscript's own logic demands it. Where a node's registry equation arrives with rendering artifacts inherited from the source extraction (a known cost of text-rendered mathematics), the equation is quoted as carried by the registry, with the dictionary and encyclopedia entries supplying the authoritative reading.

\section{The registry chain}
\label{sec:chain}

The curated chain, in proof order, is
\begin{equation*}
\begin{gathered}
\text{ID2237} \to \text{ID9492} \to \text{ID0483} \to \text{ID9491} \\
\to \text{ID9493} \to \text{ID9494} \to \text{ID0471}.
\end{gathered}
\end{equation*}
We take the nodes in order; each subsection quotes the registry equation as carried by the canonical master, then gives the dictionary definition and the encyclopedia's interpretive reading.

\subsection{ID2237: Entrainment and DAANSsphere Axis (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}quad b = \textbackslash{}frac\{2 \textbackslash{}ln \textbackslash{}phi\}\{\textbackslash{}pi\}}}\par\medskip
\noindent\textit{Dictionary definition.} Entrainment and DAANSsphere Axis --- b = (2 ln phi)/(pi) [ID2237]\par\medskip
\noindent\textit{Encyclopedia reading.} Entrainment and DAANSsphere Axis is an algebraic definition, written b = (2 ln phi)/(pi). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from phi, pi, defining b. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Entrainment\_and\_DAAN\_ID2237\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID9492: Definition of State: psi (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{State: psi = (theta, phi, epsilon, mode amplitudes) in S\textasciicircum{}2 x T\textasciicircum{}2 x R}}\par\medskip
\noindent\textit{Dictionary definition.} Definition of State: psi --- State: psi = (theta, phi, epsilon, mode amplitudes) in S\textasciicircum{}2 x T\textasciicircum{}2 x R\par\medskip
\noindent\textit{Encyclopedia reading.} Definition of State: psi is an algebraic definition, written State: psi = (theta, phi, epsilon, mode amplitudes) in S\textasciicircum{}2 x T\textasciicircum{}2 x R. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from m, o, a, p, l, u, defining State: psi. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Entrainment\_and\_DAAN\_ID9492\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID0483: Pontryagin'S Maximum Principle Control (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}begin\{adjustbox\}\{max width=\textbackslash{}linewidth,center\} \$\textbackslash{}displaystyle \textbackslash{}pi \{r\} = \textbackslash{}cdots \$ \textbackslash{}end\{adjustbox\}}}\par\medskip
\noindent\textit{Dictionary definition.} ID 483 establishes the optimal control theory for the reactor driving fields.\par\medskip
\noindent\textit{Encyclopedia reading.} T: Carrier Map is localized within the manifold and metric dynamics arc of the directory. R: Composable Action preserves the operative relation that lindblad superoperator normalization requires. A: Normalized Output fixes the admissible closure condi- tion for the entry. W: LINDBLAD SUPEROPERATOR NORMALIZA- TION is rendered as a reusable operator-level statement. I: The informational content of lindblad superoperator nor- malization is retained rather than flattened. N: LINDBLAD SUPEROPERATOR NORMALIZATION closes as a distinct normalized TRAWIN object. Interpretive role: This entry specifies the structure within the registry.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Entrainment\_and\_DAAN\_ID0483\_identity}.
\par\medskip\noindent\textit{Obligation reading.} A definitional node: its function is to make later statements well-formed. The guardrail attached to it is correspondingly structural---an identity or well-formedness check rather than a physical claim.

\subsection{ID9491: Relation: Phase Space: (theta\_target, \_target, epsilon\_target). (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{phase space: (theta\_target, \_target, epsilon\_target).}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: Phase Space: (theta\_target, \_target, epsilon\_target). --- phase space: (theta\_target, \_target, epsilon\_target).\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: Phase Space: (theta\_target, \_target, epsilon\_target). is a symbolic expression, written phase space: (theta\_target, \_target, epsilon\_target).. It introduces a symbol or relation used elsewhere in the framework. It is built from p, h, a, s, c, r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Entrainment\_and\_DAAN\_ID9491\_structure}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID9493: Definition of CLF Candidate: Vpsi) (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{CLF Candidate: Vpsi) = |Deltatheta|\textasciicircum{}2 + |Deltaphi|\textasciicircum{}2 + |Deltaepsilon|\textasciicircum{}2}}\par\medskip
\noindent\textit{Dictionary definition.} DAANS system: rotating axis n(t) rotates mode basis continuously Effect: Energy transport across m-space without dissipative loss (adiabatic transport) System locks its internal symmetry axis to external axis.\par\medskip
\noindent\textit{Encyclopedia reading.} Definition of CLF Candidate: Vpsi) is an algebraic definition, written CLF Candidate: Vpsi) = |Deltatheta|\textasciicircum{}2 + |Deltaphi|\textasciicircum{}2 + |Deltaepsilon|\textasciicircum{}2. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Entrainment\_and\_DAAN\_ID9493\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID9494: Definition of Control Law: u(psi) (Core\_Axiom)}

\noindent\textit{Registry equation:}\par
{\small\texttt{Control Law: u(psi) = -(nablaVT chosen to make V < -alphaV}}\par\medskip
\noindent\textit{Dictionary definition.} Definition of Control Law: u(psi) --- Control Law: u(psi) = -(nablaVT chosen to make V < -alphaV\par\medskip
\noindent\textit{Encyclopedia reading.} Definition of Control Law: u(psi) is an inequality / bound, written Control Law: u(psi) = -(nablaVT chosen to make V < -alphaV. It states an inequality or bound that constrains the admissible range of the quantity. It is built from V, c, h, o, s, n, defining Control Law: u(psi). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Entrainment\_and\_DAAN\_ID9494\_threshold}.
\par\medskip\noindent\textit{Obligation reading.} An axiomatic node: the chain's load-bearing assumption at this depth. Its honest treatment is exposure---state it sharply enough that data or derivation can reach it.

\subsection{ID0471: Entangled Particle Neural Injection (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}begin\{adjustbox\}\{max width=\textbackslash{}linewidth,center\} \$\textbackslash{}displaystyle \textbackslash{}rho\_\{\textbackslash{}mathrm\{bio\}\}=\textbackslash{}mathcal\{E\}(\textbackslash{}rho\_\{\textbackslash{}m athrm\{med\}\}) \$ \textbackslash{}end\{adjustbox\}}}\par\medskip
\noindent\textit{Dictionary definition.} ID 471 defines the protocol for injecting entangled states from the Mediator Channel into biological tissue.\par\medskip
\noindent\textit{Encyclopedia reading.} T: Canonical Definition is localized within the manifold and metric dynamics arc of the directory. R: Support Relation preserves the operative relation that 153,600-dimensional trajectory encoding requires. A: Support Relation 3 fixes the admissible closure condi- tion for the entry. W: 153,600-DIMENSIONAL TRAJECTORY ENCOD- ING is rendered as a reusable operator-level statement. I: The informational content of 153,600-dimensional tra- jectory encoding is retained rather than flattened. N: 153,600-DIMENSIONAL TRAJECTORY ENCOD- ING closes as a distinct normalized TRAWIN object. Interpretive role: This entry specifies the structure within the registry.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Entrainment\_and\_DAAN\_ID0471\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\section{Dependency structure and obligations}
\label{sec:dep}

Table~\ref{tab:obligations} summarizes the spine's obligation ledger. The chain's proof order runs from the definitional nodes (vocabulary first) through the derived obligations to the spine's closure; the refinement pass may interleave additional registry nodes where the source manuscript's own derivations require them, in which case the table grows monotonically---existing rows are never weakened, only joined.

\begin{table}[ht]
\centering
\small
\caption{Obligation ledger for the Entrainment and DAANSsphere axis spine.}
\label{tab:obligations}
\begin{tabular}{llp{6.2cm}}
\toprule
ID & Obligation role & Wolfram check \\
\midrule
ID2237 & Core\_Definition & \texttt{Entrainment\_and\_DAAN\_ID2237\_identity} \\
ID9492 & Core\_Definition & \texttt{Entrainment\_and\_DAAN\_ID9492\_identity} \\
ID0483 & Core\_Definition & \texttt{Entrainment\_and\_DAAN\_ID0483\_identity} \\
ID9491 & Core\_Definition & \texttt{Entrainment\_and\_DAAN\_ID9491\_structure} \\
ID9493 & Core\_Definition & \texttt{Entrainment\_and\_DAAN\_ID9493\_identity} \\
ID9494 & Core\_Axiom & \texttt{Entrainment\_and\_DAAN\_ID9494\_threshold} \\
ID0471 & Derived\_Theorem\_Obligation & \texttt{Entrainment\_and\_DAAN\_ID0471\_identity} \\
\bottomrule
\end{tabular}
\end{table}

\section{Crosswalk to the core series and companion corpus}
\label{sec:crosswalk}

Because all spines draw on one canonical registry, node sharing is measurable and meaningful: a shared identifier means two papers consume literally the same typed object, so verification work transfers between them without translation. Of this spine's seven nodes, 2 appear in core-series spines and 0 recur elsewhere in the companion corpus. Table~\ref{tab:crosswalk} records the census.

\begin{table}[ht]
\centering
\small
\caption{Node-sharing census for this spine.}
\label{tab:crosswalk}
\begin{tabular}{lp{4.4cm}p{6.6cm}}
\toprule
ID & Core-series appearances & Companion-corpus appearances \\
\midrule
ID2237 & --- & --- \\
ID9492 & II (Phase Locking) & --- \\
ID0483 & --- & --- \\
ID9491 & --- & --- \\
ID9493 & --- & --- \\
ID9494 & II (Phase Locking) & --- \\
ID0471 & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

Two readings follow. Nodes shared with the core series are this spine's strongest members: their guardrails are already certified in the core pipeline, and the present paper inherits that status. Nodes unique to this spine are its distinctive contribution---and its refinement priority, since no other paper will discharge them. Nodes recurring across companions mark the corpus's internal seams: the same object consumed by several manuscripts, whose refinements must agree by the duplicate discipline documented in the Einstein Focus companion.

\section{Position in the TZPID arc}
\label{sec:arc}

This companion is the actuator layer for the corpus's drive protocols: C9's injection enters along its addressable axis, C12's seams are placed in its polarization frame, and C15's programmable pathway runs on its controls. In the core series it instruments Paper II directly---entrainment state space and control law were that paper's registry nodes---and gives Paper I's DAANSsphere the addressability its 153600-point lattice invites.

\section{Verification pathway}
\label{sec:verify}

The spine enters the program's two-engine verification pipeline. The Isabelle focus theory \texttt{TZPID\_Spine\_Entrainment\_and\_DAANSsphere\_axis.thy} types the seven obligations over the registry's declared vocabulary, in the dependency order of Section~\ref{sec:chain}; the Wolfram check stub \texttt{Entrainment\_and\_DAANSsphere\_axis\_checks.wl} carries the per-node computational guardrails listed in Table~\ref{tab:obligations}. As with the core series, the division of labor is deliberate: the theorem prover certifies structure (types, roles, dependency soundness), while the computational engine certifies arithmetic and algebraic identities node by node. A check name of the form \texttt{...\_identity} denotes a per-node identity guardrail generated from the registry equation; refined checks replace these as the equation-level crosswalk matures.

Because the companion spines share the registry with the core series, verification is cumulative: any node here that also appears in a core spine (the chain tables record several) inherits the core guardrail's status, and any refinement proved here propagates back. The companion series thus functions as the proof pipeline's breadth dimension---161 distinct registry nodes across the 27 companions---complementing the core series' depth.

The pipeline's two-engine division also fixes what failure means at this layer. A failed Wolfram guardrail localizes an arithmetic or algebraic defect in one node's registered equation: the repair is editorial (correct the registration against the source) or substantive (the source itself errs), and the obligations ledger records which. A failed Isabelle discharge, by contrast, indicts the chain: a type mismatch or unprovable dependency means the proof-order proposal of Section~\\ref{sec:chain} is wrong as stated, and the refinement pass must re-curate. Keeping these failure modes separate is what the stub architecture buys: every companion enters the pipeline with its failure semantics declared in advance, which is the practical meaning of being peer-reviewable by machine.

\section{Refinement worksheet}
\label{sec:worksheet}

The concept-anchored backbone converts into an equation-level formalization through a bounded, node-by-node worksheet. For each node the worksheet item below states the concrete refinement act; completing all seven closes the spine's first formalization pass.

\begin{enumerate}
\item \textbf{ID2237} (\texttt{Entrainment\_and\_DAAN\_ID2237\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9492} (\texttt{Entrainment\_and\_DAAN\_ID9492\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID0483} (\texttt{Entrainment\_and\_DAAN\_ID0483\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9491} (\texttt{Entrainment\_and\_DAAN\_ID9491\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9493} (\texttt{Entrainment\_and\_DAAN\_ID9493\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9494} (\texttt{Entrainment\_and\_DAAN\_ID9494\_threshold}): state the axiom with its quantifiers explicit; attach the empirical anchor or upstream derivation candidate; declare the tolerance under which data could falsify it.
\item \textbf{ID0471} (\texttt{Entrainment\_and\_DAAN\_ID0471\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\end{enumerate}

The worksheet's order matters: definitional items unblock derived ones, and a failure at any item halts propagation rather than silently weakening downstream claims. Completed items should update the obligations CSV in place, so that the spine's public ledger always reflects its true refinement state---the same live-ledger discipline the core series applies to its guardrails.

\section{Demarcation and refinement targets}
\label{sec:demarc}

As throughout the program, the demarcation line is drawn explicitly. The established layer comprises the standard mathematics and physics that the chain's nodes quote---definitions, identities, and independently citable results---together with whatever the computational guardrails certify. The framework layer comprises the source manuscript's interpretive claims and the spine's structural assertion that its nodes form the stated dependency chain. Programmability is an engineering claim with control-theoretic content; reachability and bandwidth either meet the stated envelopes on built analogues or the control architecture is revised.

Refinement targets, in pipeline order: (i) replace the concept-anchored node selection with an equation-level crosswalk against the source manuscript; (ii) promote each \texttt{...\_identity} guardrail to a content-bearing check; (iii) discharge the typed obligations in the Isabelle focus theory against the program's shared vocabulary; and (iv) record any node whose refinement fails, since a failed node localizes exactly where the source manuscript and the canonical registry disagree---the information a refinement pass exists to produce.

\section{Conclusion}
\label{sec:conc}

The DAANSsphere axis development gives the enclosure its handles: an axis to address, a frame to orient, a boundary to program. Its refinement targets are the standard control-theory trio---reachability, bandwidth, certificates---applied to standing-wave manifolds. With the controls typed, the corpus's experimental program acquires what every laboratory needs and few unification frameworks supply: knobs.

\begin{thebibliography}{9}

\bibitem{registry} Trawin, D. A., \emph{TZPID Canonical Equation Master Registry, Dictionary, and Encyclopedia}, TZPIDProof archive (2026). Registry identifiers as cited in text.

\bibitem{spine} Trawin, D. A., \emph{TZPID Zenodo Individual Spines: Entrainment and DAANSsphere axis}, TZPIDProof archive, \texttt{zenodo\_individual\_spines/} (2026).

\bibitem{manuscript} Trawin, D. A., \emph{Entrainment and DAANSsphere axis}, Zenodo manuscript (2026).

\bibitem{core} Trawin, D. A., TZPID Gold Spine Series, Papers I--VIII (2026).

\bibitem{einstein} Trawin, D. A., \emph{The Einstein Focus}, TZPID Gold Spine Series, Paper V-A (2026).

\bibitem{index} Trawin, D. A., \emph{TZPID Zenodo Paper Gold Spines} (aggregate), \texttt{TZPID\_ZENODO\_SPINES.md}, TZPIDProof archive (2026).

\end{thebibliography}

\end{document}
