\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathptmx}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,filecolor=black,menucolor=black,anchorcolor=black,pdfauthor={Daniel Alexander Trawin},pdftitle={The Delta Function in the Bell Curve: Localized Wideband Injection},pdfsubject={TZPID Companion Spine Series, Paper C9},pdfkeywords={TZPID, Delta function in the bell curve}]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\title{The Delta Function in the Bell Curve: Localized Wideband Injection\\[0.6em]
\large TZPID Companion Spine Series, Paper C9 of XXVII\\
\normalsize Super-narrow Gaussians as frequency-injection mechanisms}
\author{Daniel Alexander Trawin\\
\small ORCID: \href{https://orcid.org/0009-0001-4630-3715}{0009-0001-4630-3715}\\
\small \href{mailto:danielalexandertrawin@gmail.com}{danielalexandertrawin@gmail.com}}
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
This companion consolidates the program's signal-theoretic kernel: whether a super-narrow Gaussian, approaching a Dirac delta, can serve as a localized mechanism for wideband frequency injection and depth-encoded control.
The source manuscript's stated thesis: ``This manuscript consolidates a long-form technical discussion into a publication-ready structure centered on one question: whether a super-narrow Gaussian (approaching a Dirac delta) can be used as a localized mechanism for wideband frequency injection and depth-encoded control. The treatment links five layers: (i) delta-as-limit mathematics, (ii) Fourier duality and uncertainty, (iii) resonant excitation in a quantu\,\ldots'' The paper organizes this thesis as a TZPID gold spine: a curated seven-node registry chain (ID9622, ID9711, ID2684, ID6170, ID3347, ID3344, ID6278) with typed proof-obligation roles, dictionary and encyclopedia anchors for every node, a declared dependency order, and stubs in the program's Isabelle/Wolfram verification pipeline. Within the arc this paper supplies the injection primitive that the corpus's drive protocols---cymatic, entrainment, and cavity---presuppose.
\end{abstract}

\section{Introduction}
\label{sec:intro}

Every drive protocol in this corpus eventually needs the same primitive: a way to deposit energy at a point while addressing a band. The delta-in-the-bell-curve treatment is the program's systematic study of that primitive. Its organizing question is precise: can a super-narrow Gaussian $G(x) = A\exp(-x^2/2\sigma^2)$, in the limit $\sigma \to 0$ approaching a Dirac delta, be used as a localized mechanism for wideband frequency injection and depth-encoded control?

The treatment links five layers, and the linkage is the content. The delta-as-limit mathematics fixes what survives the narrowing limit and what diverges. Fourier duality and the uncertainty relation then convert spatial narrowness into spectral breadth---the narrower the bell, the wider the injected band, with the product bounded below. Resonant excitation theory determines which of the injected band's components a quantum or cavity system actually accepts: the enclosure's ladder (Papers I--II) acts as the filter on the delta's broadcast. The remaining layers couple the surviving components to depth---how far into a layered or nested system the injection reaches---and to control, the encoding of addressable structure in the injection's shape.

The spine below anchors the five layers to the registry. Its refinement direction is the corpus's most laboratory-ready: bench realizations of narrow-pulse injection into spherical cavities, with the accepted spectrum compared against the enclosure ladder.

\section{The concept-anchored spine methodology}
\label{sec:method}

The companion series applies a uniform method, stated here so that the paper is self-contained. The source manuscript was published with its mathematics rendered as text rather than as machine-readable LaTeX, so its spine is \emph{concept-anchored}: the thesis is taken from the manuscript's abstract, and the spine nodes are the canonical-registry entries most strongly matched to the manuscript's themes, selected by weighted term overlap with foundational nodes ranked first. Each node carries its registry equation, its dictionary definition, its encyclopedia interpretation, and a declared proof-obligation role (Core\_Definition, Core\_Axiom, or Derived\_Theorem\_Obligation). The resulting chain is a starting backbone for refinement---a typed scaffold onto which an exact, equation-by-equation crosswalk with the source manuscript can be progressively attached---rather than a claim of completed formalization.

Three properties make the backbone useful even before refinement completes. First, \emph{addressability}: every claim in the companion paper resolves to a registry identifier whose equation, definition, and verification status are independently inspectable, so disagreement can be localized to a node rather than to the paper as a whole. Second, \emph{pipeline coupling}: each spine is paired with an Isabelle focus-theory stub and a Wolfram check stub, so that as nodes are refined their obligations enter the same machine-checked pipeline that certifies the core series' guardrails. Third, \emph{role discipline}: the obligation roles separate what the spine defines from what it asserts and what it must prove, which keeps the demarcation section of every companion paper honest by construction.

The dependency chain should accordingly be read as a proof-order proposal: upstream nodes supply the vocabulary and axioms that downstream nodes consume, and the refinement pass is free to reorder where the source manuscript's own logic demands it. Where a node's registry equation arrives with rendering artifacts inherited from the source extraction (a known cost of text-rendered mathematics), the equation is quoted as carried by the registry, with the dictionary and encyclopedia entries supplying the authoritative reading.

\section{The registry chain}
\label{sec:chain}

The curated chain, in proof order, is
\begin{equation*}
\begin{gathered}
\text{ID9622} \to \text{ID9711} \to \text{ID2684} \to \text{ID6170} \\
\to \text{ID3347} \to \text{ID3344} \to \text{ID6278}.
\end{gathered}
\end{equation*}
We take the nodes in order; each subsection quotes the registry equation as carried by the canonical master, then gives the dictionary definition and the encyclopedia's interpretive reading.

\subsection{ID9622: Relation: Gamma\_dec(Omega) (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}Gamma\_\{\textbackslash{}text\{dec\}\}(\textbackslash{}Omega)}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: Gamma\_dec(Omega) --- Gamma\_dec(Omega)\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: Gamma\_dec(Omega) is a symbolic expression, written Gamma\_dec(Omega). It introduces a symbol or relation used elsewhere in the framework. It is built from Omega. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Delta\_function\_in\_th\_ID9622\_structure}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID9711: Trawin Zero Point as Creative Singularity (ToE Part II): Psi(x,t) (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}Psi(\textbackslash{}mathbf\{x\},t) = \textbackslash{}Psi\_\{\textbackslash{}mathrm\{reg\}\}(\textbackslash{}mathbf\{x\},t) + \textbackslash{}Psi\_\{\textbackslash{}mathrm\{sing\}\}(\textbackslash{}mathbf\{x\},t),}}\par\medskip
\noindent\textit{Dictionary definition.} We model the TZP as a localized defect in the field configuration \textbackslash{}( (x,t)\textbackslash{}), supported on a two-dimensional surface (or curve in lower-dimensional projections).\par\medskip
\noindent\textit{Encyclopedia reading.} Trawin Zero Point as Creative Singularity (ToE Part II): Psi(x,t) is an algebraic definition, written Psi(x,t) = Psi\_reg(x,t) + Psi\_sing(x,t). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from x, defining Psi(x,t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Delta\_function\_in\_th\_ID9711\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID2684: Delta Function in the Bell Curve (2) (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}phi\_x(x\_2,t) \textbackslash{}propto \textbackslash{}Psi(x\_1=x,x\_2,t). \textbackslash{}boxed\{\textbackslash{},\textbackslash{}phi\_x(x\_2,t)\textbackslash{};\textbackslash{}propto\textbackslash{}; e\textasciicircum{}\{-((x+x\_2)/2)\textasciicircum{}2/(2\textbackslash{}sigma\_R\textasciicircum{}2)\}\textbackslash{};|x-x\_2 |\textasciicircum{}\{|\textbackslash{}ell|\} e\textasciicircum{}\{-(x-x\_2)\textasciicircum{}2/(2\textbackslash{}sigma\_r(t)\textasciicircum{}2)\} e\textasciicircum{}\{i\textbackslash{}ell\textbackslash{}theta(x-x\_2)\}\textbackslash{}; \textbackslash{}int e\textasciicircum{}\{\textbackslash{}tfrac\{i\}\{\textbackslash{}hbar\}p(x-x\_2+x\_0)\}\textbackslash{}tilde A(p)\textbackslash{},dp \textbackslash{},\}}}\par\medskip
\noindent\textit{Dictionary definition.} Delta Function in the Bell Curve (2) --- phi\_x(x\_2,t) prop-to Psi(x\_1=x,x\_2,t). phi\_x(x\_2,t) prop-to e\textasciicircum{}-((x+x\_2)/2)\textasciicircum{}2/(2sigma\_R\textasciicircum{}2) |x-x\_2|\textasciicircum{}|l| e\textasciicircum{}-(x-x\_2)\textasciicircum{}2/(2sigma\_r(t)\textasciicircum{}2) e\textasciicircum{}iltheta(x-x\_2) integral e\textasciicircum{}tfracip(x-x\_2+x\_0)tilde A(p [ID2684]\par\medskip
\noindent\textit{Encyclopedia reading.} phi\_x(x\_2,t) propto Psi(x\_1=x,x\_2,t). boxed\{\textbackslash{},phi\_x(x\_2,t)\textbackslash{};propto\textbackslash{}; e\textasciicircum{}\{-((x+x\_2)/2)\textasciicircum{}2/(2sigma\_R\textasciicircum{}2)\}\textbackslash{};|x-x\_2|\textasciicircum{}\{|ell|\} e\textasciicircum{}\{-(x-x\_2)\textasciicircum{}2/(2sigma\_r(t)\textasciicircum{}2)\} e\textasciicircum{}\{ielltheta(x-x\_2)\}\textbackslash{}; int e\textasciicircum{}\{tfrac\{i\}\{hbar\}p(x-x\_2+x\_0)\}tilde A(p)\textbackslash{},dp \textbackslash{},\}
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Delta\_function\_in\_th\_ID2684\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This node carries proof debt by declaration---Derived\_Theorem\_Obligation---and is therefore where the refinement pass should concentrate first: a discharged derivation here strengthens every downstream node simultaneously.

\subsection{ID6170: Starting Point --- the Gaussian Bell Curve: G(x) (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{G(x) = A e\textasciicircum{}\{-\textbackslash{}frac\{x\textasciicircum{}2\}\{2\textbackslash{}sigma\textasciicircum{}2\}\}}}\par\medskip
\noindent\textit{Dictionary definition.} Starting Point --- the Gaussian Bell Curve: G(x) --- G(x) = A e\textasciicircum{}-(x\textasciicircum{}2)/(2sigma\textasciicircum{}2)\par\medskip
\noindent\textit{Encyclopedia reading.} Starting Point --- the Gaussian Bell Curve: G(x) is an exponential / gaussian profile, written G(x) = A e\textasciicircum{}-(x\textasciicircum{}2)/(2sigma\textasciicircum{}2). It describes an exponential or Gaussian profile characterizing localized or decaying behaviour. It is built from sigma, A, x, defining G(x). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Delta\_function\_in\_th\_ID6170\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\subsection{ID3347: Quantumtopoholonavsystem Mode Frequency Expectation Value (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}begin\{equation\} g = e \textbackslash{}sqrt\{ \textbackslash{}frac\{ \textbackslash{}omega\}\{2 \textbackslash{}epsilon\_0 V\_\{ \textbackslash{}text\{mode\}\}\}\} \textbackslash{}langle d \textbackslash{}rangle \textbackslash{}end\{equation\}}}\par\medskip
\noindent\textit{Dictionary definition.} Quantumtopoholonavsystem Mode Frequency Expectation Value --- g = e sqrt frac omega2 epsilon\_0 V\_ mode < d >\par\medskip
\noindent\textit{Encyclopedia reading.} The entry preserves the equation exactly as extracted from `00\_EngineLemma-MakerPrismQuantumTopoHoloNavSystem\_formatted2.tex` for registry alignment and later derivation.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Delta\_function\_in\_th\_ID3347\_identity}.
\par\medskip\noindent\textit{Obligation reading.} A derived obligation: the spine claims this follows from what precedes it. Until the formal derivation is supplied, the computational guardrail polices at least the node's internal consistency.

\subsection{ID3344: Chsh Action Laplacian Operator (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}begin\{equation\} S\_\{ \textbackslash{}text\{CHSH\}\}(t, \textbackslash{}Omega) = 2 \textbackslash{}sqrt\{2\} \textbackslash{}exp[- \textbackslash{}Gamma\_\{ \textbackslash{}text\{dec\}\}( \textbackslash{}Omega) t] | \textbackslash{}cos[ \textbackslash{}Delta \textbackslash{}Phi( \textbackslash{}Omega, t)]| \textbackslash{}end\{equation\}}}\par\medskip
\noindent\textit{Dictionary definition.} Chsh Action Laplacian Operator --- S\_ CHSH(t, Omega) = 2 sqrt(2) exp[- Gamma\_ dec( Omega) t] | cos[ Delta Phi( Omega, t)]|\par\medskip
\noindent\textit{Encyclopedia reading.} The entry preserves the equation exactly as extracted from `00\_EngineLemma-MakerPrismQuantumTopoHoloNavSystem\_formatted2.tex` for registry alignment and later derivation.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Delta\_function\_in\_th\_ID3344\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This node carries proof debt by declaration---Derived\_Theorem\_Obligation---and is therefore where the refinement pass should concentrate first: a discharged derivation here strengthens every downstream node simultaneously.

\subsection{ID6278: Physical Interpretation (Short \& Focused): R \textasciitilde{}= 0 (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{r\textbackslash{}!\textbackslash{}approx\textbackslash{}!0}}\par\medskip
\noindent\textit{Dictionary definition.} Physical interpretation (short \& focused) - When the ring contracts (during inward breathing) the relative amplitude near \textbackslash{}(r\textbackslash{}!\par\medskip
\noindent\textit{Encyclopedia reading.} Physical Interpretation (Short \& Focused): R \textasciitilde{}= 0 is a scaling / order-of-magnitude relation, written r \textasciitilde{}= 0. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{Delta\_function\_in\_th\_ID6278\_structure}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\section{Dependency structure and obligations}
\label{sec:dep}

Table~\ref{tab:obligations} summarizes the spine's obligation ledger. The chain's proof order runs from the definitional nodes (vocabulary first) through the derived obligations to the spine's closure; the refinement pass may interleave additional registry nodes where the source manuscript's own derivations require them, in which case the table grows monotonically---existing rows are never weakened, only joined.

\begin{table}[ht]
\centering
\small
\caption{Obligation ledger for the Delta function in the bell curve spine.}
\label{tab:obligations}
\begin{tabular}{llp{6.2cm}}
\toprule
ID & Obligation role & Wolfram check \\
\midrule
ID9622 & Core\_Definition & \texttt{Delta\_function\_in\_th\_ID9622\_structure} \\
ID9711 & Core\_Definition & \texttt{Delta\_function\_in\_th\_ID9711\_identity} \\
ID2684 & Derived\_Theorem\_Obligation & \texttt{Delta\_function\_in\_th\_ID2684\_identity} \\
ID6170 & Derived\_Theorem\_Obligation & \texttt{Delta\_function\_in\_th\_ID6170\_identity} \\
ID3347 & Derived\_Theorem\_Obligation & \texttt{Delta\_function\_in\_th\_ID3347\_identity} \\
ID3344 & Derived\_Theorem\_Obligation & \texttt{Delta\_function\_in\_th\_ID3344\_identity} \\
ID6278 & Derived\_Theorem\_Obligation & \texttt{Delta\_function\_in\_th\_ID6278\_structure} \\
\bottomrule
\end{tabular}
\end{table}

\section{Crosswalk to the core series and companion corpus}
\label{sec:crosswalk}

Because all spines draw on one canonical registry, node sharing is measurable and meaningful: a shared identifier means two papers consume literally the same typed object, so verification work transfers between them without translation. Of this spine's seven nodes, 0 appear in core-series spines and 0 recur elsewhere in the companion corpus. Table~\ref{tab:crosswalk} records the census.

\begin{table}[ht]
\centering
\small
\caption{Node-sharing census for this spine.}
\label{tab:crosswalk}
\begin{tabular}{lp{4.4cm}p{6.6cm}}
\toprule
ID & Core-series appearances & Companion-corpus appearances \\
\midrule
ID9622 & --- & --- \\
ID9711 & --- & --- \\
ID2684 & --- & --- \\
ID6170 & --- & --- \\
ID3347 & --- & --- \\
ID3344 & --- & --- \\
ID6278 & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

Two readings follow. Nodes shared with the core series are this spine's strongest members: their guardrails are already certified in the core pipeline, and the present paper inherits that status. Nodes unique to this spine are its distinctive contribution---and its refinement priority, since no other paper will discharge them. Nodes recurring across companions mark the corpus's internal seams: the same object consumed by several manuscripts, whose refinements must agree by the duplicate discipline documented in the Einstein Focus companion.

\section{Position in the TZPID arc}
\label{sec:arc}

This companion is the transmitter to the corpus's receivers. The Gaussian seam operator of FlipTwistRamp (C12) is this paper's primitive wearing a phase inversion; the beat windows and bridge ratio of core Paper II are the band structure the injection must address; and the programmable hyperspherical pathway (C15) uses depth-encoded injection as its control channel. The Well of companion C7 is the same Gaussian read as potential rather than pulse---one function, two roles, which the registry records deliberately.

\section{Verification pathway}
\label{sec:verify}

The spine enters the program's two-engine verification pipeline. The Isabelle focus theory \texttt{TZPID\_Spine\_Delta\_function\_in\_the\_bell\_curve.thy} types the seven obligations over the registry's declared vocabulary, in the dependency order of Section~\ref{sec:chain}; the Wolfram check stub \texttt{Delta\_function\_in\_the\_bell\_curve\_checks.wl} carries the per-node computational guardrails listed in Table~\ref{tab:obligations}. As with the core series, the division of labor is deliberate: the theorem prover certifies structure (types, roles, dependency soundness), while the computational engine certifies arithmetic and algebraic identities node by node. A check name of the form \texttt{...\_identity} denotes a per-node identity guardrail generated from the registry equation; refined checks replace these as the equation-level crosswalk matures.

Because the companion spines share the registry with the core series, verification is cumulative: any node here that also appears in a core spine (the chain tables record several) inherits the core guardrail's status, and any refinement proved here propagates back. The companion series thus functions as the proof pipeline's breadth dimension---161 distinct registry nodes across the 27 companions---complementing the core series' depth.

The pipeline's two-engine division also fixes what failure means at this layer. A failed Wolfram guardrail localizes an arithmetic or algebraic defect in one node's registered equation: the repair is editorial (correct the registration against the source) or substantive (the source itself errs), and the obligations ledger records which. A failed Isabelle discharge, by contrast, indicts the chain: a type mismatch or unprovable dependency means the proof-order proposal of Section~\\ref{sec:chain} is wrong as stated, and the refinement pass must re-curate. Keeping these failure modes separate is what the stub architecture buys: every companion enters the pipeline with its failure semantics declared in advance, which is the practical meaning of being peer-reviewable by machine.

\section{Refinement worksheet}
\label{sec:worksheet}

The concept-anchored backbone converts into an equation-level formalization through a bounded, node-by-node worksheet. For each node the worksheet item below states the concrete refinement act; completing all seven closes the spine's first formalization pass.

\begin{enumerate}
\item \textbf{ID9622} (\texttt{Delta\_function\_in\_th\_ID9622\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9711} (\texttt{Delta\_function\_in\_th\_ID9711\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID2684} (\texttt{Delta\_function\_in\_th\_ID2684\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID6170} (\texttt{Delta\_function\_in\_th\_ID6170\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID3347} (\texttt{Delta\_function\_in\_th\_ID3347\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID3344} (\texttt{Delta\_function\_in\_th\_ID3344\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID6278} (\texttt{Delta\_function\_in\_th\_ID6278\_structure}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\end{enumerate}

The worksheet's order matters: definitional items unblock derived ones, and a failure at any item halts propagation rather than silently weakening downstream claims. Completed items should update the obligations CSV in place, so that the spine's public ledger always reflects its true refinement state---the same live-ledger discipline the core series applies to its guardrails.

\section{Demarcation and refinement targets}
\label{sec:demarc}

As throughout the program, the demarcation line is drawn explicitly. The established layer comprises the standard mathematics and physics that the chain's nodes quote---definitions, identities, and independently citable results---together with whatever the computational guardrails certify. The framework layer comprises the source manuscript's interpretive claims and the spine's structural assertion that its nodes form the stated dependency chain. The mathematics of the narrowing limit and Fourier duality is established; the framework's surplus is depth-encoded control---that injection shape addresses nested structure---which bench tests on layered cavities can confirm or strike.

Refinement targets, in pipeline order: (i) replace the concept-anchored node selection with an equation-level crosswalk against the source manuscript; (ii) promote each \texttt{...\_identity} guardrail to a content-bearing check; (iii) discharge the typed obligations in the Isabelle focus theory against the program's shared vocabulary; and (iv) record any node whose refinement fails, since a failed node localizes exactly where the source manuscript and the canonical registry disagree---the information a refinement pass exists to produce.

\section{Conclusion}
\label{sec:conc}

The delta-in-the-bell-curve study gives the corpus its injection primitive with its costs stated: narrowness buys bandwidth at the price suspended by the uncertainty bound, and the enclosure's ladder decides what is accepted. Refinement is a bench protocol away. As the first wave-group companion, it opens the corpus's signal-theoretic spine, which the kernel, ratio, seam, and address papers (C10--C13) extend.

\begin{thebibliography}{9}

\bibitem{registry} Trawin, D. A., \emph{TZPID Canonical Equation Master Registry, Dictionary, and Encyclopedia}, TZPIDProof archive (2026). Registry identifiers as cited in text.

\bibitem{spine} Trawin, D. A., \emph{TZPID Zenodo Individual Spines: Delta function in the bell curve}, TZPIDProof archive, \texttt{zenodo\_individual\_spines/} (2026).

\bibitem{manuscript} Trawin, D. A., \emph{Delta function in the bell curve}, Zenodo manuscript (2026).

\bibitem{core} Trawin, D. A., TZPID Gold Spine Series, Papers I--VIII (2026).

\bibitem{einstein} Trawin, D. A., \emph{The Einstein Focus}, TZPID Gold Spine Series, Paper V-A (2026).

\bibitem{index} Trawin, D. A., \emph{TZPID Zenodo Paper Gold Spines} (aggregate), \texttt{TZPID\_ZENODO\_SPINES.md}, TZPIDProof archive (2026).

\end{thebibliography}

\end{document}
