\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathptmx}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,filecolor=black,menucolor=black,anchorcolor=black,pdfauthor={Daniel Alexander Trawin},pdftitle={The Information Theory of Trawin Zero Points},pdfsubject={TZPID Companion Spine Series, Paper C25},pdfkeywords={TZPID, TZP Information Theory.pfd}]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\title{The Information Theory of Trawin Zero Points\\[0.6em]
\large TZPID Companion Spine Series, Paper C25 of XXVII\\
\normalsize Informational consequences of the gravitational emergence framework}
\author{Daniel Alexander Trawin\\
\small ORCID: \href{https://orcid.org/0009-0001-4630-3715}{0009-0001-4630-3715}\\
\small \href{mailto:danielalexandertrawin@gmail.com}{danielalexandertrawin@gmail.com}}
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
This companion develops the information-theoretic implications of Trawin Zero Points, building on the gravitational emergence framework and engaging contemporary observational claims.
The source manuscript's stated thesis: ``We present the information-theoretic implications of Trawin Zero Points (TZP), building upon the gravitational emergence framework established in our previous work. Recent MIT observations by Fletcher et al.'' The paper organizes this thesis as a TZPID gold spine: a curated seven-node registry chain (ID8982, ID0463, ID9525, ID4218, ID4227, ID9523, ID4226) with typed proof-obligation roles, dictionary and encyclopedia anchors for every node, a declared dependency order, and stubs in the program's Isabelle/Wolfram verification pipeline. Within the arc this paper is the bit-side ledger: what the program's geometry implies for information storage, flow, and limits.
\end{abstract}

\section{Introduction}
\label{sec:intro}

A program that derives curvature from accumulated information (companion C22) owes a treatment of information in its own right, and this companion supplies it: the information-theoretic implications of Trawin Zero Points, built directly on the gravitational emergence framework (C21) and engaged with contemporary observational claims from the experimental literature.

The anchor's informational role follows from its geometric one. A degenerate metric point is, information-theoretically, a capacity anomaly: the usual volume-scaling and area-scaling bounds on information storage (Bekenstein-type limits) presuppose non-degenerate geometry, and the TZP's $\det g = 0$ locus sits outside their hypotheses. The framework develops what replaces them---how much record the anchor's neighborhood can hold, how information flows across loops about the anchor (the causal loop invariant ID0011 and winding counter ID0020 acting as the conserved informational currencies), and how the registry's holographic projection entries (ID0104, ID8796) discipline the bulk-boundary ledger that every enclosure claim implies.

Read across the corpus, this companion is the converse of C22: there, information accumulating in time became curvature; here, curvature's anomalous point becomes a statement about information. Together they close the loop that the core arc's second-derivative constructions (Paper VIII's $h_{\mu\nu} = A\psi^*\partial_\mu\partial_\nu\psi$, Paper VI's entropy-fold tensor) hint at: geometry and information as two readings of one record. The spine below anchors the chain; refinement targets are the typed capacity bound at the anchor and the formal statement of the loop currencies' conservation.

\section{The concept-anchored spine methodology}
\label{sec:method}

The companion series applies a uniform method, stated here so that the paper is self-contained. The source manuscript was published with its mathematics rendered as text rather than as machine-readable LaTeX, so its spine is \emph{concept-anchored}: the thesis is taken from the manuscript's abstract, and the spine nodes are the canonical-registry entries most strongly matched to the manuscript's themes, selected by weighted term overlap with foundational nodes ranked first. Each node carries its registry equation, its dictionary definition, its encyclopedia interpretation, and a declared proof-obligation role (Core\_Definition, Core\_Axiom, or Derived\_Theorem\_Obligation). The resulting chain is a starting backbone for refinement---a typed scaffold onto which an exact, equation-by-equation crosswalk with the source manuscript can be progressively attached---rather than a claim of completed formalization.

Three properties make the backbone useful even before refinement completes. First, \emph{addressability}: every claim in the companion paper resolves to a registry identifier whose equation, definition, and verification status are independently inspectable, so disagreement can be localized to a node rather than to the paper as a whole. Second, \emph{pipeline coupling}: each spine is paired with an Isabelle focus-theory stub and a Wolfram check stub, so that as nodes are refined their obligations enter the same machine-checked pipeline that certifies the core series' guardrails. Third, \emph{role discipline}: the obligation roles separate what the spine defines from what it asserts and what it must prove, which keeps the demarcation section of every companion paper honest by construction.

The dependency chain should accordingly be read as a proof-order proposal: upstream nodes supply the vocabulary and axioms that downstream nodes consume, and the refinement pass is free to reorder where the source manuscript's own logic demands it. Where a node's registry equation arrives with rendering artifacts inherited from the source extraction (a known cost of text-rendered mathematics), the equation is quoted as carried by the registry, with the dictionary and encyclopedia entries supplying the authoritative reading.

\section{The registry chain}
\label{sec:chain}

The curated chain, in proof order, is
\begin{equation*}
\begin{gathered}
\text{ID8982} \to \text{ID0463} \to \text{ID9525} \to \text{ID4218} \\
\to \text{ID4227} \to \text{ID9523} \to \text{ID4226}.
\end{gathered}
\end{equation*}
We take the nodes in order; each subsection quotes the registry equation as carried by the canonical master, then gives the dictionary definition and the encyclopedia's interpretive reading.

\subsection{ID8982: Definition of S(M) S(total) (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{S(M) S(total) ==> Res(TZP}}\par\medskip
\noindent\textit{Dictionary definition.} Neural Resonance: This carrier frequency overlaps with critical exponents (tau \textasciitilde{}= 3/2) found in neural information processing[cite: 9, 38].\par\medskip
\noindent\textit{Encyclopedia reading.} Definition of S(M) S(total) is an algebraic definition, written S(M) S(total) ==> Res(TZP. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R, s, T, Z, P, defining S(M) S(total). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{TZP\_Information\_Theo\_ID8982\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID0463: Bipartition Information Integration (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}begin\{adjustbox\}\{max width=\textbackslash{}linewidth,center\} \$\textbackslash{}displaystyle \textbackslash{}Phi\_\{\textbackslash{}mathrm\{TZP\}\}=\textbackslash{}min\_\{\textbackslash{}mathcal\{P\}\}\textbackslash{}m athcal\{I\}(\textbackslash{}mathcal\{P\}) \$ \textbackslash{}end\{adjustbox\}}}\par\medskip
\noindent\textit{Dictionary definition.} ID 463 defines the integrated information measure Phi within TZP mediated systems.\par\medskip
\noindent\textit{Encyclopedia reading.} T: Aggregate Relation is localized within the manifold and metric dynamics arc of the directory. R: Geometric Constraint preserves the operative relation that causal order collapse logic requires. A: Closure Relation fixes the admissible closure condition for the entry. W: CAUSAL ORDER COLLAPSE LOGIC is rendered as a reusable operator-level statement. I: The informational content of causal order collapse logic is retained rather than flattened. N: CAUSAL ORDER COLLAPSE LOGIC closes as a distinct normalized TRAWIN object. Interpretive role: This entry specifies the structure within the registry.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{TZP\_Information\_Theo\_ID0463\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID9525: Relation: Lambda -> 1 Pm 0.5 (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}Lambda \textbackslash{}to 1 \textbackslash{}pm 0.5}}\par\medskip
\noindent\textit{Dictionary definition.} Quantum\_ Gravity\_ natural transformations : id F G\$, we demonstrate that gravitational phenomena emerge from infinite-order phase transitions where \$ \_vac(r) \_n=0\textasciicircum{} (-1)\textasciicircum{}n (n+ 12) K\_n( r-r\_ / )\$.\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: Lambda -> 1 Pm 0.5 is a symbolic expression, written Lambda -> 1 pm 0.5. It introduces a symbol or relation used elsewhere in the framework. It is built from Lambda. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{TZP\_Information\_Theo\_ID9525\_structure}.
\par\medskip\noindent\textit{Obligation reading.} A definitional node: its function is to make later statements well-formed. The guardrail attached to it is correspondingly structural---an identity or well-formedness check rather than a physical claim.

\subsection{ID4218: Critical Quantum Magnetic Flux Relation (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\$\textbackslash{}Phi\_\{\textbackslash{}text\{critical\}\} = \textbackslash{}sqrt\{\textbackslash{}hbar c\textasciicircum{}3/Ge\textasciicircum{}2\} \textbackslash{}times \textbackslash{}alpha\$}}\par\medskip
\noindent\textit{Dictionary definition.} Critical Quantum Magnetic Flux Relation --- Phi\_critical = sqrt( c\textasciicircum{}3/Ge\textasciicircum{}2) x alpha\par\medskip
\noindent\textit{Encyclopedia reading.} The entry preserves the equation exactly as extracted from `00AllEditanalysis\_all\_edit\_focus\_11\_22outputall\_edit\_equation\_arc\_compact.csv` for registry alignment and later derivation.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{TZP\_Information\_Theo\_ID4218\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID4227: Density (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\$\textbackslash{}rho\_\{\textbackslash{}text\{vac\}\}(r) \textbackslash{}sim \textbackslash{}sum\_\{n=0\}\textasciicircum{}\{\textbackslash{}infty\} (-1)\textasciicircum{}n \textbackslash{}Gamma(n+\textbackslash{}tfrac\{1\}\{2\}) K\_n(|r-r\_\{\textbackslash{}TZP\}|/\textbackslash{}xi)\$}}\par\medskip
\noindent\textit{Dictionary definition.} Density --- rho\_vac(r) \textasciitilde{} sum\_n=0\textasciicircum{}infinity (-1)\textasciicircum{}n Gamma(n+tfrac12) K\_n(|r-r\_TZP|/xi)\par\medskip
\noindent\textit{Encyclopedia reading.} The entry preserves the equation exactly as extracted from `00AllEditanalysis\_all\_edit\_focus\_11\_22outputall\_edit\_equation\_arc\_compact\_curated.csv` for registry alignment and later derivation.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{TZP\_Information\_Theo\_ID4227\_identity}.
\par\medskip\noindent\textit{Obligation reading.} A derived obligation: the spine claims this follows from what precedes it. Until the formal derivation is supplied, the computational guardrail polices at least the node's internal consistency.

\subsection{ID9523: Relation: Delta G/G \textasciitilde{}= 10\textasciicircum{}-10 (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}Delta G/G \textbackslash{}approx 10\textasciicircum{}\{-10\}}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: Delta G/G \textasciitilde{}= 10\textasciicircum{}-10 --- Delta G/G \textasciitilde{}= 10\textasciicircum{}-10\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: Delta G/G \textasciitilde{}= 10\textasciicircum{}-10 is a scaling / order-of-magnitude relation, written Delta G/G \textasciitilde{}= 10\textasciicircum{}-10. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from Delta, G. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{TZP\_Information\_Theo\_ID9523\_structure}.
\par\medskip\noindent\textit{Obligation reading.} This node carries proof debt by declaration---Derived\_Theorem\_Obligation---and is therefore where the refinement pass should concentrate first: a discharged derivation here strengthens every downstream node simultaneously.

\subsection{ID4226: Quantum Gravity Relation (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\$\textbackslash{}mathcal\{F\}: \textbackslash{}mathbf\{Quantum\}\_\textbackslash{}infty \textbackslash{}to \textbackslash{}mathbf\{Gravity\}\_\textbackslash{}infty\$}}\par\medskip
\noindent\textit{Dictionary definition.} Quantum Gravity Relation --- F: Quantum\_infinity -> Gravity\_infinity\par\medskip
\noindent\textit{Encyclopedia reading.} The entry preserves the equation exactly as extracted from `00AllEditanalysis\_all\_edit\_focus\_11\_22outputall\_edit\_equation\_arc\_compact\_curated.csv` for registry alignment and later derivation.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{TZP\_Information\_Theo\_ID4226\_structure}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\section{Dependency structure and obligations}
\label{sec:dep}

Table~\ref{tab:obligations} summarizes the spine's obligation ledger. The chain's proof order runs from the definitional nodes (vocabulary first) through the derived obligations to the spine's closure; the refinement pass may interleave additional registry nodes where the source manuscript's own derivations require them, in which case the table grows monotonically---existing rows are never weakened, only joined.

\begin{table}[ht]
\centering
\small
\caption{Obligation ledger for the TZP Information Theory.pfd spine.}
\label{tab:obligations}
\begin{tabular}{llp{6.2cm}}
\toprule
ID & Obligation role & Wolfram check \\
\midrule
ID8982 & Core\_Definition & \texttt{TZP\_Information\_Theo\_ID8982\_identity} \\
ID0463 & Core\_Definition & \texttt{TZP\_Information\_Theo\_ID0463\_identity} \\
ID9525 & Core\_Definition & \texttt{TZP\_Information\_Theo\_ID9525\_structure} \\
ID4218 & Core\_Definition & \texttt{TZP\_Information\_Theo\_ID4218\_identity} \\
ID4227 & Derived\_Theorem\_Obligation & \texttt{TZP\_Information\_Theo\_ID4227\_identity} \\
ID9523 & Derived\_Theorem\_Obligation & \texttt{TZP\_Information\_Theo\_ID9523\_structure} \\
ID4226 & Derived\_Theorem\_Obligation & \texttt{TZP\_Information\_Theo\_ID4226\_structure} \\
\bottomrule
\end{tabular}
\end{table}

\section{Crosswalk to the core series and companion corpus}
\label{sec:crosswalk}

Because all spines draw on one canonical registry, node sharing is measurable and meaningful: a shared identifier means two papers consume literally the same typed object, so verification work transfers between them without translation. Of this spine's seven nodes, 0 appear in core-series spines and 5 recur elsewhere in the companion corpus. Table~\ref{tab:crosswalk} records the census.

\begin{table}[ht]
\centering
\small
\caption{Node-sharing census for this spine.}
\label{tab:crosswalk}
\begin{tabular}{lp{4.4cm}p{6.6cm}}
\toprule
ID & Core-series appearances & Companion-corpus appearances \\
\midrule
ID8982 & --- & --- \\
ID0463 & --- & --- \\
ID9525 & --- & topological unification \\
ID4218 & --- & topological unification \\
ID4227 & --- & Gravitational-Emergence-TPZ-; topological unification; Universal Field Theory Rendered \\
ID9523 & --- & topological unification \\
ID4226 & --- & topological unification; Universal Field Theory Rendered \\
\bottomrule
\end{tabular}
\end{table}

Two readings follow. Nodes shared with the core series are this spine's strongest members: their guardrails are already certified in the core pipeline, and the present paper inherits that status. Nodes unique to this spine are its distinctive contribution---and its refinement priority, since no other paper will discharge them. Nodes recurring across companions mark the corpus's internal seams: the same object consumed by several manuscripts, whose refinements must agree by the duplicate discipline documented in the Einstein Focus companion.

\section{Position in the TZPID arc}
\label{sec:arc}

This companion pairs with C22 as the arc's informational axis: accumulation-to-geometry there, geometry-to-capacity here. It supplies the theoretical frame for C15's structured-emission readout (decodability presupposes a ledger) and underwrites the information sector $\mathcal{L}_{\mathrm{info}}$ that the Einstein Focus layer's Lagrangian inventory declares but the core arc never opened. It is the corpus's account of what, exactly, the enclosure remembers.

\section{Verification pathway}
\label{sec:verify}

The spine enters the program's two-engine verification pipeline. The Isabelle focus theory \texttt{TZPID\_Spine\_TZP\_Information\_Theory\_pfd.thy} types the seven obligations over the registry's declared vocabulary, in the dependency order of Section~\ref{sec:chain}; the Wolfram check stub \texttt{TZP\_Information\_Theory\_pfd\_checks.wl} carries the per-node computational guardrails listed in Table~\ref{tab:obligations}. As with the core series, the division of labor is deliberate: the theorem prover certifies structure (types, roles, dependency soundness), while the computational engine certifies arithmetic and algebraic identities node by node. A check name of the form \texttt{...\_identity} denotes a per-node identity guardrail generated from the registry equation; refined checks replace these as the equation-level crosswalk matures.

Because the companion spines share the registry with the core series, verification is cumulative: any node here that also appears in a core spine (the chain tables record several) inherits the core guardrail's status, and any refinement proved here propagates back. The companion series thus functions as the proof pipeline's breadth dimension---161 distinct registry nodes across the 27 companions---complementing the core series' depth.

The pipeline's two-engine division also fixes what failure means at this layer. A failed Wolfram guardrail localizes an arithmetic or algebraic defect in one node's registered equation: the repair is editorial (correct the registration against the source) or substantive (the source itself errs), and the obligations ledger records which. A failed Isabelle discharge, by contrast, indicts the chain: a type mismatch or unprovable dependency means the proof-order proposal of Section~\\ref{sec:chain} is wrong as stated, and the refinement pass must re-curate. Keeping these failure modes separate is what the stub architecture buys: every companion enters the pipeline with its failure semantics declared in advance, which is the practical meaning of being peer-reviewable by machine.

\section{Refinement worksheet}
\label{sec:worksheet}

The concept-anchored backbone converts into an equation-level formalization through a bounded, node-by-node worksheet. For each node the worksheet item below states the concrete refinement act; completing all seven closes the spine's first formalization pass.

\begin{enumerate}
\item \textbf{ID8982} (\texttt{TZP\_Information\_Theo\_ID8982\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID0463} (\texttt{TZP\_Information\_Theo\_ID0463\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9525} (\texttt{TZP\_Information\_Theo\_ID9525\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID4218} (\texttt{TZP\_Information\_Theo\_ID4218\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID4227} (\texttt{TZP\_Information\_Theo\_ID4227\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID9523} (\texttt{TZP\_Information\_Theo\_ID9523\_structure}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID4226} (\texttt{TZP\_Information\_Theo\_ID4226\_structure}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\end{enumerate}

The worksheet's order matters: definitional items unblock derived ones, and a failure at any item halts propagation rather than silently weakening downstream claims. Completed items should update the obligations CSV in place, so that the spine's public ledger always reflects its true refinement state---the same live-ledger discipline the core series applies to its guardrails.

\section{Demarcation and refinement targets}
\label{sec:demarc}

As throughout the program, the demarcation line is drawn explicitly. The established layer comprises the standard mathematics and physics that the chain's nodes quote---definitions, identities, and independently citable results---together with whatever the computational guardrails certify. The framework layer comprises the source manuscript's interpretive claims and the spine's structural assertion that its nodes form the stated dependency chain. Capacity claims at a degenerate point are theory until typed; the engagement with observational claims from the literature must track those claims' own replication status, which the refinement pass should pin with citations and dates.

Refinement targets, in pipeline order: (i) replace the concept-anchored node selection with an equation-level crosswalk against the source manuscript; (ii) promote each \texttt{...\_identity} guardrail to a content-bearing check; (iii) discharge the typed obligations in the Isabelle focus theory against the program's shared vocabulary; and (iv) record any node whose refinement fails, since a failed node localizes exactly where the source manuscript and the canonical registry disagree---the information a refinement pass exists to produce.

\section{Conclusion}
\label{sec:conc}

The information theory of TZPs writes the program's bit-side ledger: capacity where the usual bounds lapse, loop invariants as conserved currencies, and the bulk-boundary discipline that makes enclosure talk accountable. With C22 it closes the geometry-information loop at the heart of the corpus. Refinement owes the typed bound and the conservation statement---after which the $\mathcal{L}_{\mathrm{info}}$ sector, declared in the program's master Lagrangian since the Einstein gate, finally has contents.

\begin{thebibliography}{9}

\bibitem{registry} Trawin, D. A., \emph{TZPID Canonical Equation Master Registry, Dictionary, and Encyclopedia}, TZPIDProof archive (2026). Registry identifiers as cited in text.

\bibitem{spine} Trawin, D. A., \emph{TZPID Zenodo Individual Spines: TZP Information Theory.pfd}, TZPIDProof archive, \texttt{zenodo\_individual\_spines/} (2026).

\bibitem{manuscript} Trawin, D. A., \emph{TZP Information Theory.pfd}, Zenodo manuscript (2026).

\bibitem{core} Trawin, D. A., TZPID Gold Spine Series, Papers I--VIII (2026).

\bibitem{einstein} Trawin, D. A., \emph{The Einstein Focus}, TZPID Gold Spine Series, Paper V-A (2026).

\bibitem{index} Trawin, D. A., \emph{TZPID Zenodo Paper Gold Spines} (aggregate), \texttt{TZPID\_ZENODO\_SPINES.md}, TZPIDProof archive (2026).

\end{thebibliography}

\end{document}
