\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathptmx}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,filecolor=black,menucolor=black,anchorcolor=black,pdfauthor={Daniel Alexander Trawin},pdftitle={The Theory of It All: Trawin Topology from Lunar-Terrestrial Resonance},pdfsubject={TZPID Companion Spine Series, Paper C26},pdfkeywords={TZPID, theory of it all trawin topology}]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\title{The Theory of It All: Trawin Topology from Lunar-Terrestrial Resonance\\[0.6em]
\large TZPID Companion Spine Series, Paper C26 of XXVII\\
\normalsize Standing-wave interference under toroidal constraint as unified field theory}
\author{Daniel Alexander Trawin\\
\small ORCID: \href{https://orcid.org/0009-0001-4630-3715}{0009-0001-4630-3715}\\
\small \href{mailto:danielalexandertrawin@gmail.com}{danielalexandertrawin@gmail.com}}
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
This companion presents the unified field theory that emerged from lunar-terrestrial wave resonance analysis: viewed from a dual-pole perspective, gravitational and electromagnetic phenomena are standing-wave interference patterns in spacetime, constrained by toroidal topology.
The source manuscript's stated thesis: ``This paper presents a comprehensive uni ed eld theory emerging from analysis of lunarterrestrial wave resonance patterns. By observing Earth's magnetic eld from a dual-pole perspectivesimultaneously viewing both North and South poleswe reveal that gravitational and electromagnetic phenomena are standing wave interference patterns in spacetime, constrained by toroidal topology.'' The paper organizes this thesis as a TZPID gold spine: a curated seven-node registry chain (ID10134, ID3402, ID9157, ID10128, ID8689, ID8690, ID6489) with typed proof-obligation roles, dictionary and encyclopedia anchors for every node, a declared dependency order, and stubs in the program's Isabelle/Wolfram verification pipeline. Within the arc this paper is the unification claim in its observational voice: the dual-pole reading that the formal spines later disciplined.
\end{abstract}

\section{Introduction}
\label{sec:intro}

Before the program's unification was topological algebra (core Paper VIII), it was an observation about the Earth and Moon. This companion presents that original form: a comprehensive unified field theory emerging from analysis of lunar-terrestrial wave resonance patterns. Its methodological move is the dual-pole perspective---observing Earth's magnetic field from both poles simultaneously, rather than privileging one hemisphere's view---under which, the manuscript argues, gravitational and electromagnetic phenomena resolve into standing-wave interference patterns in spacetime, with toroidal topology as the constraint that selects the stable patterns.

Each element matured into typed structure downstream. The standing-wave reading became the program's universal spectrum discipline: interference patterns on a bounded domain are cavity modes, and the corpus's Bessel ladders (Papers I, II, VI) are their census. The toroidal constraint became the validation layer's load-bearing requirement (C18), the recursive habitat of C16, and finally the torus on which Paper VIII assembles the unified charge. The dual-pole perspective itself matured into the program's reciprocal-flip thread: viewing from both poles at once is the observational form of the $r \mapsto 1/r$ inversion---neither pole privileged, the physics living in the pair---which Papers I--III formalized across criticality, orbits, and the comma.

And the lunar-terrestrial laboratory remained the corpus's favorite: the resonance families this manuscript mined are the same data C18 recruits for validation. The spine below anchors the theory's chain; refinement targets are the promotion of the dual-pole construction to typed form and the resonance-pattern census against modern geomagnetic and tidal series.

\section{The concept-anchored spine methodology}
\label{sec:method}

The companion series applies a uniform method, stated here so that the paper is self-contained. The source manuscript was published with its mathematics rendered as text rather than as machine-readable LaTeX, so its spine is \emph{concept-anchored}: the thesis is taken from the manuscript's abstract, and the spine nodes are the canonical-registry entries most strongly matched to the manuscript's themes, selected by weighted term overlap with foundational nodes ranked first. Each node carries its registry equation, its dictionary definition, its encyclopedia interpretation, and a declared proof-obligation role (Core\_Definition, Core\_Axiom, or Derived\_Theorem\_Obligation). The resulting chain is a starting backbone for refinement---a typed scaffold onto which an exact, equation-by-equation crosswalk with the source manuscript can be progressively attached---rather than a claim of completed formalization.

Three properties make the backbone useful even before refinement completes. First, \emph{addressability}: every claim in the companion paper resolves to a registry identifier whose equation, definition, and verification status are independently inspectable, so disagreement can be localized to a node rather than to the paper as a whole. Second, \emph{pipeline coupling}: each spine is paired with an Isabelle focus-theory stub and a Wolfram check stub, so that as nodes are refined their obligations enter the same machine-checked pipeline that certifies the core series' guardrails. Third, \emph{role discipline}: the obligation roles separate what the spine defines from what it asserts and what it must prove, which keeps the demarcation section of every companion paper honest by construction.

The dependency chain should accordingly be read as a proof-order proposal: upstream nodes supply the vocabulary and axioms that downstream nodes consume, and the refinement pass is free to reorder where the source manuscript's own logic demands it. Where a node's registry equation arrives with rendering artifacts inherited from the source extraction (a known cost of text-rendered mathematics), the equation is quoted as carried by the registry, with the dictionary and encyclopedia entries supplying the authoritative reading.

\section{The registry chain}
\label{sec:chain}

The curated chain, in proof order, is
\begin{equation*}
\begin{gathered}
\text{ID10134} \to \text{ID3402} \to \text{ID9157} \to \text{ID10128} \\
\to \text{ID8689} \to \text{ID8690} \to \text{ID6489}.
\end{gathered}
\end{equation*}
We take the nodes in order; each subsection quotes the registry equation as carried by the canonical master, then gives the dictionary definition and the encyclopedia's interpretive reading.

\subsection{ID10134: Relation: M)---a Span of 61 Orders of Magnitude. We Validate Predictions Including... (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{m)---a span of 61 orders of magnitude. We validate predictions including: wavelength quantization (}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: m)---a span of 61 orders of magnitude. We validate predictions including: wavelength quantization (\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: M)---a Span of 61 Orders of Magnitude. We Validate Predictions Including... is a symbolic expression, written m)---a span of 61 orders of magnitude. We validate predictions including: wavele. It introduces a symbol or relation used elsewhere in the framework. It is built from m, a, s, p, n, o. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{theory\_of\_it\_all\_tra\_ID10134\_structure}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID3402: Spectral Gap Laplacian Operator (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\$\textbackslash{}Delta\textbackslash{}Phi = n\textbackslash{}Phi\_\{0\}\$}}\par\medskip
\noindent\textit{Dictionary definition.} Spectral Gap Laplacian Operator --- DeltaPhi = nPhi\_0\par\medskip
\noindent\textit{Encyclopedia reading.} The entry preserves the equation exactly as extracted from `00\_EngineLemma-MakerPrismtrawin\_topology\_unified\_field\_theory.tex` for registry alignment and later derivation.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{theory\_of\_it\_all\_tra\_ID3402\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID9157: Relation: R\_universe / N, Where R\_universe Is the Hubble Radius. for N of Order Unity (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{R\_universe / n, where R\_universe is the Hubble radius. For n of order unity,}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: R\_universe / n, where R\_universe is the Hubble radius. For n of order unity\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: R\_universe / N, Where R\_universe Is the Hubble Radius. for N of Order Unity is a symbolic expression, written R\_universe / n, where R\_universe is the Hubble radius. For n of order unity. It introduces a symbol or relation used elsewhere in the framework. It is built from R\_u, n, v, r, s, w. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{theory\_of\_it\_all\_tra\_ID9157\_structure}.
\par\medskip\noindent\textit{Obligation reading.} A definitional node: its function is to make later statements well-formed. The guardrail attached to it is correspondingly structural---an identity or well-formedness check rather than a physical claim.

\subsection{ID10128: Relation: alpha \textasciitilde{}= 1/137.036 (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}alpha \textbackslash{}approx 1/137.036}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: alpha \textasciitilde{}= 1/137.036 --- alpha \textasciitilde{}= 1/137.036\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: alpha \textasciitilde{}= 1/137.036 is a scaling / order-of-magnitude relation, written alpha \textasciitilde{}= 1/137.036. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from alpha. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{theory\_of\_it\_all\_tra\_ID10128\_structure}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\subsection{ID8689: Definition of (lambda (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{(\textbackslash{}lambda=\textbackslash{}pi R\textbackslash{}oplus\textbackslash{}approx20,015}}\par\medskip
\noindent\textit{Dictionary definition.} Definition of (lambda --- (lambda=pi Roplus\textasciitilde{}=20,015\par\medskip
\noindent\textit{Encyclopedia reading.} Definition of (lambda is a scaling / order-of-magnitude relation, written (lambda=pi Roplus\textasciitilde{}=20,015. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from pi, R, defining (lambda. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{theory\_of\_it\_all\_tra\_ID8689\_identity}.
\par\medskip\noindent\textit{Obligation reading.} A derived obligation: the spine claims this follows from what precedes it. Until the formal derivation is supplied, the computational guardrail polices at least the node's internal consistency.

\subsection{ID8690: Relation: (epsilon\textasciitilde{}=7.27x10PiPi) (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{(\textbackslash{}epsilon\textbackslash{}approx7.27\textbackslash{}times10\textbackslash{}Pi\textbackslash{}Pi)}}\par\medskip
\noindent\textit{Dictionary definition.} Planck-scale oscillations, while General Relativity's curved spacetime emerges as the macroscopic geometry of these quantum field oscillations.\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: (epsilon\textasciitilde{}=7.27x10PiPi) is a scaling / order-of-magnitude relation, written (epsilon\textasciitilde{}=7.27x10PiPi). It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from epsilon, Pi. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{theory\_of\_it\_all\_tra\_ID8690\_structure}.
\par\medskip\noindent\textit{Obligation reading.} This node carries proof debt by declaration---Derived\_Theorem\_Obligation---and is therefore where the refinement pass should concentrate first: a discharged derivation here strengthens every downstream node simultaneously.

\subsection{ID6489: \textbackslash{}\{Einstein--Rosen Bridge and Trawin Zero-Point Tunnel:\}\textbackslash{} (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{0.3em] \textbackslash{}textit\{A Theoretical Massless Transit System of Attainable Thermodynamics\textbackslash{}\textbackslash{}Through Wave and Inter-State Topology\} \} \textbackslash{}author\{ Daniel Alexander Trawin\textbackslash{}\textbackslash{}[0.3em] \textbackslash{}small ORCID: \textbackslash{}href\{https://orcid.org/0009-0001-4630-3 715\}\{0009-0001-4630-3715\}\textbackslash{}\textbackslash{}[0.5em] \textbackslash{}small \textbackslash{}texttt\{daniel.alexander.trawin@placeh ...}}\par\medskip
\noindent\textit{Dictionary definition.} \textbackslash{}\{Einstein--Rosen Bridge and Trawin Zero-Point Tunnel:\}\textbackslash{} --- 0.3em] textitA Theoretical Massless Transit System of Attainable ThermodynamicsThrough Wave and Inter-State Topology author Daniel Alexander Trawin[0.\par\medskip
\noindent\textit{Encyclopedia reading.} \textbackslash{}\{Einstein--Rosen Bridge and Trawin Zero-Point Tunnel:\}\textbackslash{} is a tbd, written 0.3em] textitA Theoretical Massless Transit System of Attainable ThermodynamicsT. Its construction method could not be determined from the available material. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{theory\_of\_it\_all\_tra\_ID6489\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\section{Dependency structure and obligations}
\label{sec:dep}

Table~\ref{tab:obligations} summarizes the spine's obligation ledger. The chain's proof order runs from the definitional nodes (vocabulary first) through the derived obligations to the spine's closure; the refinement pass may interleave additional registry nodes where the source manuscript's own derivations require them, in which case the table grows monotonically---existing rows are never weakened, only joined.

\begin{table}[ht]
\centering
\small
\caption{Obligation ledger for the theory of it all trawin topology spine.}
\label{tab:obligations}
\begin{tabular}{llp{6.2cm}}
\toprule
ID & Obligation role & Wolfram check \\
\midrule
ID10134 & Core\_Definition & \texttt{theory\_of\_it\_all\_tra\_ID10134\_structure} \\
ID3402 & Core\_Definition & \texttt{theory\_of\_it\_all\_tra\_ID3402\_identity} \\
ID9157 & Core\_Definition & \texttt{theory\_of\_it\_all\_tra\_ID9157\_structure} \\
ID10128 & Derived\_Theorem\_Obligation & \texttt{theory\_of\_it\_all\_tra\_ID10128\_structure} \\
ID8689 & Derived\_Theorem\_Obligation & \texttt{theory\_of\_it\_all\_tra\_ID8689\_identity} \\
ID8690 & Derived\_Theorem\_Obligation & \texttt{theory\_of\_it\_all\_tra\_ID8690\_structure} \\
ID6489 & Derived\_Theorem\_Obligation & \texttt{theory\_of\_it\_all\_tra\_ID6489\_identity} \\
\bottomrule
\end{tabular}
\end{table}

\section{Crosswalk to the core series and companion corpus}
\label{sec:crosswalk}

Because all spines draw on one canonical registry, node sharing is measurable and meaningful: a shared identifier means two papers consume literally the same typed object, so verification work transfers between them without translation. Of this spine's seven nodes, 0 appear in core-series spines and 5 recur elsewhere in the companion corpus. Table~\ref{tab:crosswalk} records the census.

\begin{table}[ht]
\centering
\small
\caption{Node-sharing census for this spine.}
\label{tab:crosswalk}
\begin{tabular}{lp{4.4cm}p{6.6cm}}
\toprule
ID & Core-series appearances & Companion-corpus appearances \\
\midrule
ID10134 & --- & gyromagnetic validation \\
ID3402 & --- & --- \\
ID9157 & --- & --- \\
ID10128 & --- & gyromagnetic validation \\
ID8689 & --- & gyromagnetic validation \\
ID8690 & --- & gyromagnetic validation \\
ID6489 & --- & Gravitational-Emergence-TPZ-; trawin enlil protocol; tzp type c (+2 more) \\
\bottomrule
\end{tabular}
\end{table}

Two readings follow. Nodes shared with the core series are this spine's strongest members: their guardrails are already certified in the core pipeline, and the present paper inherits that status. Nodes unique to this spine are its distinctive contribution---and its refinement priority, since no other paper will discharge them. Nodes recurring across companions mark the corpus's internal seams: the same object consumed by several manuscripts, whose refinements must agree by the duplicate discipline documented in the Einstein Focus companion.

\section{Position in the TZPID arc}
\label{sec:arc}

This companion is Paper VIII's observational ancestor and the unification group's senior member: standing waves before spectra, toroidal constraint before the assembled charge, dual poles before the formal flip. Read after the core arc it shows the program's direction of travel---from a unifying perception of one two-body system to typed obligations on every sector---and preserves the original perception the formal work must not lose.

\section{Verification pathway}
\label{sec:verify}

The spine enters the program's two-engine verification pipeline. The Isabelle focus theory \texttt{TZPID\_Spine\_theory\_of\_it\_all\_trawin\_topology.thy} types the seven obligations over the registry's declared vocabulary, in the dependency order of Section~\ref{sec:chain}; the Wolfram check stub \texttt{theory\_of\_it\_all\_trawin\_topology\_checks.wl} carries the per-node computational guardrails listed in Table~\ref{tab:obligations}. As with the core series, the division of labor is deliberate: the theorem prover certifies structure (types, roles, dependency soundness), while the computational engine certifies arithmetic and algebraic identities node by node. A check name of the form \texttt{...\_identity} denotes a per-node identity guardrail generated from the registry equation; refined checks replace these as the equation-level crosswalk matures.

Because the companion spines share the registry with the core series, verification is cumulative: any node here that also appears in a core spine (the chain tables record several) inherits the core guardrail's status, and any refinement proved here propagates back. The companion series thus functions as the proof pipeline's breadth dimension---161 distinct registry nodes across the 27 companions---complementing the core series' depth.

The pipeline's two-engine division also fixes what failure means at this layer. A failed Wolfram guardrail localizes an arithmetic or algebraic defect in one node's registered equation: the repair is editorial (correct the registration against the source) or substantive (the source itself errs), and the obligations ledger records which. A failed Isabelle discharge, by contrast, indicts the chain: a type mismatch or unprovable dependency means the proof-order proposal of Section~\\ref{sec:chain} is wrong as stated, and the refinement pass must re-curate. Keeping these failure modes separate is what the stub architecture buys: every companion enters the pipeline with its failure semantics declared in advance, which is the practical meaning of being peer-reviewable by machine.

\section{Refinement worksheet}
\label{sec:worksheet}

The concept-anchored backbone converts into an equation-level formalization through a bounded, node-by-node worksheet. For each node the worksheet item below states the concrete refinement act; completing all seven closes the spine's first formalization pass.

\begin{enumerate}
\item \textbf{ID10134} (\texttt{theory\_of\_it\_all\_tra\_ID10134\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID3402} (\texttt{theory\_of\_it\_all\_tra\_ID3402\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9157} (\texttt{theory\_of\_it\_all\_tra\_ID9157\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID10128} (\texttt{theory\_of\_it\_all\_tra\_ID10128\_structure}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID8689} (\texttt{theory\_of\_it\_all\_tra\_ID8689\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID8690} (\texttt{theory\_of\_it\_all\_tra\_ID8690\_structure}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID6489} (\texttt{theory\_of\_it\_all\_tra\_ID6489\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\end{enumerate}

The worksheet's order matters: definitional items unblock derived ones, and a failure at any item halts propagation rather than silently weakening downstream claims. Completed items should update the obligations CSV in place, so that the spine's public ledger always reflects its true refinement state---the same live-ledger discipline the core series applies to its guardrails.

\section{Demarcation and refinement targets}
\label{sec:demarc}

As throughout the program, the demarcation line is drawn explicitly. The established layer comprises the standard mathematics and physics that the chain's nodes quote---definitions, identities, and independently citable results---together with whatever the computational guardrails certify. The framework layer comprises the source manuscript's interpretive claims and the spine's structural assertion that its nodes form the stated dependency chain. The dual-pole reading is a perspective, not yet a theorem; its falsifiable content lives in the resonance-pattern census and the toroidal selection rule, both checkable against existing geophysical time series.

Refinement targets, in pipeline order: (i) replace the concept-anchored node selection with an equation-level crosswalk against the source manuscript; (ii) promote each \texttt{...\_identity} guardrail to a content-bearing check; (iii) discharge the typed obligations in the Isabelle focus theory against the program's shared vocabulary; and (iv) record any node whose refinement fails, since a failed node localizes exactly where the source manuscript and the canonical registry disagree---the information a refinement pass exists to produce.

\section{Conclusion}
\label{sec:conc}

The Theory of It All is the corpus's unification in its first voice: Earth and Moon as one resonant system, both poles watched at once, interference and toroidal constraint doing the unifying. The formal arc kept every element and paid its debts in types. What this companion preserves is the origin: the program began not with an action principle but with a way of looking, and the refinement pass should keep the census honest enough to deserve it.

\begin{thebibliography}{9}

\bibitem{registry} Trawin, D. A., \emph{TZPID Canonical Equation Master Registry, Dictionary, and Encyclopedia}, TZPIDProof archive (2026). Registry identifiers as cited in text.

\bibitem{spine} Trawin, D. A., \emph{TZPID Zenodo Individual Spines: theory of it all trawin topology}, TZPIDProof archive, \texttt{zenodo\_individual\_spines/} (2026).

\bibitem{manuscript} Trawin, D. A., \emph{theory of it all trawin topology}, Zenodo manuscript (2026).

\bibitem{core} Trawin, D. A., TZPID Gold Spine Series, Papers I--VIII (2026).

\bibitem{einstein} Trawin, D. A., \emph{The Einstein Focus}, TZPID Gold Spine Series, Paper V-A (2026).

\bibitem{index} Trawin, D. A., \emph{TZPID Zenodo Paper Gold Spines} (aggregate), \texttt{TZPID\_ZENODO\_SPINES.md}, TZPIDProof archive (2026).

\end{thebibliography}

\end{document}
