\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathptmx}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,filecolor=black,menucolor=black,anchorcolor=black,pdfauthor={Daniel Alexander Trawin},pdftitle={Gyromagnetic Validation: Toroidal Constraints and Lunar-Terrestrial Correlation},pdfsubject={TZPID Companion Spine Series, Paper C18},pdfkeywords={TZPID, gyromagnetic validation}]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\title{Gyromagnetic Validation: Toroidal Constraints and Lunar-Terrestrial Correlation\\[0.6em]
\large TZPID Companion Spine Series, Paper C18 of XXVII\\
\normalsize Empirical checkpoints for the Trawin topology's movement claims}
\author{Daniel Alexander Trawin\\
\small ORCID: \href{https://orcid.org/0009-0001-4630-3715}{0009-0001-4630-3715}\\
\small \href{mailto:danielalexandertrawin@gmail.com}{danielalexandertrawin@gmail.com}}
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
This companion validates the gyromagnetic architecture of the Trawin topology through mathematical analysis and empirical correlation with lunar-terrestrial wave patterns, with the toroidal constraint on field configurations producing the observed phenomena across scales.
The source manuscript's stated thesis: ``We validate the gyromagnetic architecture of Trawin Topology through mathematical analysis and empirical correlation with lunar-terrestrial wave patterns. The toroidal constraint on field configurations is shown to produce the observed gyromagnetic phenomena across scales, confirming the geometric unification framework.'' The paper organizes this thesis as a TZPID gold spine: a curated seven-node registry chain (ID1742, ID10134, ID10128, ID10245, ID10255, ID8689, ID8690) with typed proof-obligation roles, dictionary and encyclopedia anchors for every node, a declared dependency order, and stubs in the program's Isabelle/Wolfram verification pipeline. Within the arc this paper is the movement engine's audit: the checkpoints at which gyromagnetic theory met data.
\end{abstract}

\section{Introduction}
\label{sec:intro}

Validation papers are where frameworks acquire scars, and this companion documents the gyromagnetic architecture's. Its two instruments are mathematical analysis---consistency checks on the toroidal constraint, the requirement that admissible field configurations respect toroidal topology---and empirical correlation, with lunar-terrestrial wave patterns as the data: the coupled oscillation families of the Earth-Moon system, from tides through rotational wobble, read as a natural laboratory for cross-scale gyromagnetic claims.

The toroidal constraint is the load-bearing structure. Core Paper IV used it implicitly (poloidal/toroidal helicity, the $S^3$ topology blocking flat dipole collapse); core Paper VIII assembled the unified charge on the torus; companion C16 made the enclosure recursively toroidal. This companion's claim is that the constraint is not optional bookkeeping but the generator of observed gyromagnetic phenomenology: confine field configurations to toroidal topology and the gyromagnetic relations follow across scales, which is what the lunar-terrestrial correlations are recruited to check.

The validation layer also contributes the corpus's categorical bridges in their source form: the structure-preserving maps FrameDragging (gyroscopic modes to spacetime metric) and HelicityPreservation (magnetic states to topological invariants), with the effective field equation $G_{\mu\nu} = T_{\mathrm{EM}} + T_{\mathrm{top}}$---electromagnetic plus topological stress sourcing geometry---which Paper IV cited as the door to Paper V. The spine below anchors these contributions; refinement targets are the statistical hardening of the lunar-terrestrial correlations (windowing, nulls, multiplicity) and the promotion of the toroidal-constraint derivation to a typed theorem.

\section{The concept-anchored spine methodology}
\label{sec:method}

The companion series applies a uniform method, stated here so that the paper is self-contained. The source manuscript was published with its mathematics rendered as text rather than as machine-readable LaTeX, so its spine is \emph{concept-anchored}: the thesis is taken from the manuscript's abstract, and the spine nodes are the canonical-registry entries most strongly matched to the manuscript's themes, selected by weighted term overlap with foundational nodes ranked first. Each node carries its registry equation, its dictionary definition, its encyclopedia interpretation, and a declared proof-obligation role (Core\_Definition, Core\_Axiom, or Derived\_Theorem\_Obligation). The resulting chain is a starting backbone for refinement---a typed scaffold onto which an exact, equation-by-equation crosswalk with the source manuscript can be progressively attached---rather than a claim of completed formalization.

Three properties make the backbone useful even before refinement completes. First, \emph{addressability}: every claim in the companion paper resolves to a registry identifier whose equation, definition, and verification status are independently inspectable, so disagreement can be localized to a node rather than to the paper as a whole. Second, \emph{pipeline coupling}: each spine is paired with an Isabelle focus-theory stub and a Wolfram check stub, so that as nodes are refined their obligations enter the same machine-checked pipeline that certifies the core series' guardrails. Third, \emph{role discipline}: the obligation roles separate what the spine defines from what it asserts and what it must prove, which keeps the demarcation section of every companion paper honest by construction.

The dependency chain should accordingly be read as a proof-order proposal: upstream nodes supply the vocabulary and axioms that downstream nodes consume, and the refinement pass is free to reorder where the source manuscript's own logic demands it. Where a node's registry equation arrives with rendering artifacts inherited from the source extraction (a known cost of text-rendered mathematics), the equation is quoted as carried by the registry, with the dictionary and encyclopedia entries supplying the authoritative reading.

\section{The registry chain}
\label{sec:chain}

The curated chain, in proof order, is
\begin{equation*}
\begin{gathered}
\text{ID1742} \to \text{ID10134} \to \text{ID10128} \to \text{ID10245} \\
\to \text{ID10255} \to \text{ID8689} \to \text{ID8690}.
\end{gathered}
\end{equation*}
We take the nodes in order; each subsection quotes the registry equation as carried by the canonical master, then gives the dictionary definition and the encyclopedia's interpretive reading.

\subsection{ID1742: Gyromagnetic Validation Ratio (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}gamma=\textbackslash{}frac\{L\}\{\textbackslash{}mu\}=\textbackslash{}frac\{2n\textbackslash{}hbar\}\{qvr\}}}\par\medskip
\noindent\textit{Dictionary definition.} The equation support layer follows = L ; L=n ; = qvr2; = L = 2n qvr.\par\medskip
\noindent\textit{Encyclopedia reading.} The equation support layer follows gamma=frac\{L\}\{mu\}; L=nhbar; mu=frac\{qvr\}\{2\}; gamma=frac\{L\}\{mu\}=frac\{2nhbar\}\{qvr\}. These relations are compact review objects, not unsupported placeholders.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{gyromagnetic\_validat\_ID1742\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID10134: Relation: M)---a Span of 61 Orders of Magnitude. We Validate Predictions Including... (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{m)---a span of 61 orders of magnitude. We validate predictions including: wavelength quantization (}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: m)---a span of 61 orders of magnitude. We validate predictions including: wavelength quantization (\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: M)---a Span of 61 Orders of Magnitude. We Validate Predictions Including... is a symbolic expression, written m)---a span of 61 orders of magnitude. We validate predictions including: wavele. It introduces a symbol or relation used elsewhere in the framework. It is built from m, a, s, p, n, o. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{gyromagnetic\_validat\_ID10134\_structure}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID10128: Relation: alpha \textasciitilde{}= 1/137.036 (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}alpha \textbackslash{}approx 1/137.036}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: alpha \textasciitilde{}= 1/137.036 --- alpha \textasciitilde{}= 1/137.036\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: alpha \textasciitilde{}= 1/137.036 is a scaling / order-of-magnitude relation, written alpha \textasciitilde{}= 1/137.036. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from alpha. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{gyromagnetic\_validat\_ID10128\_structure}.
\par\medskip\noindent\textit{Obligation reading.} This node carries proof debt by declaration---Derived\_Theorem\_Obligation---and is therefore where the refinement pass should concentrate first: a discharged derivation here strengthens every downstream node simultaneously.

\subsection{ID10245: Definition of lambda (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\textbackslash{}lambda = \textbackslash{}pi R\_\textbackslash{}oplus \textbackslash{}approx 2.0015\textbackslash{}times 10\textasciicircum{}\{4\}\textbackslash{},\textbackslash{}mathrm\{km\},}}\par\medskip
\noindent\textit{Dictionary definition.} Trawin Topology introduces constrained dipole dynamics and toroidal flux topology as fundamental organizing principles, providing a mathematical bridge between discrete quantum phenomena and continuous classical fields.\par\medskip
\noindent\textit{Encyclopedia reading.} Definition of lambda is a scaling / order-of-magnitude relation, written lambda = pi R\_oplus \textasciitilde{}= 2.0015x 10\textasciicircum{}4 km. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from pi, R, defining lambda. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{gyromagnetic\_validat\_ID10245\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\subsection{ID10255: Relation: T\_semidiurnal \textasciitilde{}= 12.42\textasciitilde{}hours (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{T\_\{\textbackslash{}text\{semidiurnal\}\} \textbackslash{}approx 12.42\textasciitilde{}\textbackslash{}text\{hours\},}}\par\medskip
\noindent\textit{Dictionary definition.} Trawin Topology introduces constrained dipole dynamics and toroidal flux topology as fundamental organizing principles, providing a mathematical bridge between discrete quantum phenomena and continuous classical fields [ID10255]\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: T\_semidiurnal \textasciitilde{}= 12.42\textasciitilde{}hours is a scaling / order-of-magnitude relation, written T\_semidiurnal \textasciitilde{}= 12.42\textasciitilde{}hours. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from T\_. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{gyromagnetic\_validat\_ID10255\_structure}.
\par\medskip\noindent\textit{Obligation reading.} A derived obligation: the spine claims this follows from what precedes it. Until the formal derivation is supplied, the computational guardrail polices at least the node's internal consistency.

\subsection{ID8689: Definition of (lambda (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{(\textbackslash{}lambda=\textbackslash{}pi R\textbackslash{}oplus\textbackslash{}approx20,015}}\par\medskip
\noindent\textit{Dictionary definition.} Definition of (lambda --- (lambda=pi Roplus\textasciitilde{}=20,015\par\medskip
\noindent\textit{Encyclopedia reading.} Definition of (lambda is a scaling / order-of-magnitude relation, written (lambda=pi Roplus\textasciitilde{}=20,015. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from pi, R, defining (lambda. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{gyromagnetic\_validat\_ID8689\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This node carries proof debt by declaration---Derived\_Theorem\_Obligation---and is therefore where the refinement pass should concentrate first: a discharged derivation here strengthens every downstream node simultaneously.

\subsection{ID8690: Relation: (epsilon\textasciitilde{}=7.27x10PiPi) (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{(\textbackslash{}epsilon\textbackslash{}approx7.27\textbackslash{}times10\textbackslash{}Pi\textbackslash{}Pi)}}\par\medskip
\noindent\textit{Dictionary definition.} Planck-scale oscillations, while General Relativity's curved spacetime emerges as the macroscopic geometry of these quantum field oscillations.\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: (epsilon\textasciitilde{}=7.27x10PiPi) is a scaling / order-of-magnitude relation, written (epsilon\textasciitilde{}=7.27x10PiPi). It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from epsilon, Pi. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{gyromagnetic\_validat\_ID8690\_structure}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\section{Dependency structure and obligations}
\label{sec:dep}

Table~\ref{tab:obligations} summarizes the spine's obligation ledger. The chain's proof order runs from the definitional nodes (vocabulary first) through the derived obligations to the spine's closure; the refinement pass may interleave additional registry nodes where the source manuscript's own derivations require them, in which case the table grows monotonically---existing rows are never weakened, only joined.

\begin{table}[ht]
\centering
\small
\caption{Obligation ledger for the gyromagnetic validation spine.}
\label{tab:obligations}
\begin{tabular}{llp{6.2cm}}
\toprule
ID & Obligation role & Wolfram check \\
\midrule
ID1742 & Core\_Definition & \texttt{gyromagnetic\_validat\_ID1742\_identity} \\
ID10134 & Core\_Definition & \texttt{gyromagnetic\_validat\_ID10134\_structure} \\
ID10128 & Derived\_Theorem\_Obligation & \texttt{gyromagnetic\_validat\_ID10128\_structure} \\
ID10245 & Derived\_Theorem\_Obligation & \texttt{gyromagnetic\_validat\_ID10245\_identity} \\
ID10255 & Derived\_Theorem\_Obligation & \texttt{gyromagnetic\_validat\_ID10255\_structure} \\
ID8689 & Derived\_Theorem\_Obligation & \texttt{gyromagnetic\_validat\_ID8689\_identity} \\
ID8690 & Derived\_Theorem\_Obligation & \texttt{gyromagnetic\_validat\_ID8690\_structure} \\
\bottomrule
\end{tabular}
\end{table}

\section{Crosswalk to the core series and companion corpus}
\label{sec:crosswalk}

Because all spines draw on one canonical registry, node sharing is measurable and meaningful: a shared identifier means two papers consume literally the same typed object, so verification work transfers between them without translation. Of this spine's seven nodes, 0 appear in core-series spines and 4 recur elsewhere in the companion corpus. Table~\ref{tab:crosswalk} records the census.

\begin{table}[ht]
\centering
\small
\caption{Node-sharing census for this spine.}
\label{tab:crosswalk}
\begin{tabular}{lp{4.4cm}p{6.6cm}}
\toprule
ID & Core-series appearances & Companion-corpus appearances \\
\midrule
ID1742 & --- & --- \\
ID10134 & --- & theory of it all trawin topology \\
ID10128 & --- & theory of it all trawin topology \\
ID10245 & --- & --- \\
ID10255 & --- & --- \\
ID8689 & --- & theory of it all trawin topology \\
ID8690 & --- & theory of it all trawin topology \\
\bottomrule
\end{tabular}
\end{table}

Two readings follow. Nodes shared with the core series are this spine's strongest members: their guardrails are already certified in the core pipeline, and the present paper inherits that status. Nodes unique to this spine are its distinctive contribution---and its refinement priority, since no other paper will discharge them. Nodes recurring across companions mark the corpus's internal seams: the same object consumed by several manuscripts, whose refinements must agree by the duplicate discipline documented in the Einstein Focus companion.

\section{Position in the TZPID arc}
\label{sec:arc}

This companion is the empirical wing of the movement group: C17 supplies the attractor theory, this paper tests its topological skeleton against the nearest available two-body laboratory. Its categorical bridges seeded Paper IV's validation layer, its toroidal constraint anticipates C16's recursive habitat and Paper VIII's torus assembly, and its effective field equation is the hinge on which the arc turned from movement to gravity.

\section{Verification pathway}
\label{sec:verify}

The spine enters the program's two-engine verification pipeline. The Isabelle focus theory \texttt{TZPID\_Spine\_gyromagnetic\_validation.thy} types the seven obligations over the registry's declared vocabulary, in the dependency order of Section~\ref{sec:chain}; the Wolfram check stub \texttt{gyromagnetic\_validation\_checks.wl} carries the per-node computational guardrails listed in Table~\ref{tab:obligations}. As with the core series, the division of labor is deliberate: the theorem prover certifies structure (types, roles, dependency soundness), while the computational engine certifies arithmetic and algebraic identities node by node. A check name of the form \texttt{...\_identity} denotes a per-node identity guardrail generated from the registry equation; refined checks replace these as the equation-level crosswalk matures.

Because the companion spines share the registry with the core series, verification is cumulative: any node here that also appears in a core spine (the chain tables record several) inherits the core guardrail's status, and any refinement proved here propagates back. The companion series thus functions as the proof pipeline's breadth dimension---161 distinct registry nodes across the 27 companions---complementing the core series' depth.

The pipeline's two-engine division also fixes what failure means at this layer. A failed Wolfram guardrail localizes an arithmetic or algebraic defect in one node's registered equation: the repair is editorial (correct the registration against the source) or substantive (the source itself errs), and the obligations ledger records which. A failed Isabelle discharge, by contrast, indicts the chain: a type mismatch or unprovable dependency means the proof-order proposal of Section~\\ref{sec:chain} is wrong as stated, and the refinement pass must re-curate. Keeping these failure modes separate is what the stub architecture buys: every companion enters the pipeline with its failure semantics declared in advance, which is the practical meaning of being peer-reviewable by machine.

\section{Refinement worksheet}
\label{sec:worksheet}

The concept-anchored backbone converts into an equation-level formalization through a bounded, node-by-node worksheet. For each node the worksheet item below states the concrete refinement act; completing all seven closes the spine's first formalization pass.

\begin{enumerate}
\item \textbf{ID1742} (\texttt{gyromagnetic\_validat\_ID1742\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID10134} (\texttt{gyromagnetic\_validat\_ID10134\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID10128} (\texttt{gyromagnetic\_validat\_ID10128\_structure}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID10245} (\texttt{gyromagnetic\_validat\_ID10245\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID10255} (\texttt{gyromagnetic\_validat\_ID10255\_structure}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID8689} (\texttt{gyromagnetic\_validat\_ID8689\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID8690} (\texttt{gyromagnetic\_validat\_ID8690\_structure}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\end{enumerate}

The worksheet's order matters: definitional items unblock derived ones, and a failure at any item halts propagation rather than silently weakening downstream claims. Completed items should update the obligations CSV in place, so that the spine's public ledger always reflects its true refinement state---the same live-ledger discipline the core series applies to its guardrails.

\section{Demarcation and refinement targets}
\label{sec:demarc}

As throughout the program, the demarcation line is drawn explicitly. The established layer comprises the standard mathematics and physics that the chain's nodes quote---definitions, identities, and independently citable results---together with whatever the computational guardrails certify. The framework layer comprises the source manuscript's interpretive claims and the spine's structural assertion that its nodes form the stated dependency chain. The toroidal-constraint mathematics is auditable as stated; the lunar-terrestrial correlations are claims about data and must survive standard time-series hygiene before they count as validation rather than illustration.

Refinement targets, in pipeline order: (i) replace the concept-anchored node selection with an equation-level crosswalk against the source manuscript; (ii) promote each \texttt{...\_identity} guardrail to a content-bearing check; (iii) discharge the typed obligations in the Isabelle focus theory against the program's shared vocabulary; and (iv) record any node whose refinement fails, since a failed node localizes exactly where the source manuscript and the canonical registry disagree---the information a refinement pass exists to produce.

\section{Conclusion}
\label{sec:conc}

Gyromagnetic validation is the movement engine's encounter with the sky it can actually see: toroidal constraints checked for consistency, Earth-Moon wave families checked for the predicted correlations, and the categorical bridges that the core series later formalized. Its refinement is statistical hardening; its standing contribution is the constraint-first methodology---topology before dynamics---that the rest of the corpus inherited.

\begin{thebibliography}{9}

\bibitem{registry} Trawin, D. A., \emph{TZPID Canonical Equation Master Registry, Dictionary, and Encyclopedia}, TZPIDProof archive (2026). Registry identifiers as cited in text.

\bibitem{spine} Trawin, D. A., \emph{TZPID Zenodo Individual Spines: gyromagnetic validation}, TZPIDProof archive, \texttt{zenodo\_individual\_spines/} (2026).

\bibitem{manuscript} Trawin, D. A., \emph{gyromagnetic validation}, Zenodo manuscript (2026).

\bibitem{core} Trawin, D. A., TZPID Gold Spine Series, Papers I--VIII (2026).

\bibitem{einstein} Trawin, D. A., \emph{The Einstein Focus}, TZPID Gold Spine Series, Paper V-A (2026).

\bibitem{index} Trawin, D. A., \emph{TZPID Zenodo Paper Gold Spines} (aggregate), \texttt{TZPID\_ZENODO\_SPINES.md}, TZPIDProof archive (2026).

\end{thebibliography}

\end{document}
