\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathptmx}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,filecolor=black,menucolor=black,anchorcolor=black,pdfauthor={Daniel Alexander Trawin},pdftitle={The TZP Type-C Framework: Negative-Foundation Convergence},pdfsubject={TZPID Companion Spine Series, Paper C3},pdfkeywords={TZPID, tzp type c}]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\title{The TZP Type-C Framework: Negative-Foundation Convergence\\[0.6em]
\large TZPID Companion Spine Series, Paper C3 of XXVII\\
\normalsize Avoiding runaway divergence in oscillatory scaling}
\author{Daniel Alexander Trawin\\
\small ORCID: \href{https://orcid.org/0009-0001-4630-3715}{0009-0001-4630-3715}\\
\small \href{mailto:danielalexandertrawin@gmail.com}{danielalexandertrawin@gmail.com}}
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
This companion presents the Type-C variant of Trawin Zero Point Convergence: a response to the divergence problems that positive foundational mass-energy frameworks encounter when complex oscillatory systems are scaled.
The source manuscript's stated thesis: ``Standard models of particle physics and general relativity traditionally rely on positive foundational mass-energy frameworks, often encountering mathematical singularities and runaway divergences when scaling complex oscillatory systems. This paper introduces the Trawin Zero Point Convergence (TZP-C-) framework.'' The paper organizes this thesis as a TZPID gold spine: a curated seven-node registry chain (ID9197, ID9145, ID9146, ID9152, ID9153, ID6489, ID6733) with typed proof-obligation roles, dictionary and encyclopedia anchors for every node, a declared dependency order, and stubs in the program's Isabelle/Wolfram verification pipeline. Within the arc this paper is the program's stability argument: the reason its oscillatory scaling does not blow up where standard positive-foundation scaling does.
\end{abstract}

\section{Introduction}
\label{sec:intro}

Standard models of particle physics and gravitation build upward from positive mass-energy foundations, and a recurring cost of that choice is divergence: mathematical singularities and runaway growth when complex oscillatory systems are scaled. The Type-C framework locates the problem in the foundation rather than the scaling. If the base state is a convergent zero-point---a deficit-centred anchor toward which trajectories collapse, in the sense of the registry's founding convergence axiom (ID0000)---then oscillatory towers built upon it inherit convergence rather than divergence.

The argument matters to the program because the core series is, from one end to the other, a theory of oscillatory towers: the enclosure's eigenvalue ladders (Paper I), the locked oscillator ensembles (Paper II), the Kaluza--Klein and Bessel towers (Papers IV and VI), the regularized vacuum mode sum (Paper VII). Each tower was protected, in its own paper, by a local guardrail (cutoffs, thresholds, normalized kernels); the Type-C companion supplies the unified reason those guardrails exist to be found: the foundation converges, so every honest tower built on it has a finite reading.

The chain below assembles the registry's strongest matching nodes for this claim. The spine is concept-anchored; its refinement direction is to convert the convergence claim from a foundational reading into per-tower theorems, ideally by exhibiting each core-series guardrail as an instance of one Type-C convergence lemma.

\section{The concept-anchored spine methodology}
\label{sec:method}

The companion series applies a uniform method, stated here so that the paper is self-contained. The source manuscript was published with its mathematics rendered as text rather than as machine-readable LaTeX, so its spine is \emph{concept-anchored}: the thesis is taken from the manuscript's abstract, and the spine nodes are the canonical-registry entries most strongly matched to the manuscript's themes, selected by weighted term overlap with foundational nodes ranked first. Each node carries its registry equation, its dictionary definition, its encyclopedia interpretation, and a declared proof-obligation role (Core\_Definition, Core\_Axiom, or Derived\_Theorem\_Obligation). The resulting chain is a starting backbone for refinement---a typed scaffold onto which an exact, equation-by-equation crosswalk with the source manuscript can be progressively attached---rather than a claim of completed formalization.

Three properties make the backbone useful even before refinement completes. First, \emph{addressability}: every claim in the companion paper resolves to a registry identifier whose equation, definition, and verification status are independently inspectable, so disagreement can be localized to a node rather than to the paper as a whole. Second, \emph{pipeline coupling}: each spine is paired with an Isabelle focus-theory stub and a Wolfram check stub, so that as nodes are refined their obligations enter the same machine-checked pipeline that certifies the core series' guardrails. Third, \emph{role discipline}: the obligation roles separate what the spine defines from what it asserts and what it must prove, which keeps the demarcation section of every companion paper honest by construction.

The dependency chain should accordingly be read as a proof-order proposal: upstream nodes supply the vocabulary and axioms that downstream nodes consume, and the refinement pass is free to reorder where the source manuscript's own logic demands it. Where a node's registry equation arrives with rendering artifacts inherited from the source extraction (a known cost of text-rendered mathematics), the equation is quoted as carried by the registry, with the dictionary and encyclopedia entries supplying the authoritative reading.

\section{The registry chain}
\label{sec:chain}

The curated chain, in proof order, is
\begin{equation*}
\begin{gathered}
\text{ID9197} \to \text{ID9145} \to \text{ID9146} \to \text{ID9152} \\
\to \text{ID9153} \to \text{ID6489} \to \text{ID6733}.
\end{gathered}
\end{equation*}
We take the nodes in order; each subsection quotes the registry equation as carried by the canonical master, then gives the dictionary definition and the encyclopedia's interpretive reading.

\subsection{ID9197: Relation: r:det(J)=0andpi1(Mr)\textasciitilde{}=Zx (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{\{r:det(J)=0andpi1(M\{r\})\textasciitilde{}=Zx}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: r:det(J)=0andpi1(Mr)\textasciitilde{}=Zx --- r:det(J)=0andpi1(Mr)\textasciitilde{}=Zx\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: r:det(J)=0andpi1(Mr)\textasciitilde{}=Zx is an algebraic definition, written r:det(J)=0andpi1(Mr)\textasciitilde{}=Zx. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from r, J, M, Z. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{tzp\_type\_c\_ID9197\_identity}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID9145: Relation: .|Sigma\_j=1\textasciicircum{}N (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{.|Sigma\_\{j=1\}\textasciicircum{}\{N\}}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: .|Sigma\_j=1\textasciicircum{}N --- .|Sigma\_j=1\textasciicircum{}N\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: .|Sigma\_j=1\textasciicircum{}N is an algebraic definition, written .|Sigma\_j=1\textasciicircum{}N. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from j, N. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{tzp\_type\_c\_ID9145\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID9146: Relation: theta\_j(t))|. (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{theta\_j(t))|.}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: theta\_j(t))|. --- theta\_j(t))|.\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: theta\_j(t))|. is a symbolic expression, written theta\_j(t))|.. It introduces a symbol or relation used elsewhere in the framework. It is built from j. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{tzp\_type\_c\_ID9146\_structure}.
\par\medskip\noindent\textit{Obligation reading.} A definitional node: its function is to make later statements well-formed. The guardrail attached to it is correspondingly structural---an identity or well-formedness check rather than a physical claim.

\subsection{ID9152: Relation: rho\_e(t) (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{rho\_e(t)}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: rho\_e(t) --- rho\_e(t)\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: rho\_e(t) is a symbolic expression, written rho\_e(t). It introduces a symbol or relation used elsewhere in the framework. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{tzp\_type\_c\_ID9152\_structure}.
\par\medskip\noindent\textit{Obligation reading.} As a Core\_Definition this node contributes vocabulary rather than assertion: downstream nodes may use its object freely, but nothing is yet claimed about the world. Its refinement burden is precision---the typed form must capture exactly the object the source manuscript deploys.

\subsection{ID9153: Relation: rho\_1 cos(omega (Core\_Definition)}

\noindent\textit{Registry equation:}\par
{\small\texttt{rho\_1 cos(omega}}\par\medskip
\noindent\textit{Dictionary definition.} Relation: rho\_1 cos(omega --- rho\_1 cos(omega\par\medskip
\noindent\textit{Encyclopedia reading.} Relation: rho\_1 cos(omega is a symbolic expression, written rho\_1 cos(omega. It introduces a symbol or relation used elsewhere in the framework. It is built from c, o, s. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{tzp\_type\_c\_ID9153\_structure}.
\par\medskip\noindent\textit{Obligation reading.} This Core\_Definition fixes an object the rest of the chain consumes. In proof order it must be discharged first; in refinement it is where a mismatch between the manuscript's usage and the registry's typing would first surface.

\subsection{ID6489: \textbackslash{}\{Einstein--Rosen Bridge and Trawin Zero-Point Tunnel:\}\textbackslash{} (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{0.3em] \textbackslash{}textit\{A Theoretical Massless Transit System of Attainable Thermodynamics\textbackslash{}\textbackslash{}Through Wave and Inter-State Topology\} \} \textbackslash{}author\{ Daniel Alexander Trawin\textbackslash{}\textbackslash{}[0.3em] \textbackslash{}small ORCID: \textbackslash{}href\{https://orcid.org/0009-0001-4630-3 715\}\{0009-0001-4630-3715\}\textbackslash{}\textbackslash{}[0.5em] \textbackslash{}small \textbackslash{}texttt\{daniel.alexander.trawin@placeh ...}}\par\medskip
\noindent\textit{Dictionary definition.} \textbackslash{}\{Einstein--Rosen Bridge and Trawin Zero-Point Tunnel:\}\textbackslash{} --- 0.3em] textitA Theoretical Massless Transit System of Attainable ThermodynamicsThrough Wave and Inter-State Topology author Daniel Alexander Trawin[0.\par\medskip
\noindent\textit{Encyclopedia reading.} \textbackslash{}\{Einstein--Rosen Bridge and Trawin Zero-Point Tunnel:\}\textbackslash{} is a tbd, written 0.3em] textitA Theoretical Massless Transit System of Attainable ThermodynamicsT. Its construction method could not be determined from the available material. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{tzp\_type\_c\_ID6489\_identity}.
\par\medskip\noindent\textit{Obligation reading.} This node carries proof debt by declaration---Derived\_Theorem\_Obligation---and is therefore where the refinement pass should concentrate first: a discharged derivation here strengthens every downstream node simultaneously.

\subsection{ID6733: Quick Qualitative Reading (How the Pieces Correspond): M\textasciitilde{}= 7 (Derived\_Theorem\_Obligation)}

\noindent\textit{Registry equation:}\par
{\small\texttt{m\textbackslash{}approx 7}}\par\medskip
\noindent\textit{Dictionary definition.} Quick Qualitative Reading (How the Pieces Correspond): M\textasciitilde{}= 7 --- m\textasciitilde{}= 7\par\medskip
\noindent\textit{Encyclopedia reading.} Quick Qualitative Reading (How the Pieces Correspond): M\textasciitilde{}= 7 is a scaling / order-of-magnitude relation, written m\textasciitilde{}= 7. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from m. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
\par\medskip\noindent\textit{Computational guardrail:} \texttt{tzp\_type\_c\_ID6733\_structure}.
\par\medskip\noindent\textit{Obligation reading.} As a Derived\_Theorem\_Obligation this node owes a proof: the registry asserts that it follows from the chain's upstream vocabulary and axioms, and the Isabelle focus stub holds the slot where that derivation will be discharged.

\section{Dependency structure and obligations}
\label{sec:dep}

Table~\ref{tab:obligations} summarizes the spine's obligation ledger. The chain's proof order runs from the definitional nodes (vocabulary first) through the derived obligations to the spine's closure; the refinement pass may interleave additional registry nodes where the source manuscript's own derivations require them, in which case the table grows monotonically---existing rows are never weakened, only joined.

\begin{table}[ht]
\centering
\small
\caption{Obligation ledger for the tzp type c spine.}
\label{tab:obligations}
\begin{tabular}{llp{6.2cm}}
\toprule
ID & Obligation role & Wolfram check \\
\midrule
ID9197 & Core\_Definition & \texttt{tzp\_type\_c\_ID9197\_identity} \\
ID9145 & Core\_Definition & \texttt{tzp\_type\_c\_ID9145\_identity} \\
ID9146 & Core\_Definition & \texttt{tzp\_type\_c\_ID9146\_structure} \\
ID9152 & Core\_Definition & \texttt{tzp\_type\_c\_ID9152\_structure} \\
ID9153 & Core\_Definition & \texttt{tzp\_type\_c\_ID9153\_structure} \\
ID6489 & Derived\_Theorem\_Obligation & \texttt{tzp\_type\_c\_ID6489\_identity} \\
ID6733 & Derived\_Theorem\_Obligation & \texttt{tzp\_type\_c\_ID6733\_structure} \\
\bottomrule
\end{tabular}
\end{table}

\section{Crosswalk to the core series and companion corpus}
\label{sec:crosswalk}

Because all spines draw on one canonical registry, node sharing is measurable and meaningful: a shared identifier means two papers consume literally the same typed object, so verification work transfers between them without translation. Of this spine's seven nodes, 0 appear in core-series spines and 3 recur elsewhere in the companion corpus. Table~\ref{tab:crosswalk} records the census.

\begin{table}[ht]
\centering
\small
\caption{Node-sharing census for this spine.}
\label{tab:crosswalk}
\begin{tabular}{lp{4.4cm}p{6.6cm}}
\toprule
ID & Core-series appearances & Companion-corpus appearances \\
\midrule
ID9197 & --- & --- \\
ID9145 & --- & hms tzp \\
ID9146 & --- & hms tzp \\
ID9152 & --- & --- \\
ID9153 & --- & --- \\
ID6489 & --- & Gravitational-Emergence-TPZ-; theory of it all trawin topology; trawin enlil protocol (+2 more) \\
ID6733 & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

Two readings follow. Nodes shared with the core series are this spine's strongest members: their guardrails are already certified in the core pipeline, and the present paper inherits that status. Nodes unique to this spine are its distinctive contribution---and its refinement priority, since no other paper will discharge them. Nodes recurring across companions mark the corpus's internal seams: the same object consumed by several manuscripts, whose refinements must agree by the duplicate discipline documented in the Einstein Focus companion.

\section{Position in the TZPID arc}
\label{sec:arc}

Type-C convergence is the quiet premise of every finite sum in the core series. Paper VII's regularization (ID10165) is its clearest instance---the divergent naive sum is exhibited and then tamed---but the same structure recurs in Paper VI's normalized kernel, Paper II's bounded order parameter, and Paper I's finite mode censuses. Read with the first two companions, it completes the foundations triptych: C1 says what things are (deficits), C2 says how fields live near the anchor, and this paper says why the resulting towers converge.

\section{Verification pathway}
\label{sec:verify}

The spine enters the program's two-engine verification pipeline. The Isabelle focus theory \texttt{TZPID\_Spine\_tzp\_type\_c.thy} types the seven obligations over the registry's declared vocabulary, in the dependency order of Section~\ref{sec:chain}; the Wolfram check stub \texttt{tzp\_type\_c\_checks.wl} carries the per-node computational guardrails listed in Table~\ref{tab:obligations}. As with the core series, the division of labor is deliberate: the theorem prover certifies structure (types, roles, dependency soundness), while the computational engine certifies arithmetic and algebraic identities node by node. A check name of the form \texttt{...\_identity} denotes a per-node identity guardrail generated from the registry equation; refined checks replace these as the equation-level crosswalk matures.

Because the companion spines share the registry with the core series, verification is cumulative: any node here that also appears in a core spine (the chain tables record several) inherits the core guardrail's status, and any refinement proved here propagates back. The companion series thus functions as the proof pipeline's breadth dimension---161 distinct registry nodes across the 27 companions---complementing the core series' depth.

The pipeline's two-engine division also fixes what failure means at this layer. A failed Wolfram guardrail localizes an arithmetic or algebraic defect in one node's registered equation: the repair is editorial (correct the registration against the source) or substantive (the source itself errs), and the obligations ledger records which. A failed Isabelle discharge, by contrast, indicts the chain: a type mismatch or unprovable dependency means the proof-order proposal of Section~\\ref{sec:chain} is wrong as stated, and the refinement pass must re-curate. Keeping these failure modes separate is what the stub architecture buys: every companion enters the pipeline with its failure semantics declared in advance, which is the practical meaning of being peer-reviewable by machine.

\section{Refinement worksheet}
\label{sec:worksheet}

The concept-anchored backbone converts into an equation-level formalization through a bounded, node-by-node worksheet. For each node the worksheet item below states the concrete refinement act; completing all seven closes the spine's first formalization pass.

\begin{enumerate}
\item \textbf{ID9197} (\texttt{tzp\_type\_c\_ID9197\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9145} (\texttt{tzp\_type\_c\_ID9145\_identity}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9146} (\texttt{tzp\_type\_c\_ID9146\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9152} (\texttt{tzp\_type\_c\_ID9152\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID9153} (\texttt{tzp\_type\_c\_ID9153\_structure}): exhibit the source manuscript's working definition beside the registry equation; reconcile notation; type the object in the focus theory and confirm every downstream node consumes the typed form.
\item \textbf{ID6489} (\texttt{tzp\_type\_c\_ID6489\_identity}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\item \textbf{ID6733} (\texttt{tzp\_type\_c\_ID6733\_structure}): reconstruct the source manuscript's derivation sketch; identify the upstream nodes it actually uses (amending the chain if they differ from the curated order); discharge the proof in the focus theory or record the precise gap.
\end{enumerate}

The worksheet's order matters: definitional items unblock derived ones, and a failure at any item halts propagation rather than silently weakening downstream claims. Completed items should update the obligations CSV in place, so that the spine's public ledger always reflects its true refinement state---the same live-ledger discipline the core series applies to its guardrails.

\section{Demarcation and refinement targets}
\label{sec:demarc}

As throughout the program, the demarcation line is drawn explicitly. The established layer comprises the standard mathematics and physics that the chain's nodes quote---definitions, identities, and independently citable results---together with whatever the computational guardrails certify. The framework layer comprises the source manuscript's interpretive claims and the spine's structural assertion that its nodes form the stated dependency chain. The claim that convergence is inherited from the foundation is a structural conjecture; its honest form is a per-tower audit, and any tower in the registry that diverges despite Type-C foundations would falsify the inheritance claim in that sector.

Refinement targets, in pipeline order: (i) replace the concept-anchored node selection with an equation-level crosswalk against the source manuscript; (ii) promote each \texttt{...\_identity} guardrail to a content-bearing check; (iii) discharge the typed obligations in the Isabelle focus theory against the program's shared vocabulary; and (iv) record any node whose refinement fails, since a failed node localizes exactly where the source manuscript and the canonical registry disagree---the information a refinement pass exists to produce.

\section{Conclusion}
\label{sec:conc}

The Type-C framework converts the program's most frequent practical observation---its towers keep turning out finite---into a foundational claim with a single origin. The refinement target is to prove the inheritance: one convergence lemma at the anchor, instantiated tower by tower across the registry. Until then, Type-C stands as the organizing conjecture behind the series' guardrail culture, and the companion corpus's clearest invitation to a mathematician.

\begin{thebibliography}{9}

\bibitem{registry} Trawin, D. A., \emph{TZPID Canonical Equation Master Registry, Dictionary, and Encyclopedia}, TZPIDProof archive (2026). Registry identifiers as cited in text.

\bibitem{spine} Trawin, D. A., \emph{TZPID Zenodo Individual Spines: tzp type c}, TZPIDProof archive, \texttt{zenodo\_individual\_spines/} (2026).

\bibitem{manuscript} Trawin, D. A., \emph{tzp type c}, Zenodo manuscript (2026).

\bibitem{core} Trawin, D. A., TZPID Gold Spine Series, Papers I--VIII (2026).

\bibitem{einstein} Trawin, D. A., \emph{The Einstein Focus}, TZPID Gold Spine Series, Paper V-A (2026).

\bibitem{index} Trawin, D. A., \emph{TZPID Zenodo Paper Gold Spines} (aggregate), \texttt{TZPID\_ZENODO\_SPINES.md}, TZPIDProof archive (2026).

\end{thebibliography}

\end{document}
