\section*{ID9481: Definition of рқ‘қрқ‘Һрқ‘ҹрқ‘Ўрқ‘–рқ‘Һрқ‘ҷрқ‘ҹО©рқ‘’рқ‘һ0 рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО©}
\paragraph{Metadata.}
PiID: 2424701412147 | RTEID: RTE:P36816.8285:T4.1141 | UUID: 9f608261-8b64-5065-aac7-543ecd5fcd67

\paragraph{Canonical Statement.}
cated proof appendix for [ID 0276] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0275], [ID 0200] Node registry\_id\_0276 Support Titles Rotation Gradient; Shear Condition; Coupling Criterion Test Handle If differential rotation does not imply the stated coupling criterion, the entry fails. Canonical Equation Links \$рқ‘қрқ‘Һрқ‘ҹрқ‘Ўрқ‘–рқ‘Һрқ‘ҷрқ‘ҹО©рқ‘’рқ‘һ0 рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО©=О©innerвҲ’О©outer рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО©рқ‘’рқ‘һ0=вҮ’Ggyroрқ‘’рқ‘һ0\$ [ID 0277] Magnetic Moment Scaling Support TZPID ID0277 UUID ae765277-d72a-5b7d-887a-99e2e26949ce Type Field / Transport Statement Scale magnetofluid LOC Classification Working routing: QC809 magnetohydrodynamics; QC6 fluid and plasma dynamics arXiv Classification Primary: physics.plasm-ph; Cross-list: astro-ph.SR, gr-qc Canonical Statement This entry develops Magnetic Moment Scaling Support insid

\paragraph{Canonical Equation.}
\[
рқ‘қрқ‘Һрқ‘ҹрқ‘Ўрқ‘–рқ‘Һрқ‘ҷрқ‘ҹО©рқ‘’рқ‘һ0 рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО©=О©innerвҲ’О©outer рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО©рқ‘’рқ‘һ0=вҮ’Ggyroрқ‘’рқ‘һ0
\]

\paragraph{Dictionary.}
Definition of рқ‘қрқ‘Һрқ‘ҹрқ‘Ўрқ‘–рқ‘Һрқ‘ҷрқ‘ҹО©рқ‘’рқ‘һ0 рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО© вҖ” рқ‘қрқ‘Һрқ‘ҹрқ‘Ўрқ‘–рқ‘Һрқ‘ҷрқ‘ҹО©рқ‘’рқ‘һ0 рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО©=О©innerвҲ’О©outer рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО©рқ‘’рқ‘һ0=вҮ’Ggyroрқ‘’рқ‘һ0

\paragraph{Encyclopedia.}
Definition of рқ‘қрқ‘Һрқ‘ҹрқ‘Ўрқ‘–рқ‘Һрқ‘ҷрқ‘ҹО©рқ‘’рқ‘һ0 рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО© is an algebraic definition, written рқ‘қрқ‘Һрқ‘ҹрқ‘Ўрқ‘–рқ‘Һрқ‘ҷрқ‘ҹО©рқ‘’рқ‘һ0 рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО©=О©innerвҲ’О©outer рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО©рқ‘’рқ‘һ0=вҮ’Ggyroрқ‘’рқ‘һ0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from n, r, o, u, G, g, defining рқ‘қрқ‘Һрқ‘ҹрқ‘Ўрқ‘–рқ‘Һрқ‘ҷрқ‘ҹО©рқ‘’рқ‘һ0 рқҗ·рқ‘’рқ‘ҷрқ‘Ўрқ‘ҺО©. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
