\tzpanchor{0912}
\tzpentryheader{0912}{STEREOGRAPHIC TESSERACT UNFOLDING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{5c1b9b31-114c-5317-86fd-e531dbef574b}}\\
\textbf{PiID} & \tzpcode{7554687311595} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{919}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3487.1334 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.7457 rad}\\
\textbf{TZPID} & \tzpcode{ID0912} & \textbf{Node Dependencies}\quad \tzpidref{0911}\\
\textbf{Registry} & \tzpcode{registry\_id\_0912} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Aggregate Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
L = frac\{1\}\{4pi\}oint\_\{C\_\{1\}\}oint\_\{C\_\{2\}\}frac\{dvec\{r\} \{1\}x dvec\{r\} \{2\}*(vec\{r\} \{1\}-vec\{r\} \{2\})\}\{|vec\{r\} \{1\}-vec\{r\} \{2\}|\textasciicircum{}\{3\}\} in mathbb\{Z\}

\tzpsection{Canonical Equation}
\[
L = \frac{1}{4\pi}\oint_{C_{1}}\oint_{C_{2}}\frac{d\vec{r} {1}\times d\vec{r} {2}\cdot(\vec{r} {1}-\vec{r} {2})}{|\vec{r} {1}-\vec{r} {2}|^{3}} \in \mathbb{Z}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $\pi$: source equation symbol.
    \item $C_{1}$: source equation symbol.
    \item $C_{2}$: source equation symbol.
    \item $Z$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0912 generated source Wolfram model *)
ClearAll[K0912, Cr0912, T, R, A, W, I, N];
eq0912$1 = HoldForm[Element[L == (1/(4*Pi))*ContourIntegralC1*ContourIntegralC2[(dvec[r]*1*dvec[r]*2*(vec[r]*1 - vec[r]*2))/Abs[vec[r]*1 - vec[r]*2]^3], Z]];
eq0912$2 = HoldForm[mathcal[J]*_*out == TTZP[KTZP]];

K0912 = HoldForm[{eq0912$1, eq0912$2}];

N = "normalized TRAWIN closure object for STEREOGRAPHIC TESSERACT UNFOLDING";
I = "STEREOGRAPHIC TESSERACT UNFOLDING integration/comparison layer";
W = "STEREOGRAPHIC TESSERACT UNFOLDING wave or operator carrier";
A = "STEREOGRAPHIC TESSERACT UNFOLDING admissible action/amplitude condition";
R = "STEREOGRAPHIC TESSERACT UNFOLDING rotation/curl preservation layer";
T = "STEREOGRAPHIC TESSERACT UNFOLDING local source condition";

Cr0912[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0912 = Cr0912[K0912];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ STEREOGRAPHIC TESSERACT UNFOLDING local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ STEREOGRAPHIC TESSERACT UNFOLDING rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ STEREOGRAPHIC TESSERACT UNFOLDING admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ STEREOGRAPHIC TESSERACT UNFOLDING wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ STEREOGRAPHIC TESSERACT UNFOLDING integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for STEREOGRAPHIC TESSERACT UNFOLDING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0912] STEREOGRAPHIC TESSERACT UNFOLDING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
L = \frac{1}{4\pi}\oint_{C_{1}}\oint_{C_{2}}\frac{d\vec{r} {1}\times d\vec{r} {2}\cdot(\vec{r} {1}-\vec{r} {2})}{|\vec{r} {1}-\vec{r} {2}|^{3}} \in \mathbb{Z}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\paragraph{Primary Derivation.}
The expression \( L = \frac{1}{4\pi}\oint_{C_{1}}\oint_{C_{2}}\frac{d\vec{r} {1}\times d\vec{r} {2}\cdot(\vec{r} {1}-\vec{r} {2})}{|\vec{r} {1}-\vec{r} {2}|^{3}} \in \mathbb{Z} \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. Interpreted through TRAWIN, the equation functions as the integral carrier for the entry’s information content. According to CHL, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors STEREOGRAPHIC TESSERACT UNFOLDING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
L = \frac{1}{4\pi}\oint_{C_{1}}\oint_{C_{2}}\frac{d\vec{r} {1}\times d\vec{r} {2}\cdot(\vec{r} {1}-\vec{r} {2})}{|\vec{r} {1}-\vec{r} {2}|^{3}} \in \mathbb{Z}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0912] STEREOGRAPHIC TESSERACT UNFOLDING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
STEREOGRAPHIC TESSERACT UNFOLDING is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} L = frac 1 4pi oint sub C sub 1 oint sub C sub 2 frac dvec r 1 x dvec r 2 *(vec r 1 -vec r 2 ) |vec r 1 -vec r 2 | to the power 3 in mathbb Z. \textbf{Contextual meaning:} The entry reads STEREOGRAPHIC TESSERACT UNFOLDING as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Aggregate Relation; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, STEREOGRAPHIC TESSERACT UNFOLDING is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: L = ratio 1 4pi oint sub C sub 1 oint sub C sub 2 ratio dvec r 1 times dvec r 2 dot(vec r 1 -vec r 2 ) |vec r 1 -vec r 2 | to the power 3 in mathbb Z; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Hypersphere Surface Flattening}: The mathematical process of taking the impossible, 4D shape of the energy field and painstakingly unrolling it like a map so engineers can actually read it.
\item \textbf{Asymptotic Boundary Projection}: The realization that the very edges of the magnetic field stretch out to infinity, requiring special math just to draw them on a computer screen.
\item \textbf{Conformal Mapping Preservation}: The delicate technique of stretching and distorting the image of the plasma without accidentally changing any of the crucial angles where the magnetic lines intersect.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0912]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0912].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0912] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont STEREOGRAPHIC TESSERACT UNFOLDING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} STEREOGRAPHIC TESSERACT UNFOLDING is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``STEREOGRAPHIC TESSERACT UNFOLDING is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0912].
\par\endgroup
\vfill
\endgroup
\endgroup
