\section*{ID9412: Definition of рқңӢKK:PвҶ’рқ‘ҮвҲ—рқ‘„ рқҗәgauge}
\paragraph{Metadata.}
PiID: 3961225714298 | RTEID: RTE:P36548.8862:T3.6727 | UUID: 8226201e-67ec-5bb1-92c3-9287ff8fccc8

\paragraph{Canonical Statement.}
e Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0364], [ID 0300] Node registry\_id\_0365 Support Titles Configuration Manifold; KaluzaвҖ“Klein Sector; Gauge Quotient Test Handle If the coupled sector space cannot be formed as the stated gauge quotient of the configuration manifold, the entry fails. Canonical Equation Links P=рқ‘ҮвҲ—рқ‘„Г—рқ‘Ҷ1 KKГ—A \$рқңӢKK:PвҶ’рқ‘ҮвҲ—рқ‘„ рқҗәgauge=\{рқңҷ:R3вҶ’рқ‘Ҳ\$ (1) \$|вҲҮ2рқңҷ=0\}\$ [ID 0366] Magneto-Acoustic Hamiltonian Operator TZPID ID0366 UUID 90fa50ff-708a-5279-817f-81837f3d3d22 Type Dynamical / Variational Statement Scale field-dynamical LOC Classification Working routing: QC20.7 field theory; QA321 variational structure arXiv Classification Primary: hep-th; Cross-list: math-ph, gr-qc Canonical Statement This entry develops magneto-acoustic hamiltonian o

\paragraph{Canonical Equation.}
\[
рқңӢKK:PвҶ’рқ‘ҮвҲ—рқ‘„ рқҗәgauge={рқңҷ:R3вҶ’рқ‘Ҳ
\]

\paragraph{Dictionary.}
Definition of рқңӢKK:PвҶ’рқ‘ҮвҲ—рқ‘„ рқҗәgauge вҖ” рқңӢKK:PвҶ’рқ‘ҮвҲ—рқ‘„ рқҗәgauge=рқңҷ:R3вҶ’рқ‘Ҳ

\paragraph{Encyclopedia.}
Definition of рқңӢKK:PвҶ’рқ‘ҮвҲ—рқ‘„ рқҗәgauge is an algebraic definition, written рқңӢKK:PвҶ’рқ‘ҮвҲ—рқ‘„ рқҗәgauge=рқңҷ:R3вҶ’рқ‘Ҳ. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R, defining рқңӢKK:PвҶ’рқ‘ҮвҲ—рқ‘„ рқҗәgauge. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
