\tzpanchor{0647}
\tzpentryheader{0647}{MEDIATOR CHANNEL ENTANGLEMENT MAINTENANCE}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f7649106-40cf-5002-8caf-86faf16509e8}}\\
\textbf{PiID} & \tzpcode{8721468440901} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{654}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2485.2621 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.0949 rad}\\
\textbf{TZPID} & \tzpcode{ID0647} & \textbf{Node Dependencies}\quad \tzpidref{0646}\\
\textbf{Registry} & \tzpcode{registry\_id\_0647} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records mediator channel entanglement maintenance through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\frac{P(H_i\mid D)} {P(H_j\mid D)} = \frac{P(D\mid H_i)} {P(D\mid H_j)} \frac{P(H_i)} {P(H_j)}.
\]
\[
P(H_i\mid D) = \frac{P(D\mid H_i)P(H_i)} {P(D)}.
\]
\[
P(H_j\mid D) = \frac{P(D\mid H_j)P(H_j)} {P(D)}.
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $P$: source equation symbol.
    \item $H_i$: source equation symbol.
    \item $D$: source equation symbol.
    \item $H_j$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0647 generated source Wolfram model *)
ClearAll[K0647, Cr0647, T, R, A, W, I, N];
eq0647$1 = HoldForm[Tuple[P[HI, D]]/Tuple[P[HJ, D]] == (Tuple[P[D, HI]]/Tuple[P[D, HJ]])*(P[HI]/P[HJ])];
eq0647$2 = HoldForm[P[HI, D] == Tuple[P[D, HI]*P[HI]]/P[D]];
eq0647$3 = HoldForm[P[HJ, D] == Tuple[P[D, HJ]*P[HJ]]/P[D]];

K0647 = HoldForm[{eq0647$1, eq0647$2, eq0647$3}];

N = "normalized TRAWIN closure object for MEDIATOR CHANNEL ENTANGLEMENT MAINTENANCE";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Canonical Definition admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Canonical Definition local source condition";

Cr0647[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0647 = Cr0647[K0647];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Canonical Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Canonical Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for MEDIATOR CHANNEL ENTANGLEMENT MAINTENANCE.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0647] MEDIATOR CHANNEL ENTANGLEMENT MAINTENANCE}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{P(H_i\mid D)}
{P(H_j\mid D)}
=
\frac{P(D\mid H_i)}
{P(D\mid H_j)}
\frac{P(H_i)}
{P(H_j)} .
\end{equation}

\paragraph{Primary Derivation.}
Bayes' rule gives the posterior probability of a hypothesis $H_i$ after observing data $D$:

\begin{equation}
P(H_i\mid D)
=
\frac{P(D\mid H_i)P(H_i)}
{P(D)} .
\end{equation}

Likewise,

\begin{equation}
P(H_j\mid D)
=
\frac{P(D\mid H_j)P(H_j)}
{P(D)} .
\end{equation}

Taking the ratio cancels the evidence denominator $P(D)$:

\begin{equation}
\frac{P(H_i\mid D)}
{P(H_j\mid D)}
=
\frac{P(D\mid H_i)P(H_i)}
{P(D\mid H_j)P(H_j)} .
\end{equation}

Rearranging gives:

\begin{equation}
\boxed{
\frac{P(H_i\mid D)}
{P(H_j\mid D)}
=
\frac{P(D\mid H_i)}
{P(D\mid H_j)}
\frac{P(H_i)}
{P(H_j)} .
}
\end{equation}

\paragraph{Interpretation.}
This equation formalizes evidence accumulation: posterior odds equal likelihood ratio times prior odds.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors MEDIATOR CHANNEL ENTANGLEMENT MAINTENANCE by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Canonical Definition}\par
\[
\frac{P(H_i\mid D)} {P(H_j\mid D)} = \frac{P(D\mid H_i)} {P(D\mid H_j)} \frac{P(H_i)} {P(H_j)}.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
P(H_i\mid D) = \frac{P(D\mid H_i)P(H_i)} {P(D)}.
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
P(H_j\mid D) = \frac{P(D\mid H_j)P(H_j)} {P(D)}.
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0647] MEDIATOR CHANNEL ENTANGLEMENT MAINTENANCE}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
MEDIATOR CHANNEL ENTANGLEMENT MAINTENANCE is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} hat rho med = text Tr ext [|Psirangle langle Psi|] otimes text Topological Protection. \textbf{Contextual meaning:} The entry reads MEDIATOR CHANNEL ENTANGLEMENT MAINTENANCE as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This equation formalizes evidence accumulation: posterior odds equal likelihood ratio times prior odds.

\tzpsection{Equation Grounding}
Equation anchors: mathrm hat rho med = Tr ext [lvert Psi Psi |] otimes Topological Protection; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Middle-Man Coherence Shielding}: The heavy protection placed around the fragile, invisible wire connecting two distant quantum objects, ensuring the delicate link isn't severed by outside noise.
\item \textbf{Interstitial State Preservation}: The desperate fight to keep the empty space between the atoms just as perfectly still and quiet as the atoms themselves, so the shared magic doesn't leak out.
\item \textbf{Bridging-Tensor Stabilization}: The mathematical struts and supports bolted onto the fragile equations linking the two halves of the system, preventing the shared logic from collapsing.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0647]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0647_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0647] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont MEDIATOR CHANNEL ENTANGLEMENT MAINTENANCE}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records mediator channel entanglement maintenance through the Septenary
derivation layer, using the displayed relations as operational an...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``MEDIATOR CHANNEL ENTANGLEMENT MAINTENANCE is valid when the stated geometric or
topological relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0647_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
