\section*{ID9360: Definition of B𝜕Ω𝜙}
\paragraph{Metadata.}
PiID: 4004152970028 | RTEID: RTE:P36346.9586:T3.3399 | UUID: 2b317cf4-0ad2-505f-a393-40e423699ce4

\paragraph{Canonical Statement.}
cluded in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0054] Node registry\_id\_0055 Support Titles Confined Mode Family; Boundary Coefficient Decomposition; Boundary Effect Operator Test Handle If changing admissible boundary geometry leaves all mode amplitudes invariant when the model predicts a shift, this operator law fails. Canonical Equation Links 𝜙= \$∑\$ 𝑛 𝜙𝑛 𝑏𝑛=𝑏 geom 𝑛 +𝑏top 𝑛 +𝑏curv 𝑛 \$B𝜕Ω𝜙=\$ \$∑\$ 𝑛 𝑏𝑛 \$(𝜕Ω)\$ 𝜙𝑛 [ID 0056] Casimir-Type Phenomena TZPID ID0056 UUID 28e0092b-d55e-5f7e-a8c6-2530681b6422 Type Vacuum Energy Law Scale boundary vacuum interaction LOC Classification Working routing: QC793.5 Casimir effect; QC174.12 vacuum energy shifts arXiv Classification Primary: hep-th Cross-list: quant-ph, gr-qc Canonical Statement Boundary-separated vacuum modes generate a measurable energ

\paragraph{Canonical Equation.}
\[
B𝜕Ω𝜙=
\]

\paragraph{Dictionary.}
Definition of B𝜕Ω𝜙 — B𝜕Ω𝜙=

\paragraph{Encyclopedia.}
Definition of B𝜕Ω𝜙 is an algebraic definition, written B𝜕Ω𝜙=. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
