\section*{ID9114: Definition of U(γ)|ψ\_0⟩ψobs〉}
\paragraph{Metadata.}
PiID: 5261793780029 | RTEID: RTE:P35391.6860:T1.7659 | UUID: 76fcb792-7672-5654-ab80-eb37ab345f72

\paragraph{Canonical Statement.}
vasive measurement schemes; interplay with observerdependent states. Falsifiability / Test Handle: Measurements that show no backaction where predicted, or excessive backaction beyond predictions, would refute this operator. 0.0.66 ID 064: ObserverDependent Quantum States Type: Structural Constraint Formal Statement: The state \$ψ〉|\textbackslash{}psi\textbackslash{}rangleψ〉\$ assigned to a system depends on the observer’s trajectory through the Trawinistic manifold; specifically, \$ψobs〉=U(γ)ψ0〉|\textbackslash{}psi\_\{\textbackslash{}text\{obs\}\}\textbackslash{}rangle\$ = \$U(\textbackslash{}gamma)|\textbackslash{}psi\_0\textbackslash{}rangleψobs〉=U(γ)ψ0〉,\$ where \$U(γ)U(\textbackslash{}gamma)U(γ)\$ is a unitary transformation determined by the observer’s worldline \$γ\textbackslash{}gammaγ\$ and the temporal displacement factor. Interpretive Meaning: Different observers may assign different states to the same physical system because of their distinct motions in curved space; there is no absolute state independent of the observer. Dependencies: ID 007, ID 019 Derivable Consequence

\paragraph{Canonical Equation.}
\[
U(\gamma)|\psi_0\rangleψobs〉=U(γ)ψ0〉,
\]

\paragraph{Dictionary.}
Definition of U(γ)|ψ\_0⟩ψobs〉 — U(γ)|ψ\_0⟩ψobs〉=U(γ)ψ0〉

\paragraph{Encyclopedia.}
Definition of U(γ)|ψ\_0⟩ψobs〉 is an algebraic definition, written U(γ)|ψ\_0⟩ψobs〉=U(γ)ψ0〉. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from U, defining U(γ)|ψ\_0⟩ψobs〉. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
