\section*{ID8902: ROTATING DOUBLE HELIX GEOMETRY Canonical Statutory Formula: s\_1,2(t, Ω)}
\paragraph{Metadata.}
PiID: 8964766975831 | RTEID: RTE:P34568.4429:T0.4095 | UUID: 91d57c53-95e7-5688-a8a4-b7ddbb010444

\paragraph{Canonical Statement.}
[ID 932] ROTATING DOUBLE HELIX GEOMETRY Canonical Statutory Formula: \$s\_\{1,2\}(t, \textbackslash{}Omega) = R(\textbackslash{}Omega t)(R \textbackslash{}cos(2\textbackslash{}pi t/P + \textbackslash{}phi), R \textbackslash{}sin(2\textbackslash{}pi t/P + \textbackslash{}phi), t)\$ Formal Technical Dissertation: Parametrizes the optical propagation medium as two helical strands undergoing temporal rotation \$\textbackslash{}Omega\$. This geometry generates a 4D manifold of light paths used for quantum holographic navigation, defining the linking number and curvature/torsion modulations required for the Blob-Bit interface. Source: [3], [4]

\paragraph{Canonical Equation.}
\[
s_{1,2}(t, \Omega) = R(\Omega t)(R \cos(2\pi t/P + \phi), R \sin(2\pi t/P + \phi), t)
\]

\paragraph{Dictionary.}
ROTATING DOUBLE HELIX GEOMETRY Canonical Statutory Formula: \$s\_1,2(t, ) = R( t)(R (2 t/P + ), R (2 t/P + ), t)\$ Formal Technical Dissertation: Parametrizes the optical propagation medium as two helical strands undergoing temporal rotation Ω.

\paragraph{Encyclopedia.}
ROTATING DOUBLE HELIX GEOMETRY Canonical Statutory Formula: s\_1,2(t, Ω) is an algebraic definition, written s\_1,2(t, Ω) = R(Ω t)(R cos(2π t/P + φ), R sin(2π t/P + φ), t). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from Ω, π, φ, R, P, defining s\_1,2(t, Ω). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
