\tzpanchor{0224}
\tzpentryheader{0224}{Persistent Entropy}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{31fd56d1-8ec4-56a2-9780-8a67de8b1252}}\\
\textbf{PiID} & \tzpcode{5648233786783} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{231}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{869.8417 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.4332 rad}\\
\textbf{TZPID} & \tzpcode{ID0224} & \textbf{Node Dependencies}\quad \tzpidref{0223}\\
\textbf{Registry} & \tzpcode{registry\_id\_0224} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Entropy Weight & Normalized Distribution\\
\textbf{Closure Support} & Topological Aggregate & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Let H0, H1 and H2 denote the persistent entropies derived from a persistence diagram. They quantify the diversity of lifetimes of topological features of dimensions 0 (components), 1 (loops) and 2 (voids) respectively. High values indicate many features with varied persistence, while low values indicate few long-lived features.

\tzpsection{Canonical Equation}
\[
p_i=\frac{\ell_i}{\sum_j \ell_j}
\]
\[
H_k=-\sum_{i\in D_k}p_i\log p_i
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $p_i$: source equation symbol.
    \item $H_k$: source equation symbol.
    \item $D_k$: source equation symbol.
    \item $H_{\mathrm{pers}}$: source equation symbol.
    \item $H_0$: Hubble-scale or global comparison parameter.
    \item $H_1$: source equation symbol.
    \item $H_2$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0224 generated source Wolfram model *)
ClearAll[K0224, Cr0224, T, R, A, W, I, N];
eq0224$1 = HoldForm[pI == ellI/(SumJ*ellJ)];
eq0224$2 = HoldForm[HK == -Sum[p[i]*Log[p[i]], {i, DK}]];
eq0224$3 = HoldForm[HPers == H0 + H1 + H2];

K0224 = HoldForm[{eq0224$1, eq0224$2, eq0224$3}];

N = "normalized TRAWIN closure object for Persistent Entropy";
I = "Topological Aggregate integration/comparison layer";
W = "Normalized Distribution wave or operator carrier";
A = "Entropy Weight admissible action/amplitude condition";
R = "Normalized Distribution rotation/curl preservation layer";
T = "Entropy Weight local source condition";

Cr0224[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0224 = Cr0224[K0224];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Entropy Weight local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Normalized Distribution rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Entropy Weight admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Normalized Distribution wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Aggregate integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Persistent Entropy.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0224] Persistent Entropy}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_T^4}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,
\hbar\omega\,
\mathrm{d}\omega .
\end{equation}

\paragraph{Primary Derivation.}
Each vacuum mode of frequency $\omega$ contributes energy proportional to:

\begin{equation}
\hbar\omega .
\end{equation}

The spectral density index $\eta(\omega)$ weights the contribution of each frequency:

\begin{equation}
\eta(\omega)\hbar\omega .
\end{equation}

Integrating over all allowed frequencies up to the cutoff $\omega_{\mathrm{cut}}$ gives the weighted vacuum energy:

\begin{equation}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\hbar\omega\,\mathrm{d}\omega .
\end{equation}

To convert this to a density in Trawin units, divide by the fourth power of the base unit:

\begin{equation}
u_T^4 .
\end{equation}

Therefore,

\begin{equation}
\boxed{
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_T^4}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,
\hbar\omega\,
\mathrm{d}\omega .
}
\end{equation}

\paragraph{Interpretation.}
$\rho_{\mathrm{vac}}^{T}$ defines vacuum energy density as a spectral integral normalized by the four-dimensional Trawin base scale.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Persistent Entropy by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Entropy Weight}\par
\[
p_i=\frac{\ell_i}{\sum_j \ell_j}
\]
\noindent This records the local information weight carried by the persistence data or structural channel.\par
\noindent\textbf{2. Normalized Distribution}\par
\[
H_k=-\sum_{i\in D_k}p_i\log p_i
\]
\noindent This makes the entropy law admissible by normalizing the supporting lifetimes or amplitudes.\par
\noindent\textbf{3. Topological Aggregate}\par
\[
H_{\mathrm{pers}}=H_0+H_1+H_2
\]
\noindent This closes the entry by recombining the filtered sectors into one total diagnostic.\par

\clearpage
\noindent\textbf{[ID 0224] Persistent Entropy}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Persistent Entropy is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Let H0, H1 and H2 denote the persistent entropies derived from a persistence diagram. They quantify the diversity of lifetimes of topological features of dimensions 0 (components), 1 (loops) and 2 (voids) respectively. High values indicate many features with varied persistence, while low values indicate few long-lived features. \textbf{Contextual meaning:} The entry reads Persistent Entropy as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers. \textbf{Lemma support:} Entropy Weight; Normalized Distribution; Topological Aggregate.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub vac to the power T defines vacuum energy density as a spectral integral normalized by the four-dimensional Trawin base scale.

\tzpsection{Equation Grounding}
Equation anchors: p sub i=ratio ell sub i sum sub j ell sub j; H sub k=-sum sub iin D sub k p sub ilog p sub i; and H sub pers =H sub 0+H sub 1+H sub 2. Proof route: show that the normalized support distribution induces a well-defined entropy functional for the stated topological or informational channel. Formalization route: prove that positivity and normalization of the support weights imply finiteness of the stated entropy functional.

\tzpsection{Interpretive Role}
The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Topological Lifetime Informational Weight}: The measurement of information content based on how long specific topological features endure across different scale thresholds.
\item \textbf{Entropy of Homological Feature Persistence}: The Shannon-like entropy calculated from the distribution of lifespans of holes, voids, and connected components in a dataset.
\item \textbf{Scale-Spanning Structural Complexity}: A single scalar value summarizing the robustness and complexity of an object's geometry across all observable resolutions.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0224]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0224_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0224] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Persistent Entropy}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} let H0, H1 and H2 denote the persistent entropies derived from a persistence diagram

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Persistent Entropy is valid when the stated geometric or topological relation preserves
its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0224_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
