\tzpanchor{0695}
\tzpentryheader{0695}{Semi-Direct Product of Rotation and Gauge Symmetry}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{d6ccd557-7c97-57b8-ba5b-83b34b91904b}}\\
\textbf{PiID} & \tzpcode{8923542019956} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{702}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2667.7736 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.3957 rad}\\
\textbf{TZPID} & \tzpcode{ID0695} & \textbf{Node Dependencies}\quad \tzpidref{0694}\\
\textbf{Registry} & \tzpcode{registry\_id\_0695} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records semi-direct product of rotation and gauge symmetry through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\eta:S\circ F\Rightarrow F\circ S.
\]
\[
\eta_X^{*}\omega_{F\circ S(X)} = \omega_{S\circ F(X)}.
\]
\[
S\circ F, \qquad F\circ S.
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S$: source equation symbol.
    \item $F$: source equation symbol.
    \item $X$: source variable, local coordinate, or input state in the entry relation.
    \item $\mathcal{K}_{0695}$: canonical registry object for entry ID 0695.
    \item $\eta$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $X^{*}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0695 generated source Wolfram model *)
ClearAll[K0695, Cr0695, T, R, A, W, I, N];
eq0695$1 = HoldForm[eta:Scirc*F -> Fcirc*S];
eq0695$2 = HoldForm[etaXDaggeromegaFcircSX == omegaScircFX];
eq0695$3 = HoldForm[TZPSequence[Scirc*F, Fcirc*S]];

K0695 = HoldForm[{eq0695$1, eq0695$2, eq0695$3}];

N = "normalized TRAWIN closure object for Semi-Direct Product of Rotation and Gauge Symmetry";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0695[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0695 = Cr0695[K0695];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Semi-Direct Product of Rotation and Gauge Symmetry.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0695] Semi-Direct Product of Rotation and Gauge Symmetry}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\eta:S\circ F\Rightarrow F\circ S.
\end{equation}

\paragraph{Symplectic Preservation Law.}
\begin{equation}
\eta_X^{*}\omega_{F\circ S(X)}
=
\omega_{S\circ F(X)}.
\end{equation}

\paragraph{Primary Derivation.}
Let $S$ be a scaling functor and $F$ a structure functor.  
There are two routes:

\begin{equation}
S\circ F,
\qquad
F\circ S.
\end{equation}

A natural transformation compares these routes:
\begin{equation}
\eta:S\circ F\Rightarrow F\circ S.
\end{equation}

To preserve dynamics, the bridge must preserve the symplectic form:
\begin{equation}
\boxed{
\eta_X^{*}\omega_{F\circ S(X)}
=
\omega_{S\circ F(X)}.
}
\end{equation}

\paragraph{Interpretation.}
Scaling and structural translation are compatible only when the categorical bridge preserves phase-space geometry.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Semi-Direct Product of Rotation and Gauge Symmetry by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
\eta:S\circ F\Rightarrow F\circ S.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\eta_X^{*}\omega_{F\circ S(X)} = \omega_{S\circ F(X)}.
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
S\circ F, \qquad F\circ S.
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0695] Semi-Direct Product of Rotation and Gauge Symmetry}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Semi-Direct Product of Rotation and Gauge Symmetry is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} alpha(t)alpha(t)alpha(t). \textbf{Contextual meaning:} The entry reads Semi-Direct Product of Rotation and Gauge Symmetry as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Scaling and structural translation are compatible only when the categorical bridge preserves phase-space geometry.

\tzpsection{Equation Grounding}
Equation anchors: (T:,partial/partial t); (A:,A(x,t)); and (I:,integral rho(x,t),dV). Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spin-Twist Mathematical Entanglement}: The incredibly annoying realization that you can't just spin the machine in a circle; doing so instantly, accidentally tangles up all the invisible, abstract quantum math happening inside it.
\item \textbf{Lorentz-Invariant Frame Mixing}: The deep, relativistic proof that the laws of electromagnetism don't care if the room is spinning, as long as you remember to mix the 'time' math and the 'space' math together perfectly.
\item \textbf{Broken-Symmetry Restoration Attempts}: The desperate mathematical twisting required to prove that the messy, warped, lopsided reality we see is actually just a perfect, beautiful sphere that got slightly smeared.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0695]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0695_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0695] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Semi-Direct Product of Rotation and Gauge Symmetry}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records semi-direct product of rotation and gauge symmetry through the
Septenary derivation layer, using the displayed relations as opera...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Semi-Direct Product of Rotation and Gauge Symmetry is valid as a formal registry
statement when its source equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that the entry records semi-direct product of rotation and
gauge symmetry through the Septenary derivation layer, using the displayed relations as
operational anchors for the canonical equation chain. Scaling and structural translation
are compatible only when the categorical bridge preserves phase-space geometry. --------
----------------------------------------------------------------------------------------
------------------------. The CHL validation treats the equation as the formal anchor
and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0695_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
