\tzpanchor{0266}
\tzpentryheader{0266}{Linking Number Conservation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{af166920-0daa-544b-afdb-d3ec5ab10450}}\\
\textbf{PiID} & \tzpcode{8610454326648} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{273}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1032.9371 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.7020 rad}\\
\textbf{TZPID} & \tzpcode{ID0266} & \textbf{Node Dependencies}\quad \tzpidref{0265}\\
\textbf{Registry} & \tzpcode{registry\_id\_0266} & \textbf{Scale}\quad diagnostic\\
\textbf{LOC Classification} & QA273 dimensionless analysis & QC statistical diagnostics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: nlin.PS, physics.data-an\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The total helicity is conserved by transferring twist into writhing and vice versa; topological invariants control the dynamics of flux tubes.

\tzpsection{Canonical Equation}
\[
N_{modes} = \frac{4\pi R^2}{\lambda^2} \cdot \frac{\Delta\omega}{\omega_0}
\]
\[
frac{S_{inst}}{\hbar} \sim 1 \quad \Rightarrow \quad d_{critical} \approx \left(\frac{\hbar^2}{2m_{eff}\mu_0\mu^2}\right)^{1/5}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $N_{modes}$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\lambda$: cosmological or lemniscatic branch parameter in the entry relation.
    \item $\omega$: angular frequency term in the source equation.
    \item $\omega_0$: angular frequency term in the source equation.
    \item $S_{inst}$: source equation symbol.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
    \item $d_{critical}$: source equation symbol.
    \item $m_{eff}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0266 generated source Wolfram model *)
ClearAll[K0266, Cr0266, T, R, A, W, I, N];
eq0266$1 = HoldForm[NModes == ((4*Pi*R^2)/lambda^2)*(Deltaomega/omega0)];
eq0266$2 = HoldForm[SimilarTo[frac[SInst]*hbar, 1 -> dCritical == (hbar^2/(2*mEffmu0*mu^2))^(1/5)]];

K0266 = HoldForm[{eq0266$1, eq0266$2}];

N = "normalized TRAWIN closure object for Linking Number Conservation";
I = "Normalized Regime integration/comparison layer";
W = "Scaling Relation wave or operator carrier";
A = "Diagnostic Definition admissible action/amplitude condition";
R = "Scaling Relation rotation/curl preservation layer";
T = "Diagnostic Definition local source condition";

Cr0266[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0266 = Cr0266[K0266];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Diagnostic Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Scaling Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Diagnostic Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Scaling Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Regime integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Linking Number Conservation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0266] Linking Number Conservation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\delta S = 0.
\end{equation}

\paragraph{Primary Derivation.}
Dominant contributions to path integral arise from stationary action paths.

Thus classical trajectories satisfy:
\begin{equation}
\boxed{\delta S = 0.}
\end{equation}

\paragraph{Interpretation.}
Classical paths emerge from quantum stationary phase.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Linking Number Conservation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Diagnostic Definition}\par
\[
N_{modes} = \frac{4\pi R^2}{\lambda^2} \cdot \frac{\Delta\omega}{\omega_0}
\]
\noindent This defines the scalar diagnostic or conversion quantity named by the title.\par
\noindent\textbf{2. Scaling Relation}\par
\[
frac{S_{inst}}{\hbar} \sim 1 \quad \Rightarrow \quad d_{critical} \approx \left(\frac{\hbar^2}{2m_{eff}\mu_0\mu^2}\right)^{1/5}
\]
\noindent This elevates the quantity into a comparative scaling or correlation law.\par
\noindent\textbf{3. Normalized Regime}\par
\[
N_{modes} = \frac{4\pi R^2}{\lambda^2} \cdot \frac{\Delta\omega}{\omega_0}
\]
\noindent This closes the entry by normalizing the diagnostic against a stated reference regime.\par

\clearpage
\noindent\textbf{[ID 0266] Linking Number Conservation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Linking Number Conservation is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The total helicity is conserved by transferring twist into writhing and vice versa; topological invariants control the dynamics of flux tubes. \textbf{Contextual meaning:} The entry reads Linking Number Conservation as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons. \textbf{Lemma support:} Diagnostic Definition; Scaling Relation; Normalized Regime.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Classical paths emerge from quantum stationary phase.

\tzpsection{Equation Grounding}
Equation anchors: frac d H dt = chi sub helix dot ( S sub photon times boldsymbol mu sub eff ); frac S sub inst hbar similar to 1 Rightarrow d sub critical approximately (ratio hbar to the power 2 2m sub eff mu sub 0mu to the power 2 ) to the power 1/5; and N sub modes = ratio 4pi R to the power 2 lambda to the power 2 dot ratio Deltaomega omega sub 0. Proof route: show that the named quantity is dimensionless or consistently scaled in the regime stated by the entry. Formalization route: prove that the normalized diagnostic remains invariant under the intended rescaling.

\tzpsection{Interpretive Role}
The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Preservation of Flux Tube Entanglement}: The rigid physical law stating that once two magnetic or fluid vortex tubes are linked together like a chain, they cannot pass through one another.
\item \textbf{Gauss Integral Continuity Under Evolution}: The mathematical guarantee that the specific equation calculating the number of geometric linkages remains perfectly constant as the system moves and ages.
\item \textbf{Unbreakable Magnetic Knot Topologies}: The consequence of ideal plasma physics which dictates that the fundamental knot structure of a magnetic field is immortal and cannot be untied by continuous motion.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0266]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0266_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0266] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Linking Number Conservation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the total helicity is conserved by transferring twist into writhing and vice versa;
topological invariants control the dynamics of flux tubes

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Linking Number Conservation is valid when the total tensorial quantity is conserved
under the stated constraint.''\\
\textbf{Proof:} The source statement identifies a conserved balance law. Reading 0266 as a proposition,
validity follows by requiring the full stress, flux, or current contribution to be
included before the divergence or balance condition is evaluated.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conserved total-structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0266_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
