\tzpanchor{0215}
\tzpentryheader{0215}{Directional Gravity Negation Stage}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{740a6a7c-c430-51f1-b96c-e1c99fb84343}}\\
\textbf{PiID} & \tzpcode{3446128475648} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{222}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{834.8927 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.3756 rad}\\
\textbf{TZPID} & \tzpcode{ID0215} & \textbf{Node Dependencies}\quad \tzpidref{0214}\\
\textbf{Registry} & \tzpcode{registry\_id\_0215} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In a three-layer gyroscopic device, the top shell experiences maximum gravity negation (about 90 per cent), the middle shell acts as a gyromagnetic rotor, and the bottom shell maintains constrained dipoles, thereby producing directional thrust.

\tzpsection{Canonical Equation}
\[
P(x,t) = g(x) - F(x,t)
\]
\[
B_{\mathrm{Vimana}}(t) = D(\theta,\varphi) \cdot R_{\mathrm{gyro}}(\omega_{\mathrm{gyro}} t)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $P$: source equation symbol.
    \item $t$: source equation symbol.
    \item $F$: source equation symbol.
    \item $B_{\mathrm{Vimana}}(t)$: source equation symbol.
    \item $D$: source equation symbol.
    \item $\theta$: phase angle or local angular coordinate.
    \item $R_{\mathrm{gyro}}$: source equation symbol.
    \item $\omega_{\mathrm{gyro}}$: gyroscopic angular frequency correction.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0215 generated source Wolfram model *)
ClearAll[K0215, Cr0215, T, R, A, W, I, N];
eq0215$1 = HoldForm[P[x, t] == g[x] - F[x, t]];
eq0215$2 = HoldForm[BVimana[t] == D[theta, phi]*RGyro[omegaGyro*t]];

K0215 = HoldForm[{eq0215$1, eq0215$2}];

N = "normalized TRAWIN closure object for Directional Gravity Negation Stage";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0215[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0215 = Cr0215[K0215];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Directional Gravity Negation Stage.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0215] Directional Gravity Negation Stage}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\eta(\omega)
=
\omega^{-\beta}
e^{-\omega/\omega_0}.
\end{equation}

\paragraph{Primary Derivation.}
Let $\omega$ be a frequency variable and let $\omega_0$ be the characteristic cutoff frequency determined by the Trawin base unit.

A scale-sensitive spectral law begins with a power term:

\begin{equation}
\omega^{-\beta},
\end{equation}

where $\beta$ controls low-frequency or scale-weighted behavior.

To suppress high-frequency divergence, introduce the exponential cutoff:

\begin{equation}
e^{-\omega/\omega_0}.
\end{equation}

Multiplying the two factors gives the TZP-weighted spectral density index:

\begin{equation}
\boxed{
\eta(\omega)
=
\omega^{-\beta}
e^{-\omega/\omega_0}.
}
\end{equation}

\paragraph{Interpretation.}
$\eta(\omega)$ weights frequency contributions by combining power-law scaling with exponential cutoff suppression.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Directional Gravity Negation Stage by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
P(x,t) = g(x) - F(x,t)
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
B_{\mathrm{Vimana}}(t) = D(\theta,\varphi) \cdot R_{\mathrm{gyro}}(\omega_{\mathrm{gyro}} t)
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
B_{\mathrm{Vimana}}(t) = D(\theta,\varphi) \cdot R_{\mathrm{gyro}}(\omega_{\mathrm{gyro}} t)
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0215] Directional Gravity Negation Stage}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Directional Gravity Negation Stage is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} In a three-layer gyroscopic device, the top shell experiences maximum gravity negation (about 90 per cent), the middle shell acts as a gyromagnetic rotor, and the bottom shell maintains constrained dipoles, thereby producing directional thrust. \textbf{Contextual meaning:} The entry reads Directional Gravity Negation Stage as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform tertiary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Directional gravity negation is treated as a staged field response: the gyroscopic rotor supplies the rotating carrier, constrained dipoles stabilize the field orientation, and the top shell records the directional reduction channel.

\tzpsection{Equation Grounding}
Equation anchors:
\[
P(x,t)=g(x)-F(x,t),
\qquad
B_{\mathrm{Vimana}}(t)=D(\theta,\varphi)\cdot R_{\mathrm{gyro}}(\omega_{\mathrm{gyro}}t),
\]
with staged shell response
\[
\Delta g_{\mathrm{top}}\approx0.9\,g,\qquad
F_{\mathrm{thrust}}\propto \Delta g_{\mathrm{top}}.
\]
Proof route: show that the staged field relations remain compatible under the TRAWIN ordering. Formalization route: prove that the final directional-thrust relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform tertiary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Asymmetric Metric Stress Modification}: The hypothetical localized altering of spacetime curvature to create a net zero or reversed gravitational gradient.
\item \textbf{Orientation-Dependent Lift Operator}: The vector alignment required to couple electromagnetic or resonant phenomena to a counter-gravitational response.
\item \textbf{Shielded Tensor Contraction Zone}: A mathematically bounded region where the contraction of the stress-energy tensor produces effectively null local gravity.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0215]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0215_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0215] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Directional Gravity Negation Stage}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in a three-layer gyroscopic device, the top shell experiences maximum gravity negation
(about 90 per cent), the middle shell acts as a gyromagnetic...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Directional Gravity Negation Stage is valid as a spectral relation when frequency,
phase, and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0215_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
