\section*{ID7534: Next Steps I Can Do Now (Pick One or More): k\_2,Q}
\paragraph{Metadata.}
PiID: 6482363414334 | RTEID: RTE:P29256.1951:T4.2229 | UUID: 5a37ce06-743f-5b2b-88c8-e1bb1b6909b6

\paragraph{Canonical Statement.}
\# Next steps I can do now (pick one or more) 1. **Export a runnable Jupyter notebook** containing the exact code and plots I ran (so you can open/run it locally). 2. **Re-run the toy simulation with stronger/targeted couplings** to illustrate resonance capture (e.g., tune parameters to show partial synchronization in the inner ring or a Laplace-like chain). 3. **Compute and print specific numeric DSS examples** (exact a\_DSS in AU) for particular object sizes you care about (e.g., 1 km, 10 km, 100 km bodies) and specific T\_sys values. 4. **Upgrade the model physics**: add eccentricity dependence, include planet migration, or model spin–orbit higher harmonics (so we can test Mercury-like 3:2 captures). 5. **Make the model more realistic** for a moon system (use Saturn/Jupiter as primary, use measured \textbackslash{}(k\_2,Q\textbackslash{}) for moons, include moons’ mutual torques). 6. **Produce publication-ready figures** and a short technical writeup (equations + results + interpretation) naming the tidal criterion explicitly as the *DAT-GPT Tidal Locking Criterion* and the radius as the *DAT-GPT Synchronization Sphere (DSS)*.

\paragraph{Canonical Equation.}
\[
k_2,Q
\]

\paragraph{Dictionary.}
Relation: k\_2,Q

\paragraph{Encyclopedia.}
Next Steps I Can Do Now (Pick One or More): k\_2,Q is a symbolic expression, written k\_2,Q. It introduces a symbol or relation used elsewhere in the framework. It is built from k\_2, Q. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
