\section*{ID7507: Tests \& Observable Predictions (How to Falsify / Confirm DAT-GPT): ξ\textasciicircum{}(O)}
\paragraph{Metadata.}
PiID: 9612071512491 | RTEID: RTE:P29151.3481:T4.0502 | UUID: 9cbc5402-f53a-5dc7-b816-91278a573173

\paragraph{Canonical Statement.}
\# 9 — Tests \& observable predictions (how to falsify / confirm DAT-GPT) 1. Compute \textbackslash{}(a\_\{\textbackslash{}rm DSS\}\textbackslash{}) for a range of body sizes and \textbackslash{}(T\_\{\textbackslash{}rm sys\}\textbackslash{}) values (10\textasciicircum{}6 yr disk time → 4.5×10\textasciicircum{}9 yr age) — predict maximum radius where tidal locking occurs within these times. Compare to observed locked moons/planets. 2. Simulate a planetesimal disk with and without a giant perturber (Jupiter) — DAT-GPT predicts suppression of accretion when the giant is present due to increased \textbackslash{}(\textbackslash{}xi\textasciicircum{}\{(O)\}\textbackslash{}) and resonance kernels. 3. Model tidal locking times for known satellites vs measured spin states — check agreement. 4. For exoplanet systems, predict which close-in planets should be synchronized and which should be in higher order spin–orbit resonances depending on \textbackslash{}(Q,k\_2\textbackslash{}) — compare with observations (e.g., tidally locked hot super-Earths vs non-locked).

\paragraph{Canonical Equation.}
\[
\xi^{(O)}
\]

\paragraph{Dictionary.}
Relation: ξ\textasciicircum{}(O) [ID7507]

\paragraph{Encyclopedia.}
Tests \& Observable Predictions (How to Falsify / Confirm DAT-GPT): ξ\textasciicircum{}(O) is a symbolic expression, written ξ\textasciicircum{}(O). It introduces a symbol or relation used elsewhere in the framework. It is built from ξ, O. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
