\section*{ID8572: Definition of N}
\paragraph{Metadata.}
PiID: 0290951702835 | RTEID: RTE:P33286.9796:T4.5812 | UUID: a5a90d82-69e3-509c-a06c-b5c5d49b0a34

\paragraph{Canonical Statement.}
ula: B = \$µ0µr(H \$ +M) \$=⇒ dω \$ \$dt \$ = \$−γ(ω \$ − \$ω0) −K sin(2(θ \$ − \$θ0)) \$ Formal Technical Dissertation: Defines the electromagnetic properties of the rotating steering mechanism. The core operates under "Pi-Model" synchronization logic, utilizing a − \$sin(2∆θ) \$ torque profile to enable bi-stable phase-locking at 180-degree intervals. Source: [ID 1051] 12-NODE MULTI-PHASE TRANSDUCER SYNCHRONIZATION Canoni-cal Statutory Formula: \$Vnode(t) \$ = \$∑12\$ \$n=1 V0 \$ sin ( \$ω0t+ \$ \$nπ \$ 6 + \$ϕsync \$ ) \$⊗ δPi(∆θ) \$ Formal Technical Dissertation: The electrical drive protocol for the 12-node phased-array. It generates a rotating electromagnetic well with Pi-Model logic, allowing the core to "slip" by 180 degrees without losing frequency lock, ensuring causal continuity. Source: [ID 1052] CRYOGENIC SUPERCONDUCTING RAIL ALIGNMENT Canonical Statu-tor

\paragraph{Canonical Equation.}
\[
n=1 V0
\]

\paragraph{Dictionary.}
Definition of N — n=1 V0

\paragraph{Encyclopedia.}
Definition of N is an algebraic definition, written n=1 V0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from V, defining n. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
