\tzpanchor{0296}
\tzpentryheader{0296}{Westward Drift and Phase Lag Correlation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{97f9d8e4-8741-5d96-961e-e4d8487546b9}}\\
\textbf{PiID} & \tzpcode{1273724587006} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{303}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1149.4337 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.8939 rad}\\
\textbf{TZPID} & \tzpcode{ID0296} & \textbf{Node Dependencies}\quad \tzpidref{0295}\\
\textbf{Registry} & \tzpcode{registry\_id\_0296} & \textbf{Scale}\quad diagnostic\\
\textbf{LOC Classification} & QA273 dimensionless analysis & QC statistical diagnostics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: nlin.PS, physics.data-an\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Westward drift of magnetic features and azimuthal phase lag in gyroscopic systems correspond to Earth's westward secular variation and solar torsional oscillations, yielding a correlation of about 0.73.

\tzpsection{Canonical Equation}
\[
Then C=153,600/129,600=1
\]
\[
C = 153\{,\}600 / 129\{,\}600 = 1
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $C$: speed of light or relativistic conversion factor.
    \item $\mathcal{K}_{0296}$: canonical registry object for entry ID 0296.
    \item $T$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0296 generated source Wolfram model *)
ClearAll[K0296, Cr0296, T, R, A, W, I, N];
eq0296$1 = HoldForm[TZPSequence[Then*C == 153, 600/129, 600 == 1]];
eq0296$2 = HoldForm[C == 153600/129600];
eq0296$3 = HoldForm[TZPSequence[C == 153, 600/129, 600 == 1]];

K0296 = HoldForm[{eq0296$1, eq0296$2, eq0296$3}];

N = "normalized TRAWIN closure object for Westward Drift and Phase Lag Correlation";
I = "Normalized Regime integration/comparison layer";
W = "Scaling Relation wave or operator carrier";
A = "Diagnostic Definition admissible action/amplitude condition";
R = "Scaling Relation rotation/curl preservation layer";
T = "Diagnostic Definition local source condition";

Cr0296[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0296 = Cr0296[K0296];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Diagnostic Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Scaling Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Diagnostic Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Scaling Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Regime integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Westward Drift and Phase Lag Correlation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0296] Westward Drift and Phase Lag Correlation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Continuity Constraint.}
\begin{equation}
\partial_r(rv_r)+\partial_z(zv_z)=0.
\end{equation}

\paragraph{Resonance Operator.}
\begin{equation}
\mathcal{R}_{\mathrm{EHD}}[\mathbf{v}]
=
-\frac{\nabla p}{\rho}
+
\frac{q}{m}
(\mathbf{E}+\mathbf{v}\times\mathbf{B}).
\end{equation}

\paragraph{Mode Selection.}
\begin{equation}
\mathcal{R}_{\mathrm{EHD}}[\mathbf{v}_k]
=
\lambda_k\mathbf{v}_k.
\end{equation}

\paragraph{Primary Derivation.}
The admissible axisymmetric flow space is constrained by:
\begin{equation}
\partial_r(rv_r)+\partial_z(zv_z)=0.
\end{equation}

Pressure and electromagnetic forcing define the total acceleration operator:
\begin{equation}
\mathcal{R}_{\mathrm{EHD}}[\mathbf{v}]
=
-\frac{\nabla p}{\rho}
+
\frac{q}{m}
(\mathbf{E}+\mathbf{v}\times\mathbf{B}).
\end{equation}

Resonant modes are those reproduced by the operator up to scale:
\begin{equation}
\boxed{
\mathcal{R}_{\mathrm{EHD}}[\mathbf{v}_k]
=
\lambda_k\mathbf{v}_k.
}
\end{equation}

\paragraph{Interpretation.}
The EHD resonance operator identifies flow modes amplified by pressure and electromagnetic forcing.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Westward Drift and Phase Lag Correlation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Diagnostic Definition}\par
\[
Then C=153,600/129,600=1
\]
\noindent This defines the scalar diagnostic or conversion quantity named by the title.\par
\noindent\textbf{2. Scaling Relation}\par
\[
C = 153\{,\}600 / 129\{,\}600 = 1
\]
\noindent This elevates the quantity into a comparative scaling or correlation law.\par
\noindent\textbf{3. Normalized Regime}\par
\[
C=153,600/129,600=1
\]
\noindent This closes the entry by normalizing the diagnostic against a stated reference regime.\par

\clearpage
\noindent\textbf{[ID 0296] Westward Drift and Phase Lag Correlation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Westward Drift and Phase Lag Correlation is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Westward drift of magnetic features and azimuthal phase lag in gyroscopic systems correspond to Earth s westward secular variation and solar torsional oscillations, yielding a correlation of about 0.73. \textbf{Contextual meaning:} The entry reads Westward Drift and Phase Lag Correlation as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons. \textbf{Lemma support:} Diagnostic Definition; Scaling Relation; Normalized Regime.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The EHD resonance operator identifies flow modes amplified by pressure and electromagnetic forcing.

\tzpsection{Equation Grounding}
Equation anchors: Then C=153,600/129,600=1; C = 153 , 600 / 129 , 600 = 1; and C=153,600/129,600=1. Proof route: show that the named quantity is dimensionless or consistently scaled in the regime stated by the entry. Formalization route: prove that the normalized diagnostic remains invariant under the intended rescaling.

\tzpsection{Interpretive Role}
The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Geomagnetic Secular Variation Tracking}: The specific mathematical tracking of how the Earth's magnetic field features slowly slide to the west over centuries relative to the rocky crust.
\item \textbf{Non-Synchronous Core-Mantle Rotation}: The calculation linking the magnetic drift directly to the liquid iron core spinning slightly slower than the solid outer mantle.
\item \textbf{Propagating Wave Phase Delay Measurement}: The extraction of a specific time-delay metric showing how long it takes for a change deep in the dynamo to ripple out to the observable surface.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0296]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0296_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0296] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Westward Drift and Phase Lag Correlation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} westward drift of magnetic features and azimuthal phase lag in gyroscopic systems
correspond to Earth's westward secular variation and solar torsio...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Westward Drift and Phase Lag Correlation is valid as a spectral relation when frequency,
phase, and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0296_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
