\section*{ID9456: Definition of Im(𝛿), Fiber(𝑥)}
\paragraph{Metadata.}
PiID: 3571984922528 | RTEID: RTE:P36719.7480:T3.9542 | UUID: 65cb2ae4-d0e0-598a-90a4-cc96aa980ce1

\paragraph{Canonical Statement.}
Im(𝑑) \$⊕\$ H 𝑘 (M) \$⊕\$ Im(𝛿) Fiber(𝑥) = Hionic \$⊕\$ Hmicrotubule \$⊕\$ Hsynaptic \$⊕\$ Hmyelin Wolfram Form 𝔚TZP (K0521) \$↦−→ 〈 ΨT,\$ 𝜏(L), \$ΩT〉\$ K0521 := HoldForm(T0521) AdmissibleTZP (K0521) \$⇐⇒\$ 𝔚TZP (K0521) . \$∅\$ Wolfram register: canonical symbol lift Title lift: HODGE DECOMPOSITION \& TOPOLOGI-CAL MEMORY Symbol key: \$ΨT:\$ Trawinistic wavefunction 𝜏(L): topological charge density \$ΩT:\$ Trawinistic boundary curvature TRAWIN Normalization NormalizeTRAWIN( \$Ω𝑘\$ (M) = Im(𝑑) \$⊕\$ H 𝑘 (M) \$⊕\$ Im(𝛿), Fiber(𝑥) = Hionic \$⊕\$ Hmicrotubule \$⊕\$ Hsynaptic \$⊕\$ Hmyelin, 𝐻 𝑇 𝑛 (L) = Ker(𝜕𝑇𝑛 )/Im(𝜕𝑇𝑛+1) ) T: Hodge Decomposition is localized within the quantum-classical transition arc of the directory. R: Memory Fiber preserves the operative relation that hodge decomposition \& topological memory requires. A: Topological Memory Homology fixes the admissible closure condition for the entry. W: HODGE DECOMPOSITION \& TOPOLOGI

\paragraph{Canonical Equation.}
\[
Im(𝛿), Fiber(𝑥) = Hionic
\]

\paragraph{Dictionary.}
Im(𝑑) ⊕ H 𝑘 (M) ⊕ Im(𝛿) Fiber(𝑥) = Hionic ⊕ Hmicrotubule ⊕ Hsynaptic ⊕ Hmyelin Wolfram Form 𝔚TZP (K0521) ↦−→ 〈 ΨT 𝜏(L), ΩT〉 K0521 := HoldForm(T0521) AdmissibleTZP (K0521) ⇐⇒ 𝔚TZP (K0521) .

\paragraph{Encyclopedia.}
Definition of Im(𝛿), Fiber(𝑥) is an algebraic definition, written Im(𝛿), Fiber(𝑥) = Hionic. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from H, o, n, c, defining Im(𝛿), Fiber(𝑥). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
