\section*{ID8476: UNIVERSAL MAGNETIC SCALING LAW Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 9066175834413 | RTEID: RTE:P32914.1903:T3.9670 | UUID: 403760a5-fb5d-55c0-87e1-b6040c9f094d

\paragraph{Canonical Statement.}
[ID 1185] UNIVERSAL MAGNETIC SCALING LAW Canonical Statutory Formula: \$\textbackslash{}mu \textbackslash{}approx R\textasciicircum{}2 \textbackslash{}sqrt\{\textbackslash{}mu\_0 \textbackslash{}rho R\textasciicircum{}2 \textbackslash{}omega\textasciicircum{}2\} \textbackslash{}implies \textbackslash{}mu \textbackslash{}propto M R\textasciicircum{}2 \textbackslash{}omega\$ Formal Technical Dissertation: The Unified Scaling Constant. It demonstrates that the magnetic moment (\$\textbackslash{}mu\$) scales linearly with the angular momentum and size of the body across 47 orders of magnitude. This law unifies quantum spin, planetary dynamos, and stellar magnetospheres under a single geometric generation mechanism. Source: [1], [6], [5]

\paragraph{Canonical Equation.}
\[
\mu \approx R^2 \sqrt{\mu_0 \rho R^2 \omega^2} \implies \mu \propto M R^2 \omega
\]

\paragraph{Dictionary.}
UNIVERSAL MAGNETIC SCALING LAW Canonical Statutory Formula: \$ R\textasciicircum{}2 \_0 R\textasciicircum{}2 \textasciicircum{}2 M R\textasciicircum{}2 \$ Formal Technical Dissertation: The Unified Scaling Constant.

\paragraph{Encyclopedia.}
UNIVERSAL MAGNETIC SCALING LAW Canonical Statutory Formula is a scaling / order-of-magnitude relation, written μ ≈ R\textasciicircum{}2 √(μ\_0 ρ R\textasciicircum{}2 ω\textasciicircum{}2) ⟹ μ ∝ M R\textasciicircum{}2 ω. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from μ, ρ, ω, R, M. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
