\tzpanchor{0033}
\tzpentryheader{0033}{Principle of Least Action (TZP Variant)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{a7c58c45-8ac0-52ab-9fa3-c572b7767f5b}}\\
\textbf{PiID} & \tzpcode{8841971693993} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{40}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{128.1463 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.2111 rad}\\
\textbf{TZPID} & \tzpcode{ID0033} & \textbf{Node Dependencies}\quad \tzpidref{0032}\\
\textbf{Registry} & \tzpcode{registry\_id\_0033} & \textbf{Scale}\quad variational-principle\\
\textbf{LOC Classification} & QC20 least action & QA320 variational constraints\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: gr-qc, hep-th & \\
\textbf{Primary Support} & Boundary Data Fixing & Vanishing First Variation\\
\textbf{Closure Support} & Normalized Variational Criterion & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Among all admissible field configurations $\phi$ on $M$ with fixed boundary conditions, the actual configuration minimises or extremises the action functional $S[\phi]$ defined in ID 0032.

\tzpsection{Canonical Equation}
\[
\delta S[\phi] = 0
\]
\[
\phi\big\vert_{\partial M}
=
\phi_{0}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\delta$: point-source delta term that anchors the Green-function response.
    \item $S$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $M$: source equation symbol.
    \item $\phi_{0}$: reference zero-point flux or normalization flux.
    \item $S_{\mathrm{norm}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0033 generated source Wolfram model *)
ClearAll[K0033, Cr0033, T, R, A, W, I, N];
eq0033$1 = HoldForm[DiracDelta*S[phi] == 0];
eq0033$2 = HoldForm[phibigPartialM == phi0];
eq0033$3 = HoldForm[DiracDelta*SNorm[phi] == NormalizeTRAWIN[DiracDelta*S[phi], phiPartialM, Grad^T]];

K0033 = HoldForm[{eq0033$1, eq0033$2, eq0033$3}];

N = "normalized TRAWIN closure object for Principle of Least Action (TZP Variant)";
I = "Normalized Variational Criterion integration/comparison layer";
W = "Vanishing First Variation wave or operator carrier";
A = "Boundary Data Fixing admissible action/amplitude condition";
R = "Vanishing First Variation rotation/curl preservation layer";
T = "Boundary Data Fixing local source condition";

Cr0033[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0033 = Cr0033[K0033];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Boundary Data Fixing local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Vanishing First Variation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Boundary Data Fixing admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Vanishing First Variation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Variational Criterion integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Principle of Least Action (TZP Variant).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0033] Principle of Least Action (TZP Variant)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\delta S[\phi]=0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $S[\phi]$ be the action functional defined on field configurations $\phi$.  
Physical configurations are those for which the action is stationary under small admissible variations:

\begin{equation}
\phi \mapsto \phi+\epsilon\,\delta\phi .
\end{equation}

Expanding the action to first order in $\epsilon$ gives:

\begin{equation}
S[\phi+\epsilon\delta\phi]
=
S[\phi]
+
\epsilon\,\delta S[\phi]
+
O(\epsilon^2).
\end{equation}

For the configuration to be stationary, the first-order variation must vanish:

\begin{equation}
\boxed{
\delta S[\phi]=0 .
}
\end{equation}

\paragraph{Interpretation.}
The TZP variant of least action states that admissible physical fields extremize the Trawinistic action, including curvature, potential, and degeneracy terms.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Principle of Least Action (TZP Variant) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Boundary Data Fixing}\par
\[
\phi\big\vert_{\partial M}
=
\phi_{0}
\]
\noindent This specifies the admissible comparison class of field histories.\par
\noindent\textbf{2. Vanishing First Variation}\par
\[
\delta S[\phi] = 0
\]
\noindent This identifies the realized configuration as a stationary point of the action functional.\par
\noindent\textbf{3. Normalized Variational Criterion}\par
\[
\delta S_{\mathrm{norm}}[\phi]
=
\operatorname{Normalize}_{\mathrm{TRAWIN}}
\!\left(
\delta S[\phi],\,
\phi\vert_{\partial M},\,
\nabla^{\mathrm{T}}
\right)
\]
\noindent This closes the progression by expressing the stationary-action rule directly in the TRAWIN-normalized setting.\par

\clearpage
\noindent\textbf{[ID 0033] Principle of Least Action (TZP Variant)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Principle of Least Action (TZP Variant) is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Among all admissible field configurations phi on M with fixed boundary conditions, the actual configuration minimises or extremises the action functional S[phi] defined in ID 0032. \textbf{Contextual meaning:} The entry reads Principle of Least Action (TZP Variant) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This principle turns the action functional into a dynamical selector. It is the clean conceptual bridge from the variational object in tzpidref 0032 to the concrete field equations in tzpidref 0034. \textbf{Lemma support:} Boundary Data Fixing; Vanishing First Variation; Normalized Variational Criterion.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP variant of least action states that admissible physical fields extremize the Trawinistic action, including curvature, potential, and degeneracy terms.

\tzpsection{Equation Grounding}
Equation anchors: Among all admissible field configurations  phi  on MMM with fixed boundary conditions, the actual configuration minimises or extremises the action functional S [   ] S [ phi ] S [   ] defined in ID ,032. Among all admissible field configurations  phi  on MMM with fixed boundary conditions, the actual configuration minimises or extremises the action functional S [   ] S [ phi ] S [   ] defined in ID ,032.

\tzpsection{Interpretive Role}
This principle turns the action functional into a dynamical selector. It is the clean conceptual bridge from the variational object in ID0032 to the concrete field equations in ID0034.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Principle Least Variational Work Tzp Variant}: variational synonym for action, energy generation, admissible variation, or closure.
\item \textbf{Variational Work Variational Analogue}: variational synonym for action, energy generation, admissible variation, or closure.
\item \textbf{Variational Work Terminology}: variational synonym for action, energy generation, admissible variation, or closure.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0033]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0033_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0033] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Principle of Least Action (TZP Variant)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} among all admissible field configurations  on M with fixed boundary conditions, the
actual configuration minimises or extremises the action fun...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Principle of Least Action (TZP Variant) is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0033_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
