\section*{ID8750: Definition of x\textasciicircum{}4 - x\textasciicircum{}2 + y\textasciicircum{}2}
\paragraph{Metadata.}
PiID: 3025494780249 | RTEID: RTE:P33978.1932:T5.7201 | UUID: dca2b21c-7b75-52c5-ba21-7cebec42c9ce

\paragraph{Canonical Statement.}
rossing. If you revolve a lemniscate of Bernoulli around one of its symmetry axes, you get a sort of figure-eight shaped surface or a toroidal figure with a pinched middle. It’s plausible that the field lines in 3D near a dipole could be described by such a surface – for instance, if one considered lines of constant field magnitude or potential, you might get a lemniscate-like shape dividing regions of different field orientation. The lemniscate of Gerono (another figure-eight) is given by \$x\textasciicircum{}4 - x\textasciicircum{}2 + y\textasciicircum{}2 = 0\$ en.wikipedia.org. Interestingly, as the Wikipedia entry notes, Viviani’s curve – which is the intersection of a sphere and a cylinder – is a space curve with a figure-eight projection (in fact, its projection onto a plane is the lemniscate of Gerono)en.wikipedia.org. Viviani’s curve is three-dimensional and is one continuous loop that intersects itself when viewed from a certain angle. This i

\paragraph{Canonical Equation.}
\[
x^4 - x^2 + y^2 = 0
\]

\paragraph{Dictionary.}
Definition of x\textasciicircum{}4 - x\textasciicircum{}2 + y\textasciicircum{}2 — x\textasciicircum{}4 - x\textasciicircum{}2 + y\textasciicircum{}2 = 0

\paragraph{Encyclopedia.}
Definition of x\textasciicircum{}4 - x\textasciicircum{}2 + y\textasciicircum{}2 is an algebraic definition, written x\textasciicircum{}4 - x\textasciicircum{}2 + y\textasciicircum{}2 = 0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
