\tzpanchor{0041}
\tzpentryheader{0041}{Topological Helicity Quantisation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{6eb0a9ef-6126-556a-bfb8-47c1cae7fd7d}}\\
\textbf{PiID} & \tzpcode{9399375105820} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{48}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{159.2121 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.2623 rad}\\
\textbf{TZPID} & \tzpcode{ID0041} & \textbf{Node Dependencies}\quad \tzpidref{0040}\\
\textbf{Registry} & \tzpcode{registry\_id\_0041} & \textbf{Scale}\quad helicity-topological\\
\textbf{LOC Classification} & QC809 magnetic helicity & QA612.2 topological invariants\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph \quad Cross-list: math-ph, astro-ph.SR & \\
\textbf{Primary Support} & Helicity Integral & Winding Index\\
\textbf{Closure Support} & Flux-Quantized Helicity & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Magnetic helicity takes discrete values proportional to the winding number defined around the TZP.

\tzpsection{Canonical Equation}
\[
H
=
\int_{V}\mathbf{A}\cdot\mathbf{B}\,d^{3}x
\]
\[
H = w\,\Phi,
\qquad
w \in \mathbb{Z}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H$: source equation symbol.
    \item $V$: auxiliary target state or comparison variable.
    \item $A$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $\Phi$: flux, phase, or topological map term in the source equation.
    \item $Z$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0041 generated source Wolfram model *)
ClearAll[K0041, Cr0041, T, R, A, W, I, N];
eq0041$1 = HoldForm[H == IntegralVA*B*d^3*x];
eq0041$2 = HoldForm[Element[TZPSequence[H == w*Phi, w], Z]];
eq0041$3 = HoldForm[Element[w, Z]];
eq0041$4 = HoldForm[H == w*Phi];

K0041 = HoldForm[{eq0041$1, eq0041$2, eq0041$3, eq0041$4}];

N = "normalized TRAWIN closure object for Topological Helicity Quantisation";
I = "Flux-Quantized Helicity integration/comparison layer";
W = "Winding Index wave or operator carrier";
A = "Helicity Integral admissible action/amplitude condition";
R = "Winding Index rotation/curl preservation layer";
T = "Helicity Integral local source condition";

Cr0041[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0041 = Cr0041[K0041];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Helicity Integral local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Winding Index rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Helicity Integral admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Winding Index wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Flux-Quantized Helicity integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Topological Helicity Quantisation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0041] Topological Helicity Quantisation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
H
=
\int_V
\mathbf{A}\cdot\mathbf{B}
\,\mathrm{d}^3x .
\end{equation}

\paragraph{Quantized Form.}
\begin{equation}
H=w\,\Phi .
\end{equation}

\paragraph{Primary Derivation.}
Let $\mathbf{A}$ be the magnetic vector potential and $\mathbf{B}$ the magnetic field.  
Magnetic helicity measures the linkage, twist, and winding of magnetic field lines inside a volume $V$:

\begin{equation}
H
=
\int_V
\mathbf{A}\cdot\mathbf{B}
\,\mathrm{d}^3x .
\end{equation}

If the magnetic structure winds around the TZP with integer winding number $w$, and if $\Phi$ denotes the magnetic flux through the lemniscatic loop, then helicity decomposes into winding times flux:

\begin{equation}
\boxed{
H=w\,\Phi .
}
\end{equation}

\paragraph{Interpretation.}
Magnetic helicity becomes quantized when the field topology is constrained by integer TZP winding.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Topological Helicity Quantisation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Helicity Integral}\par
\[
H
=
\int_{V}\mathbf{A}\cdot\mathbf{B}\,d^{3}x
\]
\noindent This defines the total helicity stored by the magnetic configuration.\par
\noindent\textbf{2. Winding Index}\par
\[
w \in \mathbb{Z}
\]
\noindent This identifies the topological sector that labels the configuration.\par
\noindent\textbf{3. Flux-Quantized Helicity}\par
\[
H = w\,\Phi
\]
\noindent This closes the progression by tying the continuous field integral to a discrete winding multiple of magnetic flux.\par

\clearpage
\noindent\textbf{[ID 0041] Topological Helicity Quantisation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Topological Helicity Quantisation is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Magnetic helicity takes discrete values proportional to the winding number defined around the TZP. \textbf{Contextual meaning:} The entry reads Topological Helicity Quantisation as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} Quantized helicity is the doorway from field energetics into topology. Once helicity resolves into winding sectors, scale-invariant helicity ratios and linking-number laws can be stated without ambiguity about what counts as the conserved quantity. \textbf{Lemma support:} Helicity Integral; Winding Index; Flux-Quantized Helicity.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Magnetic helicity becomes quantized when the field topology is constrained by integer TZP winding.

\tzpsection{Equation Grounding}
Equation anchors: The magnetic helicity H=intVA B d3xH=integral V textbackslash mathbf A dot textbackslash mathbf B textbackslash, d to the power 3xH=intVA Bd3x is quantised in units of the Trawinistic winding number, i.e., H=w PhiH = wtextbackslash,PhiH=wPhi, where PhiPhiPhi is the magnetic flux through the lemniscatic loop. The magnetic helicity H=intVA B d3xH=integral V textbackslash mathbf A dot textbackslash mathbf B textbackslash, d to the power 3xH=intVA Bd3x is quantised in units of the Trawinistic winding number, i.e., H=w PhiH = wtextbackslash,PhiH=wPhi, where PhiPhiPhi is the magnetic flux through the lemniscatic loop.

\tzpsection{Interpretive Role}
Quantized helicity is the doorway from field energetics into topology. Once helicity resolves into winding sectors, scale-invariant helicity ratios and linking-number laws can be stated without ambiguity about what counts as the conserved quantity.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Shape-Preserving Twist Linkage Quantisation}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Shape-Preserving Twist Linkage Rotating-Field Analogue}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\item \textbf{Twist Linkage Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0041]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0041_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0041] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Topological Helicity Quantisation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} magnetic helicity takes discrete values proportional to the winding number defined
around the TZP

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Topological Helicity Quantisation is valid when the stated geometric or topological
relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0041_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
