\tzpanchor{0088}
\tzpentryheader{0088}{Local Electromagnetic Field--Driven Rotation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{3d8d137f-9c22-5f60-b5ec-f75597f7b9d7}}\\
\textbf{PiID} & \tzpcode{2534211706798} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{95}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{341.7235 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.5631 rad}\\
\textbf{TZPID} & \tzpcode{ID0088} & \textbf{Node Dependencies}\quad \tzpidref{0077}\\
\textbf{Registry} & \tzpcode{registry\_id\_0088} & \textbf{Scale}\quad local electromagnetic drive\\
\textbf{LOC Classification} & QC6.4 electrodynamic rotation & QC174 field-coupled dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph \quad Cross-list: astro-ph.SR, cond-mat.mtrl-sci & \\
\textbf{Primary Support} & Local Lorentz Forcing Density & Integrated Electromagnetic Torque\\
\textbf{Closure Support} & Rotation Response Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This defines how electromagnetic fields induce rotation; rotation depends on charge density, current and magnetic field configuration.

\tzpsection{Canonical Equation}
\[
\tau_{\mathrm{em}}
=
\int \mathbf{r}\times\left(\mathbf{J}\times\mathbf{B}+\rho_e\mathbf{E}\right)\,dV
\]
\[
\dot{\omega}=\frac{\tau_{\mathrm{em}}}{I_{\mathrm{T}}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\tau_{\mathrm{em}}$: source equation symbol.
    \item $J$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $\rho_e$: source equation symbol.
    \item $E$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
    \item $I_{\mathrm{T}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0088 generated source Wolfram model *)
ClearAll[K0088, Cr0088, T, R, A, W, I, N];
eq0088$1 = HoldForm[tauEm == Integral*r*(J*B + rhoEE)*dV];
eq0088$2 = HoldForm[dot[omega] == tauEm/IT];
eq0088$3 = HoldForm[J*B + rhoEE];

K0088 = HoldForm[{eq0088$1, eq0088$2, eq0088$3}];

N = "normalized TRAWIN closure object for Local Electromagnetic Field--Driven Rotation";
I = "Rotation Response Law integration/comparison layer";
W = "Integrated Electromagnetic Torque wave or operator carrier";
A = "Local Lorentz Forcing Density admissible action/amplitude condition";
R = "Integrated Electromagnetic Torque rotation/curl preservation layer";
T = "Local Lorentz Forcing Density local source condition";

Cr0088[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0088 = Cr0088[K0088];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Local Lorentz Forcing Density local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Integrated Electromagnetic Torque rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Local Lorentz Forcing Density admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Integrated Electromagnetic Torque wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Rotation Response Law integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Local Electromagnetic Field--Driven Rotation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0088] Local Electromagnetic Field--Driven Rotation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Source Density.}
\begin{equation}
\mathbf{f}_{\mathrm{em}}
=
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}.
\end{equation}

\paragraph{Integrated Torque.}
\begin{equation}
\boldsymbol{\tau}_{\mathrm{em}}
=
\int_V
\mathbf{r}\times
\left(
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}
\right)
\,\mathrm{d}V .
\end{equation}

\paragraph{Rotation Response Law.}
\begin{equation}
\dot{\omega}
=
\frac{\tau_{\mathrm{em}}}{I_T}.
\end{equation}

\paragraph{Primary Derivation.}
The local Lorentz-type forcing density is:
\begin{equation}
\mathbf{f}_{\mathrm{em}}
=
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}.
\end{equation}

The torque contribution of a small volume element is:
\begin{equation}
\mathrm{d}\boldsymbol{\tau}
=
\mathbf{r}\times\mathbf{f}_{\mathrm{em}}\,\mathrm{d}V .
\end{equation}

Therefore,
\begin{equation}
\boldsymbol{\tau}_{\mathrm{em}}
=
\int_V
\mathbf{r}\times
\left(
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}
\right)
\,\mathrm{d}V .
\end{equation}

The rotational response is:
\begin{equation}
\boxed{
\dot{\omega}
=
\frac{\tau_{\mathrm{em}}}{I_T}.
}
\end{equation}

\paragraph{Interpretation.}
This entry makes the torque budget explicit: generated rotation must be traceable to local electromagnetic force density.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Local Electromagnetic Field--Driven Rotation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Local Lorentz Forcing Density}\par
\[
\mathbf{J}\times\mathbf{B}+\rho_e\mathbf{E}
\]
\noindent This identifies the distributed source of rotational drive inside the system.\par
\noindent\textbf{2. Integrated Electromagnetic Torque}\par
\[
\tau_{\mathrm{em}}
=
\int \mathbf{r}\times\left(\mathbf{J}\times\mathbf{B}+\rho_e\mathbf{E}\right)\,dV
\]
\noindent This gathers the local drive into a net torque.\par
\noindent\textbf{3. Rotation Response Law}\par
\[
\dot{\omega}=\frac{\tau_{\mathrm{em}}}{I_{\mathrm{T}}}
\]
\noindent This closes the progression by converting the integrated field drive into angular acceleration.\par

\clearpage
\noindent\textbf{[ID 0088] Local Electromagnetic Field--Driven Rotation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Local Electromagnetic Field--Driven Rotation is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This defines how electromagnetic fields induce rotation; rotation depends on charge density, current and magnetic field configuration. \textbf{Contextual meaning:} The entry reads Local Electromagnetic Field--Driven Rotation as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry operationalizes the source of rotation in terms that can be measured or modeled locally. It prepares the way for the categorical FractalNodes scale bridging claim by making the source law explicit on both laboratory and astrophysical domains. \textbf{Lemma support:} Local Lorentz Forcing Density; Integrated Electromagnetic Torque; Rotation Response Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This entry makes the torque budget explicit: generated rotation must be traceable to local electromagnetic force density.

\tzpsection{Equation Grounding}
Equation anchors: The angular velocity omega of a rotating system is determined by local electromagnetic fields via omega=12Lintrtimes (Jtimes B+rhoeE) dVomega = ratio 1 2L integral textbackslash mathbf r times(textbackslash mathbf J timestextbackslash mathbf B + rho etextbackslash mathbf E )textbackslash, d Vomega=2L1intrtimes (Jtimes B+rhoeE)dV, where LLL is the moment of inertia determined using the Trawin base unit. The angular velocity omega of a rotating system is determined by local electromagnetic fields via omega=12Lintrtimes (Jtimes B+rhoeE) dVomega = ratio 1 2L integral textbackslash mathbf r times(textbackslash mathbf J timestextbackslash mathbf B + rho etextbackslash mathbf E )textbackslash, d Vomega=2L1intrtimes (Jtimes B+rhoeE)dV, where LLL is the moment of inertia determined using the Trawin base unit.

\tzpsection{Interpretive Role}
This entry operationalizes the source of rotation in terms that can be measured or modeled locally. It prepares the way for the categorical FractalNodes scale bridging claim by making the source law explicit on both laboratory and astrophysical domains.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Neighborhood Maxwell-Field Carrier Domain Driven Rotation}: field-energy vocabulary for charge, electromagnetic stress, or covariant flow.
\item \textbf{Neighborhood Maxwell-Field Carrier Domain Field-Energy Analogue}: field-energy vocabulary for charge, electromagnetic stress, or covariant flow.
\item \textbf{Carrier Domain Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0088]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0088_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0088] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Local Electromagnetic Field--Driven Rotation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this defines how electromagnetic fields induce rotation; rotation depends on charge
density, current and magnetic field configuration

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Local Electromagnetic Field--Driven Rotation is valid as a formal registry statement
when its source equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that this defines how electromagnetic fields induce rotation;
rotation depends on charge density, current and magnetic field configuration. This entry
makes the torque budget explicit: generated rotation must be traceable to local
electromagnetic force density. This entry operationalizes the source of rotation in
terms that can be measured or modeled locally.. The CHL validation treats the equation
as the formal anchor and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0088_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
