\section*{ID8841: Hamiltonian for H P-Gate}
\paragraph{Metadata.}
PiID: 0791191532673 | RTEID: RTE:P34331.5664:T0.0192 | UUID: 22b1e5f0-cd03-5685-9fd7-bd20c9276445

\paragraph{Canonical Statement.}
[ID 1042] PROTON-GATED MANIFOLD OPERATOR (\$\textbackslash{}hat\{H\}\_\{p-gate\}\$) Canonical Statutory Formula: \$\textbackslash{}hat\{H\} \{p-gate\} = -\textbackslash{}frac\{\textbackslash{}hbar\textasciicircum{}2\}\{2m\_p\}\textbackslash{}nabla\textasciicircum{}2 + V \{pH\}(L) \textbackslash{}otimes \textbackslash{}sum\_i \textbackslash{}delta(r-r\_i)\textbackslash{}hat\{a\}\textasciicircum{}\textbackslash{}dagger\_i \textbackslash{}hat\{a\}\_i\$ Formal Technical Dissertation: Stabilizes the protonic gradient in the operator's biological tissues. It creates a resonant "Tunneling Gate" synchronized with the acoustic carrier to maintain mitochondrial membrane potentials during high-flux events. Source: [11]

\paragraph{Canonical Equation.}
\[
\hat{H} {p-gate} = -\frac{\hbar^2}{2m_p}\nabla^2 + V {pH}(L) \otimes \sum_i \delta(r-r_i)\hat{a}^\dagger_i \hat{a}_i
\]

\paragraph{Dictionary.}
PROTON-GATED MANIFOLD OPERATOR (H\_p-gate) Canonical Statutory Formula: \$H p-gate = - \textasciicircum{}22m\_p \textasciicircum{}2 + V pH(L) \_i (r-r\_i)a\textasciicircum{} \_i a\_i\$ Formal Technical Dissertation: Stabilizes the protonic gradient in the operator's biological tissues [ID8841]

\paragraph{Encyclopedia.}
Hamiltonian for H P-Gate is a hamiltonian construction, written H p-gate = -(ħ\textasciicircum{}2)/(2m\_p)∇\textasciicircum{}2 + V pH(L) ⊗ ∑\_i δ(r-r\_i)a\textasciicircum{}†\_i a\_i. It defines a Hamiltonian that generates the system's time evolution and encodes its energy. It is built from ħ, ∇, δ, m\_p, V, p, defining H p-gate. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
