\tzpanchor{0730}
\tzpentryheader{0730}{INTEGRATED INFORMATION SCALING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{14d8b24b-ebb2-586b-9d63-fcc95c776d9e}}\\
\textbf{PiID} & \tzpcode{5981362977477} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{737}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2799.8031 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.6132 rad}\\
\textbf{TZPID} & \tzpcode{ID0730} & \textbf{Node Dependencies}\quad \tzpidref{0729}\\
\textbf{Registry} & \tzpcode{registry\_id\_0730} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records integrated information scaling through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0730}}:\mathcal{X}_{\mathrm{id0730}}\longrightarrow\mathcal{Y}_{\mathrm{id0730}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0730}})=\mathcal{O}_{\mathrm{id0730}}
\]
\[
\mathcal{O}_{\mathrm{id0730}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0730}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0730}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0730}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0730 generated source Wolfram model *)
ClearAll[K0730, Cr0730, T, R, A, W, I, N];
eq0730$1 = HoldForm[Oid0730[Xid0730] -> Yid0730];
eq0730$2 = HoldForm[NTRAWIN[OId0730] == OId0730];
eq0730$3 = HoldForm[Element[OId0730[x], YAdm]];

K0730 = HoldForm[{eq0730$1, eq0730$2, eq0730$3}];

N = "normalized TRAWIN closure object for INTEGRATED INFORMATION SCALING";
I = "INTEGRATED INFORMATION SCALING integration/comparison layer";
W = "INTEGRATED INFORMATION SCALING wave or operator carrier";
A = "INTEGRATED INFORMATION SCALING admissible action/amplitude condition";
R = "INTEGRATED INFORMATION SCALING rotation/curl preservation layer";
T = "INTEGRATED INFORMATION SCALING local source condition";

Cr0730[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0730 = Cr0730[K0730];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ INTEGRATED INFORMATION SCALING local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ INTEGRATED INFORMATION SCALING rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ INTEGRATED INFORMATION SCALING admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ INTEGRATED INFORMATION SCALING wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ INTEGRATED INFORMATION SCALING integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for INTEGRATED INFORMATION SCALING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0730] INTEGRATED INFORMATION SCALING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0730}}:\mathcal{X}_{\mathrm{id0730}}\longrightarrow\mathcal{Y}_{\mathrm{id0730}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0730}})=\mathcal{O}_{\mathrm{id0730}}
\]
\[
\mathcal{O}_{\mathrm{id0730}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0730}})=\mathcal{O}_{\mathrm{id0730}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. In the TRAWIN reading, the equation functions as the mapping carrier for the entry’s information content. In CHL terms, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors INTEGRATED INFORMATION SCALING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0730}}:\mathcal{X}_{\mathrm{id0730}}\longrightarrow\mathcal{Y}_{\mathrm{id0730}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0730}})=\mathcal{O}_{\mathrm{id0730}}
\]
\[
\mathcal{O}_{\mathrm{id0730}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0730] INTEGRATED INFORMATION SCALING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
INTEGRATED INFORMATION SCALING is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Phi sub total = sum sub j=1 to the power 153,600 phi sub j otimes M sub entanglement. \textbf{Contextual meaning:} The entry reads INTEGRATED INFORMATION SCALING as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons. \textbf{Lemma support:} Diagnostic Definition; Scaling Relation; Normalized Regime.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, INTEGRATED INFORMATION SCALING is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: frac 547 512 approximately 1.068; Deltaphi(ratio 547 512 ) = pi(ratio 35 512 ) approximately 12.3 to the power compose; and 2 to the power 9 = 512. Proof route: show that the named quantity is dimensionless or consistently scaled in the regime stated by the entry. Formalization route: prove that the normalized diagnostic remains invariant under the intended rescaling.

\tzpsection{Interpretive Role}
The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Whole-is-Greater-Than-Sum Accounting}: The bizarre calculation proving that the amount of data contained in the entire, unified machine is actually significantly larger than just adding up the data contained in all of its individual parts.
\item \textbf{Irreducible System Complexity}: The mathematical proof that you absolutely cannot understand what the machine is doing by looking at its pieces; the true magic only exists in the invisible spaces between them.
\item \textbf{Emergent Consciousness Metric}: The incredibly controversial, highly debated number that attempts to quantify exactly how 'aware' the sprawling, entangled network of the machine has actually become.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0730]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0730].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0730] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont INTEGRATED INFORMATION SCALING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} INTEGRATED INFORMATION SCALING is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``INTEGRATED INFORMATION SCALING is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0730].
\par\endgroup
\vfill
\endgroup
\endgroup
