\tzpanchor{0458}
\tzpentryheader{0458}{Output Recapture And Phase Return}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{59b758d8-db50-5cba-b3a2-6f8b7c3a5584}}\\
\textbf{PiID} & \tzpcode{9962749567351} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{465}\\
\textbf{RTEID} & \textbf{Manifest row}\quad \tzpcode{not listed} & \textbf{Source}\quad \tzpcode{Coordinate Manifest}\\
\textbf{TZPID} & \tzpcode{ID0458} & \textbf{Node Dependencies}\quad \tzpidref{0457}\\
\textbf{Registry} & \tzpcode{registry\_id\_0458} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 458 defines the real time optimization of extraction efficiency27. Based on measurement results, the control parameters uk are updated via a persistence test28282828. This ensures the system remains within the bifurcation band required for robust phase locking29292929. Stochastic Suppression: Feedback logic mitigates noise from the Wiener increment recorded during measurements30303030. Synchronized Correction: Corrections are applied within the 17.2 kHz window to maintain resonance31313131.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{C}_{\mathrm{mech}}:X\to Y
$
\end{adjustbox}
\]

\tzpsection{Canonical Equation Links}
\tzpequationlinks
  {\mathcal{C}_{\mathrm{mech}}:X\to Y}
  {\frac{dY}{dt}=F(X,Y)}
  {\mathcal{A}_{\mathrm{adm}}(Y)=1}

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{C}_{\mathrm{mech}}$: source equation symbol.
    \item $X$: source variable, local coordinate, or input state in the entry relation.
    \item $Y$: target variable or output state in the entry relation.
    \item $\mathcal{K}_{0458}$: canonical registry object for entry ID 0458.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0458 generated source Wolfram model *)
ClearAll[K0458, Cr0458, T, R, A, W, I, N];
eq0458$1 = HoldForm[$Cmech[X] -> Y$];

K0458 = HoldForm[{eq0458$1}];

N = "normalized TRAWIN closure object for Output Recapture And Phase Return";
I = "Output Recapture And Phase Return integration/comparison layer";
W = "Output Recapture And Phase Return wave or operator carrier";
A = "Output Recapture And Phase Return admissible action/amplitude condition";
R = "Output Recapture And Phase Return rotation/curl preservation layer";
T = "Output Recapture And Phase Return local source condition";

Cr0458[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0458 = Cr0458[K0458];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Output Recapture And Phase Return local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Output Recapture And Phase Return rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Output Recapture And Phase Return admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Output Recapture And Phase Return wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Output Recapture And Phase Return integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Output Recapture And Phase Return.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0458] Output Recapture And Phase Return}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\begingroup\small
\paragraph{Primary Equation.}
\begin{equation}
\mu\frac{\mathrm{d}g}{\mathrm{d}\mu}
=
\beta(g,d_{\mathrm{eff}}).
\end{equation}

\paragraph{Primary Derivation.}
Let $g(\mu)$ be a coupling constant depending on scale $\mu$.  
Near the TZP, effective dimension may vary according to the hyper-dimensional span, so the beta function depends not only on $g$ but also on $d_{\mathrm{eff}}$.

The scale derivative is written as:

\begin{equation}
\mu\frac{\mathrm{d}g}{\mathrm{d}\mu}.
\end{equation}

The renormalization flow law becomes:

\begin{equation}
\boxed{
\mu\frac{\mathrm{d}g}{\mathrm{d}\mu}
=
\beta(g,d_{\mathrm{eff}}).
}
\end{equation}

\paragraph{Wolfram Form.}
\begin{verbatim}
mu*D[g[mu], mu] == beta[g[mu], dEff[mu]]
\end{verbatim}

\paragraph{Interpretation.}
Renormalization becomes navigation through scale and effective dimension.
\endgroup

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Output Recapture And Phase Return by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{C}_{\mathrm{mech}}:X\to Y
$
\end{adjustbox}
\]

\tzpsection{Canonical Equation Links}
\tzpequationlinks
  {\mathcal{C}_{\mathrm{mech}}:X\to Y}
  {\frac{dY}{dt}=F(X,Y)}
  {\mathcal{A}_{\mathrm{adm}}(Y)=1}
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0458] Output Recapture And Phase Return}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Output Recapture And Phase Return is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 458 defines the real time optimization of extraction efficiency27. Based on measurement results, the control parameters uk are updated via a persistence test28282828. This ensures the system remains within the bifurcation band required for robust phase locking29292929. Stochastic Suppression: Feedback logic mitigates noise from the Wiener increment recorded during measurements30303030. Synchronized Correction: Corrections are applied within the 17.2 kHz window to maintain resonance31313131.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{C}_{\mathrm{mech}}:X\to Y
$
\end{adjustbox}
\]

\tzpsection{Canonical Equation Links}
\tzpequationlinks
  {\mathcal{C}_{\mathrm{mech}}:X\to Y}
  {\frac{dY}{dt}=F(X,Y)}
  {\mathcal{A}_{\mathrm{adm}}(Y)=1}

\tzpsection{Technical Interpretation}
ID 458 defines the real time optimization of extraction efficiency27. Based on measurement results, the control parameters uk are updated via a persistence test28282828. This ensures the system remains within the bifurcation band required for robust phase locking29292929. Stochastic Suppression: Feedback logic mitigates noise from the Wiener increment recorded during measurements30303030. Synchronized Correction: Corrections are applied within the 17.2 kHz window to maintain resonance31313131.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Output Recapture And Phase Return by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Output Recapture And Phase Return; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0458]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0458].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0458] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Output Recapture And Phase Return}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} Output Recapture And Phase Return is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Output Recapture And Phase Return is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0458].
\par\endgroup
\vfill
\endgroup
\endgroup
