\tzpanchor{0532}
\tzpentryheader{0532}{MICRO DOUBLE-HELIX METAMATERIAL DESIGN}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{40f9eac3-2bbe-56f5-93e3-4137b436cdb0}}\\
\textbf{PiID} & \tzpcode{9522473719070} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{539}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2046.4580 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.3719 rad}\\
\textbf{TZPID} & \tzpcode{ID0532} & \textbf{Node Dependencies}\quad \tzpidref{0531}\\
\textbf{Registry} & \tzpcode{registry\_id\_0532} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Meta-State Superposition & DNA Manifold Assembly\\
\textbf{Closure Support} & Admissibility Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
DNAManifold = sum\_\{i=1\}\textasciicircum{}\{3 x 10\textasciicircum{}9\} |DNA\_irangle otimes |DAAN\_\{i pmod\{153600\}\}rangle otimes |Kissing\_\{lfloor i/153600 rfloor\}rangle

\tzpsection{Canonical Equation}
\[
lvert \Psi_{\mathrm{meta}}\rangle = \sum_{i=1}^{3\times 10^{9}} \lvert \mathrm{DNA}_{i}\rangle \otimes \lvert \mathrm{DAAN}(i \bmod 153600)\rangle \otimes \lvert \mathrm{Kissing}(\lfloor i/153600 \rfloor)\rangle
\]
\[
mathrm{DNAManifold} = \sum_{i=1}^{3\times 10^{9}} \lvert \mathrm{DNA}_{i}\rangle \otimes \lvert \mathrm{DAAN}_{i \bmod 153600}\rangle \otimes \lvert \mathrm{Kissing}_{\lfloor i/153600 \rfloor}\rangle
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Psi_{\mathrm{meta}}$: source equation symbol.
    \item $A$: source equation symbol.
    \item $\Psi$: wavefunction or state carrier for the entry equation.
    \item $\bmod$: source equation symbol.
    \item $\lfloor$: source equation symbol.
    \item $\rfloor$: source equation symbol.
    \item $P$: source equation symbol.
    \item $D$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
    \item $A_{i}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0532 generated source Wolfram model *)
ClearAll[K0532, Cr0532, T, R, A, W, I, N];
eq0532$1 = HoldForm[Ket[PsiMeta] == SumI1^(3*10^9)*Ket[DNAI]*TensorProductKet[DAAN[ibmod153600]]*TensorProductKet[Kissing[lfloor*(i/153600)*rfloor]]];
eq0532$2 = HoldForm[mathrm[DNAManifold] == SumI1^(3*10^9)*Ket[DNAI]*TensorProductKet[DAANIbmod153600]*TensorProductKet[KissingLfloori153600*rfloor]];
eq0532$3 = HoldForm[AAdm[DNAManifold] == 1];

K0532 = HoldForm[{eq0532$1, eq0532$2, eq0532$3}];

N = "normalized TRAWIN closure object for MICRO DOUBLE-HELIX METAMATERIAL DESIGN";
I = "Admissibility Closure integration/comparison layer";
W = "DNA Manifold Assembly wave or operator carrier";
A = "Meta-State Superposition admissible action/amplitude condition";
R = "DNA Manifold Assembly rotation/curl preservation layer";
T = "Meta-State Superposition local source condition";

Cr0532[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0532 = Cr0532[K0532];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Meta-State Superposition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ DNA Manifold Assembly rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Meta-State Superposition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ DNA Manifold Assembly wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Admissibility Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for MICRO DOUBLE-HELIX METAMATERIAL DESIGN.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0532] MICRO DOUBLE-HELIX METAMATERIAL DESIGN}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
S[\phi]
=
\int_M
\mathcal{L}_T
\left(
\phi,\nabla^T\phi,g
\right)
\,\mathrm{d}^n x .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi$ be a field defined on the Trawinistic manifold $M$.  
The local dynamics are encoded in a Trawinistic Lagrangian density:

\begin{equation}
\mathcal{L}_T
\left(
\phi,\nabla^T\phi,g
\right).
\end{equation}

This density depends on the field, its Trawinistic covariant derivative, and the metric structure.

The total action is obtained by integrating the density over the manifold:

\begin{equation}
\boxed{
S[\phi]
=
\int_M
\mathcal{L}_T
\left(
\phi,\nabla^T\phi,g
\right)
\,\mathrm{d}^n x .
}
\end{equation}

\paragraph{Interpretation.}
The action functional is the master quantity from which the Trawinistic field equations are derived.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors MICRO DOUBLE-HELIX METAMATERIAL DESIGN by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Meta-State Superposition}\par
\[
lvert \Psi_{\mathrm{meta}}\rangle = \sum_{i=1}^{3\times 10^{9}} \lvert \mathrm{DNA}_{i}\rangle \otimes \lvert \mathrm{DAAN}(i \bmod 153600)\rangle \otimes \lvert \mathrm{Kissing}(\lfloor i/153600 \rfloor)\rangle
\]
\noindent This fixes the global metamaterial state as a superposition over the indexed DNA, DAAN, and kissing sectors.\par
\noindent\textbf{2. DNA Manifold Assembly}\par
\[
mathrm{DNAManifold} = \sum_{i=1}^{3\times 10^{9}} \lvert \mathrm{DNA}_{i}\rangle \otimes \lvert \mathrm{DAAN}_{i \bmod 153600}\rangle \otimes \lvert \mathrm{Kissing}_{\lfloor i/153600 \rfloor}\rangle
\]
\noindent This turns the indexed superposition into an assembled DNA manifold carrying the same combinatorial structure.\par
\noindent\textbf{3. Admissibility Closure}\par
\[
mathcal{A}_{\mathrm{adm}}\!\left(\mathrm{DNAManifold}\right)=1
\]
\noindent This closes the entry by requiring admissibility of the assembled manifold under the directory ordering.\par

\clearpage
\noindent\textbf{[ID 0532] MICRO DOUBLE-HELIX METAMATERIAL DESIGN}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
MICRO DOUBLE-HELIX METAMATERIAL DESIGN is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} DNAManifold = sum sub i=1 to the power 3 x 10 to the power 9 |DNA sub irangle otimes |DAAN sub i pmod 153600 rangle otimes |Kissing sub lfloor i/153600 rfloor rangle. \textbf{Contextual meaning:} The entry reads MICRO DOUBLE-HELIX METAMATERIAL DESIGN as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states a coherent indexed metamaterial assembly law instead of the malformed exponent and composition artifacts from the raw export. \textbf{Lemma support:} Meta-State Superposition; DNA Manifold Assembly; Admissibility Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The action functional is the master quantity from which the Trawinistic field equations are derived.

\tzpsection{Equation Grounding}
Equation anchors: lvert Psi sub meta = sum sub i=1 to the power 3times 10 to the power 9 lvert DNA sub i otimes lvert DAAN (i bmod 153600) otimes lvert Kissing (lfloor i/153600 rfloor); mathrm DNAManifold = sum sub i=1 to the power 3times 10 to the power 9 lvert DNA sub i otimes lvert DAAN sub i bmod 153600 otimes lvert Kissing sub lfloor i/153600 rfloor; and mathcal A sub adm ( DNAManifold )=1. Proof route: show that the indexed DNA, DAAN, and kissing sectors assemble into the stated meta-state and induce the admissible manifold closure. Formalization route: prove that the indexed metamaterial assembly yields an admissible DNA manifold under TRAWIN normalization.

\tzpsection{Interpretive Role}
The entry now states a coherent indexed metamaterial assembly law instead of the malformed exponent and composition artifacts from the raw export.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Chiral Nano-Structure Engineering}: The physical construction of millions of microscopic, twisting metal spirals designed to force incoming light to spin in a very specific direction.
\item \textbf{Bio-Mimetic Electromagnetic Routing}: The copying of the shape of DNA to create a physical wire that naturally rejects interference and perfectly protects the data flowing through it.
\item \textbf{Torsional Light-Bending Lattices}: The deployment of a dense forest of these metal spirals to artificially slow down and bend passing energy waves in ways that normal glass lenses cannot.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0532]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0532_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0532] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont MICRO DOUBLE-HELIX METAMATERIAL DESIGN}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} dNAManifold = sum\textbackslash{}\_=1\textbackslash{}\textasciicircum{}\textbackslash{}3 x 10\textasciicircum{}9\textbackslash{} |DNA\textbackslash{}\_irangle otimes |DAAN\textbackslash{}\_ pmod\textbackslash{}153600\textbackslash{} otimes
|Kissing\textbackslash{}\_ i/153600 rfloor

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``MICRO DOUBLE-HELIX METAMATERIAL DESIGN is valid when the stated geometric or topological
relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0532_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
