\section*{ID9264: Relation: 2πn/mointv·dℓ}
\paragraph{Metadata.}
PiID: 8377814233562 | RTEID: RTE:P35974.1693:T2.7257 | UUID: e07e70c6-4ee9-5421-a095-d6d9b80851cf

\paragraph{Canonical Statement.}
ield strength ratios. Falsifiability / Test Handle: Evaluate safety factor profiles in experimental toroidal systems and verify that instabilities occur when qqq falls below the critical threshold. 2.0.178 ID 327: Quantum Vortex Circulation Quantization Type: Definition Formal Statement: In a superfluid or Bose–Einstein condensate, the macroscopic wavefunction \$Ψ(r,t)=n(r,t)ei(r,t)\textbackslash{}Psi(r,t)\$ = \textbackslash{}sqrt\{n(r,t)\} \$eˆ\{i\textbackslash{}phi(r,t)\}Ψ(r, t)\$ = \$n(r, t)ei(r, t)exhibitscirculationquantization\$ : \$vd\$ = \$2πn/m\textbackslash{}ointv\textbackslash{}cdotd\textbackslash{}ell\$ = \$2\textbackslash{}pi\textbackslash{}hbarn/mvd\$ = \$2πn/m,wherennnistheintegerwindingnumberandmmmthemassoftheconstituentparticle.\$ Interpretive Meaning: The circulation of the velocity field around a closed loop in a superfluid is quantized in units of \$2π/m2\textbackslash{}pi\textbackslash{}hbar/m2π/m.\$ This arises from the singlevaluedness of the condensate wavefunction and underlies the stability of quantized vortices in gyromagnetic BECenhanced sys

\paragraph{Canonical Equation.}
\[
2πn/m\ointv\cdotd\ell
\]

\paragraph{Dictionary.}
Relation: 2πn/mointv·dℓ — 2πn/mointv·dℓ

\paragraph{Encyclopedia.}
Relation: 2πn/mointv·dℓ is a contour integral, written 2πn/mointv·dℓ. It is evaluated by integrating along a closed contour, capturing global or topological properties of the field. It is built from ℓ, n, m. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
