\section*{ID9499: Geometry: Curvature of Spheres and Tori}
\paragraph{Metadata.}
PiID: 4551050080190 | RTEID: RTE:P36886.7265:T4.2293 | UUID: 32be19c1-e3b4-53b7-9fdb-b9fcf0fb34b6

\paragraph{Canonical Statement.}
More abstractly, one can consider other geometric constructs. The \textbackslash{}emph\{mean curvature\} \$H\$ (an extrinsic curvature measure) of a sphere equals \$2/R\$, whereas for a torus it varies with position; the ratio \$H\textasciicircum{}2/K\$ is identically 4 for a sphere, but on a torus it fluctuates and could take values near \$1.185\$ for certain angles. The topology of the 3-sphere \$S\textasciicircum{}3\$ (a three-dimensional sphere) offers another angle: \$S\textasciicircum{}3\$ has constant positive curvature (Ricci scalar \$R\_\{\textbackslash{}text\{scalar\}\} = 6/R\textasciicircum{}2\$ if radius \$R\$), while a \textbackslash{}emph\{toroidal\} topology (genus-1 surface in higher dimensions) has a different curvature signature. Comparing a curved 3-sphere to a “flat” 3-torus (or considering a small \$S\textasciicircum{}2\$ geodesic surface embedded in \$S\textasciicircum{}3\$) yields natural dimensionless ratios. For instance, the volume of \$S\textasciicircum{}3\$ of radius \$R\$ is \$V\_\{S\textasciicircum{}3\}=2\textbackslash{}pi\textasciicircum{}2R\textasciicircum{}3\$, while the surface area of \$S\textasciicircum{}2\$ of the same \$R\$ is \$A\_\{S\textasciicircum{}2\}=4\textbackslash{}pi R\textasciicircum{}2\$. Their ratio \$V\_\{S\textasciicircum{}3\}/(R\textbackslash{}cdot A\_\{S\textasciicircum{}2\}) = \textbackslash{}frac\{2\textbackslash{}pi\textasciicircum{}2R\textasciicircum{}3\}\{4\textbackslash{}pi R\textasciicircum{}3\}=\textbackslash{}frac\{\textbackslash{}pi\}\{2\} \textbackslash{}approx 1.5708\$, not far from \$4/3 \textbackslash{}approx 1.333\$; one could imagine a modified construction or curvature weighting that yields \$1.185\$ in a topological transition between \$S\textasciicircum{}3\$ and a torus. While t

\paragraph{Canonical Equation.}
\[
), while a \emph{toroidal} topology (genus-1 surface in higher dimensions) has a different curvature signature. Comparing a curved 3-sphere to a “flat” 3-torus (or considering a small
\]

\paragraph{Dictionary.}
More abstractly, one can consider other geometric constructs.

\paragraph{Encyclopedia.}
Geometry: Curvature of Spheres and Tori is a symbolic expression, written ), while a emphtoroidal topology (genus-1 surface in higher dimensions) has a di. It introduces a symbol or relation used elsewhere in the framework. It is built from w, h, l, a, o, r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
