\section*{ID8868: ALFVEN WAVE DISPERSION (GYROSCOPIC) Canonical Statutory Formula: ω\textasciicircum{}2}
\paragraph{Metadata.}
PiID: 4263639548000 | RTEID: RTE:P34436.4134:T0.1920 | UUID: b8f31627-47d6-5187-a960-c95f6484e3ea

\paragraph{Canonical Statement.}
[ID 1007] ALFVEN WAVE DISPERSION (GYROSCOPIC) Canonical Statutory Formula: \$\textbackslash{}omega\textasciicircum{}2 = k\textasciicircum{}2 v\_A\textasciicircum{}2 \textbackslash{}left[ 1 + \textbackslash{}left( \textbackslash{}frac\{\textbackslash{}omega\_\{gyro\}\}\{\textbackslash{}omega\} \textbackslash{}right)\textasciicircum{}2 \textbackslash{}right]\$ Formal Technical Dissertation: Defines the fundamental speed and frequency scale for magneto-acoustic dynamics in a rotating frame. The gyroscopic term \$\textbackslash{}omega\_\{gyro\}\$ shifts the natural Alfvén frequencies, creating quantized standing wave modes. Source: [11]

\paragraph{Canonical Equation.}
\[
\omega^2 = k^2 v_A^2 \left[ 1 + \left( \frac{\omega_{gyro}}{\omega} \right)^2 \right]
\]

\paragraph{Dictionary.}
ALFVEN WAVE DISPERSION (GYROSCOPIC) Canonical Statutory Formula: \$ \textasciicircum{}2 = k\textasciicircum{}2 v\_A\textasciicircum{}2 [ 1 + ( \_gyro )\textasciicircum{}2 ]\$ Formal Technical Dissertation: Defines the fundamental speed and frequency scale for magneto-acoustic dynamics in a rotating frame.

\paragraph{Encyclopedia.}
ALFVEN WAVE DISPERSION (GYROSCOPIC) Canonical Statutory Formula: ω\textasciicircum{}2 is an algebraic definition, written ω\textasciicircum{}2 = k\textasciicircum{}2 v\_A\textasciicircum{}2 [ 1 + ( fracω\_gyroω )\textasciicircum{}2 ]. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from ω, k, v\_A, g, y, r, defining ω\textasciicircum{}2. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
