\tzpanchor{0910}
\tzpentryheader{0910}{CANTOR PAIRING CASCADE FUNCTION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{87293130-8971-5ab3-854b-3d2f5613287f}}\\
\textbf{PiID} & \tzpcode{2875546873115} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{917}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3479.3670 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.7329 rad}\\
\textbf{TZPID} & \tzpcode{ID0910} & \textbf{Node Dependencies}\quad \tzpidref{0909}\\
\textbf{Registry} & \tzpcode{registry\_id\_0910} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Cantor Pairing & Recursive Cascade\\
\textbf{Closure Support} & Address Reduction & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Cantor pairing cascade encodes an ordered integer stream by repeatedly applying the Cantor pairing map. Each stage remains reversible over nonnegative integer inputs, while the final address reduction maps the cascade value into the admissible directory range.

\tzpsection{Canonical Equation}
\[
C(x,y)=\frac{(x+y)(x+y+1)}{2}+y
\]
\[
c_1=C(a_1,a_2),\qquad c_{n+1}=C(c_n,a_{n+2})
\]
\[
A_{\mathrm{dir}}=1+\bigl(c_N \bmod 153600\bigr)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $C$: speed of light or relativistic conversion factor.
    \item $c_1$: source equation symbol.
    \item $a_1$: source equation symbol.
    \item $a_2$: source equation symbol.
    \item $c_{n+1}$: source equation symbol.
    \item $n$: integer mode index.
    \item $c_n$: source equation symbol.
    \item $a_{n+2}$: source equation symbol.
    \item $A_{\mathrm{dir}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0910 generated source Wolfram model *)
ClearAll[K0910, Cr0910, T, R, A, W, I, N];
eq0910$1 = HoldForm[C[x, y] == ((x + y)*(x + y + 1))/2 + y];
eq0910$2 = HoldForm[TZPSequence[c1 == C[a1, a2], cN1 == C[cN, aN2]]];
eq0910$3 = HoldForm[ADir == 1 + cNbmod153600];

K0910 = HoldForm[{eq0910$1, eq0910$2, eq0910$3}];

N = "normalized TRAWIN closure object for CANTOR PAIRING CASCADE FUNCTION";
I = "CANTOR PAIRING CASCADE FUNCTION integration/comparison layer";
W = "CANTOR PAIRING CASCADE FUNCTION wave or operator carrier";
A = "CANTOR PAIRING CASCADE FUNCTION admissible action/amplitude condition";
R = "CANTOR PAIRING CASCADE FUNCTION rotation/curl preservation layer";
T = "CANTOR PAIRING CASCADE FUNCTION local source condition";

Cr0910[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0910 = Cr0910[K0910];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ CANTOR PAIRING CASCADE FUNCTION local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ CANTOR PAIRING CASCADE FUNCTION rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ CANTOR PAIRING CASCADE FUNCTION admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ CANTOR PAIRING CASCADE FUNCTION wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ CANTOR PAIRING CASCADE FUNCTION integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for CANTOR PAIRING CASCADE FUNCTION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0910] CANTOR PAIRING CASCADE FUNCTION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
C(x,y)=\frac{(x+y)(x+y+1)}{2}+y
\]
\[
c_1=C(a_1,a_2),\qquad c_{n+1}=C(c_n,a_{n+2})
\]
\[
A_{\mathrm{dir}}=1+\bigl(c_N \bmod 153600\bigr)
\]

\paragraph{Primary Derivation.}
The relation is obtained by differentiating and applying the relevant definitions. giving the formula in the first line.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. Interpreted through TRAWIN, the equation functions as the generalized carrier for the entry’s information content. Within the CHL view, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors CANTOR PAIRING CASCADE FUNCTION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
C(x,y)=\frac{(x+y)(x+y+1)}{2}+y
\]
\[
c_1=C(a_1,a_2),\qquad c_{n+1}=C(c_n,a_{n+2})
\]
\[
A_{\mathrm{dir}}=1+\bigl(c_N \bmod 153600\bigr)
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0910] CANTOR PAIRING CASCADE FUNCTION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
CANTOR PAIRING CASCADE FUNCTION is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Cantor(x, y). \textbf{Contextual meaning:} The entry reads CANTOR PAIRING CASCADE FUNCTION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the pairing cascade as an actual recursive integer map instead of carrying broken pairing syntax into display mode. \textbf{Lemma support:} Cantor Pairing; Recursive Cascade; Address Reduction.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, CANTOR PAIRING CASCADE FUNCTION is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: gistry sub id sub 0907,CATEGORICAL ENCODING MORPHISM,CATEGORICAL ENCODING MORPHISM,tzpid sub registry ,tzpid sub registry sub foldin, decoded = Psi sub decoder [encoded, Dimensions[blob][[1]]]; gistry sub id sub 0911,TESSERACT FOLDING OPERATOR,TESSERACT FOLDING OPERATOR,tzpid sub registry ,tzpid sub registry sub foldin, surface sub point = Quotient[raw sub address - hypercube sub vertex , 16] + 1; and QUANTUM PATH INTEGRAL NAVIGATION,QUANTUM PATH INTEGRAL NAVIGATION,tzpid sub registry ,tzpid sub registry sub foldin,  Trawin[psi, t] =  tunnel +  ER +  SC +  cymatic +  TZP. Proof route: show that repeated application of the Cantor pairing function collapses the full integer sequence into a unique final address value. Formalization route: prove that the final reduced address follows from the recursive pairing cascade modulo the DAANSphere address range.

\tzpsection{Interpretive Role}
The entry now states the pairing cascade as an actual recursive integer map instead of carrying broken pairing syntax into display mode.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Bijective Integer Mapping}: The mathematical trick of taking two completely separate lists of numbers and flawlessly zipping them together into a single, unbreakable stream of data.
\item \textbf{Recursive Dimensional Collapse}: The aggressive compression algorithm that takes a 3D holographic scan of the plasma and squishes it down into a flat, 1D line of code.
\item \textbf{Deterministic Data Weaving}: The process of combining the temperature and pressure readings into a single variable, ensuring that neither piece of information can ever be separated or lost.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0910]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0910].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0910] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont CANTOR PAIRING CASCADE FUNCTION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} CANTOR PAIRING CASCADE FUNCTION is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``CANTOR PAIRING CASCADE FUNCTION is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0910].
\par\endgroup
\vfill
\endgroup
\endgroup
