\section*{ID7048: Suggested Starting Parameters \& Nondimensional Groups: R ∼ 10\textasciicircum{}-4 – 10\textasciicircum{}-3}
\paragraph{Metadata.}
PiID: 3814657412680 | RTEID: RTE:P27368.9492:T1.1133 | UUID: e39c4cbf-4f41-5f63-aed3-98db146f73cd

\paragraph{Canonical Statement.}
Practical numeric seed (lab-scale order of mag): - Characteristic radius \textbackslash{}(R \textbackslash{}sim 10\textasciicircum{}\{-4\} – 10\textasciicircum{}\{-3\}\textbackslash{}) m (100 µm–1 mm) for microfluidic shells; for bench vortex go up to cm scale. - Base speed \textbackslash{}(U\_0\textbackslash{}) such that \textbackslash{}(Re\textbackslash{}) from 10\textasciicircum{}2 to 10\textasciicircum{}4 depending on whether you want laminar/turbulent regime. - Ferrofluid magnetization fields \textbackslash{}(H\textbackslash{}) from 10\textasciicircum{}3–10\textasciicircum{}5 A/m (typical lab electromagnets) to reach Rosensweig thresholds. citeturn1search3

\paragraph{Canonical Equation.}
\[
R \sim 10^{-4} – 10^{-3}
\]

\paragraph{Dictionary.}
Practical numeric seed (lab-scale order of mag): - Characteristic radius \textbackslash{}(R 10\textasciicircum{}-4 – 10\textasciicircum{}-3\textbackslash{}) m (100 µm–1 mm) for microfluidic shells; for bench vortex go up to cm scale.

\paragraph{Encyclopedia.}
Suggested Starting Parameters \& Nondimensional Groups: R ∼ 10\textasciicircum{}-4 – 10\textasciicircum{}-3 is a scaling / order-of-magnitude relation, written R ∼ 10\textasciicircum{}-4 – 10\textasciicircum{}-3. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from R. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
