\section*{ID9466: Definition of · · · Esupport}
\paragraph{Metadata.}
PiID: 5284716050492 | RTEID: RTE:P36758.5802:T4.0182 | UUID: bf11d3b4-eeb7-5779-abc6-d97279acd924

\paragraph{Canonical Statement.}
e Certificate Lean Certificate Coq Certificate lemmaid1086\_information\_density\_tracking:sorry theoremid1086\_information\_density\_tracking Theoremid1086\_information\_density\_tracking Dependencies and Test Handle Dependencies [ID 1085], [ID 1000] Node registry\_id\_1086 Support Titles Scaling Law; Transfer Map; Transfer Map Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links 𝐼𝑑𝑒𝑛𝑠𝑖𝑡 𝑦 = log2(153, 600) \$≈\$ · · · Esupport = · · · 𝐶𝑢𝑟𝑟𝑒𝑛𝑡𝑑𝑒𝑛𝑠𝑖𝑡𝑦𝐽 : R3 × R \$→\$ R3 [ID 1087] MUTUAL INFORMATION FUNCTIONAL TZPID ID1087 UUID bef4bf06-b29a-5fd6-918a-11d2db0d66a2 Type Information Functional / Entropy Statement Scale informational LOC Classification Working routing: QA76.9 information and coding; QA614 topological data analysis arXiv Classification Primary: cs.IT; Cross-list: math.AT, math-ph Canonical Statement This entry develops mutual information functio

\paragraph{Canonical Equation.}
\[
· · · Esupport = · · · 𝐶𝑢𝑟𝑟𝑒𝑛𝑡𝑑𝑒𝑛𝑠𝑖𝑡𝑦𝐽 : R3 × R
\]

\paragraph{Dictionary.}
Definition of · · · Esupport — · · · Esupport = · · · 𝐶𝑢𝑟𝑟𝑒𝑛𝑡𝑑𝑒𝑛𝑠𝑖𝑡𝑦𝐽 : R3 × R

\paragraph{Encyclopedia.}
Definition of · · · Esupport is an algebraic definition, written · · · Esupport = · · · 𝐶𝑢𝑟𝑟𝑒𝑛𝑡𝑑𝑒𝑛𝑠𝑖𝑡𝑦𝐽 : R3 × R. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R, defining · · · Esupport. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
