\section*{ID9518: Synchronization: Kuramoto Networks and Phase Coherence: ∼ 1/r\textasciicircum{}p}
\paragraph{Metadata.}
PiID: 3302763478708 | RTEID: RTE:P36960.5077:T4.3509 | UUID: e392b38c-fbaa-55e0-abbd-474919793fe7

\paragraph{Canonical Statement.}
r by \textasciitilde{}15\%) would push them over the threshold to coalesce into a larger body. In essence, \$\textbackslash{}chi\$ could demarcate the border between chaos and order in these rotationally-supported disks: inside a certain radius, gravitation plus dissipation can synchronize orbits enough to clear gaps and form planets; outside, synchronization fails and a belt of debris remains. This nicely dovetails with the earlier geometric interpretation of a “synchronization sphere” radius – an imaginary surface around the Sun where coupling drops off. If we quantify that drop-off as a power-law in distance (e.g. coupling \$\textbackslash{}sim 1/r\textasciicircum{}p\$), the ratio of coupling at the inner edge of the asteroid belt to the threshold needed might indeed be a number like 0.85 (the inverse of \$\textbackslash{}chi\$). The DAT-GPT model formalizes this with an explicit equation for the DAT-GPT Synchronization Sphere (DSS):

\paragraph{Canonical Equation.}
\[
\sim 1/r^p
\]

\paragraph{Dictionary.}
Synchronization: Kuramoto Networks and Phase Coherence: ∼ 1/r\textasciicircum{}p — ∼ 1/r\textasciicircum{}p

\paragraph{Encyclopedia.}
Synchronization: Kuramoto Networks and Phase Coherence: ∼ 1/r\textasciicircum{}p is a scaling / order-of-magnitude relation, written ∼ 1/r\textasciicircum{}p. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from r, p. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
