\section*{ID9418: Definition of 𝜔}
\paragraph{Metadata.}
PiID: 5714298946715 | RTEID: RTE:P36572.1855:T3.7110 | UUID: 038a1801-8452-5417-b651-b44acc304060

\paragraph{Canonical Statement.}
6] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0385], [ID 0300] Node registry\_id\_0386 Support Titles Dispersion Law; Standing Quantization; Mode Closure Test Handle If a bounded Alfvén carrier cannot be quantized into admissible standing modes, the hinge law for the third hundred fails. Canonical Equation Links \$𝜔=𝑘∥𝑣A 𝑘𝑛=𝑛𝜋/𝐿∥ 𝜔𝑛=𝑛𝜋𝑣A/𝐿∥\$ [ID 0387] Triple Resonance Domain Condition TZPID ID0387 UUID db36c1ef-8045-53f2-aa00-8275f2483488 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops triple resonance domain condition inside the field theory a

\paragraph{Canonical Equation.}
\[
𝜔=𝑘∥𝑣A 𝑘𝑛=𝑛𝜋/𝐿∥ 𝜔𝑛=𝑛𝜋𝑣A/𝐿∥
\]

\paragraph{Dictionary.}
Definition of 𝜔 — 𝜔=𝑘∥𝑣A 𝑘𝑛=𝑛𝜋/𝐿∥ 𝜔𝑛=𝑛𝜋𝑣A/𝐿∥

\paragraph{Encyclopedia.}
Definition of 𝜔 is an algebraic definition, written 𝜔=𝑘∥𝑣A 𝑘𝑛=𝑛𝜋/𝐿∥ 𝜔𝑛=𝑛𝜋𝑣A/𝐿∥. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from A, defining 𝜔. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
