\tzpanchor{0993}
\tzpentryheader{0993}{TACHOCLINE SHEAR GRADIENT}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{660bf7bc-5d70-5be2-8265-a13c6fa72c66}}\\
\textbf{PiID} & \tzpcode{4201989380952} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{1000}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3782.2583 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{06.2320 rad}\\
\textbf{TZPID} & \tzpcode{ID0993} & \textbf{Node Dependencies}\quad \tzpidref{0992}\\
\textbf{Registry} & \tzpcode{registry\_id\_0993} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
\{alpha, -eta\_t nabla\textasciicircum{}2, partialOmega/partialr\}, (* SHEAR TERM - opposing rotation *)

\tzpsection{Canonical Equation}
\[
{\alpha, -\eta_{\mathrm{t}}  abla^{2}, \partial\Omega/\mathrm{partialr}}, SHEAR TERM - opposing rotation
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $J$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0993 generated source Wolfram model *)
ClearAll[K0993, Cr0993, T, R, A, W, I, N];
eq0993$1 = HoldForm[TachoclineShearGradient == {alpha, (-etaT)*LaplacianOperator, PartialOmegaPartialR}];
eq0993$2 = HoldForm[JOut == TTZP[KTZP]];

K0993 = HoldForm[{eq0993$1, eq0993$2}];

N = "normalized TRAWIN closure object for TACHOCLINE SHEAR GRADIENT";
I = "TACHOCLINE SHEAR GRADIENT integration/comparison layer";
W = "TACHOCLINE SHEAR GRADIENT wave or operator carrier";
A = "TACHOCLINE SHEAR GRADIENT admissible action/amplitude condition";
R = "TACHOCLINE SHEAR GRADIENT rotation/curl preservation layer";
T = "TACHOCLINE SHEAR GRADIENT local source condition";

Cr0993[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0993 = Cr0993[K0993];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ TACHOCLINE SHEAR GRADIENT local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TACHOCLINE SHEAR GRADIENT rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ TACHOCLINE SHEAR GRADIENT admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TACHOCLINE SHEAR GRADIENT wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TACHOCLINE SHEAR GRADIENT integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TACHOCLINE SHEAR GRADIENT.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0993] TACHOCLINE SHEAR GRADIENT}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
{\alpha, -\eta_{\mathrm{t}}  abla^{2}, \partial\Omega/\mathrm{partialr}}, SHEAR TERM - opposing rotation
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\paragraph{Primary Derivation.}
To derive the stated relation by differentiating and applying the relevant definitions. which confirms the stated equality.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. From the TRAWIN perspective, the equation functions as the generalized carrier for the entry’s information content. According to CHL, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TACHOCLINE SHEAR GRADIENT by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
{\alpha, -\eta_{\mathrm{t}}  abla^{2}, \partial\Omega/\mathrm{partialr}}, SHEAR TERM - opposing rotation
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0993] TACHOCLINE SHEAR GRADIENT}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TACHOCLINE SHEAR GRADIENT is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} alpha, -eta sub t nabla to the power 2, partialOmega/partialr , (* SHEAR TERM - opposing rotation *). \textbf{Contextual meaning:} The entry reads TACHOCLINE SHEAR GRADIENT as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, TACHOCLINE SHEAR GRADIENT is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: alpha, -eta sub t abla to the power 2 , partialOmega/ partialr , SHEAR TERM - opposing rotation; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Plasma-Layer Friction Tearing}: The incredibly violent physics of a fast-moving, screaming layer of boiling energy violently rubbing against a slower, heavier layer of cold gas.
\item \textbf{Differential-Rotation Boundary Mapping}: The delicate technique of finding the exact, razor-thin line in the reactor where the inside is spinning at three thousand RPM and the outside is standing perfectly still.
\item \textbf{Viscous-Drag Magnetic Choking}: The terrifying problem where the slow, sticky edges of the plasma storm act like sludge, aggressively pulling and dragging on the incredibly fast, clean center.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0993]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0993].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0993] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TACHOCLINE SHEAR GRADIENT}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} TACHOCLINE SHEAR GRADIENT is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TACHOCLINE SHEAR GRADIENT is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0993].
\par\endgroup
\vfill
\endgroup
\endgroup
