\section*{ID9537: Clarifying Note on the Quantum Tunneling Term: -fracħ\textasciicircum{}22m\_eff∇\textasciicircum{}2}
\paragraph{Metadata.}
PiID: 4501193071412 | RTEID: RTE:P37034.2890:T4.4725 | UUID: 90d0e2fa-b00e-5dea-b810-8c1d459ce0d3

\paragraph{Canonical Statement.}
The quantum tunneling contribution in the RNA→DNA transition captures the energetic and geometric asymmetry arising from the presence of the 2\$\textasciicircum{}\{\textbackslash{}prime\}\$-hydroxyl group in RNA. This functional group introduces a torsional barrier in the ribose ring, which is effectively modeled by a potential \$V\_\{\textbackslash{}mathrm\{barrier\}\}(r,\textbackslash{}theta,\textbackslash{}phi)\$. The Laplacian term \$-\textbackslash{}frac\{\textbackslash{}hbar\textasciicircum{}\{2\}\}\{2m\_\{\textbackslash{}mathrm\{eff\}\}\}\textbackslash{}nabla\textasciicircum{}\{2\}\$ describes the quantum delocalization of the ribose configuration along internal coordinates.

\paragraph{Canonical Equation.}
\[
-\frac{\hbar^{2}}{2m_{\mathrm{eff}}}\nabla^{2}
\]

\paragraph{Dictionary.}
The quantum tunneling contribution in the RNA→DNA transition captures the energetic and geometric asymmetry arising from the presence of the 2\textasciicircum{}prime-hydroxyl group in RNA.

\paragraph{Encyclopedia.}
Clarifying Note on the Quantum Tunneling Term: -fracħ\textasciicircum{}22m\_eff∇\textasciicircum{}2 is a differential equation, written -fracħ\textasciicircum{}22m\_eff∇\textasciicircum{}2. It relates the quantity to its derivatives, governing how the system evolves in space and time. It is built from ħ, ∇, m\_. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
