\section*{ID8542: CHROMATIN TOPOLOGICAL CARDINALITY Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 5165827658483 | RTEID: RTE:P33170.4830:T4.3893 | UUID: 4deb79dc-6938-5974-a53e-323c229f69d2

\paragraph{Canonical Statement.}
[ID 1128] CHROMATIN TOPOLOGICAL CARDINALITY Canonical Statutory Formula: \$|Obj(Bio)| \textbackslash{}approx 25k\_\{genes\} + 100k\_\{reg\} + 30k\_\{dom\} \textbackslash{}approx 155,000\$ Formal Technical Dissertation: A validation metric summing the distinct biological objects (genes, regulatory elements, and chromatin domains). The resulting cardinality (\textasciitilde{}155,000) aligns within the error margin of the 153,600-node engineered lattice, confirming the system's capacity to map the full "Biological Category." Source: [5]

\paragraph{Canonical Equation.}
\[
|Obj(Bio)| \approx 25k_{genes} + 100k_{reg} + 30k_{dom} \approx 155,000
\]

\paragraph{Dictionary.}
CHROMATIN TOPOLOGICAL CARDINALITY Canonical Statutory Formula: \$ Obj(Bio) 25k\_genes + 100k\_reg + 30k\_dom 155,000\$ Formal Technical Dissertation: A validation metric summing the distinct biological objects (genes, regulatory elements, and chromatin domains).

\paragraph{Encyclopedia.}
CHROMATIN TOPOLOGICAL CARDINALITY Canonical Statutory Formula is a scaling / order-of-magnitude relation, written |Obj(Bio)| ≈ 25k\_genes + 100k\_reg + 30k\_dom ≈ 155,000. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from O, b, j, B, o, k\_genes. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
