\section*{ID6952: Concrete Next Steps I Recommend (In Order): 1/τ Lesssim γ\_th}
\paragraph{Metadata.}
PiID: 5714159578111 | RTEID: RTE:P26996.1599:T0.4991 | UUID: c70af766-affd-58d2-b569-74bca6e025ba

\paragraph{Canonical Statement.}
\#\# Concrete next steps I recommend (in order) 1. **Decide exact frequency band** (780 nm is a convenient starting point; consider 532 nm, 590 nm, or telecom depending on dyes / fabrication constraints). 2. **Choose thermalizer**: dye (Rhodamine-class) for room-temperature experiments; exciton-polaritons (quantum wells) for stronger interactions and faster thermalization. 3. **Target a Q to beat loss**: aim to get τ such that \textbackslash{}(1/\textbackslash{}tau \textbackslash{}lesssim \textbackslash{}gamma\_\{\textbackslash{}mathrm\{th\}\}\textbackslash{}). With τ = 10 ns (Q ≈ 2.4×10\textasciicircum{}7 for our λ), loss rate \textasciitilde{}1e8 s⁻¹, comparable to a 5-ns thermalizer. 4. **Simulate** an electromagnetic model (FDTD or FEM) for your photonic-crystal torus to extract precise mode fields, Q, and group velocity. From that, compute exact FSR, mode volume, and field overlap with the thermalizer layer. 5. **Run a small rate-equation model** that couples photons and thermalizer states (pump rate, absorption cross-section, spontaneous re-emission, nonradiative loss, cavity loss) to find threshold pump power and steady-state condensate fraction. 6. **Prototype** at microwave/THz first (easier materials, superconducting mirrors), or use a larger-radius optical ring to relax fabrication tolerances.

\paragraph{Canonical Equation.}
\[
1/\tau \lesssim \gamma_{\mathrm{th}}
\]

\paragraph{Dictionary.}
Concrete Next Steps I Recommend (In Order): 1/τ Lesssim γ\_th — 1/τ lesssim γ\_th

\paragraph{Encyclopedia.}
Concrete Next Steps I Recommend (In Order): 1/τ Lesssim γ\_th is a symbolic expression, written 1/τ lesssim γ\_th. It introduces a symbol or relation used elsewhere in the framework. It is built from τ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
