\section*{ID9225: Definition of Dim(Hfrequency)}
\paragraph{Metadata.}
PiID: 2296780705765 | RTEID: RTE:P35822.7237:T2.4762 | UUID: e216b043-9e0f-5007-a828-c5b77b69d298

\paragraph{Canonical Statement.}
that mapping 16 hypercube vertices under stereographic projection yields distinct, uniformly distributed points on S2Sˆ2S2 and that projected circles correspond to quaternion geodesics. 2.0.157 ID 306: Quantum State Space Decomposition Type: Definition Formal Statement: The total Hilbert space used for quantum holographic navigation factors as \$Htotal\$ = \$Hspatial ⊗HOAM ⊗Hpolarization ⊗Hfrequency,\$ where \$dim(Hspatial)\$ = \$153,600, dim(HOAM)\$ = \$2mmax\$ + 1, \$dim(Hpolarization)\$ = 2, and \$dim(Hfrequency) =∞.\$ Interpretive Meaning: Quantum states encoding holographic information decompose into four independent subsystems: spatial address, orbital angular momentum, polarization, and frequency. This decomposition facilitates modular encoding and manipulation of quantum information across multiple degrees of freedom. Dependencies: IDs 301–305. Derivable Consequences: (1) Enables tensor product structure f

\paragraph{Canonical Equation.}
\[
dim(Hfrequency) =∞.
\]

\paragraph{Dictionary.}
Definition of Dim(Hfrequency) — dim(Hfrequency) =∞.

\paragraph{Encyclopedia.}
Definition of Dim(Hfrequency) is an algebraic definition, written dim(Hfrequency) =∞.. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
