\tzpanchor{0021}
\tzpentryheader{0021}{Trawin Characteristic Class}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{69a35368-5caf-5587-865a-f4e8fc4a5d56}}\\
\textbf{PiID} & \tzpcode{6433832795028} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{28}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{81.5477 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.1344 rad}\\
\textbf{TZPID} & \tzpcode{ID0021} & \textbf{Node Dependencies}\quad \tzpidref{0020}\\
\textbf{Registry} & \tzpcode{registry\_id\_0021} & \textbf{Scale}\quad cohomological\\
\textbf{LOC Classification} & QA612.7 characteristic classes & QA612 cohomology\\
\textbf{arXiv Classification} & Primary: math.AT \quad Cross-list: math.DG, math-ph & \\
\textbf{Primary Support} & Curvature Two-Form & Normalized Cohomology Representative\\
\textbf{Closure Support} & Holonomy-Winding Match & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Trawin characteristic class records how a gauge bundle twists around the punctured manifold obtained by removing the Trawin Zero Point. It lifts the winding-number information into a cohomological object.

\tzpsection{Canonical Equation}
\[
c_{T}
=
\left[\frac{1}{2\pi}F\right]
\in
H^{2}(M\setminus\{p\},\mathbb{Z})
\]
\[
\operatorname{hol}(\mathcal{A}) = w
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $c_{T}$: source equation symbol.
    \item $T$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $F$: source equation symbol.
    \item $H$: source equation symbol.
    \item $M$: source equation symbol.
    \item $Z$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0021 generated source Wolfram model *)
ClearAll[K0021, Cr0021, T, R, A, W, I, N];
eq0021$1 = HoldForm[Element[cT == TZPGroup[(1/(2*Pi))*F], H^2*Tuple[MsetminusList[p], Z]]];
eq0021$2 = HoldForm[hol[A] == w];
eq0021$3 = HoldForm[F];

K0021 = HoldForm[{eq0021$1, eq0021$2, eq0021$3}];

N = "normalized TRAWIN closure object for Trawin Characteristic Class";
I = "Holonomy-Winding Match integration/comparison layer";
W = "Normalized Cohomology Representative wave or operator carrier";
A = "Curvature Two-Form admissible action/amplitude condition";
R = "Normalized Cohomology Representative rotation/curl preservation layer";
T = "Curvature Two-Form local source condition";

Cr0021[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0021 = Cr0021[K0021];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Curvature Two-Form local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Normalized Cohomology Representative rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Curvature Two-Form admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Normalized Cohomology Representative wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Holonomy-Winding Match integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Trawin Characteristic Class.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0021] Trawin Characteristic Class}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
c_T
=
\left[
\frac{1}{2\pi}F
\right]
\in
H^2(M\setminus\{p\},\mathbb{Z}) .
\end{equation}

\paragraph{Primary Derivation.}
Let $F$ be the curvature two-form of a principal $U(1)$ bundle over the punctured manifold $M\setminus\{p\}$.

For a $U(1)$ bundle, the first characteristic class is obtained by normalizing curvature by $2\pi$:

\begin{equation}
\frac{1}{2\pi}F .
\end{equation}

Taking the cohomology class gives:

\begin{equation}
c_T
=
\left[
\frac{1}{2\pi}F
\right].
\end{equation}

Since the TZP is removed from the base space, the class naturally lives in:

\begin{equation}
H^2(M\setminus\{p\},\mathbb{Z}) .
\end{equation}

Thus,

\begin{equation}
\boxed{
c_T
=
\left[
\frac{1}{2\pi}F
\right]
\in
H^2(M\setminus\{p\},\mathbb{Z}) .
}
\end{equation}

\paragraph{Interpretation.}
The Trawin characteristic class records the topological charge generated by removing the TZP from the manifold.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Trawin Characteristic Class by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Curvature Two-Form}\par
\[
F
\]
\noindent This is the geometric field strength whose global integral data records twisting around the puncture.\par
\noindent\textbf{2. Normalized Cohomology Representative}\par
\[
c_{T}
=
\left[\frac{1}{2\pi}F\right]
\in
H^{2}(M\setminus\{p\},\mathbb{Z})
\]
\noindent This converts local curvature into a global integral cohomology class.\par
\noindent\textbf{3. Holonomy-Winding Match}\par
\[
\operatorname{hol}(\mathcal{A}) = w
\]
\noindent This closes the progression by tying the characteristic class directly to the winding information established in the previous entry.\par

\clearpage
\noindent\textbf{[ID 0021] Trawin Characteristic Class}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Trawin Characteristic Class is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The Trawin characteristic class TrawinChar is an element of the cohomology group H2(M  p ,Z)H 2(Msetminustextbackslash ptextbackslash ,mathbb Z )H2(M  p ,Z) defined by c sub T= [ 12piF ] ctextbackslash sub T = [ ratio 1 2textbackslash pi F ] c sub T= [ 2pi1F ] , where FFF is the curvature two-form of a principal U(1) bundle whose connection one-form has holonomy equal to the Trawinistic winding number www. \textbackslash{}. \textbf{Contextual meaning:} The entry reads Trawin Characteristic Class as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Curvature Two-Form; Normalized Cohomology Representative; Holonomy-Winding Match.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The Trawin characteristic class records the topological charge generated by removing the TZP from the manifold.

\tzpsection{Equation Grounding}
Equation anchors: The Trawin characteristic class TrawinChar is an element of the cohomology group H2(M  p ,Z)H to the power 2(Msetminustextbackslash ptextbackslash ,mathbb Z )H2(M  p ,Z) defined by c T= [ 12piF ] ctextbackslash T = [ ratio 1 2textbackslash pi F ] c T= [ 2pi1F ] , where FFF is the curvature two-form of a principal U(1) bundle whose connection one-form has holonomy equal to the Trawinistic winding number www. The Trawin characteristic class TrawinChar is an element of the cohomology group H2(M  p ,Z)H to the power 2(Msetminustextbackslash ptextbackslash ,mathbb Z )H2(M  p ,Z) defined by c T= [ 12piF ] ctextbackslash T = [ ratio 1 2textbackslash pi F ] c T= [ 2pi1F ] , where FFF is the curvature two-form of a principal U(1) bundle whose connection one-form has holonomy equal to the Trawinistic winding number www.

\tzpsection{Interpretive Role}
This class is the bundle-level avatar of the winding number. It supports gauge classification, topological charge bookkeeping, and later conservation laws that need a global rather than purely local invariant.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Trawin-Normalized Characteristic Class}: normalization vocabulary for fixed form, invariant comparison, or TRAWIN admissibility.
\item \textbf{Trawin-Normalized Normalization Analogue}: normalization vocabulary for fixed form, invariant comparison, or TRAWIN admissibility.
\item \textbf{Trawin-Normalized Terminology}: normalization vocabulary for fixed form, invariant comparison, or TRAWIN admissibility.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0021]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0021_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0021] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Trawin Characteristic Class}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the Trawin characteristic class records how a gauge bundle twists around the punctured
manifold obtained by removing the Trawin Zero Point

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Trawin Characteristic Class is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0021_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
