\tzpanchor{0200}
\tzpentryheader{0200}{Alfv\'en Wave Dispersion Relation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{db5f61c2-29f5-5b3d-9215-6b9047347a98}}\\
\textbf{PiID} & \tzpcode{4428810975665} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{207}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{776.6444 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.2797 rad}\\
\textbf{TZPID} & \tzpcode{ID0200} & \textbf{Node Dependencies}\quad \tzpidref{0199}\\
\textbf{Registry} & \tzpcode{registry\_id\_0200} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Dispersion Law & Standing Quantization\\
\textbf{Closure Support} & Mode Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In a magnetized plasma with magnetic field \(B\) and mass density \(\rho\), the Alfv\'en velocity is \(v_A=B/\sqrt{\mu_0\rho}\). For a rotating system with gyroscopic frequency \(\omega_{\mathrm{gyro}}\), the dispersion relation is treated as an implicit mode equation for \(\omega_n\), not as an independently fixed standing-wave formula.

\tzpsection{Canonical Equation}
\[
v_{\mathrm{A}} = \frac{B}{\sqrt{\mu_0 \rho}}
\]
\[
k_n=\frac{n}{R}
\]
\[
\omega_n^{4}
-
k_n^{2}v_{\mathrm{A}}^{2}\omega_n^{2}
-
k_n^{2}v_{\mathrm{A}}^{2}\omega_{\mathrm{gyro}}^{2}
=0
\]
\[
\omega_n^2
=
\frac{k_n^2v_{\mathrm{A}}^2}{2}
\left[
1+
\sqrt{
1+
4\left(
\frac{\omega_{\mathrm{gyro}}}{k_nv_{\mathrm{A}}}
\right)^2
}
\right]
\]
\[
f_n=\frac{\omega_n}{2\pi}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $v_{\mathrm{A}}$: Alfv\'en velocity of the magnetized medium.
    \item $B$: magnetic field magnitude.
    \item $\mu_0$: vacuum permeability.
    \item $\rho$: mass density of the magnetized medium.
    \item $k_n$: mode-indexed wavenumber.
    \item $n$: integer mode index.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\omega_n$: mode-indexed angular frequency.
    \item $\omega_{\mathrm{gyro}}$: gyroscopic angular frequency of the rotating system.
    \item $f_n$: mode-indexed ordinary frequency.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0200 generated source Wolfram model *)
ClearAll[K0200, Cr0200, T, R, A, W, I, N];
eq0200$1 = HoldForm[vA == B/Sqrt[mu0*rho]];
eq0200$2 = HoldForm[kN == n/R];
eq0200$3 = HoldForm[omegaN^4 - kN^2*vA^2*omegaN^2 - kN^2*vA^2*omegaGyro^2 == 0];
eq0200$4 = HoldForm[omegaN^2 == ((kN^2*vA^2)/2)[1 + sqrt[1 + 4*(omegaGyro/kNvA)^2]]];
eq0200$5 = HoldForm[fN == omegaN/(2*Pi)];
eq0200$6 = HoldForm[fN == (n*vA)/(2*Pi*R)];

K0200 = HoldForm[{eq0200$1, eq0200$2, eq0200$3, eq0200$4, eq0200$5, eq0200$6}];

N = "normalized TRAWIN closure object for Alfv\'en Wave Dispersion Relation";
I = "Mode Closure integration/comparison layer";
W = "Implicit Gyroscopic Mode Closure wave or operator carrier";
A = "Dispersion Law admissible action/amplitude condition";
R = "Implicit Gyroscopic Mode Closure rotation/curl preservation layer";
T = "Dispersion Law local source condition";

Cr0200[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0200 = Cr0200[K0200];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Dispersion Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Implicit Gyroscopic Mode Closure rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Dispersion Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Implicit Gyroscopic Mode Closure wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Mode Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Alfv\textbackslash{}'en Wave Dispersion Relation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0200] Alfv\'en Wave Dispersion Relation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
v_{\mathrm{A}} = \frac{B}{\sqrt{\mu_0 \rho}}
\]
\[
k_n=\frac{n}{R}
\]
\[
\omega_n^{4}
-
k_n^{2}v_{\mathrm{A}}^{2}\omega_n^{2}
-
k_n^{2}v_{\mathrm{A}}^{2}\omega_{\mathrm{gyro}}^{2}
=0
\]
\[
\omega_n^2
=
\frac{k_n^2v_{\mathrm{A}}^2}{2}
\left[
1+
\sqrt{
1+
4\left(
\frac{\omega_{\mathrm{gyro}}}{k_nv_{\mathrm{A}}}
\right)^2
}
\right]
\]
\[
f_n=\frac{\omega_n}{2\pi}
\]

\paragraph{Primary Derivation.}
To derive the stated relation through direct evaluation of the expression. leading to the displayed result.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. In the TRAWIN reading, the equation functions as the generalized carrier for the entry’s information content. Under CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The Alfv\'en velocity anchors the medium response; the support equations then introduce bounded wave number and gyroscopic mode closure.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Dispersion Law}\par
\[
v_{\mathrm{A}} = \frac{B}{\sqrt{\mu_0 \rho}}
\]
\noindent This fixes the traveling Alfv\textbackslash{}'en carrier that later entries quantize and redistribute.\par
\noindent\textbf{2. Implicit Gyroscopic Mode Closure}\par
\[
\omega_n^{4}
-
k_n^{2}v_{\mathrm{A}}^{2}\omega_n^{2}
-
k_n^{2}v_{\mathrm{A}}^{2}\omega_{\mathrm{gyro}}^{2}
=0
\]
\noindent This keeps the mode frequency, gyroscopic correction, and Alfv\textbackslash{}'en speed in one closure equation.\par
\noindent\textbf{3. Mode Closure}\par
\[
f_n = \frac{n v_{\mathrm{A}}}{2\pi R}
\]
\noindent This closes the progression by tying the standing spectrum to an actual mode-index relation.\par

\clearpage
\noindent\textbf{[ID 0200] Alfv\'en Wave Dispersion Relation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small

\tzpsection{Definition}

The Alfv\'en wave dispersion entry begins with the characteristic propagation speed of a magnetized medium. Its velocity balances magnetic-field strength against mass-density inertia and vacuum permeability.

\tzpsection{Contextual Meaning}

A stronger magnetic field increases the characteristic wave speed, while a denser medium reduces it because more mass responds to magnetic restoring forces. This approved velocity relation anchors the entry before rotation modifies allowed modal frequencies.

\tzpsection{Formal Statement}

\[
v_{\mathrm{A}}=\frac{B}{\sqrt{\mu_0\rho}}
\]

\tzpsection{Derivable Consequences}

At fixed density, increasing \(B\) increases \(v_{\mathrm{A}}\) linearly. At fixed field magnitude, increasing \(\rho\) reduces \(v_{\mathrm{A}}\) through inverse square-root dependence.

\tzpsection{Lemma Support}

The approved alignment states the Alfv\'en velocity relation and identifies \(v_{\mathrm{A}}\), \(B\), \(\mu_0\), and \(\rho\). Gyroscopic mode closure remains progression material.

\tzpsection{Technical Interpretation}

The relation packages magnetic restoring strength and material inertia into a speed scale used before bounded-mode and gyroscopic corrections are introduced.

\tzpsection{Equation Grounding}

\(v_{\mathrm{A}}\) is the Alfv\'en velocity of the magnetized medium; \(B\) is magnetic field magnitude; \(\mu_0\) is vacuum permeability; and \(\rho\) is mass density of the magnetized medium.

\tzpsection{Interpretive Role}

This entry anchors wave dispersion in a magnetohydrodynamic carrier relation before the derivation examines bounded and rotational corrections.

\tzpsection{TZP Thesaurus}

\noindent \textbf{Alfv\'en Velocity}: The magnetic wave-speed scale arising from field strength and medium density. \enspace\textbullet\enspace \textbf{Magnetic Restoring Force}: The field-mediated response that supports transverse propagation in a magnetized plasma. \enspace\textbullet\enspace \textbf{Gyroscopic Mode Closure}: The later implicit frequency relation that modifies the anchored wave speed.\par

\endgroup

\tzpsection{Encyclopedia Mathematica}
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0200_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0200] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Alfv\'en Wave Dispersion Relation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in a magnetized plasma, \(v_A=B/\sqrt{\mu_0\rho}\), and a rotating
gyroscopic correction produces an implicit standing-mode closure for \(\omega_n\).

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Alfvén Wave Dispersion Relation is valid as a spectral relation when frequency, phase,
and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0200_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
