\tzpanchor{0518}
\tzpentryheader{0518}{FISHER-RAO INFORMATION GEOMETRY}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{3bf3f771-8a76-52c0-861a-fdbddbb504da}}\\
\textbf{PiID} & \tzpcode{3086021394946} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{525}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1992.0929 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.2824 rad}\\
\textbf{TZPID} & \tzpcode{ID0518} & \textbf{Node Dependencies}\quad \tzpidref{0517}\\
\textbf{Registry} & \tzpcode{registry\_id\_0518} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Fisher--Rao Metric & Score Expectation\\
\textbf{Closure Support} & Information Distance & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
-> Selection rule: DeltaH\_M = 0 or n*Phi\_0

\tzpsection{Canonical Equation}
\[
g_{ij}(\theta)=\mathbb{E}_{\theta}\!\left[\partial_i\log p(X\mid\theta)\,\partial_j\log p(X\mid\theta)\right]
\]
\[
mathbb{E}_{\theta}\!\left[\partial_i\log p(X\mid\theta)\right]=0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $g_{ij}$: source equation symbol.
    \item $\theta$: phase angle or local angular coordinate.
    \item $E$: source equation symbol.
    \item $X$: source variable, local coordinate, or input state in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0518 generated source Wolfram model *)
ClearAll[K0518, Cr0518, T, R, A, W, I, N];
eq0518$1 = HoldForm[gIj[theta] == ETheta[PartialIlog*p[X, theta]*PartialJlog*p[X, theta]]];
eq0518$2 = HoldForm[mathbb[E]*_*theta[PartialIlog*p[X, theta]] == 0];
eq0518$3 = HoldForm[ds2 == SumIj*gIj[theta]*dtheta^i*dtheta^j];

K0518 = HoldForm[{eq0518$1, eq0518$2, eq0518$3}];

N = "normalized TRAWIN closure object for FISHER-RAO INFORMATION GEOMETRY";
I = "Information Distance integration/comparison layer";
W = "Score Expectation wave or operator carrier";
A = "Fisher--Rao Metric admissible action/amplitude condition";
R = "Score Expectation rotation/curl preservation layer";
T = "Fisher--Rao Metric local source condition";

Cr0518[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0518 = Cr0518[K0518];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Fisher--Rao Metric local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Score Expectation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Fisher--Rao Metric admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Score Expectation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Information Distance integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for FISHER-RAO INFORMATION GEOMETRY.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0518] FISHER-RAO INFORMATION GEOMETRY}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Delta_T\phi
=
\nabla^{T}_{a}\nabla^{T\,a}\phi .
\end{equation}

\paragraph{Primary Derivation.}
For a scalar field $\phi$, the ordinary Laplacian is obtained by taking the divergence of the gradient.  
Replacing the ordinary connection with the Trawinistic connection gives:

\begin{equation}
\Delta_T\phi
=
\nabla^{T}_{a}
\left(
\nabla^{T\,a}\phi
\right).
\end{equation}

Using index notation, this becomes:

\begin{equation}
\boxed{
\Delta_T\phi
=
\nabla^{T}_{a}\nabla^{T\,a}\phi .
}
\end{equation}

Indices are raised using the regularized inverse metric wherever the ordinary inverse fails at the TZP.

\paragraph{Interpretation.}
$\Delta_T$ is the Laplacian adapted to TZP geometry. It measures second-order field variation using the Trawinistic connection.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors FISHER-RAO INFORMATION GEOMETRY by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Fisher--Rao Metric}\par
\[
g_{ij}(\theta)=\mathbb{E}_{\theta}\!\left[\partial_i\log p(X\mid\theta)\,\partial_j\log p(X\mid\theta)\right]
\]
\noindent This fixes the Fisher--Rao metric tensor on the statistical parameter manifold.\par
\noindent\textbf{2. Score Expectation}\par
\[
mathbb{E}_{\theta}\!\left[\partial_i\log p(X\mid\theta)\right]=0
\]
\noindent This identifies the vanishing expected score condition that centers the information geometry.\par
\noindent\textbf{3. Information Distance}\par
\[
ds^2=\sum_{i,j} g_{ij}(\theta)\,d\theta^i d\theta^j
\]
\noindent This closes the entry by expressing the induced information distance element.\par

\clearpage
\noindent\textbf{[ID 0518] FISHER-RAO INFORMATION GEOMETRY}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
FISHER-RAO INFORMATION GEOMETRY is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} -> Selection rule: DeltaH sub M = 0 or n*Phi sub 0. \textbf{Contextual meaning:} The entry reads FISHER-RAO INFORMATION GEOMETRY as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states Fisher--Rao information geometry through the metric tensor, the centered score condition, and the induced distance form instead of a broken selection-rule fragment. \textbf{Lemma support:} Fisher--Rao Metric; Score Expectation; Information Distance.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub T is the Laplacian adapted to TZP geometry. It measures second-order field variation using the Trawinistic connection.

\tzpsection{Equation Grounding}
Equation anchors: g sub ij (theta)=mathbb E sub theta [partial sub ilog p(Xmidtheta) partial sub jlog p(Xmidtheta)]; mathbb E sub theta [partial sub ilog p(Xmidtheta)]=0; and ds to the power 2=sum sub i,j g sub ij (theta) dtheta to the power i dtheta to the power j. Proof route: show that the stated Fisher--Rao metric is well-defined from the centered score field and induces the quoted information distance. Formalization route: prove that the expected score condition implies the Fisher information metric used in the distance element.

\tzpsection{Interpretive Role}
The entry now states Fisher--Rao information geometry through the metric tensor, the centered score condition, and the induced distance form instead of a broken selection-rule fragment.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Statistical Manifold Distances}: The geometric calculation of exactly how hard it is to tell two slightly different probability distributions apart based on limited data.
\item \textbf{Cramer-Rao Lower Bounding}: The absolute mathematical proof of the best possible accuracy you can ever hope to achieve when trying to measure a hidden, internal variable.
\item \textbf{Probability-Density Curvature}: The realization that the space of all possible answers isn't flat, but is warped and curved based on how much information you actually possess.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0518]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0518_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0518] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont FISHER-RAO INFORMATION GEOMETRY}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} -> Selection rule: DeltaH\textbackslash{}\_M = 0 or n*Phi\textbackslash{}\_0

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``FISHER-RAO INFORMATION GEOMETRY is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that -> Selection rule: DeltaH\textbackslash{}\_M = 0 or n*Phi\textbackslash{}\_0. \_T is
the Laplacian adapted to TZP geometry. It measures second-order field variation using
the Trawinistic connection.. The CHL validation treats the equation as the formal anchor
and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0518_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
