\section*{ID9449: Definition of Π̂TZP}
\paragraph{Metadata.}
PiID: 1231459357198 | RTEID: RTE:P36692.5654:T3.9094 | UUID: 089340c8-17c8-5854-a6f3-92131bb910da

\paragraph{Canonical Statement.}
e Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0490], [ID 0400] Node registry\_id\_0491 Support Titles Diagnostic Definition; Scaling Relation; Normalized Regime Test Handle If the scalar quantity cannot be normalized or compared across the stated regimes, the entry fails. Canonical Equation Links \$⟨𝑂1\$ (0)𝑂2 (𝑟 ) \$⟩∝𝑟−(𝑁−1)\$ 𝑆ent (𝐿)=𝑠1𝐿+𝑠2 log 𝐿+𝐶 \$Π̂TZP=·\$ · · [ID 0492] UNIFIED HAMILTONIAN SUM 𝐻𝑡𝑒𝑥𝑡𝑇𝑟𝑎𝑤𝑖𝑛 TZPID ID0492 UUID c15f1319-7ab9-517c-a81e-da7bba8892c7 Type Dynamical / Variational Statement Scale field-dynamical LOC Classification Working routing: QC20.7 field theory; QA321 variational structure arXiv Classification Primary: hep-th; Cross-list: math-ph, gr-qc Canonical Statement This entry develops unified hamiltonian sum h texttrawin inside

\paragraph{Canonical Equation.}
\[
Π̂TZP=·
\]

\paragraph{Dictionary.}
Definition of Π̂TZP — Π̂TZP=·

\paragraph{Encyclopedia.}
Definition of Π̂TZP is an algebraic definition, written Π̂TZP=·. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
