\section*{ID9338: Definition of ΞΦ ΞΦ}
\paragraph{Metadata.}
PiID: 8832151375560 | RTEID: RTE:P36261.5278:T3.1992 | UUID: f46bd0ee-a327-565d-b684-a00f14001cfe

\paragraph{Canonical Statement.}
tificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0138], [ID 0024] Node registry\_id\_0139 Support Titles Flux Cancellation Law; Cosmological-Density Scaling; Flux-Ratio Residual Test Handle If balanced total flux cannot coexist with a nontrivial residual ratio that feeds the radius law, the emergence statement fails. Canonical Equation Links \$Φ++Φ−=0 𝜌Λ∼\$ ℏ𝑐 𝑅4 \$ΞΦ ΞΦ= Φ+ Φ−\$ [ID 0140] Dipole Energy 1/d4 Scaling Law TZPID ID0140 UUID 962c75ec-f1b2-55d4-b8ba-6d03776ca28e Type Universal Energy Scaling Law Scale Planck-to-cosmic dipole coupling LOC Classification Working routing: QC174 interaction laws; QB981 cosmology arXiv Classification Primary: math-ph Cross-list: gr-qc, hep-th Canonical Statement The dipole energy law closes the cosmic subsection by asserting an inv

\paragraph{Canonical Equation.}
\[
ΞΦ ΞΦ= Φ+ Φ−
\]

\paragraph{Dictionary.}
Definition of ΞΦ ΞΦ — ΞΦ ΞΦ= Φ+ Φ−

\paragraph{Encyclopedia.}
Definition of ΞΦ ΞΦ is an algebraic definition, written ΞΦ ΞΦ= Φ+ Φ−. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
