\section*{ID8481: HELICITY QUANTIZATION LADDER Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 7583441375223 | RTEID: RTE:P32933.6064:T3.9990 | UUID: 3a762711-888f-50f3-8594-003396a8b306

\paragraph{Canonical Statement.}
[ID 1191] HELICITY QUANTIZATION LADDER Canonical Statutory Formula: \$\textbackslash{}mathcal\{H\} \{eject\} / \textbackslash{}mathcal\{H\} \{source\} \textbackslash{}in \{ 2\textasciicircum{}\{-n\}, ..., 1, ..., 2\textasciicircum{}n \}\$ Formal Technical Dissertation: The discrete exhaust protocol. The system sheds topological defects (entropy) not continuously, but in quantized packets of magnetic helicity. This confirms that the Trawin reactor operates as a topological quantum computer, ejecting "error" states in integer ratios of the fundamental winding number. Source: [13], [14]

\paragraph{Canonical Equation.}
\[
\mathcal{H} {eject} / \mathcal{H} {source} \in { 2^{-n}, ..., 1, ..., 2^n }
\]

\paragraph{Dictionary.}
HELICITY QUANTIZATION LADDER Canonical Statutory Formula: \$H eject / H source 2\textasciicircum{}-n, ..., 1, ..., 2\textasciicircum{}n \$ Formal Technical Dissertation: The discrete exhaust protocol.

\paragraph{Encyclopedia.}
HELICITY QUANTIZATION LADDER Canonical Statutory Formula is a symbolic expression, written H eject / H source in 2\textasciicircum{}-n, ..., 1, ..., 2\textasciicircum{}n. It introduces a symbol or relation used elsewhere in the framework. It is built from H, j, c, s, o, u. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
