\section*{ID8784: Relation: u\_T := oint\_Γ √(|g|) dℓ}
\paragraph{Metadata.}
PiID: 4079073860251 | RTEID: RTE:P34110.2227:T5.9377 | UUID: 7b16a4f9-4853-5a5c-94f3-8c3f584079b4

\paragraph{Canonical Statement.}
invariant units to ensure numerical stability across 47 orders of scale. \#\#\#\# 4. Fundamental Scaling and Numerical Constants High-resolution stability in the DAANSsphere model requires a shift from SI units to invariant Trawin base units ( \$u\_T\$ ), anchoring scaling consistency from laboratory to astrophysical magnitudes (ID 046). * **The Trawin Base Unit (** **\$u\_T**\$ **):** Formally defined as the integral of the metric density around a **single** lemniscatic loop encircling the TZP: \$u\_T := \textbackslash{}oint\_\{\textbackslash{}Gamma\} \textbackslash{}sqrt\{|g|\} \textbackslash{}, d\textbackslash{}ell\$ (ID 006). This invariant regulates the topological charge of the system. * **Temporal and Non-Linear Parameters:** | Parameter | Symbol | Functional Role | Source ID | | ------ | ------ | ------ | ------ | | **Temporal Displacement Factor** | \$\textbackslash{}alpha(t)\$ | Ratio of local time \$dt'\$ to global time \$dt\$ near \$p\$ . | ID 007 | | **Non-Linearity Constant** | \$K\_\{NL\}\$ | Scale for second-order v

\paragraph{Canonical Equation.}
\[
u_T := \oint_{\Gamma} \sqrt{|g|} \, d\ell
\]

\paragraph{Dictionary.}
Relation: u\_T := oint\_Γ √(|g|) dℓ — u\_T := oint\_Γ √(|g|) dℓ

\paragraph{Encyclopedia.}
Relation: u\_T := oint\_Γ √(|g|) dℓ is a contour integral, written u\_T := oint\_Γ √(|g|) dℓ. It is evaluated by integrating along a closed contour, capturing global or topological properties of the field. It is built from Γ, ℓ, u\_T, g. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
