\tzpanchor{0118}
\tzpentryheader{0118}{Dominant Planetary Coupling Pairs}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{d57fb070-3dc8-586d-a34f-5d7ae1c4215e}}\\
\textbf{PiID} & \tzpcode{4709384460955} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{125}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{458.2202 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.7550 rad}\\
\textbf{TZPID} & \tzpcode{ID0118} & \textbf{Node Dependencies}\quad \tzpidref{0117}\\
\textbf{Registry} & \tzpcode{registry\_id\_0118} & \textbf{Scale}\quad pairwise planetary interaction strengths\\
\textbf{LOC Classification} & QA276 rank statistics & QB503 planetary rotation\\
\textbf{arXiv Classification} & Primary: astro-ph.EP \quad Cross-list: nlin.AO, physics.data-an & \\
\textbf{Primary Support} & Normalized Coupling Matrix & Dominant Giant-Planet Pair\\
\textbf{Closure Support} & Leading Terrestrial Pair & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The normalized coupling matrix exhibits strongest pairs as follows: Jupiter--Saturn (1.00), Venus--Earth (0.103), Earth--Jupiter (0.0115), Venus--Jupiter (0.0078), Jupiter--Uranus (0.0045), Saturn--Uranus (0.0041), Mercury--Venus (0.0032), Earth--Mars (0.0020), Mars--Jupiter (0.00185), and Jupiter--Neptune (0.00095).

\tzpsection{Canonical Equation}
\[
\widehat{A}_{ij}=\frac{A_{ij}}{\max_{p,q}A_{pq}}
\]
\[
\widehat{A}_{\mathrm{Jupiter,Saturn}} = 1
\]
\[
\widehat{A}_{\mathrm{Venus,Earth}} \approx 0.103
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $A$: source equation symbol.
    \item $A_{ij}$: source equation symbol.
    \item $A_{pq}$: source equation symbol.
    \item $\mathcal{K}_{0118}$: canonical registry object for entry ID 0118.
    \item $\max_{p,q}$: source equation symbol.
    \item $J$: source equation symbol.
    \item $S$: source equation symbol.
    \item $V$: auxiliary target state or comparison variable.
    \item $E$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0118 generated source Wolfram model *)
ClearAll[K0118, Cr0118, T, R, A, W, I, N];
eq0118$1 = HoldForm[widehat[A]*_*ij == AIj/maxPqAPq];
eq0118$2 = HoldForm[widehat[A]*_Pair[Jupiter, Saturn] == 1];
eq0118$3 = HoldForm[widehat[A]*_Pair[Venus, Earth] == 0.103];

K0118 = HoldForm[{eq0118$1, eq0118$2, eq0118$3}];

N = "normalized TRAWIN closure object for Dominant Planetary Coupling Pairs";
I = "Leading Terrestrial Pair integration/comparison layer";
W = "Dominant Giant-Planet Pair wave or operator carrier";
A = "Normalized Coupling Matrix admissible action/amplitude condition";
R = "Dominant Giant-Planet Pair rotation/curl preservation layer";
T = "Normalized Coupling Matrix local source condition";

Cr0118[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0118 = Cr0118[K0118];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Normalized Coupling Matrix local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Dominant Giant-Planet Pair rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Normalized Coupling Matrix admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Dominant Giant-Planet Pair wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Leading Terrestrial Pair integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Dominant Planetary Coupling Pairs.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0118] Dominant Planetary Coupling Pairs}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\widehat{A}_{ij}=\frac{A_{ij}}{\max_{p,q}A_{pq}}
\]
\[
\widehat{A}_{\mathrm{Jupiter,Saturn}} = 1
\]
\[
\widehat{A}_{\mathrm{Venus,Earth}} \approx 0.103
\]

\paragraph{Primary Derivation.}
This argument establishes the identity by employing standard algebraic manipulations. leading to the displayed result.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. Interpreted through TRAWIN, the equation functions as the generalized carrier for the entry’s information content. Under CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Dominant Planetary Coupling Pairs by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Normalized Coupling Matrix}\par
\[
\widehat{A}_{ij}=\frac{A_{ij}}{\max_{p,q}A_{pq}}
\]
\noindent This converts raw interaction weights into a common comparative scale.\par
\noindent\textbf{2. Dominant Giant-Planet Pair}\par
\[
\widehat{A}_{\mathrm{Jupiter,Saturn}} = 1
\]
\noindent This identifies the reference pair against which the rest of the network is judged.\par
\noindent\textbf{3. Leading Terrestrial Pair}\par
\[
\widehat{A}_{\mathrm{Venus,Earth}} \approx 0.103
\]
\noindent This closes the progression by showing that the strongest non-giant interaction is much weaker but still measurable.\par

\clearpage
\noindent\textbf{[ID 0118] Dominant Planetary Coupling Pairs}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Dominant Planetary Coupling Pairs is a Structural Constraint. The normalized coupling matrix exhibits strongest pairs as follows: Jupiter--Saturn (1.00), Venus--Earth (approximately 0.103), Earth--Jupiter (approximately 0.0115), Venus--Jupiter (approximately 0.0078), Jupiter--Uranus (approximately 0.0045), Saturn--Uranus (approximately 0.0041), Mercury--Venus (approximately 0.0032), Earth--Mars (approximately 0.0020), Mars--Jupiter (approximately 0.00185), Jupiter--Neptune (approximately 0.00095).

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The normalized coupling matrix exhibits strongest pairs as follows: Jupiter--Saturn (1.00), Venus--Earth (approximately 0.103), Earth--Jupiter (approximately 0.0115), Venus--Jupiter (approximately 0.0078), Jupiter--Uranus (approximately 0.0045), Saturn--Uranus (approximately 0.0041), Mercury--Venus (approximately 0.0032), Earth--Mars (approximately 0.0020), Mars--Jupiter (approximately 0.00185), Jupiter--Neptune (approximately 0.00095).
\textbf{Contextual meaning:} The massive gas giants dominate the coupling matrix, while terrestrial planet pairs contribute smaller couplings. This heterogeneity strongly influences cluster formation in the Kuramoto model.
\textbf{Derivable consequences:} Identification of partial clusters; parameter regimes for clustering; impetus to explore heterogeneity effects.
\textbf{Lemma support:} The normalized coupling matrix exhibits strongest pairs as follows: Jupiter--Saturn (1.00), Venus--Earth (approximately 0.103), Earth--Jupiter (approximately 0.0115), Venus--Jupiter (approximately 0.0078), Jupiter--Uranus (approximately 0.0045), Saturn--Uranus (approximately 0.0041), Mercury--Venus (approximately 0.0032), Earth--Mars (approximately 0.0020), Mars--Jupiter (approximately 0.00185), Jupiter--Neptune (approximately 0.00095).\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Simulate the Kuramoto model and compute the order parameter; compare with the cited range. ID 118: Dominant Planetary Coupling Pairs

\tzpsection{Equation Grounding}
The normalized coupling matrix exhibits strongest pairs as follows: Jupiter--Saturn (1.00), Venus--Earth (approximately 0.103), Earth--Jupiter (approximately 0.0115), Venus--Jupiter (approximately 0.0078), Jupiter--Uranus (approximately 0.0045), Saturn--Uranus (approximately 0.0041), Mercury--Venus (approximately 0.0032), Earth--Mars (approximately 0.0020), Mars--Jupiter (approximately 0.00185), Jupiter--Neptune (approximately 0.00095).

\tzpsection{Interpretive Role}
The massive gas giants dominate the coupling matrix, while terrestrial planet pairs contribute smaller couplings. This heterogeneity strongly influences cluster formation in the Kuramoto model.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Normalized Coupling Matrix}: The conversion of raw interaction weights into a common comparative scale.
\item \textbf{Dominant Giant-Planet Pair}: The identification of the reference pair against which the rest of the network is judged.
\item \textbf{Leading Terrestrial Pair}: The demonstration that the strongest non-giant interaction is much weaker but still measurable.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0118]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0118_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0118] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Dominant Planetary Coupling Pairs}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the normalized coupling matrix ranks Jupiter--Saturn as the reference pair
\((1.00)\), with Venus--Earth as the leading terrestrial pair \((0.103)\) and the remaining listed pairs below that scale.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Dominant Planetary Coupling Pairs is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0118_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
