\tzpanchor{0013}
\tzpentryheader{0013}{Null Space Projection}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{93d3669d-bb50-5ecc-af2c-93398438d3b4}}\\
\textbf{PiID} & \tzpcode{9323846264338} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{20}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{50.4819 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.0832 rad}\\
\textbf{TZPID} & \tzpcode{ID0013} & \textbf{Node Dependencies}\quad \tzpidref{0004}\\
\textbf{Registry} & \tzpcode{registry\_id\_0013} & \textbf{Scale}\quad null-geometry\\
\textbf{LOC Classification} & QA329 projection operators & QA641 degenerate geometry\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: math.DG, gr-qc & \\
\textbf{Primary Support} & Null Pairing Test & Identity Action on Null Directions\\
\textbf{Closure Support} & Zero Action on Regular Directions & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The null space projection operator $P_{\text{null}}:T_pM\to T_pM$ is defined by $P_{\text{null}}(v)=v$ if $g(v,w)=0$ for all $w\in T_pM$, and $P_{\text{null}}(v)=0$ otherwise.

\tzpsection{Canonical Equation}
\[
P_{\mathrm{null}} : T_{p}M \to T_{p}M
\]
\[
P_{\mathrm{null}}(v)
=
\begin{cases}
v, & g(v,w)=0 \text{ for all } w \in T_{p}M,\\
0, & \text{otherwise.}
\end{cases}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $P_{\mathrm{null}}$: source equation symbol.
    \item $T_{p}$: source equation symbol.
    \item $M$: source equation symbol.
    \item $v$: velocity, flow speed, or auxiliary comparison variable.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0013 generated source Wolfram model *)
ClearAll[K0013, Cr0013, T, R, A, W, I, N];
eq0013$1 = HoldForm[Pnull[TpM] -> TpM];
eq0013$2 = HoldForm[Element[TZPSequence[PNull[v] == v, g[v, w] == 0*w], TZPSequence[TPM, 0]]];
eq0013$3 = HoldForm[Element[g[v, w] == 0*w, TPM]];
eq0013$4 = HoldForm[PNull[v] == v];
eq0013$5 = HoldForm[PNull[v] == 0];

K0013 = HoldForm[{eq0013$1, eq0013$2, eq0013$3, eq0013$4, eq0013$5}];

N = "normalized TRAWIN closure object for Null Space Projection";
I = "Zero Action on Regular Directions integration/comparison layer";
W = "Identity Action on Null Directions wave or operator carrier";
A = "Null Pairing Test admissible action/amplitude condition";
R = "Identity Action on Null Directions rotation/curl preservation layer";
T = "Null Pairing Test local source condition";

Cr0013[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0013 = Cr0013[K0013];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Null Pairing Test local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Identity Action on Null Directions rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Null Pairing Test admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Identity Action on Null Directions wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Zero Action on Regular Directions integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Null Space Projection.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0013] Null Space Projection}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
P_{\mathrm{null}}(v)
=
\begin{cases}
v, & g(v,w)=0\ \text{for all}\ w\in T_pM,\\
0, & \text{otherwise}.
\end{cases}
\end{equation}

\paragraph{Primary Derivation.}
At the TZP, the degenerate metric admits null directions.  
A vector $v\in T_pM$ belongs to the null space if it pairs to zero with every tangent vector $w$:

\begin{equation}
g(v,w)=0
\qquad
\forall w\in T_pM .
\end{equation}

The null projection operator preserves vectors satisfying this condition:

\begin{equation}
P_{\mathrm{null}}(v)=v .
\end{equation}

Vectors not satisfying the null condition are removed by the projection:

\begin{equation}
P_{\mathrm{null}}(v)=0 .
\end{equation}

Thus,

\begin{equation}
\boxed{
P_{\mathrm{null}}(v)
=
\begin{cases}
v, & g(v,w)=0\ \text{for all}\ w\in T_pM,\\
0, & \text{otherwise}.
\end{cases}
}
\end{equation}

\paragraph{Interpretation.}
$P_{\mathrm{null}}$ extracts only those tangent directions annihilated by the degenerate TZP metric.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Null Space Projection by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Null Pairing Test}\par
\[
g(v,w)=0 \qquad \text{for all } w \in T_{p}M
\]
\noindent This identifies the vectors the degenerate metric cannot resolve against any tangent direction at the zero point.\par
\noindent\textbf{2. Identity Action on Null Directions}\par
\[
P_{\mathrm{null}}(v)=v
\]
\noindent This preserves the singular directions rather than suppressing them, making them explicitly available for later operators.\par
\noindent\textbf{3. Zero Action on Regular Directions}\par
\[
P_{\mathrm{null}}(v)=0 \qquad \text{otherwise}
\]
\noindent This closes the progression by cleanly separating null and non-null tangent components into two disjoint operator outputs.\par

\clearpage
\noindent\textbf{[ID 0013] Null Space Projection}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Null Space Projection is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The null space projection operator P sub null :T sub pMto T sub pM is defined by P sub null (v)=v if g(v,w)=0 for all win T sub pM, and P sub null (v)=0 otherwise. \textbf{Contextual meaning:} The entry reads Null Space Projection as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Null Pairing Test; Identity Action on Null Directions; Zero Action on Regular Directions.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
P sub null extracts only those tangent directions annihilated by the degenerate TZP metric.

\tzpsection{Equation Grounding}
Equation anchors: The null space projection operator P null:T pMrightarrowT pMPtextbackslash null :Ttextbackslash p Mto Ttextbackslash p MP null:T pMrightarrowT pM is defined by P null(v)=vPtextbackslash null (v)=vP null(v)=v if g(v,w)=0g(v,w)=0g(v,w)=0 for all winT pMwin Ttextbackslash p MwinT pM, and P null(v)=0Ptextbackslash null (v)=0P null(v)=0 otherwise. The null space projection operator P null:T pMrightarrowT pMPtextbackslash null :Ttextbackslash p Mto Ttextbackslash p MP null:T pMrightarrowT pM is defined by P null(v)=vPtextbackslash null (v)=vP null(v)=v if g(v,w)=0g(v,w)=0g(v,w)=0 for all winT pMwin Ttextbackslash p MwinT pM, and P null(v)=0Ptextbackslash null (v)=0P null(v)=0 otherwise.

\tzpsection{Interpretive Role}
This operator is the registry s first clean selector for singular tangent directions. It supports later construction of the Trawinistic connection, Laplacian, and any decomposition that must distinguish null directions from regular ones.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Null Space Projection}: normalization vocabulary for fixed form, invariant comparison, or TRAWIN admissibility.
\item \textbf{Null Space Projection Formal Analogue}: normalization vocabulary for fixed form, invariant comparison, or TRAWIN admissibility.
\item \textbf{Projection Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0013]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0013_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0013] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Null Space Projection}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the null space projection operator P\_null:T\_pM T\_pM is defined by P\_null(v)=v if
g(v,w)=0 for all w T\_pM, and P\_null(v)=0 otherwise

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Null Space Projection is valid as a tensorial/geometric statement when the stated tensor
fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0013_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
