\section*{ID7012: Concrete Recipes / Parts \& Architecture Suggestions: 10\textasciicircum{}7-10\textasciicircum{}8}
\paragraph{Metadata.}
PiID: 5995054973742 | RTEID: RTE:P27229.1532:T0.8830 | UUID: 9935e891-cce6-50fb-a6fb-5c32d1c3c679

\paragraph{Canonical Statement.}
\# Concrete recipes / parts \& architecture suggestions 1. **Containment:** photonic crystal torus or dielectric metasurface ring (SiN/TiO₂). Aim for Q↑ (target \textbackslash{}(10\textasciicircum{}7-10\textasciicircum{}8\textbackslash{}) if feasible). 2. **Pump / emitter choices:** - For proof-of-concept: **micro-LED array** (visible) fiber- or near-field coupled to the torus gap. Good for room-temp, simpler fabrication. - For lower threshold: **electrically pumped polariton microcavity** (quantum wells + DBRs) if you have epitaxial fab access. 3. **Thermalizer / interaction:** dye layer (simple) or integrate quantum wells for polaritons (faster). Dye is easier but photobleaches; quantum wells need more fab but are robust. 4. **Heat handling:** diamond or copper heat-spreader, flip-chip mount, thermal vias to the substrate, and pulsed pump if average heating is critical. 5. **Measurement:** spectral narrowing, increased coherence length, and ground-mode occupation vs pump power are your signatures for condensation. Use time-resolved PL and heterodyne coherence measurements.

\paragraph{Canonical Equation.}
\[
10^7-10^8
\]

\paragraph{Dictionary.}
Concrete Recipes / Parts \& Architecture Suggestions: 10\textasciicircum{}7-10\textasciicircum{}8 — 10\textasciicircum{}7-10\textasciicircum{}8

\paragraph{Encyclopedia.}
Concrete Recipes / Parts \& Architecture Suggestions: 10\textasciicircum{}7-10\textasciicircum{}8 is a symbolic expression, written 10\textasciicircum{}7-10\textasciicircum{}8. It introduces a symbol or relation used elsewhere in the framework. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
