\tzpanchor{0736}
\tzpentryheader{0736}{UNIFIED FIELD IDENTITY (TuT)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7acabe85-a04f-564c-b20c-83bc59a13238}}\\
\textbf{PiID} & \tzpcode{2977477130996} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{743}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2823.1025 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.6516 rad}\\
\textbf{TZPID} & \tzpcode{ID0736} & \textbf{Node Dependencies}\quad \tzpidref{0735}\\
\textbf{Registry} & \tzpcode{registry\_id\_0736} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Frequency Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records unified field identity (tut) through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0736}}:\mathcal{X}_{\mathrm{id0736}}\longrightarrow\mathcal{Y}_{\mathrm{id0736}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0736}})=\mathcal{O}_{\mathrm{id0736}}
\]
\[
\mathcal{O}_{\mathrm{id0736}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0736}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0736}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0736}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0736 generated source Wolfram model *)
ClearAll[K0736, Cr0736, T, R, A, W, I, N];
eq0736$1 = HoldForm[Oid0736[Xid0736] -> Yid0736];
eq0736$2 = HoldForm[NTRAWIN[OId0736] == OId0736];
eq0736$3 = HoldForm[Element[OId0736[x], YAdm]];

K0736 = HoldForm[{eq0736$1, eq0736$2, eq0736$3}];

N = "normalized TRAWIN closure object for UNIFIED FIELD IDENTITY (TuT)";
I = "UNIFIED FIELD IDENTITY (TuT) integration/comparison layer";
W = "UNIFIED FIELD IDENTITY (TuT) wave or operator carrier";
A = "UNIFIED FIELD IDENTITY (TuT) admissible action/amplitude condition";
R = "UNIFIED FIELD IDENTITY (TuT) rotation/curl preservation layer";
T = "UNIFIED FIELD IDENTITY (TuT) local source condition";

Cr0736[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0736 = Cr0736[K0736];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ UNIFIED FIELD IDENTITY (TuT) local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ UNIFIED FIELD IDENTITY (TuT) rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ UNIFIED FIELD IDENTITY (TuT) admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ UNIFIED FIELD IDENTITY (TuT) wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ UNIFIED FIELD IDENTITY (TuT) integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for UNIFIED FIELD IDENTITY (TuT).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0736] UNIFIED FIELD IDENTITY (TuT)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0736}}:\mathcal{X}_{\mathrm{id0736}}\longrightarrow\mathcal{Y}_{\mathrm{id0736}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0736}})=\mathcal{O}_{\mathrm{id0736}}
\]
\[
\mathcal{O}_{\mathrm{id0736}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0736}})=\mathcal{O}_{\mathrm{id0736}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. From the TRAWIN perspective, the equation functions as the mapping carrier for the entry’s information content. Within the CHL view, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors UNIFIED FIELD IDENTITY (TuT) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0736}}:\mathcal{X}_{\mathrm{id0736}}\longrightarrow\mathcal{Y}_{\mathrm{id0736}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0736}})=\mathcal{O}_{\mathrm{id0736}}
\]
\[
\mathcal{O}_{\mathrm{id0736}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0736] UNIFIED FIELD IDENTITY (TuT)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
UNIFIED FIELD IDENTITY (TuT) is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} T sub uT := Omega sub downarrow otimes A sub uparrow. \textbf{Contextual meaning:} The entry reads UNIFIED FIELD IDENTITY (TuT) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Frequency Relation; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, UNIFIED FIELD IDENTITY (TuT) is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: T sub uT := Omega sub downarrow otimes A sub uparrow; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Electro-Gravitational Blending Operator}: The single, staggering line of math that finally, flawlessly proves that the pull of a magnet and the pull of a planet are exactly the same fundamental force just looked at from different angles.
\item \textbf{Strong-Weak Force Merger Metric}: The extreme, high-energy condition where the radiation tearing an atom apart and the glue holding it together become completely mathematically indistinguishable.
\item \textbf{Total Symmetrical State Return}: The theoretical endpoint of the universe where every single law, force, and particle melts back down into the one, single, perfectly smooth, featureless equation that started it all.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0736]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0736].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0736] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont UNIFIED FIELD IDENTITY (TuT)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} UNIFIED FIELD IDENTITY (TuT) is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``UNIFIED FIELD IDENTITY (TuT) is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0736].
\par\endgroup
\vfill
\endgroup
\endgroup
