\section*{ID8827: TOPOLOGICAL QUANTIZATION AXIOM (AXIOM 4) Canonical Statutory Formula: H / (M…}
\paragraph{Metadata.}
PiID: 3331239480494 | RTEID: RTE:P34277.2013:T6.2128 | UUID: 0cb46a7f-c681-5ff0-9dea-f9da9b01db77

\paragraph{Canonical Statement.}
[ID 1158] TOPOLOGICAL QUANTIZATION AXIOM (AXIOM 4) Canonical Statutory Formula: \$\textbackslash{}mathcal\{H\} / (M R\textasciicircum{}2 \textbackslash{}omega) \textbackslash{}in \{n \textbackslash{}in \textbackslash{}mathbb\{Z\}\}\$ Formal Technical Dissertation: States that macroscopic helicity is approximately quantized in units of effective action \$\textbackslash{}hbar\_\{eff\} = M R\textasciicircum{}2 \textbackslash{}omega\$. This connects macroscopic fluid dynamics to quantum topological invariants. Source: [26]

\paragraph{Canonical Equation.}
\[
\mathcal{H} / (M R^2 \omega) \in {n \in \mathbb{Z}}
\]

\paragraph{Dictionary.}
TOPOLOGICAL QUANTIZATION AXIOM (AXIOM 4) Canonical Statutory Formula: H / (M R\textasciicircum{}2 ω) in n in Z Formal Technical Dissertation: States that macroscopic helicity is approximately quantized in units of effective action ħ\_eff = M R\textasciicircum{}2 ω.

\paragraph{Encyclopedia.}
TOPOLOGICAL QUANTIZATION AXIOM (AXIOM 4) Canonical Statutory Formula: H / (M… is a quantization / integer condition, written H / (M R\textasciicircum{}2 ω) in n in Z. It imposes a quantization condition, restricting the allowed values to a discrete set. It is built from ω, H, M, R, n. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
