\section*{ID9081: Relation: Λ\_crit≈1Λ\_crit≈1Λ\_crit≈1}
\paragraph{Metadata.}
PiID: 8443965825337 | RTEID: RTE:P35263.5397:T1.5548 | UUID: 127a6664-d194-5965-8296-13a362df04a6

\paragraph{Canonical Statement.}
field and rotation rate; informs universal scaling laws; influences stability criteria; ties into helicity quantisation. Falsifiability / Test Handle: Measurements showing strong imbalance between magnetic and rotational energies in a supposed Elsasser state would disprove this law. 0.0.42 ID 040: Universality of Elsasser Criticality Type: Structural Constraint Formal Statement: Across laboratory and astrophysical systems, the Elsasser critical parameter \$Λ\textbackslash{}LambdaΛ\$ reaches a universal value \$Λ\_crit≈1\textbackslash{}Lambda\_\{\textbackslash{}text\{crit\}\}\textbackslash{}approx1Λ\_crit≈1\$ regardless of scale. Deviations scale as a power of the Reynolds number or magnetic Prandtl number but remain bounded by an O(1)\textbackslash{}mathcal\{O\}(1)O(1) factor. Interpretive Meaning: The same critical behaviour emerges in small experiments and large astrophysical objects, reflecting a scaling functor that maps between these systems. Dependencies: ID 038, ID 037 Derivable Consequences: Justifies using l

\paragraph{Canonical Equation.}
\[
Λ_crit≈1\Lambda_{\text{crit}}\approx1Λ_crit≈1
\]

\paragraph{Dictionary.}
Relation: Λ\_crit≈1Λ\_crit≈1Λ\_crit≈1 — Λ\_crit≈1Λ\_crit≈1Λ\_crit≈1

\paragraph{Encyclopedia.}
Relation: Λ\_crit≈1Λ\_crit≈1Λ\_crit≈1 is a scaling / order-of-magnitude relation, written Λ\_crit≈1Λ\_crit≈1Λ\_crit≈1. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from c, r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
