\section*{ID9353: Definition of SD}
\paragraph{Metadata.}
PiID: 7279839400415 | RTEID: RTE:P36319.7761:T3.2952 | UUID: 0197dfaf-99ff-5412-a7d3-4d4c2bd87d5a

\paragraph{Canonical Statement.}
in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0004], [ID 0006], [ID 0007] Node registry\_id\_0010 Support Titles Displacement Variance; Infinitesimal-Time Drift Rate; Normalized Stochastic Response Test Handle Observation of purely deterministic motion with vanishing short-time variance near the claimed zero-point regime would undermine the definition. Canonical Equation Links \$⟨(Δ𝑥 )2⟩\$ 𝜎2 \$SD=limΔ𝑡→0\$ 1 \$Δ𝑡 ⟨(Δ𝑥 )2⟩\$ 𝜎 2,norm SD =NormalizeTRAWIN ( \$limΔ𝑡→0\$ \$⟨(Δ𝑥)2⟩ Δ𝑡\$ , \$⟨·⟩,\$ 𝑢𝑇 ) [ID 0011] Causal Loop Invariant TZPID ID0011 UUID b63b387a-822c-58b3-9bf9-73350cb197fa Type Definition Scale causal-topological LOC Classification Working routing: QA612 loop topology; QC174.52 causal structure arXiv Classification Primary: gr-qc Cross-list: math-ph, hep-th Canonical Statement The causal loop i

\paragraph{Canonical Equation.}
\[
SD=limΔ𝑡→0
\]

\paragraph{Dictionary.}
Definition of SD — SD=limΔ𝑡→0

\paragraph{Encyclopedia.}
Definition of SD is an algebraic definition, written SD=limΔ𝑡→0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from l, m, defining SD. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
