\section*{ID9129: Definition of (R,eiα)(R,eiβ)}
\paragraph{Metadata.}
PiID: 1207665147939 | RTEID: RTE:P35449.9343:T1.8619 | UUID: 174f48da-3059-5dc3-8477-976c88c48318

\paragraph{Canonical Statement.}
representations. Falsifiability / Test Handle: Observation of rotational or gauge transformations that cannot be described by SO(3)× U(1)SO(3)\textbackslash{}times U(1)SO(3)× U(1) would refute this definition. 0.0.94 ID 092: SemiDirect Product of Rotation and Gauge Symmetry Type: Structural Constraint Formal Statement: The full symmetry group of gyromagnetic systems is the semidirect product SO(3)U(1)SO(3)\textbackslash{}ltimes U(1)SO(3)U(1), reflecting the fact that gauge phases transform under rotations; mathematically, \$(R,eiα)(R,eiβ)=(RR,ei(α+β))(R,\$ e\{i\textbackslash{}alpha\})\textbackslash{}cdot(R’,e\{i\textbackslash{}beta\}) = (RR’, \$eˆ\{i(\textbackslash{}alpha+\textbackslash{}beta)\})(R,eiα)(R,eiβ)=(RR,ei(α+β))\$ up to an automorphism. Interpretive Meaning: Rotations and gauge phases are intertwined; this structure yields unique conserved quantities and constraints. Dependencies: ID 091 Derivable Consequences: Existence of combined gauge–rotation charges; modifications to conservation laws; topological defects carryi

\paragraph{Canonical Equation.}
\[
(R,eiα)(R,eiβ)=(RR,ei(α+β))(R,
\]

\paragraph{Dictionary.}
Definition of (R,eiα)(R,eiβ) — (R,eiα)(R,eiβ)=(RR,ei(α+β))(R

\paragraph{Encyclopedia.}
Definition of (R,eiα)(R,eiβ) is an algebraic definition, written (R,eiα)(R,eiβ)=(RR,ei(α+β))(R. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R, defining (R,eiα)(R,eiβ). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
