\tzpanchor{0438}
\tzpentryheader{0438}{Weak Measurement Feedback Loop}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{b4eebe8a-bf86-56da-bdd7-1be836cdac8a}}\\
\textbf{PiID} & \tzpcode{7931051185480} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{445}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1700.8513 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.8025 rad}\\
\textbf{TZPID} & \tzpcode{ID0438} & \textbf{Node Dependencies}\quad \tzpidref{0437}\\
\textbf{Registry} & \tzpcode{registry\_id\_0438} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Variation Law\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 438 defines the continuous monitoring strategy for the TZP singularity. By employing "weak measurements," the system extracts a record r(t) without causing a total collapse of the quantum state. This enables a real time feedback control loop where parameters ui (t) are adjusted to maximize efficiency while respecting the Heisenberg energy time uncertainty limit. Backaction Minimization: Keeping small preserves the coherence necessary for the extraction cycle. Stochastic Control: The Wiener increment dW accounts for measurement noise in the system state estimate.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
A_{\mathrm w}=\frac{\langle\psi_{f}|\hat A|\psi_{i}\rangle}{\langle\psi_{f}|\psi_{i}\rangle}
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $A_{\mathrm{w}}$: source equation symbol.
    \item $A$: source equation symbol.
    \item $\Lambda$: lemniscatic representative or canonical branch object.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $\psi_{f}$: source equation symbol.
    \item $\psi_{i}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0438 generated source Wolfram model *)
ClearAll[K0438, Cr0438, T, R, A, W, I, N];
eq0438$1 = HoldForm[$AMathrmw == (Inner[psiFAbs[hat*A]*psiI]/Inner[psiF | psiI])*$];

K0438 = HoldForm[{eq0438$1}];

N = "normalized TRAWIN closure object for Weak Measurement Feedback Loop";
I = "Weak Measurement Feedback Loop integration/comparison layer";
W = "Weak Measurement Feedback Loop wave or operator carrier";
A = "Weak Measurement Feedback Loop admissible action/amplitude condition";
R = "Weak Measurement Feedback Loop rotation/curl preservation layer";
T = "Weak Measurement Feedback Loop local source condition";

Cr0438[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0438 = Cr0438[K0438];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Weak Measurement Feedback Loop local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Weak Measurement Feedback Loop rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Weak Measurement Feedback Loop admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Weak Measurement Feedback Loop wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Weak Measurement Feedback Loop integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Weak Measurement Feedback Loop.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0438] Weak Measurement Feedback Loop}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Lambda
=
\frac{\mathbf{B}^2}
{\rho\,\mu\,\Omega^2}.
\end{equation}

\paragraph{Primary Derivation.}
Let $\mathbf{B}$ be magnetic field strength, $\rho$ mass density, $\mu$ magnetic permeability, and $\Omega$ angular rotation rate.

The magnetic contribution is represented by field magnitude squared:

\begin{equation}
\mathbf{B}^2 .
\end{equation}

The inertial-rotational scale is represented by:

\begin{equation}
\rho\,\mu\,\Omega^2 .
\end{equation}

The dimensionless comparison between these two effects defines the Elsasser-type parameter:

\begin{equation}
\boxed{
\Lambda
=
\frac{\mathbf{B}^2}
{\rho\,\mu\,\Omega^2}.
}
\end{equation}

The attractor condition is:

\begin{equation}
\Lambda \approx 1 .
\end{equation}

\paragraph{Interpretation.}
The Elsasser attractor occurs when magnetic and rotational scales enter near-balance, producing a self-organizing critical manifold.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Weak Measurement Feedback Loop by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
A_{\mathrm w}=\frac{\langle\psi_{f}|\hat A|\psi_{i}\rangle}{\langle\psi_{f}|\psi_{i}\rangle}
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0438] Weak Measurement Feedback Loop}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Weak Measurement Feedback Loop is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 438 defines the continuous monitoring strategy for the TZP singularity. By employing "weak measurements," the system extracts a record r(t) without causing a total collapse of the quantum state. This enables a real time feedback control loop where parameters ui (t) are adjusted to maximize efficiency while respecting the Heisenberg energy time uncertainty limit. Backaction Minimization: Keeping small preserves the coherence necessary for the extraction cycle. Stochastic Control: The Wiener increment dW accounts for measurement noise in the system state estimate.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
A_{\mathrm w}=\frac{\langle\psi_{f}|\hat A|\psi_{i}\rangle}{\langle\psi_{f}|\psi_{i}\rangle}
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 438 defines the continuous monitoring strategy for the TZP singularity. By employing "weak measurements," the system extracts a record r(t) without causing a total collapse of the quantum state. This enables a real time feedback control loop where parameters ui (t) are adjusted to maximize efficiency while respecting the Heisenberg energy time uncertainty limit. Backaction Minimization: Keeping small preserves the coherence necessary for the extraction cycle. Stochastic Control: The Wiener increment dW accounts for measurement noise in the system state estimate.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Weak Measurement Feedback Loop by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Weak Measurement Feedback Loop; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0438]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0438].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0438] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Weak Measurement Feedback Loop}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} hat\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} = hat\textbackslash{} + sqrt\textbackslash{} epsilon hat\textbackslash{} implies dr = sqrt\textbackslash{} langle hat\textbackslash{} rangle dt + frac\textbackslash{}\textbackslash{}\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``WEAK MEASUREMENT FEEDBACK LOOP is valid when the stated geometric or topological
relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0438].
\par\endgroup
\vfill
\endgroup
\endgroup
