\section*{ID9202: Definition of ρ∇2Φ}
\paragraph{Metadata.}
PiID: 2221032748892 | RTEID: RTE:P35733.4096:T2.3290 | UUID: a6eebbf4-e063-5cd6-907d-5a5d82c19852

\paragraph{Canonical Statement.}
ux quantization. Falsifiability / Test Handle: Detection of noninteger charges or spin values not explained by composite structures would falsify this entry. 2.0.34 ID 183: Emergent Gravity from Coherence Restoration Type: Structural Constraint Formal Statement: Gravity arises as a collective tendency of topological defects to restore coherence; summing over a mass distribution \$ρ(r)\textbackslash{}rho(\textbackslash{}mathbf\{r\})ρ(r)\$ yields a potential \$Φ\textbackslash{}PhiΦ\$ satisfying \$∇2Φ=4πGeffρ\textbackslash{}nablaˆ2\$ \textbackslash{}Phi = 4\textbackslash{}pi G\_\{\textbackslash{}text\{eff\}\} \$\textbackslash{}rho∇2Φ=4πGeffρ,\$ where GeffG\_\{\textbackslash{}text\{eff\}\}Geff is derived from the vacuum’s restoring tendency. Interpretive Meaning: Particles, as defects, create gradients in the coherence field; these gradients produce an attractive potential that can be formalized by Poisson’s equation; gravity is an emergent entropic force rather than a fundamental interaction. Dependencies: ID 177, ID 179 Derivable Consequences: Explains we

\paragraph{Canonical Equation.}
\[
\rho∇2Φ=4πGeffρ,
\]

\paragraph{Dictionary.}
Definition of ρ∇2Φ — ρ∇2Φ=4πGeffρ

\paragraph{Encyclopedia.}
Definition of ρ∇2Φ is an algebraic definition, written ρ∇2Φ=4πGeffρ. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from G, f, defining ρ∇2Φ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
