\section*{ID9444: Definition of 𝑠1−𝜏}
\paragraph{Metadata.}
PiID: 4445812314593 | RTEID: RTE:P36673.1493:T3.8774 | UUID: 2e9277d6-cd84-5acc-b782-7241af6c3bb2

\paragraph{Canonical Statement.}
e carrier that can be rendered, normalized, and linked forward into the surrounding registry pages. 𝐼 (𝑠) \$∝\$ 𝑠1−𝜏 = 𝑠−1/2 𝑃(𝑠) \$∝\$ 𝑠−𝜏 Wolfram Form 𝔚TZP (K0470) \$↦−→ 〈 ΩT, ΨT,\$ 𝜌vac \$〉\$ K0470 := HoldForm(T0470) AdmissibleTZP (K0470) \$⇐⇒\$ 𝔚TZP (K0470) . \$∅\$ Wolfram register: canonical symbol lift Title lift: SYNAPTIC AVALANCHE EXPONENT Symbol key: \$ΩT:\$ Trawinistic boundary curvature \$ΨT:\$ Trawinistic wavefunction 𝜌vac: vacuum energy density TRAWIN Normalization NormalizeTRAWIN( 𝐼 (𝑠) \$∝\$ 𝑠1−𝜏 = 𝑠−1/2, 𝑃(𝑠) \$∝\$ 𝑠−𝜏 , 𝜏 = 3/2 ) T: Avalanche Law is localized within the manifold and metric dynamics arc of the directory. R: Universal Exponent preserves the operative relation that synaptic avalanche exponent scaling requires. A: Cutoff Scaling fixes the admissible closure condition for the entry. W: SYNAPTIC AVALANCHE EXPONENT is rendered as a reusable operator-level statement. I: The informational content

\paragraph{Canonical Equation.}
\[
𝑠1−𝜏 = 𝑠−1/2, 𝑃(𝑠)
\]

\paragraph{Dictionary.}
Definition of 𝑠1−𝜏 — 𝑠1−𝜏 = 𝑠−1/2, 𝑃(𝑠)

\paragraph{Encyclopedia.}
Definition of 𝑠1−𝜏 is an algebraic definition, written 𝑠1−𝜏 = 𝑠−1/2, 𝑃(𝑠). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
