\section*{ID8866: BESSEL-WEIGHTED TIDAL TORQUE Canonical Statutory Formula: τ\_tidal(ω, Ω)}
\paragraph{Metadata.}
PiID: 4142636395480 | RTEID: RTE:P34428.6469:T0.1792 | UUID: ec41795f-29e9-5d5b-b053-c0505aea4963

\paragraph{Canonical Statement.}
[ID 1005] BESSEL-WEIGHTED TIDAL TORQUE Canonical Statutory Formula: \$\textbackslash{}tau\_\{tidal\}(\textbackslash{}omega, \textbackslash{}Omega) = \textbackslash{}frac\{1\}\{I\} \textbackslash{}sum\_\{n=1\}\textasciicircum{}\{N\} J\_n(ne)\textasciicircum{}2 \textbackslash{}sin(2(\textbackslash{}omega - n\textbackslash{}Omega))\$ Formal Technical Dissertation: Calculates the torque exerted on a spinning body in an eccentric orbit. The strength of the resonance terms is weighted by Bessel functions of the first kind \$J\_n\$ dependent on orbital eccentricity \$e\$. Source: [6], [8]

\paragraph{Canonical Equation.}
\[
\tau_{tidal}(\omega, \Omega) = \frac{1}{I} \sum_{n=1}^{N} J_n(ne)^2 \sin(2(\omega - n\Omega))
\]

\paragraph{Dictionary.}
BESSEL-WEIGHTED TIDAL TORQUE Canonical Statutory Formula: \$ \_tidal( , ) = 1I \_n=1\textasciicircum{}N J\_n(ne)\textasciicircum{}2 (2( - n ))\$ Formal Technical Dissertation: Calculates the torque exerted on a spinning body in an eccentric orbit.

\paragraph{Encyclopedia.}
BESSEL-WEIGHTED TIDAL TORQUE Canonical Statutory Formula: τ\_tidal(ω, Ω) is a series / summation, written τ\_tidal(ω, Ω) = (1)/(I) ∑\_n=1\textasciicircum{}N J\_n(ne)\textasciicircum{}2 sin(2(ω - nΩ)). It is expressed as a sum or series over modes or indices, superposing discrete contributions. It is built from ω, Ω, I, n, N, J\_n, defining τ\_tidal(ω, Ω). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
