\tzpanchor{0314}
\tzpentryheader{0314}{Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{77f53f82-0e10-5671-94b5-d84105932e52}}\\
\textbf{PiID} & \tzpcode{5588174881520} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{321}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1219.3317 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.0091 rad}\\
\textbf{TZPID} & \tzpcode{ID0314} & \textbf{Node Dependencies}\quad \tzpidref{0313}\\
\textbf{Registry} & \tzpcode{registry\_id\_0314} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Configuration Manifold & Kaluza--Klein Sector\\
\textbf{Closure Support} & Gauge Quotient & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The configuration manifold for coupled magneto-acoustic and compactified extra-dimensional modes is M=prodm=0infinity(T*SO(3)x R3otimesHmKK)/GgaugeM = prod\_/\{m=0/\}textsuperscript\{/\{infinity/\}(T\}*SO(3) x mathbb/\{R/\}\textasciicircum{}3 textbackslash otimes H/\textasciicircum{}\{\}/\{KK/\}\_m)/G\_/\{text/\{gauge/\}/\}M=prodm=0infinity(T*SO(3)x R3otimesHmKK)/Ggauge, where HmKKH/\textasciicircum{}\{\}/\{KK/\}\_mHmKK denotes the mmmth Kaluza--Klein sector Hilbert space and Ggauge=/\{phi:R3rightarrowU(1) mid nabla2phi=0/\}G\_/\{text/\{gauge/\}/\} = textbackslash/\{phi : mathbb/\{R/\}\textasciicircum{}3 -> U(1)textbackslash,|textbackslash,nabla\textasciicircum{}2phi=0textbackslash/\}Ggauge=/\{phi:R3rightarrowU(1)midnabla2phi=0/\} fixes gauge freedom.

\tzpsection{Canonical Equation}
\[
Phi = n \cdot (h/2e) \approx n \cdot 2.07 \times 10^{-15} \text{ Wb}
\]
\[
Phi = n \cdot (h/2e) \approx n \cdot 2.07 \times 10^{-15} \text{ Wb}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $n$: integer mode index.
    \item $\mathcal{K}_{0314}$: canonical registry object for entry ID 0314.
    \item $P$: source equation symbol.
    \item $W$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0314 generated source Wolfram model *)
ClearAll[K0314, Cr0314, T, R, A, W, I, N];
eq0314$1 = HoldForm[Phi == n*((h/2)*e) == (n*2.07)/10^15];
eq0314$2 = HoldForm[Phi == n*((h/2)*e) == (n*2.07)/10^15];

K0314 = HoldForm[{eq0314$1, eq0314$2}];

N = "normalized TRAWIN closure object for Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems";
I = "Gauge Quotient integration/comparison layer";
W = "Kaluza--Klein Sector wave or operator carrier";
A = "Configuration Manifold admissible action/amplitude condition";
R = "Kaluza--Klein Sector rotation/curl preservation layer";
T = "Configuration Manifold local source condition";

Cr0314[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0314 = Cr0314[K0314];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Configuration Manifold local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Kaluza--Klein Sector rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Configuration Manifold admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Kaluza--Klein Sector wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Gauge Quotient integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0314] Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
T_{\mathrm{IM}}
=
\frac{1}{u_T}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi_{m_1}$ and $\phi_{m_2}$ be modal states over the hypersurface $\Sigma$.  
Let $\mathcal{L}$ be the transfer operator.

The transfer amplitude from mode $m_2$ into mode $m_1$ is:

\begin{equation}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
\end{equation}

Because the Trawin base unit $u_T$ defines the primitive loop scale of the system, the normalized transfer rate is:

\begin{equation}
\boxed{
T_{\mathrm{IM}}
=
\frac{1}{u_T}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
}
\end{equation}

\paragraph{Interpretation.}
ID 0014 repeats and stabilizes the inter-modal transfer structure introduced earlier, now explicitly as a transfer rate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Configuration Manifold}\par
\[
Phi = n \cdot (h/2e) \approx n \cdot 2.07 \times 10^{-15} \text{ Wb}
\]
\noindent This fixes the full extended configuration manifold for the coupled magneto-acoustic and Kaluza--Klein sectors.\par
\noindent\textbf{2. Kaluza--Klein Sector}\par
\[
Phi = n \cdot (h/2e) \approx n \cdot 2.07 \times 10^{-15} \text{ Wb}
\]
\noindent This identifies the direct-sum Hilbert carrier built from the admissible compactification modes.\par
\noindent\textbf{3. Gauge Quotient}\par
\[
Phi = n \cdot (h/2e) \approx n \cdot 2.07 \times 10^{-15} \text{ Wb}
\]
\noindent This closes the entry by quotienting the phase space by the harmonic gauge freedom.\par

\clearpage
\noindent\textbf{[ID 0314] Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The configuration manifold for coupled magneto-acoustic and compactified extra-dimensional modes is M=prodm=0infinity(T*SO(3)x R3otimesHmKK)/GgaugeM = prod sub / m=0/ textsuperscript / infinity/ (T *SO(3) x mathbb/ R/ to the power 3 textbackslash otimes H/ to the power / KK/ sub m)/G sub / text/ gauge/ / M=prodm=0infinity(T*SO(3)x R3otimesHmKK)/Ggauge, where HmKKH/ to the power / KK/ sub mHmKK denotes the mmmth Kaluza--Klein sector Hilbert space and Ggauge=/ phi:R3rightarrowU(1) mid nabla2phi=0/ G sub / text/ gauge/ / = textbackslash/ phi : mathbb/ R/ to the power 3 -> U(1)textbackslash,|textbackslash,nabla to the power 2phi=0textbackslash/ Ggauge=/ phi:R3rightarrowU(1)midnabla2phi=0/ fixes gauge freedom. \textbf{Contextual meaning:} The entry reads Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the extended phase space as a clean manifold-plus-sector-plus-gauge structure instead of corrupted product notation. \textbf{Lemma support:} Configuration Manifold; Kaluza--Klein Sector; Gauge Quotient.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
ID 0014 repeats and stabilizes the inter-modal transfer structure introduced earlier, now explicitly as a transfer rate.

\tzpsection{Equation Grounding}
Equation anchors: Phi sub Q: SpinRep to Hilb; Phi sub Q(J sub z)=bigoplus sub m=-j to the power j H sub m; and Phi sub Q(e to the power iphi J sub z )=operatorname diag (e to the power imphi ) sub m=-j to the power j. Proof route: show that the coupled magneto-acoustic and Kaluza--Klein sectors assemble into the stated gauge-quotiented phase-space manifold. Formalization route: prove that the stated gauge group acts admissibly on the extended phase-space carrier and yields the stated quotient structure.

\tzpsection{Interpretive Role}
The entry now states the extended phase space as a clean manifold-plus-sector-plus-gauge structure instead of corrupted product notation.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Compactified Extra-Dimensional Dynamics}: The inclusion of hidden cylindrical spatial dimensions to unify acoustic vibrations with electromagnetic fields.
\item \textbf{Gauge-Invariant Spatialize Integration}: The quotient manifold constructed by removing redundant local phase transformations from the physical degrees of freedom.
\item \textbf{Hybrid Phonon-Photon Carrier Space}: The explicit combined geometric setting where mechanical strain and magnetic flux are treated as one continuous metric.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0314]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0314_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0314] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the configuration manifold for coupled magneto-acoustic and compactified extra-
dimensional modes is M=prodm=0infinity(T*SO(3)x R3otimesHmKK)/Ggauge...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems is valid when the
stated geometric or topological relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0314_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
