\section*{ID9148: Relation: Σ G\_i(φ\_i, θ\_i)}
\paragraph{Metadata.}
PiID: 9896959469955 | RTEID: RTE:P35523.7156:T1.9835 | UUID: 241eb6be-3f4a-5e47-87fc-e50f6776a087

\paragraph{Canonical Statement.}
ssipative terms; concept of local clusters. Falsifiability / Test Handle: Add realistic physical terms to the model and test whether coherence increases relative to the simple case. 1.0.21 ID 120: Planetary Spin–Orbit Oscillator Model Type: Operator Formal Statement: To model real planetary dynamics, augment the spinonly Kuramoto model with spin and orbital phases \$θ\_i\$ and \$φ\_i.\$ Evolution equations take the form dot \$θ\_i\$ = \$ω\_i\$ + \$Σ T\_i(θ\_i, φ\_i)\$ – D\_i ·dot \$θ\_i,\$ dot \$φ\_i\$ = Ω\_i + \$Σ G\_i(φ\_i, θ\_i)\$ – D’ i ·dot \$φ\_i,\$ where T\_i and G\_i represent tidal torques depending on phase differences and D\_i, D’ i are dissipative coefficients. Orbital distances a\_i(t) vary with time to capture elliptical orbit dynamics. Interpretive Meaning: This generalization incorporates spin–orbit coupling, tidal dissipation and timedependent orbital separations, enabling study of true spin–orbit resonances such a

\paragraph{Canonical Equation.}
\[
Σ G_i(φ_i, θ_i)
\]

\paragraph{Dictionary.}
Relation: Σ G\_i(φ\_i, θ\_i) — Σ G\_i(φ\_i, θ\_i)

\paragraph{Encyclopedia.}
Relation: Σ G\_i(φ\_i, θ\_i) is a symbolic expression, written Σ G\_i(φ\_i, θ\_i). It introduces a symbol or relation used elsewhere in the framework. It is built from G\_i. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
