\tzpanchor{0363}
\tzpentryheader{0363}{Distributed Memory Condition}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f400447d-6373-5e07-8335-857c4432594d}}\\
\textbf{PiID} & \tzpcode{3305305488204} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{370}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1409.6096 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.3226 rad}\\
\textbf{TZPID} & \tzpcode{ID0363} & \textbf{Node Dependencies}\quad \tzpidref{0362}\\
\textbf{Registry} & \tzpcode{registry\_id\_0363} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
State persistence within the DAANSsphere arises from redundancy across projections rather than storage at specific coordinates; memory is distributed holographically across the fibre bundle.

\tzpsection{Canonical Equation}
\[
\mathcal{M}=\bigoplus_{i=1}^{N}\mathcal{M}_{i}
\]
\[
\Pi_{i}\mathcal{M}=m_{i},\qquad \sum_i \Pi_i=\operatorname{id}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{M}$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
    \item $\mathcal{M}_{i}$: source equation symbol.
    \item $\mathcal{K}_{0363}$: canonical registry object for entry ID 0363.
    \item $\Pi_{i}$: source equation symbol.
    \item $\Pi$: source equation symbol.
    \item $P$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $c$: speed of light or relativistic conversion factor.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0363 generated source Wolfram model *)
ClearAll[K0363, Cr0363, T, R, A, W, I, N];
eq0363$1 = HoldForm[M == bigoplusI1^N*MI];
eq0363$2 = HoldForm[TZPSequence[PiIM == mI, SumI*PiI == id]];
eq0363$3 = HoldForm[Rec[{mI}] == M];

K0363 = HoldForm[{eq0363$1, eq0363$2, eq0363$3}];

N = "normalized TRAWIN closure object for Distributed Memory Condition";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0363[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0363 = Cr0363[K0363];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Distributed Memory Condition.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0363] Distributed Memory Condition}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{d\rho}{dt}
=
-\frac{i}{\hbar}[H,\rho]
+
\sum_k
\left(
L_k \rho L_k^\dagger
-
\frac{1}{2}
\{L_k^\dagger L_k,\rho\}
\right).
\end{equation}

\paragraph{Primary Derivation.}
For open systems interacting with environment, non-unitary corrections appear.

The most general Markovian, completely positive evolution is:
\begin{equation}
\boxed{
\frac{d\rho}{dt}
=
-\frac{i}{\hbar}[H,\rho]
+
\sum_k
\left(
L_k \rho L_k^\dagger
-
\frac{1}{2}
\{L_k^\dagger L_k,\rho\}
\right).
}
\end{equation}

\paragraph{Interpretation.}
Environment introduces decoherence and dissipation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Distributed Memory Condition by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
\mathcal{M}=\bigoplus_{i=1}^{N}\mathcal{M}_{i}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\Pi_{i}\mathcal{M}=m_{i},\qquad \sum_i \Pi_i=\operatorname{id}
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\operatorname{Rec}(\{m_i\})=\mathcal{M}
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0363] Distributed Memory Condition}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Distributed Memory Condition is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} State persistence within the DAANSsphere arises from redundancy across projections rather than storage at specific coordinates; memory is distributed holographically across the fibre bundle. \textbf{Contextual meaning:} The entry reads Distributed Memory Condition as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Environment introduces decoherence and dissipation.

\tzpsection{Equation Grounding}
Equation anchors: proof=candidate sub proofable sub chl registry sub definition sub combined,D: 0 sub Engine sub Outputspublish sub reassemble expanded sub context registry; proof=non sub chl sub or sub empirical registry sub definition sub combined,D: 0 sub Engine sub Outputspublish sub reassemble expanded sub context registry sub en; and proof=non sub chl sub or sub empirical. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Sum-to-Identity Orthogonality}: The requirement that combining all scattered memory fragments perfectly rebuilds the original, complete, and uncorrupted global state.
\item \textbf{Spatial Partitioning of Coherence}: The intentional dividing of a single quantum wavefunction into multiple independent, spatially separated storage nodes.
\item \textbf{Projective Subspace Truncation}: The use of mathematical filters to isolate and retrieve only the specific memory data stored at one precise location.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0363]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0363_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0363] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Distributed Memory Condition}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} state persistence within the DAANSsphere arises from redundancy across projections
rather than storage at specific coordinates; memory is distribut...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Distributed Memory Condition is well formed when the total space, base space, structure
group, and projection map are compatible.''\\
\textbf{Proof:} The source statement supplies a bundle-style construction. The CHL reading treats the
base as the proposition carrier, the fiber or structure group as the typed parameter,
and the projection as the categorical morphism that preserves local-to-global structure.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- principal-bundle structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0363_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
