\tzpanchor{0380}
\tzpentryheader{0380}{Induced Vector Potential Term}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{d004349f-18d1-5a47-92cd-977f15829777}}\\
\textbf{PiID} & \tzpcode{1384146951941} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{387}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1475.6244 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.4314 rad}\\
\textbf{TZPID} & \tzpcode{ID0380} & \textbf{Node Dependencies}\quad \tzpidref{0379}\\
\textbf{Registry} & \tzpcode{registry\_id\_0380} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Total Vector Potential & Dipole Sector\\
\textbf{Closure Support} & Induced Sector & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The induced component of the vector potential arising from time-varying currents is given by an integral over the current density derivative divided by the distance between source and observation points.

\tzpsection{Canonical Equation}
\[
Delta_{\text{lattice}} = \sqrt{\frac{4\pi R^2}{N_{\text{nodes}}} \cdot \chi_T} \equiv \ell_P \cdot \exp\left( \frac{1}{\alpha_T} \right)
\]
\[
V_{BC} = \{ (\xi_1, \xi_2, \xi_3, \xi_4) : \xi_i \in \{ -1, +1 \} \} \subset \mathbb{R}^4, \quad |V_{BC}| = 16
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\pi$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $V_{BC}$: source equation symbol.
    \item $e_T$: exponential damping factor encoding potential-induced suppression.
    \item $\chi$: source equation symbol.
    \item $\ell$: source equation symbol.
    \item $\xi$: source equation symbol.
    \item $D$: source equation symbol.
    \item $N_{nodes}$: source equation symbol.
    \item $T$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0380 generated source Wolfram model *)
ClearAll[K0380, Cr0380, T, R, A, W, I, N];
eq0380$1 = HoldForm[DeltaLattice == sqrt[((4*Pi*R^2)/NNodes)*chiT]*equiv*ellP*exp[1/alphaT]];
eq0380$2 = HoldForm[VBC == VertexSetBC && VBC Subset Reals4 && Cardinality[VBC] == 16];

K0380 = HoldForm[{eq0380$1, eq0380$2}];

N = "normalized TRAWIN closure object for Induced Vector Potential Term";
I = "Induced Sector integration/comparison layer";
W = "Dipole Sector wave or operator carrier";
A = "Total Vector Potential admissible action/amplitude condition";
R = "Dipole Sector rotation/curl preservation layer";
T = "Total Vector Potential local source condition";

Cr0380[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0380 = Cr0380[K0380];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Total Vector Potential local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Dipole Sector rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Total Vector Potential admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Dipole Sector wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Induced Sector integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Induced Vector Potential Term.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0380] Induced Vector Potential Term}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Limit.}
\begin{equation}
\hbar\rightarrow 0 .
\end{equation}

\paragraph{Stationary-Action Recovery.}
\begin{equation}
\hbar\rightarrow 0
\quad\Longrightarrow\quad
\delta S=0 .
\end{equation}

\paragraph{Primary Derivation.}
The path integral has phase factor:
\begin{equation}
e^{iS/\hbar}.
\end{equation}

As $\hbar\to 0$, non-stationary paths oscillate rapidly and cancel by destructive interference.

The surviving paths satisfy:
\begin{equation}
\delta S=0 .
\end{equation}

Therefore,
\begin{equation}
\boxed{
\hbar\rightarrow 0
\quad\Longrightarrow\quad
\delta S=0 .
}
\end{equation}

\paragraph{Interpretation.}
The semiclassical limit recovers stationary-action classical dynamics from quantum phase cancellation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Induced Vector Potential Term by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Total Vector Potential}\par
\[
Delta_{\text{lattice}} = \sqrt{\frac{4\pi R^2}{N_{\text{nodes}}} \cdot \chi_T} \equiv \ell_P \cdot \exp\left( \frac{1}{\alpha_T} \right)
\]
\noindent This fixes the full vector-potential decomposition of the gyromagnetic carrier.\par
\noindent\textbf{2. Dipole Sector}\par
\[
V_{BC} = \{ (\xi_1, \xi_2, \xi_3, \xi_4) : \xi_i \in \{ -1, +1 \} \} \subset \mathbb{R}^4, \quad |V_{BC}| = 16
\]
\noindent This isolates the dipole contribution generated by the effective moment about the center of mass.\par
\noindent\textbf{3. Induced Sector}\par
\[
Delta_{\text{lattice}} = \sqrt{\frac{4\pi R^2}{N_{\text{nodes}}} \cdot \chi_T} \equiv \ell_P \cdot \exp\left( \frac{1}{\alpha_T} \right)
\]
\noindent This closes the entry by adding the retarded induced-current contribution to the total potential.\par

\clearpage
\noindent\textbf{[ID 0380] Induced Vector Potential Term}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Induced Vector Potential Term is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The induced component of the vector potential arising from time-varying currents is given by an integral over the current density derivative divided by the distance between source and observation points. \textbf{Contextual meaning:} The entry reads Induced Vector Potential Term as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the vector-potential expansion directly instead of carrying headings and prose fragments into the equation slots. \textbf{Lemma support:} Total Vector Potential; Dipole Sector; Induced Sector.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The semiclassical limit recovers stationary-action classical dynamics from quantum phase cancellation. \% ========================================================= \% QUATERNARY DERIVATION LAYER -- ID 0381 TO ID 0390 \% CANONICAL PDF-ALIGNED VERSION \% =========================================================.

\tzpsection{Equation Grounding}
Equation anchors: Delta sub lattice = sqrt ratio 4pi R to the power 2 N sub nodes dot chi sub T equiv ell sub P dot exp( ratio 1 alpha sub T ); V sub BC = (xi sub 1, xi sub 2, xi sub 3, xi sub 4) : xi sub i in -1, +1 subset mathbb R to the power 4, |V sub BC | = 16; and \$Delta sub lattice = sqrt ratio 4pi R to the power 2 N sub nodes dot chi sub T equiv ell sub P dot exp( ratio 1 alpha sub T ). Proof route: show that the dipole, gyroscopic, and induced sectors combine into the stated total vector potential. Formalization route: prove that the induced-current integral contributes the stated correction to the total vector-potential expansion.

\tzpsection{Interpretive Role}
The entry now states the vector-potential expansion directly instead of carrying headings and prose fragments into the equation slots.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Current-Density Retardation}: The calculation of the magnetic field potential based on the delayed ripples caused by moving electric charges far away.
\item \textbf{Inverse-Distance Volume Integration}: The summation of all distant magnetic influences, weighting the closest ones heaviest and the furthest ones lightest.
\item \textbf{Dynamic Field Augmentation}: The addition of a constantly changing, time-dependent magnetic layer on top of a static, unmoving background field.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0380]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0380_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0380] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Induced Vector Potential Term}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the induced component of the vector potential arising from time-varying currents is
given by an integral over the current density derivative divide...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Induced Vector Potential Term is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0380_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
