\section*{ID9340: Definition of Δ𝜙}
\paragraph{Metadata.}
PiID: 3215137556003 | RTEID: RTE:P36269.2942:T3.2120 | UUID: 86c809aa-4a4b-5e7c-a4ae-ff2fa87fc151

\paragraph{Canonical Statement.}
n Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0133], [ID 0147] Node registry\_id\_0148 Support Titles Wall Phase Profile; Net Phase Jump; Wall Winding Test Handle If smooth perturbations preserving asymptotic phase values can erase the wall winding, the defect construction fails. Canonical Equation Links 𝜙 (𝑥 )=𝜋 [ 1+tanh( (𝑥−𝑥0 )/𝑤) 2 ] \$Δ𝜙=𝜙 (+∞)−𝜙 (−∞)=𝜋\$ 𝜈wall= 1 2𝜋 \$∫\$ 𝜕𝑥 𝜙 𝑑𝑥 [ID 0149] Domain Wall Robustness Criterion TZPID ID0149 UUID a400a7ad-cb53-5f22-ad42-57268df2e80d Type Robustness Criterion Scale noise tolerance of local wall patterns LOC Classification Working routing: QA371 stability theory; QA612 topological invariants arXiv Classification Primary: math-ph Cross-list: cond-mat.mes-hall, nlin.PS Canonical Statement The locally introduc

\paragraph{Canonical Equation.}
\[
Δ𝜙=𝜙 (+∞)−𝜙 (−∞)=𝜋
\]

\paragraph{Dictionary.}
Definition of Δ𝜙 — Δ𝜙=𝜙 (+∞)−𝜙 (−∞)=𝜋

\paragraph{Encyclopedia.}
Definition of Δ𝜙 is an algebraic definition, written Δ𝜙=𝜙 (+∞)−𝜙 (−∞)=𝜋. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
