\section*{ID9803: Definition of (X-x\_0)\textasciicircum{}2+(y-y\_0)\textasciicircum{}2+(z-z\_0)\textasciicircum{}2}
\paragraph{Metadata.}
PiID: 0141020672358 | RTEID: RTE:P38067.2260:T6.1744 | UUID: ab0e03d0-4ef0-5a2d-9a12-bba780f2c3f4

\paragraph{Canonical Statement.}
mathematically construct the teleportation space as \$\textbackslash{}Omega[T\textasciicircum{}2 \textbackslash{}times T\textasciicircum{}2, \textbackslash{}pi, \textbackslash{}Psi]\$ – a double torus with π-modulated entanglement field \$\textbackslash{}Psi\$. The inner torus (\$T\textasciicircum{}2\_\{\textbackslash{}text\{inner\}\}\$) has coordinates \$(θ\_1, φ\_1)\$ and represents the “sending” end, while the outer torus (\$T\textasciicircum{}2\_\{\textbackslash{}text\{outer\}\}\$) with \$(θ\_2, φ\_2)\$ is the “receiving” end. The two are connected by a fiber bundle structure: one can imagine fibers (like circles) that go from a point on the inner torus to a corresponding point on the outer torus. Embedded in the inner torus is the static bubble region: a spherical region defined by \$(x-x\_0)\textasciicircum{}2+(y-y\_0)\textasciicircum{}2+(z-z\_0)\textasciicircum{}2 = r\_\{\textbackslash{}text\{bubble\}\}\textasciicircum{}2\$ that sits inside the volume of the torus. This bubble is not filled with ordinary matter but by the PackingSphere[Hom(S³, ℝ[π])] condition – essentially it contains the abstract sphere of dimension 153600 (S³ generalized) realized within the torus volume. The bubble’s surface acts as a holographic screen where the 4D information from the packing is projected into the 3D torus. It’s also where the kissing number constraints are enforced: on that surface, we impose \$KissingNumber[n] ≡ \textbackslash{}lfloor 10\textasciicircum{}

\paragraph{Canonical Equation.}
\[
(x-x_0)^2+(y-y_0)^2+(z-z_0)^2 = r_{\text{bubble}}^2
\]

\paragraph{Dictionary.}
Definition of (X-x\_0)\textasciicircum{}2+(y-y\_0)\textasciicircum{}2+(z-z\_0)\textasciicircum{}2 — (x-x\_0)\textasciicircum{}2+(y-y\_0)\textasciicircum{}2+(z-z\_0)\textasciicircum{}2 = r\_bubble\textasciicircum{}2

\paragraph{Encyclopedia.}
Definition of (X-x\_0)\textasciicircum{}2+(y-y\_0)\textasciicircum{}2+(z-z\_0)\textasciicircum{}2 is an algebraic definition, written (x-x\_0)\textasciicircum{}2+(y-y\_0)\textasciicircum{}2+(z-z\_0)\textasciicircum{}2 = r\_bubble\textasciicircum{}2. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from r\_, defining (x-x\_0)\textasciicircum{}2+(y-y\_0)\textasciicircum{}2+(z-z\_0)\textasciicircum{}2. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
