\tzpanchor{0155}
\tzpentryheader{0155}{Chern--Simons Obstruction Class}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{0599ab7a-5300-5382-8ce8-02f8a40a6390}}\\
\textbf{PiID} & \tzpcode{7450284102701} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{162}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{601.8994 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.9917 rad}\\
\textbf{TZPID} & \tzpcode{ID0155} & \textbf{Node Dependencies}\quad \tzpidref{0154}\\
\textbf{Registry} & \tzpcode{registry\_id\_0155} & \textbf{Scale}\quad topological obstruction on a boundary hypersurface\\
\textbf{LOC Classification} & QA612 characteristic classes & QC20.7 gauge invariants\\
\textbf{arXiv Classification} & Primary: hep-th \quad Cross-list: math-ph, math.AT & \\
\textbf{Primary Support} & Invariant Integral & Field-Strength Origin\\
\textbf{Closure Support} & Obstruction Detection & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This invariant measures the topological obstruction to trivializing the gauge connections; a nonzero Chern--Simons value signals a nontrivial coupling between gravity, electromagnetism and other fields.

\tzpsection{Canonical Equation}
\[
\mathrm{CS}(A)
=
\frac{1}{4\pi}\int_{\Sigma}\operatorname{Tr}(F\wedge F)
\]
\[
F=dA+A\wedge A
\]
\[
\mathrm{CS}(A)\neq 0
\;\Longrightarrow\;
\mathcal{O}_{\mathrm{top}}\neq 0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $A$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $F$: source equation symbol.
    \item $\mathcal{O}_{\mathrm{top}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0155 generated source Wolfram model *)
ClearAll[K0155, Cr0155, T, R, A, W, I, N];
eq0155$1 = HoldForm[CS[A] == (1/(4*Pi))*IntegralSigmaTr[Fwedge*F]];
eq0155$2 = HoldForm[F == dA + Awedge*A];
eq0155$3 = HoldForm[CS[A] != 0*Longrightarrow*OTop != 0];

K0155 = HoldForm[{eq0155$1, eq0155$2, eq0155$3}];

N = "normalized TRAWIN closure object for Chern--Simons Obstruction Class";
I = "Obstruction Detection integration/comparison layer";
W = "Field-Strength Origin wave or operator carrier";
A = "Invariant Integral admissible action/amplitude condition";
R = "Field-Strength Origin rotation/curl preservation layer";
T = "Invariant Integral local source condition";

Cr0155[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0155 = Cr0155[K0155];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Invariant Integral local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Field-Strength Origin rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Invariant Integral admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Field-Strength Origin wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Obstruction Detection integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Chern--Simons Obstruction Class.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0155] Chern--Simons Obstruction Class}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathrm{CS}(A)
=
\frac{1}{4\pi}\int_{\Sigma}\operatorname{Tr}(F\wedge F)
\]
\[
F=dA+A\wedge A
\]
\[
\mathrm{CS}(A)\neq 0
\;\Longrightarrow\;
\mathcal{O}_{\mathrm{top}}\neq 0
\]

\paragraph{Primary Derivation.}
The expression \( \mathrm{CS}(A) \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. From the TRAWIN perspective, the equation functions as the integral carrier for the entry’s information content. In CHL terms, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Chern--Simons Obstruction Class by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Invariant Integral}\par
\[
\mathrm{CS}(A)
=
\frac{1}{4\pi}\int_{\Sigma}\operatorname{Tr}(F\wedge F)
\]
\noindent This defines the obstruction observable directly on the boundary hypersurface.\par
\noindent\textbf{2. Field-Strength Origin}\par
\[
F=dA+A\wedge A
\]
\noindent This identifies the curvature two-form from which the invariant is built.\par
\noindent\textbf{3. Obstruction Detection}\par
\[
\mathrm{CS}(A)\neq 0
\;\Longrightarrow\;
\mathcal{O}_{\mathrm{top}}\neq 0
\]
\noindent This closes the progression by turning a nonzero invariant into a nontrivial obstruction claim.\par

\clearpage
\noindent\textbf{[ID 0155] Chern--Simons Obstruction Class}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Chern--Simons Obstruction Class is a Definition. The obstruction class for topological unification is given by the Chern--Simons invariant CS=14   Tr [F F]CS = \textbackslash{}tfrac\{1\}\{4\textbackslash{}pi\}\textbackslash{}int\_\{\textbackslash{}Sigma\} \textbackslash{}operatorname\{Tr\}[F \textbackslash{}wedge F]CS=4 1    Tr[F F], computed from the connection form A =A dx +Bgravitational+CelectromagneticA\_\textbackslash{}mu = A\_\textbackslash{}mu dx\textasciicircum{}\{\textbackslash{}mu\} + B\_\{\textbackslash{}text\{gravitational\}\} + C\_\{\textbackslash{}text\{electromagnetic\}\}A  =A  dx +Bgravitational +Celectromagnetic .

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The obstruction class for topological unification is given by the Chern--Simons invariant CS=14   Tr [F F]CS = \textbackslash{}tfrac\{1\}\{4\textbackslash{}pi\}\textbackslash{}int\_\{\textbackslash{}Sigma\} \textbackslash{}operatorname\{Tr\}[F \textbackslash{}wedge F]CS=4 1    Tr[F F], computed from the connection form A =A dx +Bgravitational+CelectromagneticA\_\textbackslash{}mu = A\_\textbackslash{}mu dx\textasciicircum{}\{\textbackslash{}mu\} + B\_\{\textbackslash{}text\{gravitational\}\} + C\_\{\textbackslash{}text\{electromagnetic\}\}A  =A  dx +Bgravitational +Celectromagnetic .
\textbf{Contextual meaning:} This invariant measures the topological obstruction to trivializing the gauge connections; a nonzero Chern--Simons value signals a nontrivial coupling between gravity, electromagnetism and other fields.
\textbf{Derivable consequences:} Determines the level of the topological action; controls phase in path integrals; influences Berry phase; ensures anomaly cancellation. Falsifiab
\textbf{Lemma support:} The obstruction class for topological unification is given by the Chern--Simons invariant CS=14   Tr [F F]CS = \textbackslash{}tfrac\{1\}\{4\textbackslash{}pi\}\textbackslash{}int\_\{\textbackslash{}Sigma\} \textbackslash{}operatorname\{Tr\}[F \textbackslash{}wedge F]CS=4 1    Tr[F F], computed from the connection form A =A dx +Bgravitational+CelectromagneticA\_\textbackslash{}mu = A\_\textbackslash{}mu dx\textasciicircum{}\{\textbackslash{}mu\} + B\_\{\textbackslash{}text\{gravitational\}\} + C\_\{\textbackslash{}text\{electromagnetic\}\}A  =A  dx +Bgravitational +Celectromagnetic .\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This invariant measures the topological obstruction to trivializing the gauge connections; a nonzero Chern--Simons value signals a nontrivial coupling between gravity, electromagnetism and other fields.

\tzpsection{Equation Grounding}
The obstruction class for topological unification is given by the Chern--Simons invariant CS=14   Tr [F F]CS = \textbackslash{}tfrac\{1\}\{4\textbackslash{}pi\}\textbackslash{}int\_\{\textbackslash{}Sigma\} \textbackslash{}operatorname\{Tr\}[F \textbackslash{}wedge F]CS=4 1    Tr[F F], computed from the connection form A =A dx +Bgravitational+CelectromagneticA\_\textbackslash{}mu = A\_\textbackslash{}mu dx\textasciicircum{}\{\textbackslash{}mu\} + B\_\{\textbackslash{}text\{gravitational\}\} + C\_\{\textbackslash{}text\{electromagnetic\}\}A  =A  dx +Bgravitational +Celectromagnetic .

\tzpsection{Interpretive Role}
This invariant measures the topological obstruction to trivializing the gauge connections; a nonzero Chern--Simons value signals a nontrivial coupling between gravity, electromagnetism and other fields.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Invariant Integral}: The definition of the obstruction observable directly on the boundary hypersurface.
\item \textbf{Field-Strength Origin}: The identification of the curvature two-form from which the invariant is built.
\item \textbf{Obstruction Detection}: The conversion of a nonzero invariant into a nontrivial obstruction claim.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0155]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0155_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0155] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Chern--Simons Obstruction Class}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this invariant measures the topological obstruction to trivializing the gauge
connections; a nonzero Chern--Simons value signals a nontrivial coupl...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Chern--Simons Obstruction Class is valid when the stated geometric or topological
relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0155_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
