\tzpanchor{0085}
\tzpentryheader{0085}{Gyromagnetic Genesis Hypothesis}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{a2ed68c8-393b-535e-aaa7-0ab0984a15c1}}\\
\textbf{PiID} & \tzpcode{3482534211706} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{92}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{330.0739 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.5439 rad}\\
\textbf{TZPID} & \tzpcode{ID0085} & \textbf{Node Dependencies}\quad \tzpidref{0045}\\
\textbf{Registry} & \tzpcode{registry\_id\_0085} & \textbf{Scale}\quad laboratory-to-astrophysical\\
\textbf{LOC Classification} & QC6.4 gyromagnetism & QB rotational generation\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph \quad Cross-list: astro-ph.SR, gr-qc & \\
\textbf{Primary Support} & Local Electromagnetic Source Terms & Electromagnetic Torque Integral\\
\textbf{Closure Support} & Angular Momentum Generation Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Angular momentum in astrophysical and laboratory systems does not stem from primordial rotation but is continuously generated through interactions between local electromagnetic fields and matter, governed by the gyromagnetic coupling in the Trawin framework.

\tzpsection{Canonical Equation}
\[
\tau_{\mathrm{em}}
=
\int \mathbf{r}\times\left(\mathbf{J}\times\mathbf{B}+\rho_e\mathbf{E}\right)\,dV
\]
\[
\frac{d\mathbf{L}}{dt}=\tau_{\mathrm{em}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\tau_{\mathrm{em}}$: source equation symbol.
    \item $J$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $\rho_e$: source equation symbol.
    \item $E$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0085 generated source Wolfram model *)
ClearAll[K0085, Cr0085, T, R, A, W, I, N];
eq0085$1 = HoldForm[tauEm == Integral*r*(J*B + rhoEE)*dV];
eq0085$2 = HoldForm[dL/dt == tauEm];
eq0085$3 = HoldForm[J*B + rhoEE];

K0085 = HoldForm[{eq0085$1, eq0085$2, eq0085$3}];

N = "normalized TRAWIN closure object for Gyromagnetic Genesis Hypothesis";
I = "Angular Momentum Generation Law integration/comparison layer";
W = "Electromagnetic Torque Integral wave or operator carrier";
A = "Local Electromagnetic Source Terms admissible action/amplitude condition";
R = "Electromagnetic Torque Integral rotation/curl preservation layer";
T = "Local Electromagnetic Source Terms local source condition";

Cr0085[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0085 = Cr0085[K0085];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Local Electromagnetic Source Terms local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Electromagnetic Torque Integral rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Local Electromagnetic Source Terms admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Electromagnetic Torque Integral wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Angular Momentum Generation Law integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Gyromagnetic Genesis Hypothesis.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0085] Gyromagnetic Genesis Hypothesis}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Source Term.}
\begin{equation}
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}.
\end{equation}

\paragraph{Electromagnetic Torque Integral.}
\begin{equation}
\boldsymbol{\tau}_{\mathrm{em}}
=
\int_V
\mathbf{r}\times
\left(
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}
\right)
\,\mathrm{d}V .
\end{equation}

\paragraph{Angular Momentum Generation Law.}
\begin{equation}
\frac{\mathrm{d}\mathbf{L}}{\mathrm{d}t}
=
\boldsymbol{\tau}_{\mathrm{em}} .
\end{equation}

\paragraph{Primary Derivation.}
The local electromagnetic force density is:
\begin{equation}
\mathbf{f}_{\mathrm{em}}
=
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}.
\end{equation}

Torque density is position crossed with force density:
\begin{equation}
\mathbf{r}\times\mathbf{f}_{\mathrm{em}}.
\end{equation}

Integrating over a source region $V$ gives:
\begin{equation}
\boldsymbol{\tau}_{\mathrm{em}}
=
\int_V
\mathbf{r}\times
\left(
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}
\right)
\,\mathrm{d}V .
\end{equation}

The angular momentum generation law is therefore:
\begin{equation}
\boxed{
\frac{\mathrm{d}\mathbf{L}}{\mathrm{d}t}
=
\boldsymbol{\tau}_{\mathrm{em}} .
}
\end{equation}

\paragraph{Interpretation.}
Angular momentum is modeled as continuously generated by local electromagnetic source terms rather than assumed as a primordial input.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Gyromagnetic Genesis Hypothesis by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Local Electromagnetic Source Terms}\par
\[
\mathbf{J}\times\mathbf{B}+\rho_e\mathbf{E}
\]
\noindent This identifies the field content that can source rotational change.\par
\noindent\textbf{2. Electromagnetic Torque Integral}\par
\[
\tau_{\mathrm{em}}
=
\int \mathbf{r}\times\left(\mathbf{J}\times\mathbf{B}+\rho_e\mathbf{E}\right)\,dV
\]
\noindent This converts local forcing into a net rotational source term.\par
\noindent\textbf{3. Angular Momentum Generation Law}\par
\[
\frac{d\mathbf{L}}{dt}=\tau_{\mathrm{em}}
\]
\noindent This closes the progression by stating that angular momentum is produced continuously from the torque source.\par

\clearpage
\noindent\textbf{[ID 0085] Gyromagnetic Genesis Hypothesis}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Gyromagnetic Genesis Hypothesis is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Angular momentum in astrophysical and laboratory systems does not stem from primordial rotation but is continuously generated through interactions between local electromagnetic fields and matter, governed by the gyromagnetic coupling in the Trawin framework. \textbf{Contextual meaning:} The entry reads Gyromagnetic Genesis Hypothesis as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry shifts the rotational narrative from inherited motion to generated motion. It is the gateway from quantum-scale limits into the cross-scale gyromagnetic program developed by the next entries. \textbf{Lemma support:} Local Electromagnetic Source Terms; Electromagnetic Torque Integral; Angular Momentum Generation Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Angular momentum is modeled as continuously generated by local electromagnetic source terms rather than assumed as a primordial input.

\tzpsection{Equation Grounding}
Equation anchors: Angular momentum in astrophysical and laboratory systems does not stem from primordial rotation but is continuously generated through interactions between local electromagnetic fields and matter, governed by the gyromagnetic coupling in the Trawin framework. Angular momentum in astrophysical and laboratory systems does not stem from primordial rotation but is continuously generated through interactions between local electromagnetic fields and matter, governed by the gyromagnetic coupling in the Trawin framework.

\tzpsection{Interpretive Role}
This entry shifts the rotational narrative from inherited motion to generated motion. It is the gateway from quantum-scale limits into the cross-scale gyromagnetic program developed by the next entries.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Spin-Magnetic Genesis Hypothesis}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\item \textbf{Spin-Magnetic Rotating-Field Analogue}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\item \textbf{Spin-Magnetic Terminology}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0085]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0085_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0085] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Gyromagnetic Genesis Hypothesis}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} angular momentum in astrophysical and laboratory systems does not stem from primordial
rotation but is continuously generated through interactions...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Gyromagnetic Genesis Hypothesis is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0085_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
