\tzpanchor{0230}
\tzpentryheader{0230}{Bessel Interference Pattern of Emergent Matter}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{ba1d3394-743f-53eb-b215-c0338da48c1f}}\\
\textbf{PiID} & \tzpcode{3786783165271} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{237}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{893.1411 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.4716 rad}\\
\textbf{TZPID} & \tzpcode{ID0230} & \textbf{Node Dependencies}\quad \tzpidref{0229}\\
\textbf{Registry} & \tzpcode{registry\_id\_0230} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Radial Bessel Profile & First Nodal Ring\\
\textbf{Closure Support} & Fold Energy & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The radial profile of a disturbance in the hyperspherical vacuum follows the spherical Bessel function \(j_0(kr)\), with alternating constructive and destructive interference rings and a first node at \(kr_1\approx2.405\).

\tzpsection{Canonical Equation}
\[
\Psi(r,t)=\Psi_0+\varepsilon\,j_0(k r)\cos(\omega t)
\]
\[
k r_1 \approx 2.405
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Psi(r,t)$: wavefunction or state carrier for the entry equation.
    \item $\Psi_0$: original uniform field.
    \item $\varepsilon$: small amplitude of the disturbance.
    \item $j_0(kr)$: spherical Bessel radial interference pattern.
    \item $\omega$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0230 generated source Wolfram model *)
ClearAll[K0230, Cr0230, T, R, A, W, I, N];
eq0230$1 = HoldForm[Psi[r, t] == Psi0 + epsilon*j0[k*r]*Cos[omega*t]];
eq0230$2 = HoldForm[k*r1 == 2.405];
eq0230$3 = HoldForm[EFold == Integral0^r1*Abs[Psi[r, t] - Psi0]^2*r^2*dr];

K0230 = HoldForm[{eq0230$1, eq0230$2, eq0230$3}];

N = "normalized TRAWIN closure object for Bessel Interference Pattern of Emergent Matter";
I = "Fold Energy integration/comparison layer";
W = "First Nodal Ring wave or operator carrier";
A = "Radial Bessel Profile admissible action/amplitude condition";
R = "First Nodal Ring rotation/curl preservation layer";
T = "Radial Bessel Profile local source condition";

Cr0230[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0230 = Cr0230[K0230];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Radial Bessel Profile local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ First Nodal Ring rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Radial Bessel Profile admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ First Nodal Ring wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Fold Energy integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Bessel Interference Pattern of Emergent Matter.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0230] Bessel Interference Pattern of Emergent Matter}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}

Emergent matter is modeled as energy localized inside the first nodal basin of a radial Bessel interference pattern.

\paragraph{Primary Derivation.}

Let the radial interference field be
\[
\Psi(r,t)=\Psi_0+\varepsilon j_0(kr)\cos(\omega t).
\]
The first nodal ring is fixed by the first positive zero of \(J_0\):
\[
kr_1\approx 2.405,
\qquad
r_1\approx \frac{2.405}{k}.
\]
The fold energy localized inside this nodal basin is
\[
\mathcal{E}_{\mathrm{fold}}(t)=\int_{0}^{r_1}|\Psi(r,t)-\Psi_0|^2 r^2\,dr.
\]
Substituting the Bessel disturbance gives
\[
\mathcal{E}_{\mathrm{fold}}(t)=\varepsilon^2\cos^2(\omega t)\int_{0}^{r_1}j_0(kr)^2 r^2\,dr.
\]
This makes the matter-pocket strength proportional to the squared amplitude of the Bessel basin and bounded by the first destructive-interference radius.

\paragraph{Wolfram Form.}
\begin{verbatim}
Psi[r_, t_] := Psi0 + eps*SphericalBesselJ[0, k*r]*Cos[omega*t];
r1 = 2.405/k;
Efold[t_] := Integrate[Abs[Psi[r, t] - Psi0]^2*r^2, {r, 0, r1}];
\end{verbatim}

\paragraph{Interpretation.}

ID 0230 ties emergent matter to the first Bessel basin: the nodal ring bounds the pocket, while the fold-energy integral measures how much localized field energy is trapped before destructive interference cancels the profile.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The Bessel disturbance profile produces a first nodal boundary, after which the support layer measures the localized fold contribution within that radius.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Radial Bessel Profile}\par
\[
\Psi(r,t)=\Psi_0+\varepsilon\,j_0(k r)\cos(\omega t)
\]
\noindent This restores the sourced radial Bessel disturbance instead of the generic bounded-mode certificate record.\par
\noindent\textbf{2. First Nodal Ring}\par
\[
k r_1 \approx 2.405
\]
\noindent This identifies the first destructive-interference node that bounds the emergent-matter pocket.\par
\noindent\textbf{3. Fold Energy}\par
\[
\mathcal{E}_{\mathrm{fold}}=\int_{0}^{r_1}\lvert\Psi(r,t)-\Psi_0\rvert^2 r^2\,dr
\]
\noindent This closes the entry by measuring the energy localized inside the first nodal radius.\par

\clearpage
\noindent\textbf{[ID 0230] Bessel Interference Pattern of Emergent Matter}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small

\tzpsection{Definition}

A Bessel interference profile is a radial disturbance imposed on an originally uniform field. Its spherical Bessel factor describes reinforcement and cancellation, with the first node bounding the initial disturbance basin.

\tzpsection{Contextual Meaning}

The field begins at \(\Psi_0\) and receives a small oscillating perturbation of amplitude \(\varepsilon\). The term \(j_0(k r)\) governs radial variation, while \(\cos(\omega t)\) supplies temporal oscillation; its first zero marks a change in the initial coherent profile.

\tzpsection{Formal Statement}

\[
\Psi(r,t)=\Psi_0+\varepsilon\,j_0(k r)\cos(\omega t), \qquad k r_1\approx2.405
\]

\tzpsection{Derivable Consequences}

At \(k r_1\approx2.405\), the Bessel contribution vanishes. Inside that node, the first lobe defines the primary basin; changing \(\varepsilon\) alters magnitude without moving Bessel nodes.

\tzpsection{Lemma Support}

The approved passage identifies \(\Psi_0\), \(\varepsilon\), and \(j_0(k r)\), and includes the first-node relation in the retrieved source context.

\tzpsection{Technical Interpretation}

This separable modulation uses the Bessel factor for spatial geometry, the cosine for temporal phase, and amplitude for departure from background.

\tzpsection{Equation Grounding}

\(\Psi_0\) is the original uniform field; \(\varepsilon\) is the small amplitude of the disturbance; and \(j_0(k r)\) is the spherical Bessel radial interference pattern supported by the approved source.

\tzpsection{Interpretive Role}

The entry gives the progression a localized nodal geometry with a defined basin and boundary.

\tzpsection{TZP Thesaurus}

\noindent \textbf{Uniform Background Field}: The reference field value before the modeled radial perturbation is applied. \enspace\textbullet\enspace \textbf{Spherical Bessel Profile}: The radial oscillation pattern that organizes constructive and destructive rings. \enspace\textbullet\enspace \textbf{First Nodal Radius}: The first radial location at which the disturbance contribution vanishes.\par

\endgroup

\tzpsection{Encyclopedia Mathematica}
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0230_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0230] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Bessel Interference Pattern of Emergent Matter}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the radial disturbance profile is modeled by \(j_0(kr)\), with the first nodal ring at \(kr_1\approx2.405\).

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Bessel Interference Pattern of Emergent Matter is valid as a formal dynamical law when
the Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0230_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
