\tzpanchor{0971}
\tzpentryheader{0971}{LOGIT-SPHERICAL COORDINATE TRANSFORM}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{920f6fc7-75a1-5c07-8cf2-a063ed6ff1e0}}\\
\textbf{PiID} & \tzpcode{3001927876611} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{978}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3700.7106 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{06.0976 rad}\\
\textbf{TZPID} & \tzpcode{ID0971} & \textbf{Node Dependencies}\quad \tzpidref{0970}\\
\textbf{Registry} & \tzpcode{registry\_id\_0971} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Encoder Map & Logit Lift\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
mathcal\{E\} \{encoder\}(M) = text\{CantorPair\}[text\{Logit\}[text\{Mod\}[hat\{n\} * text\{diag\}(pi \{digits\}), 1]]]

\tzpsection{Canonical Equation}
\[
mathcal{E}_{\mathrm{enc}}(M)=\operatorname{CantorPair}\!\left(\operatorname{Logit}\!\left(\operatorname{Mod}\!\left(\widehat{n}\cdot \operatorname{diag}(\pi_{\mathrm{digits}}),1\right)\right)\right)
\]
\[
u=\frac{e^{t}}{1+e^{t}}\in[0,1]
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $E$: source equation symbol.
    \item $M$: source equation symbol.
    \item $n$: integer mode index.
    \item $\pi$: source equation symbol.
    \item $t$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0971 generated source Wolfram model *)
ClearAll[K0971, Cr0971, T, R, A, W, I, N];
eq0971$1 = HoldForm[mathcal[E]*_*enc*M == CantorPair[Logit[Mod[widehat[n]*diag[PiDigits], 1]]]];
eq0971$2 = HoldForm[Element[u == Exp[t]/(1 + Exp[t]), Commutator[0, 1]]];

K0971 = HoldForm[{eq0971$1, eq0971$2}];

N = "normalized TRAWIN closure object for LOGIT-SPHERICAL COORDINATE TRANSFORM";
I = "LOGIT-SPHERICAL COORDINATE TRANSFORM integration/comparison layer";
W = "LOGIT-SPHERICAL COORDINATE TRANSFORM wave or operator carrier";
A = "LOGIT-SPHERICAL COORDINATE TRANSFORM admissible action/amplitude condition";
R = "LOGIT-SPHERICAL COORDINATE TRANSFORM rotation/curl preservation layer";
T = "LOGIT-SPHERICAL COORDINATE TRANSFORM local source condition";

Cr0971[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0971 = Cr0971[K0971];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ LOGIT-SPHERICAL COORDINATE TRANSFORM local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ LOGIT-SPHERICAL COORDINATE TRANSFORM rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ LOGIT-SPHERICAL COORDINATE TRANSFORM admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ LOGIT-SPHERICAL COORDINATE TRANSFORM wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ LOGIT-SPHERICAL COORDINATE TRANSFORM integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for LOGIT-SPHERICAL COORDINATE TRANSFORM.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0971] LOGIT-SPHERICAL COORDINATE TRANSFORM}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
mathcal{E}_{\mathrm{enc}}(M)=\operatorname{CantorPair}\!\left(\operatorname{Logit}\!\left(\operatorname{Mod}\!\left(\widehat{n}\cdot \operatorname{diag}(\pi_{\mathrm{digits}}),1\right)\right)\right)
\]
\[
u=\frac{e^{t}}{1+e^{t}}\in[0,1]
\]

\paragraph{Primary Derivation.}
One can verify the equality through direct evaluation of the expression. giving the formula in the first line.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. From the TRAWIN perspective, the equation functions as the generalized carrier for the entry’s information content. Under CHL, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors LOGIT-SPHERICAL COORDINATE TRANSFORM by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
mathcal{E}_{\mathrm{enc}}(M)=\operatorname{CantorPair}\!\left(\operatorname{Logit}\!\left(\operatorname{Mod}\!\left(\widehat{n}\cdot \operatorname{diag}(\pi_{\mathrm{digits}}),1\right)\right)\right)
\]
\[
u=\frac{e^{t}}{1+e^{t}}\in[0,1]
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0971] LOGIT-SPHERICAL COORDINATE TRANSFORM}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
LOGIT-SPHERICAL COORDINATE TRANSFORM is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} mathcal E encoder (M) = text CantorPair [text Logit [text Mod [hat n * text diag (pi digits ), 1]]]. \textbf{Contextual meaning:} The entry reads LOGIT-SPHERICAL COORDINATE TRANSFORM as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states a real encoder and logit-lift chain instead of replacement-character corruption. \textbf{Lemma support:} Encoder Map; Logit Lift; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, LOGIT-SPHERICAL COORDINATE TRANSFORM is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: mathcal E sub enc (M)=operatorname CantorPair (operatorname Logit (operatorname Mod (hat n dot operatorname diag (pi sub digits ),1))); u=ratio e to the power t 1+e to the power t in[0,1]; and mathcal A sub adm ( E sub enc (M))=1. Proof route: show that the encoder map and bounded logit lift define an admissible transform. Formalization route: prove that the stated spherical logit transform closes under TRAWIN admissibility.

\tzpsection{Interpretive Role}
The entry now states a real encoder and logit-lift chain instead of replacement-character corruption.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Probability-to-Geometry Warping}: The insane math trick of taking the percentage chance of a meltdown and plotting it as a physical, 3D point on the surface of a glowing sphere.
\item \textbf{Infinite-Plane Wrapping}: The dizzying calculation required to take a flat, never-ending sheet of abstract numbers and perfectly stretch it around a round, finite object.
\item \textbf{Boundary-Condition Squashing}: The ruthless algorithm that takes numbers spiraling out toward infinity and forcefully crushes them back down so they fit neatly between zero and one.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0971]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0971].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0971] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont LOGIT-SPHERICAL COORDINATE TRANSFORM}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} LOGIT-SPHERICAL COORDINATE TRANSFORM is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``LOGIT-SPHERICAL COORDINATE TRANSFORM is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0971].
\par\endgroup
\vfill
\endgroup
\endgroup
