\section*{ID9200: Definition of t)Ψ(r,t)}
\paragraph{Metadata.}
PiID: 6922210327488 | RTEID: RTE:P35725.6431:T2.3162 | UUID: 4e4e5ba3-af04-52cd-ad9f-3fbe46b739de

\paragraph{Canonical Statement.}
to infinite propagation speed prior to decoherence. Falsifiability / Test Handle: Empirical evidence of fundamental finite speed or time at the earliest universe contradicting this hyperspherical model would falsify this definition. 2.0.29 ID 178: Local Disharmony and Bessel Mode Emergence Type: Definition Formal Statement: A local deviation from global phase coherence generates an interference wave described by \$Ψ(r,t)=Ψ0+εj0(kr)cos(ωt)\textbackslash{}Psi(r,t)\$ = \textbackslash{}Psi\_0 + \textbackslash{}varepsilon, j\_0(k r) \textbackslash{}cos(\textbackslash{}omega \$t)Ψ(r,t)=Ψ0+εj0(kr)cos(ωt),\$ where j0j\_0j0 is the spherical Bessel function of order zero; the first node at \$kr≈2.405k\$ r \textbackslash{}approx \$2.405kr≈2.405\$ defines the characteristic radius of a TZP emergence. Interpretive Meaning: When the vacuum field slips out of phase locally, it produces a standing wave pocket with Bessel profile, creating a fold that traps energy and seeds particle formation. Dependencies: ID 177 Derivable Co

\paragraph{Canonical Equation.}
\[
t)Ψ(r,t)=Ψ0+εj0(kr)cos(ωt),
\]

\paragraph{Dictionary.}
Definition of t)Ψ(r,t) — t)Ψ(r,t)=Ψ0+εj0(kr)cos(ωt)

\paragraph{Encyclopedia.}
Definition of t)Ψ(r,t) is an algebraic definition, written t)Ψ(r,t)=Ψ0+εj0(kr)cos(ωt). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from j, k, r, c, o, s, defining t)Ψ(r,t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
