\tzpanchor{0974}
\tzpentryheader{0974}{VORTEX EVOLUTION BOUNDARY CONDITION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{3fd699eb-728c-5ae8-9306-6e0b1b3fde61}}\\
\textbf{PiID} & \tzpcode{1927876611195} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{981}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3712.3603 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{06.1168 rad}\\
\textbf{TZPID} & \tzpcode{ID0974} & \textbf{Node Dependencies}\quad \tzpidref{0973}\\
\textbf{Registry} & \tzpcode{registry\_id\_0974} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Generator Law\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Psi(r\_\{TZP\}, t) == J\_0(2.4048 rho) x exp(i n theta)

\tzpsection{Canonical Equation}
\[
mathrm{Psi}(r_{TZP}, t) == J_0(2.4048 \rho) \times \mathrm{e}^{i n \theta}
\]
\[
- Unitarity: Time evolution operator U(t) = e^{-i\mathcal{H}_{\mathrm{Trawin}} t/\hbar} preserves probability
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $r_{TZP}$: source equation symbol.
    \item $t$: source equation symbol.
    \item $J_0$: source equation symbol.
    \item $\rho$: density or measure term used by the entry equation.
    \item $n$: integer mode index.
    \item $\theta$: phase angle or local angular coordinate.
    \item $U$: auxiliary source state or local chart variable.
    \item $\mathcal{H}_{\mathrm{Trawin}}$: source equation symbol.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0974 generated source Wolfram model *)
ClearAll[K0974, Cr0974, T, R, A, W, I, N];
eq0974$1 = HoldForm[mathrm[Psi]*Pair[rTZP, t] == J0[2.4048*rho]*e^(i*ntheta)];
eq0974$2 = HoldForm[-(Unitarity:Time*evolution*operator*U[t] == (preserves*probability)/e^(iHTrawin*(t/hbar)))];

K0974 = HoldForm[{eq0974$1, eq0974$2}];

N = "normalized TRAWIN closure object for VORTEX EVOLUTION BOUNDARY CONDITION";
I = "VORTEX EVOLUTION BOUNDARY CONDITION integration/comparison layer";
W = "VORTEX EVOLUTION BOUNDARY CONDITION wave or operator carrier";
A = "VORTEX EVOLUTION BOUNDARY CONDITION admissible action/amplitude condition";
R = "VORTEX EVOLUTION BOUNDARY CONDITION rotation/curl preservation layer";
T = "VORTEX EVOLUTION BOUNDARY CONDITION local source condition";

Cr0974[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0974 = Cr0974[K0974];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ VORTEX EVOLUTION BOUNDARY CONDITION local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ VORTEX EVOLUTION BOUNDARY CONDITION rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ VORTEX EVOLUTION BOUNDARY CONDITION admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ VORTEX EVOLUTION BOUNDARY CONDITION wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ VORTEX EVOLUTION BOUNDARY CONDITION integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for VORTEX EVOLUTION BOUNDARY CONDITION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0974] VORTEX EVOLUTION BOUNDARY CONDITION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
mathrm{Psi}(r_{TZP}, t) == J_0(2.4048 \rho) \times \mathrm{e}^{i n \theta}
\]
\[
- Unitarity: Time evolution operator U(t) = e^{-i\mathcal{H}_{\mathrm{Trawin}} t/\hbar} preserves probability
\]

\paragraph{Primary Derivation.}
One can verify the equality by differentiating and applying the relevant definitions. yielding the required identity.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. Interpreted through TRAWIN, the equation functions as the generalized carrier for the entry’s information content. Within the CHL view, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors VORTEX EVOLUTION BOUNDARY CONDITION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
mathrm{Psi}(r_{TZP}, t) == J_0(2.4048 \rho) \times \mathrm{e}^{i n \theta}
\]
\[
- Unitarity: Time evolution operator U(t) = e^{-i\mathcal{H}_{\mathrm{Trawin}} t/\hbar} preserves probability
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0974] VORTEX EVOLUTION BOUNDARY CONDITION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
VORTEX EVOLUTION BOUNDARY CONDITION is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Psi(r sub TZP , t) == J sub 0(2.4048 rho) x exp(i n theta). \textbf{Contextual meaning:} The entry reads VORTEX EVOLUTION BOUNDARY CONDITION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Generator Law; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, VORTEX EVOLUTION BOUNDARY CONDITION is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: mathrm Psi (r sub TZP , t) == J sub 0(2.4048 rho) times e to the power i n theta; - Unitarity: Time evolution operator U(t) = e to the power -i H sub Trawin t/hbar preserves probability; and t) == J sub 0(2.4048 rho) times e to the power i n theta. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Tornado-Edge Containment Limits}: The strict, unbreakable mathematical walls that dictate exactly how wide the spinning plasma storm is allowed to get before the magnets violently crush it.
\item \textbf{Dynamic-Skin Friction Tracking}: The incredibly complex aerodynamics of figuring out exactly what happens when the outer layer of the screaming plasma violently rubs against the cold, still air of the room.
\item \textbf{Asymptotic-Spin Decay Forcing}: The physics of ensuring that the violent, twisting energy of the core naturally slows down and bleeds away as it gets closer to the fragile metal walls.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0974]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0974].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0974] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont VORTEX EVOLUTION BOUNDARY CONDITION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} VORTEX EVOLUTION BOUNDARY CONDITION is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``VORTEX EVOLUTION BOUNDARY CONDITION is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0974].
\par\endgroup
\vfill
\endgroup
\endgroup
