\section*{ID9333: Definition of Γ̂topo |𝜓⟩}
\paragraph{Metadata.}
PiID: 2220888321513 | RTEID: RTE:P36242.1116:T3.1672 | UUID: f67c7171-9afb-5f2f-8cab-5b8a479d8403

\paragraph{Canonical Statement.}
tificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0106], [ID 0102] Node registry\_id\_0107 Support Titles Area Contribution; Protected Constant; Entropy Operator Test Handle If local circuit changes can alter the protected entropy eigenvalue without a topological transition, this operator fails. Canonical Equation Links 𝑆 (𝐴)=𝛼 |𝜕𝐴|−𝛾topo 𝛾topo>0 \$Γ̂topo |𝜓⟩=𝛾topo |𝜓⟩\$ [ID 0108] Relative-Entropy Constraint TZPID ID0108 UUID b903f02c-2ecb-57c1-a995-6784922c2ed8 Type Constraint Scale information divergence control LOC Classification Working routing: QA274 information theory; QC174.45 state distinguishability arXiv Classification Primary: quant-ph Cross-list: cs.IT, math-ph Canonical Statement Relative entropy is the control term that prevents synchronized states

\paragraph{Canonical Equation.}
\[
Γ̂topo |𝜓⟩=𝛾topo |𝜓⟩
\]

\paragraph{Dictionary.}
Definition of Γ̂topo |𝜓⟩ — Γ̂topo |𝜓⟩=𝛾topo |𝜓⟩

\paragraph{Encyclopedia.}
Definition of Γ̂topo |𝜓⟩ is an algebraic definition, written Γ̂topo |𝜓⟩=𝛾topo |𝜓⟩. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from o, p, defining Γ̂topo |𝜓⟩. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
