\section*{ID8758: Branch They Belong To. the Necessity of DAANSsphere: S DAANS}
\paragraph{Metadata.}
PiID: 8024901141952 | RTEID: RTE:P34009.2590:T5.7713 | UUID: abf42723-e6bd-58de-8d5f-c494cb7f348d

\paragraph{Canonical Statement.}
branch they belong to. The necessity of DAANSsphere becomes even clearer if we consider dynamic situations or multiple TZP systems. If two monopole loops exist, their fields could entangle in space, but each field line still has a branch identity with respect to its TZP. The coordinate system could be extended to label multiple TZPs, but that’s beyond our scope here. We focus on one TZP and its two branches. One way to formalize DAANSsphere is to say it’s the disjoint union of two spheres: \$\textbackslash{}mathcal\{S\} \{DAANS\} = S\textasciicircum{}2 \{(+)\} \textbackslash{}sqcup S\textasciicircum{}2\_\{(-)\}\$ . A point on \$\textbackslash{}mathcal\{S\} \{DAANS\}\$ is \$(\textbackslash{}hat\{n\},\textbackslash{}Upsilon)\$ where \$\textbackslash{}hat\{n\}\$ is a unit direction vector in \$ℝ\textasciicircum{}3\$ (point on \$S\textasciicircum{}2\$ ) and \$\textbackslash{}Upsilon\textbackslash{}in\{+,-\}\$ . We can also embed this into a single mathematical object by introducing a function like \$\textbackslash{}sigma = \textbackslash{}pm 1\$ and consider \$(\textbackslash{}sigma \textbackslash{}hat\{n\})\$ in an augmented space. However, since we likely want to do calculus on this, we can think in t

\paragraph{Canonical Equation.}
\[
\mathcal{S} {DAANS} = S^2 {(+)} \sqcup S^2_{(-)}
\]

\paragraph{Dictionary.}
Branch They Belong To. the Necessity of DAANSsphere: S DAANS — S DAANS = S\textasciicircum{}2 (+) sqcup S\textasciicircum{}2\_(-)

\paragraph{Encyclopedia.}
Branch They Belong To. the Necessity of DAANSsphere: S DAANS is an algebraic definition, written S DAANS = S\textasciicircum{}2 (+) sqcup S\textasciicircum{}2\_(-). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from S, defining S DAANS. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
