\section*{ID8490: BESSEL-HELIX COUPLING Canonical Statutory Formula: Ψ\_stand}
\paragraph{Metadata.}
PiID: 5223970968340 | RTEID: RTE:P32968.5554:T4.0566 | UUID: 2a3e4959-20b9-5089-a8ff-8cb85d3dfc0e

\paragraph{Canonical Statement.}
[ID 1182] BESSEL-HELIX COUPLING Canonical Statutory Formula: \$\textbackslash{}Psi\_\{stand\} = J\_n(kr) e\textasciicircum{}\{i(m\textbackslash{}phi - \textbackslash{}omega t + kz)\} \textbackslash{}otimes |S\_\{seq\}\textbackslash{}rangle\$ Formal Technical Dissertation: The standing wave solution for the metamaterial core. It describes the specific eigenstate formed by the interaction of the helical wavefunction (carrying the sequence state \$|S\_\{seq\}\textbackslash{}rangle\$) and the radial Bessel functions of the electromagnetic vortex. Source: [2]

\paragraph{Canonical Equation.}
\[
\Psi_{stand} = J_n(kr) e^{i(m\phi - \omega t + kz)} \otimes |S_{seq}\rangle
\]

\paragraph{Dictionary.}
BESSEL-HELIX COUPLING Canonical Statutory Formula: \$ \_stand = J\_n(kr) e\textasciicircum{}i(m - t + kz) S\_seq \$ Formal Technical Dissertation: The standing wave solution for the metamaterial core.

\paragraph{Encyclopedia.}
BESSEL-HELIX COUPLING Canonical Statutory Formula: Ψ\_stand is an algebraic definition, written Ψ\_stand = J\_n(kr) e\textasciicircum{}i(mφ - ω t + kz) ⊗ |S\_seq⟩. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from φ, ω, J\_n, k, r, m, defining Ψ\_stand. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
