\tzpanchor{0127}
\tzpentryheader{0127}{Multi-Domain Resonance Cascade}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{019aa313-fc31-5778-b707-95d6fa4014e3}}\\
\textbf{PiID} & \tzpcode{0955058223172} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{134}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{493.1692 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.8126 rad}\\
\textbf{TZPID} & \tzpcode{ID0127} & \textbf{Node Dependencies}\quad \tzpidref{0126}\\
\textbf{Registry} & \tzpcode{registry\_id\_0127} & \textbf{Scale}\quad mechanical-electrical-optical coupling\\
\textbf{LOC Classification} & QA371 resonance systems & QC670 nonlinear optics\\
\textbf{arXiv Classification} & Primary: physics.class-ph \quad Cross-list: physics.optics, nlin.PS & \\
\textbf{Primary Support} & Cascade Matching Rule & Beat Gap\\
\textbf{Closure Support} & Electrical Closure of the Gap & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
If the prism oscillation frequency $\omega_p$, the charge oscillation frequency $\omega_e$, and the natural vortex frequency $\omega_v$ satisfy

\tzpsection{Canonical Equation}
\[ \omega_p \pm \omega_e = \omega_v, \] then a parametric resonance arises across mechanical, electrical, and optical domains. Energy is transferred coherently among vortex motion, electric charge oscillation, and light modulation.

\[
\omega_p \pm \omega_e = \omega_v
\]
\[
\Delta \omega = |\omega_v - \omega_p|
\]
\[
\Delta \omega = \omega_e
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\omega_p$: angular frequency term in the source equation.
    \item $\omega_e$: angular frequency term in the source equation.
    \item $\omega_v$: angular frequency term in the source equation.
    \item $\omega$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0127 generated source Wolfram model *)
ClearAll[K0127, Cr0127, T, R, A, W, I, N];
eq0127$1 = HoldForm[omegaP*PlusMinus*omegaE == omegaV];
eq0127$2 = HoldForm[omegaP*PlusMinus*omegaE == omegaV];
eq0127$3 = HoldForm[Delta*omega == Abs[omegaV - omegaP]];
eq0127$4 = HoldForm[Delta*omega == omegaE];

K0127 = HoldForm[{eq0127$1, eq0127$2, eq0127$3, eq0127$4}];

N = "normalized TRAWIN closure object for Multi-Domain Resonance Cascade";
I = "Electrical Closure of the Gap integration/comparison layer";
W = "Beat Gap wave or operator carrier";
A = "Cascade Matching Rule admissible action/amplitude condition";
R = "Beat Gap rotation/curl preservation layer";
T = "Cascade Matching Rule local source condition";

Cr0127[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0127 = Cr0127[K0127];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Cascade Matching Rule local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Beat Gap rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Cascade Matching Rule admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Beat Gap wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Electrical Closure of the Gap integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Multi-Domain Resonance Cascade.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0127] Multi-Domain Resonance Cascade}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[ \omega_p \pm \omega_e = \omega_v, \] then a parametric resonance arises across mechanical, electrical, and optical domains. Energy is transferred coherently among vortex motion, electric charge oscillation, and light modulation.

\[
\omega_p \pm \omega_e = \omega_v
\]
\[
\Delta \omega = |\omega_v - \omega_p|
\]
\[
\Delta \omega = \omega_e
\]

\paragraph{Primary Derivation.}
To derive the stated relation by differentiating and applying the relevant definitions. leading to the displayed result.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. From the TRAWIN perspective, the equation functions as the generalized carrier for the entry’s information content. Within the CHL view, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Multi-Domain Resonance Cascade by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Cascade Matching Rule}\par
\[
\omega_p \pm \omega_e = \omega_v
\]
\noindent This gives the core resonance condition across prism, charge, and vortex sectors.\par
\noindent\textbf{2. Beat Gap}\par
\[
\Delta \omega = |\omega_v - \omega_p|
\]
\noindent This defines the residual spectral distance that must be bridged.\par
\noindent\textbf{3. Electrical Closure of the Gap}\par
\[
\Delta \omega = \omega_e
\]
\noindent This closes the progression by identifying the charge oscillation as the frequency that completes the match.\par

\clearpage
\noindent\textbf{[ID 0127] Multi-Domain Resonance Cascade}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Multi-Domain Resonance Cascade is a Operator. If the prism oscillation frequency  \_p, the charge oscillation frequency  \_e and the natural vortex frequency  \_v satisfy  \_p +/-  \_e =  \_v, a parametric resonance arises across mechanical, electrical and optical domains.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} If the prism oscillation frequency  \_p, the charge oscillation frequency  \_e and the natural vortex frequency  \_v satisfy  \_p +/-  \_e =  \_v, a parametric resonance arises across mechanical, electrical and optical domains.
\textbf{Contextual meaning:} By tuning these frequencies to satisfy the relation, one can create a self amplifying feedback loop that couples mechanics, electromagnetism and optics.
\textbf{Derivable consequences:} Resonant enhancement of vortex and current; electrokinetic streaming; design of electrohydrodynamic thrusters.
\textbf{Lemma support:} If the prism oscillation frequency  \_p, the charge oscillation frequency  \_e and the natural vortex frequency  \_v satisfy  \_p +/-  \_e =  \_v, a parametric resonance arises across mechanical, electrical and optical domains.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Apply an oscillating charge to a vortex and measure acceleration amplification; confirm the resonance enhancement factor. ID 127: Multi Domain Resonance Cascade

\tzpsection{Equation Grounding}
If the prism oscillation frequency  \_p, the charge oscillation frequency  \_e and the natural vortex frequency  \_v satisfy  \_p +/-  \_e =  \_v, a parametric resonance arises across mechanical, electrical and optical domains.

\tzpsection{Interpretive Role}
By tuning these frequencies to satisfy the relation, one can create a self amplifying feedback loop that couples mechanics, electromagnetism and optics.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Cascade Matching Rule}: The core resonance condition across prism, charge, and vortex sectors.
\item \textbf{Beat Gap}: The definition of the residual spectral distance that must be bridged.
\item \textbf{Electrical Closure of the Gap}: The identification of the charge oscillation as the frequency that completes the match.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0127]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0127_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0127] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Multi-Domain Resonance Cascade}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} if the prism oscillation frequency \_p, the charge oscillation frequency \_e, and the
natural vortex frequency \_v satisfy \textbackslash{}[ \_p \_e = \_v, \textbackslash{}] the...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Multi-Domain Resonance Cascade is valid as a spectral relation when frequency, phase,
and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0127_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
