\section*{ID9482: Definition of (L)+Λ}
\paragraph{Metadata.}
PiID: 4247014121478 | RTEID: RTE:P36820.7117:T4.1205 | UUID: e18dfab3-825b-57ab-bdf3-a45bc1a0118a

\paragraph{Canonical Statement.}
e Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0277], [ID 0200] Node registry\_id\_0278 Support Titles Variation Law; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links \$Ggyro⊕Ggrav→U\$ 𝑇2 𝜏 \$(L)+Λ=const.\$ on 𝑇2 𝜔2=𝑘2𝑣2 A [ 1+( 𝜔gyro 𝜔 )2] [ID 0279] Magneto-Topological Confinement and Higher-Categorical Dynamics TZPID ID0279 UUID 1cf3557f-e573-5840-8990-63faaa8262cd Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry deve

\paragraph{Canonical Equation.}
\[
(L)+Λ=const.
\]

\paragraph{Dictionary.}
Definition of (L)+Λ — (L)+Λ=const.

\paragraph{Encyclopedia.}
Definition of (L)+Λ is an algebraic definition, written (L)+Λ=const.. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from c, o, n, s, defining (L)+Λ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
