\tzpanchor{0622}
\tzpentryheader{0622}{TZP ACTIVATION DYNAMICS}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{b7348581-e575-5124-9f9c-bafdbd330be5}}\\
\textbf{PiID} & \tzpcode{8577134275778} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{629}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2392.0648 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.9414 rad}\\
\textbf{TZPID} & \tzpcode{ID0622} & \textbf{Node Dependencies}\quad \tzpidref{0621}\\
\textbf{Registry} & \tzpcode{registry\_id\_0622} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records tzp activation dynamics through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\lim_{x\to p}R_T(x)=\infty.
\]
\[
R_T(x)=R(x)+f(x).
\]
\[
\lim_{x\to p}R_T(x)<\infty.
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $R_T(x)$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $T(x)$: source equation symbol.
    \item $f(x)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0622 generated source Wolfram model *)
ClearAll[K0622, Cr0622, T, R, A, W, I, N];
eq0622$1 = HoldForm[LimitXpRT[x] == Infinity];
eq0622$2 = HoldForm[RT[x] == R[x] + f[x]];
eq0622$3 = HoldForm[LimitXpRT[x] < Infinity];

K0622 = HoldForm[{eq0622$1, eq0622$2, eq0622$3}];

N = "normalized TRAWIN closure object for TZP ACTIVATION DYNAMICS";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0622[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0622 = Cr0622[K0622];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP ACTIVATION DYNAMICS.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0622] TZP ACTIVATION DYNAMICS}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\lim_{x\to p}R_T(x)=\infty .
\end{equation}

\paragraph{Primary Derivation.}
From ID 0016, the regularized Trawin curvature is:

\begin{equation}
R_T(x)=R(x)+f(x).
\end{equation}

A regular TZP curvature condition occurs when:

\begin{equation}
\lim_{x\to p}R_T(x)<\infty .
\end{equation}

A curvature singularity occurs when this limiting value fails to remain finite. Therefore the singular condition is:

\begin{equation}
\boxed{
\lim_{x\to p}R_T(x)=\infty .
}
\end{equation}

\paragraph{Interpretation.}
ID 0022 defines the failure condition of the regulator: the TZP becomes a true curvature singularity when $R_T$ diverges.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP ACTIVATION DYNAMICS by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
\lim_{x\to p}R_T(x)=\infty.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
R_T(x)=R(x)+f(x).
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\lim_{x\to p}R_T(x)<\infty.
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0622] TZP ACTIVATION DYNAMICS}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP ACTIVATION DYNAMICS is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} D(TZP) := lim sub t -> 0 frac nabla Phi(x,t) partial Omega sub T(x,t). \textbf{Contextual meaning:} The entry reads TZP ACTIVATION DYNAMICS as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
ID 0022 defines the failure condition of the regulator: the TZP becomes a true curvature singularity when R sub T diverges.

\tzpsection{Equation Grounding}
Equation anchors: D(TZP) := lim sub t to 0 ratio abla Phi(x,t) partial Omega sub T (x,t); mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Singularity-Core Ignition Sequencing}: The incredibly dangerous, perfectly timed series of high-energy laser pulses designed to physically crack open the tiny, microscopic hole in the center of the reactor.
\item \textbf{Runaway Energy Cascading}: The terrifying, split-second moment where the machine stops consuming power and suddenly, violently begins producing a theoretically infinite amount of its own energy.
\item \textbf{Topological-Puncture Stabilization}: The desperate, frantic attempt by the control computers to immediately build a magnetic cage around the newly formed singularity before it can expand and eat the laboratory.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0622]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0622_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0622] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP ACTIVATION DYNAMICS}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records tzp activation dynamics through the Septenary derivation layer, using
the displayed relations as operational anchors for the cano...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP ACTIVATION DYNAMICS is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0622_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
