\tzpanchor{0062}
\tzpentryheader{0062}{Quantum Noise Spectra}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{86a57d30-95ec-57cb-a5d0-58b9182663d1}}\\
\textbf{PiID} & \tzpcode{2307816406286} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{69}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{240.7598 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.3967 rad}\\
\textbf{TZPID} & \tzpcode{ID0062} & \textbf{Node Dependencies}\quad \tzpidref{0049}\\
\textbf{Registry} & \tzpcode{registry\_id\_0062} & \textbf{Scale}\quad frequency-domain noise\\
\textbf{LOC Classification} & QC174 noise spectra & QA403 Fourier analysis\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: physics.data-an, hep-th & \\
\textbf{Primary Support} & Observable Fluctuation & Two-Point Correlation Transform\\
\textbf{Closure Support} & Spectrally Weighted Noise & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This defines how noise power is distributed across frequencies; curvature and the zero point modify the usual spectra.

\tzpsection{Canonical Equation}
\[
S_{O}(\omega)
=
\int d\tau\;
e^{i\omega\tau}
\langle \delta O(t)\,\delta O(t+\tau)\rangle
\]
\[
S_{O}^{(\eta)}(\omega) = S_{O}(\omega)\,\eta(\omega)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S_{O}$: source equation symbol.
    \item $O$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
    \item $\tau$: source equation symbol.
    \item $\delta$: point-source delta term that anchors the Green-function response.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0062 generated source Wolfram model *)
ClearAll[K0062, Cr0062, T, R, A, W, I, N];
eq0062$1 = HoldForm[SO[omega] == Integral*dtau*Exp[I*omegatau]*Inner[DiracDelta*O[t]*DiracDelta*O[t + tau]]];
eq0062$2 = HoldForm[SO^eta*omega == SO[omega]*eta[omega]];
eq0062$3 = HoldForm[DiracDelta*O[t]];

K0062 = HoldForm[{eq0062$1, eq0062$2, eq0062$3}];

N = "normalized TRAWIN closure object for Quantum Noise Spectra";
I = "Spectrally Weighted Noise integration/comparison layer";
W = "Two-Point Correlation Transform wave or operator carrier";
A = "Observable Fluctuation admissible action/amplitude condition";
R = "Two-Point Correlation Transform rotation/curl preservation layer";
T = "Observable Fluctuation local source condition";

Cr0062[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0062 = Cr0062[K0062];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Observable Fluctuation local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Two-Point Correlation Transform rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Observable Fluctuation admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Two-Point Correlation Transform wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Spectrally Weighted Noise integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum Noise Spectra.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0062] Quantum Noise Spectra}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{d\rho}{dt} = -\frac{i}{\hbar}[H,\rho].
\end{equation}

\paragraph{Primary Derivation.}
From Schrödinger evolution:
\begin{equation}
i\hbar \frac{d}{dt}|\psi\rangle = H|\psi\rangle.
\end{equation}

Construct density matrix $\rho = |\psi\rangle\langle \psi|$ and differentiate:
\begin{equation}
\frac{d\rho}{dt} = -\frac{i}{\hbar}[H,\rho].
\end{equation}

\paragraph{Interpretation.}
Closed-system evolution is unitary.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum Noise Spectra by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Observable Fluctuation}\par
\[
\delta O(t)
\]
\noindent This isolates the noisy part of the measured observable.\par
\noindent\textbf{2. Two-Point Correlation Transform}\par
\[
S_{O}(\omega)
=
\int d\tau\;
e^{i\omega\tau}
\langle \delta O(t)\,\delta O(t+\tau)\rangle
\]
\noindent This turns time-domain fluctuations into a spectral diagnostic.\par
\noindent\textbf{3. Spectrally Weighted Noise}\par
\[
S_{O}^{(\eta)}(\omega) = S_{O}(\omega)\,\eta(\omega)
\]
\noindent This closes the progression by inserting the TRAWIN spectral weighting into the observable noise law.\par

\clearpage
\noindent\textbf{[ID 0062] Quantum Noise Spectra}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum Noise Spectra is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This defines how noise power is distributed across frequencies; curvature and the zero point modify the usual spectra. \textbf{Contextual meaning:} The entry reads Quantum Noise Spectra as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry gives a frequency-resolved language for decoherence and measurement disturbance. It also creates a natural bridge between vacuum spectral structure and observed quantum noise. \textbf{Lemma support:} Observable Fluctuation; Two-Point Correlation Transform; Spectrally Weighted Noise.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Closed-system evolution is unitary.

\tzpsection{Equation Grounding}
Equation anchors: The noise spectrum S(omega)S(omega)S(omega) for a quantum observable in the Trawinistic framework is defined as the Fourier transform of its two-point correlation function, with weighting by the spectral density index eta(omega)eta(omega)eta(omega): S(omega)=intdtau eiomegataudeltaO(t) deltaO(t+tau) eta(omega)S(omega)=integral d tautextbackslash,e to the power iomegatau delta O(t)textbackslash,delta O(t+tau) textbackslash,eta(omega)S(omega)=intdtaueiomegataudeltaO(t)deltaO(t+tau)eta(omega). The noise spectrum S(omega)S(omega)S(omega) for a quantum observable in the Trawinistic framework is defined as the Fourier transform of its two-point correlation function, with weighting by the spectral density index eta(omega)eta(omega)eta(omega): S(omega)=intdtau eiomegataudeltaO(t) deltaO(t+tau) eta(omega)S(omega)=integral d tautextbackslash,e to the power iomegatau delta O(t)textbackslash,delta O(t+tau) textbackslash,eta(omega)S(omega)=intdtaueiomegataudeltaO(t)deltaO(t+tau)eta(omega).

\tzpsection{Interpretive Role}
This entry gives a frequency-resolved language for decoherence and measurement disturbance. It also creates a natural bridge between vacuum spectral structure and observed quantum noise.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{State-Level Noise Spectra}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Quantum-State Analogue}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Terminology}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0062]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0062_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0062] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum Noise Spectra}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this defines how noise power is distributed across frequencies; curvature and the zero
point modify the usual spectra

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum Noise Spectra is valid as a formal dynamical law when the Hamiltonian or energy
operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0062_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
