\section*{ID9468: Definition of 𝜔𝑘 𝑆ij}
\paragraph{Metadata.}
PiID: 8471605049221 | RTEID: RTE:P36766.3466:T4.0310 | UUID: f3a4c193-9c95-51f6-bb1a-d1e846143928

\paragraph{Canonical Statement.}
Isabelle Certificate Lean Certificate Coq Certificate lemmaid0873\_vibration\_coordinate\_tensor:sorry theoremid0873\_vibration\_coordinate\_tensor Theoremid0873\_vibration\_coordinate\_tensor Dependencies and Test Handle Dependencies [ID 0872], [ID 0800] Node registry\_id\_0873 Support Titles Variation Law; Aggregate Relation; Transfer Map Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links = 𝜕2𝜓 𝜕𝑥𝑖𝜕𝑥 𝑗 \$⊗\$ 𝜔𝑘 𝑆ij = · · · |𝑎 | > 𝑎max \$→\$ 𝑖𝑠𝑜𝑙𝑎𝑡𝑖𝑜𝑛𝑒𝑛𝑔𝑎𝑔𝑒 [ID 0874] RECURSIVE SYMBOLIC CASCADE TZPID ID0874 UUID c5474e71-51f7-557a-863c-938049efcef4 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops recursive symbolic cascade inside the resonance

\paragraph{Canonical Equation.}
\[
𝜔𝑘 𝑆ij = · · · |𝑎 | > 𝑎max
\]

\paragraph{Dictionary.}
Definition of 𝜔𝑘 𝑆ij — 𝜔𝑘 𝑆ij = · · · |𝑎 | > 𝑎max

\paragraph{Encyclopedia.}
Definition of 𝜔𝑘 𝑆ij is an inequality / bound, written 𝜔𝑘 𝑆ij = · · · |𝑎 | > 𝑎max. It states an inequality or bound that constrains the admissible range of the quantity. It is built from m, a, x, defining 𝜔𝑘 𝑆ij. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
