\tzpanchor{0602}
\tzpentryheader{0602}{INFORMATION DENSITY TRACKING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{363cc7f0-2a15-53b1-8a12-dbad91329b8a}}\\
\textbf{PiID} & \tzpcode{0568127145263} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{609}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2314.4004 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.8134 rad}\\
\textbf{TZPID} & \tzpcode{ID0602} & \textbf{Node Dependencies}\quad \tzpidref{0601}\\
\textbf{Registry} & \tzpcode{registry\_id\_0602} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Scaling Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records information density tracking through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
H:S^1\times[0,1]\to M.
\]
\[
H(\theta,0)=\GammaLoop(\theta).
\]
\[
H(\theta,1)=\Lambda(\theta),
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H$: source equation symbol.
    \item $S$: source equation symbol.
    \item $M$: source equation symbol.
    \item $\theta$: phase angle or local angular coordinate.
    \item $\Lambda$: lemniscatic representative or canonical branch object.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0602 generated source Wolfram model *)
ClearAll[K0602, Cr0602, T, R, A, W, I, N];
eq0602$1 = HoldForm[H[S1times01] -> M];
eq0602$2 = HoldForm[H[theta, 0] == GammaLoop[theta]];
eq0602$3 = HoldForm[H[theta, 1] == Lambda[theta]];

K0602 = HoldForm[{eq0602$1, eq0602$2, eq0602$3}];

N = "normalized TRAWIN closure object for INFORMATION DENSITY TRACKING";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Scaling Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Scaling Law local source condition";

Cr0602[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0602 = Cr0602[K0602];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Scaling Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Scaling Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for INFORMATION DENSITY TRACKING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0602] INFORMATION DENSITY TRACKING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
For any closed loop $\GammaLoop$ encircling the TZP in $M$, there exists a homotopy deforming $\GammaLoop$ into a lemniscate whose self-intersection occurs at $p$.

\paragraph{Primary Derivation.}
Let $\GammaLoop:S^1\to M$ be a closed loop surrounding $p$. Since $p$ is the limiting degeneracy point, paths enclosing $p$ may be continuously deformed while preserving their winding relation to $p$.

Introduce a homotopy:

\begin{equation}
H:S^1\times[0,1]\to M .
\end{equation}

At $s=0$, the homotopy recovers the original loop:

\begin{equation}
H(\theta,0)=\GammaLoop(\theta).
\end{equation}

At $s=1$, the loop is deformed into a figure-eight curve:

\begin{equation}
H(\theta,1)=\Lambda(\theta),
\end{equation}

where $\Lambda$ is a lemniscatic curve satisfying:

\begin{equation}
\Lambda(\theta_1)=\Lambda(\theta_2)=p,
\qquad
\theta_1\neq\theta_2 .
\end{equation}

Thus the self-intersection of the limiting loop is identified with the TZP.

\paragraph{Interpretation.}
The lemniscate is the canonical shape of TZP recurrence: two lobes, one crossing, one central point. This turns the zero point into a geometric crossing rather than a simple endpoint.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors INFORMATION DENSITY TRACKING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Scaling Law}\par
\[
H:S^1\times[0,1]\to M.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
H(\theta,0)=\GammaLoop(\theta).
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
H(\theta,1)=\Lambda(\theta),
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0602] INFORMATION DENSITY TRACKING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
INFORMATION DENSITY TRACKING is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} I sub density = log sub 2(153,600) approximately 17.23 text bits/transition. \textbf{Contextual meaning:} The entry reads INFORMATION DENSITY TRACKING as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Scaling Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The lemniscate is the canonical shape of TZP recurrence: two lobes, one crossing, one central point. This turns the zero point into a geometric crossing rather than a simple endpoint.

\tzpsection{Equation Grounding}
Equation anchors: I sub density = log sub 2(153,600) approximately 17.23 bits/transition; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Shannon Entropy Volumetric Limits}: The calculation defining the absolute theoretical maximum number of distinct data bits that can be packed into a specific 3D spatial region.
\item \textbf{Logarithmic State Space Expansion}: The realization that adding more interconnected nodes to the system increases its total possible memory capacity exponentially, not linearly.
\item \textbf{Phase-Space Information Saturation}: The exact threshold where every single possible quantum state in the designated volume is currently being used to store active data.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0602]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0602_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0602] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont INFORMATION DENSITY TRACKING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records information density tracking through the Septenary derivation layer,
using the displayed relations as operational anchors for the...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``INFORMATION DENSITY TRACKING is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0602_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
