\tzpanchor{0362}
\tzpentryheader{0362}{Scale Invariance on the DAANSsphere}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{96d74cb0-d52b-559c-8db0-d13c1cd135ad}}\\
\textbf{PiID} & \tzpcode{1330530548820} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{369}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1405.7264 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.3162 rad}\\
\textbf{TZPID} & \tzpcode{ID0362} & \textbf{Node Dependencies}\quad \tzpidref{0361}\\
\textbf{Registry} & \tzpcode{registry\_id\_0362} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The recursive toroidal model exhibits no privileged scale: structures of different sizes correspond to distinct depth encodings of the same torus. Hierarchical refinement tiers (600, 2 400, 9 600, 38 400, 153 600) represent increasing sampling density rather than changes in topology.

\tzpsection{Canonical Equation}
\[
\mathbb{S}_{\mathrm{DAAN}}(\lambda r)\cong\mathbb{S}_{\mathrm{DAAN}}(r)
\]
\[
\mathcal{F}(\lambda x)=\lambda^{\Delta}\mathcal{F}(x)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S$: source equation symbol.
    \item $\lambda$: cosmological or lemniscatic branch parameter in the entry relation.
    \item $\mathcal{F}$: source equation symbol.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $\cong$: source equation symbol.
    \item $\lambda^{\Delta}$: source equation symbol.
    \item $\chi$: source equation symbol.
    \item $D$: source equation symbol.
    \item $A$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0362 generated source Wolfram model *)
ClearAll[K0362, Cr0362, T, R, A, W, I, N];
eq0362$1 = HoldForm[SDAAN[lambda*r]*congSDAAN[r]];
eq0362$2 = HoldForm[F[lambda*x] == lambda^Delta*F[x]];
eq0362$3 = HoldForm[chi[SDAAN[lambda*r]] == chi[SDAAN[r]]];

K0362 = HoldForm[{eq0362$1, eq0362$2, eq0362$3}];

N = "normalized TRAWIN closure object for Scale Invariance on the DAANSsphere";
I = "Topological Closure integration/comparison layer";
W = "Compatibility Law wave or operator carrier";
A = "Geometric Carrier admissible action/amplitude condition";
R = "Compatibility Law rotation/curl preservation layer";
T = "Geometric Carrier local source condition";

Cr0362[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0362 = Cr0362[K0362];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Geometric Carrier local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Compatibility Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Geometric Carrier admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Compatibility Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Scale Invariance on the DAANSsphere.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0362] Scale Invariance on the DAANSsphere}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{d\rho}{dt} = -\frac{i}{\hbar}[H,\rho].
\end{equation}

\paragraph{Primary Derivation.}
From Schrödinger evolution:
\begin{equation}
i\hbar \frac{d}{dt}|\psi\rangle = H|\psi\rangle.
\end{equation}

Construct density matrix $\rho = |\psi\rangle\langle \psi|$ and differentiate:
\begin{equation}
\frac{d\rho}{dt} = -\frac{i}{\hbar}[H,\rho].
\end{equation}

\paragraph{Interpretation.}
Closed-system evolution is unitary.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Scale Invariance on the DAANSsphere by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Geometric Carrier}\par
\[
\mathbb{S}_{\mathrm{DAAN}}(\lambda r)\cong\mathbb{S}_{\mathrm{DAAN}}(r)
\]
\noindent This fixes the effective geometry or carrier space named by the entry title.\par
\noindent\textbf{2. Compatibility Law}\par
\[
\mathcal{F}(\lambda x)=\lambda^{\Delta}\mathcal{F}(x)
\]
\noindent This makes the geometry admissible by imposing its internal compatibility law.\par
\noindent\textbf{3. Topological Closure}\par
\[
\chi(\mathbb{S}_{\mathrm{DAAN}}(\lambda r))=\chi(\mathbb{S}_{\mathrm{DAAN}}(r))
\]
\noindent This closes the entry by tying the local structure to a global topological invariant.\par

\clearpage
\noindent\textbf{[ID 0362] Scale Invariance on the DAANSsphere}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Scale Invariance on the DAANSsphere is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The recursive toroidal model exhibits no privileged scale: structures of different sizes correspond to distinct depth encodings of the same torus. Hierarchical refinement tiers (600, 2 400, 9 600, 38 400, 153 600) represent increasing sampling density rather than changes in topology. \textbf{Contextual meaning:} The entry reads Scale Invariance on the DAANSsphere as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Geometric Carrier; Compatibility Law; Topological Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Closed-system evolution is unitary.

\tzpsection{Equation Grounding}
Equation anchors: com/nature-index/news/how-to-crowdfund-your-research-science-experiment-grant?utm sub source =chatgpt; c sub effective [r] = c sub 0 * Power[ 1 - (2*G*M sub TZP )/(r*c sub 0 to the power 2) - Exp[-r to the power 2/(2*u03c3 sub TZP to the power 2)] * WindingNumber[u03b8,u03c6], -1/2 ]; and (* Modified Maxwell propagation *) WaveEquation = (1/c sub effective [r] to the power 2) * D[E sub field , t,2 ] - Laplacian[E sub field , r,u03b8,u03c6 ] + Curl[Curl[E sub field ]] * Topologi. Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Conformal Fractional Mapping}: The geometric transformation proving that zooming in on the specialized spherical lattice yields the exact same connective structure.
\item \textbf{Topological Characteristic Preservation}: The rigorous mathematical demonstration that expanding the manifold does not alter its fundamental Euler or bundle invariants.
\item \textbf{Radius-Independent Angular Logic}: The property where the interaction rules between points rely entirely on relative angles, ignoring absolute physical distances.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0362]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0362_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0362] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Scale Invariance on the DAANSsphere}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the recursive toroidal model exhibits no privileged scale: structures of different sizes
correspond to distinct depth encodings of the same torus

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Scale Invariance on the DAANSsphere is valid when the stated geometric or topological
relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0362_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
