\section*{ID8822: GRAVITATIONAL TRAWIN HAMILTONIAN Canonical Statutory Formula: H Trawin\textasciicircum{}grav}
\paragraph{Metadata.}
PiID: 8545133312394 | RTEID: RTE:P34257.7852:T6.1808 | UUID: d57e323a-ccaf-5da8-952d-56f4f6799f5e

\paragraph{Canonical Statement.}
[ID 1153] GRAVITATIONAL TRAWIN HAMILTONIAN Canonical Statutory Formula: \$\textbackslash{}mathcal\{H\} \{Trawin\}\textasciicircum{}\{grav\} = \textbackslash{}mathcal\{H\} \{base\} - G \textbackslash{}sum \textbackslash{}frac\{M\_i m\_\{eff\}\}\{|r-r\_i|\} + \textbackslash{}mathcal\{H\} \{GR\} + \textbackslash{}mathcal\{H\} \{tidal\} + \textbackslash{}mathcal\{H\}\_\{frame\}\$ Formal Technical Dissertation: Expands the Master Hamiltonian to include explicit gravitational sectors: Newtonian potential, General Relativistic corrections (Weyl curvature), tidal tensor effects, and Lense-Thirring frame dragging. Source: [23]

\paragraph{Canonical Equation.}
\[
\mathcal{H} {Trawin}^{grav} = \mathcal{H} {base} - G \sum \frac{M_i m_{eff}}{|r-r_i|} + \mathcal{H} {GR} + \mathcal{H} {tidal} + \mathcal{H}_{frame}
\]

\paragraph{Dictionary.}
GRAVITATIONAL TRAWIN HAMILTONIAN Canonical Statutory Formula: \$H Trawin\textasciicircum{}grav = H base - G M\_i m\_eff r-r\_i + H GR + H tidal + H\_frame\$ Formal Technical Dissertation: Expands the Master Hamiltonian to include explicit gravitational sectors: Newtonian potential, General Relativistic corrections (Weyl c

\paragraph{Encyclopedia.}
GRAVITATIONAL TRAWIN HAMILTONIAN Canonical Statutory Formula: H Trawin\textasciicircum{}grav is a series / summation, written H Trawin\textasciicircum{}grav = H base - G ∑ fracM\_i m\_eff|r-r\_i| + H GR + H tidal + H\_frame. It is expressed as a sum or series over modes or indices, superposing discrete contributions. It is built from H, b, a, s, G, M\_i, defining H Trawin\textasciicircum{}grav. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
