\tzpanchor{0997}
\tzpentryheader{0997}{ENTANGLED OMEGA ENERGY}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f07e64b5-08a5-519d-aba0-627bbc4a4e48}}\\
\textbf{PiID} & \tzpcode{9893809525720} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{1004}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3797.7912 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{06.2576 rad}\\
\textbf{TZPID} & \tzpcode{ID0997} & \textbf{Node Dependencies}\quad \tzpidref{0996}\\
\textbf{Registry} & \tzpcode{registry\_id\_0997} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Virtual Dimension & Stored Energy\\
\textbf{Closure Support} & Rotational Sector & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
mathbb\{L\} \{X/Z\} = Omega\textasciicircum{}1 \{P/A\} otimes\_P B implies text\{VirtualDim\} = text\{Rank\}(mathbb\{L\})

\tzpsection{Canonical Equation}
\[
mathbb{L}_{X/Z}=\Omega^{1}_{P/A}\otimes_{\mathrm{P}} B \implies \operatorname{VirtualDim}=\operatorname{Rank}(\mathbb{L})
\]
\[
E=\frac{1}{2}I\omega^{2}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $X$: source variable, local coordinate, or input state in the entry relation.
    \item $Z$: source equation symbol.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $P$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $E$: source equation symbol.
    \item $I$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0997 generated source Wolfram model *)
ClearAll[K0997, Cr0997, T, R, A, W, I, N];
eq0997$1 = HoldForm[mathbb[L]*_*(X/Z) == Omega^1*_*(P/A)*TensorProductP*Bimplies*VirtualDim == Rank[L]];
eq0997$2 = HoldForm[E == (1/2)*Iomega^2];

K0997 = HoldForm[{eq0997$1, eq0997$2}];

N = "normalized TRAWIN closure object for ENTANGLED OMEGA ENERGY";
I = "ENTANGLED OMEGA ENERGY integration/comparison layer";
W = "ENTANGLED OMEGA ENERGY wave or operator carrier";
A = "ENTANGLED OMEGA ENERGY admissible action/amplitude condition";
R = "ENTANGLED OMEGA ENERGY rotation/curl preservation layer";
T = "ENTANGLED OMEGA ENERGY local source condition";

Cr0997[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0997 = Cr0997[K0997];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ ENTANGLED OMEGA ENERGY local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ ENTANGLED OMEGA ENERGY rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ ENTANGLED OMEGA ENERGY admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ ENTANGLED OMEGA ENERGY wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ ENTANGLED OMEGA ENERGY integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for ENTANGLED OMEGA ENERGY.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0997] ENTANGLED OMEGA ENERGY}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
mathbb{L}_{X/Z}=\Omega^{1}_{P/A}\otimes_{\mathrm{P}} B \implies \operatorname{VirtualDim}=\operatorname{Rank}(\mathbb{L})
\]
\[
E=\frac{1}{2}I\omega^{2}
\]

\paragraph{Primary Derivation.}
The relation is obtained using functional and analytic properties. giving the formula in the first line.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. In the TRAWIN reading, the equation functions as the generalized carrier for the entry’s information content. According to CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors ENTANGLED OMEGA ENERGY by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
mathbb{L}_{X/Z}=\Omega^{1}_{P/A}\otimes_{\mathrm{P}} B \implies \operatorname{VirtualDim}=\operatorname{Rank}(\mathbb{L})
\]
\[
E=\frac{1}{2}I\omega^{2}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0997] ENTANGLED OMEGA ENERGY}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
ENTANGLED OMEGA ENERGY is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} mathbb L X/Z = Omega to the power 1 P/A otimes sub P B implies text VirtualDim = text Rank (mathbb L ). \textbf{Contextual meaning:} The entry reads ENTANGLED OMEGA ENERGY as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states a clean virtual-dimension and rotational-energy chain instead of hybrid prose-source fragments. \textbf{Lemma support:} Virtual Dimension; Stored Energy; Rotational Sector.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, ENTANGLED OMEGA ENERGY is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: mathbb L sub X/Z =Omega to the power 1 sub P/A otimes sub P B implies operatorname VirtualDim =operatorname Rank (mathbb L ); E=ratio 1 2 Iomega to the power 2; and T=ratio 1 2 Iomega to the power 2. Proof route: show that the virtual-dimension carrier supports the stated rotational-energy sector. Formalization route: prove that the entangled carrier closes consistently with the stated stored-energy and kinetic relations.

\tzpsection{Interpretive Role}
The entry now states a clean virtual-dimension and rotational-energy chain instead of hybrid prose-source fragments.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spooky-Action Rotational Locking}: The mind-bending physics where spinning a magnet on one side of the room causes a completely disconnected magnet on the other side of the room to instantly start spinning.
\item \textbf{Non-Local Angular Momentum}: The terrifying realization that the violent, twisting energy of the reactor isn't actually stored in the plasma itself, but is spread out invisibly across the entire building.
\item \textbf{Quantum-Twist Teleportation}: The bizarre, impossible trick of hitting the brakes on a spinning atom, and having that spinning energy instantly reappear on a different atom a mile away.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0997]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0997].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0997] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont ENTANGLED OMEGA ENERGY}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} ENTANGLED OMEGA ENERGY is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ENTANGLED OMEGA ENERGY is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0997].
\par\endgroup
\vfill
\endgroup
\endgroup
