\tzpanchor{0478}
\tzpentryheader{0478}{Neural Tzp Signature Detection}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{3cbfb3e2-c642-5b08-952f-9eb180dca8ca}}\\
\textbf{PiID} & \tzpcode{2489122793818} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{485}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1840.6473 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.0328 rad}\\
\textbf{TZPID} & \tzpcode{ID0478} & \textbf{Node Dependencies}\quad \tzpidref{0477}\\
\textbf{Registry} & \tzpcode{registry\_id\_0478} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Frequency Relation & Aggregate Relation\\
\textbf{Closure Support} & Frequency Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 478 establishes real time cartography of the interface. Cross correlating SQUID flux tomography with EEG phase data identifies the moment of a successful handshake. This signature represents the manifest transition of information integration between the user and the manifold. Phase Tracking: Monitors the lock between the 17.2 kHz carrier and biological gamma rhythms. Coupling Audit: Ensures the integrated information Phi remains within safe absorption limits.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\beta_{\mathrm{helix}}=\oint_{\gamma}A
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\gamma$: source equation symbol.
    \item $A$: source equation symbol.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $\beta_{helix}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0478 generated source Wolfram model *)
ClearAll[K0478, Cr0478, T, R, A, W, I, N];
eq0478$1 = HoldForm[$betaHelix == ContourIntegralGammaA$];

K0478 = HoldForm[{eq0478$1}];

N = "normalized TRAWIN closure object for Neural Tzp Signature Detection";
I = "Neural Tzp Signature Detection integration/comparison layer";
W = "Neural Tzp Signature Detection wave or operator carrier";
A = "Neural Tzp Signature Detection admissible action/amplitude condition";
R = "Neural Tzp Signature Detection rotation/curl preservation layer";
T = "Neural Tzp Signature Detection local source condition";

Cr0478[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0478 = Cr0478[K0478];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Neural Tzp Signature Detection local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Neural Tzp Signature Detection rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Neural Tzp Signature Detection admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Neural Tzp Signature Detection wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Neural Tzp Signature Detection integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Neural Tzp Signature Detection.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0478] Neural Tzp Signature Detection}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\langle O(x)O(0)\rangle
\sim
|x|^{-2+\eta}.
\end{equation}

\paragraph{Exponent Dependence.}
\begin{equation}
\eta=\eta(d_{\mathrm{eff}},\mathrm{TZP}).
\end{equation}

\paragraph{Primary Derivation.}
At a quantum critical point, correlation length diverges and the system loses a preferred length scale.  
An observable $O(x)$ therefore has a scale-free two-point function:
\begin{equation}
\langle O(x)O(0)\rangle
\sim
|x|^{-\Delta}.
\end{equation}

With anomalous exponent $\Delta=2-\eta$, this becomes
\begin{equation}
\boxed{
\langle O(x)O(0)\rangle
\sim
|x|^{-2+\eta}.
}
\end{equation}

In the TRAWIN setting,
\begin{equation}
\eta=\eta(d_{\mathrm{eff}},\mathrm{TZP}).
\end{equation}

\paragraph{Interpretation.}
Quantum criticality is detected through power-law correlations whose exponents may depend on effective dimension and TZP deformation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Neural Tzp Signature Detection by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\beta_{\mathrm{helix}}=\oint_{\gamma}A
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0478] Neural Tzp Signature Detection}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Neural Tzp Signature Detection is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 478 establishes real time cartography of the interface. Cross correlating SQUID flux tomography with EEG phase data identifies the moment of a successful handshake. This signature represents the manifest transition of information integration between the user and the manifold. Phase Tracking: Monitors the lock between the 17.2 kHz carrier and biological gamma rhythms. Coupling Audit: Ensures the integrated information Phi remains within safe absorption limits.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\beta_{\mathrm{helix}}=\oint_{\gamma}A
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 478 establishes real time cartography of the interface. Cross correlating SQUID flux tomography with EEG phase data identifies the moment of a successful handshake. This signature represents the manifest transition of information integration between the user and the manifold. Phase Tracking: Monitors the lock between the 17.2 kHz carrier and biological gamma rhythms. Coupling Audit: Ensures the integrated information Phi remains within safe absorption limits.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Neural Tzp Signature Detection by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Neural Tzp Signature Detection; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0478]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0478].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0478] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Neural Tzp Signature Detection}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} Quantum criticality is detected through power-law correlations whose exponents may
depend on effective dimension and TZP deformation

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``NEURAL TZP SIGNATURE DETECTION is valid as a formal dynamical law when the Hamiltonian
or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0478].
\par\endgroup
\vfill
\endgroup
\endgroup
