\tzpanchor{0302}
\tzpentryheader{0302}{DAANSphere Factorization and Antipodal Pairs}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7b21b845-0fb8-5fcc-9f55-a3daf1efc5ca}}\\
\textbf{PiID} & \tzpcode{4587006606315} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{309}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1172.7331 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9323 rad}\\
\textbf{TZPID} & \tzpcode{ID0302} & \textbf{Node Dependencies}\quad \tzpidref{0301}\\
\textbf{Registry} & \tzpcode{registry\_id\_0302} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Antipodal Pair Object & Pair-Space Count\\
\textbf{Closure Support} & Opposite-Pair Admissibility & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The DAANSphere Factorization and Antipodal Pairs entry receives the antipodal-pair equations from the DAANSphereNavigationProtocol source, making the pair space and its admissibility test explicit.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathcal{P}_i=\{\mathbf{x}_i,-\mathbf{x}_i\}
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
N_{\mathrm{pair}}=\frac{N}{2}=76800
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathcal{A}_{\mathrm{anti}}(\mathbf{x}_i,\mathbf{x}_j)=1\iff \|\mathbf{x}_i+\mathbf{x}_j\|\le\varepsilon
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{P}_i$: source equation symbol.
    \item $N_{\mathrm{pair}}$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
    \item $\mathcal{A}_{\mathrm{anti}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0302 generated source Wolfram model *)
ClearAll[K0302, Cr0302, T, R, A, W, I, N];
eq0302$1 = HoldForm[$PI == Tuple[xI, -xI]*$];
eq0302$2 = HoldForm[$NPair == N/2 == 76800*$];
eq0302$3 = HoldForm[Inequality[$AAnti[xI, xJ], Equal, 1, Equal, xI + xJ, LessEqual, epsilon$]];

K0302 = HoldForm[{eq0302$1, eq0302$2, eq0302$3}];

N = "normalized TRAWIN closure object for DAANSphere Factorization and Antipodal Pairs";
I = "Opposite-Pair Admissibility integration/comparison layer";
W = "Pair-Space Count wave or operator carrier";
A = "Antipodal Pair Object admissible action/amplitude condition";
R = "Pair-Space Count rotation/curl preservation layer";
T = "Antipodal Pair Object local source condition";

Cr0302[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0302 = Cr0302[K0302];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Antipodal Pair Object local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Pair-Space Count rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Antipodal Pair Object admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Pair-Space Count wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Opposite-Pair Admissibility integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for DAANSphere Factorization and Antipodal Pairs.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0302] DAANSphere Factorization and Antipodal Pairs}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
For any closed loop $\GammaLoop$ encircling the TZP in $M$, there exists a homotopy deforming $\GammaLoop$ into a lemniscate whose self-intersection occurs at $p$.

\paragraph{Primary Derivation.}
Let $\GammaLoop:S^1\to M$ be a closed loop surrounding $p$. Since $p$ is the limiting degeneracy point, paths enclosing $p$ may be continuously deformed while preserving their winding relation to $p$.

Introduce a homotopy:

\begin{equation}
H:S^1\times[0,1]\to M .
\end{equation}

At $s=0$, the homotopy recovers the original loop:

\begin{equation}
H(\theta,0)=\GammaLoop(\theta).
\end{equation}

At $s=1$, the loop is deformed into a figure-eight curve:

\begin{equation}
H(\theta,1)=\Lambda(\theta),
\end{equation}

where $\Lambda$ is a lemniscatic curve satisfying:

\begin{equation}
\Lambda(\theta_1)=\Lambda(\theta_2)=p,
\qquad
\theta_1\neq\theta_2 .
\end{equation}

Thus the self-intersection of the limiting loop is identified with the TZP.

\paragraph{Interpretation.}
The lemniscate is the canonical shape of TZP recurrence: two lobes, one crossing, one central point. This turns the zero point into a geometric crossing rather than a simple endpoint.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors DAANSphere Factorization and Antipodal Pairs by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Antipodal Pair Object}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathcal{P}_i=\{\mathbf{x}_i,-\mathbf{x}_i\}
$
\end{adjustbox}
\]
\noindent This records the factorized pair object used by the navigation protocol.\par
\noindent\textbf{2. Pair-Space Count}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
N_{\mathrm{pair}}=\frac{N}{2}=76800
$
\end{adjustbox}
\]
\noindent This fixes the cardinality of the factorized antipodal-pair space.\par
\noindent\textbf{3. Opposite-Pair Admissibility}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathcal{A}_{\mathrm{anti}}(\mathbf{x}_i,\mathbf{x}_j)=1\iff \|\mathbf{x}_i+\mathbf{x}_j\|\le\varepsilon
$
\end{adjustbox}
\]
\noindent This closes the progression with the tolerance predicate for opposite-pair recognition.\par

\clearpage
\noindent\textbf{[ID 0302] DAANSphere Factorization and Antipodal Pairs}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
DAANSphere Factorization and Antipodal Pairs is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This factorization supports efficient hierarchical addressing and ensures that every address has a complementary opposite. \textbf{Contextual meaning:} The entry reads DAANSphere Factorization and Antipodal Pairs as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Antipodal Pair Object; Pair-Space Count; Opposite-Pair Admissibility.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The lemniscate is the canonical shape of TZP recurrence: two lobes, one crossing, one central point. This turns the zero point into a geometric crossing rather than a simple endpoint.

\tzpsection{Equation Grounding}
Equation anchors: csv,,MB sub 24b76c26a14a,registry sub id sub 0272,[ID 0272],Multi Scale Correlation Matrix,,best sub match , g sub 0 equiv ratio GM r to the power 2 approximately 9; text m/s to the power 2, g sub 0 equiv ratio GM r to the power 2 approximately 9; and ndimage import laplace \# Grid L = 128 dx = 1. Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Antipodal Symmetry Breaking}: The geometric pairing mechanism mapping diametrically opposed points into functionally distinct resonant states.
\item \textbf{Dual-Hemisphere Phase Inversion}: The spatial operator guaranteeing opposite phase alignments for coupled modes on a spherical topology.
\item \textbf{Bipartite Spherical Decomposition}: The reduction of a global manifold into two distinct but entangled functional domains.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0302]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0302_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0302] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont DAANSphere Factorization and Antipodal Pairs}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the DAANSphere Factorization and Antipodal Pairs entry receives the antipodal-pair
equations from the DAANSphereNavigationProtocol source, making t...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``DAANSphere Factorization and Antipodal Pairs is valid as a tensorial/geometric statement
when the stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0302_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
