\tzpanchor{0920}
\tzpentryheader{0920}{HOLOMORPHIC FLOW VECTOR FIELD}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{dcec160b-caec-55ba-a094-ae550aed8d0a}}\\
\textbf{PiID} & \tzpcode{1159562863882} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{927}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3518.1992 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.7969 rad}\\
\textbf{TZPID} & \tzpcode{ID0920} & \textbf{Node Dependencies}\quad \tzpidref{0919}\\
\textbf{Registry} & \tzpcode{registry\_id\_0920} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Generator Law & Geometric Constraint\\
\textbf{Closure Support} & Geometric Constraint & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
- Proposition: "Vector potential satisfies nablatimesA = B for dipole field"

\tzpsection{Canonical Equation}
\[
d\mathrm{Psi}/dt = XH[\mathrm{Psi} Hamiltonian vector field
\]
\[
- Proposition: Vector potential  abla\times A = B for dipole field
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $A$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $\mathcal{K}_{0920}$: canonical registry object for entry ID 0920.
    \item $P$: source equation symbol.
    \item $X$: source variable, local coordinate, or input state in the entry relation.
    \item $H$: source equation symbol.
    \item $V$: auxiliary target state or comparison variable.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0920 generated source Wolfram model *)
ClearAll[K0920, Cr0920, T, R, A, W, I, N];
eq0920$1 = HoldForm[D[Psi[t], t] == XH[Psi]];
eq0920$2 = HoldForm[-(Proposition:Vector*potential*abla*A == B*for*dipole*field)];

K0920 = HoldForm[{eq0920$1, eq0920$2}];

N = "normalized TRAWIN closure object for HOLOMORPHIC FLOW VECTOR FIELD";
I = "HOLOMORPHIC FLOW VECTOR FIELD integration/comparison layer";
W = "HOLOMORPHIC FLOW VECTOR FIELD wave or operator carrier";
A = "HOLOMORPHIC FLOW VECTOR FIELD admissible action/amplitude condition";
R = "HOLOMORPHIC FLOW VECTOR FIELD rotation/curl preservation layer";
T = "HOLOMORPHIC FLOW VECTOR FIELD local source condition";

Cr0920[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0920 = Cr0920[K0920];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ HOLOMORPHIC FLOW VECTOR FIELD local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ HOLOMORPHIC FLOW VECTOR FIELD rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ HOLOMORPHIC FLOW VECTOR FIELD admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ HOLOMORPHIC FLOW VECTOR FIELD wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ HOLOMORPHIC FLOW VECTOR FIELD integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for HOLOMORPHIC FLOW VECTOR FIELD.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0920] HOLOMORPHIC FLOW VECTOR FIELD}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
d\mathrm{Psi}/dt = XH[\mathrm{Psi} Hamiltonian vector field
\]
\[
- Proposition: Vector potential  abla\times A = B for dipole field
\]

\paragraph{Primary Derivation.}
One can verify the equality using functional and analytic properties. which confirms the stated equality.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. Interpreted through TRAWIN, the equation functions as the generalized carrier for the entry’s information content. Within the CHL view, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors HOLOMORPHIC FLOW VECTOR FIELD by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
d\mathrm{Psi}/dt = XH[\mathrm{Psi} Hamiltonian vector field
\]
\[
- Proposition: Vector potential  abla\times A = B for dipole field
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0920] HOLOMORPHIC FLOW VECTOR FIELD}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
HOLOMORPHIC FLOW VECTOR FIELD is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} - Proposition: Vector potential satisfies nablatimesA = B for dipole field. \textbf{Contextual meaning:} The entry reads HOLOMORPHIC FLOW VECTOR FIELD as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Generator Law; Geometric Constraint; Geometric Constraint.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, HOLOMORPHIC FLOW VECTOR FIELD is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: d Psi /dt = XH[ Psi Hamiltonian vector field; - Proposition: Vector potential ablatimes A = B for dipole field; and ablatimes A = B for dipole field. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Complex-Analytic Fluid Dynamics}: The use of advanced imaginary numbers to perfectly predict the smooth, glassy flow of the supercooled plasma.
\item \textbf{Conformal Vector Mapping}: The mathematical trick of stretching the fluid equations to fit any weird, lopsided shape the reactor chamber happens to be without breaking the physics.
\item \textbf{Cauchy-Riemann Integrity Checking}: The absolute, unbreakable rule ensuring that if the plasma is flowing smoothly in the X direction, it must also be flowing smoothly in the Y direction.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0920]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0920].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0920] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont HOLOMORPHIC FLOW VECTOR FIELD}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} HOLOMORPHIC FLOW VECTOR FIELD is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``HOLOMORPHIC FLOW VECTOR FIELD is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0920].
\par\endgroup
\vfill
\endgroup
\endgroup
