\section*{ID7612: Concrete Next Steps I Can Do for You Right Now: m\_0,p\_0,λ\_0}
\paragraph{Metadata.}
PiID: 0723623464684 | RTEID: RTE:P29559.0865:T4.7220 | UUID: 45079386-9c16-57ad-a016-34fefd278258

\paragraph{Canonical Statement.}
- (A) **Produce a full, runnable Jupyter notebook** that implements the 2D QOV simulation above, includes Poisson solver (FFT) to compute \textbackslash{}(\textbackslash{}Phi\textbackslash{}), simulates tracer test particles, and generates figures of \textbackslash{}(R(x,t), n(x,t), \textbackslash{}Phi(x,t)\textbackslash{}). - (B) **Compute parameter ranges** (orders of magnitude) showing what per-packet \textbackslash{}(m\_0,p\_0,\textbackslash{}lambda\_0\textbackslash{}) are required to recover the observed \textbackslash{}(G\textbackslash{}) if particles are created at a certain rate — useful to show plausibility or rule out the mechanism. - (C) **Derive a nondimensional parameter set** (like a Reynolds number) that controls whether emergent gravity is strong enough to produce macroscopic effects in finite time — helps identify regimes where the model could account for planets / cosmology. - (D) **Make an experimental tabletop design** (Kuramoto oscillators + token generation) that demonstrates the amplification mechanism in a lab analog.

\paragraph{Canonical Equation.}
\[
m_0,p_0,\lambda_0
\]

\paragraph{Dictionary.}
Concrete Next Steps I Can Do for You Right Now: m\_0,p\_0,λ\_0 — m\_0,p\_0,λ\_0

\paragraph{Encyclopedia.}
Concrete Next Steps I Can Do for You Right Now: m\_0,p\_0,λ\_0 is a symbolic expression, written m\_0,p\_0,λ\_0. It introduces a symbol or relation used elsewhere in the framework. It is built from m\_0, p\_0. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
