\tzpanchor{0341}
\tzpentryheader{0341}{Neuromorphic Correspondence Operator}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{df53e75a-aad9-540c-9d6a-71a7cab06396}}\\
\textbf{PiID} & \tzpcode{1715364367892} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{348}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1324.1787 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.1818 rad}\\
\textbf{TZPID} & \tzpcode{ID0341} & \textbf{Node Dependencies}\quad \tzpidref{0340}\\
\textbf{Registry} & \tzpcode{registry\_id\_0341} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This correspondence allows translation of metamaterial dynamics into neural models.

\tzpsection{Canonical Equation}
\[
\mathcal{N}:\mathcal{S}_{\mathrm{TZP}}\to\mathcal{S}_{\mathrm{neuro}}
\]
\[
\mathcal{N}(x\circ y)=\mathcal{N}(x)\star\mathcal{N}(y)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{N}$: integer mode index.
    \item $\mathcal{S}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{S}_{\mathrm{neuro}}$: source equation symbol.
    \item $x$: local field point or coordinate variable in the canonical equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0341 generated source Wolfram model *)
ClearAll[K0341, Cr0341, T, R, A, W, I, N];
eq0341$1 = HoldForm[N[STZP] -> Sneuro];
eq0341$2 = HoldForm[N[xcirc*y] == N[x]*starN[y]];
eq0341$3 = HoldForm[widehat[x] == N[x]/N];

K0341 = HoldForm[{eq0341$1, eq0341$2, eq0341$3}];

N = "normalized TRAWIN closure object for Neuromorphic Correspondence Operator";
I = "Normalized Output integration/comparison layer";
W = "Composable Action wave or operator carrier";
A = "Carrier Map admissible action/amplitude condition";
R = "Composable Action rotation/curl preservation layer";
T = "Carrier Map local source condition";

Cr0341[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0341 = Cr0341[K0341];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Carrier Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Composable Action rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Carrier Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Composable Action wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Output integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Neuromorphic Correspondence Operator.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0341] Neuromorphic Correspondence Operator}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
H
=
\int_V
\mathbf{A}\cdot\mathbf{B}
\,\mathrm{d}^3x .
\end{equation}

\paragraph{Quantized Form.}
\begin{equation}
H=w\,\Phi .
\end{equation}

\paragraph{Primary Derivation.}
Let $\mathbf{A}$ be the magnetic vector potential and $\mathbf{B}$ the magnetic field.  
Magnetic helicity measures the linkage, twist, and winding of magnetic field lines inside a volume $V$:

\begin{equation}
H
=
\int_V
\mathbf{A}\cdot\mathbf{B}
\,\mathrm{d}^3x .
\end{equation}

If the magnetic structure winds around the TZP with integer winding number $w$, and if $\Phi$ denotes the magnetic flux through the lemniscatic loop, then helicity decomposes into winding times flux:

\begin{equation}
\boxed{
H=w\,\Phi .
}
\end{equation}

\paragraph{Interpretation.}
Magnetic helicity becomes quantized when the field topology is constrained by integer TZP winding.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Neuromorphic Correspondence Operator by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Carrier Map}\par
\[
\mathcal{N}:\mathcal{S}_{\mathrm{TZP}}\to\mathcal{S}_{\mathrm{neuro}}
\]
\noindent This names the entry as an actual map between carrier domains rather than a loose metaphor.\par
\noindent\textbf{2. Composable Action}\par
\[
\mathcal{N}(x\circ y)=\mathcal{N}(x)\star\mathcal{N}(y)
\]
\noindent This inserts the map into the ordered TRAWIN chain and makes composition explicit.\par
\noindent\textbf{3. Normalized Output}\par
\[
\widehat{x}=\mathcal{N}^{-1}\mathcal{N}(x)
\]
\noindent This closes the entry by requiring that the output land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0341] Neuromorphic Correspondence Operator}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Neuromorphic Correspondence Operator is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This correspondence allows translation of metamaterial dynamics into neural models. \textbf{Contextual meaning:} The entry reads Neuromorphic Correspondence Operator as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Magnetic helicity becomes quantized when the field topology is constrained by integer TZP winding.

\tzpsection{Equation Grounding}
Equation anchors: partial; proof=candidate sub formal sub math registry sub definition sub combined,D: 0 sub Engine sub Outputspublish sub reassemble expanded sub context registry sub e; and proof=non sub chl sub or sub empirical registry sub definition sub combined,D: 0 sub Engine sub Outputspublish sub reassemble expanded sub context registry sub en. Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Cognitive-Physical Isomorphism}: The formal mathematical functor translating abstract neural network architectures into physical wave-propagation systems.
\item \textbf{Associative Memory Mapping}: The geometric rule preserving the relationships between different data states when transitioning from logic gates to optical arrays.
\item \textbf{Non-Linear Activation Functors}: The mapping of biological threshold responses directly onto the saturation behaviors of driven metamaterials.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0341]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0341_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0341] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Neuromorphic Correspondence Operator}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this correspondence allows translation of metamaterial dynamics into neural models

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Neuromorphic Correspondence Operator is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0341_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
