\tzpanchor{0378}
\tzpentryheader{0378}{Frame-Dragging Metric Correction}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{038a03af-07c0-5b88-8ad2-0656f9e512d7}}\\
\textbf{PiID} & \tzpcode{5213841469519} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{385}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1467.8579 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.4186 rad}\\
\textbf{TZPID} & \tzpcode{ID0378} & \textbf{Node Dependencies}\quad \tzpidref{0377}\\
\textbf{Registry} & \tzpcode{registry\_id\_0378} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Kerr-like Metric & Rotation Tensor\\
\textbf{Closure Support} & Mixed Components & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
At high angular velocity, spacetime acquires a Kerr-like metric whose correction tensor depends on the square of the cross product of the angular velocity and position.

\tzpsection{Canonical Equation}
\[
ds^{2}=g_{\mu\nu}dx^{\mu}dx^{\nu}+2g_{t\phi}\,dt\,d\phi
\]
\[
g_{t\phi}\approx-\frac{2GJ}{c^{3}r}\sin^{2}\theta
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $g_{\mu\nu}$: source equation symbol.
    \item $\mu$: source equation symbol.
    \item $g_{t\phi}$: source equation symbol.
    \item $t$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $c$: speed of light or relativistic conversion factor.
    \item $\theta$: phase angle or local angular coordinate.
    \item $\Omega_{\mathrm{LT}}$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0378 generated source Wolfram model *)
ClearAll[K0378, Cr0378, T, R, A, W, I, N];
eq0378$1 = HoldForm[ds2 == gMunudxmudxnu + 2*gTphi*dt*dphi];
eq0378$2 = HoldForm[gTphi == (-((2*G*J)/(c^3*r)))*Sin^2*theta];
eq0378$3 = HoldForm[OmegaLT == (2*G*J)/(c^2*r^3)];

K0378 = HoldForm[{eq0378$1, eq0378$2, eq0378$3}];

N = "normalized TRAWIN closure object for Frame-Dragging Metric Correction";
I = "Mixed Components integration/comparison layer";
W = "Rotation Tensor wave or operator carrier";
A = "Kerr-like Metric admissible action/amplitude condition";
R = "Rotation Tensor rotation/curl preservation layer";
T = "Kerr-like Metric local source condition";

Cr0378[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0378 = Cr0378[K0378];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Kerr-like Metric local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Rotation Tensor rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Kerr-like Metric admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Rotation Tensor wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Mixed Components integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Frame-Dragging Metric Correction.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0378] Frame-Dragging Metric Correction}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\langle O(x)O(0)\rangle
\sim
|x|^{-2+\eta}.
\end{equation}

\paragraph{Exponent Dependence.}
\begin{equation}
\eta=\eta(d_{\mathrm{eff}},\mathrm{TZP}).
\end{equation}

\paragraph{Primary Derivation.}
At a quantum critical point, correlation length diverges and the system loses a preferred length scale.  
An observable $O(x)$ therefore has a scale-free two-point function:
\begin{equation}
\langle O(x)O(0)\rangle
\sim
|x|^{-\Delta}.
\end{equation}

With anomalous exponent $\Delta=2-\eta$, this becomes
\begin{equation}
\boxed{
\langle O(x)O(0)\rangle
\sim
|x|^{-2+\eta}.
}
\end{equation}

In the TRAWIN setting,
\begin{equation}
\eta=\eta(d_{\mathrm{eff}},\mathrm{TZP}).
\end{equation}

\paragraph{Interpretation.}
Quantum criticality is detected through power-law correlations whose exponents may depend on effective dimension and TZP deformation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Frame-Dragging Metric Correction by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Kerr-like Metric}\par
\[
ds^{2}=g_{\mu\nu}dx^{\mu}dx^{\nu}+2g_{t\phi}\,dt\,d\phi
\]
\noindent This fixes the Kerr-like rotating correction to the background metric.\par
\noindent\textbf{2. Rotation Tensor}\par
\[
g_{t\phi}\approx-\frac{2GJ}{c^{3}r}\sin^{2}\theta
\]
\noindent This states the explicit rotation-induced correction tensor in block form.\par
\noindent\textbf{3. Mixed Components}\par
\[
\Omega_{\mathrm{LT}}=\frac{2GJ}{c^{2}r^{3}}
\]
\noindent This closes the entry by extracting the mixed time-space frame-dragging components from the rotating metric.\par

\clearpage
\noindent\textbf{[ID 0378] Frame-Dragging Metric Correction}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Frame-Dragging Metric Correction is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} At high angular velocity, spacetime acquires a Kerr-like metric whose correction tensor depends on the square of the cross product of the angular velocity and position. \textbf{Contextual meaning:} The entry reads Frame-Dragging Metric Correction as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the frame-dragging correction in explicit metric form instead of garbled matrix prose. \textbf{Lemma support:} Kerr-like Metric; Rotation Tensor; Mixed Components.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Quantum criticality is detected through power-law correlations whose exponents may depend on effective dimension and TZP deformation.

\tzpsection{Equation Grounding}
Equation anchors: u2202B/u2202t = u2207u00d7(vu00d7B) + u03b7u2207 to the power 2B + F sub tidal (t); Morphisms -> r ZeroPointExtraction: |0u27e9 u2192 |TZPu27e9,r GravitonEmission: |TZPu27e9 u2192 |Gravitonu27e9r r; and requency: omega \textasciitilde{} 10 to the power 4 - 106 rad/s - Characteristic scale: l sub classical \textasciitilde{} 1 cm Quantum Mechanics (QM): - Flux quantization: Phi sub 0 = h/(2e) = 2. Proof route: show that the rotating gyromagnetic assembly induces the stated Kerr-like metric correction and mixed frame-dragging terms. Formalization route: prove that the rotating correction tensor yields the stated mixed metric components.

\tzpsection{Interpretive Role}
The entry now states the frame-dragging correction in explicit metric form instead of garbled matrix prose.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spacetime Rotational Shearing}: The physical phenomenon where a massive, spinning object pulls the very fabric of space and time along with it like a whirlpool.
\item \textbf{Angular-Temporal Metric Cross-Terms}: The specific math in relativity that links the forward flow of time directly to movement in a circular direction.
\item \textbf{Sine-Squared Latitude Dependence}: The geometric rule showing that the twisting of space is strongest at the equator of the spinning body and drops to zero at the poles.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0378]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0378_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0378] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Frame-Dragging Metric Correction}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} at high angular velocity, spacetime acquires a Kerr-like metric whose correction tensor
depends on the square of the cross product of the angular v...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Frame-Dragging Metric Correction is valid as a tensorial/geometric statement when the
stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0378_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
