\tzpanchor{0392}
\tzpentryheader{0392}{Helicity-Induced Curvature Relation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{dfadb356-4d87-57d2-92c9-5b2117e3f8fc}}\\
\textbf{PiID} & \tzpcode{1511609433057} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{399}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1522.2231 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.5082 rad}\\
\textbf{TZPID} & \tzpcode{ID0392} & \textbf{Node Dependencies}\quad \tzpidref{0391}\\
\textbf{Registry} & \tzpcode{registry\_id\_0392} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This relation binds the geometry of configuration space to a conserved physical quantity.

\tzpsection{Canonical Equation}
\[
R_{\mu\nu\rho\sigma}=\kappa_{H}\nabla_{[\mu}H_{\nu]\rho\sigma}
\]
\[
\mathcal{K}_{H}=\lVert H\rVert^{2}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $R_{\mu\nu\rho\sigma}$: source equation symbol.
    \item $\mu$: source equation symbol.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $H$: source equation symbol.
    \item $H_{\nu]\rho\sigma}$: source equation symbol.
    \item $\mathcal{K}_{H}$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0392 generated source Wolfram model *)
ClearAll[K0392, Cr0392, T, R, A, W, I, N];
eq0392$1 = HoldForm[RMunurhosigma == kappaHGradMuHNurhosigma];
eq0392$2 = HoldForm[KH == lVert*HrVert^2];
eq0392$3 = HoldForm[Delta*R == kappaHKH];

K0392 = HoldForm[{eq0392$1, eq0392$2, eq0392$3}];

N = "normalized TRAWIN closure object for Helicity-Induced Curvature Relation";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0392[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0392 = Cr0392[K0392];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Helicity-Induced Curvature Relation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0392] Helicity-Induced Curvature Relation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
G=SO(3)\ltimes_{\varphi} U(1).
\end{equation}

\paragraph{Composition Law.}
\begin{equation}
(R,e^{i\alpha})\cdot(R',e^{i\beta})
=
\left(
RR',
e^{i\alpha}\varphi_R(e^{i\beta})
\right).
\end{equation}

\paragraph{Primary Derivation.}
If rotation and gauge phase compose independently, the group is a direct product.  
If rotations act on gauge phase through an automorphism $\varphi_R$, the coupled group is a semi-direct product:

\begin{equation}
G=SO(3)\ltimes_{\varphi}U(1).
\end{equation}

The product law becomes:
\begin{equation}
\boxed{
(R,e^{i\alpha})\cdot(R',e^{i\beta})
=
\left(
RR',
e^{i\alpha}\varphi_R(e^{i\beta})
\right).
}
\end{equation}

\paragraph{Interpretation.}
Rotation and phase are treated as interacting symmetry sectors rather than merely adjacent labels.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Helicity-Induced Curvature Relation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
R_{\mu\nu\rho\sigma}=\kappa_{H}\nabla_{[\mu}H_{\nu]\rho\sigma}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\mathcal{K}_{H}=\lVert H\rVert^{2}
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\Delta R=\kappa_{H}\mathcal{K}_{H}
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0392] Helicity-Induced Curvature Relation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Helicity-Induced Curvature Relation is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This relation binds the geometry of configuration space to a conserved physical quantity. \textbf{Contextual meaning:} The entry reads Helicity-Induced Curvature Relation as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Rotation and phase are treated as interacting symmetry sectors rather than merely adjacent labels.

\tzpsection{Equation Grounding}
Equation anchors: + H sub Trawin [psi, t] = H sub tunnel + H sub ER + H sub cymatic + H sub SC + H sub TZP , +; The Kuramoto equations used: L11: dottheta sub i = omega sub i; and frac k sub 0 N sum sub j=1 to the power N L12: K sub ij sin(theta sub j-theta sub i) L13:   (rad/day), using sidereal rotation periods (days). Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Torsion-Driven Spacetime Bending}: The physical theory proposing that an extreme amount of twisted magnetic energy can literally warp the geometry of the universe around it.
\item \textbf{Riemannian Tensor Augmentation}: The specific mathematical modification made to Einstein's equations to account for the heavy presence of magnetic knots.
\item \textbf{Proportional Curvature Scaling}: The linear rule linking the squared intensity of the magnetic twisting directly to the severity of the spatial distortion.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0392]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0392_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0392] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Helicity-Induced Curvature Relation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this relation binds the geometry of configuration space to a conserved physical quantity

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Helicity-Induced Curvature Relation is valid as a tensorial/geometric statement when the
stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0392_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
