\section*{ID9113: Definition of ψobs〉}
\paragraph{Metadata.}
PiID: 9526179378002 | RTEID: RTE:P35387.8028:T1.7595 | UUID: d4eeb419-9123-52a8-851c-a7864344ca36

\paragraph{Canonical Statement.}
uantum noise spectra; design of minimally invasive measurement schemes; interplay with observerdependent states. Falsifiability / Test Handle: Measurements that show no backaction where predicted, or excessive backaction beyond predictions, would refute this operator. 0.0.66 ID 064: ObserverDependent Quantum States Type: Structural Constraint Formal Statement: The state \$ψ〉|\textbackslash{}psi\textbackslash{}rangleψ〉\$ assigned to a system depends on the observer’s trajectory through the Trawinistic manifold; specifically, \$ψobs〉=U(γ)ψ0〉|\textbackslash{}psi\_\{\textbackslash{}text\{obs\}\}\textbackslash{}rangle\$ = \$U(\textbackslash{}gamma)|\textbackslash{}psi\_0\textbackslash{}rangleψobs〉=U(γ)ψ0〉,\$ where \$U(γ)U(\textbackslash{}gamma)U(γ)\$ is a unitary transformation determined by the observer’s worldline \$γ\textbackslash{}gammaγ\$ and the temporal displacement factor. Interpretive Meaning: Different observers may assign different states to the same physical system because of their distinct motions in curved space; there is no absolute state independent of the observer. Depende

\paragraph{Canonical Equation.}
\[
ψobs〉=U(γ)ψ0〉|\psi_{\text{obs}}\rangle
\]

\paragraph{Dictionary.}
Definition of ψobs〉 — ψobs〉=U(γ)ψ0〉|ψ\_obs⟩

\paragraph{Encyclopedia.}
Definition of ψobs〉 is an algebraic definition, written ψobs〉=U(γ)ψ0〉|ψ\_obs⟩. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from U, defining ψobs〉. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
