\tzpanchor{0745}
\tzpentryheader{0745}{FIELD ROTATION GRADIENT}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{44fce109-a5e7-5a63-ae4b-be0b838c87d8}}\\
\textbf{PiID} & \tzpcode{0996051870721} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{752}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2858.0514 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.7092 rad}\\
\textbf{TZPID} & \tzpcode{ID0745} & \textbf{Node Dependencies}\quad \tzpidref{0744}\\
\textbf{Registry} & \tzpcode{registry\_id\_0745} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Frequency Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records field rotation gradient through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0745}}:\mathcal{X}_{\mathrm{id0745}}\longrightarrow\mathcal{Y}_{\mathrm{id0745}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0745}})=\mathcal{O}_{\mathrm{id0745}}
\]
\[
\mathcal{O}_{\mathrm{id0745}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0745}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0745}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0745}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0745 generated source Wolfram model *)
ClearAll[K0745, Cr0745, T, R, A, W, I, N];
eq0745$1 = HoldForm[Oid0745[Xid0745] -> Yid0745];
eq0745$2 = HoldForm[NTRAWIN[OId0745] == OId0745];
eq0745$3 = HoldForm[Element[OId0745[x], YAdm]];

K0745 = HoldForm[{eq0745$1, eq0745$2, eq0745$3}];

N = "normalized TRAWIN closure object for FIELD ROTATION GRADIENT";
I = "FIELD ROTATION GRADIENT integration/comparison layer";
W = "FIELD ROTATION GRADIENT wave or operator carrier";
A = "FIELD ROTATION GRADIENT admissible action/amplitude condition";
R = "FIELD ROTATION GRADIENT rotation/curl preservation layer";
T = "FIELD ROTATION GRADIENT local source condition";

Cr0745[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0745 = Cr0745[K0745];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ FIELD ROTATION GRADIENT local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ FIELD ROTATION GRADIENT rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ FIELD ROTATION GRADIENT admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ FIELD ROTATION GRADIENT wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ FIELD ROTATION GRADIENT integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for FIELD ROTATION GRADIENT.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0745] FIELD ROTATION GRADIENT}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0745}}:\mathcal{X}_{\mathrm{id0745}}\longrightarrow\mathcal{Y}_{\mathrm{id0745}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0745}})=\mathcal{O}_{\mathrm{id0745}}
\]
\[
\mathcal{O}_{\mathrm{id0745}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0745}})=\mathcal{O}_{\mathrm{id0745}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. In the TRAWIN reading, the equation functions as the mapping carrier for the entry’s information content. Under CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors FIELD ROTATION GRADIENT by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0745}}:\mathcal{X}_{\mathrm{id0745}}\longrightarrow\mathcal{Y}_{\mathrm{id0745}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0745}})=\mathcal{O}_{\mathrm{id0745}}
\]
\[
\mathcal{O}_{\mathrm{id0745}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0745] FIELD ROTATION GRADIENT}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
FIELD ROTATION GRADIENT is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Delta omega = 0. \textbf{Contextual meaning:} The entry reads FIELD ROTATION GRADIENT as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Frequency Relation; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, FIELD ROTATION GRADIENT is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: Delta omega = 0; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spatial Torsion Differentials}: The exact measurement of how quickly the twisting, violent spin of the magnetic field drops off as you move from the center of the reactor out toward the walls.
\item \textbf{Shear-Stress Magnetic Tearing}: The dangerous mathematical zone where the inside of the field is spinning so much faster than the outside of the field that the invisible lines of force literally snap in half.
\item \textbf{Angular Velocity Mapping}: The creation of a perfect 3D contour map showing not how hot the plasma is, but exactly how fast every single microscopic drop of it is spinning in circles.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0745]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0745].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0745] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont FIELD ROTATION GRADIENT}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} FIELD ROTATION GRADIENT is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``FIELD ROTATION GRADIENT is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0745].
\par\endgroup
\vfill
\endgroup
\endgroup
