\tzpanchor{0022}
\tzpentryheader{0022}{TZP Curvature Singularity}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7a6a62fd-a4a3-5414-94ac-9aee6ffcc558}}\\
\textbf{PiID} & \tzpcode{4338327950288} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{29}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{85.4309 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.1408 rad}\\
\textbf{TZPID} & \tzpcode{ID0022} & \textbf{Node Dependencies}\quad \tzpidref{0016}\\
\textbf{Registry} & \tzpcode{registry\_id\_0022} & \textbf{Scale}\quad singularity\\
\textbf{LOC Classification} & QA641 singular curvature & QC178 relativistic singularities\\
\textbf{arXiv Classification} & Primary: gr-qc \quad Cross-list: math.DG, math-ph & \\
\textbf{Primary Support} & Regularized Curvature Field & Anchor Divergence Criterion\\
\textbf{Closure Support} & Singularity Classification & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The TZP curvature singularity marks the regime where even the regularized Trawin curvature fails to remain finite. It distinguishes controlled degeneracy from genuinely divergent geometric behavior at the zero point.

\tzpsection{Canonical Equation}
\[
\lim_{x\to p} R_{T}(x) = \infty
\]
\[
R_{T}(x)=\lim_{y\to x}\bigl(R(y)+f(y)\bigr)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $R_{T}(x)$: source equation symbol.
    \item $T$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\Lambda$: cosmological or lemniscatic branch parameter in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0022 generated source Wolfram model *)
ClearAll[K0022, Cr0022, T, R, A, W, I, N];
eq0022$1 = HoldForm[LimitXp*RT[x] == Infinity];
eq0022$2 = HoldForm[RT[x] == LimitYx[R[y] + f[y]]];
eq0022$3 = HoldForm[SingTZP == NormalizeTRAWINTuple[LimitXpRT[x], RT, Lambda]];

K0022 = HoldForm[{eq0022$1, eq0022$2, eq0022$3}];

N = "normalized TRAWIN closure object for TZP Curvature Singularity";
I = "Singularity Classification integration/comparison layer";
W = "Anchor Divergence Criterion wave or operator carrier";
A = "Regularized Curvature Field admissible action/amplitude condition";
R = "Anchor Divergence Criterion rotation/curl preservation layer";
T = "Regularized Curvature Field local source condition";

Cr0022[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0022 = Cr0022[K0022];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Regularized Curvature Field local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Anchor Divergence Criterion rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Regularized Curvature Field admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Anchor Divergence Criterion wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Singularity Classification integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP Curvature Singularity.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0022] TZP Curvature Singularity}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\lim_{x\to p}R_T(x)=\infty .
\end{equation}

\paragraph{Primary Derivation.}
From ID 0016, the regularized Trawin curvature is:

\begin{equation}
R_T(x)=R(x)+f(x).
\end{equation}

A regular TZP curvature condition occurs when:

\begin{equation}
\lim_{x\to p}R_T(x)<\infty .
\end{equation}

A curvature singularity occurs when this limiting value fails to remain finite. Therefore the singular condition is:

\begin{equation}
\boxed{
\lim_{x\to p}R_T(x)=\infty .
}
\end{equation}

\paragraph{Interpretation.}
ID 0022 defines the failure condition of the regulator: the TZP becomes a true curvature singularity when $R_T$ diverges.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP Curvature Singularity by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Regularized Curvature Field}\par
\[
R_{T}(x)=\lim_{y\to x}\bigl(R(y)+f(y)\bigr)
\]
\noindent This defines the curvature quantity whose anchor behavior is under inspection.\par
\noindent\textbf{2. Anchor Divergence Criterion}\par
\[
\lim_{x\to p} R_{T}(x) = \infty
\]
\noindent This identifies the exact condition under which the zero point is a genuine curvature singularity.\par
\noindent\textbf{3. Singularity Classification}\par
\[
\operatorname{Sing}_{\mathrm{TZP}}
=
\operatorname{Normalize}_{\mathrm{TRAWIN}}
\!\left(
\lim_{x\to p}R_{T}(x),\,
R_{T},\,
\Lambda
\right)
\]
\noindent This closes the progression by converting raw divergence into a normalized yes-or-no classification inside the TRAWIN scheme.\par

\clearpage
\noindent\textbf{[ID 0022] TZP Curvature Singularity}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP Curvature Singularity is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A curvature singularity at the TZP occurs when the regularised scalar curvature TrawinCurv defined in ID 016 diverges as xrightarrowpxto pxrightarrowp, that is, lim xrightarrowpR sub T(x)=infinitytextbackslash lim sub xto p Rtextbackslash sub T (x)=inftylimxrightarrowpR sub T(x)=infinity. \textbackslash{}. \textbf{Contextual meaning:} The entry reads TZP Curvature Singularity as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Regularized Curvature Field; Anchor Divergence Criterion; Singularity Classification.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
ID 0022 defines the failure condition of the regulator: the TZP becomes a true curvature singularity when R sub T diverges.

\tzpsection{Equation Grounding}
Equation anchors: A curvature singularity at the TZP occurs when the regularised scalar curvature TrawinCurv defined in ID ,016 diverges as xrightarrowpxto pxrightarrowp, that is, limu2061xrightarrowpR T(x)=infinitytextbackslash lim xto p Rtextbackslash T (x)=inftylimxrightarrowpR T(x)=infinity. A curvature singularity at the TZP occurs when the regularised scalar curvature TrawinCurv defined in ID ,016 diverges as xrightarrowpxto pxrightarrowp, that is, limu2061xrightarrowpR T(x)=infinitytextbackslash lim xto p Rtextbackslash T (x)=inftylimxrightarrowpR T(x)=infinity.

\tzpsection{Interpretive Role}
This entry provides the cutoff between acceptable regularized geometries and true curvature blow-up. It is the threshold notion later potential, Hamiltonian, and stability statements can use when deciding whether a configuration is physically admissible.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Tzp Geometric Bending Critical Locus}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\item \textbf{Geometric Bending Critical Locus Geometric Analogue}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\item \textbf{Critical Locus Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0022]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0022_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0022] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP Curvature Singularity}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the TZP curvature singularity marks the regime where even the regularized Trawin
curvature

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP Curvature Singularity is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0022_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
