\section*{ID9098: Definition of HH}
\paragraph{Metadata.}
PiID: 8569094113031 | RTEID: RTE:P35329.5545:T1.6636 | UUID: f2daa624-fc76-5529-91ff-8c70fe5958d2

\paragraph{Canonical Statement.}
o Coulomb’s law; running of electric charge; scale dependence of physical constants; coupling to boundaryinduced effects. Falsifiability / Test Handle: Highprecision QED experiments in strong gravitational fields could reveal deviations predicted by this polarization tensor. 0.0.55 ID 053: Quantum Harmonic Oscillator (TZPModified) Type: Definition Formal Statement: The TZPmodified harmonic oscillator has Hamiltonian \$H=12mp2+12mω2(q)2+δHH\$ = \textbackslash{}frac\{1\}\{2m\},pˆ2 + \textbackslash{}frac\{1\}\{2\}m\textbackslash{}omega2(q)2 + \textbackslash{}delta \$HH=2m1p2+21mω2(q)2+δH,\$ where \$δH\textbackslash{}delta HδH\$ encodes curvaturedependent corrections and qqq is measured using the Trawin base unit; ladder operators satisfy [a,a]=1[a,aˆ\textbackslash{}dagger]=1[a,a]=1 but acquire curvaturedependent phases. Interpretive Meaning: This modifies the familiar quantum harmonic oscillator to include effects of the curved manifold and the TZP; frequency and energy levels shift according to curvature. Depend

\paragraph{Canonical Equation.}
\[
HH=2m1p2+21mω2(q)2+δH,
\]

\paragraph{Dictionary.}
Definition of HH — HH=2m1p2+21mω2(q)2+δH

\paragraph{Encyclopedia.}
Definition of HH is an algebraic definition, written HH=2m1p2+21mω2(q)2+δH. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from m, p, q, H, defining HH. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
