\section*{ID9470: Definition of Δ𝜔𝑛}
\paragraph{Metadata.}
PiID: 7160504922124 | RTEID: RTE:P36774.1131:T4.0438 | UUID: 2ff44fd9-8e95-5d86-8c49-5d76023b6efc

\paragraph{Canonical Statement.}
e Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0210], [ID 0200] Node registry\_id\_0211 Support Titles Mode Quantization; Dispersion Law; Boundary Condition Test Handle If the resonance pattern cannot be organized into bounded modes with the stated boundary condition, the entry fails. Canonical Equation Links 𝜔𝑛=𝜔0 \$√\$ 1+𝑛2( 𝑐 𝜔𝑅 )2 \$Δ𝜔𝑛=𝜔𝑛+1−𝜔𝑛 𝐴(𝜔)=∑\$ 𝑛 𝑎𝑛 𝛿 (𝜔−𝜔𝑛 ) [ID 0212] Gyromagnetic Bessel Interference Operator TZPID ID0212 UUID 5b4e404d-0db2-5997-a556-9dcab8344d31 Type Field / Transport Statement Scale magnetofluid LOC Classification Working routing: QC809 magnetohydrodynamics; QC6 fluid and plasma dynamics arXiv Classification Primary: physics.plasm-ph; Cross-list: astro-ph.SR, gr-qc Canonical Statement This entry develops Gyromagnetic

\paragraph{Canonical Equation.}
\[
Δ𝜔𝑛=𝜔𝑛+1−𝜔𝑛 𝐴(𝜔)=∑
\]

\paragraph{Dictionary.}
Definition of Δ𝜔𝑛 — Δ𝜔𝑛=𝜔𝑛+1−𝜔𝑛 𝐴(𝜔)=∑

\paragraph{Encyclopedia.}
Definition of Δ𝜔𝑛 is an algebraic definition, written Δ𝜔𝑛=𝜔𝑛+1−𝜔𝑛 𝐴(𝜔)=∑. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
