\tzpanchor{0371}
\tzpentryheader{0371}{Constrained Dipole Configuration}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{dd8604bc-da15-53af-93a7-629ddf18c8f5}}\\
\textbf{PiID} & \tzpcode{8820466521384} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{378}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1440.6754 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.3738 rad}\\
\textbf{TZPID} & \tzpcode{ID0371} & \textbf{Node Dependencies}\quad \tzpidref{0370}\\
\textbf{Registry} & \tzpcode{registry\_id\_0371} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Opposing Dipole Moments & Constraint Energy Potential\\
\textbf{Closure Support} & Magnetic Helicity Invariant & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Constrained Dipole Configuration entry receives the dipole, constraint-energy, and helicity equations from the cosmological\_constant source, placing the opposing constrained moments into the Quaternary field-support page.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\boldsymbol{\mu}_1(t)=\mu_0\hat{\mathbf{z}},\qquad \boldsymbol{\mu}_2(t)=-\mu_0\hat{\mathbf{z}}
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
U_{\mathrm{con}}=\int_V\frac{\mathbf{B}\cdot\mathbf{B}}{2\mu_0}\,dV+\mathbf{F}_{\mathrm{mech}}\cdot\mathbf{d}
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
H_M=\int_V\mathbf{A}\cdot\mathbf{B}\,dV
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mu$: source equation symbol.
    \item $\mu_0$: vacuum permeability constant.
    \item $U_{\mathrm{con}}$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $F$: source equation symbol.
    \item $H_M$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0371 generated source Wolfram model *)
ClearAll[K0371, Cr0371, T, R, A, W, I, N];
eq0371$1 = HoldForm[TZPSequence[$boldsymbol[mu]*_*1*t == mu0*hat[z], boldsymbol[mu]*_*2*t == (-mu0)*hat[z]*$]];
eq0371$2 = HoldForm[$UCon == IntegralV[(B*B)/(2*mu0)]*dV + FMech*d$];
eq0371$3 = HoldForm[$HM == IntegralVA*B*dV$];

K0371 = HoldForm[{eq0371$1, eq0371$2, eq0371$3}];

N = "normalized TRAWIN closure object for Constrained Dipole Configuration";
I = "Magnetic Helicity Invariant integration/comparison layer";
W = "Constraint Energy Potential wave or operator carrier";
A = "Opposing Dipole Moments admissible action/amplitude condition";
R = "Constraint Energy Potential rotation/curl preservation layer";
T = "Opposing Dipole Moments local source condition";

Cr0371[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0371 = Cr0371[K0371];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Opposing Dipole Moments local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Constraint Energy Potential rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Opposing Dipole Moments admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Constraint Energy Potential wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Magnetic Helicity Invariant integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Constrained Dipole Configuration.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0371] Constrained Dipole Configuration}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
|\psi\rangle = \alpha|0\rangle+\beta|1\rangle,
\qquad
|\alpha|^2+|\beta|^2=1 .
\end{equation}

\paragraph{Embedding Map.}
\begin{equation}
\iota:S^2_{\mathrm{Bloch}}\hookrightarrow M .
\end{equation}

\paragraph{Primary Derivation.}
A qubit is a normalized two-level quantum state. Its amplitudes satisfy
\begin{equation}
|\alpha|^2+|\beta|^2=1 .
\end{equation}

Modulo global phase, the normalized qubit state corresponds to a point on the Bloch sphere:
\begin{equation}
|\psi\rangle \longleftrightarrow S^2_{\mathrm{Bloch}} .
\end{equation}

In the Trawinistic setting, this Bloch sphere is embedded into the ambient manifold by
\begin{equation}
\boxed{
\iota:S^2_{\mathrm{Bloch}}\hookrightarrow M .
}
\end{equation}

\paragraph{Interpretation.}
The qubit is treated as both a Hilbert-space state and a geometric object embedded into the Trawinistic manifold.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Constrained Dipole Configuration by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Opposing Dipole Moments}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\boldsymbol{\mu}_1(t)=\mu_0\hat{\mathbf{z}},\qquad \boldsymbol{\mu}_2(t)=-\mu_0\hat{\mathbf{z}}
$
\end{adjustbox}
\]
\noindent This records the source opposing dipole moments as the configuration anchors.\par
\noindent\textbf{2. Constraint Energy Potential}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
U_{\mathrm{con}}=\int_V\frac{\mathbf{B}\cdot\mathbf{B}}{2\mu_0}\,dV+\mathbf{F}_{\mathrm{mech}}\cdot\mathbf{d}
$
\end{adjustbox}
\]
\noindent This places the confinement and mechanical work term on the support page.\par
\noindent\textbf{3. Magnetic Helicity Invariant}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
H_M=\int_V\mathbf{A}\cdot\mathbf{B}\,dV
$
\end{adjustbox}
\]
\noindent This closes the constrained-field support chain with the helicity invariant.\par

\clearpage
\noindent\textbf{[ID 0371] Constrained Dipole Configuration}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Constrained Dipole Configuration is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This definition sets up a mechanically constrained dipole pair whose fields do not cancel but form nested loops due to separation and confinement. \textbf{Contextual meaning:} The entry reads Constrained Dipole Configuration as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the constrained dipole configuration as a real field construction instead of truncated prose fragments. \textbf{Lemma support:} Opposing Dipole Moments; Constraint Energy Potential; Magnetic Helicity Invariant.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The qubit is treated as both a Hilbert-space state and a geometric object embedded into the Trawinistic manifold.

\tzpsection{Equation Grounding}
Equation anchors: psi(r,z)=A , r ,exp !(-ratio (r-R) to the power 2+z to the power 2 sigma to the power 2 ); mathbf v(r,phi,z)=Big(ratio 1 r partial sub zpsi, ; q(r,z), ; -ratio 1 r partial sub rpsiBig),; abladot v=0; and q(r,z)=S ,ratio psi(r,z) r. Proof route: show that the stated dipole locations and single-dipole field law combine into the constrained total field configuration. Formalization route: prove that superposition of the two dipole sectors and the constraint sector yields the stated total field.

\tzpsection{Interpretive Role}
The entry now states the constrained dipole configuration as a real field construction instead of truncated prose fragments.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Opposing Source-Sink Localization}: The precise mathematical placement of a positive and negative magnetic pole at fixed, unmoving coordinates in space.
\item \textbf{Superposed Magnetic Field Lines}: The geometric map created when the outward flux of one pole perfectly bends to meet the inward pull of its partner.
\item \textbf{Far-Field Cancellation Effects}: The property where the opposing forces of the two poles rapidly neutralize each other at large distances from the central axis.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0371]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0371_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0371] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Constrained Dipole Configuration}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the Constrained Dipole Configuration entry receives the dipole, constraint-energy, and
helicity equations from the cosmological\textbackslash{}\_constant source, p...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Constrained Dipole Configuration is valid as a tensorial/geometric statement when the
stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0371_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
