\section*{ID6753: Branching Measure (Mode Mixing)}
\paragraph{Metadata.}
PiID: 0419947455385 | RTEID: RTE:P26223.3987:T5.5090 | UUID: ffd11b17-2799-530e-a697-1e15f72a880e

\paragraph{Canonical Statement.}
\#\#\# E — Branching measure (mode mixing) - Take angular spectrum and compute the ratio of power in the top peak to adjacent modes: \textbackslash{}[ M = \textbackslash{}frac\{|A\_\{m\textasciicircum{}*\}|\textasciicircum{}2\}\{\textbackslash{}sum\_\{m\textbackslash{}ne m\textasciicircum{}*\} |A\_m|\textasciicircum{}2\}. \textbackslash{}] - Low \textbackslash{}(M\textbackslash{}) + many nearby modes → branching / mode-mixing (fractal/IFS-like behavior). High \textbackslash{}(M\textbackslash{}) → pure spikes (simple aperture diffraction). - **Interpretation:** branching observed ⇒ structural vortex dynamics or multi-scale IFS orientation rules in the image.

\paragraph{Canonical Equation.}
\[
M = \frac{|A_{m^*}|^2}{\sum_{m\ne m^*} |A_m|^2}.
\]

\paragraph{Dictionary.}
E — Branching measure (mode mixing) - Take angular spectrum and compute the ratio of power in the top peak to adjacent modes: - Low \textbackslash{}(M\textbackslash{}) + many nearby modes → branching / mode-mixing (fractal/IFS-like behavior) [ID6753]

\paragraph{Encyclopedia.}
Branching Measure (Mode Mixing) is a series / summation, written M = frac|A\_m\textasciicircum{}*|\textasciicircum{}2∑\_mne m\textasciicircum{}* |A\_m|\textasciicircum{}2.. It is expressed as a sum or series over modes or indices, superposing discrete contributions. It is built from A\_m\textasciicircum{}*, m, A\_m, defining M. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
