\tzpanchor{0273}
\tzpentryheader{0273}{Bayesian Posterior for Gyromagnetic Genesis}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{ce6900c2-8515-5a57-822f-c63752f660ba}}\\
\textbf{PiID} & \tzpcode{3266482133936} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{280}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1060.1196 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.7468 rad}\\
\textbf{TZPID} & \tzpcode{ID0273} & \textbf{Node Dependencies}\quad \tzpidref{0272}\\
\textbf{Registry} & \tzpcode{registry\_id\_0273} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Assuming a prior probability of 0.05 for the gyromagnetic genesis hypothesis and a likelihood of about 0.047 based on twelve independent observables, the posterior probability is approximately 0.71.

\tzpsection{Canonical Equation}
\[
\Phi = n\Phi_0 = n\frac{h}{2e} \approx n \times 2.07 \times 10^{-15} \text{ Wb}
\]
\[
S = |E(\theta_1, \theta_2) - E(\theta_1, \theta_2')| + |E(\theta_1', \theta_2) + E(\theta_1', \theta_2')| > 2
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Phi$: flux, phase, or topological map term in the source equation.
    \item $n$: integer mode index.
    \item $\Phi_0$: reference zero-point flux or normalization flux.
    \item $S$: source equation symbol.
    \item $E$: source equation symbol.
    \item $\theta_1$: source equation symbol.
    \item $\theta_2$: source equation symbol.
    \item $\mu$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0273 generated source Wolfram model *)
ClearAll[K0273, Cr0273, T, R, A, W, I, N];
eq0273$1 = HoldForm[Phi == nPhi0 == n[h/(2*e)] == (n*2.07)/10^15];
eq0273$2 = HoldForm[Inequality[S, Equal, Abs[E[theta1, theta2] - E[theta1, Derivative[1][theta2]]] + Abs[E[Derivative[1][theta1], theta2] + E[Derivative[1][theta1], Derivative[1][theta2]]], Greater, 2]];
eq0273$3 = HoldForm[log10[mu/(MR^2*omega)] == -16];

K0273 = HoldForm[{eq0273$1, eq0273$2, eq0273$3}];

N = "normalized TRAWIN closure object for Bayesian Posterior for Gyromagnetic Genesis";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0273[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0273 = Cr0273[K0273];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Bayesian Posterior for Gyromagnetic Genesis.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0273] Bayesian Posterior for Gyromagnetic Genesis}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mathcal{E}:\rho\mapsto \mathcal{E}(\rho).
\end{equation}

\paragraph{CPTP Condition.}
\begin{equation}
\mathcal{E}\ \text{is completely positive and trace-preserving}.
\end{equation}

\paragraph{Primary Derivation.}
Let $\rho$ be a density operator. A quantum channel maps an input state into an output state:
\begin{equation}
\rho'=\mathcal{E}(\rho).
\end{equation}

Physical admissibility requires positivity not only on the original system, but also on any extended system:
\begin{equation}
(\mathcal{E}\otimes I_n)(X)\geq 0 .
\end{equation}

It must also preserve total probability:
\begin{equation}
\operatorname{Tr}(\mathcal{E}(\rho))=\operatorname{Tr}(\rho).
\end{equation}

Thus,
\begin{equation}
\boxed{
\mathcal{E}:\rho\mapsto\mathcal{E}(\rho)
\quad
\text{is CPTP}.
}
\end{equation}

\paragraph{Interpretation.}
A quantum channel is the admissible state-transition map for density operators, including TZP-curvature transport corrections.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Bayesian Posterior for Gyromagnetic Genesis by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
\Phi = n\Phi_0 = n\frac{h}{2e} \approx n \times 2.07 \times 10^{-15} \text{ Wb}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
S = |E(\theta_1, \theta_2) - E(\theta_1, \theta_2')| + |E(\theta_1', \theta_2) + E(\theta_1', \theta_2')| > 2
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\log_{10}\!\left(\frac{\mu}{MR^2\omega}\right)=-16
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0273] Bayesian Posterior for Gyromagnetic Genesis}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Bayesian Posterior for Gyromagnetic Genesis is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Assuming a prior probability of 0.05 for the gyromagnetic genesis hypothesis and a likelihood of about 0.047 based on twelve independent observables, the posterior probability is approximately 0.71. \textbf{Contextual meaning:} The entry reads Bayesian Posterior for Gyromagnetic Genesis as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform tertiary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
A quantum channel is the admissible state-transition map for density operators, including TZP-curvature transport corrections.

\tzpsection{Equation Grounding}
Equation anchors: p(thetamid D)=ratio p(Dmidtheta)p(theta) p(D); Lambda=ratio B to the power 2 mu sub 0rhoetaomega; and log sub 10 (ratio mu MR to the power 2omega )=-16. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform tertiary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Probability Update for Field Origin Models}: The statistical methodology used to calculate the likelihood that a magnetic field was generated by internal dynamo action rather than inherited from a primordial source.
\item \textbf{Likelihood of Seed-Field Amplification}: The calculated mathematical confidence that a tiny, random magnetic fluctuation could successfully grow into a massive planetary field given the system's parameters.
\item \textbf{Evidential Weighting of Dynamo Onset}: The rigorous statistical comparison of competing theories for magnetic genesis, heavily penalizing models that require massive, unexplained initial magnetic starting conditions.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0273]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0273_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0273] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Bayesian Posterior for Gyromagnetic Genesis}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} assuming a prior probability of 0.05 for the gyromagnetic genesis hypothesis and a
likelihood of about 0.047 based on twelve independent observable...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Bayesian Posterior for Gyromagnetic Genesis is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0273_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
