\tzpanchor{0386}
\tzpentryheader{0386}{Alfv\'en Wave Resonance Condition}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9f35890e-8998-5409-b5bd-39dd5b722112}}\\
\textbf{PiID} & \tzpcode{6951941511609} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{393}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1498.9237 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.4698 rad}\\
\textbf{TZPID} & \tzpcode{ID0386} & \textbf{Node Dependencies}\quad \tzpidref{0385}\\
\textbf{Registry} & \tzpcode{registry\_id\_0386} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Dispersion Law & Standing Quantization\\
\textbf{Closure Support} & Mode Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In a gyromagnetic system, resonant modes satisfy a modified dispersion relation in which the square of the frequency equals the square of the wavenumber times the square of the Alfv\'en velocity, corrected by finite gyroradius and sound speed terms. Resonance occurs when the driving frequency matches one of these eigenfrequencies.

\tzpsection{Canonical Equation}
\[
\omega_{n}=k_{n}v_{\mathrm{A}},
\qquad
v_{\mathrm{A}}=\frac{B}{\sqrt{\mu_{0}\rho}}
\]
\[
k_{n}=\frac{n\pi}{L_{\parallel}},
\qquad
\omega_{n}=\frac{n\pi v_{\mathrm{A}}}{L_{\parallel}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\omega_{n}$: mode-indexed angular frequency.
    \item $n$: integer mode index.
    \item $k_{n}$: mode-indexed wavenumber.
    \item $v_{\mathrm{A}}$: Alfven velocity or carrier speed.
    \item $B$: magnetic field magnitude.
    \item $\mu_{0}$: vacuum permeability constant.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\pi$: source equation symbol.
    \item $L_{\parallel}$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0386 generated source Wolfram model *)
ClearAll[K0386, Cr0386, T, R, A, W, I, N];
eq0386$1 = HoldForm[TZPSequence[omegaN == kNvA, vA == B/sqrt[mu0*rho]]];
eq0386$2 = HoldForm[TZPSequence[kN == nPi/LParallel, omegaN == (nPi*vA)/LParallel]];
eq0386$3 = HoldForm[omega == kParallelvA];
eq0386$4 = HoldForm[kN == nPi/LParallel];
eq0386$5 = HoldForm[omegaN == nPi*(vA/LParallel)];

K0386 = HoldForm[{eq0386$1, eq0386$2, eq0386$3, eq0386$4, eq0386$5}];

N = "normalized TRAWIN closure object for Alfv\'en Wave Resonance Condition";
I = "Mode Closure integration/comparison layer";
W = "Standing Quantization wave or operator carrier";
A = "Dispersion Law admissible action/amplitude condition";
R = "Standing Quantization rotation/curl preservation layer";
T = "Dispersion Law local source condition";

Cr0386[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0386 = Cr0386[K0386];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Dispersion Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Standing Quantization rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Dispersion Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Standing Quantization wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Mode Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Alfv\textbackslash{}'en Wave Resonance Condition.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0386] Alfv\'en Wave Resonance Condition}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primordial Ansatz.}
\begin{equation}
\mathbf{L}(t)=\mathbf{L}_0 .
\end{equation}

\paragraph{Source-Integrated History.}
\begin{equation}
\mathbf{L}(t)
=
\mathbf{L}_0
+
\int_0^t
\boldsymbol{\tau}_{\mathrm{em}}(t')
\,\mathrm{d}t' .
\end{equation}

\paragraph{Null Primordial Default.}
\begin{equation}
\mathbf{L}_0\approx 0 .
\end{equation}

\paragraph{Primary Derivation.}
If angular momentum is treated as primordial, then it is represented as a fixed inherited value:
\begin{equation}
\mathbf{L}(t)=\mathbf{L}_0.
\end{equation}

The Trawinistic alternative accounts for observed angular momentum by integrating generated torque through time:
\begin{equation}
\mathbf{L}(t)
=
\mathbf{L}_0
+
\int_0^t
\boldsymbol{\tau}_{\mathrm{em}}(t')
\,\mathrm{d}t' .
\end{equation}

Under the null primordial hypothesis:
\begin{equation}
\boxed{
\mathbf{L}_0\approx 0,
\qquad
\mathbf{L}(t)
\approx
\int_0^t
\boldsymbol{\tau}_{\mathrm{em}}(t')
\,\mathrm{d}t' .
}
\end{equation}

\paragraph{Interpretation.}
This entry replaces unexplained inherited rotation with a source-history explanation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Alfv\textbackslash{}'en Wave Resonance Condition by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Dispersion Law}\par
\[
\omega=k_{\parallel}v_{\mathrm{A}}
\]
\noindent This fixes the traveling Alfv\textbackslash{}'en carrier that later entries quantize and redistribute.\par
\noindent\textbf{2. Standing Quantization}\par
\[
k_{n}=n\pi/L_{\parallel}
\]
\noindent This turns the continuous wave law into an admissible standing-mode ladder on the bounded carrier.\par
\noindent\textbf{3. Mode Closure}\par
\[
\omega_{n}=n\pi v_{\mathrm{A}}/L_{\parallel}
\]
\noindent This closes the progression by tying the standing spectrum to an actual mode-index relation.\par

\clearpage
\noindent\textbf{[ID 0386] Alfv\'en Wave Resonance Condition}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Alfv en Wave Resonance Condition is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} In a gyromagnetic system, resonant modes satisfy a modified dispersion relation in which the square of the frequency equals the square of the wavenumber times the square of the Alfv en velocity, corrected by finite gyroradius and sound speed terms. Resonance occurs when the driving frequency matches one of these eigenfrequencies. \textbf{Contextual meaning:} The entry reads Alfv en Wave Resonance Condition as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The hinge entry turns the terminal synchronization logic of the third book into the carried bridge law that the quaternary volume repeatedly acts on. \textbf{Lemma support:} Dispersion Law; Standing Quantization; Mode Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This entry replaces unexplained inherited rotation with a source-history explanation.

\tzpsection{Equation Grounding}
Equation anchors: ed = (mu0/ g)(HM sub final - HM sub initial ); csv,,MB sub e20207d126a4 ,registry sub id sub 0406,[ID 0406],THE POYNTING-FLUX DAMPING ALGORITHM,,best sub match ,ell sub max approximately ratio pi theta sub res; and ell sub max approximately ratio pi theta sub res. Proof route: show that the bounded-mode condition follows from the dispersion law once the carrier is normalized on the finite rotating radius. Formalization route: prove that the standing-mode frequency formula is equivalent to the bounded Alfv en carrier under TRAWIN normalization.

\tzpsection{Interpretive Role}
The hinge entry turns the terminal synchronization logic of the third book into the carried bridge law that the quaternary volume repeatedly acts on.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Bounded Wavenumber Quantization}: The restriction that only magnetic waves of very specific lengths can survive bouncing back and forth inside the plasma cavity.
\item \textbf{Density-Dependent Phase Velocity}: The calculation showing that magnetic waves travel faster when the magnetic pull is strong, but slow down when the plasma gets heavy.
\item \textbf{Parallel-Axis Harmonic Tuning}: The requirement that the waves must fit perfectly along the main direction of the magnetic field to create a stable, standing vibration.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0386]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0386_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0386] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Alfv\'en Wave Resonance Condition}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in a gyromagnetic system, resonant modes satisfy a modified dispersion relation in which
the square of the frequency equals the square of the waven...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Alfvén Wave Resonance Condition is valid as a spectral relation when frequency, phase,
and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0386_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
