\section*{ID8826: UNIVERSAL ELSASSER CRITICALITY (AXIOM 3) Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 1333123948049 | RTEID: RTE:P34273.3181:T6.2064 | UUID: f7e78130-c660-5ab6-9b8a-b8d45792c006

\paragraph{Canonical Statement.}
[ID 1157] UNIVERSAL ELSASSER CRITICALITY (AXIOM 3) Canonical Statutory Formula: \$|E\_B - E\_\{rot\}| < \textbackslash{}epsilon \textbackslash{}implies \textbackslash{}Lambda \textbackslash{}sim \textbackslash{}mathcal\{O\}(1)\$ Formal Technical Dissertation: Axiom stating that systems self-organize toward an Elsasser number of unity, where magnetic energy density \$E\_B\$ balances rotational energy density \$E\_\{rot\}\$. This defines the stable attractor state in phase space. Source: [26]

\paragraph{Canonical Equation.}
\[
|E_B - E_{rot}| < \epsilon \implies \Lambda \sim \mathcal{O}(1)
\]

\paragraph{Dictionary.}
UNIVERSAL ELSASSER CRITICALITY (AXIOM 3) Canonical Statutory Formula: \$ E\_B - E\_rot < O(1)\$ Formal Technical Dissertation: Axiom stating that systems self-organize toward an Elsasser number of unity, where magnetic energy density E\_B balances rotational energy density E\_rot.

\paragraph{Encyclopedia.}
UNIVERSAL ELSASSER CRITICALITY (AXIOM 3) Canonical Statutory Formula is a scaling / order-of-magnitude relation, written |E\_B - E\_rot| < ε ⟹ Λ ∼ O(1). It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from ε, Λ, E\_B, E\_rot, O. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
