\tzpanchor{0037}
\tzpentryheader{0037}{Emergent Rotation Principle}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{658ba713-3c0c-58b1-95a1-2118ef9bf800}}\\
\textbf{PiID} & \tzpcode{9716939937510} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{44}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{143.6792 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.2367 rad}\\
\textbf{TZPID} & \tzpcode{ID0037} & \textbf{Node Dependencies}\quad \tzpidref{0026}\\
\textbf{Registry} & \tzpcode{registry\_id\_0037} & \textbf{Scale}\quad rotation-generation\\
\textbf{LOC Classification} & QC809 rotation and torque & QC801 electromagnetism\\
\textbf{arXiv Classification} & Primary: astro-ph.SR \quad Cross-list: physics.class-ph, gr-qc & \\
\textbf{Primary Support} & Current-Generated Angular Momentum & Electromagnetic Torque Source\\
\textbf{Closure Support} & Rotation-Magnetism Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Rotation is generated continuously through electromagnetic torques rather than being an initial condition.

\tzpsection{Canonical Equation}
\[
L
=
\int_{V}
\bigl(
\mathbf{r}\times\mathbf{J}
\bigr)\,d^{3}x
\]
\[
\frac{dL}{dt}
=
\int_{V}
\bigl(
\mathbf{J}\times\mathbf{B}
\bigr)\,d^{3}x
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $V$: auxiliary target state or comparison variable.
    \item $J$: source equation symbol.
    \item $B$: magnetic field magnitude.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0037 generated source Wolfram model *)
ClearAll[K0037, Cr0037, T, R, A, W, I, N];
eq0037$1 = HoldForm[L == IntegralV[r*J]*d^3*x];
eq0037$2 = HoldForm[dL/dt == IntegralV[J*B]*d^3*x];
eq0037$3 = HoldForm[L*rightarrowPair[J, B]];

K0037 = HoldForm[{eq0037$1, eq0037$2, eq0037$3}];

N = "normalized TRAWIN closure object for Emergent Rotation Principle";
I = "Rotation-Magnetism Closure integration/comparison layer";
W = "Electromagnetic Torque Source wave or operator carrier";
A = "Current-Generated Angular Momentum admissible action/amplitude condition";
R = "Electromagnetic Torque Source rotation/curl preservation layer";
T = "Current-Generated Angular Momentum local source condition";

Cr0037[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0037 = Cr0037[K0037];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Current-Generated Angular Momentum local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Electromagnetic Torque Source rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Current-Generated Angular Momentum admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Electromagnetic Torque Source wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Rotation-Magnetism Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Emergent Rotation Principle.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0037] Emergent Rotation Principle}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
L
=
\int_V
(\mathbf{r}\times\mathbf{J})
\,\mathrm{d}^3x .
\end{equation}

\paragraph{Secondary Evolution Equation.}
\begin{equation}
\frac{\mathrm{d}L}{\mathrm{d}t}
=
\int_V
(\mathbf{J}\times\mathbf{B})
\,\mathrm{d}^3x .
\end{equation}

\paragraph{Primary Derivation.}
Let $\mathbf{J}$ denote local current density and $\mathbf{r}$ the position vector inside a volume $V$.  
Angular momentum density is generated by the cross product:

\begin{equation}
\mathbf{r}\times\mathbf{J}.
\end{equation}

Integrating this density over the volume gives total angular momentum:

\begin{equation}
\boxed{
L
=
\int_V
(\mathbf{r}\times\mathbf{J})
\,\mathrm{d}^3x .
}
\end{equation}

If local electromagnetic interaction drives rotational change, then the torque density is modeled by:

\begin{equation}
\mathbf{J}\times\mathbf{B}.
\end{equation}

Therefore,

\begin{equation}
\boxed{
\frac{\mathrm{d}L}{\mathrm{d}t}
=
\int_V
(\mathbf{J}\times\mathbf{B})
\,\mathrm{d}^3x .
}
\end{equation}

\paragraph{Interpretation.}
Rotation is treated as an emergent accumulated effect of local electromagnetic current and field interactions rather than as a primordial conserved input.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Emergent Rotation Principle by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Current-Generated Angular Momentum}\par
\[
L
=
\int_{V}
\bigl(
\mathbf{r}\times\mathbf{J}
\bigr)\,d^{3}x
\]
\noindent This identifies angular momentum as a derived quantity built from current structure.\par
\noindent\textbf{2. Electromagnetic Torque Source}\par
\[
\frac{dL}{dt}
=
\int_{V}
\bigl(
\mathbf{J}\times\mathbf{B}
\bigr)\,d^{3}x
\]
\noindent This provides the dynamical mechanism that generates or changes rotation.\par
\noindent\textbf{3. Rotation-Magnetism Closure}\par
\[
L \leftrightarrow (\mathbf{J},\mathbf{B})
\]
\noindent This closes the progression by stating that rotational behavior is inseparable from the electromagnetic sector in the Trawinistic reading.\par

\clearpage
\noindent\textbf{[ID 0037] Emergent Rotation Principle}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Emergent Rotation Principle is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Rotation is generated continuously through electromagnetic torques rather than being an initial condition. \textbf{Contextual meaning:} The entry reads Emergent Rotation Principle as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This principle opens the rotation-and-magnetism subchain of the registry. It supports the Elsasser attractor, equipartition, and the later universal scaling laws by treating rotation as an effect of structured current flow. \textbf{Lemma support:} Current-Generated Angular Momentum; Electromagnetic Torque Source; Rotation-Magnetism Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Rotation is treated as an emergent accumulated effect of local electromagnetic current and field interactions rather than as a primordial conserved input.

\tzpsection{Equation Grounding}
Equation anchors: The total angular momentum LLL of a system in a Trawinistic manifold is not a primordial conserved quantity but emerges via L=intV(rtimes J) d3xL = integral V (textbackslash mathbf r timestextbackslash mathbf J )textbackslash, d to the power 3xL=intV(rtimes J)d3x with Jtextbackslash mathbf J J driven by local electromagnetic fields according to dLdt=intV(Jtimes B) d3xratio d L d t =integral V (textbackslash mathbf J times textbackslash mathbf B )textbackslash, d to the power 3xdtdL=intV(Jtimes B)d3x. The total angular momentum LLL of a system in a Trawinistic manifold is not a primordial conserved quantity but emerges via L=intV(rtimes J) d3xL = integral V (textbackslash mathbf r timestextbackslash mathbf J )textbackslash, d to the power 3xL=intV(rtimes J)d3x with Jtextbackslash mathbf J J driven by local electromagnetic fields according to dLdt=intV(Jtimes B) d3xratio d L d t =integral V (textbackslash mathbf J times textbackslash mathbf B )textbackslash, d to the power 3xdtdL=intV(Jtimes B)d3x.

\tzpsection{Interpretive Role}
This principle opens the rotation-and-magnetism subchain of the registry. It supports the Elsasser attractor, equipartition, and the later universal scaling laws by treating rotation as an effect of structured current flow.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Emergent Rotation Principle}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Emergent Rotation Principle Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Principle Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0037]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0037_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0037] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Emergent Rotation Principle}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} rotation is generated continuously through electromagnetic torques rather than being an
initial condition

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Emergent Rotation Principle is valid when the total tensorial quantity is conserved
under the stated constraint.''\\
\textbf{Proof:} The source statement identifies a conserved balance law. Reading 0037 as a proposition,
validity follows by requiring the full stress, flux, or current contribution to be
included before the divergence or balance condition is evaluated.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conserved total-structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0037_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
