\section*{ID9436: Definition of рқң”>рқң”maxвҮ’рқҗөem}
\paragraph{Metadata.}
PiID: 4687886144458 | RTEID: RTE:P36642.0835:T3.8262 | UUID: 6c502459-7bfc-5886-bc0c-6b40c2672541

\paragraph{Canonical Statement.}
an Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0444], [ID 0400] Node registry\_id\_0445 Support Titles Canonical Definition; Transfer Map; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links y=(рқңҷ0 ,...,рқңҷрқ‘ҒвҲ’1 , рқңғ0 ,..., рқңғрқ‘ҒвҲ’1 ) \$рқң”>рқң”maxвҮ’рқҗөem=1 ОҰ=рқ‘ӣОҰ0\$ [ID 0446] CALORIMETRIC ENTROPY VERIFICATION TZPID ID0446 UUID 68d77715-d2fc-5fdc-b3f7-5429fc3db252 Type Information Functional / Entropy Statement Scale informational LOC Classification Working routing: QA76.9 information and coding; QA614 topological data analysis arXiv Classification Primary: cs.IT; Cross-list: math.AT, math-ph Canonical Statement This entry develops calorimetric entropy verifi

\paragraph{Canonical Equation.}
\[
рқң”>рқң”maxвҮ’рқҗөem=1 ОҰ=рқ‘ӣОҰ0
\]

\paragraph{Dictionary.}
Definition of рқң”>рқң”maxвҮ’рқҗөem вҖ” рқң”>рқң”maxвҮ’рқҗөem=1 ОҰ=рқ‘ӣОҰ0

\paragraph{Encyclopedia.}
Definition of рқң”>рқң”maxвҮ’рқҗөem is an inequality / bound, written рқң”>рқң”maxвҮ’рқҗөem=1 ОҰ=рқ‘ӣОҰ0. It states an inequality or bound that constrains the admissible range of the quantity. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
