\tzpanchor{0075}
\tzpentryheader{0075}{Quantum Thermodynamics}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{29e24224-ea02-5343-bc6b-88c66d1f3118}}\\
\textbf{PiID} & \tzpcode{2089986280348} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{82}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{291.2417 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.4799 rad}\\
\textbf{TZPID} & \tzpcode{ID0075} & \textbf{Node Dependencies}\quad \tzpidref{0073}\\
\textbf{Registry} & \tzpcode{registry\_id\_0075} & \textbf{Scale}\quad quantum energy and entropy flow\\
\textbf{LOC Classification} & QC174 quantum thermodynamics & QC311 entropy and heat flow\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: cond-mat.stat-mech, hep-th & \\
\textbf{Primary Support} & Internal-Energy Balance & Entropy Change\\
\textbf{Closure Support} & TRAWIN Second Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Thermodynamic concepts remain but are modified by quantum coherence, curvature and the TZP; effective temperatures and entropy production include geometric contributions.

\tzpsection{Canonical Equation}
\[
\Delta S
\geq
\frac{Q}{T_{\mathrm{eff}}}
+
\Sigma_{\mathrm{TZP}}
\]
\[
\Delta U = Q + W
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S$: source equation symbol.
    \item $Q$: source equation symbol.
    \item $T_{\mathrm{eff}}$: source equation symbol.
    \item $U$: auxiliary source state or local chart variable.
    \item $W$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0075 generated source Wolfram model *)
ClearAll[K0075, Cr0075, T, R, A, W, I, N];
eq0075$1 = HoldForm[Delta*S >= Q/TEff + SigmaTZP];
eq0075$2 = HoldForm[Delta*U == Q + W];
eq0075$3 = HoldForm[Delta*S];

K0075 = HoldForm[{eq0075$1, eq0075$2, eq0075$3}];

N = "normalized TRAWIN closure object for Quantum Thermodynamics";
I = "TRAWIN Second Law integration/comparison layer";
W = "Entropy Change wave or operator carrier";
A = "Internal-Energy Balance admissible action/amplitude condition";
R = "Entropy Change rotation/curl preservation layer";
T = "Internal-Energy Balance local source condition";

Cr0075[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0075 = Cr0075[K0075];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Internal-Energy Balance local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Entropy Change rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Internal-Energy Balance admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Entropy Change wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TRAWIN Second Law integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum Thermodynamics.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0075] Quantum Thermodynamics}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\Delta U = Q+W .
\end{equation}

\begin{equation}
\Delta S
\geq
\frac{Q}{T_{\mathrm{eff}}}
+
\Sigma_{\mathrm{TZP}} .
\end{equation}

\paragraph{Primary Derivation.}
The first-law balance writes the change in internal energy as heat plus work:
\begin{equation}
\Delta U=Q+W .
\end{equation}

Entropy change is bounded below by heat exchange over an effective temperature:
\begin{equation}
\Delta S\geq \frac{Q}{T_{\mathrm{eff}}}.
\end{equation}

The TRAWIN correction includes an irreducible zero-point contribution $\Sigma_{\mathrm{TZP}}$, producing
\begin{equation}
\boxed{
\Delta S
\geq
\frac{Q}{T_{\mathrm{eff}}}
+
\Sigma_{\mathrm{TZP}} .
}
\end{equation}

\paragraph{Interpretation.}
Quantum thermodynamics links energy balance, entropy production, effective temperature, and zero-point correction.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum Thermodynamics by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Internal-Energy Balance}\par
\[
\Delta U = Q + W
\]
\noindent This fixes the energetic bookkeeping of the quantum process.\par
\noindent\textbf{2. Entropy Change}\par
\[
\Delta S
\]
\noindent This identifies the informational-thermodynamic quantity to be constrained.\par
\noindent\textbf{3. TRAWIN Second Law}\par
\[
\Delta S
\geq
\frac{Q}{T_{\mathrm{eff}}}
+
\Sigma_{\mathrm{TZP}}
\]
\noindent This closes the progression by inserting effective-temperature and zero-point corrections into the entropy bound.\par

\clearpage
\noindent\textbf{[ID 0075] Quantum Thermodynamics}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum Thermodynamics is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Thermodynamic concepts remain but are modified by quantum coherence, curvature and the TZP; effective temperatures and entropy production include geometric contributions. \textbf{Contextual meaning:} The entry reads Quantum Thermodynamics as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry links the information branch to energetic cost and entropy production. It provides the language needed for dissipation, transport, and irreversible quantum processes on TRAWIN backgrounds. \textbf{Lemma support:} Internal-Energy Balance; Entropy Change; TRAWIN Second Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Quantum thermodynamics links energy balance, entropy production, effective temperature, and zero-point correction.

\tzpsection{Equation Grounding}
Equation anchors: Quantum thermodynamics on the Trawinistic manifold studies energy, entropy and information flows in quantum systems; heat and work are defined via two-point measurement schemes, and the second law generalises to include curvature and zero-point contributions in the form DeltaSgeqQTeff+SigmaTZPDelta S geq ratio Q T eff + Sigma TZP DeltaSgeqTeffQ+SigmaTZP. Quantum thermodynamics on the Trawinistic manifold studies energy, entropy and information flows in quantum systems; heat and work are defined via two-point measurement schemes, and the second law generalises to include curvature and zero-point contributions in the form DeltaSgeqQTeff+SigmaTZPDelta S geq ratio Q T eff + Sigma TZP DeltaSgeqTeffQ+SigmaTZP.

\tzpsection{Interpretive Role}
This entry links the information branch to energetic cost and entropy production. It provides the language needed for dissipation, transport, and irreversible quantum processes on TRAWIN backgrounds.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{State-Level Thermodynamics}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Quantum-State Analogue}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Terminology}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0075]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0075_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0075] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum Thermodynamics}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} thermodynamic concepts remain but are modified by quantum coherence, curvature and the
TZP; effective temperatures and entropy production include g...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum Thermodynamics is valid as a formal dynamical law when the Hamiltonian or energy
operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0075_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
