\tzpanchor{0497}
\tzpentryheader{0497}{Project Scope Persistency Log}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{51a8267f-abd9-570e-a484-29b83e6e4613}}\\
\textbf{PiID} & \tzpcode{9129833673362} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{504}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1910.5453 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.1480 rad}\\
\textbf{TZPID} & \tzpcode{ID0497} & \textbf{Node Dependencies}\quad \tzpidref{0496}\\
\textbf{Registry} & \tzpcode{registry\_id\_0497} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 497 establishes the continuous integrity audit of the "Opera Omnia" dataset. By utilizing the 153,600 node addressing as a holographic index, the system ensures that every ID from 000 to 499 is cross referenced and persistently available. This prevents data fragmentation and ensures that the "Bridge Tunnel" logic remains unified as the project scales into Volume 02. Holographic Indexing: Uses the DAANSsphere to store the state of the registry itself. Metadata Closure: Confirms that all internal cross references (e.g., 1.185, 17.23, 17.2 kHz) are algebraically consistent.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
E_{\mathrm{scope}}=\{(r_i,c_i,t_i)\}_{i=1}^{N}
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $E_{\mathrm{scope}}$: source equation symbol.
    \item $r_i$: source equation symbol.
    \item $c_i$: source equation symbol.
    \item $t_i$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0497 generated source Wolfram model *)
ClearAll[K0497, Cr0497, T, R, A, W, I, N];
eq0497$1 = HoldForm[$EScope == {Tuple[rI, cI, tI]}*_*(i == 1)^N*$];

K0497 = HoldForm[{eq0497$1}];

N = "normalized TRAWIN closure object for Project Scope Persistency Log";
I = "Project Scope Persistency Log integration/comparison layer";
W = "Project Scope Persistency Log wave or operator carrier";
A = "Project Scope Persistency Log admissible action/amplitude condition";
R = "Project Scope Persistency Log rotation/curl preservation layer";
T = "Project Scope Persistency Log local source condition";

Cr0497[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0497 = Cr0497[K0497];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Project Scope Persistency Log local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Project Scope Persistency Log rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Project Scope Persistency Log admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Project Scope Persistency Log wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Project Scope Persistency Log integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Project Scope Persistency Log.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0497] Project Scope Persistency Log}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Bridge Frequency.}
\begin{equation}
f_{\mathrm{bridge}}=\frac{32}{27}f_0.
\end{equation}

\paragraph{Bridge Waveform.}
\begin{equation}
\Psi_{\mathrm{bridge}}(t)
=
G_{\sigma}(t)
\left[
\cos(2\pi f_1t)
-
\cos(2\pi f_2t+\theta)
\right].
\end{equation}

\paragraph{Primary Derivation.}
Let $f_0$ be a shared base frequency.  
The bridge frequency is fixed by:

\begin{equation}
f_{\mathrm{bridge}}=\frac{32}{27}f_0.
\end{equation}

A localized bridge is created by applying a Gaussian window $G_\sigma(t)$ to a flipped and twisted carrier pair:

\begin{equation}
\boxed{
\Psi_{\mathrm{bridge}}(t)
=
G_{\sigma}(t)
\left[
\cos(2\pi f_1t)
-
\cos(2\pi f_2t+\theta)
\right].
}
\end{equation}

\paragraph{Interpretation.}
The flip--twist transform creates a localized beat-and-cancellation bridge from paired carriers.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Project Scope Persistency Log by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
E_{\mathrm{scope}}=\{(r_i,c_i,t_i)\}_{i=1}^{N}
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0497] Project Scope Persistency Log}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Project Scope Persistency Log is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 497 establishes the continuous integrity audit of the "Opera Omnia" dataset. By utilizing the 153,600 node addressing as a holographic index, the system ensures that every ID from 000 to 499 is cross referenced and persistently available. This prevents data fragmentation and ensures that the "Bridge Tunnel" logic remains unified as the project scales into Volume 02. Holographic Indexing: Uses the DAANSsphere to store the state of the registry itself. Metadata Closure: Confirms that all internal cross references (e.g., 1.185, 17.23, 17.2 kHz) are algebraically consistent.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
E_{\mathrm{scope}}=\{(r_i,c_i,t_i)\}_{i=1}^{N}
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 497 establishes the continuous integrity audit of the "Opera Omnia" dataset. By utilizing the 153,600 node addressing as a holographic index, the system ensures that every ID from 000 to 499 is cross referenced and persistently available. This prevents data fragmentation and ensures that the "Bridge Tunnel" logic remains unified as the project scales into Volume 02. Holographic Indexing: Uses the DAANSsphere to store the state of the registry itself. Metadata Closure: Confirms that all internal cross references (e.g., 1.185, 17.23, 17.2 kHz) are algebraically consistent.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Project Scope Persistency Log by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Project Scope Persistency Log; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0497]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0497].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0497] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Project Scope Persistency Log}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} The flip--twist transform creates a localized beat-and-cancellation bridge from paired
carriers

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``PROJECT SCOPE PERSISTENCY LOG is valid when the stated operator maps admissible inputs
into the declared target class.''\\
\textbf{Proof:} The source statement is read as an operator or transformation. The proof obligation is
type preservation: admissible inputs must land in the target object without breaking the
stated constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- operator-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0497].
\par\endgroup
\vfill
\endgroup
\endgroup
