\tzpanchor{0008}
\tzpentryheader{0008}{Non-Linearity Constant $K_{\mathrm{NL}}$}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9e40ddae-727e-5aa3-8c06-19198be44786}}\\
\textbf{PiID} & \tzpcode{3589793238462} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{15}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{31.0658 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.0512 rad}\\
\textbf{TZPID} & \tzpcode{ID0008} & \textbf{Node Dependencies}\quad \tzpidref{0004}\\
\textbf{Registry} & \tzpcode{registry\_id\_0008} & \textbf{Scale}\quad field\\
\textbf{LOC Classification} & Q175 nonlinearity and field response & QA614 differential operators\\
\textbf{arXiv Classification} & Primary: nlin.CD & Cross-list: math-ph, gr-qc\\
\textbf{Primary Support} & Hessian-to-Gradient Ratio & TZP Limit of Field Response\\
\textbf{Closure Support} & Normalized Non-Linearity & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
$\KNL$ is a dimensionless constant defined by the ratio $\KNL = \frac{\lVert \Nabla^2 \PhiField \rVert}{\lVert \Nabla \PhiField \rVert^2}$ evaluated in the limit as the field $\PhiField$ approaches the TZP, with $\Nabla$ denoting the Trawinistic connection.

\tzpsection{Canonical Equation}
\[
K_{\mathrm{NL}}
=
\frac{\lVert \nabla^{2}\Phi \rVert}{\lVert \nabla\Phi \rVert^{2}}
\]
\[
K_{\mathrm{NL}}^{\mathrm{TZP}}
=
\lim_{x \to p}
\frac{\lVert \nabla^{2}\Phi(x) \rVert}{\lVert \nabla\Phi(x) \rVert^{2}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $K_{\mathrm{NL}}$: source equation symbol.
    \item $\Phi$: flux, phase, or topological map term in the source equation.
    \item $g_{\mathrm{norm}}$: source equation symbol.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $V$: auxiliary target state or comparison variable.
    \item $P$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
    \item $T$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $A$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0008 generated source Wolfram model *)
ClearAll[K0008, Cr0008, T, R, A, W, I, N];
eq0008$1 = HoldForm[KNL == (lVert*Grad^2*PhirVert)/(lVert*GradPhirVert^2)];
eq0008$2 = HoldForm[KNL^TZP == LimitXp[(lVert*Grad^2*Phi[x]*rVert)/(lVert*GradPhi[x]*rVert^2)]];
eq0008$3 = HoldForm[KNLNorm == NormalizeTRAWIN[(lVert*Grad^2*PhirVert)/(lVert*GradPhirVert^2), LimitXp*KNL, gNorm]];

K0008 = HoldForm[{eq0008$1, eq0008$2, eq0008$3}];

N = "normalized TRAWIN closure object for Non-Linearity Constant $K_{\mathrm{NL}}$";
I = "Normalized Non-Linearity integration/comparison layer";
W = "TZP Limit of Field Response wave or operator carrier";
A = "Hessian-to-Gradient Ratio admissible action/amplitude condition";
R = "TZP Limit of Field Response rotation/curl preservation layer";
T = "Hessian-to-Gradient Ratio local source condition";

Cr0008[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0008 = Cr0008[K0008];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Hessian-to-Gradient Ratio local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TZP Limit of Field Response rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Hessian-to-Gradient Ratio admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TZP Limit of Field Response wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Non-Linearity integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Non-Linearity Constant \$K\_\{\textbackslash{}mathrm\{NL\}\}\$.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0008] Non-Linearity Constant $K_{\mathrm{NL}}$}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
K_{\mathrm{NL}}
=
\frac{\left\lVert \nabla^{2}\varphi\right\rVert}
{\left\lVert \nabla\varphi\right\rVert^{2}} .
\end{equation}

\paragraph{Primary Derivation.}
Let $\varphi$ be a scalar field on the Trawinistic manifold.  
The first-order variation of the field is measured by the gradient:

\begin{equation}
\nabla\varphi .
\end{equation}

The second-order curvature or bending of the field is measured by:

\begin{equation}
\nabla^2\varphi .
\end{equation}

A dimensionless measure of non-linearity should compare second-order deformation against the square of first-order variation. Therefore define:

\begin{equation}
K_{\mathrm{NL}}
=
\frac{\text{second-order field deformation}}
{\text{first-order field variation squared}} .
\end{equation}

Substituting the appropriate differential norms gives:

\begin{equation}
\boxed{
K_{\mathrm{NL}}
=
\frac{\left\lVert \nabla^{2}\varphi\right\rVert}
{\left\lVert \nabla\varphi\right\rVert^{2}} .
}
\end{equation}

\paragraph{Interpretation.}
$K_{\mathrm{NL}}$ measures how sharply a field bends relative to its local rate of change. Large values indicate strong nonlinear behavior near the TZP.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Non-Linearity Constant \$K\_\{\textbackslash{}mathrm\{NL\}\}\$ by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Hessian-to-Gradient Ratio}\par
\[
K_{\mathrm{NL}}
=
\frac{\lVert \nabla^{2}\Phi \rVert}{\lVert \nabla\Phi \rVert^{2}}
\]
\noindent This defines the raw field-response quotient and gives a direct scalar measure of nonlinear amplification.\par
\noindent\textbf{2. TZP Limit of Field Response}\par
\[
K_{\mathrm{NL}}^{\mathrm{TZP}}
=
\lim_{x \to p}
\frac{\lVert \nabla^{2}\Phi(x) \rVert}{\lVert \nabla\Phi(x) \rVert^{2}}
\]
\noindent This localizes the constant to the singular regime where the framework expects the strongest deviation from linear behavior.\par
\noindent\textbf{3. Normalized Non-Linearity}\par
\[
K_{\mathrm{NL}}^{\mathrm{norm}}
=
\operatorname{Normalize}_{\mathrm{TRAWIN}}
\!\left(
\frac{\lVert \nabla^{2}\Phi \rVert}{\lVert \nabla\Phi \rVert^{2}},\,
\lim_{x \to p} K_{\mathrm{NL}},\,
g_{\mathrm{norm}}
\right)
\]
\noindent This closes the progression by making the non-linearity constant comparable across admissible singular geometries rather than tied to one raw coordinate description.\par

\clearpage
\noindent\textbf{[ID 0008] Non-Linearity Constant $K_{\mathrm{NL}}$}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Non Linearity Constant K sub NL label id-008-nonlinearity-constant-k sub nlk sub textnlk sub nl is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} KNL is a dimensionless constant defined by the ratio KNL = ratio lVert Nabla to the power 2 PhiField rVert lVert Nabla PhiField rVert to the power 2 evaluated in the limit as the field PhiField approaches the TZP, with Nabla denoting the Trawinistic connection. \textbf{Contextual meaning:} The entry reads Non Linearity Constant K sub NL label id-008-nonlinearity-constant-k sub nlk sub textnlk sub nl as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Hessian-to-Gradient Ratio; TZP Limit of Field Response; Normalized Non-Linearity.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
K sub NL measures how sharply a field bends relative to its local rate of change. Large values indicate strong nonlinear behavior near the TZP.

\tzpsection{Equation Grounding}
Equation anchors: K sub NL =ratio lVert abla to the power 2 varphirVert lVert ablavarphirVert to the power 2 , K sub NL =ratio lVert abla to the power 2 varphirVert lVert ablavarphirVert to the power 2 ,.

\tzpsection{Interpretive Role}
This constant marks the point where perturbative intuition becomes unreliable and singular corrections dominate. It is especially useful for deciding when later field equations need explicitly TRAWIN-normalized rather than linearized treatment.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Non Linearity Constant Nl Label}: normalization vocabulary for fixed form, invariant comparison, or TRAWIN admissibility.
\item \textbf{Non Linearity Constant Normalization Analogue}: normalization vocabulary for fixed form, invariant comparison, or TRAWIN admissibility.
\item \textbf{Nl Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0008]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0008_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0008] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Non-Linearity Constant $K_{\mathrm{NL}}$}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:}  is a dimensionless constant defined by the ratio  = \textbackslash{}lVert \textbackslash{}Nabla\textasciicircum{}2 \textbackslash{}PhiField \textbackslash{}rVert
\textasciicircum{}2 evaluated in the limit as the field  approaches the...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Non‑Linearity Constant K\_\{\textbackslash{}mathrm\{NL is valid as a formal registry statement when its
source equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that  is a dimensionless constant defined by the ratio  =
\textbackslash{}lVert \textbackslash{}Nabla\textasciicircum{}2 \textbackslash{}PhiField \textbackslash{}rVert \textasciicircum{}2 evaluated in the limit as the field  approaches
the TZP, with  denoting the Trawinistic connection. K\_NL measures how sharply a
field bends relative to its local rate of change. Large values indicate strong nonlinear
behavior near the TZP.. The CHL validation treats the equation as the formal anchor and
the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0008_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
