\tzpanchor{0312}
\tzpentryheader{0312}{Scale Invariance of Recursive Toroidal Encoding}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{530cb883-fe28-541d-a7af-c9882ef93247}}\\
\textbf{PiID} & \tzpcode{3155881748815} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{319}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1211.5653 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9963 rad}\\
\textbf{TZPID} & \tzpcode{ID0312} & \textbf{Node Dependencies}\quad \tzpidref{0311}\\
\textbf{Registry} & \tzpcode{registry\_id\_0312} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
There is no privileged scale in the recursive toroidal encoding; refining or coarsening the sampling density corresponds to different depth encodings of the same torus, not to a change in geometry.

\tzpsection{Canonical Equation}
\[
\Phi_{\lambda n}
=
\mathcal{R}_{\lambda}\!\left(\Phi_{n}\right),
\qquad
\mathcal{R}_{\lambda}:T^{2}\to T^{2}
\]
\[
\mathcal{I}\!\left(\mathcal{R}_{\lambda}\Phi\right)
=
\mathcal{I}(\Phi)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Phi_{\lambda_{n}}$: flux, phase, or topological map term in the source equation.
    \item $n$: integer mode index.
    \item $\mathcal{R}_{\lambda}$: source equation symbol.
    \item $\lambda$: cosmological or lemniscatic branch parameter in the entry relation.
    \item $\Phi_{n}$: flux, phase, or topological map term in the source equation.
    \item $T$: source equation symbol.
    \item $\mathcal{I}$: source equation symbol.
    \item $\Phi$: flux, phase, or topological map term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0312 generated source Wolfram model *)
ClearAll[K0312, Cr0312, T, R, A, W, I, N];
eq0312$1 = HoldForm[PhilambdanRlambdaleftPhinrightRlambda[T2] -> T2];
eq0312$2 = HoldForm[I[RLambdaPhi] == I[Phi]];
eq0312$3 = HoldForm[PhiLambdan == RLambda[PhiN]];
eq0312$4 = HoldForm[Rlambda[T2] -> T2];
eq0312$5 = HoldForm[I[RLambdaPhi] == I[Phi]];

K0312 = HoldForm[{eq0312$1, eq0312$2, eq0312$3, eq0312$4, eq0312$5}];

N = "normalized TRAWIN closure object for Scale Invariance of Recursive Toroidal Encoding";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0312[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0312 = Cr0312[K0312];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Scale Invariance of Recursive Toroidal Encoding.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0312] Scale Invariance of Recursive Toroidal Encoding}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
C(\phi_1,\phi_2)
=
\frac{
\left|\langle \phi_1,\phi_2\rangle\right|
}{
\lVert \phi_1\rVert\,\lVert \phi_2\rVert
}.
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi_1$ and $\phi_2$ be two field configurations on $M$.  
Their raw overlap is measured by the inner product:

\begin{equation}
\langle \phi_1,\phi_2\rangle .
\end{equation}

To remove dependence on field magnitude, normalize by the product of the two norms:

\begin{equation}
\lVert \phi_1\rVert\,\lVert \phi_2\rVert .
\end{equation}

Taking the absolute value gives a nonnegative coherence score:

\begin{equation}
\boxed{
C(\phi_1,\phi_2)
=
\frac{
\left|\langle \phi_1,\phi_2\rangle\right|
}{
\lVert \phi_1\rVert\,\lVert \phi_2\rVert
}.
}
\end{equation}

\paragraph{Interpretation.}
The field coherence metric measures normalized alignment between two field states. Values near $1$ indicate strong coherence; values near $0$ indicate decoherence or orthogonality.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Scale Invariance of Recursive Toroidal Encoding by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
\Phi_{\lambda n}=\mathcal{R}_{\lambda}\!\left(\Phi_{n}\right)
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\mathcal{R}_{\lambda}:T^{2}\longrightarrow T^{2}
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\mathcal{I}\!\left(\mathcal{R}_{\lambda}\Phi\right)=\mathcal{I}(\Phi)
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0312] Scale Invariance of Recursive Toroidal Encoding}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Scale Invariance of Recursive Toroidal Encoding is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} There is no privileged scale in the recursive toroidal encoding; refining or coarsening the sampling density corresponds to different depth encodings of the same torus, not to a change in geometry. \textbf{Contextual meaning:} The entry reads Scale Invariance of Recursive Toroidal Encoding as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The field coherence metric measures normalized alignment between two field states. Values near 1 indicate strong coherence; values near 0 indicate decoherence or orthogonality.

\tzpsection{Equation Grounding}
Equation anchors: handoff= C:azlan-assistanthandoff ; pkg= ; and j=Get-Content. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Conformal Toroidal Mapping}: The property maintaining geometric and functional identity across nested layers regardless of magnification.
\item \textbf{Fractal Loop Preservation}: The recursive symmetry ensuring winding numbers and fluxes remain constant under dimensional scaling.
\item \textbf{Isometric Parameter Conservation}: The transformation logic protecting angular periodicities against metric expansion or contraction.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0312]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0312_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0312] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Scale Invariance of Recursive Toroidal Encoding}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} there is no privileged scale in the recursive toroidal encoding; refining or coarsening
the sampling density corresponds to different depth encodin...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Scale Invariance of Recursive Toroidal Encoding is valid as a tensorial/geometric
statement when the stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0312_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
