\section*{ID9247: Relation: (ħ/(2m\_ec))∇×(μ\_1×μ\_2)/(4πε\_0cΘ2dΘ3)µeff(t) =µ1+µ2+(/(2mec))∇× (µ1×…}
\paragraph{Metadata.}
PiID: 0469279068212 | RTEID: RTE:P35908.1546:T2.6169 | UUID: 37ad5b83-f594-5c45-9fc3-afc680e2b829

\paragraph{Canonical Statement.}
r spectral control. Falsifiability / Test Handle: Apply oscillatory radial fields on a spherical shell and measure resulting field patterns inside; confirm that harmonic expansion matches predicted spherical harmonics. 2.0.172 ID 321: Effective Gyromagnetic Dipole with Quantum Correction Type: Definition Formal Statement: In a gyromagnetic system, the effective dipole moment including quantum correction is \$µeff(t)=µ1+µ2+(/(2mec))∇×(µ1×µ2)/(4π0c2d3)\textbackslash{}mu\_\{\textbackslash{}text\{eff\}\}(t)\$ = \$\textbackslash{}mu\_1\$ + \$\textbackslash{}mu\_2\$ + \$(\textbackslash{}hbar/(2m\_ec))\textbackslash{}nabla\textbackslash{}times(\textbackslash{}mu\_1\textbackslash{}times\textbackslash{}mu\_2)/(4\textbackslash{}pi\textbackslash{}epsilon\_0cΘ2dΘ3)µeff(t) =µ1+µ2+(/(2mec))∇× (µ1× µ2)/(4π0c2d3),\$ where \$µ1\textbackslash{}mu\_1µ1\$ and \$µ2\textbackslash{}mu\_2µ2\$ are the classical dipoles separated by ddd. Interpretive Meaning: Quantum corrections modify the effective dipole by adding a term proportional to the curl of the cross product of the dipoles. This term becomes significant when the separation approaches a Canonical Registry Vol. 01 111 Trawin Zero Point Contextus Canonicus 2 TZP CANONICAL REGISTRY – E

\paragraph{Canonical Equation.}
\[
(\hbar/(2m_ec))\nabla\times(\mu_1\times\mu_2)/(4\pi\epsilon_0cΘ2dΘ3)µeff(t) =µ1+µ2+(/(2mec))∇× (µ1× µ2)/(4π0c2d3),
\]

\paragraph{Dictionary.}
Relation: (ħ/(2m\_ec))∇×(μ\_1×μ\_2)/(4πε\_0cΘ2dΘ3)µeff(t) =µ1+µ2+(/(2mec))∇× (µ1× µ2)/(4π0c2d3)

\paragraph{Encyclopedia.}
Relation: (ħ/(2m\_ec))∇×(μ\_1×μ\_2)/(4πε\_0cΘ2dΘ3)µeff(t) =µ1+µ2+(/(2mec))∇× (µ1×… is a differential equation, written (ħ/(2m\_ec))∇×(μ\_1×μ\_2)/(4πε\_0cΘ2dΘ3)µeff(t) =µ1+µ2+(/(2mec))∇× (µ1× µ2)/(4π0c2d3. It relates the quantity to its derivatives, governing how the system evolves in space and time. It is built from m, c, defining (ħ/(2m\_ec))∇×(μ\_1×μ\_2)/(4πε\_0cΘ2dΘ3)µeff(t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
