\tzpanchor{0039}
\tzpentryheader{0039}{Magnetic--Coriolis Energy Equipartition}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{930cd35b-4a8b-57a4-9c4a-9427f9164d22}}\\
\textbf{PiID} & \tzpcode{1693993751058} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{46}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{151.4457 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.2495 rad}\\
\textbf{TZPID} & \tzpcode{ID0039} & \textbf{Node Dependencies}\quad \tzpidref{0038}\\
\textbf{Registry} & \tzpcode{registry\_id\_0039} & \textbf{Scale}\quad equipartition\\
\textbf{LOC Classification} & QC174 energy balance & QC809 rotating magnetized systems\\
\textbf{arXiv Classification} & Primary: astro-ph.SR \quad Cross-list: physics.plasm-ph, gr-qc & \\
\textbf{Primary Support} & Magnetic Energy Density & Rotational Energy Density\\
\textbf{Closure Support} & Equipartition Balance & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Magnetic and rotational energies equilibrate in systems obeying the unification principle.

\tzpsection{Canonical Equation}
\[
\frac{B^{2}}{2\mu}
=
\frac{1}{2}\rho(\Omega r)^{2}
\]
\[
E_{\mathrm{mag}}
=
E_{\mathrm{rot}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $B$: magnetic field magnitude.
    \item $\mu$: source equation symbol.
    \item $\rho$: density or measure term used by the entry equation.
    \item $E_{\mathrm{mag}}$: source equation symbol.
    \item $E_{\mathrm{rot}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0039 generated source Wolfram model *)
ClearAll[K0039, Cr0039, T, R, A, W, I, N];
eq0039$1 = HoldForm[B^2/(2*mu) == (1/2)*rho[Omega*r]^2];
eq0039$2 = HoldForm[EMag == ERot];
eq0039$3 = HoldForm[B^2/(2*mu)];
eq0039$4 = HoldForm[(1/2)*rho[Omega*r]^2];

K0039 = HoldForm[{eq0039$1, eq0039$2, eq0039$3, eq0039$4}];

N = "normalized TRAWIN closure object for Magnetic--Coriolis Energy Equipartition";
I = "Equipartition Balance integration/comparison layer";
W = "Rotational Energy Density wave or operator carrier";
A = "Magnetic Energy Density admissible action/amplitude condition";
R = "Rotational Energy Density rotation/curl preservation layer";
T = "Magnetic Energy Density local source condition";

Cr0039[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0039 = Cr0039[K0039];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Magnetic Energy Density local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Rotational Energy Density rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Magnetic Energy Density admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Rotational Energy Density wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Equipartition Balance integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Magnetic--Coriolis Energy Equipartition.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0039] Magnetic--Coriolis Energy Equipartition}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{\mathbf{B}^2}{2\mu}
=
\frac{1}{2}\rho(\Omega r)^2 .
\end{equation}

\paragraph{Primary Derivation.}
The magnetic energy density is:

\begin{equation}
u_B
=
\frac{\mathbf{B}^2}{2\mu}.
\end{equation}

The rotational kinetic energy density associated with angular velocity $\Omega$ at radius $r$ is:

\begin{equation}
u_{\Omega}
=
\frac{1}{2}\rho v^2 .
\end{equation}

Since tangential velocity is:

\begin{equation}
v=\Omega r,
\end{equation}

we obtain:

\begin{equation}
u_{\Omega}
=
\frac{1}{2}\rho(\Omega r)^2 .
\end{equation}

Equipartition requires:

\begin{equation}
\boxed{
\frac{\mathbf{B}^2}{2\mu}
=
\frac{1}{2}\rho(\Omega r)^2 .
}
\end{equation}

\paragraph{Interpretation.}
Magnetic--Coriolis equipartition identifies the balance point where magnetic field energy and rotational kinetic energy density match.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Magnetic--Coriolis Energy Equipartition by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Magnetic Energy Density}\par
\[
\frac{B^{2}}{2\mu}
\]
\noindent This measures the stored magnetic energy available to balance the rotational sector.\par
\noindent\textbf{2. Rotational Energy Density}\par
\[
\frac{1}{2}\rho(\Omega r)^{2}
\]
\noindent This measures the kinetic energy density associated with rotation at scale \textbackslash{}(r\textbackslash{}).\par
\noindent\textbf{3. Equipartition Balance}\par
\[
\frac{B^{2}}{2\mu}
=
\frac{1}{2}\rho(\Omega r)^{2}
\]
\noindent This closes the progression by stating that the Elsasser critical regime is an energetic balance law, not just a dimensionless coincidence.\par

\clearpage
\noindent\textbf{[ID 0039] Magnetic--Coriolis Energy Equipartition}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Magnetic--Coriolis Energy Equipartition is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Magnetic and rotational energies equilibrate in systems obeying the unification principle. \textbf{Contextual meaning:} The entry reads Magnetic--Coriolis Energy Equipartition as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This law provides the first explicit energy-balance consequence of the Elsasser attractor. It supports later universal scaling claims by showing that fields and rotation do not merely coexist but exchange energy on a common scale. \textbf{Lemma support:} Magnetic Energy Density; Rotational Energy Density; Equipartition Balance.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Magnetic--Coriolis equipartition identifies the balance point where magnetic field energy and rotational kinetic energy density match.

\tzpsection{Equation Grounding}
Equation anchors: In the vicinity of the Elsasser attractor, the magnetic energy density B22muratio textbackslash mathbf B to the power 2 2mu 2muB2 equals the kinetic energy density associated with differential rotation 12rho (Omega r)2ratio 1 2 rhotextbackslash, (Omegatextbackslash,r) to the power 221rho(Omegar)2. In the vicinity of the Elsasser attractor, the magnetic energy density B22muratio textbackslash mathbf B to the power 2 2mu 2muB2 equals the kinetic energy density associated with differential rotation 12rho (Omega r)2ratio 1 2 rhotextbackslash, (Omegatextbackslash,r) to the power 221rho(Omegar)2.

\tzpsection{Interpretive Role}
This law provides the first explicit energy-balance consequence of the Elsasser attractor. It supports later universal scaling claims by showing that fields and rotation do not merely coexist but exchange energy on a common scale.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Magnetized Rotating-Frame Force Energy Equipartition}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\item \textbf{Magnetized Rotating-Frame Force Rotating-Field Analogue}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\item \textbf{Rotating-Frame Force Terminology}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0039]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0039_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0039] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Magnetic--Coriolis Energy Equipartition}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} magnetic and rotational energies equilibrate in systems obeying the unification
principle

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Magnetic--Coriolis Energy Equipartition is valid as a formal registry statement when its
source equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that magnetic and rotational energies equilibrate in systems
obeying the unification principle. Magnetic--Coriolis equipartition identifies the
balance point where magnetic field energy and rotational kinetic energy density match.
This law provides the first explicit energy-balance consequence of the Elsasser
attractor.. The CHL validation treats the equation as the formal anchor and the semantic
text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0039_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
