\section*{ID9927: Two-Particle States and Entanglement: V\_p,σ(s)}
\paragraph{Metadata.}
PiID: 9310657922955 | RTEID: RTE:P38548.7456:T0.6846 | UUID: 836c8425-fdf8-5fa5-b4c3-4fbc35ab31bd

\paragraph{Canonical Statement.}
\textbackslash{}begin\{proposition\}[Designability of entanglement kernels along a double helix] Assume that: \textbackslash{}begin\{enumerate\}[label=(\textbackslash{}alph*)] \textbackslash{}item \$J\_p(s)\$ and \$V\_\{p,\textbackslash{}sigma\}(s)\$ can be adjusted within continuous families by modifying local material composition and cross-linking, \textbackslash{}item The spectrum of \$\textbackslash{}Hhat\_\{p\}\textasciicircum{}\{\textbackslash{}mathrm\{helix\}\}\$ is non-degenerate in a target band of energies. \textbackslash{}end\{enumerate\} Then, for any sufficiently smooth kernel \$K\_p\textasciicircum{}\{\textbackslash{}mathrm\{target\}\}\$ with compact support in \$[0,L]\textasciicircum{}2\$ and satisfying normalization and symmetry constraints, there exists a family of parameter functions \$(J\_p,V\_\{p,\textbackslash{}sigma\})\$ such that the evolved two-particle state at a design time \$T

\paragraph{Canonical Equation.}
\[
V_{p,\sigma}(s)
\]

\paragraph{Dictionary.}
Then, for any sufficiently smooth kernel K\_p\textasciicircum{}target with compact support in [0,L]\textasciicircum{}2 and satisfying normalization and symmetry constraints, there exists a family of parameter functions (J\_p,V\_p,σ) such that the evolved two-particle state at a design time \$T

\paragraph{Encyclopedia.}
Two-Particle States and Entanglement: V\_p,σ(s) is a symbolic expression, written V\_p,σ(s). It introduces a symbol or relation used elsewhere in the framework. It is built from σ, V\_p, s. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
