\section*{ID9268: Definition of LRm}
\paragraph{Metadata.}
PiID: 8142335628236 | RTEID: RTE:P35989.7022:T2.7513 | UUID: 0fcd1f4e-4a33-5376-9156-2b0849982348

\paragraph{Canonical Statement.}
ntum phase. (3) Constrains the possible velocities in superfluid augmentation of gyromagnetic devices. Falsifiability / Test Handle: Observe circulation in superfluid vortices and verify quantization; measure changes with different particle masses. 2.0.179 ID 328: Critical Magnetic Reynolds Number for SelfOrganized Dynamo Type: Conservation Law Formal Statement: A selforganized dynamo and magnetic field generation occur when the magnetic Reynolds number \$Rm=µ0σvLR\_\{\textbackslash{}text\{m\}\}\$ = \textbackslash{}mu\_0 \textbackslash{}sigma v \$LRm=µ0σvL\$ exceeds a critical threshold \$Rm,critical≈103R\_\{\textbackslash{}text\{m,critical\}\}\$ \textbackslash{}approx \$10ˆ3Rm,critical≈103.\$ Interpretive Meaning: The magnetic Reynolds number measures the ratio of magnetic advection to diffusion. Above a critical value, induced currents sustain magnetic fields against resistive dissipation, leading to dynamo action and selforganized magnetic structures. Dependencies: ID 200. Derivable

\paragraph{Canonical Equation.}
\[
LRm=µ0σvL
\]

\paragraph{Dictionary.}
Definition of LRm — LRm=µ0σvL

\paragraph{Encyclopedia.}
Definition of LRm is an algebraic definition, written LRm=µ0σvL. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from v, L, defining LRm. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
