\section*{ID9123: Relation: ╬Ż\_TZPŌłåSTeffQ+╬ŻTZP.}
\paragraph{Metadata.}
PiID: 0029741207665 | RTEID: RTE:P35426.6350:T1.8235 | UUID: a9b07220-ca7c-588a-9d05-59f7bb87c131

\paragraph{Canonical Statement.}
ty or trace preservation in contexts expected to follow these rules would challenge this definition. 0.0.77 ID 075: Quantum Thermodynamics Type: Definition Formal Statement: Quantum thermodynamics on the Trawinistic manifold studies energy, entropy and information flows in quantum systems; heat and work are defined via twopoint measurement schemes, and the second law generalises to include curvature and zeropoint contributions in the form \$ŌłåSQTeff+╬ŻTZP\textbackslash{}Delta\$ S \textbackslash{}geq \textbackslash{}frac\{Q\}\{T \{\textbackslash{}text\{eff\}\}\} + \$\textbackslash{}Sigma\_\{\textbackslash{}text\{TZP\}\}ŌłåSTeffQ+╬ŻTZP.\$ Interpretive Meaning: Thermodynamic concepts remain but are modified by quantum coherence, curvature and the TZP; effective temperatures and entropy production include geometric contributions. Canonical Registry Vol. 01 26 Trawin Zero Point Contextus Canonicus Dependencies: ID 060, ID 058 Derivable Consequences: Fluctuation theorems; bounds on quantum engines; relation to fluctuationŌĆōdissipation

\paragraph{Canonical Equation.}
\[
\Sigma_{\text{TZP}}ŌłåSTeffQ+╬ŻTZP.
\]

\paragraph{Dictionary.}
Relation: ╬Ż\_TZPŌłåSTeffQ+╬ŻTZP. ŌĆö ╬Ż\_TZPŌłåSTeffQ+╬ŻTZP.

\paragraph{Encyclopedia.}
Relation: ╬Ż\_TZPŌłåSTeffQ+╬ŻTZP. is a symbolic expression, written ╬Ż\_TZPŌłåSTeffQ+╬ŻTZP.. It introduces a symbol or relation used elsewhere in the framework. It is built from S, T, f, Q, Z, P. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
