\tzpanchor{0005}
\tzpentryheader{0005}{TZP Stability Under Symmetry-Preserving Diffeomorphisms}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{a358dfec-884d-58f0-b3d3-a7cccf1baf40}}\\
\textbf{PiID} & \tzpcode{2653589793238} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{12}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{19.4161 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.0320 rad}\\
\textbf{TZPID} & \tzpcode{ID0005} & \textbf{Node Dependencies}\quad \tzpidref{0000}\\
\textbf{Registry} & \tzpcode{registry\_id\_0005} & \textbf{Scale}\quad symmetry\\
\textbf{LOC Classification} & QA641 diffeomorphism groups & QC field symmetries\\
\textbf{arXiv Classification} & Primary: math.DG \quad Cross-list: gr-qc, math-ph & \\
\textbf{Primary Support} & Symmetry-Preserving Map & TZP Fixed-Point Condition\\
\textbf{Closure Support} & Lemniscatic Invariance & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
For any diffeomorphism $\phi: M \to M$ that preserves the symmetry group of $M$, $\phi(p) = p$ and $\phi$ leaves the local lemniscatic structure invariant.

\tzpsection{Canonical Equation}
\[
\phi : M \to M,
\qquad
\phi(p)=p
\]
\[
\phi(\Lambda)=\Lambda
\]
for every symmetry-preserving diffeomorphism $\phi$ and every local lemniscatic representative $\Lambda$ through the TZP.

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $M$: source equation symbol.
    \item $\Lambda$: lemniscatic representative or canonical branch object.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $D$: source equation symbol.
    \item $i(p)$: source equation symbol.
    \item $f_{sym}(M)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0005 generated source Wolfram model *)
ClearAll[K0005, Cr0005, T, R, A, W, I, N];
eq0005$1 = HoldForm[phi[M] -> Mphipp];
eq0005$2 = HoldForm[phi[Lambda] == Lambda];
eq0005$3 = HoldForm[Element[phi, DiffSym[M]]];
eq0005$4 = HoldForm[phi[p] == p];

K0005 = HoldForm[{eq0005$1, eq0005$2, eq0005$3, eq0005$4}];

N = "normalized TRAWIN closure object for TZP Stability Under Symmetry-Preserving Diffeomorphisms";
I = "Lemniscatic Invariance integration/comparison layer";
W = "TZP Fixed-Point Condition wave or operator carrier";
A = "Symmetry-Preserving Map admissible action/amplitude condition";
R = "TZP Fixed-Point Condition rotation/curl preservation layer";
T = "Symmetry-Preserving Map local source condition";

Cr0005[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0005 = Cr0005[K0005];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Symmetry-Preserving Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TZP Fixed-Point Condition rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Symmetry-Preserving Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TZP Fixed-Point Condition wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Lemniscatic Invariance integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP Stability Under Symmetry-Preserving Diffeomorphisms.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0005] TZP Stability Under Symmetry-Preserving Diffeomorphisms}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
For any diffeomorphism $\phi:M\to M$ preserving the symmetry group of $M$,

\begin{equation}
\phi(p)=p .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi:M\to M$ be a diffeomorphism preserving the symmetry structure of the manifold. Since $p$ is defined as the unique point where the metric degeneracy occurs,

\begin{equation}
\det(g)\big|_p=0 .
\end{equation}

If $\phi$ preserves the Trawinistic structure, then it must preserve the degeneracy locus:

\begin{equation}
\det(g)\big|_{\phi(p)}=0 .
\end{equation}

Because $p$ is unique, the only point satisfying this condition is $p$ itself. Therefore:

\begin{equation}
\phi(p)=p .
\end{equation}

\paragraph{Interpretation.}
The TZP is invariant under all structure-preserving transformations. It is therefore a fixed point of the system.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP Stability Under Symmetry-Preserving Diffeomorphisms by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Symmetry-Preserving Map}\par
\[
\phi \in \mathrm{Diff}_{\mathrm{sym}}(M)
\]
\noindent This limits the discussion to the transformations the framework actually admits as physical or geometric symmetries.\par
\noindent\textbf{2. TZP Fixed-Point Condition}\par
\[
\phi(p)=p
\]
\noindent This keeps the anchor from moving under reparameterization and preserves the uniqueness obtained in \textbackslash{}tzpidref\{0000\}.\par
\noindent\textbf{3. Lemniscatic Invariance}\par
\[
\phi(\Lambda)=\Lambda
\]
\noindent This closes the progression by showing that symmetry preserves not just the point but also the topological neighborhood structure that later dimensional branching uses.\par

\clearpage
\noindent\textbf{[ID 0005] TZP Stability Under Symmetry-Preserving Diffeomorphisms}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP Stability Under Symmetry-Preserving Diffeomorphisms is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} For any diffeomorphism phi: M to M that preserves the symmetry group of M, phi(p) = p and phi leaves the local lemniscatic structure invariant. \textbf{Contextual meaning:} The entry reads TZP Stability Under Symmetry-Preserving Diffeomorphisms as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This axiom guarantees that later coordinate choices, gauge-like rearrangements, and model symmetries are not allowed to manufacture a different anchor. It is the stability clause that keeps the registry from drifting under re-description. \textbf{Lemma support:} Symmetry-Preserving Map; TZP Fixed-Point Condition; Lemniscatic Invariance.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP is invariant under all structure-preserving transformations. It is therefore a fixed point of the system.

\tzpsection{Equation Grounding}
Equation anchors: For any diffeomorphism phi: M to M that preserves the symmetry group of M, phi(p) = p and phi leaves the local lemniscatic structure invariant. For any diffeomorphism phi: M to M that preserves the symmetry group of M, phi(p) = p and phi leaves the local lemniscatic structure invariant.

\tzpsection{Interpretive Role}
This axiom guarantees that later coordinate choices, gauge-like rearrangements, and model symmetries are not allowed to manufacture a different anchor. It is the stability clause that keeps the registry from drifting under re-description.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Tzp Stability Under Symmetry Preserving}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Tzp Stability Under Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Diffeomorphisms Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0005]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0005_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0005] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP Stability Under Symmetry-Preserving Diffeomorphisms}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} for any diffeomorphism : M M that preserves the symmetry group of M, (p) = p and
 leaves the local lemniscatic structure invariant

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP Stability Under Symmetry-Preserving Diffeomorphisms is valid when its objects and
arrows close under the stated categorical construction.''\\
\textbf{Proof:} The source statement is read as a categorical construction. The proof obligation is
closure: objects must map to admissible objects, arrows must compose, and the named
invariant must survive the induced functor.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- categorical-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0005_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
