\section*{ID6454: Step 6 — Consciousness Coupling via Beat Frequency: S(t)}
\paragraph{Metadata.}
PiID: 9493041377655 | RTEID: RTE:P25062.3153:T3.5959 | UUID: 8448f324-7213-55e4-9d53-05b83951c1de

\paragraph{Canonical Statement.}
\#\#\# Step 6 — *Consciousness coupling via beat frequency* - Modeling: \textbackslash{}(f\_1=440\textbackslash{}), \textbackslash{}(f\_2=446\textbackslash{}) → beat 6 Hz in theta band (4–8 Hz). That produces an amplitude envelope at 6 Hz. This is a valid *signal-processing* observation; entrainment of brain rhythms by auditory beats is a known phenomenon (the brain shows auditory steady-state responses and can entrain). - **Caution**: *Equating entrainment with “consciousness coupling”* is a big conceptual jump. Entrainment = measurable synchronization; “consciousness” is a complex, multi-layer phenomenon. Be explicit: this is *hypothesis* that theta entrainment correlates with a cognitive state and may modulate your mode. Do not assert causality without experimental support. - **Actionable**: model the beat as a modulation \textbackslash{}(s(t)=2\textbackslash{}cos(πΔf t)\textbackslash{}cos(2πf̄ t)\textbackslash{}) and run the numerical gating simulation (I can do this) to show how |I(t)| responds.

\paragraph{Canonical Equation.}
\[
s(t)=2\cos(πΔf t)\cos(2πf̄ t)
\]

\paragraph{Dictionary.}
Relation: s(t)=2cos(πΔf t)cos(2πf̄ t)

\paragraph{Encyclopedia.}
Step 6 — Consciousness Coupling via Beat Frequency: S(t) is an algebraic definition, written s(t)=2cos(πΔf t)cos(2πf̄ t). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from f, defining s(t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
