\section*{ID9067: Relation: Q,t r)=0∂t∂S+HT(q,∂q∂S,t)=0}
\paragraph{Metadata.}
PiID: 1518754711962 | RTEID: RTE:P35209.1746:T1.4652 | UUID: 8c28dc43-7252-5f17-8368-abd3e7b06fc9

\paragraph{Canonical Statement.}
ces spectral properties; defines ground and excited states; connects to the TZP vacuum energy. Falsifiability / Test Handle: Observation of energy spectra incompatible with the integrated Hamiltonian density would falsify this operator. 0.0.33 ID 031: Hamilton–Jacobi Equation (Trawinistic Form) Type: Operator Formal Statement: The action SSS for a classical trajectory in MMM satisfies \$∂S∂t+HT(q,∂S∂q,t)=0\textbackslash{}frac\{\textbackslash{}partial\$ S\}\{\textbackslash{}partial t\} + \textbackslash{}mathcal\{H\} \{\textbackslash{}text\{T\}\}\textbackslash{}bigl(q,\textbackslash{}frac\{\textbackslash{}partial S\}\{\textbackslash{}partial \$q\},t\textbackslash{}bigr)=0∂t∂S+HT(q,∂q∂S,t)=0,\$ where HT\textbackslash{}mathcal\{H\} \{\textbackslash{}text\{T\}\}HT is the Trawinistic Hamiltonian density and qqq denotes the configuration variables. Interpretive Meaning: This equation generalises the Hamilton–Jacobi equation to incorporate the TZP potential and metric degeneracy. It governs the stationary action principle in the Trawin framework. Dependencies: ID 029, ID 006 Derivable Consequences: Leads to particle trajectori

\paragraph{Canonical Equation.}
\[
q},t\bigr)=0∂t∂S+HT(q,∂q∂S,t)=0,
\]

\paragraph{Dictionary.}
Relation: Q,t r)=0∂t∂S+HT(q,∂q∂S,t)=0 — q,t r)=0∂t∂S+HT(q,∂q∂S,t)=0

\paragraph{Encyclopedia.}
Relation: Q,t r)=0∂t∂S+HT(q,∂q∂S,t)=0 is an algebraic definition, written q,t r)=0∂t∂S+HT(q,∂q∂S,t)=0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from q, S, H, T. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
