\tzpanchor{0020}
\tzpentryheader{0020}{Trawinistic Winding Number}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f2c432c3-10b0-5e21-a975-a04d94a134a6}}\\
\textbf{PiID} & \tzpcode{2643383279502} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{27}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{77.6644 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.1280 rad}\\
\textbf{TZPID} & \tzpcode{ID0020} & \textbf{Node Dependencies}\quad \tzpidref{0002}\\
\textbf{Registry} & \tzpcode{registry\_id\_0020} & \textbf{Scale}\quad topological-phase\\
\textbf{LOC Classification} & QA612 winding and homotopy & QC174 phase quantization\\
\textbf{arXiv Classification} & Primary: math.AT \quad Cross-list: gr-qc, math-ph & \\
\textbf{Primary Support} & Phase Gradient Along the Loop & Loop Integral Normalized by \(2\pi\)\\
\textbf{Closure Support} & Lemniscatic Quantization & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Trawinistic winding number counts the net phase accumulation around a closed loop encircling the zero point. Because the local loop class is lemniscatic rather than simply circular, the winding may take half-integer values as well as integer values.

\tzpsection{Canonical Equation}
\[
w
=
\frac{1}{2\pi}
\oint_{\Gamma}
\nabla \theta \cdot d\ell
\]
\[
w \in \tfrac{1}{2}\mathbb{Z}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\pi$: source equation symbol.
    \item $\theta$: phase angle or local angular coordinate.
    \item $Z$: source equation symbol.
    \item $\Gamma$: closed loop, path, or admissible trajectory in the entry domain.
    \item $\ell$: source equation symbol.
    \item $G$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0020 generated source Wolfram model *)
ClearAll[K0020, Cr0020, T, R, A, W, I, N];
eq0020$1 = HoldForm[w == (1/(2*Pi))*ContourIntegralGamma*Grad*theta*dell];
eq0020$2 = HoldForm[Element[w, tfrac[1]*2*Z]];
eq0020$3 = HoldForm[Grad*theta*dell];

K0020 = HoldForm[{eq0020$1, eq0020$2, eq0020$3}];

N = "normalized TRAWIN closure object for Trawinistic Winding Number";
I = "Lemniscatic Quantization integration/comparison layer";
W = "Loop Integral Normalized by \(2\pi\) wave or operator carrier";
A = "Phase Gradient Along the Loop admissible action/amplitude condition";
R = "Loop Integral Normalized by \(2\pi\) rotation/curl preservation layer";
T = "Phase Gradient Along the Loop local source condition";

Cr0020[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0020 = Cr0020[K0020];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Phase Gradient Along the Loop local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Loop Integral Normalized by \textbackslash{}(2\textbackslash{}pi\textbackslash{}) rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Phase Gradient Along the Loop admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Loop Integral Normalized by \textbackslash{}(2\textbackslash{}pi\textbackslash{}) wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Lemniscatic Quantization integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Trawinistic Winding Number.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0020] Trawinistic Winding Number}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mathcal{L}_U
=
\frac{c^4}{16\pi G}R[g]
+
\mathcal{L}_{QFT}[\Psi,A_\mu]
+
\mathcal{L}_{topo}[A_\mu]
+
\mathcal{L}_{info}[\Phi]
+
\mathcal{L}_{bio}[\Xi].
\end{equation}

\paragraph{Primary Derivation.}
A unified Trawinistic action density is constructed by summing distinct physical sectors.

The gravitational sector is given by the Einstein-Hilbert density:

\begin{equation}
\mathcal{L}_{grav}
=
\frac{c^4}{16\pi G}R[g].
\end{equation}

The quantum field contribution is:

\begin{equation}
\mathcal{L}_{QFT}[\Psi,A_\mu].
\end{equation}

The topological contribution accounts for winding, helicity, and gauge structure:

\begin{equation}
\mathcal{L}_{topo}[A_\mu].
\end{equation}

The information-field sector is:

\begin{equation}
\mathcal{L}_{info}[\Phi].
\end{equation}

The biological or organized-complexity sector is:

\begin{equation}
\mathcal{L}_{bio}[\Xi].
\end{equation}

Adding all components gives:

\begin{equation}
\boxed{
\mathcal{L}_U
=
\frac{c^4}{16\pi G}R[g]
+
\mathcal{L}_{QFT}[\Psi,A_\mu]
+
\mathcal{L}_{topo}[A_\mu]
+
\mathcal{L}_{info}[\Phi]
+
\mathcal{L}_{bio}[\Xi].
}
\end{equation}

\paragraph{Interpretation.}
This equation defines a layered Lagrangian architecture: gravity, quantum fields, topology, information, and biological organization are treated as coupled sectors of one Trawinistic action density.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Trawinistic Winding Number by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Phase Gradient Along the Loop}\par
\[
\nabla \theta \cdot d\ell
\]
\noindent This identifies the infinitesimal phase contribution accumulated as a field encircles the zero point.\par
\noindent\textbf{2. Loop Integral Normalized by \textbackslash{}(2\textbackslash{}pi\textbackslash{})}\par
\[
w
=
\frac{1}{2\pi}
\oint_{\Gamma}
\nabla \theta \cdot d\ell
\]
\noindent This converts the total phase accumulation into a dimensionless topological count.\par
\noindent\textbf{3. Lemniscatic Quantization}\par
\[
w \in \tfrac{1}{2}\mathbb{Z}
\]
\noindent This closes the progression by showing that the TZP loop class permits half-integer winding because the loop self-intersects at the anchor.\par

\clearpage
\noindent\textbf{[ID 0020] Trawinistic Winding Number}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Trawinistic Winding Number label id-020-trawinistic-winding-number is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} L sub U = ratio c to the power 4 16pi G R[g] + L sub QFT [Psi, A sub mu] + L sub topo [A sub mu] + L sub info [Phi] + L sub bio [Xi]. \textbf{Contextual meaning:} The entry reads Trawinistic Winding Number label id-020-trawinistic-winding-number as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Phase Gradient Along the Loop; Loop Integral Normalized by 2pi; Lemniscatic Quantization.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This equation defines a layered Lagrangian architecture: gravity, quantum fields, topology, information, and biological organization are treated as coupled sectors of one Trawinistic action density.

\tzpsection{Equation Grounding}
Equation anchors: L sub U = ratio c to the power 4 16pi G ,R[g] , + , L sub QFT [Psi, A sub mu] , + , L sub topo [A sub mu] , + , L sub info [Phi] , + , L sub bio [Xi]. L sub U = ratio c to the power 4 16pi G ,R[g] , + , L sub QFT [Psi, A sub mu] , + , L sub topo [A sub mu] , + , L sub info [Phi] , + , L sub bio [Xi].

\tzpsection{Interpretive Role}
This quantity is the canonical topological counter for later charge, holonomy, and causal-loop invariants. It also makes the half-branch structure of the Trawin loop geometry numerically visible.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Trawinistic Winding Number Label Id}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Trawinistic Winding Number Normalization Analogue}: normalization vocabulary for fixed form, invariant comparison, or TRAWIN admissibility.
\item \textbf{Number Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0020]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0020_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0020] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Trawinistic Winding Number}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the Trawinistic winding number counts the net phase accumulation around a closed loop
encircling the zero point

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Trawinistic Winding Number is valid when the stated geometric or topological relation
preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0020_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
