\tzpanchor{0111}
\tzpentryheader{0111}{Resonant Holographic Spiral}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{0949fa2b-1155-5ff5-be36-c1a3b06c1eb5}}\\
\textbf{PiID} & \tzpcode{2823066470938} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{118}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{431.0377 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.7102 rad}\\
\textbf{TZPID} & \tzpcode{ID0111} & \textbf{Node Dependencies}\quad \tzpidref{0110}\\
\textbf{Registry} & \tzpcode{registry\_id\_0111} & \textbf{Scale}\quad spiral-holographic growth geometry\\
\textbf{LOC Classification} & QA614.3 curves and surfaces & QA641 differential geometry\\
\textbf{arXiv Classification} & Primary: math.DG \quad Cross-list: math-ph, nlin.PS & \\
\textbf{Primary Support} & Spiral Radius Law & Golden-Ratio Exponent\\
\textbf{Closure Support} & Helical Lift & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The resonant holographic spiral is defined by the parametric relation r($\theta$) = a\,exp(b\,$\theta$), with b = $\pi$/(2\,ln\,$\phi$), where $\phi$ is the golden ratio. This parameterization encodes the Fibonacci-to-helix scaling law.

\tzpsection{Canonical Equation}
\[
r(\theta)=a e^{\beta \theta}
\]
\[
\beta = \frac{2\log \phi}{\pi}
\]
\[
z(\theta)=c\theta
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\theta$: phase angle or local angular coordinate.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $\pi$: source equation symbol.
    \item $c$: speed of light or relativistic conversion factor.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0111 generated source Wolfram model *)
ClearAll[K0111, Cr0111, T, R, A, W, I, N];
eq0111$1 = HoldForm[r[theta] == a*Exp[beta*theta]];
eq0111$2 = HoldForm[beta == (2*log*phi)/Pi];
eq0111$3 = HoldForm[z[theta] == ctheta];

K0111 = HoldForm[{eq0111$1, eq0111$2, eq0111$3}];

N = "normalized TRAWIN closure object for Resonant Holographic Spiral";
I = "Helical Lift integration/comparison layer";
W = "Golden-Ratio Exponent wave or operator carrier";
A = "Spiral Radius Law admissible action/amplitude condition";
R = "Golden-Ratio Exponent rotation/curl preservation layer";
T = "Spiral Radius Law local source condition";

Cr0111[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0111 = Cr0111[K0111];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Spiral Radius Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Golden-Ratio Exponent rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Spiral Radius Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Golden-Ratio Exponent wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Helical Lift integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Resonant Holographic Spiral.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0111] Resonant Holographic Spiral}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
r(\theta)=a e^{\beta \theta}
\]
\[
\beta = \frac{2\log \phi}{\pi}
\]
\[
z(\theta)=c\theta
\]

\paragraph{Primary Derivation.}
This argument establishes the identity by employing standard algebraic manipulations, yielding the required identity.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. Interpreted through TRAWIN, the equation functions as the generalized carrier for the entry’s information content. According to CHL, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Resonant Holographic Spiral by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Spiral Radius Law}\par
\[
r(\theta)=a e^{\beta \theta}
\]
\noindent This establishes the exponential radial growth required for a genuine self-similar spiral.\par
\noindent\textbf{2. Golden-Ratio Exponent}\par
\[
\beta = \frac{2\log \phi}{\pi}
\]
\noindent This ties the spiral directly to the same \textbackslash{}(\textbackslash{}phi\textbackslash{})-governed scale law that shaped the preceding Fibonacci entries.\par
\noindent\textbf{3. Helical Lift}\par
\[
z(\theta)=c\theta
\]
\noindent This closes the progression by turning the planar spiral into a lifted resonance path suitable for spacetime or signal embedding.\par

\clearpage
\noindent\textbf{[ID 0111] Resonant Holographic Spiral}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Resonant Holographic Spiral is a Operator. The resonant holographic spiral is defined by the parametric relation r( ) = a exp(b  ), with b =  /(2 ln  ), where   is the golden ratio.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The resonant holographic spiral is defined by the parametric relation r( ) = a exp(b  ), with b =  /(2 ln  ), where   is the golden ratio.
\textbf{Contextual meaning:} This spiral connects angular rotation to radial expansion through a constant derived from the circular constant   and the golden ratio. It represents a minimal energy, scale invariant mapping between rotation and growth.
\textbf{Derivable consequences:} Minimal energy surfaces;  --  coupling; design of helical structures; relation to the coupling principle.
\textbf{Lemma support:} The resonant holographic spiral is defined by the parametric relation r( ) = a exp(b  ), with b =  /(2 ln  ), where   is the golden ratio.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Examine growth processes and wave patterns for Fibonacci and exponential scaling features; test whether they fit the manifold's predictions. ID 111: Resonant Holographic Spiral

\tzpsection{Equation Grounding}
The resonant holographic spiral is defined by the parametric relation r( ) = a exp(b  ), with b =  /(2 ln  ), where   is the golden ratio.

\tzpsection{Interpretive Role}
This spiral connects angular rotation to radial expansion through a constant derived from the circular constant   and the golden ratio. It represents a minimal energy, scale invariant mapping between rotation and growth.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spiral Radius Law}: The establishment of the exponential radial growth required for a genuine self-similar spiral.
\item \textbf{Golden-Ratio Exponent}: The tie of the spiral directly to the same phi-governed scale law that shaped the preceding Fibonacci entries.
\item \textbf{Helical Lift}: The translation of the planar spiral into a lifted resonance path suitable for spacetime or signal embedding.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0111]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0111_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0111] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Resonant Holographic Spiral}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the resonant holographic spiral is defined by the parametric relation r() = a exp(b
), with b = /(2 ln ), where  is the golden ratio

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Resonant Holographic Spiral is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0111_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
