\tzpanchor{0382}
\tzpentryheader{0382}{Gravitomagnetic Coupling Law}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{aa5dba43-1ee3-5195-a194-121fdb82b25d}}\\
\textbf{PiID} & \tzpcode{8414695194151} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{389}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1483.3908 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.4442 rad}\\
\textbf{TZPID} & \tzpcode{ID0382} & \textbf{Node Dependencies}\quad \tzpidref{0381}\\
\textbf{Registry} & \tzpcode{registry\_id\_0382} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Gravitomagnetic Field & Mass Integral\\
\textbf{Closure Support} & Coupling Strength & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This law describes how rotation of mass generates a gravitomagnetic field analogous to magnetic fields in electromagnetism, linking general relativity and gyromagnetism.

\tzpsection{Canonical Equation}
\[
\mathbf{B}_{g}=\nabla\times\mathbf{A}_{g}
\]
\[
\mathbf{A}_{g}(\mathbf{x})=\frac{G}{c}\int \frac{\rho(\mathbf{x}^{\prime})\mathbf{v}(\mathbf{x}^{\prime})}{\lVert\mathbf{x}-\mathbf{x}^{\prime}\rVert}\,d^{3}x^{\prime}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $B$: magnetic field magnitude.
    \item $A$: source equation symbol.
    \item $G$: source equation symbol.
    \item $c$: speed of light or relativistic conversion factor.
    \item $\rho$: density or measure term used by the entry equation.
    \item $v$: velocity, flow speed, or auxiliary comparison variable.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0382 generated source Wolfram model *)
ClearAll[K0382, Cr0382, T, R, A, W, I, N];
eq0382$1 = HoldForm[BG == Grad*AG];
eq0382$2 = HoldForm[AG[x] == (G/c)*Integral[(rho[x^prime]*v[x^prime])/(lVertx - x^prime*rVert)]*d^3*x^prime];
eq0382$3 = HoldForm[kappaG == 4*(G/c^2)];

K0382 = HoldForm[{eq0382$1, eq0382$2, eq0382$3}];

N = "normalized TRAWIN closure object for Gravitomagnetic Coupling Law";
I = "Coupling Strength integration/comparison layer";
W = "Mass Integral wave or operator carrier";
A = "Gravitomagnetic Field admissible action/amplitude condition";
R = "Mass Integral rotation/curl preservation layer";
T = "Gravitomagnetic Field local source condition";

Cr0382[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0382 = Cr0382[K0382];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Gravitomagnetic Field local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Mass Integral rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Gravitomagnetic Field admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Mass Integral wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Coupling Strength integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Gravitomagnetic Coupling Law.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0382] Gravitomagnetic Coupling Law}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
Consistency between micro and macro descriptions requires that ensemble averages of quantum observables satisfy classical conservation laws and equations of motion when decoherence is effective.

\paragraph{Primary Equation.}
\begin{equation}
\frac{\mathrm{d}}{\mathrm{d}t}\langle A\rangle
=
\left\langle
\frac{i}{\hbar}[H,A]
+
\frac{\partial A}{\partial t}
\right\rangle .
\end{equation}

\paragraph{Classical Limit Condition.}
\begin{equation}
\langle A\rangle
\longrightarrow
A_{\mathrm{cl}} .
\end{equation}

\paragraph{Primary Derivation.}
For a quantum observable $A$, the expectation value evolves by the Heisenberg equation:
\begin{equation}
\frac{\mathrm{d}}{\mathrm{d}t}\langle A\rangle
=
\left\langle
\frac{i}{\hbar}[H,A]
+
\frac{\partial A}{\partial t}
\right\rangle .
\end{equation}

When decoherence suppresses interference, expectation values behave as classical ensemble variables:
\begin{equation}
\langle A\rangle
\rightarrow
A_{\mathrm{cl}}.
\end{equation}

Macro-consistency requires that these limiting variables satisfy the corresponding classical equations:
\begin{equation}
\boxed{
\mathcal{E}_{\mathrm{macro}}(A_{\mathrm{cl}})=0 .
}
\end{equation}

\paragraph{Interpretation.}
The micro-to-macro bridge is valid when quantum expectation values reproduce classical conservation and motion laws in the decohered limit.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Gravitomagnetic Coupling Law by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Gravitomagnetic Field}\par
\[
\mathbf{B}_{g}=\nabla\times\mathbf{A}_{g}
\]
\noindent This fixes the gravitomagnetic field induced by the rapidly rotating mass distribution.\par
\noindent\textbf{2. Mass Integral}\par
\[
\mathbf{A}_{g}(\mathbf{x})=\frac{G}{c}\int \frac{\rho(\mathbf{x}^{\prime})\mathbf{v}(\mathbf{x}^{\prime})}{\lVert\mathbf{x}-\mathbf{x}^{\prime}\rVert}\,d^{3}x^{\prime}
\]
\noindent This identifies the mass-moment integral that weights the field strength.\par
\noindent\textbf{3. Coupling Strength}\par
\[
\kappa_{g}=4G/c^{2}
\]
\noindent This closes the entry by packaging the mass moment into the effective gravitomagnetic coupling coefficient.\par

\clearpage
\noindent\textbf{[ID 0382] Gravitomagnetic Coupling Law}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Gravitomagnetic Coupling Law is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This law describes how rotation of mass generates a gravitomagnetic field analogous to magnetic fields in electromagnetism, linking general relativity and gyromagnetism. \textbf{Contextual meaning:} The entry reads Gravitomagnetic Coupling Law as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the gravitomagnetic coupling in explicit field-and-moment form instead of mixing it with stray code comments. \textbf{Lemma support:} Gravitomagnetic Field; Mass Integral; Coupling Strength.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The micro-to-macro bridge is valid when quantum expectation values reproduce classical conservation and motion laws in the decohered limit.

\tzpsection{Equation Grounding}
Equation anchors: mathcal P sub 0[gamma] ;= ;exp !big(i ,Phi sub rm spin (gamma)big) ;,; Phi sub rm spin =tfrac12 ,Omega[c]+pi , u ,w+ ! !integral sub Sigma !B; S sub rm e = !integral !Big[m ,ds+ e ,A sub mu dx to the power mu+tfrac hbar 2 ,omega to the power ab S sub ab Big] ;+ ; lambdabig(1- P sub 0[gamma]big); and Hto H-boldsymbolmu sub rm g !dot ! B sub rm g ,; B sub rm g propto ratio G c to the power 2 Big(ratio 3( J !dot !hat r)hat r- J r to the power 3 Big). Proof route: show that the rotating mass distribution induces the stated gravitomagnetic field through the stated mass-moment integral. Formalization route: prove that the mass-moment integral defines the stated effective gravitomagnetic coupling coefficient.

\tzpsection{Interpretive Role}
The entry now states the gravitomagnetic coupling in explicit field-and-moment form instead of mixing it with stray code comments.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Velocity-Mass Cross Product}: The formula describing how the physical momentum of moving matter generates a secondary, twisting gravitational field.
\item \textbf{Newtonian Gravitational Scaling}: The tiny constant that dictates exactly how weak this twisting gravitational field is compared to standard electromagnetic forces.
\item \textbf{Spatially Distributed Momentum Integration}: The calculation of the total twisting force by summing up the movements of every single particle in the entire system.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0382]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0382_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0382] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Gravitomagnetic Coupling Law}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this law describes how rotation of mass generates a gravitomagnetic field analogous to
magnetic fields in electromagnetism, linking general relativ...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Gravitomagnetic Coupling Law is valid as a synchronization criterion under the coupling
conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0382_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
