\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{array}
\usepackage{microtype}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,filecolor=black,pdfauthor={Daniel Alexander Trawin},pdfcreator={Trawin, Daniel Alexander},pdftitle={Can a Higher Shell Imprint the Acoustic Ruler?},pdfsubject={TZPID Gold Spine Series II, Paper XIV of XX, DOI 10.5281/zenodo.20724489}]{hyperref}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newcommand{\Mpc}{\mathrm{Mpc}}
\newcommand{\Gpc}{\mathrm{Gpc}}
\newcommand{\OmK}{\Omega_K}
\title{Can a Higher Shell Imprint the Acoustic Ruler?\\ Feeding the $S^4$/$S^5$ Mode Ladders Through the BAO, and the Nested-Shell Beat\\[0.6em]
\large TZPID Gold Spine Series II, Paper XIV of XX}
\author{Daniel Alexander Trawin\\
\small ORCID: \href{https://orcid.org/0009-0001-4630-3715}{0009-0001-4630-3715}\\
\small DOI: \href{https://doi.org/10.5281/zenodo.20724489}{10.5281/zenodo.20724489}\\
\small \href{mailto:danielalexandertrawin@gmail.com}{danielalexandertrawin@gmail.com}}
\date{June 2026}
\begin{document}
\maketitle
\begin{abstract}
Paper I established that the baryon acoustic oscillation (BAO) ruler is the flat spherical-cavity spectrum: nodes are zeros of the spherical Bessel $j_\ell$, with the first at $k r_s = \pi$. Paper XIII gave the curved spectra of the nested shells, $k_\ell R = \sqrt{\ell(\ell+n-1)}$. This paper feeds those curved $S^3$/$S^4$/$S^5$ ladders through the same acoustic test: can a higher or outer shell project a band into the observed $\sim 150\ \Mpc$ ruler? The answer is conclusive and falsifiable. Dimension shifts the offset, not the spacing: at high $\ell$ every ladder steps by $1/R$, so a higher shell makes the same comb, shifted. With the Spartan curvature bound $|\OmK| = 0.005$ ($R_c = 62.9\ \Gpc$), the closed-enclosure mode comb is $\sim 2700\times$ finer than the BAO wiggle, so curvature is invisible at the acoustic scale---the mode-space twin of the permitted-but-unseen closed universe of Paper XII. A direct outer-shell imprint would require a $\sim 23\ \Mpc$ cluster-scale shell, ruled out. Exactly one falsifiable channel survives: a nested-shell beat, in which two concentric shells differing in radius by a fractional $\varepsilon \approx 3.7\times10^{-4}$ produce a moir\'e comb on the BAO scale---possible but fine-tuned. Dimension's only genuine fingerprint is amplitude, not spacing: the degeneracy growth $\sim \ell^{n-1}$ deposits more power per band in higher shells, an envelope tilt rather than a new peak. The higher shells are neither refuted nor detected; the spine carries one specific, currently-null-but-not-excluded prediction.
\end{abstract}
\section{Introduction: the one place a hidden shell could show}
Paper XIII fixed the observable spatial slice at $S^3$ and relegated $S^4$, $S^5$ to outer shells. If those shells are physical, can they leave any trace? The most sensitive standing-wave observable in cosmology is the BAO ruler, known to fractions of a percent. If a higher shell rings, that spacing is where it would show. We extend the worked BAO check of Paper I from the flat cavity to the curved nested ladders and find a clean, falsifiable answer.
\section{Two ladders}
The flat spherical-cavity acoustic eigenvalues are zeros of $j_\ell$; the $\ell = 0$ ladder is exactly harmonic, $j_0$ zeros $= \pi, 2\pi, 3\pi, \dots$ (Paper I). The curved enclosure on $S^n$ has the Laplace spectrum
\begin{equation}
k_\ell R = \sqrt{\ell(\ell+n-1)}: \quad S^3:\ 0,1.73,2.83,3.87; \quad S^4:\ 0,2.00,3.16,4.24; \quad S^5:\ 0,2.24,3.46,4.58.
\end{equation}
\begin{remark}[Dimension shifts the offset, not the spacing]
At high $\ell$, $\sqrt{\ell(\ell+n-1)} \to \ell + (n-1)/2$, so consecutive modes differ by $1$ in $\nu$ for all $n$; in physical wavenumber the spacing is $\Delta k \to 1/R$ independent of dimension. A higher shell makes the same comb, shifted.
\end{remark}
\section{Decisive test: curvature cannot shift the BAO}
The BAO wiggle period is $\Delta k_{\mathrm{BAO}} = 2\pi/r_s = 0.0427\ \Mpc^{-1}$. The closed-enclosure mode comb has spacing $\Delta k_{\mathrm{mode}} = 1/R_c$. With $|\OmK| = 0.005$, $R_c = c/(H_0\sqrt{|\OmK|}) = 62.9\ \Gpc$, so $\Delta k_{\mathrm{mode}} = 1.6\times10^{-5}\ \Mpc^{-1}$ and
\begin{equation}
\boxed{\ \frac{\Delta k_{\mathrm{BAO}}}{\Delta k_{\mathrm{mode}}} = \frac{2\pi R_c}{r_s} \approx 2700\ }.
\label{eq:modesperwiggle}
\end{equation}
\begin{proposition}[Curvature is acoustically invisible]
The hyperspherical mode comb is $\sim 2700\times$ finer than the BAO wiggle; at acoustic scales it is effectively continuous, and the curved $S^3$ enclosure reproduces the flat $j_\ell$ ruler. This is the mode-space counterpart of Paper XII's result that a closed universe survives the distance data precisely because its discreteness cannot be seen at $|\OmK| \lesssim 0.005$.
\end{proposition}
\section{No direct outer-shell band}
For a shell's ladder to land at the BAO period requires $1/R = \Delta k_{\mathrm{BAO}}$, i.e. $R \approx 23\ \Mpc$, galaxy-cluster scale, not a cosmic enclosure. Any outer shell ($R \gg \Gpc$) has a ladder far too dense to imprint at $\sim 150\ \Mpc$. There is no direct outer-shell BAO band.
\section{The one falsifiable channel: a nested-shell beat}
Two concentric shells of radii $R$ and $R(1+\varepsilon)$ have ladders that beat with comb spacing $\Delta_{\mathrm{beat}} \approx 1/(R\varepsilon)$. For the beat to fall on the BAO scale with $R = R_c$,
\begin{equation}
\boxed{\ \varepsilon = \frac{1/\Delta k_{\mathrm{BAO}}}{R_c} \approx 3.7\times10^{-4}\ }
\end{equation}
so two nested shells differing by $\sim 0.037\%$ in radius beat into the BAO wiggle.
\begin{remark}[A real but fine-tuned prediction]
This is the single falsifiable channel by which the nest could imprint the ruler: a faint secondary periodicity locked to the BAO. It requires commensurability of the shell radii to one part in a few thousand, so it is a signature to search for, not a generic expectation---a hypothesis with a number attached, not a detection.
\end{remark}
\section{Dimension's true fingerprint: amplitude, not spacing}
Dimension changes the degeneracy (power per band), not the spacing: $S^3:\ 4,9,16,25,36$ ($\sim \ell^2$); $S^4:\ 5,14,30,55,91$ ($\sim \ell^3$); $S^5:\ 6,20,50,105,196$ ($\sim \ell^4$). A higher shell pours more power per band---an amplitude or spectral-tilt signature in the acoustic envelope, never a new peak. A different and harder measurement than the ruler spacing.
\section{Demarcation}
\textbf{Established physics:} spherical-cavity acoustics and the $j_\ell$ ruler; the curved-space Laplace spectrum $\sqrt{\ell(\ell+n-1)}$; the BAO wiggle period $2\pi/r_s$; the moir\'e-beat relation $\Delta_{\mathrm{beat}} \approx 1/(R\varepsilon)$.

\textbf{Framework synthesis:} the reading of the nested-shell ladders as physical acoustic spectra of outer enclosures; the conclusion that curvature and higher-shell dimension cannot shift the BAO spacing; and the identification of the nested-shell beat as the spine's one BAO-observable prediction.

\textbf{Predictions:} (i) the nested-shell beat at $\varepsilon \approx 3.7\times10^{-4}$, to be searched for in high-precision power spectra; (ii) a degeneracy-driven amplitude or tilt in the acoustic envelope if higher shells contribute; (iii) the null result itself---no shift in BAO spacing from curvature at $|\OmK| \lesssim 0.005$---which the framework predicts and present data confirm.
\section{Limits of the construction}
The analysis is at the level of mode spacings and degeneracies, not a full transfer-function computation; a complete treatment would propagate the nested modes through the photon--baryon Boltzmann hierarchy. The beat channel, while falsifiable, requires a coincidence the framework does not independently motivate. The entire analysis presumes the outer shells are physical resonators (Paper XIII); if they are mere embeddings, the beat channel is empty. What the paper establishes firmly is the negative result: at the measured curvature bound, no higher shell can move the BAO ruler's spacing.
\section{Conclusion: neither refuted nor detected}
Fed through the BAO, the $S^4$/$S^5$ ladders leave the acoustic ruler untouched: their combs are either far too dense or would require cluster-scale shells. The ruler at $\sim 150\ \Mpc$ remains an $S^3$ signal. The nest could reveal itself only through a fine-tuned beat at $\varepsilon \approx 3.7\times10^{-4}$ or a degeneracy-driven amplitude tilt---a single, specific, currently-null-but-not-excluded prediction. The series now turns to the operator algebra (Paper XV) before carrying the dark-energy, unification, and release-facing closure through Papers XVI--XX.
\begin{thebibliography}{9}
\bibitem{registry} Trawin, D. A., \emph{TZPID Canonical Equation Master Registry}, TZPIDProof archive (2026).
\bibitem{paper1} Trawin, D. A., \emph{Nested Hyperspherical Enclosures}, TZPID Gold Spine Series, Paper I (2026).
\bibitem{paperXI} Trawin, D. A., \emph{Sound Before Light}, TZPID Gold Spine Series II, Paper XI (2026).
\bibitem{spartan} Trawin, D. A., \emph{The Spartan Dawn Test}, TZPID Gold Spine Series II, Paper XII (2026).
\bibitem{geometry} Trawin, D. A., \emph{Exact Nested-Sphere Geometry}, TZPID Gold Spine Series II, Paper XIII (2026).
\bibitem{planck} Planck Collaboration, \emph{Planck 2018 results. VI}, Astron.\ Astrophys.\ \textbf{641}, A6 (2020). arXiv:1807.06209.
\bibitem{desi} DESI Collaboration, \emph{DESI DR2 Results II} (2025). arXiv:2503.14738.
\bibitem{harrison} Harrison, E. R., \emph{Normal modes of vibrations of the universe}, Rev.\ Mod.\ Phys.\ \textbf{39}, 862 (1967).
\end{thebibliography}
\end{document}
