\tzpanchor{0986}
\tzpentryheader{0986}{ELSASSER NUMBER EQUILIBRIUM}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{985557a3-10d6-58db-89e7-f9953cfb1215}}\\
\textbf{PiID} & \tzpcode{5909216420198} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{993}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3755.0757 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{06.1872 rad}\\
\textbf{TZPID} & \tzpcode{ID0986} & \textbf{Node Dependencies}\quad \tzpidref{0985}\\
\textbf{Registry} & \tzpcode{registry\_id\_0986} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Elsasser Balance & Order-One Window\\
\textbf{Closure Support} & Critical Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
a(r,t) approximately G\_\{rm eff\}/,frac\{M(r,t)\}\{r\textasciicircum{}2\},qquad M(r,t)=int\_\{|x|<r\}rho(x,t)/,d\textasciicircum{}3x

\tzpsection{Canonical Equation}
\[
\Lambda=\frac{B^2}{\rho\mu_0\eta\Omega}
\]
\[
\Lambda\approx 1
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Lambda$: lemniscatic representative or canonical branch object.
    \item $B$: magnetic field magnitude.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\mu_0$: vacuum permeability constant.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0986 generated source Wolfram model *)
ClearAll[K0986, Cr0986, T, R, A, W, I, N];
eq0986$1 = HoldForm[Lambda == B^2/(rhomu0*etaOmega)];
eq0986$2 = HoldForm[Lambda == 1];

K0986 = HoldForm[{eq0986$1, eq0986$2}];

N = "normalized TRAWIN closure object for ELSASSER NUMBER EQUILIBRIUM";
I = "ELSASSER NUMBER EQUILIBRIUM integration/comparison layer";
W = "ELSASSER NUMBER EQUILIBRIUM wave or operator carrier";
A = "ELSASSER NUMBER EQUILIBRIUM admissible action/amplitude condition";
R = "ELSASSER NUMBER EQUILIBRIUM rotation/curl preservation layer";
T = "ELSASSER NUMBER EQUILIBRIUM local source condition";

Cr0986[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0986 = Cr0986[K0986];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ ELSASSER NUMBER EQUILIBRIUM local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ ELSASSER NUMBER EQUILIBRIUM rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ ELSASSER NUMBER EQUILIBRIUM admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ ELSASSER NUMBER EQUILIBRIUM wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ ELSASSER NUMBER EQUILIBRIUM integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for ELSASSER NUMBER EQUILIBRIUM.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0986] ELSASSER NUMBER EQUILIBRIUM}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\Lambda=\frac{B^2}{\rho\mu_0\eta\Omega}
\]
\[
\Lambda\approx 1
\]

\paragraph{Primary Derivation.}
To derive the stated relation by differentiating and applying the relevant definitions. giving the formula in the first line.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. From the TRAWIN perspective, the equation functions as the generalized carrier for the entry’s information content. Within the CHL view, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors ELSASSER NUMBER EQUILIBRIUM by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\Lambda=\frac{B^2}{\rho\mu_0\eta\Omega}
\]
\[
\Lambda\approx 1
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0986] ELSASSER NUMBER EQUILIBRIUM}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
ELSASSER NUMBER EQUILIBRIUM is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} a(r,t) approximately G sub rm eff /,frac M(r,t) r to the power 2 ,qquad M(r,t)=int sub |x|<r rho(x,t)/,d to the power 3x. \textbf{Contextual meaning:} The entry reads ELSASSER NUMBER EQUILIBRIUM as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry sharpens the universality narrative by replacing qualitative balance with an explicit order-one criterion. \textbf{Lemma support:} Elsasser Balance; Order-One Window; Critical Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, ELSASSER NUMBER EQUILIBRIUM is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: Lambda=ratio B to the power 2 rhomu sub 0etaOmega; Lambdaapproximately 1; and ratio F sub Lorentz F sub Coriolis similar toLambda. Proof route: show that the critical regime corresponds to order-one Elsasser balance for the stated carrier variables. Formalization route: prove that the closure metric vanishes exactly at the critical balance.

\tzpsection{Interpretive Role}
The entry sharpens the universality narrative by replacing qualitative balance with an explicit order-one criterion.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Magneto-Rotational Balancing Act}: The terrifying, razor-thin physics of perfectly matching the raw power of the magnets against the dizzying, violent spinning of the liquid metal.
\item \textbf{Coriolis-Force Cancellation}: The incredibly precise technique of using electricity to forcefully push back against the natural, twisting spin of the Earth, keeping the plasma perfectly still.
\item \textbf{Order-One Dominance Locking}: The mathematical absolute that neither the spinning nor the magnets can ever be allowed to win the tug-of-war, or the entire machine will rip itself apart.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0986]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0986].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0986] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont ELSASSER NUMBER EQUILIBRIUM}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} ELSASSER NUMBER EQUILIBRIUM is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ELSASSER NUMBER EQUILIBRIUM is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0986].
\par\endgroup
\vfill
\endgroup
\endgroup
