\tzpanchor{0099}
\tzpentryheader{0099}{Cymatic Beat Frequency Topology}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{d9c6241c-9175-5159-8062-c79fa077e805}}\\
\textbf{PiID} & \tzpcode{9821480865132} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{106}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{384.4390 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.6334 rad}\\
\textbf{TZPID} & \tzpcode{ID0099} & \textbf{Node Dependencies}\quad \tzpidref{0062}\\
\textbf{Registry} & \tzpcode{registry\_id\_0099} & \textbf{Scale}\quad waveform superposition\\
\textbf{LOC Classification} & QC611 beat structures & QA927 topological waveform analysis\\
\textbf{arXiv Classification} & Primary: nlin.PS \quad Cross-list: physics.class-ph, cs.IT & \\
\textbf{Primary Support} & Beat Superposition Operator & Frequency Split and Carrier Mean\\
\textbf{Closure Support} & Discrete Coupling Windows & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Cymatic Bifurcation Topology source supplies the beat-frequency law for nearby carriers, the frequency-splitting diagnostic, and the discrete activation windows used by the TZP cymatic coupling model.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\psi_{\mathrm{beat}}(t)=2\cos\!\bigl(\pi(f_2-f_1)t\bigr)\sin\!\bigl(\pi(f_1+f_2)t\bigr)
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\Delta f=|f_2-f_1|,\qquad \bar f=\frac{f_1+f_2}{2}
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
t_n=\frac{n}{2\Delta f}\quad(440/446\,\mathrm{Hz}:\;t_n=\frac{n}{12})
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\pi$: source equation symbol.
    \item $f_2$: source equation symbol.
    \item $f_1$: source equation symbol.
    \item $t$: source equation symbol.
    \item $t_n$: source equation symbol.
    \item $n$: integer mode index.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0099 generated source Wolfram model *)
ClearAll[K0099, Cr0099, T, R, A, W, I, N];
eq0099$1 = HoldForm[$psiBeat[t] == 2*Cos[Pi[f2 - f1]*t]*Sin[Pi[f1 + f2]*t]*$];
eq0099$2 = HoldForm[TZPSequence[$Delta*f == Abs[f2 - f1], bar*f == ((f1 + f2)/2)*$]];
eq0099$3 = HoldForm[$tN == (n/(2*Delta*f))*((440/446)*(Hz:tN == n/12))*$];

K0099 = HoldForm[{eq0099$1, eq0099$2, eq0099$3}];

N = "normalized TRAWIN closure object for Cymatic Beat Frequency Topology";
I = "Discrete Coupling Windows integration/comparison layer";
W = "Frequency Split and Carrier Mean wave or operator carrier";
A = "Beat Superposition Operator admissible action/amplitude condition";
R = "Frequency Split and Carrier Mean rotation/curl preservation layer";
T = "Beat Superposition Operator local source condition";

Cr0099[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0099 = Cr0099[K0099];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Beat Superposition Operator local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Frequency Split and Carrier Mean rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Beat Superposition Operator admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Frequency Split and Carrier Mean wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Discrete Coupling Windows integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Cymatic Beat Frequency Topology.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0099] Cymatic Beat Frequency Topology}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Carrier Superposition.}
\begin{equation}
\Psi(t)=A\cos(\omega_1t)+B\cos(\omega_2t).
\end{equation}

\paragraph{Envelope--Carrier Decomposition.}
\begin{equation}
\Psi(t)
=
2C
\cos\left(
\frac{\omega_1-\omega_2}{2}t
\right)
\cos\left(
\frac{\omega_1+\omega_2}{2}t
\right).
\end{equation}

\paragraph{Coupling Windows.}
\begin{equation}
t_k=
\frac{2\pi k}{|\omega_1-\omega_2|}.
\end{equation}

\paragraph{Primary Derivation.}
For paired carriers, the raw signal is:
\begin{equation}
\Psi(t)=A\cos(\omega_1t)+B\cos(\omega_2t).
\end{equation}

For equal or normalized amplitudes, the trigonometric sum identity yields:
\begin{equation}
\Psi(t)
=
2C
\cos\left(
\frac{\omega_1-\omega_2}{2}t
\right)
\cos\left(
\frac{\omega_1+\omega_2}{2}t
\right).
\end{equation}

Envelope maxima occur at discrete times:
\begin{equation}
\boxed{
t_k=
\frac{2\pi k}{|\omega_1-\omega_2|}.
}
\end{equation}

\paragraph{Interpretation.}
Beat topology identifies discrete envelope windows where coherent coupling is strongest.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Cymatic Beat Frequency Topology by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Beat Superposition Operator}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\psi_{\mathrm{beat}}(t)=2\cos\!\bigl(\pi(f_2-f_1)t\bigr)\sin\!\bigl(\pi(f_1+f_2)t\bigr)
$
\end{adjustbox}
\]
\noindent This records the source beat operator as a product of slow modulation and fast carrier response.\par
\noindent\textbf{2. Frequency Split and Carrier Mean}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\Delta f=|f_2-f_1|,\qquad \bar f=\frac{f_1+f_2}{2}
$
\end{adjustbox}
\]
\noindent This assigns the measurable beat split and mean carrier frequency used by the topology.\par
\noindent\textbf{3. Discrete Coupling Windows}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
t_n=\frac{n}{2\Delta f}\quad(440/446\,\mathrm{Hz}:\;t_n=\frac{n}{12})
$
\end{adjustbox}
\]
\noindent This closes the progression with the activation times where the envelope aligns with the TZP coupling window.\par

\clearpage
\noindent\textbf{[ID 0099] Cymatic Beat Frequency Topology}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Cymatic Beat Frequency Topology is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Certain beat frequencies create nodal structures and energy concentration patterns that resonate with the TZP; these cymatic patterns reveal coupling between wave interference and curvature. \textbf{Contextual meaning:} The entry reads Cymatic Beat Frequency Topology as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry gives the volume its final waveform geometry before the TZP synchronization law. It identifies the topological windows in which the bridge signal is most strongly organized and most likely to couple coherently. \textbf{Lemma support:} Beat Superposition Operator; Frequency Split and Carrier Mean; Discrete Coupling Windows.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Beat topology identifies discrete envelope windows where coherent coupling is strongest.

\tzpsection{Equation Grounding}
Equation anchors: The CymaticModulationFunctor Fcy F cy Fcy maps initial carrier waves to a superposed waveform Psi(t)=Acosu2061(omega1t)+Bcosu2061(omega2t)Psi(t)=Atextbackslash cos(omega 1 t)+Btextbackslash cos(omega 2 t)Psi(t)=Acos(omega1t)+Bcos(omega2t) with a beat envelope and a carrier wave possessing topological winding; an energy extraction operator EEE identifies optimal beat frequencies that couple to the TZP at discrete times. The CymaticModulationFunctor Fcy F cy Fcy maps initial carrier waves to a superposed waveform Psi(t)=Acosu2061(omega1t)+Bcosu2061(omega2t)Psi(t)=Atextbackslash cos(omega 1 t)+Btextbackslash cos(omega 2 t)Psi(t)=Acos(omega1t)+Bcos(omega2t) with a beat envelope and a carrier wave possessing topological winding; an energy extraction operator EEE identifies optimal beat frequencies that couple to the TZP at discrete times.

\tzpsection{Interpretive Role}
This entry gives the volume its final waveform geometry before the TZP synchronization law. It identifies the topological windows in which the bridge signal is most strongly organized and most likely to couple coherently.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Acoustic Pattern Beat Frequency Global Form}: nearby spectral language for modes, resonant structure, and admissible oscillation.
\item \textbf{Acoustic Pattern Global Form Spectral Analogue}: nearby spectral language for modes, resonant structure, and admissible oscillation.
\item \textbf{Global Form Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0099]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0099_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0099] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Cymatic Beat Frequency Topology}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} certain beat frequencies create nodal structures and energy concentration patterns that
resonate with the TZP; these cymatic patterns reveal coupli...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Cymatic Beat Frequency Topology is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0099_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
