\section*{ID8644: Relation: Indicates a Pure 3-Limit Ratio (Using Only 2's and 3's), Which Connects to…}
\paragraph{Metadata.}
PiID: 2920419748442 | RTEID: RTE:P33566.5716:T5.0419 | UUID: 952b85bb-489f-509b-a88e-bee4d2be6566

\paragraph{Canonical Statement.}
\$. Here \$16/15 \textbackslash{}approx 1.06667\$ and \$10/9 \textbackslash{}approx 1.11111\$ are the two given ratios. Their product yields \$1.18518...\$, providing a neat bridge between 185 and those rational values. In other words, multiplying a number by 16/15 and then by 10/9 is equivalent to multiplying by 32/27 (about +18.5185\% net increase). This is interesting in part because \$32/27\$ emerges in various mathematical contexts (as we'll see in music and geometry below). The prime factorization \$\$32/27=2\textasciicircum{}\{\textbackslash{}wedge\}5/3\textasciicircum{}\{\textbackslash{}wedge\}3\$\$ indicates a pure 3-limit ratio (using only 2's and 3's), which connects to Pythagorean tuning in music. In summary, the number 185 shows up in base-10 cycles and as part of a special fraction (32/27) that links two simple rational steps into one compound effect. Musical Intervals and the 185 Ratio In music theory, 16/15 and 10/9 are just intonation intervals that appear in diatonic scales. 16:15 is the just diatonic semitone (minor second) of approximately 111.7 cents - for instance, the inte

\paragraph{Canonical Equation.}
\[
indicates a pure 3-limit ratio (using only 2's and 3's), which connects to Pythagorean tuning in music. In summary, the number 185 shows up in base-10 cycles and as part of a special fraction (32/27) that links two simple rational steps into one compound effect. Musical Intervals and the 185 Ratio In music theory, 16/15 and 10/9 are just intonation intervals that appear in diatonic scales. 16:15 is the just diatonic semitone (minor second) of approximately 111.7 cents - for instance, the interval between E and F or B and C in a just-tuned C major scale is 16:15 10:9 is a just minor whole tone (~182.4 cents), a slightly smaller whole step than the 9:8 major tone (203.9 cents). In a 5-limit just C major scale, the step from D to E is 10:9 and from E to F is 16:15. When these two intervals are compounded (D→E→F), the result is 32:27, which is the Pythagorean minor third spanning from D to F. Indeed, $32:27\approx1.185185$ corresponds to about 294.13 centsen.wi, slightly narrower than an equal-tempered minor third (300 cents). This 32:27 semiditone arises between the 2nd and 4th scale degrees of the just major scale (e.g. D up to F in C major). It is essentially the difference between a perfect fifth (3:2) and a Pythagorean major third (81:64), since $(3/2)÷(81/64)=32/27$medieval.org. • • • Just diatonic semitone:
\]

\paragraph{Dictionary.}
Relation: indicates a pure 3-limit ratio (using only 2's and 3's), which connects to Pythagorean tuning in music. In summary, the number 185 shows up in base-10

\paragraph{Encyclopedia.}
Relation: Indicates a Pure 3-Limit Ratio (Using Only 2's and 3's), Which Connects to… is a scaling / order-of-magnitude relation, written indicates a pure 3-limit ratio (using only 2's and 3's), which connects to Pytha. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from m, v, a, l, o, r, defining indicates a pure 3-limit ratio (using only 2's and 3's), which connects to Pythagorean tuning in music. In summary, the number 185 shows up in base-10 cycles and as part of a special fraction (32/27) that links two simple rational steps into one compound effect. Musical Intervals and the 185 Ratio In music theory, 16/15 and 10/9 are…
