\tzpanchor{0219}
\tzpentryheader{0219}{Quantum-Coriolis Operator}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{0cb02b0e-8e7c-542e-a5fd-2afd92efb34f}}\\
\textbf{PiID} & \tzpcode{1284756482337} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{226}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{850.4256 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.4012 rad}\\
\textbf{TZPID} & \tzpcode{ID0219} & \textbf{Node Dependencies}\quad \tzpidref{0218}\\
\textbf{Registry} & \tzpcode{registry\_id\_0219} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Rotating Hamiltonian & Unitary Evolution\\
\textbf{Closure Support} & Berry Phase & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The quantum-Coriolis operator bundles together the rotational Hamiltonian, the Coriolis-induced density-matrix bifurcation, and the Berry phase accumulated during rotation:

\tzpsection{Canonical Equation}
\[ H_{\mathrm{rot}} = -\hbar\, \Omega\cdot J, \] \[ \rho_{\mathrm{bif}} = \mathrm{TensorDecompose}\!\bigl(-2\,\Omega \times (\rho \otimes p)\bigr), \] \[ \gamma_{\mathrm{B}} = \int_{0}^{2\pi/\Omega} \langle \psi(t) \mid i\,\rho_{\mathrm{median}} = 0 \mid \psi(t)\rangle\,dt. \] The operator is the ordered triple formed by these three components.

\[
H_{\mathrm{rot}} = -\hbar\,\Omega\!\cdot\!J
\]
\[
U(t) = \exp\!\left(-i H_{\mathrm{rot}} t/\hbar\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H_{\mathrm{rot}}$: source equation symbol.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $J$: source equation symbol.
    \item $\rho_{\mathrm{bif}}$: source equation symbol.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\gamma_{\mathrm{B}}$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $\rho_{\mathrm{median}}$: source equation symbol.
    \item $U$: auxiliary source state or local chart variable.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0219 generated source Wolfram model *)
ClearAll[K0219, Cr0219, T, R, A, W, I, N];
eq0219$1 = HoldForm[HRot == (-hbar)*Omega*J];
eq0219$2 = HoldForm[rhoBif == TensorDecompose[-2*Omega*(rho*TensorProduct*p)]];
eq0219$3 = HoldForm[gammaB == Integral0^(2*(Pi/Omega))*Inner[psi[t], i*rhoMedian == 0, psi[t]]*dt];
eq0219$4 = HoldForm[HRot == (-hbar)*Omega*J];
eq0219$5 = HoldForm[U[t] == exp[(-i)*HRot*(t/hbar)]];
eq0219$6 = HoldForm[gammaB == Integral0^(2*(Pi/Omega))*Inner[psi[t], iPartialT, psi[t]]*dt];

K0219 = HoldForm[{eq0219$1, eq0219$2, eq0219$3, eq0219$4, eq0219$5, eq0219$6}];

N = "normalized TRAWIN closure object for Quantum-Coriolis Operator";
I = "Berry Phase integration/comparison layer";
W = "Unitary Evolution wave or operator carrier";
A = "Rotating Hamiltonian admissible action/amplitude condition";
R = "Unitary Evolution rotation/curl preservation layer";
T = "Rotating Hamiltonian local source condition";

Cr0219[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0219 = Cr0219[K0219];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Rotating Hamiltonian local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Unitary Evolution rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Rotating Hamiltonian admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Unitary Evolution wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Berry Phase integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum-Coriolis Operator.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0219] Quantum-Coriolis Operator}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Box_T\phi
=
g^{ab}
\nabla^{T}_{a}
\nabla^{T}_{b}
\phi .
\end{equation}

\paragraph{Primary Derivation.}
The ordinary d'Alembertian is the metric contraction of two covariant derivatives acting on a field.  
In Trawinistic geometry, replace the ordinary covariant derivative with $\nabla^T$:

\begin{equation}
\nabla_a\nabla_b\phi
\quad\longrightarrow\quad
\nabla^T_a\nabla^T_b\phi .
\end{equation}

Then contract using the regularized inverse metric $g^{ab}$:

\begin{equation}
\Box_T\phi
=
g^{ab}
\nabla^{T}_{a}
\nabla^{T}_{b}
\phi .
\end{equation}

\paragraph{Interpretation.}
$\Box_T$ extends wave propagation and field equations into the Trawinistic manifold by replacing ordinary derivatives with TZP-compatible covariant derivatives.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum-Coriolis Operator by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Rotating Hamiltonian}\par
\[
H_{\mathrm{rot}} = -\hbar\,\Omega\!\cdot\!J
\]
\noindent This fixes the rotating Hamiltonian that drives the Coriolis-sector quantum dynamics.\par
\noindent\textbf{2. Unitary Evolution}\par
\[
U(t) = \exp\!\left(-i H_{\mathrm{rot}} t/\hbar\right)
\]
\noindent This promotes the rotating generator into an actual unitary evolution law.\par
\noindent\textbf{3. Berry Phase}\par
\[
gamma_{\mathrm{B}} = \int_{0}^{2\pi/\Omega}\langle \psi(t)\mid i\partial_t \mid \psi(t)\rangle\,dt
\]
\noindent This closes the entry with the geometric phase accumulated over the rotation cycle.\par

\clearpage
\noindent\textbf{[ID 0219] Quantum-Coriolis Operator}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum-Coriolis Operator is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The quantum-Coriolis operator bundles together the rotational Hamiltonian, the Coriolis-induced density-matrix bifurcation, and the Berry phase accumulated during rotation: H sub rot = -hbar Omegadot J, rho sub bif = TensorDecompose bigl(-2 Omega times (rho otimes p)bigr), gamma sub B = integral sub 0 to the power 2pi/Omega psi(t) mid i rho sub median = 0 mid psi(t) dt. The operator is the ordered triple formed by these three components. \textbf{Contextual meaning:} The entry reads Quantum-Coriolis Operator as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now carries the actual rotational quantum data of the Coriolis operator instead of only the abstract operator shell. \textbf{Lemma support:} Rotating Hamiltonian; Unitary Evolution; Berry Phase.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub T extends wave propagation and field equations into the Trawinistic manifold by replacing ordinary derivatives with TZP-compatible covariant derivatives.

\tzpsection{Equation Grounding}
Equation anchors: H sub rot = -hbar Omega dot J; U(t) = exp (-i H sub rot t/hbar); and gamma sub B = integral sub 0 to the power 2pi/Omega psi(t)mid ipartial sub t mid psi(t) dt. Proof route: show that the rotating Hamiltonian generates the stated unitary evolution and induces the stated cycle Berry phase. Formalization route: prove that cyclic evolution under the rotating Hamiltonian yields the stated Berry-phase integral.

\tzpsection{Interpretive Role}
The entry now carries the actual rotational quantum data of the Coriolis operator instead of only the abstract operator shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Rotation-Induced Spin Phase Shift}: The quantum mechanical phase acquired by a particle's wavefunction due solely to the rotation of the observer's reference frame.
\item \textbf{Non-Inertial Quantum Evolution Generator}: The modified Hamiltonian explicitly incorporating the Coriolis effect as an effective vector potential.
\item \textbf{Effective Magnetic Field Analogue}: The mathematical equivalence demonstrating that mechanical rotation acts identically on a wavefunction as a true magnetic field.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0219]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0219_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0219] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum-Coriolis Operator}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the quantum-Coriolis operator bundles together the rotational Hamiltonian, the Coriolis-
induced density-matrix bifurcation, and the Berry phase acc...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum-Coriolis Operator is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0219_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
