\tzpanchor{0227}
\tzpentryheader{0227}{Simplicial Complex Entropy}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{ddc1b4d1-1cd5-56ff-9572-b8743976cb75}}\\
\textbf{PiID} & \tzpcode{8233786783165} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{234}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{881.4914 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.4524 rad}\\
\textbf{TZPID} & \tzpcode{ID0227} & \textbf{Node Dependencies}\quad \tzpidref{0226}\\
\textbf{Registry} & \tzpcode{registry\_id\_0227} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Entropy Weight & Normalized Distribution\\
\textbf{Closure Support} & Topological Aggregate & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This measure quantifies the diversity of simplex types (vertices, edges, triangles, etc.) in the simplicial complex built from the data.

\tzpsection{Canonical Equation}
\[
\chi(K)=\sum_k(-1)^k\beta_k
\]
\[
H_K=-\sum_{\sigma\in K}p_\sigma\log p_\sigma
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $K$: source equation symbol.
    \item $H_K$: source equation symbol.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $\mathcal{K}_{0227}$: canonical registry object for entry ID 0227.
    \item $\chi(K)$: source equation symbol.
    \item $\beta$: source equation symbol.
    \item $H$: source equation symbol.
    \item $i(K)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0227 generated source Wolfram model *)
ClearAll[K0227, Cr0227, T, R, A, W, I, N];
eq0227$1 = HoldForm[chi[K] == SumK[-1]^kbetaK];
eq0227$2 = HoldForm[HK == -Sum[p[sigma]*Log[p[sigma]], {sigma, K}]];

K0227 = HoldForm[{eq0227$1, eq0227$2}];

N = "normalized TRAWIN closure object for Simplicial Complex Entropy";
I = "Topological Aggregate integration/comparison layer";
W = "Normalized Distribution wave or operator carrier";
A = "Entropy Weight admissible action/amplitude condition";
R = "Normalized Distribution rotation/curl preservation layer";
T = "Entropy Weight local source condition";

Cr0227[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0227 = Cr0227[K0227];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Entropy Weight local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Normalized Distribution rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Entropy Weight admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Normalized Distribution wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Aggregate integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Simplicial Complex Entropy.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0227] Simplicial Complex Entropy}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}

Simplicial-complex entropy is derived from the distribution of simplex counts or Betti-sector contributions across dimensions of the complex.

\paragraph{Primary Derivation.}

Let \(K\) be a finite simplicial complex and let \(f_k\) denote the number of \(k\)-simplices in \(K\). The total simplex mass is
\[
F_K=\sum_{k\ge 0} f_k.
\]
When \(F_K>0\), define the dimension distribution
\[
q_k=\frac{f_k}{F_K},\qquad \sum_{k\ge 0}q_k=1.
\]
The simplicial entropy is
\[
S_{\Delta}(K)=-\sum_{k\ge 0}q_k\log q_k.
\]
The same complex carries the Euler characteristic
\[
\chi(K)=\sum_{k\ge 0}(-1)^k\beta_k,
\]
where \(\beta_k=\operatorname{rank}H_k(K)\) is the \(k\)th Betti number. A topology-weighted entropy diagnostic is then
\[
\mathcal{E}_{K}=S_{\Delta}(K)+\lambda\,|\chi(K)|.
\]

\paragraph{Wolfram Form.}
\begin{verbatim}
q = f/Total[f];
SDelta = -Total[q*Log[q]];
ChiK = Sum[(-1)^k*beta[k], {k, 0, kmax}];
EK = SDelta + lambda*Abs[ChiK];
\end{verbatim}

\paragraph{Interpretation.}

ID 0227 converts the combinatorial body of a simplicial complex into an entropy measure while keeping the Euler-characteristic aggregate visible as the topological closure term.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Simplicial Complex Entropy by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Entropy Weight}\par
\[
\chi(K)=\sum_k(-1)^k\beta_k
\]
\noindent This records the local information weight carried by the persistence data or structural channel.\par
\noindent\textbf{2. Normalized Distribution}\par
\[
\chi(K)=\sum_k(-1)^k\beta_k
\]
\noindent This makes the entropy law admissible by normalizing the supporting lifetimes or amplitudes.\par
\noindent\textbf{3. Topological Aggregate}\par
\[
\chi(K)=\sum_k(-1)^k\beta_k
\]
\noindent This closes the entry by recombining the filtered sectors into one total diagnostic.\par

\clearpage
\noindent\textbf{[ID 0227] Simplicial Complex Entropy}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Simplicial Complex Entropy is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This measure quantifies the diversity of simplex types (vertices, edges, triangles, etc.) in the simplicial complex built from the data. \textbf{Contextual meaning:} The entry reads Simplicial Complex Entropy as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers. \textbf{Lemma support:} Entropy Weight; Normalized Distribution; Topological Aggregate.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Non-commutativity introduces a minimal area scale near the zero point. Coordinate uncertainty becomes intrinsic rather than an artefact of measurement.

\tzpsection{Equation Grounding}
Equation anchors: p sub sigma=ratio w sub sigma sum sub tauin K w sub tau; H sub K=-sum sub sigmain K p sub sigmalog p sub sigma; and chi(K)=sum sub k(-1) to the power kbeta sub k. Proof route: show that the normalized support distribution induces a well-defined entropy functional for the stated topological or informational channel. Formalization route: prove that positivity and normalization of the support weights imply finiteness of the stated entropy functional.

\tzpsection{Interpretive Role}
The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Combinatorial Lattice Information Measure}: The entropy calculated from the probability distribution of different-dimensional simplices (nodes, edges, triangles) forming a network.
\item \textbf{Euler Characteristic Probability Weighting}: The incorporation of the fundamental topological invariant into a statistical mechanics framework of the network structure.
\item \textbf{Simplex-Resolution Uncertainty}: The measurement of the inherent structural ambiguity present when observing a discrete network at varying levels of coarse-graining.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0227]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0227_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0227] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Simplicial Complex Entropy}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this measure quantifies the diversity of simplex types (vertices, edges, triangles,
etc.) in the simplicial complex built from the data

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Simplicial Complex Entropy is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that this measure quantifies the diversity of simplex types
(vertices, edges, triangles, etc.) in the simplicial complex built from the data. Non-
commutativity introduces a minimal area scale near the zero point. Coordinate
uncertainty becomes intrinsic rather than an artefact of measurement.. The CHL
validation treats the equation as the formal anchor and the semantic text as the
interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0227_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
