\tzpanchor{0303}
\tzpentryheader{0303}{Rotating Double Helix Geometry}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{8536be95-fadb-5dec-a4e5-85506ef30864}}\\
\textbf{PiID} & \tzpcode{5870066063155} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{310}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1176.6163 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9387 rad}\\
\textbf{TZPID} & \tzpcode{ID0303} & \textbf{Node Dependencies}\quad \tzpidref{0302}\\
\textbf{Registry} & \tzpcode{registry\_id\_0303} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & First Helix Strand & Second Helix Strand\\
\textbf{Closure Support} & Rotation Carrier & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The rotating double helix describes an optical propagation medium combining spatial helical paths with temporal rotation.

\tzpsection{Canonical Equation}
\[
s_1(t,\Omega)=R_z(\Omega t)\!\left(R\cos\!\frac{2\pi t}{P},\,R\sin\!\frac{2\pi t}{P},\,t\right)
\]
\[
s_2(t,\Omega)=R_z(\Omega t)\!\left(R\cos\!\left(\frac{2\pi t}{P}+\pi\right),\,R\sin\!\left(\frac{2\pi t}{P}+\pi\right),\,t\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $s_1$: source equation symbol.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $R_z$: source equation symbol.
    \item $t$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\pi$: source equation symbol.
    \item $s_2$: source equation symbol.
    \item $\theta$: phase angle or local angular coordinate.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0303 generated source Wolfram model *)
ClearAll[K0303, Cr0303, T, R, A, W, I, N];
eq0303$1 = HoldForm[s1[t, Omega] == RZ[Omega*t][R*Cos[(2*Pi*t)/P], R*Sin[(2*Pi*t)/P], t]];
eq0303$2 = HoldForm[s2[t, Omega] == RZ[Omega*t][R*Cos[(2*Pi*t)/P + Pi], R*Sin[(2*Pi*t)/P + Pi], t]];
eq0303$3 = HoldForm[RZ[theta] == Costheta - Sintheta0*Sintheta*Costheta0001];

K0303 = HoldForm[{eq0303$1, eq0303$2, eq0303$3}];

N = "normalized TRAWIN closure object for Rotating Double Helix Geometry";
I = "Rotation Carrier integration/comparison layer";
W = "Second Helix Strand wave or operator carrier";
A = "First Helix Strand admissible action/amplitude condition";
R = "Second Helix Strand rotation/curl preservation layer";
T = "First Helix Strand local source condition";

Cr0303[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0303 = Cr0303[K0303];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ First Helix Strand local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Second Helix Strand rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ First Helix Strand admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Second Helix Strand wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Rotation Carrier integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Rotating Double Helix Geometry.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0303] Rotating Double Helix Geometry}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
The local topological dimension at the TZP may transition among nearby dimensional states:

\begin{equation}
\dim_p(M)\in\{n,n-1,n+1\}.
\end{equation}

\paragraph{Primary Derivation.}
Let $M$ be an $n$-dimensional manifold away from $p$. For $x\neq p$,

\begin{equation}
\dim_x(M)=n .
\end{equation}

At $p$, however, the metric degeneracy and lemniscatic self-intersection create a local ambiguity: two branches of the manifold meet at one point.

A self-intersection may locally reduce distinguishable dimensional freedom, while bifurcation into two branches may locally increase effective adjacency. Therefore the local dimensional value is not fixed to $n$ alone, but may occupy the set:

\begin{equation}
\dim_p(M)\in\{n-1,n,n+1\}.
\end{equation}

\paragraph{Interpretation.}
The TZP acts as a dimensional seam. It is not merely located inside a dimension; it controls the transition between neighboring effective dimensional states.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Rotating Double Helix Geometry by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. First Helix Strand}\par
\[
s_1(t,\Omega)=R_z(\Omega t)\!\left(R\cos\!\frac{2\pi t}{P},\,R\sin\!\frac{2\pi t}{P},\,t\right)
\]
\noindent This fixes the first rotating helical strand as an explicit parametric carrier.\par
\noindent\textbf{2. Second Helix Strand}\par
\[
s_2(t,\Omega)=R_z(\Omega t)\!\left(R\cos\!\left(\frac{2\pi t}{P}+\pi\right),\,R\sin\!\left(\frac{2\pi t}{P}+\pi\right),\,t\right)
\]
\noindent This adds the antipodal strand that completes the double-helix geometry.\par
\noindent\textbf{3. Rotation Carrier}\par
\[
R_z(\theta)=\begin{pmatrix}\cos\theta & -\sin\theta & 0\\ \sin\theta & \cos\theta & 0\\ 0 & 0 & 1\end{pmatrix}
\]
\noindent This closes the entry by defining the rotation operator that transports both strands.\par

\clearpage
\noindent\textbf{[ID 0303] Rotating Double Helix Geometry}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Rotating Double Helix Geometry is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The rotating double helix describes an optical propagation medium combining spatial helical paths with temporal rotation. \textbf{Contextual meaning:} The entry reads Rotating Double Helix Geometry as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the double helix as an actual rotating parametric geometry instead of carrying corrupted extraction prose into display mode. \textbf{Lemma support:} First Helix Strand; Second Helix Strand; Rotation Carrier.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP acts as a dimensional seam. It is not merely located inside a dimension; it controls the transition between neighboring effective dimensional states.

\tzpsection{Equation Grounding}
Equation anchors: s sub 1(t,Omega)=R sub z(Omega t) (Rcos ratio 2pi t P , Rsin ratio 2pi t P , t); s sub 2(t,Omega)=R sub z(Omega t) (Rcos (ratio 2pi t P +pi), Rsin (ratio 2pi t P +pi), t); and R sub z(theta)=begin pmatrix costheta \& -sintheta \& 0 sintheta \& costheta \& 0 0 \& 0 \& 1end pmatrix. Proof route: show that the two helical strands are related by antipodal phase shift and remain coherent under the stated rotational transport. Formalization route: prove that the rotation carrier preserves the double-helix relation between the two parametrized strands.

\tzpsection{Interpretive Role}
The entry now states the double helix as an actual rotating parametric geometry instead of carrying corrupted extraction prose into display mode.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Chiral Frame Rotation}: The active transport mechanism spinning a coupled dual-strand structure through ambient spacetime.
\item \textbf{Parametric Helical Transport}: The mathematical formulation of twin interlocking spiraling trajectories preserving constant mutual distance.
\item \textbf{Torsional Orbit Parametrization}: The geometric rule dictating the angular winding rate of a dual-phase system under continuous rotation.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0303]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0303_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0303] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Rotating Double Helix Geometry}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the rotating double helix describes an optical propagation medium combining spatial
helical paths with temporal rotation

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Rotating Double Helix Geometry is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that the rotating double helix describes an optical
propagation medium combining spatial helical paths with temporal rotation. The TZP acts
as a dimensional seam. It is not merely located inside a dimension; it controls the
transition between neighboring effective dimensional states.. The CHL validation treats
the equation as the formal anchor and the semantic text as the interpretation
constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0303_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
