\section*{ID8653: Definition of G\_backslash Texteffective}
\paragraph{Metadata.}
PiID: 8442360800719 | RTEID: RTE:P33601.5206:T5.0995 | UUID: cee9bfac-0e2c-59c6-b923-cfb0677a1f9a

\paragraph{Canonical Statement.}
ontext: Another place 1.185 arises is in discussions of spacetime curvature. If one posits a slight uniform enhancement to gravity's strength (on certain scales) by \textasciitilde{}18.5\%, then observed curvature could exceed what visible mass accounts for by a factor of 1.185. This is an elegant thought: rather than invoking dark matter, perhaps the "fabric" of spacetime carries extra curvature as a geometric effect amounting to an 18.5\% boost. For example, a galaxy's rotation or lensing might be explained if \$\$G\_\{\textbackslash{}backslash text\{effective\}\}=1.185,G\$\$ in that region. No evidence yet pins exactly 18.5\% - it's more of a design principle within the TZP theory, hinting that if new physics tweaks gravity, it might do so by this fraction. Interestingly, the double value 2.37037 has a mathematical guise as well: \$\$2.37037=64/27=(4/3)\textasciicircum{}\{\textbackslash{}wedge\}3\$\$. The fact that \$ \$(4/3)\textasciicircum{}\{\textbackslash{}wedge\}3\$\$

\paragraph{Canonical Equation.}
\[
G_{\backslash text{effective}}=1.185,G
\]

\paragraph{Dictionary.}
Definition of G\_backslash Texteffective — G\_backslash texteffective=1.185,G

\paragraph{Encyclopedia.}
Definition of G\_backslash Texteffective is an algebraic definition, written G\_backslash texteffective=1.185,G. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from G, defining G\_backslash texteffective. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
