\tzpanchor{0045}
\tzpentryheader{0045}{Dimensionless Gyromagnetic Coupling Constant}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{37e93010-5bdc-5d77-9664-1a76b84f626d}}\\
\textbf{PiID} & \tzpcode{3751058209749} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{52}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{174.7450 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.2879 rad}\\
\textbf{TZPID} & \tzpcode{ID0045} & \textbf{Node Dependencies}\quad \tzpidref{0044}\\
\textbf{Registry} & \tzpcode{registry\_id\_0045} & \textbf{Scale}\quad gyromagnetic comparison\\
\textbf{LOC Classification} & QC809 magnetic moment ratios & QC20 dimensionless parameters\\
\textbf{arXiv Classification} & Primary: astro-ph.SR \quad Cross-list: physics.plasm-ph, gr-qc & \\
\textbf{Primary Support} & Observed Magnetic Moment & Rotational Normalizer\\
\textbf{Closure Support} & Dimensionless Coupling & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This constant quantifies the universality of the relationship between rotation and magnetism.

\tzpsection{Canonical Equation}
\[
g_{\mu}
=
\frac{\mu}{M R^{2}\Omega}
\]
\[
g_{\mu} = \mathcal{O}(1)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $g_{\mu}$: source equation symbol.
    \item $\mu$: source equation symbol.
    \item $M$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $\mathcal{O}(1)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0045 generated source Wolfram model *)
ClearAll[K0045, Cr0045, T, R, A, W, I, N];
eq0045$1 = HoldForm[gMu == mu/(M*R^2*Omega)];
eq0045$2 = HoldForm[gMu == O[1]];
eq0045$3 = HoldForm[mu];
eq0045$4 = HoldForm[M*R^2*Omega];
eq0045$5 = HoldForm[gMu == mu/(M*R^2*Omega) == O[1]];

K0045 = HoldForm[{eq0045$1, eq0045$2, eq0045$3, eq0045$4, eq0045$5}];

N = "normalized TRAWIN closure object for Dimensionless Gyromagnetic Coupling Constant";
I = "Dimensionless Coupling integration/comparison layer";
W = "Rotational Normalizer wave or operator carrier";
A = "Observed Magnetic Moment admissible action/amplitude condition";
R = "Rotational Normalizer rotation/curl preservation layer";
T = "Observed Magnetic Moment local source condition";

Cr0045[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0045 = Cr0045[K0045];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Observed Magnetic Moment local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Rotational Normalizer rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Observed Magnetic Moment admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Rotational Normalizer wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Dimensionless Coupling integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Dimensionless Gyromagnetic Coupling Constant.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0045] Dimensionless Gyromagnetic Coupling Constant}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
g_{\mu}
=
\frac{\mu}
{MR^2\Omega}.
\end{equation}

\paragraph{Primary Derivation.}
Starting from the scaling law:

\begin{equation}
\mu
=
kMR^2\Omega ,
\end{equation}

divide both sides by the natural rotational magnetic scale:

\begin{equation}
MR^2\Omega .
\end{equation}

This gives:

\begin{equation}
\frac{\mu}{MR^2\Omega}=k .
\end{equation}

Define the dimensionless gyromagnetic coupling constant as:

\begin{equation}
\boxed{
g_{\mu}
=
\frac{\mu}
{MR^2\Omega}.
}
\end{equation}

\paragraph{Interpretation.}
$g_{\mu}$ removes ordinary scale factors from the magnetic moment and isolates the dimensionless coupling strength of the rotating system.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Dimensionless Gyromagnetic Coupling Constant by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Observed Magnetic Moment}\par
\[
\mu
\]
\noindent This is the dimensional observable measured from the rotating system.\par
\noindent\textbf{2. Rotational Normalizer}\par
\[
M R^{2}\Omega
\]
\noindent This is the universal scale factor imported from the magnetic-moment law.\par
\noindent\textbf{3. Dimensionless Coupling}\par
\[
g_{\mu}
=
\frac{\mu}{M R^{2}\Omega}
=
\mathcal{O}(1)
\]
\noindent This closes the progression by expressing magnetic response as a comparable order-one constant.\par

\clearpage
\noindent\textbf{[ID 0045] Dimensionless Gyromagnetic Coupling Constant}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Dimensionless Gyromagnetic Coupling Constant is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This constant quantifies the universality of the relationship between rotation and magnetism. \textbf{Contextual meaning:} The entry reads Dimensionless Gyromagnetic Coupling Constant as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This coupling is the clean registry statistic for comparing magnetic moment data. It removes the raw size of the object from the comparison and exposes whether the universal scaling law is actually holding. \textbf{Lemma support:} Observed Magnetic Moment; Rotational Normalizer; Dimensionless Coupling.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
g sub removes ordinary scale factors from the magnetic moment and isolates the dimensionless coupling strength of the rotating system.

\tzpsection{Equation Grounding}
Equation anchors: The dimensionless gyromagnetic coupling constant g sub mu is defined by g mu=muM R2 Omegagtextbackslash mu =ratio mu Mtextbackslash,R to the power 2textbackslash,Omega g mu=MR2Omegamu, where mu is the magnetic moment and M,R,OmegaM,R,OmegaM,R,Omega as in ID ,044. In the Trawinistic framework, g sub mu is predicted to be O(1) O (1)O(1) across systems. The dimensionless gyromagnetic coupling constant g sub mu is defined by g mu=muM R2 Omegagtextbackslash mu =ratio mu Mtextbackslash,R to the power 2textbackslash,Omega g mu=MR2Omegamu, where mu is the magnetic moment and M,R,OmegaM,R,OmegaM,R,Omega as in ID ,044. In the Trawinistic framework, g sub mu is predicted to be O(1) O (1)O(1) across systems.

\tzpsection{Interpretive Role}
This coupling is the clean registry statistic for comparing magnetic moment data. It removes the raw size of the object from the comparison and exposes whether the universal scaling law is actually holding.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Dimensionless Spin-Magnetic Interaction Link Constant}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\item \textbf{Spin-Magnetic Interaction Link Rotating-Field Analogue}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\item \textbf{Interaction Link Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0045]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0045_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0045] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Dimensionless Gyromagnetic Coupling Constant}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this constant quantifies the universality of the relationship between rotation and
magnetism

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Dimensionless Gyromagnetic Coupling Constant is valid as a synchronization criterion
under the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0045_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
