\tzpanchor{0306}
\tzpentryheader{0306}{Quantum State Space Decomposition}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{baf9151d-23d8-52ef-946c-ec2462096540}}\\
\textbf{PiID} & \tzpcode{0066063155881} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{313}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1188.2660 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9579 rad}\\
\textbf{TZPID} & \tzpcode{ID0306} & \textbf{Node Dependencies}\quad \tzpidref{0305}\\
\textbf{Registry} & \tzpcode{registry\_id\_0306} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Hilbert Factorization & OAM Dimension\\
\textbf{Closure Support} & Polarization Sector & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The total Hilbert space used for quantum holographic navigation factors as /(H\_\{mathrm\{total\}\} = H\_\{mathrm\{spatial\}\} otimes H\_\{mathrm\{OAM\}\} otimes H\_\{mathrm\{polarization\}\} otimes H\_\{mathrm\{frequency\}\}/), where /(dim(H\_\{mathrm\{spatial\}\}) = 153,600/), /(dim(H\_\{mathrm\{OAM\}\}) = 2 m\_\{max\} + 1/), /(dim(H\_\{mathrm\{polarization\}\}) = 2/), and /(dim(H\_\{mathrm\{frequency\}\}) = infinity/).

\tzpsection{Canonical Equation}
\[
\Phi_Q:\mathbf{SpinRep}\to\mathbf{Hilb}
\]
\[
\Phi_Q(J_z)=\bigoplus_{m=-j}^{j}H_m
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Phi_Q$: flux, phase, or topological map term in the source equation.
    \item $J_z$: source equation symbol.
    \item $H_m$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0306 generated source Wolfram model *)
ClearAll[K0306, Cr0306, T, R, A, W, I, N];
eq0306$1 = HoldForm[PhiQ[mathbfSpinRep] -> mathbfHilb];
eq0306$2 = HoldForm[PhiQ[JZ] == bigoplusMj^j*HM];
eq0306$3 = HoldForm[PhiQ[Exp[I*phi*JZ]] == diag[Exp[I*mphi]]*_*(m == -j)^j];

K0306 = HoldForm[{eq0306$1, eq0306$2, eq0306$3}];

N = "normalized TRAWIN closure object for Quantum State Space Decomposition";
I = "Polarization Sector integration/comparison layer";
W = "OAM Dimension wave or operator carrier";
A = "Hilbert Factorization admissible action/amplitude condition";
R = "OAM Dimension rotation/curl preservation layer";
T = "Hilbert Factorization local source condition";

Cr0306[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0306 = Cr0306[K0306];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Hilbert Factorization local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ OAM Dimension rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Hilbert Factorization admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ OAM Dimension wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Polarization Sector integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum State Space Decomposition.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0306] Quantum State Space Decomposition}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
u_T := \int_{\Gamma}\sqrt{|g|}\,\mathrm{d}\ell .
\end{equation}

\paragraph{Primary Derivation.}
Let $\Gamma$ be a fundamental loop encircling the Trawin Zero Point exactly once.  
The infinitesimal line element induced by the metric is:

\begin{equation}
\mathrm{d}s = \sqrt{|g|}\,\mathrm{d}\ell .
\end{equation}

Integrating this metric-weighted length around the loop gives the primitive unit associated with one complete encirclement of the TZP:

\begin{equation}
u_T = \int_{\Gamma}\mathrm{d}s .
\end{equation}

Substituting the line element yields:

\begin{equation}
\boxed{
u_T := \int_{\Gamma}\sqrt{|g|}\,\mathrm{d}\ell .
}
\end{equation}

\paragraph{Interpretation.}
The Trawin base unit $u_T$ is the fundamental geometric unit obtained by completing one metric-weighted loop around the TZP.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum State Space Decomposition by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Hilbert Factorization}\par
\[
\Phi_Q:\mathbf{SpinRep}\to\mathbf{Hilb}
\]
\noindent This fixes the full tensor-product decomposition of the quantum navigation state space.\par
\noindent\textbf{2. OAM Dimension}\par
\[
\Phi_Q(J_z)=\bigoplus_{m=-j}^{j}H_m
\]
\noindent This identifies the orbital-angular-momentum sector dimension carried by the truncation index.\par
\noindent\textbf{3. Polarization Sector}\par
\[
\Phi_Q(e^{i\phi J_z})=\operatorname{diag}(e^{im\phi})_{m=-j}^{j}
\]
\noindent This closes the entry by fixing the two-state polarization sector inside the total carrier.\par

\clearpage
\noindent\textbf{[ID 0306] Quantum State Space Decomposition}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum State Space Decomposition is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The total Hilbert space used for quantum holographic navigation factors as /(H sub mathrm total = H sub mathrm spatial otimes H sub mathrm OAM otimes H sub mathrm polarization otimes H sub mathrm frequency /), where /(dim(H sub mathrm spatial ) = 153,600/), /(dim(H sub mathrm OAM ) = 2 m sub max + 1/), /(dim(H sub mathrm polarization ) = 2/), and /(dim(H sub mathrm frequency ) = infinity/). \textbf{Contextual meaning:} The entry reads Quantum State Space Decomposition as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the state-space factorization directly instead of wrapping the Hilbert-space equations inside prose. \textbf{Lemma support:} Hilbert Factorization; OAM Dimension; Polarization Sector.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The Trawin base unit u sub T is the fundamental geometric unit obtained by completing one metric-weighted loop around the TZP.

\tzpsection{Equation Grounding}
Equation anchors: Phi sub Q: SpinRep to Hilb; Phi sub Q(J sub z)=bigoplus sub m=-j to the power j H sub m; and Phi sub Q(e to the power iphi J sub z )=operatorname diag (e to the power imphi ) sub m=-j to the power j. Proof route: show that the stated tensor-product factorization consistently separates the spatial, orbital-angular-momentum, polarization, and frequency sectors. Formalization route: prove that the stated OAM and polarization dimensions are compatible with the decomposed total Hilbert space.

\tzpsection{Interpretive Role}
The entry now states the state-space factorization directly instead of wrapping the Hilbert-space equations inside prose.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Orbital Angular Momentum Truncation}: The finite dimensional restriction of infinite spatial rotation modes into a discrete Hilbert subspace.
\item \textbf{Spin-Tensor Factorization}: The explicit mathematical separation of polarization states from continuous spatial wavefunctions.
\item \textbf{Bounded Subspace Projection}: The operator logic distilling full quantum dynamics into a localized basis of accessible eigenmodes.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0306]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0306_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0306] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum State Space Decomposition}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the total Hilbert space used for quantum holographic navigation factors as /(H\textbackslash{}\_\textbackslash{}\textbackslash{} =
H\textbackslash{}\_\textbackslash{}\textbackslash{} otimes H\textbackslash{}\_\textbackslash{}\textbackslash{} otimes H\textbackslash{}\_\textbackslash{}\textbackslash{} otimes H\textbackslash{}\_\textbackslash{}\textbackslash{}/), where /(dim(H\textbackslash{}...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum State Space Decomposition is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0306_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
