\tzpanchor{0373}
\tzpentryheader{0373}{Nested Toroidal Loop Structure}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{db13ae0c-5cb1-5724-b64e-002e4a1a8ee1}}\\
\textbf{PiID} & \tzpcode{2046652138414} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{380}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1448.4418 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.3866 rad}\\
\textbf{TZPID} & \tzpcode{ID0373} & \textbf{Node Dependencies}\quad \tzpidref{0372}\\
\textbf{Registry} & \tzpcode{registry\_id\_0373} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Toroidal Carrier & Nested Inclusion\\
\textbf{Closure Support} & Core Intersection & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The opposing dipoles create a multiply connected topology of field lines: rather than cancelling, the fields loop outward at the edges, forming nested toroidal shells of flux. This produces non-trivial helicity and linking.

\tzpsection{Canonical Equation}
\[
T_n=S^1\times S^1
\]
\[
T_{n+1}\subset T_n
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $T_n$: source equation symbol.
    \item $S$: source equation symbol.
    \item $T_{n+1}$: source equation symbol.
    \item $n$: integer mode index.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0373 generated source Wolfram model *)
ClearAll[K0373, Cr0373, T, R, A, W, I, N];
eq0373$1 = HoldForm[TN == S^1*S^1];
eq0373$2 = HoldForm[TN1 Subset TN];
eq0373$3 = HoldForm[bigcapN0*TN == TZP];

K0373 = HoldForm[{eq0373$1, eq0373$2, eq0373$3}];

N = "normalized TRAWIN closure object for Nested Toroidal Loop Structure";
I = "Core Intersection integration/comparison layer";
W = "Nested Inclusion wave or operator carrier";
A = "Toroidal Carrier admissible action/amplitude condition";
R = "Nested Inclusion rotation/curl preservation layer";
T = "Toroidal Carrier local source condition";

Cr0373[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0373 = Cr0373[K0373];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Toroidal Carrier local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Nested Inclusion rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Toroidal Carrier admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Nested Inclusion wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Core Intersection integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Nested Toroidal Loop Structure.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0373] Nested Toroidal Loop Structure}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mathcal{E}:\rho\mapsto \mathcal{E}(\rho).
\end{equation}

\paragraph{CPTP Condition.}
\begin{equation}
\mathcal{E}\ \text{is completely positive and trace-preserving}.
\end{equation}

\paragraph{Primary Derivation.}
Let $\rho$ be a density operator. A quantum channel maps an input state into an output state:
\begin{equation}
\rho'=\mathcal{E}(\rho).
\end{equation}

Physical admissibility requires positivity not only on the original system, but also on any extended system:
\begin{equation}
(\mathcal{E}\otimes I_n)(X)\geq 0 .
\end{equation}

It must also preserve total probability:
\begin{equation}
\operatorname{Tr}(\mathcal{E}(\rho))=\operatorname{Tr}(\rho).
\end{equation}

Thus,
\begin{equation}
\boxed{
\mathcal{E}:\rho\mapsto\mathcal{E}(\rho)
\quad
\text{is CPTP}.
}
\end{equation}

\paragraph{Interpretation.}
A quantum channel is the admissible state-transition map for density operators, including TZP-curvature transport corrections.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Nested Toroidal Loop Structure by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Toroidal Carrier}\par
\[
T_n=S^1\times S^1
\]
\noindent This fixes each carrier loop as a toroidal factorized object.\par
\noindent\textbf{2. Nested Inclusion}\par
\[
T_{n+1}\subset T_n
\]
\noindent This orders the toroidal family into a genuine nested inclusion chain.\par
\noindent\textbf{3. Core Intersection}\par
\[
bigcap_{n\geq 0} T_n=\mathrm{TZP}
\]
\noindent This closes the entry by driving the nested intersection to the zero-point core.\par

\clearpage
\noindent\textbf{[ID 0373] Nested Toroidal Loop Structure}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Nested Toroidal Loop Structure is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The opposing dipoles create a multiply connected topology of field lines: rather than cancelling, the fields loop outward at the edges, forming nested toroidal shells of flux. This produces non-trivial helicity and linking. \textbf{Contextual meaning:} The entry reads Nested Toroidal Loop Structure as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the toroidal nesting as a clean inclusion tower rather than leaving the carrier geometry implicit. \textbf{Lemma support:} Toroidal Carrier; Nested Inclusion; Core Intersection.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
A quantum channel is the admissible state-transition map for density operators, including TZP-curvature transport corrections.

\tzpsection{Equation Grounding}
Equation anchors: T sub n=S to the power 1times S to the power 1; T sub n+1 subset T sub n; and bigcap sub ngeq 0 T sub n= TZP. Proof route: show that the nested toroidal family contracts toward the stated zero-point core while preserving the toroidal carrier at each level. Formalization route: prove that the nested inclusion chain has the stated zero-point intersection.

\tzpsection{Interpretive Role}
The entry now states the toroidal nesting as a clean inclusion tower rather than leaving the carrier geometry implicit.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Concentric Magnetic Flux Surfaces}: The geometric arrangement of smaller, tighter donut-shaped fields resting perfectly inside larger ones, like Russian dolls.
\item \textbf{Infinite Dimensional Intersection}: The mathematical limit showing that as the toroids get infinitely small, they converge exactly onto the central zero-point singularity.
\item \textbf{Sequential Shell Inclusion}: The formal set-theory mapping proving that every inner magnetic layer is completely contained by the volume of the layer outside it.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0373]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0373_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0373] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Nested Toroidal Loop Structure}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the opposing dipoles create a multiply connected topology of field lines: rather than
cancelling, the fields loop outward at the edges, forming nes...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Nested Toroidal Loop Structure is valid as a formal dynamical law when the Hamiltonian
or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0373_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
