\tzpanchor{0645}
\tzpentryheader{0645}{ALPHA-PARTICLE HELICITY OPERATOR (hatH\_alpha)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{77a53634-bd10-57f2-b643-4792c53a99f7}}\\
\textbf{PiID} & \tzpcode{1787214684409} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{652}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2477.4957 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.0822 rad}\\
\textbf{TZPID} & \tzpcode{ID0645} & \textbf{Node Dependencies}\quad \tzpidref{0644}\\
\textbf{Registry} & \tzpcode{registry\_id\_0645} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records alpha-particle helicity operator (hath\_alpha) through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
g_{\mu} = \frac{\mu} {MR^2\Omega}.
\]
\[
\mu = kMR^2\Omega ,
\]
\[
MR^2\Omega.
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $g_{\mu}$: source equation symbol.
    \item $\mu$: source equation symbol.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $M$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $O$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0645 generated source Wolfram model *)
ClearAll[K0645, Cr0645, T, R, A, W, I, N];
eq0645$1 = HoldForm[gMu == mu/(MR^2*Omega)];
eq0645$2 = HoldForm[mu == kMR^2*Omega];
eq0645$3 = HoldForm[MR^2*Omega];

K0645 = HoldForm[{eq0645$1, eq0645$2, eq0645$3}];

N = "normalized TRAWIN closure object for ALPHA-PARTICLE HELICITY OPERATOR (hatH\_alpha)";
I = "Normalized Output integration/comparison layer";
W = "Composable Action wave or operator carrier";
A = "Carrier Map admissible action/amplitude condition";
R = "Composable Action rotation/curl preservation layer";
T = "Carrier Map local source condition";

Cr0645[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0645 = Cr0645[K0645];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Carrier Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Composable Action rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Carrier Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Composable Action wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Output integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for ALPHA-PARTICLE HELICITY OPERATOR (hatH\textbackslash{}\_alpha).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0645] ALPHA-PARTICLE HELICITY OPERATOR (hatH\_alpha)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
g_{\mu}
=
\frac{\mu}
{MR^2\Omega}.
\end{equation}

\paragraph{Primary Derivation.}
Starting from the scaling law:

\begin{equation}
\mu
=
kMR^2\Omega ,
\end{equation}

divide both sides by the natural rotational magnetic scale:

\begin{equation}
MR^2\Omega .
\end{equation}

This gives:

\begin{equation}
\frac{\mu}{MR^2\Omega}=k .
\end{equation}

Define the dimensionless gyromagnetic coupling constant as:

\begin{equation}
\boxed{
g_{\mu}
=
\frac{\mu}
{MR^2\Omega}.
}
\end{equation}

\paragraph{Interpretation.}
$g_{\mu}$ removes ordinary scale factors from the magnetic moment and isolates the dimensionless coupling strength of the rotating system.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors ALPHA-PARTICLE HELICITY OPERATOR (hatH\textbackslash{}\_alpha) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Carrier Map}\par
\[
g_{\mu} = \frac{\mu} {MR^2\Omega}.
\]
\noindent This names the entry as an actual map between carrier domains rather than a loose metaphor.\par
\noindent\textbf{2. Composable Action}\par
\[
\mu = kMR^2\Omega ,
\]
\noindent This inserts the map into the ordered TRAWIN chain and makes composition explicit.\par
\noindent\textbf{3. Normalized Output}\par
\[
MR^2\Omega.
\]
\noindent This closes the entry by requiring that the output land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0645] ALPHA-PARTICLE HELICITY OPERATOR (hatH\_alpha)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
ALPHA-PARTICLE HELICITY OPERATOR (hatH sub alpha) is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} hat H alpha = left[ frac (mathbf P -qmathbf A ) to the power 2 2m alpha + V sub Coulomb right] otimes exp(itheta sub twist * sigma * mathbf L ). \textbf{Contextual meaning:} The entry reads ALPHA-PARTICLE HELICITY OPERATOR (hatH sub alpha) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
g sub removes ordinary scale factors from the magnetic moment and isolates the dimensionless coupling strength of the rotating system. \% SEPTENARY DERIVATION LAYER -- ID 0646 TO ID 0650.

\tzpsection{Equation Grounding}
Equation anchors: r to 0; c(r) to 0; and com/watch?v=uE-8uz09YNI\&utm sub source =chatgpt. Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Heavy-Ion Torsional Coupling}: The complex equation determining how massive, highly charged helium nuclei twist the surrounding electromagnetic field lines as they pass.
\item \textbf{Radiation-Induced Magnetic Shearing}: The mapping of the sudden, violent rotational wake left behind in the metric space following an alpha decay event.
\item \textbf{Positive-Charge Spin Augmentation}: The mathematical shift adding the heavy angular momentum of a nuclear fragment directly into the total tally of the system's knotted energy.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0645]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0645_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0645] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont ALPHA-PARTICLE HELICITY OPERATOR (hatH\_alpha)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records alpha-particle helicity operator (hath\textbackslash{}\_alpha) through the Septenary
derivation layer, using the displayed relations as operation...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ALPHA-PARTICLE HELICITY OPERATOR (\textbackslash{}hat\{H\_\textbackslash{}alpha) is valid as a synchronization
criterion under the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0645_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
