\tzpanchor{0505}
\tzpentryheader{0505}{LOGIT TRANSFORMATIONS FOR BLOB-BIT SCALING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{93730383-812a-5d17-9b4c-c1589f9d3ff0}}\\
\textbf{PiID} & \tzpcode{7336244065664} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{512}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1941.6110 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.1992 rad}\\
\textbf{TZPID} & \tzpcode{ID0505} & \textbf{Node Dependencies}\quad \tzpidref{0504}\\
\textbf{Registry} & \tzpcode{registry\_id\_0505} & \textbf{Scale}\quad diagnostic\\
\textbf{LOC Classification} & QA273 dimensionless analysis & QC statistical diagnostics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: nlin.PS, physics.data-an\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
L(p) = lnleft(frac\{p\}\{1-p\}right) otimes n\_i in S\textasciicircum{}2

\tzpsection{Canonical Equation}
\[
Semigroup(T_t) = \exp(t \mathcal{L}_{\text{generator}}) \otimes \ItoIsometry
\]
\[
Lk = Wr + Tw = \text{const} \implies \HelicityInvariant
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $T_t$: source equation symbol.
    \item $\mathcal{L}$: source equation symbol.
    \item $n_i$: source equation symbol.
    \item $S^2$: two-sphere target domain.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0505 generated source Wolfram model *)
ClearAll[K0505, Cr0505, T, R, A, W, I, N];
eq0505$1 = HoldForm[Semigroup[TT] == exp[t*L]*TensorProductItoIsometry];
eq0505$2 = HoldForm[Lk == Wr + Tw == impliesHelicityInvariant];
eq0505$3 = HoldForm[Element[L[p] == ln[p/(1 - p)]*TensorProduct*nI, S^2]];

K0505 = HoldForm[{eq0505$1, eq0505$2, eq0505$3}];

N = "normalized TRAWIN closure object for LOGIT TRANSFORMATIONS FOR BLOB-BIT SCALING";
I = "Normalized Regime integration/comparison layer";
W = "Scaling Relation wave or operator carrier";
A = "Diagnostic Definition admissible action/amplitude condition";
R = "Scaling Relation rotation/curl preservation layer";
T = "Diagnostic Definition local source condition";

Cr0505[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0505 = Cr0505[K0505];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Diagnostic Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Scaling Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Diagnostic Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Scaling Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Regime integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for LOGIT TRANSFORMATIONS FOR BLOB-BIT SCALING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0505] LOGIT TRANSFORMATIONS FOR BLOB-BIT SCALING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
For any diffeomorphism $\phi:M\to M$ preserving the symmetry group of $M$,

\begin{equation}
\phi(p)=p .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi:M\to M$ be a diffeomorphism preserving the symmetry structure of the manifold. Since $p$ is defined as the unique point where the metric degeneracy occurs,

\begin{equation}
\det(g)\big|_p=0 .
\end{equation}

If $\phi$ preserves the Trawinistic structure, then it must preserve the degeneracy locus:

\begin{equation}
\det(g)\big|_{\phi(p)}=0 .
\end{equation}

Because $p$ is unique, the only point satisfying this condition is $p$ itself. Therefore:

\begin{equation}
\phi(p)=p .
\end{equation}

\paragraph{Interpretation.}
The TZP is invariant under all structure-preserving transformations. It is therefore a fixed point of the system.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors LOGIT TRANSFORMATIONS FOR BLOB-BIT SCALING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Diagnostic Definition}\par
\[
Semigroup(T_t) = \exp(t \mathcal{L}_{\text{generator}}) \otimes \ItoIsometry
\]
\noindent This defines the scalar diagnostic or conversion quantity named by the title.\par
\noindent\textbf{2. Scaling Relation}\par
\[
Lk = Wr + Tw = \text{const} \implies \HelicityInvariant
\]
\noindent This elevates the quantity into a comparative scaling or correlation law.\par
\noindent\textbf{3. Normalized Regime}\par
\[
L(p) = \ln\left(\frac{p}{1-p}\right) \otimes n_i \in S^2
\]
\noindent This closes the entry by normalizing the diagnostic against a stated reference regime.\par

\clearpage
\noindent\textbf{[ID 0505] LOGIT TRANSFORMATIONS FOR BLOB-BIT SCALING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
LOGIT TRANSFORMATIONS FOR BLOB-BIT SCALING is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} L(p) = lnleft(frac p 1-p right) otimes n sub i in S to the power 2. \textbf{Contextual meaning:} The entry reads LOGIT TRANSFORMATIONS FOR BLOB-BIT SCALING as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons. \textbf{Lemma support:} Diagnostic Definition; Scaling Relation; Normalized Regime.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP is invariant under all structure-preserving transformations. It is therefore a fixed point of the system. \% SENARY DERIVATION LAYER -- ID 0506 TO ID 0510.

\tzpsection{Equation Grounding}
Equation anchors: Semigroup(T sub t) = exp(t L sub generator ) otimes ItoIsometry; Lk = Wr + Tw = const implies HelicityInvariant; and L(p) = ln(ratio p 1-p ) otimes n sub i in S to the power 2. Proof route: show that the named quantity is dimensionless or consistently scaled in the regime stated by the entry. Formalization route: prove that the normalized diagnostic remains invariant under the intended rescaling.

\tzpsection{Interpretive Role}
The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Continuous-to-Discrete Saturation}: The mathematical smoothing function used to cleanly map a messy, infinite range of analogue values directly onto a strict binary 1 or 0.
\item \textbf{Sigmoidal Probability Squashing}: The statistical S-curve that compresses wild, runaway quantum amplitudes back down into manageable, understandable percentage chances.
\item \textbf{Quantum-Classical Boundary Thresholding}: The exact, defined tipping point where a fuzzy, uncertain quantum state is forced to finally choose a firm, classical reality.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0505]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0505_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0505] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont LOGIT TRANSFORMATIONS FOR BLOB-BIT SCALING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} l(p) = lnleft(frac\textbackslash{}\textbackslash{}1-p) otimes n\textbackslash{}\_i in S\textasciicircum{}2

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``LOGIT TRANSFORMATIONS FOR BLOB-BIT SCALING is valid when the stated operator maps
admissible inputs into the declared target class.''\\
\textbf{Proof:} The source statement is read as an operator or transformation. The proof obligation is
type preservation: admissible inputs must land in the target object without breaking the
stated constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- operator-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0505_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
