\section*{ID9199: Definition of Ψ(r,t)}
\paragraph{Metadata.}
PiID: 8692221032748 | RTEID: RTE:P35721.7599:T2.3098 | UUID: 127e7107-ca68-583c-b22b-7878f4ac68ff

\paragraph{Canonical Statement.}
icles share identical properties; sets initial conditions for perturbations; leads to infinite propagation speed prior to decoherence. Falsifiability / Test Handle: Empirical evidence of fundamental finite speed or time at the earliest universe contradicting this hyperspherical model would falsify this definition. 2.0.29 ID 178: Local Disharmony and Bessel Mode Emergence Type: Definition Formal Statement: A local deviation from global phase coherence generates an interference wave described by \$Ψ(r,t)=Ψ0+εj0(kr)cos(ωt)\textbackslash{}Psi(r,t)\$ = \textbackslash{}Psi\_0 + \textbackslash{}varepsilon, j\_0(k r) \textbackslash{}cos(\textbackslash{}omega \$t)Ψ(r,t)=Ψ0+εj0(kr)cos(ωt),\$ where j0j\_0j0 is the spherical Bessel function of order zero; the first node at \$kr≈2.405k\$ r \textbackslash{}approx \$2.405kr≈2.405\$ defines the characteristic radius of a TZP emergence. Interpretive Meaning: When the vacuum field slips out of phase locally, it produces a standing wave pocket with Bessel profile, creating a fold that

\paragraph{Canonical Equation.}
\[
Ψ(r,t)=Ψ0+εj0(kr)cos(ωt)\Psi(r,t)
\]

\paragraph{Dictionary.}
Definition of Ψ(r,t) — Ψ(r,t)=Ψ0+εj0(kr)cos(ωt)Ψ(r,t)

\paragraph{Encyclopedia.}
Definition of Ψ(r,t) is an algebraic definition, written Ψ(r,t)=Ψ0+εj0(kr)cos(ωt)Ψ(r,t). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from Ψ, j, k, r, c, o, defining Ψ(r,t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
