\tzpanchor{0396}
\tzpentryheader{0396}{Beat Frequency Resonance and Information Density}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{75a5f795-9a28-5970-b217-93af8ac106c8}}\\
\textbf{PiID} & \tzpcode{6094330572703} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{403}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1537.7559 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.5337 rad}\\
\textbf{TZPID} & \tzpcode{ID0396} & \textbf{Node Dependencies}\quad \tzpidref{0395}\\
\textbf{Registry} & \tzpcode{registry\_id\_0396} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Mode Quantization & Dispersion Law\\
\textbf{Closure Support} & Boundary Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The tripartite channel architecture predicts that resonant beat frequencies occur at fres=f0?,fres=f0alpha, where f0f0 is a base frequency and ?alpha is the fine-structure constant. Each measurement across the channels yields an information density of log2(153,600)approx17.23log2(153,600)approx17.23 bits.

\tzpsection{Canonical Equation}
\[
\omega_{\mathrm{beat}}=\lvert\omega_{1}-\omega_{2}\rvert
\]
\[
\rho_{I}=\log_{2}(153600)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\omega_{\mathrm{beat}}$: angular frequency term in the source equation.
    \item $\omega_{1}$: angular frequency term in the source equation.
    \item $\omega_{2}$: angular frequency term in the source equation.
    \item $\rho_{I}$: source equation symbol.
    \item $I$: source equation symbol.
    \item $n$: integer mode index.
    \item $\pi$: source equation symbol.
    \item $v_{\mathrm{A}}$: Alfven velocity or carrier speed.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0396 generated source Wolfram model *)
ClearAll[K0396, Cr0396, T, R, A, W, I, N];
eq0396$1 = HoldForm[omegaBeat == Abs[omega1 - omega2]];
eq0396$2 = HoldForm[rhoI == log2[153600]];
eq0396$3 = HoldForm[omegaBeat == nPi*(vA/L)];

K0396 = HoldForm[{eq0396$1, eq0396$2, eq0396$3}];

N = "normalized TRAWIN closure object for Beat Frequency Resonance and Information Density";
I = "Boundary Condition integration/comparison layer";
W = "Dispersion Law wave or operator carrier";
A = "Mode Quantization admissible action/amplitude condition";
R = "Dispersion Law rotation/curl preservation layer";
T = "Mode Quantization local source condition";

Cr0396[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0396 = Cr0396[K0396];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Mode Quantization local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Dispersion Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Mode Quantization admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Dispersion Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Boundary Condition integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Beat Frequency Resonance and Information Density.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0396] Beat Frequency Resonance and Information Density}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Continuity Constraint.}
\begin{equation}
\partial_r(rv_r)+\partial_z(zv_z)=0.
\end{equation}

\paragraph{Resonance Operator.}
\begin{equation}
\mathcal{R}_{\mathrm{EHD}}[\mathbf{v}]
=
-\frac{\nabla p}{\rho}
+
\frac{q}{m}
(\mathbf{E}+\mathbf{v}\times\mathbf{B}).
\end{equation}

\paragraph{Mode Selection.}
\begin{equation}
\mathcal{R}_{\mathrm{EHD}}[\mathbf{v}_k]
=
\lambda_k\mathbf{v}_k.
\end{equation}

\paragraph{Primary Derivation.}
The admissible axisymmetric flow space is constrained by:
\begin{equation}
\partial_r(rv_r)+\partial_z(zv_z)=0.
\end{equation}

Pressure and electromagnetic forcing define the total acceleration operator:
\begin{equation}
\mathcal{R}_{\mathrm{EHD}}[\mathbf{v}]
=
-\frac{\nabla p}{\rho}
+
\frac{q}{m}
(\mathbf{E}+\mathbf{v}\times\mathbf{B}).
\end{equation}

Resonant modes are those reproduced by the operator up to scale:
\begin{equation}
\boxed{
\mathcal{R}_{\mathrm{EHD}}[\mathbf{v}_k]
=
\lambda_k\mathbf{v}_k.
}
\end{equation}

\paragraph{Interpretation.}
The EHD resonance operator identifies flow modes amplified by pressure and electromagnetic forcing.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Beat Frequency Resonance and Information Density by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Mode Quantization}\par
\[
\omega_{\mathrm{beat}}=\lvert\omega_{1}-\omega_{2}\rvert
\]
\noindent This fixes the quantized carrier mode indexed by the bounded geometry.\par
\noindent\textbf{2. Dispersion Law}\par
\[
\rho_{I}=\log_{2}(153600)
\]
\noindent This turns the mode index into an actual propagation or resonance law.\par
\noindent\textbf{3. Boundary Condition}\par
\[
\omega_{\mathrm{beat}}=n\pi v_{\mathrm{A}}/L
\]
\noindent This closes the progression by enforcing the boundary or nodal condition that makes the pattern admissible.\par

\clearpage
\noindent\textbf{[ID 0396] Beat Frequency Resonance and Information Density}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Beat Frequency Resonance and Information Density is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The tripartite channel architecture predicts that resonant beat frequencies occur at fres=f0?,fres=f0alpha, where f0f0 is a base frequency and ?alpha is the fine-structure constant. Each measurement across the channels yields an information density of log2(153,600)approx17.23log2(153,600)approx17.23 bits. \textbf{Contextual meaning:} The entry reads Beat Frequency Resonance and Information Density as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred. \textbf{Lemma support:} Mode Quantization; Dispersion Law; Boundary Condition.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The EHD resonance operator identifies flow modes amplified by pressure and electromagnetic forcing.

\tzpsection{Equation Grounding}
Equation anchors: approx; Each measurement across the channels yields an information density of log2(153,600)approximately17; and log2(153,600)approximately17. Proof route: show that bounded carrier geometry forces the stated mode quantization and resonance law. Formalization route: prove that the stated boundary condition yields the stated discrete spectrum.

\tzpsection{Interpretive Role}
The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Wave-Interference Envelope Pulsation}: The slow, rhythmic rising and falling of energy caused by two slightly out-of-tune waves interacting with each other.
\item \textbf{Logarithmic Bit-Capacity Scaling}: The calculation showing that the total informational storage of the system grows based on the base-2 logarithm of its available states.
\item \textbf{Phase-Velocity Beat Synchronization}: The exact tuning required to make the slow interference pulse travel at the same speed as the underlying spatial waves.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0396]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0396_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0396] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Beat Frequency Resonance and Information Density}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the tripartite channel architecture predicts that resonant beat frequencies occur at
fres=f0?,fres=f0alpha, where f0f0 is a base frequency and ?alp...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Beat Frequency Resonance and Information Density is valid as a spectral relation when
frequency, phase, and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0396_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
