\tzpanchor{0142}
\tzpentryheader{0142}{Heterogeneous Coupling Limitation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{8a908860-242b-51fb-b463-5b93081e3258}}\\
\textbf{PiID} & \tzpcode{5940812848111} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{149}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{551.4175 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.9086 rad}\\
\textbf{TZPID} & \tzpcode{ID0142} & \textbf{Node Dependencies}\quad \tzpidref{0141}\\
\textbf{Registry} & \tzpcode{registry\_id\_0142} & \textbf{Scale}\quad non-monotone coherence in weighted oscillator systems\\
\textbf{LOC Classification} & QA371 nonlinear oscillators & QA299 approximation limits\\
\textbf{arXiv Classification} & Primary: nlin.AO \quad Cross-list: cond-mat.stat-mech, astro-ph.EP & \\
\textbf{Primary Support} & Response Curve & Sign-Change Condition\\
\textbf{Closure Support} & Subcritical Maximum & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In systems with wide variance in natural frequencies and coupling strengths, the Kuramoto order parameter exhibits non-monotonic dependence on the coupling constant and fails to reach high coherence levels.

\tzpsection{Canonical Equation}
\[
r=r(K_0)
\]
\[
\frac{dr}{dK_0}\ \text{changes sign}
\]
\[
r_{\max}<1
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $K_0$: source equation symbol.
    \item $r_{\max}$: source equation symbol.
    \item $\mathcal{K}_{0142}$: canonical registry object for entry ID 0142.
    \item $\max$: source equation symbol.
    \item $K$: source equation symbol.
    \item $r(K_0)$: global radius, boundary radius, or topological scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0142 generated source Wolfram model *)
ClearAll[K0142, Cr0142, T, R, A, W, I, N];
eq0142$1 = HoldForm[r == r[K0]];
eq0142$2 = HoldForm[dr/dK0];
eq0142$3 = HoldForm[rMax < 1];

K0142 = HoldForm[{eq0142$1, eq0142$2, eq0142$3}];

N = "normalized TRAWIN closure object for Heterogeneous Coupling Limitation";
I = "Subcritical Maximum integration/comparison layer";
W = "Sign-Change Condition wave or operator carrier";
A = "Response Curve admissible action/amplitude condition";
R = "Sign-Change Condition rotation/curl preservation layer";
T = "Response Curve local source condition";

Cr0142[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0142 = Cr0142[K0142];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Response Curve local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Sign-Change Condition rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Response Curve admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Sign-Change Condition wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Subcritical Maximum integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Heterogeneous Coupling Limitation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0142] Heterogeneous Coupling Limitation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
r=r(K_0)
\]
\[
\frac{dr}{dK_0}\ \text{changes sign}
\]
\[
r_{\max}<1
\]

\paragraph{Primary Derivation.}
The relation \( r=r(K_0) \) arises from taking an appropriate limit. Evaluating the expression under the stated limiting procedure and using standard limit rules yields the given equality.
\paragraph{Equation Type.}
This statement is classified as a limit relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. Interpreted through TRAWIN, the equation functions as the limit carrier for the entry’s information content. Under CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Heterogeneous Coupling Limitation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Response Curve}\par
\[
r=r(K_0)
\]
\noindent This treats coherence as a function to be studied across parameter space rather than at one fixed value.\par
\noindent\textbf{2. Sign-Change Condition}\par
\[
\frac{dr}{dK_0}\ \text{changes sign}
\]
\noindent This states the non-monotonicity that invalidates simple one-direction intuition.\par
\noindent\textbf{3. Subcritical Maximum}\par
\[
r_{\max}<1
\]
\noindent This closes the progression by saying the heterogeneous system may never reach full global locking.\par

\clearpage
\noindent\textbf{[ID 0142] Heterogeneous Coupling Limitation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Heterogeneous Coupling Limitation is a canonical-registry. In systems with wide variance in natural frequencies and coupling strengths, the Kuramoto order parameter exhibits non monotonic dependence on the coupling constant and fails to reach high coherence levels.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} In systems with wide variance in natural frequencies and coupling strengths, the Kuramoto order parameter exhibits non monotonic dependence on the coupling constant and fails to reach high coherence levels.
\textbf{Contextual meaning:} Increasing coupling strength alone does not guarantee synchronization when frequencies differ widely. Competing tendencies persist and coherence remains low.
\textbf{Derivable consequences:} Emphasis on heterogeneity reduction; need
\textbf{Lemma support:} In systems with wide variance in natural frequencies and coupling strengths, the Kuramoto order parameter exhibits non monotonic dependence on the coupling constant and fails to reach high coherence levels.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Compare synchronization patterns in networks with heterogeneous coupling distributions; verify that dominant pairs dictate cluster formation. ID 142: Heterogeneous Coupling Limitation

\tzpsection{Equation Grounding}
In systems with wide variance in natural frequencies and coupling strengths, the Kuramoto order parameter exhibits non monotonic dependence on the coupling constant and fails to reach high coherence levels.

\tzpsection{Interpretive Role}
Increasing coupling strength alone does not guarantee synchronization when frequencies differ widely. Competing tendencies persist and coherence remains low.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Response Curve}: The treatment of coherence as a function to be studied across parameter space rather than at one fixed value.
\item \textbf{Sign-Change Condition}: The non-monotonicity that invalidates simple one-direction intuition.
\item \textbf{Subcritical Maximum}: The statement that the heterogeneous system may never reach full global locking.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0142]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0142_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0142] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Heterogeneous Coupling Limitation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in systems with wide variance in natural frequencies and coupling strengths, the
Kuramoto order parameter exhibits non-monotonic dependence on the...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Heterogeneous Coupling Limitation is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0142_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
