\section*{ID8563: Definition of ∑N N}
\paragraph{Metadata.}
PiID: 2775687900290 | RTEID: RTE:P33252.0306:T4.5236 | UUID: c814f243-b4bb-5c96-937c-4c9fa5f59c22

\paragraph{Canonical Statement.}
urce: „, [ID 1004] PLANETARY SPIN-ORBIT OSCILLATOR Canonical Statutory Formula: \$θ̇i \$ = \$ωi+ \$ \$k0 N \$ \$∑\$ \$Kij sin(θj \$ − \$θi)−Diθ̇i+ τtidal \$ Formal Technical Dissertation: Models planetary bodies as coupled phase oscillators. It augments the Kuramoto model with spin-orbit torques and tidal dissipation to predict resonance capture ratios (e.g., Mercury’s 3:2 lock). Source: , [ID 1005] BESSEL-WEIGHTED TIDAL TORQUE Canonical Statutory Formula: \$τtidal(ω,Ω) \$ = 1 \$I \$ \$∑N n=1 Jn(ne) \$ 2 \$sin(2(ω \$ − \$nΩ)) \$ Formal Technical Dissertation: Calculates the torque exerted on a spinning body in an eccentric orbit. The strength of the resonance terms is weighted by Bessel functions of the first kind \$Jn \$ dependent on orbital eccentricity \$e. \$ Source: , [ID 1006] PI-LADDER TORQUE MODEL Canonical Statutory Formula: \$τπ(∆θ) \$ = − \$sin(2∆θ) \$ + \$Noise(σ) \$ F

\paragraph{Canonical Equation.}
\[
∑N n=1 Jn(ne)
\]

\paragraph{Dictionary.}
Definition of ∑N N — ∑N n=1 Jn(ne)

\paragraph{Encyclopedia.}
Definition of ∑N N is an algebraic definition, written ∑N n=1 Jn(ne). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from J, n, defining ∑N n. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
