\tzpanchor{0461}
\tzpentryheader{0461}{Atemporal Channel Null-Surface Mapping}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{b4be69d4-52df-5247-93d1-381e23232e33}}\\
\textbf{PiID} & \tzpcode{2749567351885} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{468}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1774.6325 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.9240 rad}\\
\textbf{TZPID} & \tzpcode{ID0461} & \textbf{Node Dependencies}\quad \tzpidref{0460}\\
\textbf{Registry} & \tzpcode{registry\_id\_0461} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 461 defines the Atemporal Channel, where energy extraction occurs on null surfaces and temporal ordering collapses. This channel handles quantum processing independent of substrate density or temporal scaling. Information is encoded as geometric trajectories through 153,600 dimensional space. Null Surface Projection: Maps quantum states to regions where the Jacobian determinant of spacetime approaches zero. Infinite Processing: Effectively utilizes zero duration quantum events for high order computation.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
v_{phase} \approx \frac{c}{\chi} \approx 0.84c
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $v_{phase}$: source equation symbol.
    \item $c$: speed of light or relativistic conversion factor.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\chi$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0461 generated source Wolfram model *)
ClearAll[K0461, Cr0461, T, R, A, W, I, N];
eq0461$1 = HoldForm[$vPhase == c/chi == 0.84*c$];

K0461 = HoldForm[{eq0461$1}];

N = "normalized TRAWIN closure object for Atemporal Channel Null-Surface Mapping";
I = "Atemporal Channel Null-Surface Mapping integration/comparison layer";
W = "Atemporal Channel Null-Surface Mapping wave or operator carrier";
A = "Atemporal Channel Null-Surface Mapping admissible action/amplitude condition";
R = "Atemporal Channel Null-Surface Mapping rotation/curl preservation layer";
T = "Atemporal Channel Null-Surface Mapping local source condition";

Cr0461[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0461 = Cr0461[K0461];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Atemporal Channel Null-Surface Mapping local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Atemporal Channel Null-Surface Mapping rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Atemporal Channel Null-Surface Mapping admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Atemporal Channel Null-Surface Mapping wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Atemporal Channel Null-Surface Mapping integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Atemporal Channel Null-Surface Mapping.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0461] Atemporal Channel Null-Surface Mapping}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
S_A = -\mathrm{Tr}(\rho_A \log \rho_A).
\end{equation}

\paragraph{Primary Derivation.}
Let $\rho$ be the density matrix of a composite system partitioned into subsystems $A$ and $B$.

The reduced density matrix is:
\begin{equation}
\rho_A = \mathrm{Tr}_B(\rho).
\end{equation}

The entanglement entropy is defined as:
\begin{equation}
S_A = -\mathrm{Tr}(\rho_A \log \rho_A).
\end{equation}

\paragraph{Interpretation.}
Entropy measures quantum correlation between subsystems.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Atemporal Channel Null-Surface Mapping by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
v_{phase} \approx \frac{c}{\chi} \approx 0.84c
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0461] Atemporal Channel Null-Surface Mapping}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Atemporal Channel Null-Surface Mapping is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 461 defines the Atemporal Channel, where energy extraction occurs on null surfaces and temporal ordering collapses. This channel handles quantum processing independent of substrate density or temporal scaling. Information is encoded as geometric trajectories through 153,600 dimensional space. Null Surface Projection: Maps quantum states to regions where the Jacobian determinant of spacetime approaches zero. Infinite Processing: Effectively utilizes zero duration quantum events for high order computation.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
v_{phase} \approx \frac{c}{\chi} \approx 0.84c
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 461 defines the Atemporal Channel, where energy extraction occurs on null surfaces and temporal ordering collapses. This channel handles quantum processing independent of substrate density or temporal scaling. Information is encoded as geometric trajectories through 153,600 dimensional space. Null Surface Projection: Maps quantum states to regions where the Jacobian determinant of spacetime approaches zero. Infinite Processing: Effectively utilizes zero duration quantum events for high order computation.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Atemporal Channel Null-Surface Mapping by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Atemporal Channel Null-Surface Mapping; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0461]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0461].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0461] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Atemporal Channel Null-Surface Mapping}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} = oint\textbackslash{}\_ tial Omega\textbackslash{} psi\textbackslash{}\_\textbackslash{} otimes exp(i mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{})

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ATEMPORAL CHANNEL NULL-SURFACE MAPPING is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0461].
\par\endgroup
\vfill
\endgroup
\endgroup
