\tzpanchor{0229}
\tzpentryheader{0229}{Disharmonic Fold Operator}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{8a228d07-1705-570b-bb65-3bed7ea4d046}}\\
\textbf{PiID} & \tzpcode{3378678316527} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{236}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{889.2579 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.4652 rad}\\
\textbf{TZPID} & \tzpcode{ID0229} & \textbf{Node Dependencies}\quad \tzpidref{0228}\\
\textbf{Registry} & \tzpcode{registry\_id\_0229} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Unconstrained 4D Radial Mode & Effective Hypersurface Projection\\
\textbf{Closure Support} & Projected Fold and Nodal Scale & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A local disharmonic fold is observed on an effective two-dimensional projected hypersurface derived from an unconstrained four-dimensional radial field; the projection selects a cylindrical zeroth-order Bessel profile.

\tzpsection{Canonical Equation}
\[
\mathcal{L}_4 u_4=0,\qquad u_4(r)\propto\frac{J_1(k r)}{k r}
\]
\[
\mathsf{P}_{4\to2}:\mathcal{L}_4\rightsquigarrow\mathcal{L}_2,\qquad \delta\phi_{\mathrm{proj}}(r,t)=\varepsilon J_0(k r)\cos(\omega t)
\]
\[
J_0(k r_0)=0,\qquad k r_0=2.4048255577\ldots
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $u_4$: unconstrained four-dimensional radial carrier field.
    \item $\varepsilon$: small phase-deviation amplitude.
    \item $J_0(kr)$: cylindrical zeroth-order Bessel profile on the effective projected slice.
    \item $\omega$: angular frequency of the projected oscillation.
    \item $r_0$: first-node radius of the projected Bessel profile.
    \item $\mathcal{L}_4,\mathcal{L}_2$: four-dimensional and projected two-dimensional radial Helmholtz operators.
    \item $\mathsf{P}_{4\to2}$: declared hypersurface projection selecting the effective two-dimensional radial sector.
    \item $\delta\phi_{\mathrm{proj}}(r,t)$: projected local phase-deviation field.
    \item $J_1(k r)/(k r)$: regular unconstrained four-dimensional radial profile.
    \item $k$: radial wavenumber of the projected disturbance.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0229 generated source Wolfram model *)
ClearAll[K0229, Cr0229, T, R, A, W, I, N];
eq0229$1 = HoldForm[u4[r] == BesselJ[1, k*r]/(k*r)];
eq0229$2 = HoldForm[P4to2[L4] == L2];
eq0229$3 = HoldForm[deltaPhiProjected[r, t] == epsilon*BesselJ[0, k*r]*Cos[omega*t]];
eq0229$4 = HoldForm[k*r0 == BesselJZero[0, 1]];

K0229 = HoldForm[{eq0229$1, eq0229$2, eq0229$3, eq0229$4}];

N = "normalized TRAWIN closure object for Disharmonic Fold Operator";
I = "Projected Fold and Nodal Scale integration/comparison layer";
W = "Effective Hypersurface Projection wave or operator carrier";
A = "Unconstrained 4D Radial Mode admissible action/amplitude condition";
R = "Effective Hypersurface Projection rotation/curl preservation layer";
T = "Unconstrained 4D Radial Mode local source condition";

Cr0229[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0229 = Cr0229[K0229];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Unconstrained 4D Radial Mode local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Effective Hypersurface Projection rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Unconstrained 4D Radial Mode admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Effective Hypersurface Projection wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Projected Fold and Nodal Scale integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Disharmonic Fold Operator.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0229] Disharmonic Fold Operator}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Unconstrained Four-Dimensional Mode.}
For a radially symmetric field on a four-spatial-dimensional slice,
\[
\mathcal{L}_4u_4=\left(\partial_r^2+\frac{3}{r}\partial_r+k^2\right)u_4=0,\qquad u_4(r)\propto\frac{J_1(k r)}{k r}.
\]
Its first boundary node satisfies \(J_1(k r^{(4)}_0)=0\), hence \(k r^{(4)}_0\approx3.8317059702\).
\paragraph{Hypersurface Projection Rule.}
Introduce the model constraint \(\mathsf{P}_{4\to2}\) selecting the effective two-dimensional longitudinal sector:
\[
\mathsf{P}_{4\to2}:\mathcal{L}_4\rightsquigarrow\mathcal{L}_2=\partial_r^2+\frac{1}{r}\partial_r+k^2.
\]
The projected localized fold therefore obeys
\[
\delta\phi_{\mathrm{proj}}(r,t)=\varepsilon J_0(k r)\cos(\omega t),\qquad J_0(k r_0)=0,\quad k r_0\approx2.4048255577.
\]
\paragraph{Interpretation.}
The higher-dimensional event remains hyperspherical in origin; its printed nodal metric is the effective projected observation selected by the declared constraint. This completes the node convention as a model-conditional extension of the sourced entry.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The explicit projection \(\mathsf{P}_{4\to2}\) maps the four-dimensional radial carrier to an effective two-dimensional disturbance profile, for which \(J_0(k r_0)=0\) gives \(k r_0\approx2.4048255577\).
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Unconstrained 4D Radial Mode}\par
\[
\left(\partial_r^2+\frac{3}{r}\partial_r+k^2\right)u_4(r)=0
\]
\[
u_4(r)\propto\frac{J_1(k r)}{k r},\qquad k r^{(4)}_0\approx3.8317059702
\]
\noindent The isotropic four-spatial-dimensional carrier supplies the higher-dimensional radial origin of the event.\par
\noindent\textbf{2. Effective Hypersurface Projection}\par
\[
\mathsf{P}_{4\to2}:\left(\partial_r^2+\frac{3}{r}\partial_r+k^2\right)\rightsquigarrow\left(\partial_r^2+\frac{1}{r}\partial_r+k^2\right)
\]
\noindent The declared geometric constraint selects the effective two-dimensional radial sector used by the observed disturbance.\par
\noindent\textbf{3. Projected Fold and Nodal Scale}\par
\[
\delta\phi_{\mathrm{proj}}(r,t)=\varepsilon J_0(k r)\cos(\omega t)
\]
\[
J_0(k r_0)=0,\qquad k r_0\approx2.4048255577
\]
\noindent The projected mode gives the node value recorded by the resonance metric without misidentifying it as spherical Bessel j-zero.\par

\clearpage
\noindent\textbf{[ID 0229] Disharmonic Fold Operator}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small

\tzpsection{Definition}

The disharmonic fold operator is a localized departure from coherent background behavior observed in an effective two-dimensional hypersurface sector. Its projected radial component is modeled by the ordinary zeroth-order Bessel profile \(J_0(k r)\), while its higher-dimensional carrier begins as an unconstrained four-dimensional radial wave.

\tzpsection{Contextual Meaning}

The entry keeps the disturbance hyperspherical in origin without forcing its observable node metric to be a four-dimensional boundary zero. An explicit projection constraint \(\mathsf{P}_{4\to2}\) selects the two-dimensional longitudinal observation sector, where concentric radial rings naturally carry the required \(J_0\) node.

\tzpsection{Formal Statement}

\[
u_4(r)\propto\frac{J_1(k r)}{k r},\qquad
\mathsf{P}_{4\to2}:\mathcal{L}_4\rightsquigarrow\mathcal{L}_2,\qquad
\delta\phi_{\mathrm{proj}}(r,t)=\varepsilon J_0(k r)\cos(\omega t)
\]
\[
J_0(k r_0)=0,\qquad k r_0\approx2.4048255577
\]

\tzpsection{Derivable Consequences}

The unconstrained four-dimensional mode has first boundary zero at \(k r\approx3.8317059702\), whereas the projected two-dimensional mode has first zero at \(k r\approx2.4048255577\). The projection rule therefore converts a higher-dimensional origin into the nodal scale recorded for the localized fold.

\tzpsection{Lemma Support}

The retrieved source supplies the local disturbance and records its node near 2.405. The hypersurface-projection derivation is an author-specified model extension: it resolves the previously inconsistent spherical notation by making the displayed node explicitly cylindrical \(J_0\) in the projected sector.

\tzpsection{Technical Interpretation}

This is a controlled dimensional-reduction model. The operator \(\mathsf{P}_{4\to2}\) must be understood as a declared effective constraint or observation rule, not merely as evaluation of an isotropic four-dimensional solution on a plane. Under that rule, the radial equations and node values are consistent.

\tzpsection{Equation Grounding}

\(u_4\) is the unconstrained four-dimensional radial carrier; \(\mathsf{P}_{4\to2}\) is the effective projection constraint; \(\delta\phi_{\mathrm{proj}}\) is the observed local phase deviation; \(J_0\) is the projected cylindrical Bessel profile; and \(r_0\) is its first-node radius.

\tzpsection{Interpretive Role}

This entry links the higher-dimensional metric arc to a measurable projected resonance scale: the field event may originate in the hyperspherical sector while the recorded nodal pattern is evaluated in its effective planar observation layer.

\tzpsection{TZP Thesaurus}

\noindent \textbf{Disharmonic Fold}: A local departure from harmonic coherence represented as a structured disturbance. \enspace\textbullet\enspace \textbf{Hypersurface Projection}: The effective dimensional-reduction constraint selecting the observed radial sector. \enspace\textbullet\enspace \textbf{First Node}: The first radius at which the projected ordinary Bessel profile reaches zero.\par

\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0229].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0229] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Disharmonic Fold Operator}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} Under the declared projection constraint,
\[
\mathsf{P}_{4\to2}:\mathcal{L}_4\rightsquigarrow\mathcal{L}_2,\qquad \delta\phi_{\mathrm{proj}}(r,t)=\varepsilon J_0(k r)\cos(\omega t).
\]
\textbf{Logic Validation:}\\
\textbf{Proposition:} The effective projected profile realizes the recorded first-node scale.\\
\textbf{Proof:} The regular 4D radial Helmholtz solution is proportional to \(J_1(k r)/(k r)\). By the stated model constraint, the observed sector obeys the 2D radial operator and has regular solution \(J_0(k r)\). Hence \(J_0(k r_0)=0\) gives \(k r_0=2.4048255577\ldots\).\\
\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE UNDER PROJECTION CONSTRAINT}\\
\textbf{Formal Status:} THEORETICAL -- author-approved geometric extension in the production source truth\\
\textbf{Physical Status:} THEORETICAL -- projected realization remains to be tested
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0229].
\par\endgroup
\vfill
\endgroup
\endgroup
