\section*{ID8930: IMPEDANCE MATCHING KERNEL Canonical Statutory Formula: Z\_match}
\paragraph{Metadata.}
PiID: 6923488962766 | RTEID: RTE:P34677.1732:T0.5886 | UUID: cf38bcab-7d7d-5d7c-ba2d-fda3d267a3a8

\paragraph{Canonical Statement.}
[ID 925] IMPEDANCE MATCHING KERNEL Canonical Statutory Formula: \$Z\_\{match\} = \textbackslash{}text\{LinearSolve\}[Z\_\{hemisphere\} \textbackslash{}otimes I, Flatten[Z\_\{sphere\}]]\$ Formal Technical Dissertation: The transformation matrix that matches the impedance of the 78,000-point hemisphere to the 153,600-point inner sphere. It ensures lossless energy transfer by solving for the optimal coupling coefficients [22]. Source: [22]

\paragraph{Canonical Equation.}
\[
Z_{match} = \text{LinearSolve}[Z_{hemisphere} \otimes I, Flatten[Z_{sphere}]]
\]

\paragraph{Dictionary.}
IMPEDANCE MATCHING KERNEL Canonical Statutory Formula: \$Z\_match = LinearSolve[Z\_hemisphere I, Flatten[Z\_sphere]]\$ Formal Technical Dissertation: The transformation matrix that matches the impedance of the 78,000-point hemisphere to the 153,600-point inner sphere.

\paragraph{Encyclopedia.}
IMPEDANCE MATCHING KERNEL Canonical Statutory Formula: Z\_match is an algebraic definition, written Z\_match = LinearSolve[Z\_hemisphere ⊗ I, Flatten[Z\_sphere]]. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from Z\_hemisphere, I, F, l, a, n, defining Z\_match. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
