\section*{ID9473: Definition of)}
\paragraph{Metadata.}
PiID: 0504922124247 | RTEID: RTE:P36785.7627:T4.0630 | UUID: d716f96a-9b46-5c96-9d8d-41e4f5b354de

\paragraph{Canonical Statement.}
belle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0228], [ID 0200] Node registry\_id\_0229 Support Titles Mode Quantization; Dispersion Law; Boundary Condition Test Handle If the resonance pattern cannot be organized into bounded modes with the stated boundary condition, the entry fails. Canonical Equation Links \$Ψ(𝑟\$ ,𝑡 \$)=Ψ0+𝜖\$ 𝑗0 (𝑘𝑟 ) cos(𝜔𝑡 ) 𝛿𝜙 (𝑟 ,𝑡 )=𝜖 𝑗0 (𝑘𝑟 ) cos(𝜔𝑡 ) \$lim𝑟→∞\$ 𝛿𝜙 (𝑟 ,𝑡 )=0 [ID 0230] Bessel Interference Pattern of Emergent Matter TZPID ID0230 UUID ba1d3394-743f-53eb-b215-c0338da48c1f Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Stat

\paragraph{Canonical Equation.}
\[
)=Ψ0+𝜖
\]

\paragraph{Dictionary.}
Definition of) — )=Ψ0+𝜖

\paragraph{Encyclopedia.}
Definition of) is an algebraic definition, written )=Ψ0+𝜖. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
