\tzpanchor{0133}
\tzpentryheader{0133}{Topological Protection via Phase Winding}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{2ff47d2a-4476-5d20-ab5d-97bb9804a8ef}}\\
\textbf{PiID} & \tzpcode{8223172535940} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{140}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{516.4685 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.8510 rad}\\
\textbf{TZPID} & \tzpcode{ID0133} & \textbf{Node Dependencies}\quad \tzpidref{0132}\\
\textbf{Registry} & \tzpcode{registry\_id\_0133} & \textbf{Scale}\quad windowed phase winding and domain-wall protection\\
\textbf{LOC Classification} & QA612 algebraic topology & QA371 phase systems\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: cond-mat.mes-hall, nlin.PS & \\
\textbf{Primary Support} & Winding Number Formula & Nontrivial Sector\\
\textbf{Closure Support} & Domain-Wall Protection & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A phase ramp within the Gaussian window endows the bridge tone with a non-trivial winding number. Such a phase winding embedded in a domain wall cannot be removed by local continuous deformations; removal requires crossing the seam globally.

\tzpsection{Canonical Equation}
\[
\nu=\frac{1}{2\pi}\oint d\phi
\]
\[
\nu\neq 0
\]
\[
\mathcal{W}_{\mathrm{wall}}[\phi]\sim \nu
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\pi$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $\mathcal{W}_{\mathrm{wall}}$: source equation symbol.
    \item $\mathcal{K}_{0133}$: canonical registry object for entry ID 0133.
    \item $\nu$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0133 generated source Wolfram model *)
ClearAll[K0133, Cr0133, T, R, A, W, I, N];
eq0133$1 = HoldForm[nu == (1/(2*Pi))*ContourIntegral*dphi];
eq0133$2 = HoldForm[nu != 0];
eq0133$3 = HoldForm[SimilarTo[WWall[phi], nu]];

K0133 = HoldForm[{eq0133$1, eq0133$2, eq0133$3}];

N = "normalized TRAWIN closure object for Topological Protection via Phase Winding";
I = "Domain-Wall Protection integration/comparison layer";
W = "Nontrivial Sector wave or operator carrier";
A = "Winding Number Formula admissible action/amplitude condition";
R = "Nontrivial Sector rotation/curl preservation layer";
T = "Winding Number Formula local source condition";

Cr0133[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0133 = Cr0133[K0133];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Winding Number Formula local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Nontrivial Sector rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Winding Number Formula admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Nontrivial Sector wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Domain-Wall Protection integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Topological Protection via Phase Winding.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0133] Topological Protection via Phase Winding}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\nu=\frac{1}{2\pi}\oint d\phi
\]
\[
\nu\neq 0
\]
\[
\mathcal{W}_{\mathrm{wall}}[\phi]\sim \nu
\]

\paragraph{Primary Derivation.}
The relation is obtained by employing standard algebraic manipulations, yielding the required identity.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. Interpreted through TRAWIN, the equation functions as the generalized carrier for the entry’s information content. According to CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Topological Protection via Phase Winding by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Winding Number Formula}\par
\[
\nu=\frac{1}{2\pi}\oint d\phi
\]
\noindent This turns the inserted phase profile into a global integer-valued invariant.\par
\noindent\textbf{2. Nontrivial Sector}\par
\[
\nu\neq 0
\]
\noindent This states the condition under which the phase pattern leaves the trivial deformation class.\par
\noindent\textbf{3. Domain-Wall Protection}\par
\[
\mathcal{W}_{\mathrm{wall}}[\phi]\sim \nu
\]
\noindent This closes the progression by tying the protected seam directly to the winding number carried by the phase field.\par

\clearpage
\noindent\textbf{[ID 0133] Topological Protection via Phase Winding}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Topological Protection via Phase Winding is a Structural Constraint. A phase ramp within the Gaussian window endows the bridge tone with a non trivial winding number. Such a phase winding embedded in a domain wall cannot be removed by local continuous deformations; removal requires crossing the seam globally.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A phase ramp within the Gaussian window endows the bridge tone with a non trivial winding number. Such a phase winding embedded in a domain wall cannot be removed by local continuous deformations; removal requires crossing the seam globally.
\textbf{Contextual meaning:} Such a phase winding embedded in a domain wall cannot be removed by local continuous deformations; removal requires crossing the seam globally.
\textbf{Derivable consequences:} Source evidence records the entry as a reusable object whose consequences should be read from the matched formal statement and local proof route.
\textbf{Lemma support:} A phase ramp within the Gaussian window endows the bridge tone with a non trivial winding number. Such a phase winding embedded in a domain wall cannot be removed by local continuous deformations; removal requires crossing the seam globally.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Apply phase flip and twist in synthesized signals and observe cancellation or persistent winding; test robustness to amplitude perturbations. ID 133: Topological Protection via Phase Winding

\tzpsection{Equation Grounding}
A phase ramp within the Gaussian window endows the bridge tone with a non trivial winding number. Such a phase winding embedded in a domain wall cannot be removed by local continuous deformations; removal requires crossing the seam globally.

\tzpsection{Interpretive Role}
Such a phase winding embedded in a domain wall cannot be removed by local continuous deformations; removal requires crossing the seam globally.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Winding Number Formula}: The conversion of the inserted phase profile into a global integer-valued invariant.
\item \textbf{Nontrivial Sector}: The condition under which the phase pattern leaves the trivial deformation class.
\item \textbf{Domain-Wall Protection}: The tying of the protected seam directly to the winding number carried by the phase field.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0133]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0133_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0133] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Topological Protection via Phase Winding}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a phase ramp within the Gaussian window endows the bridge tone with a non-trivial
winding number

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Topological Protection via Phase Winding is valid when the stated geometric or
topological relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0133_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
