\section*{ID8894: TESSERACT HIERARCHICAL PARTITIONING Canonical Statutory Formula: A\_total}
\paragraph{Metadata.}
PiID: 4820179289647 | RTEID: RTE:P34537.3772:T0.3583 | UUID: e0c0acff-9d70-5fc9-9536-a14a1be4d464

\paragraph{Canonical Statement.}
[ID 962] TESSERACT HIERARCHICAL PARTITIONING Canonical Statutory Formula: \$A\_\{total\} = \textbackslash{}bigoplus\_\{v=1\}\textasciicircum{}\{16\} (V\_v \textbackslash{}otimes \textbackslash{}mathcal\{S\} \{9600\})\$ Formal Technical Dissertation: Formalizes the hierarchical addressing structure of the navigation system. The total address space is partitioned into 16 hypercubic vertices (\$V\_v\$), each acting as a parent node for a sub-manifold of 9,600 surface points (\$\textbackslash{}mathcal\{S\} \{9600\}\$), enabling the projection of 4D tesseract geometry onto the 3D sphere. Source: [2]

\paragraph{Canonical Equation.}
\[
A_{total} = \bigoplus_{v=1}^{16} (V_v \otimes \mathcal{S} {9600})
\]

\paragraph{Dictionary.}
TESSERACT HIERARCHICAL PARTITIONING Canonical Statutory Formula: \$A\_total = \_v=1\textasciicircum{}16 (V\_v S 9600)\$ Formal Technical Dissertation: Formalizes the hierarchical addressing structure of the navigation system.

\paragraph{Encyclopedia.}
TESSERACT HIERARCHICAL PARTITIONING Canonical Statutory Formula: A\_total is an algebraic definition, written A\_total = oplus\_v=1\textasciicircum{}16 (V\_v ⊗ S 9600). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from v, V\_v, S, defining A\_total. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
