\tzpanchor{0324}
\tzpentryheader{0324}{Helicity Functional in Rotating Frame}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7f88c5e7-417c-59f5-8024-da1a1f71dede}}\\
\textbf{PiID} & \tzpcode{5209209628292} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{331}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1258.1640 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.0731 rad}\\
\textbf{TZPID} & \tzpcode{ID0324} & \textbf{Node Dependencies}\quad \tzpidref{0323}\\
\textbf{Registry} & \tzpcode{registry\_id\_0324} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Rotating Helicity & Rotational Correction\\
\textbf{Closure Support} & Helicity Invariance & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Helicity measures the knottedness of magnetic field lines.

\tzpsection{Canonical Equation}
\[
H(t)=\int_V A(r,t)\cdot B(r,t)\,d^3r-\frac{\omega}{c^2}\int_V r\times(E\times B)\,d^3r
\]
\[
F^{\mathrm{rot}}_{\mu u}=\Lambda_{\mu}^{\ \alpha}\Lambda_{ u}^{\ \beta}F^{\mathrm{lab}}_{\alpha\beta}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H$: source equation symbol.
    \item $A$: source equation symbol.
    \item $t$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $\omega$: angular frequency term in the source equation.
    \item $c$: speed of light or relativistic conversion factor.
    \item $E$: source equation symbol.
    \item $\mu$: source equation symbol.
    \item $\Lambda_{\mu}$: source equation symbol.
    \item $\Lambda_{u}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0324 generated source Wolfram model *)
ClearAll[K0324, Cr0324, T, R, A, W, I, N];
eq0324$1 = HoldForm[H[t] == IntegralV*A[r, t]*B[r, t]*d^3*r - (omega/c^2)*IntegralV*r*(E*B)*d^3*r];
eq0324$2 = HoldForm[F^rot*_*(mu*u) == LambdaMu^alpha*LambdaU^beta*F^lab*_*alphabeta];
eq0324$3 = HoldForm[frac[d]*dt*H[t] == 0];

K0324 = HoldForm[{eq0324$1, eq0324$2, eq0324$3}];

N = "normalized TRAWIN closure object for Helicity Functional in Rotating Frame";
I = "Helicity Invariance integration/comparison layer";
W = "Rotational Correction wave or operator carrier";
A = "Rotating Helicity admissible action/amplitude condition";
R = "Rotational Correction rotation/curl preservation layer";
T = "Rotating Helicity local source condition";

Cr0324[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0324 = Cr0324[K0324];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Rotating Helicity local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Rotational Correction rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Rotating Helicity admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Rotational Correction wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Helicity Invariance integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Helicity Functional in Rotating Frame.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0324] Helicity Functional in Rotating Frame}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_T^4}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,
\hbar\omega\,
\mathrm{d}\omega .
\end{equation}

\paragraph{Primary Derivation.}
Each vacuum mode of frequency $\omega$ contributes energy proportional to:

\begin{equation}
\hbar\omega .
\end{equation}

The spectral density index $\eta(\omega)$ weights the contribution of each frequency:

\begin{equation}
\eta(\omega)\hbar\omega .
\end{equation}

Integrating over all allowed frequencies up to the cutoff $\omega_{\mathrm{cut}}$ gives the weighted vacuum energy:

\begin{equation}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\hbar\omega\,\mathrm{d}\omega .
\end{equation}

To convert this to a density in Trawin units, divide by the fourth power of the base unit:

\begin{equation}
u_T^4 .
\end{equation}

Therefore,

\begin{equation}
\boxed{
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_T^4}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,
\hbar\omega\,
\mathrm{d}\omega .
}
\end{equation}

\paragraph{Interpretation.}
$\rho_{\mathrm{vac}}^{T}$ defines vacuum energy density as a spectral integral normalized by the four-dimensional Trawin base scale.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Helicity Functional in Rotating Frame by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Rotating Helicity}\par
\[
H(t)=\int_V A(r,t)\cdot B(r,t)\,d^3r-\frac{\omega}{c^2}\int_V r\times(E\times B)\,d^3r
\]
\noindent This fixes the magnetic helicity functional in the rotating frame.\par
\noindent\textbf{2. Rotational Correction}\par
\[
F^{\mathrm{rot}}_{\mu u}=\Lambda_{\mu}^{\ \alpha}\Lambda_{ u}^{\ \beta}F^{\mathrm{lab}}_{\alpha\beta}
\]
\noindent This identifies the Lorentz-rotated field-strength tensor that transports the lab frame into the rotating frame.\par
\noindent\textbf{3. Helicity Invariance}\par
\[
frac{d}{dt}H(t)=0
\]
\noindent This closes the entry by stating invariance of the helicity functional under admissible continuous deformation.\par

\clearpage
\noindent\textbf{[ID 0324] Helicity Functional in Rotating Frame}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Helicity Functional in Rotating Frame is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Helicity measures the knottedness of magnetic field lines. \textbf{Contextual meaning:} The entry reads Helicity Functional in Rotating Frame as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the rotating-frame helicity law explicitly instead of dragging broken integral text into display mode. \textbf{Lemma support:} Rotating Helicity; Rotational Correction; Helicity Invariance.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub vac to the power T defines vacuum energy density as a spectral integral normalized by the four-dimensional Trawin base scale.

\tzpsection{Equation Grounding}
Equation anchors: H(t)=integral sub V A(r,t)dot B(r,t) d to the power 3r-ratio omega c to the power 2 integral sub V rtimes(Etimes B) d to the power 3r; F to the power rot sub mu u =Lambda sub mu to the power alpha Lambda sub u to the power beta F to the power lab sub alphabeta; and frac d dt H(t)=0. Proof route: show that the rotating-frame correction preserves the helicity functional under the admissible field evolution. Formalization route: prove that the transformed field tensor yields a time-invariant rotating-frame helicity.

\tzpsection{Interpretive Role}
The entry now states the rotating-frame helicity law explicitly instead of dragging broken integral text into display mode.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Coriolis-Modified Magnetohydrodynamics}: The altered equations of fluid and field motion required when analyzing a system from a continuously spinning vantage point.
\item \textbf{Frame-Dependent Lorentz Transformations}: The mathematical shifting of electric and magnetic field definitions resulting from the transition into a non-inertial reference frame.
\item \textbf{Rotational Helicity Conservation}: The proof that total knotted flux remains a constant invariant even when subjected to active spatial rotation.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0324]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0324_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0324] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Helicity Functional in Rotating Frame}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} helicity measures the knottedness of magnetic field lines

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Helicity Functional in Rotating Frame is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0324_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
