\section*{ID9106: Definition of dcidlnµ}
\paragraph{Metadata.}
PiID: 1303150952617 | RTEID: RTE:P35360.6202:T1.7148 | UUID: 1b7b88af-efa7-5e43-8c77-cd9da9e668a4

\paragraph{Canonical Statement.}
al constants; linkage of UV and IR fixed points; constraints on emergent phenomena. Falsifiability / Test Handle: Failure to observe predicted dimensional crossovers in critical phenomena or highenergy processes would refute this constraint. 0.0.61 ID 059: Scale Dependence of Physical Constants Type: Structural Constraint Formal Statement: Physical constants cic\_ici in the Trawinistic framework are functions of scale \$µ\textbackslash{}muµ\$ and effective dimension dimeff\textbackslash{}dim\_\{\textbackslash{}text\{eff\}\}dimeff; specifically, \$dcidlnµ=fi(cj,dimeff)\textbackslash{}frac\{\textbackslash{}text\{d\}c\_i\}\{\textbackslash{}text\{d\}\textbackslash{}ln\textbackslash{}mu\}\$ = \$f\_i(c\_j,\textbackslash{}dim\_\{\textbackslash{}text\{eff\}\})dlnµdci=fi(cj,dimeff),\$ where functions fif\_ifi encode curvature and zeropoint contributions. Interpretive Meaning: Fundamental constants such as coupling strengths are not truly constant but run with scale due to quantum and geometric effects; their evolution ties to renormalisation flow. Dependencies: ID 058 Derivable Consequences: Variation of constants across sca

\paragraph{Canonical Equation.}
\[
dcidlnµ=fi(cj,dimeff)\frac{\text{d}c_i}{\text{d}\ln\mu}
\]

\paragraph{Dictionary.}
Definition of dcidlnµ — dcidlnµ=fi(cj,dimeff)(dc\_i)/(dlnμ)

\paragraph{Encyclopedia.}
Definition of dcidlnµ is an algebraic definition, written dcidlnµ=fi(cj,dimeff)(dc\_i)/(dlnμ). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from μ, f, c, j, m, c\_i, defining dcidlnµ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
