\section*{ID9355: Definition of)}
\paragraph{Metadata.}
PiID: 7983940041529 | RTEID: RTE:P36327.5425:T3.3079 | UUID: 062737e6-397a-5120-a1b6-1cb588e3c3af

\paragraph{Canonical Statement.}
te HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0016] Node registry\_id\_0022 Support Titles Regularized Curvature Field; Anchor Divergence Criterion; Singularity Classification Test Handle If all physically relevant TZP geometries admit finite regularized curvature at the anchor, the singularity definition would be unsupported. Canonical Equation Links 𝑅𝑇 (𝑥 \$)=lim𝑦→𝑥\$ ( 𝑅 (𝑦)+ 𝑓 (𝑦) ) \$lim𝑥→𝑝\$ 𝑅𝑇 (𝑥 \$)=∞ SingTZP=NormalizeTRAWIN(lim𝑥→𝑝\$ 𝑅𝑇 (𝑥 ) , 𝑅𝑇 \$,Λ)\$ [ID 0023] TZP Potential Term TZPID ID0023 UUID 1786a77f-3042-596a-ab6d-7ec10b409a08 Type Definition Scale potential LOC Classification Working routing: QC174.45 potential theory; QC178 gravitation and field energy arXiv Classification Primary: gr-qc Cross-list: hep-th, math-ph Canonical Statement The TZP potential term models the energetic influence of proximity to the zero po

\paragraph{Canonical Equation.}
\[
)=∞ SingTZP=NormalizeTRAWIN(lim𝑥→𝑝
\]

\paragraph{Dictionary.}
Definition of) — )=∞ SingTZP=NormalizeTRAWIN(lim𝑥→𝑝

\paragraph{Encyclopedia.}
Definition of) is an algebraic definition, written )=∞ SingTZP=NormalizeTRAWIN(lim𝑥→𝑝. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from S, n, g, T, Z, P, defining ). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
