\section*{ID8479: ACOUSTIC LENSE-THIRRING PRECESSION Canonical Statutory Formula: Ω\_drag ∝ ∇ ×…}
\paragraph{Metadata.}
PiID: 6175834413752 | RTEID: RTE:P32925.8400:T3.9862 | UUID: a76fe505-3ab2-57ac-95c6-77de069893ad

\paragraph{Canonical Statement.}
[ID 1189] ACOUSTIC LENSE-THIRRING PRECESSION Canonical Statutory Formula: \$\textbackslash{}Omega\_\{drag\} \textbackslash{}propto \textbackslash{}nabla \textbackslash{}times \textbackslash{}vec\{v\}\_\{acoustic\}\$ Formal Technical Dissertation: Postulates a "Frame-Dragging" effect induced by sound. Intense, structured acoustic fields generate a local curvature in the effective metric of the core, inducing a precession analogous to the gravitational Lense-Thirring effect, thereby allowing the system to steer the Zero Point locus using audio frequencies. Source: [11]

\paragraph{Canonical Equation.}
\[
\Omega_{drag} \propto \nabla \times \vec{v}_{acoustic}
\]

\paragraph{Dictionary.}
ACOUSTIC LENSE-THIRRING PRECESSION Canonical Statutory Formula: Ω\_drag ∝ ∇ × v\_acoustic Formal Technical Dissertation: Postulates a "Frame-Dragging" effect induced by sound.

\paragraph{Encyclopedia.}
ACOUSTIC LENSE-THIRRING PRECESSION Canonical Statutory Formula: Ω\_drag ∝ ∇ ×… is a differential equation, written Ω\_drag ∝ ∇ × v\_acoustic. It relates the quantity to its derivatives, governing how the system evolves in space and time. It is built from ∇, r, a, g, v, c. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
