\tzpanchor{0873}
\tzpentryheader{0873}{VIBRATION COORDINATE TENSOR}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{c1b2eed6-d81a-52e2-b34a-7e758f6edee4}}\\
\textbf{PiID} & \tzpcode{5332083814206} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{880}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3335.6878 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.4962 rad}\\
\textbf{TZPID} & \tzpcode{ID0873} & \textbf{Node Dependencies}\quad \tzpidref{0872}\\
\textbf{Registry} & \tzpcode{registry\_id\_0873} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Aggregate Relation\\
\textbf{Closure Support} & Transfer Map & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records vibration coordinate tensor through a normalized Nonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0873}}:\mathcal{X}_{\mathrm{id0873}}\longrightarrow\mathcal{Y}_{\mathrm{id0873}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0873}})=\mathcal{O}_{\mathrm{id0873}}
\]
\[
\mathcal{O}_{\mathrm{id0873}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0873}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0873}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0873}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0873 generated source Wolfram model *)
ClearAll[K0873, Cr0873, T, R, A, W, I, N];
eq0873$1 = HoldForm[Oid0873[Xid0873] -> Yid0873];
eq0873$2 = HoldForm[NTRAWIN[OId0873] == OId0873];
eq0873$3 = HoldForm[Element[OId0873[x], YAdm]];

K0873 = HoldForm[{eq0873$1, eq0873$2, eq0873$3}];

N = "normalized TRAWIN closure object for VIBRATION COORDINATE TENSOR";
I = "VIBRATION COORDINATE TENSOR integration/comparison layer";
W = "VIBRATION COORDINATE TENSOR wave or operator carrier";
A = "VIBRATION COORDINATE TENSOR admissible action/amplitude condition";
R = "VIBRATION COORDINATE TENSOR rotation/curl preservation layer";
T = "VIBRATION COORDINATE TENSOR local source condition";

Cr0873[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0873 = Cr0873[K0873];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ VIBRATION COORDINATE TENSOR local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ VIBRATION COORDINATE TENSOR rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ VIBRATION COORDINATE TENSOR admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ VIBRATION COORDINATE TENSOR wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ VIBRATION COORDINATE TENSOR integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for VIBRATION COORDINATE TENSOR.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0873] VIBRATION COORDINATE TENSOR}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0873}}:\mathcal{X}_{\mathrm{id0873}}\longrightarrow \mathcal{Y}_{\mathrm{id0873}},\qquad
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0873}})=\mathcal{O}_{\mathrm{id0873}},\qquad
\mathcal{O}_{\mathrm{id0873}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

\paragraph{Primary Derivation.} Let $x\in \mathcal{X}_{\mathrm{id0873}}$ be the local coordinate or field sample.  The entry transform is\[
y=\mathcal{O}_{\mathrm{id0873}}(x),\qquad \mathcal{O}_{\mathrm{id0873}}:\mathcal{X}_{\mathrm{id0873}}\longrightarrow \mathcal{Y}_{\mathrm{id0873}}.
\]

Its differential transport is represented by the id-local Jacobian\[
J_{0873}(x)=D\mathcal{O}_{\mathrm{id0873}}\big|_x,\qquad \det J_{0873}(x)\neq 0
\]

Compatibility with the Nonary chain is enforced by\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0873}})=\mathcal{O}_{\mathrm{id0873}},\qquad y\in\mathcal{Y}_{\mathrm{adm}}.
\]

Thus the Nonary derivation for [ID 0873] is the three-stage passage
\[
\mathcal{X}_{\mathrm{id0873}}\xrightarrow{\,\mathcal{O}_{\mathrm{id0873}}\,} \mathcal{Y}_{\mathrm{id0873}}\xrightarrow{\,\mathcal{N}_{\mathrm{TRAWIN}}\,} \mathcal{Y}_{\mathrm{adm}},
\]
with the entry title fixing the meaning of the carrier and the TRAWIN normalization fixing the admissibility test.

\paragraph{Interpretation.} VIBRATION COORDINATE TENSOR is read as a transport rule: it converts local data into an admissible Nonary coordinate while preserving enough differential structure for the following entry to use it.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors VIBRATION COORDINATE TENSOR by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0873}}:\mathcal{X}_{\mathrm{id0873}}\longrightarrow\mathcal{Y}_{\mathrm{id0873}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0873}})=\mathcal{O}_{\mathrm{id0873}}
\]
\[
\mathcal{O}_{\mathrm{id0873}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0873] VIBRATION COORDINATE TENSOR}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
VIBRATION COORDINATE TENSOR is a registry definition in Resonance and Phase Locking with secondary pressure from Biological and Biomolecular Analogies.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} - Rotor imbalance -> Vibration -> Structural failure. \textbf{Contextual meaning:} The entry reads VIBRATION COORDINATE TENSOR as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Aggregate Relation; Transfer Map.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, VIBRATION COORDINATE TENSOR is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: V sub ijk :=ratio partial to the power 2 psi partial x sub i partial x sub j otimesomega sub k; S sub ij = integral sub x sub i to the power x sub j sqrt(2m(V[x] - E)) dx; and - Vibration: |a| > a sub max to isolation engage. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Omni-Directional Shake Tracking}: The dizzying mathematical grid that doesn't just track where an atom is, but precisely maps out exactly how far and how fast it is jittering in every possible 3D direction simultaneously.
\item \textbf{Acoustic-Strain Matrix Sizing}: The heavy calculations measuring exactly how much physical, tearing stress the deafening sound waves are putting on the steel walls of the containment vessel.
\item \textbf{High-Frequency Displacement Gradients}: The terrifying realization that the rapid, microscopic vibrations aren't just moving the atoms; they are actively, slowly ripping the entire crystal lattice of the room apart.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0873]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0873].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0873] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont VIBRATION COORDINATE TENSOR}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} VIBRATION COORDINATE TENSOR is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``VIBRATION COORDINATE TENSOR is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0873].
\par\endgroup
\vfill
\endgroup
\endgroup
