\section*{ID9082: Hamiltonian for H}
\paragraph{Metadata.}
PiID: 4439658253375 | RTEID: RTE:P35267.4229:T1.5612 | UUID: 2e93879a-dc9c-54d3-8d6b-dc20ddf8051e

\paragraph{Canonical Statement.}
pse of dimensionless parameters; constrains parameter spaces in simulations; leads to universality classes. Falsifiability / Test Handle: Discovery of systems that systematically violate the critical value across scales would falsify this universality. 0.0.43 ID 041: Topological Helicity Quantisation Type: Definition Formal Statement: The magnetic helicity H= \$∫\$ VABd3xH=\textbackslash{}int\_\{V\} \textbackslash{}mathbf\{A\}\textbackslash{}cdot \textbackslash{}mathbf\{B\},\textbackslash{}text\{d\}ˆ3xH= \$∫\$ VABd3x is quantised in units of the Trawinistic winding number, i.e., \$H=wΦH\$ = \$w,\textbackslash{}PhiH=wΦ,\$ where \$Φ\textbackslash{}PhiΦ\$ is the magnetic flux through the lemniscatic loop. Interpretive Meaning: Magnetic helicity takes discrete values proportional to the winding number defined around the TZP. This quantisation persists across scales and ensures topological stability. Dependencies: ID 020, ID 037 Derivable Consequences: Constrains dynamo processes; links helicity to angular momentum g

\paragraph{Canonical Equation.}
\[
H=wΦH
\]

\paragraph{Dictionary.}
Hamiltonian for H — H=wΦH

\paragraph{Encyclopedia.}
Hamiltonian for H is an algebraic definition, written H=wΦH. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from w, defining H. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
