\tzpanchor{0746}
\tzpentryheader{0746}{DERIVATIVE OF DIMENSIONAL DRIFT}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{143c930c-2202-545c-827a-4241aa277ed4}}\\
\textbf{PiID} & \tzpcode{9960518707211} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{753}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2861.9347 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.7156 rad}\\
\textbf{TZPID} & \tzpcode{ID0746} & \textbf{Node Dependencies}\quad \tzpidref{0745}\\
\textbf{Registry} & \tzpcode{registry\_id\_0746} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records derivative of dimensional drift through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0746}}:\mathcal{X}_{\mathrm{id0746}}\longrightarrow\mathcal{Y}_{\mathrm{id0746}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0746}})=\mathcal{O}_{\mathrm{id0746}}
\]
\[
\mathcal{O}_{\mathrm{id0746}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0746}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0746}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0746}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0746 generated source Wolfram model *)
ClearAll[K0746, Cr0746, T, R, A, W, I, N];
eq0746$1 = HoldForm[Oid0746[Xid0746] -> Yid0746];
eq0746$2 = HoldForm[NTRAWIN[OId0746] == OId0746];
eq0746$3 = HoldForm[Element[OId0746[x], YAdm]];

K0746 = HoldForm[{eq0746$1, eq0746$2, eq0746$3}];

N = "normalized TRAWIN closure object for DERIVATIVE OF DIMENSIONAL DRIFT";
I = "DERIVATIVE OF DIMENSIONAL DRIFT integration/comparison layer";
W = "DERIVATIVE OF DIMENSIONAL DRIFT wave or operator carrier";
A = "DERIVATIVE OF DIMENSIONAL DRIFT admissible action/amplitude condition";
R = "DERIVATIVE OF DIMENSIONAL DRIFT rotation/curl preservation layer";
T = "DERIVATIVE OF DIMENSIONAL DRIFT local source condition";

Cr0746[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0746 = Cr0746[K0746];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ DERIVATIVE OF DIMENSIONAL DRIFT local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ DERIVATIVE OF DIMENSIONAL DRIFT rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ DERIVATIVE OF DIMENSIONAL DRIFT admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ DERIVATIVE OF DIMENSIONAL DRIFT wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ DERIVATIVE OF DIMENSIONAL DRIFT integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for DERIVATIVE OF DIMENSIONAL DRIFT.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0746] DERIVATIVE OF DIMENSIONAL DRIFT}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0746}}:\mathcal{X}_{\mathrm{id0746}}\longrightarrow\mathcal{Y}_{\mathrm{id0746}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0746}})=\mathcal{O}_{\mathrm{id0746}}
\]
\[
\mathcal{O}_{\mathrm{id0746}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0746}})=\mathcal{O}_{\mathrm{id0746}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. In the TRAWIN reading, the equation functions as the mapping carrier for the entry’s information content. Within the CHL view, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors DERIVATIVE OF DIMENSIONAL DRIFT by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0746}}:\mathcal{X}_{\mathrm{id0746}}\longrightarrow\mathcal{Y}_{\mathrm{id0746}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0746}})=\mathcal{O}_{\mathrm{id0746}}
\]
\[
\mathcal{O}_{\mathrm{id0746}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0746] DERIVATIVE OF DIMENSIONAL DRIFT}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
DERIVATIVE OF DIMENSIONAL DRIFT is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} dot S>= 0. \textbf{Contextual meaning:} The entry reads DERIVATIVE OF DIMENSIONAL DRIFT as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, DERIVATIVE OF DIMENSIONAL DRIFT is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: L sub k = W sub r + T sub w; R sub m = u03bc sub 0 u03c3 L v = Lu00b2 u03c9 u03bc sub 0 u03c3; and t SD to the power 2 = textbackslash lim textbackslash Delta ttextbackslash to 0 textbackslash frac 1 textbackslash De. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spatial-Volume Expansion Rates}: The terrifying, continuous calculation of exactly how fast the bizarre physics of the core are actively stretching and enlarging the literal, physical size of the inside of the room.
\item \textbf{Fractional Topology Shifts}: The tracking of the slow, creeping math error as the system gradually, accidentally slides from being a perfect 3D volume into a weird 2.9D fractal shape.
\item \textbf{Metric-Fabric Stretching Acceleration}: The measurement not just of how far space has bent, but whether the process of bending is actively speeding up and running out of control toward the singularity.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0746]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0746].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0746] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont DERIVATIVE OF DIMENSIONAL DRIFT}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} DERIVATIVE OF DIMENSIONAL DRIFT is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``DERIVATIVE OF DIMENSIONAL DRIFT is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0746].
\par\endgroup
\vfill
\endgroup
\endgroup
