\tzpanchor{0372}
\tzpentryheader{0372}{Magnetic Energy and Pressure Functional}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{8ed983ae-d2c9-5161-ac7d-4798f9b46b71}}\\
\textbf{PiID} & \tzpcode{8204665213841} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{379}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1444.5586 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.3802 rad}\\
\textbf{TZPID} & \tzpcode{ID0372} & \textbf{Node Dependencies}\quad \tzpidref{0371}\\
\textbf{Registry} & \tzpcode{registry\_id\_0372} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Magnetic Energy Density & Integrated Magnetic Energy\\
\textbf{Closure Support} & Constraint Energy & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The magnetic energy density inside the spherical enclosure is half the square of the magnetic field divided by the permeability. The total magnetic energy within a radius is obtained by integrating this density over the volume. Mechanical compression contributes an additional constraint energy with a force that scales inversely with the fourth power of separation.

\tzpsection{Canonical Equation}
\[
u_{B}=\frac{B^{2}}{2\mu_{0}}
\]
\[
E_{B}=\int_{\Omega}u_{B}\,dV
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $u_{B}$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $\mu_{0}$: vacuum permeability constant.
    \item $E_{B}$: source equation symbol.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $p_{B}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0372 generated source Wolfram model *)
ClearAll[K0372, Cr0372, T, R, A, W, I, N];
eq0372$1 = HoldForm[uB == B^2/(2*mu0)];
eq0372$2 = HoldForm[EB == IntegralOmegauB*dV];
eq0372$3 = HoldForm[pB == B^2/(2*mu0)];

K0372 = HoldForm[{eq0372$1, eq0372$2, eq0372$3}];

N = "normalized TRAWIN closure object for Magnetic Energy and Pressure Functional";
I = "Constraint Energy integration/comparison layer";
W = "Integrated Magnetic Energy wave or operator carrier";
A = "Magnetic Energy Density admissible action/amplitude condition";
R = "Integrated Magnetic Energy rotation/curl preservation layer";
T = "Magnetic Energy Density local source condition";

Cr0372[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0372 = Cr0372[K0372];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Magnetic Energy Density local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Integrated Magnetic Energy rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Magnetic Energy Density admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Integrated Magnetic Energy wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Constraint Energy integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Magnetic Energy and Pressure Functional.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0372] Magnetic Energy and Pressure Functional}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
[q,p]=i\hbar .
\end{equation}

\paragraph{Primary Derivation.}
Continuous-variable quantum systems use observables with continuous spectra, such as position $q$ and momentum $p$.

The commutator is defined by
\begin{equation}
[q,p]=qp-pq .
\end{equation}

Canonical quantization imposes
\begin{equation}
\boxed{
[q,p]=i\hbar .
}
\end{equation}

In the Trawinistic extension, curvature may modify the phase-space volume element while preserving the canonical commutator as the primary algebraic witness.

\paragraph{Interpretation.}
Continuous-variable systems extend the registry from finite qubit states into infinite-dimensional Hilbert-space dynamics.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Magnetic Energy and Pressure Functional by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Magnetic Energy Density}\par
\[
u_{B}=\frac{B^{2}}{2\mu_{0}}
\]
\noindent This fixes the local magnetic energy density carried by the field configuration.\par
\noindent\textbf{2. Integrated Magnetic Energy}\par
\[
E_{B}=\int_{\Omega}u_{B}\,dV
\]
\noindent This integrates the density over the bounded spherical carrier to obtain the total magnetic energy.\par
\noindent\textbf{3. Constraint Energy}\par
\[
p_{B}=\frac{B^{2}}{2\mu_{0}}
\]
\noindent This closes the entry by adding the mechanical compression contribution into the total constraint energy.\par

\clearpage
\noindent\textbf{[ID 0372] Magnetic Energy and Pressure Functional}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Magnetic Energy and Pressure Functional is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The magnetic energy density inside the spherical enclosure is half the square of the magnetic field divided by the permeability. The total magnetic energy within a radius is obtained by integrating this density over the volume. Mechanical compression contributes an additional constraint energy with a force that scales inversely with the fourth power of separation. \textbf{Contextual meaning:} The entry reads Magnetic Energy and Pressure Functional as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now gives magnetic pressure and compressive energy a real energy-density and integral structure instead of broken modulus fragments. \textbf{Lemma support:} Magnetic Energy Density; Integrated Magnetic Energy; Constraint Energy.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Continuous-variable systems extend the registry from finite qubit states into infinite-dimensional Hilbert-space dynamics.

\tzpsection{Equation Grounding}
Equation anchors: T, Hc = 11; I = 0; and kgcdotm to the power 2, omega = 10 to the power 4 rad/s to T = 5 MJ - Example: I = 0. Proof route: show that integrating the magnetic energy density over the bounded domain and adding mechanical compression yields the stated constraint energy. Formalization route: prove that the stated constraint energy follows from the integrated magnetic energy and the mechanical compression term.

\tzpsection{Interpretive Role}
The entry now gives magnetic pressure and compressive energy a real energy-density and integral structure instead of broken modulus fragments.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Squared-Field Energy Density}: The standard physical law dictating that the energy stored in a magnetic field grows exponentially with the strength of the field.
\item \textbf{Volumetric Flux Compression}: The total potential energy calculated by integrating the local magnetic tension across the entire bounded spatial domain.
\item \textbf{Plasma Containment Stress}: The outward mechanical force exerted by the crowded magnetic field lines pushing against the physical boundaries of the system.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0372]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0372_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0372] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Magnetic Energy and Pressure Functional}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the magnetic energy density inside the spherical enclosure is half the square of the
magnetic field divided by the permeability

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Magnetic Energy and Pressure Functional is valid when the stated operator maps
admissible inputs into the declared target class.''\\
\textbf{Proof:} The source statement is read as an operator or transformation. The proof obligation is
type preservation: admissible inputs must land in the target object without breaking the
stated constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- operator-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0372_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
