\section*{ID8487: FIBONACCI PROJECTIVE MORPHISM Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 1375223970968 | RTEID: RTE:P32956.9058:T4.0374 | UUID: 857eebfd-99e6-5e75-a662-4af8be60496c

\paragraph{Canonical Statement.}
[ID 1179] FIBONACCI PROJECTIVE MORPHISM Canonical Statutory Formula: \$\textbackslash{}Pi: ACGT\textasciicircum{}N \textbackslash{}xrightarrow\{\textbackslash{}text\{Helical\}\} \textbackslash{}text\{Fibonacci\}(S\textasciicircum{}2\_\{153600\})\$ Formal Technical Dissertation: The projection operator for the DAANSphere. It defines the specific morphism that maps the linear \$4\textasciicircum{}N\$ biological sequence onto the spherical geometry of the 153,600-node Fibonacci lattice, converting sequence data into spatial coordinates. Source: [3]

\paragraph{Canonical Equation.}
\[
\Pi: ACGT^N \xrightarrow{\text{Helical}} \text{Fibonacci}(S^2_{153600})
\]

\paragraph{Dictionary.}
FIBONACCI PROJECTIVE MORPHISM Canonical Statutory Formula: \$ : ACGT\textasciicircum{}N Helical Fibonacci(S\textasciicircum{}2\_153600)\$ Formal Technical Dissertation: The projection operator for the DAANSphere.

\paragraph{Encyclopedia.}
FIBONACCI PROJECTIVE MORPHISM Canonical Statutory Formula is a symbolic expression, written Π: ACGT\textasciicircum{}N xrightarrowHelical Fibonacci(S\textasciicircum{}2\_153600). It introduces a symbol or relation used elsewhere in the framework. It is built from Π, A, C, G, T, N. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
