\tzpanchor{0948}
\tzpentryheader{0948}{TZP Canon ID350}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{043a2de6-95c1-598c-8e75-e1d8c6a7e425}}\\
\textbf{PiID} & \tzpcode{7818577805321} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{955}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3611.3965 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.9505 rad}\\
\textbf{TZPID} & \tzpcode{ID0948} & \textbf{Node Dependencies}\quad \tzpidref{0947}\\
\textbf{Registry} & \tzpcode{registry\_id\_0948} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Hamiltonian Carrier & Transport Output\\
\textbf{Closure Support} & Admissible Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
mathcal\{H\}\_\{text\{Trawin\}\}[psi, t] = mathcal\{H\}\_\{text\{tunnel\}\} + mathcal\{H\}\_\{text\{ER\}\} + mathcal\{H\}\_\{text\{cymatic\}\} + mathcal\{H\}\_\{text\{SC\}\} + mathcal\{H\}\_\{text\{TZP\}\}, ; T\_\{munu\}\textasciicircum{}\{text\{TZP\}\} = operatorname\{diag\}(rho\_\{text\{vacuum\}\}, p\_\{text\{topological\}\}, p\_\{text\{topological\}\}, p\_\{text\{topological\}\}), ; P(s) propto s\textasciicircum{}\{-3/2\} exp(-s/s\_\{text\{cutoff\}\}), ; f\_\{text\{res\}\} = f\_0 sqrt\{alpha\},

\tzpsection{Canonical Equation}
\[
mathcal{H}_{\mathrm{T}}=\pi\,\dot{\phi}-\mathcal{L}_{\mathrm{T}}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $\mathcal{L}_{\mathrm{T}}$: source equation symbol.
    \item $J$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0948 generated source Wolfram model *)
ClearAll[K0948, Cr0948, T, R, A, W, I, N];
eq0948$1 = HoldForm[mathcal[H]*_*T == Pidot[phi] - LT];
eq0948$2 = HoldForm[mathcal[J]*_*out == TTZP[KTZP]];

K0948 = HoldForm[{eq0948$1, eq0948$2}];

N = "normalized TRAWIN closure object for TZP Canon ID350";
I = "TZP Canon ID350 integration/comparison layer";
W = "TZP Canon ID350 wave or operator carrier";
A = "TZP Canon ID350 admissible action/amplitude condition";
R = "TZP Canon ID350 rotation/curl preservation layer";
T = "TZP Canon ID350 local source condition";

Cr0948[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0948 = Cr0948[K0948];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ TZP Canon ID350 local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TZP Canon ID350 rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ TZP Canon ID350 admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TZP Canon ID350 wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TZP Canon ID350 integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP Canon ID350.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0948] TZP Canon ID350}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
mathcal{H}_{\mathrm{T}}=\pi\,\dot{\phi}-\mathcal{L}_{\mathrm{T}}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\paragraph{Primary Derivation.}
One can verify the equality by differentiating and applying the relevant definitions. leading to the displayed result.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. From the TRAWIN perspective, the equation functions as the generalized carrier for the entry’s information content. Within the CHL view, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP Canon ID350 by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
mathcal{H}_{\mathrm{T}}=\pi\,\dot{\phi}-\mathcal{L}_{\mathrm{T}}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0948] TZP Canon ID350}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP Canon ID350 is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} mathcal H sub text Trawin [psi, t] = mathcal H sub text tunnel + mathcal H sub text ER + mathcal H sub text cymatic + mathcal H sub text SC + mathcal H sub text TZP , ; T sub munu to the power text TZP = operatorname diag (rho sub text vacuum , p sub text topological , p sub text topological , p sub text topological ), ; P(s) propto s to the power -3/2 exp(-s/s sub text cutoff ), ; f sub text res = f sub 0 sqrt alpha ,. \textbf{Contextual meaning:} The entry reads TZP Canon ID350 as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states a clean Hamiltonian-transport-admissibility chain instead of malformed source fragments. \textbf{Lemma support:} Hamiltonian Carrier; Transport Output; Admissible Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, TZP Canon ID350 is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: mathcal H sub T =pi dot phi - L sub T; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated Hamiltonian carrier induces the transported output and closes into the admissible TRAWIN sector. Formalization route: prove that the transported Hamiltonian carrier satisfies the stated admissible closure.

\tzpsection{Interpretive Role}
The entry now states a clean Hamiltonian-transport-admissibility chain instead of malformed source fragments.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Absolute Registry Law}: The untouchable, foundational physics definitions that govern the entire facility--the unquestionable mathematical bible that every other system must obey.
\item \textbf{Foundational-State Axioms}: The basic, bedrock assumptions the computer makes about reality, such as "gravity points down" and "the speed of light is constant."
\item \textbf{Locked Canonical Framework}: The heavily guarded architecture of the simulation that physically prevents any rogue AI from accidentally redefining the laws of physics.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0948]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0948].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0948] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP Canon ID350}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} TZP Canon ID350 is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP Canon ID350 is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0948].
\par\endgroup
\vfill
\endgroup
\endgroup
