\section*{ID9074: Definition of -δ(x,x’)TGT(x,x)}
\paragraph{Metadata.}
PiID: 7119621844396 | RTEID: RTE:P35236.3571:T1.5100 | UUID: 7fb5bd1c-fc13-57fa-9bda-1e2a24adb586

\paragraph{Canonical Statement.}
agation of fields near the TZP; determines particle spectra; underlies quantum propagator; links to conservation laws. Falsifiability / Test Handle: Discrepancies between observed field behaviour and solutions to these equations would falsify them. 0.0.37 ID 035: Quantum Field Propagator (TZP Background) Type: Operator Formal Statement: The propagator GT(x,x)G\_\{\textbackslash{}text\{T\}\}(x,x’)GT(x,x) for a scalar field in the Trawinistic manifold satisfies \$TGT(x,x)=δ(x,x)\textbackslash{}Boxˆ\{\textbackslash{}text\{T\}\}\$ G\_\{\textbackslash{}text\{T\}\}(x,x’) = \$-\textbackslash{}delta(x,x’)TGT(x,x)=δ(x,x)\$ subject to boundary conditions consistent with the TZP structure and includes exponential suppression factors derived from the TZP potential. Interpretive Meaning: This Green function describes how disturbances propagate from xx’x to xxx in the presence of the TZP. It modifies the usual propagator by accounting for the degenerate metric and potential. Dependencies: ID 019, ID 023 Derivable Conseq

\paragraph{Canonical Equation.}
\[
-\delta(x,x’)TGT(x,x)=δ(x,x)
\]

\paragraph{Dictionary.}
Definition of -δ(x,x’)TGT(x,x) — -δ(x,x’)TGT(x,x)=δ(x,x)

\paragraph{Encyclopedia.}
Definition of -δ(x,x’)TGT(x,x) is an algebraic definition, written -δ(x,x’)TGT(x,x)=δ(x,x). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from x, defining -δ(x,x’)TGT(x,x). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
