\section*{ID9042: Definition of c\_T}
\paragraph{Metadata.}
PiID: 2882250545255 | RTEID: RTE:P35112.0940:T1.3053 | UUID: 55687616-be7b-59b4-8454-52e636466144

\paragraph{Canonical Statement.}
ntisation; constrains allowed vortices and monopoles; informs the characteristic class; influences the spectrum of permitted states. Falsifiability / Test Handle: Detection of continuous or nonquantised phase accumulation around the TZP would contradict this definition. 0.0.23 ID 021: Trawin Characteristic Class Type: Definition Formal Statement: The Trawin characteristic class c\_Tc\_\{\textbackslash{}text\{T\}\}c\_T is an element of the cohomology group H2(M\{p\},Z)Hˆ2(M\textbackslash{}setminus\{p\},\textbackslash{}mathbb\{Z\})H2(M\{p\},Z) defined by \$c\_T=[12πF]c\_\{\textbackslash{}text\{T\}\}=[\textbackslash{}frac\{1\}\{2\textbackslash{}pi\}F]c\_T=[2π1F],\$ where FFF is the curvature twoform of a principal U(1) bundle whose connection oneform has holonomy equal to the Trawinistic winding number www . Interpretive Meaning: This class encodes the global topological information associated with the TZP and determines how bundles twist around the zero point. It generalises familiar characteristic classes to the Trawin framework. Dependencies: ID 020 Der

\paragraph{Canonical Equation.}
\[
c_T=[12πF]c_{\text{T}}=[\frac{1}{2\pi}F]c_T=[2π1F],
\]

\paragraph{Dictionary.}
Definition of c\_T — c\_T=[12πF]c\_T=[(1)/(2π)F]c\_T=[2π1F]

\paragraph{Encyclopedia.}
Definition of c\_T is an algebraic definition, written c\_T=[12πF]c\_T=[(1)/(2π)F]c\_T=[2π1F]. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from π, F, c\_, defining c\_T. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
