\section*{ID9179: Relation: ∫ ΣF/(2π)c\_1}
\paragraph{Metadata.}
PiID: 8623625612521 | RTEID: RTE:P35644.0954:T2.1818 | UUID: 973ddede-e22f-51e7-841c-20c86dcc20f8

\paragraph{Canonical Statement.}
eomorphisms. Falsifiability / Test Handle: Discovery of symmetries outside U(1)× SU(2)× SU(3)× Diff(M)U(1) \textbackslash{}times SU(2) \textbackslash{}times SU(3) \textbackslash{}times \textbackslash{}text\{Diff\}(\textbackslash{}mathcal\{M\})U(1)× SU(2)× SU(3)× Diff(M) or failure to define such a bundle would falsify this entry. 2.0.13 ID 162: Associated Bundles and Vacuum Extraction Type: Definition Formal Statement: From the principal bundle one constructs associated bun- dles: the gravitational tangent bundle, an electromagnetic line bundle with first Chern class c1= \$∫ ΣF/(2π)c\_1\$ = \$\textbackslash{}int\_\{\textbackslash{}Sigma\}F/(2\textbackslash{}pi)c1 =∫ΣF/(2π), anuclearvectorbundleofrank8, andavacuumextractionbundletrivializingintoL2(R)LΘ2(\textbackslash{}mathbb\{R\})L2(R).\$ Interpretive Meaning: Each fundamental interaction corresponds to an associated bundle derived from the principal bundle; the vacuum extraction bundle encodes Hilbertspace valued fibers for zeropoint energy extraction. Dependencies: ID 161 Derivable Consequences

\paragraph{Canonical Equation.}
\[
∫ ΣF/(2π)c_1
\]

\paragraph{Dictionary.}
Relation: ∫ ΣF/(2π)c\_1 — ∫ ΣF/(2π)c\_1

\paragraph{Encyclopedia.}
Relation: ∫ ΣF/(2π)c\_1 is a symbolic expression, written ∫ ΣF/(2π)c\_1. It introduces a symbol or relation used elsewhere in the framework. It is built from F, c\_1. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
