\tzpanchor{0304}
\tzpentryheader{0304}{Helical Transfer Function with Berry and Sagnac Phases}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{560f423f-3292-5056-a896-ab2476c8fa10}}\\
\textbf{PiID} & \tzpcode{8700660631558} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{311}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1180.4995 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9451 rad}\\
\textbf{TZPID} & \tzpcode{ID0304} & \textbf{Node Dependencies}\quad \tzpidref{0303}\\
\textbf{Registry} & \tzpcode{registry\_id\_0304} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Transfer Function & Dispersion Frequency\\
\textbf{Closure Support} & Geometric Phase Sum & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Light propagating through a rotating helical medium accumulates both a geometrical Berry phase, proportional to the golden ratio logarithm, and a Sagnac phase due to rotation.

\tzpsection{Canonical Equation}
\[
H(k)=A(k)\exp\!\left(i(\phi_{\mathrm{B}}+\phi_{\mathrm{S}})\right)
\]
\[
\omega_m=c\sqrt{k_z^2+(m/R)^2+2m\Omega/n}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H$: source equation symbol.
    \item $A$: source equation symbol.
    \item $\phi_{\mathrm{B}}$: flux, phase, or topological map term in the source equation.
    \item $\phi_{\mathrm{S}}$: flux, phase, or topological map term in the source equation.
    \item $\omega_m$: angular frequency term in the source equation.
    \item $c$: speed of light or relativistic conversion factor.
    \item $k_z(m/R)$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $n$: integer mode index.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0304 generated source Wolfram model *)
ClearAll[K0304, Cr0304, T, R, A, W, I, N];
eq0304$1 = HoldForm[H[k] == A[k]*exp[i[phiB + phiS]]];
eq0304$2 = HoldForm[omegaM == cSqrt[kZ^2 + (m/R)^2 + 2*(mOmega/n)]];
eq0304$3 = HoldForm[PhiGeom == phiB + phiS];

K0304 = HoldForm[{eq0304$1, eq0304$2, eq0304$3}];

N = "normalized TRAWIN closure object for Helical Transfer Function with Berry and Sagnac Phases";
I = "Geometric Phase Sum integration/comparison layer";
W = "Dispersion Frequency wave or operator carrier";
A = "Transfer Function admissible action/amplitude condition";
R = "Dispersion Frequency rotation/curl preservation layer";
T = "Transfer Function local source condition";

Cr0304[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0304 = Cr0304[K0304];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Transfer Function local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Dispersion Frequency rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Transfer Function admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Dispersion Frequency wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Geometric Phase Sum integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Helical Transfer Function with Berry and Sagnac Phases.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0304] Helical Transfer Function with Berry and Sagnac Phases}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\det(g)\big|_{p}=0,
\qquad
g^{-1}\big|_{p}\ \text{does not exist},
\qquad
\det(g)\neq 0\ \text{for}\ x\neq p .
\end{equation}

\paragraph{Primary Derivation.}
A metric tensor $g$ admits an inverse $g^{-1}$ precisely when its determinant is nonzero:

\begin{equation}
g^{-1}\ \text{exists}
\iff
\det(g)\neq 0 .
\end{equation}

The Trawinistic manifold is ordinary away from $p$, so:

\begin{equation}
\det(g)(x)\neq 0,
\qquad x\neq p .
\end{equation}

At the TZP, invertibility fails. Hence:

\begin{equation}
g^{-1}\big|_p \ \text{does not exist}.
\end{equation}

By the determinant criterion, this implies:

\begin{equation}
\det(g)\big|_p=0 .
\end{equation}

\paragraph{Interpretation.}
ID 0004 strengthens ID 0001 by explicitly separating the ordinary region from the TZP degeneracy region.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Helical Transfer Function with Berry and Sagnac Phases by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Transfer Function}\par
\[
H(k)=A(k)\exp\!\left(i(\phi_{\mathrm{B}}+\phi_{\mathrm{S}})\right)
\]
\noindent This fixes the helical transfer function for the rotating orbital-angular-momentum mode.\par
\noindent\textbf{2. Dispersion Frequency}\par
\[
\omega_m=c\sqrt{k_z^2+(m/R)^2+2m\Omega/n}
\]
\noindent This adds the mode dispersion law that determines the transport frequency.\par
\noindent\textbf{3. Geometric Phase Sum}\par
\[
\Phi_{\mathrm{geom}}=\phi_{\mathrm{B}}+\phi_{\mathrm{S}}
\]
\noindent This closes the entry by summing the Berry and Sagnac phase sectors carried by the helical channel.\par

\clearpage
\noindent\textbf{[ID 0304] Helical Transfer Function with Berry and Sagnac Phases}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Helical Transfer Function with Berry and Sagnac Phases is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Light propagating through a rotating helical medium accumulates both a geometrical Berry phase, proportional to the golden ratio logarithm, and a Sagnac phase due to rotation. \textbf{Contextual meaning:} The entry reads Helical Transfer Function with Berry and Sagnac Phases as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now carries the transfer function as an explicit phase-weighted transport law instead of malformed extraction prose. \textbf{Lemma support:} Transfer Function; Dispersion Frequency; Geometric Phase Sum.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
ID 0004 strengthens ID 0001 by explicitly separating the ordinary region from the TZP degeneracy region.

\tzpsection{Equation Grounding}
Equation anchors: H sub m(Omega,t)=exp (i(omega sub m t+Phi to the power Berry sub m+Phi to the power Sagnac sub m(Omega))); omega sub m = csqrt k sub z to the power 2 + (m/R) to the power 2 + 2mOmega/n; and Phi to the power Berry sub m=ratio 2lnvarphi pi mt,; Phi to the power Sagnac sub m(Omega)=ratio 4piOmega R to the power 2 lambda sub 0 c m. Proof route: show that the helical transport law factors into the stated carrier frequency and geometric phase contributions. Formalization route: prove that the rotating helical mode admits the stated decomposition into dispersion, Berry phase, and Sagnac phase.

\tzpsection{Interpretive Role}
The entry now carries the transfer function as an explicit phase-weighted transport law instead of malformed extraction prose.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Gyroscopic Phase Shift}: The non-reciprocal accumulation of phase delay induced by the rotational motion of the carrier medium.
\item \textbf{Topological Berry Holonomy}: The geometric phase accrued by a quantum state traversing a closed cyclic path in parameter space.
\item \textbf{Chiral Dispersion Modulation}: The frequency-dependent splitting of wave propagation velocities induced by ambient frame-dragging.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0304]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0304_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0304] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Helical Transfer Function with Berry and Sagnac Phases}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} light propagating through a rotating helical medium accumulates both a geometrical Berry
phase, proportional to the golden ratio logarithm, and a S...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Helical Transfer Function with Berry and Sagnac Phases is valid when the stated
geometric or topological relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0304_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
