\section*{ID8518: EFFECTIVE GRAVITATIONAL COUPLING Canonical Statutory Formula: G\_eff}
\paragraph{Metadata.}
PiID: 1738188399944 | RTEID: RTE:P33077.2857:T4.2357 | UUID: a5c883c3-6a8f-5486-9416-3dd39886e1cf

\paragraph{Canonical Statement.}
[ID 1145] EFFECTIVE GRAVITATIONAL COUPLING Canonical Statutory Formula: \$G\_\{eff\} = G\_0 [1 + \textbackslash{}epsilon \textbackslash{}cos(\textbackslash{}omega t)]\_\{time-avg\} \textbackslash{}rightarrow G\_0\$ Formal Technical Dissertation: Postulates that the gravitational constant \$G\$ is not a fundamental static value but the time-averaged coupling strength of spacetime oscillations at the Planck frequency (\$\textbackslash{}approx 10\textasciicircum{}\{43\}\$ Hz). Observable variations emerge only at intermediate beat frequencies. Source:

\paragraph{Canonical Equation.}
\[
G_{eff} = G_0 [1 + \epsilon \cos(\omega t)]_{time-avg} \rightarrow G_0
\]

\paragraph{Dictionary.}
EFFECTIVE GRAVITATIONAL COUPLING Canonical Statutory Formula: \$G\_eff = G\_0 [1 + ( t)]\_time-avg G\_0\$ Formal Technical Dissertation: Postulates that the gravitational constant G is not a fundamental static value but the time-averaged coupling strength of spacetime oscillations at the Planck frequency

\paragraph{Encyclopedia.}
EFFECTIVE GRAVITATIONAL COUPLING Canonical Statutory Formula: G\_eff is an algebraic definition, written G\_eff = G\_0 [1 + ε cos(ω t)]\_time-avg arrow G\_0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from ε, ω, G\_0, m, a, v, defining G\_eff. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
