\tzpanchor{0619}
\tzpentryheader{0619}{SQUID FLUX TOMOGRAPHY}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{294d9068-6e22-50ee-a5ef-987f3d2ed3db}}\\
\textbf{PiID} & \tzpcode{2778577134275} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{626}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2380.4151 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.9222 rad}\\
\textbf{TZPID} & \tzpcode{ID0619} & \textbf{Node Dependencies}\quad \tzpidref{0618}\\
\textbf{Registry} & \tzpcode{registry\_id\_0619} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records squid flux tomography through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\Box_T\phi = g^{ab} \nabla^{T}_{a} \nabla^{T}_{b} \phi.
\]
\[
\nabla_a\nabla_b\phi \quad\longrightarrow\quad \nabla^T_a\nabla^T_b\phi.
\]
\[
\mathcal{A}_{\mathrm{TZP}}(\mathrm{id}_{0619})=\mathcal{A}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $T$: source equation symbol.
    \item $T_a$: source equation symbol.
    \item $T_b$: source equation symbol.
    \item $\mathcal{A}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{A}_{\mathrm{adm}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0619 generated source Wolfram model *)
ClearAll[K0619, Cr0619, T, R, A, W, I, N];
eq0619$1 = HoldForm[BoxTphi == g^ab*Grad^T*_*a*Grad^T*_*b*phi];
eq0619$2 = HoldForm[GradAGrad_bphi -> Grad^TAGrad^TBphi];
eq0619$3 = HoldForm[ATZP[id0619] == AAdm];

K0619 = HoldForm[{eq0619$1, eq0619$2, eq0619$3}];

N = "normalized TRAWIN closure object for SQUID FLUX TOMOGRAPHY";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Canonical Definition admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Canonical Definition local source condition";

Cr0619[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0619 = Cr0619[K0619];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Canonical Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Canonical Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for SQUID FLUX TOMOGRAPHY.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0619] SQUID FLUX TOMOGRAPHY}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Box_T\phi
=
g^{ab}
\nabla^{T}_{a}
\nabla^{T}_{b}
\phi .
\end{equation}

\paragraph{Primary Derivation.}
The ordinary d'Alembertian is the metric contraction of two covariant derivatives acting on a field.  
In Trawinistic geometry, replace the ordinary covariant derivative with $\nabla^T$:

\begin{equation}
\nabla_a\nabla_b\phi
\quad\longrightarrow\quad
\nabla^T_a\nabla^T_b\phi .
\end{equation}

Then contract using the regularized inverse metric $g^{ab}$:

\begin{equation}
\Box_T\phi
=
g^{ab}
\nabla^{T}_{a}
\nabla^{T}_{b}
\phi .
\end{equation}

\paragraph{Interpretation.}
$\Box_T$ extends wave propagation and field equations into the Trawinistic manifold by replacing ordinary derivatives with TZP-compatible covariant derivatives.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors SQUID FLUX TOMOGRAPHY by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Canonical Definition}\par
\[
\Box_T\phi = g^{ab} \nabla^{T}_{a} \nabla^{T}_{b} \phi.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\nabla_a\nabla_b\phi \quad\longrightarrow\quad \nabla^T_a\nabla^T_b\phi.
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\mathcal{A}_{\mathrm{TZP}}(\mathrm{id}_{0619})=\mathcal{A}_{\mathrm{adm}}
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0619] SQUID FLUX TOMOGRAPHY}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
SQUID FLUX TOMOGRAPHY is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Phi = nPhi sub 0 implies text Quantized Flux Detection. \textbf{Contextual meaning:} The entry reads SQUID FLUX TOMOGRAPHY as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub T extends wave propagation and field equations into the Trawinistic manifold by replacing ordinary derivatives with TZP-compatible covariant derivatives.

\tzpsection{Equation Grounding}
Equation anchors: Phi = nPhi sub 0 implies Quantized Flux Detection; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Superconducting Interference Magnetometry}: The deployment of incredibly sensitive, microscopic loops of frozen wire designed to detect even the faintest whisper of a passing magnetic field.
\item \textbf{Quantum-Phase Shift Detection}: The process of measuring the tiny, barely noticeable changes in the electrical current that occur when a single, solitary electron spins the wrong way inside the reactor.
\item \textbf{High-Resolution 3D Magnetic Mapping}: The combination of thousands of these tiny sensors to draw a perfect, real-time, holographic picture of the invisible, twisting tornado of energy trapped inside the core.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0619]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0619_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0619] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont SQUID FLUX TOMOGRAPHY}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records squid flux tomography through the Septenary derivation layer, using
the displayed relations as operational anchors for the canoni...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``SQUID FLUX TOMOGRAPHY is valid as a spectral relation when frequency, phase, and
propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0619_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
