\tzpanchor{0019}
\tzpentryheader{0019}{Trawinistic d'Alembertian}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{6d74c597-ddfc-52d2-adb1-f8d00b173427}}\\
\textbf{PiID} & \tzpcode{6264338327950} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{26}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{73.7812 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.1216 rad}\\
\textbf{TZPID} & \tzpcode{ID0019} & \textbf{Node Dependencies}\quad \tzpidref{0016}\\
\textbf{Registry} & \tzpcode{registry\_id\_0019} & \textbf{Scale}\quad wave-operator\\
\textbf{LOC Classification} & QC174.5 wave propagation & QA431 hyperbolic operators\\
\textbf{arXiv Classification} & Primary: gr-qc \quad Cross-list: hep-th, math-ph & \\
\textbf{Primary Support} & Regularized Inverse Metric & Double Trawinistic Covariant Derivative\\
\textbf{Closure Support} & Normalized d'Alembertian & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Trawinistic d'Alembertian is the wave operator induced by the regularized inverse metric and the Trawinistic connection. It governs propagation on the singularly aware manifold in the same way the ordinary box operator governs wave evolution on regular space-time.

\tzpsection{Canonical Equation}
\[
\Box_{\mathrm{T}}\phi
=
g_{\mathrm{reg}}^{ab}
\nabla^{\mathrm{T}}_{a}
\nabla^{\mathrm{T}}_{b}\phi
\]
\[
g_{\mathrm{reg}}^{ab}
=
\left(g^{-1}\right)_{\mathrm{reg}}^{ab}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $g_{\mathrm{reg}}$: source equation symbol.
    \item $\Box_{\mathrm{T}}$: Trawinistic wave operator governing propagation on the TZP background.
    \item $B$: magnetic field magnitude.
    \item $T$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0019 generated source Wolfram model *)
ClearAll[K0019, Cr0019, T, R, A, W, I, N];
eq0019$1 = HoldForm[BoxTphi == gReg^ab*Grad^T*_*a*Grad^T*_*b*phi];
eq0019$2 = HoldForm[gReg^ab == (_*reg^ab)/g];
eq0019$3 = HoldForm[Grad^T*_*a*Grad^T*_*b*phi];

K0019 = HoldForm[{eq0019$1, eq0019$2, eq0019$3}];

N = "normalized TRAWIN closure object for Trawinistic d'Alembertian";
I = "Normalized d'Alembertian integration/comparison layer";
W = "Double Trawinistic Covariant Derivative wave or operator carrier";
A = "Regularized Inverse Metric admissible action/amplitude condition";
R = "Double Trawinistic Covariant Derivative rotation/curl preservation layer";
T = "Regularized Inverse Metric local source condition";

Cr0019[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0019 = Cr0019[K0019];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Regularized Inverse Metric local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Double Trawinistic Covariant Derivative rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Regularized Inverse Metric admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Double Trawinistic Covariant Derivative wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized d'Alembertian integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Trawinistic d'Alembertian.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0019] Trawinistic d'Alembertian}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Box_T\phi
=
g^{ab}
\nabla^{T}_{a}
\nabla^{T}_{b}
\phi .
\end{equation}

\paragraph{Primary Derivation.}
The ordinary d'Alembertian is the metric contraction of two covariant derivatives acting on a field.  
In Trawinistic geometry, replace the ordinary covariant derivative with $\nabla^T$:

\begin{equation}
\nabla_a\nabla_b\phi
\quad\longrightarrow\quad
\nabla^T_a\nabla^T_b\phi .
\end{equation}

Then contract using the regularized inverse metric $g^{ab}$:

\begin{equation}
\Box_T\phi
=
g^{ab}
\nabla^{T}_{a}
\nabla^{T}_{b}
\phi .
\end{equation}

\paragraph{Interpretation.}
$\Box_T$ extends wave propagation and field equations into the Trawinistic manifold by replacing ordinary derivatives with TZP-compatible covariant derivatives.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Trawinistic d'Alembertian by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Regularized Inverse Metric}\par
\[
g_{\mathrm{reg}}^{ab}
=
\left(g^{-1}\right)_{\mathrm{reg}}^{ab}
\]
\noindent This provides the raised-index structure needed to turn second covariant derivatives into a wave operator.\par
\noindent\textbf{2. Double Trawinistic Covariant Derivative}\par
\[
\nabla^{\mathrm{T}}_{a}
\nabla^{\mathrm{T}}_{b}\phi
\]
\noindent This forms the raw second-order propagation term before contraction.\par
\noindent\textbf{3. Normalized d'Alembertian}\par
\[
\Box_{\mathrm{T}}\phi
=
g_{\mathrm{reg}}^{ab}
\nabla^{\mathrm{T}}_{a}
\nabla^{\mathrm{T}}_{b}\phi
\]
\noindent This closes the progression by producing the singularly aware wave operator that later field equations can directly use.\par

\clearpage
\noindent\textbf{[ID 0019] Trawinistic d'Alembertian}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Trawinistic d Alembertian is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The Trawinistic d Alembertian  TBox T  T acting on a field  phi  is given by  T =gabnablaT sub anablaT sub b Box T phi= gtextsuperscript ab nabla T textbackslash sub a nabla T textbackslash sub b phi T =gabnablaT sub anablaT sub b , where gabg ab gab is the regularised inverse metric and nablaTnabla T nabla\$T the Trawinistic connection. \textbackslash{}. \textbf{Contextual meaning:} The entry reads Trawinistic d Alembertian as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Regularized Inverse Metric; Double Trawinistic Covariant Derivative; Normalized d Alembertian.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub T extends wave propagation and field equations into the Trawinistic manifold by replacing ordinary derivatives with TZP-compatible covariant derivatives.

\tzpsection{Equation Grounding}
Equation anchors: The Trawinistic d Alembertian  TBox to the power T  T acting on a field  phi  is given by  T =gab ablaT a ablaT b Box to the power T phi= gtextsuperscript ab abla T textbackslash a abla to the power T textbackslash b phi T =gab ablaT a ablaT b , where gabg to the power ab gab is the regularised inverse metric and ablaT abla to the power T ablaT the Trawinistic connection. The Trawinistic d Alembertian  TBox to the power T  T acting on a field  phi  is given by  T =gab ablaT a ablaT b Box to the power T phi= gtextsuperscript ab abla T textbackslash a abla to the power T textbackslash b phi T =gab ablaT a ablaT b , where gabg to the power ab gab is the regularised inverse metric and ablaT abla to the power T ablaT the Trawinistic connection.

\tzpsection{Interpretive Role}
This operator is the canonical propagation engine for Trawinistic wave equations. It connects the singular geometry, the regularized curvature sector, and the derivative structure into one transport law.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Trawinistic Alembertian}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Trawinistic Alembertian Normalization Analogue}: normalization vocabulary for fixed form, invariant comparison, or TRAWIN admissibility.
\item \textbf{Alembertian Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0019]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0019_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0019] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Trawinistic d'Alembertian}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the Trawinistic d'Alembertian is the wave operator induced by the regularized inverse
metric and the Trawinistic connection

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Trawinistic d'Alembertian is valid as a spectral relation when frequency, phase, and
propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0019_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
