\section*{ID9015: Definition of plimτ→∞γ(τ)}
\paragraph{Metadata.}
PiID: 9406034021665 | RTEID: RTE:P35007.2470:T1.1325 | UUID: be478719-cf70-57b5-a755-d0f9ed407726

\paragraph{Canonical Statement.}
Zero Point Contextus Canonicus This prologue establishes the context for the canonical registry that follows. The registry entries refer back to these definitions and structures but remain axiomatic and generative in their own right. 0.0.2 ID 000: Existence and Uniqueness of the Trawin Zero Point Type: Axiom Formal Statement: There exists exactly one point ppp in the Trawinistic manifold MMM such that for all geodesics \$γ\textbackslash{}gammaγ\$ in MMM, \$limτ→∞γ(τ)\$ = \$p\textbackslash{}lim\_\{\textbackslash{}tau\textbackslash{}to\textbackslash{}infty\}\textbackslash{}gamma(\textbackslash{}tau)\$ = \$plimτ→∞γ(τ)=p;\$ furthermore, ppp is the unique fixed point under any symmetrypreserving diffeomorphism \$:M→M\textbackslash{}phi:M\textbackslash{}rightarrow M:M→M.\$ Interpretive Meaning: A single Trawin Zero Point (TZP) anchors the manifold; all trajectories and fields asymptotically converge to this point. This axiom asserts that the universe has a unique zeropoint reference and that no other equivalent points exist. Dependencies: Primitive

\paragraph{Canonical Equation.}
\[
plimτ→∞γ(τ)=p;
\]

\paragraph{Dictionary.}
Zero Point Contextus Canonicus This prologue establishes the context for the canonical registry that follows.

\paragraph{Encyclopedia.}
Definition of plimτ→∞γ(τ) is an algebraic definition, written plimτ→∞γ(τ)=p;. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from p, defining plimτ→∞γ(τ). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
