\tzpanchor{0136}
\tzpentryheader{0136}{Celestial Gyromagnetic Motion Axiom}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{a06d4ce0-a222-57f7-8ee5-f0df4c477ef0}}\\
\textbf{PiID} & \tzpcode{3172535940812} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{143}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{528.1182 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.8702 rad}\\
\textbf{TZPID} & \tzpcode{ID0136} & \textbf{Node Dependencies}\quad \tzpidref{0135}\\
\textbf{Registry} & \tzpcode{registry\_id\_0136} & \textbf{Scale}\quad toroidal celestial dynamics\\
\textbf{LOC Classification} & QB355 orbital mechanics & QA641 geometric structures\\
\textbf{arXiv Classification} & Primary: gr-qc \quad Cross-list: astro-ph.EP, math-ph & \\
\textbf{Primary Support} & Toroidal Bundle Statement & Gyromagnetic Ratio Law\\
\textbf{Closure Support} & Averaged Force Recovery & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Celestial gyromagnetic motion is described by orbits that are geodesics on a principal $T^2$-bundle. The gyromagnetic ratio $\gamma=L/\mu$ is universal for rotating systems, with $\gamma=2n\hbar/(qvr)$ for integer $n$. Classical Newtonian gravity is recovered from the averaged toroidal potential $F=GMm/r^2=V_{\mathrm{toroidal}}/\mathrm{time}$.

\tzpsection{Canonical Equation}
\[
\pi:\mathcal{P}\to \mathcal{M},
\qquad
\mathrm{fiber}(\pi)=T^2
\]
\[
\gamma=\frac{L}{\mu}=\frac{2n\hbar}{qvr}
\]
\[
F_{\mathrm{avg}}(r)=\frac{GMm}{r^2}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\pi$: source equation symbol.
    \item $\mathcal{P}$: source equation symbol.
    \item $\mathcal{M}$: source equation symbol.
    \item $T$: source equation symbol.
    \item $\gamma$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $\mu$: source equation symbol.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
    \item $F_{\mathrm{avg}}(r)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0136 generated source Wolfram model *)
ClearAll[K0136, Cr0136, T, R, A, W, I, N];
eq0136$1 = HoldForm[pi[P] -> MfiberpiT2];
eq0136$2 = HoldForm[gamma == L/mu == (2*nhbar)/qvr];
eq0136$3 = HoldForm[FAvg[r] == GMm/r^2];

K0136 = HoldForm[{eq0136$1, eq0136$2, eq0136$3}];

N = "normalized TRAWIN closure object for Celestial Gyromagnetic Motion Axiom";
I = "Averaged Force Recovery integration/comparison layer";
W = "Gyromagnetic Ratio Law wave or operator carrier";
A = "Toroidal Bundle Statement admissible action/amplitude condition";
R = "Gyromagnetic Ratio Law rotation/curl preservation layer";
T = "Toroidal Bundle Statement local source condition";

Cr0136[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0136 = Cr0136[K0136];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Toroidal Bundle Statement local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Gyromagnetic Ratio Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Toroidal Bundle Statement admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Gyromagnetic Ratio Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Averaged Force Recovery integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Celestial Gyromagnetic Motion Axiom.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0136] Celestial Gyromagnetic Motion Axiom}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\pi:\mathcal{P}\to \mathcal{M},
\qquad
\mathrm{fiber}(\pi)=T^2
\]
\[
\gamma=\frac{L}{\mu}=\frac{2n\hbar}{qvr}
\]
\[
F_{\mathrm{avg}}(r)=\frac{GMm}{r^2}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \qquad \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. From the TRAWIN perspective, the equation functions as the mapping carrier for the entry’s information content. According to CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Celestial Gyromagnetic Motion Axiom by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Toroidal Bundle Statement}\par
\[
\pi:\mathcal{P}\to \mathcal{M},
\qquad
\mathrm{fiber}(\pi)=T^2
\]
\noindent This gives the geometric carrier for the celestial motion axiom.\par
\noindent\textbf{2. Gyromagnetic Ratio Law}\par
\[
\gamma=\frac{L}{\mu}=\frac{2n\hbar}{qvr}
\]
\noindent This inserts the universal rotating-system ratio into the toroidal framework.\par
\noindent\textbf{3. Averaged Force Recovery}\par
\[
F_{\mathrm{avg}}(r)=\frac{GMm}{r^2}
\]
\noindent This closes the progression by recovering the familiar inverse-square force from the averaged toroidal picture.\par

\clearpage
\noindent\textbf{[ID 0136] Celestial Gyromagnetic Motion Axiom}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Celestial Gyromagnetic Motion Axiom is a Axiom. Celestial gyromagnetic motion is described by orbits that are geodesics on a principal T  bundle. The gyromagnetic ratio   = L/  is universal for rotating systems, given by   = (2 n  )/(q v r), where n is an integer.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Celestial gyromagnetic motion is described by orbits that are geodesics on a principal T  bundle. The gyromagnetic ratio   = L/  is universal for rotating systems, given by   = (2 n  )/(q v r), where n is an integer.
\textbf{Contextual meaning:} This axiom quantizes celestial motion and links it to gyromagnetic properties. It shows that gravitation emerges from a toroidal potential averaged over cycles, unifying rotation and gravity.
\textbf{Derivable consequences:} Quantization of orbital angular momentum; universal gyromagnetic ratio; derivation of Newton's law from toroidal dynamics; predictions for gyromagnetic resonances.
\textbf{Lemma support:} Celestial gyromagnetic motion is described by orbits that are geodesics on a principal T  bundle. The gyromagnetic ratio   = L/  is universal for rotating systems, given by   = (2 n  )/(q v r), where n is an integer.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Measure gyromagnetic ratios of astrophysical bodies and test for universality; d

\tzpsection{Equation Grounding}
Celestial gyromagnetic motion is described by orbits that are geodesics on a principal T  bundle. The gyromagnetic ratio   = L/  is universal for rotating systems, given by   = (2 n  )/(q v r), where n is an integer.

\tzpsection{Interpretive Role}
This axiom quantizes celestial motion and links it to gyromagnetic properties. It shows that gravitation emerges from a toroidal potential averaged over cycles, unifying rotation and gravity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Toroidal Bundle Statement}: The geometric carrier for the celestial motion axiom.
\item \textbf{Gyromagnetic Ratio Law}: The insertion of the universal rotating-system ratio into the toroidal framework.
\item \textbf{Averaged Force Recovery}: The recovery of the familiar inverse-square force from the averaged toroidal picture.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0136]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0136_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0136] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Celestial Gyromagnetic Motion Axiom}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} celestial gyromagnetic motion is described by orbits that are geodesics on a principal
T\textasciicircum{}2-bundle

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Celestial Gyromagnetic Motion Axiom is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0136_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
