\tzpanchor{0343}
\tzpentryheader{0343}{Atemporal Null Surface Basis}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{b0dc4d52-0e64-56e4-b8fb-669f186cf7af}}\\
\textbf{PiID} & \tzpcode{1536436789259} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{350}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1331.9452 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.1946 rad}\\
\textbf{TZPID} & \tzpcode{ID0343} & \textbf{Node Dependencies}\quad \tzpidref{0342}\\
\textbf{Registry} & \tzpcode{registry\_id\_0343} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The atemporal null surface acts as an infinite-capacity holographic screen where information exists as a superposition of all possible configurations. The 153,600 DAANSphere points provide a complete basis for decomposing this infinite-dimensional information into finite readable chunks via standing wave mediation. Each point is an independent quantum channel endowed with topological protection, enabling error-free retrieval despite decoherence.

\tzpsection{Canonical Equation}
\[
\mathcal{N}_{0}=\{x\mid g(v,v)=0\}
\]
\[
n^{a}\nabla_{a}\tau=0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{N}_{0}$: source equation symbol.
    \item $v$: velocity, flow speed, or auxiliary comparison variable.
    \item $n$: integer mode index.
    \item $\tau$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0343 generated source Wolfram model *)
ClearAll[K0343, Cr0343, T, R, A, W, I, N];
eq0343$1 = HoldForm[N0 == {x, g[v, v] == 0}];
eq0343$2 = HoldForm[n^a*GradAtau == 0];
eq0343$3 = HoldForm[Sigma == bigcupAlphaN0^alpha];

K0343 = HoldForm[{eq0343$1, eq0343$2, eq0343$3}];

N = "normalized TRAWIN closure object for Atemporal Null Surface Basis";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0343[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0343 = Cr0343[K0343];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Atemporal Null Surface Basis.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0343] Atemporal Null Surface Basis}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
Lk
=
\frac{1}{4\pi}
\oint_{C_1}
\oint_{C_2}
\frac{
(\mathbf{r}_1-\mathbf{r}_2)
\cdot
(\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2)
}{
|\mathbf{r}_1-\mathbf{r}_2|^3
}.
\end{equation}

\paragraph{Primary Derivation.}
Let $C_1$ and $C_2$ be two closed magnetic flux tubes or field-line loops.  
The Gauss linking integral measures how many times the two loops wind around one another.

For points $\mathbf{r}_1\in C_1$ and $\mathbf{r}_2\in C_2$, the relative displacement is:

\begin{equation}
\mathbf{r}_1-\mathbf{r}_2 .
\end{equation}

The oriented area element generated by the two path differentials is:

\begin{equation}
\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2 .
\end{equation}

Normalizing by the cubic separation gives the universal linking density:

\begin{equation}
\frac{
(\mathbf{r}_1-\mathbf{r}_2)
\cdot
(\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2)
}{
|\mathbf{r}_1-\mathbf{r}_2|^3
}.
\end{equation}

The full linking number is:

\begin{equation}
\boxed{
Lk
=
\frac{1}{4\pi}
\oint_{C_1}
\oint_{C_2}
\frac{
(\mathbf{r}_1-\mathbf{r}_2)
\cdot
(\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2)
}{
|\mathbf{r}_1-\mathbf{r}_2|^3
}.
}
\end{equation}

\paragraph{Interpretation.}
The linking number is integer-valued and topologically stable. It supplies the universal counting rule behind helicity quantisation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Atemporal Null Surface Basis by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
\mathcal{N}_{0}=\{x\mid g(v,v)=0\}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
n^{a}\nabla_{a}\tau=0
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\Sigma=\bigcup_{\alpha}\mathcal{N}_{0}^{(\alpha)}
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0343] Atemporal Null Surface Basis}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Atemporal Null Surface Basis is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The atemporal null surface acts as an infinite-capacity holographic screen where information exists as a superposition of all possible configurations. The 153,600 DAANSphere points provide a complete basis for decomposing this infinite-dimensional information into finite readable chunks via standing wave mediation. Each point is an independent quantum channel endowed with topological protection, enabling error-free retrieval despite decoherence. \textbf{Contextual meaning:} The entry reads Atemporal Null Surface Basis as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The linking number is integer-valued and topologically stable. It supplies the universal counting rule behind helicity quantisation.

\tzpsection{Equation Grounding}
Equation anchors: proof=non sub chl sub or sub empirical registry sub definition sub combined,D: 0 sub Engine sub Outputspublish sub reassemble expanded sub context registry sub en; proof=candidate sub formal sub math registry sub definition sub combined,D: 0 sub Engine sub Outputspublish sub reassemble expanded sub context registry sub e; and proof=candidate sub proofable sub chl. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Light-Cone Geometry Projection}: The definition of a coordinate surface moving exactly at the speed of light, effectively freezing the progression of proper time.
\item \textbf{Time-Independent Subspace}: The mathematical isolation of a localized region where dynamics are entirely governed by spatial geometry rather than chronological evolution.
\item \textbf{Causality Boundary Mapping}: The organization of spacetime into distinct zones separated by surfaces across which physical information cannot pass.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0343]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0343_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0343] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Atemporal Null Surface Basis}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the atemporal null surface acts as an infinite-capacity holographic screen where
information exists as a superposition of all possible configurations

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Atemporal Null Surface Basis is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0343_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
