\tzpanchor{0208}
\tzpentryheader{0208}{Acoustic Frame-Dragging Metric}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{fd0632a6-99da-5bc8-b7c7-2118d16ac947}}\\
\textbf{PiID} & \tzpcode{7566593344612} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{215}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{807.7102 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.3309 rad}\\
\textbf{TZPID} & \tzpcode{ID0208} & \textbf{Node Dependencies}\quad \tzpidref{0207}\\
\textbf{Registry} & \tzpcode{registry\_id\_0208} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Dragged Metric & Mixed Component\\
\textbf{Closure Support} & Wave Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Rotation drags the inertial frame, effectively warping spacetime for sound waves.

\tzpsection{Canonical Equation}
\[
g_{00} = -\left(c^2 - \lvert \omega \times r \rvert^2\right)
\]
\[
g_{0i} = -(\omega \times r)_i
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $g_{00}$: source equation symbol.
    \item $c$: speed of light or relativistic conversion factor.
    \item $\omega$: angular frequency term in the source equation.
    \item $g_{0i}$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0208 generated source Wolfram model *)
ClearAll[K0208, Cr0208, T, R, A, W, I, N];
eq0208$1 = HoldForm[g00 == -(c^2 - Abs[omega*r]^2)];
eq0208$2 = HoldForm[g0*i == (-(omega*r))*_i];
eq0208$3 = HoldForm[BoxG*phi == 0];

K0208 = HoldForm[{eq0208$1, eq0208$2, eq0208$3}];

N = "normalized TRAWIN closure object for Acoustic Frame-Dragging Metric";
I = "Wave Law integration/comparison layer";
W = "Mixed Component wave or operator carrier";
A = "Dragged Metric admissible action/amplitude condition";
R = "Mixed Component rotation/curl preservation layer";
T = "Dragged Metric local source condition";

Cr0208[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0208 = Cr0208[K0208];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Dragged Metric local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Mixed Component rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Dragged Metric admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Mixed Component wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Wave Law integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Acoustic Frame-Dragging Metric.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0208] Acoustic Frame-Dragging Metric}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
K_{\mathrm{NL}}
=
\frac{\left\lVert \nabla^{2}\varphi\right\rVert}
{\left\lVert \nabla\varphi\right\rVert^{2}} .
\end{equation}

\paragraph{Primary Derivation.}
Let $\varphi$ be a scalar field on the Trawinistic manifold.  
The first-order variation of the field is measured by the gradient:

\begin{equation}
\nabla\varphi .
\end{equation}

The second-order curvature or bending of the field is measured by:

\begin{equation}
\nabla^2\varphi .
\end{equation}

A dimensionless measure of non-linearity should compare second-order deformation against the square of first-order variation. Therefore define:

\begin{equation}
K_{\mathrm{NL}}
=
\frac{\text{second-order field deformation}}
{\text{first-order field variation squared}} .
\end{equation}

Substituting the appropriate differential norms gives:

\begin{equation}
\boxed{
K_{\mathrm{NL}}
=
\frac{\left\lVert \nabla^{2}\varphi\right\rVert}
{\left\lVert \nabla\varphi\right\rVert^{2}} .
}
\end{equation}

\paragraph{Interpretation.}
$K_{\mathrm{NL}}$ measures how sharply a field bends relative to its local rate of change. Large values indicate strong nonlinear behavior near the TZP.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Acoustic Frame-Dragging Metric by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Dragged Metric}\par
\[
g_{00} = -\left(c^2 - \lvert \omega \times r \rvert^2\right)
\]
\noindent This fixes the dragged temporal component of the effective metric.\par
\noindent\textbf{2. Mixed Component}\par
\[
g_{0i} = -(\omega \times r)_i
\]
\noindent This resolves the off-diagonal rotational mixing induced by the gyroscopic frame.\par
\noindent\textbf{3. Wave Law}\par
\[
Box_g \phi = 0
\]
\noindent This closes the entry with the curved-space acoustic wave equation.\par

\clearpage
\noindent\textbf{[ID 0208] Acoustic Frame-Dragging Metric}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Acoustic Frame-Dragging Metric is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Rotation drags the inertial frame, effectively warping spacetime for sound waves. \textbf{Contextual meaning:} The entry reads Acoustic Frame-Dragging Metric as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now carries an explicit frame-dragged metric and its acoustic wave law, which is the right geometric carrier for the next splitting page. \textbf{Lemma support:} Dragged Metric; Mixed Component; Wave Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
K sub NL measures how sharply a field bends relative to its local rate of change. Large values indicate strong nonlinear behavior near the TZP.

\tzpsection{Equation Grounding}
Equation anchors: g sub 00 = -(c to the power 2 - lvert omega times r rvert to the power 2); g sub 0i = -(omega times r) sub i; and Box sub g phi = 0. Proof route: show that the rotating acoustic frame induces the stated effective metric and curved-space wave law. Formalization route: prove that the stated mixed metric components imply the stated covariant acoustic wave equation.

\tzpsection{Interpretive Role}
The entry now carries an explicit frame-dragged metric and its acoustic wave law, which is the right geometric carrier for the next splitting page.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Gyroscopic Acoustic Metric Perturbation}: The effective curvature experienced by sound waves propagating through a rapidly rotating fluid.
\item \textbf{Rotational Fluid Shear Coupling}: The off-diagonal terms representing how the fluid's angular momentum sweeps acoustic phonons along its path.
\item \textbf{Covariant Acoustic Wave Transport}: The generalized wave equation treating sound propagation as geodesic motion in an artificial spacetime geometry.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0208]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0208_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0208] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Acoustic Frame-Dragging Metric}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} rotation drags the inertial frame, effectively warping spacetime for sound waves

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Acoustic Frame-Dragging Metric is valid as a tensorial/geometric statement when the
stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0208_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
