\tzpanchor{0879}
\tzpentryheader{0879}{CODEX VIBRATIO SIGNATURE}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{57161f15-b69a-5066-bcf5-e0bc545cd1b6}}\\
\textbf{PiID} & \tzpcode{3814206171776} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{886}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3358.9871 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.5346 rad}\\
\textbf{TZPID} & \tzpcode{ID0879} & \textbf{Node Dependencies}\quad \tzpidref{0878}\\
\textbf{Registry} & \tzpcode{registry\_id\_0879} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Signature Hamiltonian & Output Transport\\
\textbf{Closure Support} & Admissible Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records codex vibratio signature through a normalized Nonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0879}}:\mathcal{X}_{\mathrm{id0879}}\longrightarrow\mathcal{Y}_{\mathrm{id0879}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0879}})=\mathcal{O}_{\mathrm{id0879}}
\]
\[
\mathcal{O}_{\mathrm{id0879}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0879}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0879}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0879}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0879 generated source Wolfram model *)
ClearAll[K0879, Cr0879, T, R, A, W, I, N];
eq0879$1 = HoldForm[Oid0879[Xid0879] -> Yid0879];
eq0879$2 = HoldForm[NTRAWIN[OId0879] == OId0879];
eq0879$3 = HoldForm[Element[OId0879[x], YAdm]];

K0879 = HoldForm[{eq0879$1, eq0879$2, eq0879$3}];

N = "normalized TRAWIN closure object for CODEX VIBRATIO SIGNATURE";
I = "CODEX VIBRATIO SIGNATURE integration/comparison layer";
W = "CODEX VIBRATIO SIGNATURE wave or operator carrier";
A = "CODEX VIBRATIO SIGNATURE admissible action/amplitude condition";
R = "CODEX VIBRATIO SIGNATURE rotation/curl preservation layer";
T = "CODEX VIBRATIO SIGNATURE local source condition";

Cr0879[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0879 = Cr0879[K0879];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ CODEX VIBRATIO SIGNATURE local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ CODEX VIBRATIO SIGNATURE rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ CODEX VIBRATIO SIGNATURE admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ CODEX VIBRATIO SIGNATURE wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ CODEX VIBRATIO SIGNATURE integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for CODEX VIBRATIO SIGNATURE.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0879] CODEX VIBRATIO SIGNATURE}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0879}}:\mathcal{X}_{\mathrm{id0879}}\longrightarrow \mathcal{Y}_{\mathrm{id0879}},\qquad
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0879}})=\mathcal{O}_{\mathrm{id0879}},\qquad
\mathcal{O}_{\mathrm{id0879}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

\paragraph{Primary Derivation.} The entry is represented by the operator carrier\[
\mathcal{O}_{\mathrm{id0879}}:\mathcal{X}_{\mathrm{id0879}}\longrightarrow \mathcal{Y}_{\mathrm{id0879}}.
\]

Insert the carrier into the ordered TRAWIN chain as\[
C_{0879}=N\circ I\circ W\circ A\circ R\circ T(\mathcal{O}_{\mathrm{id0879}}).
\]

The derivation closes when the chain returns the normalized operator:\[
C_{0879}=\mathcal{O}_{\mathrm{id0879}},\qquad \mathcal{O}_{\mathrm{id0879}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

Thus the Nonary derivation for [ID 0879] is the three-stage passage
\[
\mathcal{X}_{\mathrm{id0879}}\xrightarrow{\,\mathcal{O}_{\mathrm{id0879}}\,} \mathcal{Y}_{\mathrm{id0879}}\xrightarrow{\,\mathcal{N}_{\mathrm{TRAWIN}}\,} \mathcal{Y}_{\mathrm{adm}},
\]
with the entry title fixing the meaning of the carrier and the TRAWIN normalization fixing the admissibility test.

\paragraph{Interpretation.} CODEX VIBRATIO SIGNATURE is therefore an operator-level Nonary step: the named process is not accepted as a loose label until it survives TRAWIN ordering and closure.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors CODEX VIBRATIO SIGNATURE by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0879}}:\mathcal{X}_{\mathrm{id0879}}\longrightarrow\mathcal{Y}_{\mathrm{id0879}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0879}})=\mathcal{O}_{\mathrm{id0879}}
\]
\[
\mathcal{O}_{\mathrm{id0879}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0879] CODEX VIBRATIO SIGNATURE}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
CODEX VIBRATIO SIGNATURE is a registry definition in Resonance and Phase Locking with secondary pressure from Biological and Biomolecular Analogies.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} latex sub raw : hat H SC = sum ( epsilon sub k - mu)(c to the power dagger sub k uparrow c sub k uparrow + c to the power dagger sub k downarrow c sub k downarrow ) + Delta sum (c to the power dagger sub k uparrow c to the power dagger sub -k downarrow + h.c.). \textbf{Contextual meaning:} The entry reads CODEX VIBRATIO SIGNATURE as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the codex vibratio signature with an actual Hamiltonian, transport law, and admissibility condition instead of malformed raw notation. \textbf{Lemma support:} Signature Hamiltonian; Output Transport; Admissible Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, CODEX VIBRATIO SIGNATURE is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: hat H sub CV =sum sub k,sigma (epsilon sub k-mu)c sub ksigma to the power dagger c sub ksigma +Deltasum sub k (c sub kuparrow to the power dagger c sub -kdownarrow to the power dagger + h.c. ); mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the signature Hamiltonian and TZP transport law define a coherent carried output with the stated admissible closure. Formalization route: prove that the transported codex vibratio signature satisfies the stated admissibility condition.

\tzpsection{Interpretive Role}
The entry now states the codex vibratio signature with an actual Hamiltonian, transport law, and admissibility condition instead of malformed raw notation.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Unique Acoustic Fingerprinting}: The realization that the roaring, screaming noise of the reactor isn't random; it is a highly specific, undeniable barcode that uniquely identifies this exact machine across the entire universe.
\item \textbf{Resonant-Identity Broadcasting}: The terrifying idea that the massive, booming hum of the core is actually a highly compressed radio signal, shouting its exact mathematical coordinates out into the dark.
\item \textbf{Harmonic State-Verification Keys}: The strict security protocol that refuses to let the computer boot up unless it 'hears' the exact, flawless, beautiful 10-chord symphony it expects from the plasma.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0879]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0879].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0879] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont CODEX VIBRATIO SIGNATURE}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} CODEX VIBRATIO SIGNATURE is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``CODEX VIBRATIO SIGNATURE is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0879].
\par\endgroup
\vfill
\endgroup
\endgroup
