\tzpanchor{0240}
\tzpentryheader{0240}{Magnetic Reynolds Number Regimes}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7f9ce01e-f4b6-5850-8311-3d33a957902d}}\\
\textbf{PiID} & \tzpcode{2712019091456} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{247}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{931.9733 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.5356 rad}\\
\textbf{TZPID} & \tzpcode{ID0240} & \textbf{Node Dependencies}\quad \tzpidref{0239}\\
\textbf{Registry} & \tzpcode{registry\_id\_0240} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Dimensionless Ratio & Critical Regime\\
\textbf{Closure Support} & Normalized Threshold & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The transition between laminar and dynamo regimes in magnetohydrodynamics is organized by the magnetic Reynolds number \(R_m=\mu_0\sigma vL\). Laboratory flows with \(R_m\ll1\) are diffusion-dominated, Earth's core at \(R_m\sim10^3\) is near dynamo threshold, and stellar interiors at \(R_m\sim10^8\)--\(10^{10}\) are fully turbulent dynamos.

\tzpsection{Canonical Equation}
\[
R_m=\mu_0\sigma vL
\]
\[
R_m<1\Rightarrow \text{diffusion dominated}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $R_m$: source equation symbol.
    \item $\mu_0$: vacuum permeability constant.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $\mathcal{K}_{0240}$: canonical registry object for entry ID 0240.
    \item $\mu$: source equation symbol.
    \item $\gg$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0240 generated source Wolfram model *)
ClearAll[K0240, Cr0240, T, R, A, W, I, N];
eq0240$1 = HoldForm[RM == mu0*sigma*vL];
eq0240$2 = HoldForm[RM < 1 -> DiffusionDominated];
eq0240$3 = HoldForm[RM > 1 -> DynamoDominated];

K0240 = HoldForm[{eq0240$1, eq0240$2, eq0240$3}];

N = "normalized TRAWIN closure object for Magnetic Reynolds Number Regimes";
I = "Normalized Threshold integration/comparison layer";
W = "Critical Regime wave or operator carrier";
A = "Dimensionless Ratio admissible action/amplitude condition";
R = "Critical Regime rotation/curl preservation layer";
T = "Dimensionless Ratio local source condition";

Cr0240[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0240 = Cr0240[K0240];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Dimensionless Ratio local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Critical Regime rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Dimensionless Ratio admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Critical Regime wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Threshold integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Magnetic Reynolds Number Regimes.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0240] Magnetic Reynolds Number Regimes}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Lambda_{\mathrm{crit}}\approx 1 .
\end{equation}

\paragraph{Primary Derivation.}
From the Elsasser parameter,

\begin{equation}
\Lambda
=
\frac{\mathbf{B}^2}
{\rho\,\mu\,\Omega^2},
\end{equation}

criticality occurs when magnetic and rotational terms are balanced.

Balance means the numerator and denominator are of the same order:

\begin{equation}
\mathbf{B}^2
\sim
\rho\,\mu\,\Omega^2 .
\end{equation}

Therefore,

\begin{equation}
\frac{\mathbf{B}^2}
{\rho\,\mu\,\Omega^2}
\sim
1 .
\end{equation}

Thus,

\begin{equation}
\boxed{
\Lambda_{\mathrm{crit}}\approx 1 .
}
\end{equation}

\paragraph{Interpretation.}
The critical Elsasser value marks a universal balance architecture across scales: the point where magnetic organization and rotational inertia enter comparable strength.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Magnetic Reynolds Number Regimes by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Dimensionless Ratio}\par
\[
R_m=\mu_0\sigma vL
\]
\noindent This defines the transport-to-diffusion balance that controls the magnetic regime.\par
\noindent\textbf{2. Critical Regime}\par
\[
R_m<1\Rightarrow \text{diffusion dominated}
\]
\noindent This marks the onset of the self-organizing dynamo window.\par
\noindent\textbf{3. Normalized Threshold}\par
\[
R_m\gg 1\Rightarrow \text{dynamo dominated}
\]
\noindent This closes the entry by normalizing the actual regime against the critical threshold.\par

\clearpage
\noindent\textbf{[ID 0240] Magnetic Reynolds Number Regimes}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Magnetic Reynolds Number Regimes is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The transition between laminar and dynamo regimes in magnetohydrodynamics is organized by \(R_m=\mu_0\sigma vL\). Flows with \(R_m\ll1\) are diffusion-dominated, while \(R_m\gg1\) marks a dynamo-dominated regime. \textbf{Contextual meaning:} The entry reads Magnetic Reynolds Number Regimes as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry gives the later dynamo closure pages an actual diagnostic parameter instead of a purely verbal regime claim. \textbf{Lemma support:} Dimensionless Ratio; Critical Regime; Normalized Threshold.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The magnetic Reynolds number measures the competition between field advection and magnetic diffusion. Small values are diffusion dominated; large values permit dynamo action.

\tzpsection{Equation Grounding}
Equation anchors: R sub m=mu sub 0sigma vL; R sub m<1Rightarrow diffusion dominated; and R sub mgg 1Rightarrow dynamo dominated. Proof route: show that exceeding the critical ratio is necessary for the self-excited magnetic regime stated in the surrounding arc. Formalization route: prove that the normalized dynamo ratio is dimensionless and monotone in the stated transport variables.

\tzpsection{Interpretive Role}
The entry gives the later dynamo closure pages an actual diagnostic parameter instead of a purely verbal regime claim.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Diffusion-Dominated Subcritical Flow}: The classification of a system where electrical resistance destroys magnetic fields faster than fluid motion can build them up.
\item \textbf{Advection-Driven Dynamo Transition}: The specific critical threshold where fluid turbulence begins to stretch, fold, and exponentially amplify seed magnetic fields.
\item \textbf{High-Rm Turbulence and Flux Expulsion}: The extreme regime where highly conductive fluid forcefully expels magnetic fields from turbulent eddies into concentrated ropes.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0240]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0240_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0240] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Magnetic Reynolds Number Regimes}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the transition between laminar and dynamo regimes in magnetohydrodynamics is
organized by \(R_m=\mu_0\sigma vL\), with \(R_m\ll1\) diffusion dominated and \(R_m\gg1\)
dynamo dominated.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Magnetic Reynolds Number Regimes is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that the magnetic Reynolds number compares field
advection to magnetic diffusion. The CHL validation treats the dimensionless equation
\(R_m=\mu_0\sigma vL\) and the regime inequalities \(R_m<1\) and \(R_m\gg1\) as the
formal anchors, with the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0240_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
