\tzpanchor{0015}
\tzpentryheader{0015}{Spectral Density Index (TZP-Weighted)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{bf43db7d-0601-5537-88c4-fde5458c8433}}\\
\textbf{PiID} & \tzpcode{2384626433832} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{22}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{58.2483 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.0960 rad}\\
\textbf{TZPID} & \tzpcode{ID0015} & \textbf{Node Dependencies}\quad \tzpidref{0006}\\
\textbf{Registry} & \tzpcode{registry\_id\_0015} & \textbf{Scale}\quad spectral\\
\textbf{LOC Classification} & QC174.17 spectral analysis & QC670 fluctuation spectra\\
\textbf{arXiv Classification} & Primary: cond-mat.stat-mech \quad Cross-list: math-ph, gr-qc & \\
\textbf{Primary Support} & Power-Law Spectral Weight & Exponential Ultraviolet Cutoff\\
\textbf{Closure Support} & TZP-Weighted Spectral Index & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The spectral density index is defined by $\eta(\omega)=\omega^{-\beta}e^{-\omega/\omega_0}$, where $\omega_0$ is a characteristic frequency fixed by $u_T$ and $\beta$ is a dimensionless exponent determined by the hyper-dimensional span.

\tzpsection{Canonical Equation}
\[
\eta(\omega)
=
\omega^{-\beta} e^{-\omega/\omega_{0}}
\]
\[
\omega_{0} = \omega_{0}(u_{T}),
\qquad
\beta = \beta(S_{\mathrm{HD}})
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\omega$: angular frequency term in the source equation.
    \item $\omega_{0}$: angular frequency term in the source equation.
    \item $u_{T}$: source equation symbol.
    \item $T$: source equation symbol.
    \item $S_{\mathrm{HD}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0015 generated source Wolfram model *)
ClearAll[K0015, Cr0015, T, R, A, W, I, N];
eq0015$1 = HoldForm[eta[omega] == 1/(omega^beta*e^(omega/omega0))];
eq0015$2 = HoldForm[TZPSequence[omega0 == omega0[uT], beta == beta[SHD]]];
eq0015$3 = HoldForm[omega^(-beta)];
eq0015$4 = HoldForm[e^(-omega/omega0)];

K0015 = HoldForm[{eq0015$1, eq0015$2, eq0015$3, eq0015$4}];

N = "normalized TRAWIN closure object for Spectral Density Index (TZP-Weighted)";
I = "TZP-Weighted Spectral Index integration/comparison layer";
W = "Exponential Ultraviolet Cutoff wave or operator carrier";
A = "Power-Law Spectral Weight admissible action/amplitude condition";
R = "Exponential Ultraviolet Cutoff rotation/curl preservation layer";
T = "Power-Law Spectral Weight local source condition";

Cr0015[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0015 = Cr0015[K0015];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Power-Law Spectral Weight local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Exponential Ultraviolet Cutoff rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Power-Law Spectral Weight admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Exponential Ultraviolet Cutoff wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TZP-Weighted Spectral Index integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Spectral Density Index (TZP-Weighted).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0015] Spectral Density Index (TZP-Weighted)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\eta(\omega)
=
\omega^{-\beta}
e^{-\omega/\omega_0}.
\end{equation}

\paragraph{Primary Derivation.}
Let $\omega$ be a frequency variable and let $\omega_0$ be the characteristic cutoff frequency determined by the Trawin base unit.

A scale-sensitive spectral law begins with a power term:

\begin{equation}
\omega^{-\beta},
\end{equation}

where $\beta$ controls low-frequency or scale-weighted behavior.

To suppress high-frequency divergence, introduce the exponential cutoff:

\begin{equation}
e^{-\omega/\omega_0}.
\end{equation}

Multiplying the two factors gives the TZP-weighted spectral density index:

\begin{equation}
\boxed{
\eta(\omega)
=
\omega^{-\beta}
e^{-\omega/\omega_0}.
}
\end{equation}

\paragraph{Interpretation.}
$\eta(\omega)$ weights frequency contributions by combining power-law scaling with exponential cutoff suppression.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Spectral Density Index (TZP-Weighted) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Power-Law Spectral Weight}\par
\[
\omega^{-\beta}
\]
\noindent This sets the large-scale shape of the spectrum and controls how strongly lower frequencies are favored.\par
\noindent\textbf{2. Exponential Ultraviolet Cutoff}\par
\[
e^{-\omega/\omega_{0}}
\]
\noindent This inserts the characteristic-frequency suppression that keeps the spectrum from remaining scale-free at high frequency.\par
\noindent\textbf{3. TZP-Weighted Spectral Index}\par
\[
\eta(\omega)
=
\omega^{-\beta} e^{-\omega/\omega_{0}}
\]
\noindent This closes the progression by combining scaling and cutoff into one spectral weighting law tied to the Trawin base unit and hyper-dimensional span.\par

\clearpage
\noindent\textbf{[ID 0015] Spectral Density Index (TZP-Weighted)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Spectral Density Index (TZP-Weighted) is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The spectral density index is defined by eta(omega)=omega to the power -beta e to the power -omega/omega sub 0 , where omega sub 0 is a characteristic frequency fixed by u sub T and beta is a dimensionless exponent determined by the hyper-dimensional span. \textbf{Contextual meaning:} The entry reads Spectral Density Index (TZP-Weighted) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Power-Law Spectral Weight; Exponential Ultraviolet Cutoff; TZP-Weighted Spectral Index.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
() weights frequency contributions by combining power-law scaling with exponential cutoff suppression.

\tzpsection{Equation Grounding}
Equation anchors: The spectral density index eta(omega)eta(omega)eta(omega) is defined as eta(omega)=omega-beta e-omega/omega 0eta(omega)=omegatextsuperscript -beta textbackslash,e -omega/omegatextbackslash 0 eta(omega)=omega-betae-omega/omega 0, where omega 0omegatextbackslash 0omega 0 is a characteristic frequency determined by TrawinBase and beta is a dimensionless exponent that depends on the hyper-dimensional span. The spectral density index eta(omega)eta(omega)eta(omega) is defined as eta(omega)=omega-beta e-omega/omega 0eta(omega)=omegatextsuperscript -beta textbackslash,e -omega/omegatextbackslash 0 eta(omega)=omega-betae-omega/omega 0, where omega 0omegatextbackslash 0omega 0 is a characteristic frequency determined by TrawinBase and beta is a dimensionless exponent that depends on the hyper-dimensional span.

\tzpsection{Interpretive Role}
This index controls how singular corrections reweight spectral content across scales. It becomes a practical input for noise models, fluctuation spectra, and any later renormalization flow that depends on frequency distribution.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Spectral Concentration Field Index Tzp Weighted}: nearby spectral language for modes, resonant structure, and admissible oscillation.
\item \textbf{Concentration Field Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Concentration Field Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0015]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0015_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0015] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Spectral Density Index (TZP-Weighted)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the spectral density index is defined by ()=\textasciicircum{}-e\textasciicircum{}-/\_0, where \_0 is a characteristic
frequency fixed by u\_T and  is a dimensionless exponent...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Spectral Density Index (TZP-Weighted) is valid as a spectral relation when frequency,
phase, and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0015_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
