\section*{ID9349: Definition of 𝐹}
\paragraph{Metadata.}
PiID: 6003727983940 | RTEID: RTE:P36304.2432:T3.2696 | UUID: 12160ebd-318f-5762-bbd0-011ebdd365a3

\paragraph{Canonical Statement.}
for [ID 0174] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0173], [ID 0161] Node registry\_id\_0174 Support Titles Curvature Form; Field Strength Tensor; Covariant Commutator Test Handle If the commutator vanishes where the connection is declared nontrivial, the curvature statement fails. Canonical Equation Links \$𝐹=𝑑𝐴+𝐴∧𝐴\$ [𝐷𝜇 ,𝐷𝜈 ]=𝐹𝜇𝜈 NormalizeTRAWIN(𝐹, [𝐷𝜇 ,𝐷𝜈 ],curvature) [ID 0175] Holonomy and Closed Loops TZPID ID0175 UUID f0e85c64-af01-48c5-aa00-715bddee7873 Type Loop Statement Scale geometric LOC Classification Working routing: QA612.6 fiber bundles; QC topology and gauge arXiv Classification Primary: math.DG; Cross-list: math-ph, hep-th Canonical Statement Holonomy records what a connection does after tran

\paragraph{Canonical Equation.}
\[
𝐹=𝑑𝐴+𝐴∧𝐴
\]

\paragraph{Dictionary.}
Definition of 𝐹 — 𝐹=𝑑𝐴+𝐴∧𝐴

\paragraph{Encyclopedia.}
Definition of 𝐹 is an algebraic definition, written 𝐹=𝑑𝐴+𝐴∧𝐴. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
