\tzpanchor{0782}
\tzpentryheader{0782}{WEYL CURVATURE NORMALIZATION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e3b91f5b-cc6d-508d-9802-0f541800d461}}\\
\textbf{PiID} & \tzpcode{9731732816096} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{789}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2997.8474 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.9395 rad}\\
\textbf{TZPID} & \tzpcode{ID0782} & \textbf{Node Dependencies}\quad \tzpidref{0781}\\
\textbf{Registry} & \tzpcode{registry\_id\_0782} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Weyl Curvature & Normalization Map\\
\textbf{Closure Support} & Closure Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records weyl curvature normalization through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0782}}:\mathcal{X}_{\mathrm{id0782}}\longrightarrow\mathcal{Y}_{\mathrm{id0782}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0782}})=\mathcal{O}_{\mathrm{id0782}}
\]
\[
\mathcal{O}_{\mathrm{id0782}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0782}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0782}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0782}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0782 generated source Wolfram model *)
ClearAll[K0782, Cr0782, T, R, A, W, I, N];
eq0782$1 = HoldForm[Oid0782[Xid0782] -> Yid0782];
eq0782$2 = HoldForm[NTRAWIN[OId0782] == OId0782];
eq0782$3 = HoldForm[Element[OId0782[x], YAdm]];

K0782 = HoldForm[{eq0782$1, eq0782$2, eq0782$3}];

N = "normalized TRAWIN closure object for WEYL CURVATURE NORMALIZATION";
I = "WEYL CURVATURE NORMALIZATION integration/comparison layer";
W = "WEYL CURVATURE NORMALIZATION wave or operator carrier";
A = "WEYL CURVATURE NORMALIZATION admissible action/amplitude condition";
R = "WEYL CURVATURE NORMALIZATION rotation/curl preservation layer";
T = "WEYL CURVATURE NORMALIZATION local source condition";

Cr0782[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0782 = Cr0782[K0782];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ WEYL CURVATURE NORMALIZATION local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ WEYL CURVATURE NORMALIZATION rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ WEYL CURVATURE NORMALIZATION admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ WEYL CURVATURE NORMALIZATION wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ WEYL CURVATURE NORMALIZATION integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for WEYL CURVATURE NORMALIZATION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0782] WEYL CURVATURE NORMALIZATION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0782}}:\mathcal{X}_{\mathrm{id0782}}\longrightarrow\mathcal{Y}_{\mathrm{id0782}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0782}})=\mathcal{O}_{\mathrm{id0782}}
\]
\[
\mathcal{O}_{\mathrm{id0782}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
This condition \( \mathcal{O}_{\mathrm{id0782}}:\mathcal{X}_{\mathrm{id0782}}\longrightarrow\mathcal{Y}_{\mathrm{id0782}} \) enforces a normalization. It sets the quantity to a fixed value away from special points and introduces a delta-function source at those points, ensuring that the integral of the quantity equals the specified constant.
\paragraph{Equation Type.}
This statement is classified as a normalization relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. In the TRAWIN reading, the equation functions as the normalized carrier for the entry’s information content. In CHL terms, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors WEYL CURVATURE NORMALIZATION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0782}}:\mathcal{X}_{\mathrm{id0782}}\longrightarrow\mathcal{Y}_{\mathrm{id0782}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0782}})=\mathcal{O}_{\mathrm{id0782}}
\]
\[
\mathcal{O}_{\mathrm{id0782}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0782] WEYL CURVATURE NORMALIZATION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
WEYL CURVATURE NORMALIZATION is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} mathcal H GR = frac hbar to the power 2 2m eff C sub munurhosigma otimes psi. \textbf{Contextual meaning:} The entry reads WEYL CURVATURE NORMALIZATION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states a clean curvature-normalization chain instead of relying on malformed imported operator composition. \textbf{Lemma support:} Weyl Curvature; Normalization Map; Closure Condition.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, WEYL CURVATURE NORMALIZATION is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: mathcal F : Quantum sub infinity to Gravity sub infinity; eta: id Rightarrow F compose G; and rho sub vac (r) similar to sum sub n=0 to the power infinity (-1) to the power n Gamma(n+tfrac 1 2 ) K sub n(|r-r sub TZP |/xi). Proof route: show that the normalized Weyl observable follows from the stated curvature contraction and remains admissible. Formalization route: prove that the normalized Weyl curvature observable satisfies the stated closure condition.

\tzpsection{Interpretive Role}
The entry now states a clean curvature-normalization chain instead of relying on malformed imported operator composition.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Conformal Spacetime Scaling}: The mathematical trick of zooming in or out on the universe to ignore the overall expansion and focus purely on the local twisting and shearing of gravity.
\item \textbf{Traceless Gravitational Tensors}: The isolation of the specific parts of Einstein's equations that describe tidal forces--the stretching of objects--rather than the overall volume changes.
\item \textbf{Metric Distortion Benchmarking}: The process of taking the wild, terrifying relativistic math and forcing it to sit neatly on a scale from 0 to 1 so the engineers can actually read the dials.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0782]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0782].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0782] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont WEYL CURVATURE NORMALIZATION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} WEYL CURVATURE NORMALIZATION is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``WEYL CURVATURE NORMALIZATION is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0782].
\par\endgroup
\vfill
\endgroup
\endgroup
