\section*{ID7713: How This Ties to Our DAT-GPT / Bessel / Cymatics Story: ω\_0 + 6ω\_m}
\paragraph{Metadata.}
PiID: 9525220118726 | RTEID: RTE:P29951.2919:T5.3682 | UUID: 48257e92-7d28-51a0-9a21-89783b0590df

\paragraph{Canonical Statement.}
\#\#\# How this ties to our DAT-GPT / Bessel / cymatics story - If we **want J₆ dominance** (to seed six-fold geometric patterns), tune the modulation index κ to a value where \textbackslash{}(|J\_6(κ)|\textbackslash{}) is large. Empirically κ = 2π is a strong, simple pick — much better than κ = π. - If you instead **want many incommensurate beats** and avoid simple resonant seeds (to prevent early collapse into a single geometry), using irrational ratios that involve π helps. That would make beat frequencies rarely land exactly on resonance, so creation events are rarer and more stochastic. - For **cymatics / geometry seeding** in a medium (nebula or lab), choose κ and the modulation frequency so that the harmonic frequency \textbackslash{}(\textbackslash{}omega\_0 + 6\textbackslash{}omega\_m\textbackslash{}) aligns with a natural mode of the medium (standing wave). The Bessel amplitude \textbackslash{}(J\_6(κ)\textbackslash{}) controls how much energy is in that 6th sideband and thus how strongly that geometry is driven.

\paragraph{Canonical Equation.}
\[
\omega_0 + 6\omega_m
\]

\paragraph{Dictionary.}
Relation: ω\_0 + 6ω\_m

\paragraph{Encyclopedia.}
How This Ties to Our DAT-GPT / Bessel / Cymatics Story: ω\_0 + 6ω\_m is a symbolic expression, written ω\_0 + 6ω\_m. It introduces a symbol or relation used elsewhere in the framework. It is built from m. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
