\section*{ID8897: ROUND-TRIP FIDELITY METRIC Canonical Statutory Formula: F\_RT}
\paragraph{Metadata.}
PiID: 0179289647669 | RTEID: RTE:P34549.0268:T0.3775 | UUID: 2b3fd09d-8fb1-56d8-947d-ccedec7eb1da

\paragraph{Canonical Statement.}
[ID 966] ROUND-TRIP FIDELITY METRIC Canonical Statutory Formula: \$F\_\{RT\} = |\textbackslash{}langle \textbackslash{}psi\_\{in\} | \textbackslash{}mathcal\{D\}(\textbackslash{}mathcal\{E\}(\textbackslash{}psi\_\{in\})) \textbackslash{}rangle|\textasciicircum{}2 > 0.999999\$ Formal Technical Dissertation: Sets the operational threshold for signal integrity. The system guarantees that a state subjected to the full encoding (\$\textbackslash{}mathcal\{E\}\$) and decoding (\$\textbackslash{}mathcal\{D\}\$) cycle retains a fidelity greater than 99.9999\% compared to the original input state. Source: [2]

\paragraph{Canonical Equation.}
\[
F_{RT} = |\langle \psi_{in} | \mathcal{D}(\mathcal{E}(\psi_{in})) \rangle|^2 > 0.999999
\]

\paragraph{Dictionary.}
ROUND-TRIP FIDELITY METRIC Canonical Statutory Formula: \$F\_RT = \_in D(E( \_in)) \textasciicircum{}2 0.999999\$ Formal Technical Dissertation: Sets the operational threshold for signal integrity.

\paragraph{Encyclopedia.}
ROUND-TRIP FIDELITY METRIC Canonical Statutory Formula: F\_RT is an expectation / trace over state, written F\_RT = |⟨ ψ\_in | D(E(ψ\_in)) ⟩|\textasciicircum{}2 > 0.999999. It is computed as an expectation value or trace over a quantum state, producing an observable. It is built from n, D, E, defining F\_RT. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
