\tzpanchor{0104}
\tzpentryheader{0104}{Holographic Information Projection}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{27639270-db1d-5ad8-a84f-dcd2252fe2c2}}\\
\textbf{PiID} & \tzpcode{8086513282306} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{111}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{403.8551 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.6654 rad}\\
\textbf{TZPID} & \tzpcode{ID0104} & \textbf{Node Dependencies}\quad \tzpidref{0103}\\
\textbf{Registry} & \tzpcode{registry\_id\_0104} & \textbf{Scale}\quad bulk-boundary information transfer\\
\textbf{LOC Classification} & QC174.17 quantum field structure & QA315 variational and integral methods\\
\textbf{arXiv Classification} & Primary: hep-th \quad Cross-list: quant-ph, math-ph & \\
\textbf{Primary Support} & Entropy-Area Law & Encoding Map\\
\textbf{Closure Support} & Boundary Reconstruction & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Information in the bulk of a space can be faithfully represented on its lower-dimensional boundary.

\tzpsection{Canonical Equation}
\[
S_A = \frac{\operatorname{Area}(\gamma_A)}{4 G_N}
\]
\[
\mathcal{O}_{\mathrm{bulk}}(x)=\int K(x,y)\,\mathcal{O}_{\mathrm{bdy}}(y)\,dy
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S_A$: source equation symbol.
    \item $\gamma_A$: source equation symbol.
    \item $G_N$: source equation symbol.
    \item $\mathcal{O}_{\mathrm{bulk}}(x)$: source equation symbol.
    \item $K$: source equation symbol.
    \item $\mathcal{O}_{\mathrm{bdy}}(y)$: source equation symbol.
    \item $U_{\mathrm{enc}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0104 generated source Wolfram model *)
ClearAll[K0104, Cr0104, T, R, A, W, I, N];
eq0104$1 = HoldForm[SA == Area[gammaA]/(4*GN)];
eq0104$2 = HoldForm[OBulk[x] == Integral*K[x, y]*OBdy[y]*dy];
eq0104$3 = HoldForm[Uenc[lvertlogicalrangle] -> lvertphysicalrangle];

K0104 = HoldForm[{eq0104$1, eq0104$2, eq0104$3}];

N = "normalized TRAWIN closure object for Holographic Information Projection";
I = "Boundary Reconstruction integration/comparison layer";
W = "Encoding Map wave or operator carrier";
A = "Entropy-Area Law admissible action/amplitude condition";
R = "Encoding Map rotation/curl preservation layer";
T = "Entropy-Area Law local source condition";

Cr0104[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0104 = Cr0104[K0104];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Entropy-Area Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Encoding Map rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Entropy-Area Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Encoding Map wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Boundary Reconstruction integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Holographic Information Projection.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0104] Holographic Information Projection}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
S_A = \frac{\operatorname{Area}(\gamma_A)}{4 G_N}
\]
\[
\mathcal{O}_{\mathrm{bulk}}(x)=\int K(x,y)\,\mathcal{O}_{\mathrm{bdy}}(y)\,dy
\]

\paragraph{Primary Derivation.}
The expression \( S_A = \frac{\operatorname{Area}(\gamma_A)}{4 G_N} \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. Interpreted through TRAWIN, the equation functions as the integral carrier for the entry’s information content. In CHL terms, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Holographic Information Projection by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Entropy-Area Law}\par
\[
S_A = \frac{\operatorname{Area}(\gamma_A)}{4 G_N}
\]
\noindent This identifies the first projection invariant by converting bulk geometry into boundary entropy.\par
\noindent\textbf{2. Encoding Map}\par
\[
U_{\mathrm{enc}} : \lvert \mathrm{logical}\rangle \mapsto \lvert \mathrm{physical}\rangle
\]
\noindent This inserts protected information storage so the projection does not erase logical structure.\par
\noindent\textbf{3. Boundary Reconstruction}\par
\[
\mathcal{O}_{\mathrm{bulk}}(x)=\int K(x,y)\,\mathcal{O}_{\mathrm{bdy}}(y)\,dy
\]
\noindent This closes the progression by showing how bulk observables are recovered from projected data.\par

\clearpage
\noindent\textbf{[ID 0104] Holographic Information Projection}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Holographic Information Projection is a Operator. The holographic projection is defined as an association of three components: (1) Bulk--boundary correspondence governed by the Ryu--Takayanagi relation S\_A = min[Area( \_A)/(4 G\_N)]; (2) Quantum error correction, where logical information encoded in bulk states is protected by an encoding map U\_encoding: |logical  to |physical ; and (3) Wedge reconstruction, expressed as O\_bulk(x) =   M\_K(x,y) O\_boundary(y) dy.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The holographic projection is defined as an association of three components: (1) Bulk--boundary correspondence governed by the Ryu--Takayanagi relation S\_A = min[Area( \_A)/(4 G\_N)]; (2) Quantum error correction, where logical information encoded in bulk states is protected by an encoding map U\_encoding: |logical  to |physical ; and (3) Wedge reconstruction, expressed as O\_bulk(x) =   M\_K(x,y) O\_boundary(y) dy.
\textbf{Contextual meaning:} Information in the bulk of a space can be faithfully represented on its lower dimensional boundary. The projection includes built in error correction and an explicit formula for reconstructing bulk observables from boundary data.
\textbf{Derivable consequences:} Area law for entanglement; entanglement wedge reconstruction; bridge to quantum gravity; error c
\textbf{Lemma support:} The holographic projection is defined as an association of three components: (1) Bulk--boundary correspondence governed by the Ryu--Takayanagi relation S\_A = min[Area( \_A)/(4 G\_N)]; (2) Quantum error correction, where logical information encoded in bulk states is protected by an encoding map U\_encoding: |logical  to |physical ; and (3) Wedge reconstruction, expressed as O\_bulk(x) =   M\_K(x,y) O\_boundary(y) dy.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Observe physical systems exhibiting Hopf links (for example linked vortices or spin textures) and test whether they mirror predicted energy--information cycles. ID 104: Holographic Information Projection

\tzpsection{Equation Grounding}
The holographic projection is defined as an association of three components: (1) Bulk--boundary correspondence governed by the Ryu--Takayanagi relation S\_A = min[Area( \_A)/(4 G\_N)]; (2) Quantum error correction, where logical information encoded in bulk states is protected by an encoding map U\_encoding: |logical  to |physical ; and (3) Wedge reconstruction, expressed as O\_bulk(x) =   M\_K(x,y) O\_boundary(y) dy.

\tzpsection{Interpretive Role}
Information in the bulk of a space can be faithfully represented on its lower dimensional boundary. The projection includes built in error correction and an explicit formula for reconstructing bulk observables from boundary data.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Entropy-Area Law}: The first projection invariant converting bulk geometry into boundary entropy.
\item \textbf{Encoding Map}: The insertion of protected information storage so the projection does not erase logical structure.
\item \textbf{Boundary Reconstruction}: The recovery of bulk observables from projected data.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0104]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0104_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0104] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Holographic Information Projection}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} information in the bulk of a space can be faithfully represented on its lower-
dimensional boundary

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Holographic Information Projection is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0104_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
