\tzpanchor{0043}
\tzpentryheader{0043}{Helicity Linking Number Universality}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{3f955b8c-e2c2-51a0-ad7c-ed0cda376010}}\\
\textbf{PiID} & \tzpcode{9937510582097} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{50}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{166.9785 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.2751 rad}\\
\textbf{TZPID} & \tzpcode{ID0043} & \textbf{Node Dependencies}\quad \tzpidref{0041}\\
\textbf{Registry} & \tzpcode{registry\_id\_0043} & \textbf{Scale}\quad linking-topological\\
\textbf{LOC Classification} & QA612.2 linking invariants & QC809 magnetic topology\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: physics.plasm-ph, astro-ph.SR & \\
\textbf{Primary Support} & Pairwise Curve Data & Gauss Linking Integral\\
\textbf{Closure Support} & Integer Universality & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The linking number between magnetic structures is universally quantised.

\tzpsection{Canonical Equation}
\[
\operatorname{Lk}(C_{1},C_{2})
=
\frac{1}{4\pi}
\oint_{C_{1}}\oint_{C_{2}}
\frac{(\mathbf{r}_{1}-\mathbf{r}_{2})\cdot
\left(d\mathbf{r}_{1}\times d\mathbf{r}_{2}\right)}
{\lvert \mathbf{r}_{1}-\mathbf{r}_{2} \rvert^{3}}
\]
\[
\operatorname{Lk}(C_{1},C_{2}) \in \mathbb{Z}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $C_{1}$: source equation symbol.
    \item $C_{2}$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $Z$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0043 generated source Wolfram model *)
ClearAll[K0043, Cr0043, T, R, A, W, I, N];
eq0043$1 = HoldForm[Lk[C1, C2] == (1/(4*Pi))*ContourIntegralC1*ContourIntegralC2[((r1 - r2)*(dr1*dr2))/Abs[r1 - r2]^3]];
eq0043$2 = HoldForm[Element[Lk[C1, C2], Z]];
eq0043$3 = HoldForm[Pair[C1, C2]];

K0043 = HoldForm[{eq0043$1, eq0043$2, eq0043$3}];

N = "normalized TRAWIN closure object for Helicity Linking Number Universality";
I = "Integer Universality integration/comparison layer";
W = "Gauss Linking Integral wave or operator carrier";
A = "Pairwise Curve Data admissible action/amplitude condition";
R = "Gauss Linking Integral rotation/curl preservation layer";
T = "Pairwise Curve Data local source condition";

Cr0043[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0043 = Cr0043[K0043];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Pairwise Curve Data local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Gauss Linking Integral rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Pairwise Curve Data admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Gauss Linking Integral wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Integer Universality integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Helicity Linking Number Universality.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0043] Helicity Linking Number Universality}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
Lk
=
\frac{1}{4\pi}
\oint_{C_1}
\oint_{C_2}
\frac{
(\mathbf{r}_1-\mathbf{r}_2)
\cdot
(\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2)
}{
|\mathbf{r}_1-\mathbf{r}_2|^3
}.
\end{equation}

\paragraph{Primary Derivation.}
Let $C_1$ and $C_2$ be two closed magnetic flux tubes or field-line loops.  
The Gauss linking integral measures how many times the two loops wind around one another.

For points $\mathbf{r}_1\in C_1$ and $\mathbf{r}_2\in C_2$, the relative displacement is:

\begin{equation}
\mathbf{r}_1-\mathbf{r}_2 .
\end{equation}

The oriented area element generated by the two path differentials is:

\begin{equation}
\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2 .
\end{equation}

Normalizing by the cubic separation gives the universal linking density:

\begin{equation}
\frac{
(\mathbf{r}_1-\mathbf{r}_2)
\cdot
(\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2)
}{
|\mathbf{r}_1-\mathbf{r}_2|^3
}.
\end{equation}

The full linking number is:

\begin{equation}
\boxed{
Lk
=
\frac{1}{4\pi}
\oint_{C_1}
\oint_{C_2}
\frac{
(\mathbf{r}_1-\mathbf{r}_2)
\cdot
(\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2)
}{
|\mathbf{r}_1-\mathbf{r}_2|^3
}.
}
\end{equation}

\paragraph{Interpretation.}
The linking number is integer-valued and topologically stable. It supplies the universal counting rule behind helicity quantisation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Helicity Linking Number Universality by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Pairwise Curve Data}\par
\[
(C_{1}, C_{2})
\]
\noindent This specifies the two oriented flux-tube cores whose linkage is being measured.\par
\noindent\textbf{2. Gauss Linking Integral}\par
\[
\operatorname{Lk}(C_{1},C_{2})
=
\frac{1}{4\pi}
\oint_{C_{1}}\oint_{C_{2}}
\frac{(\mathbf{r}_{1}-\mathbf{r}_{2})\cdot
\left(d\mathbf{r}_{1}\times d\mathbf{r}_{2}\right)}
{\lvert \mathbf{r}_{1}-\mathbf{r}_{2} \rvert^{3}}
\]
\noindent This computes the linking number directly from the geometry of the two curves.\par
\noindent\textbf{3. Integer Universality}\par
\[
\operatorname{Lk}(C_{1},C_{2}) \in \mathbb{Z}
\]
\noindent This closes the progression by showing that the result is an invariant topological class rather than a continuously drifting measurement.\par

\clearpage
\noindent\textbf{[ID 0043] Helicity Linking Number Universality}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Helicity Linking Number Universality is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The linking number between magnetic structures is universally quantised. \textbf{Contextual meaning:} The entry reads Helicity Linking Number Universality as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry is the discrete counterpart to the helicity constraint. It turns continuous field linkage into an integer topological invariant and therefore stabilizes the meaning of magnetic knotting across scales and boundary realizations. \textbf{Lemma support:} Pairwise Curve Data; Gauss Linking Integral; Integer Universality.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The linking number is integer-valued and topologically stable. It supplies the universal counting rule behind helicity quantisation.

\tzpsection{Equation Grounding}
Equation anchors: The linking number LkLkLk between two magnetic flux tubes in a Trawinistic manifold is given by Lk=14pi C1 C2(r1-r2) (dr1times dr2) r1-r2 3Lk = ratio 1 4textbackslash pi textbackslash oint C 1 textbackslash oint C 2 ratio (textbackslash mathbf r 1-textbackslash mathbf r 2)dot( d textbackslash mathbf r 1times d textbackslash mathbf r 2) textbartextbackslash mathbf r 1-textbackslash mathbf r 2textbar to the power 3 Lk=4pi1 C1 C2 r1-r2 3(r1-r2) (dr1times dr2) and is restricted to integer values. This integer is independent of system scale and boundary conditions. The linking number LkLkLk between two magnetic flux tubes in a Trawinistic manifold is given by Lk=14pi C1 C2(r1-r2) (dr1times dr2) r1-r2 3Lk = ratio 1 4textbackslash pi textbackslash oint C 1 textbackslash oint C 2 ratio (textbackslash mathbf r 1-textbackslash mathbf r 2)dot( d textbackslash mathbf r 1times d textbackslash mathbf r 2) textbartextbackslash mathbf r 1-textbackslash mathbf r 2textbar to the power 3 Lk=4pi1 C1 C2 r1-r2 3(r1-r2) (dr1times dr2) and is restricted to integer values. This integer is independent of system scale and boundary conditions.

\tzpsection{Interpretive Role}
This entry is the discrete counterpart to the helicity constraint. It turns continuous field linkage into an integer topological invariant and therefore stabilizes the meaning of magnetic knotting across scales and boundary realizations.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Twist Linkage Linking Number Universality}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Twist Linkage Rotating-Field Analogue}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\item \textbf{Twist Linkage Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0043]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0043_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0043] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Helicity Linking Number Universality}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the linking number between magnetic structures is universally quantised

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Helicity Linking Number Universality is valid when the stated geometric or topological
relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0043_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
