\section*{ID9479: Definition of Φ}
\paragraph{Metadata.}
PiID: 2124247014121 | RTEID: RTE:P36809.0621:T4.1013 | UUID: 12ff1c14-736e-55ce-bc16-ed4b0ce6692a

\paragraph{Canonical Statement.}
for [ID 0273] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0272], [ID 0200] Node registry\_id\_0273 Support Titles Variation Law; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links \$Φ=𝑛Φ0=𝑛\$ ℎ \$2𝑒≈𝑛×2.07×10−15\$ Wb 𝑆= |𝐸 (𝜃1 , 𝜃2 )−𝐸 (𝜃1 , 𝜃 ′ 2 ) |+|𝐸 (𝜃 ′1 , 𝜃2 )+𝐸 (𝜃 ′1 , 𝜃 ′ 2 ) |>2 log10 ( 𝜇 𝑀𝑅2𝜔 ) =−16 [ID 0274] Elsasser Universality Support TZPID ID0274 UUID a34868f5-991b-56b8-b896-8ee7858bd925 Type Field / Transport Statement Scale magnetofluid LOC Classification Working routing: QC809 magnetohydrodynamics; QC6 fluid and plasma dynamics arXiv Classification Primary: physics.p

\paragraph{Canonical Equation.}
\[
Φ=𝑛Φ0=𝑛
\]

\paragraph{Dictionary.}
Definition of Φ — Φ=𝑛Φ0=𝑛

\paragraph{Encyclopedia.}
Definition of Φ is an algebraic definition, written Φ=𝑛Φ0=𝑛. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
