\section*{ID9198: Definition of Zr:det(J)}
\paragraph{Metadata.}
PiID: 2869222103274 | RTEID: RTE:P35717.8767:T2.3034 | UUID: 54b7c0e8-4ae7-5dc4-b2a9-61161f3d3f6d

\paragraph{Canonical Statement.}
ability / Test Handle: Absence of any sign of superluminal or nonlocal signalling in controlled experiments would falsify this entry. Canonical Registry Vol. 01 59 Trawin Zero Point Contextus Canonicus 2 TZP CANONICAL REGISTRY – ENTRIES 150–199 2.0.27 ID 176: Convergence Locus Equation Type: Structural Constraint Formal Statement: The convergence locus of unified interactions is the set \$\{r:det(J)=0∧π1(M\{r\})∼=Z×\$ Z\}\{r : \textbackslash{}det(J) = 0 \textbackslash{}wedge \textbackslash{}pi\_1(\textbackslash{}mathcal\{M\}\textbackslash{}setminus\{r\}) \textbackslash{}cong \textbackslash{}mathbb\{Z\} \textbackslash{}times \$\textbackslash{}mathbb\{Z\}\}\{r:det(J)=0∧π1(M\{r\})∼=Z×\$ Z\}. Interpretive Meaning: This equation defines the unique geometric points where the topology changes and the TZP is realized; the vanishing Jacobian indicates a degeneracy, and the doubleloop fundamental group identifies the lemniscate structure. Dependencies: ID 168 Derivable Consequences: Identifies the coordinate of the TZP; predicts that only one such point exists per cycle; guides geometry

\paragraph{Canonical Equation.}
\[
\mathbb{Z}}{r:det(J)=0∧π1(M{r})∼=Z×
\]

\paragraph{Dictionary.}
Definition of Zr:det(J) — Zr:det(J)=0∧π1(Mr)∼=Z×

\paragraph{Encyclopedia.}
Definition of Zr:det(J) is an algebraic definition, written Zr:det(J)=0∧π1(Mr)∼=Z×. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from M, r, Z, defining Zr:det(J). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
