\section*{ID9263: Definition of Ψ(r,t)}
\paragraph{Metadata.}
PiID: 8837781423356 | RTEID: RTE:P35970.2861:T2.7193 | UUID: 96dca7e5-ddff-56a0-a1a1-376ab57a7d41

\paragraph{Canonical Statement.}
inement devices. (2) Determines allowable field configurations for stable gyromagnetic vortices. (3) Ties the geometry of the torus to field strength ratios. Falsifiability / Test Handle: Evaluate safety factor profiles in experimental toroidal systems and verify that instabilities occur when qqq falls below the critical threshold. 2.0.178 ID 327: Quantum Vortex Circulation Quantization Type: Definition Formal Statement: In a superfluid or Bose–Einstein condensate, the macroscopic wavefunction \$Ψ(r,t)=n(r,t)ei(r,t)\textbackslash{}Psi(r,t)\$ = \textbackslash{}sqrt\{n(r,t)\} \$eˆ\{i\textbackslash{}phi(r,t)\}Ψ(r, t)\$ = \$n(r, t)ei(r, t)exhibitscirculationquantization\$ : \$vd\$ = \$2πn/m\textbackslash{}ointv\textbackslash{}cdotd\textbackslash{}ell\$ = \$2\textbackslash{}pi\textbackslash{}hbarn/mvd\$ = \$2πn/m,wherennnistheintegerwindingnumberandmmmthemassoftheconstituentparticle.\$ Interpretive Meaning: The circulation of the velocity field around a closed loop in a superfluid is quantized in units of \$2π/m2\textbackslash{}pi\textbackslash{}hbar/m2π/m.\$ This arises from the s

\paragraph{Canonical Equation.}
\[
Ψ(r,t)=n(r,t)ei(r,t)\Psi(r,t)
\]

\paragraph{Dictionary.}
Definition of Ψ(r,t) — Ψ(r,t)=n(r,t)ei(r,t)Ψ(r,t)

\paragraph{Encyclopedia.}
Definition of Ψ(r,t) is an algebraic definition, written Ψ(r,t)=n(r,t)ei(r,t)Ψ(r,t). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from Ψ, n, r, defining Ψ(r,t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
