\section*{ID8937: FEEDBACK STABILITY LYAPUNOV FUNCTION Canonical Statutory Formula: V[Φ]}
\paragraph{Metadata.}
PiID: 9627668440323 | RTEID: RTE:P34704.3557:T0.6334 | UUID: a705359f-26cb-53c0-b166-882273609f90

\paragraph{Canonical Statement.}
[ID 853] FEEDBACK STABILITY LYAPUNOV FUNCTION Canonical Statutory Formula: \$V[\textbackslash{}Phi] = ||\textbackslash{}Phi - \textbackslash{}Phi\_\{target\}||\textasciicircum{}2 \textbackslash{}implies \textbackslash{}sum (-D[V, t]) > 0\$ Formal Technical Dissertation: A categorical limit feedback loop ensures system stability. The Lyapunov function candidate \$V\$ measures the distance from the target cymatic field state. Stability is verified when the energy of the field remains below \$E\_\{critical\}\$ via a Barrier Certificate. Source: [9]

\paragraph{Canonical Equation.}
\[
V[\Phi] = ||\Phi - \Phi_{target}||^2 \implies \sum (-D[V, t]) > 0
\]

\paragraph{Dictionary.}
FEEDBACK STABILITY LYAPUNOV FUNCTION Canonical Statutory Formula: \$V[ ] = - \_target \textasciicircum{}2 (-D[V, t]) 0\$ Formal Technical Dissertation: A categorical limit feedback loop ensures system stability.

\paragraph{Encyclopedia.}
FEEDBACK STABILITY LYAPUNOV FUNCTION Canonical Statutory Formula: V[Φ] is a series / summation, written V[Φ] = ||Φ - Φ\_target||\textasciicircum{}2 ⟹ ∑ (-D[V, t]) > 0. It is expressed as a sum or series over modes or indices, superposing discrete contributions. It is built from Φ, a, r, g, D, V, defining V[Φ]. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
