\tzpanchor{0400}
\tzpentryheader{0400}{Cosmological Constant and Master Unification Equation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{895ad95b-a967-5f89-8cab-2927da8d5972}}\\
\textbf{PiID} & \tzpcode{3305727036575} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{407}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1553.2888 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.5593 rad}\\
\textbf{TZPID} & \tzpcode{ID0400} & \textbf{Node Dependencies}\quad \tzpidref{0399}\\
\textbf{Registry} & \tzpcode{registry\_id\_0400} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Residual Vacuum Density & Frequency Susceptibility\\
\textbf{Closure Support} & Magneto-Acoustic Dispersion & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 400 establishes the cosmological constant and master unification equation as the handoff from TZP vacuum pressure residue into the registry's metric and stress energy chain. In this entry, Lambda is treated as an emergent residual vacuum pressure after topological equilibration at the Trawin Zero Point; the equation chain regularizes vacuum density against global topological and information constraints, leaving a small positive state pressure. It prepares ID 401, where the electromagnetic stress energy tensor converts that residue into momentum flux.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\rho_{\Lambda}=\frac{\hbar c}{R^4}\,\frac{\Phi_0}{\Phi_{\mathrm{total}}}\sim H_0^2\approx6\times10^{-10}\,\mathrm{J\,m^{-3}}
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\rho_{\Lambda}$: residual vacuum density associated with the cosmological constant.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
    \item $c$: speed of light or relativistic conversion factor.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\Phi_0$: reference zero-point flux or normalization flux.
    \item $\Phi_{\mathrm{total}}$: total flux or information-normalization denominator.
    \item $H_0$: Hubble-scale or global comparison parameter.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0400 generated source Wolfram model *)
ClearAll[K0400, Cr0400, T, R, A, W, I, N];
eq0400$1 = HoldForm[$rhoLambda == ((hbar*c)/R^4)*(Phi0/PhiTotal)*sim*H0^2 == (6*mathrm[J/m^3]*$)/10^10];

K0400 = HoldForm[{eq0400$1}];

N = "6*10^-10 Joule/Meter^3 normalized density";
I = "H0^2 global integration/comparison scale";
W = "(hbar*c/R^4) wave-density carrier";
A = "Phi0/PhiTotal admissible flux ratio";
R = "global radius/topological circulation scale";
T = "local residual vacuum pressure";

Cr0400[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0400 = Cr0400[K0400];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ local residual vacuum pressure.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ global radius/topological circulation scale.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Phi0/PhiTotal admissible flux ratio.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ (hbar*c/R\textasciicircum{}4) wave-density carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ H0\textasciicircum{}2 global integration/comparison scale.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ 6*10\textasciicircum{}-10 Joule/Meter\textasciicircum{}3 normalized density.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0400] Cosmological Constant and Master Unification Equation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\rho_{\Lambda}=\frac{\hbar c}{R^4}\,\frac{\Phi_0}{\Phi_{\mathrm{total}}}\sim H_0^2\approx6\times10^{-10}\,\mathrm{J\,m^{-3}}
$
\end{adjustbox}
\]

\paragraph{Primary Derivation.}
One can verify the equality by employing standard algebraic manipulations. leading to the displayed result.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. Interpreted through TRAWIN, the equation functions as the generalized carrier for the entry’s information content. Under CHL, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Cosmological Constant and Master Unification Equation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\rho_{\Lambda}=\frac{\hbar c}{R^4}\,\frac{\Phi_0}{\Phi_{\mathrm{total}}}\sim H_0^2\approx6\times10^{-10}\,\mathrm{J\,m^{-3}}
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0400] Cosmological Constant and Master Unification Equation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Cosmological Constant and Master Unification Equation is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 400 establishes the cosmological constant and master unification equation as the handoff from TZP vacuum pressure residue into the registry's metric and stress energy chain. In this entry, Lambda is treated as an emergent residual vacuum pressure after topological equilibration at the Trawin Zero Point; the equation chain regularizes vacuum density against global topological and information constraints, leaving a small positive state pressure. It prepares ID 401, where the electromagnetic stress energy tensor converts that residue into momentum flux.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\rho_{\Lambda}=\frac{\hbar c}{R^4}\,\frac{\Phi_0}{\Phi_{\mathrm{total}}}\sim H_0^2\approx6\times10^{-10}\,\mathrm{J\,m^{-3}}
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 400 establishes the cosmological constant and master unification equation as the handoff from TZP vacuum pressure residue into the registry's metric and stress energy chain. In this entry, Lambda is treated as an emergent residual vacuum pressure after topological equilibration at the Trawin Zero Point; the equation chain regularizes vacuum density against global topological and information constraints, leaving a small positive state pressure. It prepares ID 401, where the electromagnetic stress energy tensor converts that residue into momentum flux.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Cosmological Constant and Master Unification Equation by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Cosmological Constant and Master Unification Equation; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0400]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0400_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0400] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Cosmological Constant and Master Unification Equation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the cosmological constant (Lambda) in the Trawin framework is an emergent scalar
representing the residual vacuum pressure after topological equili...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Cosmological Constant and Master Unification Equation is valid as a synchronization
criterion under the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0400_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
