\section*{ID9147: Relation: Σ T\_i(θ\_i, φ\_i)}
\paragraph{Metadata.}
PiID: 2989695946995 | RTEID: RTE:P35519.8323:T1.9771 | UUID: 8d3aa951-e82e-57f5-832d-8a1f598636b1

\paragraph{Canonical Statement.}
rtance of spin–orbit resonances; impetus for including dissipative terms; concept of local clusters. Falsifiability / Test Handle: Add realistic physical terms to the model and test whether coherence increases relative to the simple case. 1.0.21 ID 120: Planetary Spin–Orbit Oscillator Model Type: Operator Formal Statement: To model real planetary dynamics, augment the spinonly Kuramoto model with spin and orbital phases \$θ\_i\$ and \$φ\_i.\$ Evolution equations take the form dot \$θ\_i\$ = \$ω\_i\$ + \$Σ T\_i(θ\_i, φ\_i)\$ – D\_i ·dot \$θ\_i,\$ dot \$φ\_i\$ = Ω\_i + \$Σ G\_i(φ\_i, θ\_i)\$ – D’ i ·dot \$φ\_i,\$ where T\_i and G\_i represent tidal torques depending on phase differences and D\_i, D’ i are dissipative coefficients. Orbital distances a\_i(t) vary with time to capture elliptical orbit dynamics. Interpretive Meaning: This generalization incorporates spin–orbit coupling, tidal dissipation and timedependent orbital separat

\paragraph{Canonical Equation.}
\[
Σ T_i(θ_i, φ_i)
\]

\paragraph{Dictionary.}
Relation: Σ T\_i(θ\_i, φ\_i) — Σ T\_i(θ\_i, φ\_i)

\paragraph{Encyclopedia.}
Relation: Σ T\_i(θ\_i, φ\_i) is a symbolic expression, written Σ T\_i(θ\_i, φ\_i). It introduces a symbol or relation used elsewhere in the framework. It is built from T\_i. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
