\section*{ID8574: Definition of 2ζ(−1/2)}
\paragraph{Metadata.}
PiID: 9095170283529 | RTEID: RTE:P33294.7461:T4.5940 | UUID: 7287ed30-90f4-5b77-a060-e47b70fb88e0

\paragraph{Canonical Statement.}
DISSIPATION MODELING Canonical Statutory Formula: \$dρ dt \$ = − \$i \$ ℏ \$[Ĥ, ρ] \$ + \$∑\$ \$n γn \$ ( \$LnρL \$ † \$n \$ − 1 \$2\{L \$ † \$nLn, ρ\} \$ ) Formal Technical Dissertation: Models the non-unitary evolution of the system state. Jump operators \$Ln \$ ensure the system thermalizes cor-rectly with the bosonic bath while maintaining the coherence of the extracted energy. Source: [ID 1059] ZETA FUNCTION REGULARIZATION Canonical Statutory Formula: \$Evacuum \$ = −ℏ \$2ζ(−1/2) =⇒ \$ Finite \$Eextracted \$ Formal Technical Dissertation: Resolves the infinite zero-point energy sum via analytic continuation. It extracts a finite, actionable energy value from the vacuum spectrum, ensuring the generator operates as a consistent quantum heat engine. Source: [ID 1060] CASIMIR BOUNDARY OPTIMIZATION Canonical Statutory Formula: \$∆E \$ = \$Evacuum(B) \$ − \$Evacuum(A) \$ =

\paragraph{Canonical Equation.}
\[
2ζ(−1/2) =⇒
\]

\paragraph{Dictionary.}
DISSIPATION MODELING Canonical Statutory Formula: dρ dt = − i ℏ [Ĥ, ρ] + ∑ n γn ( LnρL † n − 1 2L † nLn, ρ ) Formal Technical Dissertation: Models the non-unitary evolution of the system state.

\paragraph{Encyclopedia.}
Definition of 2ζ(−1/2) is an algebraic definition, written 2ζ(−1/2) =⇒. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
