\tzpanchor{0129}
\tzpentryheader{0129}{Chromatic Ion Sorting}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{c9d5d8bf-a468-5f99-b335-61e0a229fe76}}\\
\textbf{PiID} & \tzpcode{5505822317253} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{136}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{500.9356 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.8254 rad}\\
\textbf{TZPID} & \tzpcode{ID0129} & \textbf{Node Dependencies}\quad \tzpidref{0128}\\
\textbf{Registry} & \tzpcode{registry\_id\_0129} & \textbf{Scale}\quad wavelength-dependent ionic stratification\\
\textbf{LOC Classification} & QC670 optics & QC611 conduction in media\\
\textbf{arXiv Classification} & Primary: physics.optics \quad Cross-list: physics.plasm-ph, cond-mat.mtrl-sci & \\
\textbf{Primary Support} & Red-to-Large-Ion Bias & Blue-to-Small-Ion Bias\\
\textbf{Closure Support} & Radial Charge Separation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Different wavelengths of light are absorbed preferentially by ions of different mass (for example red light by larger ions and blue light by smaller). Sweeping wavelengths across a vortex using an oscillating prism creates radial stratification of ions by mass, forming a natural charge gradient.

\tzpsection{Canonical Equation}
\[
\lambda_{\mathrm{red}} \rightsquigarrow m_{\mathrm{large}}
\]
\[
\lambda_{\mathrm{blue}} \rightsquigarrow m_{\mathrm{small}}
\]
\[
\frac{\partial q}{\partial r} \neq 0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\lambda_{\mathrm{red}}$: source equation symbol.
    \item $m_{\mathrm{large}}$: source equation symbol.
    \item $\lambda_{\mathrm{blue}}$: source equation symbol.
    \item $m_{\mathrm{small}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0129 generated source Wolfram model *)
ClearAll[K0129, Cr0129, T, R, A, W, I, N];
eq0129$1 = HoldForm[lambdaRed*squigarrow*mLarge];
eq0129$2 = HoldForm[lambdaBlue*squigarrow*mSmall];
eq0129$3 = HoldForm[(Partial*q)/(Partial*r) != 0];

K0129 = HoldForm[{eq0129$1, eq0129$2, eq0129$3}];

N = "normalized TRAWIN closure object for Chromatic Ion Sorting";
I = "Radial Charge Separation integration/comparison layer";
W = "Blue-to-Small-Ion Bias wave or operator carrier";
A = "Red-to-Large-Ion Bias admissible action/amplitude condition";
R = "Blue-to-Small-Ion Bias rotation/curl preservation layer";
T = "Red-to-Large-Ion Bias local source condition";

Cr0129[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0129 = Cr0129[K0129];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Red-to-Large-Ion Bias local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Blue-to-Small-Ion Bias rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Red-to-Large-Ion Bias admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Blue-to-Small-Ion Bias wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Radial Charge Separation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Chromatic Ion Sorting.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0129] Chromatic Ion Sorting}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\lambda_{\mathrm{red}} \rightsquigarrow m_{\mathrm{large}}
\]
\[
\lambda_{\mathrm{blue}} \rightsquigarrow m_{\mathrm{small}}
\]
\[
\frac{\partial q}{\partial r} \neq 0
\]

\paragraph{Primary Derivation.}
One can verify the equality by differentiating and applying the relevant definitions. yielding the required identity.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. From the TRAWIN perspective, the equation functions as the generalized carrier for the entry’s information content. Under CHL, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Chromatic Ion Sorting by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Red-to-Large-Ion Bias}\par
\[
\lambda_{\mathrm{red}} \rightsquigarrow m_{\mathrm{large}}
\]
\noindent This states one branch of the wavelength-dependent sorting rule.\par
\noindent\textbf{2. Blue-to-Small-Ion Bias}\par
\[
\lambda_{\mathrm{blue}} \rightsquigarrow m_{\mathrm{small}}
\]
\noindent This completes the complementary branch of the sorting map.\par
\noindent\textbf{3. Radial Charge Separation}\par
\[
\frac{\partial q}{\partial r} \neq 0
\]
\noindent This closes the progression by turning wavelength sorting into a measurable charge gradient across the vortex radius.\par

\clearpage
\noindent\textbf{[ID 0129] Chromatic Ion Sorting}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Chromatic Ion Sorting is a Structural Constraint. Different wavelengths of light are absorbed preferentially by ions of different mass (for example red light by larger ions and blue light by smaller). Sweeping wavelengths across a vortex using an oscillating prism creates radial stratification of ions by mass, forming a natural charge gradient.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Different wavelengths of light are absorbed preferentially by ions of different mass (for example red light by larger ions and blue light by smaller). Sweeping wavelengths across a vortex using an oscillating prism creates radial stratification of ions by mass, forming a natural charge gradient.
\textbf{Contextual meaning:} Light can sort ions in a vortex according to their absorption spectra, leading to mass dependent radial distribution and a built in "charge battery."
\textbf{Derivable consequences:} Design of ion sorting devices; synergy with current concentration and electrohydrodynamic resonance; formation of radial charge gradients.
\textbf{Lemma support:} Different wavelengths of light are absorbed preferentially by ions of different mass (for example red light by larger ions and blue light by smaller). Sweeping wavelengths across a vortex using an oscillating prism creates radial stratification of ions by mass, forming a natural charge gradient.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Light can sort ions in a vortex according to their absorption spectra, leading to mass dependent radial distribution and a built in "charge battery."

\tzpsection{Equation Grounding}
Different wavelengths of light are absorbed preferentially by ions of different mass (for example red light by larger ions and blue light by smaller). Sweeping wavelengths across a vortex using an oscillating prism creates radial stratification of ions by mass, forming a natural charge gradient.

\tzpsection{Interpretive Role}
Light can sort ions in a vortex according to their absorption spectra, leading to mass dependent radial distribution and a built in "charge battery."
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Red-to-Large-Ion Bias}: The specification of one branch of the wavelength-dependent sorting rule.
\item \textbf{Blue-to-Small-Ion Bias}: The completion of the complementary branch of the sorting map.
\item \textbf{Radial Charge Separation}: The conversion of wavelength sorting into a measurable charge gradient across the vortex radius.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0129]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0129_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0129] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Chromatic Ion Sorting}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} different wavelengths of light are absorbed preferentially by ions of different mass
(for example red light by larger ions and blue light by smaller)

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Chromatic Ion Sorting is valid as a spectral relation when frequency, phase, and
propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0129_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
