\tzpanchor{0125}
\tzpentryheader{0125}{Current Concentration Effect}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{c90fed22-aad9-5e4f-992c-b17188818728}}\\
\textbf{PiID} & \tzpcode{4609550582231} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{132}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{485.4028 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.7998 rad}\\
\textbf{TZPID} & \tzpcode{ID0125} & \textbf{Node Dependencies}\quad \tzpidref{0124}\\
\textbf{Registry} & \tzpcode{registry\_id\_0125} & \textbf{Scale}\quad current focusing at vortex core\\
\textbf{LOC Classification} & QC611 electric conduction & QA911 fluid mechanics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph \quad Cross-list: physics.flu-dyn, cond-mat.mtrl-sci & \\
\textbf{Primary Support} & Ohmic Current Law & Core Conductivity Gain\\
\textbf{Closure Support} & Core Current Gain & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In a conductive fluid subject to enhanced radial acceleration, the ion density increases toward the vortex centre. Since the current density obeys

\tzpsection{Canonical Equation}
\[ J = \sigma E, \] and the conductivity $\sigma$ is proportional to the ion concentration, the centre becomes more conductive than the bulk, \[ \sigma_{\mathrm{centre}} > \sigma_{\mathrm{bulk}}. \] Consequently, the same applied electric field produces an enhanced current density at the vortex core, yielding an electromagnetic pinch effect.

\[
J = \sigma E
\]
\[
\sigma_{\mathrm{centre}} > \sigma_{\mathrm{bulk}}
\]
\[
J_{\mathrm{centre}} > J_{\mathrm{bulk}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $J$: source equation symbol.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $E$: source equation symbol.
    \item $\sigma_{\mathrm{centre}}$: source equation symbol.
    \item $\sigma_{\mathrm{bulk}}$: source equation symbol.
    \item $J_{\mathrm{centre}}$: source equation symbol.
    \item $J_{\mathrm{bulk}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0125 generated source Wolfram model *)
ClearAll[K0125, Cr0125, T, R, A, W, I, N];
eq0125$1 = HoldForm[J == sigma*E];
eq0125$2 = HoldForm[sigmaCentre > sigmaBulk];
eq0125$3 = HoldForm[J == sigma*E];
eq0125$4 = HoldForm[sigmaCentre > sigmaBulk];
eq0125$5 = HoldForm[JCentre > JBulk];

K0125 = HoldForm[{eq0125$1, eq0125$2, eq0125$3, eq0125$4, eq0125$5}];

N = "normalized TRAWIN closure object for Current Concentration Effect";
I = "Core Current Gain integration/comparison layer";
W = "Core Conductivity Gain wave or operator carrier";
A = "Ohmic Current Law admissible action/amplitude condition";
R = "Core Conductivity Gain rotation/curl preservation layer";
T = "Ohmic Current Law local source condition";

Cr0125[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0125 = Cr0125[K0125];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Ohmic Current Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Core Conductivity Gain rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Ohmic Current Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Core Conductivity Gain wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Core Current Gain integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Current Concentration Effect.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0125] Current Concentration Effect}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[ J = \sigma E, \] and the conductivity $\sigma$ is proportional to the ion concentration, the centre becomes more conductive than the bulk, \[ \sigma_{\mathrm{centre}} > \sigma_{\mathrm{bulk}}. \] Consequently, the same applied electric field produces an enhanced current density at the vortex core, yielding an electromagnetic pinch effect.

\[
J = \sigma E
\]
\[
\sigma_{\mathrm{centre}} > \sigma_{\mathrm{bulk}}
\]
\[
J_{\mathrm{centre}} > J_{\mathrm{bulk}}
\]

\paragraph{Primary Derivation.}
This argument establishes the identity through direct evaluation of the expression. giving the formula in the first line.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. In the TRAWIN reading, the equation functions as the generalized carrier for the entry’s information content. According to CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Current Concentration Effect by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Ohmic Current Law}\par
\[
J = \sigma E
\]
\noindent This supplies the direct relation between conductivity increase and current increase.\par
\noindent\textbf{2. Core Conductivity Gain}\par
\[
\sigma_{\mathrm{centre}} > \sigma_{\mathrm{bulk}}
\]
\noindent This states the concentration effect created by the focused vortex core.\par
\noindent\textbf{3. Core Current Gain}\par
\[
J_{\mathrm{centre}} > J_{\mathrm{bulk}}
\]
\noindent This closes the progression by converting the conductivity gradient into a measurable current enhancement.\par

\clearpage
\noindent\textbf{[ID 0125] Current Concentration Effect}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Current Concentration Effect is a canonical-registry. In a conductive fluid under enhanced radial acceleration, ion density increases toward the vortex centre. Since current density J =   E and   (conductivity) is proportional to ion

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} In a conductive fluid under enhanced radial acceleration, ion density increases toward the vortex centre. Since current density J =   E and   (conductivity) is proportional to ion
\textbf{Contextual meaning:} Strong vortices concentrate ions, increasing conductivity and producing pinch like concentration of current at the core.
\textbf{Derivable consequences:} Electrohydrodynamic coupling; design of ion focusing devices; synergy with charge oscillation.
\textbf{Lemma support:} In a conductive fluid under enhanced radial acceleration, ion density increases toward the vortex centre. Since current density J =   E and   (conductivity) is proportional to ion\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Strong vortices concentrate ions, increasing conductivity and producing pinch like concentration of current at the core.

\tzpsection{Equation Grounding}
In a conductive fluid under enhanced radial acceleration, ion density increases toward the vortex centre. Since current density J =   E and   (conductivity) is proportional to ion

\tzpsection{Interpretive Role}
Strong vortices concentrate ions, increasing conductivity and producing pinch like concentration of current at the core.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Ohmic Current Law}: The direct relation between conductivity increase and current increase.
\item \textbf{Core Conductivity Gain}: The concentration effect created by the focused vortex core.
\item \textbf{Core Current Gain}: The conversion of the conductivity gradient into a measurable current enhancement.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0125]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0125_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0125] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Current Concentration Effect}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in a conductive fluid subject to enhanced radial acceleration, the ion density increases
toward the vortex centre

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Current Concentration Effect is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that in a conductive fluid subject to enhanced radial
acceleration, the ion density increases toward the vortex centre. Since the current
density obeys \textbackslash{}[ J = E, \textbackslash{}] and the conductivity  is proportional to the ion
concentration, the centre becomes more conductive than the bulk, \textbackslash{}[ \_centre > \_bulk. \textbackslash{}]
Consequently, the same applied electric field produces an enhanced current density at
the vortex core, yielding an electromagnetic pinch effect.. The CHL validation treats
the equation as the formal anchor and the semantic text as the interpretation
constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0125_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
