\section*{ID9348: Definition of ¤Γhor}
\paragraph{Metadata.}
PiID: 5600372798394 | RTEID: RTE:P36300.3600:T3.2632 | UUID: 2d18ad10-eca5-53cf-ae1a-dd8efe6887c5

\paragraph{Canonical Statement.}
for [ID 0173] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0161], [ID 0163] Node registry\_id\_0173 Support Titles Horizontal Lift; Gauge Transport; Connection Form Test Handle If the lift acquires vertical motion or fails to follow the base curve, the transport statement fails. Canonical Equation Links 𝜔 ( ¤𝛾)=0 \$¤Γhor=Lift𝜔\$ ( ¤𝛾) NormalizeTRAWIN(𝜔 ( ¤𝛾) ,Lift𝜔 ( ¤𝛾) ,transport) [ID 0174] Curvature and Field Strength TZPID ID0174 UUID 1355a44d-fd6f-4cdf-9d8d-b63cd60dbc22 Type Curvature Statement Scale geometric LOC Classification Working routing: QA612.6 fiber bundles; QC gauge theory arXiv Classification Primary: math.DG; Cross-list: hep-th, math-ph Canonical Statement Curvature is the field-strength carrier of the

\paragraph{Canonical Equation.}
\[
¤Γhor=Lift𝜔
\]

\paragraph{Dictionary.}
Definition of ¤Γhor — ¤Γhor=Lift𝜔

\paragraph{Encyclopedia.}
Definition of ¤Γhor is an algebraic definition, written ¤Γhor=Lift𝜔. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from L, f, defining ¤Γhor. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
