\section*{ID9359: Definition of Ω⊂𝑀 −ΔT𝜙𝑛}
\paragraph{Metadata.}
PiID: 9400415297002 | RTEID: RTE:P36343.0754:T3.3335 | UUID: 34dff161-083c-50a5-be42-430a7bbddb81

\paragraph{Canonical Statement.}
cate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0018], [ID 0050] Node registry\_id\_0054 Support Titles Confined Domain; Laplacian Eigenmode Equation; Discrete Mode Frequency Test Handle If an admissible bounded geometry with the stated boundary conditions still produces a continuous spectrum where discreteness is claimed, this entry fails. Canonical Equation Links \$Ω⊂𝑀 −ΔT𝜙𝑛=𝜆𝑛𝜙𝑛\$ 𝜔2 𝑛=𝜆𝑛+𝑚2 [ID 0055] Boundary-Induced Quantum Effects TZPID ID0055 UUID 9f353752-5725-54aa-9377-9646e355e321 Type Boundary Operator Law Scale quantum boundary response LOC Classification Working routing: QC174.17 boundary quantum effects; QC20 spectral boundary operators arXiv Classification Primary: quant-ph Cross-list: hep-th, math-ph Canonical Statement Boundaries do not merely truncate a fiel

\paragraph{Canonical Equation.}
\[
Ω⊂𝑀 −ΔT𝜙𝑛=𝜆𝑛𝜙𝑛
\]

\paragraph{Dictionary.}
Definition of Ω⊂𝑀 −ΔT𝜙𝑛 — Ω⊂𝑀 −ΔT𝜙𝑛=𝜆𝑛𝜙𝑛

\paragraph{Encyclopedia.}
Definition of Ω⊂𝑀 −ΔT𝜙𝑛 is an algebraic definition, written Ω⊂𝑀 −ΔT𝜙𝑛=𝜆𝑛𝜙𝑛. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
