\section*{ID8543: QUANTUM-BIOLOGICAL NOISE FILTER Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 1658276584835 | RTEID: RTE:P33174.3662:T4.3957 | UUID: eda8b439-d7dd-5305-96f0-b58eb2e9ac59

\paragraph{Canonical Statement.}
[ID 1129] QUANTUM-BIOLOGICAL NOISE FILTER Canonical Statutory Formula: \$\textbackslash{}frac\{I\_\{retained\}\}\{I\_\{total\}\} \textbackslash{}approx \textbackslash{}frac\{153,600\}\{6 \textbackslash{}cdot 10\textasciicircum{}9\} \textbackslash{}sim 2.56 \textbackslash{}times 10\textasciicircum{}\{-5\}\$ Formal Technical Dissertation: The Optimality Condition for the system's data acquisition. It asserts that while raw base-pair information is vast, the "Relevant Information" for quantum intent is sparse (\$I\_\{relevant\} \textbackslash{}ll I\_\{total\}\$), justifying the massive dimensional reduction to the 153,600 control nodes to filter out non-functional noise. Source: [7]

\paragraph{Canonical Equation.}
\[
\frac{I_{retained}}{I_{total}} \approx \frac{153,600}{6 \cdot 10^9} \sim 2.56 \times 10^{-5}
\]

\paragraph{Dictionary.}
QUANTUM-BIOLOGICAL NOISE FILTER Canonical Statutory Formula: \$ I\_retainedI\_total 153,6006 10\textasciicircum{}9 2.56 10\textasciicircum{}-5\$ Formal Technical Dissertation: The Optimality Condition for the system's data acquisition.

\paragraph{Encyclopedia.}
QUANTUM-BIOLOGICAL NOISE FILTER Canonical Statutory Formula is a scaling / order-of-magnitude relation, written fracI\_retainedI\_total ≈ (153,600)/(6 · 10\textasciicircum{}9) ∼ 2.56 × 10\textasciicircum{}-5. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from I\_retained, I\_total. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
