\section*{ID9884: Definition of n\_physical/n\_logical}
\paragraph{Metadata.}
PiID: 6912091409387 | RTEID: RTE:P38381.7670:T0.4095 | UUID: 6182e2e1-4327-5384-b039-8fc736ec9588

\paragraph{Canonical Statement.}
tial speedups. In our case, by leveraging the constant \$\textbackslash{}pi\$ and topological constructs, we see a complexity scaling that involves \$\textbackslash{}pi\$ in the exponent. For certain problems that map naturally onto our 153600-dimensional manifold (e.g. those that can be encoded in the sphere packing or toroidal structure), we achieve a running time of about \$O(\textbackslash{}text\{poly\}(n)\textasciicircum{}\{1/\textbackslash{}pi\})\$ for tasks that on a classical computer might be \$O(n)\$ or worse. More concretely, some resource scaling results extracted from our protocols include: Quantum Resource Overhead: Logical vs physical qubits scaling was found to be \$n\_\{\textbackslash{}text\{physical\}\}/n\_\{\textbackslash{}text\{logical\}\} = O((\textbackslash{}log n\_\{\textbackslash{}text\{logical\}\})\textasciicircum{}\{\textbackslash{}pi\})\$. This is an extremely slow-growing overhead (logarithm to the power of π). For comparison, surface codes have overhead poly(\$n\$), often linear or near-linear. Our architecture’s overhead growing as \$(\textbackslash{}log n)\textasciicircum{}\{3.14...\}\$ is almost constant for practical sizes. This means we can scale up the number of logical qubits (for computation) with only a very modest increase in physical qubits, thanks to topological protection. In essence, the more qubits we have, error correction complexity rises sub-poly

\paragraph{Canonical Equation.}
\[
n_{\text{physical}}/n_{\text{logical}} = O((\log n_{\text{logical}})^{\pi})
\]

\paragraph{Dictionary.}
Definition of n\_physical/n\_logical — n\_physical/n\_logical = O((log n\_logical)\textasciicircum{}π)

\paragraph{Encyclopedia.}
Definition of n\_physical/n\_logical is an algebraic definition, written n\_physical/n\_logical = O((log n\_logical)\textasciicircum{}π). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from π, O, n\_, defining n\_physical/n\_logical. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
