\section*{ID9343: Definition of)}
\paragraph{Metadata.}
PiID: 5137556003727 | RTEID: RTE:P36280.9439:T3.2312 | UUID: e3634446-79f2-5755-bf57-9f16f03f66b3

\paragraph{Canonical Statement.}
n Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0154], [ID 0155] Node registry\_id\_0156 Support Titles Band Definition; Triple-Overlap Cocycle; Classifying-Space Closure Test Handle If the proposed band and cocycle data do not define a structure classified by 𝐾 (Z, 3), the higher gerbe statement fails. Canonical Equation Links Band(Hgerbe \$)=Aut(HHilbert⊗𝑇M)\$ 𝑔𝑖 𝑗𝑘=exp ( 2𝜋𝑖 \$∫\$ 𝑈𝑖 𝑗𝑘 𝐻3 ) \$𝐵Hgerbe≃𝐾\$ (Z,3) [ID 0157] Forces as Objects in a Higher Category TZPID ID0157 UUID 641830f9-c206-5e71-93b5-e46996191ea8 Type Categorical Statement Scale force sectors as categorical objects LOC Classification Working routing: QA169 category theory; QC6 gauge and interaction structure arXiv Classification Primary: math.CT Cross-list: hep-th, math-ph Canonical Stat

\paragraph{Canonical Equation.}
\[
)=Aut(HHilbert⊗𝑇M)
\]

\paragraph{Dictionary.}
Definition of) — )=Aut(HHilbert⊗𝑇M)

\paragraph{Encyclopedia.}
Definition of) is an algebraic definition, written )=Aut(HHilbert⊗𝑇M). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from A, u, H, l, b, r, defining ). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
