\tzpanchor{0326}
\tzpentryheader{0326}{Toroidal Field Safety Factor Constraint}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{6c320087-a4c3-5954-907f-18aad0d16cc4}}\\
\textbf{PiID} & \tzpcode{0920962829254} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{333}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1265.9304 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.0859 rad}\\
\textbf{TZPID} & \tzpcode{ID0326} & \textbf{Node Dependencies}\quad \tzpidref{0325}\\
\textbf{Registry} & \tzpcode{registry\_id\_0326} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Safety Factor & Critical Threshold\\
\textbf{Closure Support} & Stability Margin & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The safety factor characterizes the ratio of toroidal to poloidal field components in a toroidal confinement system.

\tzpsection{Canonical Equation}
\[
q(r)=\frac{rB_{\phi}}{RB_{\theta}}
\]
\[
q_{\mathrm{critical}}\approx2
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $\theta$: phase angle or local angular coordinate.
    \item $q_{\mathrm{critical}}$: source equation symbol.
    \item $\mathcal{M}_{q}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0326 generated source Wolfram model *)
ClearAll[K0326, Cr0326, T, R, A, W, I, N];
eq0326$1 = HoldForm[q[r] == rBPhi/RBTheta];
eq0326$2 = HoldForm[qCritical == 2];
eq0326$3 = HoldForm[Inequality[MQ, Equal, q[r] - qCritical, Greater, 0]];

K0326 = HoldForm[{eq0326$1, eq0326$2, eq0326$3}];

N = "normalized TRAWIN closure object for Toroidal Field Safety Factor Constraint";
I = "Stability Margin integration/comparison layer";
W = "Critical Threshold wave or operator carrier";
A = "Safety Factor admissible action/amplitude condition";
R = "Critical Threshold rotation/curl preservation layer";
T = "Safety Factor local source condition";

Cr0326[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0326 = Cr0326[K0326];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Safety Factor local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Critical Threshold rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Safety Factor admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Critical Threshold wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Stability Margin integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Toroidal Field Safety Factor Constraint.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0326] Toroidal Field Safety Factor Constraint}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}

The secondary spectral function at the Trawin Zero Point encodes the distribution of excitations across the frequency domain.

\paragraph{Primary Derivation.}

Let $\Phi(t)$ be a temporal bridge function describing oscillatory behaviour near the TZP.
The secondary spectrum is defined as the modulus squared of its Fourier transform:

\begin{equation}
S(\omega) = \left| \int_{-\infty}^{\infty} \Phi(t) e^{-i\omega t} \, \mathrm{d}t \right|^2 .
\end{equation}

This quantity measures how strongly each frequency component contributes to the bridge dynamics.

\paragraph{Interpretation.}

By squaring the Fourier amplitude, the spectral function highlights resonant frequencies and suppresses phases, providing a power distribution over $\omega$.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Toroidal Field Safety Factor Constraint by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Safety Factor}\par
\[
q(r)=\frac{rB_{\phi}}{RB_{\theta}}
\]
\noindent This fixes the toroidal-field safety factor used to diagnose stability of the nested confinement carrier.\par
\noindent\textbf{2. Critical Threshold}\par
\[
q_{\mathrm{critical}}\approx2
\]
\noindent This identifies the critical threshold required for admissible confinement.\par
\noindent\textbf{3. Stability Margin}\par
\[
\mathcal{M}_{q}=q(r)-q_{\mathrm{critical}}>0
\]
\noindent This closes the entry by imposing the stability inequality that the safety factor must satisfy.\par

\clearpage
\noindent\textbf{[ID 0326] Toroidal Field Safety Factor Constraint}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Toroidal Field Safety Factor Constraint is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The safety factor characterizes the ratio of toroidal to poloidal field components in a toroidal confinement system. \textbf{Contextual meaning:} The entry reads Toroidal Field Safety Factor Constraint as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the safety-factor stability condition directly instead of carrying stray engineering prose and Unicode superscripts into the equation block. \textbf{Lemma support:} Safety Factor; Critical Threshold; Stability Margin.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
By squaring the Fourier amplitude, the spectral function highlights resonant frequencies and suppresses phases, providing a power distribution over.

\tzpsection{Equation Grounding}
Equation anchors: approx; q sub critical approximately 2; and qcriticalapproximately2. Proof route: show that the toroidal configuration remains admissible only when the stated safety factor exceeds the critical threshold. Formalization route: prove that the stated confinement inequality follows from the definition of the toroidal safety factor.

\tzpsection{Interpretive Role}
The entry now states the safety-factor stability condition directly instead of carrying stray engineering prose and Unicode superscripts into the equation block.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Helical Pitch Stability}: The dimensionless ratio of toroidal to poloidal magnetic field lines required to prevent plasma disruption.
\item \textbf{Confinement Threshold Margin}: The critical numerical boundary separating stable wave containment from chaotic, turbulent breakdown.
\item \textbf{Kink-Instability Suppression}: The geometric winding rule ensuring that a circulating flow does not cross itself and induce catastrophic short-circuits.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0326]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0326_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0326] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Toroidal Field Safety Factor Constraint}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the safety factor characterizes the ratio of toroidal to poloidal field components in a
toroidal confinement system

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Toroidal Field Safety Factor Constraint is valid when the stated operator maps
admissible inputs into the declared target class.''\\
\textbf{Proof:} The source statement is read as an operator or transformation. The proof obligation is
type preservation: admissible inputs must land in the target object without breaking the
stated constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- operator-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0326_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
