\tzpanchor{0799}
\tzpentryheader{0799}{SO(3) times U(1) Configuration Bundle}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{605026f9-d74d-5f70-809e-5bab9d1455c6}}\\
\textbf{PiID} & \tzpcode{9502445945534} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{806}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3063.8622 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.0483 rad}\\
\textbf{TZPID} & \tzpcode{ID0799} & \textbf{Node Dependencies}\quad \tzpidref{0798}\\
\textbf{Registry} & \tzpcode{registry\_id\_0799} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records so(3) times u(1) configuration bundle through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0799}}:\mathcal{X}_{\mathrm{id0799}}\longrightarrow\mathcal{Y}_{\mathrm{id0799}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0799}})=\mathcal{O}_{\mathrm{id0799}}
\]
\[
\mathcal{O}_{\mathrm{id0799}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0799}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0799}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0799}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0799 generated source Wolfram model *)
ClearAll[K0799, Cr0799, T, R, A, W, I, N];
eq0799$1 = HoldForm[Oid0799[Xid0799] -> Yid0799];
eq0799$2 = HoldForm[NTRAWIN[OId0799] == OId0799];
eq0799$3 = HoldForm[Element[OId0799[x], YAdm]];

K0799 = HoldForm[{eq0799$1, eq0799$2, eq0799$3}];

N = "normalized TRAWIN closure object for SO(3) times U(1) Configuration Bundle";
I = "SO(3) times U(1) Configuration Bundle integration/comparison layer";
W = "SO(3) times U(1) Configuration Bundle wave or operator carrier";
A = "SO(3) times U(1) Configuration Bundle admissible action/amplitude condition";
R = "SO(3) times U(1) Configuration Bundle rotation/curl preservation layer";
T = "SO(3) times U(1) Configuration Bundle local source condition";

Cr0799[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0799 = Cr0799[K0799];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ SO(3) times U(1) Configuration Bundle local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ SO(3) times U(1) Configuration Bundle rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ SO(3) times U(1) Configuration Bundle admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ SO(3) times U(1) Configuration Bundle wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ SO(3) times U(1) Configuration Bundle integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for SO(3) times U(1) Configuration Bundle.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0799] SO(3) times U(1) Configuration Bundle}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0799}}:\mathcal{X}_{\mathrm{id0799}}\longrightarrow\mathcal{Y}_{\mathrm{id0799}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0799}})=\mathcal{O}_{\mathrm{id0799}}
\]
\[
\mathcal{O}_{\mathrm{id0799}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0799}})=\mathcal{O}_{\mathrm{id0799}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. From the TRAWIN perspective, the equation functions as the mapping carrier for the entry’s information content. According to CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors SO(3) times U(1) Configuration Bundle by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0799}}:\mathcal{X}_{\mathrm{id0799}}\longrightarrow\mathcal{Y}_{\mathrm{id0799}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0799}})=\mathcal{O}_{\mathrm{id0799}}
\]
\[
\mathcal{O}_{\mathrm{id0799}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0799] SO(3) times U(1) Configuration Bundle}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
SO(3) times U(1) Configuration Bundle is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} nablax H=J. \textbf{Contextual meaning:} The entry reads SO(3) times U(1) Configuration Bundle as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Geometric Carrier; Compatibility Law; Topological Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, SO(3) times U(1) Configuration Bundle is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: vec p sub i,k = RadialDepth i k dot SphericalVec i; Torus = S to the power 1 times S to the power 1; and [ vec p sub i,k = RadialDepth i k dot SphericalVec i Each axis SphericalVec i corresponds to a projection of a generati. Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Nuclear-Symmetry Mathematical Flipping}: The incredibly useful math trick of pretending that protons and neutrons are actually the exact same particle, just pointing in slightly different, invisible, abstract directions.
\item \textbf{Abstract Charge-Space Rotations}: The bizarre calculations where you don't physically move the particle in the room, you just rotate its invisible, internal identity dials to magically change how it interacts with the world.
\item \textbf{SU(2) Flavor-State Groupings}: The heavy algebra required to keep track of particles that are constantly, rapidly shapeshifting into each other while trapped inside the blinding heat of the reactor core.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0799]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0799].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0799] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont SO(3) times U(1) Configuration Bundle}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} SO(3) times U(1) Configuration Bundle is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``SO(3) times U(1) Configuration Bundle is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0799].
\par\endgroup
\vfill
\endgroup
\endgroup
