\section*{ID6819: S³ (Hypersphere) Eigenmodes — Discreteness, Global Interference, and Why S³ S: Y\_ell\textasciicircum{}m}
\paragraph{Metadata.}
PiID: 8221818528624 | RTEID: RTE:P26479.6913:T5.9313 | UUID: ad343c80-f0e1-538e-9d75-3204068ca984

\paragraph{Canonical Statement.}
**Consequences:** - Modes are discrete in \textbackslash{}(k\textbackslash{}) → more coherent global interference; constructive alignment across the whole closed manifold is easier (standing waves). - Large-scale low-n modes are few and dominate global pattern; their angular parts \textbackslash{}(Y\_\textbackslash{}ell\textasciicircum{}m\textbackslash{}) produce global-lobe patterns on the S³ hypersurface (when projected to a 2-sphere sky they create aligned filamentary impressions). - Thus a hyperspherical universe naturally supports *global Bessel-like interference trees* because radial eigenfunctions are standing, not continuum traveling waves.

\paragraph{Canonical Equation.}
\[
Y_\ell^m
\]

\paragraph{Dictionary.}
Consequences: - Modes are discrete in \textbackslash{}(k\textbackslash{}) → more coherent global interference; constructive alignment across the whole closed manifold is easier (standing waves).

\paragraph{Encyclopedia.}
S³ (Hypersphere) Eigenmodes — Discreteness, Global Interference, and Why S³ S: Y\_ell\textasciicircum{}m is a symbolic expression, written Y\_ℓ\textasciicircum{}m. It introduces a symbol or relation used elsewhere in the framework. It is built from ell, Y, m. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
