\section*{ID8828: EVOLUTIONARY TIMELINE SCALING Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 3312394804947 | RTEID: RTE:P34281.0845:T6.2192 | UUID: 00d12278-810a-52b4-8adc-6e551c9eb2f1

\paragraph{Canonical Statement.}
[ID 1160] EVOLUTIONARY TIMELINE SCALING Canonical Statutory Formula: \$t\_\{eq\}(S) \textbackslash{}propto S\textasciicircum{}\textbackslash{}alpha : 10\textasciicircum{}\{-2\}s (\textbackslash{}text\{Lab\}) \textbackslash{}to 10\textasciicircum{}\{10\}yr (\textbackslash{}text\{Galaxy\})\$ Formal Technical Dissertation: Scaling law for the time to reach equilibrium across astrophysical scales. It maps the ignition and stabilization times from laboratory scales to galactic structures, validating the universality of the TZP framework. Source: [28]

\paragraph{Canonical Equation.}
\[
t_{eq}(S) \propto S^\alpha : 10^{-2}s (\text{Lab}) \to 10^{10}yr (\text{Galaxy})
\]

\paragraph{Dictionary.}
EVOLUTIONARY TIMELINE SCALING Canonical Statutory Formula: \$t\_eq(S) S\textasciicircum{} : 10\textasciicircum{}-2s (Lab) 10\textasciicircum{}10yr (Galaxy)\$ Formal Technical Dissertation: Scaling law for the time to reach equilibrium across astrophysical scales.

\paragraph{Encyclopedia.}
EVOLUTIONARY TIMELINE SCALING Canonical Statutory Formula is a scaling / order-of-magnitude relation, written t\_eq(S) ∝ S\textasciicircum{}α : 10\textasciicircum{}-2s (Lab) → 10\textasciicircum{}10yr (Galaxy). It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from α, t\_eq, S, s, y, r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
