\tzpanchor{0057}
\tzpentryheader{0057}{Quantum Phase Transitions}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{c0a08f7d-59bb-5c73-a9be-4bec0e32ff4f}}\\
\textbf{PiID} & \tzpcode{9445923078164} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{64}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{221.3437 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.3647 rad}\\
\textbf{TZPID} & \tzpcode{ID0057} & \textbf{Node Dependencies}\quad \tzpidref{0053}\\
\textbf{Registry} & \tzpcode{registry\_id\_0057} & \textbf{Scale}\quad zero-temperature transition\\
\textbf{LOC Classification} & QC174.17 quantum criticality & QC20 phase-transition theory\\
\textbf{arXiv Classification} & Primary: cond-mat.stat-mech \quad Cross-list: quant-ph, hep-th & \\
\textbf{Primary Support} & Control Parameter & Gap Closure Criterion\\
\textbf{Closure Support} & Divergent Correlation Length & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A quantum phase transition occurs when the ground state of a system on the Trawinistic manifold changes non-analytically as a function of a control parameter at zero temperature; the critical point is characterized by divergent correlation length determined by the Trawinistic Laplacian eigenvalues.

\tzpsection{Canonical Equation}
\[
\Delta(g_{c}) = 0
\]
\[
\xi \sim |g-g_{c}|^{-\nu}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $g_{c}$: source equation symbol.
    \item $c$: speed of light or relativistic conversion factor.
    \item $\mathcal{K}_{0057}$: canonical registry object for entry ID 0057.
    \item $\Delta(g_{c})$: source equation symbol.
    \item $\xi$: source equation symbol.
    \item $\nu$: source equation symbol.
    \item $D$: source equation symbol.
    \item $a(g_{c})$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0057 generated source Wolfram model *)
ClearAll[K0057, Cr0057, T, R, A, W, I, N];
eq0057$1 = HoldForm[Delta[gC] == 0];
eq0057$2 = HoldForm[SimilarTo[xi, Abs[g - gC]^(-nu)]];
eq0057$3 = HoldForm[g];

K0057 = HoldForm[{eq0057$1, eq0057$2, eq0057$3}];

N = "normalized TRAWIN closure object for Quantum Phase Transitions";
I = "Divergent Correlation Length integration/comparison layer";
W = "Gap Closure Criterion wave or operator carrier";
A = "Control Parameter admissible action/amplitude condition";
R = "Gap Closure Criterion rotation/curl preservation layer";
T = "Control Parameter local source condition";

Cr0057[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0057 = Cr0057[K0057];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Control Parameter local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Gap Closure Criterion rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Control Parameter admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Gap Closure Criterion wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Divergent Correlation Length integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum Phase Transitions.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0057] Quantum Phase Transitions}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\Delta(g_c)=0 .
\end{equation}

\begin{equation}
\xi \sim |g-g_c|^{-\nu}.
\end{equation}

\paragraph{Primary Derivation.}
Let $g$ be a control parameter and $g_c$ its critical value.  
A quantum phase transition occurs at zero temperature when the ground state changes non-analytically.

The critical point is identified by collapse of the spectral gap:

\begin{equation}
\Delta(g_c)=0 .
\end{equation}

Near the critical point, the correlation length diverges as a power law:

\begin{equation}
\boxed{
\xi \sim |g-g_c|^{-\nu}.
}
\end{equation}

\paragraph{Interpretation.}
Quantum criticality is marked by gap closure and divergence of correlation length.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum Phase Transitions by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Control Parameter}\par
\[
g
\]
\noindent This is the tuning parameter that moves the system through its ground-state family.\par
\noindent\textbf{2. Gap Closure Criterion}\par
\[
\Delta(g_{c}) = 0
\]
\noindent This identifies the critical point through collapse of the spectral gap.\par
\noindent\textbf{3. Divergent Correlation Length}\par
\[
\xi \sim |g-g_{c}|^{-\nu}
\]
\noindent This closes the progression by showing that the transition reorganizes correlations across all scales.\par

\clearpage
\noindent\textbf{[ID 0057] Quantum Phase Transitions}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum Phase Transitions is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A quantum phase transition occurs when the ground state of a system on the Trawinistic manifold changes non-analytically as a function of a control parameter at zero temperature; the critical point is characterized by divergent correlation length determined by the Trawinistic Laplacian eigenvalues. \textbf{Contextual meaning:} The entry reads Quantum Phase Transitions as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry gives the registry a way to talk about genuinely new ground-state structure rather than small perturbative drift. It also ties spectral data, confinement, and renormalization language together in a single criticality framework. \textbf{Lemma support:} Control Parameter; Gap Closure Criterion; Divergent Correlation Length.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Quantum criticality is marked by gap closure and divergence of correlation length.

\tzpsection{Equation Grounding}
Equation anchors: A quantum phase transition occurs when the ground state of a system on the Trawinistic manifold changes non-analytically as a function of a control parameter at zero temperature; the critical point is characterized by divergent correlation length determined by the Trawinistic Laplacian eigenvalues. A quantum phase transition occurs when the ground state of a system on the Trawinistic manifold changes non-analytically as a function of a control parameter at zero temperature; the critical point is characterized by divergent correlation length determined by the Trawinistic Laplacian eigenvalues.

\tzpsection{Interpretive Role}
This entry gives the registry a way to talk about genuinely new ground-state structure rather than small perturbative drift. It also ties spectral data, confinement, and renormalization language together in a single criticality framework.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{State-Level Cycle Angle Transitions}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Cycle Angle Quantum-State Analogue}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{Cycle Angle Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0057]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0057_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0057] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum Phase Transitions}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a quantum phase transition occurs when the ground state of a system on the Trawinistic
manifold changes non-analytically as a function of a control...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum Phase Transitions is valid when the total tensorial quantity is conserved under
the stated constraint.''\\
\textbf{Proof:} The source statement identifies a conserved balance law. Reading 0057 as a proposition,
validity follows by requiring the full stress, flux, or current contribution to be
included before the divergence or balance condition is evaluated.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conserved total-structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0057_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
