\section*{ID8559: Definition of V}
\paragraph{Metadata.}
PiID: 5314277568790 | RTEID: RTE:P33236.4978:T4.4980 | UUID: 4fcff134-dccb-5cce-861c-8e7b07134064

\paragraph{Canonical Statement.}
a: \$CTZP \$ := \$[[n, k, d]] \$ = [] Formal Technical Dissertation: Defines the specific quantum error-correcting code integrated into the system. It operates on \$n \$ = \$153, \$ 600 physical qubits (matching the DAANSphere nodes) to encode \$k \$ = \$49, \$ 152 logical qubits with a code distance of \$d \$ = 391, providing robust topological protection against local decoherence. Source: [ID 962] TESSERACT HIERARCHICAL PARTITIONING Canonical Statutory For-mula: \$Atotal \$ = \$⊕16\$ \$v=1(Vv ⊗S9600) \$ Formal Technical Dissertation: Formalizes the hierarchical addressing structure of the navigation system. The total address space is partitioned into 16 hyper-cubic vertices \$(Vv), \$ each acting as a parent node for a sub-manifold of 9,600 surface points (S9600), enabling the projection of 4D tesseract geometry onto the 3D sphere. Source: [ID 963] LOGARITHMIC ADDRESS DIMENSIONALITY C

\paragraph{Canonical Equation.}
\[
v=1(Vv ⊗S9600)
\]

\paragraph{Dictionary.}
Definition of V — v=1(Vv ⊗S9600)

\paragraph{Encyclopedia.}
Definition of V is an algebraic definition, written v=1(Vv ⊗S9600). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from V, S, defining v. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
