\section*{ID9018: Definition of α(t)}
\paragraph{Metadata.}
PiID: 6034021665443 | RTEID: RTE:P35018.8967:T1.1517 | UUID: 6ba324e9-ba0c-5272-9c58-dbb5086255d2

\paragraph{Canonical Statement.}
able Consequences: Normalises other quantities (e.g., temporal displacement factor); serves as scaling factor in Hamiltonians; anchors definitions of physical constants; permits comparison across scales. Falsifiability / Test Handle: If measurements around the TZP produce inconsistent loop integrals, the notion of a unique base unit would be invalid. 0.0.9 ID 007: Temporal Displacement Factor Type: Definition Formal Statement: The temporal displacement factor \$α(t)\textbackslash{}alpha(t)α(t)\$ is defined by \$α(t)=dtdt\textbackslash{}alpha(t)\$ = \$\textbackslash{}frac\{\textbackslash{}text\{d\}t’\}\{\textbackslash{}text\{d\}t\}α(t)\$ = \$dtdt, wherett′tisthelocaltimemeasuredalongageodesicapproachingpppandtttistheglobaltimeparameter.\$ Interpretive Meaning: This factor quantifies how the flow of time near the TZP differs from the global flow of time. It captures temporal dilation or contraction due to the metric degeneracy. Dependencies: ID 001, ID 004 Derivable Consequences: Modifies Hamilt

\paragraph{Canonical Equation.}
\[
α(t)=dtdt\alpha(t)
\]

\paragraph{Dictionary.}
Definition of α(t) — α(t)=dtdtα(t)

\paragraph{Encyclopedia.}
Definition of α(t) is an algebraic definition, written α(t)=dtdtα(t). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from α, defining α(t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
