\tzpanchor{0704}
\tzpentryheader{0704}{TOROIDAL FLUX COMPRESSION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{5dd280e2-616d-5af1-bd6a-6c90e3528a4c}}\\
\textbf{PiID} & \tzpcode{9956112129021} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{711}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2702.7226 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.4533 rad}\\
\textbf{TZPID} & \tzpcode{ID0704} & \textbf{Node Dependencies}\quad \tzpidref{0703}\\
\textbf{Registry} & \tzpcode{registry\_id\_0704} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records toroidal flux compression through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0704}}:\mathcal{X}_{\mathrm{id0704}}\longrightarrow\mathcal{Y}_{\mathrm{id0704}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0704}})=\mathcal{O}_{\mathrm{id0704}}
\]
\[
\mathcal{O}_{\mathrm{id0704}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0704}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0704}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0704}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0704 generated source Wolfram model *)
ClearAll[K0704, Cr0704, T, R, A, W, I, N];
eq0704$1 = HoldForm[Oid0704[Xid0704] -> Yid0704];
eq0704$2 = HoldForm[NTRAWIN[OId0704] == OId0704];
eq0704$3 = HoldForm[Element[OId0704[x], YAdm]];

K0704 = HoldForm[{eq0704$1, eq0704$2, eq0704$3}];

N = "normalized TRAWIN closure object for TOROIDAL FLUX COMPRESSION";
I = "TOROIDAL FLUX COMPRESSION integration/comparison layer";
W = "TOROIDAL FLUX COMPRESSION wave or operator carrier";
A = "TOROIDAL FLUX COMPRESSION admissible action/amplitude condition";
R = "TOROIDAL FLUX COMPRESSION rotation/curl preservation layer";
T = "TOROIDAL FLUX COMPRESSION local source condition";

Cr0704[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0704 = Cr0704[K0704];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ TOROIDAL FLUX COMPRESSION local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TOROIDAL FLUX COMPRESSION rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ TOROIDAL FLUX COMPRESSION admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TOROIDAL FLUX COMPRESSION wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TOROIDAL FLUX COMPRESSION integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TOROIDAL FLUX COMPRESSION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0704] TOROIDAL FLUX COMPRESSION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0704}}:\mathcal{X}_{\mathrm{id0704}}\longrightarrow\mathcal{Y}_{\mathrm{id0704}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0704}})=\mathcal{O}_{\mathrm{id0704}}
\]
\[
\mathcal{O}_{\mathrm{id0704}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0704}})=\mathcal{O}_{\mathrm{id0704}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. Within the TRAWIN framework, the equation functions as the mapping carrier for the entry’s information content. Within the CHL view, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TOROIDAL FLUX COMPRESSION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0704}}:\mathcal{X}_{\mathrm{id0704}}\longrightarrow\mathcal{Y}_{\mathrm{id0704}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0704}})=\mathcal{O}_{\mathrm{id0704}}
\]
\[
\mathcal{O}_{\mathrm{id0704}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0704] TOROIDAL FLUX COMPRESSION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TOROIDAL FLUX COMPRESSION is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} P(A) propto A to the power -3/2. \textbf{Contextual meaning:} The entry reads TOROIDAL FLUX COMPRESSION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, TOROIDAL FLUX COMPRESSION is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: hat mu sub T = mu sub 0 dot exp( -ratio alpha sub T chi sub T dot ratio H sub twist P sub T dot V sub core ) equiv [ epsilon sub T c sub eff to the power 2(r) ] to the power -1; \$hat mu sub T = mu sub 0 dot exp( -ratio alpha sub T chi sub T dot ratio H sub twist P sub T dot V sub core ) equiv [ epsilon sub T c sub eff to the power 2(r) ] to the power -1; and FORMAL TECHNICAL DISSERTATION:The Metric Permeability Operator, denoted as. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Z-Pinch Current Instabilities}: The mapping of sudden, violent kinks and bulges that appear when massive amounts of electricity are fired straight down the center of a column of plasma.
\item \textbf{Theta-Pinch Magnetic Constriction}: The use of an external, rapidly shrinking ring of magnetic force to squeeze a plasma core uniformly inward toward its center axis.
\item \textbf{Sausage-Instability Wavelengths}: The specific mathematical spacing determining where the compressed plasma stream will naturally attempt to bulge outward and break its own containment.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0704]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0704].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0704] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TOROIDAL FLUX COMPRESSION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} TOROIDAL FLUX COMPRESSION is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TOROIDAL FLUX COMPRESSION is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0704].
\par\endgroup
\vfill
\endgroup
\endgroup
