\tzpanchor{0460}
\tzpentryheader{0460}{Temporal Channel Data Gating}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{1f46fd87-e7c6-557f-a70a-a884e6b9c70d}}\\
\textbf{PiID} & \tzpcode{6274956735188} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{467}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1770.7493 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.9177 rad}\\
\textbf{TZPID} & \tzpcode{ID0460} & \textbf{Node Dependencies}\quad \tzpidref{0459}\\
\textbf{Registry} & \tzpcode{registry\_id\_0460} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 460 formalizes the Temporal Channel as the primary conduit for classical data bound by causality. This channel operates on null surface projections where temporal ordering is maintained for standard control interfaces. Gating logic ensures vacuum information is down sampled for human intuitive pattern recognition and linear logic. Causal Consistency: Observational data retrieved from the manifold does not violate chronological constraints. Interface Logic: Provides the classical control layer required for system feedback and monitoring.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{C}_{\text{temp}} = \max \mathcal{I}(X
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{C}$: speed of light or relativistic conversion factor.
    \item $\mathcal{I}$: source equation symbol.
    \item $X$: source variable, local coordinate, or input state in the entry relation.
    \item $\mathcal{K}_{0460}$: canonical registry object for entry ID 0460.
    \item $\max$: source equation symbol.
    \item $C_{temp}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0460 generated source Wolfram model *)
ClearAll[K0460, Cr0460, T, R, A, W, I, N];
eq0460$1 = HoldForm[CTemp == Max[I[X]]];

K0460 = HoldForm[{eq0460$1}];

N = "normalized TRAWIN closure object for Temporal Channel Data Gating";
I = "Temporal Channel Data Gating integration/comparison layer";
W = "Temporal Channel Data Gating wave or operator carrier";
A = "Temporal Channel Data Gating admissible action/amplitude condition";
R = "Temporal Channel Data Gating rotation/curl preservation layer";
T = "Temporal Channel Data Gating local source condition";

Cr0460[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0460 = Cr0460[K0460];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Temporal Channel Data Gating local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Temporal Channel Data Gating rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Temporal Channel Data Gating admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Temporal Channel Data Gating wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Temporal Channel Data Gating integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Temporal Channel Data Gating.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0460] Temporal Channel Data Gating}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
C(\phi_1,\phi_2)
=
\frac{
|\langle \phi_1,\phi_2\rangle|
}{
\|\phi_1\|\,\|\phi_2\|
}.
\end{equation}

\paragraph{Decoherence Limit.}
\begin{equation}
C(t)\rightarrow 0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi_1$ and $\phi_2$ be two quantum field states.  
Their normalized overlap is:

\begin{equation}
C(\phi_1,\phi_2)
=
\frac{
|\langle \phi_1,\phi_2\rangle|
}{
\|\phi_1\|\,\|\phi_2\|
}.
\end{equation}

If environmental coupling, curvature noise, or zero-point disturbance destroys phase alignment, then the time-dependent coherence decreases:

\begin{equation}
C(t)
=
C(\phi_1(t),\phi_2(t)).
\end{equation}

Decoherence occurs in the limiting regime:

\begin{equation}
\boxed{
C(t)\rightarrow 0 .
}
\end{equation}

\paragraph{Interpretation.}
Coherence is normalized state overlap; decoherence is the decay of that overlap under admissible disturbance.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Temporal Channel Data Gating by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{C}_{\text{temp}} = \max \mathcal{I}(X
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0460] Temporal Channel Data Gating}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Temporal Channel Data Gating is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 460 formalizes the Temporal Channel as the primary conduit for classical data bound by causality. This channel operates on null surface projections where temporal ordering is maintained for standard control interfaces. Gating logic ensures vacuum information is down sampled for human intuitive pattern recognition and linear logic. Causal Consistency: Observational data retrieved from the manifold does not violate chronological constraints. Interface Logic: Provides the classical control layer required for system feedback and monitoring.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{C}_{\text{temp}} = \max \mathcal{I}(X
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 460 formalizes the Temporal Channel as the primary conduit for classical data bound by causality. This channel operates on null surface projections where temporal ordering is maintained for standard control interfaces. Gating logic ensures vacuum information is down sampled for human intuitive pattern recognition and linear logic. Causal Consistency: Observational data retrieved from the manifold does not violate chronological constraints. Interface Logic: Provides the classical control layer required for system feedback and monitoring.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Temporal Channel Data Gating by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Temporal Channel Data Gating; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0460]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0460].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0460] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Temporal Channel Data Gating}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} = max mathcal\textbackslash{}(X;Y) text\textbackslash{} s.t

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TEMPORAL CHANNEL DATA GATING is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} = max mathcal\textbackslash{}(X;Y) text\textbackslash{} s.t. \textbackslash{} Delta t >
0 land text\textbackslash{}. Coherence is normalized state overlap; decoherence is the decay of that
overlap under admissible disturbance.. The CHL validation treats the equation as the
formal anchor and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0460].
\par\endgroup
\vfill
\endgroup
\endgroup
