\section*{ID9403: Definition of B𝑔}
\paragraph{Metadata.}
PiID: 3709069793961 | RTEID: RTE:P36513.9372:T3.6151 | UUID: 561f039b-f258-5884-a4b1-5d1461894811

\paragraph{Canonical Statement.}
325] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0324], [ID 0300] Node registry\_id\_0325 Support Titles Gravitomagnetic Field; Mass Integral; Coupling Strength Test Handle If the rotating mass moment does not induce the stated gravitomagnetic field and coupling strength, the entry fails. Canonical Equation Links \$B𝑔=∇×A𝑔\$ J𝑚= \$∫\$ 𝜌(r) r×v(r) 𝑑3𝑟 L𝑔=𝜅𝑔 J𝑚 ·B𝑔 [ID 0326] Toroidal Field Safety Factor Constraint TZPID ID0326 UUID 6c320087-a4c3-5954-907f-18aad0d16cc4 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops toroidal field

\paragraph{Canonical Equation.}
\[
B𝑔=∇×A𝑔
\]

\paragraph{Dictionary.}
Definition of B𝑔 — B𝑔=∇×A𝑔

\paragraph{Encyclopedia.}
Definition of B𝑔 is an algebraic definition, written B𝑔=∇×A𝑔. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from A, defining B𝑔. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
