\section*{ID9513: Synchronization: Kuramoto Networks and Phase Coherence}
\paragraph{Metadata.}
PiID: 6996033027634 | RTEID: RTE:P36941.0916:T4.3189 | UUID: 94bc9ec7-e3ab-5e0d-9990-2232cd592b63

\paragraph{Canonical Statement.}
Synchronization phenomena, particularly as described by the Kuramoto model of coupled oscillators, offer another arena to interpret the ratio \$\textbackslash{}chi\$. The Kuramoto model’s classical threshold for synchronization in a population of oscillators occurs when the coupling \$K\$ exceeds the spread in natural frequencies. In a simple case of two oscillators (or one oscillator’s spin vs orbit, as in tidal locking), the condition for phase-locking is \textbackslash{}begin\{equation\} K ;>; |\textbackslash{}omega\_1 - \textbackslash{}omega\_2|,, \textbackslash{}end\{equation\} meaning the coupling must be just larger than the frequency difference. In a marginal case \$K = |\textbackslash{}omega\_1-\textbackslash{}omega\_2|\$, one gets a neutrally stable phase relation (on the verge of slipping). Now, suppose we demand a certain safety margin – say the coupling is 18.5\% stronger than the bare minimum: \$K = 1.185,|\textbackslash{}omega\_1-\textbackslash{}omega\_2|\$. This would ensure robust phase-locking even in the presence of noise or detuning. The appearance of \$1.185\$ here is not a standard result of Kuramoto theory \textbackslash{}textit\{per se\}, but we can postulate it as a design principle in the DAT-GPT model: nature might “choose” a coupling about 18.5\%

\paragraph{Canonical Equation.}
\[
K = |\omega_1-\omega_2|
\]

\paragraph{Dictionary.}
Synchronization phenomena, particularly as described by the Kuramoto model of coupled oscillators, offer another arena to interpret the ratio χ.

\paragraph{Encyclopedia.}
Synchronization: Kuramoto Networks and Phase Coherence is an algebraic definition, written K = |ω\_1-ω\_2|. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
