\section*{ID9023: Definition of I\_CL}
\paragraph{Metadata.}
PiID: 2166544375589 | RTEID: RTE:P35038.3128:T1.1837 | UUID: 5ab41135-a2db-50e9-b7cf-a26c2e61f462

\paragraph{Canonical Statement.}
000, ID 004 Derivable Consequences: Enters the diffusion terms of field equations; connects to vacuum energy density; influences decoherence of quantum states; helps define noise spectra. Falsifiability / Test Handle: Observation of deterministic, noisefree dynamics near the TZP would make this definition untenable. 0.0.13 ID 011: Causal Loop Invariant Type: Definition Formal Statement: For any closed causal loop \$Γ\textbackslash{}GammaΓ\$ passing through ppp, the invariant I\_CLI\_\{\textbackslash{}text\{CL\}\}I\_CL is given by \$I\_CL=ΓAdxI\_\{\textbackslash{}text\{CL\}\}=\textbackslash{}oint\_\{\textbackslash{}Gamma\}A\textbackslash{}cdot \textbackslash{}text\{d\}xI\_CL=ΓAdx,\$ where AAA is a oneform potential whose exterior derivative vanishes outside the TZP and has support only at ppp. Interpretive Meaning: The integral of the potential around a causal loop yields a conserved quantity characterising the loop’s interaction with the zero point. It encodes the fact that causal loops are quantised by the lemniscatic structure. Dependencies: ID 002 Derivable Consequences:

\paragraph{Canonical Equation.}
\[
I_CL=ΓAdxI_{\text{CL}}=\oint_{\Gamma}A\cdot \text{d}xI_CL=ΓAdx,
\]

\paragraph{Dictionary.}
Definition of I\_CL — I\_CL=ΓAdxI\_CL=oint\_ΓA· dxI\_CL=ΓAdx

\paragraph{Encyclopedia.}
Definition of I\_CL is a contour integral, written I\_CL=ΓAdxI\_CL=oint\_ΓA· dxI\_CL=ΓAdx. It is evaluated by integrating along a closed contour, capturing global or topological properties of the field. It is built from Γ, A, x, I\_, I\_C, L, defining I\_CL. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
