\tzpanchor{0344}
\tzpentryheader{0344}{Holographic Braille Encoding Dictionary}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9fbb72eb-29ca-566d-942b-facf5f14464f}}\\
\textbf{PiID} & \tzpcode{5364367892590} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{351}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1335.8284 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.2010 rad}\\
\textbf{TZPID} & \tzpcode{ID0344} & \textbf{Node Dependencies}\quad \tzpidref{0343}\\
\textbf{Registry} & \tzpcode{registry\_id\_0344} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The mapping between the atemporal null surface and DAANSphere addresses defines a holographic braille dictionary. Each of the 153,600 dimensions captures a distinct topological feature; sequences of addresses encode complex information flow patterns across the null boundary, analogous to braille dots forming letters.

\tzpsection{Canonical Equation}
\[
\mathcal{B}:\partial\Omega\to\{0,1\}^{6}
\]
\[
\mathcal{D}(\mathcal{B}(p))=s_{p}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{B}$: magnetic field magnitude.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $\mathcal{D}$: source equation symbol.
    \item $s_{p}$: source equation symbol.
    \item $s_{q}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0344 generated source Wolfram model *)
ClearAll[K0344, Cr0344, T, R, A, W, I, N];
eq0344$1 = HoldForm[B[partialOmega] -> 16];
eq0344$2 = HoldForm[D[B[p]] == sP];
eq0344$3 = HoldForm[B[p] == B[q]*Longrightarrow*sP == sQ];

K0344 = HoldForm[{eq0344$1, eq0344$2, eq0344$3}];

N = "normalized TRAWIN closure object for Holographic Braille Encoding Dictionary";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0344[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0344 = Cr0344[K0344];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Holographic Braille Encoding Dictionary.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0344] Holographic Braille Encoding Dictionary}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mu
=
kMR^2\Omega .
\end{equation}

\paragraph{Primary Derivation.}
For a rotating body, the inertial rotational scale is controlled by the moment of inertia:

\begin{equation}
I
\sim
MR^2 .
\end{equation}

Angular momentum scales as:

\begin{equation}
L
\sim
I\Omega
\sim
MR^2\Omega .
\end{equation}

If the magnetic moment $\mu$ is proportional to this rotational scale, introduce proportionality constant $k$:

\begin{equation}
\boxed{
\mu
=
kMR^2\Omega .
}
\end{equation}

\paragraph{Interpretation.}
The magnetic moment is modeled as proportional to mass, squared radius, and angular velocity, with $k$ encoding the Trawinistic coupling scale.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Holographic Braille Encoding Dictionary by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
\mathcal{B}:\partial\Omega\to\{0,1\}^{6}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\mathcal{D}(\mathcal{B}(p))=s_{p}
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\mathcal{B}(p)=\mathcal{B}(q)\Longrightarrow s_{p}=s_{q}
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0344] Holographic Braille Encoding Dictionary}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Holographic Braille Encoding Dictionary is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The mapping between the atemporal null surface and DAANSphere addresses defines a holographic braille dictionary. Each of the 153,600 dimensions captures a distinct topological feature; sequences of addresses encode complex information flow patterns across the null boundary, analogous to braille dots forming letters. \textbf{Contextual meaning:} The entry reads Holographic Braille Encoding Dictionary as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The magnetic moment is modeled as proportional to mass, squared radius, and angular velocity, with k encoding the Trawinistic coupling scale.

\tzpsection{Equation Grounding}
Equation anchors: proof=candidate sub formal sub math registry sub definition sub combined,D: 0 sub Engine sub Outputspublish sub reassemble expanded sub context registry sub e; proof=non sub chl sub or sub empirical registry sub definition sub combined,D: 0 sub Engine sub Outputspublish sub reassemble expanded sub context registry sub en; and proof=candidate sub proofable sub chl registry sub definition sub combined,D: 0 sub Engine sub Outputspublish sub reassemble expanded sub context registry. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Six-Dimensional Boolean Projection}: The direct translation of complex surface geometries into simple, six-bit on-off binary data arrays.
\item \textbf{Deterministic State Compaction}: The rigorously defined map converting continuous physical field variations into discrete, readable informational symbols.
\item \textbf{Entropy-Preserving Isomorphism}: The proof that translating a quantum state into the discrete encoding alphabet loses no fundamental structural information.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0344]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0344_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0344] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Holographic Braille Encoding Dictionary}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the mapping between the atemporal null surface and DAANSphere addresses defines a
holographic braille dictionary

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Holographic Braille Encoding Dictionary is valid as a synchronization criterion under
the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0344_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
