\section*{ID8864: MAXWELL STRESS ANISOTROPY FEEDBACK Canonical Statutory Formula: τ\_mag}
\paragraph{Metadata.}
PiID: 6041426363954 | RTEID: RTE:P34420.8805:T0.1664 | UUID: 6b5f4942-c538-5449-ab51-c96255999137

\paragraph{Canonical Statement.}
[ID 1002] MAXWELL STRESS ANISOTROPY FEEDBACK Canonical Statutory Formula: \$\textbackslash{}tau\_\{mag\} = \textbackslash{}oint (\textbackslash{}mathbf\{r\} \textbackslash{}times (\textbackslash{}mathbf\{J\} \textbackslash{}times \textbackslash{}mathbf\{B\})) dV \textbackslash{}implies \textbackslash{}Delta \textbackslash{}omega > 0\$ Formal Technical Dissertation: Describes the self-sustaining feedback loop where magnetic field generation amplifies rotation through Maxwell stress anisotropy, driving the system toward a stable attractor in phase space. Source: [1], [2]

\paragraph{Canonical Equation.}
\[
\tau_{mag} = \oint (\mathbf{r} \times (\mathbf{J} \times \mathbf{B})) dV \implies \Delta \omega > 0
\]

\paragraph{Dictionary.}
MAXWELL STRESS ANISOTROPY FEEDBACK Canonical Statutory Formula: \$ \_mag = (r (J B)) dV 0\$ Formal Technical Dissertation: Describes the self-sustaining feedback loop where magnetic field generation amplifies rotation through Maxwell stress anisotropy, driving the system toward a stable attractor in ph

\paragraph{Encyclopedia.}
MAXWELL STRESS ANISOTROPY FEEDBACK Canonical Statutory Formula: τ\_mag is a contour integral, written τ\_mag = oint (r × (J × B)) dV ⟹ Δ ω > 0. It is evaluated by integrating along a closed contour, capturing global or topological properties of the field. It is built from Δ, ω, r, J, B, V, defining τ\_mag. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
