\tzpanchor{0114}
\tzpentryheader{0114}{$\pi$--$\phi$ Coupling Principle}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{06d76674-333b-5c27-b0c0-e502dedd05ae}}\\
\textbf{PiID} & \tzpcode{3066470938446} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{121}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{442.6873 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.7294 rad}\\
\textbf{TZPID} & \tzpcode{ID0114} & \textbf{Node Dependencies}\quad \tzpidref{0113}\\
\textbf{Registry} & \tzpcode{registry\_id\_0114} & \textbf{Scale}\quad minimal-energy helical configuration\\
\textbf{LOC Classification} & QA315 calculus of variations & QA641 differential geometry\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: math.DG, physics.class-ph & \\
\textbf{Primary Support} & Action Functional & Stationarity Condition\\
\textbf{Closure Support} & Selected Coupling Exponent & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Minimal-energy helical configurations satisfy $\partial$S/$\partial$b = 0, which implies b = 2\,ln\,$\phi$/$\pi$. Thus circular measure $\pi$ and golden-ratio scaling $\phi$ are rigidly coupled.

\tzpsection{Canonical Equation}
\[
\mathcal{S}(\beta)=\int_{\theta_0}^{\theta_1}\mathcal{L}(\beta,\theta)\,d\theta
\]
\[
\frac{\partial \mathcal{S}}{\partial \beta}=0
\]
\[
\beta_{\ast}=\frac{2\log \phi}{\pi}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{S}$: source equation symbol.
    \item $\theta_0$: source equation symbol.
    \item $\theta_1$: source equation symbol.
    \item $\mathcal{L}$: source equation symbol.
    \item $\theta$: phase angle or local angular coordinate.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $\pi$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0114 generated source Wolfram model *)
ClearAll[K0114, Cr0114, T, R, A, W, I, N];
eq0114$1 = HoldForm[S[beta] == IntegralTheta0^theta1*L[beta, theta]*dtheta];
eq0114$2 = HoldForm[(Partial*S)/(Partial*beta) == 0];
eq0114$3 = HoldForm[betaAst == (2*log*phi)/Pi];

K0114 = HoldForm[{eq0114$1, eq0114$2, eq0114$3}];

N = "normalized TRAWIN closure object for $\pi$--$\phi$ Coupling Principle";
I = "Selected Coupling Exponent integration/comparison layer";
W = "Stationarity Condition wave or operator carrier";
A = "Action Functional admissible action/amplitude condition";
R = "Stationarity Condition rotation/curl preservation layer";
T = "Action Functional local source condition";

Cr0114[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0114 = Cr0114[K0114];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Action Functional local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Stationarity Condition rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Action Functional admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Stationarity Condition wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Selected Coupling Exponent integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for \$\textbackslash{}pi\$--\$\textbackslash{}phi\$ Coupling Principle.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0114] $\pi$--$\phi$ Coupling Principle}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{S}(\beta)=\int_{\theta_0}^{\theta_1}\mathcal{L}(\beta,\theta)\,d\theta
\]
\[
\frac{\partial \mathcal{S}}{\partial \beta}=0
\]
\[
\beta_{\ast}=\frac{2\log \phi}{\pi}
\]

\paragraph{Primary Derivation.}
The expression \( \mathcal{S}(\beta)=\int_{\theta_0}^{\theta_1}\mathcal{L}(\beta,\theta)\,d\theta \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. In the TRAWIN reading, the equation functions as the integral carrier for the entry’s information content. According to CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors \$\textbackslash{}pi\$--\$\textbackslash{}phi\$ Coupling Principle by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Action Functional}\par
\[
\mathcal{S}(\beta)=\int_{\theta_0}^{\theta_1}\mathcal{L}(\beta,\theta)\,d\theta
\]
\noindent This packages the helical family into a quantity that can be optimized rather than merely described.\par
\noindent\textbf{2. Stationarity Condition}\par
\[
\frac{\partial \mathcal{S}}{\partial \beta}=0
\]
\noindent This singles out the preferred exponent by requiring the action to be extremal.\par
\noindent\textbf{3. Selected Coupling Exponent}\par
\[
\beta_{\ast}=\frac{2\log \phi}{\pi}
\]
\noindent This closes the progression by identifying the variationally selected exponent with the structural ratio already derived.\par

\clearpage
\noindent\textbf{[ID 0114] $\pi$--$\phi$ Coupling Principle}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
\$\textbackslash{}pi\$--\$\textbackslash{}phi\$ Coupling Principle is a Postulate  . Minimal energy helical configurations extremize a geometric action S such that dS/db = 0 implies b = 2 ln phi / pi.  

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Minimal energy helical configurations extremize a geometric action S such that dS/db = 0 implies b = 2 ln phi / pi.  
\textbf{Contextual meaning:} The radial growth exponent of the helical embedding is not arbitrary but fixed by a coupling between pi (circular measure) and phi (the golden rat
\textbf{Derivable consequences:} Helical geodesics;  --  coupling principle; quantization of helical modes; constraint on allowable embeddings.
\textbf{Lemma support:} Minimal energy helical configurations extremize a geometric action S such that dS/db = 0 implies b = 2 ln phi / pi.  \par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Measure trajectories or structures expected to follow this embedding and confirm the predicted radial exponent. ID 114:  --  Coupling Principle

\tzpsection{Equation Grounding}
Minimal energy helical configurations extremize a geometric action S such that dS/db = 0 implies b = 2 ln phi / pi.  

\tzpsection{Interpretive Role}
The radial growth exponent of the helical embedding is not arbitrary but fixed by a coupling between pi (circular measure) and phi (the golden rat
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Action Functional}: The packaging of the helical family into a quantity that can be optimized rather than merely described.
\item \textbf{Stationarity Condition}: The selection of the preferred exponent by requiring the action to be extremal.
\item \textbf{Selected Coupling Exponent}: The identification of the variationally selected exponent with the structural ratio already derived.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0114]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0114_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0114] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont $\pi$--$\phi$ Coupling Principle}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} minimal-energy helical configurations satisfy  tialS/ tialb = 0, which implies b = 2
ln /

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``\textbackslash{}pi--\textbackslash{}phi Coupling Principle is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0114_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
