\tzpanchor{0115}
\tzpentryheader{0115}{Kuramoto Planetary Spin Model}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7e0d5e34-31cb-5ced-815c-3d4684eb2c93}}\\
\textbf{PiID} & \tzpcode{0664709384460} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{122}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{446.5705 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.7358 rad}\\
\textbf{TZPID} & \tzpcode{ID0115} & \textbf{Node Dependencies}\quad \tzpidref{0114}\\
\textbf{Registry} & \tzpcode{registry\_id\_0115} & \textbf{Scale}\quad planetary spin synchronization\\
\textbf{LOC Classification} & QA371 dynamical systems & QB503 planetary rotation\\
\textbf{arXiv Classification} & Primary: nlin.AO \quad Cross-list: physics.data-an, astro-ph.EP & \\
\textbf{Primary Support} & Phase Evolution Law & Weighted Planetary Coupling\\
\textbf{Closure Support} & Finite Ensemble Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This model idealizes planetary spins as coupled oscillators to study whether gravitational couplings can induce synchronization analogous to the Kuramoto model.

\tzpsection{Canonical Equation}
\[
\dot{\theta}_i
=
\omega_i
\;+\;
\frac{K}{N}\sum_{j=1}^{N}A_{ij}\sin(\theta_j-\theta_i)
\]
\[
A_{ij}=\frac{\sqrt{m_i m_j}}{|a_i-a_j|}
\]
\[
N=8
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\theta$: phase angle or local angular coordinate.
    \item $\omega_i$: angular frequency term in the source equation.
    \item $K$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
    \item $A_{ij}$: source equation symbol.
    \item $\theta_j$: source equation symbol.
    \item $\theta_i$: source equation symbol.
    \item $m_i$: source equation symbol.
    \item $m_j$: source equation symbol.
    \item $a_i$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0115 generated source Wolfram model *)
ClearAll[K0115, Cr0115, T, R, A, W, I, N];
eq0115$1 = HoldForm[dot[theta]*_i == omegaI + (K/N)*SumJ1^N*AIjSin[thetaJ - thetaI]];
eq0115$2 = HoldForm[AIj == Sqrt[mI*mJ]/Abs[aI - aJ]];
eq0115$3 = HoldForm[N == 8];

K0115 = HoldForm[{eq0115$1, eq0115$2, eq0115$3}];

N = "normalized TRAWIN closure object for Kuramoto Planetary Spin Model";
I = "Finite Ensemble Closure integration/comparison layer";
W = "Weighted Planetary Coupling wave or operator carrier";
A = "Phase Evolution Law admissible action/amplitude condition";
R = "Weighted Planetary Coupling rotation/curl preservation layer";
T = "Phase Evolution Law local source condition";

Cr0115[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0115 = Cr0115[K0115];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Phase Evolution Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Weighted Planetary Coupling rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Phase Evolution Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Weighted Planetary Coupling wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Finite Ensemble Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Kuramoto Planetary Spin Model.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0115] Kuramoto Planetary Spin Model}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\dot{\theta}_i
=
\omega_i
\;+\;
\frac{K}{N}\sum_{j=1}^{N}A_{ij}\sin(\theta_j-\theta_i)
\]
\[
A_{ij}=\frac{\sqrt{m_i m_j}}{|a_i-a_j|}
\]
\[
N=8
\]

\paragraph{Primary Derivation.}
One can verify the equality through direct evaluation of the expression. leading to the displayed result.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. Within the TRAWIN framework, the equation functions as the generalized carrier for the entry’s information content. In CHL terms, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Kuramoto Planetary Spin Model by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Phase Evolution Law}\par
\[
\dot{\theta}_i
=
\omega_i
\;+\;
\frac{K}{N}\sum_{j=1}^{N}A_{ij}\sin(\theta_j-\theta_i)
\]
\noindent This establishes each planet as a driven phase oscillator with collective coupling.\par
\noindent\textbf{2. Weighted Planetary Coupling}\par
\[
A_{ij}=\frac{\sqrt{m_i m_j}}{|a_i-a_j|}
\]
\noindent This turns qualitative interaction into a measurable weight using mass and orbital separation.\par
\noindent\textbf{3. Finite Ensemble Closure}\par
\[
N=8
\]
\noindent This closes the progression by declaring the actual system size for the classical eight-planet model.\par

\clearpage
\noindent\textbf{[ID 0115] Kuramoto Planetary Spin Model}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Kuramoto Planetary Spin Model is a canonical-registry. Model each planet as a phase oscillator with rotational angle  \_i obeying dot  \_i =  \_i + (k /N)    \_\{j=1\}\textasciicircum{}\{N\} K\_\{ij\} sin( \_j --  \_i), where  \_i is the natural spin frequency and K\_\{ij\} proportional to (m\_i m\_j)/|a\_i -- a\_j|  is a symmetric coupling matrix built from planetary masses m\_i and separations |a\_i -- a\_j|.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Model each planet as a phase oscillator with rotational angle  \_i obeying dot  \_i =  \_i + (k /N)    \_\{j=1\}\textasciicircum{}\{N\} K\_\{ij\} sin( \_j --  \_i), where  \_i is the natural spin frequency and K\_\{ij\} proportional to (m\_i m\_j)/|a\_i -- a\_j|  is a symmetric coupling matrix built from planetary masses m\_i and separations |a\_i -- a\_j|.
\textbf{Contextual meaning:} Kuramoto Model for Planetary Revolution As a foundation, we recapitulate the Kuramoto phase-oscillator model in the context of planetary orbits. We treat each planet as a phase oscillator moving on a circle (its orbit). Denote the **orbital phase** of planet \$i\$ by \$\textbackslash{}phi\_i(t)\$, measured in \$[0,2\textbackslash{}pi)\$ relative to some fixed reference direction (e.g., the vernal equinox direction in the orbital plane):contentReference[oaicite:60]\{index=60\}:contentReference[oaicite:61] \{index=61\}.
\textbf{Derivable consequences:} Source evidence records the entry as a reusable object whose consequences should be read from the matched formal statement and local proof route.
\textbf{Lemma support:} Model each planet as a phase oscillator with rotational angle  \_i obeying dot  \_i =  \_i + (k /N)    \_\{j=1\}\textasciicircum{}\{N\} K\_\{ij\} sin( \_j --  \_i), where  \_i is the natural spin frequency and K\_\{ij\} proportional to (m\_i m\_j)/|a\_i -- a\_j|  is a symmetric coupling matrix built from planetary masses m\_i and separations |a\_i -- a\_j|.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Kuramoto Model for Planetary Revolution As a foundation, we recapitulate the Kuramoto phase-oscillator model in the context of planetary orbits. We treat each planet as a phase oscillator moving on a circle (its orbit). Denote the **orbital phase** of planet \$i\$ by \$\textbackslash{}phi\_i(t)\$, measured in \$[0,2\textbackslash{}pi)\$ relative to some fixed reference direction (e.g., the vernal equinox direction in the orbital plane):contentReference[oaicite:60]\{index=60\}:contentReference[oaicite:61] \{index=61\}.

\tzpsection{Equation Grounding}
Model each planet as a phase oscillator with rotational angle  \_i obeying dot  \_i =  \_i + (k /N)    \_\{j=1\}\textasciicircum{}\{N\} K\_\{ij\} sin( \_j --  \_i), where  \_i is the natural spin frequency and K\_\{ij\} proportional to (m\_i m\_j)/|a\_i -- a\_j|  is a symmetric coupling matrix built from planetary masses m\_i and separations |a\_i -- a\_j|.

\tzpsection{Interpretive Role}
Kuramoto Model for Planetary Revolution As a foundation, we recapitulate the Kuramoto phase-oscillator model in the context of planetary orbits. We treat each planet as a phase oscillator moving on a circle (its orbit). Denote the **orbital phase** of planet \$i\$ by \$\textbackslash{}phi\_i(t)\$, measured in \$[0,2\textbackslash{}pi)\$ relative to some fixed reference direction (e.g., the vernal equinox direction in the orbital plane):contentReference[oaicite:60]\{index=60\}:contentReference[oaicite:61] \{index=61\}.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Phase Evolution Law}: The establishment of each planet as a driven phase oscillator with collective coupling.
\item \textbf{Weighted Planetary Coupling}: The translation of qualitative interaction into a measurable weight using mass and orbital separation.
\item \textbf{Finite Ensemble Closure}: The declaration of the actual system size for the classical eight-planet model.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0115]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0115_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0115] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Kuramoto Planetary Spin Model}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this model idealizes planetary spins as coupled oscillators to study whether
gravitational couplings can induce synchronization analogous to the Ku...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Kuramoto Planetary Spin Model is valid as a synchronization criterion under the coupling
conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0115_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
