\tzpanchor{0201}
\tzpentryheader{0201}{Standing Wave Quantization}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7f39a061-6fb0-58ac-b7dd-be8b9a126802}}\\
\textbf{PiID} & \tzpcode{4288109756659} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{208}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{780.5276 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.2861 rad}\\
\textbf{TZPID} & \tzpcode{ID0201} & \textbf{Node Dependencies}\quad \tzpidref{0200}\\
\textbf{Registry} & \tzpcode{registry\_id\_0201} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Mode Quantization & Dispersion Law\\
\textbf{Closure Support} & Boundary Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In a bounded rotating plasma of radius $R$, Alfv\'en waves form standing modes with frequencies

\tzpsection{Canonical Equation}
\[ f_n = \frac{n v_A}{2\pi R}, \qquad n \in \mathbb{N}_{>0}. \]

\[
\Psi_{\mathrm{wave}} = \sum_{l\ge 2}\sum_{m=-l}^{l} A_{l,m}Y_l^m(\theta,\lambda)e^{i\omega_{l,m}t}
\]
\[
\omega_{\mathrm{KK}}^{2} = \omega_{\mathrm{acoustic}}^{2} + \omega_{\mathrm{magnetic}}^{2} + \left(\frac{m_{\mathrm{KK}}c}{R_{\mathrm{KK}}}\right)^{2}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $f_n$: mode-indexed ordinary frequency.
    \item $n$: integer mode index.
    \item $v_A$: Alfven velocity or carrier speed.
    \item $\pi$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\Psi_{\mathrm{wave}}$: source equation symbol.
    \item $A_{l,m}$: source equation symbol.
    \item $Y_l$: source equation symbol.
    \item $\theta$: phase angle or local angular coordinate.
    \item $\lambda$: cosmological or lemniscatic branch parameter in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0201 generated source Wolfram model *)
ClearAll[K0201, Cr0201, T, R, A, W, I, N];
eq0201$1 = HoldForm[Element[TZPSequence[fN == (n*vA)/(2*Pi*R), n], N0]];
eq0201$2 = HoldForm[PsiWave == SumL2*SumMl^l*ALmYL^m[theta, lambda]*e^iomegaLmt];
eq0201$3 = HoldForm[omegaKK^2 == omegaAcoustic^2 + omegaMagnetic^2 + (mKKc/RKK)^2];

K0201 = HoldForm[{eq0201$1, eq0201$2, eq0201$3}];

N = "normalized TRAWIN closure object for Standing Wave Quantization";
I = "Boundary Condition integration/comparison layer";
W = "Dispersion Law wave or operator carrier";
A = "Mode Quantization admissible action/amplitude condition";
R = "Dispersion Law rotation/curl preservation layer";
T = "Mode Quantization local source condition";

Cr0201[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0201 = Cr0201[K0201];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Mode Quantization local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Dispersion Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Mode Quantization admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Dispersion Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Boundary Condition integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Standing Wave Quantization.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0201] Standing Wave Quantization}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\det(g)\big|_{p}=0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $(M,g)$ be a manifold equipped with metric tensor $g$. Away from the Trawin Zero Point $p$, the metric is assumed nondegenerate:

\begin{equation}
\det(g)\neq 0,
\qquad x\neq p .
\end{equation}

At the TZP, the manifold undergoes a structural collapse of ordinary metric invertibility. This means the inverse metric $g^{-1}$ cannot be defined at $p$.

A metric tensor is invertible if and only if its determinant is nonzero. Therefore, non-invertibility at $p$ implies:

\begin{equation}
\det(g)\big|_{p}=0 .
\end{equation}

\paragraph{Interpretation.}
The TZP is marked by metric degeneracy. This is the first mathematical signature that ordinary geometry fails at the zero point and must be replaced by a Trawinistic structure.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Standing Wave Quantization by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Mode Quantization}\par
\[
\Psi_{\mathrm{wave}} = \sum_{l\ge 2}\sum_{m=-l}^{l} A_{l,m}Y_l^m(\theta,\lambda)e^{i\omega_{l,m}t}
\]
\noindent This fixes the quantized carrier mode indexed by the bounded geometry.\par
\noindent\textbf{2. Dispersion Law}\par
\[
\omega_{\mathrm{KK}}^{2} = \omega_{\mathrm{acoustic}}^{2} + \omega_{\mathrm{magnetic}}^{2} + \left(\frac{m_{\mathrm{KK}}c}{R_{\mathrm{KK}}}\right)^{2}
\]
\noindent This turns the mode index into an actual propagation or resonance law.\par
\noindent\textbf{3. Boundary Condition}\par
\[
\omega_{\mathrm{KK}}^{2} = \omega_{\mathrm{acoustic}}^{2} + \omega_{\mathrm{magnetic}}^{2} + \left(\frac{m_{\mathrm{KK}}c}{R_{\mathrm{KK}}}\right)^{2}
\]
\noindent This closes the progression by enforcing the boundary or nodal condition that makes the pattern admissible.\par

\clearpage
\noindent\textbf{[ID 0201] Standing Wave Quantization}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Standing Wave Quantization is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} In a bounded rotating plasma of radius \(R\), Alfv\'en waves form standing modes with frequencies \(f_n=n v_{\mathrm{A}}/(2\pi R)\), where \(n\in\mathbb{N}_{>0}\). \textbf{Contextual meaning:} The entry reads Standing Wave Quantization as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred. \textbf{Lemma support:} Mode Quantization; Dispersion Law; Boundary Condition.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP is marked by metric degeneracy. This is the first mathematical signature that ordinary geometry fails at the zero point and must be replaced by a Trawinistic structure.

\tzpsection{Equation Grounding}
Equation anchors:
\[
\Psi_{\mathrm{wave}}=\sum_{l\ge2}\sum_{m=-l}^{l}A_{l,m}Y_l^m(\theta,\lambda)e^{i\omega_{l,m}t},\qquad
f_n=\frac{n v_{\mathrm{A}}}{2\pi R},
\]
and
\[
\omega_{\mathrm{KK}}^{2}=\omega_{\mathrm{acoustic}}^{2}+\omega_{\mathrm{magnetic}}^{2}
+\left(\frac{m_{\mathrm{KK}}c}{R_{\mathrm{KK}}}\right)^2.
\]
Proof route: show that bounded carrier geometry forces the stated mode quantization and resonance law. Formalization route: prove that the stated boundary condition yields the stated discrete spectrum.

\tzpsection{Interpretive Role}
The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Bounded Field Mode Extraction}: The mathematical restriction of allowed wavelengths to integer multiples satisfying fixed spatial boundaries.
\item \textbf{Resonant Carrier Frequency Mapping}: The discrete assignment of allowed frequencies ensuring perfectly constructive self-interference.
\item \textbf{Spatial Discretization of Wave Action}: The limitation of continuous energy distribution into explicitly separated nodal and antinodal regions.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0201]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0201_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0201] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Standing Wave Quantization}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in a bounded rotating plasma of radius R, Alfv\textbackslash{}'en waves form standing modes with
frequencies

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Standing Wave Quantization Type: Operator is valid as a spectral relation when
frequency, phase, and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0201_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
