\tzpanchor{0275}
\tzpentryheader{0275}{Protostellar Magnetic-First Sequence}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{6ef58bd5-5195-5aeb-baf0-ed6ef655d34e}}\\
\textbf{PiID} & \tzpcode{6648213393607} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{282}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1067.8861 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.7595 rad}\\
\textbf{TZPID} & \tzpcode{ID0275} & \textbf{Node Dependencies}\quad \tzpidref{0274}\\
\textbf{Registry} & \tzpcode{registry\_id\_0275} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In collapsing protostars, magnetic fields reach steady state at around ten thousand years while rotation stabilises only at about a million years; thus magnetic stabilisation precedes rotational stabilisation.

\tzpsection{Canonical Equation}
\[
omega^{2} = k^{2} v_{\mathrm{A}}^{2}\left[1 + \left(\frac{\omega_{\mathrm{gyro}}}{\omega}\right)^{2}\right]
\]
\[
\eta_{J_z}\circ\Phi_Q(f)=\mathcal{B}(f)\circ\eta_{J_z}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $v_{\mathrm{A}}$: Alfven velocity or carrier speed.
    \item $\omega_{\mathrm{gyro}}$: gyroscopic angular frequency correction.
    \item $\omega$: angular frequency term in the source equation.
    \item $J_z$: source equation symbol.
    \item $\Phi_Q(f)$: flux, phase, or topological map term in the source equation.
    \item $\mathcal{B}(f)$: magnetic field magnitude.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0275 generated source Wolfram model *)
ClearAll[K0275, Cr0275, T, R, A, W, I, N];
eq0275$1 = HoldForm[omega^2 == k^2*vA^2[1 + (omegaGyro/omega)^2]];
eq0275$2 = HoldForm[etaJzcircPhiQ[f] == B[f]*circetaJz];
eq0275$3 = HoldForm[omega^2 == k^2*vA^2[1 + (omegaGyro/omega)^2]];

K0275 = HoldForm[{eq0275$1, eq0275$2, eq0275$3}];

N = "normalized TRAWIN closure object for Protostellar Magnetic-First Sequence";
I = "Normalized Output integration/comparison layer";
W = "Composable Action wave or operator carrier";
A = "Carrier Map admissible action/amplitude condition";
R = "Composable Action rotation/curl preservation layer";
T = "Carrier Map local source condition";

Cr0275[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0275 = Cr0275[K0275];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Carrier Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Composable Action rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Carrier Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Composable Action wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Output integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Protostellar Magnetic-First Sequence.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0275] Protostellar Magnetic-First Sequence}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\Delta U = Q+W .
\end{equation}

\begin{equation}
\Delta S
\geq
\frac{Q}{T_{\mathrm{eff}}}
+
\Sigma_{\mathrm{TZP}} .
\end{equation}

\paragraph{Primary Derivation.}
The first-law balance writes the change in internal energy as heat plus work:
\begin{equation}
\Delta U=Q+W .
\end{equation}

Entropy change is bounded below by heat exchange over an effective temperature:
\begin{equation}
\Delta S\geq \frac{Q}{T_{\mathrm{eff}}}.
\end{equation}

The TRAWIN correction includes an irreducible zero-point contribution $\Sigma_{\mathrm{TZP}}$, producing
\begin{equation}
\boxed{
\Delta S
\geq
\frac{Q}{T_{\mathrm{eff}}}
+
\Sigma_{\mathrm{TZP}} .
}
\end{equation}

\paragraph{Interpretation.}
Quantum thermodynamics links energy balance, entropy production, effective temperature, and zero-point correction.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Protostellar Magnetic-First Sequence by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Carrier Map}\par
\[
omega^{2} = k^{2} v_{\mathrm{A}}^{2}\left[1 + \left(\frac{\omega_{\mathrm{gyro}}}{\omega}\right)^{2}\right]
\]
\noindent This names the entry as an actual map between carrier domains rather than a loose metaphor.\par
\noindent\textbf{2. Composable Action}\par
\[
\eta_{J_z}\circ\Phi_Q(f)=\mathcal{B}(f)\circ\eta_{J_z}
\]
\noindent This inserts the map into the ordered TRAWIN chain and makes composition explicit.\par
\noindent\textbf{3. Normalized Output}\par
\[
\omega^{2} = k^{2} v_{\mathrm{A}}^{2}\left[1 + \left(\frac{\omega_{\mathrm{gyro}}}{\omega}\right)^{2}\right]
\]
\noindent This closes the entry by requiring that the output land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0275] Protostellar Magnetic-First Sequence}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Protostellar Magnetic-First Sequence is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} In collapsing protostars, magnetic fields reach steady state at around ten thousand years while rotation stabilises only at about a million years; thus magnetic stabilisation precedes rotational stabilisation. \textbf{Contextual meaning:} The entry reads Protostellar Magnetic-First Sequence as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Quantum thermodynamics links energy balance, entropy production, effective temperature, and zero-point correction.

\tzpsection{Equation Grounding}
Equation anchors:
\[
\omega^2=k^2v_A^2\left[1+\left(\frac{\omega_{\mathrm{gyro}}}{\omega}\right)^2\right],
\qquad
\Delta E\approx\frac{\Phi_0^2}{2L}\approx10^{-21}\,\mathrm{J}.
\]
Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Magnetic-Precedence Stellar Formation Model}: The theory asserting that strong, primordial magnetic fields exist before and actively guide the collapse of a gas cloud into a new star.
\item \textbf{Flux-Driven Protostellar Collapse Regulation}: The mechanism by which magnetic tension physically slows down and controls gravity, preventing a gas cloud from collapsing too quickly.
\item \textbf{Helical Channeling of Accretion Disk}: The process where the twisted magnetic field lines of a newborn star funnel incoming gas to its poles and blast excess material out as polar jets.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0275]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0275_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0275] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Protostellar Magnetic-First Sequence}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in collapsing protostars, magnetic fields reach steady state at around ten thousand
years while rotation stabilises only at about a million years;...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Protostellar Magnetic-First Sequence is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0275_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
