\tzpanchor{0375}
\tzpentryheader{0375}{Spherical Harmonic Expansion}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7c10e7d8-64de-5fab-a5a1-e6390aa7ccdb}}\\
\textbf{PiID} & \tzpcode{4665213841469} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{382}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1456.2083 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.3994 rad}\\
\textbf{TZPID} & \tzpcode{ID0375} & \textbf{Node Dependencies}\quad \tzpidref{0374}\\
\textbf{Registry} & \tzpcode{registry\_id\_0375} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Field Expansion & Modal Coefficients\\
\textbf{Closure Support} & Angular Basis & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The radial and tangential components of the magnetic field inside the sphere expand as sums of spherical harmonics with radial functions chosen to satisfy the interior equations and boundary conditions.

\tzpsection{Canonical Equation}
\[
B(r,\theta,\phi)=\sum_{\ell=0}^{\infty}\sum_{m=-\ell}^{\ell} a_{\ell m}(r)\,Y_{\ell}^{m}(\theta,\phi)
\]
\[
a_{\ell m}(r)=\int_{S^2} B(r,\theta,\phi)\,\overline{Y_{\ell}^{m}(\theta,\phi)}\,d\Omega
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $B$: magnetic field magnitude.
    \item $\theta$: phase angle or local angular coordinate.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $a_{\ell m}(r)$: source equation symbol.
    \item $Y_{\ell}$: source equation symbol.
    \item $S^2$: two-sphere target domain.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $Y_{\ell'}$: source equation symbol.
    \item $\delta_{\ell\ell'}$: source equation symbol.
    \item $\delta_{mm'}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0375 generated source Wolfram model *)
ClearAll[K0375, Cr0375, T, R, A, W, I, N];
eq0375$1 = HoldForm[B[r, theta, phi] == SumEll0^Infinity*SumMell^ell*aEllm[r]*YEll^m*Pair[theta, phi]];
eq0375$2 = HoldForm[aEllm[r] == IntegralS2*B[r, theta, phi]*overline[YEll^m*Pair[theta, phi]]*dOmega];
eq0375$3 = HoldForm[intS2*YEll^m*overline[YEll^Derivative[1][m]]*dOmega == DiracDeltaEllellDiracDeltaMm];

K0375 = HoldForm[{eq0375$1, eq0375$2, eq0375$3}];

N = "normalized TRAWIN closure object for Spherical Harmonic Expansion";
I = "Angular Basis integration/comparison layer";
W = "Modal Coefficients wave or operator carrier";
A = "Field Expansion admissible action/amplitude condition";
R = "Modal Coefficients rotation/curl preservation layer";
T = "Field Expansion local source condition";

Cr0375[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0375 = Cr0375[K0375];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Field Expansion local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Modal Coefficients rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Field Expansion admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Modal Coefficients wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Angular Basis integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Spherical Harmonic Expansion.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0375] Spherical Harmonic Expansion}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\Delta U = Q+W .
\end{equation}

\begin{equation}
\Delta S
\geq
\frac{Q}{T_{\mathrm{eff}}}
+
\Sigma_{\mathrm{TZP}} .
\end{equation}

\paragraph{Primary Derivation.}
The first-law balance writes the change in internal energy as heat plus work:
\begin{equation}
\Delta U=Q+W .
\end{equation}

Entropy change is bounded below by heat exchange over an effective temperature:
\begin{equation}
\Delta S\geq \frac{Q}{T_{\mathrm{eff}}}.
\end{equation}

The TRAWIN correction includes an irreducible zero-point contribution $\Sigma_{\mathrm{TZP}}$, producing
\begin{equation}
\boxed{
\Delta S
\geq
\frac{Q}{T_{\mathrm{eff}}}
+
\Sigma_{\mathrm{TZP}} .
}
\end{equation}

\paragraph{Interpretation.}
Quantum thermodynamics links energy balance, entropy production, effective temperature, and zero-point correction.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Spherical Harmonic Expansion by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Field Expansion}\par
\[
B(r,\theta,\phi)=\sum_{\ell=0}^{\infty}\sum_{m=-\ell}^{\ell} a_{\ell m}(r)\,Y_{\ell}^{m}(\theta,\phi)
\]
\noindent This fixes the angular decomposition of the carrier field into spherical harmonics.\par
\noindent\textbf{2. Modal Coefficients}\par
\[
a_{\ell m}(r)=\int_{S^2} B(r,\theta,\phi)\,\overline{Y_{\ell}^{m}(\theta,\phi)}\,d\Omega
\]
\noindent This extracts the radial mode coefficients from the angular field profile.\par
\noindent\textbf{3. Angular Basis}\par
\[
int_{S^2}Y_{\ell}^{m}\overline{Y_{\ell'}^{m'}}\,d\Omega=\delta_{\ell\ell'}\delta_{mm'}
\]
\noindent This closes the entry with the orthogonality law that makes the modal decomposition admissible.\par

\clearpage
\noindent\textbf{[ID 0375] Spherical Harmonic Expansion}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Spherical Harmonic Expansion is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The radial and tangential components of the magnetic field inside the sphere expand as sums of spherical harmonics with radial functions chosen to satisfy the interior equations and boundary conditions. \textbf{Contextual meaning:} The entry reads Spherical Harmonic Expansion as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now carries a proper harmonic decomposition rather than a prose description of angular expansion. \textbf{Lemma support:} Field Expansion; Modal Coefficients; Angular Basis.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Quantum thermodynamics links energy balance, entropy production, effective temperature, and zero-point correction.

\tzpsection{Equation Grounding}
Equation anchors: B(r,theta,phi)=sum sub ell=0 to the power infinity sum sub m=-ell to the power ell a sub ell m (r) Y sub ell to the power m (theta,phi); a sub ell m (r)=integral sub S to the power 2 B(r,theta,phi) overline Y sub ell to the power m (theta,phi) dOmega; and int sub S to the power 2 Y sub ell to the power m overline Y sub ell to the power m dOmega=delta sub ellell delta sub mm . Proof route: show that the stated field admits the spherical-harmonic decomposition with the given coefficient formula. Formalization route: prove that orthogonality of the spherical harmonics yields the stated coefficient extraction law.

\tzpsection{Interpretive Role}
The entry now carries a proper harmonic decomposition rather than a prose description of angular expansion.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Orthogonal Angular Decomposition}: The mathematical technique of breaking a complex, lumpy 3D field into a neat stack of standard, symmetric spherical wave shapes.
\item \textbf{Radial Mode Amplitude Extraction}: The integration process used to figure out exactly how much of each specific spherical wave shape is present in the total chaotic field.
\item \textbf{Basis-Function Completeness}: The rigorous proof that any possible continuous field shape can be perfectly rebuilt by stacking enough of these spherical harmonics together.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0375]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0375_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0375] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Spherical Harmonic Expansion}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the radial and tangential components of the magnetic field inside the sphere expand as
sums of spherical harmonics with radial functions chosen to...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Spherical Harmonic Expansion is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0375_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
