\section*{ID9439: Definition of (Ω)}
\paragraph{Metadata.}
PiID: 7886144458123 | RTEID: RTE:P36653.7332:T3.8454 | UUID: cd544970-aae0-585e-afa0-471ab4729dde

\paragraph{Canonical Statement.}
D 0456] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0455], [ID 0400] Node registry\_id\_0456 Support Titles Variation Law; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links 𝛾loss \$(Ω)=𝛾0 (1+𝛼Ω2𝑅2/𝑐2\$ ) Jout=· · · Aadm(Jout )=· · · [ID 0457] RESONANCE HOLD-STATE MAINTENANCE TZPID ID0457 UUID c5ec1df3-8ae4-5ab4-9732-e169dbcd56c2 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops resonance hold-state maintena

\paragraph{Canonical Equation.}
\[
(Ω)=𝛾0 (1+𝛼Ω2𝑅2/𝑐2
\]

\paragraph{Dictionary.}
Definition of (Ω) — (Ω)=𝛾0 (1+𝛼Ω2𝑅2/𝑐2

\paragraph{Encyclopedia.}
Definition of (Ω) is an algebraic definition, written (Ω)=𝛾0 (1+𝛼Ω2𝑅2/𝑐2. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
