\section*{ID8579: Definition of P (T)dt}
\paragraph{Metadata.}
PiID: 7028352971634 | RTEID: RTE:P33314.1622:T4.6260 | UUID: f45eec14-aee8-5782-8aa7-6ba72df7bb6e

\paragraph{Canonical Statement.}
and vacuum coupling. Source: [ID 1074] COUPLING ACTIVATION RAMP Canonical Statutory Formula: \$Ĥint(t) \$ = \$λ(t) \$ \$∑\$ \$Ψ̂left ⊗ Ψ̂right =⇒ \$ TZP Ignition Formal Technical Dissertation: Marks the "Ignition" of the TZP. Gradually increasing coupling strength between Left (Information) and Right (Energy) vortices initiates the interchange through the lemniscatic crossing point. Source: [ID 1075] EXTRACTION PHASE TIMING Canonical Statutory Formula: \$Wext \$ \$=∫\$ \$τext \$ 0 \$P (t)dt =⇒ \$ Steady-State Extraction Formal Technical Dissertation: Establishes the duration of the steady-state extraction phase. The system maintains resonant coupling to scavenge energy/information, balanced against the energy-time uncertainty relation. Source: [ID 1076] RESET PHASE \& ENTROPY CLEARING Canonical Statutory Formula: \$Qreset ≥ kBT \$ ln 2 · \$Nbits =⇒ \$ Landauer Damping Formal Te

\paragraph{Canonical Equation.}
\[
P (t)dt =⇒
\]

\paragraph{Dictionary.}
Definition of P (T)dt — P (t)dt =⇒

\paragraph{Encyclopedia.}
Definition of P (T)dt is an algebraic definition, written P (t)dt =⇒. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
