\section*{ID9411: Definition of 𝑇∗𝑄, 𝐺gauge}
\paragraph{Metadata.}
PiID: 9396122571429 | RTEID: RTE:P36545.0030:T3.6663 | UUID: b09fda09-196a-5ad6-ab96-d18cf3fb694f

\paragraph{Canonical Statement.}
nked forward into the surrounding registry pages. P = 𝑇∗𝑄 × 𝑆1 KK × A 𝜋KK : P \$→\$ 𝑇∗𝑄 Wolfram Form 𝔚TZP (K0365) \$↦−→ 〈 Φ𝜏\$ , \$Ω\$ T, \$ΨT 〉\$ K0365 := HoldForm(T0365) AdmissibleTZP (K0365) \$⇐⇒𝔚TZP\$ (K0365) . \$∅\$ Wolfram register: canonical symbol lift Title lift: Extended Phase Space for Magneto-Acoustic KK Systems Symbol key: \$Φ𝜏\$ : phase-time symmetry \$ΩT:\$ Trawinistic boundary curvature \$ΨT:\$ Trawinistic wavefunction TRAWIN Normalization NormalizeTRAWIN( P = 𝑇∗𝑄 × 𝑆1 KK × A, 𝜋KK : P \$→\$ 𝑇∗𝑄, 𝐺gauge = \{𝜙 : R3 \$→\$ 𝑈 (1) | \$∇2𝜙\$ = 0\} ) T: Configuration Manifold is localized within the field the-ory and action principles arc of the directory. R: Kaluza–Klein Sector preserves the operative relation that extended phase space for magneto-acoustic kk sys-tems requires. A: Gauge Quotient fixes the admissible closure condition for the entry. W: Extended Phase Space for Magneto-Acoustic KK Sys-tems is rendered a

\paragraph{Canonical Equation.}
\[
𝑇∗𝑄, 𝐺gauge = {𝜙 : R3
\]

\paragraph{Dictionary.}
Definition of 𝑇∗𝑄, 𝐺gauge — 𝑇∗𝑄, 𝐺gauge = 𝜙 : R3

\paragraph{Encyclopedia.}
Definition of 𝑇∗𝑄, 𝐺gauge is an algebraic definition, written 𝑇∗𝑄, 𝐺gauge = 𝜙 : R3. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R, defining 𝑇∗𝑄, 𝐺gauge. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
