\section*{ID10128: Relation: α ≈ 1/137.036}
\paragraph{Metadata.}
PiID: 0069752148293 | RTEID: RTE:P39329.2732:T1.9707 | UUID: 4e6a5c0c-cfce-5305-bf62-d73bb6ae404f

\paragraph{Canonical Statement.}
l-pole perspective---simultaneously viewing both North and South poles---we reveal that gravitational and electromagnetic phenomena are standing wave interference patterns in spacetime, constrained by toroidal topology. The framework, termed \textbackslash{}textbf\{Trawin Topology\}, demonstrates that what appears as continuous gravitational force in Newtonian mechanics is the time-averaged manifestation of Planck-scale oscillations (\$\textbackslash{}approx 10\textasciicircum{}\{43\}\$ Hz), while Einstein's curved spacetime emerges as the macroscopic geometry of these quantum field oscillations. We rigorously derive the fine structure constant \$\textbackslash{}alpha \textbackslash{}approx 1/137.036\$ from toroidal winding numbers, explain the speed of light \$c\$ as toroidal field impedance, and present the photon as a transverse wave in this topology. The dipole constraint energy \$U \textbackslash{}propto \textbackslash{}mu\textasciicircum{}2/d\textasciicircum{}4 \textbackslash{}to \textbackslash{}infty\$ as separation \$d \textbackslash{}to 0\$ forces toroidal structure at all scales from Planck length (\$10\textasciicircum{}\{-35\}\$ m) to cosmic radius (\$10\textasciicircum{}\{26\}\$ m)---a span of 61 orders of magnitude. We validate predictions including: wavelength quantization (\$\textbackslash{}lambda = \textbackslash{}pi R\_\textbackslash{}oplus \textbackslash{}approx 20\{,\}015\$ km), semidiurnal

\paragraph{Canonical Equation.}
\[
\alpha \approx 1/137.036
\]

\paragraph{Dictionary.}
Relation: α ≈ 1/137.036 — α ≈ 1/137.036

\paragraph{Encyclopedia.}
Relation: α ≈ 1/137.036 is a scaling / order-of-magnitude relation, written α ≈ 1/137.036. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from α. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
