\tzpanchor{0335}
\tzpentryheader{0335}{Gravitational Emergence Modification to Einstein Equations}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{dcfb1350-16cb-5fcd-92b2-2f9f921b33fd}}\\
\textbf{PiID} & \tzpcode{9254091715364} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{342}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1300.8794 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.1434 rad}\\
\textbf{TZPID} & \tzpcode{ID0335} & \textbf{Node Dependencies}\quad \tzpidref{0334}\\
\textbf{Registry} & \tzpcode{registry\_id\_0335} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Modified Einstein Equation & Far-Field Vanishing\\
\textbf{Closure Support} & TZP Divergence & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
TZP singularities introduce additional source terms into the Einstein equations, altering spacetime curvature.

\tzpsection{Canonical Equation}
\[
R_{\mu\nu}-\frac{1}{2}g_{\mu\nu}R+\Lambda g_{\mu\nu}=\frac{8\pi G}{c^4}T_{\mu\nu}+\Phi_{\mu\nu}^{\mathrm{TZP}}
\]
\[
\Phi_{\mu\nu}^{\mathrm{TZP}} \to 0 \qquad \text{far from the TZP}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $R_{\mu\nu}$: source equation symbol.
    \item $\mu$: source equation symbol.
    \item $g_{\mu\nu}$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\Lambda$: lemniscatic representative or canonical branch object.
    \item $\pi$: source equation symbol.
    \item $G$: source equation symbol.
    \item $c$: speed of light or relativistic conversion factor.
    \item $T_{\mu\nu}$: source equation symbol.
    \item $\Phi_{\mu\nu}$: flux, phase, or topological map term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0335 generated source Wolfram model *)
ClearAll[K0335, Cr0335, T, R, A, W, I, N];
eq0335$1 = HoldForm[RMunu - (1/2)*gMunuR + Lambda*gMunu == ((8*Pi*G)/c^4)*TMunu + PhiMunu^TZP];
eq0335$2 = HoldForm[PhiMunu^TZP -> 0];
eq0335$3 = HoldForm[PhiMunu^TZP -> Infinity];

K0335 = HoldForm[{eq0335$1, eq0335$2, eq0335$3}];

N = "normalized TRAWIN closure object for Gravitational Emergence Modification to Einstein Equations";
I = "TZP Divergence integration/comparison layer";
W = "Far-Field Vanishing wave or operator carrier";
A = "Modified Einstein Equation admissible action/amplitude condition";
R = "Far-Field Vanishing rotation/curl preservation layer";
T = "Modified Einstein Equation local source condition";

Cr0335[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0335 = Cr0335[K0335];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Modified Einstein Equation local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Far-Field Vanishing rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Modified Einstein Equation admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Far-Field Vanishing wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TZP Divergence integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Gravitational Emergence Modification to Einstein Equations.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0335] Gravitational Emergence Modification to Einstein Equations}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Box_T G_T(x,x')
=
-\delta(x,x') .
\end{equation}

\paragraph{Primary Derivation.}
Let $G_T(x,x')$ be the Green function or propagator for a scalar field on the Trawinistic background.

The propagator is defined as the response at $x$ to a point source at $x'$.  
The appropriate wave operator is the Trawinistic d'Alembertian:

\begin{equation}
\Box_T .
\end{equation}

For a Green function, applying the wave operator returns the negative delta source:

\begin{equation}
\Box_T G_T(x,x')
=
-\delta(x,x') .
\end{equation}

Thus,

\begin{equation}
\boxed{
\Box_T G_T(x,x')
=
-\delta(x,x') .
}
\end{equation}

Boundary conditions are chosen to remain compatible with the TZP structure and may include exponential suppression induced by $V_T$.

\paragraph{Interpretation.}
The TZP propagator measures how field disturbances travel through a Trawinistic background with degenerate geometry and zero-point boundary structure.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Gravitational Emergence Modification to Einstein Equations by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Modified Einstein Equation}\par
\[
R_{\mu\nu}-\frac{1}{2}g_{\mu\nu}R+\Lambda g_{\mu\nu}=\frac{8\pi G}{c^4}T_{\mu\nu}+\Phi_{\mu\nu}^{\mathrm{TZP}}
\]
\noindent This fixes the Einstein equation modified by the topological singularity sector.\par
\noindent\textbf{2. Far-Field Vanishing}\par
\[
\Phi_{\mu\nu}^{\mathrm{TZP}} \to 0 \qquad \text{far from the TZP}
\]
\noindent This identifies the asymptotic regime in which the singular contribution decays away and classical gravity is recovered.\par
\noindent\textbf{3. TZP Divergence}\par
\[
\left\|\Phi_{\mu\nu}^{\mathrm{TZP}}\right\| \to \infty \qquad \text{at the TZP}
\]
\noindent This closes the entry by stating the singular concentration of the correction term at the zero-point locus itself.\par

\clearpage
\noindent\textbf{[ID 0335] Gravitational Emergence Modification to Einstein Equations}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Gravitational Emergence Modification to Einstein Equations is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} TZP singularities introduce additional source terms into the Einstein equations, altering spacetime curvature. \textbf{Contextual meaning:} The entry reads Gravitational Emergence Modification to Einstein Equations as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the gravitational-emergence modification directly, which is much closer to the sourced field-equation claim than the old certificate record shell. \textbf{Lemma support:} Modified Einstein Equation; Far-Field Vanishing; TZP Divergence.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP propagator measures how field disturbances travel through a Trawinistic background with degenerate geometry and zero-point boundary structure. \% ========================================================= \% QUATERNARY DERIVATION LAYER -- ID 0336 TO ID 0340 \% =========================================================.

\tzpsection{Equation Grounding}
Equation anchors: R sub mu u -ratio 1 2 g sub mu u R+Lambda g sub mu u =ratio 8pi G c to the power 4 T sub mu u +Phi sub mu u to the power TZP; Phi sub mu u to the power TZP to 0 ; far from the TZP; and left Phi sub mu u to the power TZP to infinity ; at the TZP. Proof route: show that the added TZP correction modifies Einstein dynamics locally while decaying away from the singular locus. Formalization route: prove that the stated far-field and singular-locus limits are consistent with the modified Einstein equation.

\tzpsection{Interpretive Role}
The entry now states the gravitational-emergence modification directly, which is much closer to the sourced field-equation claim than the old certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Topological Stress-Energy Injection}: The explicit addition of a non-standard source term to the right side of the general relativistic field equations.
\item \textbf{Asymptotic Classical Recovery}: The mathematical proof that singular quantum corrections rapidly vanish at macroscopic distances from the zero point.
\item \textbf{Geometric Curvature Divergence}: The localized disruption of spacetime smoothness directly at the coordinate location of the topological defect.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0335]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0335_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0335] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Gravitational Emergence Modification to Einstein Equations}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} tZP singularities introduce additional source terms into the Einstein equations,
altering spacetime curvature

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Gravitational Emergence Modification to Einstein Equations is valid as a
tensorial/geometric statement when the stated tensor fields are well formed on the
specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0335_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
