\tzpanchor{0070}
\tzpentryheader{0070}{Quantum Information Units}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7a88e214-d0d9-5aaf-a824-07a5c02605c7}}\\
\textbf{PiID} & \tzpcode{0628620899862} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{77}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{271.8255 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.4479 rad}\\
\textbf{TZPID} & \tzpcode{ID0070} & \textbf{Node Dependencies}\quad \tzpidref{0065}\\
\textbf{Registry} & \tzpcode{registry\_id\_0070} & \textbf{Scale}\quad finite-dimensional quantum subsystem\\
\textbf{LOC Classification} & QC174 quantum information units & QA278 finite-dimensional Hilbert spaces\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: hep-th, gr-qc & \\
\textbf{Primary Support} & Local Subsystem & Dimensional Invariant\\
\textbf{Closure Support} & Canonical Model Space & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A quantum information unit (qunit) in the Trawinistic framework is defined as a minimal Hilbert space of dimension ddd associated with a quantum subsystem; its implementation may be qubit (d=2d=2d=2) or higher-dimensional, with states encoded in curvature-protected degrees of freedom.

\tzpsection{Canonical Equation}
\[
\mathcal{H}_{\mathrm{qunit}} \cong \mathbb{C}^{d}
\]
\[
\dim \mathcal{H}_{\mathrm{qunit}} = d
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{H}_{\mathrm{qunit}}$: source equation symbol.
    \item $C$: speed of light or relativistic conversion factor.
    \item $\mathcal{K}_{0070}$: canonical registry object for entry ID 0070.
    \item $\cong$: source equation symbol.
    \item $\dim$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0070 generated source Wolfram model *)
ClearAll[K0070, Cr0070, T, R, A, W, I, N];
eq0070$1 = HoldForm[HQunitcong*C^d];
eq0070$2 = HoldForm[Dim*HQunit == d];
eq0070$3 = HoldForm[HQunit];

K0070 = HoldForm[{eq0070$1, eq0070$2, eq0070$3}];

N = "normalized TRAWIN closure object for Quantum Information Units";
I = "Canonical Model Space integration/comparison layer";
W = "Dimensional Invariant wave or operator carrier";
A = "Local Subsystem admissible action/amplitude condition";
R = "Dimensional Invariant rotation/curl preservation layer";
T = "Local Subsystem local source condition";

Cr0070[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0070 = Cr0070[K0070];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Local Subsystem local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Dimensional Invariant rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Local Subsystem admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Dimensional Invariant wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Canonical Model Space integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum Information Units.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0070] Quantum Information Units}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
m_A = gv.
\end{equation}

\paragraph{Primary Derivation.}
Gauge field interacting with scalar vacuum acquires mass.

Thus:
\begin{equation}
\boxed{
m_A = gv.
}
\end{equation}

\paragraph{Interpretation.}
Gauge symmetry breaking generates massive vector bosons.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum Information Units by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Local Subsystem}\par
\[
\mathcal{H}_{\mathrm{qunit}}
\]
\noindent This identifies the finite subsystem used to store quantum information.\par
\noindent\textbf{2. Dimensional Invariant}\par
\[
\dim \mathcal{H}_{\mathrm{qunit}} = d
\]
\noindent This fixes the information capacity of the unit.\par
\noindent\textbf{3. Canonical Model Space}\par
\[
\mathcal{H}_{\mathrm{qunit}} \cong \mathbb{C}^{d}
\]
\noindent This closes the progression by identifying the standard finite-dimensional realization of the unit.\par

\clearpage
\noindent\textbf{[ID 0070] Quantum Information Units}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum Information Units is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A quantum information unit (qunit) in the Trawinistic framework is defined as a minimal Hilbert space of dimension ddd associated with a quantum subsystem; its implementation may be qubit (d=2d=2d=2) or higher-dimensional, with states encoded in curvature-protected degrees of freedom. \textbf{Contextual meaning:} The entry reads Quantum Information Units as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry is the doorway from abstract quantum theory into information processing. It supplies the unit from which qubits, higher-dimensional qudits, and channel constructions are built. \textbf{Lemma support:} Local Subsystem; Dimensional Invariant; Canonical Model Space.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Gauge symmetry breaking generates massive vector bosons. \% CANONICAL PDF-ALIGNED VERSION.

\tzpsection{Equation Grounding}
Equation anchors: A quantum information unit (qunit) in the Trawinistic framework is defined as a minimal Hilbert space of dimension ddd associated with a quantum subsystem; its implementation may be qubit (d=2d=2d=2) or higher-dimensional, with states encoded in curvature-protected degrees of freedom. A quantum information unit (qunit) in the Trawinistic framework is defined as a minimal Hilbert space of dimension ddd associated with a quantum subsystem; its implementation may be qubit (d=2d=2d=2) or higher-dimensional, with states encoded in curvature-protected degrees of freedom.

\tzpsection{Interpretive Role}
This entry is the doorway from abstract quantum theory into information processing. It supplies the unit from which qubits, higher-dimensional qudits, and channel constructions are built.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{State-Level Information Units}: alternate wording for the entry's information balance, coherence state, or entropy role.
\item \textbf{State-Level Quantum-State Analogue}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Terminology}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0070]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0070_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0070] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum Information Units}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a quantum information unit (qunit) in the Trawinistic framework is defined as a minimal
Hilbert space of dimension ddd associated with a quantum su...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum Information Units is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0070_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
