\tzpanchor{0385}
\tzpentryheader{0385}{Critical Magnetic Reynolds Number}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{4ea07247-3048-5d4a-85c9-73fa80d06679}}\\
\textbf{PiID} & \tzpcode{4695194151160} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{392}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1495.0405 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.4634 rad}\\
\textbf{TZPID} & \tzpcode{ID0385} & \textbf{Node Dependencies}\quad \tzpidref{0384}\\
\textbf{Registry} & \tzpcode{registry\_id\_0385} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Dimensionless Ratio & Critical Regime\\
\textbf{Closure Support} & Normalized Threshold & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A gyromagnetic system exhibits a phase transition to self-organised dynamo action when the magnetic Reynolds number exceeds a critical value on the order of 1 000. Above this threshold, spontaneous magnetic field amplification occurs.

\tzpsection{Canonical Equation}
\[
R_m=\mu_0\sigma vL
\]
\[
R_m=\mu_0\sigma L^2\omega
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $R_m$: source equation symbol.
    \item $\mu_0$: vacuum permeability constant.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $\omega$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0385 generated source Wolfram model *)
ClearAll[K0385, Cr0385, T, R, A, W, I, N];
eq0385$1 = HoldForm[RM == mu0*sigma*vL];
eq0385$2 = HoldForm[RM == mu0*sigma*L^2*omega];
eq0385$3 = HoldForm[RM == vL/eta];

K0385 = HoldForm[{eq0385$1, eq0385$2, eq0385$3}];

N = "normalized TRAWIN closure object for Critical Magnetic Reynolds Number";
I = "Normalized Threshold integration/comparison layer";
W = "Critical Regime wave or operator carrier";
A = "Dimensionless Ratio admissible action/amplitude condition";
R = "Critical Regime rotation/curl preservation layer";
T = "Dimensionless Ratio local source condition";

Cr0385[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0385 = Cr0385[K0385];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Dimensionless Ratio local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Critical Regime rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Dimensionless Ratio admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Critical Regime wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Threshold integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Critical Magnetic Reynolds Number.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0385] Critical Magnetic Reynolds Number}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Source Term.}
\begin{equation}
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}.
\end{equation}

\paragraph{Electromagnetic Torque Integral.}
\begin{equation}
\boldsymbol{\tau}_{\mathrm{em}}
=
\int_V
\mathbf{r}\times
\left(
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}
\right)
\,\mathrm{d}V .
\end{equation}

\paragraph{Angular Momentum Generation Law.}
\begin{equation}
\frac{\mathrm{d}\mathbf{L}}{\mathrm{d}t}
=
\boldsymbol{\tau}_{\mathrm{em}} .
\end{equation}

\paragraph{Primary Derivation.}
The local electromagnetic force density is:
\begin{equation}
\mathbf{f}_{\mathrm{em}}
=
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}.
\end{equation}

Torque density is position crossed with force density:
\begin{equation}
\mathbf{r}\times\mathbf{f}_{\mathrm{em}}.
\end{equation}

Integrating over a source region $V$ gives:
\begin{equation}
\boldsymbol{\tau}_{\mathrm{em}}
=
\int_V
\mathbf{r}\times
\left(
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}
\right)
\,\mathrm{d}V .
\end{equation}

The angular momentum generation law is therefore:
\begin{equation}
\boxed{
\frac{\mathrm{d}\mathbf{L}}{\mathrm{d}t}
=
\boldsymbol{\tau}_{\mathrm{em}} .
}
\end{equation}

\paragraph{Interpretation.}
Angular momentum is modeled as continuously generated by local electromagnetic source terms rather than assumed as a primordial input.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Critical Magnetic Reynolds Number by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Dimensionless Ratio}\par
\[
R_m=\mu_0\sigma vL
\]
\noindent This defines the transport-to-diffusion balance that controls the magnetic regime.\par
\noindent\textbf{2. Critical Regime}\par
\[
R_m=\mu_0\sigma L^2\omega
\]
\noindent This marks the onset of the self-organizing dynamo window.\par
\noindent\textbf{3. Normalized Threshold}\par
\[
R_m=\frac{vL}{\eta}
\]
\noindent This closes the entry by normalizing the actual regime against the critical threshold.\par

\clearpage
\noindent\textbf{[ID 0385] Critical Magnetic Reynolds Number}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Critical Magnetic Reynolds Number is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A gyromagnetic system exhibits a phase transition to self-organised dynamo action when the magnetic Reynolds number exceeds a critical value on the order of 1 000. Above this threshold, spontaneous magnetic field amplification occurs. \textbf{Contextual meaning:} The entry reads Critical Magnetic Reynolds Number as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry gives the later dynamo closure pages an actual diagnostic parameter instead of a purely verbal regime claim. \textbf{Lemma support:} Dimensionless Ratio; Critical Regime; Normalized Threshold.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Angular momentum is modeled as continuously generated by local electromagnetic source terms rather than assumed as a primordial input.

\tzpsection{Equation Grounding}
Equation anchors: R sub m=mu sub 0sigma vL; R sub m=mu sub 0sigma L to the power 2omega; and R sub m=ratio vL eta. Proof route: show that exceeding the critical ratio is necessary for the self-excited magnetic regime stated in the surrounding arc. Formalization route: prove that the normalized dynamo ratio is dimensionless and monotone in the stated transport variables.

\tzpsection{Interpretive Role}
The entry gives the later dynamo closure pages an actual diagnostic parameter instead of a purely verbal regime claim.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Advection-Diffusion Dominance Ratio}: The specific number telling you whether a magnetic field is being dragged along by the fluid or if it's slipping through like ghost.
\item \textbf{Dynamo Self-Excitation Point}: The precise speed the fluid must reach before it stops just stretching the magnetic field and starts actively creating new magnetic energy.
\item \textbf{Conductivity-Length Scaling Factor}: The metric showing how the size of the system and its ability to carry current combine to determine its overall magnetic stability.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0385]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0385_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0385] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Critical Magnetic Reynolds Number}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a gyromagnetic system exhibits a phase transition to self-organised dynamo action when
the magnetic Reynolds number exceeds a critical value on the...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Critical Magnetic Reynolds Number is valid as a formal registry statement when its
source equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that a gyromagnetic system exhibits a phase transition to
self-organised dynamo action when the magnetic Reynolds number exceeds a critical value
on the order of 1 000. Above this threshold, spontaneous magnetic field amplification
occurs. Angular momentum is modeled as continuously generated by local electromagnetic
source terms rather than assumed as a primordial input.. The CHL validation treats the
equation as the formal anchor and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0385_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
