\section*{ID9641: Definition of p\_i}
\paragraph{Metadata.}
PiID: 3840700707360 | RTEID: RTE:P37438.1440:T5.1379 | UUID: d49921e8-776c-5431-b04a-f0507e7b0717

\paragraph{Canonical Statement.}
roduct of these 18 qubits to create a pure quantum state in a \$2\textasciicircum{}\{18\}\$-dimensional Hilbert space. Normalize the resulting vector to unit length. \textbackslash{}subsection\{Quantum-to-Holographic-Wavefront Transformation\} Once a quantum state has been prepared corresponding to a particular DAANSphere address, the next stage converts this discrete quantum information into a continuous holographic wavefront suitable for optical propagation. Extract the address index by measuring the quantum state in the computational basis, yielding an integer from 1 to 153,600. Retrieve the corresponding Cartesian coordinates \$\textbackslash{}mathbf\{p\}\_i = (x\_i, y\_i, z\_i)\$ from the pre-computed Fibonacci sphere distribution. Convert to spherical angles \$\textbackslash{}theta\_i = \textbackslash{}arccos(z\_i)\$ and \$\textbackslash{}phi\_i = \textbackslash{}arctan(x\_i, y\_i)\$. Generate the complex wavefront amplitude at this point by evaluating the target intensity function \$I(\textbackslash{}theta, \textbackslash{}phi)\$ and combining with a phase pattern determined by the Gerchberg-Saxton algorithm or another phase retrieval method. The result is a complex number \$A\_i e\textasciicircum{}\{i\textbackslash{}varphi\_i\}\$ representing the holographic field value at address \$i\$. Decompose this co

\paragraph{Canonical Equation.}
\[
\mathbf{p}_i = (x_i, y_i, z_i)
\]

\paragraph{Dictionary.}
Definition of p\_i — p\_i = (x\_i, y\_i, z\_i)

\paragraph{Encyclopedia.}
Definition of p\_i is an algebraic definition, written p\_i = (x\_i, y\_i, z\_i). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from x\_i, y\_i, z\_i, defining p\_i. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
