\section*{ID9950: Relation: T\textasciicircum{}00,T\textasciicircum{}0i,T\textasciicircum{}ij}
\paragraph{Metadata.}
PiID: 4610126483699 | RTEID: RTE:P38638.0597:T0.8318 | UUID: 2f3570ba-4a30-5984-b07e-f4081d7ab9ea

\paragraph{Canonical Statement.}
ho\} F\_\{beta\}\{\}\textasciicircum{}\{rho\} pass \# (Use tensor libraries to avoid manual index mistakes.) Notes: • For index manipulations, using a tensor CAS (xAct for Mathematica, einsteinpy or sympy.tensor) avoids index-order errors. • Keep expressions symbolic as long as possible; only substitute numeric parameters (e.g., fixed rotation rate \$\textbackslash{}omega\$) at the end. 9. Simplifications for slow rotation / near-field If rotation speed is nonrelativistic, expand in small parameter \$\textbackslash{}beta = |\textbackslash{}omega\textbackslash{}times r|/c\$ and keep up to \$\textbackslash{}mathcal\{O\}(\textbackslash{}beta)\$ or \$\textbackslash{}mathcal\{O\}(\textbackslash{}beta\textasciicircum{}2)\$ as needed. Provide these approximate forms for \$T\textasciicircum{}\{00\},T\textasciicircum{}\{0i\},T\textasciicircum{}\{ij\}\$ for readability and physical interpretation. 10. Checklist / deliverables you can request next • Full symbolic expansion of \$T\textasciicircum{}\{\textbackslash{}mu\textbackslash{}nu\}\$ components using the exact metric and \$A\_\{\textbackslash{}rm total\}\$ from your notes (I will substitute your explicit metric and potential and produce the long component expressions). • A runnable SymPy notebook (.ipynb) that computes \$T\textasciicircum{}\{\textbackslash{}mu\textbackslash{}nu\}\$, performs the 3+1 decomposition at sample points, and diagonalizes \$S\textasciicircum{}i\{\}\_j\$. • A first-order expansion in \$\textbackslash{}beta\$ with simplifie

\paragraph{Canonical Equation.}
\[
T^{00},T^{0i},T^{ij}
\]

\paragraph{Dictionary.}
Relation: T\textasciicircum{}00,T\textasciicircum{}0i,T\textasciicircum{}ij — T\textasciicircum{}00,T\textasciicircum{}0i,T\textasciicircum{}ij

\paragraph{Encyclopedia.}
Relation: T\textasciicircum{}00,T\textasciicircum{}0i,T\textasciicircum{}ij is a symbolic expression, written T\textasciicircum{}00,T\textasciicircum{}0i,T\textasciicircum{}ij. It introduces a symbol or relation used elsewhere in the framework. It is built from T, j. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
