\tzpanchor{0068}
\tzpentryheader{0068}{Berry Phase and Geometric Phase Effects}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{24c97b56-7ceb-5c0b-8500-d74713947725}}\\
\textbf{PiID} & \tzpcode{6406286208998} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{75}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{264.0591 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.4351 rad}\\
\textbf{TZPID} & \tzpcode{ID0068} & \textbf{Node Dependencies}\quad \tzpidref{0020}\\
\textbf{Registry} & \tzpcode{registry\_id\_0068} & \textbf{Scale}\quad adiabatic quantum transport\\
\textbf{LOC Classification} & QC174 geometric phases & QA614 holonomy\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: math-ph, gr-qc & \\
\textbf{Primary Support} & Closed Adiabatic Path & Berry Phase Integral\\
\textbf{Closure Support} & TRAWIN-Extended Total Phase & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Slow changes in parameters lead to geometric phases that depend on the path, not just the end points; curvature and topology modify these phases.

\tzpsection{Canonical Equation}
\[
\gamma_{\mathrm{B}}
=
i\oint_{\Gamma}\langle \psi \mid \nabla_{\lambda}\psi\rangle\cdot d\lambda
\]
\[
\gamma_{\mathrm{tot}}
=
\gamma_{\mathrm{dyn}} + \gamma_{\mathrm{B}} + \gamma_{\mathrm{L}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\gamma_{\mathrm{B}}$: source equation symbol.
    \item $\lambda$: cosmological or lemniscatic branch parameter in the entry relation.
    \item $\gamma_{\mathrm{tot}}$: source equation symbol.
    \item $\gamma_{\mathrm{dyn}}$: source equation symbol.
    \item $\gamma_{\mathrm{L}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0068 generated source Wolfram model *)
ClearAll[K0068, Cr0068, T, R, A, W, I, N];
eq0068$1 = HoldForm[gammaB == iContourIntegralGammaInner[psi, GradLambdapsi]*dlambda];
eq0068$2 = HoldForm[gammaTot == gammaDyn + gammaB + gammaL];
eq0068$3 = HoldForm[Gamma];

K0068 = HoldForm[{eq0068$1, eq0068$2, eq0068$3}];

N = "normalized TRAWIN closure object for Berry Phase and Geometric Phase Effects";
I = "TRAWIN-Extended Total Phase integration/comparison layer";
W = "Berry Phase Integral wave or operator carrier";
A = "Closed Adiabatic Path admissible action/amplitude condition";
R = "Berry Phase Integral rotation/curl preservation layer";
T = "Closed Adiabatic Path local source condition";

Cr0068[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0068 = Cr0068[K0068];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Closed Adiabatic Path local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Berry Phase Integral rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Closed Adiabatic Path admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Berry Phase Integral wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TRAWIN-Extended Total Phase integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Berry Phase and Geometric Phase Effects.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0068] Berry Phase and Geometric Phase Effects}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
V(\phi) = \lambda(\phi^2 - v^2)^2.
\end{equation}

\paragraph{Primary Derivation.}
Potential admits degenerate minima at:
\begin{equation}
\phi = \pm v.
\end{equation}

Choice of vacuum breaks symmetry.

\paragraph{Interpretation.}
Vacuum selection induces broken symmetry.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Berry Phase and Geometric Phase Effects by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Closed Adiabatic Path}\par
\[
\Gamma
\]
\noindent This is the parameter-space loop along which the state is transported.\par
\noindent\textbf{2. Berry Phase Integral}\par
\[
\gamma_{\mathrm{B}}
=
i\oint_{\Gamma}\langle \psi \mid \nabla_{\lambda}\psi\rangle\cdot d\lambda
\]
\noindent This extracts the geometric phase from adiabatic transport.\par
\noindent\textbf{3. TRAWIN-Extended Total Phase}\par
\[
\gamma_{\mathrm{tot}}
=
\gamma_{\mathrm{dyn}} + \gamma_{\mathrm{B}} + \gamma_{\mathrm{L}}
\]
\noindent This closes the progression by incorporating lemniscatic winding into the phase budget.\par

\clearpage
\noindent\textbf{[ID 0068] Berry Phase and Geometric Phase Effects}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Berry Phase and Geometric Phase Effects is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Slow changes in parameters lead to geometric phases that depend on the path, not just the end points; curvature and topology modify these phases. \textbf{Contextual meaning:} The entry reads Berry Phase and Geometric Phase Effects as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry links observer transport, topological structure, and state evolution. It shows how geometry leaves a directly measurable trace in quantum phase accumulation. \textbf{Lemma support:} Closed Adiabatic Path; Berry Phase Integral; TRAWIN-Extended Total Phase.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Vacuum selection induces broken symmetry.

\tzpsection{Equation Grounding}
Equation anchors: For a quantum system undergoing adiabatic evolution along a closed path Gamma in parameter space, the Berry phase is gammaB=i Gammapsi  ablalambdapsi dlambdagamma B = itextbackslash oint Gamma textbackslash psitextbar abla lambda textbackslash psi dot d lambdagammaB=i Gammapsi  ablalambdapsi dlambda; in the Trawinistic framework, additional phases arise from curvature and lemniscatic winding. For a quantum system undergoing adiabatic evolution along a closed path Gamma in parameter space, the Berry phase is gammaB=i Gammapsi  ablalambdapsi dlambdagamma B = itextbackslash oint Gamma textbackslash psitextbar abla lambda textbackslash psi dot d lambdagammaB=i Gammapsi  ablalambdapsi dlambda; in the Trawinistic framework, additional phases arise from curvature and lemniscatic winding.

\tzpsection{Interpretive Role}
This entry links observer transport, topological structure, and state evolution. It shows how geometry leaves a directly measurable trace in quantum phase accumulation.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Geometric Phase Cycle Angle Geometric Cycle Angle Effects}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\item \textbf{Geometric Phase Cycle Angle Cycle Angle Geometric Analogue}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\item \textbf{Cycle Angle Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0068]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0068_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0068] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Berry Phase and Geometric Phase Effects}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} slow changes in parameters lead to geometric phases that depend on the path, not just
the end points; curvature and topology modify these phases

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Berry Phase and Geometric Phase Effects is valid when the stated geometric or
topological relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0068_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
