\section*{ID9180: Definition of ∫\_ΣF/(2π)c1}
\paragraph{Metadata.}
PiID: 6236256125216 | RTEID: RTE:P35647.9787:T2.1882 | UUID: fb7592b2-6623-5888-8d10-172cdec1b230

\paragraph{Canonical Statement.}
ifiability / Test Handle: Discovery of symmetries outside U(1)× SU(2)× SU(3)× Diff(M)U(1) \textbackslash{}times SU(2) \textbackslash{}times SU(3) \textbackslash{}times \textbackslash{}text\{Diff\}(\textbackslash{}mathcal\{M\})U(1)× SU(2)× SU(3)× Diff(M) or failure to define such a bundle would falsify this entry. 2.0.13 ID 162: Associated Bundles and Vacuum Extraction Type: Definition Formal Statement: From the principal bundle one constructs associated bun- dles: the gravitational tangent bundle, an electromagnetic line bundle with first Chern class c1= \$∫ ΣF/(2π)c\_1\$ = \$\textbackslash{}int\_\{\textbackslash{}Sigma\}F/(2\textbackslash{}pi)c1 =∫ΣF/(2π), anuclearvectorbundleofrank8, andavacuumextractionbundletrivializingintoL2(R)LΘ2(\textbackslash{}mathbb\{R\})L2(R).\$ Interpretive Meaning: Each fundamental interaction corresponds to an associated bundle derived from the principal bundle; the vacuum extraction bundle encodes Hilbertspace valued fibers for zeropoint energy extraction. Dependencies: ID 161 Derivable Consequences: Determines how matter and field representations are fibered; ensures gauge invariance of particle fiel

\paragraph{Canonical Equation.}
\[
\int_{\Sigma}F/(2\pi)c1 =∫ΣF/(2π), anuclearvectorbundleofrank8, andavacuumextractionbundletrivializingintoL2(R)LΘ2(\mathbb{R})L2(R).
\]

\paragraph{Dictionary.}
Definition of ∫\_ΣF/(2π)c1 — ∫\_ΣF/(2π)c1 =∫ΣF/(2π), anuclearvectorbundleofrank8, andavacuumextractionbundletrivializingintoL2(R)LΘ2(R)L2(R).

\paragraph{Encyclopedia.}
Definition of ∫\_ΣF/(2π)c1 is an integral expression, written ∫\_ΣF/(2π)c1 =∫ΣF/(2π), anuclearvectorbundleofrank8, andavacuumextractionbundletr. It is obtained by integrating over a domain, accumulating contributions across the region of interest. It is built from F, a, n, u, c, l, defining ∫\_ΣF/(2π)c1. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
