\section*{ID9469: Definition of)±Ωdrag 𝐷𝑒𝑙𝑡𝑎𝜔}
\paragraph{Metadata.}
PiID: 4716050492212 | RTEID: RTE:P36770.2299:T4.0374 | UUID: a28d5b05-9cc9-536f-9e0e-0514bed80e3f

\paragraph{Canonical Statement.}
9] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0208], [ID 0200] Node registry\_id\_0209 Support Titles Base Dispersion; Frame Split; Mode Gap Test Handle If the dragged frame does not split the base dispersion into the stated branches, the entry fails. Canonical Equation Links 𝑜𝑚𝑒𝑔𝑎2 0=𝑐 2 𝑠𝑘 2 𝑜𝑚𝑒𝑔𝑎± (𝑘 )=𝜔0 (𝑘 \$)±Ωdrag 𝐷𝑒𝑙𝑡𝑎𝜔=𝜔+−𝜔−=2Ωdrag\$ [ID 0210] Dimensional Access Ladder TZPID ID0210 UUID f40541c6-f726-5fd8-8c43-d9d298e14719 Type Operator / Transfer Statement Scale transfer LOC Classification Working routing: QA329 operator theory; QA169 categorical structure arXiv Classification Primary: math.CT; Cross-list: math-ph, cs.LO Canonical Statement This entry develops Dimensional Access Ladder inside the information synchronization

\paragraph{Canonical Equation.}
\[
)±Ωdrag 𝐷𝑒𝑙𝑡𝑎𝜔=𝜔+−𝜔−=2Ωdrag
\]

\paragraph{Dictionary.}
Definition of)±Ωdrag 𝐷𝑒𝑙𝑡𝑎𝜔 — )±Ωdrag 𝐷𝑒𝑙𝑡𝑎𝜔=𝜔+−𝜔−=2Ωdrag

\paragraph{Encyclopedia.}
Definition of)±Ωdrag 𝐷𝑒𝑙𝑡𝑎𝜔 is an algebraic definition, written )±Ωdrag 𝐷𝑒𝑙𝑡𝑎𝜔=𝜔+−𝜔−=2Ωdrag. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from r, a, g, defining )±Ωdrag 𝐷𝑒𝑙𝑡𝑎𝜔. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
