\section*{ID9352: Relation: =lim𝑥→𝑝 ∥∇2Φ(𝑥) ∥ ∥∇Φ(𝑥) ∥2}
\paragraph{Metadata.}
PiID: 3727983940041 | RTEID: RTE:P36315.8929:T3.2888 | UUID: c0823dcf-d32d-5c68-ac34-8db7f8fe7351

\paragraph{Canonical Statement.}
regate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0004] Node registry\_id\_0008 Support Titles Hessian-to-Gradient Ratio; TZP Limit of Field Response; Normalized Non-Linearity Test Handle If measured fields near the proposed anchor never show singular enhancement of second-order response relative to first-order variation, the constant is unsupported. Canonical Equation Links 𝐾NL= \$∥∇2Φ∥ ∥∇Φ∥2\$ 𝐾TZP NL \$=lim𝑥→𝑝 ∥∇2Φ(𝑥) ∥ ∥∇Φ(𝑥) ∥2\$ 𝐾norm NL =NormalizeTRAWIN ( \$∥∇2Φ∥ ∥∇Φ∥2\$ , \$lim𝑥→𝑝\$ 𝐾NL , 𝑔norm ) [ID 0009] Hyper-Dimensional Span TZPID ID0009 UUID 10d00b66-ffcf-5948-945f-34443de537a2 Type Definition Scale hyper-dimensional LOC Classification Working routing: QA611.75 higher-dimensional geometry; QC174.17 field integration arXiv Classification Primary: hep-th Cross-list: math-ph, gr-qc Canonical Statement The hyper-dimensi

\paragraph{Canonical Equation.}
\[
=lim𝑥→𝑝 ∥∇2Φ(𝑥) ∥ ∥∇Φ(𝑥) ∥2
\]

\paragraph{Dictionary.}
Relation: =lim𝑥→𝑝 ∥∇2Φ(𝑥) ∥ ∥∇Φ(𝑥) ∥2 — =lim𝑥→𝑝 ∥∇2Φ(𝑥) ∥ ∥∇Φ(𝑥) ∥2

\paragraph{Encyclopedia.}
Relation: =lim𝑥→𝑝 ∥∇2Φ(𝑥) ∥ ∥∇Φ(𝑥) ∥2 is an algebraic definition, written =lim𝑥→𝑝 ∥∇2Φ(𝑥) ∥ ∥∇Φ(𝑥) ∥2. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from l, m. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
