\tzpanchor{0731}
\tzpentryheader{0731}{COLD-START COOLDOWN PROTOCOL}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{4040151c-b20e-5781-a8b6-5cafa7dff43c}}\\
\textbf{PiID} & \tzpcode{9813629774771} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{738}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2803.6863 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.6196 rad}\\
\textbf{TZPID} & \tzpcode{ID0731} & \textbf{Node Dependencies}\quad \tzpidref{0730}\\
\textbf{Registry} & \tzpcode{registry\_id\_0731} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records cold-start cooldown protocol through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0731}}:\mathcal{X}_{\mathrm{id0731}}\longrightarrow\mathcal{Y}_{\mathrm{id0731}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0731}})=\mathcal{O}_{\mathrm{id0731}}
\]
\[
\mathcal{O}_{\mathrm{id0731}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0731}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0731}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0731}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0731 generated source Wolfram model *)
ClearAll[K0731, Cr0731, T, R, A, W, I, N];
eq0731$1 = HoldForm[Oid0731[Xid0731] -> Yid0731];
eq0731$2 = HoldForm[NTRAWIN[OId0731] == OId0731];
eq0731$3 = HoldForm[Element[OId0731[x], YAdm]];

K0731 = HoldForm[{eq0731$1, eq0731$2, eq0731$3}];

N = "normalized TRAWIN closure object for COLD-START COOLDOWN PROTOCOL";
I = "COLD-START COOLDOWN PROTOCOL integration/comparison layer";
W = "COLD-START COOLDOWN PROTOCOL wave or operator carrier";
A = "COLD-START COOLDOWN PROTOCOL admissible action/amplitude condition";
R = "COLD-START COOLDOWN PROTOCOL rotation/curl preservation layer";
T = "COLD-START COOLDOWN PROTOCOL local source condition";

Cr0731[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0731 = Cr0731[K0731];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ COLD-START COOLDOWN PROTOCOL local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ COLD-START COOLDOWN PROTOCOL rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ COLD-START COOLDOWN PROTOCOL admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ COLD-START COOLDOWN PROTOCOL wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ COLD-START COOLDOWN PROTOCOL integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for COLD-START COOLDOWN PROTOCOL.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0731] COLD-START COOLDOWN PROTOCOL}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0731}}:\mathcal{X}_{\mathrm{id0731}}\longrightarrow\mathcal{Y}_{\mathrm{id0731}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0731}})=\mathcal{O}_{\mathrm{id0731}}
\]
\[
\mathcal{O}_{\mathrm{id0731}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0731}})=\mathcal{O}_{\mathrm{id0731}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. Interpreted through TRAWIN, the equation functions as the mapping carrier for the entry’s information content. Within the CHL view, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors COLD-START COOLDOWN PROTOCOL by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0731}}:\mathcal{X}_{\mathrm{id0731}}\longrightarrow\mathcal{Y}_{\mathrm{id0731}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0731}})=\mathcal{O}_{\mathrm{id0731}}
\]
\[
\mathcal{O}_{\mathrm{id0731}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0731] COLD-START COOLDOWN PROTOCOL}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
COLD-START COOLDOWN PROTOCOL is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} T(t) = T sub env exp(-alpha t) implies T sub bath <= 4.2 text K. \textbf{Contextual meaning:} The entry reads COLD-START COOLDOWN PROTOCOL as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, COLD-START COOLDOWN PROTOCOL is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: handoff = Join-Path; inbox = Join-Path; and cmdbox = Join-Path. Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Gradual Thermal Shock Prevention}: The painfully slow, highly monitored procedure of freezing the massive metal machine to ensure it doesn't shatter or snap from sudden temperature drops.
\item \textbf{Pre-Ignition Baseline Reset}: The operational requirement to drag the entire system down to absolute zero, forcing all the chaotic, bouncing atoms into a completely still, silent resting state.
\item \textbf{Cryogenic Stabilization Window}: The mandatory waiting period proving that the deep freeze has evenly penetrated all the way to the core before any high-voltage energy is injected.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0731]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0731].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0731] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont COLD-START COOLDOWN PROTOCOL}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} COLD-START COOLDOWN PROTOCOL is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``COLD-START COOLDOWN PROTOCOL is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0731].
\par\endgroup
\vfill
\endgroup
\endgroup
