\tzpanchor{0030}
\tzpentryheader{0030}{TZP-Modified Hamiltonian Operator}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{dab5c87f-69b6-5a8c-9d7d-d6e427a32dd5}}\\
\textbf{PiID} & \tzpcode{5028841971693} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{37}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{116.4967 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.1920 rad}\\
\textbf{TZPID} & \tzpcode{ID0030} & \textbf{Node Dependencies}\quad \tzpidref{0029}\\
\textbf{Registry} & \tzpcode{registry\_id\_0030} & \textbf{Scale}\quad quantum-hamiltonian\\
\textbf{LOC Classification} & QC174.45 Hamiltonian operators & QA320 operator methods\\
\textbf{arXiv Classification} & Primary: hep-th \quad Cross-list: quant-ph, gr-qc & \\
\textbf{Primary Support} & Hamiltonian Density Input & Hypersurface Integration\\
\textbf{Closure Support} & State Action & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The TZP-modified Hamiltonian acts on a state $|\Psi\rangle$ as $H_{\mathrm{T}}|\Psi\rangle=\int_{\Sigma}\mathcal{H}_{\mathrm{T}}\,d\Sigma\,|\Psi\rangle$, where $\mathcal{H}_{\mathrm{T}}$ is the Hamiltonian density of ID 0029.

\tzpsection{Canonical Equation}
\[
H_{\mathrm{T}}\lvert\Psi\rangle
=
\int_{\Sigma}\mathcal{H}_{\mathrm{T}}\,d\Sigma\;\lvert\Psi\rangle
\]
\[
\Sigma \cap \{p\} = \varnothing
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H_{\mathrm{T}}$: source equation symbol.
    \item $\Psi$: wavefunction or state carrier for the entry equation.
    \item $\Sigma$: conductivity or coupling coefficient in the source equation.
    \item $\cap$: source equation symbol.
    \item $\varnothing$: source equation symbol.
    \item $P$: source equation symbol.
    \item $S$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0030 generated source Wolfram model *)
ClearAll[K0030, Cr0030, T, R, A, W, I, N];
eq0030$1 = HoldForm[HTAbs[Psi] == IntegralSigmaHT*dSigma*Abs[Psi]];
eq0030$2 = HoldForm[Sigmacap*{p} == varnothing];
eq0030$3 = HoldForm[HT];
eq0030$4 = HoldForm[IntegralSigmaHT*dSigma];

K0030 = HoldForm[{eq0030$1, eq0030$2, eq0030$3, eq0030$4}];

N = "normalized TRAWIN closure object for TZP-Modified Hamiltonian Operator";
I = "State Action integration/comparison layer";
W = "Hypersurface Integration wave or operator carrier";
A = "Hamiltonian Density Input admissible action/amplitude condition";
R = "Hypersurface Integration rotation/curl preservation layer";
T = "Hamiltonian Density Input local source condition";

Cr0030[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0030 = Cr0030[K0030];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Hamiltonian Density Input local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Hypersurface Integration rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Hamiltonian Density Input admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Hypersurface Integration wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ State Action integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP-Modified Hamiltonian Operator.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0030] TZP-Modified Hamiltonian Operator}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
H_{\mathrm{T}}\lvert\Psi\rangle
=
\int_{\Sigma}\mathcal{H}_{\mathrm{T}}\,d\Sigma\;\lvert\Psi\rangle
\]
\[
\Sigma \cap \{p\} = \varnothing
\]

\paragraph{Primary Derivation.}
The identity \( H_{\mathrm{T}}\lvert\Psi\rangle \) is an operator relation. Applying the operator to the relevant function and using its algebraic properties (such as linearity, commutators, or derivative rules) leads to the displayed equality.
\paragraph{Equation Type.}
This statement is classified as a operator relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. From the TRAWIN perspective, the equation functions as the operator-level carrier for the entry’s information content. According to CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP-Modified Hamiltonian Operator by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Hamiltonian Density Input}\par
\[
\mathcal{H}_{\mathrm{T}}
\]
\noindent This supplies the local energy content that must be assembled into a full operator.\par
\noindent\textbf{2. Hypersurface Integration}\par
\[
\int_{\Sigma}\mathcal{H}_{\mathrm{T}}\,d\Sigma
\]
\noindent This builds the global operator from local density data on a regular slice.\par
\noindent\textbf{3. State Action}\par
\[
H_{\mathrm{T}}\lvert\Psi\rangle
=
\int_{\Sigma}\mathcal{H}_{\mathrm{T}}\,d\Sigma\;\lvert\Psi\rangle
\]
\noindent This closes the progression by turning the integrated density into a genuine operator acting on the state space.\par

\clearpage
\noindent\textbf{[ID 0030] TZP-Modified Hamiltonian Operator}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP-Modified Hamiltonian Operator is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The TZP-modified Hamiltonian acts on a state |Psi as H sub T |Psi=integral sub Sigma H sub T dSigma |Psi, where H sub T is the Hamiltonian density of ID 0029. \textbf{Contextual meaning:} The entry reads TZP-Modified Hamiltonian Operator as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This operator is the bridge between local field energetics and full state evolution. It provides the object later spectral, propagator, and quantum-thermodynamic entries can use as their canonical generator. \textbf{Lemma support:} Hamiltonian Density Input; Hypersurface Integration; State Action.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technical interpretation remains tied to the local registry and equation witness.

\tzpsection{Equation Grounding}
Equation anchors: The TZP-modified Hamiltonian HTH T HT acts on a state  PsitextbarPsi Psi as HT Psi=integralSigmaHT dSigma  PsirangleH T textbarPsi = integral Sigma H T textbackslash, d Sigmatextbackslash,textbarPsirangleHT Psi=integralSigmaHTdSigma Psi, where HT H T HT is the Hamiltonian density of ID ,029. The TZP-modified Hamiltonian HTH T HT acts on a state  PsitextbarPsi Psi as HT Psi=integralSigmaHT dSigma  PsirangleH T textbarPsi = integral Sigma H T textbackslash, d Sigmatextbackslash,textbarPsirangleHT Psi=integralSigmaHTdSigma Psi, where HT H T HT is the Hamiltonian density of ID ,029.

\tzpsection{Interpretive Role}
This operator is the bridge between local field energetics and full state evolution. It provides the object later spectral, propagator, and quantum-thermodynamic entries can use as their canonical generator.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Tzp Modified Energy Generator Mapping Rule}: operator-level synonym for the entry's map, rule, state transition, or procedure.
\item \textbf{Energy Generator Mapping Rule Variational Analogue}: operator-level synonym for the entry's map, rule, state transition, or procedure.
\item \textbf{Mapping Rule Terminology}: operator-level synonym for the entry's map, rule, state transition, or procedure.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0030]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0030_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0030] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP-Modified Hamiltonian Operator}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the TZP-modified Hamiltonian acts on a state | as H\_T|=\_H\_T d |, where H\_T is the
Hamiltonian density of ID 0029

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP-Modified Hamiltonian Operator is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0030_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
