\section*{ID9358: Definition of ∇𝜇∇𝜇𝜙 (∇𝜇∇𝜇+𝑚2+𝜉𝑅)𝜙}
\paragraph{Metadata.}
PiID: 3940041529700 | RTEID: RTE:P36339.1922:T3.3271 | UUID: 518fe12b-9890-5388-9884-af21b1fc5d28

\paragraph{Canonical Statement.}
ild. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0017], [ID 0019], [ID 0034] Node registry\_id\_0050 Support Titles Bundle-Valued Quantum Field; Covariant Wave Operator; Curved-Manifold Field Equation Test Handle If the curved background requires connection-compatible transport but the proposed field law is not covariant under admissible coordinate changes, this entry fails. Canonical Equation Links \$𝜙∈Γ (𝐸→𝑀\$ ) \$∇𝜇∇𝜇𝜙 (∇𝜇∇𝜇+𝑚2+𝜉𝑅)𝜙=0\$ [ID 0051] Zero-Point Fluctuations TZPID ID0051 UUID ff04e0f3-b9b1-5a10-921a-25089cf7a918 Type Quantum Commutator Law Scale vacuum commutator LOC Classification Working routing: QC174.12 vacuum fluctuations; QC174.17 field commutators arXiv Classification Primary: quant-ph Cross-list: hep-th, gr-qc Canonical Statement At the Trawin zero point, vacuum activity is registered by nontrivial field-mome

\paragraph{Canonical Equation.}
\[
∇𝜇∇𝜇𝜙 (∇𝜇∇𝜇+𝑚2+𝜉𝑅)𝜙=0
\]

\paragraph{Dictionary.}
Definition of ∇𝜇∇𝜇𝜙 (∇𝜇∇𝜇+𝑚2+𝜉𝑅)𝜙 — ∇𝜇∇𝜇𝜙 (∇𝜇∇𝜇+𝑚2+𝜉𝑅)𝜙=0

\paragraph{Encyclopedia.}
Definition of ∇𝜇∇𝜇𝜙 (∇𝜇∇𝜇+𝑚2+𝜉𝑅)𝜙 is an algebraic definition, written ∇𝜇∇𝜇𝜙 (∇𝜇∇𝜇+𝑚2+𝜉𝑅)𝜙=0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
