\section*{ID8946: TZP VACUUM ENERGY DENSITY Canonical Statutory Formula: ⟨ ρ\_vac ⟩\_TZP}
\paragraph{Metadata.}
PiID: 0323260927524 | RTEID: RTE:P34739.3047:T0.6910 | UUID: 14c116e6-215a-55c4-b5c7-1e480f3b4729

\paragraph{Canonical Statement.}
[ID 859] TZP VACUUM ENERGY DENSITY Canonical Statutory Formula: \$\textbackslash{}langle \textbackslash{}rho\_\{vac\} \textbackslash{}rangle\_\{TZP\} = \textbackslash{}frac\{\textbackslash{}hbar c\}\{a\textasciicircum{}4\} \textbackslash{}times \textbackslash{}nu\_T\textasciicircum{}2\$ Formal Technical Dissertation: The vacuum energy density at the zero point scales quadratically with the topological winding number \$\textbackslash{}nu\_T\$ and inversely with the fourth power of the scale parameter \$a\$. Source: [12]

\paragraph{Canonical Equation.}
\[
\langle \rho_{vac} \rangle_{TZP} = \frac{\hbar c}{a^4} \times \nu_T^2
\]

\paragraph{Dictionary.}
TZP VACUUM ENERGY DENSITY Canonical Statutory Formula: \$ \_vac \_TZP = ca\textasciicircum{}4 \_T\textasciicircum{}2\$ Formal Technical Dissertation: The vacuum energy density at the zero point scales quadratically with the topological winding number ν\_T and inversely with the fourth power of the scale parameter a.

\paragraph{Encyclopedia.}
TZP VACUUM ENERGY DENSITY Canonical Statutory Formula: ⟨ ρ\_vac ⟩\_TZP is an expectation / trace over state, written ⟨ ρ\_vac ⟩\_TZP = (ħ c)/(a\textasciicircum{}4) × ν\_T\textasciicircum{}2. It is computed as an expectation value or trace over a quantum state, producing an observable. It is built from ħ, c, a, T, defining ⟨ ρ\_vac ⟩\_TZP. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
