\tzpanchor{0672}
\tzpentryheader{0672}{ROUND-TRIP FIDELITY METRIC}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{12d03b9e-0c09-5d46-a4a6-6c1751a91d12}}\\
\textbf{PiID} & \tzpcode{5495853710507} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{679}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2582.3427 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.2549 rad}\\
\textbf{TZPID} & \tzpcode{ID0672} & \textbf{Node Dependencies}\quad \tzpidref{0671}\\
\textbf{Registry} & \tzpcode{registry\_id\_0672} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records round-trip fidelity metric through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
[q,p]=i\hbar.
\]
\[
[q,p]=qp-pq.
\]
\[
\boxed{ [q,p]=i\hbar. }
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
    \item $\mathcal{K}_{0672}$: canonical registry object for entry ID 0672.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0672 generated source Wolfram model *)
ClearAll[K0672, Cr0672, T, R, A, W, I, N];
eq0672$1 = HoldForm[Commutator[q, p] == ihbar];
eq0672$2 = HoldForm[Commutator[q, p] == qp - pq];
eq0672$3 = HoldForm[Commutator[q, p] == ihbar];

K0672 = HoldForm[{eq0672$1, eq0672$2, eq0672$3}];

N = "normalized TRAWIN closure object for ROUND-TRIP FIDELITY METRIC";
I = "Topological Closure integration/comparison layer";
W = "Compatibility Law wave or operator carrier";
A = "Geometric Carrier admissible action/amplitude condition";
R = "Compatibility Law rotation/curl preservation layer";
T = "Geometric Carrier local source condition";

Cr0672[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0672 = Cr0672[K0672];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Geometric Carrier local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Compatibility Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Geometric Carrier admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Compatibility Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for ROUND-TRIP FIDELITY METRIC.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0672] ROUND-TRIP FIDELITY METRIC}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
[q,p]=i\hbar .
\end{equation}

\paragraph{Primary Derivation.}
Continuous-variable quantum systems use observables with continuous spectra, such as position $q$ and momentum $p$.

The commutator is defined by
\begin{equation}
[q,p]=qp-pq .
\end{equation}

Canonical quantization imposes
\begin{equation}
\boxed{
[q,p]=i\hbar .
}
\end{equation}

In the Trawinistic extension, curvature may modify the phase-space volume element while preserving the canonical commutator as the primary algebraic witness.

\paragraph{Interpretation.}
Continuous-variable systems extend the registry from finite qubit states into infinite-dimensional Hilbert-space dynamics.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors ROUND-TRIP FIDELITY METRIC by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Geometric Carrier}\par
\[
[q,p]=i\hbar.
\]
\noindent This fixes the effective geometry or carrier space named by the entry title.\par
\noindent\textbf{2. Compatibility Law}\par
\[
[q,p]=qp-pq.
\]
\noindent This makes the geometry admissible by imposing its internal compatibility law.\par
\noindent\textbf{3. Topological Closure}\par
\[
\boxed{ [q,p]=i\hbar. }
\]
\noindent This closes the entry by tying the local structure to a global topological invariant.\par

\clearpage
\noindent\textbf{[ID 0672] ROUND-TRIP FIDELITY METRIC}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
ROUND-TRIP FIDELITY METRIC is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} F sub RT = |langle psi sub in | mathcal D (mathcal E (psi sub in )) rangle| to the power 2 > 0.999999. \textbf{Contextual meaning:} The entry reads ROUND-TRIP FIDELITY METRIC as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Geometric Carrier; Compatibility Law; Topological Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Continuous-variable systems extend the registry from finite qubit states into infinite-dimensional Hilbert-space dynamics.

\tzpsection{Equation Grounding}
Equation anchors: ratio 153 , 000 129 , 000 = 1; bd to the power bulk = u03b7 sub u03bcu03bd + (4G sub N/d) u222b d to the power d k T sub u03bcu03bd The file is too long and its contents have been truncated; and ity conservation:r H[u03a8recon] = Hobs (22)r The reconstruction algorithm employs spectral decomposition in the basis of spherical harufffemonics and. Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Signal-Degradation Echo Bouncing}: The brutally honest measurement of sending a perfectly crisp, clean piece of data across the room, bouncing it off the far wall, and weeping at how garbled and ruined it looks when it comes back.
\item \textbf{Quantum-State Survival Percentage}: The terrifyingly low, decimal-point number proving exactly what tiny fraction of the magical, superposed reality actually managed to survive the harsh, noisy, hot trip through the physical wires.
\item \textbf{Error-Accumulation Cycle Counting}: The depressing realization that every single time the computer thinks about the number, reads it, or writes it, it adds a tiny, unavoidable smudge of noise that slowly ruins the answer.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0672]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0672_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0672] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont ROUND-TRIP FIDELITY METRIC}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records round-trip fidelity metric through the Septenary derivation layer,
using the displayed relations as operational anchors for the c...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ROUND-TRIP FIDELITY METRIC is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0672_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
