\tzpanchor{0364}
\tzpentryheader{0364}{Unified Navigation and Temporal Winding}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{b0e5b7db-c033-51c4-b3f6-e92b5e2b7941}}\\
\textbf{PiID} & \tzpcode{3053054882046} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{371}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1413.4928 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.3290 rad}\\
\textbf{TZPID} & \tzpcode{ID0364} & \textbf{Node Dependencies}\quad \tzpidref{0363}\\
\textbf{Registry} & \tzpcode{registry\_id\_0364} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Depth Encoding Map & Variational Navigation Path\\
\textbf{Closure Support} & Persistence Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Unified Navigation and Temporal Winding entry receives the depth encoding and trajectory equations from the DAANSphereNavigationProtocol source, binding indexed depth, variational navigation, and persistence.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
u=\frac{X+1/2}{10^L+1},\qquad t=\alpha\log\!\frac{u}{1-u},\qquad r=e^t
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\gamma^\ast=\arg\min_{\gamma}\int_0^1\mathcal{L}(\gamma,\dot{\gamma},s)\,ds
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\lambda_{\max}(\gamma)<0
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $X$: source variable, local coordinate, or input state in the entry relation.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $t$: source equation symbol.
    \item $\gamma$: source equation symbol.
    \item $\lambda_{\max}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0364 generated source Wolfram model *)
ClearAll[K0364, Cr0364, T, R, A, W, I, N];
eq0364$1 = HoldForm[TZPSequence[$u == (X + 1/2)/(10^L + 1), t == alphalog[u/(1 - u)], r == e^t$]];
eq0364$2 = HoldForm[$gamma^ast == argminGammaIntegral0^1*L[gamma, dot[gamma], s]*ds$];
eq0364$3 = HoldForm[$lambdaMax[gamma] < 0*$];

K0364 = HoldForm[{eq0364$1, eq0364$2, eq0364$3}];

N = "normalized TRAWIN closure object for Unified Navigation and Temporal Winding";
I = "Persistence Condition integration/comparison layer";
W = "Variational Navigation Path wave or operator carrier";
A = "Depth Encoding Map admissible action/amplitude condition";
R = "Variational Navigation Path rotation/curl preservation layer";
T = "Depth Encoding Map local source condition";

Cr0364[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0364 = Cr0364[K0364];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Depth Encoding Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Variational Navigation Path rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Depth Encoding Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Variational Navigation Path wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Persistence Condition integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Unified Navigation and Temporal Winding.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0364] Unified Navigation and Temporal Winding}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\rho \rightarrow \frac{P \rho P}{\mathrm{Tr}(P\rho)}.
\end{equation}

\paragraph{Primary Derivation.}
Measurement with projector $P$ collapses the state.

Post-measurement state is:
\begin{equation}
\rho' = \frac{P \rho P}{\mathrm{Tr}(P\rho)}.
\end{equation}

\paragraph{Interpretation.}
Projection enforces classical outcome selection.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Unified Navigation and Temporal Winding by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Depth Encoding Map}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
u=\frac{X+1/2}{10^L+1},\qquad t=\alpha\log\!\frac{u}{1-u},\qquad r=e^t
$
\end{adjustbox}
\]
\noindent This places the source depth encoding on the unified navigation support page.\par
\noindent\textbf{2. Variational Navigation Path}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\gamma^\ast=\arg\min_{\gamma}\int_0^1\mathcal{L}(\gamma,\dot{\gamma},s)\,ds
$
\end{adjustbox}
\]
\noindent This records the trajectory selection rule for the navigation path.\par
\noindent\textbf{3. Persistence Condition}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\lambda_{\max}(\gamma)<0
$
\end{adjustbox}
\]
\noindent This closes the navigation page with the stability condition for persistent transport.\par

\clearpage
\noindent\textbf{[ID 0364] Unified Navigation and Temporal Winding}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Unified Navigation and Temporal Winding is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Navigation, beam steering, quantum state mapping and spatial addressing on the DAANSsphere operate on the same toroidal manifold. Temporal evolution may be interpreted as motion along a toroidal cycle rather than linear progression. \textbf{Contextual meaning:} The entry reads Unified Navigation and Temporal Winding as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Depth Encoding Map; Variational Navigation Path; Persistence Condition.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Projection enforces classical outcome selection.

\tzpsection{Equation Grounding}
Equation anchors: s sub 1=ratio 16 15 ,; s sub 2=ratio 10 9 ,; s sub 3=s sub 1 s sub 2=ratio 32 27; delta(s) := s-1; and chi := ratio 32 27 =1+ratio 5 27 =1.185185ldots. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spatiotemporal Helical Trajectories}: The interlocking of a particle's physical movement with a strictly defined periodic oscillation in its internal time phase.
\item \textbf{Chronological Loop Integrals}: The evaluation of how much 'time' a system accumulates when forced to travel along a closed physical circuit.
\item \textbf{Coupled Metric-Time Dilations}: The synchronization of local time progression with the physical twisting of the spatial navigation path.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0364]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0364_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0364] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Unified Navigation and Temporal Winding}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} navigation, beam steering, quantum state mapping and spatial addressing on the
DAANSsphere operate on the same toroidal manifold

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Unified Navigation and Temporal Winding is valid when the stated geometric or
topological relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0364_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
