\section*{ID7533: Quick Interpretation — What the Results Show: R\textasciicircum{}5/a\textasciicircum{}6}
\paragraph{Metadata.}
PiID: 7648236341433 | RTEID: RTE:P29252.3119:T4.2165 | UUID: f93fb7a5-4514-5981-89c1-8c7d146a8d73

\paragraph{Canonical Statement.}
\# Quick interpretation — what the results show 1. **DAT-GPT Synchronization Sphere (DSS)** - The analytic \textbackslash{}(a\_\{\textbackslash{}rm DSS\}\textbackslash{}) from the DAT-GPT timescale formula has an extremely strong dependence on object radius (\textbackslash{}(R\textasciicircum{}5\textbackslash{})) and distance (\textbackslash{}(a\textasciicircum{}6\textbackslash{})). For **km-scale bodies** the Sun’s DSS is *many orders of magnitude smaller than the asteroid belt or Kuiper belt*. In other words: the Sun cannot tidally synchronize km-sized objects at 2–4 AU (asteroid belt) or at Kuiper distances within typical system lifetimes. This matches the physical intuition we encoded in the model: tidal torque scales like \textbackslash{}(R\textasciicircum{}5/a\textasciicircum{}6\textbackslash{}) and is negligible for small bodies at large distances. - Put plainly: **DDS ≪ belt radii** for small bodies — so tidal synchronizing power from the Sun is not the reason for non-accretion of the belts.

\paragraph{Canonical Equation.}
\[
R^5/a^6
\]

\paragraph{Dictionary.}
Quick interpretation — what the results show 1 [ID7533]

\paragraph{Encyclopedia.}
Quick Interpretation — What the Results Show: R\textasciicircum{}5/a\textasciicircum{}6 is a symbolic expression, written R\textasciicircum{}5/a\textasciicircum{}6. It introduces a symbol or relation used elsewhere in the framework. It is built from R, a. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
