\section*{ID9051: Definition of ∫ ΣJΘμ, dΣ\_μQ}
\paragraph{Metadata.}
PiID: 5255640564482 | RTEID: RTE:P35147.0430:T1.3628 | UUID: 11627458-d9c2-5c61-83a2-2f574b4a3eb7

\paragraph{Canonical Statement.}
es: Determines contributions to the cosmological constant; influences vacuum polarisation; enters stress–energy tensor in field equations; relates to emergent rotation principle. Falsifiability / Test Handle: Measurement of vacuum energy density inconsistent with this integral formulation would falsify the definition. 0.0.27 ID 025: Conservation Law: TZP Topological Charge Type: Conservation Law Formal Statement: The topological charge QQQ associated with the TZP is defined by Q= \$∫ ΣJµdΣ\_µQ\$ = \$\textbackslash{}int \{\textbackslash{}Sigma\}JΘ\{\textbackslash{}mu\}, \textbackslash{}text\{d\}\textbackslash{}Sigma\_\{\textbackslash{}mu\}Q =∫ΣJµdΣ\_µ,whereJµJΘ\{\textbackslash{}mu\}Jµisaconservedcurrentsatisfying∇T\_µJµ=\$ \$0\textbackslash{}nabla\{\textbackslash{}text\{T\}\}\_\{\textbackslash{}mu\}J\{\textbackslash{}mu\}\$ = \$0∇T\_µJµ= 0andΣ\textbackslash{}SigmaΣisaspacelikehypersurfaceenclosingppp;QQQequalstheTrawinisticwindingnumberwww.\$ Interpretive Meaning: This law states that the topological charge associated with loops around the TZP is conserved. It equates the integral of a conserved current to the winding number defined earlier. Dependencies: ID 020, ID 017 Derivable Consequences:

\paragraph{Canonical Equation.}
\[
\int {\Sigma}JΘ{\mu}, \text{d}\Sigma_{\mu}Q =∫ΣJµdΣ_µ,whereJµJΘ{\mu}Jµisaconservedcurrentsatisfying∇T_µJµ=
\]

\paragraph{Dictionary.}
Definition of ∫ ΣJΘμ, dΣ\_μQ — ∫ ΣJΘμ, dΣ\_μQ =∫ΣJµdΣ\_µ,whereJµJΘμJµisaconservedcurrentsatisfying∇T\_µJµ=

\paragraph{Encyclopedia.}
Definition of ∫ ΣJΘμ, dΣ\_μQ is an integral expression, written ∫ ΣJΘμ, dΣ\_μQ =∫ΣJµdΣ\_µ,whereJµJΘμJµisaconservedcurrentsatisfying∇T\_µJµ=. It is obtained by integrating over a domain, accumulating contributions across the region of interest. It is built from μ, J, w, h, r, s, defining ∫ ΣJΘμ, dΣ\_μQ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
