\tzpanchor{0676}
\tzpentryheader{0676}{ATTRIBUTE ALLOCATION VIA METAMATERIAL MAPPING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{8c014865-7640-5496-afee-50c60aee1118}}\\
\textbf{PiID} & \tzpcode{8537105079227} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{683}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2597.8756 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.2805 rad}\\
\textbf{TZPID} & \tzpcode{ID0676} & \textbf{Node Dependencies}\quad \tzpidref{0675}\\
\textbf{Registry} & \tzpcode{registry\_id\_0676} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records attribute allocation via metamaterial mapping through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
S(\omega) = 2\hbar \coth\left( \frac{\hbar\omega}{2k_B T_{\mathrm{eff}}} \right) \operatorname{Im}R(\omega).
\]
\[
T_{\mathrm{eff}} = T_{\mathrm{eff}}^{\mathrm{th}} + T_{\mathrm{eff}}^{\mathrm{TZP}}.
\]
\[
\operatorname{Im}R(\omega).
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
    \item $k_B$: source equation symbol.
    \item $T_{\mathrm{eff}}$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0676 generated source Wolfram model *)
ClearAll[K0676, Cr0676, T, R, A, W, I, N];
eq0676$1 = HoldForm[S[omega] == 2*hbarcoth[hbaromega/(2*kB*TEff)]*ImR[omega]];
eq0676$2 = HoldForm[TEff == TEff^th + TEff^TZP];
eq0676$3 = HoldForm[ImR[omega]];

K0676 = HoldForm[{eq0676$1, eq0676$2, eq0676$3}];

N = "normalized TRAWIN closure object for ATTRIBUTE ALLOCATION VIA METAMATERIAL MAPPING";
I = "Normalized Output integration/comparison layer";
W = "Composable Action wave or operator carrier";
A = "Carrier Map admissible action/amplitude condition";
R = "Composable Action rotation/curl preservation layer";
T = "Carrier Map local source condition";

Cr0676[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0676 = Cr0676[K0676];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Carrier Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Composable Action rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Carrier Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Composable Action wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Output integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for ATTRIBUTE ALLOCATION VIA METAMATERIAL MAPPING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0676] ATTRIBUTE ALLOCATION VIA METAMATERIAL MAPPING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
S(\omega)
=
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right)
\operatorname{Im}R(\omega).
\end{equation}

\paragraph{Effective Temperature Split.}
\begin{equation}
T_{\mathrm{eff}}
=
T_{\mathrm{eff}}^{\mathrm{th}}
+
T_{\mathrm{eff}}^{\mathrm{TZP}} .
\end{equation}

\paragraph{Primary Derivation.}
Let $S(\omega)$ be the noise spectrum and $R(\omega)$ the response function.  
Dissipation is encoded by the imaginary part:
\begin{equation}
\operatorname{Im}R(\omega).
\end{equation}

The fluctuation factor is set by the effective thermal and zero-point scale:
\begin{equation}
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right).
\end{equation}

Multiplying the two pieces gives:
\begin{equation}
\boxed{
S(\omega)
=
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right)
\operatorname{Im}R(\omega).
}
\end{equation}

\paragraph{Interpretation.}
Noise and response are coupled through an effective temperature that includes ordinary thermal and TZP contributions.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors ATTRIBUTE ALLOCATION VIA METAMATERIAL MAPPING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Carrier Map}\par
\[
S(\omega) = 2\hbar \coth\left( \frac{\hbar\omega}{2k_B T_{\mathrm{eff}}} \right) \operatorname{Im}R(\omega).
\]
\noindent This names the entry as an actual map between carrier domains rather than a loose metaphor.\par
\noindent\textbf{2. Composable Action}\par
\[
T_{\mathrm{eff}} = T_{\mathrm{eff}}^{\mathrm{th}} + T_{\mathrm{eff}}^{\mathrm{TZP}}.
\]
\noindent This inserts the map into the ordered TRAWIN chain and makes composition explicit.\par
\noindent\textbf{3. Normalized Output}\par
\[
\operatorname{Im}R(\omega).
\]
\noindent This closes the entry by requiring that the output land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0676] ATTRIBUTE ALLOCATION VIA METAMATERIAL MAPPING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
ATTRIBUTE ALLOCATION VIA METAMATERIAL MAPPING is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A sub meta = text AssocThread [ text Pos, Ph, Amp, Topo -> text Partition [text IntDigits (C, 256], 64]]. \textbf{Contextual meaning:} The entry reads ATTRIBUTE ALLOCATION VIA METAMATERIAL MAPPING as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Noise and response are coupled through an effective temperature that includes ordinary thermal and TZP contributions.

\tzpsection{Equation Grounding}
Equation anchors: R sub mu u - tfrac 1 2 R ,g sub mu u + Lambda sub eff (r) ,g sub mu u = ratio 8pi G c to the power 4 , T sub mu u sub TZP ,; R sub mu u - tfrac 1 2 R ,g sub mu u + Lambda sub eff (r) ,g sub mu u = ratio 8pi G c to the power 4 , T sub mu u sub TZP , ; and \$ R sub mu u - tfrac 1 2 R ,g sub mu u + Lambda sub eff (r) ,g sub mu u = ratio 8pi G c to the power 4 , T sub mu u sub TZP ,. Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Physical Logic-Gate Engineering}: The mind-bending process of literally building the 'if/then' rules of a computer program directly into the physical shape, curves, and twists of a solid block of engineered metal.
\item \textbf{Spatially-Encoded Quantum Sorting}: The clever trick of making the invisible, bouncing energy naturally sort itself into the correct answer bins simply because the shape of the room physically forces it to go there.
\item \textbf{Hardware-Hardcoded Equation Solving}: The realization that the machine isn't actually 'calculating' the answer; the bizarre, twisted shape of the metal walls simply makes every wrong answer impossible to reach.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0676]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0676_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0676] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont ATTRIBUTE ALLOCATION VIA METAMATERIAL MAPPING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records attribute allocation via metamaterial mapping through the Septenary
derivation layer, using the displayed relations as operationa...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ATTRIBUTE ALLOCATION VIA METAMATERIAL MAPPING is valid when the stated operator maps
admissible inputs into the declared target class.''\\
\textbf{Proof:} The source statement is read as an operator or transformation. The proof obligation is
type preservation: admissible inputs must land in the target object without breaking the
stated constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- operator-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0676_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
