\tzpanchor{0738}
\tzpentryheader{0738}{BIPARTITION INFORMATION INTEGRATION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{2cd1476a-ff11-597d-9fb4-3b547ded3ae2}}\\
\textbf{PiID} & \tzpcode{7747713099605} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{745}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2830.8689 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.6644 rad}\\
\textbf{TZPID} & \tzpcode{ID0738} & \textbf{Node Dependencies}\quad \tzpidref{0737}\\
\textbf{Registry} & \tzpcode{registry\_id\_0738} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records bipartition information integration through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0738}}:\mathcal{X}_{\mathrm{id0738}}\longrightarrow\mathcal{Y}_{\mathrm{id0738}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0738}})=\mathcal{O}_{\mathrm{id0738}}
\]
\[
\mathcal{O}_{\mathrm{id0738}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0738}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0738}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0738}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0738 generated source Wolfram model *)
ClearAll[K0738, Cr0738, T, R, A, W, I, N];
eq0738$1 = HoldForm[Oid0738[Xid0738] -> Yid0738];
eq0738$2 = HoldForm[NTRAWIN[OId0738] == OId0738];
eq0738$3 = HoldForm[Element[OId0738[x], YAdm]];

K0738 = HoldForm[{eq0738$1, eq0738$2, eq0738$3}];

N = "normalized TRAWIN closure object for BIPARTITION INFORMATION INTEGRATION";
I = "BIPARTITION INFORMATION INTEGRATION integration/comparison layer";
W = "BIPARTITION INFORMATION INTEGRATION wave or operator carrier";
A = "BIPARTITION INFORMATION INTEGRATION admissible action/amplitude condition";
R = "BIPARTITION INFORMATION INTEGRATION rotation/curl preservation layer";
T = "BIPARTITION INFORMATION INTEGRATION local source condition";

Cr0738[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0738 = Cr0738[K0738];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ BIPARTITION INFORMATION INTEGRATION local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ BIPARTITION INFORMATION INTEGRATION rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ BIPARTITION INFORMATION INTEGRATION admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ BIPARTITION INFORMATION INTEGRATION wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ BIPARTITION INFORMATION INTEGRATION integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for BIPARTITION INFORMATION INTEGRATION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0738] BIPARTITION INFORMATION INTEGRATION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0738}}:\mathcal{X}_{\mathrm{id0738}}\longrightarrow\mathcal{Y}_{\mathrm{id0738}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0738}})=\mathcal{O}_{\mathrm{id0738}}
\]
\[
\mathcal{O}_{\mathrm{id0738}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The expression \( \mathcal{O}_{\mathrm{id0738}}:\mathcal{X}_{\mathrm{id0738}}\longrightarrow\mathcal{Y}_{\mathrm{id0738}} \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. From the TRAWIN perspective, the equation functions as the integral carrier for the entry’s information content. According to CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors BIPARTITION INFORMATION INTEGRATION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0738}}:\mathcal{X}_{\mathrm{id0738}}\longrightarrow\mathcal{Y}_{\mathrm{id0738}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0738}})=\mathcal{O}_{\mathrm{id0738}}
\]
\[
\mathcal{O}_{\mathrm{id0738}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0738] BIPARTITION INFORMATION INTEGRATION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
BIPARTITION INFORMATION INTEGRATION is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Phi sub TZP = min I(text partition ). \textbf{Contextual meaning:} The entry reads BIPARTITION INFORMATION INTEGRATION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, BIPARTITION INFORMATION INTEGRATION is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: Phi sub TZP = min I( partition ); mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Dual-Hemisphere Data Merging}: The final, brutal calculation that slams the answers from the left side of the machine and the right side of the machine together to see if they match.
\item \textbf{Cross-Boundary Coherence Verification}: The mathematical proof checking whether the invisible quantum thread stretched across the middle of the room actually survived the entire violent experiment.
\item \textbf{Split-State Recombination Logic}: The complex, delicate sewing process of taking a shredded, separated quantum idea and stitching it back together into one single, readable, and useful truth.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0738]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0738].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0738] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont BIPARTITION INFORMATION INTEGRATION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} BIPARTITION INFORMATION INTEGRATION is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``BIPARTITION INFORMATION INTEGRATION is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0738].
\par\endgroup
\vfill
\endgroup
\endgroup
