\tzpanchor{0293}
\tzpentryheader{0293}{Opposing Field Regions Correlation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{15708457-03fb-5f6d-a7c5-92f652caf331}}\\
\textbf{PiID} & \tzpcode{9141273724587} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{300}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1137.7841 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.8747 rad}\\
\textbf{TZPID} & \tzpcode{ID0293} & \textbf{Node Dependencies}\quad \tzpidref{0292}\\
\textbf{Registry} & \tzpcode{registry\_id\_0293} & \textbf{Scale}\quad diagnostic\\
\textbf{LOC Classification} & QA273 dimensionless analysis & QC statistical diagnostics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: nlin.PS, physics.data-an\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In the gyromagnetic correlation matrix, regions of opposing fields---pressed magnet anti-alignment in the laboratory and inner/outer core opposition in planets---show a correlation coefficient of 0.95.

\tzpsection{Canonical Equation}
\[
C_{ij} = \frac{\operatorname{cov}(x_i,x_j)}{\sigma_i\sigma_j}
\]
\[
C_{\lambda i,\lambda j}=C_{ij}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $C_{ij}$: source equation symbol.
    \item $x_i$: source equation symbol.
    \item $x_j$: source equation symbol.
    \item $\sigma_i$: source equation symbol.
    \item $\sigma_j$: source equation symbol.
    \item $C_{\lambda_{i},\lambda_{j}}$: source equation symbol.
    \item $\lambda$: cosmological or lemniscatic branch parameter in the entry relation.
    \item $C$: speed of light or relativistic conversion factor.
    \item $F$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0293 generated source Wolfram model *)
ClearAll[K0293, Cr0293, T, R, A, W, I, N];
eq0293$1 = HoldForm[CIj == Tuple[cov[xI, xJ]]/sigmaIsigmaJ];
eq0293$2 = HoldForm[CLambdailambdaj == CIj];
eq0293$3 = HoldForm[CF < Infinity];

K0293 = HoldForm[{eq0293$1, eq0293$2, eq0293$3}];

N = "normalized TRAWIN closure object for Opposing Field Regions Correlation";
I = "Normalized Regime integration/comparison layer";
W = "Scaling Relation wave or operator carrier";
A = "Diagnostic Definition admissible action/amplitude condition";
R = "Scaling Relation rotation/curl preservation layer";
T = "Diagnostic Definition local source condition";

Cr0293[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0293 = Cr0293[K0293];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Diagnostic Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Scaling Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Diagnostic Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Scaling Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Regime integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Opposing Field Regions Correlation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0293] Opposing Field Regions Correlation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\mathcal{L}_{X_H}\omega=0.
\end{equation}

\begin{equation}
\phi_t^{*}\omega=\omega.
\end{equation}

\paragraph{Primary Derivation.}
Let $\omega$ be the symplectic form and $X_H$ the Hamiltonian vector field.  
Hamiltonian flow preserves the symplectic form when:

\begin{equation}
\mathcal{L}_{X_H}\omega=0.
\end{equation}

Integrating the infinitesimal flow produces the global preservation law:

\begin{equation}
\boxed{
\phi_t^{*}\omega=\omega.
}
\end{equation}

\paragraph{Interpretation.}
Admissible Hamiltonian evolution preserves phase-space topology and Liouville structure.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Opposing Field Regions Correlation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Diagnostic Definition}\par
\[
C_{ij} = \frac{\operatorname{cov}(x_i,x_j)}{\sigma_i\sigma_j}
\]
\noindent This defines the scalar diagnostic or conversion quantity named by the title.\par
\noindent\textbf{2. Scaling Relation}\par
\[
C_{\lambda i,\lambda j}=C_{ij}
\]
\noindent This elevates the quantity into a comparative scaling or correlation law.\par
\noindent\textbf{3. Normalized Regime}\par
\[
\|C\|_{F}<\infty
\]
\noindent This closes the entry by normalizing the diagnostic against a stated reference regime.\par

\clearpage
\noindent\textbf{[ID 0293] Opposing Field Regions Correlation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Opposing Field Regions Correlation is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} In the gyromagnetic correlation matrix, regions of opposing fields---pressed magnet anti-alignment in the laboratory and inner/outer core opposition in planets---show a correlation coefficient of 0.95. \textbf{Contextual meaning:} The entry reads Opposing Field Regions Correlation as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons. \textbf{Lemma support:} Diagnostic Definition; Scaling Relation; Normalized Regime.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Admissible Hamiltonian evolution preserves phase-space topology and Liouville structure.

\tzpsection{Equation Grounding}
Equation anchors: C sub ij = ratio operatorname cov (x sub i,x sub j) sigma sub isigma sub j; C sub lambda i,lambda j =C sub ij; and C sub F <infinity. Proof route: show that the named quantity is dimensionless or consistently scaled in the regime stated by the entry. Formalization route: prove that the normalized diagnostic remains invariant under the intended rescaling.

\tzpsection{Interpretive Role}
The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Anti-Parallel Domain Phase Alignment}: The statistical tracking of how two magnetic or acoustic regions pointing in completely opposite directions somehow manage to perfectly sync their pulsations.
\item \textbf{Inverse-Field Subsystem Synchronization}: The mathematical proof that a positive energy node and a negative energy node can lock together and exchange information without canceling each other out.
\item \textbf{Non-Local Inter-Region Dependency}: The calculation showing that the behavior of the "up" oriented vortex is strictly and instantaneously dictated by the behavior of the distant "down" oriented vortex.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0293]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0293_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0293] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Opposing Field Regions Correlation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in the gyromagnetic correlation matrix, regions of opposing fields---pressed magnet
anti-alignment in the laboratory and inner/outer core oppositio...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Opposing Field Regions Correlation is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0293_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
