\section*{ID9465: Relation: 𝑃𝑟𝑜𝑡𝑒𝑐𝑡𝑒𝑑𝑐𝑜ℎ𝑒𝑟𝑒𝑛𝑐𝑒𝑡𝑖𝑚𝑒𝜏protected = 𝜏d×, Xicoherence =}
\paragraph{Metadata.}
PiID: 2528471605049 | RTEID: RTE:P36754.6970:T4.0118 | UUID: e6cfe17b-11dc-5ee9-a645-0f5fe2bd9fcb

\paragraph{Canonical Statement.}
\$→\$ 𝑃𝑟𝑜𝑡𝑒𝑐𝑡𝑒𝑑𝑐𝑜ℎ𝑒𝑟𝑒𝑛𝑐𝑒𝑡𝑖𝑚𝑒𝜏protected = 𝜏d× Wolfram Form 𝔚TZP (K1069) \$↦−→ 〈 ΩT, ΨT,\$ 𝜌vac \$〉\$ K1069 := HoldForm(T1069) AdmissibleTZP (K1069) \$⇐⇒\$ 𝔚TZP (K1069) . \$∅\$ Wolfram register: canonical symbol lift Title lift: RAMSEY INTERFEROMETRY COHER-ENCE TESTING Symbol key: \$ΩT:\$ Trawinistic boundary curvature \$ΨT:\$ Trawinistic wavefunction 𝜌vac: vacuum energy density TRAWIN Normalization NormalizeTRAWIN ( 𝑇𝑍𝑃𝐷𝑒 𝑓 𝑖𝑛𝑖𝑡𝑖𝑜𝑛 : \$𝑃ℎ𝑎𝑠𝑒𝑐𝑜ℎ𝑒𝑟𝑒𝑛𝑐𝑒‘Σi(𝜙i𝑚𝑜𝑑2𝜋)equiv0‘ →\$ 𝑒𝑛𝑒𝑟𝑔𝑦𝑐𝑜𝑛𝑐𝑒𝑛𝑡𝑟𝑎𝑡𝑖𝑜𝑛, 𝑆𝑡𝑒𝑝 [4 \$→\$ 𝑃𝑟𝑜𝑡𝑒𝑐𝑡𝑒𝑑𝑐𝑜ℎ𝑒𝑟𝑒𝑛𝑐𝑒𝑡𝑖𝑚𝑒𝜏protected = 𝜏d×, xicoherence = \$ℏ𝑣F/(𝜋Δgap);𝐶𝑜ℎ𝑒𝑟𝑒𝑛𝑐𝑒𝑙𝑒𝑛𝑔𝑡ℎ\$ ) T: Transfer Map is localized within the category theory and proof structure arc of the directory. R: Support Relation preserves the operative relation that ramsey interferometry coherence testing requires. A: Closure Relation fixes the admissible closure condition for the entry. W: RAMSEY INTERFEROMETRY COHERENCE TESTING is rendered as a reusable operator-level state

\paragraph{Canonical Equation.}
\[
𝑃𝑟𝑜𝑡𝑒𝑐𝑡𝑒𝑑𝑐𝑜ℎ𝑒𝑟𝑒𝑛𝑐𝑒𝑡𝑖𝑚𝑒𝜏protected = 𝜏d×, xicoherence =
\]

\paragraph{Dictionary.}
Relation: 𝑃𝑟𝑜𝑡𝑒𝑐𝑡𝑒𝑑𝑐𝑜ℎ𝑒𝑟𝑒𝑛𝑐𝑒𝑡𝑖𝑚𝑒𝜏protected = 𝜏d×, Xicoherence = — 𝑃𝑟𝑜𝑡𝑒𝑐𝑡𝑒𝑑𝑐𝑜ℎ𝑒𝑟𝑒𝑛𝑐𝑒𝑡𝑖𝑚𝑒𝜏protected = 𝜏d×, xicoherence =

\paragraph{Encyclopedia.}
Relation: 𝑃𝑟𝑜𝑡𝑒𝑐𝑡𝑒𝑑𝑐𝑜ℎ𝑒𝑟𝑒𝑛𝑐𝑒𝑡𝑖𝑚𝑒𝜏protected = 𝜏d×, Xicoherence = is an algebraic definition, written 𝑃𝑟𝑜𝑡𝑒𝑐𝑡𝑒𝑑𝑐𝑜ℎ𝑒𝑟𝑒𝑛𝑐𝑒𝑡𝑖𝑚𝑒𝜏protected = 𝜏d×, xicoherence =. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from x, c, o, h, r, n, defining 𝑃𝑟𝑜𝑡𝑒𝑐𝑡𝑒𝑑𝑐𝑜ℎ𝑒𝑟𝑒𝑛𝑐𝑒𝑡𝑖𝑚𝑒𝜏protected. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
