\tzpanchor{0590}
\tzpentryheader{0590}{17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{43fca527-fcc7-5347-b84b-e99c7f445e4b}}\\
\textbf{PiID} & \tzpcode{7669405132000} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{597}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2267.8017 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.7366 rad}\\
\textbf{TZPID} & \tzpcode{ID0590} & \textbf{Node Dependencies}\quad \tzpidref{0589}\\
\textbf{Registry} & \tzpcode{registry\_id\_0590} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Scaling Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
f\_\{carrier\} = frac\{v\_s\}\{lambda\} approximately 17.2 text\{ kHz\} implies text\{Phase-Lock with \} hat\{Gamma\} \{up\}

\tzpsection{Canonical Equation}
\[
f_{carrier} = \frac{v_{\mathrm{s}}}{\lambda} \approx 17.2 \text{ kHz} \implies \text{Phase-Lock } \mathrm{hat}{\mathrm{Gamma}} {up}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $f_{carrier}$: source equation symbol.
    \item $v_{\mathrm{s}}$: source equation symbol.
    \item $\lambda$: cosmological or lemniscatic branch parameter in the entry relation.
    \item $J$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{J}_{\mathrm{out}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0590 generated source Wolfram model *)
ClearAll[K0590, Cr0590, T, R, A, W, I, N];
eq0590$1 = HoldForm[fCarrier == vS/lambda == 17.2*implies*hat[Gamma]*up];
eq0590$2 = HoldForm[mathcal[J]*_*out == TTZP[KTZP]];
eq0590$3 = HoldForm[mathcal[A]*_*adm*JOut == 1];

K0590 = HoldForm[{eq0590$1, eq0590$2, eq0590$3}];

N = "normalized TRAWIN closure object for 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Scaling Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Scaling Law local source condition";

Cr0590[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0590 = Cr0590[K0590];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Scaling Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Scaling Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0590] 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Invariant Matching Condition.}
\begin{equation}
\Pi_k^{\mathrm{lab}}
=
\Pi_k^{\mathrm{astro}} .
\end{equation}

\paragraph{Scale Equivalence Map.}
\begin{equation}
F_{\mathrm{scale}}:
\mathcal{S}_{\mathrm{lab}}
\longrightarrow
\mathcal{S}_{\mathrm{astro}} .
\end{equation}

\paragraph{Primary Derivation.}
Let $\Pi_k$ denote a dimensionless invariant governing a dynamical system.  
Laboratory and astrophysical systems are structurally comparable only when their governing invariant sets match:
\begin{equation}
\Pi_k^{\mathrm{lab}}
=
\Pi_k^{\mathrm{astro}} .
\end{equation}

A scale map then translates the laboratory realization into the astrophysical realization:
\begin{equation}
F_{\mathrm{scale}}:
\mathcal{S}_{\mathrm{lab}}
\to
\mathcal{S}_{\mathrm{astro}} .
\end{equation}

Thus,
\begin{equation}
\boxed{
\Xi_{\mathrm{eq}}
=
\mathrm{NormalizeTRAWIN}
\left(
\mathcal{S}_{\mathrm{lab}},
\mathcal{S}_{\mathrm{astro}},
F_{\mathrm{scale}},
\Pi_k
\right).
}
\end{equation}

\paragraph{Interpretation.}
Laboratory demonstrations become structurally meaningful for astrophysical systems only when the scale map preserves the relevant dimensionless invariants.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Scaling Law}\par
\[
f_{carrier} = \frac{v_{\mathrm{s}}}{\lambda} \approx 17.2 \text{ kHz} \implies \text{Phase-Lock } \mathrm{hat}{\mathrm{Gamma}} {up}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right)=1
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0590] 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} f sub carrier = frac v sub s lambda approximately 17.2 text kHz implies text Phase-Lock with hat Gamma up. \textbf{Contextual meaning:} The entry reads 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Scaling Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Laboratory demonstrations become structurally meaningful for astrophysical systems only when the scale map preserves the relevant dimensionless invariants. \% SENARY DERIVATION LAYER -- ID 0591 TO ID 0600 \% CANONICAL PDF-ALIGNED VERSION.

\tzpsection{Equation Grounding}
Equation anchors: f sub carrier = ratio v sub s lambda approximately 17.2 kHz implies Phase-Lock hat Gamma up; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Ultrasonic Baseline Frequency Locking}: The tuning of the entire physical structure to vibrate at one specific, incredibly high-pitched hum.
\item \textbf{Piezoelectric Drive Resonance}: The constant, rhythmic electrical stimulation used to maintain the exact acoustic tone required to keep the quantum states stable.
\item \textbf{Acoustic-Geometric Wave Matching}: The precision engineering ensuring that the physical length of the chamber is exactly matched to the wavelength of the 17.2 kilohertz sound.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0590]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0590_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0590] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} f\textbackslash{}\_\textbackslash{} = frac\textbackslash{}\_s\textbackslash{}\textbackslash{} approximately 17.2 text\textbackslash{} kHz\textbackslash{} implies text-Lock with \textbackslash{} hat\textbackslash{} \textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION is valid as a synchronization criterion under
the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0590_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
