\section*{ID9258: Definition of Bgravitomagnetic(r)}
\paragraph{Metadata.}
PiID: 1207388377814 | RTEID: RTE:P35950.8700:T2.6873 | UUID: 13fae8fc-7282-5523-b462-73b9e4272239

\paragraph{Canonical Statement.}
h stable gyromagnetic vortices. (3) Provides a test for numerical simulations of rotating magnetized systems. Falsifiability / Test Handle: Compute helicity in experiments or simulations of rotating magnets; verify invariance despite dynamic changes and confirm the contribution of the second term. 2.0.176 ID 325: Gravitomagnetic Coupling Term Type: Definition Formal Statement: In a rapidly rotating gyromagnetic system approaching relativistic tangential velocities, the gravitomagnetic field is \$Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3rB\_\{\textbackslash{}text\{gravitomagnetic\}\}(r)\$ = (2G/cˆ2) (\textbackslash{}omega \textbackslash{}times r)/rˆ3 \textbackslash{}int\_V \$\textbackslash{}rho(r’)|r’|2,d3r’Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3r,\$ where \$ρ(r)\textbackslash{}rho(r)ρ(r)\$ is the mass density. Interpretive Meaning: This term represents the coupling between rotation and gravity, analogous to the magnetic field produced by moving charges. It arises from general relativistic framedragging and indicates that rotating mass distributions c

\paragraph{Canonical Equation.}
\[
Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3rB_{\text{gravitomagnetic}}(r)
\]

\paragraph{Dictionary.}
Definition of Bgravitomagnetic(r) — Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3rB\_gravitomagnetic(r)

\paragraph{Encyclopedia.}
Definition of Bgravitomagnetic(r) is an algebraic definition, written Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3rB\_gravitomagnetic(r). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from G, c, r, V, B\_, defining Bgravitomagnetic(r). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
