\section*{ID9457: Definition of рқң”vort}
\paragraph{Metadata.}
PiID: 5719849225284 | RTEID: RTE:P36723.6312:T3.9606 | UUID: 9b02c72c-f05b-51ae-82cd-88a1d6ffa9c9

\paragraph{Canonical Statement.}
or [ID 0538] Isabelle Certificate Lean Certificate Coq Certificate lemmaid0538\_self\_perpetuating\_vortex\_dynamo:sorry theoremid0538\_self\_perpetuating\_vortex\_dynamo Theoremid0538\_self\_perpetuating\_vortex\_dynamo Dependencies and Test Handle Dependencies [ID 0537], [ID 0500] Node registry\_id\_0538 Support Titles Vorticity Carrier; Induction Law; Dynamo Growth Rate Test Handle If the induction law does not sustain the stated magnetic-energy growth observable, the entry fails. Canonical Equation Links \$рқң”vort=вҲҮГ—рқ‘Ј рқң•tрқҗө=вҲҮГ—(рқ‘ЈГ—рқҗө)+рқңӮвҲҮ2рқҗө\$ рқӣҫdyn=В· В· В· [ID 0539] THE pi-KISSING MANIFOLD AXIOM TZPID ID0539 UUID bede8553-48e5-5099-9101-aca0bfa68435 Type Geometric / Topological Statement Scale geometric LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math.DG; Cross-list: math-ph, math.AT Canonical Statement This entry develops the pi-kissing manifold axiom insi

\paragraph{Canonical Equation.}
\[
рқң”vort=вҲҮГ—рқ‘Ј рқң•tрқҗө=вҲҮГ—(рқ‘ЈГ—рқҗө)+рқңӮвҲҮ2рқҗө
\]

\paragraph{Dictionary.}
Definition of рқң”vort вҖ” рқң”vort=вҲҮГ—рқ‘Ј рқң•tрқҗө=вҲҮГ—(рқ‘ЈГ—рқҗө)+рқңӮвҲҮ2рқҗө

\paragraph{Encyclopedia.}
Definition of рқң”vort is an algebraic definition, written рқң”vort=вҲҮГ—рқ‘Ј рқң•tрқҗө=вҲҮГ—(рқ‘ЈГ—рқҗө)+рқңӮвҲҮ2рқҗө. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
