\tzpanchor{0574}
\tzpentryheader{0574}{SPATIAL CONVOLUTION OF OMEGA}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{65bfaf9c-56fb-5f28-9b9c-1e1a98826586}}\\
\textbf{PiID} & \tzpcode{7675238467481} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{581}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2205.6701 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.6343 rad}\\
\textbf{TZPID} & \tzpcode{ID0574} & \textbf{Node Dependencies}\quad \tzpidref{0573}\\
\textbf{Registry} & \tzpcode{registry\_id\_0574} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
v=omega R:

\tzpsection{Canonical Equation}
\[
mathcal{K}_{\mathrm{TZP}} = \mathcal{K}_0 + \delta \mathcal{K}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $K$: source equation symbol.
    \item $\mathcal{K}_0$: source equation symbol.
    \item $\delta$: point-source delta term that anchors the Green-function response.
    \item $J$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{J}_{\mathrm{out}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0574 generated source Wolfram model *)
ClearAll[K0574, Cr0574, T, R, A, W, I, N];
eq0574$1 = HoldForm[mathcal[K]*_*TZP == K0 + DiracDelta*K];
eq0574$2 = HoldForm[mathcal[J]*_*out == TTZP[KTZP]];
eq0574$3 = HoldForm[mathcal[A]*_*adm*JOut == 1];

K0574 = HoldForm[{eq0574$1, eq0574$2, eq0574$3}];

N = "normalized TRAWIN closure object for SPATIAL CONVOLUTION OF OMEGA";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0574[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0574 = Cr0574[K0574];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for SPATIAL CONVOLUTION OF OMEGA.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0574] SPATIAL CONVOLUTION OF OMEGA}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mathcal{E}(\rho)=\sum_k E_k\rho E_k^\dagger .
\end{equation}

\paragraph{Trace-Preserving Constraint.}
\begin{equation}
\sum_k E_k^\dagger E_k = I .
\end{equation}

\paragraph{Primary Derivation.}
A completely positive map admits a Kraus representation:
\begin{equation}
\mathcal{E}(\rho)=\sum_k E_k\rho E_k^\dagger .
\end{equation}

Trace preservation requires
\begin{equation}
\operatorname{Tr}(\mathcal{E}(\rho))=\operatorname{Tr}(\rho).
\end{equation}

Using cyclicity of trace,
\begin{equation}
\operatorname{Tr}(\mathcal{E}(\rho))
=
\operatorname{Tr}\left(
\rho\sum_k E_k^\dagger E_k
\right).
\end{equation}

This equals $\operatorname{Tr}(\rho)$ for all $\rho$ precisely when
\begin{equation}
\boxed{
\sum_k E_k^\dagger E_k = I .
}
\end{equation}

\paragraph{Interpretation.}
CPTP maps preserve both positivity and total probability, making them valid quantum-state transformations.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors SPATIAL CONVOLUTION OF OMEGA by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
mathcal{K}_{\mathrm{TZP}} = \mathcal{K}_0 + \delta \mathcal{K}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right)=1
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0574] SPATIAL CONVOLUTION OF OMEGA}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
SPATIAL CONVOLUTION OF OMEGA is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} v=omega R:. \textbf{Contextual meaning:} The entry reads SPATIAL CONVOLUTION OF OMEGA as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
CPTP maps preserve both positivity and total probability, making them valid quantum-state transformations.

\tzpsection{Equation Grounding}
Equation anchors: mathcal K sub TZP = K sub 0 + delta K; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Curvature-Smearing Integration}: The mathematical process of taking a sharp, violent spike in gravity and smoothing it out over the surrounding area to see how it affects the neighbors.
\item \textbf{Non-Local Geometric Influences}: The calculation proving that the twisting of space at point A is entirely dependent on the rippling echoes of a magnetic storm happening at point B.
\item \textbf{Boundary-Condition Blurring}: The realization that the hard, solid metal walls of the reactor don't actually stop the math; the equations just slowly fade away into the concrete of the building.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0574]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0574_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0574] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont SPATIAL CONVOLUTION OF OMEGA}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} CPTP maps preserve both positivity and total probability, making them valid quantum-
state transformations

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``SPATIAL CONVOLUTION OF OMEGA is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0574_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
