\tzpanchor{0313}
\tzpentryheader{0313}{Time as a Toroidal Winding Parameter}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f1791df6-8d5a-54c5-800e-ee2ea864c611}}\\
\textbf{PiID} & \tzpcode{1558817488152} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{320}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1215.4485 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.0027 rad}\\
\textbf{TZPID} & \tzpcode{ID0313} & \textbf{Node Dependencies}\quad \tzpidref{0312}\\
\textbf{Registry} & \tzpcode{registry\_id\_0313} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Within the recursive toroidal framework, temporal evolution is interpreted as motion along a toroidal cycle rather than as linear progression. The parameter $t$ labels winding around the torus and links successive projections to positions on the same underlying loop.

\tzpsection{Canonical Equation}
\[
\theta(t)=\theta_{0}+\omega t \pmod{2\pi}
\]
\[
\tau=\frac{\theta-\theta_{0}}{\omega},\qquad W=\frac{1}{2\pi}\oint d\theta
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\theta(t)$: phase angle or local angular coordinate.
    \item $\theta_{0}$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
    \item $t$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $\tau$: source equation symbol.
    \item $W$: source equation symbol.
    \item $Z$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0313 generated source Wolfram model *)
ClearAll[K0313, Cr0313, T, R, A, W, I, N];
eq0313$1 = HoldForm[theta[t] == theta0 + omega*tPlusMinusod[2*Pi]];
eq0313$2 = HoldForm[TZPSequence[tau == (theta - theta0)/omega, W == (1/(2*Pi))*ContourIntegral*dtheta]];
eq0313$3 = HoldForm[Element[W, Z]];

K0313 = HoldForm[{eq0313$1, eq0313$2, eq0313$3}];

N = "normalized TRAWIN closure object for Time as a Toroidal Winding Parameter";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0313[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0313 = Cr0313[K0313];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Time as a Toroidal Winding Parameter.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0313] Time as a Toroidal Winding Parameter}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
P_{\mathrm{null}}(v)
=
\begin{cases}
v, & g(v,w)=0\ \text{for all}\ w\in T_pM,\\
0, & \text{otherwise}.
\end{cases}
\end{equation}

\paragraph{Primary Derivation.}
At the TZP, the degenerate metric admits null directions.  
A vector $v\in T_pM$ belongs to the null space if it pairs to zero with every tangent vector $w$:

\begin{equation}
g(v,w)=0
\qquad
\forall w\in T_pM .
\end{equation}

The null projection operator preserves vectors satisfying this condition:

\begin{equation}
P_{\mathrm{null}}(v)=v .
\end{equation}

Vectors not satisfying the null condition are removed by the projection:

\begin{equation}
P_{\mathrm{null}}(v)=0 .
\end{equation}

Thus,

\begin{equation}
\boxed{
P_{\mathrm{null}}(v)
=
\begin{cases}
v, & g(v,w)=0\ \text{for all}\ w\in T_pM,\\
0, & \text{otherwise}.
\end{cases}
}
\end{equation}

\paragraph{Interpretation.}
$P_{\mathrm{null}}$ extracts only those tangent directions annihilated by the degenerate TZP metric.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Time as a Toroidal Winding Parameter by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
\theta(t)=\theta_{0}+\omega t \pmod{2\pi}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\tau=\frac{\theta-\theta_{0}}{\omega},\qquad W=\frac{1}{2\pi}\oint d\theta
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
W\in\mathbb{Z}
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0313] Time as a Toroidal Winding Parameter}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Time as a Toroidal Winding Parameter is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Within the recursive toroidal framework, temporal evolution is interpreted as motion along a toroidal cycle rather than as linear progression. The parameter t labels winding around the torus and links successive projections to positions on the same underlying loop. \textbf{Contextual meaning:} The entry reads Time as a Toroidal Winding Parameter as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
P sub null extracts only those tangent directions annihilated by the degenerate TZP metric.

\tzpsection{Equation Grounding}
Equation anchors: omega to the power 2 = k to the power 2 v sub A to the power 2 [1 + (ratio omega sub gyro omega ) to the power 2 ]; | | **N** | Normalization / closure | \$4( N to the power -1 um i ) or boundary condition ( n ot F=0 ); and Delta E = ratio (Phi sub 0) to the power 2 2L approximately ratio (2.07 times 10 to the power -15 ) to the power 2 2 times 10 to the power -9 approximately 10 to the power -21 , J. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Cyclic Temporal Evolution}: The conceptualization of time as an angular coordinate strictly bound to a repeating circular domain.
\item \textbf{Phase-Locked Chronology}: The linkage of dynamical progression to explicit geometric rotation around a toroidal major axis.
\item \textbf{Periodic Boundary Chronometry}: The mathematical boundary condition forcing time-dependent states to perfectly repeat after one full revolution.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0313]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0313_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0313] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Time as a Toroidal Winding Parameter}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} within the recursive toroidal framework, temporal evolution is interpreted as motion
along a toroidal cycle rather than as linear progression

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Time as a Toroidal Winding Parameter is valid when the stated geometric or topological
relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0313_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
