\section*{ID8900: QUANTUM STATE SPACE DECOMPOSITION Canonical Statutory Formula: H\_total}
\paragraph{Metadata.}
PiID: 9289647669758 | RTEID: RTE:P34560.6765:T0.3967 | UUID: c5b78e77-af88-5597-9c24-32c9f4d9fe9d

\paragraph{Canonical Statement.}
[ID 931] QUANTUM STATE SPACE DECOMPOSITION Canonical Statutory Formula: \$H\_\{total\} = H\_\{spatial\} \textbackslash{}otimes H\_\{OAM\} \textbackslash{}otimes H\_\{polarization\} \textbackslash{}otimes H\_\{frequency\}\$ Formal Technical Dissertation: Defines the total Hilbert space used for quantum holographic navigation. It factors into four independent subsystems: the spatial address (\$dim = 153,600\$), orbital angular momentum (\$dim = 2m\_\{max\} + 1\$), polarization (\$dim = 2\$), and frequency (\$dim = \textbackslash{}infty\$). This modular decomposition allows for selective entanglement generation and independent CPTP map design. Source: [1], [2]

\paragraph{Canonical Equation.}
\[
H_{total} = H_{spatial} \otimes H_{OAM} \otimes H_{polarization} \otimes H_{frequency}
\]

\paragraph{Dictionary.}
QUANTUM STATE SPACE DECOMPOSITION Canonical Statutory Formula: \$H\_total = H\_spatial H\_OAM H\_polarization H\_frequency\$ Formal Technical Dissertation: Defines the total Hilbert space used for quantum holographic navigation.

\paragraph{Encyclopedia.}
QUANTUM STATE SPACE DECOMPOSITION Canonical Statutory Formula: H\_total is an algebraic definition, written H\_total = H\_spatial ⊗ H\_OAM ⊗ H\_polarization ⊗ H\_frequency. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from H\_spatial, H\_OAM, H\_polarization, H\_frequency, defining H\_total. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
