\tzpanchor{0405}
\tzpentryheader{0405}{The Infinite-Order Transition Divergence}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{6739da21-b566-5943-a6b1-d3f33701f902}}\\
\textbf{PiID} & \tzpcode{2703657595919} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{412}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1572.7049 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.5913 rad}\\
\textbf{TZPID} & \tzpcode{ID0405} & \textbf{Node Dependencies}\quad \tzpidref{0404}\\
\textbf{Registry} & \tzpcode{registry\_id\_0405} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation 2\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 405 establishes the "Phase Transition" logic that distinguishes Trawinistic Field Theory from standard statistical thermodynamics. While conventional physics recognizes first order (discontinuous density) and second order (discontinuous heat capacity) transitions, the TZP manifests as a transition of infinite order. At the critical coordinate tauc, every derivative of the thermodynamic potential undergoes asymptotic divergence. This absolute divergence is the fundamental mechanism that induces the deltagnu [ID 404]. It proves that the observed phenomenon of gravity is a volumetric displacement force generated by the release of isotropic vacuum pressure residue at the singularity. By anchoring the coordinate system at p, the framework successfully resolves Academic Paradigm Dominance Bias, shifting the interpretation from "force" to "vibrating code" geometry.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\lim_{T \to 0} \frac{\partial^n F}{\partial T^n}\bigg|_{r_{\mathrm{c}}} = \cdots
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $T$: source equation symbol.
    \item $n$: integer mode index.
    \item $F$: source equation symbol.
    \item $r_{\mathrm{c}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0405 generated source Wolfram model *)
ClearAll[K0405, Cr0405, T, R, A, W, I, N];
eq0405$1 = HoldForm[LimitT0[(Partial^n*F)/(Partial*T^n)]*bigg | _*rC == Ellipsis];

K0405 = HoldForm[{eq0405$1}];

N = "normalized TRAWIN closure object for The Infinite-Order Transition Divergence";
I = "The Infinite-Order Transition Divergence integration/comparison layer";
W = "The Infinite-Order Transition Divergence wave or operator carrier";
A = "The Infinite-Order Transition Divergence admissible action/amplitude condition";
R = "The Infinite-Order Transition Divergence rotation/curl preservation layer";
T = "The Infinite-Order Transition Divergence local source condition";

Cr0405[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0405 = Cr0405[K0405];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ The Infinite-Order Transition Divergence local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ The Infinite-Order Transition Divergence rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ The Infinite-Order Transition Divergence admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ The Infinite-Order Transition Divergence wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ The Infinite-Order Transition Divergence integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for The Infinite-Order Transition Divergence.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0405] The Infinite-Order Transition Divergence}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
For any diffeomorphism $\phi:M\to M$ preserving the symmetry group of $M$,

\begin{equation}
\phi(p)=p .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi:M\to M$ be a diffeomorphism preserving the symmetry structure of the manifold. Since $p$ is defined as the unique point where the metric degeneracy occurs,

\begin{equation}
\det(g)\big|_p=0 .
\end{equation}

If $\phi$ preserves the Trawinistic structure, then it must preserve the degeneracy locus:

\begin{equation}
\det(g)\big|_{\phi(p)}=0 .
\end{equation}

Because $p$ is unique, the only point satisfying this condition is $p$ itself. Therefore:

\begin{equation}
\phi(p)=p .
\end{equation}

\paragraph{Interpretation.}
The TZP is invariant under all structure-preserving transformations. It is therefore a fixed point of the system.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors The Infinite-Order Transition Divergence by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\lim_{T \to 0} \frac{\partial^n F}{\partial T^n}\bigg|_{r_{\mathrm{c}}} = \cdots
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0405] The Infinite-Order Transition Divergence}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
The Infinite-Order Transition Divergence is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 405 establishes the "Phase Transition" logic that distinguishes Trawinistic Field Theory from standard statistical thermodynamics. While conventional physics recognizes first order (discontinuous density) and second order (discontinuous heat capacity) transitions, the TZP manifests as a transition of infinite order. At the critical coordinate tauc, every derivative of the thermodynamic potential undergoes asymptotic divergence. This absolute divergence is the fundamental mechanism that induces the deltagnu [ID 404]. It proves that the observed phenomenon of gravity is a volumetric displacement force generated by the release of isotropic vacuum pressure residue at the singularity. By anchoring the coordinate system at p, the framework successfully resolves Academic Paradigm Dominance Bias, shifting the interpretation from "force" to "vibrating code" geometry.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\lim_{T \to 0} \frac{\partial^n F}{\partial T^n}\bigg|_{r_{\mathrm{c}}} = \cdots
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 405 establishes the "Phase Transition" logic that distinguishes Trawinistic Field Theory from standard statistical thermodynamics. While conventional physics recognizes first order (discontinuous density) and second order (discontinuous heat capacity) transitions, the TZP manifests as a transition of infinite order. At the critical coordinate tauc, every derivative of the thermodynamic potential undergoes asymptotic divergence. This absolute divergence is the fundamental mechanism that induces the deltagnu [ID 404]. It proves that the observed phenomenon of gravity is a volumetric displacement force generated by the release of isotropic vacuum pressure residue at the singularity. By anchoring the coordinate system at p, the framework successfully resolves Academic Paradigm Dominance Bias, shifting the interpretation from "force" to "vibrating code" geometry.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors The Infinite-Order Transition Divergence by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
The Infinite-Order Transition Divergence; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0405]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0405].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0405] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont The Infinite-Order Transition Divergence}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} lim\textbackslash{}\_ -> tau\textbackslash{}\_c\textbackslash{} left| frac tial\textasciicircum{}n Omega\textbackslash{} tial tau\textasciicircum{}n\textbackslash{} right| = infinity, quad forall n
in mathbb\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``THE INFINITE-ORDER TRANSITION DIVERGENCE is valid when the total tensorial quantity is
conserved under the stated constraint.''\\
\textbf{Proof:} The source statement identifies a conserved balance law. Reading 0405 as a proposition,
validity follows by requiring the full stress, flux, or current contribution to be
included before the divergence or balance condition is evaluated.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conserved total-structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0405].
\par\endgroup
\vfill
\endgroup
\endgroup
