\tzpanchor{0246}
\tzpentryheader{0246}{$\pi$-Kissing Topology}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{28a7eb0b-f19e-5fd6-8e87-4d2d5387589f}}\\
\textbf{PiID} & \tzpcode{9091456485669} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{253}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{955.2726 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.5740 rad}\\
\textbf{TZPID} & \tzpcode{ID0246} & \textbf{Node Dependencies}\quad \tzpidref{0245}\\
\textbf{Registry} & \tzpcode{registry\_id\_0246} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Quantum coherence in the DAANSphere is stabilised by arranging superconducting resonators in a configuration where neighbouring resonators touch at discrete points (the pi-kissing topology), forming a network of weak links that distribute coherence.

\tzpsection{Canonical Equation}
\[
\mathcal{K}_{\pi}=\{(i,j):\partial R_i\cap\partial R_j\neq\varnothing\}
\]
\[
omega_{\rm obs}= \frac{k\!\cdot\! u_{\rm em}}{k\!\cdot\! u_{\rm obs}}\;\omega_{\rm em},\qquad \mathcal D=\frac{1}{\gamma(1-\boldsymbol\beta\!\cdot\!\hat{\mathbf n})},\ \  u_{\rm obs}=\mathcal D\, u_{\rm em}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{K}_{\pi}$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $R_i$: source equation symbol.
    \item $R_j$: source equation symbol.
    \item $u_{\mathrm{em}}$: source equation symbol.
    \item $u_{\mathrm{obs}}$: source equation symbol.
    \item $\omega_{\mathrm{em}}$: angular frequency term in the source equation.
    \item $D$: source equation symbol.
    \item $\gamma$: source equation symbol.
    \item $n$: integer mode index.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0246 generated source Wolfram model *)
ClearAll[K0246, Cr0246, T, R, A, W, I, N];
eq0246$1 = HoldForm[KPi == RegionAdjacencyPairs[Pi]];
eq0246$2 = HoldForm[TZPSequence[omegaRmobs == ((k*uRmem)/(k*uRmobs))*omegaRmem, D == 1/gamma[1 - boldsymbolbeta*mathbf*nHat], uRmobs == D*uRmem]];
eq0246$3 = HoldForm[TZPSequence[tRmobs == tRmem + Abs[mathbfR[tRmem]]/c, mathbf*R == mathbf*xRmem[tRmem] - mathbf*xRmobs[tRmobs]]];

K0246 = HoldForm[{eq0246$1, eq0246$2, eq0246$3}];

N = "normalized TRAWIN closure object for $\pi$-Kissing Topology";
I = "Topological Closure integration/comparison layer";
W = "Compatibility Law wave or operator carrier";
A = "Geometric Carrier admissible action/amplitude condition";
R = "Compatibility Law rotation/curl preservation layer";
T = "Geometric Carrier local source condition";

Cr0246[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0246 = Cr0246[K0246];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Geometric Carrier local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Compatibility Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Geometric Carrier admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Compatibility Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for \$\textbackslash{}pi\$-Kissing Topology.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0246] $\pi$-Kissing Topology}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{Q}{Q'}
=
\mathcal{O}(1).
\end{equation}

\paragraph{Primary Derivation.}
Let $Q$ and $Q'$ be corresponding quantities related by a scaling map between laboratory and astrophysical systems.

If the scaling preserves the essential dimensionless structure, then the transformed quantity should not diverge across the mapped systems. Thus the ratio:

\begin{equation}
\frac{Q}{Q'}
\end{equation}

must remain bounded within a finite order-of-magnitude interval.

This boundedness condition is expressed as:

\begin{equation}
\boxed{
\frac{Q}{Q'}
=
\mathcal{O}(1).
}
\end{equation}

\paragraph{Interpretation.}
The scaling relation is valid when corresponding quantities remain order-equivalent despite extreme differences in physical size.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors \$\textbackslash{}pi\$-Kissing Topology by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Geometric Carrier}\par
\[
\mathcal{K}_{\pi}=\{(i,j):\partial R_i\cap\partial R_j\neq\varnothing\}
\]
\noindent This fixes the effective geometry or carrier space named by the entry title.\par
\noindent\textbf{2. Compatibility Law}\par
\[
omega_{\rm obs}= \frac{k\!\cdot\! u_{\rm em}}{k\!\cdot\! u_{\rm obs}}\;\omega_{\rm em},\qquad \mathcal D=\frac{1}{\gamma(1-\boldsymbol\beta\!\cdot\!\hat{\mathbf n})},\ \  u_{\rm obs}=\mathcal D\, u_{\rm em}
\]
\noindent This makes the geometry admissible by imposing its internal compatibility law.\par
\noindent\textbf{3. Topological Closure}\par
\[
t_{\rm obs}=t_{\rm em}+\frac{|\mathbf R(t_{\rm em})|}{c},\quad \mathbf R=\mathbf x_{\rm em}(t_{\rm em})-\mathbf x_{\rm obs}(t_{\rm obs})
\]
\noindent This closes the entry by tying the local structure to a global topological invariant.\par

\clearpage
\noindent\textbf{[ID 0246] $\pi$-Kissing Topology}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
pi-Kissing Topology is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Quantum coherence in the DAANSphere is stabilised by arranging superconducting resonators in a configuration where neighbouring resonators touch at discrete points (the pi-kissing topology), forming a network of weak links that distribute coherence. \textbf{Contextual meaning:} The entry reads pi-Kissing Topology as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the tertiary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Geometric Carrier; Compatibility Law; Topological Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The scaling relation is valid when corresponding quantities remain order-equivalent despite extreme differences in physical size.

\tzpsection{Equation Grounding}
Equation anchors:
\[
\mathcal{K}_{\pi}=\{(i,j):\partial R_i\cap\partial R_j\neq\varnothing\},
\qquad
\omega_{\mathrm{obs}}=\frac{k\cdot u_{\mathrm{em}}}{k\cdot u_{\mathrm{obs}}}\,\omega_{\mathrm{em}},
\]
and
\[
\mathcal{D}=\frac{1}{\gamma(1-\boldsymbol{\beta}\cdot\hat{\mathbf n})},
\qquad
u_{\mathrm{obs}}=\mathcal{D}\,u_{\mathrm{em}}.
\]
Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the tertiary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Tangential Oscillation Sphere Packing}: The mathematical modeling of resonant waves as packed spheres that precisely touch at tangent points to transfer energy flawlessly.
\item \textbf{Maximum Density Phase Synchronization}: The geometric configuration allowing the maximum number of independent oscillators to sync without destructive interference.
\item \textbf{Coherent Boundary Touching Configurations}: The exact topological conditions required for separate energy domains to interact purely through constructive boundary contact.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0246]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0246_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0246] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont $\pi$-Kissing Topology}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} quantum coherence in the DAANSphere is stabilised by arranging superconducting
resonators in a configuration where neighbouring resonators touch at...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``pi-Kissing Topology is valid as a formal dynamical law when the Hamiltonian or energy
operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0246_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
