\tzpanchor{0641}
\tzpentryheader{0641}{LOGARITHMIC ADDRESS DIMENSIONALITY}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{be9e5b46-39d5-56c4-80f9-404b29fa3a6d}}\\
\textbf{PiID} & \tzpcode{3637178721468} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{648}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2465.8460 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.0630 rad}\\
\textbf{TZPID} & \tzpcode{ID0641} & \textbf{Node Dependencies}\quad \tzpidref{0640}\\
\textbf{Registry} & \tzpcode{registry\_id\_0641} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Scaling Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records logarithmic address dimensionality through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
H = \int_V \mathbf{A}\cdot\mathbf{B} \,\mathrm{d}^3x.
\]
\[
H=w\,\Phi.
\]
\[
\boxed{ H=w\,\Phi. }
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H$: source equation symbol.
    \item $A$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $\Phi$: flux, phase, or topological map term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0641 generated source Wolfram model *)
ClearAll[K0641, Cr0641, T, R, A, W, I, N];
eq0641$1 = HoldForm[H == IntegralV*A*B*d^3*x];
eq0641$2 = HoldForm[H == w*Phi];
eq0641$3 = HoldForm[H == w*Phi];

K0641 = HoldForm[{eq0641$1, eq0641$2, eq0641$3}];

N = "normalized TRAWIN closure object for LOGARITHMIC ADDRESS DIMENSIONALITY";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Scaling Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Scaling Law local source condition";

Cr0641[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0641 = Cr0641[K0641];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Scaling Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Scaling Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for LOGARITHMIC ADDRESS DIMENSIONALITY.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0641] LOGARITHMIC ADDRESS DIMENSIONALITY}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
H
=
\int_V
\mathbf{A}\cdot\mathbf{B}
\,\mathrm{d}^3x .
\end{equation}

\paragraph{Quantized Form.}
\begin{equation}
H=w\,\Phi .
\end{equation}

\paragraph{Primary Derivation.}
Let $\mathbf{A}$ be the magnetic vector potential and $\mathbf{B}$ the magnetic field.  
Magnetic helicity measures the linkage, twist, and winding of magnetic field lines inside a volume $V$:

\begin{equation}
H
=
\int_V
\mathbf{A}\cdot\mathbf{B}
\,\mathrm{d}^3x .
\end{equation}

If the magnetic structure winds around the TZP with integer winding number $w$, and if $\Phi$ denotes the magnetic flux through the lemniscatic loop, then helicity decomposes into winding times flux:

\begin{equation}
\boxed{
H=w\,\Phi .
}
\end{equation}

\paragraph{Interpretation.}
Magnetic helicity becomes quantized when the field topology is constrained by integer TZP winding.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors LOGARITHMIC ADDRESS DIMENSIONALITY by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Scaling Law}\par
\[
H = \int_V \mathbf{A}\cdot\mathbf{B} \,\mathrm{d}^3x.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
H=w\,\Phi.
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\boxed{ H=w\,\Phi. }
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0641] LOGARITHMIC ADDRESS DIMENSIONALITY}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
LOGARITHMIC ADDRESS DIMENSIONALITY is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} D sub addr = lceil log sub 2(153,600) rceil approximately 17.23 -> 18 text bits. \textbf{Contextual meaning:} The entry reads LOGARITHMIC ADDRESS DIMENSIONALITY as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Scaling Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Magnetic helicity becomes quantized when the field topology is constrained by integer TZP winding.

\tzpsection{Equation Grounding}
Equation anchors: D sub addr = lceil log sub 2(153,600) rceil approximately 17.23 to 18 bits; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{State-Space Exponential Compression}: The incredibly efficient mathematical numbering system that allows you to cram a map of billions of different locations into a zip code that is only a few numbers long.
\item \textbf{Bit-Depth Scaling Limits}: The harsh, unavoidable reality that every time you want to double the size and complexity of the machine, you have to completely redesign and expand the fundamental language the computers use to talk to each other.
\item \textbf{Information-Density Bottlenecking}: The frustrating discovery that the raw processing power of the quantum core is actually outrunning the ability of the classical computers to assign names to the answers it is spitting out.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0641]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0641_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0641] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont LOGARITHMIC ADDRESS DIMENSIONALITY}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records logarithmic address dimensionality through the Septenary derivation
layer, using the displayed relations as operational anchors f...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``LOGARITHMIC ADDRESS DIMENSIONALITY is valid when the stated geometric or topological
relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0641_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
