\tzpanchor{0658}
\tzpentryheader{0658}{Convergence Locus Equation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f8728512-fc4f-554c-a4ba-abf27a6345cd}}\\
\textbf{PiID} & \tzpcode{0122495343014} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{665}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2527.9776 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.1653 rad}\\
\textbf{TZPID} & \tzpcode{ID0658} & \textbf{Node Dependencies}\quad \tzpidref{0657}\\
\textbf{Registry} & \tzpcode{registry\_id\_0658} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records convergence locus equation through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\mu\frac{\mathrm{d}g}{\mathrm{d}\mu} = \beta(g,d_{\mathrm{eff}}).
\]
\[
\mu\frac{\mathrm{d}g}{\mathrm{d}\mu}.
\]
\[
\boxed{ \mu\frac{\mathrm{d}g}{\mathrm{d}\mu} = \beta(g,d_{\mathrm{eff}}). }
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mu$: source equation symbol.
    \item $d_{\mathrm{eff}}$: source equation symbol.
    \item $\mathcal{K}_{0658}$: canonical registry object for entry ID 0658.
    \item $\beta(g,d_{eff})$: source equation symbol.
    \item $a(g,d_{eff})$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0658 generated source Wolfram model *)
ClearAll[K0658, Cr0658, T, R, A, W, I, N];
eq0658$1 = HoldForm[mu[dg/dmu] == beta[g, dEff]];
eq0658$2 = HoldForm[mu[dg/dmu]];
eq0658$3 = HoldForm[mu[dg/dmu] == beta[g, dEff]];

K0658 = HoldForm[{eq0658$1, eq0658$2, eq0658$3}];

N = "normalized TRAWIN closure object for Convergence Locus Equation";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Canonical Definition admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Canonical Definition local source condition";

Cr0658[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0658 = Cr0658[K0658];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Canonical Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Canonical Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Convergence Locus Equation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0658] Convergence Locus Equation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mu\frac{\mathrm{d}g}{\mathrm{d}\mu}
=
\beta(g,d_{\mathrm{eff}}).
\end{equation}

\paragraph{Primary Derivation.}
Let $g(\mu)$ be a coupling constant depending on scale $\mu$.  
Near the TZP, effective dimension may vary according to the hyper-dimensional span, so the beta function depends not only on $g$ but also on $d_{\mathrm{eff}}$.

The scale derivative is written as:

\begin{equation}
\mu\frac{\mathrm{d}g}{\mathrm{d}\mu}.
\end{equation}

The renormalization flow law becomes:

\begin{equation}
\boxed{
\mu\frac{\mathrm{d}g}{\mathrm{d}\mu}
=
\beta(g,d_{\mathrm{eff}}).
}
\end{equation}

\paragraph{Interpretation.}
Renormalization becomes navigation through scale and effective dimension.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Convergence Locus Equation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Canonical Definition}\par
\[
\mu\frac{\mathrm{d}g}{\mathrm{d}\mu} = \beta(g,d_{\mathrm{eff}}).
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\mu\frac{\mathrm{d}g}{\mathrm{d}\mu}.
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\boxed{ \mu\frac{\mathrm{d}g}{\mathrm{d}\mu} = \beta(g,d_{\mathrm{eff}}). }
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0658] Convergence Locus Equation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Convergence Locus Equation is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} 32/27=2 to the power wedge 5/3 to the power wedge 3. \textbf{Contextual meaning:} The entry reads Convergence Locus Equation as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Renormalization becomes navigation through scale and effective dimension.

\tzpsection{Equation Grounding}
Equation anchors: 32/27=2 to the power wedge 5/3 to the power wedge 3; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Central-Attractor Pinpointing}: The massive, system-wide calculation used to find the exact, single microscopic dot where all the twisting lines of force and energy are ultimately trying to drag themselves.
\item \textbf{Inevitable-State Destiny Mapping}: The mathematical proof that no matter where you start the experiment, or how messy the initial splash is, the entire system is fated to eventually settle into this one, specific, unmoving shape.
\item \textbf{Multi-Variable Equilibrium Intersection}: The beautiful, elegant moment in the math where a dozen completely different, competing forces all finally cross paths and perfectly cancel each other out, leaving total silence.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0658]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0658_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0658] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Convergence Locus Equation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records convergence locus equation through the Septenary derivation layer,
using the displayed relations as operational anchors for the c...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Convergence Locus Equation is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that the entry records convergence locus equation through the
Septenary derivation layer, using the displayed relations as operational anchors for the
canonical equation chain. Renormalization becomes navigation through scale and effective
dimension. -----------------------------------------------------------------------------
-------------------------------------------. The CHL validation treats the equation as
the formal anchor and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0658_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
