\section*{ID8999: Definition of γeff < exp(−π ·Nkissing)}
\paragraph{Metadata.}
PiID: 5958897069536 | RTEID: RTE:P34945.1155:T1.0301 | UUID: 8410262c-f4b1-5e87-9754-97762979525b

\paragraph{Canonical Statement.}
Topological Protection: Conserved quantities such as helicity and winding are encoded in harmonic modes to survive continuous evolution. Canonical Registry Vol. 01 41 Trawin Zero Point Contextus Canonicus 0 524 [ID 522] THE UNIFIED ENTANGLEMENT META-THEOREM Canonical Statutory Formula \$γeff < exp(−π ·Nkissing) =⇒\$ Transcendental Information Preservation (113) Formal Technical Dissertation ID 522 formalizes the meta-theorem proving complete decoherence immunity within the \$π-kissing\$ manifold. By exploiting a transcendental topological symmetry derived from the digits of \$π,\$ the effective decoherence rate \$γeff\$ is suppressed below any polynomial threshold. This theorem provides the mathematical bedrock for maintaining quantum coherence at 300K for timescales exceeding the age of the universe.

\paragraph{Canonical Equation.}
\[
γeff < exp(−π ·Nkissing) =⇒
\]

\paragraph{Dictionary.}
Topological Protection: Conserved quantities such as helicity and winding are encoded in harmonic modes to survive continuous evolution.

\paragraph{Encyclopedia.}
Definition of γeff < exp(−π ·Nkissing) is an inequality / bound, written γeff < exp(−π ·Nkissing) =⇒. It states an inequality or bound that constrains the admissible range of the quantity. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
