\tzpanchor{0214}
\tzpentryheader{0214}{Frame-Dragging Bessel Shift}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{96e6ed09-1028-537a-ad30-bce7be82c7f4}}\\
\textbf{PiID} & \tzpcode{3344612847564} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{221}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{831.0095 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.3692 rad}\\
\textbf{TZPID} & \tzpcode{ID0214} & \textbf{Node Dependencies}\quad \tzpidref{0213}\\
\textbf{Registry} & \tzpcode{registry\_id\_0214} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Natural Mode & Dragged Mode\\
\textbf{Closure Support} & Shift Difference & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Gyroscopic frame-dragging shifts the Bessel order from the natural-gravity mode

\tzpsection{Canonical Equation}
\[ J_{3/2}(k r) \] to the dragged-frame mode \[ J_{1/2}(k r). \] The difference field \[ J_{3/2}(k r) - J_{1/2}(k r) \] creates an antipodal basin in the interference pattern.

\[
J_{3/2}(kr)
\]
\[
J_{1/2}(kr)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $J_{3/2}(kr)$: source equation symbol.
    \item $J_{1/2}(kr)$: source equation symbol.
    \item $J$: source equation symbol.
    \item $\mathcal{K}_{0214}$: canonical registry object for entry ID 0214.
    \item $D$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0214 generated source Wolfram model *)
ClearAll[K0214, Cr0214, T, R, A, W, I, N];
eq0214$1 = HoldForm[J32[k*r]];
eq0214$2 = HoldForm[J12[k*r]];
eq0214$3 = HoldForm[J32[k*r] - J12[k*r]];
eq0214$4 = HoldForm[J32[kr]];
eq0214$5 = HoldForm[J12[kr]];
eq0214$6 = HoldForm[Delta*J == J32[kr] - J12[kr]];

K0214 = HoldForm[{eq0214$1, eq0214$2, eq0214$3, eq0214$4, eq0214$5, eq0214$6}];

N = "normalized TRAWIN closure object for Frame-Dragging Bessel Shift";
I = "Shift Difference integration/comparison layer";
W = "Dragged Mode wave or operator carrier";
A = "Natural Mode admissible action/amplitude condition";
R = "Dragged Mode rotation/curl preservation layer";
T = "Natural Mode local source condition";

Cr0214[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0214 = Cr0214[K0214];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Natural Mode local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Dragged Mode rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Natural Mode admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Dragged Mode wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Shift Difference integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Frame-Dragging Bessel Shift.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0214] Frame-Dragging Bessel Shift}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
T_{\mathrm{IM}}
=
\frac{1}{u_T}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi_{m_1}$ and $\phi_{m_2}$ be modal states over the hypersurface $\Sigma$.  
Let $\mathcal{L}$ be the transfer operator.

The transfer amplitude from mode $m_2$ into mode $m_1$ is:

\begin{equation}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
\end{equation}

Because the Trawin base unit $u_T$ defines the primitive loop scale of the system, the normalized transfer rate is:

\begin{equation}
\boxed{
T_{\mathrm{IM}}
=
\frac{1}{u_T}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
}
\end{equation}

\paragraph{Interpretation.}
ID 0014 repeats and stabilizes the inter-modal transfer structure introduced earlier, now explicitly as a transfer rate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Frame-Dragging Bessel Shift by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Natural Mode}\par
\[
J_{3/2}(kr)
\]
\noindent This fixes the natural Bessel mode of the undragged sector.\par
\noindent\textbf{2. Dragged Mode}\par
\[
J_{1/2}(kr)
\]
\noindent This identifies the shifted dragged-frame mode.\par
\noindent\textbf{3. Shift Difference}\par
\[
Delta J = J_{3/2}(kr) - J_{1/2}(kr)
\]
\noindent This closes the entry with the explicit mode difference that creates the interference basin.\par

\clearpage
\noindent\textbf{[ID 0214] Frame-Dragging Bessel Shift}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Frame-Dragging Bessel Shift is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Gyroscopic frame-dragging shifts the Bessel order from the natural-gravity mode J sub 3/2 (k r) to the dragged-frame mode J sub 1/2 (k r). The difference field J sub 3/2 (k r) - J sub 1/2 (k r) creates an antipodal basin in the interference pattern. \textbf{Contextual meaning:} The entry reads Frame-Dragging Bessel Shift as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now presents the Bessel-order shift directly, which is much cleaner than carrying the earlier prose sentence in display math. \textbf{Lemma support:} Natural Mode; Dragged Mode; Shift Difference.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
ID 0014 repeats and stabilizes the inter-modal transfer structure introduced earlier, now explicitly as a transfer rate.

\tzpsection{Equation Grounding}
Equation anchors: J sub 3/2 (kr); J sub 1/2 (kr); and Delta J = J sub 3/2 (kr) - J sub 1/2 (kr). Proof route: show that frame-dragging shifts the natural Bessel order into the stated dragged-frame order and difference pattern. Formalization route: prove that the stated Bessel-order difference defines the interference basin claimed by the entry.

\tzpsection{Interpretive Role}
The entry now presents the Bessel-order shift directly, which is much cleaner than carrying the earlier prose sentence in display math.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Order-Shifted Radial Eigenfunctions}: The mathematical alteration of Bessel wave solutions caused by the non-inertial rotation of the propagation medium.
\item \textbf{Azimuthal Drift Induced Nodal Displacement}: The physical twisting and shifting of zero-amplitude standing wave nodes due to fluid vorticity.
\item \textbf{Non-Inertial Bessel Resonance Scaling}: The adjustment of resonant frequencies specifically compensating for the angular momentum of the cavity.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0214]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0214_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0214] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Frame-Dragging Bessel Shift}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} gyroscopic frame-dragging shifts the Bessel order from the natural-gravity mode \textbackslash{}[
J\_3/2(k r) \textbackslash{}] to the dragged-frame mode \textbackslash{}[ J\_1/2(k r)

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Frame-Dragging Bessel Shift is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that gyroscopic frame-dragging shifts the Bessel order from
the natural-gravity mode \textbackslash{}[ J\_3/2(k r) \textbackslash{}] to the dragged-frame mode \textbackslash{}[ J\_1/2(k r). \textbackslash{}]
The difference field \textbackslash{}[ J\_3/2(k r) - J\_1/2(k r) \textbackslash{}] creates an antipodal basin in the
interference pattern. ID 0014 repeats and stabilizes the inter-modal transfer structure
introduced earlier, now explicitly as a transfer rate.. The CHL validation treats the
equation as the formal anchor and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0214_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
