\tzpanchor{0162}
\tzpentryheader{0162}{Associated Bundles and Vacuum Extraction}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{4bea5ffe-d9a0-5a08-898c-689e82bfca78}}\\
\textbf{PiID} & \tzpcode{1027019385211} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{169}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{629.0820 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.0365 rad}\\
\textbf{TZPID} & \tzpcode{ID0162} & \textbf{Node Dependencies}\quad \tzpidref{0161}\\
\textbf{Registry} & \tzpcode{registry\_id\_0162} & \textbf{Scale}\quad field-sector bundles induced from the principal bundle\\
\textbf{LOC Classification} & QA612.6 associated bundles & QC20 electromagnetic topology\\
\textbf{arXiv Classification} & Primary: math.DG \quad Cross-list: hep-th, quant-ph & \\
\textbf{Primary Support} & Beat-to-Energy Functor & Vacuum Extraction Density\\
\textbf{Closure Support} & TZP Coupling Integral & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Associated Bundles and Vacuum Extraction entry receives the extraction portion of the cymatic bifurcation source: a beat-to-energy functor, a vacuum-weighted extraction density, and a TZP coupling integral.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathcal{F}_{\mathrm{beat}\to E}:\mathbf{Acoustic}\longrightarrow\mathbf{Energy}
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathcal{E}_{\mathrm{extract}}(t)=|\mathcal{B}(t)|^2\,\mathcal{C}(t)^2\,\rho_{\mathrm{vac}}
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\eta_{\mathrm{TZP}}=\int_0^T \mathcal{E}_{\mathrm{extract}}(t)\,\chi_{\mathrm{TZP}}(t)\,dt
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{F}$: source equation symbol.
    \item $E$: source equation symbol.
    \item $\mathcal{E}_{\mathrm{extract}}(t)$: source equation symbol.
    \item $\mathcal{B}(t)$: magnetic field magnitude.
    \item $\mathcal{C}(t)$: speed of light or relativistic conversion factor.
    \item $\rho_{\mathrm{vac}}$: source equation symbol.
    \item $T$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0162 generated source Wolfram model *)
ClearAll[K0162, Cr0162, T, R, A, W, I, N];
eq0162$1 = HoldForm[$FbeattoE[mathbfAcoustic] -> mathbfEnergy$];
eq0162$2 = HoldForm[$EExtract[t] == Abs[B[t]]^2*C[t]^2*rhoVac$];
eq0162$3 = HoldForm[$etaTZP == Integral0^T*EExtract[t]*chiTZP[t]*dt$];

K0162 = HoldForm[{eq0162$1, eq0162$2, eq0162$3}];

N = "normalized TRAWIN closure object for Associated Bundles and Vacuum Extraction";
I = "TZP Coupling Integral integration/comparison layer";
W = "Vacuum Extraction Density wave or operator carrier";
A = "Beat-to-Energy Functor admissible action/amplitude condition";
R = "Vacuum Extraction Density rotation/curl preservation layer";
T = "Beat-to-Energy Functor local source condition";

Cr0162[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0162 = Cr0162[K0162];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Beat-to-Energy Functor local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Vacuum Extraction Density rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Beat-to-Energy Functor admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Vacuum Extraction Density wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TZP Coupling Integral integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Associated Bundles and Vacuum Extraction.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0162] Associated Bundles and Vacuum Extraction}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathcal{F}_{\mathrm{beat}\to E}:\mathbf{Acoustic}\longrightarrow\mathbf{Energy}
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathcal{E}_{\mathrm{extract}}(t)=|\mathcal{B}(t)|^2\,\mathcal{C}(t)^2\,\rho_{\mathrm{vac}}
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\eta_{\mathrm{TZP}}=\int_0^T \mathcal{E}_{\mathrm{extract}}(t)\,\chi_{\mathrm{TZP}}(t)\,dt
$
\end{adjustbox}
\]

\paragraph{Primary Derivation.}
The expression \( \mathcal{F}_{\mathrm{beat}\to E}:\mathbf{Acoustic}\longrightarrow\mathbf{Energy} \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. Within the TRAWIN framework, the equation functions as the integral carrier for the entry’s information content. Under CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Associated Bundles and Vacuum Extraction by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Beat-to-Energy Functor}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathcal{F}_{\mathrm{beat}\to E}:\mathbf{Acoustic}\longrightarrow\mathbf{Energy}
$
\end{adjustbox}
\]
\noindent This places the source functorial map on the vacuum extraction support page.\par
\noindent\textbf{2. Vacuum Extraction Density}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathcal{E}_{\mathrm{extract}}(t)=|\mathcal{B}(t)|^2\,\mathcal{C}(t)^2\,\rho_{\mathrm{vac}}
$
\end{adjustbox}
\]
\noindent This records the envelope, carrier, and vacuum-density factors used for extraction.\par
\noindent\textbf{3. TZP Coupling Integral}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\eta_{\mathrm{TZP}}=\int_0^T \mathcal{E}_{\mathrm{extract}}(t)\,\chi_{\mathrm{TZP}}(t)\,dt
$
\end{adjustbox}
\]
\noindent This closes the extraction chain as a time-windowed TZP coupling yield.\par

\clearpage
\noindent\textbf{[ID 0162] Associated Bundles and Vacuum Extraction}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Associated Bundles and Vacuum Extraction is a Definition  . From the principal bundle one constructs associated bundles: the gravitational tangent bundle, an electromagnetic line bundle with first Chern class , a nuclear vector bundle of rank 8, and a vacuum extraction bundle trivializing into .  

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} From the principal bundle one constructs associated bundles: the gravitational tangent bundle, an electromagnetic line bundle with first Chern class , a nuclear vector bundle of rank 8, and a vacuum extraction bundle trivializing into .  
\textbf{Contextual meaning:} Each fundamental interaction corresponds to an associated bundle derived from the principal bundle; the vacuum extraction bundle encodes Hilbert space valued fibers for zero point energy extraction.  
\textbf{Derivable consequences:} Determines how matter and field representations are fibered; ensures gauge invariance of particle fields; defines quantization of electromagnetic flux; provides a space for vacuum excitations.  
\textbf{Lemma support:} From the principal bundle one constructs associated bundles: the gravitational tangent bundle, an electromagnetic line bundle with first Chern class , a nuclear vector bundle of rank 8, and a vacuum extraction bundle trivializing into .  \par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Absence of these associated bundles or mismatch in rank or Chern class would c

\tzpsection{Equation Grounding}
From the principal bundle one constructs associated bundles: the gravitational tangent bundle, an electromagnetic line bundle with first Chern class , a nuclear vector bundle of rank 8, and a vacuum extraction bundle trivializing into .  

\tzpsection{Interpretive Role}
Each fundamental interaction corresponds to an associated bundle derived from the principal bundle; the vacuum extraction bundle encodes Hilbert space valued fibers for zero point energy extraction.  
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Gravitational Associated Bundle}: The definition of the geometric sector induced from the principal bundle.
\item \textbf{Electromagnetic Topological Charge}: The recording of the topological content of the electromagnetic associated bundle.
\item \textbf{Vacuum Bundle Realization}: The identification of the vacuum-extraction sector with a Hilbert-type associated bundle.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0162]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0162_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0162] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Associated Bundles and Vacuum Extraction}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} each fundamental interaction corresponds to an associated bundle derived from the
principal bundle; the vacuum extraction bundle encodes Hilbert-sp...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Associated Bundles and Vacuum Extraction is well formed when the total space, base
space, structure group, and projection map are compatible.''\\
\textbf{Proof:} The source statement supplies a bundle-style construction. The CHL reading treats the
base as the proposition carrier, the fiber or structure group as the typed parameter,
and the projection as the categorical morphism that preserves local-to-global structure.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- principal-bundle structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0162_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
