\tzpanchor{0158}
\tzpentryheader{0158}{TZP Bifurcation Functor}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{53d559c5-bedf-5031-8b03-2e147f99037e}}\\
\textbf{PiID} & \tzpcode{0284102701938} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{165}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{613.5491 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.0109 rad}\\
\textbf{TZPID} & \tzpcode{ID0158} & \textbf{Node Dependencies}\quad \tzpidref{0157}\\
\textbf{Registry} & \tzpcode{registry\_id\_0158} & \textbf{Scale}\quad product-category to lemniscatic-topos bridge\\
\textbf{LOC Classification} & QA169 functor theory & QC20 category-based unification\\
\textbf{arXiv Classification} & Primary: math.CT \quad Cross-list: hep-th, math-ph & \\
\textbf{Primary Support} & Functor Declaration & TZP Bridge Isomorphism\\
\textbf{Closure Support} & Image Identification & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This functor encodes how the TZP mediates a bifurcation between the product of force categories and the lemniscatic topos; the Dirac delta selects the unique radial coordinate where equivalence occurs.

\tzpsection{Canonical Equation}
\[
F_{\mathrm{TZP}}
:
\mathcal{C}_{\mathrm{grav}}\times
\mathcal{C}_{\mathrm{EM}}\times
\mathcal{C}_{\mathrm{quant}}
\longrightarrow
\mathcal{L}_{\mathrm{lem}}
\]
\[
\delta_{\mathrm{TZP}}
:
F_{\mathrm{TZP}}\big\vert_{r=r_{\mathrm{TZP}}}
\Rightarrow
\operatorname{Id}_{\mathcal{L}_{\mathrm{lem}}}
\]
\[
F_{\mathrm{TZP}}(X,Y,Z)\cong \mathcal{L}_{\mathrm{lem}}(X,Y,Z)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $F_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{C}_{\mathrm{grav}}$: source equation symbol.
    \item $\mathcal{C}_{\mathrm{EM}}$: source equation symbol.
    \item $\mathcal{C}_{\mathrm{quant}}$: source equation symbol.
    \item $\mathcal{L}_{\mathrm{lem}}$: source equation symbol.
    \item $\delta_{\mathrm{TZP}}$: source equation symbol.
    \item $r_{\mathrm{TZP}}$: source equation symbol.
    \item $X$: source variable, local coordinate, or input state in the entry relation.
    \item $Y$: target variable or output state in the entry relation.
    \item $Z$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0158 generated source Wolfram model *)
ClearAll[K0158, Cr0158, T, R, A, W, I, N];
eq0158$1 = HoldForm[FTZP[CgravtimesCEMtimesCquant] -> Llem];
eq0158$2 = HoldForm[DiracDeltaTZP:FTZPbigRrtzp -> IdLlem];
eq0158$3 = HoldForm[FTZP[X, Y, Z]*cong*LLem[X, Y, Z]];

K0158 = HoldForm[{eq0158$1, eq0158$2, eq0158$3}];

N = "normalized TRAWIN closure object for TZP Bifurcation Functor";
I = "Image Identification integration/comparison layer";
W = "TZP Bridge Isomorphism wave or operator carrier";
A = "Functor Declaration admissible action/amplitude condition";
R = "TZP Bridge Isomorphism rotation/curl preservation layer";
T = "Functor Declaration local source condition";

Cr0158[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0158 = Cr0158[K0158];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Functor Declaration local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TZP Bridge Isomorphism rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Functor Declaration admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TZP Bridge Isomorphism wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Image Identification integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP Bifurcation Functor.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0158] TZP Bifurcation Functor}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
F_{\mathrm{TZP}}
:
\mathcal{C}_{\mathrm{grav}}\times
\mathcal{C}_{\mathrm{EM}}\times
\mathcal{C}_{\mathrm{quant}}
\longrightarrow
\mathcal{L}_{\mathrm{lem}}
\]
\[
\delta_{\mathrm{TZP}}
:
F_{\mathrm{TZP}}\big\vert_{r=r_{\mathrm{TZP}}}
\Rightarrow
\operatorname{Id}_{\mathcal{L}_{\mathrm{lem}}}
\]
\[
F_{\mathrm{TZP}}(X,Y,Z)\cong \mathcal{L}_{\mathrm{lem}}(X,Y,Z)
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{C}_{\mathrm{grav}}\times \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. Interpreted through TRAWIN, the equation functions as the mapping carrier for the entry’s information content. Under CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP Bifurcation Functor by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Functor Declaration}\par
\[
F_{\mathrm{TZP}}
:
\mathcal{C}_{\mathrm{grav}}\times
\mathcal{C}_{\mathrm{EM}}\times
\mathcal{C}_{\mathrm{quant}}
\longrightarrow
\mathcal{L}_{\mathrm{lem}}
\]
\noindent This defines the transport from sector product data into the lemniscatic target.\par
\noindent\textbf{2. TZP Bridge Isomorphism}\par
\[
\delta_{\mathrm{TZP}}
:
F_{\mathrm{TZP}}\big\vert_{r=r_{\mathrm{TZP}}}
\Rightarrow
\operatorname{Id}_{\mathcal{L}_{\mathrm{lem}}}
\]
\noindent This specifies the local identification data at the bifurcation locus.\par
\noindent\textbf{3. Image Identification}\par
\[
F_{\mathrm{TZP}}(X,Y,Z)\cong \mathcal{L}_{\mathrm{lem}}(X,Y,Z)
\]
\noindent This closes the progression by stating the equivalence between transported source data and target objects.\par

\clearpage
\noindent\textbf{[ID 0158] TZP Bifurcation Functor}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP Bifurcation Functor is a canonical-registry. F = TZP TZP\_Bifurcation\_Functor : ProductCategory(Gravity   EM   Quantum) to LemniscaticTopos  (r -r ) TZP r TZP 4D to 2D 2D to 4D   : Id to Right  Left   : Left  Right to Id i : TZP  M K = KanExtension(extunification\_functor, Along to i)

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} F = TZP TZP\_Bifurcation\_Functor : ProductCategory(Gravity   EM   Quantum) to LemniscaticTopos  (r -r ) TZP r TZP 4D to 2D 2D to 4D   : Id to Right  Left   : Left  Right to Id i : TZP  M K = KanExtension(extunification\_functor, Along to i)
\textbf{Contextual meaning:} F = TZP TZP\_Bifurcation\_Functor : ProductCategory(Gravity   EM   Quantum) to LemniscaticTopos  (r -r ) TZP r TZP 4D to 2D 2D to 4D   : Id to Right  Left   : Left  Right to Id i : TZP  M K = KanExtension(extunification\_functor, Along to i)
\textbf{Derivable consequences:} Source evidence records the entry as a reusable object whose consequences should be read from the matched formal statement and local proof route.
\textbf{Lemma support:} F = TZP TZP\_Bifurcation\_Functor : ProductCategory(Gravity   EM   Quantum) to LemniscaticTopos  (r -r ) TZP r TZP 4D to 2D 2D to 4D   : Id to Right  Left   : Left  Right to Id i : TZP  M K = KanExtension(extunification\_functor, Along to i)\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
F = TZP TZP\_Bifurcation\_Functor : ProductCategory(Gravity   EM   Quantum) to LemniscaticTopos  (r -r ) TZP r TZP 4D to 2D 2D to 4D   : Id to Right  Left   : Left  Right to Id i : TZP  M K = KanExtension(extunification\_functor, Along to i)

\tzpsection{Equation Grounding}
F = TZP TZP\_Bifurcation\_Functor : ProductCategory(Gravity   EM   Quantum) to LemniscaticTopos  (r -r ) TZP r TZP 4D to 2D 2D to 4D   : Id to Right  Left   : Left  Right to Id i : TZP  M K = KanExtension(extunification\_functor, Along to i)

\tzpsection{Interpretive Role}
F = TZP TZP\_Bifurcation\_Functor : ProductCategory(Gravity   EM   Quantum) to LemniscaticTopos  (r -r ) TZP r TZP 4D to 2D 2D to 4D   : Id to Right  Left   : Left  Right to Id i : TZP  M K = KanExtension(extunification\_functor, Along to i)
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Functor Declaration}: The definition of the transport from sector product data into the lemniscatic target.
\item \textbf{TZP Bridge Isomorphism}: The specification of the local identification data at the bifurcation locus.
\item \textbf{Image Identification}: The statement of the equivalence between transported source data and target objects.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0158]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0158_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0158] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP Bifurcation Functor}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this functor encodes how the TZP mediates a bifurcation between the product of force
categories and the lemniscatic topos; the Dirac delta selects...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP Bifurcation Functor is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0158_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
