\section*{ID9410: Definition of Π𝑖M}
\paragraph{Metadata.}
PiID: 7939612257142 | RTEID: RTE:P36541.1197:T3.6599 | UUID: 49c87a0c-22c0-5f4b-8a61-07186fc26154

\paragraph{Canonical Statement.}
sabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0362], [ID 0300] Node registry\_id\_0363 Support Titles Variation Law; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links M= \$⊕𝑁\$ 𝑖=1M𝑖 \$Π𝑖M=𝑚𝑖\$ , \$∑\$ 𝑖 \$Π𝑖=id\$ Rec(\{𝑚𝑖 \})=M [ID 0364] Unified Navigation and Temporal Winding TZPID ID0364 UUID b0e5b7db-c033-51c4-b3f6-e92b5e2b7941 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops unified navigation and

\paragraph{Canonical Equation.}
\[
Π𝑖M=𝑚𝑖
\]

\paragraph{Dictionary.}
Definition of Π𝑖M — Π𝑖M=𝑚𝑖

\paragraph{Encyclopedia.}
Definition of Π𝑖M is an algebraic definition, written Π𝑖M=𝑚𝑖. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
