\tzpanchor{0236}
\tzpentryheader{0236}{Magnetic Reynolds Number}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{6343f00d-0714-5c02-ad52-d2d67da1ce7a}}\\
\textbf{PiID} & \tzpcode{3165271201909} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{243}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{916.4404 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.5100 rad}\\
\textbf{TZPID} & \tzpcode{ID0236} & \textbf{Node Dependencies}\quad \tzpidref{0235}\\
\textbf{Registry} & \tzpcode{registry\_id\_0236} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Dimensionless Ratio & Critical Regime\\
\textbf{Closure Support} & Normalized Threshold & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The magnetic Reynolds number is R\_m = mu\_0 sigma L v = L\^{}2 omega mu\_0 sigma, representing the ratio of magnetic advection to diffusion.

\tzpsection{Canonical Equation}
\[
R_m=\mu_0\sigma vL
\]
\[
R_m=\mu_0\sigma L^2\omega
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $R_m$: source equation symbol.
    \item $\mu_0$: vacuum permeability constant.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $\omega$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0236 generated source Wolfram model *)
ClearAll[K0236, Cr0236, T, R, A, W, I, N];
eq0236$1 = HoldForm[RM == mu0*sigma*vL];
eq0236$2 = HoldForm[RM == mu0*sigma*L^2*omega];
eq0236$3 = HoldForm[RM == vL/eta];

K0236 = HoldForm[{eq0236$1, eq0236$2, eq0236$3}];

N = "normalized TRAWIN closure object for Magnetic Reynolds Number";
I = "Normalized Threshold integration/comparison layer";
W = "Critical Regime wave or operator carrier";
A = "Dimensionless Ratio admissible action/amplitude condition";
R = "Critical Regime rotation/curl preservation layer";
T = "Dimensionless Ratio local source condition";

Cr0236[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0236 = Cr0236[K0236];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Dimensionless Ratio local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Critical Regime rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Dimensionless Ratio admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Critical Regime wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Threshold integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Magnetic Reynolds Number.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0236] Magnetic Reynolds Number}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mathcal{V}_T\phi_{\omega}
=
\sqrt{
\frac{\hbar\omega}{2}
}
\,\phi_{\omega}
\coth\left(
\frac{\omega}{2\omega_0}
\right).
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi_{\omega}$ be a field mode of frequency $\omega$.  
The zero-point amplitude of a harmonic mode is proportional to:

\begin{equation}
\sqrt{\frac{\hbar\omega}{2}} .
\end{equation}

In the TZP setting, this amplitude is modulated by a spectral thermal-like factor:

\begin{equation}
\coth\left(
\frac{\omega}{2\omega_0}
\right),
\end{equation}

where $\omega_0$ is the characteristic frequency determined by the spectral density scale.

Acting on the mode $\phi_{\omega}$ gives:

\begin{equation}
\boxed{
\mathcal{V}_T\phi_{\omega}
=
\sqrt{
\frac{\hbar\omega}{2}
}
\,\phi_{\omega}
\coth\left(
\frac{\omega}{2\omega_0}
\right).
}
\end{equation}

\paragraph{Interpretation.}
The vacuum fluctuation operator assigns each mode a zero-point amplitude corrected by the TZP spectral scale.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Magnetic Reynolds Number by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Dimensionless Ratio}\par
\[
R_m=\mu_0\sigma vL
\]
\noindent This defines the transport-to-diffusion balance that controls the magnetic regime.\par
\noindent\textbf{2. Critical Regime}\par
\[
R_m=\mu_0\sigma L^2\omega
\]
\noindent This marks the onset of the self-organizing dynamo window.\par
\noindent\textbf{3. Normalized Threshold}\par
\[
R_m=\frac{vL}{\eta}
\]
\noindent This closes the entry by normalizing the actual regime against the critical threshold.\par

\clearpage
\noindent\textbf{[ID 0236] Magnetic Reynolds Number}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Magnetic Reynolds Number is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The magnetic Reynolds number is R sub m = mu sub 0 sigma L v = L 2 omega mu sub 0 sigma, representing the ratio of magnetic advection to diffusion. \textbf{Contextual meaning:} The entry reads Magnetic Reynolds Number as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry gives the later dynamo closure pages an actual diagnostic parameter instead of a purely verbal regime claim. \textbf{Lemma support:} Dimensionless Ratio; Critical Regime; Normalized Threshold.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The vacuum fluctuation operator assigns each mode a zero-point amplitude corrected by the TZP spectral scale.

\tzpsection{Equation Grounding}
Equation anchors: R sub m=mu sub 0sigma vL; R sub m=mu sub 0sigma L to the power 2omega; and R sub m=ratio vL eta. Proof route: show that exceeding the critical ratio is necessary for the self-excited magnetic regime stated in the surrounding arc. Formalization route: prove that the normalized dynamo ratio is dimensionless and monotone in the stated transport variables.

\tzpsection{Interpretive Role}
The entry gives the later dynamo closure pages an actual diagnostic parameter instead of a purely verbal regime claim.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Advective-to-Diffusive Magnetic Ratio}: The dimensionless number determining whether magnetic field lines are dragged by fluid motion or slip through it via resistance.
\item \textbf{Conductivity-Governed Flux Entrainment}: The threshold characterizing how strongly a highly conductive plasma binds and carries its own internal magnetic structure.
\item \textbf{Plasma Flow Domination Threshold}: The specific value (Rm > 1) where fluid kinetic energy officially overpowers magnetic diffusion.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0236]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0236_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0236] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Magnetic Reynolds Number}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the magnetic Reynolds number is R\textbackslash{}\_m = mu\textbackslash{}\_0 sigma L v = L\textbackslash{}\textasciicircum{}2 omega mu\textbackslash{}\_0 sigma,
representing the ratio of magnetic advection to diffusion

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Magnetic Reynolds Number is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0236_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
