\tzpanchor{0241}
\tzpentryheader{0241}{Elsasser Number Scaling Law}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{ed34e834-1db7-56f6-a841-906774806fb8}}\\
\textbf{PiID} & \tzpcode{7120190914564} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{248}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{935.8565 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.5420 rad}\\
\textbf{TZPID} & \tzpcode{ID0241} & \textbf{Node Dependencies}\quad \tzpidref{0240}\\
\textbf{Registry} & \tzpcode{registry\_id\_0241} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Elsasser Balance & Order-One Window\\
\textbf{Closure Support} & Critical Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Elsasser number across diverse systems tends toward unity; laboratory values range from 10\^{}-2 to 10\^{}1, the Earth's core from 0.5 to 2, and Jovian and solar interiors from 1 to 10.

\tzpsection{Canonical Equation}
\[
\Lambda=\frac{B^2}{\rho\mu_0\eta\Omega}
\]
\[
10^{-2}\leq\Lambda_{\mathrm{lab}}\leq 10^{1}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Lambda$: lemniscatic representative or canonical branch object.
    \item $B$: magnetic field magnitude.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\mu_0$: vacuum permeability constant.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $\Lambda_{\mathrm{lab}}$: source equation symbol.
    \item $\Lambda_{\mathrm{core}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0241 generated source Wolfram model *)
ClearAll[K0241, Cr0241, T, R, A, W, I, N];
eq0241$1 = HoldForm[Lambda == B^2/(rhomu0*etaOmega)];
eq0241$2 = HoldForm[10^(-2) <= LambdaLab <= 10^1];
eq0241$3 = HoldForm[LambdaCore == 1];

K0241 = HoldForm[{eq0241$1, eq0241$2, eq0241$3}];

N = "normalized TRAWIN closure object for Elsasser Number Scaling Law";
I = "Critical Closure integration/comparison layer";
W = "Order-One Window wave or operator carrier";
A = "Elsasser Balance admissible action/amplitude condition";
R = "Order-One Window rotation/curl preservation layer";
T = "Elsasser Balance local source condition";

Cr0241[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0241 = Cr0241[K0241];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Elsasser Balance local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Order-One Window rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Elsasser Balance admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Order-One Window wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Critical Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Elsasser Number Scaling Law.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0241] Elsasser Number Scaling Law}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
H
=
\int_V
\mathbf{A}\cdot\mathbf{B}
\,\mathrm{d}^3x .
\end{equation}

\paragraph{Quantized Form.}
\begin{equation}
H=w\,\Phi .
\end{equation}

\paragraph{Primary Derivation.}
Let $\mathbf{A}$ be the magnetic vector potential and $\mathbf{B}$ the magnetic field.  
Magnetic helicity measures the linkage, twist, and winding of magnetic field lines inside a volume $V$:

\begin{equation}
H
=
\int_V
\mathbf{A}\cdot\mathbf{B}
\,\mathrm{d}^3x .
\end{equation}

If the magnetic structure winds around the TZP with integer winding number $w$, and if $\Phi$ denotes the magnetic flux through the lemniscatic loop, then helicity decomposes into winding times flux:

\begin{equation}
\boxed{
H=w\,\Phi .
}
\end{equation}

\paragraph{Interpretation.}
Magnetic helicity becomes quantized when the field topology is constrained by integer TZP winding.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Elsasser Number Scaling Law by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Elsasser Balance}\par
\[
\Lambda=\frac{B^2}{\rho\mu_0\eta\Omega}
\]
\noindent This defines the balance between magnetic and rotational effects.\par
\noindent\textbf{2. Order-One Window}\par
\[
10^{-2}\leq\Lambda_{\mathrm{lab}}\leq 10^{1}
\]
\noindent This isolates the order-one window emphasized throughout the magnetic-universality arc.\par
\noindent\textbf{3. Critical Closure}\par
\[
\Lambda_{\mathrm{core}}\approx 1
\]
\noindent This closes the entry by measuring departure from the critical balance.\par

\clearpage
\noindent\textbf{[ID 0241] Elsasser Number Scaling Law}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Elsasser Number Scaling Law is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The Elsasser number across diverse systems tends toward unity; laboratory values range from 10 -2 to 10 1, the Earth s core from 0.5 to 2, and Jovian and solar interiors from 1 to 10. \textbf{Contextual meaning:} The entry reads Elsasser Number Scaling Law as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry sharpens the universality narrative by replacing qualitative balance with an explicit order-one criterion. \textbf{Lemma support:} Elsasser Balance; Order-One Window; Critical Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Magnetic helicity becomes quantized when the field topology is constrained by integer TZP winding.

\tzpsection{Equation Grounding}
Equation anchors: Lambda=ratio B to the power 2 rhomu sub 0etaOmega; 10 to the power -2 leqLambda sub lab leq 10 to the power 1; and Lambda sub core approximately 1. Proof route: show that the critical regime corresponds to order-one Elsasser balance for the stated carrier variables. Formalization route: prove that the closure metric vanishes exactly at the critical balance.

\tzpsection{Interpretive Role}
The entry sharpens the universality narrative by replacing qualitative balance with an explicit order-one criterion.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Universal Magnetic-Rotational Feedback Scaling}: The derivation of a broad physical law constraining the relationship between a planet's spin and the strength of its magnetic field.
\item \textbf{Parameter-Space Confinement of Planetary Dynamos}: The observation that almost all active celestial dynamos naturally self-regulate to an Elsasser number of approximately one.
\item \textbf{Equipartition Regimes Across Scale}: The principle demonstrating that the balance of Coriolis and Lorentz forces holds true from laboratory spheres to gas giant planets.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0241]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0241_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0241] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Elsasser Number Scaling Law}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the Elsasser number across diverse systems tends toward unity; laboratory values range
from 10\textbackslash{}\textasciicircum{}-2 to 10\textbackslash{}\textasciicircum{}1, the Earth's core from 0.5 to 2, and Jo...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Elsasser Number Scaling Law is valid when the stated geometric or topological relation
preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0241_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
