\section*{ID9865: Resulting Entangled Electron–Phonon Kernels: K\_e,ph(x\_e,x\_ph;θ\_e,ph)}
\paragraph{Metadata.}
PiID: 9895353945909 | RTEID: RTE:P38307.9858:T0.2879 | UUID: 46ac06d4-ebae-5222-91f9-30c889284be4

\paragraph{Canonical Statement.}
Under suitable approximations (linear response, weak coupling), one can derive effective kernels \textbackslash{}[ K\_\{e,\textbackslash{}mathrm\{ph\}\}(x\_e,x\_\{\textbackslash{}mathrm\{ph\}\};\textbackslash{}theta\_\{e,\textbackslash{}mathrm\{ph\}\}) \textbackslash{}] describing the joint state of an electron at position \$x\_e\$ and a phonon at \$x\_\{\textbackslash{}mathrm\{ph\}\}\$. The design task then becomes to tune \$g\_\{n,\textbackslash{}sigma\}(q)\$, and thus the local geometry and composition parameters, so that \$K\_\{e,\textbackslash{}mathrm\{ph\}\}\$ approximates a desired target kernel, for example one that maximizes a specific entanglement monotone while respecting energy and bandwidth constraints.

\paragraph{Canonical Equation.}
\[
K_{e,\mathrm{ph}}(x_e,x_{\mathrm{ph}};\theta_{e,\mathrm{ph}})
\]

\paragraph{Dictionary.}
Under suitable approximations (linear response, weak coupling), one can derive effective kernels describing the joint state of an electron at position x\_e and a phonon at x\_ph [ID9865]

\paragraph{Encyclopedia.}
Resulting Entangled Electron–Phonon Kernels: K\_e,ph(x\_e,x\_ph;θ\_e,ph) is a symbolic expression, written K\_e,ph(x\_e,x\_ph;θ\_e,ph). It introduces a symbol or relation used elsewhere in the framework. It is built from K\_e, x\_e, x\_. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
