\section*{ID9867: Cymatic Control of Meta-Atom Parameters: K\_p(x\_1,x\_2;θ\_p(t))}
\paragraph{Metadata.}
PiID: 9535394590944 | RTEID: RTE:P38315.7522:T0.3007 | UUID: 7383a971-44d1-57c8-9b05-673e5b49005b

\paragraph{Canonical Statement.}
In addition to gravitational-wave coupling, the cymatic term \$\textbackslash{}Hhat\_\{\textbackslash{}mathrm\{cymatic\}\}\$ in \textbackslash{}eqref\{eq:Htrawin-paper3\} drives material parameters within the meta-atoms. Acoustic pressure fields at frequencies \$\textbackslash{}Omega\_\{\textbackslash{}mathrm\{cym\}\}\$ and their harmonics modulate local potentials \$V\_\{p,\textbackslash{}sigma\}(s)\$ and couplings \$J\_p(s)\$, effectively sweeping through families of entanglement kernels \$K\_p(x\_1,x\_2;\textbackslash{}theta\_p(t))\$. The interplay between gravitational modulation and cymatic control allows one to synchronize topological, geometric, and material degrees of freedom at or near the TZP.

\paragraph{Canonical Equation.}
\[
K_p(x_1,x_2;\theta_p(t))
\]

\paragraph{Dictionary.}
In addition to gravitational-wave coupling, the cymatic term Hhat\_cymatic in eq:Htrawin-paper3 drives material parameters within the meta-atoms.

\paragraph{Encyclopedia.}
Cymatic Control of Meta-Atom Parameters: K\_p(x\_1,x\_2;θ\_p(t)) is a symbolic expression, written K\_p(x\_1,x\_2;θ\_p(t)). It introduces a symbol or relation used elsewhere in the framework. It is built from K\_p, x\_1, x\_2, p. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
