\section*{ID8817: GERBE BANDING (CHERN CLASS) Canonical Statutory Formula: MathfrakG Gerbe}
\paragraph{Metadata.}
PiID: 5916685451333 | RTEID: RTE:P34238.3691:T6.1488 | UUID: 937d551a-1907-5f72-8493-f4b6b99cd1ef

\paragraph{Canonical Statement.}
[ID 1144] GERBE BANDING (CHERN CLASS) Canonical Statutory Formula: \$\textbackslash{}mathfrak\{G\} \{gerbe\} = \textbackslash{}text\{Gerbe\}[U(1) \{quant\}, c\_3 \textbackslash{}in H\textasciicircum{}3(\textbackslash{}mathcal\{M\}, \textbackslash{}mathbb\{Z\})]\$ Formal Technical Dissertation: Specifies the U(1) quantum Gerbe banded by the third Chern class \$c\_3\$. This invariant enforces the quantization of vacuum flux within the stack structure. Source: [17]

\paragraph{Canonical Equation.}
\[
\mathfrak{G} {gerbe} = \text{Gerbe}[U(1) {quant}, c_3 \in H^3(\mathcal{M}, \mathbb{Z})]
\]

\paragraph{Dictionary.}
GERBE BANDING (CHERN CLASS) Canonical Statutory Formula: \$ G gerbe = Gerbe[U(1) quant, c\_3 H\textasciicircum{}3(M, Z)]\$ Formal Technical Dissertation: Specifies the U(1) quantum Gerbe banded by the third Chern class c\_3.

\paragraph{Encyclopedia.}
GERBE BANDING (CHERN CLASS) Canonical Statutory Formula: MathfrakG Gerbe is an algebraic definition, written mathfrakG gerbe = Gerbe[U(1) quant, c\_3 in H\textasciicircum{}3(M, Z)]. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from U, q, u, a, n, c\_3, defining mathfrakG gerbe. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
