\section*{ID8873: NODAL MASS OPERATOR Canonical Statutory Formula: M I}
\paragraph{Metadata.}
PiID: 3954800044800 | RTEID: RTE:P34455.8295:T0.2239 | UUID: 691adca4-2bf6-5755-be9d-907b91f2b435

\paragraph{Canonical Statement.}
[ID 1021] NODAL MASS OPERATOR Canonical Statutory Formula: \$\textbackslash{}hat\{M\} i = \textbackslash{}int \{\textbackslash{}Omega\_i\} \textbackslash{}rho\_\{vac\} \textbackslash{}cdot R\_i(t) \textbackslash{}cdot \textbackslash{}det(J\_p) dV\$ Formal Technical Dissertation: Formalizes mass as an "Inertial Shadow" resulting from the interference of vacuum oscillators. Mass precipitates at nodes where phase coherence \$R\_i\$ approaches unity and the Jacobian determinant vanishes. Source: [31]

\paragraph{Canonical Equation.}
\[
\hat{M} i = \int {\Omega_i} \rho_{vac} \cdot R_i(t) \cdot \det(J_p) dV
\]

\paragraph{Dictionary.}
NODAL MASS OPERATOR Canonical Statutory Formula: \$M i = \_i \_vac R\_i(t) (J\_p) dV\$ Formal Technical Dissertation: Formalizes mass as an "Inertial Shadow" resulting from the interference of vacuum oscillators.

\paragraph{Encyclopedia.}
NODAL MASS OPERATOR Canonical Statutory Formula: M I is an expectation / trace over state, written M i = ∫ Ω\_i ρ\_vac · R\_i(t) · det(J\_p) dV. It is computed as an expectation value or trace over a quantum state, producing an observable. It is built from v, a, c, R\_i, J\_p, V, defining M i. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
