\tzpanchor{0455}
\tzpentryheader{0455}{Extraction Phase Timing}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{563e5249-03de-562b-884d-a015e562cd88}}\\
\textbf{PiID} & \tzpcode{2379962749567} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{462}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1762.9828 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.9049 rad}\\
\textbf{TZPID} & \tzpcode{ID0455} & \textbf{Node Dependencies}\quad \tzpidref{0454}\\
\textbf{Registry} & \tzpcode{registry\_id\_0455} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Unified Density & Euler-Lagrange Flow\\
\textbf{Closure Support} & Stationary Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 455 establishes the duration of the steady state extraction phase within the duty cycle12. During the extraction phase, the system maintains resonant coupling with vacuum fluctuations to scavenge energy and information packets13. This phase is subject to the energy time uncertainty relation E t >= \textasciitilde{}/2, requiring a balance between extraction rate and state precision14. Coherence Window: Extraction must complete before decoherence cascades disrupt the 153,600 node lattice15151515. Torque Balance: Angular momentum transfer logic is monitored to prevent mechanical drift during the steady state16161616.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{L}_{U} = \cdots
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{L}_{U}$: source equation symbol.
    \item $U$: auxiliary source state or local chart variable.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $\cdot s$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0455 generated source Wolfram model *)
ClearAll[K0455, Cr0455, T, R, A, W, I, N];
eq0455$1 = HoldForm[LU == Ellipsis];

K0455 = HoldForm[{eq0455$1}];

N = "normalized TRAWIN closure object for Extraction Phase Timing";
I = "Extraction Phase Timing integration/comparison layer";
W = "Extraction Phase Timing wave or operator carrier";
A = "Extraction Phase Timing admissible action/amplitude condition";
R = "Extraction Phase Timing rotation/curl preservation layer";
T = "Extraction Phase Timing local source condition";

Cr0455[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0455 = Cr0455[K0455];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Extraction Phase Timing local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Extraction Phase Timing rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Extraction Phase Timing admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Extraction Phase Timing wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Extraction Phase Timing integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Extraction Phase Timing.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0455] Extraction Phase Timing}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
B_{\partial\Omega}\phi
=
\sum_n b_n(\partial\Omega)\,\phi_n .
\end{equation}

\paragraph{Coefficient Decomposition.}
\begin{equation}
b_n
=
b_n^{\mathrm{geom}}
+
b_n^{\mathrm{top}}
+
b_n^{\mathrm{curv}} .
\end{equation}

\paragraph{Primary Derivation.}
From mode quantization, a confined field can be expanded as:

\begin{equation}
\phi=\sum_n \phi_n .
\end{equation}

Boundary geometry modifies the amplitude or phase of each mode through coefficients $b_n(\partial\Omega)$.

The boundary-response operator is therefore:

\begin{equation}
\boxed{
B_{\partial\Omega}\phi
=
\sum_n b_n(\partial\Omega)\,\phi_n .
}
\end{equation}

The coefficient naturally decomposes into geometric, topological, and curvature components:

\begin{equation}
b_n
=
b_n^{\mathrm{geom}}
+
b_n^{\mathrm{top}}
+
b_n^{\mathrm{curv}} .
\end{equation}

\paragraph{Interpretation.}
Boundaries actively reshape quantum fields by reweighting their confined mode expansion.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Extraction Phase Timing by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{L}_{U} = \cdots
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0455] Extraction Phase Timing}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Extraction Phase Timing is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 455 establishes the duration of the steady state extraction phase within the duty cycle12. During the extraction phase, the system maintains resonant coupling with vacuum fluctuations to scavenge energy and information packets13. This phase is subject to the energy time uncertainty relation E t >= \textbackslash{}textasciitilde\{\}/2, requiring a balance between extraction rate and state precision14. Coherence Window: Extraction must complete before decoherence cascades disrupt the 153,600 node lattice15151515. Torque Balance: Angular momentum transfer logic is monitored to prevent mechanical drift during the steady state16161616.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{L}_{U} = \cdots
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 455 establishes the duration of the steady state extraction phase within the duty cycle12. During the extraction phase, the system maintains resonant coupling with vacuum fluctuations to scavenge energy and information packets13. This phase is subject to the energy time uncertainty relation E t >= \textbackslash{}textasciitilde\{\}/2, requiring a balance between extraction rate and state precision14. Coherence Window: Extraction must complete before decoherence cascades disrupt the 153,600 node lattice15151515. Torque Balance: Angular momentum transfer logic is monitored to prevent mechanical drift during the steady state16161616.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Extraction Phase Timing by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Extraction Phase Timing; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0455]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0455].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0455] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Extraction Phase Timing}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} w\textbackslash{}\_\textbackslash{}\textbackslash{} = int\textbackslash{}\_0\textasciicircum{}\textbackslash{}\_\textbackslash{}\textbackslash{}\textbackslash{} P(t) dt implies text-State Extraction\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``EXTRACTION PHASE TIMING is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0455].
\par\endgroup
\vfill
\endgroup
\endgroup
