\section*{ID7090: How This Compares to Standard Theory: ∼ 10\textasciicircum{}-13}
\paragraph{Metadata.}
PiID: 9046883834363 | RTEID: RTE:P27532.0445:T1.3820 | UUID: ab4d6df3-1b26-54ec-b683-649404a9b86f

\paragraph{Canonical Statement.}
\# 7) How this compares to standard theory - **Newtonian gravity / GR:** predict no dependence of gravitational acceleration on the test mass (universality of free fall). That corresponds to \textbackslash{}(\textbackslash{}alpha=0\textbackslash{}). - **If you measure a nonzero α (significantly outside uncertainties)** you would have discovered a violation of equivalence principle / new coupling. The standard experimental literature places very tight constraints on composition-dependent violations (Eötvös parameter limits \textbackslash{}( \textbackslash{}sim 10\textasciicircum{}\{-13\}\textbackslash{}) or better), but your α parameter as defined here is suppressed by \textbackslash{}(m/M\_\textbackslash{}oplus\textbackslash{}) which makes an α of moderate size produce tiny Δa unless α is enormous.

\paragraph{Canonical Equation.}
\[
\sim 10^{-13}
\]

\paragraph{Dictionary.}
Relation: ∼ 10\textasciicircum{}-13

\paragraph{Encyclopedia.}
How This Compares to Standard Theory: ∼ 10\textasciicircum{}-13 is a scaling / order-of-magnitude relation, written ∼ 10\textasciicircum{}-13. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
