\tzpanchor{0298}
\tzpentryheader{0298}{Self-Excited Dynamo Threshold}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{8401d723-eb17-5361-8551-e610b0f1d8ce}}\\
\textbf{PiID} & \tzpcode{7372458700660} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{305}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1157.2002 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9067 rad}\\
\textbf{TZPID} & \tzpcode{ID0298} & \textbf{Node Dependencies}\quad \tzpidref{0297}\\
\textbf{Registry} & \tzpcode{registry\_id\_0298} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A self-excited dynamo requires the magnetic Reynolds number to exceed a threshold; in liquid-metal experiments R\_m is about 10--50, while planetary dynamos require R\_m around 50 for Mercury and up to 10\^{}4 for Earth and Jupiter.

\tzpsection{Canonical Equation}
\[
R_m=\mu_0\sigma vL
\]
\[
recession and Spin-Orbit Misalignment,display_{\mathrm{bracket}},display_{\mathrm{bracket}},R_m=\frac{vL}{\eta}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $R_m$: source equation symbol.
    \item $\mu_0$: vacuum permeability constant.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $\mathcal{K}_{0298}$: canonical registry object for entry ID 0298.
    \item $\mu$: source equation symbol.
    \item $\eta$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $S$: source equation symbol.
    \item $O$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0298 generated source Wolfram model *)
ClearAll[K0298, Cr0298, T, R, A, W, I, N];
eq0298$1 = HoldForm[RM == mu0*sigma*vL];
eq0298$2 = HoldForm[TZPSequence[recession*and*Spin - Orbit*Misalignment, displayBracket, displayBracket, RM == vL/eta]];
eq0298$3 = HoldForm[RM == vL/eta];

K0298 = HoldForm[{eq0298$1, eq0298$2, eq0298$3}];

N = "normalized TRAWIN closure object for Self-Excited Dynamo Threshold";
I = "Normalized Regime integration/comparison layer";
W = "Scaling Relation wave or operator carrier";
A = "Diagnostic Definition admissible action/amplitude condition";
R = "Scaling Relation rotation/curl preservation layer";
T = "Diagnostic Definition local source condition";

Cr0298[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0298 = Cr0298[K0298];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Diagnostic Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Scaling Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Diagnostic Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Scaling Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Regime integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Self-Excited Dynamo Threshold.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0298] Self-Excited Dynamo Threshold}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Gaussian Approximant.}
\begin{equation}
G_{\sigma}(t)
=
\frac{1}{\sigma\sqrt{2\pi}}
\exp\left(
-\frac{t^2}{2\sigma^2}
\right).
\end{equation}

\paragraph{Delta Limit.}
\begin{equation}
\delta_{\mathrm{inj}}
=
\lim_{\sigma\to0}G_{\sigma}(t).
\end{equation}

\paragraph{Spectral Law.}
\begin{equation}
\widehat{\delta}_{\mathrm{inj}}(\omega)=1.
\end{equation}

\paragraph{Primary Derivation.}
A normalized Gaussian pulse becomes increasingly localized as $\sigma\to0$:

\begin{equation}
G_{\sigma}(t)
=
\frac{1}{\sigma\sqrt{2\pi}}
\exp\left(
-\frac{t^2}{2\sigma^2}
\right).
\end{equation}

In the distributional limit,
\begin{equation}
\delta_{\mathrm{inj}}
=
\lim_{\sigma\to0}G_{\sigma}(t).
\end{equation}

The Fourier transform of the delta distribution is constant:
\begin{equation}
\boxed{
\widehat{\delta}_{\mathrm{inj}}(\omega)=1.
}
\end{equation}

\paragraph{Interpretation.}
A sharply localized injection supplies broad spectral content while preserving local bridge architecture.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Self-Excited Dynamo Threshold by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Diagnostic Definition}\par
\[
R_m=\mu_0\sigma vL
\]
\noindent This defines the scalar diagnostic or conversion quantity named by the title.\par
\noindent\textbf{2. Scaling Relation}\par
\[
recession and Spin-Orbit Misalignment,display_{\mathrm{bracket}},display_{\mathrm{bracket}},R_m=\frac{vL}{\eta}
\]
\noindent This elevates the quantity into a comparative scaling or correlation law.\par
\noindent\textbf{3. Normalized Regime}\par
\[
R_m=\frac{vL}{\eta}
\]
\noindent This closes the entry by normalizing the diagnostic against a stated reference regime.\par

\clearpage
\noindent\textbf{[ID 0298] Self-Excited Dynamo Threshold}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Self-Excited Dynamo Threshold is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A self-excited dynamo requires the magnetic Reynolds number to exceed a threshold; in liquid-metal experiments R sub m is about 10--50, while planetary dynamos require R sub m around 50 for Mercury and up to 10 4 for Earth and Jupiter. \textbf{Contextual meaning:} The entry reads Self-Excited Dynamo Threshold as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons. \textbf{Lemma support:} Diagnostic Definition; Scaling Relation; Normalized Regime.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
A sharply localized injection supplies broad spectral content while preserving local bridge architecture.

\tzpsection{Equation Grounding}
Equation anchors: R sub m=mu sub 0sigma vL; R sub m=mu sub 0sigma L to the power 2omega; and R sub m=ratio vL eta. Proof route: show that the named quantity is dimensionless or consistently scaled in the regime stated by the entry. Formalization route: prove that the normalized diagnostic remains invariant under the intended rescaling.

\tzpsection{Interpretive Role}
The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Minimum Advection Limit for Amplification}: The exact calculation of the required fluid velocity and conductivity needed for a spinning metal core to start generating more magnetism than it loses to resistance.
\item \textbf{Spontaneous Magnetic Field Generation Onset}: The critical mathematical point where the internal feedback loop of the fluid becomes positive, causing a tiny magnetic seed to explode into a massive field.
\item \textbf{Critical Turbulence Point for Feedback}: The required ratio of twisting, cyclonic fluid motion (helicity) to smooth fluid flow needed to successfully close the dynamo loop and sustain the field forever.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0298]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0298_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0298] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Self-Excited Dynamo Threshold}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a self-excited dynamo requires the magnetic Reynolds number to exceed a threshold; in
liquid-metal experiments R\textbackslash{}\_m is about 10--50, while planetar...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Self-Excited Dynamo Threshold is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that a self-excited dynamo requires the magnetic Reynolds
number to exceed a threshold; in liquid-metal experiments R\textbackslash{}\_m is about 10--50, while
planetary dynamos require R\textbackslash{}\_m around 50 for Mercury and up to 10\textbackslash{}\textasciicircum{}4 for Earth and
Jupiter. A sharply localized injection supplies broad spectral content while preserving
local bridge architecture. The entry turns a named scalar quantity into a portable
diagnostic that can anchor nearby comparisons.. The CHL validation treats the equation
as the formal anchor and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0298_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
