\tzpanchor{0065}
\tzpentryheader{0065}{Entanglement Structure}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e1695cee-e298-5d55-a7c1-69a47b9ce1c9}}\\
\textbf{PiID} & \tzpcode{7816406286208} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{72}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{252.4094 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.4159 rad}\\
\textbf{TZPID} & \tzpcode{ID0065} & \textbf{Node Dependencies}\quad \tzpidref{0063}\\
\textbf{Registry} & \tzpcode{registry\_id\_0065} & \textbf{Scale}\quad bipartite and reduced states\\
\textbf{LOC Classification} & QC174.17 entanglement theory & QA188 trace operations\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: hep-th, gr-qc & \\
\textbf{Primary Support} & Composite State & Reduced Density Matrix\\
\textbf{Closure Support} & Entanglement Entropy & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This defines how subsystems are entangled, accounting for the geometric and topological features of the TZP.

\tzpsection{Canonical Equation}
\[
\rho_{A} = \operatorname{Tr}_{B}(\rho_{AB})
\]
\[
S(\rho_{A})
=
-\operatorname{Tr}\!\left(\rho_{A}\log\rho_{A}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\rho_{A}$: source equation symbol.
    \item $A$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $\rho_{AB}$: source equation symbol.
    \item $S$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0065 generated source Wolfram model *)
ClearAll[K0065, Cr0065, T, R, A, W, I, N];
eq0065$1 = HoldForm[rhoA == TrB[rhoAB]];
eq0065$2 = HoldForm[S[rhoA] == -Tr[rhoAlogrhoA]];
eq0065$3 = HoldForm[rhoAB];

K0065 = HoldForm[{eq0065$1, eq0065$2, eq0065$3}];

N = "normalized TRAWIN closure object for Entanglement Structure";
I = "Entanglement Entropy integration/comparison layer";
W = "Reduced Density Matrix wave or operator carrier";
A = "Composite State admissible action/amplitude condition";
R = "Reduced Density Matrix rotation/curl preservation layer";
T = "Composite State local source condition";

Cr0065[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0065 = Cr0065[K0065];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Composite State local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Reduced Density Matrix rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Composite State admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Reduced Density Matrix wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Entanglement Entropy integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Entanglement Structure.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0065] Entanglement Structure}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mathcal{Z}
=
\int \mathcal{D}\phi \, e^{iS[\phi]/\hbar}.
\end{equation}

\paragraph{Primary Derivation.}
Quantum amplitudes are obtained by summing over all field configurations.

Thus:
\begin{equation}
\boxed{
\mathcal{Z}
=
\int \mathcal{D}\phi \, e^{iS[\phi]/\hbar}.
}
\end{equation}

\paragraph{Interpretation.}
Quantum evolution is a weighted sum over histories.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Entanglement Structure by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Composite State}\par
\[
\rho_{AB}
\]
\noindent This is the joint state before subsystem reduction.\par
\noindent\textbf{2. Reduced Density Matrix}\par
\[
\rho_{A} = \operatorname{Tr}_{B}(\rho_{AB})
\]
\noindent This isolates the local state of subsystem \textbackslash{}(A\textbackslash{}).\par
\noindent\textbf{3. Entanglement Entropy}\par
\[
S(\rho_{A})
=
-\operatorname{Tr}\!\left(\rho_{A}\log\rho_{A}\right)
\]
\noindent This closes the progression by quantifying how much information remains shared across the bipartition.\par

\clearpage
\noindent\textbf{[ID 0065] Entanglement Structure}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Entanglement Structure is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This defines how subsystems are entangled, accounting for the geometric and topological features of the TZP. \textbf{Contextual meaning:} The entry reads Entanglement Structure as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry supplies the core quantitative language for the registry s quantum-information branch. It also sets up FractalNodes and topological entanglement descriptions in the next entries. \textbf{Lemma support:} Composite State; Reduced Density Matrix; Entanglement Entropy.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Quantum evolution is a weighted sum over histories.

\tzpsection{Equation Grounding}
Equation anchors: The entanglement structure of a multipartite quantum state on the Trawinistic manifold is characterised by the partition function E(rhoA)=Tru2061 rhoAlogu2061rhoAE(rho A)=textbackslash operatorname Tr textbackslash,rho A textbackslash log rho AE(rhoA)=TrrhoAlogrhoA, where rhoArho ArhoA is the reduced density matrix; curvature and zero-point effects enter through the definition of partial trace and the Hilbert space factorization. The entanglement structure of a multipartite quantum state on the Trawinistic manifold is characterised by the partition function E(rhoA)=Tru2061 rhoAlogu2061rhoAE(rho A)=textbackslash operatorname Tr textbackslash,rho A textbackslash log rho AE(rhoA)=TrrhoAlogrhoA, where rhoArho ArhoA is the reduced density matrix; curvature and zero-point effects enter through the definition of partial trace and the Hilbert space factorization.

\tzpsection{Interpretive Role}
This entry supplies the core quantitative language for the registry s quantum-information branch. It also sets up FractalNodes and topological entanglement descriptions in the next entries.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Entanglement Structure}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Entanglement Structure Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Structure Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0065]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0065_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0065] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Entanglement Structure}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this defines how subsystems are entangled, accounting for the geometric and topological
features of the TZP

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Entanglement Structure is valid as a formal dynamical law when the Hamiltonian or energy
operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0065_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
