\tzpanchor{0452}
\tzpentryheader{0452}{Resonance Peak Frequency Sweep}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{3b5fa0cd-7614-5ab3-8583-bd9ea6a2e817}}\\
\textbf{PiID} & \tzpcode{4462379962749} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{459}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1755.2164 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.8921 rad}\\
\textbf{TZPID} & \tzpcode{ID0452} & \textbf{Node Dependencies}\quad \tzpidref{0451}\\
\textbf{Registry} & \tzpcode{registry\_id\_0452} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Mode Quantization & Dispersion Law\\
\textbf{Closure Support} & Boundary Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 452 establishes the scanning protocol to locate Trawin Zero Point coupling modes. The frequency is swept near 17.2 kHz to identify peaks in energy extraction. These resonances signal alignment of acoustic standing waves with the 153,600 node lattice. Cymatic Locking: Matching the frequency to lemniscatic geometry enhances extraction efficiency. Mode Selection: The sweep identifies specific spherical modes to be pumped during operation.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
k_{\mathrm{n}} = \frac{n\pi}{L}
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $k_{\mathrm{n}}$: mode-indexed wavenumber.
    \item $n$: integer mode index.
    \item $\pi$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0452 generated source Wolfram model *)
ClearAll[K0452, Cr0452, T, R, A, W, I, N];
eq0452$1 = HoldForm[$kN == (nPi/L)*$];

K0452 = HoldForm[{eq0452$1}];

N = "normalized TRAWIN closure object for Resonance Peak Frequency Sweep";
I = "Resonance Peak Frequency Sweep integration/comparison layer";
W = "Resonance Peak Frequency Sweep wave or operator carrier";
A = "Resonance Peak Frequency Sweep admissible action/amplitude condition";
R = "Resonance Peak Frequency Sweep rotation/curl preservation layer";
T = "Resonance Peak Frequency Sweep local source condition";

Cr0452[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0452 = Cr0452[K0452];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Resonance Peak Frequency Sweep local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Resonance Peak Frequency Sweep rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Resonance Peak Frequency Sweep admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Resonance Peak Frequency Sweep wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Resonance Peak Frequency Sweep integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Resonance Peak Frequency Sweep.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0452] Resonance Peak Frequency Sweep}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Pi_{\mu\nu}(x,x')
=
\left.
\frac{\delta^2 W[A]}
{\delta A_\mu(x)\,\delta A_\nu(x')}
\right|_{A=0}.
\end{equation}

\paragraph{Transversality Constraint.}
\begin{equation}
\nabla^\mu \Pi_{\mu\nu}(x,x')=0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $W[A]$ be the effective generating functional for a gauge field $A_\mu$.  
The first variation of $W[A]$ measures linear response to a gauge perturbation.

The second variation extracts the vacuum response tensor:

\begin{equation}
\Pi_{\mu\nu}(x,x')
=
\left.
\frac{\delta^2 W[A]}
{\delta A_\mu(x)\,\delta A_\nu(x')}
\right|_{A=0}.
\end{equation}

Gauge-compatible conservation requires the response tensor to be transverse:

\begin{equation}
\nabla^\mu \Pi_{\mu\nu}(x,x')=0 .
\end{equation}

\paragraph{Interpretation.}
Vacuum polarization records how the vacuum screens, dresses, or responds to gauge excitation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Resonance Peak Frequency Sweep by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
k_{\mathrm{n}} = \frac{n\pi}{L}
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0452] Resonance Peak Frequency Sweep}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Resonance Peak Frequency Sweep is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 452 establishes the scanning protocol to locate Trawin Zero Point coupling modes. The frequency is swept near 17.2 kHz to identify peaks in energy extraction. These resonances signal alignment of acoustic standing waves with the 153,600 node lattice. Cymatic Locking: Matching the frequency to lemniscatic geometry enhances extraction efficiency. Mode Selection: The sweep identifies specific spherical modes to be pumped during operation.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
k_{\mathrm{n}} = \frac{n\pi}{L}
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 452 establishes the scanning protocol to locate Trawin Zero Point coupling modes. The frequency is swept near 17.2 kHz to identify peaks in energy extraction. These resonances signal alignment of acoustic standing waves with the 153,600 node lattice. Cymatic Locking: Matching the frequency to lemniscatic geometry enhances extraction efficiency. Mode Selection: The sweep identifies specific spherical modes to be pumped during operation.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Resonance Peak Frequency Sweep by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Resonance Peak Frequency Sweep; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0452]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0452].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0452] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Resonance Peak Frequency Sweep}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} omega\textbackslash{}\_\textbackslash{}\textbackslash{} = text max\textbackslash{}\textbackslash{}\_f /\textbackslash{} mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{}(f) /\textbackslash{} cap f\textbackslash{}\_\textbackslash{}\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``RESONANCE PEAK FREQUENCY SWEEP is valid as a formal dynamical law when the Hamiltonian
or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0452].
\par\endgroup
\vfill
\endgroup
\endgroup
