\section*{ID9155: Relation: (ρ\_e/ρ)E\_r.}
\paragraph{Metadata.}
PiID: 4699556576121 | RTEID: RTE:P35550.8981:T2.0283 | UUID: de036402-7817-5fc4-b193-25fb2515156a

\paragraph{Canonical Statement.}
es: Electrohydrodynamic coupling; design of ionfocusing devices; synergy with charge oscillation. Falsifiability / Test Handle: Measure conductivity distribution in a vortex; observe current focusing and pinch behaviours. 1.0.27 ID 126: Electrohydrodynamic Resonance Operator Type: Operator Formal Statement: Apply a fluctuating negative charge density \$ρ\_e(t)\$ = \$ρ\_0\$ + \$ρ\_1 cos(ω\$ t) to a vortex region. The total radial acceleration becomes a\_total = \$–(1/ρ)·[∂P\_hydro/∂r+∂P\_electric/∂r]\$ + \$(ρ\_e/ρ)E\_r.\$ When \$ω\$ matches the natural vortex frequency, parametric amplification yields a\_total between 5 and 20 times the baseline a\_r. Interpretive Meaning: Oscillating electric charge modifies the pressure field and produces large amplification of vortex strength, defining an electrohydrodynamic resonance. Dependencies: 125 Derivable Consequences: Resonant enhancement of vortex and current; electrokin

\paragraph{Canonical Equation.}
\[
(ρ_e/ρ)E_r.
\]

\paragraph{Dictionary.}
Relation: (ρ\_e/ρ)E\_r. — (ρ\_e/ρ)E\_r.

\paragraph{Encyclopedia.}
Relation: (ρ\_e/ρ)E\_r. is a symbolic expression, written (ρ\_e/ρ)E\_r.. It introduces a symbol or relation used elsewhere in the framework. It is built from E\_r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
