\section*{ID9414: Definition of 𝑇𝑛+1⊂𝑇𝑛 𝑏𝑖𝑔𝑐𝑎𝑝𝑛≥0𝑇𝑛}
\paragraph{Metadata.}
PiID: 6122571429894 | RTEID: RTE:P36556.6526:T3.6855 | UUID: 9e6d09b5-31e6-5654-a675-f1461e128050

\paragraph{Canonical Statement.}
Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0372], [ID 0300] Node registry\_id\_0373 Support Titles Toroidal Carrier; Nested Inclusion; Core Intersection Test Handle If the toroidal family cannot be ordered into the stated nested chain with zero-point core intersection, the entry fails. Canonical Equation Links 𝑇𝑛=𝑆 1×𝑆1 \$𝑇𝑛+1⊂𝑇𝑛 𝑏𝑖𝑔𝑐𝑎𝑝𝑛≥0𝑇𝑛=TZP\$ [ID 0374] Oscillatory Boundary Field Operator TZPID ID0374 UUID e147a455-7189-504b-b01d-93e39361ef1d Type Operator / Transfer Statement Scale transfer LOC Classification Working routing: QA329 operator theory; QA169 categorical structure arXiv Classification Primary: math.CT; Cross-list: math-ph, cs.LO Canonical Statement This entry develops oscillatory boundary field operator inside the field th

\paragraph{Canonical Equation.}
\[
𝑇𝑛+1⊂𝑇𝑛 𝑏𝑖𝑔𝑐𝑎𝑝𝑛≥0𝑇𝑛=TZP
\]

\paragraph{Dictionary.}
Definition of 𝑇𝑛+1⊂𝑇𝑛 𝑏𝑖𝑔𝑐𝑎𝑝𝑛≥0𝑇𝑛 — 𝑇𝑛+1⊂𝑇𝑛 𝑏𝑖𝑔𝑐𝑎𝑝𝑛≥0𝑇𝑛=TZP

\paragraph{Encyclopedia.}
Definition of 𝑇𝑛+1⊂𝑇𝑛 𝑏𝑖𝑔𝑐𝑎𝑝𝑛≥0𝑇𝑛 is an algebraic definition, written 𝑇𝑛+1⊂𝑇𝑛 𝑏𝑖𝑔𝑐𝑎𝑝𝑛≥0𝑇𝑛=TZP. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from T, Z, P, defining 𝑇𝑛+1⊂𝑇𝑛 𝑏𝑖𝑔𝑐𝑎𝑝𝑛≥0𝑇𝑛. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
