\section*{ID9336: Definition of lim𝑑→0 Comp(𝑑)}
\paragraph{Metadata.}
PiID: 0888321513755 | RTEID: RTE:P36253.7613:T3.1864 | UUID: fa6799d8-13a2-5068-b68d-0f77237ba039

\paragraph{Canonical Statement.}
t: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0089], [ID 0134] Node registry\_id\_0135 Support Titles Component Scaling Law; Short-Distance Divergence; Scale Domain Test Handle If the component law is not monotone on positive distances or cannot be consistently interpreted on the stated scale interval, the universal constraint fails. Canonical Equation Links Comp(𝑑)= 3𝜇0𝜇1𝜇2 2𝜋𝑑4 \$lim𝑑→0 Comp(𝑑)=∞ 𝑑∈[ℓP\$ ,𝑅H ] [ID 0136] Celestial Gyromagnetic Motion Axiom TZPID ID0136 UUID a06d4ce0-a222-57f7-8ee5-f0df4c477ef0 Type Geometric Motion Axiom Scale toroidal celestial dynamics LOC Classification Working routing: QB355 orbital mechanics; QA641 geometric structures arXiv Classification Primary: gr-qc Cross-list: astro-ph.EP, math-ph Canonical Statement The celestial gyromagnetic motion axiom treats orbita

\paragraph{Canonical Equation.}
\[
lim𝑑→0 Comp(𝑑)=∞ 𝑑∈[ℓP
\]

\paragraph{Dictionary.}
Definition of lim𝑑→0 Comp(𝑑) — lim𝑑→0 Comp(𝑑)=∞ 𝑑∈[ℓP

\paragraph{Encyclopedia.}
Definition of lim𝑑→0 Comp(𝑑) is an algebraic definition, written lim𝑑→0 Comp(𝑑)=∞ 𝑑∈[ℓP. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from P, defining lim𝑑→0 Comp(𝑑). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
