\section*{ID9893: Strain Coupling to TZP-Localized Modes: Ω\_GW}
\paragraph{Metadata.}
PiID: 9387001264560 | RTEID: RTE:P38416.7160:T0.4671 | UUID: 406aa9d0-f8a2-56f8-b382-60e509c9a11c

\paragraph{Canonical Statement.}
Because the meta-atoms support entangled modes and tunable acoustic (cymatic) resonances, the system can be tuned such that the gravitational-wave frequency satisfies discrete resonance conditions of the form \textbackslash{}begin\{equation\} \textbackslash{}Omega\_\{\textbackslash{}mathrm\{GW\}\} = \textbackslash{}Omega\_\{\textbackslash{}mathrm\{cym\}\} \textbackslash{},\textbackslash{}varphi\textasciicircum{}n, \textbackslash{}end\{equation\} where \$\textbackslash{}Omega\_\{\textbackslash{}mathrm\{cym\}\}\$ is a cymatic base frequency (e.g. near 432 Hz in suitable units) and \$\textbackslash{}varphi\$ is the golden ratio. At such resonances, the gravitational-wave modulation of the TZP-localized Hamiltonian sector is enhanced, providing a potential experimental handle on curvature-vacuum coupling.

\paragraph{Canonical Equation.}
\[
\Omega_{\mathrm{GW}} = \Omega_{\mathrm{cym}} \,\varphi^n,
\]

\paragraph{Dictionary.}
Because the meta-atoms support entangled modes and tunable acoustic (cymatic) resonances, the system can be tuned such that the gravitational-wave frequency satisfies discrete resonance conditions of the form where Ω\_cym is a cymatic base frequency (e.g.

\paragraph{Encyclopedia.}
Strain Coupling to TZP-Localized Modes: Ω\_GW is an algebraic definition, written Ω\_GW = Ω\_cym φ\textasciicircum{}n. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from φ, n, defining Ω\_GW. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
