\tzpanchor{0464}
\tzpentryheader{0464}{Causal Order Collapse Logic}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f560f150-fbb2-5728-9a73-ad31fc498af9}}\\
\textbf{PiID} & \tzpcode{9567351885752} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{471}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1786.2822 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.9432 rad}\\
\textbf{TZPID} & \tzpcode{ID0464} & \textbf{Node Dependencies}\quad \tzpidref{0463}\\
\textbf{Registry} & \tzpcode{registry\_id\_0464} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Aggregate Relation & Geometric Constraint\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 464 formalizes the logic of temporal collapse at TZP locations. As the Jacobian determinant approaches zero, traditional temporal ordering is replaced by scale invariant quantum behavior. This allows correlations to persist at millisecond scales that traditionally decohere at femtosecond scales. Dimensional Collapse: Manages the transition from three dimensional temporal data to atemporal projections. Metric Invariance: Proves that topological protection operates independently of temporal scaling.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
W=\frac{1}{2\pi i}\oint_{C}\frac{dD}{D}
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $W$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $C$: speed of light or relativistic conversion factor.
    \item $D$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0464 generated source Wolfram model *)
ClearAll[K0464, Cr0464, T, R, A, W, I, N];
eq0464$1 = HoldForm[$W == (1/(2*Pi*i))*ContourIntegralC[dD/D]*$];

K0464 = HoldForm[{eq0464$1}];

N = "normalized TRAWIN closure object for Causal Order Collapse Logic";
I = "Causal Order Collapse Logic integration/comparison layer";
W = "Causal Order Collapse Logic wave or operator carrier";
A = "Causal Order Collapse Logic admissible action/amplitude condition";
R = "Causal Order Collapse Logic rotation/curl preservation layer";
T = "Causal Order Collapse Logic local source condition";

Cr0464[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0464 = Cr0464[K0464];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Causal Order Collapse Logic local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Causal Order Collapse Logic rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Causal Order Collapse Logic admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Causal Order Collapse Logic wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Causal Order Collapse Logic integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Causal Order Collapse Logic.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0464] Causal Order Collapse Logic}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\rho \rightarrow \frac{P \rho P}{\mathrm{Tr}(P\rho)}.
\end{equation}

\paragraph{Primary Derivation.}
Measurement with projector $P$ collapses the state.

Post-measurement state is:
\begin{equation}
\rho' = \frac{P \rho P}{\mathrm{Tr}(P\rho)}.
\end{equation}

\paragraph{Interpretation.}
Projection enforces classical outcome selection.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Causal Order Collapse Logic by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
W=\frac{1}{2\pi i}\oint_{C}\frac{dD}{D}
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0464] Causal Order Collapse Logic}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Causal Order Collapse Logic is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 464 formalizes the logic of temporal collapse at TZP locations. As the Jacobian determinant approaches zero, traditional temporal ordering is replaced by scale invariant quantum behavior. This allows correlations to persist at millisecond scales that traditionally decohere at femtosecond scales. Dimensional Collapse: Manages the transition from three dimensional temporal data to atemporal projections. Metric Invariance: Proves that topological protection operates independently of temporal scaling.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
W=\frac{1}{2\pi i}\oint_{C}\frac{dD}{D}
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 464 formalizes the logic of temporal collapse at TZP locations. As the Jacobian determinant approaches zero, traditional temporal ordering is replaced by scale invariant quantum behavior. This allows correlations to persist at millisecond scales that traditionally decohere at femtosecond scales. Dimensional Collapse: Manages the transition from three dimensional temporal data to atemporal projections. Metric Invariance: Proves that topological protection operates independently of temporal scaling.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Causal Order Collapse Logic by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Causal Order Collapse Logic; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0464]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0464].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0464] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Causal Order Collapse Logic}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} det[J] -> 0 implies nabla\textbackslash{}\_\textbackslash{} nabla\textbackslash{}\_\textbackslash{} Phi\textbackslash{}\_\textbackslash{}\textbackslash{} neq 0

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``CAUSAL ORDER COLLAPSE LOGIC is well formed when the total space, base space, structure
group, and projection map are compatible.''\\
\textbf{Proof:} The source statement supplies a bundle-style construction. The CHL reading treats the
base as the proposition carrier, the fiber or structure group as the typed parameter,
and the projection as the categorical morphism that preserves local-to-global structure.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- principal-bundle structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0464].
\par\endgroup
\vfill
\endgroup
\endgroup
