\section*{ID9228: Definition of Ggauge}
\paragraph{Metadata.}
PiID: 6780705765615 | RTEID: RTE:P35834.3733:T2.4954 | UUID: 41720a90-2c28-59c8-abda-ae46a41f80a1

\paragraph{Canonical Statement.}
jectories correspond to cycles on a toroidal manifold. 2.0.165 ID 314: Extended Phase Space for MagnetoAcoustic–Kaluza–Klein Systems Type: Definition Formal Statement: The configuration manifold for coupled magnetoacoustic and compactified extradimensional modes is \$M=m=0∞(TSO(3)× R3⊗HmKK)/GgaugeM\$ = \textbackslash{}prod \{m=0\}\{\textbackslash{}infty\}(T*SO(3) \textbackslash{}times \textbackslash{}mathbb\{R\}ˆ3 \textbackslash{}otimes \$Hˆ\{KK\} m)/G \{\textbackslash{}text\{gauge\}\}M=m=0∞(TSO(3)× R3⊗HmKK)/Ggauge,\$ where HmKKHˆ\{KK\} mHmKK denotes the mmmth Kaluza–Klein sector Hilbert space and \$Ggauge=\{:R3→U(1)∇2=0\}G \{\textbackslash{}text\{gauge\}\}\$ = \{\textbackslash{}phi : \textbackslash{}mathbb\{R\}ˆ3 \textbackslash{}to \$U(1),|,\textbackslash{}nablaˆ2\textbackslash{}phi=0\}Ggauge=\{:R3→U(1)∇2=0\}\$ fixes gauge freedom. Interpretive Meaning: This extended phase space captures the degrees of freedom for magnetoacoustic fields coupled to a tower of Kaluza–Klein modes. It includes rotational and translational variables as well as gauge degrees of freedom and infinite KK sectors. Dependencies: ID 200 (implicit magnetoacous

\paragraph{Canonical Equation.}
\[
Ggauge={:R3→U(1)∇2=0}G {\text{gauge}}
\]

\paragraph{Dictionary.}
Definition of Ggauge — Ggauge=:R3→U(1)∇2=0G gauge

\paragraph{Encyclopedia.}
Definition of Ggauge is an algebraic definition, written Ggauge=:R3→U(1)∇2=0G gauge. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R, U, G, defining Ggauge. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
