\section*{ID9141: Relation: ⊗ diag(eˆ(–λ\_i/λ))}
\paragraph{Metadata.}
PiID: 9425902989695 | RTEID: RTE:P35496.5330:T1.9387 | UUID: 4a99a0f1-368a-5465-b362-a768be9fb98f

\paragraph{Canonical Statement.}
ltoroidal coupling; criteria for energy extraction; relations between coherence length and entanglement; links to topological entropy. Falsifiability / Test Handle: Compute the functional for candidate modes and compare with observed helical–toroidal couplings; test if nature selects configurations maximizing this functional. 1.0.7 ID 106: PhaseCoherence Matrix Type: Operator Formal Statement: The phasecoherence matrix on a toroidal–helical lattice is given by PhaseCoherence = (orderParameter) \$⊗ diag(eˆ(–λ\_i/λ)),\$ where orderParameter is an ensembleaveraged complex exponential and \$λ\_i\$ are the Laplacian eigenvalues. The correlation length follows from the Fourier transform of exp(–|x|/) ·cos(k\_F x). Interpretive Meaning: This matrix encodes how phases on a helical lattice are correlated. Modes with larger Laplacian eigenvalues are exponentially suppressed, yielding finite correlation lengths. Dependencie

\paragraph{Canonical Equation.}
\[
⊗ diag(eˆ(–λ_i/λ)),
\]

\paragraph{Dictionary.}
Relation: ⊗ diag(eˆ(–λ\_i/λ)) — ⊗ diag(eˆ(–λ\_i/λ))

\paragraph{Encyclopedia.}
Relation: ⊗ diag(eˆ(–λ\_i/λ)) is a symbolic expression, written ⊗ diag(eˆ(–λ\_i/λ)). It introduces a symbol or relation used elsewhere in the framework. It is built from a, g. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
