\section*{ID9291: Relation: τdecoherence/(kBT)τ\_decoherence}
\paragraph{Metadata.}
PiID: 8222468012248 | RTEID: RTE:P36079.0163:T2.8985 | UUID: a5964980-a461-5cbe-ae31-e9facd6e6c07

\paragraph{Canonical Statement.}
(3) Provides a theoretical basis for designing neural networks with builtin criticality. Falsifiability / Test Handle: Apply the correspondence to a metamaterial simulation and compare resultant neural network dynamics with known neural statistics; confirm matching avalanche exponents and flow patterns. 2.0.193 ID 342: Decoherence and Information Retrieval Constraints Type: Structural Constraint Formal Statement: Information retrieval from tripartite entanglement is limited by decoherence time \$τdecoherence/(kBT)\textbackslash{}tau\_\{\textbackslash{}text\{decoherence\}\}\$ \textbackslash{}sim \textbackslash{}hbar/(k\_B \$T)τdecoherence/(kBT),\$ the quantum nocommunication theorem, and the holographic bound, which restricts the accessible information to A/(4P2)A/(4\textbackslash{}ell\_Pˆ2)A/(4P2) bits. Retrieval requires O(N)O(\textbackslash{}sqrt\{N\})O(N) operations for a database of size NNN. Interpretive Meaning: Even within the tripartite architecture, information extraction faces fundamental constraints imposed by thermodyn

\paragraph{Canonical Equation.}
\[
τdecoherence/(kBT)\tau_{\text{decoherence}}
\]

\paragraph{Dictionary.}
(3) Provides a theoretical basis for designing neural networks with builtin criticality.

\paragraph{Encyclopedia.}
Relation: τdecoherence/(kBT)τ\_decoherence is a symbolic expression, written τdecoherence/(kBT)τ\_decoherence. It introduces a symbol or relation used elsewhere in the framework. It is built from c, o, h, r, n, k. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
