\section*{ID8467: Definition of M(x)}
\paragraph{Metadata.}
PiID: 9959957449066 | RTEID: RTE:P32879.2413:T3.9094 | UUID: 52932134-9847-5e74-aad4-b96dd62309ff

\paragraph{Canonical Statement.}
frac\{r\}\{R\} + \textbackslash{}phi\_0)\$\$ This logarithmic spiral encodes **discrete scale invariance** , allowing the manifold to maintain resonant coherence across multiple spatial scales. The \$G\$ -field drives three critical material modulations (Source: DSE 6): * **Permeability Modulation:** The magnetic permeability is altered according to \$\textbackslash{}mu(x) = \textbackslash{}mu\_0 [1 + \textbackslash{}epsilon\_\textbackslash{}mu G(x)]\$ . * **Magnetization Orientation:** The magnetization vector is steered by the spiral tangent relative to the DAANS axis: \$M(x) = M\_0 h(G) \textbackslash{}hat\{t\}\_\{spiral\}\$ . * **Geometric Mode-Mixing:** The fractal patterns facilitate symmetry breaking, which forces different vibrational modes to couple, re-routing energy that would otherwise remain "locked" in static modes. **Transition:** These continuous surface patterns are organized and controlled through a discrete, high-density node lattice.

\paragraph{Canonical Equation.}
\[
M(x) = M_0 h(G) \hat{t}_{spiral}
\]

\paragraph{Dictionary.}
Definition of M(x) — M(x) = M\_0 h(G) t\_spiral

\paragraph{Encyclopedia.}
Definition of M(x) is an algebraic definition, written M(x) = M\_0 h(G) t\_spiral. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from M\_0, h, G, s, p, r, defining M(x). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
