\section*{ID9226: Definition of M}
\paragraph{Metadata.}
PiID: 2967807057656 | RTEID: RTE:P35826.6069:T2.4826 | UUID: df993afa-afcf-5d5d-bd03-422104573521

\paragraph{Canonical Statement.}
lanation for resonances and recurrences in wave dynamics. (3) Links time evolution with phase evolution on toroidal fibers. Falsifiability / Test Handle: Analyze dynamical simulations of field configurations and verify that phase trajectories correspond to cycles on a toroidal manifold. 2.0.165 ID 314: Extended Phase Space for MagnetoAcoustic–Kaluza–Klein Systems Type: Definition Formal Statement: The configuration manifold for coupled magnetoacoustic and compactified extradimensional modes is \$M=m=0∞(TSO(3)× R3⊗HmKK)/GgaugeM\$ = \textbackslash{}prod \{m=0\}\{\textbackslash{}infty\}(T*SO(3) \textbackslash{}times \textbackslash{}mathbb\{R\}ˆ3 \textbackslash{}otimes \$Hˆ\{KK\} m)/G \{\textbackslash{}text\{gauge\}\}M=m=0∞(TSO(3)× R3⊗HmKK)/Ggauge,\$ where HmKKHˆ\{KK\} mHmKK denotes the mmmth Kaluza–Klein sector Hilbert space and \$Ggauge=\{:R3→U(1)∇2=0\}G \{\textbackslash{}text\{gauge\}\}\$ = \{\textbackslash{}phi : \textbackslash{}mathbb\{R\}ˆ3 \textbackslash{}to \$U(1),|,\textbackslash{}nablaˆ2\textbackslash{}phi=0\}Ggauge=\{:R3→U(1)∇2=0\}\$ fixes gauge freedom. Interpretive Meaning: This extended phase space captures the degr

\paragraph{Canonical Equation.}
\[
M=m=0∞(TSO(3)× R3⊗HmKK)/GgaugeM
\]

\paragraph{Dictionary.}
Definition of M — M=m=0∞(TSO(3)× R3⊗HmKK)/GgaugeM

\paragraph{Encyclopedia.}
Definition of M is an algebraic definition, written M=m=0∞(TSO(3)× R3⊗HmKK)/GgaugeM. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from m, T, S, O, R, H, defining M. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
