\tzpanchor{0407}
\tzpentryheader{0407}{The Update Operator Refresh Rate}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{2773db7c-bbcf-57a4-af4c-4c4b6767c1eb}}\\
\textbf{PiID} & \tzpcode{0365759591953} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{414}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1580.4714 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.6041 rad}\\
\textbf{TZPID} & \tzpcode{ID0407} & \textbf{Node Dependencies}\quad \tzpidref{0406}\\
\textbf{Registry} & \tzpcode{registry\_id\_0407} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 407 defines the fundamental temporal discretization of the L. In the Trawinistic framework, time is reified as the discrete execution of the up at the singularity. At the TZP, the "Refresh Rate" achieves a stationary node, pinning information against the Planck scale carrier. This rate determines the bandwidth for the Fneural. By synchronizing the acoustic carrier with a sub harmonic of the up, the reactor achieves "Causal Phase Lock," permitting extraction without inducing temporal decoherence in the macroscopic manifold.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
g_{\mu\nu}=\eta_{\mu\nu}+h_{\mu\nu}
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $g_{\mu\nu}$: source equation symbol.
    \item $\mu$: source equation symbol.
    \item $h_{\mu\nu}$: source equation symbol.
    \item $\mathcal{K}_{0407}$: canonical registry object for entry ID 0407.
    \item $\nu$: source equation symbol.
    \item $\eta_{\mu\nu}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0407 generated source Wolfram model *)
ClearAll[K0407, Cr0407, T, R, A, W, I, N];
eq0407$1 = HoldForm[$gMunu == etaMunu + hMunu$];

K0407 = HoldForm[{eq0407$1}];

N = "normalized TRAWIN closure object for The Update Operator Refresh Rate";
I = "The Update Operator Refresh Rate integration/comparison layer";
W = "The Update Operator Refresh Rate wave or operator carrier";
A = "The Update Operator Refresh Rate admissible action/amplitude condition";
R = "The Update Operator Refresh Rate rotation/curl preservation layer";
T = "The Update Operator Refresh Rate local source condition";

Cr0407[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0407 = Cr0407[K0407];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ The Update Operator Refresh Rate local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ The Update Operator Refresh Rate rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ The Update Operator Refresh Rate admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ The Update Operator Refresh Rate wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ The Update Operator Refresh Rate integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for The Update Operator Refresh Rate.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0407] The Update Operator Refresh Rate}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\alpha(t)=\frac{\mathrm{d}t'}{\mathrm{d}t}.
\end{equation}

\paragraph{Primary Derivation.}
Let $t$ denote ordinary parameter time and let $t'$ denote displaced or transformed time measured through the Trawinistic structure.

If $t'$ depends smoothly on $t$, then the infinitesimal rate of temporal displacement is given by the derivative:

\begin{equation}
\mathrm{d}t' = \alpha(t)\,\mathrm{d}t .
\end{equation}

Solving for $\alpha(t)$ gives:

\begin{equation}
\boxed{
\alpha(t)=\frac{\mathrm{d}t'}{\mathrm{d}t}.
}
\end{equation}

\paragraph{Interpretation.}
The temporal displacement factor measures how transformed time stretches, compresses, or shifts relative to ordinary time.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors The Update Operator Refresh Rate by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
g_{\mu\nu}=\eta_{\mu\nu}+h_{\mu\nu}
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0407] The Update Operator Refresh Rate}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
The Update Operator Refresh Rate is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 407 defines the fundamental temporal discretization of the L. In the Trawinistic framework, time is reified as the discrete execution of the up at the singularity. At the TZP, the "Refresh Rate" achieves a stationary node, pinning information against the Planck scale carrier. This rate determines the bandwidth for the Fneural. By synchronizing the acoustic carrier with a sub harmonic of the up, the reactor achieves "Causal Phase Lock," permitting extraction without inducing temporal decoherence in the macroscopic manifold.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
g_{\mu\nu}=\eta_{\mu\nu}+h_{\mu\nu}
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 407 defines the fundamental temporal discretization of the L. In the Trawinistic framework, time is reified as the discrete execution of the up at the singularity. At the TZP, the "Refresh Rate" achieves a stationary node, pinning information against the Planck scale carrier. This rate determines the bandwidth for the Fneural. By synchronizing the acoustic carrier with a sub harmonic of the up, the reactor achieves "Causal Phase Lock," permitting extraction without inducing temporal decoherence in the macroscopic manifold.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors The Update Operator Refresh Rate by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
The Update Operator Refresh Rate; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0407]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0407].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0407] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont The Update Operator Refresh Rate}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} updateOperator = lim\textbackslash{}\_ t -> t\textbackslash{}\_P\textbackslash{} frac mathbf\textbackslash{}\textbackslash{} t\textbackslash{} otimes hat\textbackslash{}\textbackslash{} implies 10\textasciicircum{}\textbackslash{}43\textbackslash{} text\textbackslash{}
Hz\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``THE UPDATE OPERATOR REFRESH RATE is valid when the stated operator maps admissible
inputs into the declared target class.''\\
\textbf{Proof:} The source statement is read as an operator or transformation. The proof obligation is
type preservation: admissible inputs must land in the target object without breaking the
stated constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- operator-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0407].
\par\endgroup
\vfill
\endgroup
\endgroup
