\tzpanchor{0501}
\tzpentryheader{0501}{CANTOR PAIRING \& DETERMINISTIC ADDRESSING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{0d054575-4b3e-52ed-8495-b41fa587a698}}\\
\textbf{PiID} & \tzpcode{8336733624406} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{508}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1926.0782 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.1736 rad}\\
\textbf{TZPID} & \tzpcode{ID0501} & \textbf{Node Dependencies}\quad \tzpidref{0500}\\
\textbf{Registry} & \tzpcode{registry\_id\_0501} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
pi\_\{text\{address\}\}(a, b) = frac\{1\}\{2\}(a+b)(a+b+1) + b pmod\{153,600\}

\tzpsection{Canonical Equation}
\[
pi_{ \text{stereo}}(q_0, q_1, q_2, q_3) = \frac{1}{1 - q_3}(q_0, q_1, q_2)
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $q_0$: source equation symbol.
    \item $q_1$: source equation symbol.
    \item $q_2$: source equation symbol.
    \item $q_3$: source equation symbol.
    \item $J$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{J}_{\mathrm{out}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0501 generated source Wolfram model *)
ClearAll[K0501, Cr0501, T, R, A, W, I, N];
eq0501$1 = HoldForm[pi[q0, q1, q2, q3] == (1/(1 - q3))*Tuple[q0, q1, q2]];
eq0501$2 = HoldForm[mathcal[J]*_*out == TTZP[KTZP]];
eq0501$3 = HoldForm[mathcal[A]*_*adm*JOut == 1];

K0501 = HoldForm[{eq0501$1, eq0501$2, eq0501$3}];

N = "normalized TRAWIN closure object for CANTOR PAIRING \& DETERMINISTIC ADDRESSING";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Canonical Definition admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Canonical Definition local source condition";

Cr0501[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0501 = Cr0501[K0501];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Canonical Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Canonical Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for CANTOR PAIRING \textbackslash{}\& DETERMINISTIC ADDRESSING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0501] CANTOR PAIRING \& DETERMINISTIC ADDRESSING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\det(g)\big|_{p}=0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $(M,g)$ be a manifold equipped with metric tensor $g$. Away from the Trawin Zero Point $p$, the metric is assumed nondegenerate:

\begin{equation}
\det(g)\neq 0,
\qquad x\neq p .
\end{equation}

At the TZP, the manifold undergoes a structural collapse of ordinary metric invertibility. This means the inverse metric $g^{-1}$ cannot be defined at $p$.

A metric tensor is invertible if and only if its determinant is nonzero. Therefore, non-invertibility at $p$ implies:

\begin{equation}
\det(g)\big|_{p}=0 .
\end{equation}

\paragraph{Interpretation.}
The TZP is marked by metric degeneracy. This is the first mathematical signature that ordinary geometry fails at the zero point and must be replaced by a Trawinistic structure.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors CANTOR PAIRING \textbackslash{}\& DETERMINISTIC ADDRESSING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Canonical Definition}\par
\[
pi_{ \text{stereo}}(q_0, q_1, q_2, q_3) = \frac{1}{1 - q_3}(q_0, q_1, q_2)
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right)=1
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0501] CANTOR PAIRING \& DETERMINISTIC ADDRESSING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
CANTOR PAIRING \& DETERMINISTIC ADDRESSING is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} pi sub text address (a, b) = frac 1 2 (a+b)(a+b+1) + b pmod 153,600. \textbf{Contextual meaning:} The entry reads CANTOR PAIRING \& DETERMINISTIC ADDRESSING as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP is marked by metric degeneracy. This is the first mathematical signature that ordinary geometry fails at the zero point and must be replaced by a Trawinistic structure.

\tzpsection{Equation Grounding}
Equation anchors: pi sub stereo (q sub 0, q sub 1, q sub 2, q sub 3) = ratio 1 1 - q sub 3 (q sub 0, q sub 1, q sub 2); mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Bijective Integer Mapping}: The mathematically rigorous function that compresses two distinct coordinates into a single, perfectly reversible scalar value.
\item \textbf{N-Dimensional State Flattening}: The recursive process of collapsing complex, multi-variable geometric locations down onto a simple, one-dimensional number line.
\item \textbf{Lossless Data Coordinate Tracking}: The absolute guarantee that condensing an address does not destroy or blur any of the original spatial or phase information.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0501]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0501_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0501] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont CANTOR PAIRING \& DETERMINISTIC ADDRESSING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} pi\textbackslash{}\_\textbackslash{}\textbackslash{}(a, b) = frac\textbackslash{}1\textbackslash{}\textbackslash{}2\textbackslash{}(a+b)(a+b+1) + b pmod\textbackslash{}153,600\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``CANTOR PAIRING \& DETERMINISTIC ADDRESSING is valid as a tensorial/geometric statement
when the stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0501_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
