\section*{ID9437: Definition of (Δ𝑡)}
\paragraph{Metadata.}
PiID: 6878861444581 | RTEID: RTE:P36645.9667:T3.8326 | UUID: 121b7c5f-1922-5652-b54c-9bc8df463276

\paragraph{Canonical Statement.}
0447] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0446], [ID 0400] Node registry\_id\_0447 Support Titles Support Relation 1; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links 𝐶𝑅 \$(Δ𝑡 )=exp(−Δ𝑡/𝑇2,𝑅\$ ) Jout=· · · Aadm(Jout )=· · · [ID 0448] PARALLEL DAANSSPHERE ARRAY SCALING TZPID ID0448 UUID f1774f05-3b88-5544-9f80-3ab22c27fddf Type Geometric / Topological Statement Scale geometric LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math.DG; Cross-list: math-ph, math.AT Canonical Statement This entry develops parallel

\paragraph{Canonical Equation.}
\[
(Δ𝑡 )=exp(−Δ𝑡/𝑇2,𝑅
\]

\paragraph{Dictionary.}
Definition of (Δ𝑡) — (Δ𝑡 )=exp(−Δ𝑡/𝑇2,𝑅

\paragraph{Encyclopedia.}
Definition of (Δ𝑡) is an algebraic definition, written (Δ𝑡 )=exp(−Δ𝑡/𝑇2,𝑅. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from x, p, defining (Δ𝑡 ). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
