\section*{ID8509: TORUS CURVATURE CONTRAST Canonical Statutory Formula: κ\_ratio}
\paragraph{Metadata.}
PiID: 5984917541738 | RTEID: RTE:P33042.3367:T4.1781 | UUID: 5a7832e6-7048-58f7-8300-879747e8ce0c

\paragraph{Canonical Statement.}
[ID 1156] TORUS CURVATURE CONTRAST Canonical Statutory Formula: \$\textbackslash{}kappa\_\{ratio\} = \textbackslash{}frac\{R+r\}\{R-r\} \textbackslash{}approx 2\textbackslash{}chi \textbackslash{}approx 2.37037\$ Formal Technical Dissertation: Establishes the geometric limit for the DAANSphere core. A torus with a major-to-minor radius ratio of \textasciitilde{}2.46 yields a curvature contrast of exactly double the Trawin Constant (\$2\textbackslash{}chi\$), marking the critical transition point from a "thick" torus to a "near-spherical" topology. Source: [5], [6]

\paragraph{Canonical Equation.}
\[
\kappa_{ratio} = \frac{R+r}{R-r} \approx 2\chi \approx 2.37037
\]

\paragraph{Dictionary.}
TORUS CURVATURE CONTRAST Canonical Statutory Formula: \$ \_ratio = R+rR-r 2 2.37037\$ Formal Technical Dissertation: Establishes the geometric limit for the DAANSphere core.

\paragraph{Encyclopedia.}
TORUS CURVATURE CONTRAST Canonical Statutory Formula: κ\_ratio is a scaling / order-of-magnitude relation, written κ\_ratio = (R+r)/(R-r) ≈ 2χ ≈ 2.37037. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from χ, R, r, defining κ\_ratio. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
