\tzpanchor{0237}
\tzpentryheader{0237}{Elsasser Number}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{6ce26ee0-6b8a-5d7a-97e4-895be16b4e5d}}\\
\textbf{PiID} & \tzpcode{1652712019091} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{244}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{920.3236 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.5164 rad}\\
\textbf{TZPID} & \tzpcode{ID0237} & \textbf{Node Dependencies}\quad \tzpidref{0236}\\
\textbf{Registry} & \tzpcode{registry\_id\_0237} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Elsasser Balance & Order-One Window\\
\textbf{Closure Support} & Critical Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Elsasser number is defined as Lambda = B\^{}2/(mu\_0 rho eta omega), representing the ratio of magnetic to Coriolis forces.

\tzpsection{Canonical Equation}
\[
\Lambda=\frac{B^2}{\rho\mu_0\eta\Omega}
\]
\[
\Lambda\approx 1
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Lambda$: lemniscatic representative or canonical branch object.
    \item $B$: magnetic field magnitude.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\mu_0$: vacuum permeability constant.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $F_{\mathrm{Lorentz}}$: source equation symbol.
    \item $F_{\mathrm{Coriolis}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0237 generated source Wolfram model *)
ClearAll[K0237, Cr0237, T, R, A, W, I, N];
eq0237$1 = HoldForm[Lambda == B^2/(rhomu0*etaOmega)];
eq0237$2 = HoldForm[Lambda == 1];
eq0237$3 = HoldForm[SimilarTo[FLorentz/FCoriolis, Lambda]];

K0237 = HoldForm[{eq0237$1, eq0237$2, eq0237$3}];

N = "normalized TRAWIN closure object for Elsasser Number";
I = "Critical Closure integration/comparison layer";
W = "Order-One Window wave or operator carrier";
A = "Elsasser Balance admissible action/amplitude condition";
R = "Order-One Window rotation/curl preservation layer";
T = "Elsasser Balance local source condition";

Cr0237[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0237 = Cr0237[K0237];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Elsasser Balance local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Order-One Window rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Elsasser Balance admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Order-One Window wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Critical Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Elsasser Number.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0237] Elsasser Number}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
L
=
\int_V
(\mathbf{r}\times\mathbf{J})
\,\mathrm{d}^3x .
\end{equation}

\paragraph{Secondary Evolution Equation.}
\begin{equation}
\frac{\mathrm{d}L}{\mathrm{d}t}
=
\int_V
(\mathbf{J}\times\mathbf{B})
\,\mathrm{d}^3x .
\end{equation}

\paragraph{Primary Derivation.}
Let $\mathbf{J}$ denote local current density and $\mathbf{r}$ the position vector inside a volume $V$.  
Angular momentum density is generated by the cross product:

\begin{equation}
\mathbf{r}\times\mathbf{J}.
\end{equation}

Integrating this density over the volume gives total angular momentum:

\begin{equation}
\boxed{
L
=
\int_V
(\mathbf{r}\times\mathbf{J})
\,\mathrm{d}^3x .
}
\end{equation}

If local electromagnetic interaction drives rotational change, then the torque density is modeled by:

\begin{equation}
\mathbf{J}\times\mathbf{B}.
\end{equation}

Therefore,

\begin{equation}
\boxed{
\frac{\mathrm{d}L}{\mathrm{d}t}
=
\int_V
(\mathbf{J}\times\mathbf{B})
\,\mathrm{d}^3x .
}
\end{equation}

\paragraph{Interpretation.}
Rotation is treated as an emergent accumulated effect of local electromagnetic current and field interactions rather than as a primordial conserved input.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Elsasser Number by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Elsasser Balance}\par
\[
\Lambda=\frac{B^2}{\rho\mu_0\eta\Omega}
\]
\noindent This defines the balance between magnetic and rotational effects.\par
\noindent\textbf{2. Order-One Window}\par
\[
\Lambda\approx 1
\]
\noindent This isolates the order-one window emphasized throughout the magnetic-universality arc.\par
\noindent\textbf{3. Critical Closure}\par
\[
\frac{F_{\mathrm{Lorentz}}}{F_{\mathrm{Coriolis}}}\sim\Lambda
\]
\noindent This closes the entry by measuring departure from the critical balance.\par

\clearpage
\noindent\textbf{[ID 0237] Elsasser Number}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Elsasser Number is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The Elsasser number is defined as Lambda = B 2/(mu sub 0 rho eta omega), representing the ratio of magnetic to Coriolis forces. \textbf{Contextual meaning:} The entry reads Elsasser Number as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry sharpens the universality narrative by replacing qualitative balance with an explicit order-one criterion. \textbf{Lemma support:} Elsasser Balance; Order-One Window; Critical Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Rotation is treated as an emergent accumulated effect of local electromagnetic current and field interactions rather than as a primordial conserved input.

\tzpsection{Equation Grounding}
Equation anchors: Lambda=ratio B to the power 2 rhomu sub 0etaOmega; Lambdaapproximately 1; and ratio F sub Lorentz F sub Coriolis similar toLambda. Proof route: show that the critical regime corresponds to order-one Elsasser balance for the stated carrier variables. Formalization route: prove that the closure metric vanishes exactly at the critical balance.

\tzpsection{Interpretive Role}
The entry sharpens the universality narrative by replacing qualitative balance with an explicit order-one criterion.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Lorentz-Coriolis Force Equilibrium}: The dimensionless ratio measuring the exact balance between magnetic tension forces and the Coriolis force in a rotating body.
\item \textbf{Magnetic-Rotational Energy Balance}: The diagnostic number determining whether the magnetic field or the rotational fluid shear is the dominant structural driver.
\item \textbf{Geodynamo Coupling Parameter}: The critical threshold indicating the optimal condition for the self-sustaining generation of a planetary magnetic field.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0237]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0237_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0237] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Elsasser Number}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the Elsasser number is defined as Lambda = B\textbackslash{}\textasciicircum{}2/(mu\textbackslash{}\_0 rho eta omega), representing the
ratio of magnetic to Coriolis forces

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Elsasser Number is valid when the total tensorial quantity is conserved under the stated
constraint.''\\
\textbf{Proof:} The source statement identifies a conserved balance law. Reading 0237 as a proposition,
validity follows by requiring the full stress, flux, or current contribution to be
included before the divergence or balance condition is evaluated.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conserved total-structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0237_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
