\section*{ID9107: Definition of f\_i(c\_j,dim\_eff)dlnµdci}
\paragraph{Metadata.}
PiID: 3031509526179 | RTEID: RTE:P35364.5035:T1.7212 | UUID: d1f91ea4-8fc0-5790-aaab-44a7661325e8

\paragraph{Canonical Statement.}
on emergent phenomena. Falsifiability / Test Handle: Failure to observe predicted dimensional crossovers in critical phenomena or highenergy processes would refute this constraint. 0.0.61 ID 059: Scale Dependence of Physical Constants Type: Structural Constraint Formal Statement: Physical constants cic\_ici in the Trawinistic framework are functions of scale \$µ\textbackslash{}muµ\$ and effective dimension dimeff\textbackslash{}dim\_\{\textbackslash{}text\{eff\}\}dimeff; specifically, \$dcidlnµ=fi(cj,dimeff)\textbackslash{}frac\{\textbackslash{}text\{d\}c\_i\}\{\textbackslash{}text\{d\}\textbackslash{}ln\textbackslash{}mu\}\$ = \$f\_i(c\_j,\textbackslash{}dim\_\{\textbackslash{}text\{eff\}\})dlnµdci=fi(cj,dimeff),\$ where functions fif\_ifi encode curvature and zeropoint contributions. Interpretive Meaning: Fundamental constants such as coupling strengths are not truly constant but run with scale due to quantum and geometric effects; their evolution ties to renormalisation flow. Dependencies: ID 058 Derivable Consequences: Variation of constants across scales; interplay with cosmological observations; constra

\paragraph{Canonical Equation.}
\[
f_i(c_j,\dim_{\text{eff}})dlnµdci=fi(cj,dimeff),
\]

\paragraph{Dictionary.}
Definition of f\_i(c\_j,dim\_eff)dlnµdci — f\_i(c\_j,dim\_eff)dlnµdci=fi(cj,dimeff)

\paragraph{Encyclopedia.}
Definition of f\_i(c\_j,dim\_eff)dlnµdci is an algebraic definition, written f\_i(c\_j,dim\_eff)dlnµdci=fi(cj,dimeff). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from f, c, j, m, defining f\_i(c\_j,dim\_eff)dlnµdci. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
