\tzpanchor{0003}
\tzpentryheader{0003}{Dimensional Ambiguity at TZP}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f5f9715a-3ac7-559c-a109-4c47042303f3}}\\
\textbf{PiID} & \tzpcode{5926535897932} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{10}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{11.6497 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.0192 rad}\\
\textbf{TZPID} & \tzpcode{ID0003} & \textbf{Node Dependencies}\quad \tzpidref{0002}\\
\textbf{Registry} & \tzpcode{registry\_id\_0003} & \textbf{Scale}\quad dimensional\\
\textbf{LOC Classification} & QA611.4 dimension theory & QC gravitation foundations\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: gr-qc, hep-th & \\
\textbf{Primary Support} & Ambient Branch Set & Lemniscatic Transition Rule\\
\textbf{Closure Support} & Normalized Dimensional Reading & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The local topological dimension at the TZP satisfies $\dim_p(M)\in\DimRange$ for an ambient $n$-dimensional manifold, and transitions between these branches are governed by the lemniscatic self-intersection.

\tzpsection{Canonical Equation}
\[
\dim_{p}(M) \in \{n-1,n,n+1\}
\]
\[
\Delta_{\mathrm{branch}}
:
\Lambda \longrightarrow \{n-1,n,n+1\}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $M$: source equation symbol.
    \item $n$: integer mode index.
    \item $\Lambda$: lemniscatic representative or canonical branch object.
    \item $\dim_{p}(M)$: source equation symbol.
    \item $\Delta_{branch}$: source equation symbol.
    \item $D$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $T$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $A$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0003 generated source Wolfram model *)
ClearAll[K0003, Cr0003, T, R, A, W, I, N];
eq0003$1 = HoldForm[Element[DimP[M], {n - 1, n, n + 1}]];
eq0003$2 = HoldForm[Deltabranch[Lambda] -> n1nn1];
eq0003$3 = HoldForm[Deltabranch[Lambda] -> n1nn1];
eq0003$4 = HoldForm[DimPNorm[M] == NormalizeTRAWINTuple[DimP[M], DeltaBranch, Lambda]];

K0003 = HoldForm[{eq0003$1, eq0003$2, eq0003$3, eq0003$4}];

N = "normalized TRAWIN closure object for Dimensional Ambiguity at TZP";
I = "Normalized Dimensional Reading integration/comparison layer";
W = "Lemniscatic Transition Rule wave or operator carrier";
A = "Ambient Branch Set admissible action/amplitude condition";
R = "Lemniscatic Transition Rule rotation/curl preservation layer";
T = "Ambient Branch Set local source condition";

Cr0003[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0003 = Cr0003[K0003];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Ambient Branch Set local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Lemniscatic Transition Rule rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Ambient Branch Set admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Lemniscatic Transition Rule wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Dimensional Reading integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Dimensional Ambiguity at TZP.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0003] Dimensional Ambiguity at TZP}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
The local topological dimension at the TZP may transition among nearby dimensional states:

\begin{equation}
\dim_p(M)\in\{n,n-1,n+1\}.
\end{equation}

\paragraph{Primary Derivation.}
Let $M$ be an $n$-dimensional manifold away from $p$. For $x\neq p$,

\begin{equation}
\dim_x(M)=n .
\end{equation}

At $p$, however, the metric degeneracy and lemniscatic self-intersection create a local ambiguity: two branches of the manifold meet at one point.

A self-intersection may locally reduce distinguishable dimensional freedom, while bifurcation into two branches may locally increase effective adjacency. Therefore the local dimensional value is not fixed to $n$ alone, but may occupy the set:

\begin{equation}
\dim_p(M)\in\{n-1,n,n+1\}.
\end{equation}

\paragraph{Interpretation.}
The TZP acts as a dimensional seam. It is not merely located inside a dimension; it controls the transition between neighboring effective dimensional states.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Dimensional Ambiguity at TZP by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Ambient Branch Set}\par
\[
\dim_{p}(M) \in \{n-1,n,n+1\}
\]
\noindent This introduces the controlled ambiguity and rules out arbitrary dimensional drift.\par
\noindent\textbf{2. Lemniscatic Transition Rule}\par
\[
\Delta_{\mathrm{branch}} :
\Lambda \longrightarrow \{n-1,n,n+1\}
\]
\noindent This ties dimensional choice directly to the topological double passage established in the previous ID.\par
\noindent\textbf{3. Normalized Dimensional Reading}\par
\[
\dim_{p}^{\mathrm{norm}}(M)
=
\operatorname{Normalize}_{\mathrm{TRAWIN}}
\!\left(
\dim_{p}(M),\,
\Delta_{\mathrm{branch}},\,
\Lambda
\right)
\]
\noindent This closes the progression by turning a branching ambiguity into a usable local dimension for later integrations and field operators.\par

\clearpage
\noindent\textbf{[ID 0003] Dimensional Ambiguity at TZP}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Dimensional Ambiguity at TZP is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The local topological dimension at the TZP satisfies dim sub p(M)inDimRange for an ambient n-dimensional manifold, and transitions between these branches are governed by the lemniscatic self-intersection. \textbf{Contextual meaning:} The entry reads Dimensional Ambiguity at TZP as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This is the first entry that explicitly permits extra or reduced local degrees of freedom at the zero point. It sets up the logic later used for hyper-dimensional span, measure corrections, and singular scaling laws. \textbf{Lemma support:} Ambient Branch Set; Lemniscatic Transition Rule; Normalized Dimensional Reading.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP acts as a dimensional seam. It is not merely located inside a dimension; it controls the transition between neighboring effective dimensional states.

\tzpsection{Equation Grounding}
Equation anchors: The local topological dimension dim sub p(M) at the TZP takes values in n,n pm 1 DimRange n,npm1 for a surrounding n-dimensional manifold, and transitions between these values are governed by the lemniscatic self-intersection. The local topological dimension dim sub p(M) at the TZP takes values in n,n pm 1 DimRange n,npm1 for a surrounding n-dimensional manifold, and transitions between these values are governed by the lemniscatic self-intersection.

\tzpsection{Interpretive Role}
This is the first entry that explicitly permits extra or reduced local degrees of freedom at the zero point. It sets up the logic later used for hyper-dimensional span, measure corrections, and singular scaling laws.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Cross-Dimensional Ambiguity Tzp}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Cross-Dimensional Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Cross-Dimensional Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0003]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0003_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0003] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Dimensional Ambiguity at TZP}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the local topological dimension at the TZP satisfies \_p(M) for an ambient
n-dimensional manifold, and transitions between these branches are go...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Dimensional Ambiguity at TZP is valid when the stated geometric or topological relation
preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0003_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
