\tzpanchor{0066}
\tzpentryheader{0066}{Multipartite Entanglement FractalNodes}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{d00b2e1f-7450-562e-96ac-cb3b989d3526}}\\
\textbf{PiID} & \tzpcode{8164062862089} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{73}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{256.2927 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.4223 rad}\\
\textbf{TZPID} & \tzpcode{ID0066} & \textbf{Node Dependencies}\quad \tzpidref{0065}\\
\textbf{Registry} & \tzpcode{registry\_id\_0066} & \textbf{Scale}\quad multipartite entanglement graph\\
\textbf{LOC Classification} & QC174 multipartite entanglement & QA166 graph theory\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: math.CO, hep-th & \\
\textbf{Primary Support} & Subsystem Vertex Set & Entanglement Weight Assignment\\
\textbf{Closure Support} & Multipartite Entanglement Graph & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A multipartite entanglement network is a graph G(V,E)G(V,E)G(V,E) whose vertices VVV label subsystems and whose weighted edges EEE represent pairwise entanglement measured by entanglement entropy or negativity; curvature-dependent weights reflect the effect of the Trawinistic manifold.

\tzpsection{Canonical Equation}
\[
G = (V,E,w)
\]
\[
w_{ij} = \mathcal{E}_{ij}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $G$: source equation symbol.
    \item $V$: auxiliary target state or comparison variable.
    \item $E$: source equation symbol.
    \item $w_{ij}$: source equation symbol.
    \item $\mathcal{E}_{ij}$: source equation symbol.
    \item $v_{1}$: source equation symbol.
    \item $v_{n}$: source equation symbol.
    \item $n$: integer mode index.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0066 generated source Wolfram model *)
ClearAll[K0066, Cr0066, T, R, A, W, I, N];
eq0066$1 = HoldForm[G == Tuple[V, E, w]];
eq0066$2 = HoldForm[wIj == EIj];
eq0066$3 = HoldForm[V == Tuple[v1, dots, vN]];

K0066 = HoldForm[{eq0066$1, eq0066$2, eq0066$3}];

N = "normalized TRAWIN closure object for Multipartite Entanglement FractalNodes";
I = "Multipartite Entanglement Graph integration/comparison layer";
W = "Entanglement Weight Assignment wave or operator carrier";
A = "Subsystem Vertex Set admissible action/amplitude condition";
R = "Entanglement Weight Assignment rotation/curl preservation layer";
T = "Subsystem Vertex Set local source condition";

Cr0066[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0066 = Cr0066[K0066];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Subsystem Vertex Set local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Entanglement Weight Assignment rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Subsystem Vertex Set admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Entanglement Weight Assignment wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Multipartite Entanglement Graph integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Multipartite Entanglement FractalNodes.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0066] Multipartite Entanglement FractalNodes}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\delta S = 0.
\end{equation}

\paragraph{Primary Derivation.}
Dominant contributions to path integral arise from stationary action paths.

Thus classical trajectories satisfy:
\begin{equation}
\boxed{\delta S = 0.}
\end{equation}

\paragraph{Interpretation.}
Classical paths emerge from quantum stationary phase.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Multipartite Entanglement FractalNodes by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Subsystem Vertex Set}\par
\[
V = \{v_{1},\dots,v_{n}\}
\]
\noindent This identifies the individual subsystems in the multipartite state.\par
\noindent\textbf{2. Entanglement Weight Assignment}\par
\[
w_{ij} = \mathcal{E}_{ij}
\]
\noindent This assigns an entanglement strength to each relevant pairwise relation.\par
\noindent\textbf{3. Multipartite Entanglement Graph}\par
\[
G = (V,E,w)
\]
\noindent This closes the progression by organizing the full many-body correlation pattern as a weighted FractalNodes graph.\par

\clearpage
\noindent\textbf{[ID 0066] Multipartite Entanglement FractalNodes}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Multipartite Entanglement Networks is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A multipartite entanglement network is a graph G(V,E)G(V,E)G(V,E) whose vertices VVV label subsystems and whose weighted edges EEE represent pairwise entanglement measured by entanglement entropy or negativity; curvature-dependent weights reflect the effect of the Trawinistic manifold. \textbf{Contextual meaning:} The entry reads Multipartite Entanglement Networks as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry extends entanglement from one cut to a many-body architecture. It supports later topological and geometric descriptions by turning correlation structure into an explicit graph object. \textbf{Lemma support:} Subsystem Vertex Set; Entanglement Weight Assignment; Multipartite Entanglement Graph.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Classical paths emerge from quantum stationary phase.

\tzpsection{Equation Grounding}
Equation anchors: A multipartite entanglement network is a graph G(V,E)G(V,E)G(V,E) whose vertices VVV label subsystems and whose weighted edges EEE represent pairwise entanglement measured by entanglement entropy or negativity; curvature-dependent weights reflect the effect of the Trawinistic manifold. A multipartite entanglement network is a graph G(V,E)G(V,E)G(V,E) whose vertices VVV label subsystems and whose weighted edges EEE represent pairwise entanglement measured by entanglement entropy or negativity; curvature-dependent weights reflect the effect of the Trawinistic manifold.

\tzpsection{Interpretive Role}
This entry extends entanglement from one cut to a many-body architecture. It supports later topological and geometric descriptions by turning correlation structure into an explicit graph object.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Multipartite Entanglement FractalNodes}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Multipartite Entanglement FractalNodes Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{FractalNodes Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0066]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0066_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0066] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Multipartite Entanglement FractalNodes}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a multipartite entanglement network is a graph G(V,E)G(V,E)G(V,E) whose vertices VVV
label subsystems and whose weighted edges EEE represent pairwi...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Multipartite Entanglement Networks is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0066_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
