\section*{ID8927: TESLA HEMISPHERE RESONANCE Canonical Statutory Formula: ω\_tesla}
\paragraph{Metadata.}
PiID: 0296923488962 | RTEID: RTE:P34665.5235:T0.5695 | UUID: 678eecc9-41f8-5c08-aa7d-9cde970db6a9

\paragraph{Canonical Statement.}
[ID 922] TESLA HEMISPHERE RESONANCE Canonical Statutory Formula: \$\textbackslash{}omega\_\{tesla\} = \textbackslash{}frac\{1\}\{\textbackslash{}sqrt\{L\_\{sec\} C\_\{self\}\}\} \textbackslash{}implies 158.3 \textbackslash{}text\{ kHz\}\$ Formal Technical Dissertation: The resonance condition for the secondary coil of the Tesla hemisphere base. It balances the inductance (\$L\_\{sec\}\$) and self-capacitance (\$C\_\{self\}\$) to achieve the target frequency of 158.3 kHz for field enhancement [19]. Source: [19]

\paragraph{Canonical Equation.}
\[
\omega_{tesla} = \frac{1}{\sqrt{L_{sec} C_{self}}} \implies 158.3 \text{ kHz}
\]

\paragraph{Dictionary.}
TESLA HEMISPHERE RESONANCE Canonical Statutory Formula: \$ \_tesla = 1 L\_sec C\_self 158.3 kHz\$ Formal Technical Dissertation: The resonance condition for the secondary coil of the Tesla hemisphere base.

\paragraph{Encyclopedia.}
TESLA HEMISPHERE RESONANCE Canonical Statutory Formula: ω\_tesla is an algebraic definition, written ω\_tesla = frac1sqrtL\_sec C\_self ⟹ 158.3 kHz. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from L\_sec, C\_self, defining ω\_tesla. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
