\section*{ID9455: Definition of Πaudit}
\paragraph{Metadata.}
PiID: 9357198492252 | RTEID: RTE:P36715.8647:T3.9478 | UUID: 9b6cb277-d783-50e6-87e1-6824d7ad2a72

\paragraph{Canonical Statement.}
oq Certificate lemmaid0519\_lense\_thirring\_relativistic\_audit: sorry theoremid0519\_lense\_thirring\_relativistic\_audit Theoremid0519\_lense\_thirring\_relativistic\_audit Dependencies and Test Handle Dependencies [ID 0518], [ID 0500] Node registry\_id\_0519 Support Titles Frame-Dragging Frequency; Gravitomagnetic Field; Audit Ratio Test Handle If the observed precession cannot be normalized against the Lense–Thirring baseline, the entry fails. Canonical Equation Links \$ΩLT\$ (𝑟 )= 2𝐺𝐽 𝑐2𝑟3 𝐵g (𝑟 )=· · · \$Πaudit= Ωobs ΩLT\$ [ID 0520] NON-ABELIAN GAUGE SYMMETRY \& SU(2) PROJECTION TZPID ID0520 UUID 5923fb72-7630-57b1-a463-8d3e22067e16 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops non-abelian gauge symmetry \& su(2) projection i

\paragraph{Canonical Equation.}
\[
Πaudit= Ωobs ΩLT
\]

\paragraph{Dictionary.}
Definition of Πaudit — Πaudit= Ωobs ΩLT

\paragraph{Encyclopedia.}
Definition of Πaudit is an algebraic definition, written Πaudit= Ωobs ΩLT. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from o, b, s, L, T, defining Πaudit. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
