\section*{ID9197: Relation: r:det(J)=0∧π1(Mr)∼=Z×}
\paragraph{Metadata.}
PiID: 6286922210327 | RTEID: RTE:P35713.9934:T2.2970 | UUID: d0aeba72-2f02-5ea1-83a5-37cc3a4d8faf

\paragraph{Canonical Statement.}
field; relates to closed timelike curves and temporal entanglement; may test relativity constraints. Falsifiability / Test Handle: Absence of any sign of superluminal or nonlocal signalling in controlled experiments would falsify this entry. Canonical Registry Vol. 01 59 Trawin Zero Point Contextus Canonicus 2 TZP CANONICAL REGISTRY – ENTRIES 150–199 2.0.27 ID 176: Convergence Locus Equation Type: Structural Constraint Formal Statement: The convergence locus of unified interactions is the set \$\{r:det(J)=0∧π1(M\{r\})∼=Z×\$ Z\}\{r : \textbackslash{}det(J) = 0 \textbackslash{}wedge \textbackslash{}pi\_1(\textbackslash{}mathcal\{M\}\textbackslash{}setminus\{r\}) \textbackslash{}cong \textbackslash{}mathbb\{Z\} \textbackslash{}times \$\textbackslash{}mathbb\{Z\}\}\{r:det(J)=0∧π1(M\{r\})∼=Z×\$ Z\}. Interpretive Meaning: This equation defines the unique geometric points where the topology changes and the TZP is realized; the vanishing Jacobian indicates a degeneracy, and the doubleloop fundamental group identifies the lemniscate structure. Dependencies: ID 168 Derivable

\paragraph{Canonical Equation.}
\[
{r:det(J)=0∧π1(M{r})∼=Z×
\]

\paragraph{Dictionary.}
Relation: r:det(J)=0∧π1(Mr)∼=Z× — r:det(J)=0∧π1(Mr)∼=Z×

\paragraph{Encyclopedia.}
Relation: r:det(J)=0∧π1(Mr)∼=Z× is an algebraic definition, written r:det(J)=0∧π1(Mr)∼=Z×. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from r, J, M, Z. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
