\tzpanchor{0098}
\tzpentryheader{0098}{Delta-Function Signal Injection}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{163d4db7-703e-5cdf-aefc-0070a8425638}}\\
\textbf{PiID} & \tzpcode{7982148086513} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{105}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{380.5558 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.6270 rad}\\
\textbf{TZPID} & \tzpcode{ID0098} & \textbf{Node Dependencies}\quad \tzpidref{0062}\\
\textbf{Registry} & \tzpcode{registry\_id\_0098} & \textbf{Scale}\quad wideband insertion\\
\textbf{LOC Classification} & QC611 signal injection & QA927 Gaussian approximants\\
\textbf{arXiv Classification} & Primary: math.AP \quad Cross-list: physics.ins-det, cs.IT & \\
\textbf{Primary Support} & Localized Gaussian Approximant & Delta-Injection Limit\\
\textbf{Closure Support} & Spectral Excitation Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Impulsive signals excite a wide range of frequencies and can probe systems across scales; they serve as carriers for encoding information or exploring resonance structures.

\tzpsection{Canonical Equation}
\[
G_{\sigma}(t)
=
\frac{1}{\sigma\sqrt{2\pi}}
\exp\!\left(-\frac{t^2}{2\sigma^2}\right)
\]
\[
\delta_{\mathrm{inj}} = \lim_{\sigma \to 0} G_{\sigma}(t)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $G_{\sigma}(t)$: source equation symbol.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $\pi$: source equation symbol.
    \item $t$: source equation symbol.
    \item $\delta_{\mathrm{inj}}$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0098 generated source Wolfram model *)
ClearAll[K0098, Cr0098, T, R, A, W, I, N];
eq0098$1 = HoldForm[GSigma[t] == (1/sigmaSqrt[2*Pi])*exp[-(t^2/(2*sigma^2))]];
eq0098$2 = HoldForm[DiracDeltaInj == LimitSigma0*GSigma[t]];
eq0098$3 = HoldForm[widehat[DiracDeltaInj]*omega == 1];

K0098 = HoldForm[{eq0098$1, eq0098$2, eq0098$3}];

N = "normalized TRAWIN closure object for Delta-Function Signal Injection";
I = "Spectral Excitation Law integration/comparison layer";
W = "Delta-Injection Limit wave or operator carrier";
A = "Localized Gaussian Approximant admissible action/amplitude condition";
R = "Delta-Injection Limit rotation/curl preservation layer";
T = "Localized Gaussian Approximant local source condition";

Cr0098[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0098 = Cr0098[K0098];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Localized Gaussian Approximant local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Delta-Injection Limit rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Localized Gaussian Approximant admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Delta-Injection Limit wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Spectral Excitation Law integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Delta-Function Signal Injection.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0098] Delta-Function Signal Injection}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Gaussian Approximant.}
\begin{equation}
G_{\sigma}(t)
=
\frac{1}{\sigma\sqrt{2\pi}}
\exp\left(
-\frac{t^2}{2\sigma^2}
\right).
\end{equation}

\paragraph{Delta Limit.}
\begin{equation}
\delta_{\mathrm{inj}}
=
\lim_{\sigma\to0}G_{\sigma}(t).
\end{equation}

\paragraph{Spectral Law.}
\begin{equation}
\widehat{\delta}_{\mathrm{inj}}(\omega)=1.
\end{equation}

\paragraph{Primary Derivation.}
A normalized Gaussian pulse becomes increasingly localized as $\sigma\to0$:

\begin{equation}
G_{\sigma}(t)
=
\frac{1}{\sigma\sqrt{2\pi}}
\exp\left(
-\frac{t^2}{2\sigma^2}
\right).
\end{equation}

In the distributional limit,
\begin{equation}
\delta_{\mathrm{inj}}
=
\lim_{\sigma\to0}G_{\sigma}(t).
\end{equation}

The Fourier transform of the delta distribution is constant:
\begin{equation}
\boxed{
\widehat{\delta}_{\mathrm{inj}}(\omega)=1.
}
\end{equation}

\paragraph{Interpretation.}
A sharply localized injection supplies broad spectral content while preserving local bridge architecture.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Delta-Function Signal Injection by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Localized Gaussian Approximant}\par
\[
G_{\sigma}(t)
=
\frac{1}{\sigma\sqrt{2\pi}}
\exp\!\left(-\frac{t^2}{2\sigma^2}\right)
\]
\noindent This identifies the finite pulse used to model a sharply localized input.\par
\noindent\textbf{2. Delta-Injection Limit}\par
\[
\delta_{\mathrm{inj}} = \lim_{\sigma \to 0} G_{\sigma}(t)
\]
\noindent This turns the Gaussian family into a formal impulse operator.\par
\noindent\textbf{3. Spectral Excitation Law}\par
\[
\widehat{\delta_{\mathrm{inj}}}(\omega) = 1
\]
\noindent This closes the progression by expressing the wideband content supplied by the injection.\par

\clearpage
\noindent\textbf{[ID 0098] Delta-Function Signal Injection}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Delta-Function Signal Injection is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Impulsive signals excite a wide range of frequencies and can probe systems across scales; they serve as carriers for encoding information or exploring resonance structures. \textbf{Contextual meaning:} The entry reads Delta-Function Signal Injection as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry provides the volume with its controlled impulse mechanism. It enables the final bridge from geometric modulation to information-rich excitation at the Trawin Zero Point. \textbf{Lemma support:} Localized Gaussian Approximant; Delta-Injection Limit; Spectral Excitation Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
A sharply localized injection supplies broad spectral content while preserving local bridge architecture.

\tzpsection{Equation Grounding}
Equation anchors: A delta-function injection operator deltainjdelta inj deltainj applies a narrow Gaussian pulse g(t)=1sigma2pie-t2/(2sigma2)g(t)=ratio 1 sigmasqrt 2textbackslash pi etextsuperscript -t 2/(2sigma to the power 2) g(t)=sigma2pi1e-t2/(2sigma2) with sigmato0sigmato 0sigmato0 to a system, approximating the Dirac delta and introducing broad spectral content; the operator can encode depth information and wideband signals in the Trawin framework. A delta-function injection operator deltainjdelta inj deltainj applies a narrow Gaussian pulse g(t)=1sigma2pie-t2/(2sigma2)g(t)=ratio 1 sigmasqrt 2textbackslash pi etextsuperscript -t 2/(2sigma to the power 2) g(t)=sigma2pi1e-t2/(2sigma2) with sigmato0sigmato 0sigmato0 to a system, approximating the Dirac delta and introducing broad spectral content; the operator can encode depth information and wideband signals in the Trawin framework.

\tzpsection{Interpretive Role}
This entry provides the volume with its controlled impulse mechanism. It enables the final bridge from geometric modulation to information-rich excitation at the Trawin Zero Point.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Function Signal Injection}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Function Signal Injection Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Injection Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0098]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0098_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0098] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Delta-Function Signal Injection}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} impulsive signals excite a wide range of frequencies and can probe systems across
scales; they serve as carriers for encoding information or explor...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Delta-Function Signal Injection is valid as a spectral relation when frequency, phase,
and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0098_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
