\tzpanchor{0108}
\tzpentryheader{0108}{Relative-Entropy Constraint}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{b903f02c-2ecb-57c1-a995-6784922c2ed8}}\\
\textbf{PiID} & \tzpcode{5132823066470} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{115}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{419.3880 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.6910 rad}\\
\textbf{TZPID} & \tzpcode{ID0108} & \textbf{Node Dependencies}\quad \tzpidref{0107}\\
\textbf{Registry} & \tzpcode{registry\_id\_0108} & \textbf{Scale}\quad information divergence control\\
\textbf{LOC Classification} & QA274 information theory & QC174.45 state distinguishability\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: cs.IT, math-ph & \\
\textbf{Primary Support} & Relative-Entropy Definition & Positivity Bound\\
\textbf{Closure Support} & Functional Insertion & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This measure quantifies how different two states are.

\tzpsection{Canonical Equation}
\[
D(\rho\Vert\sigma)= \operatorname{Tr}\!\left[\rho(\log\rho-\log\sigma)\right]
\]
\[
D(\rho\Vert\sigma)\ge 0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $D$: source equation symbol.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $\delta$: source equation symbol.
    \item $\mathcal{S}_{\mathrm{sync}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0108 generated source Wolfram model *)
ClearAll[K0108, Cr0108, T, R, A, W, I, N];
eq0108$1 = HoldForm[D[rhoVertsigma] == Tr[rho[logrho - logsigma]]];
eq0108$2 = HoldForm[D[rhoVertsigma] >= 0];
eq0108$3 = HoldForm[((DiracDelta*SSync)/(DiracDelta*rho))*supset*beta*D[rhoVertsigma]];

K0108 = HoldForm[{eq0108$1, eq0108$2, eq0108$3}];

N = "normalized TRAWIN closure object for Relative-Entropy Constraint";
I = "Functional Insertion integration/comparison layer";
W = "Positivity Bound wave or operator carrier";
A = "Relative-Entropy Definition admissible action/amplitude condition";
R = "Positivity Bound rotation/curl preservation layer";
T = "Relative-Entropy Definition local source condition";

Cr0108[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0108 = Cr0108[K0108];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Relative-Entropy Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Positivity Bound rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Relative-Entropy Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Positivity Bound wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Functional Insertion integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Relative-Entropy Constraint.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0108] Relative-Entropy Constraint}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
D(\rho\Vert\sigma)= \operatorname{Tr}\!\left[\rho(\log\rho-\log\sigma)\right]
\]
\[
D(\rho\Vert\sigma)\ge 0
\]

\paragraph{Primary Derivation.}
This condition \( D(\rho\Vert\sigma)= \operatorname{Tr}\!\left[\rho(\log\rho-\log\sigma)\right] \) enforces a normalization. It sets the quantity to a fixed value away from special points and introduces a delta-function source at those points, ensuring that the integral of the quantity equals the specified constant.
\paragraph{Equation Type.}
This statement is classified as a normalization relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. In the TRAWIN reading, the equation functions as the normalized carrier for the entry’s information content. Under CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Relative-Entropy Constraint by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Relative-Entropy Definition}\par
\[
D(\rho\Vert\sigma)= \operatorname{Tr}\!\left[\rho(\log\rho-\log\sigma)\right]
\]
\noindent This identifies the mismatch term that compares actual and target synchronized states.\par
\noindent\textbf{2. Positivity Bound}\par
\[
D(\rho\Vert\sigma)\ge 0
\]
\noindent This promotes the mismatch measure to a true constraint rather than a free correction term.\par
\noindent\textbf{3. Functional Insertion}\par
\[
\frac{\delta \mathcal{S}_{\mathrm{sync}}}{\delta \rho} \supset \beta\, D(\rho\Vert\sigma)
\]
\noindent This closes the progression by feeding the divergence bound directly back into the master synchronization law.\par

\clearpage
\noindent\textbf{[ID 0108] Relative-Entropy Constraint}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Relative-Entropy Constraint is a Constraint. The relative entropy between two states   and   is D(   ) = Tr[  (log   -- log  )].

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The relative entropy between two states   and   is D(   ) = Tr[  (log   -- log  )].
\textbf{Contextual meaning:} This measure quantifies how different two states are. Lower relative entropy means the states are more aligned; the synchronization functional thus favours states that are similar in statistical structure.
\textbf{Derivable consequences:} Convergence of helical and toroidal probability distributions; co
\textbf{Lemma support:} The relative entropy between two states   and   is D(   ) = Tr[  (log   -- log  )].\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Compute entanglement entropy for different partitions and verify the constant term; test for exponential suppression of boundary corrections. ID 108: Relative Entropy Constraint

\tzpsection{Equation Grounding}
The relative entropy between two states   and   is D(   ) = Tr[  (log   -- log  )].

\tzpsection{Interpretive Role}
This measure quantifies how different two states are. Lower relative entropy means the states are more aligned; the synchronization functional thus favours states that are similar in statistical structure.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Relative-Entropy Definition}: The mismatch term that compares actual and target synchronized states.
\item \textbf{Positivity Bound}: The promotion of the mismatch measure to a true constraint rather than a free correction term.
\item \textbf{Functional Insertion}: The feeding of the divergence bound directly back into the master synchronization law.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0108]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0108_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0108] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Relative-Entropy Constraint}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this measure quantifies how different two states are

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Relative-Entropy Constraint is valid as a synchronization criterion under the coupling
conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0108_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
