\section*{ID8916: TESSERACT FOLDING OPERATOR Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 3271314251702 | RTEID: RTE:P34622.8080:T0.4991 | UUID: 570c23df-6b55-5cb7-a1d9-d6f6715ec6ec

\paragraph{Canonical Statement.}
[ID 911] TESSERACT FOLDING OPERATOR Canonical Statutory Formula: \$Fold\_\{4D\}(A) := ((A \textbackslash{}land 15) - 1) \textbackslash{}times 9600 + (\textbackslash{}text\{Quotient\}(A - (A \textbackslash{}land 15), 16) \textbackslash{}mod 9600)\$ Formal Technical Dissertation: The projection function that maps a raw linear address \$A\$ onto the geometry of a 4D hypercube (tesseract). It separates the address into a vertex index (16 possibilities) and a surface point (9600 per vertex) [8]. Source: [8]

\paragraph{Canonical Equation.}
\[
Fold_{4D}(A) := ((A \land 15) - 1) \times 9600 + (\text{Quotient}(A - (A \land 15), 16) \mod 9600)
\]

\paragraph{Dictionary.}
TESSERACT FOLDING OPERATOR Canonical Statutory Formula: \$Fold\_4D(A) := ((A 15) - 1) 9600 + (Quotient(A - (A 15), 16) 9600)\$ Formal Technical Dissertation: The projection function that maps a raw linear address A onto the geometry of a 4D hypercube (tesseract).

\paragraph{Encyclopedia.}
TESSERACT FOLDING OPERATOR Canonical Statutory Formula is an algebraic definition, written Fold\_4D(A) := ((A land 15) - 1) × 9600 + (Quotient(A - (A land 15), 16) mod 9600. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from F, o, l, d\_4D, A. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
