\tzpanchor{0319}
\tzpentryheader{0319}{Magnetic Pressure and Compressive Energy}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{8ee3a70f-deb5-51a0-9e85-394d5ee44733}}\\
\textbf{PiID} & \tzpcode{7488152092096} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{326}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1238.7478 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.0411 rad}\\
\textbf{TZPID} & \tzpcode{ID0319} & \textbf{Node Dependencies}\quad \tzpidref{0318}\\
\textbf{Registry} & \tzpcode{registry\_id\_0319} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Magnetic Energy Density & Integrated Magnetic Energy\\
\textbf{Closure Support} & Constraint Energy & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The magnetic energy density is

\tzpsection{Canonical Equation}
\[ u_{\mathrm{mag}}(r,t)=\frac{\lvert B(r,t)\rvert^{2}}{2\mu_{0}}. \] The total magnetic energy inside radius $R$ is \[ U_{\mathrm{mag}} = \int_{0}^{R}\int_{0}^{\pi}\int_{0}^{2\pi} \frac{\lvert B(r,t)\rvert^{2}}{2\mu_{0}} r^{2}\sin\theta \, dr\, d\theta\, d\phi. \] Mechanical compression contributes the constraint energy \[ U_{\mathrm{constraint}}=U_{\mathrm{mag}} + F_{\mathrm{mech}} d, \] where the force between opposite dipoles separated by distance $d$ is \[ F_{\mathrm{mech}} = \frac{3\mu_{0}}{2\pi d^{4}} \left( \mu_{1}\cdot\mu_{2} - 2(\mu_{1}\cdot \hat d)(\mu_{2}\cdot \hat d) \right). \]

\[
u_{B}=\frac{B^{2}}{2\mu_{0}}
\]
\[
E_{B}=\int_{\Omega}u_{B}\,dV
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $u_{\mathrm{mag}}(r,t)$: source equation symbol.
    \item $t$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $\mu_{0}$: vacuum permeability constant.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\pi$: source equation symbol.
    \item $\theta$: phase angle or local angular coordinate.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $U_{\mathrm{constraint}}$: source equation symbol.
    \item $F_{\mathrm{mech}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0319 generated source Wolfram model *)
ClearAll[K0319, Cr0319, T, R, A, W, I, N];
eq0319$1 = HoldForm[uMag[r, t] == Abs[B[r, t]]^2/(2*mu0)];
eq0319$2 = HoldForm[UMag == Integral0^R*Integral0^Pi*Integral0^(2*Pi)*(Abs[B[r, t]]^2/(2*mu0))*r^2*Sintheta*dr*dtheta*dphi];
eq0319$3 = HoldForm[UConstraint == UMag + FMech*d];
eq0319$4 = HoldForm[FMech == ((3*mu0)/(2*Pi*d^4))*(mu1*mu2 - 2*(mu1*hat*d)*(mu2*hat*d))];
eq0319$5 = HoldForm[uB == B^2/(2*mu0)];
eq0319$6 = HoldForm[EB == IntegralOmegauB*dV];

K0319 = HoldForm[{eq0319$1, eq0319$2, eq0319$3, eq0319$4, eq0319$5, eq0319$6}];

N = "normalized TRAWIN closure object for Magnetic Pressure and Compressive Energy";
I = "Constraint Energy integration/comparison layer";
W = "Integrated Magnetic Energy wave or operator carrier";
A = "Magnetic Energy Density admissible action/amplitude condition";
R = "Integrated Magnetic Energy rotation/curl preservation layer";
T = "Magnetic Energy Density local source condition";

Cr0319[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0319 = Cr0319[K0319];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Magnetic Energy Density local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Integrated Magnetic Energy rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Magnetic Energy Density admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Integrated Magnetic Energy wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Constraint Energy integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Magnetic Pressure and Compressive Energy.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0319] Magnetic Pressure and Compressive Energy}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Box_T\phi
=
g^{ab}
\nabla^{T}_{a}
\nabla^{T}_{b}
\phi .
\end{equation}

\paragraph{Primary Derivation.}
The ordinary d'Alembertian is the metric contraction of two covariant derivatives acting on a field.  
In Trawinistic geometry, replace the ordinary covariant derivative with $\nabla^T$:

\begin{equation}
\nabla_a\nabla_b\phi
\quad\longrightarrow\quad
\nabla^T_a\nabla^T_b\phi .
\end{equation}

Then contract using the regularized inverse metric $g^{ab}$:

\begin{equation}
\Box_T\phi
=
g^{ab}
\nabla^{T}_{a}
\nabla^{T}_{b}
\phi .
\end{equation}

\paragraph{Interpretation.}
$\Box_T$ extends wave propagation and field equations into the Trawinistic manifold by replacing ordinary derivatives with TZP-compatible covariant derivatives.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Magnetic Pressure and Compressive Energy by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Magnetic Energy Density}\par
\[
u_{B}=\frac{B^{2}}{2\mu_{0}}
\]
\noindent This fixes the local magnetic energy density carried by the field configuration.\par
\noindent\textbf{2. Integrated Magnetic Energy}\par
\[
E_{B}=\int_{\Omega}u_{B}\,dV
\]
\noindent This integrates the density over the bounded spherical carrier to obtain the total magnetic energy.\par
\noindent\textbf{3. Constraint Energy}\par
\[
p_{B}=\frac{B^{2}}{2\mu_{0}}
\]
\noindent This closes the entry by adding the mechanical compression contribution into the total constraint energy.\par

\clearpage
\noindent\textbf{[ID 0319] Magnetic Pressure and Compressive Energy}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Magnetic Pressure and Compressive Energy is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The magnetic energy density is u sub mag (r,t)=ratio lvert B(r,t)rvert to the power 2 2mu sub 0 . The total magnetic energy inside radius R is U sub mag = integral sub 0 to the power R integral sub 0 to the power pi integral sub 0 to the power 2pi ratio lvert B(r,t)rvert to the power 2 2mu sub 0 r to the power 2 sintheta dr dtheta dphi. Mechanical compression contributes the constraint energy U sub constraint =U sub mag + F sub mech d, where the force between opposite dipoles separated by distance d is F sub mech = ratio 3mu sub 0 2pi d to the power 4 ( mu sub 1 dotmu sub 2 - 2(mu sub 1 dot hat d)(mu sub 2 dot hat d) ). \textbf{Contextual meaning:} The entry reads Magnetic Pressure and Compressive Energy as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now gives magnetic pressure and compressive energy a real energy-density and integral structure instead of broken modulus fragments. \textbf{Lemma support:} Magnetic Energy Density; Integrated Magnetic Energy; Constraint Energy.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub T extends wave propagation and field equations into the Trawinistic manifold by replacing ordinary derivatives with TZP-compatible covariant derivatives.

\tzpsection{Equation Grounding}
Equation anchors: (x to the power 2 + y to the power 2) to the power 2 = 2a to the power 2(x to the power 2 - y to the power 2); mathbf v (p) = 0, abla v (p) eq 0, det (J sub p) equiv 0; and \$(x to the power 2 + y to the power 2) to the power 2 = 2a to the power 2(x to the power 2 - y to the power 2). Proof route: show that integrating the magnetic energy density over the bounded domain and adding mechanical compression yields the stated constraint energy. Formalization route: prove that the stated constraint energy follows from the integrated magnetic energy and the mechanical compression term.

\tzpsection{Interpretive Role}
The entry now gives magnetic pressure and compressive energy a real energy-density and integral structure instead of broken modulus fragments.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Ponderomotive Force Density}: The macroscopic mechanical stress exerted on a plasma by the energy gradient of the confining magnetic field.
\item \textbf{Volumetric Magnetic Energy Confinement}: The total potential energy stored inside a closed domain via the compression of magnetic flux lines.
\item \textbf{Magnetoelastic Stress Tensor}: The matrix describing the balance between expanding magnetic field pressure and inward structural tension.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0319]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0319_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0319] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Magnetic Pressure and Compressive Energy}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the magnetic energy density is The total magnetic energy inside radius R is Mechanical
compression contributes the constraint energy where the fo...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Magnetic Pressure and Compressive Energy is valid as a spectral relation when frequency,
phase, and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0319_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
