\section*{ID9474: Definition of)}
\paragraph{Metadata.}
PiID: 5049221242470 | RTEID: RTE:P36789.6460:T4.0694 | UUID: e278395a-d295-5d13-8f13-a434fe99e16e

\paragraph{Canonical Statement.}
abelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0229], [ID 0200] Node registry\_id\_0230 Support Titles Radial Bessel Profile; First Nodal Ring; Fold Energy Test Handle If the radial disturbance does not exhibit the stated Bessel node or finite localized fold energy, the entry fails. Canonical Equation Links 𝑃𝑠𝑖 (𝑟 ,𝑡 \$)=Ψ0+𝜀\$ 𝑗0 (𝑘𝑟 ) cos(𝜔𝑡 ) \$𝑘𝑟1≈2.405\$ 𝑚𝑎𝑡ℎ𝑐𝑎𝑙𝐸fold= \$∫\$ 𝑟1 0 \$|Ψ(𝑟\$ ,𝑡 \$)−Ψ0\$ |2𝑟2 𝑑𝑟 [ID 0231] Characteristic Radius of Disharmony TZPID ID0231 UUID 87122055-41f3-5212-9ef0-c9b424e505d7 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical State

\paragraph{Canonical Equation.}
\[
)=Ψ0+𝜀
\]

\paragraph{Dictionary.}
Definition of) — )=Ψ0+𝜀

\paragraph{Encyclopedia.}
Definition of) is an algebraic definition, written )=Ψ0+𝜀. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
