\tzpanchor{0289}
\tzpentryheader{0289}{Persistent Entropy Measures}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{165f2970-a02e-5064-bc36-b24c768417bc}}\\
\textbf{PiID} & \tzpcode{6024914127372} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{296}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1122.2512 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.8491 rad}\\
\textbf{TZPID} & \tzpcode{ID0289} & \textbf{Node Dependencies}\quad \tzpidref{0288}\\
\textbf{Registry} & \tzpcode{registry\_id\_0289} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Entropy Weight & Normalized Distribution\\
\textbf{Closure Support} & Topological Aggregate & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Persistent entropy quantifies the diversity of feature lifetimes; higher values correspond to rich multi-scale structure in data.

\tzpsection{Canonical Equation}
\[
p_i=\frac{\ell_i}{\sum_j \ell_j}
\]
\[
H_k=-\sum_{i\in D_k}p_i\log p_i
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $p_i$: source equation symbol.
    \item $H_k$: source equation symbol.
    \item $D_k$: source equation symbol.
    \item $H_{\mathrm{pers}}$: source equation symbol.
    \item $H_0$: Hubble-scale or global comparison parameter.
    \item $H_1$: source equation symbol.
    \item $H_2$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0289 generated source Wolfram model *)
ClearAll[K0289, Cr0289, T, R, A, W, I, N];
eq0289$1 = HoldForm[pI == ellI/(SumJ*ellJ)];
eq0289$2 = HoldForm[HK == -Sum[p[i]*Log[p[i]], {i, DK}]];
eq0289$3 = HoldForm[HPers == H0 + H1 + H2];

K0289 = HoldForm[{eq0289$1, eq0289$2, eq0289$3}];

N = "normalized TRAWIN closure object for Persistent Entropy Measures";
I = "Topological Aggregate integration/comparison layer";
W = "Normalized Distribution wave or operator carrier";
A = "Entropy Weight admissible action/amplitude condition";
R = "Normalized Distribution rotation/curl preservation layer";
T = "Entropy Weight local source condition";

Cr0289[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0289 = Cr0289[K0289];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Entropy Weight local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Normalized Distribution rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Entropy Weight admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Normalized Distribution wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Aggregate integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Persistent Entropy Measures.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0289] Persistent Entropy Measures}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Scale-Translation Functor.}
\begin{equation}
F:\mathrm{LabGyro}\longrightarrow\mathrm{AstroRot}.
\end{equation}

\paragraph{Functorial Composition Law.}
\begin{equation}
F(g\circ f)
=
F(g)\circ F(f).
\end{equation}

\paragraph{Natural Equivalence Witness.}
\begin{equation}
\eta:F\Rightarrow G .
\end{equation}

\paragraph{Primary Derivation.}
Let $\mathrm{LabGyro}$ be a category of laboratory gyromagnetic systems and $\mathrm{AstroRot}$ a category of astrophysical rotating systems.

A scale-translation functor assigns:
\begin{equation}
F:\mathrm{LabGyro}\to\mathrm{AstroRot}.
\end{equation}

To preserve dynamical structure, it must preserve composition:
\begin{equation}
F(g\circ f)=F(g)\circ F(f).
\end{equation}

If two such translations $F$ and $G$ encode the same cross-scale content, a natural transformation witnesses their equivalence:
\begin{equation}
\boxed{
\eta:F\Rightarrow G .
}
\end{equation}

\paragraph{Interpretation.}
FractalNodes supply a categorical bridge between laboratory gyromagnetic behavior and astrophysical rotating systems.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Persistent Entropy Measures by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Entropy Weight}\par
\[
p_i=\frac{\ell_i}{\sum_j \ell_j}
\]
\noindent This records the local information weight carried by the persistence data or structural channel.\par
\noindent\textbf{2. Normalized Distribution}\par
\[
H_k=-\sum_{i\in D_k}p_i\log p_i
\]
\noindent This makes the entropy law admissible by normalizing the supporting lifetimes or amplitudes.\par
\noindent\textbf{3. Topological Aggregate}\par
\[
H_{\mathrm{pers}}=H_0+H_1+H_2
\]
\noindent This closes the entry by recombining the filtered sectors into one total diagnostic.\par

\clearpage
\noindent\textbf{[ID 0289] Persistent Entropy Measures}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Persistent Entropy Measures is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Persistent entropy quantifies the diversity of feature lifetimes; higher values correspond to rich multi-scale structure in data. \textbf{Contextual meaning:} The entry reads Persistent Entropy Measures as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers. \textbf{Lemma support:} Entropy Weight; Normalized Distribution; Topological Aggregate.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
FractalNodes supply a categorical bridge between laboratory gyromagnetic behavior and astrophysical rotating systems.

\tzpsection{Equation Grounding}
Equation anchors: p sub i=ratio ell sub i sum sub j ell sub j; H sub k=-sum sub iin D sub k p sub ilog p sub i; and H sub pers =H sub 0+H sub 1+H sub 2. Proof route: show that the normalized support distribution induces a well-defined entropy functional for the stated topological or informational channel. Formalization route: prove that positivity and normalization of the support weights imply finiteness of the stated entropy functional.

\tzpsection{Interpretive Role}
The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Lifespan Analysis of Homological Voids}: The calculation of entropy based purely on how long an empty hole or gap in a dataset or physical structure survives as you zoom out to larger scales.
\item \textbf{Structural Persistence Information Weight}: The assignment of high informational value to features of a system that stubbornly remain constant no matter how much the system is stretched or blurred.
\item \textbf{Topological Stability Diagnostics}: The use of entropy mathematics to pinpoint exactly when a complex, vibrating network is about to structurally collapse into chaos.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0289]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0289_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0289] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Persistent Entropy Measures}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} persistent entropy quantifies the diversity of feature lifetimes; higher values
correspond to rich multi-scale structure in data

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Persistent Entropy Measures is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that persistent entropy quantifies the diversity of feature
lifetimes; higher values correspond to rich multi-scale structure in data. FractalNodes
supply a categorical bridge between laboratory gyromagnetic behavior and astrophysical
rotating systems. The entry turns a qualitative complexity claim into a counted
diagnostic that can be compared across neighboring persistence or information layers..
The CHL validation treats the equation as the formal anchor and the semantic text as the
interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0289_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
