\tzpanchor{0923}
\tzpentryheader{0923}{METAMATERIAL EFFECTIVE INDEX}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{a9a1097d-052e-5f87-9b51-835d13fa3175}}\\
\textbf{PiID} & \tzpcode{9562863882353} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{930}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3529.8489 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.8161 rad}\\
\textbf{TZPID} & \tzpcode{ID0923} & \textbf{Node Dependencies}\quad \tzpidref{0922}\\
\textbf{Registry} & \tzpcode{registry\_id\_0923} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
S\_0 = int\_\{d\_\{min\}\}\textasciicircum{}\{d\_\{bolt\}\} sqrt\{2m\_\{eff\} V[d]\} /, dd

\tzpsection{Canonical Equation}
\[
mu(x)=\mu_{0}[1+\epsilon_{\mu}G(x)
\]
\[
u = (index + 1/2)/n
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mu_{0}$: vacuum permeability constant.
    \item $\mu$: source equation symbol.
    \item $G$: source equation symbol.
    \item $n$: integer mode index.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0923 generated source Wolfram model *)
ClearAll[K0923, Cr0923, T, R, A, W, I, N];
eq0923$1 = HoldForm[mu[x] == mu0*(1 + epsilonMu*G[x])];
eq0923$2 = HoldForm[u == (index + 1/2)/n];

K0923 = HoldForm[{eq0923$1, eq0923$2}];

N = "normalized TRAWIN closure object for METAMATERIAL EFFECTIVE INDEX";
I = "METAMATERIAL EFFECTIVE INDEX integration/comparison layer";
W = "METAMATERIAL EFFECTIVE INDEX wave or operator carrier";
A = "METAMATERIAL EFFECTIVE INDEX admissible action/amplitude condition";
R = "METAMATERIAL EFFECTIVE INDEX rotation/curl preservation layer";
T = "METAMATERIAL EFFECTIVE INDEX local source condition";

Cr0923[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0923 = Cr0923[K0923];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ METAMATERIAL EFFECTIVE INDEX local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ METAMATERIAL EFFECTIVE INDEX rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ METAMATERIAL EFFECTIVE INDEX admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ METAMATERIAL EFFECTIVE INDEX wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ METAMATERIAL EFFECTIVE INDEX integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for METAMATERIAL EFFECTIVE INDEX.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0923] METAMATERIAL EFFECTIVE INDEX}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
mu(x)=\mu_{0}[1+\epsilon_{\mu}G(x)
\]
\[
u = (index + 1/2)/n
\]

\paragraph{Primary Derivation.}
The relation is obtained through direct evaluation of the expression. giving the formula in the first line.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. Interpreted through TRAWIN, the equation functions as the generalized carrier for the entry’s information content. Within the CHL view, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors METAMATERIAL EFFECTIVE INDEX by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
mu(x)=\mu_{0}[1+\epsilon_{\mu}G(x)
\]
\[
u = (index + 1/2)/n
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0923] METAMATERIAL EFFECTIVE INDEX}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
METAMATERIAL EFFECTIVE INDEX is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} S sub 0 = int sub d sub min to the power d sub bolt sqrt 2m sub eff V[d] /, dd. \textbf{Contextual meaning:} The entry reads METAMATERIAL EFFECTIVE INDEX as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, METAMATERIAL EFFECTIVE INDEX is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: mu(x)=mu sub 0 [1+epsilon sub mu G(x); u = (index + 1/2)/n; and S sub 0 = in t sub d sub min to the power d sub bolt sqrt 2m sub eff V[d dd. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Negative Refraction Bending}: The impossible physics of using specially engineered metals to force the light coming out of the reactor to bend backward, creating a perfect optical illusion.
\item \textbf{Sub-Wavelength Structural Tuning}: The microscopic carving of the reactor walls to make them completely invisible to the radar and microwaves used by the sensor arrays.
\item \textbf{Macroscopic Permittivity Averaging}: The mathematical trick of treating a messy, jagged wall of wires and circuits as if it were a perfectly smooth, solid sheet of glass.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0923]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0923].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0923] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont METAMATERIAL EFFECTIVE INDEX}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} METAMATERIAL EFFECTIVE INDEX is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``METAMATERIAL EFFECTIVE INDEX is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0923].
\par\endgroup
\vfill
\endgroup
\endgroup
