\section*{ID9475: Definition of · 𝐽𝑚}
\paragraph{Metadata.}
PiID: 0492212424701 | RTEID: RTE:P36793.5292:T4.0758 | UUID: 3e66a115-813a-5695-979d-56896246f0cf

\paragraph{Canonical Statement.}
ed, and linked forward into the surrounding registry pages. 𝜌𝑚 = 𝜌TZP − 𝜌coh \$Δ𝜌coh\$ > 𝜌𝑐 \$⇒\$ 𝜌𝑚 > 0 Wolfram Form 𝔚TZP (K0233) \$↦−→ 〈 ΩT, ΨT,\$ 𝜌vac \$〉\$ K0233 := HoldForm(T0233) AdmissibleTZP (K0233) \$⇐⇒\$ 𝔚TZP (K0233) . \$∅\$ Wolfram register: canonical symbol lift Title lift: Matter Emergence from Local Coherence Break Symbol key: \$ΩT:\$ Trawinistic boundary curvature \$ΨT:\$ Trawinistic wavefunction 𝜌vac: vacuum energy density TRAWIN Normalization NormalizeTRAWIN (𝜌𝑚 = 𝜌TZP − 𝜌coh, 𝜕𝑡 𝜌𝑚 + \$∇\$ · 𝐽𝑚 = 𝑆coh, 𝜕𝑡 𝜌𝑚 + \$∇\$ · 𝐽𝑚 = 𝑆coh) T: Vacuum Density is localized within the information syn-chronization arc of the directory. R: Emergence Flow preserves the operative relation that matter emergence from local coherence break requires. A: Matter Threshold fixes the admissible closure condition for the entry. W: Matter Emergence from Local Coherence Break is ren-dered as a reusable operator-level statement. I: The

\paragraph{Canonical Equation.}
\[
· 𝐽𝑚 = 𝑆coh, 𝜕𝑡 𝜌𝑚 +
\]

\paragraph{Dictionary.}
Definition of · 𝐽𝑚 — · 𝐽𝑚 = 𝑆coh, 𝜕𝑡 𝜌𝑚 +

\paragraph{Encyclopedia.}
Definition of · 𝐽𝑚 is an algebraic definition, written · 𝐽𝑚 = 𝑆coh, 𝜕𝑡 𝜌𝑚 +. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from c, o, h, defining · 𝐽𝑚. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
