\section*{ID8908: PROTON-GATED MANIFOLD OPERATOR Canonical Statutory Formula: H P-Gate}
\paragraph{Metadata.}
PiID: 6975831832713 | RTEID: RTE:P34591.7423:T0.4479 | UUID: 431bcd38-2bdd-5b3a-bd68-7bcdb3fc5ee0

\paragraph{Canonical Statement.}
[ID 939] PROTON-GATED MANIFOLD OPERATOR Canonical Statutory Formula: \$\textbackslash{}hat\{H\} \{p-gate\} = \textbackslash{}frac\{-\textbackslash{}hbar\textasciicircum{}2\}\{2m\_p\}\textbackslash{}nabla\textasciicircum{}2 + V \{pH\}(L) \textbackslash{}otimes \textbackslash{}sum\_i \textbackslash{}delta(r-r\_i)\textbackslash{}hat\{a\}\textasciicircum{}\textbackslash{}dagger\_i \textbackslash{}hat\{a\}\_i\$ Formal Technical Dissertation: Stabilizes the protonic gradient in the operator's biological tissues against vacuum-induced drift. It creates a resonant tunneling gate synchronized with the acoustic carrier to maintain mitochondrial membrane potentials during high-flux events. Source: [16], [17]

\paragraph{Canonical Equation.}
\[
\hat{H} {p-gate} = \frac{-\hbar^2}{2m_p}\nabla^2 + V {pH}(L) \otimes \sum_i \delta(r-r_i)\hat{a}^\dagger_i \hat{a}_i
\]

\paragraph{Dictionary.}
PROTON-GATED MANIFOLD OPERATOR Canonical Statutory Formula: \$H p-gate = - \textasciicircum{}22m\_p \textasciicircum{}2 + V pH(L) \_i (r-r\_i)a\textasciicircum{} \_i a\_i\$ Formal Technical Dissertation: Stabilizes the protonic gradient in the operator's biological tissues against vacuum-induced drift.

\paragraph{Encyclopedia.}
PROTON-GATED MANIFOLD OPERATOR Canonical Statutory Formula: H P-Gate is a hamiltonian construction, written H p-gate = (-ħ\textasciicircum{}2)/(2m\_p)∇\textasciicircum{}2 + V pH(L) ⊗ ∑\_i δ(r-r\_i)a\textasciicircum{}†\_i a\_i. It defines a Hamiltonian that generates the system's time evolution and encodes its energy. It is built from ħ, ∇, δ, m\_p, V, p, defining H p-gate. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
