\tzpanchor{0047}
\tzpentryheader{0047}{Bayesian Evidence Accumulation Framework}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{aee5652e-c2ff-5884-ba08-2a5a678a86f6}}\\
\textbf{PiID} & \tzpcode{5105820974944} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{54}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{182.5114 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.3007 rad}\\
\textbf{TZPID} & \tzpcode{ID0047} & \textbf{Node Dependencies}\quad \tzpidref{0046}\\
\textbf{Registry} & \tzpcode{registry\_id\_0047} & \textbf{Scale}\quad model selection\\
\textbf{LOC Classification} & QA279 Bayesian inference & QC20 scientific model comparison\\
\textbf{arXiv Classification} & Primary: stat.ML \quad Cross-list: physics.data-an, hep-th & \\
\textbf{Primary Support} & Competing Hypotheses & Bayes Factor\\
\textbf{Closure Support} & Posterior Odds Update & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Hypotheses in the TZP framework are evaluated using Bayesian inference, where evidence accumulates via likelihood ratios and simpler models are preferred.

\tzpsection{Canonical Equation}
\[
\frac{P(H_{i}\mid D)}{P(H_{j}\mid D)}
=
\frac{P(D\mid H_{i})}{P(D\mid H_{j})}
\frac{P(H_{i})}{P(H_{j})}
\]
\[
B_{ij}
=
\frac{P(D\mid H_{i})}{P(D\mid H_{j})}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $P$: source equation symbol.
    \item $H_{i}$: source equation symbol.
    \item $D$: source equation symbol.
    \item $H_{j}$: source equation symbol.
    \item $B_{ij}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0047 generated source Wolfram model *)
ClearAll[K0047, Cr0047, T, R, A, W, I, N];
eq0047$1 = HoldForm[Tuple[P[HI, D]]/Tuple[P[HJ, D]] == (Tuple[P[D, HI]]/Tuple[P[D, HJ]])*(P[HI]/P[HJ])];
eq0047$2 = HoldForm[BIj == Tuple[P[D, HI]]/Tuple[P[D, HJ]]];
eq0047$3 = HoldForm[Pair[HI, HJ]];
eq0047$4 = HoldForm[Tuple[P[HI, D]]/Tuple[P[HJ, D]] == BIj[P[HI]/P[HJ]]];

K0047 = HoldForm[{eq0047$1, eq0047$2, eq0047$3, eq0047$4}];

N = "normalized TRAWIN closure object for Bayesian Evidence Accumulation Framework";
I = "Posterior Odds Update integration/comparison layer";
W = "Bayes Factor wave or operator carrier";
A = "Competing Hypotheses admissible action/amplitude condition";
R = "Bayes Factor rotation/curl preservation layer";
T = "Competing Hypotheses local source condition";

Cr0047[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0047 = Cr0047[K0047];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Competing Hypotheses local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Bayes Factor rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Competing Hypotheses admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Bayes Factor wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Posterior Odds Update integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Bayesian Evidence Accumulation Framework.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0047] Bayesian Evidence Accumulation Framework}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{P(H_i\mid D)}
{P(H_j\mid D)}
=
\frac{P(D\mid H_i)}
{P(D\mid H_j)}
\frac{P(H_i)}
{P(H_j)} .
\end{equation}

\paragraph{Primary Derivation.}
Bayes' rule gives the posterior probability of a hypothesis $H_i$ after observing data $D$:

\begin{equation}
P(H_i\mid D)
=
\frac{P(D\mid H_i)P(H_i)}
{P(D)} .
\end{equation}

Likewise,

\begin{equation}
P(H_j\mid D)
=
\frac{P(D\mid H_j)P(H_j)}
{P(D)} .
\end{equation}

Taking the ratio cancels the evidence denominator $P(D)$:

\begin{equation}
\frac{P(H_i\mid D)}
{P(H_j\mid D)}
=
\frac{P(D\mid H_i)P(H_i)}
{P(D\mid H_j)P(H_j)} .
\end{equation}

Rearranging gives:

\begin{equation}
\boxed{
\frac{P(H_i\mid D)}
{P(H_j\mid D)}
=
\frac{P(D\mid H_i)}
{P(D\mid H_j)}
\frac{P(H_i)}
{P(H_j)} .
}
\end{equation}

\paragraph{Interpretation.}
This equation formalizes evidence accumulation: posterior odds equal likelihood ratio times prior odds.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Bayesian Evidence Accumulation Framework by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Competing Hypotheses}\par
\[
(H_{i}, H_{j})
\]
\noindent This identifies the pair of models being compared against the same evidence.\par
\noindent\textbf{2. Bayes Factor}\par
\[
B_{ij}
=
\frac{P(D\mid H_{i})}{P(D\mid H_{j})}
\]
\noindent This isolates the evidence contribution before priors are applied.\par
\noindent\textbf{3. Posterior Odds Update}\par
\[
\frac{P(H_{i}\mid D)}{P(H_{j}\mid D)}
=
B_{ij}
\frac{P(H_{i})}{P(H_{j})}
\]
\noindent This closes the progression by turning evidence and prior commitments into an updated model ranking.\par

\clearpage
\noindent\textbf{[ID 0047] Bayesian Evidence Accumulation Framework}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Bayesian Evidence Accumulation Framework is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Hypotheses in the TZP framework are evaluated using Bayesian inference, where evidence accumulates via likelihood ratios and simpler models are preferred. \textbf{Contextual meaning:} The entry reads Bayesian Evidence Accumulation Framework as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This framework gives the registry a disciplined way to absorb new evidence. It also links the physical canon to a publication workflow, because entries can be strengthened, weakened, or retired by explicit posterior updates. \textbf{Lemma support:} Competing Hypotheses; Bayes Factor; Posterior Odds Update.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This equation formalizes evidence accumulation: posterior odds equal likelihood ratio times prior odds.

\tzpsection{Equation Grounding}
Equation anchors: When comparing competing Trawinistic hypotheses H iHtextbackslash iH i, the posterior odds satisfy P(H i D)P(H j D)=P(D H i)P(D H j)P(H i)P(H j)ratio P(Htextbackslash itextbar D) P(Htextbackslash jtextbar D) = ratio P(Dtextbar Htextbackslash i) P(Dtextbar Htextbackslash j) ratio P(Htextbackslash i) P(Htextbackslash j) P(H j D)P(H i D)=P(D H j)P(D H i)P(H j)P(H i), with likelihoods P(D H i)P(Dtextbar Htextbackslash i)P(D H i) computed using the Trawinistic action and priors chosen to penalise complexity. When comparing competing Trawinistic hypotheses H iHtextbackslash iH i, the posterior odds satisfy P(H i D)P(H j D)=P(D H i)P(D H j)P(H i)P(H j)ratio P(Htextbackslash itextbar D) P(Htextbackslash jtextbar D) = ratio P(Dtextbar Htextbackslash i) P(Dtextbar Htextbackslash j) ratio P(Htextbackslash i) P(Htextbackslash j) P(H j D)P(H i D)=P(D H j)P(D H i)P(H j)P(H i), with likelihoods P(D H i)P(Dtextbar Htextbackslash i)P(D H i) computed using the Trawinistic action and priors chosen to penalise complexity.

\tzpsection{Interpretive Role}
This framework gives the registry a disciplined way to absorb new evidence. It also links the physical canon to a publication workflow, because entries can be strengthened, weakened, or retired by explicit posterior updates.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Bayesian Evidence Field Buildup Framework}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Field Buildup Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Field Buildup Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0047]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0047_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0047] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Bayesian Evidence Accumulation Framework}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} hypotheses in the TZP framework are evaluated using Bayesian inference, where evidence
accumulates via likelihood ratios and simpler models are pre...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Bayesian Evidence Accumulation Framework is valid as a formal registry statement when
its source equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that hypotheses in the TZP framework are evaluated using
Bayesian inference, where evidence accumulates via likelihood ratios and simpler models
are preferred. This equation formalizes evidence accumulation: posterior odds equal
likelihood ratio times prior odds. This framework gives the registry a disciplined way
to absorb new evidence.. The CHL validation treats the equation as the formal anchor and
the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0047_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
