\tzpanchor{0577}
\tzpentryheader{0577}{CANTOR PAIRING CASCADE FUNCTION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e7303e0b-ccba-5c8b-991a-246c30d3d7aa}}\\
\textbf{PiID} & \tzpcode{5238467481846} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{584}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2217.3198 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.6535 rad}\\
\textbf{TZPID} & \tzpcode{ID0577} & \textbf{Node Dependencies}\quad \tzpidref{0576}\\
\textbf{Registry} & \tzpcode{registry\_id\_0577} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Cantor Pairing & Recursive Cascade\\
\textbf{Closure Support} & Address Reduction & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Cantor(x, y)

\tzpsection{Canonical Equation}
\[
C(x,y) = (1 \ll (x+y)) + (1 \ll y) - 1
\]
\[
C(x,y) = (1 \ll (x+y)) + (1 \ll y) - 1
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $C$: speed of light or relativistic conversion factor.
    \item $\theta$: phase angle or local angular coordinate.
    \item $r_0$: source equation symbol.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $\ll$: source equation symbol.
    \item $r$: global radius, boundary radius, or topological scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0577 generated source Wolfram model *)
ClearAll[K0577, Cr0577, T, R, A, W, I, N];
eq0577$1 = HoldForm[C[x, y] == 1*ll*(x + y) + 1*ll*y - 1];
eq0577$2 = HoldForm[C[x, y] == 1*ll*(x + y) + 1*ll*y - 1];
eq0577$3 = HoldForm[r[theta] == r0*Exp[ktheta]];

K0577 = HoldForm[{eq0577$1, eq0577$2, eq0577$3}];

N = "normalized TRAWIN closure object for CANTOR PAIRING CASCADE FUNCTION";
I = "Address Reduction integration/comparison layer";
W = "Recursive Cascade wave or operator carrier";
A = "Cantor Pairing admissible action/amplitude condition";
R = "Recursive Cascade rotation/curl preservation layer";
T = "Cantor Pairing local source condition";

Cr0577[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0577 = Cr0577[K0577];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Cantor Pairing local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Recursive Cascade rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Cantor Pairing admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Recursive Cascade wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Address Reduction integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for CANTOR PAIRING CASCADE FUNCTION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0577] CANTOR PAIRING CASCADE FUNCTION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\Pi_{JJ}(\omega)
=
\int
dt\,
e^{i\omega t}
\langle J(t)J(0)\rangle .
\end{equation}

\begin{equation}
\sigma(\omega)
=
\frac{1}{\omega}
\operatorname{Im}\Pi_{JJ}(\omega).
\end{equation}

\paragraph{Primary Derivation.}
Let $J(t)$ be a current operator.  
The current--current response function is obtained by Fourier transforming the correlation:
\begin{equation}
\Pi_{JJ}(\omega)
=
\int
dt\,
e^{i\omega t}
\langle J(t)J(0)\rangle .
\end{equation}

The transport coefficient is then extracted from the dissipative part of that correlator:
\begin{equation}
\boxed{
\sigma(\omega)
=
\frac{1}{\omega}
\operatorname{Im}\Pi_{JJ}(\omega).
}
\end{equation}

\paragraph{Interpretation.}
Transport coefficients arise from quantum current correlations rather than from purely classical response laws.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors CANTOR PAIRING CASCADE FUNCTION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Cantor Pairing}\par
\[
C(x,y) = (1 \ll (x+y)) + (1 \ll y) - 1
\]
\noindent This fixes the base Cantor pairing function used to combine two integers into one.\par
\noindent\textbf{2. Recursive Cascade}\par
\[
C(x,y) = (1 \ll (x+y)) + (1 \ll y) - 1
\]
\noindent This extends the pairing into the recursive cascade that collapses the full digit stream.\par
\noindent\textbf{3. Address Reduction}\par
\[
r(\theta)=r_0\,e^{k\theta}
\]
\noindent This closes the entry by reducing the final cascade value to the admissible DAANSphere address range.\par

\clearpage
\noindent\textbf{[ID 0577] CANTOR PAIRING CASCADE FUNCTION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
CANTOR PAIRING CASCADE FUNCTION is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Cantor(x, y). \textbf{Contextual meaning:} The entry reads CANTOR PAIRING CASCADE FUNCTION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the pairing cascade as an actual recursive integer map instead of carrying broken pairing syntax into display mode. \textbf{Lemma support:} Cantor Pairing; Recursive Cascade; Address Reduction.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Transport coefficients arise from quantum current correlations rather than from purely classical response laws.

\tzpsection{Equation Grounding}
Equation anchors: C(x,y) = (1 ll (x+y)) + (1 ll y) - 1; \$C(x,y) = (1 ll (x+y)) + (1 ll y) - 1; and r(theta)=r sub 0 e to the power ktheta. Proof route: show that repeated application of the Cantor pairing function collapses the full integer sequence into a unique final address value. Formalization route: prove that the final reduced address follows from the recursive pairing cascade modulo the DAANSphere address range.

\tzpsection{Interpretive Role}
The entry now states the pairing cascade as an actual recursive integer map instead of carrying broken pairing syntax into display mode.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Nested Integer Convolution}: The recursive application of pairing functions to compress high-dimensional arrays into a 1D scalar line.
\item \textbf{Deterministic State Collapse}: The non-lossy algorithm ensuring unique reversibility from a singular address back to its parent indices.
\item \textbf{Sequential Digit Stream Reduction}: The iterative folding of quantum register strings into finite bounded address locations.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0577]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0577_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0577] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont CANTOR PAIRING CASCADE FUNCTION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} Transport coefficients arise from quantum current correlations rather than from purely
classical response laws

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``CANTOR PAIRING CASCADE FUNCTION is valid as a formal dynamical law when the Hamiltonian
or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0577_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
