\section*{ID9044: Definition of limx→pR\_T(x)}
\paragraph{Metadata.}
PiID: 8225054525564 | RTEID: RTE:P35119.8605:T1.3181 | UUID: e57934ad-f036-5604-b2ea-84f913cbc1f8

\paragraph{Canonical Statement.}
pological charge; influences the vacuum structure; determines the existence of certain instantons. Falsifiability / Test Handle: Empirical failure to detect the predicted holonomy or mismatch between the class and winding measurements would challenge this definition. 0.0.24 ID 022: TZP Curvature Singularity Type: Definition Formal Statement: A curvature singularity at the TZP occurs when the regularised scalar curvature R\_TR\_\{\textbackslash{}text\{T\}\}R\_T defined in ID 016 diverges as \$x→px\textbackslash{}to px→p,\$ that is, \$limx→pR\_T(x)=∞\textbackslash{}lim \{x\textbackslash{}to p\}R\_\{\textbackslash{}text\{T\}\}(x)=\textbackslash{}inftylimx→pR\_T(x)=∞.\$ Interpretive Meaning: This entry recognises that even after regularisation, certain configurations lead to unbounded curvature at the zero point. It distinguishes between benign degeneracy and true singularity. Dependencies: ID 016 Derivable Consequences: Identifies physical conditions (e.g., energy densities) that produce singularities; constrains acceptable solutions to field equations; motivat

\paragraph{Canonical Equation.}
\[
limx→pR_T(x)=∞\lim {x\to p}R_{\text{T}}(x)=\inftylimx→pR_T(x)=∞.
\]

\paragraph{Dictionary.}
Definition of limx→pR\_T(x) — limx→pR\_T(x)=∞lim x→ pR\_T(x)=inftylimx→pR\_T(x)=∞.

\paragraph{Encyclopedia.}
Definition of limx→pR\_T(x) is a limiting process, written limx→pR\_T(x)=∞lim x→ pR\_T(x)=inftylimx→pR\_T(x)=∞.. It is defined through a limit, describing the behaviour of the quantity as a parameter approaches a critical value. It is built from x, p, R\_, R\_T, defining limx→pR\_T(x). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
