\tzpanchor{0351}
\tzpentryheader{0351}{TZP Singularity Conditions}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{66ecb048-0b52-55e8-9722-e90617594d60}}\\
\textbf{PiID} & \tzpcode{8925903600113} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{358}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1363.0109 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.2458 rad}\\
\textbf{TZPID} & \tzpcode{ID0351} & \textbf{Node Dependencies}\quad \tzpidref{0350}\\
\textbf{Registry} & \tzpcode{registry\_id\_0351} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A point qualifies as a Trawin Zero Point when three conditions hold simultaneously: (1) the topological winding number around the point is non-zero, (2) the Jacobian determinant of the spacetime transformation tends to zero, and (3) an infinite-order phase transition emerges.

\tzpsection{Canonical Equation}
\[
{q, p} = \Psi_0, Initial conditions
\]
\[
Maxwell boundary conditions at r = R
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Psi_0$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $R_{\mathrm{boundary}}$: source equation symbol.
    \item $\Psi$: wavefunction or state carrier for the entry equation.
    \item $P$: source equation symbol.
    \item $I$: source equation symbol.
    \item $M$: source equation symbol.
    \item $A$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0351 generated source Wolfram model *)
ClearAll[K0351, Cr0351, T, R, A, W, I, N];
eq0351$1 = HoldForm[TZPSequence[Pair[q, p] == Psi0, Initial*conditions]];
eq0351$2 = HoldForm[Maxwell*boundary*conditions*at*r == R];
eq0351$3 = HoldForm[5.*Apply*boundary*conditions*at*r == RBoundary];

K0351 = HoldForm[{eq0351$1, eq0351$2, eq0351$3}];

N = "normalized TRAWIN closure object for TZP Singularity Conditions";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Canonical Definition admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Canonical Definition local source condition";

Cr0351[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0351 = Cr0351[K0351];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Canonical Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Canonical Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP Singularity Conditions.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0351] TZP Singularity Conditions}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
[\phi(x),\pi(y)] = i\hbar\,\delta(x,y).
\end{equation}

\paragraph{Vacuum Witness.}
\begin{equation}
\langle 0|[\phi(x),\pi(y)]|0\rangle \neq 0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi(x)$ be a quantum field and $\pi(y)$ its canonical conjugate momentum.  
Canonical quantization requires that the field and its conjugate momentum fail to commute at equal time:

\begin{equation}
[\phi(x),\pi(y)]
=
\phi(x)\pi(y)-\pi(y)\phi(x).
\end{equation}

The canonical field--momentum commutator is then imposed as:

\begin{equation}
[\phi(x),\pi(y)] = i\hbar\,\delta(x,y).
\end{equation}

Taking the vacuum expectation value gives the zero-point witness:

\begin{equation}
\langle 0|[\phi(x),\pi(y)]|0\rangle
=
i\hbar\,\delta(x,y).
\end{equation}

Thus, at coincident support, the vacuum is not classically silent:

\begin{equation}
\boxed{
\langle 0|[\phi(x),\pi(y)]|0\rangle \neq 0 .
}
\end{equation}

\paragraph{Interpretation.}
Zero-point fluctuation is registered by non-vanishing field--momentum commutation rather than by classical rest.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP Singularity Conditions by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Canonical Definition}\par
\[
{q, p} = \Psi_0, Initial conditions
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
Maxwell boundary conditions at r = R
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
5. Apply boundary conditions at r = R_{\mathrm{boundary}}
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0351] TZP Singularity Conditions}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP Singularity Conditions is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A point qualifies as a Trawin Zero Point when three conditions hold simultaneously: (1) the topological winding number around the point is non-zero, (2) the Jacobian determinant of the spacetime transformation tends to zero, and (3) an infinite-order phase transition emerges. \textbf{Contextual meaning:} The entry reads TZP Singularity Conditions as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Zero-point fluctuation is registered by non-vanishing field--momentum commutation rather than by classical rest.

\tzpsection{Equation Grounding}
Equation anchors: q, p = Psi sub 0, Initial conditions; Maxwell boundary conditions at r = R; and 5. Apply boundary conditions at r = R sub boundary. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Fixed Initial-Boundary Configuration}: The strict imposition of starting states and edge behaviors required to reliably generate the zero-point structure.
\item \textbf{Maxwellian Field Termination}: The specific rules governing how electromagnetic lines of force must behave exactly at the edge of the bounded singular region.
\item \textbf{Deterministic Singularity Sourcing}: The proof that a specific, known combination of inputs will inescapably collapse into the central topological defect.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0351]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0351_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0351] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP Singularity Conditions}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a point qualifies as a Trawin Zero Point when three conditions hold simultaneously: (1)
the topological winding number around the point is non-zero...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP Singularity Conditions is valid when the stated geometric or topological relation
preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0351_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
