\tzpanchor{0586}
\tzpentryheader{0586}{BERRY PHASE TOMOGRAPHY (ATEMPORAL READOUT)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{dbb7a53c-3863-599d-a3ad-f9e99d31161c}}\\
\textbf{PiID} & \tzpcode{1846766940513} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{593}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2252.2688 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.7110 rad}\\
\textbf{TZPID} & \tzpcode{ID0586} & \textbf{Node Dependencies}\quad \tzpidref{0585}\\
\textbf{Registry} & \tzpcode{registry\_id\_0586} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Berry Phase Integral & Readout Carrier\\
\textbf{Closure Support} & Admissibility Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
gamma\_n = oint\_C mathbf\{A\} * dmathbf\{R\} = int\_S mathbf\{F\} * dmathbf\{S\} implies text\{Readout(Atemporal Channel)\}

\tzpsection{Canonical Equation}
\[
gamma_{n}=\oint_{C}\mathbf{A}\cdot d\mathbf{R}=\int_{S}\mathbf{F}\cdot d\mathbf{S}
\]
\[
mathcal{J}_{\mathrm{out}}=\mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $n$: integer mode index.
    \item $C$: speed of light or relativistic conversion factor.
    \item $A$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $S$: source equation symbol.
    \item $F$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{J}_{\mathrm{out}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0586 generated source Wolfram model *)
ClearAll[K0586, Cr0586, T, R, A, W, I, N];
eq0586$1 = HoldForm[gammaN == ContourIntegralCA*dR == IntegralSF*dS];
eq0586$2 = HoldForm[mathcal[J]*_*out == TTZP[KTZP]];
eq0586$3 = HoldForm[mathcal[A]*_*adm*JOut == 1];

K0586 = HoldForm[{eq0586$1, eq0586$2, eq0586$3}];

N = "normalized TRAWIN closure object for BERRY PHASE TOMOGRAPHY (ATEMPORAL READOUT)";
I = "Admissibility Closure integration/comparison layer";
W = "Readout Carrier wave or operator carrier";
A = "Berry Phase Integral admissible action/amplitude condition";
R = "Readout Carrier rotation/curl preservation layer";
T = "Berry Phase Integral local source condition";

Cr0586[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0586 = Cr0586[K0586];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Berry Phase Integral local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Readout Carrier rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Berry Phase Integral admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Readout Carrier wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Admissibility Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for BERRY PHASE TOMOGRAPHY (ATEMPORAL READOUT).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0586] BERRY PHASE TOMOGRAPHY (ATEMPORAL READOUT)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primordial Ansatz.}
\begin{equation}
\mathbf{L}(t)=\mathbf{L}_0 .
\end{equation}

\paragraph{Source-Integrated History.}
\begin{equation}
\mathbf{L}(t)
=
\mathbf{L}_0
+
\int_0^t
\boldsymbol{\tau}_{\mathrm{em}}(t')
\,\mathrm{d}t' .
\end{equation}

\paragraph{Null Primordial Default.}
\begin{equation}
\mathbf{L}_0\approx 0 .
\end{equation}

\paragraph{Primary Derivation.}
If angular momentum is treated as primordial, then it is represented as a fixed inherited value:
\begin{equation}
\mathbf{L}(t)=\mathbf{L}_0.
\end{equation}

The Trawinistic alternative accounts for observed angular momentum by integrating generated torque through time:
\begin{equation}
\mathbf{L}(t)
=
\mathbf{L}_0
+
\int_0^t
\boldsymbol{\tau}_{\mathrm{em}}(t')
\,\mathrm{d}t' .
\end{equation}

Under the null primordial hypothesis:
\begin{equation}
\boxed{
\mathbf{L}_0\approx 0,
\qquad
\mathbf{L}(t)
\approx
\int_0^t
\boldsymbol{\tau}_{\mathrm{em}}(t')
\,\mathrm{d}t' .
}
\end{equation}

\paragraph{Interpretation.}
This entry replaces unexplained inherited rotation with a source-history explanation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors BERRY PHASE TOMOGRAPHY (ATEMPORAL READOUT) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Berry Phase Integral}\par
\[
gamma_{n}=\oint_{C}\mathbf{A}\cdot d\mathbf{R}=\int_{S}\mathbf{F}\cdot d\mathbf{S}
\]
\noindent This fixes the geometric-phase integral that carries the atemporal readout content of the entry.\par
\noindent\textbf{2. Readout Carrier}\par
\[
mathcal{J}_{\mathrm{out}}=\mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent This identifies the TRAWIN output carrier produced by the readout channel.\par
\noindent\textbf{3. Admissibility Closure}\par
\[
mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right)=1
\]
\noindent This closes the entry by requiring the readout carrier to land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0586] BERRY PHASE TOMOGRAPHY (ATEMPORAL READOUT)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
BERRY PHASE TOMOGRAPHY (ATEMPORAL READOUT) is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} gamma sub n = oint sub C mathbf A * dmathbf R = int sub S mathbf F * dmathbf S implies text Readout(Atemporal Channel). \textbf{Contextual meaning:} The entry reads BERRY PHASE TOMOGRAPHY (ATEMPORAL READOUT) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states berry-phase tomography through a geometric phase integral, a TRAWIN readout carrier, and an explicit admissibility closure instead of corrupted vector-field prose. \textbf{Lemma support:} Berry Phase Integral; Readout Carrier; Admissibility Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This entry replaces unexplained inherited rotation with a source-history explanation.

\tzpsection{Equation Grounding}
Equation anchors: gamma sub n =oint sub C A dot d R =integral sub S F dot d S; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated geometric-phase integral induces the quoted atemporal readout carrier. Formalization route: prove that the resulting readout carrier satisfies the stated admissibility predicate.

\tzpsection{Interpretive Role}
The entry now states berry-phase tomography through a geometric phase integral, a TRAWIN readout carrier, and an explicit admissibility closure instead of corrupted vector-field prose.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Geometric Wave-History Mapping}: The process of scanning the final state of the system to perfectly reverse-engineer exactly what twisted path it took to get there.
\item \textbf{Time-Independent State Slicing}: The measurement technique that captures a perfect 3D snapshot of the energy without accidentally interfering with its ongoing forward motion.
\item \textbf{Holonomic Quantum Memory Retrieval}: The readout method that extracts stored information not by looking at the energy itself, but by measuring the permanent scars it left on the surrounding geometry.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0586]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0586_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0586] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont BERRY PHASE TOMOGRAPHY (ATEMPORAL READOUT)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} gamma\textbackslash{}\_n = oint\textbackslash{}\_C mathbf\textbackslash{} * dmathbf\textbackslash{} = int\textbackslash{}\_S mathbf\textbackslash{} * dmathbf\textbackslash{} implies text(Atemporal
Channel)\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``BERRY PHASE TOMOGRAPHY (ATEMPORAL READOUT) is valid when the stated geometric or
topological relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0586_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
