\tzpanchor{0926}
\tzpentryheader{0926}{TOPOLOGICAL CHERN NUMBER}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{639e19c0-1b42-5429-aadf-2b319d3e7445}}\\
\textbf{PiID} & \tzpcode{2863882353787} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{933}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3541.4985 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.8353 rad}\\
\textbf{TZPID} & \tzpcode{ID0926} & \textbf{Node Dependencies}\quad \tzpidref{0925}\\
\textbf{Registry} & \tzpcode{registry\_id\_0926} & \textbf{Scale}\quad diagnostic\\
\textbf{LOC Classification} & QA273 dimensionless analysis & QC statistical diagnostics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: nlin.PS, physics.data-an\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
C\_1 = frac\{1\}\{2pi\} int\_\{BZ\} F * dS in mathbb\{Z\}

\tzpsection{Canonical Equation}
\[
F_{lev} = \frac{p_{rms}^2 A}{2 \rho c^2} + \frac{B^2 A}{2 \mu_0} = mg + F_{perturb}
\]
\[
Z_{match} = \text{LinearSolve}[Z_{hemisphere} \otimes I, Flatten[Z_{sphere}]]
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $F_{lev}$: source equation symbol.
    \item $p_{rms}$: source equation symbol.
    \item $A$: source equation symbol.
    \item $\rho$: density or measure term used by the entry equation.
    \item $c$: speed of light or relativistic conversion factor.
    \item $B$: magnetic field magnitude.
    \item $\mu_0$: vacuum permeability constant.
    \item $F_{perturb}$: source equation symbol.
    \item $Z_{match}$: source equation symbol.
    \item $Z_{hemisphere}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0926 generated source Wolfram model *)
ClearAll[K0926, Cr0926, T, R, A, W, I, N];
eq0926$1 = HoldForm[FLev == (pRms^2*A)/(2*rho*c^2) + (B^2*A)/(2*mu0) == mg + FPerturb];
eq0926$2 = HoldForm[ZMatch == TZPGroup[ZHemisphere*TensorProduct*I, Flatten[ZSphere]]];

K0926 = HoldForm[{eq0926$1, eq0926$2}];

N = "normalized TRAWIN closure object for TOPOLOGICAL CHERN NUMBER";
I = "TOPOLOGICAL CHERN NUMBER integration/comparison layer";
W = "TOPOLOGICAL CHERN NUMBER wave or operator carrier";
A = "TOPOLOGICAL CHERN NUMBER admissible action/amplitude condition";
R = "TOPOLOGICAL CHERN NUMBER rotation/curl preservation layer";
T = "TOPOLOGICAL CHERN NUMBER local source condition";

Cr0926[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0926 = Cr0926[K0926];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ TOPOLOGICAL CHERN NUMBER local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TOPOLOGICAL CHERN NUMBER rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ TOPOLOGICAL CHERN NUMBER admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TOPOLOGICAL CHERN NUMBER wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TOPOLOGICAL CHERN NUMBER integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TOPOLOGICAL CHERN NUMBER.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0926] TOPOLOGICAL CHERN NUMBER}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
F_{lev} = \frac{p_{rms}^2 A}{2 \rho c^2} + \frac{B^2 A}{2 \mu_0} = mg + F_{perturb}
\]
\[
Z_{match} = \text{LinearSolve}[Z_{hemisphere} \otimes I, Flatten[Z_{sphere}]]
\]

\paragraph{Primary Derivation.}
The relation is obtained through direct evaluation of the expression. giving the formula in the first line.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. From the TRAWIN perspective, the equation functions as the generalized carrier for the entry’s information content. Within the CHL view, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TOPOLOGICAL CHERN NUMBER by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
F_{lev} = \frac{p_{rms}^2 A}{2 \rho c^2} + \frac{B^2 A}{2 \mu_0} = mg + F_{perturb}
\]
\[
Z_{match} = \text{LinearSolve}[Z_{hemisphere} \otimes I, Flatten[Z_{sphere}]]
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0926] TOPOLOGICAL CHERN NUMBER}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TOPOLOGICAL CHERN NUMBER is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} C sub 1 = frac 1 2pi int sub BZ F * dS in mathbb Z. \textbf{Contextual meaning:} The entry reads TOPOLOGICAL CHERN NUMBER as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons. \textbf{Lemma support:} Diagnostic Definition; Scaling Relation; Normalized Regime.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, TOPOLOGICAL CHERN NUMBER is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: F sub lev = ratio p sub rms to the power 2 A 2 rho c to the power 2 + ratio B to the power 2 A 2 mu sub 0 = mg + F sub perturb; Z sub match = LinearSolve [Z sub hemisphere otimes I, Flatten[Z sub sphere ]]; and C sub 1 = ratio 1 2pi integral sub BZ F dot dS in mathbb Z. Proof route: show that the named quantity is dimensionless or consistently scaled in the regime stated by the entry. Formalization route: prove that the normalized diagnostic remains invariant under the intended rescaling.

\tzpsection{Interpretive Role}
The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Integer-Quantized Field Invariants}: The discovery that the chaotic, swirling magnetic field is actually governed by simple, unbreakable whole numbers that physically cannot change.
\item \textbf{Fiber Bundle Twisting Measurement}: The mathematical calculation of exactly how many times the invisible lines of force are knotted and tangled around themselves inside the plasma.
\item \textbf{Global Geometric Invariant Tracking}: The sweeping scan that ignores the messy details of the plasma and only looks at the massive, overarching shape of the entire storm.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0926]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0926].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0926] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TOPOLOGICAL CHERN NUMBER}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} TOPOLOGICAL CHERN NUMBER is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TOPOLOGICAL CHERN NUMBER is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0926].
\par\endgroup
\vfill
\endgroup
\endgroup
