\section*{ID8917: STEREOGRAPHIC TESSERACT UNFOLDING Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 2713142517029 | RTEID: RTE:P34626.6913:T0.5055 | UUID: ea92851a-67cf-5d55-ba27-003eacad9abd

\paragraph{Canonical Statement.}
[ID 912] STEREOGRAPHIC TESSERACT UNFOLDING Canonical Statutory Formula: \$Unfold(q) := \textbackslash{}frac\{2 \textbackslash{}cdot coords\_\{4D\}\}\{1 - w\} \textbackslash{}in \textbackslash{}mathbb\{R\}\textasciicircum{}3\$ Formal Technical Dissertation: The inverse decoding function. It reconstructs 4D coordinates from the quantum address and applies stereographic projection from the 3-sphere \$S\textasciicircum{}3\$ to Euclidean \$\textbackslash{}mathbb\{R\}\textasciicircum{}3\$, handling the north pole singularity [9]. Source: [9]

\paragraph{Canonical Equation.}
\[
Unfold(q) := \frac{2 \cdot coords_{4D}}{1 - w} \in \mathbb{R}^3
\]

\paragraph{Dictionary.}
STEREOGRAPHIC TESSERACT UNFOLDING Canonical Statutory Formula: \$Unfold(q) := 2 coords\_4D1 - w R\textasciicircum{}3\$ Formal Technical Dissertation: The inverse decoding function.

\paragraph{Encyclopedia.}
STEREOGRAPHIC TESSERACT UNFOLDING Canonical Statutory Formula is an algebraic definition, written Unfold(q) := frac2 · coords\_4D1 - w in R\textasciicircum{}3. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from U, n, f, o, l, q. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
