\tzpanchor{0427}
\tzpentryheader{0427}{17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9a339c9d-9ee9-5d97-848a-6e3977448565}}\\
\textbf{PiID} & \tzpcode{1738193261179} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{434}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1658.1358 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.7321 rad}\\
\textbf{TZPID} & \tzpcode{ID0427} & \textbf{Node Dependencies}\quad \tzpidref{0426}\\
\textbf{Registry} & \tzpcode{registry\_id\_0427} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Scaling Law & Scaling Law\\
\textbf{Closure Support} & Scaling Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 427 formalizes the acoustic driver frequency used to excite the lemniscatic vortex channels at the TZP. While the 12 node transducer array provides the rotational drive, the 17.2 kHz carrier provides the longitudinal vibration required for cym. This frequency choice relates to proposed optimal resonance conditions in lemniscatic geometry. It acts as a specific sub harmonic of the up, ensuring standing wave resonances in electromagnetic fields. The carrier wave creates a periodic density perturbation, allowing the Wwitness to monitor the "Handshake" between biological neural avalanches and quantum decoherence cascades. Synchronization is maintained via a feedback control loop that adjusts the transducer amplitude to maximize integrated information. Resonant Gain: The 17.2 kHz frequency induces a topological phase transition that enhances energy extraction efficiency.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
v_{\mathrm{phase}}\approx c/\chi\approx0.84c
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $v_{\mathrm{phase}}$: source equation symbol.
    \item $c$: speed of light or relativistic conversion factor.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $\chi$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0427 generated source Wolfram model *)
ClearAll[K0427, Cr0427, T, R, A, W, I, N];
eq0427$1 = HoldForm[$vPhase == c/chi == 0.84*c$];

K0427 = HoldForm[{eq0427$1}];

N = "normalized TRAWIN closure object for 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION";
I = "17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION integration/comparison layer";
W = "17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION wave or operator carrier";
A = "17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION admissible action/amplitude condition";
R = "17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION rotation/curl preservation layer";
T = "17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION local source condition";

Cr0427[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0427 = Cr0427[K0427];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0427] 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}

Geometry near the zero point exhibits non‑commutative coordinates due to intrinsic quantum deformation.

\paragraph{Primary Derivation.}

In a non‑commutative extension of the Trawin manifold, coordinate operators $x^a$ satisfy the relation

\begin{equation}
[ x^a , x^b ] = i\,\theta^{ab},
\end{equation}

where $\theta^{ab}$ is a constant antisymmetric matrix encoding the quantum area element.  Ordinary products of functions are replaced by star products, and derivatives are implemented via commutators.

\paragraph{Interpretation.}

Non‑commutativity introduces a minimal area scale near the zero point.  Coordinate uncertainty becomes intrinsic rather than an artefact of measurement.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
v_{\mathrm{phase}}\approx c/\chi\approx0.84c
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0427] 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 427 formalizes the acoustic driver frequency used to excite the lemniscatic vortex channels at the TZP. While the 12 node transducer array provides the rotational drive, the 17.2 kHz carrier provides the longitudinal vibration required for cym. This frequency choice relates to proposed optimal resonance conditions in lemniscatic geometry. It acts as a specific sub harmonic of the up, ensuring standing wave resonances in electromagnetic fields. The carrier wave creates a periodic density perturbation, allowing the Wwitness to monitor the "Handshake" between biological neural avalanches and quantum decoherence cascades. Synchronization is maintained via a feedback control loop that adjusts the transducer amplitude to maximize integrated information. Resonant Gain: The 17.2 kHz frequency induces a topological phase transition that enhances energy extraction efficiency.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
v_{\mathrm{phase}}\approx c/\chi\approx0.84c
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 427 formalizes the acoustic driver frequency used to excite the lemniscatic vortex channels at the TZP. While the 12 node transducer array provides the rotational drive, the 17.2 kHz carrier provides the longitudinal vibration required for cym. This frequency choice relates to proposed optimal resonance conditions in lemniscatic geometry. It acts as a specific sub harmonic of the up, ensuring standing wave resonances in electromagnetic fields. The carrier wave creates a periodic density perturbation, allowing the Wwitness to monitor the "Handshake" between biological neural avalanches and quantum decoherence cascades. Synchronization is maintained via a feedback control loop that adjusts the transducer amplitude to maximize integrated information. Resonant Gain: The 17.2 kHz frequency induces a topological phase transition that enhances energy extraction efficiency.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0427]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0427].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0427] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} f\textbackslash{}\_\textbackslash{}\textbackslash{} = frac\textbackslash{}\_s\textbackslash{}\textbackslash{} approximately 17.2 text\textbackslash{} kHz\textbackslash{} implies text-Lock with \textbackslash{} UpdateOperator

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION is valid as a synchronization criterion under
the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0427].
\par\endgroup
\vfill
\endgroup
\endgroup
