\tzpanchor{0870}
\tzpentryheader{0870}{ENTRAINMENT FREQUENCY FIELD}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{6c2e39b2-03fe-5251-8cdd-ab7eaac3627d}}\\
\textbf{PiID} & \tzpcode{5875332083814} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{877}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3324.0381 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.4770 rad}\\
\textbf{TZPID} & \tzpcode{ID0870} & \textbf{Node Dependencies}\quad \tzpidref{0869}\\
\textbf{Registry} & \tzpcode{registry\_id\_0870} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Aggregate Relation\\
\textbf{Closure Support} & Variation Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records entrainment frequency field through a normalized Nonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0870}}:\mathcal{X}_{\mathrm{id0870}}\longrightarrow\mathcal{Y}_{\mathrm{id0870}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0870}})=\mathcal{O}_{\mathrm{id0870}}
\]
\[
\mathcal{O}_{\mathrm{id0870}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0870}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0870}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0870}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0870 generated source Wolfram model *)
ClearAll[K0870, Cr0870, T, R, A, W, I, N];
eq0870$1 = HoldForm[Oid0870[Xid0870] -> Yid0870];
eq0870$2 = HoldForm[NTRAWIN[OId0870] == OId0870];
eq0870$3 = HoldForm[Element[OId0870[x], YAdm]];

K0870 = HoldForm[{eq0870$1, eq0870$2, eq0870$3}];

N = "normalized TRAWIN closure object for ENTRAINMENT FREQUENCY FIELD";
I = "ENTRAINMENT FREQUENCY FIELD integration/comparison layer";
W = "ENTRAINMENT FREQUENCY FIELD wave or operator carrier";
A = "ENTRAINMENT FREQUENCY FIELD admissible action/amplitude condition";
R = "ENTRAINMENT FREQUENCY FIELD rotation/curl preservation layer";
T = "ENTRAINMENT FREQUENCY FIELD local source condition";

Cr0870[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0870 = Cr0870[K0870];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ ENTRAINMENT FREQUENCY FIELD local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ ENTRAINMENT FREQUENCY FIELD rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ ENTRAINMENT FREQUENCY FIELD admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ ENTRAINMENT FREQUENCY FIELD wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ ENTRAINMENT FREQUENCY FIELD integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for ENTRAINMENT FREQUENCY FIELD.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0870] ENTRAINMENT FREQUENCY FIELD}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0870}}:\mathcal{X}_{\mathrm{id0870}}\longrightarrow \mathcal{Y}_{\mathrm{id0870}},\qquad
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0870}})=\mathcal{O}_{\mathrm{id0870}},\qquad
\mathcal{O}_{\mathrm{id0870}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

\paragraph{Primary Derivation.} Let $\psi_{0870}(x,t)$ be the local wave or phase carrier.  The entry assigns the carrier mode\[
\psi_{0870}=\mathcal{O}_{\mathrm{id0870}}(x).
\]

A reusable harmonic witness is the phase-weighted state\[
I_{0870}(t)=A_{0870}(t)e^{i\theta_{0870}(t)}.
\]

Stable closure requires phase locking and admissible landing:\[
\dot{\theta}_{0870}(t)=\omega_{\mathrm{lock},0870},\qquad \mathcal{O}_{\mathrm{id0870}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

Thus the Nonary derivation for [ID 0870] is the three-stage passage
\[
\mathcal{X}_{\mathrm{id0870}}\xrightarrow{\,\mathcal{O}_{\mathrm{id0870}}\,} \mathcal{Y}_{\mathrm{id0870}}\xrightarrow{\,\mathcal{N}_{\mathrm{TRAWIN}}\,} \mathcal{Y}_{\mathrm{adm}},
\]
with the entry title fixing the meaning of the carrier and the TRAWIN normalization fixing the admissibility test.

\paragraph{Interpretation.} ENTRAINMENT FREQUENCY FIELD closes as a phase-and-mode statement: the entry is usable when its harmonic carrier locks to the local admissible channel.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors ENTRAINMENT FREQUENCY FIELD by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0870}}:\mathcal{X}_{\mathrm{id0870}}\longrightarrow\mathcal{Y}_{\mathrm{id0870}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0870}})=\mathcal{O}_{\mathrm{id0870}}
\]
\[
\mathcal{O}_{\mathrm{id0870}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0870] ENTRAINMENT FREQUENCY FIELD}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
ENTRAINMENT FREQUENCY FIELD is a registry definition in Resonance and Phase Locking with secondary pressure from Biological and Biomolecular Analogies.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} F,G Poisson = sum i (frac partial F partial q to the power i frac partial G partialpi sub i -frac partial G partial q to the power i frac partial F partialpi sub i ) + sum sub ijk epsilon to the power ijk omega to the power i frac partial F partialomega to the power j frac partial G partialomega to the power k. \textbf{Contextual meaning:} The entry reads ENTRAINMENT FREQUENCY FIELD as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Aggregate Relation; Variation Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, ENTRAINMENT FREQUENCY FIELD is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: mathcal F sub e (x,t):=ratio partial Psi partial t + abladotOmega; w = ratio 1 2pi oint sub C abla arg Psi dot dell in mathbb Z; and boxed ratio partial zeta partial t + J( Psi , zeta +f) = u abla to the power 2 sub s zeta + F(theta,lambda,t). Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spatially Distributed Phase-Locking}: The invisible, humming web of energy that spreads out from the reactor, physically forcing every single loose bolt, wire, and atom in the room to vibrate at the exact same pitch.
\item \textbf{Global Harmonic Subjugation}: The terrifying realization that the power of the machine is so overwhelming it simply overrides the natural laws of the surrounding materials, forcing them all to obey its master clock.
\item \textbf{Acoustic-Electromagnetic Symbiosis}: The point where the physical shaking of the metal walls and the invisible twisting of the magnetic fields become so perfectly aligned that they merge into one single, terrifyingly powerful new force.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0870]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0870].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0870] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont ENTRAINMENT FREQUENCY FIELD}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} ENTRAINMENT FREQUENCY FIELD is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ENTRAINMENT FREQUENCY FIELD is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0870].
\par\endgroup
\vfill
\endgroup
\endgroup
