\tzpanchor{0398}
\tzpentryheader{0398}{Topological Information Functor}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{eb5dffa1-f9ed-5606-b302-fd3878e1082a}}\\
\textbf{PiID} & \tzpcode{9433057270365} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{405}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1545.5224 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.5465 rad}\\
\textbf{TZPID} & \tzpcode{ID0398} & \textbf{Node Dependencies}\quad \tzpidref{0397}\\
\textbf{Registry} & \tzpcode{registry\_id\_0398} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Functor Map & Naturality Law\\
\textbf{Closure Support} & Entropy Conservation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Introduce the functor

\tzpsection{Canonical Equation}
\[ F:\mathsf{InfoCategory}[4D]\to \mathsf{InfoCategory}[2D], \] mapping four-dimensional information states $\psi_{4D}$ to two-dimensional states $\psi_{2D}$. The component map uses an information density built from von Neumann entropy, Fisher information, and Kolmogorov complexity together with topological charges such as the Chern number, winding number, and kissing number. A kissing-invariant factor \[ K = \prod_{n=1}^{N} \left( 1+\mathrm{InfoDensity}[\psi]\, \mathrm{digit}_{n}(\pi) \right)^{1/n} \] rescales the information so that \[ \mathrm{Information}[\psi_{2D}] = \mathrm{Information}[\psi_{4D}]\,K. \] Naturality requires \[ F(g\circ f)=F(g)\circ F(f), \] and information conservation imposes \[ S[F(\psi)]\geq S(\psi)-\log(\pi N). \]

\[
F:\mathrm{InfoCategory}[4D]\longrightarrow \mathrm{InfoCategory}[2D]
\]
\[
F(g\circ f)=F(g)\circ F(f)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $F$: source equation symbol.
    \item $K$: source equation symbol.
    \item $n$: integer mode index.
    \item $\pi$: source equation symbol.
    \item $S$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0398 generated source Wolfram model *)
ClearAll[K0398, Cr0398, T, R, A, W, I, N];
eq0398$1 = HoldForm[F[mathsfInfoCategory4D] -> mathsfInfoCategory2D];
eq0398$2 = HoldForm[K == prodN1^N*(1 + InfoDensity[psi]*digitN[Pi])^(1/n)];
eq0398$3 = HoldForm[Information[psi2*D] == Information[psi4*D]*K];
eq0398$4 = HoldForm[F[gcirc*f] == F[g]*circ*F[f]];
eq0398$5 = HoldForm[S[F[psi]] >= S[psi] - log[Pi*N]];
eq0398$6 = HoldForm[F[InfoCategory4D] -> InfoCategory2D];

K0398 = HoldForm[{eq0398$1, eq0398$2, eq0398$3, eq0398$4, eq0398$5, eq0398$6}];

N = "normalized TRAWIN closure object for Topological Information Functor";
I = "Entropy Conservation integration/comparison layer";
W = "Naturality Law wave or operator carrier";
A = "Functor Map admissible action/amplitude condition";
R = "Naturality Law rotation/curl preservation layer";
T = "Functor Map local source condition";

Cr0398[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0398 = Cr0398[K0398];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Functor Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Naturality Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Functor Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Naturality Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Entropy Conservation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Topological Information Functor.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0398] Topological Information Functor}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Gaussian Approximant.}
\begin{equation}
G_{\sigma}(t)
=
\frac{1}{\sigma\sqrt{2\pi}}
\exp\left(
-\frac{t^2}{2\sigma^2}
\right).
\end{equation}

\paragraph{Delta Limit.}
\begin{equation}
\delta_{\mathrm{inj}}
=
\lim_{\sigma\to0}G_{\sigma}(t).
\end{equation}

\paragraph{Spectral Law.}
\begin{equation}
\widehat{\delta}_{\mathrm{inj}}(\omega)=1.
\end{equation}

\paragraph{Primary Derivation.}
A normalized Gaussian pulse becomes increasingly localized as $\sigma\to0$:

\begin{equation}
G_{\sigma}(t)
=
\frac{1}{\sigma\sqrt{2\pi}}
\exp\left(
-\frac{t^2}{2\sigma^2}
\right).
\end{equation}

In the distributional limit,
\begin{equation}
\delta_{\mathrm{inj}}
=
\lim_{\sigma\to0}G_{\sigma}(t).
\end{equation}

The Fourier transform of the delta distribution is constant:
\begin{equation}
\boxed{
\widehat{\delta}_{\mathrm{inj}}(\omega)=1.
}
\end{equation}

\paragraph{Interpretation.}
A sharply localized injection supplies broad spectral content while preserving local bridge architecture.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Topological Information Functor by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Functor Map}\par
\[
F:\mathrm{InfoCategory}[4D]\longrightarrow \mathrm{InfoCategory}[2D]
\]
\noindent This fixes the functor carrying four-dimensional information states into two-dimensional states.\par
\noindent\textbf{2. Naturality Law}\par
\[
F(g\circ f)=F(g)\circ F(f)
\]
\noindent This imposes the naturality law that keeps the functor compatible with composition.\par
\noindent\textbf{3. Entropy Conservation}\par
\[
S[F(\psi)]\geq S(\psi)-\log(N\pi)
\]
\noindent This closes the entry with the entropy-conservation inequality that bounds admissible information loss.\par

\clearpage
\noindent\textbf{[ID 0398] Topological Information Functor}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Topological Information Functor is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Introduce the functor F:mathsf InfoCategory [4D]to mathsf InfoCategory [2D], mapping four-dimensional information states psi sub 4D to two-dimensional states psi sub 2D . The component map uses an information density built from von Neumann entropy, Fisher information, and Kolmogorov complexity together with topological charges such as the Chern number, winding number, and kissing number. A kissing-invariant factor K = prod sub n=1 to the power N ( 1+ InfoDensity [psi] digit sub n (pi) ) to the power 1/n rescales the information so that Information [psi sub 2D ] = Information [psi sub 4D ] K. Naturality requires F(gcompose f)=F(g)compose F(f), and information conservation imposes S[F(psi)]geq S(psi)-log(pi N). \textbf{Contextual meaning:} The entry reads Topological Information Functor as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the topological information functor through a clean mapping, naturality law, and entropy bound. \textbf{Lemma support:} Functor Map; Naturality Law; Entropy Conservation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
A sharply localized injection supplies broad spectral content while preserving local bridge architecture.

\tzpsection{Equation Grounding}
Equation anchors: F: InfoCategory [4D]to InfoCategory [2D]; F(gcompose f)=F(g)compose F(f); and S[F(psi)]geq S(psi)-log(Npi). Proof route: show that the stated functor preserves composition and satisfies the stated information-conservation bound. Formalization route: prove that the entropy inequality is compatible with the stated functorial collapse from four to two dimensions.

\tzpsection{Interpretive Role}
The entry now states the topological information functor through a clean mapping, naturality law, and entropy bound.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Dimensional Down-Sampling Projection}: The mathematical translation that successfully crams the complex data of a 4D universe into a flat, 2D holographic surface.
\item \textbf{Commutative Categorical Mapping}: The rigorous proof that changing the order of how you process the data doesn't change the final flat 2D picture you get at the end.
\item \textbf{Logarithmic Entropy Leakage Bound}: The calculation of exactly how much detail is unavoidably lost when crushing the 4D data down into a 2D format.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0398]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0398_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0398] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Topological Information Functor}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} introduce the functor \textbackslash{}[ F:InfoCategory[4D] InfoCategory[2D], \textbackslash{}] mapping four-
dimensional information states \_4D to two-dimensional states \_2D

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Topological Information Functor is valid when the total tensorial quantity is conserved
under the stated constraint.''\\
\textbf{Proof:} The source statement identifies a conserved balance law. Reading 0398 as a proposition,
validity follows by requiring the full stress, flux, or current contribution to be
included before the divergence or balance condition is evaluated.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conserved total-structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0398_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
