\section*{ID6757: Short, Readable Explanation of the Tree vs Lung Geometry: ∇·U}
\paragraph{Metadata.}
PiID: 9474553859381 | RTEID: RTE:P26238.9316:T5.5346 | UUID: ba1aaa1e-74ce-53f8-86f0-c1546ac569c7

\paragraph{Canonical Statement.}
\#\# 4) Short, readable explanation of the “tree vs lung” geometry You noticed rays **branching outward like trees, not lung-like inward folding**. That’s a directional diagnostic: - **Tree-like (branches outward):** indicates **divergent flow** from a source (positive radial flux) or diffraction radiating out from the pupil. - **Lung-like (folding inward):** would indicate **convergent flow** (sinks) or wave interference focusing inward. In the TZP + sphere language, this corresponds to the sign of \textbackslash{}(\textbackslash{}nabla\textbackslash{}cdot\textbackslash{}mathbf\{u\}\textbackslash{}) locally and to the sign of the streamfunction vorticity. Opposite hemispheres with opposite sign produce the “left image sounds one way and the earth image sounds the other” effect you noticed.

\paragraph{Canonical Equation.}
\[
\nabla\cdot\mathbf{u}
\]

\paragraph{Dictionary.}
Short, Readable Explanation of the Tree vs Lung Geometry: ∇·U — ∇·u

\paragraph{Encyclopedia.}
Short, Readable Explanation of the Tree vs Lung Geometry: ∇·U is a differential equation, written ∇·u. It relates the quantity to its derivatives, governing how the system evolves in space and time. It is built from ∇, u. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
