\tzpanchor{0137}
\tzpentryheader{0137}{Megastructure Formation Theorem}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{6b9c486f-0d73-533d-bfca-36431c1172f9}}\\
\textbf{PiID} & \tzpcode{1725359408128} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{144}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{532.0014 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.8766 rad}\\
\textbf{TZPID} & \tzpcode{ID0137} & \textbf{Node Dependencies}\quad \tzpidref{0136}\\
\textbf{Registry} & \tzpcode{registry\_id\_0137} & \textbf{Scale}\quad universe-scale filament spacing\\
\textbf{LOC Classification} & QB981 cosmology & QA612 topological structure\\
\textbf{arXiv Classification} & Primary: astro-ph.CO \quad Cross-list: gr-qc, math-ph & \\
\textbf{Primary Support} & Megastructure Wavelength Law & Observed-Scale Match\\
\textbf{Closure Support} & Toroidal Flux-Tube Class & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Standing-wave interference across the universe produces filaments with wavelength \(\lambda=\pi R_{\mathrm{universe}}/n\), where \(R_{\mathrm{universe}}\) is the Hubble radius. For the selected mode scale, this gives \(\lambda\approx150\,\mathrm{Mpc}\). These filaments are modeled as flux tubes with \(T^2\) topology, and the predicted spacing is compared against observed cosmic-web scales.

\tzpsection{Canonical Equation}
\[
\lambda=\frac{\pi R_{\mathrm{universe}}}{n}
\]
\[
\lambda \approx 150\ \mathrm{Mpc}
\]
\[
\mathcal{F}_{\mathrm{web}}\sim T^2
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\lambda$: filament wavelength.
    \item $R_{\mathrm{universe}}$: Hubble radius.
    \item $n$: integer mode index.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0137 generated source Wolfram model *)
ClearAll[K0137, Cr0137, T, R, A, W, I, N];
eq0137$1 = HoldForm[lambda == (Pi*RUniverse)/n];
eq0137$2 = HoldForm[lambda == 150*Mpc];
eq0137$3 = HoldForm[SimilarTo[FWeb, T^2]];

K0137 = HoldForm[{eq0137$1, eq0137$2, eq0137$3}];

N = "normalized TRAWIN closure object for Megastructure Formation Theorem";
I = "Toroidal Flux-Tube Class integration/comparison layer";
W = "Observed-Scale Match wave or operator carrier";
A = "Megastructure Wavelength Law admissible action/amplitude condition";
R = "Observed-Scale Match rotation/curl preservation layer";
T = "Megastructure Wavelength Law local source condition";

Cr0137[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0137 = Cr0137[K0137];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Megastructure Wavelength Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Observed-Scale Match rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Megastructure Wavelength Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Observed-Scale Match wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Toroidal Flux-Tube Class integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Megastructure Formation Theorem.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0137] Megastructure Formation Theorem}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\lambda=\frac{\pi R_{\mathrm{universe}}}{n}
\]
\[
\lambda \approx 150\ \mathrm{Mpc}
\]
\[
\mathcal{F}_{\mathrm{web}}\sim T^2
\]

\paragraph{Primary Derivation.}
To derive the stated relation through direct evaluation of the expression. yielding the required identity.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. Within the TRAWIN framework, the equation functions as the generalized carrier for the entry’s information content. In CHL terms, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The progression evaluates the wavelength law at its selected scale and then records the conditional topological classification of the resulting filament model.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Megastructure Wavelength Law}\par
\[
\lambda=\frac{\pi R_{\mathrm{universe}}}{n}
\]
\noindent This gives the interference-controlled spacing scale for large filaments.\par
\noindent\textbf{2. Observed-Scale Match}\par
\[
\lambda \approx 150\ \mathrm{Mpc}
\]
\noindent This ties the wavelength law to the stated observationally relevant spacing.\par
\noindent\textbf{3. Toroidal Flux-Tube Class}\par
\[
\mathcal{F}_{\mathrm{web}}\sim T^2
\]
\noindent This closes the progression by assigning the resulting filaments a toroidal topological character.\par

\clearpage
\noindent\textbf{[ID 0137] Megastructure Formation Theorem}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small

\tzpsection{Definition}

The megastructure wavelength law is a mode-indexed spacing relation for large-scale filaments. It sets a filament wavelength from a global radius scale and an integer mode count.

\tzpsection{Contextual Meaning}

The global length scale is the Hubble radius, \(R_{\mathrm{universe}}\), and the output is filament wavelength \(\lambda\). A standing-wave reading partitions the large domain into repeated spacing intervals; topology or cosmic-web comparison remains later interpretation.

\tzpsection{Formal Statement}

\[
\lambda=\frac{\pi R_{\mathrm{universe}}}{n}
\]

\tzpsection{Derivable Consequences}

For fixed Hubble radius, increasing \(n\) reduces \(\lambda\); for fixed \(n\), increasing the global radius increases wavelength proportionally. The approximate \(150\,\mathrm{Mpc}\) value is an evaluated comparison.

\tzpsection{Lemma Support}

The approved alignment states the equation and identifies \(\lambda\) as filament wavelength and \(R_{\mathrm{universe}}\) as Hubble radius. It does not validate later topology claims.

\tzpsection{Technical Interpretation}

The coefficient \(\pi/n\) scales a global radial measure by mode count, organizing modeled spacing rather than asserting an unrestricted empirical fit.

\tzpsection{Equation Grounding}

\(\lambda\) denotes filament wavelength and \(R_{\mathrm{universe}}\) denotes the Hubble radius in the approved equation-aligned source. The mode symbol \(n\) appears in the mathematical relation but awaits separate symbol-level source approval.

\tzpsection{Interpretive Role}

This entry translates a global radius assumption into a spacing law referenced conditionally by later topology and comparison layers.

\tzpsection{TZP Thesaurus}

\noindent \textbf{Filament Wavelength}: The modeled interval between standing-wave filament features. \enspace\textbullet\enspace \textbf{Hubble Radius}: The global radius scale used by the approved wavelength relation. \enspace\textbullet\enspace \textbf{Mode-Indexed Spacing}: A spacing obtained by scaling a global length with an integer mode count.\par

\endgroup

\tzpsection{Encyclopedia Mathematica}
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0137_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0137] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Megastructure Formation Theorem}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} standing-wave interference gives a filament spacing
\(\lambda=\pi R_{\mathrm{universe}}/n\), with the selected mode scale compared to \(\lambda\approx150\,\mathrm{Mpc}\).

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Megastructure Formation Theorem is valid as a spectral relation when frequency, phase,
and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0137_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
