\tzpanchor{0677}
\tzpentryheader{0677}{FEEDBACK PHASE PARAMETER ADJUSTMENT}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7b04fb43-1398-5058-b5f1-c0977b889e82}}\\
\textbf{PiID} & \tzpcode{5371050792279} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{684}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2601.7588 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.2869 rad}\\
\textbf{TZPID} & \tzpcode{ID0677} & \textbf{Node Dependencies}\quad \tzpidref{0676}\\
\textbf{Registry} & \tzpcode{registry\_id\_0677} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Geometric Constraint & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records feedback phase parameter adjustment through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\Pi_{JJ}(\omega) = \int dt\, e^{i\omega t} \langle J(t)J(0)\rangle.
\]
\[
\sigma(\omega) = \frac{1}{\omega} \operatorname{Im}\Pi_{JJ}(\omega).
\]
\[
\boxed{ \sigma(\omega) = \frac{1}{\omega} \operatorname{Im}\Pi_{JJ}(\omega). }
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\omega$: angular frequency term in the source equation.
    \item $t$: source equation symbol.
    \item $J$: source equation symbol.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0677 generated source Wolfram model *)
ClearAll[K0677, Cr0677, T, R, A, W, I, N];
eq0677$1 = HoldForm[PiJJ[omega] == Integral*dt*Exp[I*omega*t]*Inner[J[t]*J[0]]];
eq0677$2 = HoldForm[sigma[omega] == (1/omega)*ImPiJJ[omega]];
eq0677$3 = HoldForm[sigma[omega] == (1/omega)*ImPiJJ[omega]];

K0677 = HoldForm[{eq0677$1, eq0677$2, eq0677$3}];

N = "normalized TRAWIN closure object for FEEDBACK PHASE PARAMETER ADJUSTMENT";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Geometric Constraint admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Geometric Constraint local source condition";

Cr0677[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0677 = Cr0677[K0677];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Geometric Constraint local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Geometric Constraint admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for FEEDBACK PHASE PARAMETER ADJUSTMENT.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0677] FEEDBACK PHASE PARAMETER ADJUSTMENT}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\Pi_{JJ}(\omega)
=
\int
dt\,
e^{i\omega t}
\langle J(t)J(0)\rangle .
\end{equation}

\begin{equation}
\sigma(\omega)
=
\frac{1}{\omega}
\operatorname{Im}\Pi_{JJ}(\omega).
\end{equation}

\paragraph{Primary Derivation.}
Let $J(t)$ be a current operator.  
The current--current response function is obtained by Fourier transforming the correlation:
\begin{equation}
\Pi_{JJ}(\omega)
=
\int
dt\,
e^{i\omega t}
\langle J(t)J(0)\rangle .
\end{equation}

The transport coefficient is then extracted from the dissipative part of that correlator:
\begin{equation}
\boxed{
\sigma(\omega)
=
\frac{1}{\omega}
\operatorname{Im}\Pi_{JJ}(\omega).
}
\end{equation}

\paragraph{Interpretation.}
Transport coefficients arise from quantum current correlations rather than from purely classical response laws.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors FEEDBACK PHASE PARAMETER ADJUSTMENT by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Geometric Constraint}\par
\[
\Pi_{JJ}(\omega) = \int dt\, e^{i\omega t} \langle J(t)J(0)\rangle.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\sigma(\omega) = \frac{1}{\omega} \operatorname{Im}\Pi_{JJ}(\omega).
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\boxed{ \sigma(\omega) = \frac{1}{\omega} \operatorname{Im}\Pi_{JJ}(\omega). }
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0677] FEEDBACK PHASE PARAMETER ADJUSTMENT}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
FEEDBACK PHASE PARAMETER ADJUSTMENT is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} u sub k+1 = u sub k + eta nabla sub u [I] implies text Optimization. \textbf{Contextual meaning:} The entry reads FEEDBACK PHASE PARAMETER ADJUSTMENT as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Geometric Constraint; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Transport coefficients arise from quantum current correlations rather than from purely classical response laws.

\tzpsection{Equation Grounding}
Equation anchors: w difference (binaural-style) beats (1--40 Hz), scale both by the same factor so the difference becomes a target beat : S = Delta B; For a practical target Hz (example): S = 24,000 10 = 2,400; and Hz, f  B = 129,600 2,400 = 54. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Real-Time Destructive-Interference Tuning}: The rapid, panicked twisting of the control knobs to ensure the sound wave you are pumping into the room is exactly, perfectly opposite to the noise you are trying to cancel out.
\item \textbf{Resonance-Drift Algorithmic Chasing}: The frustrating realization that as the metal gets hot, its tune changes, forcing the computers to constantly, endlessly slide their frequencies up and down just to stay in the sweet spot.
\item \textbf{Closed-Loop Harmonic Correction}: The brilliant, self-correcting wiring that takes the ugly, screeching mistakes coming out of the microphone and instantly feeds them backwards into the speaker to silence the room.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0677]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0677_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0677] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont FEEDBACK PHASE PARAMETER ADJUSTMENT}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records feedback phase parameter adjustment through the Septenary derivation
layer, using the displayed relations as operational anchors...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``FEEDBACK PHASE PARAMETER ADJUSTMENT is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0677_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
