\section*{ID9420: Definition of K𝐻}
\paragraph{Metadata.}
PiID: 1429894671543 | RTEID: RTE:P36579.9520:T3.7238 | UUID: 9663980f-8aa9-55c8-af13-aec4bc0f8dc8

\paragraph{Canonical Statement.}
le Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0391], [ID 0300] Node registry\_id\_0392 Support Titles Variation Law; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links \$𝑅𝜇𝜈𝜌𝜎=𝜅𝐻∇[𝜇𝐻𝜈\$ ]𝜌𝜎 \$K𝐻=∥𝐻 ∥2 Δ𝑅=𝜅𝐻K𝐻\$ [ID 0393] Unified Trawin Hamiltonian TZPID ID0393 UUID 7dbbbf3e-744a-55b6-960c-d8d5ec244af7 Type Dynamical / Variational Statement Scale field-dynamical LOC Classification Working routing: QC20.7 field theory; QA321 variational structure arXiv Classification Primary: hep-th; Cross-list: math-ph, gr-qc Canonical Statement This entry develops unified trawin hamiltonian inside the field theory and a

\paragraph{Canonical Equation.}
\[
K𝐻=∥𝐻 ∥2 Δ𝑅=𝜅𝐻K𝐻
\]

\paragraph{Dictionary.}
Definition of K𝐻 — K𝐻=∥𝐻 ∥2 Δ𝑅=𝜅𝐻K𝐻

\paragraph{Encyclopedia.}
Definition of K𝐻 is an algebraic definition, written K𝐻=∥𝐻 ∥2 Δ𝑅=𝜅𝐻K𝐻. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from K, defining K𝐻. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
