\section*{ID9415: Definition of Ψ(𝜃+2𝜋,𝑡)}
\paragraph{Metadata.}
PiID: 1225714298946 | RTEID: RTE:P36560.5359:T3.6919 | UUID: a1fc203e-ee48-5402-989b-03c2d0276364

\paragraph{Canonical Statement.}
belle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0373], [ID 0300] Node registry\_id\_0374 Support Titles Boundary Forcing; Angular Periodicity; Radial Carrier Test Handle If the stated angular periodicities do not induce the stated oscillatory boundary field, the entry fails. Canonical Equation Links \$Ψ(𝜃,𝑡\$ )=𝐴(𝜃 )𝑒𝑖𝜔𝑡 \$Ψ(𝜃+2𝜋,𝑡 )=Ψ(𝜃,𝑡\$ ) 𝑅 (𝑟 )=𝑅0𝐽𝑚 (𝑘𝑟 ) [ID 0375] Spherical Harmonic Expansion TZPID ID0375 UUID 7c10e7d8-64de-5fab-a5a1-e6390aa7ccdb Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops spherical harmonic expansion inside the fiel

\paragraph{Canonical Equation.}
\[
Ψ(𝜃+2𝜋,𝑡 )=Ψ(𝜃,𝑡
\]

\paragraph{Dictionary.}
Definition of Ψ(𝜃+2𝜋,𝑡) — Ψ(𝜃+2𝜋,𝑡 )=Ψ(𝜃,𝑡

\paragraph{Encyclopedia.}
Definition of Ψ(𝜃+2𝜋,𝑡) is an algebraic definition, written Ψ(𝜃+2𝜋,𝑡 )=Ψ(𝜃,𝑡. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
