\tzpanchor{0376}
\tzpentryheader{0376}{Gyromagnetic State Vector}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{48f3ad89-191d-500d-abf5-8c83c3edd0e3}}\\
\textbf{PiID} & \tzpcode{6652138414695} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{383}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1460.0915 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.4058 rad}\\
\textbf{TZPID} & \tzpcode{ID0376} & \textbf{Node Dependencies}\quad \tzpidref{0375}\\
\textbf{Registry} & \tzpcode{registry\_id\_0376} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & State Superposition & Normalization\\
\textbf{Closure Support} & Precession Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The state of a gyromagnetic propulsion system is described by a vector comprising the centre-of-mass position, the gyroscopic angular velocity, the effective dipole moment and the mechanical angular momentum.

\tzpsection{Canonical Equation}
\[
lvert\Psi_{\mathrm{gyro}}(t)\rangle=\alpha(t)\lvert\uparrow\rangle+\beta(t)\lvert\downarrow\rangle
\]
\[
|\alpha(t)|^2+|\beta(t)|^2=1
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Psi_{\mathrm{gyro}}(t)$: source equation symbol.
    \item $t$: source equation symbol.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
    \item $\Psi$: wavefunction or state carrier for the entry equation.
    \item $\alpha(t)$: source equation symbol.
    \item $\uparrow$: source equation symbol.
    \item $\beta(t)$: source equation symbol.
    \item $\downarrow$: source equation symbol.
    \item $P$: source equation symbol.
    \item $H_{gyro}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0376 generated source Wolfram model *)
ClearAll[K0376, Cr0376, T, R, A, W, I, N];
eq0376$1 = HoldForm[Ket[PsiGyro[t]] == alpha[t]*Ket[uparrow] + beta[t]*Ket[downarrow]];
eq0376$2 = HoldForm[Abs[alpha[t]]^2 + Abs[beta[t]]^2 == 1];
eq0376$3 = HoldForm[Ket[PsiGyro[t]] == Ket[PsiGyro[0]]/e^(iHGyrot/hbar)];

K0376 = HoldForm[{eq0376$1, eq0376$2, eq0376$3}];

N = "normalized TRAWIN closure object for Gyromagnetic State Vector";
I = "Precession Law integration/comparison layer";
W = "Normalization wave or operator carrier";
A = "State Superposition admissible action/amplitude condition";
R = "Normalization rotation/curl preservation layer";
T = "State Superposition local source condition";

Cr0376[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0376 = Cr0376[K0376];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ State Superposition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Normalization rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ State Superposition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Normalization wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Precession Law integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Gyromagnetic State Vector.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0376] Gyromagnetic State Vector}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
S(\omega)
=
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right)
\operatorname{Im}R(\omega).
\end{equation}

\paragraph{Effective Temperature Split.}
\begin{equation}
T_{\mathrm{eff}}
=
T_{\mathrm{eff}}^{\mathrm{th}}
+
T_{\mathrm{eff}}^{\mathrm{TZP}} .
\end{equation}

\paragraph{Primary Derivation.}
Let $S(\omega)$ be the noise spectrum and $R(\omega)$ the response function.  
Dissipation is encoded by the imaginary part:
\begin{equation}
\operatorname{Im}R(\omega).
\end{equation}

The fluctuation factor is set by the effective thermal and zero-point scale:
\begin{equation}
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right).
\end{equation}

Multiplying the two pieces gives:
\begin{equation}
\boxed{
S(\omega)
=
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right)
\operatorname{Im}R(\omega).
}
\end{equation}

\paragraph{Interpretation.}
Noise and response are coupled through an effective temperature that includes ordinary thermal and TZP contributions.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Gyromagnetic State Vector by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. State Superposition}\par
\[
lvert\Psi_{\mathrm{gyro}}(t)\rangle=\alpha(t)\lvert\uparrow\rangle+\beta(t)\lvert\downarrow\rangle
\]
\noindent This fixes the two-sector gyromagnetic state as a time-dependent superposition.\par
\noindent\textbf{2. Normalization}\par
\[
|\alpha(t)|^2+|\beta(t)|^2=1
\]
\noindent This imposes the normalization condition on the admissible state amplitudes.\par
\noindent\textbf{3. Precession Law}\par
\[
lvert\Psi_{\mathrm{gyro}}(t)\rangle=e^{-iH_{\mathrm{gyro}}t/\hbar}\lvert\Psi_{\mathrm{gyro}}(0)\rangle
\]
\noindent This closes the entry with the Hamiltonian precession law governing the state evolution.\par

\clearpage
\noindent\textbf{[ID 0376] Gyromagnetic State Vector}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Gyromagnetic State Vector is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The state of a gyromagnetic propulsion system is described by a vector comprising the centre-of-mass position, the gyroscopic angular velocity, the effective dipole moment and the mechanical angular momentum. \textbf{Contextual meaning:} The entry reads Gyromagnetic State Vector as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now presents the gyromagnetic state as a real quantum carrier instead of falling back to unstructured prose. \textbf{Lemma support:} State Superposition; Normalization; Precession Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Noise and response are coupled through an effective temperature that includes ordinary thermal and TZP contributions.

\tzpsection{Equation Grounding}
Equation anchors: lvertPsi sub gyro (t)=alpha(t)lvertuparrow+beta(t)lvertdownarrow; |alpha(t)| to the power 2+|beta(t)| to the power 2=1; and lvertPsi sub gyro (t)=e to the power -iH sub gyro t/hbar lvertPsi sub gyro (0). Proof route: show that the stated precession law preserves the normalization of the gyromagnetic state vector. Formalization route: prove that the Hamiltonian evolution keeps the state inside the normalized admissible two-sector carrier.

\tzpsection{Interpretive Role}
The entry now presents the gyromagnetic state as a real quantum carrier instead of falling back to unstructured prose.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spin-Up Spin-Down Superposition}: The quantum mechanical representation of a particle existing simultaneously in two opposite states of magnetic rotation.
\item \textbf{Probability Amplitude Normalization}: The strict mathematical rule forcing the sum of the chances of finding the particle in either state to equal exactly one hundred percent.
\item \textbf{Larmor Precession Evolution}: The predictable, rhythmic wobbling of the quantum state vector as it reacts to the pull of an external magnetic field over time.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0376]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0376_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0376] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Gyromagnetic State Vector}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the state of a gyromagnetic propulsion system is described by a vector comprising the
centre-of-mass position, the gyroscopic angular velocity, the...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Gyromagnetic State Vector is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0376_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
