\tzpanchor{0317}
\tzpentryheader{0317}{Reverse Harmonic Decomposition Algorithm}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{cd06e785-7356-51c8-ac37-79d00bfa758c}}\\
\textbf{PiID} & \tzpcode{8174881520920} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{324}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1230.9814 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.0283 rad}\\
\textbf{TZPID} & \tzpcode{ID0317} & \textbf{Node Dependencies}\quad \tzpidref{0316}\\
\textbf{Registry} & \tzpcode{registry\_id\_0317} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Mode Quantization & Dispersion Law\\
\textbf{Closure Support} & Boundary Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Given an observed spectrum $S_{\mathrm{obs}}(\omega,k)$, form a mode table, measure the observed helicity $H_{\mathrm{obs}}$, and for each resonance $\omega_i$ perform a spherical-harmonic transform to extract $(n_i,\ell_i,m_i)$. Solve

\tzpsection{Canonical Equation}
\[ \omega_i - \omega_{\mathrm{uncoupled}}(n_i,\ell_i,m_i) = m^{\mathrm{KK}}_{i}\frac{c}{R_{\mathrm{KK}}}, \] compute the amplitude $A_i$ from the helicity data, and reconstruct the initial field by summing the corresponding eigenmodes with phase factor \[ \exp\!\left(\frac{2\pi i\, m^{\mathrm{KK}}_{i} z}{R_{\mathrm{KK}}}\right). \]

\[
f(t)=\sum_{n\geq0} a_n e^{in\omega t}
\]
\[
a_n=\frac{1}{2\pi}\int_0^{2\pi} f(t)e^{-in\omega t}\,dt
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\omega_i$: angular frequency term in the source equation.
    \item $\omega_{\mathrm{uncoupled}}$: angular frequency term in the source equation.
    \item $n_i$: source equation symbol.
    \item $m_i$: source equation symbol.
    \item $c$: speed of light or relativistic conversion factor.
    \item $R_{\mathrm{KK}}$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $n$: integer mode index.
    \item $a_n$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0317 generated source Wolfram model *)
ClearAll[K0317, Cr0317, T, R, A, W, I, N];
eq0317$1 = HoldForm[omegaI - omegaUncoupled[nI, ellI, mI] == m^KK*_*i*(c/RKK)];
eq0317$2 = HoldForm[exp[(2*Pi*im^KK*_*i*z)/RKK]];
eq0317$3 = HoldForm[f[t] == SumN0*aN*Exp[I*nomega*t]];
eq0317$4 = HoldForm[aN == (1/(2*Pi))*Integral0^(2*Pi)*f[t]*Exp[(-inomega)*t]*dt];
eq0317$5 = HoldForm[fRev[t] == SumN0*aN*Exp[(-inomega)*t]];

K0317 = HoldForm[{eq0317$1, eq0317$2, eq0317$3, eq0317$4, eq0317$5}];

N = "normalized TRAWIN closure object for Reverse Harmonic Decomposition Algorithm";
I = "Boundary Condition integration/comparison layer";
W = "Dispersion Law wave or operator carrier";
A = "Mode Quantization admissible action/amplitude condition";
R = "Dispersion Law rotation/curl preservation layer";
T = "Mode Quantization local source condition";

Cr0317[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0317 = Cr0317[K0317];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Mode Quantization local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Dispersion Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Mode Quantization admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Dispersion Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Boundary Condition integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Reverse Harmonic Decomposition Algorithm.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0317] Reverse Harmonic Decomposition Algorithm}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\nabla^{T}g=0,
\qquad
T(\nabla^{T})=0
\quad
(x\neq p).
\end{equation}

\paragraph{Primary Derivation.}
Away from the TZP, the geometry should reduce to ordinary metric-compatible differential geometry. Therefore the Trawinistic connection $\nabla^{T}$ must satisfy metric compatibility:

\begin{equation}
\nabla^{T}g=0 .
\end{equation}

It must also be torsion-free away from the degenerate point:

\begin{equation}
T(\nabla^{T})=0,
\qquad x\neq p .
\end{equation}

When $\det(g)\neq 0$, the unique connection satisfying metric compatibility and zero torsion is the Levi-Civita connection. Hence:

\begin{equation}
\nabla^{T}=\nabla^{LC},
\qquad x\neq p .
\end{equation}

At $p$, where $\det(g)|_p=0$, $\nabla^{T}$ is extended by the rule that null vectors are annihilated or stabilized under the degenerate structure.

\paragraph{Interpretation.}
The Trawinistic connection preserves ordinary geometry away from $p$ while extending the differential structure into the TZP degeneracy.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Reverse Harmonic Decomposition Algorithm by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Mode Quantization}\par
\[
f(t)=\sum_{n\geq0} a_n e^{in\omega t}
\]
\noindent This fixes the quantized carrier mode indexed by the bounded geometry.\par
\noindent\textbf{2. Dispersion Law}\par
\[
a_n=\frac{1}{2\pi}\int_0^{2\pi} f(t)e^{-in\omega t}\,dt
\]
\noindent This turns the mode index into an actual propagation or resonance law.\par
\noindent\textbf{3. Boundary Condition}\par
\[
f_{\mathrm{rev}}(t)=\sum_{n\geq0}a_n e^{-in\omega t}
\]
\noindent This closes the progression by enforcing the boundary or nodal condition that makes the pattern admissible.\par

\clearpage
\noindent\textbf{[ID 0317] Reverse Harmonic Decomposition Algorithm}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Reverse Harmonic Decomposition Algorithm is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Given an observed spectrum S sub obs (omega,k), form a mode table, measure the observed helicity H sub obs , and for each resonance omega sub i perform a spherical-harmonic transform to extract (n sub i,ell sub i,m sub i). Solve omega sub i - omega sub uncoupled (n sub i,ell sub i,m sub i) = m to the power KK sub i ratio c R sub KK , compute the amplitude A sub i from the helicity data, and reconstruct the initial field by summing the corresponding eigenmodes with phase factor exp (ratio 2pi i m to the power KK sub i z R sub KK ). \textbf{Contextual meaning:} The entry reads Reverse Harmonic Decomposition Algorithm as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred. \textbf{Lemma support:} Mode Quantization; Dispersion Law; Boundary Condition.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The Trawinistic connection preserves ordinary geometry away from p while extending the differential structure into the TZP degeneracy.

\tzpsection{Equation Grounding}
Equation anchors: html?utm sub source =chatgpt; com/incidents/8cY8jdUpEGGbsSMSQk7J?utm sub source =chatgpt; and org/wiki/Google sub Compute sub Engine?utm sub source =chatgpt. Proof route: show that bounded carrier geometry forces the stated mode quantization and resonance law. Formalization route: prove that the stated boundary condition yields the stated discrete spectrum.

\tzpsection{Interpretive Role}
The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Inverse Fourier Projection}: The analytical method synthesizing complex localized pulses from a dense superposition of elementary frequency waves.
\item \textbf{Negative-Phase Spectral Extraction}: The numerical isolation of time-reversed frequency components required for backward-propagating signal generation.
\item \textbf{Discrete Harmonic Reconstruction}: The assembly of a continuous global field strictly from isolated, quantized orbital momentum modes.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0317]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0317_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0317] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Reverse Harmonic Decomposition Algorithm}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} given an observed spectrum S\_obs(,k), form a mode table, measure the observed helicity
H\_obs, and for each resonance \_i perform a spherical-h...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Reverse Harmonic Decomposition Algorithm is valid as a spectral relation when frequency,
phase, and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0317_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
