\section*{ID8588: Definition of λDf(x)}
\paragraph{Metadata.}
PiID: 1634456212964 | RTEID: RTE:P33349.1112:T4.6836 | UUID: f7da17c9-744d-5ddb-80d8-a14ce70a75f0

\paragraph{Canonical Statement.}
the total energy operator. Unifies cavity modes, mechanical vibrations, fractal coupling, and tunneling. Convergence to a stable eigenvalue indicates system "Ignition." Source: [ID 1113] EXPERIMENTAL DEVIATION TOLERANCE Canonical Statutory Formula: \$σerror ≤ |χtheoretical−χobserved| ≤ 0.05 \$ Formal Technical Dissertation: Establishes error bounds. The observed ratio must remain within 5 Source: [ID 1114] SCALE INVARIANCE CONFIRMATION Canonical Statutory Formula: \$f(λx) \$ = \$λDf(x) =⇒ D ≈ 3/2 \$ Formal Technical Dissertation: Confirms scale invariance. System dynamics follow a power-law with exponent \$D ≈ 1.5, \$ proving operation at self-organized criticality and successful entrainment across scales. Source: [ID 1115] ENERGY-TIME UNCERTAINTY GUARDRAILS Canonical Statutory For-mula: \$∆E ·∆t ≥ \$ ℏ 2 \$⊗ηrect \$ Formal Technical Dissertation: Quantum safety limits. Extraction

\paragraph{Canonical Equation.}
\[
λDf(x) =⇒ D ≈ 3/2
\]

\paragraph{Dictionary.}
Definition of λDf(x) — λDf(x) =⇒ D ≈ 3/2

\paragraph{Encyclopedia.}
Definition of λDf(x) is an algebraic definition, written λDf(x) =⇒ D ≈ 3/2. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from D, defining λDf(x). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
