\section*{ID8514: PYTHAGOREAN HARMONIC BRIDGE Canonical Statutory Formula: s\_3}
\paragraph{Metadata.}
PiID: 1754173818839 | RTEID: RTE:P33061.7528:T4.2101 | UUID: cb1960f4-a9b7-5fc6-bc0d-bd7d32cb6756

\paragraph{Canonical Statement.}
[ID 1161] PYTHAGOREAN HARMONIC BRIDGE Canonical Statutory Formula: \$s\_3 = s\_1 \textbackslash{}cdot s\_2 = (\textbackslash{}frac\{16\}\{15\}) \textbackslash{}cdot (\textbackslash{}frac\{10\}\{9\}) = \textbackslash{}frac\{32\}\{27\}\$ Formal Technical Dissertation: The composite operator linking the "Micro-Shift" (\$16/15\$) and "Meso-Shift" (\$10/9\$) into the "Macro-Shift" (\$32/27\$). It demonstrates how simple rational intervals compound to create the critical 18.5\% excess required for regime change. Source: [1], [14]

\paragraph{Canonical Equation.}
\[
s_3 = s_1 \cdot s_2 = (\frac{16}{15}) \cdot (\frac{10}{9}) = \frac{32}{27}
\]

\paragraph{Dictionary.}
PYTHAGOREAN HARMONIC BRIDGE Canonical Statutory Formula: \$s\_3 = s\_1 s\_2 = ( 1615) ( 109) = 3227\$ Formal Technical Dissertation: The composite operator linking the "Micro-Shift" (16/15) and "Meso-Shift" (10/9) into the "Macro-Shift" (32/27).

\paragraph{Encyclopedia.}
PYTHAGOREAN HARMONIC BRIDGE Canonical Statutory Formula: s\_3 is an algebraic definition, written s\_3 = s\_1 · s\_2 = ((16)/(15)) · ((10)/(9)) = (32)/(27). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from s\_1, s\_2, defining s\_3. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
