\section*{ID9028: Definition of (ω)}
\paragraph{Metadata.}
PiID: 4437558900456 | RTEID: RTE:P35057.7289:T1.2157 | UUID: 467f11f2-49b7-58fa-ad73-e5013ae52cd3

\paragraph{Canonical Statement.}
decoherence rates; appears in spectral density calculations; and relates to crossmodal coherence. Falsifiability / Test Handle: Experimentally measured transfer rates that disagree with predicted values after accounting for the Trawinistic Lagrangian would challenge this operator. Canonical Registry Vol. 01 6 Trawin Zero Point Contextus Canonicus 0.0.17 ID 015: Spectral Density Index (TZPWeighted) Type: Definition Formal Statement: The spectral density index \$(ω)\textbackslash{}eta(\textbackslash{}omega)(ω)\$ is defined as \$(ω)=ωβeω/ω\_0\textbackslash{}eta(\textbackslash{}omega)=\textbackslash{}omega\{-\textbackslash{}beta\},e\{-\textbackslash{}omega/\textbackslash{}omega\_0\}(ω)=ωβeω/ω\_0,\$ where \$ω\_0\textbackslash{}omega\_0ω\_0\$ is a characteristic frequency determined by u\_Tu\_\{\textbackslash{}text\{T\}\}u\_T and \$β\textbackslash{}betaβ\$ is a dimensionless exponent that depends on the hyperdimensional span. Interpretive Meaning: This function weights contributions of different frequencies to the spectral density in a way that reflects the presence of the TZP. Low frequencies are suppressed or enhanced depending on \$β\textbackslash{}betaβ.\$ Dep

\paragraph{Canonical Equation.}
\[
(ω)=ωβeω/ω_0\eta(\omega)=\omega{-\beta},e{-\omega/\omega_0}(ω)=ωβeω/ω_0,
\]

\paragraph{Dictionary.}
Definition of (ω) — (ω)=ωβeω/ω\_0η(ω)=ω-β,e-ω/ω\_0(ω)=ωβeω/ω\_0

\paragraph{Encyclopedia.}
Definition of (ω) is an algebraic definition, written (ω)=ωβeω/ω\_0η(ω)=ω-β,e-ω/ω\_0(ω)=ωβeω/ω\_0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from η, ω, β, defining (ω). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
