\section*{ID8512: CRITICAL PHASE MARGIN CALIBRATION Canonical Statutory Formula: φ\_c := (π)/(6)…}
\paragraph{Metadata.}
PiID: 4917541738188 | RTEID: RTE:P33053.9863:T4.1973 | UUID: 098311a7-ae1a-5c20-8000-4c06858d3dc7

\paragraph{Canonical Statement.}
[ID 1159] CRITICAL PHASE MARGIN CALIBRATION Canonical Statutory Formula: \$\textbackslash{}phi\_c := \textbackslash{}frac\{\textbackslash{}pi\}\{6\} \textbackslash{}approx 30\textasciicircum{}\textbackslash{}circ\$ Formal Technical Dissertation: The canonical calibration of the bifurcation band. By setting the critical margin to \$\textbackslash{}pi/6\$, the system locks the Pythagorean minor third (\$32/27\$) as the precise trigger that exceeds the threshold by a factor of exactly \$10/9\$, unifying the harmonic ladder. Source: [8], [11]

\paragraph{Canonical Equation.}
\[
\phi_c := \frac{\pi}{6} \approx 30^\circ
\]

\paragraph{Dictionary.}
CRITICAL PHASE MARGIN CALIBRATION Canonical Statutory Formula: φ\_c := (π)/(6) ≈ 30\textasciicircum{}circ Formal Technical Dissertation: The canonical calibration of the bifurcation band.

\paragraph{Encyclopedia.}
CRITICAL PHASE MARGIN CALIBRATION Canonical Statutory Formula: φ\_c := (π)/(6)… is a scaling / order-of-magnitude relation, written φ\_c := (π)/(6) ≈ 30\textasciicircum{}circ. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from π, c. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
