\section*{ID8558: Definition of |Blobtest|}
\paragraph{Metadata.}
PiID: 4531427756879 | RTEID: RTE:P33232.6145:T4.4916 | UUID: 61b1a1d0-9db8-5fef-b54e-7921a1f31a6a

\paragraph{Canonical Statement.}
0 per vertex). Source: [ID 912] STEREOGRAPHIC TESSERACT UNFOLDING Canonical Statutory For-mula: \$Unfold(q) \$ := \$2·coords4D \$ \$1−w ∈ \$ R3 Formal Technical Dissertation: The inverse decoding function. It reconstructs 4D coordinates from the quantum address and applies stereographic pro-jection from the 3-sphere \$S3 \$ to Euclidean R3, handling the north pole singularity. Source: [ID 913] BIJECTION INJECTION VERIFIER Canonical Statutory Formula: \$|Unique(f(Blobtest))| \$ == \$|Blobtest| =⇒ Injection \$ Formal Technical Dissertation: A verification logic gate that asserts the injectivity of the encoding system. It confirms that the cardinality of the set of encoded ad-dresses equals the cardinality of the input test manifold, proving no collisions occur. Source: [ID 914] QUANTUM PATH INTEGRAL NAVIGATION Canonical Statutory Formula: \$Ψnav \$ = \$∫\$ 1 0 \$e \$ \$i(addrt−addrs)tJ0( \$ \$√\$

\paragraph{Canonical Equation.}
\[
|Blobtest| =⇒ Injection
\]

\paragraph{Dictionary.}
Definition of |Blobtest| — |Blobtest| =⇒ Injection

\paragraph{Encyclopedia.}
Definition of |Blobtest| is an algebraic definition, written |Blobtest| =⇒ Injection. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from I, n, j, c, o, defining |Blobtest|. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
