\section*{ID9416: Definition of ⟩}
\paragraph{Metadata.}
PiID: 2257142989467 | RTEID: RTE:P36564.4191:T3.6982 | UUID: 9fe54307-3f4c-52e2-a7cb-a779114d6261

\paragraph{Canonical Statement.}
Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0375], [ID 0300] Node registry\_id\_0376 Support Titles State Superposition; Normalization; Precession Law Test Handle If the gyromagnetic Hamiltonian does not preserve state normalization, the entry fails. Canonical Equation Links \$𝑙𝑣𝑒𝑟𝑡Ψgyro\$ (𝑡 ) \$⟩=𝛼(𝑡\$ ) \$|↑⟩+𝛽\$ (𝑡 ) \$|↓⟩\$ |𝛼(𝑡 ) |2+|𝛽 (𝑡 ) |2=1 \$𝑙𝑣𝑒𝑟𝑡Ψgyro\$ (𝑡 ) \$⟩=𝑒−𝑖𝐻gyro𝑡/ℏ |Ψgyro\$ (0) \$⟩\$ [ID 0377] Effective Dipole with Quantum Correction TZPID ID0377 UUID dbf4a76a-0efc-596c-bb2d-e10208f95a56 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops effective dipole with quantum correction in

\paragraph{Canonical Equation.}
\[
⟩=𝑒−𝑖𝐻gyro𝑡/ℏ |Ψgyro
\]

\paragraph{Dictionary.}
Definition of ⟩ — ⟩=𝑒−𝑖𝐻gyro𝑡/ℏ |Ψgyro

\paragraph{Encyclopedia.}
Definition of ⟩ is an algebraic definition, written ⟩=𝑒−𝑖𝐻gyro𝑡/ℏ |Ψgyro. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from g, y, r, o, defining ⟩. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
