\tzpanchor{0242}
\tzpentryheader{0242}{Universal Helicity Number}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7c1a39d3-651b-5454-938e-7f3cdb9e8a3a}}\\
\textbf{PiID} & \tzpcode{1201909145648} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{249}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{939.7397 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.5484 rad}\\
\textbf{TZPID} & \tzpcode{ID0242} & \textbf{Node Dependencies}\quad \tzpidref{0241}\\
\textbf{Registry} & \tzpcode{registry\_id\_0242} & \textbf{Scale}\quad diagnostic\\
\textbf{LOC Classification} & QA273 dimensionless analysis & QC statistical diagnostics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: nlin.PS, physics.data-an\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The dimensionless product lambda R (force-free parameter times system size) has a mean value approximately 5 with a standard deviation of about 4 across laboratory magnets, Earth's core, solar corona and accretion disks.

\tzpsection{Canonical Equation}
\[
H=\int_V A\cdot B\,dV
\]
\[
\lambda R\approx 5
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H$: source equation symbol.
    \item $A$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $\lambda$: cosmological or lemniscatic branch parameter in the entry relation.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\sigma_{\lambda R}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0242 generated source Wolfram model *)
ClearAll[K0242, Cr0242, T, R, A, W, I, N];
eq0242$1 = HoldForm[H == IntegralV*A*B*dV];
eq0242$2 = HoldForm[lambda*R == 5];
eq0242$3 = HoldForm[sigmaLambdaR == 4];

K0242 = HoldForm[{eq0242$1, eq0242$2, eq0242$3}];

N = "normalized TRAWIN closure object for Universal Helicity Number";
I = "Normalized Regime integration/comparison layer";
W = "Scaling Relation wave or operator carrier";
A = "Diagnostic Definition admissible action/amplitude condition";
R = "Scaling Relation rotation/curl preservation layer";
T = "Diagnostic Definition local source condition";

Cr0242[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0242 = Cr0242[K0242];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Diagnostic Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Scaling Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Diagnostic Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Scaling Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Regime integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Universal Helicity Number.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0242] Universal Helicity Number}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{H}{\mathbf{B}^2 L}
=
\mathrm{constant}.
\end{equation}

\paragraph{Primary Derivation.}
Magnetic helicity has the characteristic scaling form:

\begin{equation}
H
\sim
\mathbf{B}^2 L .
\end{equation}

Here $\mathbf{B}^2$ captures magnetic field intensity and $L$ captures the characteristic system scale.

To remove scale dependence, divide helicity by this natural scale:

\begin{equation}
\frac{H}{\mathbf{B}^2L}.
\end{equation}

If topology is preserved under scale transformations, then this dimensionless ratio remains invariant:

\begin{equation}
\boxed{
\frac{H}{\mathbf{B}^2 L}
=
\mathrm{constant}.
}
\end{equation}

\paragraph{Interpretation.}
Helicity functions as a scale-independent constraint: the topological content remains stable even when the system size changes.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Universal Helicity Number by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Diagnostic Definition}\par
\[
H=\int_V A\cdot B\,dV
\]
\noindent This defines the scalar diagnostic or conversion quantity named by the title.\par
\noindent\textbf{2. Scaling Relation}\par
\[
\lambda R\approx 5
\]
\noindent This elevates the quantity into a comparative scaling or correlation law.\par
\noindent\textbf{3. Normalized Regime}\par
\[
\sigma_{\lambda R}\approx 4
\]
\noindent This closes the entry by normalizing the diagnostic against a stated reference regime.\par

\clearpage
\noindent\textbf{[ID 0242] Universal Helicity Number}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Universal Helicity Number is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The dimensionless product lambda R (force-free parameter times system size) has a mean value approximately 5 with a standard deviation of about 4 across laboratory magnets, Earth s core, solar corona and accretion disks. \textbf{Contextual meaning:} The entry reads Universal Helicity Number as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons. \textbf{Lemma support:} Diagnostic Definition; Scaling Relation; Normalized Regime.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Helicity functions as a scale-independent constraint: the topological content remains stable even when the system size changes.

\tzpsection{Equation Grounding}
Equation anchors: H=integral sub V Adot B dV; lambda Rapproximately 5; and sigma sub lambda R approximately 4. Proof route: show that the named quantity is dimensionless or consistently scaled in the regime stated by the entry. Formalization route: prove that the normalized diagnostic remains invariant under the intended rescaling.

\tzpsection{Interpretive Role}
The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Global Topological Linking Characteristic}: The extraction of a singular, scale-independent number summarizing the total twist and writhe of a system's vector field.
\item \textbf{Scale-Invariant Magnetic Twist Density}: The demonstration that the fundamental geometry of magnetic knotting remains constant regardless of the absolute size of the plasma.
\item \textbf{Universal Helicity Normalization Ratio}: The standard mathematical benchmark allowing the topological complexity of disparate astrophysical bodies to be directly compared.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0242]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0242_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0242] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Universal Helicity Number}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the dimensionless product lambda R (force-free parameter times system size) has a mean
value approximately 5 with a standard deviation of about 4 a...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Universal Helicity Number is valid when the stated geometric or topological relation
preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0242_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
