\section*{ID9145: Relation: ·|Σ\_j=1ˆN}
\paragraph{Metadata.}
PiID: 9029896959469 | RTEID: RTE:P35512.0659:T1.9643 | UUID: 2dc8a72a-f1fd-5d1a-af5d-c8e729d95ebf

\paragraph{Canonical Statement.}
oupling strengths in the planetary Kuramoto model. Retrograde rotation is represented by negative periods. Dependencies: 115 Derivable Consequences: Natural frequency vector; coupling matrix values; ranking of coupling strengths; baseline for simulation. Falsifiability / Test Handle: Update with refined observational data and test sensitivity of results to parameter changes. 1.0.18 ID 117: SpinCoherence Order Parameter Type: Operator Formal Statement: Define the coherence measure r(k0) = (1/N) \$·|Σ\_\{j=1\}ˆ\{N\}\$ exp(i \$θ\_j(t))|.\$ In numerical simulations using the planetary data and a range of coupling constants, r was observed to be approximately 0.18–0.54 depending on coupling strength, with no strong global synchronization. Interpretive Meaning: This order parameter quantifies how aligned the planetary spins become under the Kuramoto model. Low values indicate incoherence; partial clustering can occu

\paragraph{Canonical Equation.}
\[
·|Σ_{j=1}ˆ{N}
\]

\paragraph{Dictionary.}
Relation: ·|Σ\_j=1ˆN — ·|Σ\_j=1ˆN

\paragraph{Encyclopedia.}
Relation: ·|Σ\_j=1ˆN is an algebraic definition, written ·|Σ\_j=1ˆN. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from j, N. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
