\section*{ID6987: Important Inequality / Physical Intuition: N\_e > N\_d/2}
\paragraph{Metadata.}
PiID: 6028764962867 | RTEID: RTE:P27132.0727:T0.7230 | UUID: 408f5558-b684-5b3f-afe7-bd128c460f95

\paragraph{Canonical Statement.}
Stimulated gain term sign is controlled by \textbackslash{}((\textbackslash{}sigma\_\textbackslash{}text\{em\}N\_e - \textbackslash{}sigma\_\textbackslash{}text\{abs\}(N\_d-N\_e))\textbackslash{}). If that term becomes **positive**, net stimulated emission > absorption and photons can grow rapidly. For equal cross-sections this requires \textbackslash{}(N\_e > N\_d/2\textbackslash{}) (i.e., inversion), which is typically *not* the mechanism for photon BEC experiments — they instead rely on thermalization + chemical potential effects so you can get macroscopic ground-mode occupation without inversion. So don’t fixate on inversion; instead aim to make thermalization faster than loss (i.e., increase τ\_c or lower loss and/or increase thermalization rates).

\paragraph{Canonical Equation.}
\[
N_e > N_d/2
\]

\paragraph{Dictionary.}
Stimulated gain term sign is controlled by \textbackslash{}(( \_emN\_e - \_abs(N\_d-N\_e))\textbackslash{}) [ID6987]

\paragraph{Encyclopedia.}
Important Inequality / Physical Intuition: N\_e > N\_d/2 is an inequality / bound, written N\_e > N\_d/2. It states an inequality or bound that constrains the admissible range of the quantity. It is built from N\_e, N\_d. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
