\section*{ID9345: Definition of ΩB}
\paragraph{Metadata.}
PiID: 3755600372798 | RTEID: RTE:P36288.7103:T3.2440 | UUID: 71041c97-cf1c-5bd9-b816-1298930ababd

\paragraph{Canonical Statement.}
icate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0164], [ID 0162] Node registry\_id\_0165 Support Titles Berry Curvature Formula; Quantized Flux; Monopole Diagnosis Test Handle If the Berry curvature integrated over spheres about the TZP is not quantized or does not define a stable Chern number, the monopole statement fails. Canonical Equation Links \$ΩB=Im(𝜕𝑖 ⟨𝜓 |𝜕𝑗𝜓⟩−𝜕𝑗 ⟨𝜓 |𝜕𝑖𝜓⟩) ∮\$ 𝑆 (TZP) \$ΩB=2𝜋\$ 𝐶1 \$𝐶1≠0 =⇒\$ TZP acts as a Berry monopole [ID 0166] Unified Geometry and Kähler Manifold TZPID ID0166 UUID 53a55d18-efce-5172-a0a1-d6c55cee0982 Type Geometric Synthesis Scale combined metric-curvature-complex structure LOC Classification Working routing: QA767 Kähler geometry; QA927 geometric quantum theory arXiv Classification Primary: math.DG Cross-list: quant-ph, math-ph Cano

\paragraph{Canonical Equation.}
\[
ΩB=Im(𝜕𝑖 ⟨𝜓 |𝜕𝑗𝜓⟩−𝜕𝑗 ⟨𝜓 |𝜕𝑖𝜓⟩) ∮
\]

\paragraph{Dictionary.}
Definition of ΩB — ΩB=Im(𝜕𝑖 ⟨𝜓 |𝜕𝑗𝜓⟩−𝜕𝑗 ⟨𝜓 |𝜕𝑖𝜓⟩) ∮

\paragraph{Encyclopedia.}
Definition of ΩB is an algebraic definition, written ΩB=Im(𝜕𝑖 ⟨𝜓 |𝜕𝑗𝜓⟩−𝜕𝑗 ⟨𝜓 |𝜕𝑖𝜓⟩) ∮. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from I, m, defining ΩB. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
