\section*{ID8790: RETROCAUSAL PROPAGATOR (WHEELER-FEYNMAN) Canonical Statutory Formula: G\_diff}
\paragraph{Metadata.}
PiID: 3860251522742 | RTEID: RTE:P34133.5221:T5.9761 | UUID: 508e53f2-92fe-5175-ba34-3cc6c4d5fd04

\paragraph{Canonical Statement.}
[ID 1165] RETROCAUSAL PROPAGATOR (WHEELER-FEYNMAN) Canonical Statutory Formula: \$G\_\{diff\} = \textbackslash{}frac\{1\}\{2\}(G\_\{ret\} + G\_\{adv\}) = \textbackslash{}frac\{1\}\{2\}\textbackslash{}left( \textbackslash{}frac\{\textbackslash{}delta(t' - t - r/c)\}\{r\} - \textbackslash{}frac\{\textbackslash{}delta(t' - t + r/c)\}\{r\} \textbackslash{}right)\$ Formal Technical Dissertation: The propagator for the Transactional Interpretation implementation. It combines 50\% retarded (forward-time) and 50\% advanced (backward-time) Green's functions to establish a standing wave "handshake" across time, acting as the carrier wave for the atemporal channel. Source: [4]

\paragraph{Canonical Equation.}
\[
G_{diff} = \frac{1}{2}(G_{ret} + G_{adv}) = \frac{1}{2}\left( \frac{\delta(t' - t - r/c)}{r} - \frac{\delta(t' - t + r/c)}{r} \right)
\]

\paragraph{Dictionary.}
Relation: G\_diff = (1)/(2)(G\_ret + G\_adv) = (1)/(2) ( (δ(t' - t - r/c))/(r) - (δ(t' - t + r/c))/(r) )

\paragraph{Encyclopedia.}
RETROCAUSAL PROPAGATOR (WHEELER-FEYNMAN) Canonical Statutory Formula: G\_diff is an algebraic definition, written G\_diff = (1)/(2)(G\_ret + G\_adv) = (1)/(2) ( (δ(t' - t - r/c))/(r) - (δ(t' - t + . It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from δ, G\_ret, G\_adv, r, c, defining G\_diff. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
