\section*{ID8982: Definition of S(M)− S(total)}
\paragraph{Metadata.}
PiID: 8360900323809 | RTEID: RTE:P34879.1007:T0.9214 | UUID: 64265072-f236-50da-ac35-132d784a92c3

\paragraph{Canonical Statement.}
Neural Resonance: This carrier frequency overlaps with critical exponents \$(τ ≈ 3/2)\$ found in neural information processing[cite: 9, 38]. [ID 428] TOROIDAL FLUX-GATING \& CHANNEL SEGREGATION Canonical Statutory Formula \$I(T\$ : \$A :M)\$ = \$S(T\$ ) + \$S(A)\$ + \$S(M)− S(total) =⇒ Res(TZP\$ ) (28) Formal Technical Dissertation ID 428 establishes the tripartite information architecture that emerges when energy is extracted at a Trawin Zero Point[cite: 17, 19]. The flow spontaneously segregates into three distinct channels: the Temporal Channel (classical data), the Atemporal Channel (null surface projection), and the Mediator Channel (quantum entanglement bridge)[cite: 20, 21]. This

\paragraph{Canonical Equation.}
\[
S(M)− S(total) =⇒ Res(TZP
\]

\paragraph{Dictionary.}
Neural Resonance: This carrier frequency overlaps with critical exponents (τ ≈ 3/2) found in neural information processing[cite: 9, 38].

\paragraph{Encyclopedia.}
Definition of S(M)− S(total) is an algebraic definition, written S(M)− S(total) =⇒ Res(TZP. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R, s, T, Z, P, defining S(M)− S(total). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
