\section*{ID9003: Definition of ω\_n}
\paragraph{Metadata.}
PiID: 8970695365349 | RTEID: RTE:P34960.6484:T1.0557 | UUID: abcc6732-62a6-53df-a3d1-5e7d42163c29

\paragraph{Canonical Statement.}
e system to sustain extreme internal temperatures (\$\textbackslash{}sim 10\textasciicircum{}7\$ K at the singularity) while the surrounding vessel remains in a superconducting state, effectively nullifying thermal entropic death within the active manifold. From an engineering perspective, \$\textbackslash{}hat\{\textbackslash{}mathcal\{H\}\} \{\textbackslash{}text\{cymatic\}\}\$ is implemented through a tessellated array of piezoelectric transducers mounted on the vibration plinth. These transducers inject a multi-frequency harmonic series—specifically the Golden Ratio series (\$\textbackslash{}omega\_n = \textbackslash{}omega\_base / \textbackslash{}phi\textasciicircum{}n\$)—to ensure fractal resonance across all scales. Laboratory verification of the Cymatic Field Modulation Term is achieved via high-speed laser vibrometry and the observation of Chladni-Trawin Patterns in the ferrofluid core. These patterns represent the physical manifestation of the "Vibrating Code," where the geometry of the fluid vortex aligns perfectly with the predicted nodal lattice. The

\paragraph{Canonical Equation.}
\[
\omega_n = \omega_base / \phi^n
\]

\paragraph{Dictionary.}
Definition of ω\_n — ω\_n = ω\_base / φ\textasciicircum{}n

\paragraph{Encyclopedia.}
Definition of ω\_n is an algebraic definition, written ω\_n = ω\_base / φ\textasciicircum{}n. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from φ, b, a, s, n, defining ω\_n. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
