\tzpanchor{0374}
\tzpentryheader{0374}{Oscillatory Boundary Field Operator}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e147a455-7189-504b-b01d-93e39361ef1d}}\\
\textbf{PiID} & \tzpcode{0466521384146} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{381}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1452.3251 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.3930 rad}\\
\textbf{TZPID} & \tzpcode{ID0374} & \textbf{Node Dependencies}\quad \tzpidref{0373}\\
\textbf{Registry} & \tzpcode{registry\_id\_0374} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Boundary Forcing & Angular Periodicity\\
\textbf{Closure Support} & Radial Carrier & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A spherical shell partitioned into domains of alternating sign imposes a radial boundary field described by a sign function times a harmonic oscillation. The interior field is expanded in spherical harmonics to satisfy both Maxwell's equations and the boundary sign pattern.

\tzpsection{Canonical Equation}
\[
\Psi(\theta,t)=A(\theta)e^{i\omega t}
\]
\[
\Psi(\theta+2\pi,t)=\Psi(\theta,t)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Psi$: wavefunction or state carrier for the entry equation.
    \item $t$: source equation symbol.
    \item $A$: source equation symbol.
    \item $\theta$: phase angle or local angular coordinate.
    \item $\omega$: angular frequency term in the source equation.
    \item $\pi$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $R_{0}$: source equation symbol.
    \item $J_{m}(kr)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0374 generated source Wolfram model *)
ClearAll[K0374, Cr0374, T, R, A, W, I, N];
eq0374$1 = HoldForm[Psi[theta, t] == A[theta]*Exp[I*omega*t]];
eq0374$2 = HoldForm[Psi[theta + 2*Pi, t] == Psi[theta, t]];
eq0374$3 = HoldForm[R[r] == R0*JM[kr]];

K0374 = HoldForm[{eq0374$1, eq0374$2, eq0374$3}];

N = "normalized TRAWIN closure object for Oscillatory Boundary Field Operator";
I = "Radial Carrier integration/comparison layer";
W = "Angular Periodicity wave or operator carrier";
A = "Boundary Forcing admissible action/amplitude condition";
R = "Angular Periodicity rotation/curl preservation layer";
T = "Boundary Forcing local source condition";

Cr0374[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0374 = Cr0374[K0374];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Boundary Forcing local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Angular Periodicity rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Boundary Forcing admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Angular Periodicity wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Radial Carrier integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Oscillatory Boundary Field Operator.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0374] Oscillatory Boundary Field Operator}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mathcal{E}(\rho)=\sum_k E_k\rho E_k^\dagger .
\end{equation}

\paragraph{Trace-Preserving Constraint.}
\begin{equation}
\sum_k E_k^\dagger E_k = I .
\end{equation}

\paragraph{Primary Derivation.}
A completely positive map admits a Kraus representation:
\begin{equation}
\mathcal{E}(\rho)=\sum_k E_k\rho E_k^\dagger .
\end{equation}

Trace preservation requires
\begin{equation}
\operatorname{Tr}(\mathcal{E}(\rho))=\operatorname{Tr}(\rho).
\end{equation}

Using cyclicity of trace,
\begin{equation}
\operatorname{Tr}(\mathcal{E}(\rho))
=
\operatorname{Tr}\left(
\rho\sum_k E_k^\dagger E_k
\right).
\end{equation}

This equals $\operatorname{Tr}(\rho)$ for all $\rho$ precisely when
\begin{equation}
\boxed{
\sum_k E_k^\dagger E_k = I .
}
\end{equation}

\paragraph{Interpretation.}
CPTP maps preserve both positivity and total probability, making them valid quantum-state transformations.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Oscillatory Boundary Field Operator by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Boundary Forcing}\par
\[
\Psi(\theta,t)=A(\theta)e^{i\omega t}
\]
\noindent This fixes the oscillatory radial boundary field imposed on the tessellated spherical shell.\par
\noindent\textbf{2. Angular Periodicity}\par
\[
\Psi(\theta+2\pi,t)=\Psi(\theta,t)
\]
\noindent This identifies the integer angular periodicities that govern the sign-flipping boundary pattern.\par
\noindent\textbf{3. Radial Carrier}\par
\[
R(r)=R_{0}J_{m}(kr)
\]
\noindent This closes the entry by relating the tessellation cell sizes to the chosen angular mode counts.\par

\clearpage
\noindent\textbf{[ID 0374] Oscillatory Boundary Field Operator}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Oscillatory Boundary Field Operator is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A spherical shell partitioned into domains of alternating sign imposes a radial boundary field described by a sign function times a harmonic oscillation. The interior field is expanded in spherical harmonics to satisfy both Maxwell s equations and the boundary sign pattern. \textbf{Contextual meaning:} The entry reads Oscillatory Boundary Field Operator as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the oscillatory boundary forcing as an actual angular field law instead of corrupted sign-pattern prose. \textbf{Lemma support:} Boundary Forcing; Angular Periodicity; Radial Carrier.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
CPTP maps preserve both positivity and total probability, making them valid quantum-state transformations.

\tzpsection{Equation Grounding}
Equation anchors: a sub l,m t boxed Psi(theta,lambda,t)=Psi sub rm dipole (theta,lambda)+Psi sub rm axial (theta,lambda)+sum sub l,m A sub l,m Y sub l to the power m (theta,lambda) e to the power iomeg; stry sub id sub 0371,[ID 0371],Constrained Dipole Configuration,inline sub dollar ,inline sub dollar , abla dot vec A sub dipole = 0, abla dot vec A sub dipole = 0,title sub j:0; and B= ablatimes A sub rm dipole ,; E=-partial sub t A - ablaPhi. Proof route: show that the stated oscillatory boundary field is periodic with the stated angular mode counts and tessellation scales. Formalization route: prove that the integer periodicities determine the stated angular cell widths and boundary sign pattern.

\tzpsection{Interpretive Role}
The entry now states the oscillatory boundary forcing as an actual angular field law instead of corrupted sign-pattern prose.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spatially Alternating Edge Forcing}: The application of a boundary condition that flips between positive and negative values in a strict, predictable grid pattern.
\item \textbf{Time-Harmonic Surface Waves}: The rhythmic, clock-like pulsation of the boundary field, driving continuous resonant energy into the bulk of the system.
\item \textbf{Integer-Mode Shell Harmonics}: The restriction of the boundary vibrations to exact whole numbers, ensuring the waves wrap perfectly around the spherical perimeter.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0374]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0374_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0374] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Oscillatory Boundary Field Operator}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a spherical shell partitioned into domains of alternating sign imposes a radial boundary
field described by a sign function times a harmonic oscill...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Oscillatory Boundary Field Operator is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0374_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
