\tzpanchor{0095}
\tzpentryheader{0095}{Natural Transformation Preserving Symplectic Structure}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{4319037a-1185-5351-b281-eb7404c4c3eb}}\\
\textbf{PiID} & \tzpcode{7067982148086} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{102}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{368.9061 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.6078 rad}\\
\textbf{TZPID} & \tzpcode{ID0095} & \textbf{Node Dependencies}\quad \tzpidref{0089}\\
\textbf{Registry} & \tzpcode{registry\_id\_0095} & \textbf{Scale}\quad categorical symplectic compatibility\\
\textbf{LOC Classification} & QA169 natural transformations & QA614.7 symplectic invariance\\
\textbf{arXiv Classification} & Primary: math.CT \quad Cross-list: math.SG, physics.class-ph & \\
\textbf{Primary Support} & Two Competing Routes & Natural Transformation Witness\\
\textbf{Closure Support} & Symplectic Compatibility Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Scaling and mapping between laboratory and astrophysical systems commute in a way that preserves the underlying phase space geometry; this ensures consistency of predictions.

\tzpsection{Canonical Equation}
\[
\eta : S \circ F \Rightarrow F \circ S
\]
\[
\eta_X^{\ast}\omega_{F\circ S(X)} = \omega_{S\circ F(X)}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S$: source equation symbol.
    \item $F$: source equation symbol.
    \item $X$: source variable, local coordinate, or input state in the entry relation.
    \item $\mathcal{K}_{0095}$: canonical registry object for entry ID 0095.
    \item $\eta$: source equation symbol.
    \item $\ast$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $X^{\ast}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0095 generated source Wolfram model *)
ClearAll[K0095, Cr0095, T, R, A, W, I, N];
eq0095$1 = HoldForm[eta:Scirc*F -> Fcirc*S];
eq0095$2 = HoldForm[etaX^ast*omegaFcircSX == omegaScircFX];
eq0095$3 = HoldForm[TZPSequence[Scirc*F, Fcirc*S]];

K0095 = HoldForm[{eq0095$1, eq0095$2, eq0095$3}];

N = "normalized TRAWIN closure object for Natural Transformation Preserving Symplectic Structure";
I = "Symplectic Compatibility Law integration/comparison layer";
W = "Natural Transformation Witness wave or operator carrier";
A = "Two Competing Routes admissible action/amplitude condition";
R = "Natural Transformation Witness rotation/curl preservation layer";
T = "Two Competing Routes local source condition";

Cr0095[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0095 = Cr0095[K0095];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Two Competing Routes local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Natural Transformation Witness rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Two Competing Routes admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Natural Transformation Witness wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Symplectic Compatibility Law integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Natural Transformation Preserving Symplectic Structure.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0095] Natural Transformation Preserving Symplectic Structure}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\eta:S\circ F\Rightarrow F\circ S.
\end{equation}

\paragraph{Symplectic Preservation Law.}
\begin{equation}
\eta_X^{*}\omega_{F\circ S(X)}
=
\omega_{S\circ F(X)}.
\end{equation}

\paragraph{Primary Derivation.}
Let $S$ be a scaling functor and $F$ a structure functor.  
There are two routes:

\begin{equation}
S\circ F,
\qquad
F\circ S.
\end{equation}

A natural transformation compares these routes:
\begin{equation}
\eta:S\circ F\Rightarrow F\circ S.
\end{equation}

To preserve dynamics, the bridge must preserve the symplectic form:
\begin{equation}
\boxed{
\eta_X^{*}\omega_{F\circ S(X)}
=
\omega_{S\circ F(X)}.
}
\end{equation}

\paragraph{Interpretation.}
Scaling and structural translation are compatible only when the categorical bridge preserves phase-space geometry.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Natural Transformation Preserving Symplectic Structure by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Two Competing Routes}\par
\[
S \circ F,
\qquad
F \circ S
\]
\noindent This identifies the two scale-translation paths whose compatibility is at stake.\par
\noindent\textbf{2. Natural Transformation Witness}\par
\[
\eta : S \circ F \Rightarrow F \circ S
\]
\noindent This provides the categorical bridge between the two routes.\par
\noindent\textbf{3. Symplectic Compatibility Law}\par
\[
\eta_X^{\ast}\omega_{F\circ S(X)} = \omega_{S\circ F(X)}
\]
\noindent This closes the progression by requiring the bridge to preserve the phase-space structure itself.\par

\clearpage
\noindent\textbf{[ID 0095] Natural Transformation Preserving Symplectic Structure}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Natural Transformation Preserving Symplectic Structure is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Scaling and mapping between laboratory and astrophysical systems commute in a way that preserves the underlying phase space geometry; this ensures consistency of predictions. \textbf{Contextual meaning:} The entry reads Natural Transformation Preserving Symplectic Structure as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry ensures that scaling and structural translation do not fight each other. It is the coherence law that lets the volume move confidently between analogues, functors, and Hamiltonian geometry. \textbf{Lemma support:} Two Competing Routes; Natural Transformation Witness; Symplectic Compatibility Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Scaling and structural translation are compatible only when the categorical bridge preserves phase-space geometry.

\tzpsection{Equation Grounding}
Equation anchors: There exists a natural transformation eta:ScircFRightarrowFcircSeta: S textbackslash circ F textbackslash Rightarrow F textbackslash circ Seta:ScircFRightarrowFcircS between the scaling functor SSS and the category-theoretic functor FFF that preserves the symplectic structure of phase space; diagrammatically, the following commutes: F(S(Lab))toetaS(F(Lab))F(S( Lab )) textbackslash xrightarrow eta S(F( Lab ))F(S(Lab))etaS(F(Lab)). There exists a natural transformation eta:ScircFRightarrowFcircSeta: S textbackslash circ F textbackslash Rightarrow F textbackslash circ Seta:ScircFRightarrowFcircS between the scaling functor SSS and the category-theoretic functor FFF that preserves the symplectic structure of phase space; diagrammatically, the following commutes: F(S(Lab))toetaS(F(Lab))F(S( Lab )) textbackslash xrightarrow eta S(F( Lab ))F(S(Lab))etaS(F(Lab)).

\tzpsection{Interpretive Role}
This entry ensures that scaling and structural translation do not fight each other. It is the coherence law that lets the volume move confidently between analogues, functors, and Hamiltonian geometry.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Natural Transformation Preserving Symplectic Structure}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Natural Transformation Preserving Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Structure Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0095]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0095_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0095] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Natural Transformation Preserving Symplectic Structure}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} scaling and mapping between laboratory and astrophysical systems commute in a way that
preserves the underlying phase space geometry; this ensures...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Natural Transformation Preserving Symplectic Structure is valid when its objects and
arrows close under the stated categorical construction.''\\
\textbf{Proof:} The source statement is read as a categorical construction. The proof obligation is
closure: objects must map to admissible objects, arrows must compose, and the named
invariant must survive the induced functor.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- categorical-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0095_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
