\section*{ID9149: Relation: ∂(R v\_r)/∂R}
\paragraph{Metadata.}
PiID: 8969594699556 | RTEID: RTE:P35527.5988:T1.9899 | UUID: 34ce08b0-6c69-5663-977c-24d05429f625

\paragraph{Canonical Statement.}
; predictions about vortex stability; interplay with radial pressure gradients. Falsifiability / Test Handle: Vary inflow angle in controlled experiments and measure vortex strength and stability. 1.0.23 ID 122: Cross Symmetry Vortex Focusing Type: Structural Constraint Formal Statement: A crossshaped stopper dividing an opening into four quadrants creates a stagnationpoint geometry with symmetric pressure gradients. The incompressible flow continuity equation in cylindrical coordinates, (1/r) \$∂(r v\_r)/∂r\$ + \$∂ v\_z/∂\$ z = 0, implies that as downward velocity v\_z increases, radial velocity v\_r must increase. The cross geometry enforces four symmetric channels, amplifying radial inflow. Interpretive Meaning: This geometry pulls fluid from all directions equally and focuses potential flow toward the centre, enhancing vortex formation. Dependencies: 121 Derivable Consequences: Amplified radial pressur

\paragraph{Canonical Equation.}
\[
∂(r v_r)/∂r
\]

\paragraph{Dictionary.}
Relation: ∂(R v\_r)/∂R — ∂(r v\_r)/∂r

\paragraph{Encyclopedia.}
Relation: ∂(R v\_r)/∂R is a symbolic expression, written ∂(r v\_r)/∂r. It introduces a symbol or relation used elsewhere in the framework. It is built from r, v\_r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
