\section*{ID9819: Definition of D}
\paragraph{Metadata.}
PiID: 0072452256326 | RTEID: RTE:P38129.3576:T6.2768 | UUID: 6ac982f2-fd64-5640-a937-55b43eacce99

\paragraph{Canonical Statement.}
obability \$1-p\$). This is like a tailored depolarizing channel that respects the kissing structure. Because of the stabilizer and topological codes (next step), we can correct those specific errors up to a threshold \$p < 1 - 1/\textbackslash{}pi \textbackslash{}approx 0.682\$. Error Correction (𝒞): On the receiving end, we apply a topological error-correcting code native to the kissing graph. In our implementation, we use a surface-code-like approach on a kissing lattice where stabilizers are defined by products of Pauli Z around closed loops of kissing contacts and Pauli X across dual loops. The code distance comes out as \$d = 2\textbackslash{}lfloor\textbackslash{}sqrt\{N\_\{\textbackslash{}max\}\textbackslash{}pi\}\textbackslash{}rfloor + 1\$ (for \$N\_\{\textbackslash{}max\}=153600\$, \$\textbackslash{}sqrt\{153600\textbackslash{}pi\}\textbackslash{}approx 694\$, so \$d\textbackslash{}approx1389\$!). This enormous distance indicates the ability to correct a huge number of errors. A minimum-weight perfect matching decoder is used to pair up any syndrome flips, weighted by probabilities derived from the error model. The net effect is that any corruption in the transmission will be identified and corrected with overwhelming probability. Decoding \& Verification (𝒱): Finally, the corrected trajectory is decoded back into

\paragraph{Canonical Equation.}
\[
d = 2\lfloor\sqrt{N_{\max}\pi}\rfloor + 1
\]

\paragraph{Dictionary.}
Definition of D — d = 2lfloorsqrtN\_maxπrfloor + 1

\paragraph{Encyclopedia.}
Definition of D is an algebraic definition, written d = 2lfloorsqrtN\_maxπrfloor + 1. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from π, N\_, defining d. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
