\section*{ID8998: Definition of SUq(2)TZP}
\paragraph{Metadata.}
PiID: 4595889706953 | RTEID: RTE:P34941.2323:T1.0237 | UUID: 5af7daca-a321-544d-b61f-b66cc5cd5ac1

\paragraph{Canonical Statement.}
Metric Perturbation: In the rotating frame, the effective metric incorporates the Lense-Thirring term \$h0i,\$ which is essential for preserving gauge invariance at high angular velocities. [ID 520] NON-ABELIAN GAUGE SYMMETRY \& \$SU(2)\$ PROJECTION Canonical Statutory Formula \$SUq(2)TZP =⇒ q\$ = \$exp(iπνT\$ ) (111) Formal Technical Dissertation ID 520 formalizes the transition from Abelian \$U(1)\$ gauge theories to the non-Abelian \$SUq(2)TZP\$ quantum group structure localized at the Trawin Zero Point. This deformation utilizes the quantized winding number \$νT\$ to enable extra-dimensional access via \$SU(2)\$ or \$SU(3)\$ symmetries. The projection ensures that non-Abelian flux structures remain stable during the 4D to 2D dimensional collapse gateway.

\paragraph{Canonical Equation.}
\[
SUq(2)TZP =⇒ q
\]

\paragraph{Dictionary.}
Metric Perturbation: In the rotating frame, the effective metric incorporates the Lense-Thirring term h0i which is essential for preserving gauge invariance at high angular velocities.

\paragraph{Encyclopedia.}
Definition of SUq(2)TZP is an algebraic definition, written SUq(2)TZP =⇒ q. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from q, defining SUq(2)TZP. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
