\section*{ID9399: Definition of SDAAN}
\paragraph{Metadata.}
PiID: 7254370906979 | RTEID: RTE:P36498.4043:T3.5895 | UUID: bf52b31c-d0ff-520a-a5c5-1ecec320aea0

\paragraph{Canonical Statement.}
endix for [ID 0302] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0301], [ID 0300] Node registry\_id\_0302 Support Titles Geometric Carrier; Compatibility Law; Topological Closure Test Handle If the geometric deformation breaks compatibility or destroys the named invariant, the entry fails. Canonical Equation Links \$SDAAN=S+∪S−\$ A2=idSDAAN [𝑥 ]+[𝑥∗ ]=0 [ID 0303] Rotating Double Helix Geometry TZPID ID0303 UUID 8536be95-fadb-5dec-a4e5-85506ef30864 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops rotating double helix geometry inside

\paragraph{Canonical Equation.}
\[
SDAAN=S+∪S−
\]

\paragraph{Dictionary.}
Definition of SDAAN — SDAAN=S+∪S−

\paragraph{Encyclopedia.}
Definition of SDAAN is an algebraic definition, written SDAAN=S+∪S−. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from S, defining SDAAN. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
