\section*{ID6839: Predictions \& Empirical Signatures (What to Look for in Real Cosmic Maps)}
\paragraph{Metadata.}
PiID: 6660443325888 | RTEID: RTE:P26557.3558:T6.0592 | UUID: 460c5ee8-7d62-533d-9c71-ddb8cb89613c

\paragraph{Canonical Statement.}
\#\# 6) Predictions \& empirical signatures (what to look for in real cosmic maps) - **Prediction 1 (scale-angular coupling):** filaments at scale \textbackslash{}(≈1/k\textbackslash{}) will preferentially point along directions where \textbackslash{}(\textbackslash{}sum\_m \textbackslash{}delta\_\{\textbackslash{}ell m\}(k)Y\_\textbackslash{}ell\textasciicircum{}m(\textbackslash{}hat n)\textbackslash{}) is maximal (i.e., dominant angular modal alignment). Test with SBT + tidal-tensor alignment. - **Prediction 2 (doubling effect):** a dominant angular harmonic \textbackslash{}(m\textbackslash{}) will be visible as roughly \textbackslash{}(2m\textbackslash{}) radial spike-like features when projected into intensity (optical PSF analogy); in cosmic maps, this shows as periodic angular repetition of filamentary intersections. - **Prediction 3 (S³ signature):** if universe curvature is positive and near detection limit, you will find discrete radial-frequency peaks and long-range coherence in filament directions — measurable as non-trivial correlations between widely separated large-scale filament orientations beyond what ΛCDM random phases predict.

\paragraph{Canonical Equation.}
\[
\sum_m \delta_{\ell m}(k)Y_\ell^m(\hat n)
\]

\paragraph{Dictionary.}
Relation: ∑\_m δ\_ℓ m(k)Y\_ℓ\textasciicircum{}m(hat n)

\paragraph{Encyclopedia.}
Predictions \& Empirical Signatures (What to Look for in Real Cosmic Maps) is a series / summation, written ∑\_m δ\_ℓ m(k)Y\_ℓ\textasciicircum{}m(hat n). It is expressed as a sum or series over modes or indices, superposing discrete contributions. It is built from ell, m, k, Y, n. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
