\section*{ID9128: Definition of ρ\_eE),dVω}
\paragraph{Metadata.}
PiID: 4120766514793 | RTEID: RTE:P35446.0511:T1.8555 | UUID: 0f81a64f-c7dc-564e-96ec-1a986907a164

\paragraph{Canonical Statement.}
urement of truly isolated systems with constant angular momentum over time without external torques would refute this constraint. 0.0.90 ID 088: Local Electromagnetic Field–Driven Rotation Type: Definition Canonical Registry Vol. 01 30 Trawin Zero Point Contextus Canonicus Formal Statement: The angular velocity \$ω\textbackslash{}omegaω\$ of a rotating system is determined by local electromagnetic fields via \$ω=12L\$ \$∫\$ r× (J× \$B+ρeE)dV\textbackslash{}omega\$ = \textbackslash{}frac\{1\}\{2L\}\textbackslash{}int \textbackslash{}mathbf\{r\}\textbackslash{}times(\textbackslash{}mathbf\{J\}\textbackslash{}times\textbackslash{}mathbf\{B\} + \$\textbackslash{}rho\_e\textbackslash{}mathbf\{E\}),\textbackslash{}text\{d\}Vω=2L1 ∫\$ r× (J× \$B+ρeE)dV,\$ where LLL is the moment of inertia determined using the Trawin base unit. Interpretive Meaning: This defines how electromagnetic fields induce rotation; rotation depends on charge density, current and magnetic field configuration. Dependencies: ID 087 Derivable Consequences: Predictions of spinup in magnetised plasmas; relations between field strength and rotational velocity;

\paragraph{Canonical Equation.}
\[
\rho_e\mathbf{E}),\text{d}Vω=2L1 ∫
\]

\paragraph{Dictionary.}
Definition of ρ\_eE),dVω — ρ\_eE),dVω=2L1 ∫

\paragraph{Encyclopedia.}
Definition of ρ\_eE),dVω is an expectation / trace over state, written ρ\_eE),dVω=2L1 ∫. It is computed as an expectation value or trace over a quantum state, producing an observable. It is built from L, defining ρ\_eE),dVω. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
