\section*{ID9861: Relation: It Cost ≈ 10\textasciicircum{}6 × N\_max\textasciicircum{}1.5}
\paragraph{Metadata.}
PiID: 0359989535394 | RTEID: RTE:P38292.4529:T0.2623 | UUID: 171d7e0c-0227-57b9-a6aa-f19e99bb0a1d

\paragraph{Canonical Statement.}
resonant modes might suffice thanks to mode multiplexing. Classical Compute for Pre-processing: Some steps involve classical calculations (decoders, functor mappings). Complexity is about \$O(n\textasciicircum{}\textbackslash{}pi)\$ for naive classical simulation, which is intractable for large \$n\$. But these tasks (like decoding a topological code with \$n=153600\$) are manageable with modern HPC for \$n\textbackslash{}sim10\textasciicircum{}5\$. We foresee needing classical co-processors, maybe cloud resources, to run heavy math like persistent homology on large graphs in real-time. Financial \& Human Resources: A rough cost function came out of our analysis: \$\{\textbackslash{}it cost\} \textbackslash{}approx 10\textasciicircum{}6 \textbackslash{}times N\_\{\textbackslash{}max\}\textasciicircum{}\{1.5\}\$. Plugging \$N\_\{\textbackslash{}max\}=153600\$, this is \$10\textasciicircum{}6 * (1.536×10\textasciicircum{}5)\textasciicircum{}1.5 ≈ \$10\textasciicircum{}6 * 1.90×10\textasciicircum{}7 = \$1.9×10\textasciicircum{}\{13\}\$ – about \$19 trillion – clearly not realistic for now. However, that's extrapolating full scale. A smaller 10\% scale prototype would be \$19 billion, and a 1\% scale (maybe \textasciitilde{}1536 dimension) is \$190 million. These figures indicate a significant investment, but not outlandish given large government/industry projects (e.g., CERN or big semiconductor fabs cost in the billions). It’s plausible that initial

\paragraph{Canonical Equation.}
\[
{\it cost} \approx 10^6 \times N_{\max}^{1.5}
\]

\paragraph{Dictionary.}
Relation: It Cost ≈ 10\textasciicircum{}6 × N\_max\textasciicircum{}1.5 — it cost ≈ 10\textasciicircum{}6 × N\_max\textasciicircum{}1.5

\paragraph{Encyclopedia.}
Relation: It Cost ≈ 10\textasciicircum{}6 × N\_max\textasciicircum{}1.5 is a scaling / order-of-magnitude relation, written it cost ≈ 10\textasciicircum{}6 × N\_max\textasciicircum{}1.5. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from c, o, s, N\_. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
