\section*{ID9045: Definition of V\_T(x)}
\paragraph{Metadata.}
PiID: 2250545255640 | RTEID: RTE:P35123.7437:T1.3245 | UUID: b30c3a00-889e-5ebe-9d90-46c1e789f30b

\paragraph{Canonical Statement.}
physical conditions (e.g., energy densities) that produce singularities; constrains acceptable solutions to field equations; motivates introduction of potential terms; affects stability. Falsifiability / Test Handle: Finding finite regularised curvature for all physically realised configurations would refute the presence of curvature singularities. 0.0.25 ID 023: TZP Potential Term Type: Definition Formal Statement: The TZP potential V\_T(x)V\_\{\textbackslash{}text\{T\}\}(x)V\_T(x) is defined near the zero point as \$V\_T(x)=λexp(d(x,p)u\_T)V\_\{\textbackslash{}text\{T\}\}(x)=\textbackslash{}lambda,\textbackslash{}exp\textbackslash{}bigl(-\textbackslash{}frac\{d(x,p)\}\{u\_\{\textbackslash{}text\{T\}\}\}\textbackslash{}bigr)V\_T(x)=λexp(u\_Td(x,p)),\$ where \$λ\textbackslash{}lambdaλ\$ is a coupling constant and d(x,p)d(x,p)d(x,p) is the geodesic distance from xxx to ppp. Interpretive Meaning: This potential models the energy associated with proximity to the TZP. It decreases exponentially with distance, reflecting the localisation of the zeropoint influence. Dependencies: ID 006, ID 001 Derivable Consequences: Appears in the Hamiltonian density

\paragraph{Canonical Equation.}
\[
V_T(x)=λexp(d(x,p)u_T)V_{\text{T}}(x)=\lambda,\exp\bigl(-\frac{d(x,p)}{u_{\text{T}}}\bigr)V_T(x)=λexp(u_Td(x,p)),
\]

\paragraph{Dictionary.}
Definition of V\_T(x) — V\_T(x)=λexp(d(x,p)u\_T)V\_T(x)=λ,exp l(-fracd(x,p)u\_T r)V\_T(x)=λexp(u\_Td(x,p))

\paragraph{Encyclopedia.}
Definition of V\_T(x) is a differential equation, written V\_T(x)=λexp(d(x,p)u\_T)V\_T(x)=λ,exp l(-fracd(x,p)u\_T r)V\_T(x)=λexp(u\_Td(x,p)). It relates the quantity to its derivatives, governing how the system evolves in space and time. It is built from λ, x, p, u\_T, V\_, u\_, defining V\_T(x). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
