\section*{ID8573: Definition of S(T)+S(A)+S(M)−S(total)}
\paragraph{Metadata.}
PiID: 2909517028352 | RTEID: RTE:P33290.8629:T4.5876 | UUID: 14bb401e-35eb-5279-bf53-663f2cd2b7f9

\paragraph{Canonical Statement.}
54] 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZATION Canonical Statutory Formula: \$fcarrier \$ = \$vs \$ \$λ ≈ 17.2 \$ kHz \$=⇒ \$ Phase-Lock with \$Γ̂up \$ Formal Technical Dissertation: Formalizes the acoustic driver frequency. 17.2 kHz acts as a sub-harmonic of the \$Γ̂up \$ refresh rate, creating the "Acoustic Coriolis" effect that twists vacuum flow near the TZP for rectification. Source: [ID 1055] TOROIDAL FLUX-GATING (TRIPARTITE) Canonical Statutory Formula: \$I(T \$ : \$A :M) \$ = \$S(T )+S(A)+S(M)−S(total) =⇒ Res(TZP \$ ) Formal Technical Dissertation: Daniel Alexander Trawin 18 Trawin Zero Point Opera Omnia Pomerium Internum Formalizes the segregation of vacuum flux into Temporal, Atemporal, and Mediator channels. This architecture allows independent optimization of energy extraction and information processing while satisfying thermodynamic bounds. Source: [ID 1056] BERRY PHASE TOMOGRAPHY (ATEMPORAL REA

\paragraph{Canonical Equation.}
\[
S(T )+S(A)+S(M)−S(total) =⇒ Res(TZP
\]

\paragraph{Dictionary.}
Definition of S(T)+S(A)+S(M)−S(total) — S(T )+S(A)+S(M)−S(total) =⇒ Res(TZP

\paragraph{Encyclopedia.}
Definition of S(T)+S(A)+S(M)−S(total) is an algebraic definition, written S(T )+S(A)+S(M)−S(total) =⇒ Res(TZP. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R, s, T, Z, P, defining S(T )+S(A)+S(M)−S(total). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
