\section*{ID9351: Definition of (Γ)}
\paragraph{Metadata.}
PiID: 0372798394004 | RTEID: RTE:P36312.0096:T3.2824 | UUID: 69a49be6-6f63-574e-bcc8-cc13d512d205

\paragraph{Canonical Statement.}
te Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0001] Node registry\_id\_0002 Support Titles Encircling Loop Condition; Lemniscatic Homotopy; TZP Self-Intersection Test Handle A loop class around the TZP that cannot be deformed into a figure-eight with a singular crossing would falsify the axiom. Canonical Equation Links \$Γ⊂𝑀,\$ Wind𝑝 \$(Γ)=1 Γ∼Λ Λ(0)=Λ(1/2)=𝑝\$ [ID 0003] Dimensional Ambiguity at TZP TZPID ID0003 UUID f5f9715a-3ac7-559c-a109-4c47042303f3 Type Axiom Scale dimensional LOC Classification Working routing: QA611.4 dimension theory; QC gravitation foundations arXiv Classification Primary: math-ph Cross-list: gr-qc, hep-th Canonical Statement At the Trawin Zero Point, dimension is not forced to stay on a single branch. The local topological dim

\paragraph{Canonical Equation.}
\[
(Γ)=1 Γ∼Λ Λ(0)=Λ(1/2)=𝑝
\]

\paragraph{Dictionary.}
Definition of (Γ) — (Γ)=1 Γ∼Λ Λ(0)=Λ(1/2)=𝑝

\paragraph{Encyclopedia.}
Definition of (Γ) is an algebraic definition, written (Γ)=1 Γ∼Λ Λ(0)=Λ(1/2)=𝑝. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
