\tzpanchor{0967}
\tzpentryheader{0967}{BIJECTIVE MAPPING VERIFICATION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{bfc3f150-42fa-5818-8386-0172a811f755}}\\
\textbf{PiID} & \tzpcode{0661300192787} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{974}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3685.1778 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{06.0720 rad}\\
\textbf{TZPID} & \tzpcode{ID0967} & \textbf{Node Dependencies}\quad \tzpidref{0966}\\
\textbf{Registry} & \tzpcode{registry\_id\_0967} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
forall y in A, exists! x in B : f(x) = y implies |Unique(f(B))| equiv |B|

\tzpsection{Canonical Equation}
\[
(x^2 + y^2)^2 = 2a^2(x^2 - y^2)
\]
\[
mathbf{v}(p) = 0, \quad  abla \mathbf{v}(p)  eq 0, \quad \text{det}(J_p) \equiv 0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $v$: velocity, flow speed, or auxiliary comparison variable.
    \item $J_p$: source equation symbol.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $J$: source equation symbol.
    \item $t(J_p)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0967 generated source Wolfram model *)
ClearAll[K0967, Cr0967, T, R, A, W, I, N];
eq0967$1 = HoldForm[(x^2 + y^2)^2 == 2*a^2*(x^2 - y^2)];
eq0967$2 = HoldForm[TZPSequence[mathbf[v]*p == 0, abla*v[p]*eq0, JP*equiv0]];

K0967 = HoldForm[{eq0967$1, eq0967$2}];

N = "normalized TRAWIN closure object for BIJECTIVE MAPPING VERIFICATION";
I = "BIJECTIVE MAPPING VERIFICATION integration/comparison layer";
W = "BIJECTIVE MAPPING VERIFICATION wave or operator carrier";
A = "BIJECTIVE MAPPING VERIFICATION admissible action/amplitude condition";
R = "BIJECTIVE MAPPING VERIFICATION rotation/curl preservation layer";
T = "BIJECTIVE MAPPING VERIFICATION local source condition";

Cr0967[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0967 = Cr0967[K0967];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ BIJECTIVE MAPPING VERIFICATION local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ BIJECTIVE MAPPING VERIFICATION rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ BIJECTIVE MAPPING VERIFICATION admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ BIJECTIVE MAPPING VERIFICATION wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ BIJECTIVE MAPPING VERIFICATION integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for BIJECTIVE MAPPING VERIFICATION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0967] BIJECTIVE MAPPING VERIFICATION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
(x^2 + y^2)^2 = 2a^2(x^2 - y^2)
\]
\[
mathbf{v}(p) = 0, \quad  abla \mathbf{v}(p)  eq 0, \quad \text{det}(J_p) \equiv 0
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( mathbf{v}(p) = 0, \quad abla \mathbf{v}(p) eq 0, \quad \text{det}(J_p) \equiv 0 \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. Interpreted through TRAWIN, the equation functions as the mapping carrier for the entry’s information content. According to CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors BIJECTIVE MAPPING VERIFICATION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
(x^2 + y^2)^2 = 2a^2(x^2 - y^2)
\]
\[
mathbf{v}(p) = 0, \quad  abla \mathbf{v}(p)  eq 0, \quad \text{det}(J_p) \equiv 0
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0967] BIJECTIVE MAPPING VERIFICATION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
BIJECTIVE MAPPING VERIFICATION is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} forall y in A, exists! x in B : f(x) = y implies |Unique(f(B))| equiv |B|. \textbf{Contextual meaning:} The entry reads BIJECTIVE MAPPING VERIFICATION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, BIJECTIVE MAPPING VERIFICATION is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: (x to the power 2 + y to the power 2) to the power 2 = 2a to the power 2(x to the power 2 - y to the power 2); mathbf v (p) = 0, abla v (p) eq 0, det (J sub p) equiv 0; and \$(x to the power 2 + y to the power 2) to the power 2 = 2a to the power 2(x to the power 2 - y to the power 2). Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Symmetrical Function Auditing}: The rigorous mathematical proof that every single switch in the control room is wired to exactly one magnet, and every magnet is wired to exactly one switch.
\item \textbf{Reversible-Logic Confirmation}: The terrifying check ensuring that if the computer knows how to spin the reactor up, it also mathematically knows exactly how to spin it back down.
\item \textbf{Zero-Collision State Mapping}: The absolute guarantee that two completely different emergencies will never accidentally trigger the exact same warning alarm.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0967]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0967].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0967] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont BIJECTIVE MAPPING VERIFICATION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} BIJECTIVE MAPPING VERIFICATION is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``BIJECTIVE MAPPING VERIFICATION is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0967].
\par\endgroup
\vfill
\endgroup
\endgroup
