\section*{ID7692: Immediate Next Steps I Can Do for You Now (Pick Any; I’ll Do It Immediately): J\_n\textasciicircum{}2}
\paragraph{Metadata.}
PiID: 1071257012668 | RTEID: RTE:P29869.7442:T5.2339 | UUID: 09455730-4ed0-5698-9e2f-64efd7a2d5b7

\paragraph{Canonical Statement.}
- 1) **Compute and show** the κ locations where \textbackslash{}(|J\_6(\textbackslash{}kappa)|\textbackslash{}) is maximized (and show a plot of \textbackslash{}(J\_n\textasciicircum{}2\textbackslash{}) for n=0…10) — so you get the concrete “magic κ” values. *(I attempted this but the analysis tool hiccupped; I can retry if you want.)* - 2) **Make a full notebook** that: (a) scans κ and plots Bessel weights, (b) runs a 2D Kuramoto+Bessel creation simulation, (c) computes emergent density and a proxy potential, and (d) exports figures for cymatic-like patterns. - 3) **Design a realistic dusty-plasma lab protocol** you can try or collaborate on (equipment, parameter ranges, diagnostics). - 4) **Back-of-envelope numbers** calculating the amount of per-event mass/momentum needed to approach Newtonian gravity on small scales (plausibility bound).

\paragraph{Canonical Equation.}
\[
J_n^2
\]

\paragraph{Dictionary.}
Relation: J\_n\textasciicircum{}2

\paragraph{Encyclopedia.}
Immediate Next Steps I Can Do for You Now (Pick Any; I’ll Do It Immediately): J\_n\textasciicircum{}2 is a symbolic expression, written J\_n\textasciicircum{}2. It introduces a symbol or relation used elsewhere in the framework. It is built from J\_n. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
