\section*{ID7430: Key Numeric Results (Final Order Parameter R After 50 Years): k\_0: k\_0=0.5}
\paragraph{Metadata.}
PiID: 8181152843667 | RTEID: RTE:P28852.3400:T3.5575 | UUID: acfc9a9f-8089-5883-8435-362197c2ee31

\paragraph{Canonical Statement.}
Interpretation: with the particular physically-inspired coupling matrix and our normalization, small-to-moderate coupling strengths do **not** drive global phase-locking; you see only modest changes in coherence. At one intermediate scale (here \textbackslash{}(k\_0=0.5\textbackslash{})) the system showed a *higher* coherence (r ≈ 0.54), indicating partial clustering can occur for certain parameter regimes. But behavior is non-monotonic with k0 because (1) our coupling matrix is strongly heterogeneous (a few pairs dominate), and (2) natural frequencies span many orders (retrograde Venus and very fast gas-giant spins), so competing tendencies appear.

\paragraph{Canonical Equation.}
\[
k_0=0.5
\]

\paragraph{Dictionary.}
Interpretation: with the particular physically-inspired coupling matrix and our normalization, small-to-moderate coupling strengths do not drive global phase-locking; you see only modest changes in coherence.

\paragraph{Encyclopedia.}
Key Numeric Results (Final Order Parameter R After 50 Years): k\_0: k\_0=0.5 is an algebraic definition, written k\_0=0.5. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
