\tzpanchor{0147}
\tzpentryheader{0147}{Bridge-Flip Cancellation Operator}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{fb437664-b6b4-5e3d-9dec-5e86776e5229}}\\
\textbf{PiID} & \tzpcode{1284811174502} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{154}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{570.8336 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.9406 rad}\\
\textbf{TZPID} & \tzpcode{ID0147} & \textbf{Node Dependencies}\quad \tzpidref{0146}\\
\textbf{Registry} & \tzpcode{registry\_id\_0147} & \textbf{Scale}\quad Gaussian-window bridge annihilation event\\
\textbf{LOC Classification} & QA371 signal operators & QC20 wave phenomena\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: nlin.PS, physics.class-ph & \\
\textbf{Primary Support} & Flip Phase & Cancellation Signal\\
\textbf{Closure Support} & Local Amplitude Null & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
When the bridge tone is inserted with a phase flip ($\phi_3 = \pi$) within the Gaussian window, the bridge locally cancels one of the carriers, causing temporary local annihilation of amplitude.

\tzpsection{Canonical Equation}
\[
\phi_3=\pi
\]
\[
s_{\mathrm{flip}}(t)=g(t)\bigl(s_1(t)-s_{\mathrm{bridge}}(t)\bigr)
\]
\[
A_{\mathrm{loc}}(t)\approx 0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\phi_3$: flux, phase, or topological map term in the source equation.
    \item $\pi$: source equation symbol.
    \item $s_{\mathrm{flip}}(t)$: source equation symbol.
    \item $s_1(t)$: source equation symbol.
    \item $s_{\mathrm{bridge}}(t)$: source equation symbol.
    \item $A_{\mathrm{loc}}(t)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0147 generated source Wolfram model *)
ClearAll[K0147, Cr0147, T, R, A, W, I, N];
eq0147$1 = HoldForm[phi3 == Pi];
eq0147$2 = HoldForm[sFlip[t] == g[t]*(s1[t] - sBridge[t])];
eq0147$3 = HoldForm[ALoc[t] == 0];

K0147 = HoldForm[{eq0147$1, eq0147$2, eq0147$3}];

N = "normalized TRAWIN closure object for Bridge-Flip Cancellation Operator";
I = "Local Amplitude Null integration/comparison layer";
W = "Cancellation Signal wave or operator carrier";
A = "Flip Phase admissible action/amplitude condition";
R = "Cancellation Signal rotation/curl preservation layer";
T = "Flip Phase local source condition";

Cr0147[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0147 = Cr0147[K0147];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Flip Phase local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Cancellation Signal rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Flip Phase admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Cancellation Signal wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Local Amplitude Null integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Bridge-Flip Cancellation Operator.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0147] Bridge-Flip Cancellation Operator}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\phi_3=\pi
\]
\[
s_{\mathrm{flip}}(t)=g(t)\bigl(s_1(t)-s_{\mathrm{bridge}}(t)\bigr)
\]
\[
A_{\mathrm{loc}}(t)\approx 0
\]

\paragraph{Primary Derivation.}
The identity \( \phi_3=\pi \) is an operator relation. Applying the operator to the relevant function and using its algebraic properties (such as linearity, commutators, or derivative rules) leads to the displayed equality.
\paragraph{Equation Type.}
This statement is classified as a operator relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. Within the TRAWIN framework, the equation functions as the operator-level carrier for the entry’s information content. According to CHL, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Bridge-Flip Cancellation Operator by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Flip Phase}\par
\[
\phi_3=\pi
\]
\noindent This supplies the discrete inversion needed for local cancellation.\par
\noindent\textbf{2. Cancellation Signal}\par
\[
s_{\mathrm{flip}}(t)=g(t)\bigl(s_1(t)-s_{\mathrm{bridge}}(t)\bigr)
\]
\noindent This constructs the actual windowed destructive-interference signal.\par
\noindent\textbf{3. Local Amplitude Null}\par
\[
A_{\mathrm{loc}}(t)\approx 0
\]
\noindent This closes the progression by recording the annihilation effect at the centre of the event.\par

\clearpage
\noindent\textbf{[ID 0147] Bridge-Flip Cancellation Operator}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Bridge-Flip Cancellation Operator is a Operator. When the bridge tone is inserted with a phase flip (   =  ) within the Gaussian window, the bridge locally cancels one of the carriers, causing temporary local annihilation of amplitude.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} When the bridge tone is inserted with a phase flip (   =  ) within the Gaussian window, the bridge locally cancels one of the carriers, causing temporary local annihilation of amplitude.
\textbf{Contextual meaning:} Mechanical and electrical forces separate ions by mass, leading to radial stratification and persistent charge gradients.
\textbf{Derivable consequences:} Mass dependent separation; creation of internal electric fields; synergy with chromatic ion sorting; design of vortex batteries.
\textbf{Lemma support:} When the bridge tone is inserted with a phase flip (   =  ) within the Gaussian window, the bridge locally cancels one of the carriers, causing temporary local annihilation of amplitude.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Measure radial ion concentration profiles under combined acceleration and oscillating charge; confirm heavier ions accumulate at the centre. ID 147: Bridge Flip Cancellation Operator

\tzpsection{Equation Grounding}
When the bridge tone is inserted with a phase flip (   =  ) within the Gaussian window, the bridge locally cancels one of the carriers, causing temporary local annihilation of amplitude.

\tzpsection{Interpretive Role}
Mechanical and electrical forces separate ions by mass, leading to radial stratification and persistent charge gradients.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Flip Phase}: The supply of the discrete inversion needed for local cancellation.
\item \textbf{Cancellation Signal}: The construction of the actual windowed destructive-interference signal.
\item \textbf{Local Amplitude Null}: The recording of the annihilation effect at the centre of the event.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0147]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0147_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0147] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Bridge-Flip Cancellation Operator}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} when the bridge tone is inserted with a phase flip (₃ = ) within the Gaussian
window, the bridge locally cancels one of the carriers, causing t...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Bridge-Flip Cancellation Operator is valid when the stated operator maps admissible
inputs into the declared target class.''\\
\textbf{Proof:} The source statement is read as an operator or transformation. The proof obligation is
type preservation: admissible inputs must land in the target object without breaking the
stated constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- operator-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0147_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
