\tzpanchor{0320}
\tzpentryheader{0320}{Oscillatory Boundary Field Configuration}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{aab0a55e-56eb-5646-93a6-788f6f292d57}}\\
\textbf{PiID} & \tzpcode{4881520920962} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{327}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1242.6311 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.0475 rad}\\
\textbf{TZPID} & \tzpcode{ID0320} & \textbf{Node Dependencies}\quad \tzpidref{0319}\\
\textbf{Registry} & \tzpcode{registry\_id\_0320} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Boundary Forcing & Angular Periodicity\\
\textbf{Closure Support} & Radial Carrier & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
On the surface of a spherical shell of radius $R$, partitioned into tessellated domains $\Omega_{+}$ and $\Omega_{-}$ by angular coordinates $(\theta,\phi)$, impose the radial boundary field

\tzpsection{Canonical Equation}
\[ B_{\mathrm{bnd}}(\theta,\phi,t) = B_{0}\, \operatorname{sgn}\!\bigl(\sin(n_{\theta}\theta)\sin(n_{\phi}\phi)\bigr) e^{i\omega t}\,\hat r, \] where $n_{\theta},n_{\phi}\in\mathbb{Z}$ set the periodicity. This oscillatory boundary condition drives interference patterns inside the enclosure.

\[
B_{\mathrm{bnd}}(\theta,\phi,t)=B_0\,\operatorname{sgn}\!\bigl(\sin(n_{\theta}\theta)\sin(n_{\phi}\phi)\bigr)e^{i\omega t}\,\hat r
\]
\[
n_{\theta},n_{\phi}\in \mathbb{Z}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $B_{\mathrm{bnd}}$: source equation symbol.
    \item $\theta$: phase angle or local angular coordinate.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $t$: source equation symbol.
    \item $B_{0}$: source equation symbol.
    \item $n_{\theta}$: source equation symbol.
    \item $n_{\phi}$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
    \item $Z$: source equation symbol.
    \item $\pi$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0320 generated source Wolfram model *)
ClearAll[K0320, Cr0320, T, R, A, W, I, N];
eq0320$1 = HoldForm[BBnd[theta, phi, t] == B0*sgn[Sin[nThetatheta]*Sin[nPhiphi]]*Exp[I*omega*t]*hat*r];
eq0320$2 = HoldForm[BBnd[theta, phi, t] == B0*sgn[Sin[nThetatheta]*Sin[nPhiphi]]*Exp[I*omega*t]*hat*r];
eq0320$3 = HoldForm[Element[TZPSequence[nTheta, nPhi], Z]];
eq0320$4 = HoldForm[TZPSequence[Deltatheta == (2*Pi)/nTheta, Deltaphi == (2*Pi)/nPhi]];

K0320 = HoldForm[{eq0320$1, eq0320$2, eq0320$3, eq0320$4}];

N = "normalized TRAWIN closure object for Oscillatory Boundary Field Configuration";
I = "Radial Carrier integration/comparison layer";
W = "Angular Periodicity wave or operator carrier";
A = "Boundary Forcing admissible action/amplitude condition";
R = "Angular Periodicity rotation/curl preservation layer";
T = "Boundary Forcing local source condition";

Cr0320[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0320 = Cr0320[K0320];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Boundary Forcing local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Angular Periodicity rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Boundary Forcing admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Angular Periodicity wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Radial Carrier integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Oscillatory Boundary Field Configuration.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0320] Oscillatory Boundary Field Configuration}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mathcal{L}_U
=
\frac{c^4}{16\pi G}R[g]
+
\mathcal{L}_{QFT}[\Psi,A_\mu]
+
\mathcal{L}_{topo}[A_\mu]
+
\mathcal{L}_{info}[\Phi]
+
\mathcal{L}_{bio}[\Xi].
\end{equation}

\paragraph{Primary Derivation.}
A unified Trawinistic action density is constructed by summing distinct physical sectors.

The gravitational sector is given by the Einstein-Hilbert density:

\begin{equation}
\mathcal{L}_{grav}
=
\frac{c^4}{16\pi G}R[g].
\end{equation}

The quantum field contribution is:

\begin{equation}
\mathcal{L}_{QFT}[\Psi,A_\mu].
\end{equation}

The topological contribution accounts for winding, helicity, and gauge structure:

\begin{equation}
\mathcal{L}_{topo}[A_\mu].
\end{equation}

The information-field sector is:

\begin{equation}
\mathcal{L}_{info}[\Phi].
\end{equation}

The biological or organized-complexity sector is:

\begin{equation}
\mathcal{L}_{bio}[\Xi].
\end{equation}

Adding all components gives:

\begin{equation}
\boxed{
\mathcal{L}_U
=
\frac{c^4}{16\pi G}R[g]
+
\mathcal{L}_{QFT}[\Psi,A_\mu]
+
\mathcal{L}_{topo}[A_\mu]
+
\mathcal{L}_{info}[\Phi]
+
\mathcal{L}_{bio}[\Xi].
}
\end{equation}

\paragraph{Interpretation.}
This equation defines a layered Lagrangian architecture: gravity, quantum fields, topology, information, and biological organization are treated as coupled sectors of one Trawinistic action density.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Oscillatory Boundary Field Configuration by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Boundary Forcing}\par
\[
B_{\mathrm{bnd}}(\theta,\phi,t)=B_0\,\operatorname{sgn}\!\bigl(\sin(n_{\theta}\theta)\sin(n_{\phi}\phi)\bigr)e^{i\omega t}\,\hat r
\]
\noindent This fixes the oscillatory radial boundary field imposed on the tessellated spherical shell.\par
\noindent\textbf{2. Angular Periodicity}\par
\[
n_{\theta},n_{\phi}\in \mathbb{Z}
\]
\noindent This identifies the integer angular periodicities that govern the sign-flipping boundary pattern.\par
\noindent\textbf{3. Radial Carrier}\par
\[
Delta\theta=\frac{2\pi}{n_{\theta}},\qquad \Delta\phi=\frac{2\pi}{n_{\phi}}
\]
\noindent This closes the entry by relating the tessellation cell sizes to the chosen angular mode counts.\par

\clearpage
\noindent\textbf{[ID 0320] Oscillatory Boundary Field Configuration}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Oscillatory Boundary Field Configuration is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} On the surface of a spherical shell of radius R, partitioned into tessellated domains Omega sub + and Omega sub - by angular coordinates (theta,phi), impose the radial boundary field B sub bnd (theta,phi,t) = B sub 0 operatorname sgn bigl(sin(n sub theta theta)sin(n sub phi phi)bigr) e to the power iomega t hat r, where n sub theta ,n sub phi inmathbb Z set the periodicity. This oscillatory boundary condition drives interference patterns inside the enclosure. \textbf{Contextual meaning:} The entry reads Oscillatory Boundary Field Configuration as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the oscillatory boundary forcing as an actual angular field law instead of corrupted sign-pattern prose. \textbf{Lemma support:} Boundary Forcing; Angular Periodicity; Radial Carrier.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This equation defines a layered Lagrangian architecture: gravity, quantum fields, topology, information, and biological organization are treated as coupled sectors of one Trawinistic action density. \% ========================================================= \% QUATERNARY DERIVATION LAYER -- ID 0321 TO ID 0325 \% =========================================================.

\tzpsection{Equation Grounding}
Equation anchors: B sub bnd (theta,phi,t)=B sub 0 operatorname sgn bigl(sin(n sub theta theta)sin(n sub phi phi)bigr)e to the power iomega t hat r; n sub theta ,n sub phi in mathbb Z; and Deltatheta=ratio 2pi n sub theta ,; Deltaphi=ratio 2pi n sub phi. Proof route: show that the stated oscillatory boundary field is periodic with the stated angular mode counts and tessellation scales. Formalization route: prove that the integer periodicities determine the stated angular cell widths and boundary sign pattern.

\tzpsection{Interpretive Role}
The entry now states the oscillatory boundary forcing as an actual angular field law instead of corrupted sign-pattern prose.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Alternating-Sign Spherical Forcing}: The spatial patterning of boundary conditions where adjacent tessellation cells carry inverse charge or phase.
\item \textbf{Radial Standing-Wave Constraints}: The dynamic boundary operators enforcing strict nodes and antinodes along the outer perimeter of a resonant cavity.
\item \textbf{Resonant Tessellation Dynamics}: The angular discretization strategy locking specific vibration frequencies to the geometric size of surface tiles.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0320]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0320_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0320] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Oscillatory Boundary Field Configuration}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} on the surface of a spherical shell of radius R, partitioned into tessellated domains
\_+ and \_- by angular coordinates (,), impose the radi...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Oscillatory Boundary Field Configuration is valid as a synchronization criterion under
the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0320_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
