\section*{ID8791: CONSISTENCY FIXED-POINT MAP Canonical Statutory Formula: ρ\_CTC}
\paragraph{Metadata.}
PiID: 8602515227429 | RTEID: RTE:P34137.4053:T5.9825 | UUID: ba4d4c03-a283-557e-93ff-e98a59a165e9

\paragraph{Canonical Statement.}
[ID 1167] CONSISTENCY FIXED-POINT MAP Canonical Statutory Formula: \$\textbackslash{}rho\_\{CTC\} = \textbackslash{}text\{Tr\} \{CV\} [ U (\textbackslash{}rho \{past\} \textbackslash{}otimes \textbackslash{}rho\_\{CTC\}) U\textasciicircum{}\textbackslash{}dagger ] \textbackslash{}implies \textbackslash{}Phi(\textbackslash{}rho) = \textbackslash{}rho\$ Formal Technical Dissertation: The algorithmic solver for the Deutsch CTC model. It finds the fixed-point density matrix \$\textbackslash{}rho\_\{CTC\}\$ that remains invariant after interacting with the past, ensuring that the information sent back in time generates the exact future state from which it was sent. Source: [6]

\paragraph{Canonical Equation.}
\[
\rho_{CTC} = \text{Tr} {CV} [ U (\rho {past} \otimes \rho_{CTC}) U^\dagger ] \implies \Phi(\rho) = \rho
\]

\paragraph{Dictionary.}
CONSISTENCY FIXED-POINT MAP Canonical Statutory Formula: \$ \_CTC = Tr CV [ U ( past \_CTC) U\textasciicircum{} ] ( ) = \$ Formal Technical Dissertation: The algorithmic solver for the Deutsch CTC model.

\paragraph{Encyclopedia.}
CONSISTENCY FIXED-POINT MAP Canonical Statutory Formula: ρ\_CTC is an expectation / trace over state, written ρ\_CTC = Tr CV [ U (ρ past ⊗ ρ\_CTC) U\textasciicircum{}† ] ⟹ Φ(ρ) = ρ. It is computed as an expectation value or trace over a quantum state, producing an observable. It is built from ρ, Φ, C, V, U, p, defining ρ\_CTC. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
