\tzpanchor{0305}
\tzpentryheader{0305}{Tesseract Projection and Four-Dimensional Addressing}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{69166f18-fb1a-593f-b40e-66d2b4879745}}\\
\textbf{PiID} & \tzpcode{7006606315588} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{312}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1184.3827 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9515 rad}\\
\textbf{TZPID} & \tzpcode{ID0305} & \textbf{Node Dependencies}\quad \tzpidref{0304}\\
\textbf{Registry} & \tzpcode{registry\_id\_0305} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Quaternion Carrier & Stereographic Projection\\
\textbf{Closure Support} & Tesseract Address Set & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The tesseract projection stage converts binary blob-matrix indices into geometric directions on the sphere by using stereographic projection from S3S\^{}3S3.

\tzpsection{Canonical Equation}
\[
q=(q_0,q_1,q_2,q_3)\in S^3,\qquad q_0^2+q_1^2+q_2^2+q_3^2=1
\]
\[
pi_{\mathrm{stereo}}(q)=\frac{(q_0,q_1,q_2)}{1-q_3}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $q_0$: source equation symbol.
    \item $q_1$: source equation symbol.
    \item $q_2$: source equation symbol.
    \item $q_3$: source equation symbol.
    \item $S^3$: three-sphere source domain.
    \item $V_{\mathrm{tes}}$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0305 generated source Wolfram model *)
ClearAll[K0305, Cr0305, T, R, A, W, I, N];
eq0305$1 = HoldForm[Element[q == Tuple[q0, q1, q2, q3], TZPSequence[S^3, q0^2 + q1^2 + q2^2 + q3^2 == 1]]];
eq0305$2 = HoldForm[piStereo[q] == Tuple[q0, q1, q2]/(1 - q3)];
eq0305$3 = HoldForm[VTes == {Tuple[PlusMinus1, PlusMinus1, PlusMinus1, PlusMinus1]} Subset R^4];

K0305 = HoldForm[{eq0305$1, eq0305$2, eq0305$3}];

N = "normalized TRAWIN closure object for Tesseract Projection and Four-Dimensional Addressing";
I = "Tesseract Address Set integration/comparison layer";
W = "Stereographic Projection wave or operator carrier";
A = "Quaternion Carrier admissible action/amplitude condition";
R = "Stereographic Projection rotation/curl preservation layer";
T = "Quaternion Carrier local source condition";

Cr0305[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0305 = Cr0305[K0305];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Quaternion Carrier local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Stereographic Projection rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Quaternion Carrier admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Stereographic Projection wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Tesseract Address Set integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Tesseract Projection and Four-Dimensional Addressing.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0305] Tesseract Projection and Four-Dimensional Addressing}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
For any diffeomorphism $\phi:M\to M$ preserving the symmetry group of $M$,

\begin{equation}
\phi(p)=p .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi:M\to M$ be a diffeomorphism preserving the symmetry structure of the manifold. Since $p$ is defined as the unique point where the metric degeneracy occurs,

\begin{equation}
\det(g)\big|_p=0 .
\end{equation}

If $\phi$ preserves the Trawinistic structure, then it must preserve the degeneracy locus:

\begin{equation}
\det(g)\big|_{\phi(p)}=0 .
\end{equation}

Because $p$ is unique, the only point satisfying this condition is $p$ itself. Therefore:

\begin{equation}
\phi(p)=p .
\end{equation}

\paragraph{Interpretation.}
The TZP is invariant under all structure-preserving transformations. It is therefore a fixed point of the system.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Tesseract Projection and Four-Dimensional Addressing by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Quaternion Carrier}\par
\[
q=(q_0,q_1,q_2,q_3)\in S^3,\qquad q_0^2+q_1^2+q_2^2+q_3^2=1
\]
\noindent This fixes the unit-quaternion carrier that supplies the four-dimensional address space.\par
\noindent\textbf{2. Stereographic Projection}\par
\[
pi_{\mathrm{stereo}}(q)=\frac{(q_0,q_1,q_2)}{1-q_3}
\]
\noindent This maps the quaternion carrier into the three-dimensional stereographic chart used by the directory.\par
\noindent\textbf{3. Tesseract Address Set}\par
\[
V_{\mathrm{tes}}=\{(\pm1,\pm1,\pm1,\pm1)\}\subset \mathbb{R}^4
\]
\noindent This closes the entry by identifying the tesseract vertex set that the addressing scheme indexes.\par

\clearpage
\noindent\textbf{[ID 0305] Tesseract Projection and Four-Dimensional Addressing}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Tesseract Projection and Four-Dimensional Addressing is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The tesseract projection stage converts binary blob-matrix indices into geometric directions on the sphere by using stereographic projection from S3S 3S3. \textbf{Contextual meaning:} The entry reads Tesseract Projection and Four-Dimensional Addressing as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the quaternion-to-stereographic-to-tesseract chain explicitly instead of leaving broken prose fragments in display math. \textbf{Lemma support:} Quaternion Carrier; Stereographic Projection; Tesseract Address Set.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP is invariant under all structure-preserving transformations. It is therefore a fixed point of the system. \% ========================================================= \% QUATERNARY DERIVATION LAYER -- ID 0306 TO ID 0310 \% =========================================================.

\tzpsection{Equation Grounding}
Equation anchors: q=(q sub 0,q sub 1,q sub 2,q sub 3)in S to the power 3,; q sub 0 to the power 2+q sub 1 to the power 2+q sub 2 to the power 2+q sub 3 to the power 2=1; pi sub stereo (q)=ratio (q sub 0,q sub 1,q sub 2) 1-q sub 3; and V sub tes = (pm1,pm1,pm1,pm1) subset mathbb R to the power 4. Proof route: show that the stated stereographic projection consistently maps the unit-quaternion carrier into the three-dimensional address chart while preserving the tesseract indexing frame. Formalization route: prove that the stereographic address map is well defined on the unit-quaternion carrier away from the projection pole and supports the stated tesseract vertex addressing.

\tzpsection{Interpretive Role}
The entry now states the quaternion-to-stereographic-to-tesseract chain explicitly instead of leaving broken prose fragments in display math.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Stereographic Hypercube Mapping}: The dimensional reduction technique projecting a 4D spatial lattice into a 3D computational volume.
\item \textbf{Quaternary Vertex Indexing}: The coordinate logic organizing discrete states into a 16-node boolean hypercube structure.
\item \textbf{Unit Quaternion Address Space}: The representation of spatial coordinates as hypersphere points governed by non-commutative rotational algebras.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0305]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0305_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0305] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Tesseract Projection and Four-Dimensional Addressing}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the tesseract projection stage converts binary blob-matrix indices into geometric
directions on the sphere by using stereographic projection from S...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Tesseract Projection and Four-Dimensional Addressing is valid as a tensorial/geometric
statement when the stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0305_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
