\tzpanchor{0457}
\tzpentryheader{0457}{Resonance Hold-State Maintenance}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{c5ec1df3-8ae4-5ab4-9732-e169dbcd56c2}}\\
\textbf{PiID} & \tzpcode{7996274956735} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{464}\\
\textbf{RTEID} & \textbf{Manifest row}\quad \tzpcode{not listed} & \textbf{Source}\quad \tzpcode{Coordinate Manifest}\\
\textbf{TZPID} & \tzpcode{ID0457} & \textbf{Node Dependencies}\quad \tzpidref{0456}\\
\textbf{Registry} & \tzpcode{registry\_id\_0457} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Mode Quantization & Dispersion Law\\
\textbf{Closure Support} & Boundary Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 457 formalizes the collapse of superpositions for information readout. Quantum states acquired during extraction are measured, converting atemporal correlations into classical observational data. This readout is constrained by the Holevo bound, mapping the final 17.23 bits of information to the DAANSsphere axis. Tomographic Readout: Single shot quantum state tomography reconstructs the density matrix of extracted states. State Collapse: The measurement provides the data necessary for the next cycle's feedback adjustments.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
k_{\mathrm{n}} = \frac{n\pi}{L}
$
\end{adjustbox}
\]

\tzpsection{Canonical Equation Links}
\tzpequationlinks
  {k_{\mathrm{n}} = \frac{n\pi}{L}}
  {\omega_{\mathrm{n}} = v\,k_{\mathrm{n}}}
  {\Phi_{\mathrm{n}}|_{\partial\Omega}=0}

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $k_{\mathrm{n}}$: mode-indexed wavenumber.
    \item $n$: integer mode index.
    \item $\pi$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0457 generated source Wolfram model *)
ClearAll[K0457, Cr0457, T, R, A, W, I, N];
eq0457$1 = HoldForm[$kN == (nPi/L)*$];

K0457 = HoldForm[{eq0457$1}];

N = "normalized TRAWIN closure object for Resonance Hold-State Maintenance";
I = "Resonance Hold-State Maintenance integration/comparison layer";
W = "Resonance Hold-State Maintenance wave or operator carrier";
A = "Resonance Hold-State Maintenance admissible action/amplitude condition";
R = "Resonance Hold-State Maintenance rotation/curl preservation layer";
T = "Resonance Hold-State Maintenance local source condition";

Cr0457[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0457 = Cr0457[K0457];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Resonance Hold-State Maintenance local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Resonance Hold-State Maintenance rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Resonance Hold-State Maintenance admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Resonance Hold-State Maintenance wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Resonance Hold-State Maintenance integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Resonance Hold-State Maintenance.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0457] Resonance Hold-State Maintenance}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\begingroup\small
\paragraph{Primary Equations.}
\begin{equation}
\Delta(g_c)=0 .
\end{equation}

\begin{equation}
\xi \sim |g-g_c|^{-\nu}.
\end{equation}

\paragraph{Primary Derivation.}
Let $g$ be a control parameter and $g_c$ its critical value.  
A quantum phase transition occurs at zero temperature when the ground state changes non-analytically.

The critical point is identified by collapse of the spectral gap:

\begin{equation}
\Delta(g_c)=0 .
\end{equation}

Near the critical point, the correlation length diverges as a power law:

\begin{equation}
\boxed{
\xi \sim |g-g_c|^{-\nu}.
}
\end{equation}

\paragraph{Wolfram Form.}
\begin{verbatim}
Delta[gC] == 0
xi ~ Abs[g - gC]^(-nu)
\end{verbatim}

\paragraph{Interpretation.}
Quantum criticality is marked by gap closure and divergence of correlation length.
\endgroup

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Resonance Hold-State Maintenance by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
k_{\mathrm{n}} = \frac{n\pi}{L}
$
\end{adjustbox}
\]

\tzpsection{Canonical Equation Links}
\tzpequationlinks
  {k_{\mathrm{n}} = \frac{n\pi}{L}}
  {\omega_{\mathrm{n}} = v\,k_{\mathrm{n}}}
  {\Phi_{\mathrm{n}}|_{\partial\Omega}=0}
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0457] Resonance Hold-State Maintenance}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Resonance Hold-State Maintenance is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 457 formalizes the collapse of superpositions for information readout. Quantum states acquired during extraction are measured, converting atemporal correlations into classical observational data. This readout is constrained by the Holevo bound, mapping the final 17.23 bits of information to the DAANSsphere axis. Tomographic Readout: Single shot quantum state tomography reconstructs the density matrix of extracted states. State Collapse: The measurement provides the data necessary for the next cycle's feedback adjustments.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
k_{\mathrm{n}} = \frac{n\pi}{L}
$
\end{adjustbox}
\]

\tzpsection{Canonical Equation Links}
\tzpequationlinks
  {k_{\mathrm{n}} = \frac{n\pi}{L}}
  {\omega_{\mathrm{n}} = v\,k_{\mathrm{n}}}
  {\Phi_{\mathrm{n}}|_{\partial\Omega}=0}

\tzpsection{Technical Interpretation}
ID 457 formalizes the collapse of superpositions for information readout. Quantum states acquired during extraction are measured, converting atemporal correlations into classical observational data. This readout is constrained by the Holevo bound, mapping the final 17.23 bits of information to the DAANSsphere axis. Tomographic Readout: Single shot quantum state tomography reconstructs the density matrix of extracted states. State Collapse: The measurement provides the data necessary for the next cycle's feedback adjustments.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Resonance Hold-State Maintenance by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Resonance Hold-State Maintenance; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0457]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0457].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0457] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Resonance Hold-State Maintenance}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} Resonance Hold-State Maintenance is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Resonance Hold-State Maintenance is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0457].
\par\endgroup
\vfill
\endgroup
\endgroup
