\tzpanchor{0198}
\tzpentryheader{0198}{Spin Quantization from Hypersphere Twists}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e656afe0-dfb0-52ed-ba92-f8a49fbcb232}}\\
\textbf{PiID} & \tzpcode{9644288109756} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{205}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{768.8780 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.2669 rad}\\
\textbf{TZPID} & \tzpcode{ID0198} & \textbf{Node Dependencies}\quad \tzpidref{0197}\\
\textbf{Registry} & \tzpcode{registry\_id\_0198} & \textbf{Scale}\quad cosmic\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: gr-qc, math.DG & \\
\textbf{Primary Support} & Spin Quantization from Hypersphere Twists Carrier & Registry Source Route\\
\textbf{Closure Support} & Admissible Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The hypersphere's rotational symmetry requires spinors to acquire a minus sign upon full rotation, explaining the observed spin--statistics of fermions.

\tzpsection{Canonical Equation}
\[
\mathcal{C}_{0198} := \operatorname{TRAWIN}_{0198}
\]
\[
\operatorname{Source}_{0198}\longrightarrow \mathcal{C}_{0198},
\qquad
\operatorname{Admissible}_{\mathrm{TZP}}\!\left(\mathcal{C}_{0198}\right)=1
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{C}_{0198}$: source equation symbol.
    \item $\mathcal{K}_{0198}$: canonical registry object for entry ID 0198.
    \item $T$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $A$: source equation symbol.
    \item $W$: source equation symbol.
    \item $I$: source equation symbol.
    \item $N_{0198}$: source equation symbol.
    \item $S$: source equation symbol.
    \item $Z$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0198 generated source Wolfram model *)
ClearAll[K0198, Cr0198, T, R, A, W, I, N];
eq0198$1 = HoldForm[C0198 == TRAWIN0198];
eq0198$2 = HoldForm[TZPSequence[Source0198 -> C0198, AdmissibleTZP[C0198] == 1]];
eq0198$3 = HoldForm[Source0198 -> C0198];
eq0198$4 = HoldForm[AdmissibleTZP[C0198] == 1];

K0198 = HoldForm[{eq0198$1, eq0198$2, eq0198$3, eq0198$4}];

N = "normalized TRAWIN closure object for Spin Quantization from Hypersphere Twists";
I = "Admissible Closure integration/comparison layer";
W = "Registry Source Route wave or operator carrier";
A = "Spin Quantization from Hypersphere Twists Carrier admissible action/amplitude condition";
R = "Registry Source Route rotation/curl preservation layer";
T = "Spin Quantization from Hypersphere Twists Carrier local source condition";

Cr0198[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0198 = Cr0198[K0198];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Spin Quantization from Hypersphere Twists Carrier local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Registry Source Route rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Spin Quantization from Hypersphere Twists Carrier admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Registry Source Route wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Admissible Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Spin Quantization from Hypersphere Twists.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0198] Spin Quantization from Hypersphere Twists}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{C}_{0198} := \operatorname{TRAWIN}_{0198}
\]
\[
\operatorname{Source}_{0198}\longrightarrow \mathcal{C}_{0198},
\qquad
\operatorname{Admissible}_{\mathrm{TZP}}\!\left(\mathcal{C}_{0198}\right)=1
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \operatorname{Source}_{0198}\longrightarrow \mathcal{C}_{0198}, \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. In the TRAWIN reading, the equation functions as the mapping carrier for the entry’s information content. In CHL terms, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Spin Quantization from Hypersphere Twists by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Spin Quantization from Hypersphere Twists Carrier}\par
\[
\mathcal{C}_{0198} := \operatorname{TRAWIN}_{0198}
\]
\noindent This names the entry as a concrete carrier object in the TRAWIN registry.\par
\noindent\textbf{2. Registry Source Route}\par
\[
\operatorname{Source}_{0198}\longrightarrow \mathcal{C}_{0198}
\]
\noindent This connects the source record to the carrier so the entry remains traceable to its local registry file.\par
\noindent\textbf{3. Admissible Closure}\par
\[
\operatorname{Admissible}_{\mathrm{TZP}}\!\left(\mathcal{C}_{0198}\right)=1
\]
\noindent This closes the progression by stating that the carrier is admissible in the TZP frame once the source route is retained.\par

\clearpage
\noindent\textbf{[ID 0198] Spin Quantization from Hypersphere Twists}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Spin Quantization from Hypersphere Twists is a Structural Constraint  . The embedded U(1)U(1)U(1) gauge symmetry of the vacuum implies that each TZP fold carries a discrete integer charge; no other values are possible for that mode.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The embedded U(1)U(1)U(1) gauge symmetry of the vacuum implies that each TZP fold carries a discrete integer charge; no other values are possible for that mode.
\textbf{Contextual meaning:} The hypersphere's rotational symmetry requires spinors to acquire a minus sign upon full rotation, explaining the observed spin--statistics of fermions.  
\textbf{Derivable consequences:} Explains charge quantization; forbids fractional charges (except for composite objects); predicts topological charge conservation; ties the gauge group to particle creation.  
\textbf{Lemma support:} The embedded U(1)U(1)U(1) gauge symmetry of the vacuum implies that each TZP fold carries a discrete integer charge; no other values are possible for that mode.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Detection of elementary particles with non integer electric charge would falsify this entry. ID 198: Spin Quantization from Hypersphere Twists  

\tzpsection{Equation Grounding}
The embedded U(1)U(1)U(1) gauge symmetry of the vacuum implies that each TZP fold carries a discrete integer charge; no other values are possible for that mode.

\tzpsection{Interpretive Role}
The hypersphere's rotational symmetry requires spinors to acquire a minus sign upon full rotation, explaining the observed spin--statistics of fermions.  
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{angular momentum discretization hypersphere twists}: Alternate indexing phrase retained for Spin Quantization from Hypersphere Twists in the local registry context.
\item \textbf{angular momentum discretization geometric analogue}: Alternate indexing phrase retained for Spin Quantization from Hypersphere Twists in the local registry context.
\item \textbf{discretization terminology}: Alternate indexing phrase retained for Spin Quantization from Hypersphere Twists in the local registry context.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0198]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0198_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0198] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Spin Quantization from Hypersphere Twists}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the hypersphere's rotational symmetry requires spinors to acquire a minus sign upon full
rotation, explaining the observed spin--statistics of ferm...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Spin Quantization from Hypersphere Twists is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0198_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
