\section*{ID8475: ELSASSER ATTRACTOR LIMIT Canonical Statutory Formula: Λ}
\paragraph{Metadata.}
PiID: 4906617583441 | RTEID: RTE:P32910.3071:T3.9606 | UUID: 7e0347cc-b0d5-51d6-9420-6a033a2e4f57

\paragraph{Canonical Statement.}
[ID 1184] ELSASSER ATTRACTOR LIMIT Canonical Statutory Formula: \$\textbackslash{}Lambda = \textbackslash{}frac\{B\textasciicircum{}2\}\{\textbackslash{}mu\_0 \textbackslash{}rho \textbackslash{}eta \textbackslash{}omega\} \textbackslash{}to 1\$ Formal Technical Dissertation: Defines the universal stability criterion for all self-organizing magnetofluids. Whether in a laboratory liquid-sodium sphere or a galactic core, the system inevitably evolves toward an Elsasser number of exactly unity, representing a perfect equipartition between magnetic energy density and the Coriolis force. Source: [1], [4], [5]

\paragraph{Canonical Equation.}
\[
\Lambda = \frac{B^2}{\mu_0 \rho \eta \omega} \to 1
\]

\paragraph{Dictionary.}
ELSASSER ATTRACTOR LIMIT Canonical Statutory Formula: \$ = B\textasciicircum{}2 \_0 1\$ Formal Technical Dissertation: Defines the universal stability criterion for all self-organizing magnetofluids.

\paragraph{Encyclopedia.}
ELSASSER ATTRACTOR LIMIT Canonical Statutory Formula: Λ is an algebraic definition, written Λ = (B\textasciicircum{}2)/(μ\_0 ρ η ω) → 1. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from ρ, η, ω, B, defining Λ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
