\tzpanchor{0090}
\tzpentryheader{0090}{Laboratory $\leftrightarrow$ Astrophysical Structural Equivalence}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{ab54f12c-5502-5948-a467-e979f2e145f2}}\\
\textbf{PiID} & \tzpcode{3421170679821} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{97}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{349.4900 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.5759 rad}\\
\textbf{TZPID} & \tzpcode{ID0090} & \textbf{Node Dependencies}\quad \tzpidref{0085}\\
\textbf{Registry} & \tzpcode{registry\_id\_0090} & \textbf{Scale}\quad laboratory-to-astrophysical\\
\textbf{LOC Classification} & QC6.4 rotational analogues & QB460 structural astrophysics\\
\textbf{arXiv Classification} & Primary: physics.class-ph \quad Cross-list: astro-ph.SR, physics.plasm-ph & \\
\textbf{Primary Support} & Laboratory Invariant Set & Astrophysical Matching Condition\\
\textbf{Closure Support} & Scale Equivalence Map & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The scaling functor FFF maps laboratory gyromagnetic systems to astrophysical analogues by scaling lengths, times and field strengths while preserving dimensionless parameters like the Reynolds number and magnetic Reynolds number.

\tzpsection{Canonical Equation}
\[
\Pi_{k}^{\mathrm{lab}} = \Pi_{k}^{\mathrm{astro}}
\]
\[
F_{\mathrm{scale}} : \mathcal{S}_{\mathrm{lab}} \longrightarrow \mathcal{S}_{\mathrm{astro}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $F_{\mathrm{scale}}$: source equation symbol.
    \item $\mathcal{S}_{\mathrm{lab}}$: source equation symbol.
    \item $\mathcal{S}_{\mathrm{astro}}$: source equation symbol.
    \item $\mathcal{K}_{0090}$: canonical registry object for entry ID 0090.
    \item $\Pi_{k}$: source equation symbol.
    \item $P$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0090 generated source Wolfram model *)
ClearAll[K0090, Cr0090, T, R, A, W, I, N];
eq0090$1 = HoldForm[PiK^lab == PiK^astro];
eq0090$2 = HoldForm[Fscale[Slab] -> Sastro];
eq0090$3 = HoldForm[PiK^lab];

K0090 = HoldForm[{eq0090$1, eq0090$2, eq0090$3}];

N = "normalized TRAWIN closure object for Laboratory $\leftrightarrow$ Astrophysical Structural Equivalence";
I = "Scale Equivalence Map integration/comparison layer";
W = "Astrophysical Matching Condition wave or operator carrier";
A = "Laboratory Invariant Set admissible action/amplitude condition";
R = "Astrophysical Matching Condition rotation/curl preservation layer";
T = "Laboratory Invariant Set local source condition";

Cr0090[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0090 = Cr0090[K0090];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Laboratory Invariant Set local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Astrophysical Matching Condition rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Laboratory Invariant Set admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Astrophysical Matching Condition wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Scale Equivalence Map integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Laboratory \$\textbackslash{}leftrightarrow\$ Astrophysical Structural Equivalence.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0090] Laboratory $\leftrightarrow$ Astrophysical Structural Equivalence}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Invariant Matching Condition.}
\begin{equation}
\Pi_k^{\mathrm{lab}}
=
\Pi_k^{\mathrm{astro}} .
\end{equation}

\paragraph{Scale Equivalence Map.}
\begin{equation}
F_{\mathrm{scale}}:
\mathcal{S}_{\mathrm{lab}}
\longrightarrow
\mathcal{S}_{\mathrm{astro}} .
\end{equation}

\paragraph{Primary Derivation.}
Let $\Pi_k$ denote a dimensionless invariant governing a dynamical system.  
Laboratory and astrophysical systems are structurally comparable only when their governing invariant sets match:
\begin{equation}
\Pi_k^{\mathrm{lab}}
=
\Pi_k^{\mathrm{astro}} .
\end{equation}

A scale map then translates the laboratory realization into the astrophysical realization:
\begin{equation}
F_{\mathrm{scale}}:
\mathcal{S}_{\mathrm{lab}}
\to
\mathcal{S}_{\mathrm{astro}} .
\end{equation}

Thus,
\begin{equation}
\boxed{
\Xi_{\mathrm{eq}}
=
\mathrm{NormalizeTRAWIN}
\left(
\mathcal{S}_{\mathrm{lab}},
\mathcal{S}_{\mathrm{astro}},
F_{\mathrm{scale}},
\Pi_k
\right).
}
\end{equation}

\paragraph{Interpretation.}
Laboratory demonstrations become structurally meaningful for astrophysical systems only when the scale map preserves the relevant dimensionless invariants.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Laboratory \$\textbackslash{}leftrightarrow\$ Astrophysical Structural Equivalence by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Laboratory Invariant Set}\par
\[
\Pi_{k}^{\mathrm{lab}}
\]
\noindent This identifies the scale-free quantities measured in the laboratory realization.\par
\noindent\textbf{2. Astrophysical Matching Condition}\par
\[
\Pi_{k}^{\mathrm{lab}} = \Pi_{k}^{\mathrm{astro}}
\]
\noindent This states the criterion under which the two systems share the same structural content.\par
\noindent\textbf{3. Scale Equivalence Map}\par
\[
F_{\mathrm{scale}} : \mathcal{S}_{\mathrm{lab}} \longrightarrow \mathcal{S}_{\mathrm{astro}}
\]
\noindent This closes the progression by promoting invariant matching into an explicit cross-scale morphism.\par

\clearpage
\noindent\textbf{[ID 0090] Laboratory $\leftrightarrow$ Astrophysical Structural Equivalence}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Laboratory   Astrophysical Structural Equivalence is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The scaling functor FFF maps laboratory gyromagnetic systems to astrophysical analogues by scaling lengths, times and field strengths while preserving dimensionless parameters like the Reynolds number and magnetic Reynolds number. \textbf{Contextual meaning:} The entry reads Laboratory   Astrophysical Structural Equivalence as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry gives the final gyromagnetic tranche its empirical bridge. It explains why laboratory demonstrations can count as evidence for astrophysical dynamics when the relevant invariants survive the change of scale. \textbf{Lemma support:} Laboratory Invariant Set; Astrophysical Matching Condition; Scale Equivalence Map.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Laboratory demonstrations become structurally meaningful for astrophysical systems only when the scale map preserves the relevant dimensionless invariants. \% CANONICAL PDF-ALIGNED VERSION.

\tzpsection{Equation Grounding}
Equation anchors: The scaling functor FFF maps laboratory gyromagnetic systems to astrophysical analogues by scaling lengths, times and field strengths while preserving dimensionless parameters like the Reynolds number and magnetic Reynolds number. The scaling functor FFF maps laboratory gyromagnetic systems to astrophysical analogues by scaling lengths, times and field strengths while preserving dimensionless parameters like the Reynolds number and magnetic Reynolds number.

\tzpsection{Interpretive Role}
This entry gives the final gyromagnetic tranche its empirical bridge. It explains why laboratory demonstrations can count as evidence for astrophysical dynamics when the relevant invariants survive the change of scale.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Laboratory Astrophysical Structural Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Laboratory Astrophysical Structural Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Equivalence Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0090]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0090_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0090] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Laboratory $\leftrightarrow$ Astrophysical Structural Equivalence}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the scaling functor FFF maps laboratory gyromagnetic systems to astrophysical analogues
by scaling lengths, times and field strengths while preserv...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Laboratory  to  Astrophysical Structural Equivalence is valid when its objects and arrows
close under the stated categorical construction.''\\
\textbf{Proof:} The source statement is read as a categorical construction. The proof obligation is
closure: objects must map to admissible objects, arrows must compose, and the named
invariant must survive the induced functor.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- categorical-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0090_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
