\tzpanchor{0276}
\tzpentryheader{0276}{Differential Rotation Ubiquity}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{12c17f25-708c-563a-b917-8f50a4c6e86b}}\\
\textbf{PiID} & \tzpcode{6482133936072} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{283}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1071.7693 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.7659 rad}\\
\textbf{TZPID} & \tzpcode{ID0276} & \textbf{Node Dependencies}\quad \tzpidref{0275}\\
\textbf{Registry} & \tzpcode{registry\_id\_0276} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Rotation Gradient & Shear Condition\\
\textbf{Closure Support} & Coupling Criterion & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Every observed rotating astrophysical body exhibits internal differential rotation---from Earth's inner--outer core shear and Jupiter's zonal bands to the Sun's latitudinal gradients and galactic rotation curves---and this differential rotation is necessary for gyromagnetic coupling.

\tzpsection{Canonical Equation}
\[
partial_r \Omega  eq 0
\]
\[
Delta \Omega = \Omega_{\mathrm{inner}} - \Omega_{\mathrm{outer}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $\Omega_{\mathrm{inner}}$: angular frequency term in the source equation.
    \item $\Omega_{\mathrm{outer}}$: angular frequency term in the source equation.
    \item $\mathcal{G}_{\mathrm{gyro}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0276 generated source Wolfram model *)
ClearAll[K0276, Cr0276, T, R, A, W, I, N];
eq0276$1 = HoldForm[partialR*Omega*eq0];
eq0276$2 = HoldForm[Delta*Omega == OmegaInner - OmegaOuter];
eq0276$3 = HoldForm[Delta*Omega*eq0Longrightarrow*GGyro*eq0];

K0276 = HoldForm[{eq0276$1, eq0276$2, eq0276$3}];

N = "normalized TRAWIN closure object for Differential Rotation Ubiquity";
I = "Coupling Criterion integration/comparison layer";
W = "Shear Condition wave or operator carrier";
A = "Rotation Gradient admissible action/amplitude condition";
R = "Shear Condition rotation/curl preservation layer";
T = "Rotation Gradient local source condition";

Cr0276[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0276 = Cr0276[K0276];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Rotation Gradient local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Shear Condition rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Rotation Gradient admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Shear Condition wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Coupling Criterion integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Differential Rotation Ubiquity.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0276] Differential Rotation Ubiquity}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
S(\omega)
=
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right)
\operatorname{Im}R(\omega).
\end{equation}

\paragraph{Effective Temperature Split.}
\begin{equation}
T_{\mathrm{eff}}
=
T_{\mathrm{eff}}^{\mathrm{th}}
+
T_{\mathrm{eff}}^{\mathrm{TZP}} .
\end{equation}

\paragraph{Primary Derivation.}
Let $S(\omega)$ be the noise spectrum and $R(\omega)$ the response function.  
Dissipation is encoded by the imaginary part:
\begin{equation}
\operatorname{Im}R(\omega).
\end{equation}

The fluctuation factor is set by the effective thermal and zero-point scale:
\begin{equation}
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right).
\end{equation}

Multiplying the two pieces gives:
\begin{equation}
\boxed{
S(\omega)
=
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right)
\operatorname{Im}R(\omega).
}
\end{equation}

\paragraph{Interpretation.}
Noise and response are coupled through an effective temperature that includes ordinary thermal and TZP contributions.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Differential Rotation Ubiquity by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Rotation Gradient}\par
\[
partial_r \Omega  eq 0
\]
\noindent This fixes the existence of differential rotation as a nonzero rotation gradient.\par
\noindent\textbf{2. Shear Condition}\par
\[
Delta \Omega = \Omega_{\mathrm{inner}} - \Omega_{\mathrm{outer}}
\]
\noindent This measures the actual rotational shear across the carrier.\par
\noindent\textbf{3. Coupling Criterion}\par
\[
Delta \Omega  eq 0 \Longrightarrow \mathcal{G}_{\mathrm{gyro}}  eq 0
\]
\noindent This closes the entry by linking nonzero shear to gyromagnetic coupling.\par

\clearpage
\noindent\textbf{[ID 0276] Differential Rotation Ubiquity}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Differential Rotation Ubiquity is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Every observed rotating astrophysical body exhibits internal differential rotation---from Earth s inner--outer core shear and Jupiter s zonal bands to the Sun s latitudinal gradients and galactic rotation curves---and this differential rotation is necessary for gyromagnetic coupling. \textbf{Contextual meaning:} The entry reads Differential Rotation Ubiquity as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states differential rotation as a measurable shear condition rather than only a broad observational claim. \textbf{Lemma support:} Rotation Gradient; Shear Condition; Coupling Criterion.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Noise and response are coupled through an effective temperature that includes ordinary thermal and TZP contributions.

\tzpsection{Equation Grounding}
Equation anchors: partial sub r Omega eq 0; Delta Omega = Omega sub inner - Omega sub outer; and Delta Omega eq 0 implies G sub gyro eq 0. Proof route: show that nonzero differential rotation is necessary for the stated gyromagnetic coupling criterion. Formalization route: prove that the stated nonzero shear implies the gyromagnetic coupling condition.

\tzpsection{Interpretive Role}
The entry now states differential rotation as a measurable shear condition rather than only a broad observational claim.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Universal Presence of Radial Shear}: The observation that almost all fluid celestial bodies spin faster at their equators than their poles, or faster at their cores than their surfaces.
\item \textbf{Latitude-Dependent Angular Velocity Normalization}: The mathematical mapping of exactly how spin speeds continuously change as you move across the surface or deep into the interior of a star or planet.
\item \textbf{Driving Force of Toroidal Field Generation}: The critical mechanism where this uneven spinning catches, stretches, and wraps magnetic field lines tightly around the body's equator.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0276]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0276_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0276] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Differential Rotation Ubiquity}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} every observed rotating astrophysical body exhibits internal differential rotation---
from Earth's inner--outer core shear and Jupiter's zonal bands...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Differential Rotation Ubiquity is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0276_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
