\section*{ID8809: MAGNETIC INTERACTION POTENTIAL Canonical Statutory Formula: U\_mag}
\paragraph{Metadata.}
PiID: 0724716259166 | RTEID: RTE:P34207.3033:T6.0976 | UUID: 354b2b8b-74b3-5879-b495-17851cd6e203

\paragraph{Canonical Statement.}
[ID 1125] MAGNETIC INTERACTION POTENTIAL Canonical Statutory Formula: \$U\_\{mag\} = -\textbackslash{}vec\{\textbackslash{}mu\} \{total\}(t) \textbackslash{}cdot \textbackslash{}vec\{B\} \{external\}(\textbackslash{}vec\{r\} \{cm\}, t) + U \{self\}[d(t)]\$ Formal Technical Dissertation: Defines the potential energy of the magnetic system. It includes the interaction with external fields and the self-interaction energy of opposing dipoles, which diverges as separation distance \$d \textbackslash{}to 0\$, necessitating mechanical constraints. Source: [4]

\paragraph{Canonical Equation.}
\[
U_{mag} = -\vec{\mu} {total}(t) \cdot \vec{B} {external}(\vec{r} {cm}, t) + U {self}[d(t)]
\]

\paragraph{Dictionary.}
MAGNETIC INTERACTION POTENTIAL Canonical Statutory Formula: \$U\_mag = - total(t) B external(r cm, t) + U self[d(t)]\$ Formal Technical Dissertation: Defines the potential energy of the magnetic system.

\paragraph{Encyclopedia.}
MAGNETIC INTERACTION POTENTIAL Canonical Statutory Formula: U\_mag is an algebraic definition, written U\_mag = -μ total(t) · B external(r cm, t) + U self[d(t)]. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from μ, o, a, l, B, x, defining U\_mag. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
