\tzpanchor{0044}
\tzpentryheader{0044}{\texorpdfstring{\(\mu \propto M R^{2}\Omega\)}{mu proportional to MR^2 Omega} Universal Scaling Law}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{8cdb7274-2724-5919-932a-63364dac5d2d}}\\
\textbf{PiID} & \tzpcode{9375105820974} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{51}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{170.8618 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.2815 rad}\\
\textbf{TZPID} & \tzpcode{ID0044} & \textbf{Node Dependencies}\quad \tzpidref{0040}\\
\textbf{Registry} & \tzpcode{registry\_id\_0044} & \textbf{Scale}\quad magnetic-moment universal\\
\textbf{LOC Classification} & QC809 magnetic moments & QC20 comparative scaling laws\\
\textbf{arXiv Classification} & Primary: astro-ph.SR & Cross-list: physics.plasm-ph, gr-qc\\
\textbf{Primary Support} & Rotational Scale Product & Universal Proportionality Constant\\
\textbf{Closure Support} & Magnetic Moment Scaling Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The magnetic moment scales with the product of mass, square of size, and rotation rate across 47 orders of magnitude, indicating a deep link between inertial and magnetic properties.

\tzpsection{Canonical Equation}
\[
\mu
=
k\,M R^{2}\Omega
\]
\[
k \approx \mathrm{const.}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mu$: source equation symbol.
    \item $M$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0044 generated source Wolfram model *)
ClearAll[K0044, Cr0044, T, R, A, W, I, N];
eq0044$1 = HoldForm[mu == k*MR^2*Omega];
eq0044$2 = HoldForm[k == const];
eq0044$3 = HoldForm[M*R^2*Omega];
eq0044$4 = HoldForm[k == mu/(M*R^2*Omega)];

K0044 = HoldForm[{eq0044$1, eq0044$2, eq0044$3, eq0044$4}];

N = "normalized TRAWIN closure object for \texorpdfstring{\(\mu \propto M R^{2}\Omega\)}{mu proportional to MR^2 Omega} Universal Scaling Law";
I = "Magnetic Moment Scaling Law integration/comparison layer";
W = "Universal Proportionality Constant wave or operator carrier";
A = "Rotational Scale Product admissible action/amplitude condition";
R = "Universal Proportionality Constant rotation/curl preservation layer";
T = "Rotational Scale Product local source condition";

Cr0044[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0044 = Cr0044[K0044];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Rotational Scale Product local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Universal Proportionality Constant rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Rotational Scale Product admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Universal Proportionality Constant wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Magnetic Moment Scaling Law integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for \textbackslash{}texorpdfstring\{\textbackslash{}(\textbackslash{}mu \textbackslash{}propto M R\textasciicircum{}\{2\}\textbackslash{}Omega\textbackslash{})\}\{mu proportional to MR\textasciicircum{}2 Omega\} Universal Scaling Law.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0044] \texorpdfstring{\(\mu \propto M R^{2}\Omega\)}{mu proportional to MR^2 Omega} Universal Scaling Law}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mu
=
kMR^2\Omega .
\end{equation}

\paragraph{Primary Derivation.}
For a rotating body, the inertial rotational scale is controlled by the moment of inertia:

\begin{equation}
I
\sim
MR^2 .
\end{equation}

Angular momentum scales as:

\begin{equation}
L
\sim
I\Omega
\sim
MR^2\Omega .
\end{equation}

If the magnetic moment $\mu$ is proportional to this rotational scale, introduce proportionality constant $k$:

\begin{equation}
\boxed{
\mu
=
kMR^2\Omega .
}
\end{equation}

\paragraph{Interpretation.}
The magnetic moment is modeled as proportional to mass, squared radius, and angular velocity, with $k$ encoding the Trawinistic coupling scale.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors \textbackslash{}texorpdfstring\{\textbackslash{}(\textbackslash{}mu \textbackslash{}propto M R\textasciicircum{}\{2\}\textbackslash{}Omega\textbackslash{})\}\{mu proportional to MR\textasciicircum{}2 Omega\} Universal Scaling Law by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Rotational Scale Product}\par
\[
M R^{2}\Omega
\]
\noindent This collects the mass, geometric extent, and angular speed that seed the magnetic moment.\par
\noindent\textbf{2. Universal Proportionality Constant}\par
\[
k = \frac{\mu}{M R^{2}\Omega}
\]
\noindent This extracts the normalized coefficient that can be compared across systems.\par
\noindent\textbf{3. Magnetic Moment Scaling Law}\par
\[
\mu
=
k\,M R^{2}\Omega
\]
\noindent This closes the progression by promoting the rotational scale product into a universal predictive law for magnetic moment.\par

\clearpage
\noindent\textbf{[ID 0044] \texorpdfstring{\(\mu \propto M R^{2}\Omega\)}{mu proportional to MR^2 Omega} Universal Scaling Law}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
mu   M R2 omega Universal Scaling Law is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The magnetic moment scales with the product of mass, square of size, and rotation rate across 47 orders of magnitude, indicating a deep link between inertial and magnetic properties. \textbf{Contextual meaning:} The entry reads mu   M R2 omega Universal Scaling Law as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This law turns the Elsasser and helicity story into a concrete observable prediction. It explains why bodies spanning wide ranges of scale can still be compared on a single magnetic-moment axis once their rotational geometry is normalized. \textbf{Lemma support:} Rotational Scale Product; Universal Proportionality Constant; Magnetic Moment Scaling Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The magnetic moment is modeled as proportional to mass, squared radius, and angular velocity, with k encoding the Trawinistic coupling scale.

\tzpsection{Equation Grounding}
Equation anchors: The magnetic moment mu of a rotating body obeys mu=k M R2 Omegamu = ktextbackslash,Mtextbackslash,R to the power 2textbackslash,Omegamu=kMR2Omega, where MMM is mass, RRR the characteristic radius, Omega the angular velocity, and kkk a universal proportionality constant determined by the Trawin base unit. The magnetic moment mu of a rotating body obeys mu=k M R2 Omegamu = ktextbackslash,Mtextbackslash,R to the power 2textbackslash,Omegamu=kMR2Omega, where MMM is mass, RRR the characteristic radius, Omega the angular velocity, and kkk a universal proportionality constant determined by the Trawin base unit.

\tzpsection{Interpretive Role}
This law turns the Elsasser and helicity story into a concrete observable prediction. It explains why bodies spanning wide ranges of scale can still be compared on a single magnetic-moment axis once their rotational geometry is normalized.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Omega Universal Scaling Governing Relation}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Governing Relation Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Governing Relation Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0044]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0044_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0044] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont \texorpdfstring{\(\mu \propto M R^{2}\Omega\)}{mu proportional to MR^2 Omega} Universal Scaling Law}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the magnetic moment scales with the product of mass, square of size, and rotation rate
across 47 orders of magnitude, indicating a deep link betwee...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``\textbackslash{}mu ∝ M R² \textbackslash{}omega Universal Scaling Law is valid as a synchronization criterion
under the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0044_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
