\section*{ID9240: Definition of |B(r,t)|ˆ2/(2μ\_0)umag(r,t)}
\paragraph{Metadata.}
PiID: 5144632046927 | RTEID: RTE:P35880.9720:T2.5721 | UUID: 6bb82ef0-c63e-52f7-804e-ebceee0b9705

\paragraph{Canonical Statement.}
oidal flux loops due to the opposing orientation. (3) Creates intense magnetic pressure and linking when compressed. Falsifiability / Test Handle: Construct or simulate a pair of opposite dipoles in a spherical enclosure and measure the resulting field distribution; verify superposition and constraint contributions. 2.0.170 ID 319: Magnetic Pressure and Compressive Energy Type: Definition Formal Statement: The magnetic energy density of a field is \$umag(r,t)=B(r,t)2/(2µ0)u\_\{\textbackslash{}text\{mag\}\}(r,t)\$ = \$|B(r,t)|ˆ2/(2\textbackslash{}mu\_0)umag(r,t)=B(r,t)2/(2µ0).\$ The total magnetic energy inside radius RRR is Umag= \$∫\$ 0R \$∫ 0π∫02πB(r,t)2/(2µ0)r2sinθdrdθdU\_\{\textbackslash{}text\{mag\}\}\$ = \textbackslash{}int\_0ˆR \textbackslash{}int\_0ˆ\{\textbackslash{}pi\} \textbackslash{}int\_0ˆ\{2\textbackslash{}pi\} |B(r,t)|ˆ2/(2\textbackslash{}mu\_0) ; rˆ2 \textbackslash{}sin\textbackslash{}theta,dr d\textbackslash{}theta d\textbackslash{}phiUmag= \$∫\$ 0R \$∫\$ \$0π∫02πB(r,t)2/(2µ0)r2sinθdrdθd.\$ Canonical Registry Vol. 01 110 Trawin Zero Point Contextus Canonicus 2 TZP CANONICAL REGISTRY – ENTRIES 150–199 Mechanical compression of the dipo

\paragraph{Canonical Equation.}
\[
|B(r,t)|ˆ2/(2\mu_0)umag(r,t)=B(r,t)2/(2µ0).
\]

\paragraph{Dictionary.}
Definition of |B(r,t)|ˆ2/(2μ\_0)umag(r,t) — |B(r,t)|ˆ2/(2μ\_0)umag(r,t)=B(r,t)2/(2µ0).

\paragraph{Encyclopedia.}
Definition of |B(r,t)|ˆ2/(2μ\_0)umag(r,t) is an algebraic definition, written |B(r,t)|ˆ2/(2μ\_0)umag(r,t)=B(r,t)2/(2µ0).. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from B, r, defining |B(r,t)|ˆ2/(2μ\_0)umag(r,t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
