\tzpanchor{0271}
\tzpentryheader{0271}{Universal Dipole Scaling Law}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f37ed4d5-5752-5d1a-82ee-dfc4061c50d5}}\\
\textbf{PiID} & \tzpcode{5432664821339} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{278}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1052.3532 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.7340 rad}\\
\textbf{TZPID} & \tzpcode{ID0271} & \textbf{Node Dependencies}\quad \tzpidref{0270}\\
\textbf{Registry} & \tzpcode{registry\_id\_0271} & \textbf{Scale}\quad diagnostic\\
\textbf{LOC Classification} & QA273 dimensionless analysis & QC statistical diagnostics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: nlin.PS, physics.data-an\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A single scaling law links magnetic moments to mass, radius and rotation rate, suggesting a universal mechanism for field generation.

\tzpsection{Canonical Equation}
\[
m=IA
\]
\[
B(r)=\frac{\mu_0}{4\pi}\frac{2m}{r^3}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $B$: magnetic field magnitude.
    \item $\mu_0$: vacuum permeability constant.
    \item $\pi$: source equation symbol.
    \item $\mathcal{K}_{0271}$: canonical registry object for entry ID 0271.
    \item $\mu$: source equation symbol.
    \item $I$: source equation symbol.
    \item $A$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0271 generated source Wolfram model *)
ClearAll[K0271, Cr0271, T, R, A, W, I, N];
eq0271$1 = HoldForm[m == IA];
eq0271$2 = HoldForm[B[r] == (mu0/(4*Pi))*((2*m)/r^3)];

K0271 = HoldForm[{eq0271$1, eq0271$2}];

N = "normalized TRAWIN closure object for Universal Dipole Scaling Law";
I = "Normalized Regime integration/comparison layer";
W = "Scaling Relation wave or operator carrier";
A = "Diagnostic Definition admissible action/amplitude condition";
R = "Scaling Relation rotation/curl preservation layer";
T = "Diagnostic Definition local source condition";

Cr0271[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0271 = Cr0271[K0271];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Diagnostic Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Scaling Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Diagnostic Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Scaling Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Regime integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Universal Dipole Scaling Law.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0271] Universal Dipole Scaling Law}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
|\psi\rangle = \alpha|0\rangle+\beta|1\rangle,
\qquad
|\alpha|^2+|\beta|^2=1 .
\end{equation}

\paragraph{Embedding Map.}
\begin{equation}
\iota:S^2_{\mathrm{Bloch}}\hookrightarrow M .
\end{equation}

\paragraph{Primary Derivation.}
A qubit is a normalized two-level quantum state. Its amplitudes satisfy
\begin{equation}
|\alpha|^2+|\beta|^2=1 .
\end{equation}

Modulo global phase, the normalized qubit state corresponds to a point on the Bloch sphere:
\begin{equation}
|\psi\rangle \longleftrightarrow S^2_{\mathrm{Bloch}} .
\end{equation}

In the Trawinistic setting, this Bloch sphere is embedded into the ambient manifold by
\begin{equation}
\boxed{
\iota:S^2_{\mathrm{Bloch}}\hookrightarrow M .
}
\end{equation}

\paragraph{Interpretation.}
The qubit is treated as both a Hilbert-space state and a geometric object embedded into the Trawinistic manifold.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Universal Dipole Scaling Law by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Diagnostic Definition}\par
\[
m=IA
\]
\noindent This defines the scalar diagnostic or conversion quantity named by the title.\par
\noindent\textbf{2. Scaling Relation}\par
\[
B(r)=\frac{\mu_0}{4\pi}\frac{2m}{r^3}
\]
\noindent This elevates the quantity into a comparative scaling or correlation law.\par
\noindent\textbf{3. Normalized Regime}\par
\[
m=IA
\]
\noindent This closes the entry by normalizing the diagnostic against a stated reference regime.\par

\clearpage
\noindent\textbf{[ID 0271] Universal Dipole Scaling Law}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Universal Dipole Scaling Law is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A single scaling law links magnetic moments to mass, radius and rotation rate, suggesting a universal mechanism for field generation. \textbf{Contextual meaning:} The entry reads Universal Dipole Scaling Law as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons. \textbf{Lemma support:} Diagnostic Definition; Scaling Relation; Normalized Regime.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The qubit is treated as both a Hilbert-space state and a geometric object embedded into the Trawinistic manifold.

\tzpsection{Equation Grounding}
Equation anchors: m=IA; B(r)=ratio mu sub 0 4pi ratio 2m r to the power 3; and Bpropto r to the power -3. Proof route: show that the named quantity is dimensionless or consistently scaled in the regime stated by the entry. Formalization route: prove that the normalized diagnostic remains invariant under the intended rescaling.

\tzpsection{Interpretive Role}
The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Scale-Invariant Magnetic Dipole Formulation}: The unifying equation capable of predicting the magnetic field strength of both a tiny lab experiment and a massive gas giant using the exact same formula.
\item \textbf{Inverse-Cube Field Attenuation Rule}: The fundamental law stating that the strength of the generated dipole magnetic field drops off precisely with the cube of the distance from the source.
\item \textbf{Cross-Disciplinary Magnetization Predictor}: The robust mathematical model that accurately scales expected magnetic properties using only core density, radius, and rotation rate, regardless of the material.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0271]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0271_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0271] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Universal Dipole Scaling Law}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a single scaling law links magnetic moments to mass, radius and rotation rate,
suggesting a universal mechanism for field generation

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Universal Dipole Scaling Law is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0271_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
