\tzpanchor{0040}
\tzpentryheader{0040}{Universality of Elsasser Criticality}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{a7b9a6b4-8776-5064-a317-c6c3990e4b4c}}\\
\textbf{PiID} & \tzpcode{6939937510582} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{47}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{155.3289 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.2559 rad}\\
\textbf{TZPID} & \tzpcode{ID0040} & \textbf{Node Dependencies}\quad \tzpidref{0038}\\
\textbf{Registry} & \tzpcode{registry\_id\_0040} & \textbf{Scale}\quad universal magneto-rotational\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC174.4 critical plasma balance\\
\textbf{arXiv Classification} & Primary: astro-ph.SR \quad Cross-list: physics.plasm-ph, gr-qc & \\
\textbf{Primary Support} & Magnetic-Rotational Control Ratio & Universal Critical Value\\
\textbf{Closure Support} & Bounded Cross-Scale Deviation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The same critical behaviour emerges in small experiments and large astrophysical objects, reflecting a scaling functor that maps between these systems.

\tzpsection{Canonical Equation}
\[
\Lambda
=
\frac{B^{2}}{\rho\,\mu\,\Omega^{2}}
\]
\[
\Lambda_{\mathrm{crit}} \approx 1
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Lambda$: lemniscatic representative or canonical branch object.
    \item $B$: magnetic field magnitude.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\mu$: source equation symbol.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $\Lambda_{\mathrm{crit}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0040 generated source Wolfram model *)
ClearAll[K0040, Cr0040, T, R, A, W, I, N];
eq0040$1 = HoldForm[Lambda == B^2/(rho*mu*Omega^2)];
eq0040$2 = HoldForm[LambdaCrit == 1];
eq0040$3 = HoldForm[Abs[Lambda - 1] <= epsilonSys];

K0040 = HoldForm[{eq0040$1, eq0040$2, eq0040$3}];

N = "normalized TRAWIN closure object for Universality of Elsasser Criticality";
I = "Bounded Cross-Scale Deviation integration/comparison layer";
W = "Universal Critical Value wave or operator carrier";
A = "Magnetic-Rotational Control Ratio admissible action/amplitude condition";
R = "Universal Critical Value rotation/curl preservation layer";
T = "Magnetic-Rotational Control Ratio local source condition";

Cr0040[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0040 = Cr0040[K0040];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Magnetic-Rotational Control Ratio local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Universal Critical Value rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Magnetic-Rotational Control Ratio admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Universal Critical Value wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Bounded Cross-Scale Deviation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Universality of Elsasser Criticality.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0040] Universality of Elsasser Criticality}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Lambda_{\mathrm{crit}}\approx 1 .
\end{equation}

\paragraph{Primary Derivation.}
From the Elsasser parameter,

\begin{equation}
\Lambda
=
\frac{\mathbf{B}^2}
{\rho\,\mu\,\Omega^2},
\end{equation}

criticality occurs when magnetic and rotational terms are balanced.

Balance means the numerator and denominator are of the same order:

\begin{equation}
\mathbf{B}^2
\sim
\rho\,\mu\,\Omega^2 .
\end{equation}

Therefore,

\begin{equation}
\frac{\mathbf{B}^2}
{\rho\,\mu\,\Omega^2}
\sim
1 .
\end{equation}

Thus,

\begin{equation}
\boxed{
\Lambda_{\mathrm{crit}}\approx 1 .
}
\end{equation}

\paragraph{Interpretation.}
The critical Elsasser value marks a universal balance architecture across scales: the point where magnetic organization and rotational inertia enter comparable strength.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Universality of Elsasser Criticality by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Magnetic-Rotational Control Ratio}\par
\[
\Lambda
=
\frac{B^{2}}{\rho\,\mu\,\Omega^{2}}
\]
\noindent This defines the dimensionless comparison between magnetic intensity and rotational inertia.\par
\noindent\textbf{2. Universal Critical Value}\par
\[
\Lambda_{\mathrm{crit}} \approx 1
\]
\noindent This states that the balanced regime is the same target across very different physical systems.\par
\noindent\textbf{3. Bounded Cross-Scale Deviation}\par
\[
\left|\Lambda - 1\right| \leq \varepsilon_{\mathrm{sys}}
\]
\noindent This closes the progression by allowing system-dependent perturbations without surrendering the universal critical center.\par

\clearpage
\noindent\textbf{[ID 0040] Universality of Elsasser Criticality}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Universality of Elsasser Criticality is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The same critical behaviour emerges in small experiments and large astrophysical objects, reflecting a scaling functor that maps between these systems. \textbf{Contextual meaning:} The entry reads Universality of Elsasser Criticality as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry upgrades the Elsasser attractor from a local criterion into a universal comparative law. It underwrites later helicity, magnetic-moment, and scaling entries by establishing that order-one criticality persists across enormous changes of scale. \textbf{Lemma support:} Magnetic-Rotational Control Ratio; Universal Critical Value; Bounded Cross-Scale Deviation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The critical Elsasser value marks a universal balance architecture across scales: the point where magnetic organization and rotational inertia enter comparable strength.

\tzpsection{Equation Grounding}
Equation anchors: Across laboratory and astrophysical systems, the Elsasser critical parameter Lambdatextbackslash LambdaLambda reaches a universal value Lambda critapproximately1textbackslash Lambdatextbackslash crit approximately1Lambda critapproximately1 regardless of scale. Deviations scale as a power of the Reynolds number or magnetic Prandtl number but remain bounded by an O(1) O (1)O(1) factor. Across laboratory and astrophysical systems, the Elsasser critical parameter Lambdatextbackslash LambdaLambda reaches a universal value Lambda critapproximately1textbackslash Lambdatextbackslash crit approximately1Lambda critapproximately1 regardless of scale. Deviations scale as a power of the Reynolds number or magnetic Prandtl number but remain bounded by an O(1) O (1)O(1) factor.

\tzpsection{Interpretive Role}
This entry upgrades the Elsasser attractor from a local criterion into a universal comparative law. It underwrites later helicity, magnetic-moment, and scaling entries by establishing that order-one criticality persists across enormous changes of scale.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Universality Mhd Ratio Criticality}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Mhd Ratio Rotating-Field Analogue}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\item \textbf{Mhd Ratio Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0040]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0040_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0040] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Universality of Elsasser Criticality}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the same critical behaviour emerges in small experiments and large astrophysical
objects, reflecting a scaling functor that maps between these systems

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Universality of Elsasser Criticality is valid when its objects and arrows close under
the stated categorical construction.''\\
\textbf{Proof:} The source statement is read as a categorical construction. The proof obligation is
closure: objects must map to admissible objects, arrows must compose, and the named
invariant must survive the induced functor.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- categorical-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0040_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
