\section*{Q394 ID9931: ID9931: Relation: Ω[T\textasciicircum{}2 × T\textasciicircum{}2, π, DAAN]}
\paragraph{Metadata.}
PiID: 6579229552498 | RTEID: RTE:P38564.2785:T0.7102 | UUID: a3266d07-c60d-52a1-ac1a-934e8407e273

\paragraph{Semantic Queue.}
Status: batch003\_started; class: candidate\_real\_algebra\_segment; role: .

\paragraph{Canonical Statement.}
is constructed such that it preserves the essential structure (natural transformations ensure information-theoretic quantities and topological invariants commute with the mapping). This homological functor guarantees that information (entropy, logical bits) encoded in the 4D sphere configuration is preserved upon projection to the 2D topological manifold – a key requirement for lossless dimensional collapse at the TZP. Mathematically, the particle-specific entanglement protocol is captured by an overarching Unified Entanglement Meta-Theorem. One formulation (from the Ω-protocol) states: “The \$Ω[T\textasciicircum{}2 \textbackslash{}times T\textasciicircum{}2, \textbackslash{}pi, \textbackslash{}text\{DAAN\}]\$ kissing protocol achieves complete decoherence suppression for all particle–neural entanglement”. The proof employs a combination of Lindblad spectrum analysis and topological gap protection. We derive that the Liouvillian of the open system has a degenerate zero eigenvalue corresponding to a protected steady state, and a spectral gap \$\textbackslash{}lambda\_\{1\}\$ on the order of \$\textbackslash{}pi,\textbackslash{}Delta\_\{\textbackslash{}text\{topological\}\}/N\_\{\textbackslash{}max\}\$ (with \$N\_\{\textbackslash{}max\}\$ the maximum kissing number) separates this steady state from excited dec

\paragraph{Canonical Equation.}
\[
Ω[T^2 \times T^2, \pi, \text{DAAN}]
\]

\paragraph{Source Truth.}
See ../../tzp\_id/ID9931/ID9931.source\_truth.json and ../../tzp\_id/ID9931/ID9931.tex.
