\section*{ID9504: Cosmological Flow: Matter–Energy Transitions and TZP Emergence: α ≈ 1/137}
\paragraph{Metadata.}
PiID: 5008019086996 | RTEID: RTE:P36906.1426:T4.2613 | UUID: 3c6c01c8-4de9-5c6d-b57c-e4255e4cb283

\paragraph{Canonical Statement.}
no such precise number is evident in data). On a more accessible front, consider the continuous creation idea in steady-state cosmology (now outdated) or more modern vacuum decay ideas: a slight bias in vacuum fluctuations (say one particle created per \$10\textasciicircum{}\{80\}\$ vacuum oscillations) could accumulate over cosmic time to create matter. The rate would be governed by a dimensionless constant – perhaps related to the fine structure constant or others, but our \$\textbackslash{}chi\$ could be a composite of fundamental constants. For example, \$\textbackslash{}chi - 1 = 0.185\$ might equal something like \$\textbackslash{}frac\{\textbackslash{}alpha\}\{2\textbackslash{}pi\}\$ (with \$\textbackslash{}alpha \textbackslash{}approx 1/137\$ giving \$\textbackslash{}alpha/2\textbackslash{}pi \textbackslash{}approx 0.116\$ – not quite, but these are the orders of magnitude we are philosophically invoking).

\paragraph{Canonical Equation.}
\[
\alpha \approx 1/137
\]

\paragraph{Dictionary.}
Relation: α ≈ 1/137

\paragraph{Encyclopedia.}
Cosmological Flow: Matter–Energy Transitions and TZP Emergence: α ≈ 1/137 is a scaling / order-of-magnitude relation, written α ≈ 1/137. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from α. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
