\section*{ID8641: Definition of 2/37}
\paragraph{Metadata.}
PiID: 8382920419748 | RTEID: RTE:P33554.9220:T5.0227 | UUID: 94fc2bec-58e1-5f7a-a49b-26dba6e56688

\paragraph{Canonical Statement.}
The connection is no coincidence: \$\$\textbackslash{}backslash frac\{32\}\{27\}=1.185185...\$\$ and \$32/27\$ simplifies from \$\$(16/15)ltimes(10/9)\$\$ (as shown below) tying 185 to those rational ratios. In modular arithmetic terms, 185's factors yield interesting congruences. Since \$185 \textbackslash{}equiv 5 \textbackslash{}pmod\{9\}\$ and also \$185 \textbackslash{}equiv 5 \textbackslash{}pmod\{15\}\$, the number leaves the same remainder 5 when divided by 9, 15, or 27. Its factor 37 is well-known for generating repetend cycles in base-10; for instance \$\$1/37=0.1overline\{027\}\$,\$ \$\$2/37=0.1overline\{054\}\$\$, \$\$5/37=0.1overline\{135\}\$\$, etc., illustrating how 37 "cycles" through three-digit sequences The appearance of 185 as a repeating sequence (in \$5/27\$ or \$32/27\$) is a direct result of these modular relationships in our decimal system.

\paragraph{Canonical Equation.}
\[
2/37=0.1overline{054}
\]

\paragraph{Dictionary.}
The connection is no coincidence: and 32/27 simplifies from (as shown below) tying 185 to those rational ratios.

\paragraph{Encyclopedia.}
Definition of 2/37 is an algebraic definition, written 2/37=0.1overline054. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from o, v, r, l, n, defining 2/37. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
