\tzpanchor{0046}
\tzpentryheader{0046}{Order-of-Magnitude Invariance Across 47 Orders of Scale}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{59e1fc03-0c22-567b-8ca0-fc7fc16122f1}}\\
\textbf{PiID} & \tzpcode{7510582097494} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{53}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{178.6282 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.2943 rad}\\
\textbf{TZPID} & \tzpcode{ID0046} & \textbf{Node Dependencies}\quad \tzpidref{0040}\\
\textbf{Registry} & \tzpcode{registry\_id\_0046} & \textbf{Scale}\quad cross-scale invariance\\
\textbf{LOC Classification} & QC20 scaling invariance & QC174 comparative physical systems\\
\textbf{arXiv Classification} & Primary: astro-ph.SR \quad Cross-list: physics.gen-ph, gr-qc & \\
\textbf{Primary Support} & Paired Observable & Normalized Scale Ratio\\
\textbf{Closure Support} & One-Decade Invariance Window & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The unification theory predicts that properly normalised physical quantities maintain similar magnitudes over an enormous range of scales, highlighting deep structural consistency.

\tzpsection{Canonical Equation}
\[
\mathcal{R}
=
\frac{Q}{Q'}
\]
\[
\left|\log_{10}\mathcal{R}\right| \leq 1
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{R}$: global radius, boundary radius, or topological scale.
    \item $Q$: source equation symbol.
    \item $\mathcal{K}_{0046}$: canonical registry object for entry ID 0046.
    \item $\log_{10}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0046 generated source Wolfram model *)
ClearAll[K0046, Cr0046, T, R, A, W, I, N];
eq0046$1 = HoldForm[R == Q/Derivative[1][Q]];
eq0046$2 = HoldForm[Abs[log10*R] <= 1];
eq0046$3 = HoldForm[Tuple[Q, Derivative[1][Q]]];

K0046 = HoldForm[{eq0046$1, eq0046$2, eq0046$3}];

N = "normalized TRAWIN closure object for Order-of-Magnitude Invariance Across 47 Orders of Scale";
I = "One-Decade Invariance Window integration/comparison layer";
W = "Normalized Scale Ratio wave or operator carrier";
A = "Paired Observable admissible action/amplitude condition";
R = "Normalized Scale Ratio rotation/curl preservation layer";
T = "Paired Observable local source condition";

Cr0046[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0046 = Cr0046[K0046];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Paired Observable local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Normalized Scale Ratio rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Paired Observable admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Normalized Scale Ratio wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ One-Decade Invariance Window integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Order-of-Magnitude Invariance Across 47 Orders of Scale.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0046] Order-of-Magnitude Invariance Across 47 Orders of Scale}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{Q}{Q'}
=
\mathcal{O}(1).
\end{equation}

\paragraph{Primary Derivation.}
Let $Q$ and $Q'$ be corresponding quantities related by a scaling map between laboratory and astrophysical systems.

If the scaling preserves the essential dimensionless structure, then the transformed quantity should not diverge across the mapped systems. Thus the ratio:

\begin{equation}
\frac{Q}{Q'}
\end{equation}

must remain bounded within a finite order-of-magnitude interval.

This boundedness condition is expressed as:

\begin{equation}
\boxed{
\frac{Q}{Q'}
=
\mathcal{O}(1).
}
\end{equation}

\paragraph{Interpretation.}
The scaling relation is valid when corresponding quantities remain order-equivalent despite extreme differences in physical size.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Order-of-Magnitude Invariance Across 47 Orders of Scale by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Paired Observable}\par
\[
(Q, Q')
\]
\noindent This identifies the quantity being compared across two widely separated scales.\par
\noindent\textbf{2. Normalized Scale Ratio}\par
\[
\mathcal{R}
=
\frac{Q}{Q'}
\]
\noindent This forms the direct cross-scale comparison statistic.\par
\noindent\textbf{3. One-Decade Invariance Window}\par
\[
\left|\log_{10}\mathcal{R}\right| \leq 1
\]
\noindent This closes the progression by bounding acceptable drift to a single order of magnitude despite the enormous scale span.\par

\clearpage
\noindent\textbf{[ID 0046] Order-of-Magnitude Invariance Across 47 Orders of Scale}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Order-of-Magnitude Invariance Across 47 Orders of Scale is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The unification theory predicts that properly normalised physical quantities maintain similar magnitudes over an enormous range of scales, highlighting deep structural consistency. \textbf{Contextual meaning:} The entry reads Order-of-Magnitude Invariance Across 47 Orders of Scale as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This principle is the registry-level justification for publishing a single comparative canon instead of unrelated scale-specific notebooks. It says that once the correct normalization is chosen, the same structure remains visible from laboratory systems to astrophysical ones. \textbf{Lemma support:} Paired Observable; Normalized Scale Ratio; One-Decade Invariance Window.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The scaling relation is valid when corresponding quantities remain order-equivalent despite extreme differences in physical size.

\tzpsection{Equation Grounding}
Equation anchors: For quantities QQQ and Q Q Q  related by the scaling functor between laboratory and astrophysical systems, the ratio QQ ratio Q Q Q Q remains within a single order of magnitude across 47 orders of magnitude in size. For quantities QQQ and Q Q Q  related by the scaling functor between laboratory and astrophysical systems, the ratio QQ ratio Q Q Q Q remains within a single order of magnitude across 47 orders of magnitude in size.

\tzpsection{Interpretive Role}
This principle is the registry-level justification for publishing a single comparative canon instead of unrelated scale-specific notebooks. It says that once the correct normalization is chosen, the same structure remains visible from laboratory systems to astrophysical ones.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Order Magnitude Invariance Across 47}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Order Magnitude Invariance Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Scale Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0046]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0046_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0046] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Order-of-Magnitude Invariance Across 47 Orders of Scale}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the unification theory predicts that properly normalised physical quantities maintain
similar magnitudes over an enormous range of scales, highligh...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Order-of-Magnitude Invariance Across 47 Orders of Scale is valid when its objects and
arrows close under the stated categorical construction.''\\
\textbf{Proof:} The source statement is read as a categorical construction. The proof obligation is
closure: objects must map to admissible objects, arrows must compose, and the named
invariant must survive the induced functor.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- categorical-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0046_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
