\section*{ID8871: VOLUMETRIC DISPLACEMENT INTEGRAL Canonical Statutory Formula: VD}
\paragraph{Metadata.}
PiID: 3639548000448 | RTEID: RTE:P34448.0630:T0.2111 | UUID: 94b06969-5267-5c5b-b75f-145636d4adb9

\paragraph{Canonical Statement.}
[ID 1017] VOLUMETRIC DISPLACEMENT INTEGRAL Canonical Statutory Formula: \$VD = \textbackslash{}iiint\_\{\textbackslash{}Omega\} (\textbackslash{}sqrt\{-g\} - \textbackslash{}Phi\_\{obj\}) d\textasciicircum{}3x \textbackslash{}implies F\_g = \textbackslash{}rho\_\{vac\} \textbackslash{}cdot VD \textbackslash{}cdot \textbackslash{}nabla g\_\{\textbackslash{}mu\textbackslash{}nu\}\$ Formal Technical Dissertation: Redefines gravity as a volumetric buoyancy force. The integral calculates the volume of vacuum energy displaced by an object; "Stillness" is achieved when this integral balances external forces. Source: [26], [25]

\paragraph{Canonical Equation.}
\[
VD = \iiint_{\Omega} (\sqrt{-g} - \Phi_{obj}) d^3x \implies F_g = \rho_{vac} \cdot VD \cdot \nabla g_{\mu\nu}
\]

\paragraph{Dictionary.}
VOLUMETRIC DISPLACEMENT INTEGRAL Canonical Statutory Formula: \$VD = \_ ( -g - \_obj) d\textasciicircum{}3x F\_g = \_vac VD g\_ \$ Formal Technical Dissertation: Redefines gravity as a volumetric buoyancy force.

\paragraph{Encyclopedia.}
VOLUMETRIC DISPLACEMENT INTEGRAL Canonical Statutory Formula: VD is an expectation / trace over state, written VD = iiint\_Ω (√(-g) - Φ\_obj) d\textasciicircum{}3x ⟹ F\_g = ρ\_vac · VD · ∇ g\_μν. It is computed as an expectation value or trace over a quantum state, producing an observable. It is built from Ω, ∇, μ, ν, g, o, defining VD. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
