\tzpanchor{0885}
\tzpentryheader{0885}{SUBHARMONIC DUAL-SPIN PROJECTION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{007b0218-31b6-5ac8-8f85-7b620af5e7d1}}\\
\textbf{PiID} & \tzpcode{6171776691473} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{892}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3382.2864 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.5730 rad}\\
\textbf{TZPID} & \tzpcode{ID0885} & \textbf{Node Dependencies}\quad \tzpidref{0884}\\
\textbf{Registry} & \tzpcode{registry\_id\_0885} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Mode Quantization & Dispersion Law\\
\textbf{Closure Support} & Boundary Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records subharmonic dual-spin projection through a normalized Nonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0885}}:\mathcal{X}_{\mathrm{id0885}}\longrightarrow\mathcal{Y}_{\mathrm{id0885}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0885}})=\mathcal{O}_{\mathrm{id0885}}
\]
\[
\mathcal{O}_{\mathrm{id0885}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0885}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0885}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0885}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0885 generated source Wolfram model *)
ClearAll[K0885, Cr0885, T, R, A, W, I, N];
eq0885$1 = HoldForm[Oid0885[Xid0885] -> Yid0885];
eq0885$2 = HoldForm[NTRAWIN[OId0885] == OId0885];
eq0885$3 = HoldForm[Element[OId0885[x], YAdm]];

K0885 = HoldForm[{eq0885$1, eq0885$2, eq0885$3}];

N = "normalized TRAWIN closure object for SUBHARMONIC DUAL-SPIN PROJECTION";
I = "SUBHARMONIC DUAL-SPIN PROJECTION integration/comparison layer";
W = "SUBHARMONIC DUAL-SPIN PROJECTION wave or operator carrier";
A = "SUBHARMONIC DUAL-SPIN PROJECTION admissible action/amplitude condition";
R = "SUBHARMONIC DUAL-SPIN PROJECTION rotation/curl preservation layer";
T = "SUBHARMONIC DUAL-SPIN PROJECTION local source condition";

Cr0885[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0885 = Cr0885[K0885];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ SUBHARMONIC DUAL-SPIN PROJECTION local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ SUBHARMONIC DUAL-SPIN PROJECTION rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ SUBHARMONIC DUAL-SPIN PROJECTION admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ SUBHARMONIC DUAL-SPIN PROJECTION wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ SUBHARMONIC DUAL-SPIN PROJECTION integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for SUBHARMONIC DUAL-SPIN PROJECTION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0885] SUBHARMONIC DUAL-SPIN PROJECTION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0885}}:\mathcal{X}_{\mathrm{id0885}}\longrightarrow \mathcal{Y}_{\mathrm{id0885}},\qquad
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0885}})=\mathcal{O}_{\mathrm{id0885}},\qquad
\mathcal{O}_{\mathrm{id0885}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

\paragraph{Primary Derivation.} Let $\psi_{0885}(x,t)$ be the local wave or phase carrier.  The entry assigns the carrier mode\[
\psi_{0885}=\mathcal{O}_{\mathrm{id0885}}(x).
\]

A reusable harmonic witness is the phase-weighted state\[
I_{0885}(t)=A_{0885}(t)e^{i\theta_{0885}(t)}.
\]

Stable closure requires phase locking and admissible landing:\[
\dot{\theta}_{0885}(t)=\omega_{\mathrm{lock},0885},\qquad \mathcal{O}_{\mathrm{id0885}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

Thus the Nonary derivation for [ID 0885] is the three-stage passage
\[
\mathcal{X}_{\mathrm{id0885}}\xrightarrow{\,\mathcal{O}_{\mathrm{id0885}}\,} \mathcal{Y}_{\mathrm{id0885}}\xrightarrow{\,\mathcal{N}_{\mathrm{TRAWIN}}\,} \mathcal{Y}_{\mathrm{adm}},
\]
with the entry title fixing the meaning of the carrier and the TRAWIN normalization fixing the admissibility test.

\paragraph{Interpretation.} SUBHARMONIC DUAL-SPIN PROJECTION closes as a phase-and-mode statement: the entry is usable when its harmonic carrier locks to the local admissible channel.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors SUBHARMONIC DUAL-SPIN PROJECTION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0885}}:\mathcal{X}_{\mathrm{id0885}}\longrightarrow\mathcal{Y}_{\mathrm{id0885}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0885}})=\mathcal{O}_{\mathrm{id0885}}
\]
\[
\mathcal{O}_{\mathrm{id0885}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0885] SUBHARMONIC DUAL-SPIN PROJECTION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
SUBHARMONIC DUAL-SPIN PROJECTION is a registry definition in Resonance and Phase Locking with secondary pressure from Biological and Biomolecular Analogies.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} 1. Spin up gyroscope: omega = 0 -> omega sub max over 10-60 seconds. \textbf{Contextual meaning:} The entry reads SUBHARMONIC DUAL-SPIN PROJECTION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred. \textbf{Lemma support:} Mode Quantization; Dispersion Law; Boundary Condition.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, SUBHARMONIC DUAL-SPIN PROJECTION is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: gamma sub gold = 2pi (1 - ratio 1 Phi ) = pi(3 - sqrt 5 ) approximately 137.508 to the power compose; z sub k = 1 - ratio 2k+1 N ( ranging from +1 to -1); and theta sub k = arccos(z sub k). Proof route: show that bounded carrier geometry forces the stated mode quantization and resonance law. Formalization route: prove that the stated boundary condition yields the stated discrete spectrum.

\tzpsection{Interpretive Role}
The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Fractional-Rotation Quantum States}: The deeply confusing math required to track a particle that only spins half a circle before miraculously resetting itself as if it had spun all the way around.
\item \textbf{Bisected Angular Momentum Pairing}: The realization that the heavy, sluggish overall turning of the machine is actually powered by two completely different, incredibly fast, invisible tornados spinning in opposite directions.
\item \textbf{Half-Step Frequency Locking}: The discovery that the loudest, most violent shaking of the reactor happens not when you match its pitch exactly, but when you play a note exactly one full octave below it.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0885]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0885].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0885] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont SUBHARMONIC DUAL-SPIN PROJECTION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} SUBHARMONIC DUAL-SPIN PROJECTION is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``SUBHARMONIC DUAL-SPIN PROJECTION is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0885].
\par\endgroup
\vfill
\endgroup
\endgroup
