\tzpanchor{0631}
\tzpentryheader{0631}{QUARK-GLUON PLASMA RESIDUE OPERATOR (hatQ\_gp)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9e1459ac-45b9-5fa2-8faa-ffbf991dfb64}}\\
\textbf{PiID} & \tzpcode{5778960917363} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{638}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2427.0138 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.9990 rad}\\
\textbf{TZPID} & \tzpcode{ID0631} & \textbf{Node Dependencies}\quad \tzpidref{0630}\\
\textbf{Registry} & \tzpcode{registry\_id\_0631} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records quark-gluon plasma residue operator (hatq\_gp) through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\frac{\partial S}{\partial t} + \mathcal{H}_T \left( q,\frac{\partial S}{\partial q},t \right) = 0.
\]
\[
p_q=\frac{\partial S}{\partial q}.
\]
\[
\mathcal{H}_T(q,p_q,t).
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S$: source equation symbol.
    \item $t$: source equation symbol.
    \item $\mathcal{H}_T$: source equation symbol.
    \item $p_q$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0631 generated source Wolfram model *)
ClearAll[K0631, Cr0631, T, R, A, W, I, N];
eq0631$1 = HoldForm[(Partial*S)/(Partial*t) + HT[q, (Partial*S)/(Partial*q), t] == 0];
eq0631$2 = HoldForm[pQ == (Partial*S)/(Partial*q)];
eq0631$3 = HoldForm[HT[q, pQ, t]];

K0631 = HoldForm[{eq0631$1, eq0631$2, eq0631$3}];

N = "normalized TRAWIN closure object for QUARK-GLUON PLASMA RESIDUE OPERATOR (hatQ\_gp)";
I = "Normalized Output integration/comparison layer";
W = "Composable Action wave or operator carrier";
A = "Carrier Map admissible action/amplitude condition";
R = "Composable Action rotation/curl preservation layer";
T = "Carrier Map local source condition";

Cr0631[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0631 = Cr0631[K0631];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Carrier Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Composable Action rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Carrier Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Composable Action wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Output integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for QUARK-GLUON PLASMA RESIDUE OPERATOR (hatQ\textbackslash{}\_gp).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0631] QUARK-GLUON PLASMA RESIDUE OPERATOR (hatQ\_gp)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{\partial S}{\partial t}
+
\mathcal{H}_T
\left(
q,\frac{\partial S}{\partial q},t
\right)
=
0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $S(q,t)$ be the action function for a classical trajectory on the Trawinistic manifold.  
The canonical momentum is obtained from the action by:

\begin{equation}
p_q=\frac{\partial S}{\partial q}.
\end{equation}

The Hamiltonian density or Hamiltonian function in Trawinistic form is:

\begin{equation}
\mathcal{H}_T(q,p_q,t).
\end{equation}

Substituting $p_q=\partial S/\partial q$ into the Hamiltonian gives:

\begin{equation}
\mathcal{H}_T
\left(
q,\frac{\partial S}{\partial q},t
\right).
\end{equation}

The Hamilton--Jacobi condition states that time evolution of the action cancels the Hamiltonian contribution:

\begin{equation}
\boxed{
\frac{\partial S}{\partial t}
+
\mathcal{H}_T
\left(
q,\frac{\partial S}{\partial q},t
\right)
=
0 .
}
\end{equation}

\paragraph{Interpretation.}
This equation translates Trawinistic Hamiltonian dynamics into an action-based evolution law.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors QUARK-GLUON PLASMA RESIDUE OPERATOR (hatQ\textbackslash{}\_gp) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Carrier Map}\par
\[
\frac{\partial S}{\partial t} + \mathcal{H}_T \left( q,\frac{\partial S}{\partial q},t \right) = 0.
\]
\noindent This names the entry as an actual map between carrier domains rather than a loose metaphor.\par
\noindent\textbf{2. Composable Action}\par
\[
p_q=\frac{\partial S}{\partial q}.
\]
\noindent This inserts the map into the ordered TRAWIN chain and makes composition explicit.\par
\noindent\textbf{3. Normalized Output}\par
\[
\mathcal{H}_T(q,p_q,t).
\]
\noindent This closes the entry by requiring that the output land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0631] QUARK-GLUON PLASMA RESIDUE OPERATOR (hatQ\_gp)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
QUARK-GLUON PLASMA RESIDUE OPERATOR (hatQ sub gp) is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} hat Q gp = text Tr [F munu F to the power munu ] otimes expleft(-frac T sub c T(L) right) implies SU(3) sub color text Pinning. \textbf{Contextual meaning:} The entry reads QUARK-GLUON PLASMA RESIDUE OPERATOR (hatQ sub gp) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This equation translates Trawinistic Hamiltonian dynamics into an action-based evolution law.

\tzpsection{Equation Grounding}
Equation anchors: R sub S = ratio 2GM c to the power 2; 10K** **Total:** \textasciitilde{}; and omega spin approximately Omega orbit. Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{High-Energy Chromodynamic Scaffolding}: The mathematical ghost left behind in the field's structure from the absolute highest-energy, fundamental particle interactions.
\item \textbf{Strong-Force Entanglement Echo}: The residual twisting in the geometric metric that remembers the intense, unbreakable bonds holding atomic nuclei together.
\item \textbf{Primordial State Reversion Sourcing}: The operator simulating the extreme, universe-shattering heat and pressure required to melt normal matter down to its most basic, soup-like form.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0631]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0631_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0631] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont QUARK-GLUON PLASMA RESIDUE OPERATOR (hatQ\_gp)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records quark-gluon plasma residue operator (hatq\textbackslash{}\_gp) through the Septenary
derivation layer, using the displayed relations as operation...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``QUARK-GLUON PLASMA RESIDUE OPERATOR (\textbackslash{}hat\{Q\_\{gp) is valid as a formal dynamical law
when the Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0631_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
