\tzpanchor{0280}
\tzpentryheader{0280}{Resonant Magnetoacoustic Functor Network}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{954abdb8-debe-5b1e-a63f-fdf58324cea9}}\\
\textbf{PiID} & \tzpcode{1339360726024} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{287}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1087.3022 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.7915 rad}\\
\textbf{TZPID} & \tzpcode{ID0280} & \textbf{Node Dependencies}\quad \tzpidref{0279}\\
\textbf{Registry} & \tzpcode{registry\_id\_0280} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A resonant magnetoacoustic functor network maps between categories of acoustic vibrations and electromagnetic oscillations; the coupling is captured by a dynamic susceptibility tensor that adapts across scales.

\tzpsection{Canonical Equation}
\[
\omega^2=k^2(c_s^2+v_A^2)
\]
\[
\omega^2=k^2(c_s^2+v_A^2)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\omega$: angular frequency term in the source equation.
    \item $c_s$: source equation symbol.
    \item $A$: source equation symbol.
    \item $\mathcal{K}_{0280}$: canonical registry object for entry ID 0280.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0280 generated source Wolfram model *)
ClearAll[K0280, Cr0280, T, R, A, W, I, N];
eq0280$1 = HoldForm[omega^2 == k^2*(cS^2 + vA^2)];
eq0280$2 = HoldForm[omega^2 == k^2*(cS^2 + vA^2)];

K0280 = HoldForm[{eq0280$1, eq0280$2}];

N = "normalized TRAWIN closure object for Resonant Magnetoacoustic Functor Network";
I = "Normalized Output integration/comparison layer";
W = "Composable Action wave or operator carrier";
A = "Carrier Map admissible action/amplitude condition";
R = "Composable Action rotation/curl preservation layer";
T = "Carrier Map local source condition";

Cr0280[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0280 = Cr0280[K0280];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Carrier Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Composable Action rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Carrier Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Composable Action wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Output integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Resonant Magnetoacoustic Functor Network.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0280] Resonant Magnetoacoustic Functor Network}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Limit.}
\begin{equation}
\hbar\rightarrow 0 .
\end{equation}

\paragraph{Stationary-Action Recovery.}
\begin{equation}
\hbar\rightarrow 0
\quad\Longrightarrow\quad
\delta S=0 .
\end{equation}

\paragraph{Primary Derivation.}
The path integral has phase factor:
\begin{equation}
e^{iS/\hbar}.
\end{equation}

As $\hbar\to 0$, non-stationary paths oscillate rapidly and cancel by destructive interference.

The surviving paths satisfy:
\begin{equation}
\delta S=0 .
\end{equation}

Therefore,
\begin{equation}
\boxed{
\hbar\rightarrow 0
\quad\Longrightarrow\quad
\delta S=0 .
}
\end{equation}

\paragraph{Interpretation.}
The semiclassical limit recovers stationary-action classical dynamics from quantum phase cancellation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Resonant Magnetoacoustic Functor Network by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Carrier Map}\par
\[
\omega^2=k^2(c_s^2+v_A^2)
\]
\noindent This names the entry as an actual map between carrier domains rather than a loose metaphor.\par
\noindent\textbf{2. Composable Action}\par
\[
\omega^2=k^2(c_s^2+v_A^2)
\]
\noindent This inserts the map into the ordered TRAWIN chain and makes composition explicit.\par
\noindent\textbf{3. Normalized Output}\par
\[
\omega^2=k^2(c_s^2+v_A^2)
\]
\noindent This closes the entry by requiring that the output land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0280] Resonant Magnetoacoustic Functor Network}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Resonant Magnetoacoustic Functor Network is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A resonant magnetoacoustic functor network maps between categories of acoustic vibrations and electromagnetic oscillations; the coupling is captured by a dynamic susceptibility tensor that adapts across scales. \textbf{Contextual meaning:} The entry reads Resonant Magnetoacoustic Functor Network as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The semiclassical limit recovers stationary-action classical dynamics from quantum phase cancellation.

\tzpsection{Equation Grounding}
Equation anchors:
\[
\Phi_{\mathrm{MA}}:\mathcal{C}_{\mathrm{ac}}\to\mathcal{C}_{\mathrm{mag}},
\qquad
\Phi_{\mathrm{MA}}(g\circ f)=\Phi_{\mathrm{MA}}(g)\circ\Phi_{\mathrm{MA}}(f),
\qquad
\omega^2=k^2(c_s^2+v_A^2).
\]
Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Category-Theoretic Transduction of Sound and Spin}: The algebraic mapping explicitly defining how sound waves bouncing in a cavity perfectly translate into the generation of magnetic spin waves.
\item \textbf{Nodal Mapping of Coupled Oscillations}: The abstract tracking of how the zero-points of an acoustic wave physically align with and drive the zero-points of a magnetic standing wave.
\item \textbf{Relational Network of Phonon-Magnon States}: The complex web of equations defining exactly which sound frequencies are permitted to interact with and boost which specific magnetic frequencies.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0280]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0280_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0280] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Resonant Magnetoacoustic Functor Network}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a resonant magnetoacoustic functor network maps between categories of acoustic
vibrations and electromagnetic oscillations; the coupling is capture...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Resonant Magnetoacoustic Functor Network is valid as a synchronization criterion under
the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0280_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
