\section*{ID8520: TIDAL WAVELENGTH QUANTIZATION Canonical Statutory Formula: λ\_tidal}
\paragraph{Metadata.}
PiID: 3818839994469 | RTEID: RTE:P33085.0521:T4.2485 | UUID: 06f520b1-c409-5c69-9380-6bb85aebcce3

\paragraph{Canonical Statement.}
[ID 1147] TIDAL WAVELENGTH QUANTIZATION Canonical Statutory Formula: \$\textbackslash{}lambda\_\{tidal\} = \textbackslash{}oint\_\{S\textasciicircum{}1\} k \textbackslash{}cdot dl = \textbackslash{}frac\{2\textbackslash{}pi R\_\{\textbackslash{}oplus\}\}\{n\} \textbackslash{}approx 20,015\$ km Formal Technical Dissertation: Theorem 1. Demonstrates that the tidal field wavelength is not arbitrary but is enforced by topological boundary conditions on the Earth's closed manifold (\$S\textasciicircum{}2\$), requiring exactly \$n=2\$ wavelengths to satisfy phase matching. Source:

\paragraph{Canonical Equation.}
\[
\lambda_{tidal} = \oint_{S^1} k \cdot dl = \frac{2\pi R_{\oplus}}{n} \approx 20,015
\]

\paragraph{Dictionary.}
TIDAL WAVELENGTH QUANTIZATION Canonical Statutory Formula: \$ \_tidal = \_S\textasciicircum{}1 k dl = 2 R\_ n 20,015\$ km Formal Technical Dissertation: Theorem 1.

\paragraph{Encyclopedia.}
TIDAL WAVELENGTH QUANTIZATION Canonical Statutory Formula: λ\_tidal is a contour integral, written λ\_tidal = oint\_S\textasciicircum{}1 k · dl = frac2π R\_oplusn ≈ 20,015. It is evaluated by integrating along a closed contour, capturing global or topological properties of the field. It is built from π, S, k, l, R\_, n, defining λ\_tidal. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
