\section*{ID9362: Definition of ⟨𝑂micro ⟩ ⟨𝑂macro ⟩}
\paragraph{Metadata.}
PiID: 0415297002878 | RTEID: RTE:P36354.7251:T3.3527 | UUID: ada58db6-7a23-5391-ae2c-e020a7ffbab1

\paragraph{Canonical Statement.}
cate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0059], [ID 0080], [ID 0081] Node registry\_id\_0082 Support Titles Microscopic Observable Layer; Coarse-Graining Map; Dynamical Consistency Law Test Handle If the macro evolution cannot be recovered by a single admissible coarse-graining map, this entry fails. Canonical Equation Links \$⟨𝑂micro ⟩ ⟨𝑂macro ⟩=C(⟨𝑂micro ⟩)\$ 𝑑 𝑑𝑡 \$⟨𝑄macro ⟩=C(\$ 𝑑 𝑑𝑡 \$⟨𝑄micro ⟩)\$ [ID 0083] TZP Constraints at Quantum Scale TZPID ID0083 UUID 44831401-8840-51de-9f8a-8d36f979a15d Type Quantum-Scale Constraint Scale sub-microscopic / TZP-limited LOC Classification Working routing: QC174 quantum constraints; QC20 zero-point scale analysis arXiv Classification Primary: quant-ph Cross-list: hep-th, gr-qc Canonical Statement At sufficiently

\paragraph{Canonical Equation.}
\[
⟨𝑂micro ⟩ ⟨𝑂macro ⟩=C(⟨𝑂micro ⟩)
\]

\paragraph{Dictionary.}
Definition of ⟨𝑂micro ⟩ ⟨𝑂macro ⟩ — ⟨𝑂micro ⟩ ⟨𝑂macro ⟩=C(⟨𝑂micro ⟩)

\paragraph{Encyclopedia.}
Definition of ⟨𝑂micro ⟩ ⟨𝑂macro ⟩ is an algebraic definition, written ⟨𝑂micro ⟩ ⟨𝑂macro ⟩=C(⟨𝑂micro ⟩). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from C, m, c, r, o, defining ⟨𝑂micro ⟩ ⟨𝑂macro ⟩. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
