\tzpanchor{0633}
\tzpentryheader{0633}{TESSERACT HIERARCHICAL PARTITIONING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{de4219ad-331c-53c6-99b6-9d9203a204a5}}\\
\textbf{PiID} & \tzpcode{7896091736371} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{640}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2434.7802 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.0118 rad}\\
\textbf{TZPID} & \tzpcode{ID0633} & \textbf{Node Dependencies}\quad \tzpidref{0632}\\
\textbf{Registry} & \tzpcode{registry\_id\_0633} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records tesseract hierarchical partitioning through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\delta S[\phi]=0.
\]
\[
\phi \mapsto \phi+\epsilon\,\delta\phi.
\]
\[
S[\phi+\epsilon\delta\phi] = S[\phi] + \epsilon\,\delta S[\phi] + O(\epsilon^2).
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\delta$: point-source delta term that anchors the Green-function response.
    \item $S$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $O$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0633 generated source Wolfram model *)
ClearAll[K0633, Cr0633, T, R, A, W, I, N];
eq0633$1 = HoldForm[DiracDelta*S[phi] == 0];
eq0633$2 = HoldForm[phi -> phi + epsilon*DiracDeltaphi];
eq0633$3 = HoldForm[S[phi + epsilonDiracDeltaphi] == S[phi] + epsilon*DiracDelta*S[phi] + O[epsilon^2]];

K0633 = HoldForm[{eq0633$1, eq0633$2, eq0633$3}];

N = "normalized TRAWIN closure object for TESSERACT HIERARCHICAL PARTITIONING";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Canonical Definition admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Canonical Definition local source condition";

Cr0633[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0633 = Cr0633[K0633];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Canonical Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Canonical Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TESSERACT HIERARCHICAL PARTITIONING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0633] TESSERACT HIERARCHICAL PARTITIONING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\delta S[\phi]=0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $S[\phi]$ be the action functional defined on field configurations $\phi$.  
Physical configurations are those for which the action is stationary under small admissible variations:

\begin{equation}
\phi \mapsto \phi+\epsilon\,\delta\phi .
\end{equation}

Expanding the action to first order in $\epsilon$ gives:

\begin{equation}
S[\phi+\epsilon\delta\phi]
=
S[\phi]
+
\epsilon\,\delta S[\phi]
+
O(\epsilon^2).
\end{equation}

For the configuration to be stationary, the first-order variation must vanish:

\begin{equation}
\boxed{
\delta S[\phi]=0 .
}
\end{equation}

\paragraph{Interpretation.}
The TZP variant of least action states that admissible physical fields extremize the Trawinistic action, including curvature, potential, and degeneracy terms.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TESSERACT HIERARCHICAL PARTITIONING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Canonical Definition}\par
\[
\delta S[\phi]=0.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\phi \mapsto \phi+\epsilon\,\delta\phi.
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
S[\phi+\epsilon\delta\phi] = S[\phi] + \epsilon\,\delta S[\phi] + O(\epsilon^2).
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0633] TESSERACT HIERARCHICAL PARTITIONING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TESSERACT HIERARCHICAL PARTITIONING is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A sub total = bigoplus sub v=1 to the power 16 (V sub v otimes mathcal S 9600 ). \textbf{Contextual meaning:} The entry reads TESSERACT HIERARCHICAL PARTITIONING as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP variant of least action states that admissible physical fields extremize the Trawinistic action, including curvature, potential, and degeneracy terms.

\tzpsection{Equation Grounding}
Equation anchors: A sub total = bigoplus sub v=1 to the power 16 (V sub v otimes S 9600 ); mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{4D Hypercube Subspace Slicing}: The mind-bending mathematical process of taking a four-dimensional box of data and neatly chopping it up into smaller, easily sortable 3D cubes.
\item \textbf{Nested Geometric Data Structures}: The organization of the massive quantum memory banks into a Russian-doll-like hierarchy, where opening one folder just reveals smaller, more complex folders inside.
\item \textbf{High-Dimensional Address Indexing}: The complex numbering system required to accurately locate one single, specific piece of information floating somewhere inside a space that has more directions than humanly imaginable.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0633]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0633_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0633] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TESSERACT HIERARCHICAL PARTITIONING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records tesseract hierarchical partitioning through the Septenary derivation
layer, using the displayed relations as operational anchors...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TESSERACT HIERARCHICAL PARTITIONING is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0633_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
