\section*{ID9357: Definition of 𝑤∈Z 𝐻}
\paragraph{Metadata.}
PiID: 8394004152970 | RTEID: RTE:P36335.3090:T3.3207 | UUID: f948381b-10d7-5d62-bd39-dd68d2e79518

\paragraph{Canonical Statement.}
Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0040] Node registry\_id\_0041 Support Titles Helicity Integral; Winding Index; Flux-Quantized Helicity Test Handle A magnetic configuration with fixed flux and preserved winding class but non-integer helicity jumps would violate this quantization law. Canonical Equation Links 𝐻= \$∫\$ 𝑉 A·B 𝑑3𝑥 \$𝑤∈Z 𝐻=𝑤Φ\$ [ID 0042] Magnetic Helicity as Scale-Invariant Constraint TZPID ID0042 UUID bf1444a8-f6b0-5ffb-be6d-bec2087b87d7 Type Constraint Law Scale scale-invariant helicity LOC Classification Working routing: QC809 helicity constraints; QC20 scaling laws arXiv Classification Primary: physics.plasm-ph Cross-list: astro-ph.SR, math-ph Canonical Statement The TRAWIN framework treats helicity as a scale-resis

\paragraph{Canonical Equation.}
\[
𝑤∈Z 𝐻=𝑤Φ
\]

\paragraph{Dictionary.}
Definition of 𝑤∈Z 𝐻 — 𝑤∈Z 𝐻=𝑤Φ

\paragraph{Encyclopedia.}
Definition of 𝑤∈Z 𝐻 is an algebraic definition, written 𝑤∈Z 𝐻=𝑤Φ. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
