\section*{ID9146: Relation: θ\_j(t))|.}
\paragraph{Metadata.}
PiID: 0298969594699 | RTEID: RTE:P35515.9491:T1.9707 | UUID: 0c7bb5e3-2bf9-53c5-9ae2-ffc4b96d6666

\paragraph{Canonical Statement.}
e planetary Kuramoto model. Retrograde rotation is represented by negative periods. Dependencies: 115 Derivable Consequences: Natural frequency vector; coupling matrix values; ranking of coupling strengths; baseline for simulation. Falsifiability / Test Handle: Update with refined observational data and test sensitivity of results to parameter changes. 1.0.18 ID 117: SpinCoherence Order Parameter Type: Operator Formal Statement: Define the coherence measure r(k0) = (1/N) \$·|Σ\_\{j=1\}ˆ\{N\}\$ exp(i \$θ\_j(t))|.\$ In numerical simulations using the planetary data and a range of coupling constants, r was observed to be approximately 0.18–0.54 depending on coupling strength, with no strong global synchronization. Interpretive Meaning: This order parameter quantifies how aligned the planetary spins become under the Kuramoto model. Low values indicate incoherence; partial clustering can occur at particular cou

\paragraph{Canonical Equation.}
\[
θ_j(t))|.
\]

\paragraph{Dictionary.}
Relation: θ\_j(t))|. — θ\_j(t))|.

\paragraph{Encyclopedia.}
Relation: θ\_j(t))|. is a symbolic expression, written θ\_j(t))|.. It introduces a symbol or relation used elsewhere in the framework. It is built from j. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
