\tzpanchor{0079}
\tzpentryheader{0079}{Quantum Chaos Indicators}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9da73010-6967-5eee-92ac-4744951fa655}}\\
\textbf{PiID} & \tzpcode{9862803482534} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{86}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{306.7745 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.5055 rad}\\
\textbf{TZPID} & \tzpcode{ID0079} & \textbf{Node Dependencies}\quad \tzpidref{0062}\\
\textbf{Registry} & \tzpcode{registry\_id\_0079} & \textbf{Scale}\quad operator scrambling\\
\textbf{LOC Classification} & QC174 quantum chaos & QC20 Lyapunov diagnostics\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: hep-th, cond-mat.stat-mech & \\
\textbf{Primary Support} & Evolving Operator Pair & OTOC Diagnostic\\
\textbf{Closure Support} & Lyapunov-Type Growth & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This quantifies the sensitivity of quantum systems to initial conditions; the bound on chaos is influenced by the geometry.

\tzpsection{Canonical Equation}
\[
F(t)
=
\left\langle
\left[W(t),V(0)\right]^{\dagger}
\left[W(t),V(0)\right]
\right\rangle
\]
\[
F(t) \sim e^{\lambda_{\mathrm{L}} t}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $F$: source equation symbol.
    \item $W$: source equation symbol.
    \item $V$: auxiliary target state or comparison variable.
    \item $\lambda_{\mathrm{L}}$: source equation symbol.
    \item $t$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0079 generated source Wolfram model *)
ClearAll[K0079, Cr0079, T, R, A, W, I, N];
eq0079$1 = HoldForm[F[t] == Inner[Commutator[W[t], V[0]]^Dagger[W[t], V[0]]]];
eq0079$2 = HoldForm[SimilarTo[F[t], e^(lambdaL*t)]];
eq0079$3 = HoldForm[Tuple[W[t], V[0]]];

K0079 = HoldForm[{eq0079$1, eq0079$2, eq0079$3}];

N = "normalized TRAWIN closure object for Quantum Chaos Indicators";
I = "Lyapunov-Type Growth integration/comparison layer";
W = "OTOC Diagnostic wave or operator carrier";
A = "Evolving Operator Pair admissible action/amplitude condition";
R = "OTOC Diagnostic rotation/curl preservation layer";
T = "Evolving Operator Pair local source condition";

Cr0079[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0079 = Cr0079[K0079];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Evolving Operator Pair local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ OTOC Diagnostic rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Evolving Operator Pair admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ OTOC Diagnostic wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Lyapunov-Type Growth integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum Chaos Indicators.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0079] Quantum Chaos Indicators}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
F(t)
=
\left\langle
[W(t),V(0)]^\dagger
[W(t),V(0)]
\right\rangle .
\end{equation}

\paragraph{Growth Law.}
\begin{equation}
F(t)\sim e^{\lambda_L t}.
\end{equation}

\paragraph{Primary Derivation.}
Quantum chaos is measured by how rapidly initially separated operators fail to commute under time evolution.

The commutator is:
\begin{equation}
[W(t),V(0)] .
\end{equation}

Its squared magnitude is:
\begin{equation}
[W(t),V(0)]^\dagger[W(t),V(0)] .
\end{equation}

Taking the expectation value gives the chaos indicator:
\begin{equation}
\boxed{
F(t)
=
\left\langle
[W(t),V(0)]^\dagger
[W(t),V(0)]
\right\rangle .
}
\end{equation}

The early-time growth is characterized by a Lyapunov exponent:
\begin{equation}
F(t)\sim e^{\lambda_L t}.
\end{equation}

\paragraph{Interpretation.}
The OTOC-style quantity $F(t)$ measures operator scrambling and quantum sensitivity to initial structure.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum Chaos Indicators by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Evolving Operator Pair}\par
\[
(W(t),V(0))
\]
\noindent This identifies the observables used to probe scrambling.\par
\noindent\textbf{2. OTOC Diagnostic}\par
\[
F(t)
=
\left\langle
\left[W(t),V(0)\right]^{\dagger}
\left[W(t),V(0)\right]
\right\rangle
\]
\noindent This measures the growth of operator noncommutativity.\par
\noindent\textbf{3. Lyapunov-Type Growth}\par
\[
F(t) \sim e^{\lambda_{\mathrm{L}} t}
\]
\noindent This closes the progression by extracting the scrambling rate from the OTOC behavior.\par

\clearpage
\noindent\textbf{[ID 0079] Quantum Chaos Indicators}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum Chaos Indicators is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This quantifies the sensitivity of quantum systems to initial conditions; the bound on chaos is influenced by the geometry. \textbf{Contextual meaning:} The entry reads Quantum Chaos Indicators as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry gives the registry a quantitative chaos probe that interfaces naturally with transport, criticality, and information scrambling. It is the dynamic complement to the static entanglement and critical-scaling indicators. \textbf{Lemma support:} Evolving Operator Pair; OTOC Diagnostic; Lyapunov-Type Growth.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The OTOC-style quantity F(t) measures operator scrambling and quantum sensitivity to initial structure.

\tzpsection{Equation Grounding}
Equation anchors: Quantum chaos in the Trawinistic framework is diagnosed using out-of-time-ordered correlators (OTOCs) F(t)= [ W(t),V(0) ] ? [ W(t),V(0) ] rangleF(t)= [ W(t), V(0) ] to the power dagger [ W(t),V(0) ] rangleF(t)= [ W(t),V(0) ] ? [ W(t),V(0) ] , whose exponential growth rate (Lyapunov exponent) is bounded by curvature and the zero-point energy scale. Quantum chaos in the Trawinistic framework is diagnosed using out-of-time-ordered correlators (OTOCs) F(t)= [ W(t),V(0) ] ? [ W(t),V(0) ] rangleF(t)= [ W(t), V(0) ] to the power dagger [ W(t),V(0) ] rangleF(t)= [ W(t),V(0) ] ? [ W(t),V(0) ] , whose exponential growth rate (Lyapunov exponent) is bounded by curvature and the zero-point energy scale.

\tzpsection{Interpretive Role}
This entry gives the registry a quantitative chaos probe that interfaces naturally with transport, criticality, and information scrambling. It is the dynamic complement to the static entanglement and critical-scaling indicators.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{State-Level Chaos Indicators}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Quantum-State Analogue}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Terminology}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0079]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0079_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0079] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum Chaos Indicators}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this quantifies the sensitivity of quantum systems to initial conditions; the bound on
chaos is influenced by the geometry

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum Chaos Indicators is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0079_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
