\tzpanchor{0519}
\tzpentryheader{0519}{LENSE-THIRRING RELATIVISTIC AUDIT}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{5f6ea3a2-0f47-56d5-b1db-439e7df3e45c}}\\
\textbf{PiID} & \tzpcode{0860213949463} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{526}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1995.9761 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.2888 rad}\\
\textbf{TZPID} & \tzpcode{ID0519} & \textbf{Node Dependencies}\quad \tzpidref{0518}\\
\textbf{Registry} & \tzpcode{registry\_id\_0519} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Frame-Dragging Frequency & Gravitomagnetic Field\\
\textbf{Closure Support} & Audit Ratio & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Bmag = frac\{GNewton\}\{c\textasciicircum{}2\} left( frac\{3(mathbf\{J\}*mathbf\{r\})mathbf\{r\}\}\{r\textasciicircum{}5\} - frac\{mathbf\{J\}\}\{r\textasciicircum{}3\} right)

\tzpsection{Canonical Equation}
\[
Omega_{\mathrm{LT}}(r)=\frac{2GJ}{c^2 r^3}
\]
\[
B_{\mathrm{g}}(r)=\frac{G}{c^2}\!\left(\frac{3(J\cdot \hat r)\hat r-J}{r^3}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $c$: speed of light or relativistic conversion factor.
    \item $B_{\mathrm{g}}(r)$: source equation symbol.
    \item $G$: source equation symbol.
    \item $J$: source equation symbol.
    \item $\Omega_{\mathrm{obs}}$: angular frequency term in the source equation.
    \item $\Omega_{\mathrm{LT}}$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0519 generated source Wolfram model *)
ClearAll[K0519, Cr0519, T, R, A, W, I, N];
eq0519$1 = HoldForm[OmegaLT[r] == (2*G*J)/(c^2*r^3)];
eq0519$2 = HoldForm[BG[r] == (G/c^2)*((3*(J*hat*r)*hat*r - J)/r^3)];
eq0519$3 = HoldForm[PiAudit == OmegaObs/OmegaLT];

K0519 = HoldForm[{eq0519$1, eq0519$2, eq0519$3}];

N = "normalized TRAWIN closure object for LENSE-THIRRING RELATIVISTIC AUDIT";
I = "Audit Ratio integration/comparison layer";
W = "Gravitomagnetic Field wave or operator carrier";
A = "Frame-Dragging Frequency admissible action/amplitude condition";
R = "Gravitomagnetic Field rotation/curl preservation layer";
T = "Frame-Dragging Frequency local source condition";

Cr0519[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0519 = Cr0519[K0519];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Frame-Dragging Frequency local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Gravitomagnetic Field rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Frame-Dragging Frequency admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Gravitomagnetic Field wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Audit Ratio integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for LENSE-THIRRING RELATIVISTIC AUDIT.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0519] LENSE-THIRRING RELATIVISTIC AUDIT}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Box_T\phi
=
g^{ab}
\nabla^{T}_{a}
\nabla^{T}_{b}
\phi .
\end{equation}

\paragraph{Primary Derivation.}
The ordinary d'Alembertian is the metric contraction of two covariant derivatives acting on a field.  
In Trawinistic geometry, replace the ordinary covariant derivative with $\nabla^T$:

\begin{equation}
\nabla_a\nabla_b\phi
\quad\longrightarrow\quad
\nabla^T_a\nabla^T_b\phi .
\end{equation}

Then contract using the regularized inverse metric $g^{ab}$:

\begin{equation}
\Box_T\phi
=
g^{ab}
\nabla^{T}_{a}
\nabla^{T}_{b}
\phi .
\end{equation}

\paragraph{Interpretation.}
$\Box_T$ extends wave propagation and field equations into the Trawinistic manifold by replacing ordinary derivatives with TZP-compatible covariant derivatives.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors LENSE-THIRRING RELATIVISTIC AUDIT by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Frame-Dragging Frequency}\par
\[
Omega_{\mathrm{LT}}(r)=\frac{2GJ}{c^2 r^3}
\]
\noindent This fixes the Lense--Thirring frame-dragging frequency used as the audit baseline.\par
\noindent\textbf{2. Gravitomagnetic Field}\par
\[
B_{\mathrm{g}}(r)=\frac{G}{c^2}\!\left(\frac{3(J\cdot \hat r)\hat r-J}{r^3}\right)
\]
\noindent This identifies the associated gravitomagnetic field generated by the rotating source.\par
\noindent\textbf{3. Audit Ratio}\par
\[
Pi_{\mathrm{audit}}=\frac{\Omega_{\mathrm{obs}}}{\Omega_{\mathrm{LT}}}
\]
\noindent This closes the entry by normalizing the observed precession against the relativistic prediction.\par

\clearpage
\noindent\textbf{[ID 0519] LENSE-THIRRING RELATIVISTIC AUDIT}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
LENSE-THIRRING RELATIVISTIC AUDIT is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Bmag = frac GNewton c to the power 2 left( frac 3(mathbf J *mathbf r )mathbf r r to the power 5 - frac mathbf J r to the power 3 right). \textbf{Contextual meaning:} The entry reads LENSE-THIRRING RELATIVISTIC AUDIT as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the relativistic audit through frame-dragging frequency, gravitomagnetic field, and an observational audit ratio instead of malformed Christoffel prose. \textbf{Lemma support:} Frame-Dragging Frequency; Gravitomagnetic Field; Audit Ratio.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub T extends wave propagation and field equations into the Trawinistic manifold by replacing ordinary derivatives with TZP-compatible covariant derivatives.

\tzpsection{Equation Grounding}
Equation anchors: Omega sub LT (r)=ratio 2GJ c to the power 2 r to the power 3; B sub g (r)=ratio G c to the power 2 (ratio 3(Jdot hat r)hat r-J r to the power 3 ); and Pi sub audit =ratio Omega sub obs Omega sub LT. Proof route: show that the stated gravitomagnetic field induces the quoted Lense--Thirring precession scale and supports the audit ratio. Formalization route: prove that the audit ratio is dimensionless and correctly compares observed precession to the relativistic baseline.

\tzpsection{Interpretive Role}
The entry now states the relativistic audit through frame-dragging frequency, gravitomagnetic field, and an observational audit ratio instead of malformed Christoffel prose.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Frame-Dragging Verification}: The rigorous experimental cross-check to ensure that the spinning mass of the machine is actually twisting spacetime exactly as Einstein predicted.
\item \textbf{Gravitomagnetic Precession Tracking}: The incredibly delicate measurement of how a tiny, perfect gyroscope slowly wobbles off-axis simply because the space around it is rotating.
\item \textbf{Off-Diagonal Metric Calibration}: The fine-tuning of the sensors to isolate the incredibly weak relativistic effects from the overwhelming background noise of the Earth's own gravity.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0519]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0519_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0519] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont LENSE-THIRRING RELATIVISTIC AUDIT}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} bmag = frac\textbackslash{}\textasciicircum{}2\textbackslash{} left( frac\textbackslash{}3(mathbf\textbackslash{}*mathbf\textbackslash{})mathbf\textbackslash{}\textbackslash{}\textasciicircum{}5\textbackslash{} - frac\textbackslash{}\textbackslash{}\textasciicircum{}3\textbackslash{} right)

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``LENSE-THIRRING RELATIVISTIC AUDIT is valid as a spectral relation when frequency, phase,
and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0519_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
