\tzpanchor{0445}
\tzpentryheader{0445}{Squid Flux Tomography Installation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{02952169-f74a-5a07-8a44-846f38cf14d5}}\\
\textbf{PiID} & \tzpcode{1854807446237} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{452}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1728.0338 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.8473 rad}\\
\textbf{TZPID} & \tzpcode{ID0445} & \textbf{Node Dependencies}\quad \tzpidref{0444}\\
\textbf{Registry} & \tzpcode{registry\_id\_0445} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Transfer Map\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 445 formalizes the installation of Superconducting Quantum Interference Devices (SQUIDs) to characterize system performance. SQUIDs provide the sensitivity required to detect the infinitesimal changes in magnetic flux that signal successful energy extraction from the vacuum ground state. These sensors are placed at the 12 nodes of the DAANSsphere to provide a real time map of the Jp field strength. Extraction Mapping: Directly measures the nPhi0 quantized packets retrieved by the Energy Channel. Feedback Integration: The SQUID output is fed into the Hcontrol loop to maintain optimal resonance.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathbf{y}=(\phi_0,\ldots,\phi_{N-1},\theta_0,\ldots,\theta_{N-1})
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\phi_0$: reference zero-point flux or normalization flux.
    \item $\phi_{N-1}$: flux, phase, or topological map term in the source equation.
    \item $N$: normalization, count, or closure parameter in the entry relation.
    \item $\theta_0$: source equation symbol.
    \item $\theta_{N-1}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0445 generated source Wolfram model *)
ClearAll[K0445, Cr0445, T, R, A, W, I, N];
eq0445$1 = HoldForm[$y == Tuple[phi0, ldots, phiN1, theta0, ldots, thetaN1]*$];

K0445 = HoldForm[{eq0445$1}];

N = "normalized TRAWIN closure object for Squid Flux Tomography Installation";
I = "Squid Flux Tomography Installation integration/comparison layer";
W = "Squid Flux Tomography Installation wave or operator carrier";
A = "Squid Flux Tomography Installation admissible action/amplitude condition";
R = "Squid Flux Tomography Installation rotation/curl preservation layer";
T = "Squid Flux Tomography Installation local source condition";

Cr0445[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0445 = Cr0445[K0445];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Squid Flux Tomography Installation local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Squid Flux Tomography Installation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Squid Flux Tomography Installation admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Squid Flux Tomography Installation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Squid Flux Tomography Installation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Squid Flux Tomography Installation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0445] Squid Flux Tomography Installation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
g_{\mu}
=
\frac{\mu}
{MR^2\Omega}.
\end{equation}

\paragraph{Primary Derivation.}
Starting from the scaling law:

\begin{equation}
\mu
=
kMR^2\Omega ,
\end{equation}

divide both sides by the natural rotational magnetic scale:

\begin{equation}
MR^2\Omega .
\end{equation}

This gives:

\begin{equation}
\frac{\mu}{MR^2\Omega}=k .
\end{equation}

Define the dimensionless gyromagnetic coupling constant as:

\begin{equation}
\boxed{
g_{\mu}
=
\frac{\mu}
{MR^2\Omega}.
}
\end{equation}

\paragraph{Interpretation.}
$g_{\mu}$ removes ordinary scale factors from the magnetic moment and isolates the dimensionless coupling strength of the rotating system.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Squid Flux Tomography Installation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathbf{y}=(\phi_0,\ldots,\phi_{N-1},\theta_0,\ldots,\theta_{N-1})
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0445] Squid Flux Tomography Installation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Squid Flux Tomography Installation is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 445 formalizes the installation of Superconducting Quantum Interference Devices (SQUIDs) to characterize system performance. SQUIDs provide the sensitivity required to detect the infinitesimal changes in magnetic flux that signal successful energy extraction from the vacuum ground state. These sensors are placed at the 12 nodes of the DAANSsphere to provide a real time map of the Jp field strength. Extraction Mapping: Directly measures the nPhi0 quantized packets retrieved by the Energy Channel. Feedback Integration: The SQUID output is fed into the Hcontrol loop to maintain optimal resonance.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathbf{y}=(\phi_0,\ldots,\phi_{N-1},\theta_0,\ldots,\theta_{N-1})
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 445 formalizes the installation of Superconducting Quantum Interference Devices (SQUIDs) to characterize system performance. SQUIDs provide the sensitivity required to detect the infinitesimal changes in magnetic flux that signal successful energy extraction from the vacuum ground state. These sensors are placed at the 12 nodes of the DAANSsphere to provide a real time map of the Jp field strength. Extraction Mapping: Directly measures the nPhi0 quantized packets retrieved by the Energy Channel. Feedback Integration: The SQUID output is fed into the Hcontrol loop to maintain optimal resonance.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Squid Flux Tomography Installation by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Squid Flux Tomography Installation; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0445]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0445].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0445] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Squid Flux Tomography Installation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} phi = n Phi\textbackslash{}\_0 implies text Flux Detection\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``SQUID FLUX TOMOGRAPHY INSTALLATION is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0445].
\par\endgroup
\vfill
\endgroup
\endgroup
