\tzpanchor{0002}
\tzpentryheader{0002}{Trawinistic Manifold}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{73321d3f-caa4-5712-bcd8-267d3d7e73ad}}\\
\textbf{PiID} & \tzpcode{1592653589793} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{9}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{03.8832 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.0064 rad}\\
\textbf{TZPID} & \tzpcode{ID0002} & \textbf{Node Dependencies}\quad \tzpidref{0000}\\
\textbf{Registry} & \tzpcode{registry\_id\_0002} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 differential geometry & QC gravitation and relativity\\
\textbf{arXiv Classification} & Primary: math.DG \quad Cross-list: gr-qc, math-ph & \\
\textbf{Primary Support} & Singular Metric Locus & Exterior Regularity\\
\textbf{Closure Support} & Inverse-Metric Split & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A Trawinistic manifold is a smooth manifold $(M,g)$ equipped with a Lorentzian metric $g$ such that $\det g|_p = 0$ at the TZP and $g$ is non-degenerate elsewhere.

\tzpsection{Canonical Equation}
\[
(M,g)\ \text{is Trawinistic}
\quad \Longleftrightarrow \quad
\det g\vert_{p}=0
\ \text{and}\ 
\det g(x)\neq 0 \ \text{for}\ x\neq p
\]
\[
g^{-1}(x)\ \text{exists for}\ x\neq p,
\qquad
g^{-1}\vert_{p}\ \text{does not exist}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $M$: source equation symbol.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $T$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $g(x)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0002 generated source Wolfram model *)
ClearAll[K0002, Cr0002, T, R, A, W, I, N];
eq0002$1 = HoldForm[Pair[M, g] == Det*gP == 0 && Det*g[x] != 0 && x != p];
eq0002$2 = HoldForm[TZPSequence[(x*x)/g != p, (_*p)/g]];
eq0002$3 = HoldForm[Det*gP == 0];
eq0002$4 = HoldForm[Det*g[x] != 0*(x != p)];
eq0002$5 = HoldForm[TZPSequence[(_*p)/g, (x*x)/g != p]];

K0002 = HoldForm[{eq0002$1, eq0002$2, eq0002$3, eq0002$4, eq0002$5}];

N = "normalized TRAWIN closure object for Trawinistic Manifold";
I = "Inverse-Metric Split integration/comparison layer";
W = "Exterior Regularity wave or operator carrier";
A = "Singular Metric Locus admissible action/amplitude condition";
R = "Exterior Regularity rotation/curl preservation layer";
T = "Singular Metric Locus local source condition";

Cr0002[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0002 = Cr0002[K0002];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Singular Metric Locus local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Exterior Regularity rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Singular Metric Locus admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Exterior Regularity wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Inverse-Metric Split integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Trawinistic Manifold.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0002] Trawinistic Manifold}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
For any closed loop $\GammaLoop$ encircling the TZP in $M$, there exists a homotopy deforming $\GammaLoop$ into a lemniscate whose self-intersection occurs at $p$.

\paragraph{Primary Derivation.}
Let $\GammaLoop:S^1\to M$ be a closed loop surrounding $p$. Since $p$ is the limiting degeneracy point, paths enclosing $p$ may be continuously deformed while preserving their winding relation to $p$.

Introduce a homotopy:

\begin{equation}
H:S^1\times[0,1]\to M .
\end{equation}

At $s=0$, the homotopy recovers the original loop:

\begin{equation}
H(\theta,0)=\GammaLoop(\theta).
\end{equation}

At $s=1$, the loop is deformed into a figure-eight curve:

\begin{equation}
H(\theta,1)=\Lambda(\theta),
\end{equation}

where $\Lambda$ is a lemniscatic curve satisfying:

\begin{equation}
\Lambda(\theta_1)=\Lambda(\theta_2)=p,
\qquad
\theta_1\neq\theta_2 .
\end{equation}

Thus the self-intersection of the limiting loop is identified with the TZP.

\paragraph{Interpretation.}
The lemniscate is the canonical shape of TZP recurrence: two lobes, one crossing, one central point. This turns the zero point into a geometric crossing rather than a simple endpoint.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Trawinistic Manifold by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Singular Metric Locus}\par
\[
\det g\vert_{p}=0
\]
\noindent This identifies the exact geometric location where ordinary metric structure breaks and the Trawinistic manifold departs from standard relativity.\par
\noindent\textbf{2. Exterior Regularity}\par
\[
\det g(x)\neq 0 \qquad (x\neq p)
\]
\noindent This preserves usable differential geometry everywhere outside the zero point, so the singularity is localized rather than diffuse.\par
\noindent\textbf{3. Inverse-Metric Split}\par
\[
g^{-1}\vert_{p}\ \text{does not exist},
\qquad
g^{-1}(x)\ \text{exists for}\ x\neq p
\]
\noindent This completes the progression by separating the normalized exterior geometry from the singular anchor that all later constructions reference.\par

\clearpage
\noindent\textbf{[ID 0002] Trawinistic Manifold}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Lemniscatic Self-Intersection is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} For any closed loop GammaLoop encircling the TZP in Manifold, there exists a homotopy that deforms GammaLoop into a lemniscate (figure-eight) whose self-intersection occurs at p. \textbf{Contextual meaning:} The entry reads Lemniscatic Self-Intersection as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This definition gives later IDs a place to live: loops can encircle the TZP, dimensions can branch there, and time or field quantities can acquire singular corrections while remaining well-defined off the anchor. \textbf{Lemma support:} Singular Metric Locus; Exterior Regularity; Inverse-Metric Split.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP is marked by metric degeneracy. This is the first mathematical signature that ordinary geometry fails at the zero point and must be replaced by a Trawinistic structure.

\tzpsection{Equation Grounding}
Equation anchors: For any closed loop GammaLoop encircling the TZP in Manifold, there exists a homotopy that deforms GammaLoop into a lemniscate (figure-eight) whose self-intersection occurs at p. For any closed loop GammaLoop encircling the TZP in Manifold, there exists a homotopy that deforms GammaLoop into a lemniscate (figure-eight) whose self-intersection occurs at p.

\tzpsection{Interpretive Role}
This definition gives later IDs a place to live: loops can encircle the TZP, dimensions can branch there, and time or field quantities can acquire singular corrections while remaining well-defined off the anchor.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Trawinistic Geometric Space Label Id 001}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\item \textbf{Geometric Space Geometric Space Geometric Analogue}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\item \textbf{Geometric Space Terminology}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0002]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0002_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0002] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Trawinistic Manifold}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} for any closed loop  encircling the TZP in , there exists a homotopy that deforms 
into a lemniscate (figure-eight) whose self-intersection o...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Lemniscatic Self-Intersection is valid as a tensorial/geometric statement when the
stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0002_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
