\section*{ID9103: Definition of (1+ε)ECas(L)}
\paragraph{Metadata.}
PiID: 9411303150952 | RTEID: RTE:P35348.9706:T1.6956 | UUID: 7cfe75d3-b96f-5238-b7a2-ad008306f0b0

\paragraph{Canonical Statement.}
difications to correlation functions; interplay with vacuum polarization. Falsifiability / Test Handle: Experimental measurement of boundaryinduced forces or shifts that disagree with this operator’s predictions would test its validity. 0.0.58 ID 056: CasimirType Phenomena Type: Conservation Law Formal Statement: The Casimir energy between two uncharged, parallel boundaries separated by distance LLL in the Trawinistic framework is \$ECas(L)=π2720L3(1+)E \{\textbackslash{}text\{Cas\}\}(L)=\$ -\textbackslash{}frac\{\textbackslash{}piˆ2\}\{720 Lˆ3\} \$(1+\textbackslash{}epsilon)ECas(L)=720L3π2(1+),\$ where \textbackslash{}epsilon encodes curvature and TZP corrections. Interpretive Meaning: Even empty space exerts forces due to vacuum fluctuations; these forces are modified by the TZP environment. Dependencies: ID 055, ID 051 Derivable Consequences: Attraction between plates in vacuum; constraints on boundary configurations; contributions to renormalisation; insights into vacuum energy problem. Falsifiabilit

\paragraph{Canonical Equation.}
\[
(1+\epsilon)ECas(L)=720L3π2(1+),
\]

\paragraph{Dictionary.}
Definition of (1+ε)ECas(L) — (1+ε)ECas(L)=720L3π2(1+)

\paragraph{Encyclopedia.}
Definition of (1+ε)ECas(L) is an algebraic definition, written (1+ε)ECas(L)=720L3π2(1+). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from L, defining (1+ε)ECas(L). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
