\tzpanchor{0071}
\tzpentryheader{0071}{Qubit Manifold Embedding}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{46918399-7596-54c1-b54d-3ac37fa9dde4}}\\
\textbf{PiID} & \tzpcode{6286208998628} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{78}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{275.7088 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.4543 rad}\\
\textbf{TZPID} & \tzpcode{ID0071} & \textbf{Node Dependencies}\quad \tzpidref{0070}\\
\textbf{Registry} & \tzpcode{registry\_id\_0071} & \textbf{Scale}\quad two-level quantum geometry\\
\textbf{LOC Classification} & QC174 qubit geometry & QA613 embedded manifolds\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: math-ph, gr-qc & \\
\textbf{Primary Support} & Two-Level Hilbert Space & Projective State Space\\
\textbf{Closure Support} & TRAWIN Embedding & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Qubits are represented by two-level systems embedded in the Trawinistic manifold such that their Bloch sphere is mapped to a submanifold of $M$; the embedding respects the curvature and lemniscatic structure, allowing local operations and topological protection.

\tzpsection{Canonical Equation}
\[
\mathcal{H}_{\mathrm{qubit}} \cong \mathbb{C}^{2}
\]
\[
\mathbb{CP}^{1} \cong S^{2} \hookrightarrow M
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{H}_{\mathrm{qubit}}$: source equation symbol.
    \item $C$: speed of light or relativistic conversion factor.
    \item $S^{2}$: two-sphere target domain.
    \item $M$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0071 generated source Wolfram model *)
ClearAll[K0071, Cr0071, T, R, A, W, I, N];
eq0071$1 = HoldForm[HQubitcong*C^2];
eq0071$2 = HoldForm[CP^1*cong*S^2*hookrightarrow*M];
eq0071$3 = HoldForm[CP^1*cong*S^2];

K0071 = HoldForm[{eq0071$1, eq0071$2, eq0071$3}];

N = "normalized TRAWIN closure object for Qubit Manifold Embedding";
I = "TRAWIN Embedding integration/comparison layer";
W = "Projective State Space wave or operator carrier";
A = "Two-Level Hilbert Space admissible action/amplitude condition";
R = "Projective State Space rotation/curl preservation layer";
T = "Two-Level Hilbert Space local source condition";

Cr0071[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0071 = Cr0071[K0071];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Two-Level Hilbert Space local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Projective State Space rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Two-Level Hilbert Space admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Projective State Space wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TRAWIN Embedding integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Qubit Manifold Embedding.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0071] Qubit Manifold Embedding}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
|\psi\rangle = \alpha|0\rangle+\beta|1\rangle,
\qquad
|\alpha|^2+|\beta|^2=1 .
\end{equation}

\paragraph{Embedding Map.}
\begin{equation}
\iota:S^2_{\mathrm{Bloch}}\hookrightarrow M .
\end{equation}

\paragraph{Primary Derivation.}
A qubit is a normalized two-level quantum state. Its amplitudes satisfy
\begin{equation}
|\alpha|^2+|\beta|^2=1 .
\end{equation}

Modulo global phase, the normalized qubit state corresponds to a point on the Bloch sphere:
\begin{equation}
|\psi\rangle \longleftrightarrow S^2_{\mathrm{Bloch}} .
\end{equation}

In the Trawinistic setting, this Bloch sphere is embedded into the ambient manifold by
\begin{equation}
\boxed{
\iota:S^2_{\mathrm{Bloch}}\hookrightarrow M .
}
\end{equation}

\paragraph{Interpretation.}
The qubit is treated as both a Hilbert-space state and a geometric object embedded into the Trawinistic manifold.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Qubit Manifold Embedding by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Two-Level Hilbert Space}\par
\[
\mathcal{H}_{\mathrm{qubit}} \cong \mathbb{C}^{2}
\]
\noindent This fixes the qubit as the simplest nontrivial qunit.\par
\noindent\textbf{2. Projective State Space}\par
\[
\mathbb{CP}^{1} \cong S^{2}
\]
\noindent This identifies the pure-state geometry as the Bloch sphere.\par
\noindent\textbf{3. TRAWIN Embedding}\par
\[
\mathbb{CP}^{1} \cong S^{2} \hookrightarrow M
\]
\noindent This closes the progression by placing the qubit geometry inside the ambient manifold.\par

\clearpage
\noindent\textbf{[ID 0071] Qubit Manifold Embedding}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Qubit Manifold Embedding is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Qubits are represented by two-level systems embedded in the Trawinistic manifold such that their Bloch sphere is mapped to a submanifold of M; the embedding respects the curvature and lemniscatic structure, allowing local operations and topological protection. \textbf{Contextual meaning:} The entry reads Qubit Manifold Embedding as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry gives a geometric home to the basic information unit. It supports gate transport, geometric phase accumulation, and protected encoding of two-level states on the manifold. \textbf{Lemma support:} Two-Level Hilbert Space; Projective State Space; TRAWIN Embedding.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The qubit is treated as both a Hilbert-space state and a geometric object embedded into the Trawinistic manifold.

\tzpsection{Equation Grounding}
Equation anchors: Qubits are represented by two-level systems embedded in the Trawinistic manifold such that their Bloch sphere is mapped to a submanifold of MMM; the embedding respects the curvature and lemniscatic structure, allowing local operations and topological protection. Qubits are represented by two-level systems embedded in the Trawinistic manifold such that their Bloch sphere is mapped to a submanifold of MMM; the embedding respects the curvature and lemniscatic structure, allowing local operations and topological protection.

\tzpsection{Interpretive Role}
This entry gives a geometric home to the basic information unit. It supports gate transport, geometric phase accumulation, and protected encoding of two-level states on the manifold.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Qubit Geometric Space Embedding}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\item \textbf{Geometric Space Geometric Analogue}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\item \textbf{Geometric Space Terminology}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0071]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0071_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0071] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Qubit Manifold Embedding}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} qubits are represented by two-level systems embedded in the Trawinistic manifold such
that their Bloch sphere is mapped to a submanifold of M; th...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Qubit Manifold Embedding is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0071_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
