\section*{ID9342: Definition of 𝐹}
\paragraph{Metadata.}
PiID: 1513755600372 | RTEID: RTE:P36277.0606:T3.2248 | UUID: e09f2905-4cfd-5fe8-b63f-3b8a379b7d3b

\paragraph{Canonical Statement.}
ertificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0154], [ID 0153] Node registry\_id\_0155 Support Titles Invariant Integral; Field-Strength Origin; Obstruction Detection Test Handle If a nonzero Chern–Simons invariant can occur while the topological obstruction remains trivial, the obstruction class fails. Canonical Equation Links CS(𝐴)= 1 4𝜋 \$∫ Σ\$ \$Tr(𝐹∧𝐹\$ ) \$𝐹=𝑑𝐴+𝐴∧𝐴 CS(𝐴)≠0 =⇒ Otop≠0\$ [ID 0156] Higher Gerbe Structure TZPID ID0156 UUID 06ed5405-01b0-5b24-95c8-cb7ab2e75859 Type Higher Structure Statement Scale higher-bundle organization of the unified field LOC Classification Working routing: QA612 higher cohomology; QA169 higher categories arXiv Classification Primary: math.AT Cross-list: hep-th, math-ph Canonical Statement The unified field is lifted from ordinary bundle data

\paragraph{Canonical Equation.}
\[
𝐹=𝑑𝐴+𝐴∧𝐴 CS(𝐴)≠0 =⇒ Otop≠0
\]

\paragraph{Dictionary.}
Definition of 𝐹 — 𝐹=𝑑𝐴+𝐴∧𝐴 CS(𝐴)≠0 =⇒ Otop≠0

\paragraph{Encyclopedia.}
Definition of 𝐹 is an algebraic definition, written 𝐹=𝑑𝐴+𝐴∧𝐴 CS(𝐴)≠0 =⇒ Otop≠0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from C, S, O, o, p, defining 𝐹. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
