\section*{ID6730: Short Conceptual Synthesis for Your TZP Story: A(φ)}
\paragraph{Metadata.}
PiID: 9820595510022 | RTEID: RTE:P26134.0846:T5.3618 | UUID: 12d42ea2-09ed-5868-8840-b217e111c98c

\paragraph{Canonical Statement.}
If you like, I’ll now: - produce a short Python script (NumPy + SciPy + matplotlib) that implements the **practical measurement algorithm** above (polar transform, \textbackslash{}(A(\textbackslash{}phi)\textbackslash{}) Fourier spectrum, Airy fit, vane-count detection), *ready to run on your images* when you can upload them; **or** - generate a synthetic demo: create a fractal TZP map, convolve with realistic PSFs for several \textbackslash{}(f\textbackslash{}\#\textbackslash{}) and vane counts, and show how the spikes appear and how the spherical-harmonic correlation recovers the underlying TZP.

\paragraph{Canonical Equation.}
\[
A(\phi)
\]

\paragraph{Dictionary.}
If you like, I’ll now: - produce a short Python script (NumPy + SciPy + matplotlib) that implements the practical measurement algorithm above (polar transform, \textbackslash{}(A( )\textbackslash{}) Fourier spectrum, Airy fit, vane-count detection), ready to run on your images when you can upload them; or - generate a synthetic

\paragraph{Encyclopedia.}
Short Conceptual Synthesis for Your TZP Story: A(φ) is a symbolic expression, written A(φ). It introduces a symbol or relation used elsewhere in the framework. It is built from φ, A. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
