\section*{ID8764: Relation: E\textasciicircum{}2 + B\textasciicircum{}2}
\paragraph{Metadata.}
PiID: 1141952123828 | RTEID: RTE:P34032.5583:T5.8097 | UUID: 69029ef3-82a6-5762-a3bb-e0b2c095a8cb

\paragraph{Canonical Statement.}
away from our brane (in a brane-world scenario). However, their gravitational influence could still be felt if gravity propagates in the higher dimension (which many models allow). Imagine that for every field line (or bundle of field lines) that emerges from TZP⁺ and re-enters at TZP⁻, there is a segment of that loop that is literally “outside” our observable universe (in the 4th dimension). That segment can carry energy. If the field is an electromagnetic one, energy is stored in the field ( \$E\textasciicircum{}2 + B\textasciicircum{}2\$ terms) all along the loop. The portion of energy in the 3D portions might be visible (e.g. through electromagnetic effects or pressure on matter), but the portion in the 4D segment would be invisible to us directly – yet gravitationally it would still contribute to curvature (since in general relativity any stress-energy, even in extra dimensions, can affect 4D geometry depending on the setup).

\paragraph{Canonical Equation.}
\[
E^2 + B^2
\]

\paragraph{Dictionary.}
Relation: E\textasciicircum{}2 + B\textasciicircum{}2 — E\textasciicircum{}2 + B\textasciicircum{}2

\paragraph{Encyclopedia.}
Relation: E\textasciicircum{}2 + B\textasciicircum{}2 is a symbolic expression, written E\textasciicircum{}2 + B\textasciicircum{}2. It introduces a symbol or relation used elsewhere in the framework. It is built from E, B. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
