\tzpanchor{0011}
\tzpentryheader{0011}{Causal Loop Invariant}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{b63b387a-822c-58b3-9bf9-73350cb197fa}}\\
\textbf{PiID} & \tzpcode{9793238462643} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{18}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{42.7154 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.0704 rad}\\
\textbf{TZPID} & \tzpcode{ID0011} & \textbf{Node Dependencies}\quad \tzpidref{0002}\\
\textbf{Registry} & \tzpcode{registry\_id\_0011} & \textbf{Scale}\quad causal-topological\\
\textbf{LOC Classification} & QA612 loop topology & QC174.52 causal structure\\
\textbf{arXiv Classification} & Primary: gr-qc \quad Cross-list: math-ph, hep-th & \\
\textbf{Primary Support} & Closed Causal Loop & Loop Integral of the Potential\\
\textbf{Closure Support} & Supported-Zero Curvature Exterior & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The causal loop invariant measures the phase-like content accumulated by a closed causal trajectory that passes through the Trawin Zero Point. It packages the loop's interaction with the singular anchor into a conserved scalar quantity.

\tzpsection{Canonical Equation}
\[
I_{\mathrm{CL}}
=
\oint_{\Gamma} A \cdot dx
\]
\[
dA = 0 \quad \text{on } M \setminus \{p\}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $I_{\mathrm{CL}}$: source equation symbol.
    \item $A$: source equation symbol.
    \item $M$: source equation symbol.
    \item $\Gamma$: closed loop, path, or admissible trajectory in the entry domain.
    \item $G$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0011 generated source Wolfram model *)
ClearAll[K0011, Cr0011, T, R, A, W, I, N];
eq0011$1 = HoldForm[ICL == ContourIntegralGamma*A*dx];
eq0011$2 = HoldForm[dA == 0*Msetminus*{p}];
eq0011$3 = HoldForm[Gamma*p];

K0011 = HoldForm[{eq0011$1, eq0011$2, eq0011$3}];

N = "normalized TRAWIN closure object for Causal Loop Invariant";
I = "Supported-Zero Curvature Exterior integration/comparison layer";
W = "Loop Integral of the Potential wave or operator carrier";
A = "Closed Causal Loop admissible action/amplitude condition";
R = "Loop Integral of the Potential rotation/curl preservation layer";
T = "Closed Causal Loop local source condition";

Cr0011[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0011 = Cr0011[K0011];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Closed Causal Loop local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Loop Integral of the Potential rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Closed Causal Loop admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Loop Integral of the Potential wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Supported-Zero Curvature Exterior integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Causal Loop Invariant.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0011] Causal Loop Invariant}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
I_{\mathrm{CL}}
=
\oint_{\Gamma} A\cdot \mathrm{d}x .
\end{equation}

\paragraph{Primary Derivation.}
Let $\Gamma$ be a closed causal loop passing through or encircling the TZP.  
Let $A$ be a one-form potential defined along the loop.

The infinitesimal contribution of the potential along the path is:

\begin{equation}
A\cdot \mathrm{d}x .
\end{equation}

Integrating this contribution over the full closed loop gives the loop invariant:

\begin{equation}
I_{\mathrm{CL}}
=
\oint_{\Gamma} A\cdot \mathrm{d}x .
\end{equation}

If $\mathrm{d}A=0$ away from $p$ and support is concentrated at the TZP, then the loop integral depends only on the causal winding around $p$.

\paragraph{Interpretation.}
$I_{\mathrm{CL}}$ records the accumulated causal phase around the TZP. It is invariant under deformations of $\Gamma$ that preserve the winding relation to $p$.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Causal Loop Invariant by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Closed Causal Loop}\par
\[
\Gamma \ \text{closed and causal through } p
\]
\noindent This specifies the admissible trajectory class and ties the invariant to loops that genuinely encounter the singular anchor.\par
\noindent\textbf{2. Loop Integral of the Potential}\par
\[
I_{\mathrm{CL}}
=
\oint_{\Gamma} A \cdot dx
\]
\noindent This converts the causal loop into a scalar quantity by integrating the one-form potential around the full circuit.\par
\noindent\textbf{3. Supported-Zero Curvature Exterior}\par
\[
dA = 0 \quad \text{on } M \setminus \{p\}
\]
\noindent This closes the progression by forcing all nontrivial contribution to concentrate at the zero point rather than leak across the surrounding manifold.\par

\clearpage
\noindent\textbf{[ID 0011] Causal Loop Invariant}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Causal Loop Invariant is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} For any closed causal loop Gamma passing through ppp, the invariant ICL is given by I sub CL= GammaA dxItextbackslash sub CL =textbackslash oint sub Gamma Adot d xI sub CL= GammaA dx, where AAA is a one-form potential whose exterior derivative vanishes outside the TZP and has support only at ppp. \textbackslash{}. \textbf{Contextual meaning:} The entry reads Causal Loop Invariant as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Closed Causal Loop; Loop Integral of the Potential; Supported-Zero Curvature Exterior.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
I sub CL records the accumulated causal phase around the TZP. It is invariant under deformations of that preserve the winding relation to p.

\tzpsection{Equation Grounding}
Equation anchors: For any closed causal loop Gamma passing through ppp, the invariant ICL is given by I CL= GammaA dxItextbackslash CL =textbackslash oint Gamma Adot d xI CL= GammaA dx, where AAA is a one-form potential whose exterior derivative vanishes outside the TZP and has support only at ppp. For any closed causal loop Gamma passing through ppp, the invariant ICL is given by I CL= GammaA dxItextbackslash CL =textbackslash oint Gamma Adot d xI CL= GammaA dx, where AAA is a one-form potential whose exterior derivative vanishes outside the TZP and has support only at ppp.

\tzpsection{Interpretive Role}
This invariant is the loop-level quantity that later winding, holonomy, and phase quantization statements can build on. It turns causal circulation around the zero point into something countable and testable.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Causal Loop Conserved Quantity}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Conserved Quantity Normalization Analogue}: normalization vocabulary for fixed form, invariant comparison, or TRAWIN admissibility.
\item \textbf{Conserved Quantity Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0011]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0011_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0011] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Causal Loop Invariant}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} for any closed causal loop  passing through ppp, the invariant  is given by
I\textbackslash{}\_CL=∮A⋅dxI\textbackslash{}\_\textbackslash{}\textbackslash{}CL\textbackslash{}\textbackslash{}= oint\textbackslash{}\_\textbackslash{}\textbackslash{}A \textbackslash{}d\textbackslash{}xI\textbackslash{}\_CL=∮A⋅dx, where AAA is a...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Causal Loop Invariant is valid as a formal dynamical law when the Hamiltonian or energy
operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0011_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
