\section*{ID9016: Relation: :M→Mφ:M→ M:M→M}
\paragraph{Metadata.}
PiID: 4060340216654 | RTEID: RTE:P35011.1303:T1.1389 | UUID: 9ee0f5e5-7965-53de-afe0-ac9c5ae465a6

\paragraph{Canonical Statement.}
ear the zero point. Dependencies: ID 001 Derivable Consequences: Enables definition of null space projections; implies that curvature scalars may diverge at ppp; allows for curvature singularity entry; motivates modified field equations. Falsifiability / Test Handle: Detection of a regular, invertible metric in the vicinity of the predicted TZP would falsify this condition. 0.0.7 ID 005: TZP Stability Under SymmetryPreserving Diffeomorphisms Type: Axiom Formal Statement: For any diffeomorphism \$:M→M\textbackslash{}phi:M\textbackslash{}to M:M→M\$ that preserves the symmetry group of MMM, (p)=p\textbackslash{}phi(p)=p(p)=p and \textbackslash{}phi leaves the local lemniscatic structure invariant. Interpretive Meaning: Symmetries of the manifold cannot move or alter the TZP; it remains fixed and its lemniscatic neighbourhood is preserved. This ensures stability of the zero point under allowable coordinate transformations. Dependencies: ID 000, ID 002 Derivable Consequenc

\paragraph{Canonical Equation.}
\[
:M→M\phi:M\to M:M→M
\]

\paragraph{Dictionary.}
Relation: :M→Mφ:M→ M:M→M — :M→Mφ:M→ M:M→M

\paragraph{Encyclopedia.}
Relation: :M→Mφ:M→ M:M→M is a symbolic expression, written :M→Mφ:M→ M:M→M. It introduces a symbol or relation used elsewhere in the framework. It is built from φ, M. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
