\tzpanchor{0078}
\tzpentryheader{0078}{Quantum Criticality}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{4866b4f0-b8a8-5181-bd4d-ba85535dfa34}}\\
\textbf{PiID} & \tzpcode{9986280348253} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{85}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{302.8913 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.4991 rad}\\
\textbf{TZPID} & \tzpcode{ID0078} & \textbf{Node Dependencies}\quad \tzpidref{0057}\\
\textbf{Registry} & \tzpcode{registry\_id\_0078} & \textbf{Scale}\quad quantum critical regime\\
\textbf{LOC Classification} & QC174 critical scaling & QC20 universality classes\\
\textbf{arXiv Classification} & Primary: cond-mat.stat-mech \quad Cross-list: quant-ph, hep-th & \\
\textbf{Primary Support} & Critical Observable & Power-Law Correlator\\
\textbf{Closure Support} & Anomalous Exponent Dependence & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Critical points display universality and scale invariance; the TZP modifies exponents and the number of relevant operators.

\tzpsection{Canonical Equation}
\[
\langle O(x)O(0)\rangle
\sim
\lvert x\rvert^{-2+\eta}
\]
\[
\eta = \eta(d_{\mathrm{eff}},\mathrm{TZP})
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $O$: source equation symbol.
    \item $d_{\mathrm{eff}}$: source equation symbol.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $\rvert\eta$: source equation symbol.
    \item $\eta$: source equation symbol.
    \item $T$: source equation symbol.
    \item $Z$: source equation symbol.
    \item $P$: source equation symbol.
    \item $a(d_{eff},TZP)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0078 generated source Wolfram model *)
ClearAll[K0078, Cr0078, T, R, A, W, I, N];
eq0078$1 = HoldForm[SimilarTo[Inner[O[x]*O[0]], Abs[x]^(-2 + eta)]];
eq0078$2 = HoldForm[eta == eta[dEff, TZP]];
eq0078$3 = HoldForm[O[x]];

K0078 = HoldForm[{eq0078$1, eq0078$2, eq0078$3}];

N = "normalized TRAWIN closure object for Quantum Criticality";
I = "Anomalous Exponent Dependence integration/comparison layer";
W = "Power-Law Correlator wave or operator carrier";
A = "Critical Observable admissible action/amplitude condition";
R = "Power-Law Correlator rotation/curl preservation layer";
T = "Critical Observable local source condition";

Cr0078[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0078 = Cr0078[K0078];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Critical Observable local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Power-Law Correlator rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Critical Observable admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Power-Law Correlator wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Anomalous Exponent Dependence integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum Criticality.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0078] Quantum Criticality}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\langle O(x)O(0)\rangle
\sim
|x|^{-2+\eta}.
\end{equation}

\paragraph{Exponent Dependence.}
\begin{equation}
\eta=\eta(d_{\mathrm{eff}},\mathrm{TZP}).
\end{equation}

\paragraph{Primary Derivation.}
At a quantum critical point, correlation length diverges and the system loses a preferred length scale.  
An observable $O(x)$ therefore has a scale-free two-point function:
\begin{equation}
\langle O(x)O(0)\rangle
\sim
|x|^{-\Delta}.
\end{equation}

With anomalous exponent $\Delta=2-\eta$, this becomes
\begin{equation}
\boxed{
\langle O(x)O(0)\rangle
\sim
|x|^{-2+\eta}.
}
\end{equation}

In the TRAWIN setting,
\begin{equation}
\eta=\eta(d_{\mathrm{eff}},\mathrm{TZP}).
\end{equation}

\paragraph{Interpretation.}
Quantum criticality is detected through power-law correlations whose exponents may depend on effective dimension and TZP deformation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum Criticality by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Critical Observable}\par
\[
O(x)
\]
\noindent This is the field or operator whose long-range critical behavior is being measured.\par
\noindent\textbf{2. Power-Law Correlator}\par
\[
\langle O(x)O(0)\rangle
\sim
\lvert x\rvert^{-2+\eta}
\]
\noindent This expresses the loss of characteristic length scale at criticality.\par
\noindent\textbf{3. Anomalous Exponent Dependence}\par
\[
\eta = \eta(d_{\mathrm{eff}},\mathrm{TZP})
\]
\noindent This closes the progression by tying the scaling exponent to effective dimension and zero-point data.\par

\clearpage
\noindent\textbf{[ID 0078] Quantum Criticality}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum Criticality is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Critical points display universality and scale invariance; the TZP modifies exponents and the number of relevant operators. \textbf{Contextual meaning:} The entry reads Quantum Criticality as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry sharpens the criticality story from the previous tranche by focusing on explicit observable scaling. It gives the registry a direct way to compare critical data across geometry, scale, and zero-point deformation. \textbf{Lemma support:} Critical Observable; Power-Law Correlator; Anomalous Exponent Dependence.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Quantum criticality is detected through power-law correlations whose exponents may depend on effective dimension and TZP deformation.

\tzpsection{Equation Grounding}
Equation anchors: At a quantum critical point, system observables obey scaling relations with critical exponents determined by universality class and effective dimension dimu2061efftextbackslash dim eff dimeff; correlation functions follow power laws langleO(x)O(0)  x -2+eta O(x)O(0) textbackslash sim textbar xtextbar to the power -2+eta langleO(x)O(0)  x -2+eta, where etaetaeta depends on curvature and the TZP. At a quantum critical point, system observables obey scaling relations with critical exponents determined by universality class and effective dimension dimu2061efftextbackslash dim eff dimeff; correlation functions follow power laws langleO(x)O(0)  x -2+eta O(x)O(0) textbackslash sim textbar xtextbar to the power -2+eta langleO(x)O(0)  x -2+eta, where etaetaeta depends on curvature and the TZP.

\tzpsection{Interpretive Role}
This entry sharpens the criticality story from the previous tranche by focusing on explicit observable scaling. It gives the registry a direct way to compare critical data across geometry, scale, and zero-point deformation.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{State-Level Criticality}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Quantum-State Analogue}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Terminology}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0078]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0078_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0078] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum Criticality}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} critical points display universality and scale invariance; the TZP modifies exponents
and the number of relevant operators

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum Criticality is valid as a formal dynamical law when the Hamiltonian or energy
operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0078_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
