\section*{ID8560: Definition of Y}
\paragraph{Metadata.}
PiID: 3142775687900 | RTEID: RTE:P33240.3810:T4.5044 | UUID: 7a76ca77-a208-5436-915e-b198fa08bff2

\paragraph{Canonical Statement.}
stantaneous state retrieval. Source: [ID 966] ROUND-TRIP FIDELITY METRIC Canonical Statutory Formula: \$FRT \$ = \$|⟨ψin|D(E(ψin))⟩|2 > 0.999999 \$ Formal Technical Dissertation: Sets the operational threshold for signal integrity. The system guarantees that a state subjected to the full encoding (E) and decoding (D) cycle retains a fidelity greater than 99.9999 Source: [ID 967] BIJECTIVE MAPPING VERIFICATION Canonical Statutory Formula: \$∀y ∈ A, ∃!x ∈ B \$ : \$f(x) \$ = \$y =⇒ |Unique(f(B))| ≡ |B| \$ Formal Technical Dissertation: The mathematical proof of the system’s encoding efficiency. It verifies that the mapping between the blob manifold \$B \$ and the address space \$A \$ is both injective and surjective (bijective), ensuring no data collisions and full coverage of the manifold. Source: [ID 968] HAMMING DISTANCE OPTIMIZATION Canonical Statutory Formula: min \$∑\$ \$i,j dH(xi, xj

\paragraph{Canonical Equation.}
\[
y =⇒ |Unique(f(B))| ≡ |B|
\]

\paragraph{Dictionary.}
Definition of Y — y =⇒ |Unique(f(B))| ≡ |B|

\paragraph{Encyclopedia.}
Definition of Y is an algebraic definition, written y =⇒ |Unique(f(B))| ≡ |B|. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from U, n, q, u, f, B, defining y. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
