\tzpanchor{0299}
\tzpentryheader{0299}{Rotation Tilt via Coriolis Coupling (joy's Law Analogue)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{c822804d-f799-5809-a68d-680dec980e0f}}\\
\textbf{PiID} & \tzpcode{3724587006606} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{306}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1161.0834 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9131 rad}\\
\textbf{TZPID} & \tzpcode{ID0299} & \textbf{Node Dependencies}\quad \tzpidref{0298}\\
\textbf{Registry} & \tzpcode{registry\_id\_0299} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Rotationally induced tilts of magnetic structures follow a simple latitudinal scaling, providing a diagnostic for internal rotation.

\tzpsection{Canonical Equation}
\[
\dot{\theta}_i=\omega_i+\sum_{j\ne i}\frac{K_{ij}}{N}\sin(\theta_j-\theta_i)
\]
\[
a_{\mathrm{DSS}}=\left(\frac{3k_{2,i}GM_P^2R_i^5T_{\mathrm{sys}}}{\omega_iI_iQ_i}\right)^{1/6}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\theta$: phase angle or local angular coordinate.
    \item $\omega_i$: angular frequency term in the source equation.
    \item $K_{ij}$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
    \item $\theta_j$: source equation symbol.
    \item $\theta_i$: source equation symbol.
    \item $a_{\mathrm{DSS}}$: source equation symbol.
    \item $k_{2,i}$: source equation symbol.
    \item $R_i$: source equation symbol.
    \item $\omega_iI$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0299 generated source Wolfram model *)
ClearAll[K0299, Cr0299, T, R, A, W, I, N];
eq0299$1 = HoldForm[dot[theta]*_i == omegaI + SumJi[KIj/N]*Sin[thetaJ - thetaI]];
eq0299$2 = HoldForm[aDSS == ((3*k2*iGMP^2*RI^5*TSys)/(omegaII_iQI))^(1/6)];
eq0299$3 = HoldForm[SimilarTo[tanalpha, eq2*Omegatau]];

K0299 = HoldForm[{eq0299$1, eq0299$2, eq0299$3}];

N = "normalized TRAWIN closure object for Rotation Tilt via Coriolis Coupling (joy's Law Analogue)";
I = "Normalized Regime integration/comparison layer";
W = "Scaling Relation wave or operator carrier";
A = "Diagnostic Definition admissible action/amplitude condition";
R = "Scaling Relation rotation/curl preservation layer";
T = "Diagnostic Definition local source condition";

Cr0299[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0299 = Cr0299[K0299];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Diagnostic Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Scaling Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Diagnostic Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Scaling Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Regime integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Rotation Tilt via Coriolis Coupling (joy's Law Analogue).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0299] Rotation Tilt via Coriolis Coupling (joy's Law Analogue)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Carrier Superposition.}
\begin{equation}
\Psi(t)=A\cos(\omega_1t)+B\cos(\omega_2t).
\end{equation}

\paragraph{Envelope--Carrier Decomposition.}
\begin{equation}
\Psi(t)
=
2C
\cos\left(
\frac{\omega_1-\omega_2}{2}t
\right)
\cos\left(
\frac{\omega_1+\omega_2}{2}t
\right).
\end{equation}

\paragraph{Coupling Windows.}
\begin{equation}
t_k=
\frac{2\pi k}{|\omega_1-\omega_2|}.
\end{equation}

\paragraph{Primary Derivation.}
For paired carriers, the raw signal is:
\begin{equation}
\Psi(t)=A\cos(\omega_1t)+B\cos(\omega_2t).
\end{equation}

For equal or normalized amplitudes, the trigonometric sum identity yields:
\begin{equation}
\Psi(t)
=
2C
\cos\left(
\frac{\omega_1-\omega_2}{2}t
\right)
\cos\left(
\frac{\omega_1+\omega_2}{2}t
\right).
\end{equation}

Envelope maxima occur at discrete times:
\begin{equation}
\boxed{
t_k=
\frac{2\pi k}{|\omega_1-\omega_2|}.
}
\end{equation}

\paragraph{Interpretation.}
Beat topology identifies discrete envelope windows where coherent coupling is strongest.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Rotation Tilt via Coriolis Coupling (joy's Law Analogue) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Diagnostic Definition}\par
\[
\dot{\theta}_i=\omega_i+\sum_{j\ne i}\frac{K_{ij}}{N}\sin(\theta_j-\theta_i)
\]
\noindent This defines the scalar diagnostic or conversion quantity named by the title.\par
\noindent\textbf{2. Scaling Relation}\par
\[
a_{\mathrm{DSS}}=\left(\frac{3k_{2,i}GM_P^2R_i^5T_{\mathrm{sys}}}{\omega_iI_iQ_i}\right)^{1/6}
\]
\noindent This elevates the quantity into a comparative scaling or correlation law.\par
\noindent\textbf{3. Normalized Regime}\par
\[
\tan\alpha\simeq2\Omega\tau
\]
\noindent This closes the entry by normalizing the diagnostic against a stated reference regime.\par

\clearpage
\noindent\textbf{[ID 0299] Rotation Tilt via Coriolis Coupling (joy's Law Analogue)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Rotation Tilt via Coriolis Coupling (Joy s Law Analogue) is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Rotationally induced tilts of magnetic structures follow a simple latitudinal scaling, providing a diagnostic for internal rotation. \textbf{Contextual meaning:} The entry reads Rotation Tilt via Coriolis Coupling (Joy s Law Analogue) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons. \textbf{Lemma support:} Diagnostic Definition; Scaling Relation; Normalized Regime.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Beat topology identifies discrete envelope windows where coherent coupling is strongest.

\tzpsection{Equation Grounding}
Equation anchors:
\[
\dot{\theta}_i=\omega_i+\sum_{j\ne i}\frac{K_{ij}}{N}\sin(\theta_j-\theta_i),
\]
\[
a_{\mathrm{DSS}}=
\left(
\frac{3k_{2,i}GM_P^2R_i^5T_{\mathrm{sys}}}
{\omega_i I_i Q_i}
\right)^{1/6},
\qquad
\tan\alpha\simeq2\Omega\tau.
\]
Proof route: show that the named quantity is dimensionless or consistently scaled in the regime stated by the entry. Formalization route: prove that the normalized diagnostic remains invariant under the intended rescaling.

\tzpsection{Interpretive Role}
The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Latitude-Dependent Sunspot Tilting}: The mathematical rule dictating that magnetic flux tubes erupting through a surface will naturally twist, with the tilt angle strictly dependent on how far they are from the equator.
\item \textbf{Coriolis Helicity Enforcement on Erupting Flux}: The calculation showing how the Coriolis force physically grabs a rising, expanding bubble of magnetic plasma and violently twists it into a spiral.
\item \textbf{Rotational Distortion of Buoyant Magnetics}: The formulation tracking how the sheer speed of a planet's rotation deforms and bends rising magnetic fields, converting toroidal (horizontal) fields into poloidal (vertical) ones.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0299]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0299_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0299] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Rotation Tilt via Coriolis Coupling (joy's Law Analogue)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} rotationally induced tilts of magnetic structures follow a simple latitudinal scaling,
providing a diagnostic for internal rotation

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Rotation Tilt via Coriolis Coupling (Joy's Law Analogue) is valid as a synchronization
criterion under the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0299_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
