\section*{ID9829: Relation: F\_Ω: PackingSphere → ToroidalCategory}
\paragraph{Metadata.}
PiID: 3265134105592 | RTEID: RTE:P38168.1898:T0.0576 | UUID: 99a5a613-a413-5063-8cee-3d381d4231ad

\paragraph{Canonical Statement.}
this introduces a transcendental topological symmetry that typical environmental noise cannot easily break. The entanglement framework is formalized through a category-theoretic functor we denote \$F\_\{\textbackslash{}Omega\}\$, which maps the sphere packing configuration to the toroidal topological space used in our quantum protocols. In formal terms, we define a category whose objects include the PackingSphere (encapsulating the \$S\textasciicircum{}3\$ sphere packing with π-modulated kissing numbers) and the ToroidalCategory (encapsulating the inner and outer \$T\textasciicircum{}2\$ tori and the entangled “bubble” connecting them). The functor \$F\_\{\textbackslash{}Omega\}: \textbackslash{}text\{PackingSphere\} \textbackslash{}to \textbackslash{}text\{ToroidalCategory\}\$ is constructed such that it preserves the essential structure (natural transformations ensure information-theoretic quantities and topological invariants commute with the mapping). This homological functor guarantees that information (entropy, logical bits) encoded in the 4D sphere configuration is preserved upon projection to the 2D topological manifold – a key requirement for lossless dimensional collapse at the TZP. Mathematically, the particle-specific entanglement protocol is captured by a

\paragraph{Canonical Equation.}
\[
F_{\Omega}: \text{PackingSphere} \to \text{ToroidalCategory}
\]

\paragraph{Dictionary.}
Relation: F\_Ω: PackingSphere → ToroidalCategory — F\_Ω: PackingSphere → ToroidalCategory

\paragraph{Encyclopedia.}
Relation: F\_Ω: PackingSphere → ToroidalCategory is a symbolic expression, written F\_Ω: PackingSphere → ToroidalCategory. It introduces a symbol or relation used elsewhere in the framework. It is built from Ω, F\_. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
