\section*{ID8911: QUARK-GLUON PLASMA RESIDUE OPERATOR Canonical Statutory Formula: Q Gp}
\paragraph{Metadata.}
PiID: 5831832713142 | RTEID: RTE:P34603.3919:T0.4671 | UUID: b63b7c71-5c5f-5905-b430-f250ad534a06

\paragraph{Canonical Statement.}
[ID 944] QUARK-GLUON PLASMA RESIDUE OPERATOR Canonical Statutory Formula: \$\textbackslash{}hat\{Q\} \{gp\} = \textbackslash{}text\{Tr\}[F \{\textbackslash{}mu\textbackslash{}nu\}F\textasciicircum{}\{\textbackslash{}mu\textbackslash{}nu\}] \textbackslash{}otimes \textbackslash{}exp(-T\_c/T(L)) \textbackslash{}implies SU(3)\_\{color\}\$ Formal Technical Dissertation: Stabilizes sub-nucleonic fluctuations at the TZP core. It pins the strong-force interactions of any incipient QGP residue to the DAANSphere lattice, preventing color leakage while utilizing the residue as a superfluid lubricant for the vacuum flow. Source: [26], [27]

\paragraph{Canonical Equation.}
\[
\hat{Q} {gp} = \text{Tr}[F {\mu\nu}F^{\mu\nu}] \otimes \exp(-T_c/T(L)) \implies SU(3)_{color}
\]

\paragraph{Dictionary.}
QUARK-GLUON PLASMA RESIDUE OPERATOR Canonical Statutory Formula: \$Q gp = Tr[F F\textasciicircum{} ] (-T\_c/T(L)) SU(3)\_color\$ Formal Technical Dissertation: Stabilizes sub-nucleonic fluctuations at the TZP core.

\paragraph{Encyclopedia.}
QUARK-GLUON PLASMA RESIDUE OPERATOR Canonical Statutory Formula: Q Gp is an expectation / trace over state, written Q gp = Tr[F μνF\textasciicircum{}μν] ⊗ exp(-T\_c/T(L)) ⟹ SU(3)\_color. It is computed as an expectation value or trace over a quantum state, producing an observable. It is built from μ, ν, F, T\_c, T, L, defining Q gp. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
