\section*{ID8267: Electromagnetic: T\textasciicircum{}μν\_rm EM}
\paragraph{Metadata.}
PiID: 9110137751721 | RTEID: RTE:P32102.5969:T2.6297 | UUID: d6b90e46-9f36-5636-a3cc-31c469f7cbce

\paragraph{Canonical Statement.}
What I didn’t do (so you know the limits) - I treated only the **electromagnetic** contribution in the explicit substitution above (i.e., \textbackslash{}(T\textasciicircum{}\{\textbackslash{}mu\textbackslash{}nu\}\_\{\textbackslash{}rm EM\}\textbackslash{})). The general matter/gyro imperfect-fluid terms from your file were left in symbolic/placeholder form (ρ, p, qᵘ, π\textasciicircum{}\{μν\}) because your notes contain those terms in a high-level Lagrangian form rather than explicit component functions — I can expand those once you confirm the mechanical constitutive relations you want used (e.g., rigid rotor with specified density distribution, spring constants, or explicit current densities). - The rotating metric used is the common Born-type coordinate form (flat space in rotating coords). If you want a different metric (e.g., full GR frame-dragging solution or a custom metric in your notes), I can substitute that instead — just point me to the explicit metric expression or tell me which file block to use.

\paragraph{Canonical Equation.}
\[
T^{\mu\nu}_{\rm EM}
\]

\paragraph{Dictionary.}
Electromagnetic: T\textasciicircum{}μν\_rm EM — T\textasciicircum{}μν\_rm EM

\paragraph{Encyclopedia.}
Electromagnetic: T\textasciicircum{}μν\_rm EM is a symbolic expression, written T\textasciicircum{}μν\_rm EM. It introduces a symbol or relation used elsewhere in the framework. It is built from μ, ν, T, E, M. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
