\tzpanchor{0307}
\tzpentryheader{0307}{Helical Propagator and Gerchberg--Saxton Phase Retrieval}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{55e52b85-239c-5ec6-8e2d-7b20e3fa8ae7}}\\
\textbf{PiID} & \tzpcode{0660631558817} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{314}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1192.1492 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9643 rad}\\
\textbf{TZPID} & \tzpcode{ID0307} & \textbf{Node Dependencies}\quad \tzpidref{0306}\\
\textbf{Registry} & \tzpcode{registry\_id\_0307} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Propagation Step & Intensity Projection\\
\textbf{Closure Support} & Convergence Error & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Define a propagation operator \(P\) representing forward propagation through a helical medium. Given a target intensity distribution \(I_{\mathrm{target}}\), initialize a complex field \(\psi_0 = \sqrt{I_{\mathrm{target}}}\, e^{i \varphi_0}\). Iterate: (1) \(\tilde{\psi}_n = P[\psi_n]\); (2) enforce intensity: \(\tilde{\psi}_n \leftarrow \sqrt{I_{\mathrm{target}}}\, e^{i \arg(\tilde{\psi}_n)}\); (3) \(\psi_{n+1} = P^{-1}[\tilde{\psi}_n]\); (4) enforce input domain constraints. Convergence is monitored by the error metric \(\epsilon_n = \|\, |P[\psi_n]|^2 - I_{\mathrm{target}} \|^2 / \|I_{\mathrm{target}}\|^2.\)

\tzpsection{Canonical Equation}
\[
tilde{\psi}_n=P[\psi_n]
\]
\[
tilde{\psi}_n\leftarrow \sqrt{I_{\mathrm{target}}}\,e^{i\arg(\tilde{\psi}_n)}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $P$: source equation symbol.
    \item $I_{\mathrm{target}}$: source equation symbol.
    \item $e_T$: exponential damping factor encoding potential-induced suppression.
    \item $\psi$: source equation symbol.
    \item $\arg$: source equation symbol.
    \item $g$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0307 generated source Wolfram model *)
ClearAll[K0307, Cr0307, T, R, A, W, I, N];
eq0307$1 = HoldForm[tilde[psi]*_n == P[psiN]];
eq0307$2 = HoldForm[tilde[psi]*_narrowsqrt[ITarget]*e^iarg[tilde[psi]*_n]];
eq0307$3 = HoldForm[epsilonN == (Abs[P[psiN]]^2 - ITarget^2)/ITarget^2];

K0307 = HoldForm[{eq0307$1, eq0307$2, eq0307$3}];

N = "normalized TRAWIN closure object for Helical Propagator and Gerchberg--Saxton Phase Retrieval";
I = "Convergence Error integration/comparison layer";
W = "Intensity Projection wave or operator carrier";
A = "Propagation Step admissible action/amplitude condition";
R = "Intensity Projection rotation/curl preservation layer";
T = "Propagation Step local source condition";

Cr0307[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0307 = Cr0307[K0307];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Propagation Step local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Intensity Projection rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Propagation Step admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Intensity Projection wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Convergence Error integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Helical Propagator and Gerchberg--Saxton Phase Retrieval.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0307] Helical Propagator and Gerchberg--Saxton Phase Retrieval}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\alpha(t)=\frac{\mathrm{d}t'}{\mathrm{d}t}.
\end{equation}

\paragraph{Primary Derivation.}
Let $t$ denote ordinary parameter time and let $t'$ denote displaced or transformed time measured through the Trawinistic structure.

If $t'$ depends smoothly on $t$, then the infinitesimal rate of temporal displacement is given by the derivative:

\begin{equation}
\mathrm{d}t' = \alpha(t)\,\mathrm{d}t .
\end{equation}

Solving for $\alpha(t)$ gives:

\begin{equation}
\boxed{
\alpha(t)=\frac{\mathrm{d}t'}{\mathrm{d}t}.
}
\end{equation}

\paragraph{Interpretation.}
The temporal displacement factor measures how transformed time stretches, compresses, or shifts relative to ordinary time.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Helical Propagator and Gerchberg--Saxton Phase Retrieval by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Propagation Step}\par
\[
tilde{\psi}_n=P[\psi_n]
\]
\noindent This fixes the forward helical propagation step of the Gerchberg--Saxton iteration.\par
\noindent\textbf{2. Intensity Projection}\par
\[
tilde{\psi}_n\leftarrow \sqrt{I_{\mathrm{target}}}\,e^{i\arg(\tilde{\psi}_n)}
\]
\noindent This projects the propagated field back onto the target-intensity constraint.\par
\noindent\textbf{3. Convergence Error}\par
\[
epsilon_n=\frac{\left\||P[\psi_n]|^2-I_{\mathrm{target}}\right\|^2}{\left\|I_{\mathrm{target}}\right\|^2}
\]
\noindent This closes the entry with the normalized error metric that monitors convergence.\par

\clearpage
\noindent\textbf{[ID 0307] Helical Propagator and Gerchberg--Saxton Phase Retrieval}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Helical Propagator and Gerchberg--Saxton Phase Retrieval is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Define a propagation operator P representing forward propagation through a helical medium. Given a target intensity distribution I sub target , initialize a complex field psi sub 0 = sqrt I sub target e to the power i varphi sub 0 . Iterate: (1) tilde psi sub n = P[psi sub n]; (2) enforce intensity: tilde psi sub n leftarrow sqrt I sub target e to the power i arg(tilde psi sub n) ; (3) psi sub n+1 = P to the power -1 [tilde psi sub n]; (4) enforce input domain constraints. Convergence is monitored by the error metric epsilon sub n = |P[psi sub n]| to the power 2 - I sub target to the power 2 / I sub target to the power 2. \textbf{Contextual meaning:} The entry reads Helical Propagator and Gerchberg--Saxton Phase Retrieval as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the phase-retrieval loop as an actual propagator algorithm instead of mixing setup prose with inline math. \textbf{Lemma support:} Propagation Step; Intensity Projection; Convergence Error.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The temporal displacement factor measures how transformed time stretches, compresses, or shifts relative to ordinary time.

\tzpsection{Equation Grounding}
Equation anchors: tilde psi sub n=P[psi sub n]; tilde psi sub nleftarrow sqrt I sub target e to the power iarg(tilde psi sub n); and epsilon sub n=ratio |P[psi sub n]| to the power 2-I sub target to the power 2 I sub target to the power 2. Proof route: show that alternating helical propagation and intensity projection yields the stated iterative retrieval scheme with the stated error monitor. Formalization route: prove that the stated error metric is well defined for the constrained propagator iteration and measures convergence toward the target intensity.

\tzpsection{Interpretive Role}
The entry now states the phase-retrieval loop as an actual propagator algorithm instead of mixing setup prose with inline math.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Iterative Phase Convergence}: The algorithmic loop matching wave propagation amplitudes to fixed spatial intensity constraints.
\item \textbf{Forward-Backward Wave Transport}: The numerical simulation technique continuously propagating fields between object and Fourier domains.
\item \textbf{Target Intensity Constraint Operator}: The mathematical projection forcing an evolving wavefront to match empirically measured power distributions.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0307]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0307_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0307] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Helical Propagator and Gerchberg--Saxton Phase Retrieval}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} define a propagation operator \textbackslash{}(P\textbackslash{}) representing forward propagation through a helical
medium

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Helical Propagator and Gerchberg--Saxton Phase Retrieval is valid as a
tensorial/geometric statement when the stated tensor fields are well formed on the
specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0307_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
