\section*{ID9097: Hamiltonian for H}
\paragraph{Metadata.}
PiID: 8856909411303 | RTEID: RTE:P35325.6712:T1.6572 | UUID: 43252d7b-731b-5c9a-9c5f-56460150dda7

\paragraph{Canonical Statement.}
onditions. Dependencies: ID 017, ID 050 Derivable Consequences: Modifications to Coulomb’s law; running of electric charge; scale dependence of physical constants; coupling to boundaryinduced effects. Falsifiability / Test Handle: Highprecision QED experiments in strong gravitational fields could reveal deviations predicted by this polarization tensor. 0.0.55 ID 053: Quantum Harmonic Oscillator (TZPModified) Type: Definition Formal Statement: The TZPmodified harmonic oscillator has Hamiltonian \$H=12mp2+12mω2(q)2+δHH\$ = \textbackslash{}frac\{1\}\{2m\},pˆ2 + \textbackslash{}frac\{1\}\{2\}m\textbackslash{}omega2(q)2 + \textbackslash{}delta \$HH=2m1p2+21mω2(q)2+δH,\$ where \$δH\textbackslash{}delta HδH\$ encodes curvaturedependent corrections and qqq is measured using the Trawin base unit; ladder operators satisfy [a,a]=1[a,aˆ\textbackslash{}dagger]=1[a,a]=1 but acquire curvaturedependent phases. Interpretive Meaning: This modifies the familiar quantum harmonic oscillator to include effects of the curved manifo

\paragraph{Canonical Equation.}
\[
H=12mp2+12mω2(q)2+δHH
\]

\paragraph{Dictionary.}
Hamiltonian for H — H=12mp2+12mω2(q)2+δHH

\paragraph{Encyclopedia.}
Hamiltonian for H is an algebraic definition, written H=12mp2+12mω2(q)2+δHH. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from m, p, q, defining H. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
