\section*{ID9917: Relation: ∑ a\_n e\textasciicircum{}-N S}
\paragraph{Metadata.}
PiID: 2109276457931 | RTEID: RTE:P38509.9133:T0.6206 | UUID: 79b4910b-8a61-50fd-9e4c-62cbd4511dbb

\paragraph{Canonical Statement.}
– one can interpret the persistent currents in the superconducting loops as carriers of logical qubits that cannot disappear without trace. We keep track of these via monitors that measure total quantum numbers (e.g., total fermion parity, total spin) across the manifold. Any change would indicate leakage out of the computational subspace, which should be corrected or at least flagged. Resurgent Series and Convergence Checks: Because the TZP induces an infinite-order phase transition, we utilize resurgent trans-series expansions for certain calculations, meaning we express some observables as \$\textbackslash{}sum a\_n e\textasciicircum{}\{-n S\}\$ plus perhaps non-perturbative series in factorial (these come from the Stokes phenomena around TZP). We have proven that these series super-converge (faster than any finite power) to the exact solution. In implementation, we can take partial sums of these series and verify they approach the expected values within tolerance. This is a form of analytic verification that the system’s mathematics holds up – if we see divergence, it would imply an unaccounted effect. In summary, the integrated TZPQV

\paragraph{Canonical Equation.}
\[
\sum a_n e^{-n S}
\]

\paragraph{Dictionary.}
Relation: ∑ a\_n e\textasciicircum{}-N S — ∑ a\_n e\textasciicircum{}-n S

\paragraph{Encyclopedia.}
Relation: ∑ a\_n e\textasciicircum{}-N S is a series / summation, written ∑ a\_n e\textasciicircum{}-n S. It is expressed as a sum or series over modes or indices, superposing discrete contributions. It is built from a\_n, n, S. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
