\tzpanchor{0060}
\tzpentryheader{0060}{Quantum Coherence and Decoherence}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{165714e4-2c49-54df-8e7b-2d99f10aeb4c}}\\
\textbf{PiID} & \tzpcode{5923078164062} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{67}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{232.9933 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.3839 rad}\\
\textbf{TZPID} & \tzpcode{ID0060} & \textbf{Node Dependencies}\quad \tzpidref{0012}\\
\textbf{Registry} & \tzpcode{registry\_id\_0060} & \textbf{Scale}\quad quantum state overlap\\
\textbf{LOC Classification} & QC174.17 coherence theory & QA56 inner-product spaces\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: hep-th, gr-qc & \\
\textbf{Primary Support} & State Pair & Normalized Coherence Metric\\
\textbf{Closure Support} & Decoherence Limit & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This entry formalizes how quantum superpositions lose coherence; curvature and zero-point fluctuations accelerate decoherence.

\tzpsection{Canonical Equation}
\[
\mathcal{C}(\phi_{1},\phi_{2})
=
\frac{\left|\langle \phi_{1},\phi_{2}\rangle\right|}
\lVert\phi_{1}\rVert\,\lVert\phi_{2}\rVert
\]
\[
\mathcal{C}(t) \to 0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{C}$: speed of light or relativistic conversion factor.
    \item $\phi_{1}$: flux, phase, or topological map term in the source equation.
    \item $\phi_{2}$: flux, phase, or topological map term in the source equation.
    \item $\mathcal{K}_{0060}$: canonical registry object for entry ID 0060.
    \item $V$: auxiliary target state or comparison variable.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0060 generated source Wolfram model *)
ClearAll[K0060, Cr0060, T, R, A, W, I, N];
eq0060$1 = HoldForm[C[phi1, phi2] == fracTuple[Abs[Inner[phi1, phi2]]]*lVertphi1*rVert*lVertphi2*rVert];
eq0060$2 = HoldForm[C[t] -> 0];
eq0060$3 = HoldForm[Pair[phi1, phi2]];

K0060 = HoldForm[{eq0060$1, eq0060$2, eq0060$3}];

N = "normalized TRAWIN closure object for Quantum Coherence and Decoherence";
I = "Decoherence Limit integration/comparison layer";
W = "Normalized Coherence Metric wave or operator carrier";
A = "State Pair admissible action/amplitude condition";
R = "Normalized Coherence Metric rotation/curl preservation layer";
T = "State Pair local source condition";

Cr0060[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0060 = Cr0060[K0060];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ State Pair local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Normalized Coherence Metric rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ State Pair admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Normalized Coherence Metric wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Decoherence Limit integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum Coherence and Decoherence.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0060] Quantum Coherence and Decoherence}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
C(\phi_1,\phi_2)
=
\frac{
|\langle \phi_1,\phi_2\rangle|
}{
\|\phi_1\|\,\|\phi_2\|
}.
\end{equation}

\paragraph{Decoherence Limit.}
\begin{equation}
C(t)\rightarrow 0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi_1$ and $\phi_2$ be two quantum field states.  
Their normalized overlap is:

\begin{equation}
C(\phi_1,\phi_2)
=
\frac{
|\langle \phi_1,\phi_2\rangle|
}{
\|\phi_1\|\,\|\phi_2\|
}.
\end{equation}

If environmental coupling, curvature noise, or zero-point disturbance destroys phase alignment, then the time-dependent coherence decreases:

\begin{equation}
C(t)
=
C(\phi_1(t),\phi_2(t)).
\end{equation}

Decoherence occurs in the limiting regime:

\begin{equation}
\boxed{
C(t)\rightarrow 0 .
}
\end{equation}

\paragraph{Interpretation.}
Coherence is normalized state overlap; decoherence is the decay of that overlap under admissible disturbance.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum Coherence and Decoherence by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. State Pair}\par
\[
(\phi_{1},\phi_{2})
\]
\noindent This identifies the two quantum states whose phase relation is being tracked.\par
\noindent\textbf{2. Normalized Coherence Metric}\par
\[
\mathcal{C}(\phi_{1},\phi_{2})
=
\frac{\left|\langle \phi_{1},\phi_{2}\rangle\right|}
\lVert\phi_{1}\rVert\,\lVert\phi_{2}\rVert
\]
\noindent This converts raw overlap into a scale-free coherence measure.\par
\noindent\textbf{3. Decoherence Limit}\par
\[
\mathcal{C}(t) \to 0
\]
\noindent This closes the progression by expressing environmental loss of coherence as decay of the normalized overlap.\par

\clearpage
\noindent\textbf{[ID 0060] Quantum Coherence and Decoherence}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum Coherence and Decoherence is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This entry formalizes how quantum superpositions lose coherence; curvature and zero-point fluctuations accelerate decoherence. \textbf{Contextual meaning:} The entry reads Quantum Coherence and Decoherence as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry gives the registry a clean coherence diagnostic. It also prepares the next steps in decoherence, pointer states, and measurement disturbance by giving a direct quantity that can decay under interaction. \textbf{Lemma support:} State Pair; Normalized Coherence Metric; Decoherence Limit.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Coherence is normalized state overlap; decoherence is the decay of that overlap under admissible disturbance. \% CANONICAL PDF-ALIGNED VERSION.

\tzpsection{Equation Grounding}
Equation anchors: Quantum coherence on the Trawinistic manifold is quantified by the field coherence metric C( 1, 2)=  1, 2   1   2 C(phi 1,phi 2)=ratio textbarphi 1,phi 2textbar textbackslashtextbarphi 1textbackslashtextbartextbackslashtextbarphi 2textbackslashtextbar C( 1, 2)=  1   2   1, 2 ; decoherence occurs when Cto0Cto 0Cto0 due to coupling with environmental degrees of freedom or curvature-induced noise. Quantum coherence on the Trawinistic manifold is quantified by the field coherence metric C( 1, 2)=  1, 2   1   2 C(phi 1,phi 2)=ratio textbarphi 1,phi 2textbar textbackslashtextbarphi 1textbackslashtextbartextbackslashtextbarphi 2textbackslashtextbar C( 1, 2)=  1   2   1, 2 ; decoherence occurs when Cto0Cto 0Cto0 due to coupling with environmental degrees of freedom or curvature-induced noise.

\tzpsection{Interpretive Role}
This entry gives the registry a clean coherence diagnostic. It also prepares the next steps in decoherence, pointer states, and measurement disturbance by giving a direct quantity that can decay under interaction.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{State-Level Phase Order Decoherence}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Phase Order Quantum-State Analogue}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{Phase Order Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0060]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0060_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0060] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum Coherence and Decoherence}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this entry formalizes how quantum superpositions lose coherence; curvature and zero-
point fluctuations accelerate decoherence

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum Coherence and Decoherence is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0060_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
