\tzpanchor{0216}
\tzpentryheader{0216}{Unified Propulsion Field Definition}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{37f4103e-40c7-5ce8-ad88-21c22374defa}}\\
\textbf{PiID} & \tzpcode{4461284756482} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{223}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{838.7760 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.3820 rad}\\
\textbf{TZPID} & \tzpcode{ID0216} & \textbf{Node Dependencies}\quad \tzpidref{0215}\\
\textbf{Registry} & \tzpcode{registry\_id\_0216} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The unified propulsion field \(P\) at position \(x\) and time \(t\) is defined by subtracting the gyromagnetic Bessel interference field from the natural gravitational vector.

\tzpsection{Canonical Equation}
\[
P(x,t)=g(x)-F(x,t)
\]
\[
\mathcal{J}_{\mathrm{out}}=\mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $P$: source equation symbol.
    \item $t$: source equation symbol.
    \item $F$: source equation symbol.
    \item $\mathcal{J}_{\mathrm{out}}$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{A}_{\mathrm{adm}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0216 generated source Wolfram model *)
ClearAll[K0216, Cr0216, T, R, A, W, I, N];
eq0216$1 = HoldForm[P[x, t] == g[x] - F[x, t]];
eq0216$2 = HoldForm[JOut == TTZP[KTZP]];
eq0216$3 = HoldForm[JOut == TTZP[KTZP]];
eq0216$4 = HoldForm[AAdm[JOut] == 1];

K0216 = HoldForm[{eq0216$1, eq0216$2, eq0216$3, eq0216$4}];

N = "normalized TRAWIN closure object for Unified Propulsion Field Definition";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Canonical Definition admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Canonical Definition local source condition";

Cr0216[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0216 = Cr0216[K0216];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Canonical Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Canonical Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Unified Propulsion Field Definition.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0216] Unified Propulsion Field Definition}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
R_T
=
\lim_{x\to p}
\left(
R+f(x)
\right).
\end{equation}

\paragraph{Primary Derivation.}
Let $R$ denote the ordinary Ricci scalar curvature of the manifold.  
Near the TZP, ordinary curvature may diverge because the metric becomes degenerate.

To produce a finite Trawinistic curvature quantity, introduce a regulator function $f(x)$ designed to cancel or absorb the divergent contribution near $p$:

\begin{equation}
R_{\mathrm{reg}}(x)=R(x)+f(x).
\end{equation}

The TZP curvature is then defined as the limiting regularized curvature at the zero point:

\begin{equation}
\boxed{
R_T
=
\lim_{x\to p}
\left(
R+f(x)
\right).
}
\end{equation}

\paragraph{Interpretation.}
$R_T$ is the curvature seen through the TZP regulator. It separates uncontrolled singular behavior from a finite Trawinistic curvature condition.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Unified Propulsion Field Definition by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Canonical Definition}\par
\[
P(x,t)=g(x)-F(x,t)
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right)=1
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0216] Unified Propulsion Field Definition}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Unified Propulsion Field Definition is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The unified propulsion field P at position x and time t is P(x,t) = g(x) - F(x,t), where g(x) is the natural gravitational vector and F(x,t) is the gyromagnetic Bessel interference field. \textbf{Contextual meaning:} The entry reads Unified Propulsion Field Definition as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform tertiary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
R sub T is the curvature seen through the TZP regulator. It separates uncontrolled singular behavior from a finite Trawinistic curvature condition.

\tzpsection{Equation Grounding}
Equation anchors:
\[
P(x,t)=g(x)-F(x,t),
\qquad
\mathcal{J}_{\mathrm{out}}=\mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right),
\qquad
\mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right)=1.
\]
Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform tertiary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Integrated Thrust Tensor Generation}: The derivation of a macroscopic propulsive force directly from the unification of electromagnetic and gravitational metric terms.
\item \textbf{Vacuum-Gradient Momentum Transfer}: The theoretical mechanism by which momentum is imparted to a craft by pushing against the structured quantum vacuum.
\item \textbf{Propulsive Metric Deformation Limit}: The physical constraint on how much local spacetime can be warped to generate thrust before structural collapse.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0216]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0216_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0216] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Unified Propulsion Field Definition}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the unified propulsion field is \(P(x,t)=g(x)-F(x,t)\), where \(g(x)\) is the gravitational carrier and \(F(x,t)\) is the gyromagnetic Bessel interference field.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Unified Propulsion Field Definition is valid as a tensorial/geometric statement when the
stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0216_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
