\tzpanchor{0291}
\tzpentryheader{0291}{Wasserstein Entropy of Persistence Diagrams}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{af35abd9-a7d3-5cee-bf3b-a7c78d5740f6}}\\
\textbf{PiID} & \tzpcode{2491412737245} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{298}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1130.0176 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.8619 rad}\\
\textbf{TZPID} & \tzpcode{ID0291} & \textbf{Node Dependencies}\quad \tzpidref{0290}\\
\textbf{Registry} & \tzpcode{registry\_id\_0291} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Entropy Weight & Normalized Distribution\\
\textbf{Closure Support} & Topological Aggregate & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Higher Wasserstein entropy reflects a greater variety of feature shapes in the data's topological signature.

\tzpsection{Canonical Equation}
\[
rate = \Sigma_{\mathrm{shannon}} \times BandwidthFrequency
\]
\[
rate = \Sigma_{\mathrm{shannon}} \times BandwidthFrequency
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\rho_{\mathrm{ideal}}$: source equation symbol.
    \item $\mathcal{K}_{0291}$: canonical registry object for entry ID 0291.
    \item $\Sigma_{shannon}$: source equation symbol.
    \item $S$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $F$: source equation symbol.
    \item $Q$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0291 generated source Wolfram model *)
ClearAll[K0291, Cr0291, T, R, A, W, I, N];
eq0291$1 = HoldForm[rate == SigmaShannon*BandwidthFrequency];
eq0291$2 = HoldForm[rate == SigmaShannon*BandwidthFrequency];
eq0291$3 = HoldForm[fidelity == QuantumFidelity[rhoIdeal, rhoActual]];

K0291 = HoldForm[{eq0291$1, eq0291$2, eq0291$3}];

N = "normalized TRAWIN closure object for Wasserstein Entropy of Persistence Diagrams";
I = "Topological Aggregate integration/comparison layer";
W = "Normalized Distribution wave or operator carrier";
A = "Entropy Weight admissible action/amplitude condition";
R = "Normalized Distribution rotation/curl preservation layer";
T = "Entropy Weight local source condition";

Cr0291[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0291 = Cr0291[K0291];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Entropy Weight local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Normalized Distribution rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Entropy Weight admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Normalized Distribution wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Aggregate integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Wasserstein Entropy of Persistence Diagrams.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0291] Wasserstein Entropy of Persistence Diagrams}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
P \longrightarrow M,
\qquad
\mathrm{Struct}(P)=SO(3)\times U(1).
\end{equation}

\begin{equation}
\sigma:M\longrightarrow P.
\end{equation}

\paragraph{Primary Derivation.}
Let $M$ be the base manifold of admissible configurations. Rotational orientation is represented by $SO(3)$, while gauge phase is represented by $U(1)$.

A bundle carrying both data has structure group:
\begin{equation}
SO(3)\times U(1).
\end{equation}

Thus,
\begin{equation}
P\to M,
\qquad
\mathrm{Struct}(P)=SO(3)\times U(1).
\end{equation}

A physical configuration is then a section:
\begin{equation}
\boxed{
\sigma:M\to P.
}
\end{equation}

\paragraph{Interpretation.}
Rotational and gauge-phase data are organized into one configuration bundle.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Wasserstein Entropy of Persistence Diagrams by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Entropy Weight}\par
\[
rate = \Sigma_{\mathrm{shannon}} \times BandwidthFrequency
\]
\noindent This records the local information weight carried by the persistence data or structural channel.\par
\noindent\textbf{2. Normalized Distribution}\par
\[
rate = \Sigma_{\mathrm{shannon}} \times BandwidthFrequency
\]
\noindent This makes the entropy law admissible by normalizing the supporting lifetimes or amplitudes.\par
\noindent\textbf{3. Topological Aggregate}\par
\[
fidelity = QuantumFidelity[\rho_{\mathrm{ideal}}
\]
\noindent This closes the entry by recombining the filtered sectors into one total diagnostic.\par

\clearpage
\noindent\textbf{[ID 0291] Wasserstein Entropy of Persistence Diagrams}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Wasserstein Entropy of Persistence Diagrams is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Higher Wasserstein entropy reflects a greater variety of feature shapes in the data s topological signature. \textbf{Contextual meaning:} The entry reads Wasserstein Entropy of Persistence Diagrams as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers. \textbf{Lemma support:} Entropy Weight; Normalized Distribution; Topological Aggregate.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Rotational and gauge-phase data are organized into one configuration bundle.

\tzpsection{Equation Grounding}
Equation anchors: rate = Sigma sub shannon times BandwidthFrequency; rate = Sigma sub shannon times BandwidthFrequency; and fidelity = QuantumFidelity[rho sub ideal. Proof route: show that the normalized support distribution induces a well-defined entropy functional for the stated topological or informational channel. Formalization route: prove that positivity and normalization of the support weights imply finiteness of the stated entropy functional.

\tzpsection{Interpretive Role}
The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Transformation Cost Between Topological States}: The entropy calculated by measuring the exact mathematical "effort" required to slide, reshape, and match the structural holes of one system to another.
\item \textbf{Distributional Distance Entropy Calculation}: The rigorous mapping of the difference between two chaotic states by comparing the lifespans of their topological features rather than their exact coordinates.
\item \textbf{Morphological Evolution Complexity}: The measurement of how unpredictably the fundamental shape of a system is mutating over time, using advanced optimal transport mathematics.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0291]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0291_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0291] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Wasserstein Entropy of Persistence Diagrams}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} higher Wasserstein entropy reflects a greater variety of feature shapes in the data's
topological signature

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Wasserstein Entropy of Persistence Diagrams is well formed when the total space, base
space, structure group, and projection map are compatible.''\\
\textbf{Proof:} The source statement supplies a bundle-style construction. The CHL reading treats the
base as the proposition carrier, the fiber or structure group as the typed parameter,
and the projection as the categorical morphism that preserves local-to-global structure.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- principal-bundle structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0291_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
