\section*{ID9087: Definition of k,M,Rˆ2,Ωµ}
\paragraph{Metadata.}
PiID: 5825337543885 | RTEID: RTE:P35286.8390:T1.5932 | UUID: 449fa4da-8baa-596f-a03a-f996886bf0d8

\paragraph{Canonical Statement.}
Predicts conservation of linking during reconnection; supports invariance of helicity ratio; guides design of laboratory experiments to emulate astrophysical processes; contributes to energy cascades. Falsifiability / Test Handle: Observation of fractional or noninteger linking numbers in magnetic structures would falsify this universality. 0.0.46 ID 044: \$µ\$ M Rš \$ω\$ Universal Scaling Law Type: Definition Formal Statement: The magnetic moment \$µ\textbackslash{}muµ\$ of a rotating body obeys \$µ=kMR2Ω\textbackslash{}mu\$ = \$k,M,Rˆ2,\textbackslash{}Omegaµ=kMR2Ω,\$ where MMM is mass, RRR the characteristic radius, Ω\textbackslash{}OmegaΩ the angular velocity, and kkk a universal proportionality constant determined by the Trawin base unit. Interpretive Meaning: The magnetic moment scales with the product of mass, square of size, and rotation rate across 47 orders of magnitude, indicating a deep link between inertial and magnetic properties. Dependencies: ID 037 Derivable C

\paragraph{Canonical Equation.}
\[
k,M,Rˆ2,\Omegaµ=kMR2Ω,
\]

\paragraph{Dictionary.}
Predicts conservation of linking during reconnection; supports invariance of helicity ratio; guides design of laboratory experiments to emulate astrophysical processes; contributes to energy cascades.

\paragraph{Encyclopedia.}
Definition of k,M,Rˆ2,Ωµ is an algebraic definition, written k,M,Rˆ2,Ωµ=kMR2Ω. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from k, M, R, defining k,M,Rˆ2,Ωµ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
