\section*{ID6842: Practical Code Sketch (Outline You Can Run): ∑\_k δ\_ell M(k) j\_ell(k R)}
\paragraph{Metadata.}
PiID: 0443325888569 | RTEID: RTE:P26569.0055:T6.0784 | UUID: ef97c856-a04a-5946-aacc-7abcdb810210

\paragraph{Canonical Statement.}
\#\# 7) Practical code sketch (outline you can run) - Compute SBT using (pseudocode): ```python for l in range(Lmax): for m in range(-l,l+1): for k in k\_grid: delta\_lm[k] = integral\_r\_and\_omega( delta(r,theta,phi) * j\_l(k r) * conj(Y\_lm(theta,phi)) * r\textasciicircum{}2 ) ``` - Compute tidal tensor using finite differences in Fourier space (Poisson solve): \textbackslash{}(\textbackslash{}Phi\_k = -\textbackslash{}delta\_k/k\textasciicircum{}2\textbackslash{}), transform back to compute ∂i∂jΦ. - Compare filament directions (eigenvector e3) with angular maxima of \textbackslash{}(\textbackslash{}sum\_k \textbackslash{}delta\_\{\textbackslash{}ell m\}(k) j\_\textbackslash{}ell(k r)\textbackslash{}).

\paragraph{Canonical Equation.}
\[
\sum_k \delta_{\ell m}(k) j_\ell(k r)
\]

\paragraph{Dictionary.}
Practical Code Sketch (Outline You Can Run): ∑\_k δ\_ell M(k) j\_ell(k R) — ∑\_k δ\_ℓ m(k) j\_ℓ(k r)

\paragraph{Encyclopedia.}
Practical Code Sketch (Outline You Can Run): ∑\_k δ\_ell M(k) j\_ell(k R) is a series / summation, written ∑\_k δ\_ℓ m(k) j\_ℓ(k r). It is expressed as a sum or series over modes or indices, superposing discrete contributions. It is built from ell, k, m, j, r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
