\tzpanchor{0130}
\tzpentryheader{0130}{Bridging Frequency Ratio}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{b32343ad-963b-57ef-ab2e-a23485fc7f4c}}\\
\textbf{PiID} & \tzpcode{5058223172535} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{137}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{504.8189 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.8318 rad}\\
\textbf{TZPID} & \tzpcode{ID0130} & \textbf{Node Dependencies}\quad \tzpidref{0129}\\
\textbf{Registry} & \tzpcode{registry\_id\_0130} & \textbf{Scale}\quad beat alignment across carrier bands\\
\textbf{LOC Classification} & QA371 resonance systems & QC670 wave and optical frequencies\\
\textbf{arXiv Classification} & Primary: physics.class-ph \quad Cross-list: physics.optics, nlin.PS & \\
\textbf{Primary Support} & Bridge Ratio & Carrier Rescaling\\
\textbf{Closure Support} & Bridge Frequency & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Given two carrier frequencies \(f_A\) and \(f_B\), scale both by a common factor \(S=\Delta/B\), where \(\Delta\) is the original frequency separation and \(B\) is the target beat frequency. The bridge carrier is then obtained by applying the rational lift \(r=32/27\) to the rescaled \(f_B\) carrier.

\tzpsection{Canonical Equation}
\[
r = \frac{32}{27}
\]
\[
S = \frac{\Delta}{B},
\qquad
f_A' = \frac{f_A}{S},
\qquad
f_B' = \frac{f_B}{S}
\]
\[
f_{\mathrm{bridge}} = r\,f_B'
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $f_A$: source equation symbol.
    \item $f_B$: source equation symbol.
    \item $f_{\mathrm{bridge}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0130 generated source Wolfram model *)
ClearAll[K0130, Cr0130, T, R, A, W, I, N];
eq0130$1 = HoldForm[r == 32/27];
eq0130$2 = HoldForm[TZPSequence[S == Delta/B, Derivative[1][fA] == fA/S, Derivative[1][fB] == fB/S]];
eq0130$3 = HoldForm[fBridge == r*Derivative[1][fB]];

K0130 = HoldForm[{eq0130$1, eq0130$2, eq0130$3}];

N = "normalized TRAWIN closure object for Bridging Frequency Ratio";
I = "Bridge Frequency integration/comparison layer";
W = "Carrier Rescaling wave or operator carrier";
A = "Bridge Ratio admissible action/amplitude condition";
R = "Carrier Rescaling rotation/curl preservation layer";
T = "Bridge Ratio local source condition";

Cr0130[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0130 = Cr0130[K0130];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Bridge Ratio local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Carrier Rescaling rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Bridge Ratio admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Carrier Rescaling wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Bridge Frequency integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Bridging Frequency Ratio.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0130] Bridging Frequency Ratio}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
r = \frac{32}{27}
\]
\[
S = \frac{\Delta}{B},
\qquad
f_A' = \frac{f_A}{S},
\qquad
f_B' = \frac{f_B}{S}
\]
\[
f_{\mathrm{bridge}} = r\,f_B'
\]

\paragraph{Primary Derivation.}
The relation is obtained by employing standard algebraic manipulations, yielding the required identity.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. From the TRAWIN perspective, the equation functions as the generalized carrier for the entry’s information content. Under CHL, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Bridging Frequency Ratio by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Bridge Ratio}\par
\[
r = \frac{32}{27}
\]
\noindent This identifies the rational lift factor used to move the aligned carrier into the bridge band.\par
\noindent\textbf{2. Carrier Rescaling}\par
\[
S = \frac{\Delta}{B},
\qquad
f_A' = \frac{f_A}{S},
\qquad
f_B' = \frac{f_B}{S}
\]
\noindent This enforces the common scaling that makes the target beat explicit before bridging.\par
\noindent\textbf{3. Bridge Frequency}\par
\[
f_{\mathrm{bridge}} = r\,f_B'
\]
\noindent This closes the progression by producing the new carrier that sits in the desired bridge relation to the rescaled system.\par

\clearpage
\noindent\textbf{[ID 0130] Bridging Frequency Ratio}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Bridging Frequency Ratio is a canonical-registry. Given two carriers f\_A and f\_B, scale both by the same factor S =  /B so that the difference becomes the target beat B. Define f\_A' = f\_A/S, f\_B' = f\_B/S and the bridging frequency f\_bridge = f\_B'   r. Interpretive Meaning: The rational ratio 32/27 acts as a deterministic map between two frequency states, serving as a "bridge" operator that stitches otherwise distinct carriers through a simple multiplication. Dependencies: Primitive

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Given two carriers f\_A and f\_B, scale both by the same factor S =  /B so that the difference becomes the target beat B. Define f\_A' = f\_A/S, f\_B' = f\_B/S and the bridging frequency f\_bridge = f\_B'   r. Interpretive Meaning: The rational ratio 32/27 acts as a deterministic map between two frequency states, serving as a "bridge" operator that stitches otherwise distinct carriers through a simple multiplication. Dependencies: Primitive
\textbf{Contextual meaning:} The rational ratio 32/27 acts as a deterministic map between two frequency states, serving as a "bridge" operator that stitches otherwise distinct carriers through a simple multiplication.
\textbf{Derivable consequences:} Source evidence records the entry as a reusable object whose consequences should be read from the matched formal statement and local proof route.
\textbf{Lemma support:} Given two carriers f\_A and f\_B, scale both by the same factor S =  /B so that the difference becomes the target beat B. Define f\_A' = f\_A/S, f\_B' = f\_B/S and the bridging frequency f\_bridge = f\_B'   r. Interpretive Meaning: The rational ratio 32/27 acts as a deterministic map between two frequency states, serving as a "bridge" operator that stitches otherwise distinct carriers through a simple multiplication. Dependencies: Primitive\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The rational ratio 32/27 acts as a deterministic map between two frequency states, serving as a "bridge" operator that stitches otherwise distinct carriers through a simple multiplication.

\tzpsection{Equation Grounding}
Given two carriers f\_A and f\_B, scale both by the same factor S =  /B so that the difference becomes the target beat B. Define f\_A' = f\_A/S, f\_B' = f\_B/S and the bridging frequency f\_bridge = f\_B'   r. Interpretive Meaning: The rational ratio 32/27 acts as a deterministic map between two frequency states, serving as a "bridge" operator that stitches otherwise distinct carriers through a simple multiplication. Dependencies: Primitive

\tzpsection{Interpretive Role}
The rational ratio 32/27 acts as a deterministic map between two frequency states, serving as a "bridge" operator that stitches otherwise distinct carriers through a simple multiplication.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Bridge Ratio}: The identification of the rational lift factor used to move the aligned carrier into the bridge band.
\item \textbf{Carrier Rescaling}: The enforcement of the common scaling that makes the target beat explicit before bridging.
\item \textbf{Bridge Frequency}: The production of the new carrier that sits in the desired bridge relation to the rescaled system.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0130]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0130_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0130] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Bridging Frequency Ratio}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} given two carrier frequencies \(f_A\) and \(f_B\), scale both by
\(S=\Delta/B\) and define the bridge carrier by \(f_{\mathrm{bridge}}=(32/27)f_B'\).

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Bridging Frequency Ratio is valid as a spectral relation when frequency, phase, and
propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0130_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
