\tzpanchor{0661}
\tzpentryheader{0661}{Convergence Locus Equation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{bcac5523-e54e-5a62-a29f-23b2af499e58}}\\
\textbf{PiID} & \tzpcode{2495343014654} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{668}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2539.6272 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.1845 rad}\\
\textbf{TZPID} & \tzpcode{ID0661} & \textbf{Node Dependencies}\quad \tzpidref{0660}\\
\textbf{Registry} & \tzpcode{registry\_id\_0661} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records convergence locus equation through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
S_A = -\mathrm{Tr}(\rho_A \log \rho_A).
\]
\[
\rho_A = \mathrm{Tr}_B(\rho).
\]
\[
\mathcal{A}_{\mathrm{TZP}}(\mathrm{id}_{0661})=\mathcal{A}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S_A$: source equation symbol.
    \item $\rho_A$: source equation symbol.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\mathcal{A}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{A}_{\mathrm{adm}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0661 generated source Wolfram model *)
ClearAll[K0661, Cr0661, T, R, A, W, I, N];
eq0661$1 = HoldForm[SA == -Tr[rhoAlog*rhoA]];
eq0661$2 = HoldForm[rhoA == TrB[rho]];
eq0661$3 = HoldForm[ATZP[id0661] == AAdm];

K0661 = HoldForm[{eq0661$1, eq0661$2, eq0661$3}];

N = "normalized TRAWIN closure object for Convergence Locus Equation";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Canonical Definition admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Canonical Definition local source condition";

Cr0661[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0661 = Cr0661[K0661];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Canonical Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Canonical Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Convergence Locus Equation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0661] Convergence Locus Equation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
S_A = -\mathrm{Tr}(\rho_A \log \rho_A).
\end{equation}

\paragraph{Primary Derivation.}
Let $\rho$ be the density matrix of a composite system partitioned into subsystems $A$ and $B$.

The reduced density matrix is:
\begin{equation}
\rho_A = \mathrm{Tr}_B(\rho).
\end{equation}

The entanglement entropy is defined as:
\begin{equation}
S_A = -\mathrm{Tr}(\rho_A \log \rho_A).
\end{equation}

\paragraph{Interpretation.}
Entropy measures quantum correlation between subsystems.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Convergence Locus Equation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Canonical Definition}\par
\[
S_A = -\mathrm{Tr}(\rho_A \log \rho_A).
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\rho_A = \mathrm{Tr}_B(\rho).
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\mathcal{A}_{\mathrm{TZP}}(\mathrm{id}_{0661})=\mathcal{A}_{\mathrm{adm}}
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0661] Convergence Locus Equation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Convergence Locus Equation is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} 4 to the power wedge 3=64. \textbf{Contextual meaning:} The entry reads Convergence Locus Equation as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Entropy measures quantum correlation between subsystems.

\tzpsection{Equation Grounding}
Equation anchors: 4 to the power wedge 3=64; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Strange-Attractor Dimensionality Scaling}: The bizarre mathematical discovery that the spot the system is trying to collapse into isn't a 3D ball, or a 2D circle, but a jagged, infinitely complex fractional shape like 2.5 dimensions.
\item \textbf{Lyapunov Exponent Trajectory Squeezing}: The incredibly specific calculation measuring exactly how fast two particles, dropped into the machine at completely different spots, are violently shoved together into the exact same location.
\item \textbf{Irreversible Information Loss Mapping}: The proof that once the system falls into the trap and settles down, it is absolutely, mathematically impossible to rewind the tape and figure out what the messy, chaotic starting condition was.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0661]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0661_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0661] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Convergence Locus Equation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records convergence locus equation through the Septenary derivation layer,
using the displayed relations as operational anchors for the c...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Convergence Locus Equation is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0661_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
