\section*{ID8803: ZERO-POINT ENERGY PUMPING MECHANISM Canonical Statutory Formula: η\_extraction}
\paragraph{Metadata.}
PiID: 9958180724716 | RTEID: RTE:P34184.0039:T6.0592 | UUID: 36cb7f4c-7e92-5b60-8732-52c28666f538

\paragraph{Canonical Statement.}
[ID 1184] ZERO-POINT ENERGY PUMPING MECHANISM Canonical Statutory Formula: \$\textbackslash{}eta\_\{extraction\} = 1 - \textbackslash{}exp(-\textbackslash{}pi \textbackslash{}cdot K\_\{max\}) \textbackslash{}approx 1\$ Formal Technical Dissertation: Formalizes the extraction efficiency at the critical frequency (\$8.8 \textbackslash{}times 10\textasciicircum{}\{16\}\$ Hz). As the Kissing Number \$K\_\{max\}\$ of the lattice approaches 153,600, the efficiency \$\textbackslash{}eta\$ approaches unity, enabling near-perfect vacuum energy harvesting. Source: [23]

\paragraph{Canonical Equation.}
\[
\eta_{extraction} = 1 - \exp(-\pi \cdot K_{max}) \approx 1
\]

\paragraph{Dictionary.}
ZERO-POINT ENERGY PUMPING MECHANISM Canonical Statutory Formula: \$ \_extraction = 1 - (- K\_max) 1\$ Formal Technical Dissertation: Formalizes the extraction efficiency at the critical frequency (8.8 × 10\textasciicircum{}16 Hz).

\paragraph{Encyclopedia.}
ZERO-POINT ENERGY PUMPING MECHANISM Canonical Statutory Formula: η\_extraction is a scaling / order-of-magnitude relation, written η\_extraction = 1 - exp(-π · K\_max) ≈ 1. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from π, K\_max, defining η\_extraction. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
