\tzpanchor{0146}
\tzpentryheader{0146}{Ion Density Redistribution Mechanism}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e017f642-46e9-587f-a23c-1c6c56a41db0}}\\
\textbf{PiID} & \tzpcode{8128481117450} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{153}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{566.9504 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.9342 rad}\\
\textbf{TZPID} & \tzpcode{ID0146} & \textbf{Node Dependencies}\quad \tzpidref{0145}\\
\textbf{Registry} & \tzpcode{registry\_id\_0146} & \textbf{Scale}\quad heavy/light ion separation in driven vortex cores\\
\textbf{LOC Classification} & QC611 conduction in media & QC718 plasma and charged fluids\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph \quad Cross-list: physics.flu-dyn, cond-mat.mtrl-sci & \\
\textbf{Primary Support} & Heavy-Ion Core Gain & Light-Ion Oscillatory Response\\
\textbf{Closure Support} & Battery Charge Functional & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Under high radial acceleration and oscillating charge, heavier ions concentrate at the vortex centre while lighter ions oscillate with the electric field. This results in ionic stratification and formation of a natural ``charge battery'' structure.

\tzpsection{Canonical Equation}
\[
n_h^{\mathrm{centre}} > n_h^{\mathrm{bulk}}
\]
\[
n_l(t)=n_{l,0}+\delta n_l \cos(\omega t)
\]
\[
Q_{\mathrm{batt}}=\int_V \rho_q\, dV
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $n_h$: source equation symbol.
    \item $n_l(t)$: source equation symbol.
    \item $n_{l,0}$: source equation symbol.
    \item $\delta$: point-source delta term that anchors the Green-function response.
    \item $\omega$: angular frequency term in the source equation.
    \item $t$: source equation symbol.
    \item $Q_{\mathrm{batt}}$: source equation symbol.
    \item $\rho_q$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0146 generated source Wolfram model *)
ClearAll[K0146, Cr0146, T, R, A, W, I, N];
eq0146$1 = HoldForm[nH^centre > nH^bulk];
eq0146$2 = HoldForm[nL[t] == nL0 + DiracDelta*nL*Cos[omega*t]];
eq0146$3 = HoldForm[QBatt == IntegralV*rhoQ*dV];

K0146 = HoldForm[{eq0146$1, eq0146$2, eq0146$3}];

N = "normalized TRAWIN closure object for Ion Density Redistribution Mechanism";
I = "Battery Charge Functional integration/comparison layer";
W = "Light-Ion Oscillatory Response wave or operator carrier";
A = "Heavy-Ion Core Gain admissible action/amplitude condition";
R = "Light-Ion Oscillatory Response rotation/curl preservation layer";
T = "Heavy-Ion Core Gain local source condition";

Cr0146[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0146 = Cr0146[K0146];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Heavy-Ion Core Gain local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Light-Ion Oscillatory Response rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Heavy-Ion Core Gain admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Light-Ion Oscillatory Response wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Battery Charge Functional integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Ion Density Redistribution Mechanism.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0146] Ion Density Redistribution Mechanism}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
n_h^{\mathrm{centre}} > n_h^{\mathrm{bulk}}
\]
\[
n_l(t)=n_{l,0}+\delta n_l \cos(\omega t)
\]
\[
Q_{\mathrm{batt}}=\int_V \rho_q\, dV
\]

\paragraph{Primary Derivation.}
The expression \( n_h^{\mathrm{centre}} > n_h^{\mathrm{bulk}} \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. Interpreted through TRAWIN, the equation functions as the integral carrier for the entry’s information content. Under CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Ion Density Redistribution Mechanism by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Heavy-Ion Core Gain}\par
\[
n_h^{\mathrm{centre}} > n_h^{\mathrm{bulk}}
\]
\noindent This states the static inward bias of the heavier species.\par
\noindent\textbf{2. Light-Ion Oscillatory Response}\par
\[
n_l(t)=n_{l,0}+\delta n_l \cos(\omega t)
\]
\noindent This records the greater time-dependent participation of the lighter species in the driven field.\par
\noindent\textbf{3. Battery Charge Functional}\par
\[
Q_{\mathrm{batt}}=\int_V \rho_q\, dV
\]
\noindent This closes the progression by converting the redistributed charge field into a stored net structure.\par

\clearpage
\noindent\textbf{[ID 0146] Ion Density Redistribution Mechanism}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Ion Density Redistribution Mechanism is a Structural Constraint. Under high radial acceleration and oscillating charge, heavier ions concentrate at the vortex centre while lighter ions oscillate with the electric field. This results in ionic stratification and formation of a natural "charge battery" structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Under high radial acceleration and oscillating charge, heavier ions concentrate at the vortex centre while lighter ions oscillate with the electric field. This results in ionic stratification and formation of a natural "charge battery" structure.
\textbf{Contextual meaning:} Mechanical and electrical forces separate ions by mass, leading to radial stratification and persistent charge gradients.
\textbf{Derivable consequences:} Mass dependent separation; creation of internal electric fields; synergy with chromatic ion sorting; design of vortex batteries. Falsifiability
\textbf{Lemma support:} Under high radial acceleration and oscillating charge, heavier ions concentrate at the vortex centre while lighter ions oscillate with the electric field. This results in ionic stratification and formation of a natural "charge battery" structure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Implement design changes individually and measure resulting pressure gradients and accelerations to validate predicted improvements. ID 146: Ion Density Redistribution Mechanism

\tzpsection{Equation Grounding}
Under high radial acceleration and oscillating charge, heavier ions concentrate at the vortex centre while lighter ions oscillate with the electric field. This results in ionic stratification and formation of a natural "charge battery" structure.

\tzpsection{Interpretive Role}
Mechanical and electrical forces separate ions by mass, leading to radial stratification and persistent charge gradients.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Heavy-Ion Core Gain}: The statement of the static inward bias of the heavier species.
\item \textbf{Light-Ion Oscillatory Response}: The record of the greater time-dependent participation of the lighter species in the driven field.
\item \textbf{Battery Charge Functional}: The conversion of the redistributed charge field into a stored net structure.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0146]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0146_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0146] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Ion Density Redistribution Mechanism}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} under high radial acceleration and oscillating charge, heavier ions concentrate at the
vortex centre while lighter ions oscillate with the electric...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Ion Density Redistribution Mechanism is valid as a formal registry statement when its
source equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that under high radial acceleration and oscillating charge,
heavier ions concentrate at the vortex centre while lighter ions oscillate with the
electric field. This results in ionic stratification and formation of a natural ``charge
battery'' structure. This entry continues the device arc by turning conductivity
enhancement into actual species-level separation.. The CHL validation treats the
equation as the formal anchor and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0146_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
