\section*{ID9458: Definition of MTZP : Jac(𝑝)}
\paragraph{Metadata.}
PiID: 7198492252847 | RTEID: RTE:P36727.5144:T3.9670 | UUID: 3fa1ac28-7486-557e-aa4e-5802057038f5

\paragraph{Canonical Statement.}
Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops the trawin zero point (tzp) existence axiom inside the quantum-classical transition arc of the directory. It treats the named object as a TRAWIN-admissible carrier that can be rendered, normalized, and linked forward into the surrounding registry pages. \$∃!\$ 𝑝 \$∈\$ MTZP : Jac(𝑝) = 0 \$∧ ΦB(𝑝)\$ = 𝜋 SingularityStructure(𝑝)  \$Node∞(MTZP)\$ Wolfram Form 𝔚TZP (K0550) \$↦−→ 〈 ΨT, Ω\$ T, 𝜌vac \$〉\$ K0550 := HoldForm(T0550) AdmissibleTZP (K0550) \$⇐⇒\$ 𝔚TZP (K0550) . \$∅\$ Wolfram register: canonical symbol lift Title lift: THE TRAWIN ZERO POINT (TZP) EXIS-TENCE AXIOM Symbol key: \$ΨT:\$ Trawinistic wavefunction \$ΩT:\$ Trawinistic boundary curvature 𝜌vac: vacuum energy density TRAWIN Norma

\paragraph{Canonical Equation.}
\[
MTZP : Jac(𝑝) = 0
\]

\paragraph{Dictionary.}
Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops the trawin zero point (tzp) existence axiom inside the quantum-c

\paragraph{Encyclopedia.}
Definition of MTZP : Jac(𝑝) is an algebraic definition, written MTZP : Jac(𝑝) = 0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
