\tzpanchor{0132}
\tzpentryheader{0132}{Phase Flip and Twist Transformation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{5038161e-c1f3-51a9-9f3d-d87f1af50b07}}\\
\textbf{PiID} & \tzpcode{5822317253594} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{139}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{512.5853 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.8446 rad}\\
\textbf{TZPID} & \tzpcode{ID0132} & \textbf{Node Dependencies}\quad \tzpidref{0131}\\
\textbf{Registry} & \tzpcode{registry\_id\_0132} & \textbf{Scale}\quad windowed bridge-tone phase manipulation\\
\textbf{LOC Classification} & QA371 phase transformations & QC20 wave phenomena\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: nlin.PS, physics.class-ph & \\
\textbf{Primary Support} & Phase Flip & Twist Function\\
\textbf{Closure Support} & Twisted Bridge Tone & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Within the Gaussian window, a phase flip imposes the constant shift

\tzpsection{Canonical Equation}
\[ \phi_3 = \pi, \] producing local cancellation of the bridge tone. A phase twist instead introduces the phase ramp \[ \phi_3(t) = \phi_0 + \kappa t, \] which generates a local winding number. Both operations act on the bridge tone only.

\[
\phi_3=\pi
\]
\[
\vartheta_{\mathrm{twist}}(t)=\kappa (t-t_0)
\]
\[
s_3^{\mathrm{twist}}(t)=g(t)\cos\!\bigl(2\pi f_{\mathrm{bridge}} t+\phi_3+\vartheta_{\mathrm{twist}}(t)\bigr)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\phi_3$: flux, phase, or topological map term in the source equation.
    \item $\pi$: source equation symbol.
    \item $\phi_0$: reference zero-point flux or normalization flux.
    \item $t$: source equation symbol.
    \item $t_0$: source equation symbol.
    \item $s_3$: source equation symbol.
    \item $f_{\mathrm{bridge}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0132 generated source Wolfram model *)
ClearAll[K0132, Cr0132, T, R, A, W, I, N];
eq0132$1 = HoldForm[phi3 == Pi];
eq0132$2 = HoldForm[phi3[t] == phi0 + kappa*t];
eq0132$3 = HoldForm[phi3 == Pi];
eq0132$4 = HoldForm[varthetaTwist[t] == kappa[t - t0]];
eq0132$5 = HoldForm[s3^twist*t == g[t]*Cos[2*Pi*fBridge*t + phi3 + varthetaTwist[t]]];

K0132 = HoldForm[{eq0132$1, eq0132$2, eq0132$3, eq0132$4, eq0132$5}];

N = "normalized TRAWIN closure object for Phase Flip and Twist Transformation";
I = "Twisted Bridge Tone integration/comparison layer";
W = "Twist Function wave or operator carrier";
A = "Phase Flip admissible action/amplitude condition";
R = "Twist Function rotation/curl preservation layer";
T = "Phase Flip local source condition";

Cr0132[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0132 = Cr0132[K0132];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Phase Flip local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Twist Function rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Phase Flip admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Twist Function wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Twisted Bridge Tone integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Phase Flip and Twist Transformation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0132] Phase Flip and Twist Transformation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[ \phi_3 = \pi, \] producing local cancellation of the bridge tone. A phase twist instead introduces the phase ramp \[ \phi_3(t) = \phi_0 + \kappa t, \] which generates a local winding number. Both operations act on the bridge tone only.

\[
\phi_3=\pi
\]
\[
\vartheta_{\mathrm{twist}}(t)=\kappa (t-t_0)
\]
\[
s_3^{\mathrm{twist}}(t)=g(t)\cos\!\bigl(2\pi f_{\mathrm{bridge}} t+\phi_3+\vartheta_{\mathrm{twist}}(t)\bigr)
\]

\paragraph{Primary Derivation.}
The relation is obtained through direct evaluation of the expression. yielding the required identity.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. Interpreted through TRAWIN, the equation functions as the generalized carrier for the entry’s information content. In CHL terms, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Phase Flip and Twist Transformation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Phase Flip}\par
\[
\phi_3=\pi
\]
\noindent This introduces the discrete inversion used inside the Gaussian insertion window.\par
\noindent\textbf{2. Twist Function}\par
\[
\vartheta_{\mathrm{twist}}(t)=\kappa (t-t_0)
\]
\noindent This adds a continuous phase drift that can accumulate across the window.\par
\noindent\textbf{3. Twisted Bridge Tone}\par
\[
s_3^{\mathrm{twist}}(t)=g(t)\cos\!\bigl(2\pi f_{\mathrm{bridge}} t+\phi_3+\vartheta_{\mathrm{twist}}(t)\bigr)
\]
\noindent This closes the progression by expressing the fully transformed local bridge carrier.\par

\clearpage
\noindent\textbf{[ID 0132] Phase Flip and Twist Transformation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Phase Flip and Twist Transformation is a Operator. Define a time localized Gaussian envelope g(t) = exp(-[(t -- t ) ]/(2   )). A signal combining scaled carriers and the bridge tone is s(t) = A  sin(2  f\_A' t +   ) + A  sin(2  f\_B' t +   ) + A  g(t) sin(2  f\_bridge t +   ), where   is small relative to the beat period.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Define a time localized Gaussian envelope g(t) = exp(-[(t -- t ) ]/(2   )). A signal combining scaled carriers and the bridge tone is s(t) = A  sin(2  f\_A' t +   ) + A  sin(2  f\_B' t +   ) + A  g(t) sin(2  f\_bridge t +   ), where   is small relative to the beat period.
\textbf{Contextual meaning:} A Gaussian envelope inserts the bridging tone only at specific times, creating a narrow "seam" between carriers.
\textbf{Derivable consequences:} Design of binaural beats; scaling of frequencies to desired difference; foundation for Gaussian insertion and phase manipulation.
\textbf{Lemma support:} Define a time localized Gaussian envelope g(t) = exp(-[(t -- t ) ]/(2   )). A signal combining scaled carriers and the bridge tone is s(t) = A  sin(2  f\_A' t +   ) + A  sin(2  f\_B' t +   ) + A  g(t) sin(2  f\_bridge t +   ), where   is small relative to the beat period.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Implement the scaling and verify that the resulting beat frequency matches the target; test stability of the bridging mapping. ID 131: Gaussian Window Insertion Operator

\tzpsection{Equation Grounding}
Define a time localized Gaussian envelope g(t) = exp(-[(t -- t ) ]/(2   )). A signal combining scaled carriers and the bridge tone is s(t) = A  sin(2  f\_A' t +   ) + A  sin(2  f\_B' t +   ) + A  g(t) sin(2  f\_bridge t +   ), where   is small relative to the beat period.

\tzpsection{Interpretive Role}
A Gaussian envelope inserts the bridging tone only at specific times, creating a narrow "seam" between carriers.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Phase Flip}: The introduction of the discrete inversion used inside the Gaussian insertion window.
\item \textbf{Twist Function}: The addition of a continuous phase drift that can accumulate across the window.
\item \textbf{Twisted Bridge Tone}: The expression of the fully transformed local bridge carrier.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0132]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0132_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0132] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Phase Flip and Twist Transformation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} within the Gaussian window, a phase flip imposes the constant shift \textbackslash{}[ \_3 = , \textbackslash{}]
producing local cancellation of the bridge tone

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Phase Flip and Twist Transformation is valid when the stated geometric or topological
relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0132_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
