\section*{ID10238: Predictions and Experimental Tests: Δ G/G ∼ 10\textasciicircum{}-3}
\paragraph{Metadata.}
PiID: 5107163785290 | RTEID: RTE:P39756.4276:T2.6745 | UUID: f7cd0d21-e93d-5c47-b951-b0c198a68cd3

\paragraph{Canonical Statement.}
\textbackslash{}begin\{enumerate\} \textbackslash{}item \textbackslash{}textbf\{Gravitational Constant Modulation.\} \$G\$ should vary sinusoidally with lunar phase at \$\textbackslash{}Delta G/G \textbackslash{}sim 10\textasciicircum{}\{-3\}\$, with period \$\textbackslash{}sim 27.32\$ days. High-precision gravimetry can detect this. \textbackslash{}item \textbackslash{}textbf\{Beat Frequency Modes.\} Gravitational wave detectors should observe subtle modulation sidebands around primary frequencies, corresponding to solar/lunar beat patterns. Standard GR predicts nearly clean sinusoids; Trawin predicts FM-like modulation structure. \textbackslash{}item \textbackslash{}textbf\{Quantum Flux Quantization in the Magnetosphere.\} Earth's field should exhibit discrete jumps during geomagnetic storms correspo

\paragraph{Canonical Equation.}
\[
\Delta G/G \sim 10^{-3}
\]

\paragraph{Dictionary.}
Predictions and Experimental Tests: Δ G/G ∼ 10\textasciicircum{}-3 — Δ G/G ∼ 10\textasciicircum{}-3

\paragraph{Encyclopedia.}
Predictions and Experimental Tests: Δ G/G ∼ 10\textasciicircum{}-3 is a scaling / order-of-magnitude relation, written Δ G/G ∼ 10\textasciicircum{}-3. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from Δ, G. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
