\tzpanchor{0329}
\tzpentryheader{0329}{Alfv\'en Wave Resonance in Gyromagnetic Systems}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{fa90a52d-cc76-5528-a6ba-dd4ece94974d}}\\
\textbf{PiID} & \tzpcode{0962829254091} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{336}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1277.5801 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.1051 rad}\\
\textbf{TZPID} & \tzpcode{ID0329} & \textbf{Node Dependencies}\quad \tzpidref{0328}\\
\textbf{Registry} & \tzpcode{registry\_id\_0329} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Dispersion Law & Standing Quantization\\
\textbf{Closure Support} & Mode Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The dispersion relation for Alfv'en waves in a gyromagnetic system with multipole corrections is omega2=k2vA2(1+k2lambda2)(1+k2rhos2)omega\textasciicircum{}2 = k\textasciicircum{}2 v\_A\textasciicircum{}2 bigl(1 + k\textasciicircum{}2 lambda\textasciicircum{}2bigr)(1 + k\textasciicircum{}2 rho\_s\textasciicircum{}2)omega2=k2vA2(1+k2lambda2)(1+k2rhos2), where vA=B/mu0rhov\_A = B/sqrt/\{mu\_0 rho/\}vA=B/mu0rho is the Alfv'en velocity and lambda,rhoslambda, rho\_slambda,rhos are characteristic length scales.

\tzpsection{Canonical Equation}
\[
\omega_{n}=k_{n}v_{\mathrm{A}},\qquad v_{\mathrm{A}}=B/\sqrt{\mu_{0}\rho}
\]
\[
k_{n}=n\pi/L,\qquad \Omega_{\mathrm{g}}=qB/m
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\omega_{n}$: mode-indexed angular frequency.
    \item $n$: integer mode index.
    \item $k_{n}$: mode-indexed wavenumber.
    \item $v_{\mathrm{A}}$: Alfven velocity or carrier speed.
    \item $B$: magnetic field magnitude.
    \item $\mu_{0}$: vacuum permeability constant.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\pi$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $\Omega_{\mathrm{g}}$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0329 generated source Wolfram model *)
ClearAll[K0329, Cr0329, T, R, A, W, I, N];
eq0329$1 = HoldForm[TZPSequence[omegaN == kNvA, vA == B/sqrt[mu0*rho]]];
eq0329$2 = HoldForm[TZPSequence[kN == nPi/L, OmegaG == qB/m]];
eq0329$3 = HoldForm[omegaN == mOmegaG];

K0329 = HoldForm[{eq0329$1, eq0329$2, eq0329$3}];

N = "normalized TRAWIN closure object for Alfv\'en Wave Resonance in Gyromagnetic Systems";
I = "Mode Closure integration/comparison layer";
W = "Standing Quantization wave or operator carrier";
A = "Dispersion Law admissible action/amplitude condition";
R = "Standing Quantization rotation/curl preservation layer";
T = "Dispersion Law local source condition";

Cr0329[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0329 = Cr0329[K0329];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Dispersion Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Standing Quantization rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Dispersion Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Standing Quantization wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Mode Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Alfv\textbackslash{}'en Wave Resonance in Gyromagnetic Systems.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0329] Alfv\'en Wave Resonance in Gyromagnetic Systems}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}

Synchronization between oscillators can be modelled by a phase‑locked loop equation.

\paragraph{Primary Derivation.}

Let $\theta(t)$ denote the phase difference between an input signal and a reference oscillator.  A first‑order phase‑locked loop (PLL) obeys

\begin{equation}
\dot{\theta}(t) = \omega_{\mathrm{in}} - \omega_{\mathrm{out}} - K\sin\theta(t),
\end{equation}

where $K$ is the loop gain.  Locking occurs when the mean phase drift vanishes, i.e. $\omega_{\mathrm{in}} = \omega_{\mathrm{out}}$ and $\sin\theta(t)$ balances any mismatch.
Linearizing around the locked state yields stability conditions on $K$.

\paragraph{Interpretation.}

Phase‑locked loops are ubiquitous in signal processing.  Near the TZP they describe how energy and information streams adjust their phases to maintain coherence.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Alfv\textbackslash{}'en Wave Resonance in Gyromagnetic Systems by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Dispersion Law}\par
\[
\omega_{n}=k_{n}v_{\mathrm{A}},\qquad v_{\mathrm{A}}=B/\sqrt{\mu_{0}\rho}
\]
\noindent This fixes the traveling Alfv\textbackslash{}'en carrier that later entries quantize and redistribute.\par
\noindent\textbf{2. Standing Quantization}\par
\[
k_{n}=n\pi/L,\qquad \Omega_{\mathrm{g}}=qB/m
\]
\noindent This turns the continuous wave law into an admissible standing-mode ladder on the bounded carrier.\par
\noindent\textbf{3. Mode Closure}\par
\[
\omega_{n}\approx m\Omega_{\mathrm{g}}
\]
\noindent This closes the progression by tying the standing spectrum to an actual mode-index relation.\par

\clearpage
\noindent\textbf{[ID 0329] Alfv\'en Wave Resonance in Gyromagnetic Systems}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Alfv en Wave Resonance in Gyromagnetic Systems is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The dispersion relation for Alfv en waves in a gyromagnetic system with multipole corrections is omega2=k2vA2(1+k2lambda2)(1+k2rhos2)omega to the power 2 = k to the power 2 v sub A to the power 2 bigl(1 + k to the power 2 lambda to the power 2bigr)(1 + k to the power 2 rho sub s to the power 2)omega2=k2vA2(1+k2lambda2)(1+k2rhos2), where vA=B/mu0rhov sub A = B/sqrt/ mu sub 0 rho/ vA=B/mu0rho is the Alfv en velocity and lambda,rhoslambda, rho sub slambda,rhos are characteristic length scales. \textbf{Contextual meaning:} The entry reads Alfv en Wave Resonance in Gyromagnetic Systems as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The hinge entry turns the terminal synchronization logic of the third book into the carried bridge law that the quaternary volume repeatedly acts on. \textbf{Lemma support:} Dispersion Law; Standing Quantization; Mode Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Phase-locked loops are ubiquitous in signal processing. Near the TZP they describe how energy and information streams adjust their phases to maintain coherence.

\tzpsection{Equation Grounding}
Equation anchors: [L82] r u00d7 (E u00d7 B) dr [L83] 3x +r [L84] Xu221er [L85] m=1r [L86] mr [L87] RKKr [L88] HKKr [L89] m (9)r [L90] Proposition 2; quantization:r [L57] Ir [L58] v u00b7 du2113 =r [L59] 2u03c0u210fnr [L60] mr [L61] (15)r [L62] 5 Critical Phenomena and Phase Transitionsr [L63] 5; and r [L83] 2u03c12r [L84] sr [L85] u0013r [L86] (17)r [L87] Where vA = B/u221au00b50u03c1 is the Alfvu00b4en velocity. Proof route: show that the bounded-mode condition follows from the dispersion law once the carrier is normalized on the finite rotating radius. Formalization route: prove that the standing-mode frequency formula is equivalent to the bounded Alfv en carrier under TRAWIN normalization.

\tzpsection{Interpretive Role}
The hinge entry turns the terminal synchronization logic of the third book into the carried bridge law that the quaternary volume repeatedly acts on.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Magnetohydrodynamic Standing Waves}: The stable oscillation of coupled plasma ions and magnetic field lines trapped within a bounded geometric cavity.
\item \textbf{Transverse Magnetic Tension Propagation}: The specific wave mode where restoring forces are provided by the elasticity of the magnetic flux tubes.
\item \textbf{Bounded Plasma Frequency Quantization}: The restriction of continuous Alfven velocities into a discrete ladder of allowed standing-mode frequencies.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0329]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0329_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0329] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Alfv\'en Wave Resonance in Gyromagnetic Systems}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the dispersion relation for Alfv'en waves in a gyromagnetic system with multipole
corrections is omega2=k2vA2(1+k2lambda2)(1+k2rhos2)omega\textasciicircum{}2 = k\textasciicircum{}2...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Alfvén Wave Resonance in Gyromagnetic Systems is valid as a spectral relation when
frequency, phase, and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0329_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
