\tzpanchor{0323}
\tzpentryheader{0323}{Gyromagnetic Vector Potential Expansion}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{02da6bfe-6636-57d4-b891-8d8109da5fec}}\\
\textbf{PiID} & \tzpcode{1520920962829} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{330}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1254.2807 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.0667 rad}\\
\textbf{TZPID} & \tzpcode{ID0323} & \textbf{Node Dependencies}\quad \tzpidref{0322}\\
\textbf{Registry} & \tzpcode{registry\_id\_0323} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Total Vector Potential & Dipole Sector\\
\textbf{Closure Support} & Induced Sector & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The vector potential is decomposed into contributions from the effective dipole, the gyroscopic current distribution, and induced currents due to time-varying fields.

\tzpsection{Canonical Equation}
\[
\mathbf{A}=\mathbf{A}_{\mathrm{dip}}+\mathbf{A}_{\mathrm{ind}}
\]
\[
\mathbf{A}_{\mathrm{dip}}=\frac{\mu_{0}}{4\pi}\frac{\mathbf{m}\times\mathbf{r}}{\lVert\mathbf{r}\rVert^{3}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $A$: source equation symbol.
    \item $\mu_{0}$: vacuum permeability constant.
    \item $\pi$: source equation symbol.
    \item $J$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0323 generated source Wolfram model *)
ClearAll[K0323, Cr0323, T, R, A, W, I, N];
eq0323$1 = HoldForm[A == ADip + AInd];
eq0323$2 = HoldForm[ADip == (mu0/(4*Pi))*((m*r)/lVertrrVert^3)];
eq0323$3 = HoldForm[AInd[r] == (mu0/(4*Pi))*Integral[JInd[r^prime]/(lVertr - r^prime*rVert)]*d^3*r^prime];

K0323 = HoldForm[{eq0323$1, eq0323$2, eq0323$3}];

N = "normalized TRAWIN closure object for Gyromagnetic Vector Potential Expansion";
I = "Induced Sector integration/comparison layer";
W = "Dipole Sector wave or operator carrier";
A = "Total Vector Potential admissible action/amplitude condition";
R = "Dipole Sector rotation/curl preservation layer";
T = "Total Vector Potential local source condition";

Cr0323[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0323 = Cr0323[K0323];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Total Vector Potential local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Dipole Sector rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Total Vector Potential admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Dipole Sector wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Induced Sector integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Gyromagnetic Vector Potential Expansion.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0323] Gyromagnetic Vector Potential Expansion}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
V_T(x)
=
\lambda
\exp\left(
-\frac{d(x,p)}{u_T}
\right).
\end{equation}

\paragraph{Primary Derivation.}
Let $d(x,p)$ be the geodesic distance from a point $x$ to the TZP.  
A potential localized around $p$ should be strongest at $x=p$ and decay with distance.

At the zero point:

\begin{equation}
d(p,p)=0 .
\end{equation}

Therefore:

\begin{equation}
V_T(p)=\lambda e^0=\lambda .
\end{equation}

To create exponential decay away from $p$, scale distance by the Trawin base unit $u_T$:

\begin{equation}
\exp\left(-\frac{d(x,p)}{u_T}\right).
\end{equation}

Multiplying by coupling constant $\lambda$ gives:

\begin{equation}
\boxed{
V_T(x)
=
\lambda
\exp\left(
-\frac{d(x,p)}{u_T}
\right).
}
\end{equation}

\paragraph{Interpretation.}
The TZP potential is a localized exponential well or source centered at $p$, controlled by the coupling $\lambda$ and decay scale $u_T$.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Gyromagnetic Vector Potential Expansion by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Total Vector Potential}\par
\[
\mathbf{A}=\mathbf{A}_{\mathrm{dip}}+\mathbf{A}_{\mathrm{ind}}
\]
\noindent This fixes the full vector-potential decomposition of the gyromagnetic carrier.\par
\noindent\textbf{2. Dipole Sector}\par
\[
\mathbf{A}_{\mathrm{dip}}=\frac{\mu_{0}}{4\pi}\frac{\mathbf{m}\times\mathbf{r}}{\lVert\mathbf{r}\rVert^{3}}
\]
\noindent This isolates the dipole contribution generated by the effective moment about the center of mass.\par
\noindent\textbf{3. Induced Sector}\par
\[
\mathbf{A}_{\mathrm{ind}}(\mathbf{r})=\frac{\mu_{0}}{4\pi}\int \frac{\mathbf{J}_{\mathrm{ind}}(\mathbf{r}^{\prime})}{\lVert\mathbf{r}-\mathbf{r}^{\prime}\rVert}\,d^{3}r^{\prime}
\]
\noindent This closes the entry by adding the retarded induced-current contribution to the total potential.\par

\clearpage
\noindent\textbf{[ID 0323] Gyromagnetic Vector Potential Expansion}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Gyromagnetic Vector Potential Expansion is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The vector potential is decomposed into contributions from the effective dipole, the gyroscopic current distribution, and induced currents due to time-varying fields. \textbf{Contextual meaning:} The entry reads Gyromagnetic Vector Potential Expansion as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the vector-potential expansion directly instead of carrying headings and prose fragments into the equation slots. \textbf{Lemma support:} Total Vector Potential; Dipole Sector; Induced Sector.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP potential is a localized exponential well or source centered at p, controlled by the coupling and decay scale u sub T.

\tzpsection{Equation Grounding}
Equation anchors: approx; a critical value qcriticalapproximately2; and qcriticalapproximately2. Proof route: show that the dipole, gyroscopic, and induced sectors combine into the stated total vector potential. Formalization route: prove that the induced-current integral contributes the stated correction to the total vector-potential expansion.

\tzpsection{Interpretive Role}
The entry now states the vector-potential expansion directly instead of carrying headings and prose fragments into the equation slots.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Retarded Induced Currents}: The vector field component generated dynamically by the time-delayed motion of distant electric charges.
\item \textbf{Multipolar Magnetic Expansion}: The series approximation breaking down a complex magnetic field into its fundamental dipole, quadrupole, and higher-order geometric shapes.
\item \textbf{Superposed Vector Fields}: The linear combination of static background potentials with active, time-varying dynamic potentials.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0323]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0323_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0323] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Gyromagnetic Vector Potential Expansion}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the vector potential is decomposed into contributions from the effective dipole, the
gyroscopic current distribution, and induced currents due to t...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Gyromagnetic Vector Potential Expansion is valid as a synchronization criterion under
the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0323_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
