\section*{ID9346: Definition of Gunif}
\paragraph{Metadata.}
PiID: 7556003727983 | RTEID: RTE:P36292.5935:T3.2504 | UUID: af4d18d5-d78a-5e96-8c30-7cc93dfb1a29

\paragraph{Canonical Statement.}
belle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0164], [ID 0165] Node registry\_id\_0166 Support Titles Unified Triple; Compatibility Relation; Unitary Holonomy Test Handle If no complex structure can simultaneously relate the metric and Berry form as stated, the Kähler-manifold synthesis fails. Canonical Equation Links \$Gunif=(𝑔,ΩB\$ ,𝐽 ) \$ΩB\$ (𝑋,𝑌 )=𝑔 (𝐽𝑋,𝑌 ) Hol(Gunif \$)⊆𝑈\$ (𝑛) [ID 0167] Unified Field Equation (Einstein–Yang–Mills–Quantum) TZPID ID0167 UUID 546d824d-3c7f-599b-99c0-dee2403a5346 Type Field Equation Scale full relativistic-gauge-quantum closure law LOC Classification Working routing: QC178 field equations; QC174 Yang–Mills structure arXiv Classification Primary: hep-th Cross-list: gr-qc, math-ph Canonical St

\paragraph{Canonical Equation.}
\[
Gunif=(𝑔,ΩB
\]

\paragraph{Dictionary.}
Definition of Gunif — Gunif=(𝑔,ΩB

\paragraph{Encyclopedia.}
Definition of Gunif is an algebraic definition, written Gunif=(𝑔,ΩB. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from B, defining Gunif. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
