\tzpanchor{0148}
\tzpentryheader{0148}{Phase Twist-Induced Domain Wall}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{aedb7b37-6bc8-5cf4-81fe-4f81732b3912}}\\
\textbf{PiID} & \tzpcode{2848111745028} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{155}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{574.7169 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.9470 rad}\\
\textbf{TZPID} & \tzpcode{ID0148} & \textbf{Node Dependencies}\quad \tzpidref{0147}\\
\textbf{Registry} & \tzpcode{registry\_id\_0148} & \textbf{Scale}\quad windowed phase-ramp seam between frequency states\\
\textbf{LOC Classification} & QA612 algebraic topology & QA371 phase systems\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: cond-mat.mes-hall, nlin.PS & \\
\textbf{Primary Support} & Wall Phase Profile & Net Phase Jump\\
\textbf{Closure Support} & Wall Winding & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Introducing a smooth phase ramp over the Gaussian window creates a domain wall connecting two frequency states. The ramp carries a non-trivial winding number, forming a topological defect that cannot be removed by local perturbations.

\tzpsection{Canonical Equation}
\[
\phi(x)=\pi\left[\frac{1+\tanh((x-x_0)/w)}{2}\right]
\]
\[
\Delta\phi = \phi(+\infty)-\phi(-\infty)=\pi
\]
\[
\nu_{\mathrm{wall}}=\frac{1}{2\pi}\int \partial_x\phi\,dx
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\phi(x)$: flux, phase, or topological map term in the source equation.
    \item $\pi$: source equation symbol.
    \item $x_0$: source equation symbol.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $\tanh$: source equation symbol.
    \item $\Delta$: source equation symbol.
    \item $\nu_{wall}$: source equation symbol.
    \item $D$: source equation symbol.
    \item $i(x)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0148 generated source Wolfram model *)
ClearAll[K0148, Cr0148, T, R, A, W, I, N];
eq0148$1 = HoldForm[phi[x] == Pi[(1 + tanh[(x - x0)/w])/2]];
eq0148$2 = HoldForm[Deltaphi == phi[Plus[Infinity]] - phi[-Infinity] == Pi];
eq0148$3 = HoldForm[nuWall == (1/(2*Pi))*Integral*PartialXphi*dx];

K0148 = HoldForm[{eq0148$1, eq0148$2, eq0148$3}];

N = "normalized TRAWIN closure object for Phase Twist-Induced Domain Wall";
I = "Wall Winding integration/comparison layer";
W = "Net Phase Jump wave or operator carrier";
A = "Wall Phase Profile admissible action/amplitude condition";
R = "Net Phase Jump rotation/curl preservation layer";
T = "Wall Phase Profile local source condition";

Cr0148[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0148 = Cr0148[K0148];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Wall Phase Profile local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Net Phase Jump rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Wall Phase Profile admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Net Phase Jump wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Wall Winding integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Phase Twist-Induced Domain Wall.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0148] Phase Twist-Induced Domain Wall}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\phi(x)=\pi\left[\frac{1+\tanh((x-x_0)/w)}{2}\right]
\]
\[
\Delta\phi = \phi(+\infty)-\phi(-\infty)=\pi
\]
\[
\nu_{\mathrm{wall}}=\frac{1}{2\pi}\int \partial_x\phi\,dx
\]

\paragraph{Primary Derivation.}
The relation is obtained by differentiating and applying the relevant definitions. yielding the required identity.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. From the TRAWIN perspective, the equation functions as the generalized carrier for the entry’s information content. In CHL terms, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Phase Twist-Induced Domain Wall by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Wall Phase Profile}\par
\[
\phi(x)=\pi\left[\frac{1+\tanh((x-x_0)/w)}{2}\right]
\]
\noindent This defines the smooth transition between the two local phase sectors.\par
\noindent\textbf{2. Net Phase Jump}\par
\[
\Delta\phi = \phi(+\infty)-\phi(-\infty)=\pi
\]
\noindent This states the nontrivial jump carried by the wall.\par
\noindent\textbf{3. Wall Winding}\par
\[
\nu_{\mathrm{wall}}=\frac{1}{2\pi}\int \partial_x\phi\,dx
\]
\noindent This closes the progression by turning the seam into a quantifiable topological object.\par

\clearpage
\noindent\textbf{[ID 0148] Phase Twist-Induced Domain Wall}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Phase Twist-Induced Domain Wall is a Structural Constraint. Introducing a smooth phase ramp over the Gaussian window creates a domain wall connecting two frequency states. The ramp carries a non trivial winding number, forming a topological defect that cannot be removed by local perturbations.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Introducing a smooth phase ramp over the Gaussian window creates a domain wall connecting two frequency states. The ramp carries a non trivial winding number, forming a topological defect that cannot be removed by local perturbations.
\textbf{Contextual meaning:} Dependencies: 131 Derivable Consequences: Local amplitude gating; selective inversion; design of gating functions; controlled signal switching. Falsifiability / Test Handle: Synthesize signals with a phase flipped bridge and observe local cancellation; vary phase to confirm effect disappears for other values. ID 148: Phase Twist Induced Domain Wall Type: Structural Constraint Formal Statement: Introducing a smooth phase ramp over the Gaussian window creates a domain wall connecting two frequency states.
\textbf{Derivable consequences:} Local amplitude gating; selective inversion; design of gating functions; controlled signal switching.
\textbf{Lemma support:} Introducing a smooth phase ramp over the Gaussian window creates a domain wall connecting two frequency states. The ramp carries a non trivial winding number, forming a topological defect that cannot be removed by local perturbations.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Synthesize signals with a phase flipped bridge and observe local cancellation; vary phase to confirm effect disappears for other values. ID 148: Phase Twist Induced Domain Wall

\tzpsection{Equation Grounding}
Introducing a smooth phase ramp over the Gaussian window creates a domain wall connecting two frequency states. The ramp carries a non trivial winding number, forming a topological defect that cannot be removed by local perturbations.

\tzpsection{Interpretive Role}
Dependencies: 131 Derivable Consequences: Local amplitude gating; selective inversion; design of gating functions; controlled signal switching. Falsifiability / Test Handle: Synthesize signals with a phase flipped bridge and observe local cancellation; vary phase to confirm effect disappears for other values. ID 148: Phase Twist Induced Domain Wall Type: Structural Constraint Formal Statement: Introducing a smooth phase ramp over the Gaussian window creates a domain wall connecting two frequency states.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Wall Phase Profile}: The definition of the smooth transition between the two local phase sectors.
\item \textbf{Net Phase Jump}: The statement of the nontrivial jump carried by the wall.
\item \textbf{Wall Winding}: The conversion of the seam into a quantifiable topological object.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0148]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0148_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0148] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Phase Twist-Induced Domain Wall}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} introducing a smooth phase ramp over the Gaussian window creates a domain wall
connecting two frequency states

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Phase Twist-Induced Domain Wall is valid as a spectral relation when frequency, phase,
and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0148_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
