\tzpanchor{0487}
\tzpentryheader{0487}{Hilbert Space Decomposition}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{df975d95-bd3e-56fc-8b43-b34b995b5973}}\\
\textbf{PiID} & \tzpcode{3818301194912} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{494}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1875.5963 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.0904 rad}\\
\textbf{TZPID} & \tzpcode{ID0487} & \textbf{Node Dependencies}\quad \tzpidref{0486}\\
\textbf{Registry} & \tzpcode{registry\_id\_0487} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Generator Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 487 defines multi modal state tracking across the tripartite channels. By decomposing the global Hilbert space, the system can independently optimize the Energy and Information lobes without causing cross channel interference. This is the foundation for natural multi qubit gates. Subspace Management: Allocates computational resources between the classical address and quantum payload. Modal Independence: Allows for the rotation of the DAANS axis without collapsing the atemporal state.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{H}_{\text{total}} = \cdots
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{H}$: source equation symbol.
    \item $\mathcal{K}_{0487}$: canonical registry object for entry ID 0487.
    \item $\cdot s$: source equation symbol.
    \item $H_{total}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0487 generated source Wolfram model *)
ClearAll[K0487, Cr0487, T, R, A, W, I, N];
eq0487$1 = HoldForm[H == Ellipsis];

K0487 = HoldForm[{eq0487$1}];

N = "normalized TRAWIN closure object for Hilbert Space Decomposition";
I = "Hilbert Space Decomposition integration/comparison layer";
W = "Hilbert Space Decomposition wave or operator carrier";
A = "Hilbert Space Decomposition admissible action/amplitude condition";
R = "Hilbert Space Decomposition rotation/curl preservation layer";
T = "Hilbert Space Decomposition local source condition";

Cr0487[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0487 = Cr0487[K0487];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Hilbert Space Decomposition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Hilbert Space Decomposition rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Hilbert Space Decomposition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Hilbert Space Decomposition wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Hilbert Space Decomposition integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Hilbert Space Decomposition.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0487] Hilbert Space Decomposition}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\dot{\omega}(t)
=
\frac{\tau_{\mathrm{em}}(t)}{I_T}.
\end{equation}

\begin{equation}
\omega(t)
=
\omega(0)
+
\frac{1}{I_T}
\int_0^t
\tau_{\mathrm{em}}(t')
\,\mathrm{d}t' .
\end{equation}

\paragraph{Primary Derivation.}
Let $I_T$ be the Trawinistic moment of inertia.  
Angular momentum is related to angular velocity by:
\begin{equation}
L=I_T\omega .
\end{equation}

Differentiating gives:
\begin{equation}
\dot{L}
=
I_T\dot{\omega},
\end{equation}
assuming $I_T$ is constant over the interval.

Since $\dot{L}=\tau_{\mathrm{em}}$, we obtain:
\begin{equation}
\dot{\omega}(t)
=
\frac{\tau_{\mathrm{em}}(t)}{I_T}.
\end{equation}

Integrating through time gives:
\begin{equation}
\boxed{
\omega(t)
=
\omega(0)
+
\frac{1}{I_T}
\int_0^t
\tau_{\mathrm{em}}(t')
\,\mathrm{d}t' .
}
\end{equation}

\paragraph{Interpretation.}
Rotation is the accumulated response to torque history, scaled by the effective moment of inertia.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Hilbert Space Decomposition by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{H}_{\text{total}} = \cdots
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0487] Hilbert Space Decomposition}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Hilbert Space Decomposition is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 487 defines multi modal state tracking across the tripartite channels. By decomposing the global Hilbert space, the system can independently optimize the Energy and Information lobes without causing cross channel interference. This is the foundation for natural multi qubit gates. Subspace Management: Allocates computational resources between the classical address and quantum payload. Modal Independence: Allows for the rotation of the DAANS axis without collapsing the atemporal state.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{H}_{\text{total}} = \cdots
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 487 defines multi modal state tracking across the tripartite channels. By decomposing the global Hilbert space, the system can independently optimize the Energy and Information lobes without causing cross channel interference. This is the foundation for natural multi qubit gates. Subspace Management: Allocates computational resources between the classical address and quantum payload. Modal Independence: Allows for the rotation of the DAANS axis without collapsing the atemporal state.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Hilbert Space Decomposition by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Hilbert Space Decomposition; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0487]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0487].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0487] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Hilbert Space Decomposition}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} = mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} otimes mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} otimes mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``HILBERT SPACE DECOMPOSITION is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} = mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} otimes mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} otimes
mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{}. Rotation is the accumulated response to torque history, scaled by the
effective moment of inertia. -----------------------------------------------------------
-------------------------------------------------------------. The CHL validation treats
the equation as the formal anchor and the semantic text as the interpretation
constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0487].
\par\endgroup
\vfill
\endgroup
\endgroup
