\section*{ID9229: Definition of U(1),|,∇ˆ2φ}
\paragraph{Metadata.}
PiID: 7807057656151 | RTEID: RTE:P35838.2566:T2.5018 | UUID: df696ca2-97b5-5477-9702-c99fedd68cbf

\paragraph{Canonical Statement.}
4: Extended Phase Space for MagnetoAcoustic–Kaluza–Klein Systems Type: Definition Formal Statement: The configuration manifold for coupled magnetoacoustic and compactified extradimensional modes is \$M=m=0∞(TSO(3)× R3⊗HmKK)/GgaugeM\$ = \textbackslash{}prod \{m=0\}\{\textbackslash{}infty\}(T*SO(3) \textbackslash{}times \textbackslash{}mathbb\{R\}ˆ3 \textbackslash{}otimes \$Hˆ\{KK\} m)/G \{\textbackslash{}text\{gauge\}\}M=m=0∞(TSO(3)× R3⊗HmKK)/Ggauge,\$ where HmKKHˆ\{KK\} mHmKK denotes the mmmth Kaluza–Klein sector Hilbert space and \$Ggauge=\{:R3→U(1)∇2=0\}G \{\textbackslash{}text\{gauge\}\}\$ = \{\textbackslash{}phi : \textbackslash{}mathbb\{R\}ˆ3 \textbackslash{}to \$U(1),|,\textbackslash{}nablaˆ2\textbackslash{}phi=0\}Ggauge=\{:R3→U(1)∇2=0\}\$ fixes gauge freedom. Interpretive Meaning: This extended phase space captures the degrees of freedom for magnetoacoustic fields coupled to a tower of Kaluza–Klein modes. It includes rotational and translational variables as well as gauge degrees of freedom and infinite KK sectors. Dependencies: ID 200 (implicit magnetoacoustic theory). Derivable Consequences: (1) Provides the state space for defi

\paragraph{Canonical Equation.}
\[
U(1),|,\nablaˆ2\phi=0}Ggauge={:R3→U(1)∇2=0}
\]

\paragraph{Dictionary.}
Definition of U(1),|,∇ˆ2φ — U(1),|,∇ˆ2φ=0Ggauge=:R3→U(1)∇2=0

\paragraph{Encyclopedia.}
Definition of U(1),|,∇ˆ2φ is a differential equation, written U(1),|,∇ˆ2φ=0Ggauge=:R3→U(1)∇2=0. It relates the quantity to its derivatives, governing how the system evolves in space and time. It is built from G, g, a, u, R, U, defining U(1),|,∇ˆ2φ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
