\tzpanchor{0755}
\tzpentryheader{0755}{NEUTRINO GHOST-FIELD MAPPING (hatPhi\_nu)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{8bf42df8-be46-5d5c-8d61-09aaee47431d}}\\
\textbf{PiID} & \tzpcode{7211349999998} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{762}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2896.8837 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.7732 rad}\\
\textbf{TZPID} & \tzpcode{ID0755} & \textbf{Node Dependencies}\quad \tzpidref{0754}\\
\textbf{Registry} & \tzpcode{registry\_id\_0755} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records neutrino ghost-field mapping (hatphi\_nu) through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0755}}:\mathcal{X}_{\mathrm{id0755}}\longrightarrow\mathcal{Y}_{\mathrm{id0755}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0755}})=\mathcal{O}_{\mathrm{id0755}}
\]
\[
\mathcal{O}_{\mathrm{id0755}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0755}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0755}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0755}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0755 generated source Wolfram model *)
ClearAll[K0755, Cr0755, T, R, A, W, I, N];
eq0755$1 = HoldForm[Oid0755[Xid0755] -> Yid0755];
eq0755$2 = HoldForm[NTRAWIN[OId0755] == OId0755];
eq0755$3 = HoldForm[Element[OId0755[x], YAdm]];

K0755 = HoldForm[{eq0755$1, eq0755$2, eq0755$3}];

N = "normalized TRAWIN closure object for NEUTRINO GHOST-FIELD MAPPING (hatPhi\_nu)";
I = "NEUTRINO GHOST-FIELD MAPPING (hatPhi\_nu) integration/comparison layer";
W = "NEUTRINO GHOST-FIELD MAPPING (hatPhi\_nu) wave or operator carrier";
A = "NEUTRINO GHOST-FIELD MAPPING (hatPhi\_nu) admissible action/amplitude condition";
R = "NEUTRINO GHOST-FIELD MAPPING (hatPhi\_nu) rotation/curl preservation layer";
T = "NEUTRINO GHOST-FIELD MAPPING (hatPhi\_nu) local source condition";

Cr0755[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0755 = Cr0755[K0755];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ NEUTRINO GHOST-FIELD MAPPING (hatPhi\textbackslash{}\_nu) local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ NEUTRINO GHOST-FIELD MAPPING (hatPhi\textbackslash{}\_nu) rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ NEUTRINO GHOST-FIELD MAPPING (hatPhi\textbackslash{}\_nu) admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ NEUTRINO GHOST-FIELD MAPPING (hatPhi\textbackslash{}\_nu) wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ NEUTRINO GHOST-FIELD MAPPING (hatPhi\textbackslash{}\_nu) integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for NEUTRINO GHOST-FIELD MAPPING (hatPhi\textbackslash{}\_nu).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0755] NEUTRINO GHOST-FIELD MAPPING (hatPhi\_nu)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0755}}:\mathcal{X}_{\mathrm{id0755}}\longrightarrow\mathcal{Y}_{\mathrm{id0755}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0755}})=\mathcal{O}_{\mathrm{id0755}}
\]
\[
\mathcal{O}_{\mathrm{id0755}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0755}})=\mathcal{O}_{\mathrm{id0755}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. From the TRAWIN perspective, the equation functions as the mapping carrier for the entry’s information content. Within the CHL view, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors NEUTRINO GHOST-FIELD MAPPING (hatPhi\textbackslash{}\_nu) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0755}}:\mathcal{X}_{\mathrm{id0755}}\longrightarrow\mathcal{Y}_{\mathrm{id0755}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0755}})=\mathcal{O}_{\mathrm{id0755}}
\]
\[
\mathcal{O}_{\mathrm{id0755}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0755] NEUTRINO GHOST-FIELD MAPPING (hatPhi\_nu)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
NEUTRINO GHOST-FIELD MAPPING (hatPhi sub nu) is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} hat Phi nu = int sub L psi to the power dagger nu gamma to the power mu (1-gamma sub 5) partial sub mu psi sub nu dV otimes N sub glob. \textbf{Contextual meaning:} The entry reads NEUTRINO GHOST-FIELD MAPPING (hatPhi sub nu) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, NEUTRINO GHOST-FIELD MAPPING (hatPhi sub nu) is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: frac 547 512 approximately 1.068; Deltaphi(ratio 547 512 ) = pi(ratio 35 512 ) approximately 12.3 to the power compose; and v sub phase approximately ratio c chi approximately 0.84c. Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Weak-Interaction Topological Bleed}: The extremely subtle mathematical term accounting for the almost imperceptible amount of energy carried away by practically massless, invisible particles.
\item \textbf{Massless Particle Background Interference}: The process of isolating the faint, background static in the geometry caused by the universe's constant shower of neutrinos.
\item \textbf{Deep-Penetration Energy Loss}: The operator calculating the tiny fraction of the system's total information that completely escapes containment by simply passing through solid matter.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0755]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0755].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0755] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont NEUTRINO GHOST-FIELD MAPPING (hatPhi\_nu)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} NEUTRINO GHOST-FIELD MAPPING (hatPhi\textbackslash{}\_nu) is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``NEUTRINO GHOST-FIELD MAPPING (hatPhi\textbackslash{}\_nu) is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0755].
\par\endgroup
\vfill
\endgroup
\endgroup
