\section*{ID9339: Definition of ¤𝜃}
\paragraph{Metadata.}
PiID: 8321513755600 | RTEID: RTE:P36265.4110:T3.2056 | UUID: ce0eb325-5857-5bc6-9bb6-b6ad5a7f04da

\paragraph{Canonical Statement.}
cate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0120], [ID 0142] Node registry\_id\_0143 Support Titles Resonant Ratio; Tidal Torque Law; Torque-Driven Spin Evolution Test Handle If the stated tidal torque cannot create stable rational locking points in the spin dynamics, the proposition fails. Canonical Equation Links \$Ωspin Ωorb\$ = 3 2 \$𝜏tidal∝−𝛾\$ sin ( 2𝜃−3𝑀 ) \$¤𝜃=Ωspin+𝜏tidal\$ [ID 0144] Improved Model Parameter Sweep TZPID ID0144 UUID 475cc172-bfc4-5758-9807-1046a8a18db8 Type Computational Sweep Protocol Scale partial synchronization regime exploration LOC Classification Working routing: QA276 computational parameter studies; QA371 nonlinear oscillators arXiv Classification Primary: nlin.AO Cross-list: physics.data-an, astro-ph.EP Canonical Statement To understand comp

\paragraph{Canonical Equation.}
\[
¤𝜃=Ωspin+𝜏tidal
\]

\paragraph{Dictionary.}
Definition of ¤𝜃 — ¤𝜃=Ωspin+𝜏tidal

\paragraph{Encyclopedia.}
Definition of ¤𝜃 is an algebraic definition, written ¤𝜃=Ωspin+𝜏tidal. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from s, p, n, a, l, defining ¤𝜃. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
