\tzpanchor{0644}
\tzpentryheader{0644}{MEASUREMENT PHASE INTEGRATION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{4cf61e32-fa75-5ab1-830a-ba23b76b0f63}}\\
\textbf{PiID} & \tzpcode{7178721468440} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{651}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2473.6125 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.0758 rad}\\
\textbf{TZPID} & \tzpcode{ID0644} & \textbf{Node Dependencies}\quad \tzpidref{0643}\\
\textbf{Registry} & \tzpcode{registry\_id\_0644} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Aggregate Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records measurement phase integration through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\mu = kMR^2\Omega.
\]
\[
I \sim MR^2.
\]
\[
L \sim I\Omega \sim MR^2\Omega.
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mu$: source equation symbol.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $I$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0644 generated source Wolfram model *)
ClearAll[K0644, Cr0644, T, R, A, W, I, N];
eq0644$1 = HoldForm[mu == kMR^2*Omega];
eq0644$2 = HoldForm[SimilarTo[I, MR^2]];
eq0644$3 = HoldForm[SimilarTo[L, SimilarTo[IOmega, MR^2*Omega]]];

K0644 = HoldForm[{eq0644$1, eq0644$2, eq0644$3}];

N = "normalized TRAWIN closure object for MEASUREMENT PHASE INTEGRATION";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Aggregate Relation admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Aggregate Relation local source condition";

Cr0644[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0644 = Cr0644[K0644];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Aggregate Relation local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Aggregate Relation admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for MEASUREMENT PHASE INTEGRATION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0644] MEASUREMENT PHASE INTEGRATION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mu
=
kMR^2\Omega .
\end{equation}

\paragraph{Primary Derivation.}
For a rotating body, the inertial rotational scale is controlled by the moment of inertia:

\begin{equation}
I
\sim
MR^2 .
\end{equation}

Angular momentum scales as:

\begin{equation}
L
\sim
I\Omega
\sim
MR^2\Omega .
\end{equation}

If the magnetic moment $\mu$ is proportional to this rotational scale, introduce proportionality constant $k$:

\begin{equation}
\boxed{
\mu
=
kMR^2\Omega .
}
\end{equation}

\paragraph{Interpretation.}
The magnetic moment is modeled as proportional to mass, squared radius, and angular velocity, with $k$ encoding the Trawinistic coupling scale.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors MEASUREMENT PHASE INTEGRATION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Aggregate Relation}\par
\[
\mu = kMR^2\Omega.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
I \sim MR^2.
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
L \sim I\Omega \sim MR^2\Omega.
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0644] MEASUREMENT PHASE INTEGRATION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
MEASUREMENT PHASE INTEGRATION is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} M = sum sub i |irangle langle i| otimes |irangle sub cl implies text Holevo Readout. \textbf{Contextual meaning:} The entry reads MEASUREMENT PHASE INTEGRATION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Aggregate Relation; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The magnetic moment is modeled as proportional to mass, squared radius, and angular velocity, with k encoding the Trawinistic coupling scale.

\tzpsection{Equation Grounding}
Equation anchors: M = sum sub i lvert i i| otimes lvert i sub cl implies Holevo Readout; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Continuous-Observation Data Smoothing}: The clever trick of never taking your eyes off the rolling quantum wave, using the constant stream of blurry data to build a perfectly sharp picture of what is happening.
\item \textbf{Probe-Induced Decoherence Compensation}: The incredibly difficult math required to constantly subtract the damage and interference your own sensors are causing to the fragile experiment you are trying to watch.
\item \textbf{Real-Time State-Vector Updating}: The rapid-fire, microsecond-perfect calculations constantly adjusting the computers' best guess at what the quantum ghosts are doing, based on the newest, tiniest piece of evidence.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0644]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0644_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0644] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont MEASUREMENT PHASE INTEGRATION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records measurement phase integration through the Septenary derivation layer,
using the displayed relations as operational anchors for th...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``MEASUREMENT PHASE INTEGRATION is valid as a synchronization criterion under the coupling
conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0644_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
