\tzpanchor{0607}
\tzpentryheader{0607}{PROTON-GATED MANIFOLD OPERATOR (hatH\_p-gate)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{eb0b3c9f-214d-500f-a327-6d7be8754eb4}}\\
\textbf{PiID} & \tzpcode{2714526356082} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{614}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2333.8165 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.8454 rad}\\
\textbf{TZPID} & \tzpcode{ID0607} & \textbf{Node Dependencies}\quad \tzpidref{0606}\\
\textbf{Registry} & \tzpcode{registry\_id\_0607} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records proton-gated manifold operator (hath\_p-gate) through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\alpha(t)=\frac{\mathrm{d}t'}{\mathrm{d}t}.
\]
\[
\mathrm{d}t' = \alpha(t)\,\mathrm{d}t.
\]
\[
\boxed{ \alpha(t)=\frac{\mathrm{d}t'}{\mathrm{d}t}. }
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $t$: source equation symbol.
    \item $\mathcal{K}_{0607}$: canonical registry object for entry ID 0607.
    \item $\alpha(t)$: source equation symbol.
    \item $a(t)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0607 generated source Wolfram model *)
ClearAll[K0607, Cr0607, T, R, A, W, I, N];
eq0607$1 = HoldForm[alpha[t] == Derivative[1][dt]/dt];
eq0607$2 = HoldForm[Derivative[1][dt] == alpha[t]*dt];
eq0607$3 = HoldForm[alpha[t] == Derivative[1][dt]/dt];

K0607 = HoldForm[{eq0607$1, eq0607$2, eq0607$3}];

N = "normalized TRAWIN closure object for PROTON-GATED MANIFOLD OPERATOR (hatH\_p-gate)";
I = "Topological Closure integration/comparison layer";
W = "Compatibility Law wave or operator carrier";
A = "Geometric Carrier admissible action/amplitude condition";
R = "Compatibility Law rotation/curl preservation layer";
T = "Geometric Carrier local source condition";

Cr0607[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0607 = Cr0607[K0607];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Geometric Carrier local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Compatibility Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Geometric Carrier admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Compatibility Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for PROTON-GATED MANIFOLD OPERATOR (hatH\textbackslash{}\_p-gate).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0607] PROTON-GATED MANIFOLD OPERATOR (hatH\_p-gate)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\alpha(t)=\frac{\mathrm{d}t'}{\mathrm{d}t}.
\end{equation}

\paragraph{Primary Derivation.}
Let $t$ denote ordinary parameter time and let $t'$ denote displaced or transformed time measured through the Trawinistic structure.

If $t'$ depends smoothly on $t$, then the infinitesimal rate of temporal displacement is given by the derivative:

\begin{equation}
\mathrm{d}t' = \alpha(t)\,\mathrm{d}t .
\end{equation}

Solving for $\alpha(t)$ gives:

\begin{equation}
\boxed{
\alpha(t)=\frac{\mathrm{d}t'}{\mathrm{d}t}.
}
\end{equation}

\paragraph{Interpretation.}
The temporal displacement factor measures how transformed time stretches, compresses, or shifts relative to ordinary time.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors PROTON-GATED MANIFOLD OPERATOR (hatH\textbackslash{}\_p-gate) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Geometric Carrier}\par
\[
\alpha(t)=\frac{\mathrm{d}t'}{\mathrm{d}t}.
\]
\noindent This fixes the effective geometry or carrier space named by the entry title.\par
\noindent\textbf{2. Compatibility Law}\par
\[
\mathrm{d}t' = \alpha(t)\,\mathrm{d}t.
\]
\noindent This makes the geometry admissible by imposing its internal compatibility law.\par
\noindent\textbf{3. Topological Closure}\par
\[
\boxed{ \alpha(t)=\frac{\mathrm{d}t'}{\mathrm{d}t}. }
\]
\noindent This closes the entry by tying the local structure to a global topological invariant.\par

\clearpage
\noindent\textbf{[ID 0607] PROTON-GATED MANIFOLD OPERATOR (hatH\_p-gate)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
PROTON-GATED MANIFOLD OPERATOR (hatH sub p-gate) is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} hat H p-gate = -frac hbar to the power 2 2m sub p nabla to the power 2 + V pH (L) otimes sum sub i delta(r-r sub i)hat a to the power dagger sub i hat a sub i. \textbf{Contextual meaning:} The entry reads PROTON-GATED MANIFOLD OPERATOR (hatH sub p-gate) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Geometric Carrier; Compatibility Law; Topological Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The temporal displacement factor measures how transformed time stretches, compresses, or shifts relative to ordinary time.

\tzpsection{Equation Grounding}
Equation anchors: P(x,t) := W[Q] = abla to the power 2 Q - ratio 1 c to the power 2 partial sub t to the power 2 Q; mathbf F (x,t) := A(x,t) ,P(x,t); and M=S to the power 2 times S to the power 1 subsetmathbb R to the power 4. Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Ionic Charge-Field Rerouting}: The mechanism where the massive positive charge of a single proton is used as a physical switch to instantly divert the flow of surrounding energy waves.
\item \textbf{Subatomic Mass-Barrier Erection}: The deployment of heavy nuclear particles to create a sudden, localized gravity-well that temporarily blocks the passage of lighter, faster signals.
\item \textbf{Coulomb-Forced Trajectory Bending}: The use of extreme, localized electric fields to physically warp the straight-line path of a passing quantum state.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0607]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0607_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0607] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont PROTON-GATED MANIFOLD OPERATOR (hatH\_p-gate)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records proton-gated manifold operator (hath\textbackslash{}\_p-gate) through the Septenary
derivation layer, using the displayed relations as operationa...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``PROTON-GATED MANIFOLD OPERATOR (\textbackslash{}hat\{H\_\{p-gate) is valid as a tensorial/geometric
statement when the stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0607_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
