\tzpanchor{0587}
\tzpentryheader{0587}{CARNOT EFFICIENCY LIMITS (eta\_total)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9eb3aa66-9479-5974-ba29-112fe8ba1d8e}}\\
\textbf{PiID} & \tzpcode{8467669405132} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{594}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2256.1520 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.7174 rad}\\
\textbf{TZPID} & \tzpcode{ID0587} & \textbf{Node Dependencies}\quad \tzpidref{0586}\\
\textbf{Registry} & \tzpcode{registry\_id\_0587} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
eta\_\{total\} = eta\_\{coupling\} x eta\_\{extract\} x eta\_\{rect\} x eta\_\{thermal\}

\tzpsection{Canonical Equation}
\[
eta_{total} = \eta_{coupling} \times \eta_{extract} \times \eta_{rect} \times \eta_{thermal}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $J$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
    \item $A$: source equation symbol.
    \item $\mathcal{J}_{\mathrm{out}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0587 generated source Wolfram model *)
ClearAll[K0587, Cr0587, T, R, A, W, I, N];
eq0587$1 = HoldForm[etaTotal == etaCoupling*etaExtract*etaRect*etaThermal];
eq0587$2 = HoldForm[mathcal[J]*_*out == TTZP[KTZP]];
eq0587$3 = HoldForm[mathcal[A]*_*adm*JOut == 1];

K0587 = HoldForm[{eq0587$1, eq0587$2, eq0587$3}];

N = "normalized TRAWIN closure object for CARNOT EFFICIENCY LIMITS (eta\_total)";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Canonical Definition admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Canonical Definition local source condition";

Cr0587[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0587 = Cr0587[K0587];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Canonical Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Canonical Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for CARNOT EFFICIENCY LIMITS (eta\textbackslash{}\_total).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0587] CARNOT EFFICIENCY LIMITS (eta\_total)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\dot{\omega}(t)
=
\frac{\tau_{\mathrm{em}}(t)}{I_T}.
\end{equation}

\begin{equation}
\omega(t)
=
\omega(0)
+
\frac{1}{I_T}
\int_0^t
\tau_{\mathrm{em}}(t')
\,\mathrm{d}t' .
\end{equation}

\paragraph{Primary Derivation.}
Let $I_T$ be the Trawinistic moment of inertia.  
Angular momentum is related to angular velocity by:
\begin{equation}
L=I_T\omega .
\end{equation}

Differentiating gives:
\begin{equation}
\dot{L}
=
I_T\dot{\omega},
\end{equation}
assuming $I_T$ is constant over the interval.

Since $\dot{L}=\tau_{\mathrm{em}}$, we obtain:
\begin{equation}
\dot{\omega}(t)
=
\frac{\tau_{\mathrm{em}}(t)}{I_T}.
\end{equation}

Integrating through time gives:
\begin{equation}
\boxed{
\omega(t)
=
\omega(0)
+
\frac{1}{I_T}
\int_0^t
\tau_{\mathrm{em}}(t')
\,\mathrm{d}t' .
}
\end{equation}

\paragraph{Interpretation.}
Rotation is the accumulated response to torque history, scaled by the effective moment of inertia.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors CARNOT EFFICIENCY LIMITS (eta\textbackslash{}\_total) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Canonical Definition}\par
\[
eta_{total} = \eta_{coupling} \times \eta_{extract} \times \eta_{rect} \times \eta_{thermal}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right)=1
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0587] CARNOT EFFICIENCY LIMITS (eta\_total)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
CARNOT EFFICIENCY LIMITS (eta sub total) is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} eta sub total = eta sub coupling x eta sub extract x eta sub rect x eta sub thermal. \textbf{Contextual meaning:} The entry reads CARNOT EFFICIENCY LIMITS (eta sub total) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Rotation is the accumulated response to torque history, scaled by the effective moment of inertia.

\tzpsection{Equation Grounding}
Equation anchors: eta sub total = eta sub coupling times eta sub extract times eta sub rect times eta sub thermal; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Absolute Thermodynamic Ceiling}: The inescapable, fundamental law of physics dictating the absolute maximum amount of heat that can ever be converted into useful work.
\item \textbf{Idealized Heat-Engine Scaling}: The comparison between the messy, real-world performance of the machine and the perfect, frictionless mathematical ideal.
\item \textbf{Temperature-Gradient Power Cap}: The calculation showing that no matter how clever the engineering, the output is forever limited by the difference between the hottest and coldest parts of the reactor.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0587]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0587_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0587] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont CARNOT EFFICIENCY LIMITS (eta\_total)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} eta\textbackslash{}\_\textbackslash{} = eta\textbackslash{}\_\textbackslash{} x eta\textbackslash{}\_\textbackslash{} x eta\textbackslash{}\_\textbackslash{} x eta\textbackslash{}\_\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``CARNOT EFFICIENCY LIMITS (\textbackslash{}eta\_\{total) is valid as a synchronization criterion under
the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0587_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
