\tzpanchor{0141}
\tzpentryheader{0141}{Kuramoto Dominant Coupling Hypothesis}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{3a692337-eb69-5a86-8472-d66934e5c4f5}}\\
\textbf{PiID} & \tzpcode{3594081284811} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{148}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{547.5343 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.9022 rad}\\
\textbf{TZPID} & \tzpcode{ID0141} & \textbf{Node Dependencies}\quad \tzpidref{0140}\\
\textbf{Registry} & \tzpcode{registry\_id\_0141} & \textbf{Scale}\quad cluster-dominant oscillator networks\\
\textbf{LOC Classification} & QA371 nonlinear oscillators & QA276 network statistics\\
\textbf{arXiv Classification} & Primary: nlin.AO \quad Cross-list: astro-ph.EP, physics.data-an & \\
\textbf{Primary Support} & Dominant Share & Global Suppression Rule\\
\textbf{Closure Support} & Cluster Preference & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In networks with strongly heterogeneous couplings, global synchronization is suppressed unless the largest coupling pairs represent a significant fraction of total coupling. Planetary spins illustrate this: the Jupiter--Saturn pair dominates, so cluster dynamics should be analyzed in subsets rather than globally.

\tzpsection{Canonical Equation}
\[
\chi_{\max}=\frac{A_{\max}}{\sum_{i<j}A_{ij}}
\]
\[
\chi_{\max}<\chi_{\mathrm{crit}}
\;\Longrightarrow\;
r_{\mathrm{global}}\ll 1
\]
\[
r_{\mathrm{cluster}}>r_{\mathrm{global}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $A_{\max}$: source equation symbol.
    \item $A_{ij}$: source equation symbol.
    \item $r_{\mathrm{global}}$: source equation symbol.
    \item $r_{\mathrm{cluster}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0141 generated source Wolfram model *)
ClearAll[K0141, Cr0141, T, R, A, W, I, N];
eq0141$1 = HoldForm[chiMax == AMax/SumIjAIj];
eq0141$2 = HoldForm[chiMax < chiCritLongrightarrow*rGloballl1];
eq0141$3 = HoldForm[rCluster > rGlobal];

K0141 = HoldForm[{eq0141$1, eq0141$2, eq0141$3}];

N = "normalized TRAWIN closure object for Kuramoto Dominant Coupling Hypothesis";
I = "Cluster Preference integration/comparison layer";
W = "Global Suppression Rule wave or operator carrier";
A = "Dominant Share admissible action/amplitude condition";
R = "Global Suppression Rule rotation/curl preservation layer";
T = "Dominant Share local source condition";

Cr0141[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0141 = Cr0141[K0141];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Dominant Share local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Global Suppression Rule rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Dominant Share admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Global Suppression Rule wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Cluster Preference integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Kuramoto Dominant Coupling Hypothesis.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0141] Kuramoto Dominant Coupling Hypothesis}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\chi_{\max}=\frac{A_{\max}}{\sum_{i<j}A_{ij}}
\]
\[
\chi_{\max}<\chi_{\mathrm{crit}}
\;\Longrightarrow\;
r_{\mathrm{global}}\ll 1
\]
\[
r_{\mathrm{cluster}}>r_{\mathrm{global}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \chi_{\max}<\chi_{\mathrm{crit}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. From the TRAWIN perspective, the equation functions as the mapping carrier for the entry’s information content. In CHL terms, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Kuramoto Dominant Coupling Hypothesis by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Dominant Share}\par
\[
\chi_{\max}=\frac{A_{\max}}{\sum_{i<j}A_{ij}}
\]
\noindent This quantifies how much of the total coupling budget is concentrated in the strongest pair.\par
\noindent\textbf{2. Global Suppression Rule}\par
\[
\chi_{\max}<\chi_{\mathrm{crit}}
\;\Longrightarrow\;
r_{\mathrm{global}}\ll 1
\]
\noindent This states the hypothesized failure of full synchronization when no dominant share crosses the needed threshold.\par
\noindent\textbf{3. Cluster Preference}\par
\[
r_{\mathrm{cluster}}>r_{\mathrm{global}}
\]
\noindent This closes the progression by saying the observable coherence should migrate into subsets before it appears globally.\par

\clearpage
\noindent\textbf{[ID 0141] Kuramoto Dominant Coupling Hypothesis}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Kuramoto Dominant Coupling Hypothesis is a Structural Constraint. In networks with strongly heterogeneous couplings, global synchronization is suppressed unless the largest coupling pairs represent a significant fraction of total coupling. Planetary spins illustrate this: the Jupiter--Saturn pair dominates, so cluster dynamics should be analyzed in subsets rather than globally.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} In networks with strongly heterogeneous couplings, global synchronization is suppressed unless the largest coupling pairs represent a significant fraction of total coupling. Planetary spins illustrate this: the Jupiter--Saturn pair dominates, so cluster dynamics should be analyzed in subsets rather than globally.
\textbf{Contextual meaning:} The distribution of coupling strengths determines whether synchronization occurs globally or only within dominant subclusters.
\textbf{Derivable consequences:} Predictions of field strengths at different scales; connection to natural transformation; justification for universal toroidal topology.
\textbf{Lemma support:} In networks with strongly heterogeneous couplings, global synchronization is suppressed unless the largest coupling pairs represent a significant fraction of total coupling. Planetary spins illustrate this: the Jupiter--Saturn pair dominates, so cluster dynamics should be analyzed in subsets rather than globally.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Measure dipole interactions over a range of distances and verify the 1/d  law; test topological implications. ID 141: Kuramoto Dominant Coupling Hypothesis

\tzpsection{Equation Grounding}
In networks with strongly heterogeneous couplings, global synchronization is suppressed unless the largest coupling pairs represent a significant fraction of total coupling. Planetary spins illustrate this: the Jupiter--Saturn pair dominates, so cluster dynamics should be analyzed in subsets rather than globally.

\tzpsection{Interpretive Role}
The distribution of coupling strengths determines whether synchronization occurs globally or only within dominant subclusters.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Dominant Share}: The quantification of how much of the total coupling budget is concentrated in the strongest pair.
\item \textbf{Global Suppression Rule}: The hypothesized failure of full synchronization when no dominant share crosses the needed threshold.
\item \textbf{Cluster Preference}: The statement that the observable coherence should migrate into subsets before it appears globally.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0141]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0141_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0141] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Kuramoto Dominant Coupling Hypothesis}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in networks with strongly heterogeneous couplings, global synchronization is suppressed
unless the largest coupling pairs represent a significant f...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Kuramoto Dominant Coupling Hypothesis is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0141_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
