\tzpanchor{0456}
\tzpentryheader{0456}{Recovery Window Reset Logic}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7d4cd757-98a5-5283-86c0-4e7c4abba2b6}}\\
\textbf{PiID} & \tzpcode{3799627495673} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{463}\\
\textbf{RTEID} & \textbf{Manifest row}\quad \tzpcode{not listed} & \textbf{Source}\quad \tzpcode{Coordinate Manifest}\\
\textbf{TZPID} & \tzpcode{ID0456} & \textbf{Node Dependencies}\quad \tzpidref{0455}\\
\textbf{Registry} & \tzpcode{registry\_id\_0456} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 456 defines the restoration phase required for thermodynamic consistency. After extraction, the system must clear accumulated entropy by dissipating the Landauer cost of bit erasure into the thermal bath. This prevents "Entropy Leakage" that could stall the Trawin Zero Point coupling. Thermal Venting: Noble gas buffers carry reset heat to the liquid nitrogen jacket. Address Reset: The DAANSsphere coordinates are re indexed for the next operational cycle.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\gamma_{\text{loss}}(\Omega) = \gamma_0(1 + \alpha \Omega^2 R^2/c^2)
$
\end{adjustbox}
\]

\tzpsection{Canonical Equation Links}
\tzpequationlinks
  {\gamma_{\text{loss}}(\Omega) = \gamma_0(1 + \alpha \Omega^2 R^2/c^2)}
  {\mathcal{J}_{\mathrm{out}} = \cdots}
  {\mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right) = \cdots}

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\gamma$: source equation symbol.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $\gamma_0$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $c$: speed of light or relativistic conversion factor.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0456 generated source Wolfram model *)
ClearAll[K0456, Cr0456, T, R, A, W, I, N];
eq0456$1 = HoldForm[$gamma[Omega] == gamma0[1 + alpha*Omega^2*(R^2/c^2)]*$];

K0456 = HoldForm[{eq0456$1}];

N = "normalized TRAWIN closure object for Recovery Window Reset Logic";
I = "Recovery Window Reset Logic integration/comparison layer";
W = "Recovery Window Reset Logic wave or operator carrier";
A = "Recovery Window Reset Logic admissible action/amplitude condition";
R = "Recovery Window Reset Logic rotation/curl preservation layer";
T = "Recovery Window Reset Logic local source condition";

Cr0456[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0456 = Cr0456[K0456];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Recovery Window Reset Logic local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Recovery Window Reset Logic rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Recovery Window Reset Logic admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Recovery Window Reset Logic wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Recovery Window Reset Logic integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Recovery Window Reset Logic.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0456] Recovery Window Reset Logic}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\begingroup\small
\paragraph{Primary Equation.}
\begin{equation}
E_{\mathrm{Cas}}(L)
=
-\frac{\pi^2}{720L^3}(1+\epsilon).
\end{equation}

\paragraph{Primary Derivation.}
For two ideal parallel boundaries separated by distance $L$, the standard scalar form of Casimir-type energy per unit area scales as:

\begin{equation}
E_{\mathrm{Cas}}^{(0)}(L)
=
-\frac{\pi^2}{720L^3}.
\end{equation}

In the Trawinistic setting, curvature, topology, and TZP boundary corrections are collected into a dimensionless perturbation $\epsilon$.

Thus,

\begin{equation}
E_{\mathrm{Cas}}(L)
=
E_{\mathrm{Cas}}^{(0)}(L)(1+\epsilon).
\end{equation}

Substitution gives:

\begin{equation}
\boxed{
E_{\mathrm{Cas}}(L)
=
-\frac{\pi^2}{720L^3}(1+\epsilon).
}
\end{equation}

\paragraph{Wolfram Form.}
\begin{verbatim}
ECas[L_] := -(Pi^2/(720*L^3))*(1 + epsilon)
\end{verbatim}

\paragraph{Interpretation.}
Casimir-type behavior arises from boundary-altered vacuum modes, with $\epsilon$ collecting TRAWIN corrections.
\endgroup

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Recovery Window Reset Logic by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\gamma_{\text{loss}}(\Omega) = \gamma_0(1 + \alpha \Omega^2 R^2/c^2)
$
\end{adjustbox}
\]

\tzpsection{Canonical Equation Links}
\tzpequationlinks
  {\gamma_{\text{loss}}(\Omega) = \gamma_0(1 + \alpha \Omega^2 R^2/c^2)}
  {\mathcal{J}_{\mathrm{out}} = \cdots}
  {\mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right) = \cdots}
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0456] Recovery Window Reset Logic}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Recovery Window Reset Logic is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 456 defines the restoration phase required for thermodynamic consistency. After extraction, the system must clear accumulated entropy by dissipating the Landauer cost of bit erasure into the thermal bath. This prevents "Entropy Leakage" that could stall the Trawin Zero Point coupling. Thermal Venting: Noble gas buffers carry reset heat to the liquid nitrogen jacket. Address Reset: The DAANSsphere coordinates are re indexed for the next operational cycle.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\gamma_{\text{loss}}(\Omega) = \gamma_0(1 + \alpha \Omega^2 R^2/c^2)
$
\end{adjustbox}
\]

\tzpsection{Canonical Equation Links}
\tzpequationlinks
  {\gamma_{\text{loss}}(\Omega) = \gamma_0(1 + \alpha \Omega^2 R^2/c^2)}
  {\mathcal{J}_{\mathrm{out}} = \cdots}
  {\mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right) = \cdots}

\tzpsection{Technical Interpretation}
ID 456 defines the restoration phase required for thermodynamic consistency. After extraction, the system must clear accumulated entropy by dissipating the Landauer cost of bit erasure into the thermal bath. This prevents "Entropy Leakage" that could stall the Trawin Zero Point coupling. Thermal Venting: Noble gas buffers carry reset heat to the liquid nitrogen jacket. Address Reset: The DAANSsphere coordinates are re indexed for the next operational cycle.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Recovery Window Reset Logic by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Recovery Window Reset Logic; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0456]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0456].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0456] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Recovery Window Reset Logic}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} Recovery Window Reset Logic is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Recovery Window Reset Logic is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0456].
\par\endgroup
\vfill
\endgroup
\endgroup
