\section*{ID9480: Definition of Ωinner −Ωouter, 𝐷𝑒𝑙𝑡𝑎Ω𝑒𝑞0}
\paragraph{Metadata.}
PiID: 1242470141214 | RTEID: RTE:P36812.9453:T4.1077 | UUID: 3831aa75-17e5-5cb6-a4f9-c4230df36940

\paragraph{Canonical Statement.}
ormalized, and linked forward into the surrounding registry pages. \$𝑝𝑎𝑟𝑡𝑖𝑎𝑙𝑟Ω𝑒𝑞0\$ \$𝐷𝑒𝑙𝑡𝑎Ω\$ = \$Ωinner −Ωouter\$ Wolfram Form 𝔚TZP (K0276) \$↦−→ 〈 𝜕Ω/𝜕𝑟, ΩT, ΨT\$ \$〉\$ K0276 := HoldForm(T0276) AdmissibleTZP (K0276) \$⇐⇒\$ 𝔚TZP (K0276) . \$∅\$ Wolfram register: canonical symbol lift Title lift: Differential Rotation Ubiquity Symbol key: \$𝜕Ω/𝜕𝑟:\$ angular shear gradient \$ΩT:\$ Trawinistic boundary curvature \$ΨT:\$ Trawinistic wavefunction TRAWIN Normalization NormalizeTRAWIN( \$𝑝𝑎𝑟𝑡𝑖𝑎𝑙𝑟Ω𝑒𝑞0, 𝐷𝑒𝑙𝑡𝑎Ω\$ = \$Ωinner −Ωouter, 𝐷𝑒𝑙𝑡𝑎Ω𝑒𝑞0 =⇒\$ Ggyro𝑒𝑞0 ) T: Rotation Gradient is localized within the information synchronization arc of the directory. R: Shear Condition preserves the operative relation that differential rotation ubiquity requires. A: Coupling Criterion fixes the admissible closure condi-tion for the entry. W: Differential Rotation Ubiquity is rendered as a reusable operator-level statement. I: The informational content of

\paragraph{Canonical Equation.}
\[
Ωinner −Ωouter, 𝐷𝑒𝑙𝑡𝑎Ω𝑒𝑞0 =⇒
\]

\paragraph{Dictionary.}
Definition of Ωinner −Ωouter, 𝐷𝑒𝑙𝑡𝑎Ω𝑒𝑞0 — Ωinner −Ωouter, 𝐷𝑒𝑙𝑡𝑎Ω𝑒𝑞0 =⇒

\paragraph{Encyclopedia.}
Definition of Ωinner −Ωouter, 𝐷𝑒𝑙𝑡𝑎Ω𝑒𝑞0 is an algebraic definition, written Ωinner −Ωouter, 𝐷𝑒𝑙𝑡𝑎Ω𝑒𝑞0 =⇒. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
