\section*{ID7670: Cymatics, Seed Crystals, and Nebula vs Lab Scales: λ: λ = V/F (2)}
\paragraph{Metadata.}
PiID: 6591228508555 | RTEID: RTE:P29784.3133:T5.0931 | UUID: d2a7b63f-97ed-5245-a347-b8ab4c1f6aec

\paragraph{Canonical Statement.}
4. **About 432 (Hz vs kHz) and “theta state”** - *432 Hz* is a musical tuning often referenced in cymatics communities; it’s audible and produces visually pleasing patterns in liquids. - *432 kHz* is ultrasonic and would produce much smaller spatial patterns (tiny wavelengths) — not usually used in standard cymatics but used in ultrasonic particle trapping / acoustic levitation. - *“Theta”* (brainwave band) is \textasciitilde{}4–8 Hz; if by “theta state” you meant a low-frequency coherent carrier, then modulation/harmonics built on that would produce vastly different spatial scales than a kHz carrier. In the QOV picture you can use any carrier; the scale of structures follows \textbackslash{}(\textbackslash{}lambda = v/f\textbackslash{}).

\paragraph{Canonical Equation.}
\[
\lambda = v/f
\]

\paragraph{Dictionary.}
Cymatics, Seed Crystals, and Nebula vs Lab Scales: λ: λ = V/F (2) — λ = v/f

\paragraph{Encyclopedia.}
Cymatics, Seed Crystals, and Nebula vs Lab Scales: λ: λ = V/F (2) is an algebraic definition, written λ = v/f. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from v, f, defining λ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
