\section*{ID9334: Definition of (𝜌∥𝜎)}
\paragraph{Metadata.}
PiID: 2208883215137 | RTEID: RTE:P36245.9949:T3.1736 | UUID: 9e967572-7043-5e1e-ba4f-700c1bca0cca

\paragraph{Canonical Statement.}
Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0107], [ID 0105] Node registry\_id\_0108 Support Titles Relative-Entropy Definition; Positivity Bound; Functional Insertion Test Handle If admissible synchronization updates can make the relative-entropy term negative, this constraint fails. Canonical Equation Links 𝐷 \$(𝜌∥𝜎)=Tr[𝜌(log\$ 𝜌−log 𝜎) ] 𝐷 \$(𝜌∥𝜎)≥0\$ 𝛿Ssync 𝛿𝜌 \$⊃𝛽\$ 𝐷 \$(𝜌∥𝜎)\$ [ID 0109] Fibonacci Sequence TZPID ID0109 UUID 3fef2fa4-a4cb-5862-99e5-50832d601839 Type Recurrence Law Scale discrete growth sequence LOC Classification Working routing: QA273 recurrence relations; QA174 combinatorial sequences arXiv Classification Primary: math.CO Cross-list: math-ph, nlin.CD Canonical Statement The Fibonacci sequence is introdu

\paragraph{Canonical Equation.}
\[
(𝜌∥𝜎)=Tr[𝜌(log
\]

\paragraph{Dictionary.}
Definition of (𝜌∥𝜎) — (𝜌∥𝜎)=Tr[𝜌(log

\paragraph{Encyclopedia.}
Definition of (𝜌∥𝜎) is an algebraic definition, written (𝜌∥𝜎)=Tr[𝜌(log. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from T, r, l, o, g, defining (𝜌∥𝜎). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
