\section*{ID9435: Definition of 0.84𝑐, 𝑓0}
\paragraph{Metadata.}
PiID: 8468788614445 | RTEID: RTE:P36638.2003:T3.8198 | UUID: 5ca79bb2-e8b1-51c8-b092-8f06e95318f7

\paragraph{Canonical Statement.}
ed, normalized, and linked forward into the surrounding registry pages. 𝑣phase \$≈\$ 𝑐/𝜒 \$≈\$ 0.84𝑐 𝑓0 = 17.2 kHz Wolfram Form 𝔚TZP (K0427) \$↦−→ 〈 ΩT, ΨT,\$ 𝜌vac \$〉\$ K0427 := HoldForm(T0427) AdmissibleTZP (K0427) \$⇐⇒\$ 𝔚TZP (K0427) . \$∅\$ Wolfram register: canonical symbol lift Title lift: 17.2 kHz ACOUSTIC CARRIER SYNCHRO-NIZATION Symbol key: \$ΩT:\$ Trawinistic boundary curvature \$ΨT:\$ Trawinistic wavefunction 𝜌vac: vacuum energy density TRAWIN Normalization NormalizeTRAWIN( 𝑣phase \$≈\$ 𝑐/𝜒 \$≈\$ 0.84𝑐, 𝑓0 = 17.2 kHz, 𝑓 = 443 Hz \$≈\$ 432 Hz ( 1 + 𝜙−2 )) T: Scaling Law is localized within the manifold and metric dynamics arc of the directory. R: Scaling Law preserves the operative relation that 17.2 khz acoustic carrier synchronization requires. A: Scaling Law fixes the admissible closure condition for the entry. W: 17.2 kHz ACOUSTIC CARRIER SYNCHRONIZA-TION is rendered as a reusable operator-level statement. I: The informat

\paragraph{Canonical Equation.}
\[
0.84𝑐, 𝑓0 = 17.2 kHz, 𝑓 = 443 Hz
\]

\paragraph{Dictionary.}
Definition of 0.84𝑐, 𝑓0 — 0.84𝑐, 𝑓0 = 17.2 kHz, 𝑓 = 443 Hz

\paragraph{Encyclopedia.}
Definition of 0.84𝑐, 𝑓0 is an algebraic definition, written 0.84𝑐, 𝑓0 = 17.2 kHz, 𝑓 = 443 Hz. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from k, H, z, defining 0.84𝑐, 𝑓0. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
