\tzpanchor{0105}
\tzpentryheader{0105}{Master Synchronization Functional}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{97d9382b-6936-50c8-9710-0702a0aa4e39}}\\
\textbf{PiID} & \tzpcode{0865132823066} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{112}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{407.7383 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.6718 rad}\\
\textbf{TZPID} & \tzpcode{ID0105} & \textbf{Node Dependencies}\quad \tzpidref{0104}\\
\textbf{Registry} & \tzpcode{registry\_id\_0105} & \textbf{Scale}\quad global synchronization law\\
\textbf{LOC Classification} & QA315 variational methods & QC174.45 information and synchronization\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: quant-ph, hep-th & \\
\textbf{Primary Support} & Phase-Gradient Cost & Relative-Entropy Term\\
\textbf{Closure Support} & Stationarity Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This variational principle determines how helical and toroidal modes align at the TZP by maximizing coherence, topological entanglement and relative entropy under an energy constraint.

\tzpsection{Canonical Equation}
\[
\mathcal{S}_{\mathrm{sync}}[\rho,\theta,\Phi]
=
\int_{\mathcal{M}} \left(
\alpha \lvert \nabla \theta \rvert^2 + \beta D(\rho\Vert\sigma) + \gamma \lvert \Phi_{\mathrm{bulk}}-\Phi_{\mathrm{bdy}}\rvert^2
\right)\, d\mu
\]
\[
\delta \mathcal{S}_{\mathrm{sync}} = 0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{S}_{\mathrm{sync}}$: source equation symbol.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\theta$: phase angle or local angular coordinate.
    \item $\Phi$: flux, phase, or topological map term in the source equation.
    \item $\mathcal{M}$: source equation symbol.
    \item $D$: source equation symbol.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $\gamma$: source equation symbol.
    \item $\Phi_{\mathrm{bulk}}$: flux, phase, or topological map term in the source equation.
    \item $\Phi_{\mathrm{bdy}}$: flux, phase, or topological map term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0105 generated source Wolfram model *)
ClearAll[K0105, Cr0105, T, R, A, W, I, N];
eq0105$1 = HoldForm[SSync[rho, theta, Phi] == IntegralM[alpha*Abs[Grad*theta]^2 + beta*D[rhoVertsigma] + gamma*Abs[PhiBulk - PhiBdy]^2]*dmu];
eq0105$2 = HoldForm[DiracDelta*SSync == 0];
eq0105$3 = HoldForm[IntegralM*alpha*Abs[Grad*theta]^2*dmu];
eq0105$4 = HoldForm[IntegralM*beta*D[rhoVertsigma]*dmu];

K0105 = HoldForm[{eq0105$1, eq0105$2, eq0105$3, eq0105$4}];

N = "normalized TRAWIN closure object for Master Synchronization Functional";
I = "Stationarity Condition integration/comparison layer";
W = "Relative-Entropy Term wave or operator carrier";
A = "Phase-Gradient Cost admissible action/amplitude condition";
R = "Relative-Entropy Term rotation/curl preservation layer";
T = "Phase-Gradient Cost local source condition";

Cr0105[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0105 = Cr0105[K0105];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Phase-Gradient Cost local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Relative-Entropy Term rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Phase-Gradient Cost admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Relative-Entropy Term wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Stationarity Condition integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Master Synchronization Functional.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0105] Master Synchronization Functional}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{S}_{\mathrm{sync}}[\rho,\theta,\Phi]
=
\int_{\mathcal{M}} \left(
\alpha \lvert \nabla \theta \rvert^2 + \beta D(\rho\Vert\sigma) + \gamma \lvert \Phi_{\mathrm{bulk}}-\Phi_{\mathrm{bdy}}\rvert^2
\right)\, d\mu
\]
\[
\delta \mathcal{S}_{\mathrm{sync}} = 0
\]

\paragraph{Primary Derivation.}
The expression \( \mathcal{S}_{\mathrm{sync}}[\rho,\theta,\Phi] \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. Within the TRAWIN framework, the equation functions as the integral carrier for the entry’s information content. In CHL terms, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Master Synchronization Functional by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Phase-Gradient Cost}\par
\[
\int_{\mathcal{M}} \alpha \lvert \nabla \theta \rvert^2\, d\mu
\]
\noindent This introduces the energetic price of losing coherent phase alignment across the bridge.\par
\noindent\textbf{2. Relative-Entropy Term}\par
\[
\int_{\mathcal{M}} \beta D(\rho\Vert\sigma)\, d\mu
\]
\noindent This adds the informational penalty that keeps synchronized states close to the target distribution.\par
\noindent\textbf{3. Stationarity Condition}\par
\[
\delta \mathcal{S}_{\mathrm{sync}} = 0
\]
\noindent This closes the progression by defining synchronization as a variational extremum rather than an arbitrary heuristic balance.\par

\clearpage
\noindent\textbf{[ID 0105] Master Synchronization Functional}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Master Synchronization Functional is a canonical-registry. The holographic projection is defined as an association of three components: (1) Bulk--boundary correspondence governed by the Ryu--Takayanagi relation S\textbackslash{}\_A = min\{[\}Area(\$\textbackslash{}gamma\$\textbackslash{}\_A)/(4\textbackslash{},G\textbackslash{}\_N)\{]\}; (2) Quantum error correction, where logical information encoded in bulk states is protected by an encoding map U\textbackslash{}\_encoding: \textbackslash{}textbar logical\$\textbackslash{}rangle\$\textbackslash{}rightarrow\$\textbackslash{}textbar physical\$\textbackslash{}rangle\$; and (3) Wedge reconstruction, expressed as O\textbackslash{}\_bulk(x) = \$\textbackslash{}int\$ M\textbackslash{}\_K(x,y) O\textbackslash{}\_boundary(y) dy. Formal Fields Node: registry\_id\_0104 Proof Matches (0) No proof matches currently indexed. ...

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The holographic projection is defined as an association of three components: (1) Bulk--boundary correspondence governed by the Ryu--Takayanagi relation S\textbackslash{}\_A = min\{[\}Area(\$\textbackslash{}gamma\$\textbackslash{}\_A)/(4\textbackslash{},G\textbackslash{}\_N)\{]\}; (2) Quantum error correction, where logical information encoded in bulk states is protected by an encoding map U\textbackslash{}\_encoding: \textbackslash{}textbar logical\$\textbackslash{}rangle\$\textbackslash{}rightarrow\$\textbackslash{}textbar physical\$\textbackslash{}rangle\$; and (3) Wedge reconstruction, expressed as O\textbackslash{}\_bulk(x) = \$\textbackslash{}int\$ M\textbackslash{}\_K(x,y) O\textbackslash{}\_boundary(y) dy. Formal Fields Node: registry\_id\_0104 Proof Matches (0) No proof matches currently indexed. 16.107 [ID 0105] Master Synchronization Functional Identity TZPID: [ID 0105] Registry ID : registry\_id\_0105 UUID: 97d9382b-6936-50c8-9710-0702a0aa4e39 Equation Source Define the functional Lemma Lemma (Master Synchronization Functional).
\textbf{Contextual meaning:} The holographic projection is defined as an association of three components: (1) Bulk--boundary correspondence governed by the Ryu--Takayanagi relation S\textbackslash{}\_A = min\{[\}Area(\$\textbackslash{}gamma\$\textbackslash{}\_A)/(4\textbackslash{},G\textbackslash{}\_N)\{]\}; (2) Quantum error correction, where logical information encoded in bulk states is protected by an encoding map U\textbackslash{}\_encoding: \textbackslash{}textbar logical\$\textbackslash{}rangle\$\textbackslash{}rightarrow\$\textbackslash{}textbar physical\$\textbackslash{}rangle\$; and (3) Wedge reconstruction, expressed as O\textbackslash{}\_bulk(x) = \$\textbackslash{}int\$ M\textbackslash{}\_K(x,y) O\textbackslash{}\_boundary(y) dy. Formal Fields Node: registry\_id\_0104 Proof Matches (0) No proof matches currently indexed. 16.107 [ID 0105] Master Synchronization Functional Identity TZPID: [ID 0105] Registry ID : registry\_id\_0105 UUID: 97d9382b-6936-50c8-9710-0702a0aa4e39 Equation Source Define the functional Lemma Lemma (Master Synchronization Functional).
\textbf{Derivable consequences:} Source evidence records the entry as a reusable object whose consequences should be read from the matched formal statement and local proof route.
\textbf{Lemma support:} The holographic projection is defined as an association of three components: (1) Bulk--boundary correspondence governed by the Ryu--Takayanagi relation S\textbackslash{}\_A = min\{[\}Area(\$\textbackslash{}gamma\$\textbackslash{}\_A)/(4\textbackslash{},G\textbackslash{}\_N)\{]\}; (2) Quantum error correction, where logical information encoded in bulk states is protected by an encoding map U\textbackslash{}\_encoding: \textbackslash{}textbar logical\$\textbackslash{}rangle\$\textbackslash{}rightarrow\$\textbackslash{}textbar physical\$\textbackslash{}rangle\$; and (3) Wedge reconstruction, expressed as O\textbackslash{}\_bulk(x) = \$\textbackslash{}int\$ M\textbackslash{}\_K(x,y) O\textbackslash{}\_boundary(y) dy. Formal Fields Node: registry\_id\_0104 Proof Matches (0) No proof matches currently indexed. 16.107 [ID 0105] Master Synchronization Functional Identity TZPID: [ID 0105] Registry ID : registry\_id\_0105 UUID: 97d9382b-6936-50c8-9710-0702a0aa4e39 Equation Source Define the functional Lemma Lemma (Master Synchronization Functional).\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The holographic projection is defined as an association of three components: (1) Bulk--boundary correspondence governed by the Ryu--Takayanagi relation S\textbackslash{}\_A = min\{[\}Area(\$\textbackslash{}gamma\$\textbackslash{}\_A)/(4\textbackslash{},G\textbackslash{}\_N)\{]\}; (2) Quantum error correction, where logical information encoded in bulk states is protected by an encoding map U\textbackslash{}\_encoding: \textbackslash{}textbar logical\$\textbackslash{}rangle\$\textbackslash{}rightarrow\$\textbackslash{}textbar physical\$\textbackslash{}rangle\$; and (3) Wedge reconstruction, expressed as O\textbackslash{}\_bulk(x) = \$\textbackslash{}int\$ M\textbackslash{}\_K(x,y) O\textbackslash{}\_boundary(y) dy. Formal Fields Node: registry\_id\_0104 Proof Matches (0) No proof matches currently indexed. 16.107 [ID 0105] Master Synchronization Functional Identity TZPID: [ID 0105] Registry ID : registry\_id\_0105 UUID: 97d9382b-6936-50c8-9710-0702a0aa4e39 Equation Source Define the functional Lemma Lemma (Master Synchronization Functional).

\tzpsection{Equation Grounding}
The holographic projection is defined as an association of three components: (1) Bulk--boundary correspondence governed by the Ryu--Takayanagi relation S\textbackslash{}\_A = min\{[\}Area(\$\textbackslash{}gamma\$\textbackslash{}\_A)/(4\textbackslash{},G\textbackslash{}\_N)\{]\}; (2) Quantum error correction, where logical information encoded in bulk states is protected by an encoding map U\textbackslash{}\_encoding: \textbackslash{}textbar logical\$\textbackslash{}rangle\$\textbackslash{}rightarrow\$\textbackslash{}textbar physical\$\textbackslash{}rangle\$; and (3) Wedge reconstruction, expressed as O\textbackslash{}\_bulk(x) = \$\textbackslash{}int\$ M\textbackslash{}\_K(x,y) O\textbackslash{}\_boundary(y) dy. Formal Fields Node: registry\_id\_0104 Proof Matches (0) No proof matches currently indexed. 16.107 [ID 0105] Master Synchronization Functional Identity TZPID: [ID 0105] Registry ID : registry\_id\_0105 UUID: 97d9382b-6936-50c8-9710-0702a0aa4e39 Equation Source Define the functional Lemma Lemma (Master Synchronization Functional).

\tzpsection{Interpretive Role}
The holographic projection is defined as an association of three components: (1) Bulk--boundary correspondence governed by the Ryu--Takayanagi relation S\textbackslash{}\_A = min\{[\}Area(\$\textbackslash{}gamma\$\textbackslash{}\_A)/(4\textbackslash{},G\textbackslash{}\_N)\{]\}; (2) Quantum error correction, where logical information encoded in bulk states is protected by an encoding map U\textbackslash{}\_encoding: \textbackslash{}textbar logical\$\textbackslash{}rangle\$\textbackslash{}rightarrow\$\textbackslash{}textbar physical\$\textbackslash{}rangle\$; and (3) Wedge reconstruction, expressed as O\textbackslash{}\_bulk(x) = \$\textbackslash{}int\$ M\textbackslash{}\_K(x,y) O\textbackslash{}\_boundary(y) dy. Formal Fields Node: registry\_id\_0104 Proof Matches (0) No proof matches currently indexed. 16.107 [ID 0105] Master Synchronization Functional Identity TZPID: [ID 0105] Registry ID : registry\_id\_0105 UUID: 97d9382b-6936-50c8-9710-0702a0aa4e39 Equation Source Define the functional Lemma Lemma (Master Synchronization Functional).
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Phase-Gradient Cost}: The energetic price of losing coherent phase alignment across the bridge.
\item \textbf{Relative-Entropy Term}: The informational penalty that keeps synchronized states close to the target distribution.
\item \textbf{Stationarity Condition}: The definition of synchronization as a variational extremum rather than an arbitrary heuristic balance.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0105]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0105_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0105] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Master Synchronization Functional}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this variational principle determines how helical and toroidal modes align at the TZP by
maximizing coherence, topological entanglement and relativ...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Master Synchronization Functional is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0105_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
