\tzpanchor{0664}
\tzpentryheader{0664}{Null Space Projection}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{340a5b98-ec3f-5569-98f0-4dfa7e9323ea}}\\
\textbf{PiID} & \tzpcode{5343014654958} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{671}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2551.2769 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.2037 rad}\\
\textbf{TZPID} & \tzpcode{ID0664} & \textbf{Node Dependencies}\quad \tzpidref{0663}\\
\textbf{Registry} & \tzpcode{registry\_id\_0664} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records null space projection through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\rho \rightarrow \frac{P \rho P}{\mathrm{Tr}(P\rho)}.
\]
\[
\rho' = \frac{P \rho P}{\mathrm{Tr}(P\rho)}.
\]
\[
\mathcal{A}_{\mathrm{TZP}}(\mathrm{id}_{0664})=\mathcal{A}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\rho$: density or measure term used by the entry equation.
    \item $P$: source equation symbol.
    \item $\mathcal{A}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{A}_{\mathrm{adm}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0664 generated source Wolfram model *)
ClearAll[K0664, Cr0664, T, R, A, W, I, N];
eq0664$1 = HoldForm[rho*arrow[(P*rho*P)/Tr[Prho]]];
eq0664$2 = HoldForm[Derivative[1][rho] == (P*rho*P)/Tr[Prho]];
eq0664$3 = HoldForm[ATZP[id0664] == AAdm];

K0664 = HoldForm[{eq0664$1, eq0664$2, eq0664$3}];

N = "normalized TRAWIN closure object for Null Space Projection";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0664[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0664 = Cr0664[K0664];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Null Space Projection.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0664] Null Space Projection}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\rho \rightarrow \frac{P \rho P}{\mathrm{Tr}(P\rho)}.
\end{equation}

\paragraph{Primary Derivation.}
Measurement with projector $P$ collapses the state.

Post-measurement state is:
\begin{equation}
\rho' = \frac{P \rho P}{\mathrm{Tr}(P\rho)}.
\end{equation}

\paragraph{Interpretation.}
Projection enforces classical outcome selection.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Null Space Projection by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
\rho \rightarrow \frac{P \rho P}{\mathrm{Tr}(P\rho)}.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\rho' = \frac{P \rho P}{\mathrm{Tr}(P\rho)}.
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\mathcal{A}_{\mathrm{TZP}}(\mathrm{id}_{0664})=\mathcal{A}_{\mathrm{adm}}
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0664] Null Space Projection}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Null Space Projection is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Rightarrow. \textbf{Contextual meaning:} The entry reads Null Space Projection as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Projection enforces classical outcome selection.

\tzpsection{Equation Grounding}
Equation anchors: cos\textasciitilde{}theta to the power prime =hat r dothat n (t); u(x,t)=sum sub l,m,n q sub lmn (t)U sub lmn (x); and Rotated Polar Angle The polar angle relative to the DAANS axis is cos\textasciitilde{}theta to the power prime =hat r dothat n (t). Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Gauge-Redundancy Mathematical Pruning}: The highly technical process of combing through the physics equations and deleting all the 'fake' forces and 'imaginary' spins that look important but don't actually physically exist in the real room.
\item \textbf{Orthogonal-State Blindness Enforcement}: The tuning of the sensors so they become completely, literally blind to certain types of radiation, focusing all their sensitivity purely on the specific type of energy we care about.
\item \textbf{Unobservable-Dimension Flattening}: The trick of pretending the complex, 7-dimensional string-theory math is just a flat piece of 3D paper, because the extra four dimensions are so incredibly small they don't actually change the final answer.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0664]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0664_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0664] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Null Space Projection}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records null space projection through the Septenary derivation layer, using
the displayed relations as operational anchors for the canoni...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Null Space Projection is well formed when the total space, base space, structure group,
and projection map are compatible.''\\
\textbf{Proof:} The source statement supplies a bundle-style construction. The CHL reading treats the
base as the proposition carrier, the fiber or structure group as the typed parameter,
and the projection as the categorical morphism that preserves local-to-global structure.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- principal-bundle structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0664_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
