\tzpanchor{0310}
\tzpentryheader{0310}{Recursive Toroidal Fiber Bundle}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{d2ef418f-ef35-5ff4-8441-1d7381bddb50}}\\
\textbf{PiID} & \tzpcode{0631558817488} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{317}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1203.7988 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9835 rad}\\
\textbf{TZPID} & \tzpcode{ID0310} & \textbf{Node Dependencies}\quad \tzpidref{0309}\\
\textbf{Registry} & \tzpcode{registry\_id\_0310} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Bundle Projection & Toroidal Fiber\\
\textbf{Closure Support} & Self-Similar Fiber Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The DAANSphere is interpreted as the base space $S^2$ of a fiber bundle

\tzpsection{Canonical Equation}
\[ T \longrightarrow E \longrightarrow S^2, \] where the fiber over each point is a projection of the same torus \[ T = S^1 \times S^1. \] Formally, the total space $E$ encodes the addressable states so that the local toroidal fibers are mutually isomorphic, $T_i \cong T_j \cong T$ for all sampled addresses.

\[
T=\partial_t
\]
\[
R=\mathrm{Id}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $T$: source equation symbol.
    \item $E$: source equation symbol.
    \item $S^2$: two-sphere target domain.
    \item $S$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0310 generated source Wolfram model *)
ClearAll[K0310, Cr0310, T, R, A, W, I, N];
eq0310$1 = HoldForm[T -> E -> S^2];
eq0310$2 = HoldForm[T == S^1*S^1];
eq0310$3 = HoldForm[T == PartialT];
eq0310$4 = HoldForm[R == Id];
eq0310$5 = HoldForm[A == Id];

K0310 = HoldForm[{eq0310$1, eq0310$2, eq0310$3, eq0310$4, eq0310$5}];

N = "normalized TRAWIN closure object for Recursive Toroidal Fiber Bundle";
I = "Self-Similar Fiber Law integration/comparison layer";
W = "Toroidal Fiber wave or operator carrier";
A = "Bundle Projection admissible action/amplitude condition";
R = "Toroidal Fiber rotation/curl preservation layer";
T = "Bundle Projection local source condition";

Cr0310[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0310 = Cr0310[K0310];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Bundle Projection local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Toroidal Fiber rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Bundle Projection admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Toroidal Fiber wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Self-Similar Fiber Law integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Recursive Toroidal Fiber Bundle.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0310] Recursive Toroidal Fiber Bundle}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\sigma_{\mathrm{SD}}^{2}
=
\lim_{\Delta t\to 0}
\frac{1}{\Delta t}
\left\langle
(\Delta x)^2
\right\rangle .
\end{equation}

\paragraph{Primary Derivation.}
Let $\Delta x$ be the displacement of a test particle over a small time interval $\Delta t$ near the TZP.  
The mean-square displacement is:

\begin{equation}
\left\langle(\Delta x)^2\right\rangle .
\end{equation}

A diffusion-like drift magnitude is obtained by measuring the rate at which this mean-square displacement accumulates per unit time:

\begin{equation}
\frac{1}{\Delta t}
\left\langle(\Delta x)^2\right\rangle .
\end{equation}

Taking the infinitesimal-time limit gives the stochastic drift magnitude:

\begin{equation}
\boxed{
\sigma_{\mathrm{SD}}^{2}
=
\lim_{\Delta t\to 0}
\frac{1}{\Delta t}
\left\langle
(\Delta x)^2
\right\rangle .
}
\end{equation}

\paragraph{Interpretation.}
$\sigma_{\mathrm{SD}}^{2}$ measures the infinitesimal drift intensity induced by stochastic fluctuations near the TZP.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Recursive Toroidal Fiber Bundle by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Bundle Projection}\par
\[
T=\partial_t
\]
\noindent This fixes the base toroidal fiber-bundle projection over the spherical carrier.\par
\noindent\textbf{2. Toroidal Fiber}\par
\[
R=\mathrm{Id}
\]
\noindent This identifies the torus fiber used at each addressable point.\par
\noindent\textbf{3. Self-Similar Fiber Law}\par
\[
A=\mathrm{Id}
\]
\noindent This closes the entry by enforcing the self-similar equivalence of fibers across the bundle.\par

\clearpage
\noindent\textbf{[ID 0310] Recursive Toroidal Fiber Bundle}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Recursive Toroidal Fiber Bundle is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The DAANSphere is interpreted as the base space S to the power 2 of a fiber bundle T to E to S to the power 2, where the fiber over each point is a projection of the same torus T = S to the power 1 times S to the power 1. Formally, the total space E encodes the addressable states so that the local toroidal fibers are mutually isomorphic, T sub i cong T sub j cong T for all sampled addresses. \textbf{Contextual meaning:} The entry reads Recursive Toroidal Fiber Bundle as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the recursive toroidal bundle as an actual base-space, fiber, and equivalence structure instead of noisy mixed-format prose. \textbf{Lemma support:} Bundle Projection; Toroidal Fiber; Self-Similar Fiber Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub SD to the power 2 measures the infinitesimal drift intensity induced by stochastic fluctuations near the TZP. \% ========================================================= \% QUATERNARY DERIVATION LAYER -- ID 0311 TO ID 0315 \% =========================================================.

\tzpsection{Equation Grounding}
Equation anchors: T=partial sub t; R= Id; and A= Id. Proof route: show that the stated bundle projection and repeated torus fibers produce the claimed self-similar address structure. Formalization route: prove that the repeated torus-fiber equivalence is compatible with the stated bundle projection over the spherical base.

\tzpsection{Interpretive Role}
The entry now states the recursive toroidal bundle as an actual base-space, fiber, and equivalence structure instead of noisy mixed-format prose.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Self-Similar Annular Topology}: The geometric nesting where each point on a base manifold itself contains a secondary closed circular geometry.
\item \textbf{Fibrational Loop Projection}: The mapping rules governing how continuous trajectories wrap around the internal toroidal spaces.
\item \textbf{Base-to-Fiber Equivalence}: The structural invariant dictating that local cross-sections perfectly mirror the global cyclic manifold.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0310]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0310_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0310] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Recursive Toroidal Fiber Bundle}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the DAANSphere is interpreted as the base space S\textasciicircum{}2 of a fiber bundle \textbackslash{}[ T E S\textasciicircum{}2, \textbackslash{}]
where the fiber over each point is a projection of the same...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Recursive Toroidal Fiber Bundle is well formed when the total space, base space,
structure group, and projection map are compatible.''\\
\textbf{Proof:} The source statement supplies a bundle-style construction. The CHL reading treats the
base as the proposition carrier, the fiber or structure group as the typed parameter,
and the projection as the categorical morphism that preserves local-to-global structure.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- principal-bundle structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0310_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
