\section*{ID9429: Definition of ¥𝑢}
\paragraph{Metadata.}
PiID: 1543578468788 | RTEID: RTE:P36614.9010:T3.7814 | UUID: 1322bb38-4e05-598d-a826-db56c7c1ccb8

\paragraph{Canonical Statement.}
[ID 0407] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0406], [ID 0400] Node registry\_id\_0407 Support Titles Carrier Map; Composable Action; Normalized Output Test Handle If the stated map fails to compose or its output leaves the admissible target class, the entry fails. Canonical Equation Links 𝑔𝜇𝜈=𝜂𝜇𝜈+ℎ𝜇𝜈 𝜌 \$¥𝑢=(𝜆+𝜇)∇(∇·𝑢)+𝜇∇2𝑢+\$ 𝑓ext \$∇𝜇𝑇\$ 𝜇𝜈 \$damp≤0\$ [ID 0408] CYMATIC-VACUUM COUPLING (𝑋𝑖𝑡𝑒𝑥𝑡𝑐𝑦𝑚) TZPID ID0408 UUID c59789ea-60aa-5f13-93a0-84e828fce015 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops cymatic-vacuum coupling (xi textc

\paragraph{Canonical Equation.}
\[
¥𝑢=(𝜆+𝜇)∇(∇·𝑢)+𝜇∇2𝑢+
\]

\paragraph{Dictionary.}
Definition of ¥𝑢 — ¥𝑢=(𝜆+𝜇)∇(∇·𝑢)+𝜇∇2𝑢+

\paragraph{Encyclopedia.}
Definition of ¥𝑢 is an algebraic definition, written ¥𝑢=(𝜆+𝜇)∇(∇·𝑢)+𝜇∇2𝑢+. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
