\section*{ID9175: Relation: tfrac14π∫ ΣTr[FwedgeF ]CS}
\paragraph{Metadata.}
PiID: 7337862362561 | RTEID: RTE:P35628.5626:T2.1562 | UUID: 6e6163df-5125-584b-ab8d-7b71a10497e4

\paragraph{Canonical Statement.}
dencies: Primitive Derivable Consequences: Quantization of Chern–Simons levels; discrete classification of vacuum sectors; quantized coupling constants; impetus for topological transitions. Falsifiability / Test Handle: Detection of noninteger or continuous gerbe classes would falsify this classification. 2.0.6 ID 155: Chern–Simons Obstruction Class Type: Definition Formal Statement: The obstruction class for topological unification is given by the Chern–Simons invariant \$CS=14π∫ΣTr[F∧F ]CS\$ = \$\textbackslash{}tfrac\{1\}\{4\textbackslash{}pi\}\textbackslash{}int \{\textbackslash{}Sigma\}\textbackslash{}operatorname\{Tr\}[F\textbackslash{}wedgeF ]CS\$ = \$4π1∫ΣTr[F∧F ], computedfromtheconnectionformAµ= Aµdxµ+Bgravitational\$ + \$CelectromagneticA\_\textbackslash{}mu\$ = Canonical Registry Vol. 01 52 Trawin Zero Point Contextus Canonicus 2 TZP CANONICAL REGISTRY – ENTRIES 150–199 \$A\_\textbackslash{}mudxΘ\{\textbackslash{}mu\}+B\_\{\textbackslash{}text\{gravitational\}\}+ C\_\{\textbackslash{}text\{electromagnetic\}\}Aµ= Aµdxµ+Bgravitational\$ + \$Celectromagnetic.\$ Interpretive Meaning: This invariant measures the topological obstruct

\paragraph{Canonical Equation.}
\[
\tfrac{1}{4\pi}\int {\Sigma}\operatorname{Tr}[F\wedgeF ]CS
\]

\paragraph{Dictionary.}
Relation: tfrac14π∫ ΣTr[FwedgeF ]CS — tfrac14π∫ ΣTr[FwedgeF ]CS

\paragraph{Encyclopedia.}
Relation: tfrac14π∫ ΣTr[FwedgeF ]CS is an integral expression, written tfrac14π∫ ΣTr[FwedgeF ]CS. It is obtained by integrating over a domain, accumulating contributions across the region of interest. It is built from π, Σ, F, C, S. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
