\tzpanchor{0367}
\tzpentryheader{0367}{Reverse Harmonic Functor Pair}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{a2c20017-81f0-51b8-887f-15ab964227ba}}\\
\textbf{PiID} & \tzpcode{3054882046652} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{374}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1425.1425 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.3482 rad}\\
\textbf{TZPID} & \tzpcode{ID0367} & \textbf{Node Dependencies}\quad \tzpidref{0366}\\
\textbf{Registry} & \tzpcode{registry\_id\_0367} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Mode Quantization & Dispersion Law\\
\textbf{Closure Support} & Boundary Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The forward harmonic decomposition functor mapping field configurations to observed spectra admits a right adjoint that reconstructs field configurations from spectra. For objects X in the field category and Y in the spectral category, there is a natural isomorphism between morphisms from the forward image of X to Y and morphisms from X to the reverse image of Y.

\tzpsection{Canonical Equation}
\[
\mathcal{F}:\mathbf{Harm}\to\mathbf{RevHarm}
\]
\[
\mathcal{G}:\mathbf{RevHarm}\to\mathbf{Harm}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{F}$: source equation symbol.
    \item $\mathcal{G}$: source equation symbol.
    \item $\mathcal{K}_{0367}$: canonical registry object for entry ID 0367.
    \item $H$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0367 generated source Wolfram model *)
ClearAll[K0367, Cr0367, T, R, A, W, I, N];
eq0367$1 = HoldForm[F[mathbfHarm] -> mathbfRevHarm];
eq0367$2 = HoldForm[G[mathbfRevHarm] -> mathbfHarm];
eq0367$3 = HoldForm[GcircF == idHarm];

K0367 = HoldForm[{eq0367$1, eq0367$2, eq0367$3}];

N = "normalized TRAWIN closure object for Reverse Harmonic Functor Pair";
I = "Boundary Condition integration/comparison layer";
W = "Dispersion Law wave or operator carrier";
A = "Mode Quantization admissible action/amplitude condition";
R = "Dispersion Law rotation/curl preservation layer";
T = "Mode Quantization local source condition";

Cr0367[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0367 = Cr0367[K0367];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Mode Quantization local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Dispersion Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Mode Quantization admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Dispersion Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Boundary Condition integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Reverse Harmonic Functor Pair.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0367] Reverse Harmonic Functor Pair}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Gamma[\phi] = W[J] - \int J\phi.
\end{equation}

\paragraph{Primary Derivation.}
Effective action is Legendre transform of generating functional.

Thus:
\begin{equation}
\boxed{
\Gamma[\phi] = W[J] - \int J\phi.
}
\end{equation}

\paragraph{Interpretation.}
Encodes full quantum corrections.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Reverse Harmonic Functor Pair by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Mode Quantization}\par
\[
\mathcal{F}:\mathbf{Harm}\to\mathbf{RevHarm}
\]
\noindent This fixes the quantized carrier mode indexed by the bounded geometry.\par
\noindent\textbf{2. Dispersion Law}\par
\[
\mathcal{G}:\mathbf{RevHarm}\to\mathbf{Harm}
\]
\noindent This turns the mode index into an actual propagation or resonance law.\par
\noindent\textbf{3. Boundary Condition}\par
\[
\mathcal{G}\circ\mathcal{F}=\operatorname{id}_{\mathbf{Harm}}
\]
\noindent This closes the progression by enforcing the boundary or nodal condition that makes the pattern admissible.\par

\clearpage
\noindent\textbf{[ID 0367] Reverse Harmonic Functor Pair}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Reverse Harmonic Functor Pair is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The forward harmonic decomposition functor mapping field configurations to observed spectra admits a right adjoint that reconstructs field configurations from spectra. For objects X in the field category and Y in the spectral category, there is a natural isomorphism between morphisms from the forward image of X to Y and morphisms from X to the reverse image of Y. \textbf{Contextual meaning:} The entry reads Reverse Harmonic Functor Pair as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred. \textbf{Lemma support:} Mode Quantization; Dispersion Law; Boundary Condition.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Encodes full quantum corrections.

\tzpsection{Equation Grounding}
Equation anchors: H sub env = sum sub k hbar omega sub k E sub k to the power dagger E sub k + H sub env-coupling; H sub env = sum sub k hbar omega sub k E sub k to the power dagger E sub k + H sub env-coupling; and ac g sub a g sub b Delta sub c(t) + dots H sub eff = begin pmatrix E sub a \& T sub eff (t) T sub eff to the power *(t) \& E sub b end pmatrix , T sub eff (t) approximately fr. Proof route: show that bounded carrier geometry forces the stated mode quantization and resonance law. Formalization route: prove that the stated boundary condition yields the stated discrete spectrum.

\tzpsection{Interpretive Role}
The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Time-Reversal Symmetry Mapping}: The specific algebraic tool that flips the chronological progression of a wave, calculating its exact backward trajectory.
\item \textbf{Inward-Focusing Phase Conjugation}: The physical process of taking an expanding, radiating wave and precisely reversing it to converge on its original source point.
\item \textbf{Bi-Directional Operator Identity}: The formal proof that applying the forward evolution followed immediately by the reverse evolution results in zero net change.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0367]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0367_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0367] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Reverse Harmonic Functor Pair}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the forward harmonic decomposition functor mapping field configurations to observed
spectra admits a right adjoint that reconstructs field configur...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Reverse Harmonic Functor Pair is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0367_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
