\section*{ID8780: Definition of Xi}
\paragraph{Metadata.}
PiID: 0911407907386 | RTEID: RTE:P34094.6898:T5.9121 | UUID: 0e53cb8a-d734-5553-b255-7828cb64dc89

\paragraph{Canonical Statement.}
e \$\textbackslash{}Xi(x,t)\$ as a scalar that is +1 if the local field is primarily from TZP⁺ branch and -1 if from TZP⁻ branch (or some continuous measure, say \$\textbackslash{}Xi = \textbackslash{}cos\textbackslash{}alpha\$ where \$\textbackslash{}alpha\$ is angle in DAANSspace between local field direction and some reference orientation). A simulation could transport a marker along field lines to label them plus or minus, thereby generating \$\textbackslash{}Xi(x)\$ in space – akin to dyeing the field lines different colors and seeing where those colors go. Initially, at TZP⁺, \$\textbackslash{}Xi=+1\$ and at TZP⁻, \$\textbackslash{}Xi=-1\$ . Along the loop in 4D, \$\textbackslash{}Xi\$ might be +1 until the loop crosses TZP then flips to -1. The simulation might then produce an image where space near TZP⁺ is colored differently than space near TZP⁻, with a gradient or boundary surface where \$\textbackslash{}Xi\$ transitions. That boundary would in fact be the surface where field from both branches meet and cancel or interact – possibly

\paragraph{Canonical Equation.}
\[
\Xi=+1
\]

\paragraph{Dictionary.}
Definition of Xi — Xi=+1

\paragraph{Encyclopedia.}
Definition of Xi is an algebraic definition, written Xi=+1. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
