\section*{ID9459: Definition of Clocus}
\paragraph{Metadata.}
PiID: 1984922528471 | RTEID: RTE:P36731.3976:T3.9734 | UUID: 878c8c98-d8d9-55cd-a2ef-932211e1b4c5

\paragraph{Canonical Statement.}
, 𝑎𝑛 \$≠\$ 0 \$∀𝑛\$ Clocus = \{𝑟 : det(Jac) (𝑟) = 0 \$∧\$ 𝜋1(M \textbackslash{} \{𝑟\})  Z × Z\} Wolfram Form 𝔚TZP (K0554) \$↦−→ 〈 ΨT, Ω\$ T, 𝜌vac \$〉\$ K0554 := HoldForm(T0554) AdmissibleTZP (K0554) \$⇐⇒\$ 𝔚TZP (K0554) . \$∅\$ Wolfram register: canonical symbol lift Title lift: THE JACOBIAN FLOW SINGULARITY (STAGNATION POINT DYNAMICS) Symbol key: \$ΨT:\$ Trawinistic wavefunction \$ΩT:\$ Trawinistic boundary curvature 𝜌vac: vacuum energy density TRAWIN Normalization NormalizeTRAWIN( 𝐹 (𝑇) = \$∞∑\$ 𝑛=1 𝑎𝑛𝑇 𝑛, 𝑎𝑛 \$≠\$ 0 \$∀𝑛,\$ Clocus = \{𝑟 : det(Jac) (𝑟) = 0 \$∧\$ 𝜋1(M \textbackslash{} \{𝑟\})  Z × Z\}, Aadm(Clocus) = 1 ) T: Analytic Flow Series is localized within the quantum-classical transition arc of the directory. R: Singular Locus preserves the operative relation that the jacobian flow singularity (stagnation point dynamics) re-quires. A: Admissible Closure fixes the admissible closure condi-tion for the entry. W: THE JACOBIAN FLOW SINGULARITY (STAGNA-TION POINT DYN

\paragraph{Canonical Equation.}
\[
Clocus = {𝑟 : det(Jac) (𝑟) = 0
\]

\paragraph{Dictionary.}
Definition of Clocus — Clocus = 𝑟 : det(Jac) (𝑟) = 0

\paragraph{Encyclopedia.}
Definition of Clocus is an algebraic definition, written Clocus = 𝑟 : det(Jac) (𝑟) = 0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from J, a, c, defining Clocus. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
