\section*{ID6555: How to Translate Your Spherical Vortex Model into a Cosmological Counterpart: Dω/Dt}
\paragraph{Metadata.}
PiID: 9212507712629 | RTEID: RTE:P25454.5207:T4.2421 | UUID: 69b632bf-d4b1-55ca-8c84-351676c71b10

\paragraph{Canonical Statement.}
5. **Vorticity dynamics** - Where your fluid vorticity equation used \textbackslash{}(D\textbackslash{}omega/Dt = (\textbackslash{}omega\textbackslash{}cdot\textbackslash{}nabla)\textbackslash{}mathbf\{v\} + \textbackslash{}ldots\textbackslash{}), cosmological vorticity for dark matter is near zero in linear theory and grows at small scales via shell crossing and velocity dispersion. For baryonic gas, shock/turbulence ­terms produce vorticity similar to fluid flows (IGM turbulence literature). So expect vortex-like filaments in baryons; in dark matter you see filamentary **multi-stream** flows whose projection can look vortexy but are collisionless in origin. citeturn1academia20turn1academia22

\paragraph{Canonical Equation.}
\[
D\omega/Dt = (\omega\cdot\nabla)\mathbf{v} + \ldots
\]

\paragraph{Dictionary.}
Relation: Dω/Dt = (ω·∇)v + ldots

\paragraph{Encyclopedia.}
How to Translate Your Spherical Vortex Model into a Cosmological Counterpart: Dω/Dt is a differential equation, written Dω/Dt = (ω·∇)v + ldots. It relates the quantity to its derivatives, governing how the system evolves in space and time. It is built from ω, ∇, v, defining Dω/Dt. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
