\section*{ID9024: Relation: P\_null:T\_pM→T\_pMP\_null:T\_p}
\paragraph{Metadata.}
PiID: 1665443755890 | RTEID: RTE:P35042.1960:T1.1901 | UUID: 51b944d4-aa51-5bd3-87da-cb7b6a6086c4

\paragraph{Canonical Statement.}
decoherence. Dependencies: ID 001, ID 016 Derivable Consequences: Provides a quantitative handle on decoherence; enters definitions of entanglement structure; influences measurement backaction; informs information flux calculations. Falsifiability / Test Handle: Observation of field configurations that violate the predicted coherence bounds (e.g., exceeding 1) would falsify this definition. 0.0.15 ID 013: Null Space Projection Type: Operator Formal Statement: The null space projection operator \$P\_null:T\_pM→T\_pMP\_\{\textbackslash{}text\{null\}\}:T\_p\$ M\textbackslash{}to T\_p \$MP\_null:T\_pM→T\_pM\$ is defined by P\_null(v)=vP\_\{\textbackslash{}text\{null\}\}(v)=vP\_null(v)=v if g(v,w)=0g(v,w)=0g(v,w)=0 for all \$w∈T\_pMw\textbackslash{}in\$ T\_p \$Mw∈T\_pM,\$ and P\_null(v)=0P\_\{\textbackslash{}text\{null\}\}(v)=0P\_null(v)=0 otherwise. Interpretive Meaning: This operator extracts the components of a tangent vector that lie in the null space of the degenerate metric at the TZP. It identifies directions in which the metric

\paragraph{Canonical Equation.}
\[
P_null:T_pM→T_pMP_{\text{null}}:T_p
\]

\paragraph{Dictionary.}
Relation: P\_null:T\_pM→T\_pMP\_null:T\_p — P\_null:T\_pM→T\_pMP\_null:T\_p

\paragraph{Encyclopedia.}
Relation: P\_null:T\_pM→T\_pMP\_null:T\_p is a symbolic expression, written P\_null:T\_pM→T\_pMP\_null:T\_p. It introduces a symbol or relation used elsewhere in the framework. It is built from P\_n, u, l, T\_p, M, P\_. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
