\section*{ID9519: Synchronization: Kuramoto Networks and Phase Coherence: ∼ χ\textasciicircum{}-1}
\paragraph{Metadata.}
PiID: 3027634787081 | RTEID: RTE:P36964.3910:T4.3573 | UUID: 1f7c0fba-bc85-521f-a4fe-b5a71a22f6cd

\paragraph{Canonical Statement.}
From another angle, consider a network of orbiting asteroids or Kuiper belt objects beyond the synchronization sphere of the Sun. These bodies are effectively uncoupled – they don’t coalesce into a planet due to lack of synchrony in their phases. We can say the Sun’s influence (via gravitational phase coupling or oscillation entrainment) at that distance is below threshold. Perhaps at the very edge of influence, the coupling is \$\textbackslash{}sim \textbackslash{}chi\textasciicircum{}\{-1\}\$ (about 0.84) times the required value – just insufficient to synchronize phases and thus to allow collective accretion. A slightly stronger coupling (had the bodies been closer by \textasciitilde{}15\%) would push them over the threshold to coalesce into a larger body. In essence, \$\textbackslash{}chi\$ could demarcate the border between chaos and order in these rotationally-supported disks: inside a certain radius, gravitation plus dissipation can synchronize orbits enough to clear gaps and form planets; outside, synchronizat

\paragraph{Canonical Equation.}
\[
\sim \chi^{-1}
\]

\paragraph{Dictionary.}
From another angle, consider a network of orbiting asteroids or Kuiper belt objects beyond the synchronization sphere of the Sun.

\paragraph{Encyclopedia.}
Synchronization: Kuramoto Networks and Phase Coherence: ∼ χ\textasciicircum{}-1 is a scaling / order-of-magnitude relation, written ∼ χ\textasciicircum{}-1. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from χ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
