\section*{ID9105: Definition of β(g,dim eff)µdµdg}
\paragraph{Metadata.}
PiID: 1130315095261 | RTEID: RTE:P35356.7370:T1.7084 | UUID: b0ea179c-8c1f-52aa-ac55-a24ea82f227c

\paragraph{Canonical Statement.}
ndle: Observing no critical behaviour where the theory predicts a quantum phase transition would challenge this definition. 0.0.60 ID 058: Renormalization Flow as Dimensional Navigation Type: Structural Constraint Formal Statement: The renormalization group flow on the Trawinistic manifold is interpreted as navigation through effective dimensions defined by the hyperdimensional span; coupling constants \$g(µ)g(\textbackslash{}mu)g(µ)\$ evolve according to \$µdgdµ=β(g,dimeff)\textbackslash{}mu\textbackslash{}frac\{\textbackslash{}text\{d\}g\}\{\textbackslash{}text\{d\}\textbackslash{}mu\}\$ = \$\textbackslash{}beta(g,\textbackslash{}dim \{\textbackslash{}text\{eff\}\})µdµdg=β(g,dimeff),\$ where dimeff\textbackslash{}dim\_\{\textbackslash{}text\{eff\}\}dimeff varies near the TZP. Interpretive Meaning: Changes in scale correspond to moving through spaces of different effective dimension; the zero point provides a pivot for dimensional transitions. Dependencies: ID 009, ID 057 Derivable Consequences: Explanation of dimensional crossovers; predictions of scaledependent physical constants; linkage of UV and IR fixed poi

\paragraph{Canonical Equation.}
\[
\beta(g,\dim {\text{eff}})µdµdg=β(g,dimeff),
\]

\paragraph{Dictionary.}
Definition of β(g,dim eff)µdµdg — β(g,dim eff)µdµdg=β(g,dimeff)

\paragraph{Encyclopedia.}
Definition of β(g,dim eff)µdµdg is an algebraic definition, written β(g,dim eff)µdµdg=β(g,dimeff). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from g, m, f, defining β(g,dim eff)µdµdg. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
