\section*{ID9017: Relation: ∫\_Γ√(|g|), dellu\_T…}
\paragraph{Metadata.}
PiID: 0603402166544 | RTEID: RTE:P35015.0135:T1.1453 | UUID: 31b6a7cb-7ae0-5b2e-957e-46c0f3e593b8

\paragraph{Canonical Statement.}
ion of topological charge; restricts allowed gauge transformations; informs the characteristic class. Falsifiability / Test Handle: Discovery of a symmetry transformation that moves the zero point or changes the lemniscatic structure would violate this axiom. Canonical Registry Vol. 01 3 Trawin Zero Point Contextus Canonicus 0.0.8 ID 006: Trawin Base Unit Type: Definition Formal Statement: The Trawin base unit u\_Tu\_\{\textbackslash{}text\{T\}\}u\_T is defined by the invariant relation u\_T:= \$∫ Γgdu\_\{\textbackslash{}text\{T\}\}\$ := \$\textbackslash{}int\_\{\textbackslash{}Gamma\}\textbackslash{}sqrt\{|g|\}, \textbackslash{}text\{d\}\textbackslash{}ellu\_T :=∫ΓgdtakenoverafundamentalloopΓ\textbackslash{}GammaΓencirclingtheTZPexactlyonce.\$ Interpretive Meaning: The base unit of measurement in the TZP framework is the integral of the metric density around a single lemniscatic loop. It replaces conventional units and ensures scaling consistent with the zero point. Dependencies: ID 002, ID 004 Derivable Consequences: Normalises other quantities (e.g., temporal displacement factor); serves as scaling factor in Hamiltonians; an

\paragraph{Canonical Equation.}
\[
\int_{\Gamma}\sqrt{|g|}, \text{d}\ellu_T :=∫ΓgdtakenoverafundamentalloopΓ\GammaΓencirclingtheTZPexactlyonce.
\]

\paragraph{Dictionary.}
Relation: ∫\_Γ√(|g|), dellu\_T… — ∫\_Γ√(|g|), dellu\_T :=∫ΓgdtakenoverafundamentalloopΓΓΓencirclingtheTZPexactlyonce.

\paragraph{Encyclopedia.}
Relation: ∫\_Γ√(|g|), dellu\_T… is an integral expression, written ∫\_Γ√(|g|), dellu\_T :=∫ΓgdtakenoverafundamentalloopΓΓΓencirclingtheTZPexactlyonce. It is obtained by integrating over a domain, accumulating contributions across the region of interest. It is built from Γ, g, T, a, k, n. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
