\section*{ID9350: Definition of ∇2Φ}
\paragraph{Metadata.}
PiID: 0037279839400 | RTEID: RTE:P36308.1264:T3.2760 | UUID: a0a3392d-1525-5086-9980-45a3f580f790

\paragraph{Canonical Statement.}
ID 0183] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0182], [ID 0179] Node registry\_id0183 Support Titles Coherence Restoration; Potential Equation; Effective Gravity Test Handle If the field does not restore coherence or fails to yield a potential equation, the gravity statement fails. Canonical Equation Links \$∇2Φ=4𝜋𝐺eff𝜌 𝐺eff≪𝐺 NormalizeTRAWIN(∇2Φ,𝐺eff\$ ,gravity) [ID 0184] Weakness of Gravity from Particle Perturbations TZPID ID0184 UUID 4ef3b3fa-5d59-45c9-9620-66b3c1f5ef6a Type Scaling Statement Scale cosmic LOC Classification Working routing: QB gravitation and relativity arXiv Classification Primary: gr-qc; Cross-list: astro-ph.CO, hep-th Canonical Statement Gravity is weak because each particle perturbs the coherence field only slightly. The

\paragraph{Canonical Equation.}
\[
∇2Φ=4𝜋𝐺eff𝜌 𝐺eff≪𝐺 NormalizeTRAWIN(∇2Φ,𝐺eff
\]

\paragraph{Dictionary.}
Definition of ∇2Φ — ∇2Φ=4𝜋𝐺eff𝜌 𝐺eff≪𝐺 NormalizeTRAWIN(∇2Φ,𝐺eff

\paragraph{Encyclopedia.}
Definition of ∇2Φ is an algebraic definition, written ∇2Φ=4𝜋𝐺eff𝜌 𝐺eff≪𝐺 NormalizeTRAWIN(∇2Φ,𝐺eff. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from f, N, o, r, m, a, defining ∇2Φ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
