\section*{ID9260: Definition of Q(r)}
\paragraph{Metadata.}
PiID: 0738837781423 | RTEID: RTE:P35958.6364:T2.7001 | UUID: 98bbbe46-377a-5cab-bc42-d79d541eb42c

\paragraph{Canonical Statement.}
to general relativity. Falsifiability / Test Handle: Attempt to detect gravitomagnetic fields using sensitive gyroscopes or interferometry; compare observations with predicted magnitude and spatial dependence. Canonical Registry Vol. 01 113 Trawin Zero Point Contextus Canonicus 2 TZP CANONICAL REGISTRY – ENTRIES 150–199 2.0.177 ID 326: Toroidal Field Safety Factor Constraint Type: Structural Constraint Formal Statement: For a nested toroidal magnetic confinement configuration, the safety factor \$q(r)=rB/(R0Bθ)q(r)\$ = r B\_\{\textbackslash{}phi\}/(R\_0 \$B\_\{\textbackslash{}theta\})q(r)=rB/(R0Bθ)\$ must exceed a critical value \$qcritical≈2.8q\_\{\textbackslash{}text\{critical\}\}\textbackslash{}approx 2.8qcritical≈2.8\$ to ensure stability. Interpretive Meaning: The safety factor characterizes the ratio of toroidal to poloidal field components in a toroidal confinement system. Exceeding the critical threshold prevents kink and tearing instabilities, ensuring stable confinement o

\paragraph{Canonical Equation.}
\[
q(r)=rB/(R0Bθ)q(r)
\]

\paragraph{Dictionary.}
Definition of Q(r) — q(r)=rB/(R0Bθ)q(r)

\paragraph{Encyclopedia.}
Definition of Q(r) is an algebraic definition, written q(r)=rB/(R0Bθ)q(r). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from r, B, R, q, defining q(r). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
