\tzpanchor{0292}
\tzpentryheader{0292}{Simplicial and Homological Entropy}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{1aca5bfd-2bdb-5dd9-bc56-7a3fdceb607a}}\\
\textbf{PiID} & \tzpcode{4914127372458} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{299}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1133.9008 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.8683 rad}\\
\textbf{TZPID} & \tzpcode{ID0292} & \textbf{Node Dependencies}\quad \tzpidref{0291}\\
\textbf{Registry} & \tzpcode{registry\_id\_0292} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Entropy Weight & Normalized Distribution\\
\textbf{Closure Support} & Topological Aggregate & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
These entropies measure the complexity of a simplicial complex or its homology group structure; larger values indicate richer topology.

\tzpsection{Canonical Equation}
\[
p_k=\frac{n_k}{\sum_j n_j}
\]
\[
H_s=-\sum_k p_k\log_2 p_k
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $p_k$: source equation symbol.
    \item $n_k$: source equation symbol.
    \item $n_j$: source equation symbol.
    \item $H_s$: source equation symbol.
    \item $H_h$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0292 generated source Wolfram model *)
ClearAll[K0292, Cr0292, T, R, A, W, I, N];
eq0292$1 = HoldForm[pK == nK/(SumJ*nJ)];
eq0292$2 = HoldForm[HS == (-SumK)*pKlog2*pK];
eq0292$3 = HoldForm[HH == (-SumK)*betaK^ast*log2*betaK^ast];

K0292 = HoldForm[{eq0292$1, eq0292$2, eq0292$3}];

N = "normalized TRAWIN closure object for Simplicial and Homological Entropy";
I = "Topological Aggregate integration/comparison layer";
W = "Normalized Distribution wave or operator carrier";
A = "Entropy Weight admissible action/amplitude condition";
R = "Normalized Distribution rotation/curl preservation layer";
T = "Entropy Weight local source condition";

Cr0292[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0292 = Cr0292[K0292];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Entropy Weight local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Normalized Distribution rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Entropy Weight admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Normalized Distribution wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Aggregate integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Simplicial and Homological Entropy.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0292] Simplicial and Homological Entropy}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
G=SO(3)\ltimes_{\varphi} U(1).
\end{equation}

\paragraph{Composition Law.}
\begin{equation}
(R,e^{i\alpha})\cdot(R',e^{i\beta})
=
\left(
RR',
e^{i\alpha}\varphi_R(e^{i\beta})
\right).
\end{equation}

\paragraph{Primary Derivation.}
If rotation and gauge phase compose independently, the group is a direct product.  
If rotations act on gauge phase through an automorphism $\varphi_R$, the coupled group is a semi-direct product:

\begin{equation}
G=SO(3)\ltimes_{\varphi}U(1).
\end{equation}

The product law becomes:
\begin{equation}
\boxed{
(R,e^{i\alpha})\cdot(R',e^{i\beta})
=
\left(
RR',
e^{i\alpha}\varphi_R(e^{i\beta})
\right).
}
\end{equation}

\paragraph{Interpretation.}
Rotation and phase are treated as interacting symmetry sectors rather than merely adjacent labels.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Simplicial and Homological Entropy by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Entropy Weight}\par
\[
p_k=\frac{n_k}{\sum_j n_j}
\]
\noindent This records the local information weight carried by the persistence data or structural channel.\par
\noindent\textbf{2. Normalized Distribution}\par
\[
H_s=-\sum_k p_k\log_2 p_k
\]
\noindent This makes the entropy law admissible by normalizing the supporting lifetimes or amplitudes.\par
\noindent\textbf{3. Topological Aggregate}\par
\[
H_h=-\sum_k \beta_k^{\ast}\log_2\beta_k^{\ast}
\]
\noindent This closes the entry by recombining the filtered sectors into one total diagnostic.\par

\clearpage
\noindent\textbf{[ID 0292] Simplicial and Homological Entropy}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Simplicial and Homological Entropy is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} These entropies measure the complexity of a simplicial complex or its homology group structure; larger values indicate richer topology. \textbf{Contextual meaning:} The entry reads Simplicial and Homological Entropy as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers. \textbf{Lemma support:} Entropy Weight; Normalized Distribution; Topological Aggregate.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Rotation and phase are treated as interacting symmetry sectors rather than merely adjacent labels.

\tzpsection{Equation Grounding}
Equation anchors: p sub k=ratio n sub k sum sub j n sub j; H sub s=-sum sub k p sub klog sub 2 p sub k; and H sub h=-sum sub k beta sub k to the power ast log sub 2beta sub k to the power ast. Proof route: show that the normalized support distribution induces a well-defined entropy functional for the stated topological or informational channel. Formalization route: prove that positivity and normalization of the support weights imply finiteness of the stated entropy functional.

\tzpsection{Interpretive Role}
The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Lattice Discretization Uncertainty Measure}: The calculation of the fundamental information lost when a smooth, continuous physical shape is approximated by a rigid grid of triangles and tetrahedrons.
\item \textbf{Entropy Derived from Polyhedral Ranks}: The tracking of system complexity simply by counting the ratio of points to lines to faces in its underlying geometric scaffolding.
\item \textbf{Discrete Geometry Information Loss}: The precise mathematical boundary indicating how much of a continuous wave's data is permanently destroyed when mapped onto a finite computational mesh.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0292]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0292_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0292] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Simplicial and Homological Entropy}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} these entropies measure the complexity of a simplicial complex or its homology group
structure; larger values indicate richer topology

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Simplicial and Homological Entropy is valid when the stated geometric or topological
relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0292_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
