\section*{ID8493: UNIVERSAL AVALANCHE SCALING Canonical Statutory Formula: P(s) ∝ s\textasciicircum{}-τ, τ ≈ 3/2}
\paragraph{Metadata.}
PiID: 3970968340800 | RTEID: RTE:P32980.2051:T4.0758 | UUID: 1287dbef-b850-561b-8264-7309d96824b6

\paragraph{Canonical Statement.}
[ID 1167] UNIVERSAL AVALANCHE SCALING Canonical Statutory Formula: \$P(s) \textbackslash{}propto s\textasciicircum{}\{-\textbackslash{}tau\}, \textbackslash{}quad \textbackslash{}tau \textbackslash{}approx 3/2\$ Formal Technical Dissertation: The universal organizing principle of the system. It identifies the critical exponent \$\textbackslash{}tau \textbackslash{}approx 1.5\$ as the signature of topological protection, appearing identically in quantum decoherence cascades, neural avalanches, and the Trawin reactor dynamics, indicating a shared "Universality Class" of processing. Source: [7], [8], [9]

\paragraph{Canonical Equation.}
\[
P(s) \propto s^{-\tau}, \quad \tau \approx 3/2
\]

\paragraph{Dictionary.}
UNIVERSAL AVALANCHE SCALING Canonical Statutory Formula: P(s) ∝ s\textasciicircum{}-τ, τ ≈ 3/2 Formal Technical Dissertation: The universal organizing principle of the system.

\paragraph{Encyclopedia.}
UNIVERSAL AVALANCHE SCALING Canonical Statutory Formula: P(s) ∝ s\textasciicircum{}-τ, τ ≈ 3/2 is a scaling / order-of-magnitude relation, written P(s) ∝ s\textasciicircum{}-τ, τ ≈ 3/2. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from τ, P, s. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
