\tzpanchor{0290}
\tzpentryheader{0290}{Betti Curve Entropy}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f935a8f8-bb61-52e6-9007-a409503eb686}}\\
\textbf{PiID} & \tzpcode{0249141273724} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{297}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1126.1344 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.8555 rad}\\
\textbf{TZPID} & \tzpcode{ID0290} & \textbf{Node Dependencies}\quad \tzpidref{0289}\\
\textbf{Registry} & \tzpcode{registry\_id\_0290} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Entropy Weight & Normalized Distribution\\
\textbf{Closure Support} & Topological Aggregate & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
It assesses how topological complexity evolves with scale; variable Betti curves indicate hierarchical organisation.

\tzpsection{Canonical Equation}
\[
\beta_k(\epsilon)=\operatorname{rank}H_k(X_{\epsilon})
\]
\[
p_i=\frac{|\Delta\beta_i|}{\sum_j|\Delta\beta_j|}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H_k$: source equation symbol.
    \item $p_i$: source equation symbol.
    \item $H_{\beta}$: source equation symbol.
    \item $\mathcal{K}_{0290}$: canonical registry object for entry ID 0290.
    \item $\beta$: source equation symbol.
    \item $\epsilon$: source equation symbol.
    \item $\Delta$: source equation symbol.
    \item $H$: source equation symbol.
    \item $X_{\epsilon}$: source equation symbol.
    \item $D$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0290 generated source Wolfram model *)
ClearAll[K0290, Cr0290, T, R, A, W, I, N];
eq0290$1 = HoldForm[betaK[epsilon] == rankHK[XEpsilon]];
eq0290$2 = HoldForm[pI == Abs[DeltabetaI]/SumJAbs[DeltabetaJ]];
eq0290$3 = HoldForm[HBeta == (-SumI)*pIlog*pI];

K0290 = HoldForm[{eq0290$1, eq0290$2, eq0290$3}];

N = "normalized TRAWIN closure object for Betti Curve Entropy";
I = "Topological Aggregate integration/comparison layer";
W = "Normalized Distribution wave or operator carrier";
A = "Entropy Weight admissible action/amplitude condition";
R = "Normalized Distribution rotation/curl preservation layer";
T = "Entropy Weight local source condition";

Cr0290[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0290 = Cr0290[K0290];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Entropy Weight local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Normalized Distribution rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Entropy Weight admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Normalized Distribution wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Aggregate integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Betti Curve Entropy.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0290] Betti Curve Entropy}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Invariant Matching Condition.}
\begin{equation}
\Pi_k^{\mathrm{lab}}
=
\Pi_k^{\mathrm{astro}} .
\end{equation}

\paragraph{Scale Equivalence Map.}
\begin{equation}
F_{\mathrm{scale}}:
\mathcal{S}_{\mathrm{lab}}
\longrightarrow
\mathcal{S}_{\mathrm{astro}} .
\end{equation}

\paragraph{Primary Derivation.}
Let $\Pi_k$ denote a dimensionless invariant governing a dynamical system.  
Laboratory and astrophysical systems are structurally comparable only when their governing invariant sets match:
\begin{equation}
\Pi_k^{\mathrm{lab}}
=
\Pi_k^{\mathrm{astro}} .
\end{equation}

A scale map then translates the laboratory realization into the astrophysical realization:
\begin{equation}
F_{\mathrm{scale}}:
\mathcal{S}_{\mathrm{lab}}
\to
\mathcal{S}_{\mathrm{astro}} .
\end{equation}

Thus,
\begin{equation}
\boxed{
\Xi_{\mathrm{eq}}
=
\mathrm{NormalizeTRAWIN}
\left(
\mathcal{S}_{\mathrm{lab}},
\mathcal{S}_{\mathrm{astro}},
F_{\mathrm{scale}},
\Pi_k
\right).
}
\end{equation}

\paragraph{Interpretation.}
Laboratory demonstrations become structurally meaningful for astrophysical systems only when the scale map preserves the relevant dimensionless invariants.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Betti Curve Entropy by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Entropy Weight}\par
\[
\beta_k(\epsilon)=\operatorname{rank}H_k(X_{\epsilon})
\]
\noindent This records the local information weight carried by the persistence data or structural channel.\par
\noindent\textbf{2. Normalized Distribution}\par
\[
p_i=\frac{|\Delta\beta_i|}{\sum_j|\Delta\beta_j|}
\]
\noindent This makes the entropy law admissible by normalizing the supporting lifetimes or amplitudes.\par
\noindent\textbf{3. Topological Aggregate}\par
\[
H_{\beta}=-\sum_i p_i\log p_i
\]
\noindent This closes the entry by recombining the filtered sectors into one total diagnostic.\par

\clearpage
\noindent\textbf{[ID 0290] Betti Curve Entropy}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Betti Curve Entropy is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} It assesses how topological complexity evolves with scale; variable Betti curves indicate hierarchical organisation. \textbf{Contextual meaning:} The entry reads Betti Curve Entropy as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers. \textbf{Lemma support:} Entropy Weight; Normalized Distribution; Topological Aggregate.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Laboratory demonstrations become structurally meaningful for astrophysical systems only when the scale map preserves the relevant dimensionless invariants.

\tzpsection{Equation Grounding}
Equation anchors: beta sub k(epsilon)=operatorname rank H sub k(X sub epsilon ); p sub i=ratio |Deltabeta sub i| sum sub j|Deltabeta sub j|; and H sub beta =-sum sub i p sub ilog p sub i. Proof route: show that the normalized support distribution induces a well-defined entropy functional for the stated topological or informational channel. Formalization route: prove that positivity and normalization of the support weights imply finiteness of the stated entropy functional.

\tzpsection{Interpretive Role}
The entry turns a qualitative complexity claim into a counted diagnostic that can be compared across neighboring persistence or information layers.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Continuous Trace of Topological Features}: The generation of a unique entropy graph by continuously counting the number of isolated clusters, loops, and hollow voids in a system as it evolves.
\item \textbf{Rank Variation Complexity Metric}: The measurement of how wildly the connectivity of a network fluctuates over time, providing a deep signature of the system's internal chaos or order.
\item \textbf{Evolving Topology Information Content}: The calculation proving that a smoothly changing geometry contains a specific, measurable amount of hidden data based on its tearing and merging boundaries.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0290]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0290_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0290] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Betti Curve Entropy}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} it assesses how topological complexity evolves with scale; variable Betti curves
indicate hierarchical organisation

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Betti Curve Entropy is valid when the stated geometric or topological relation preserves
its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0290_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
