\tzpanchor{0921}
\tzpentryheader{0921}{FISHER INFORMATION METRIC (ACQUISITION)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{566e5a26-61d9-5a39-8b9b-f329610741d0}}\\
\textbf{PiID} & \tzpcode{1595628638823} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{928}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3522.0824 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.8033 rad}\\
\textbf{TZPID} & \tzpcode{ID0921} & \textbf{Node Dependencies}\quad \tzpidref{0920}\\
\textbf{Registry} & \tzpcode{registry\_id\_0921} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
u(theta,lambda,t) /;=/; -frac\{1\}\{Rsintheta\}/,frac\{partialPsi\}\{partialtheta\},qquad v(theta,lambda,t) /;=/; frac\{1\}\{R\}/,frac\{partialPsi\}\{partiallambda\}.

\tzpsection{Canonical Equation}
\[
omega_{tesla} = \frac{1}{\sqrt{L_{sec} C_{self}}} \implies 158.3 \text{ kHz}
\]
\[
omega_{tesla} = \frac{1}{\sqrt{L_{sec} C_{self}}} \implies 158.3 \text{ kHz}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $L_{sec}$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $C_{self}$: source equation symbol.
    \item $\mathcal{K}_{0921}$: canonical registry object for entry ID 0921.
    \item $\implies$: source equation symbol.
    \item $H$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0921 generated source Wolfram model *)
ClearAll[K0921, Cr0921, T, R, A, W, I, N];
eq0921$1 = HoldForm[omegaTesla == (1/sqrt[LSec*CSelf])*implies158*0.3];
eq0921$2 = HoldForm[omegaTesla == (1/sqrt[LSec*CSelf])*implies158*0.3];

K0921 = HoldForm[{eq0921$1, eq0921$2}];

N = "normalized TRAWIN closure object for FISHER INFORMATION METRIC (ACQUISITION)";
I = "FISHER INFORMATION METRIC (ACQUISITION) integration/comparison layer";
W = "FISHER INFORMATION METRIC (ACQUISITION) wave or operator carrier";
A = "FISHER INFORMATION METRIC (ACQUISITION) admissible action/amplitude condition";
R = "FISHER INFORMATION METRIC (ACQUISITION) rotation/curl preservation layer";
T = "FISHER INFORMATION METRIC (ACQUISITION) local source condition";

Cr0921[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0921 = Cr0921[K0921];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ FISHER INFORMATION METRIC (ACQUISITION) local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ FISHER INFORMATION METRIC (ACQUISITION) rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ FISHER INFORMATION METRIC (ACQUISITION) admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ FISHER INFORMATION METRIC (ACQUISITION) wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ FISHER INFORMATION METRIC (ACQUISITION) integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for FISHER INFORMATION METRIC (ACQUISITION).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0921] FISHER INFORMATION METRIC (ACQUISITION)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
omega_{tesla} = \frac{1}{\sqrt{L_{sec} C_{self}}} \implies 158.3 \text{ kHz}
\]
\[
omega_{tesla} = \frac{1}{\sqrt{L_{sec} C_{self}}} \implies 158.3 \text{ kHz}
\]

\paragraph{Primary Derivation.}
One can verify the equality by employing standard algebraic manipulations, yielding the required identity.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. In the TRAWIN reading, the equation functions as the generalized carrier for the entry’s information content. Within the CHL view, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors FISHER INFORMATION METRIC (ACQUISITION) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
omega_{tesla} = \frac{1}{\sqrt{L_{sec} C_{self}}} \implies 158.3 \text{ kHz}
\]
\[
omega_{tesla} = \frac{1}{\sqrt{L_{sec} C_{self}}} \implies 158.3 \text{ kHz}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0921] FISHER INFORMATION METRIC (ACQUISITION)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
FISHER INFORMATION METRIC (ACQUISITION) is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} u(theta,lambda,t) /;=/; -frac 1 Rsintheta /,frac partialPsi partialtheta ,qquad v(theta,lambda,t) /;=/; frac 1 R /,frac partialPsi partiallambda. \textbf{Contextual meaning:} The entry reads FISHER INFORMATION METRIC (ACQUISITION) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Geometric Carrier; Compatibility Law; Topological Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, FISHER INFORMATION METRIC (ACQUISITION) is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: g sub ibar j = partial sub i partial sub bar j log(1 + sum |z sub k| to the power 2/R sub k); g sub ij (theta) = -E[ratio partial to the power 2 partial theta sub i partial theta sub j log p(x|theta)]; and omega sub tesla = ratio 1 sqrt L sub sec C sub self implies 158.3 kHz. Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Statistical Distance Measurement}: The calculation of exactly how much the chaotic, jumping numbers on the sensor readouts differ from the smooth, safe numbers the engineers actually want to see.
\item \textbf{Cramer-Rao Lower Bound Cracking}: The terrifying realization that there is a physical, mathematical limit to how accurate the sensors can ever possibly be, no matter how much money is spent on them.
\item \textbf{Probability Density Curvature}: The mapping of the "shape" of the sensor noise, revealing hidden, dangerous patterns lurking inside the seemingly random static.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0921]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0921].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0921] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont FISHER INFORMATION METRIC (ACQUISITION)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} FISHER INFORMATION METRIC (ACQUISITION) is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``FISHER INFORMATION METRIC (ACQUISITION) is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0921].
\par\endgroup
\vfill
\endgroup
\endgroup
