\tzpanchor{0800}
\tzpentryheader{0800}{SO(3) times U(1) Configuration Bundle}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{034b4c49-358a-5dcc-988b-41b6e08db6d5}}\\
\textbf{PiID} & \tzpcode{5024459455346} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{807}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3067.7454 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.0547 rad}\\
\textbf{TZPID} & \tzpcode{ID0800} & \textbf{Node Dependencies}\quad \tzpidref{0799}\\
\textbf{Registry} & \tzpcode{registry\_id\_0800} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records so(3) times u(1) configuration bundle through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0800}}:\mathcal{X}_{\mathrm{id0800}}\longrightarrow\mathcal{Y}_{\mathrm{id0800}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0800}})=\mathcal{O}_{\mathrm{id0800}}
\]
\[
\mathcal{O}_{\mathrm{id0800}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0800}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0800}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0800}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0800 generated source Wolfram model *)
ClearAll[K0800, Cr0800, T, R, A, W, I, N];
eq0800$1 = HoldForm[Oid0800[Xid0800] -> Yid0800];
eq0800$2 = HoldForm[NTRAWIN[OId0800] == OId0800];
eq0800$3 = HoldForm[Element[OId0800[x], YAdm]];

K0800 = HoldForm[{eq0800$1, eq0800$2, eq0800$3}];

N = "normalized TRAWIN closure object for SO(3) times U(1) Configuration Bundle";
I = "SO(3) times U(1) Configuration Bundle integration/comparison layer";
W = "SO(3) times U(1) Configuration Bundle wave or operator carrier";
A = "SO(3) times U(1) Configuration Bundle admissible action/amplitude condition";
R = "SO(3) times U(1) Configuration Bundle rotation/curl preservation layer";
T = "SO(3) times U(1) Configuration Bundle local source condition";

Cr0800[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0800 = Cr0800[K0800];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ SO(3) times U(1) Configuration Bundle local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ SO(3) times U(1) Configuration Bundle rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ SO(3) times U(1) Configuration Bundle admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ SO(3) times U(1) Configuration Bundle wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ SO(3) times U(1) Configuration Bundle integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for SO(3) times U(1) Configuration Bundle.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0800] SO(3) times U(1) Configuration Bundle}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0800}}:\mathcal{X}_{\mathrm{id0800}}\longrightarrow \mathcal{Y}_{\mathrm{id0800}},\qquad
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0800}})=\mathcal{O}_{\mathrm{id0800}},\qquad
\mathcal{O}_{\mathrm{id0800}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

\paragraph{Primary Derivation.} The carrier of the entry is the id-specific bundle map.  Define\[
\mathcal{O}_{\mathrm{id0800}}:\mathcal{X}_{\mathrm{id0800}}\longrightarrow \mathcal{Y}_{\mathrm{id0800}}.
\]

The TRAWIN normalization acts as an internal compatibility projector:\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0800}})=\mathcal{O}_{\mathrm{id0800}}.
\]

Topological closure is obtained by requiring every admissible input to land inside the allowed target class:\[
\mathcal{O}_{\mathrm{id0800}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

Thus the Nonary derivation for [ID 0800] is the three-stage passage
\[
\mathcal{X}_{\mathrm{id0800}}\xrightarrow{\,\mathcal{O}_{\mathrm{id0800}}\,} \mathcal{Y}_{\mathrm{id0800}}\xrightarrow{\,\mathcal{N}_{\mathrm{TRAWIN}}\,} \mathcal{Y}_{\mathrm{adm}},
\]
with the entry title fixing the meaning of the carrier and the TRAWIN normalization fixing the admissibility test.

\paragraph{Interpretation.} SO(3) times U(1) Configuration Bundle is therefore treated as a stable carrier: it can transport the Nonary state only when its bundle map is normalized and its output remains inside the admissible target geometry.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors SO(3) times U(1) Configuration Bundle by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0800}}:\mathcal{X}_{\mathrm{id0800}}\longrightarrow\mathcal{Y}_{\mathrm{id0800}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0800}})=\mathcal{O}_{\mathrm{id0800}}
\]
\[
\mathcal{O}_{\mathrm{id0800}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0800] SO(3) times U(1) Configuration Bundle}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
SO(3) times U(1) Configuration Bundle is a registry definition in Resonance and Phase Locking with secondary pressure from Biological and Biomolecular Analogies.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} B=nablax A. \textbf{Contextual meaning:} The entry reads SO(3) times U(1) Configuration Bundle as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Geometric Carrier; Compatibility Law; Topological Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, SO(3) times U(1) Configuration Bundle is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: vec p sub i,k = RadialDepth i k dot SphericalVec i; Torus = S to the power 1 times S to the power 1; and [ vec p sub i,k = RadialDepth i k dot SphericalVec i Each axis SphericalVec i corresponds to a projection of a generati. Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Hopf-Fibration Twisted Geometry}: The mind-bending realization that the 3D surface of the sphere isn't actually flat; it is entirely made out of an infinite number of perfectly nested, unbreakable, interlocking circles.
\item \textbf{Magnetic Monopole Charge Mapping}: The use of this twisted, circular geometry to perfectly describe the weird, impossible shape of the magnetic field that would be generated by a magnet that only had a North pole.
\item \textbf{Global-to-Local Topological Bridging}: The massive mathematical effort to prove that the tiny, invisible twists happening on the surface of a single atom are exactly, flawlessly mirroring the grand, sweeping shape of the entire reactor chamber.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0800]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0800].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0800] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont SO(3) times U(1) Configuration Bundle}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} SO(3) times U(1) Configuration Bundle is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``SO(3) times U(1) Configuration Bundle is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0800].
\par\endgroup
\vfill
\endgroup
\endgroup
