\section*{ID8865: PLANETARY SPIN-ORBIT OSCILLATOR Canonical Statutory Formula: θ I}
\paragraph{Metadata.}
PiID: 0414263639548 | RTEID: RTE:P34424.7637:T0.1728 | UUID: 06a97df3-da92-53bb-b4b8-6a36f28546dd

\paragraph{Canonical Statement.}
[ID 1004] PLANETARY SPIN-ORBIT OSCILLATOR Canonical Statutory Formula: \$\textbackslash{}dot\{\textbackslash{}theta\} i = \textbackslash{}omega\_i + \textbackslash{}frac\{k\_0\}\{N\} \textbackslash{}sum K \{ij\} \textbackslash{}sin(\textbackslash{}theta\_j - \textbackslash{}theta\_i) - D\_i \textbackslash{}dot\{\textbackslash{}theta\} i + \textbackslash{}tau \{tidal\}\$ Formal Technical Dissertation: Models planetary bodies as coupled phase oscillators. It augments the Kuramoto model with spin-orbit torques and tidal dissipation to predict resonance capture ratios (e.g., Mercury's 3:2 lock). Source: [6], [7]

\paragraph{Canonical Equation.}
\[
\dot{\theta} i = \omega_i + \frac{k_0}{N} \sum K {ij} \sin(\theta_j - \theta_i) - D_i \dot{\theta} i + \tau {tidal}
\]

\paragraph{Dictionary.}
PLANETARY SPIN-ORBIT OSCILLATOR Canonical Statutory Formula: \$ i = \_i + k\_0N K ij ( \_j - \_i) - D\_i i + tidal\$ Formal Technical Dissertation: Models planetary bodies as coupled phase oscillators.

\paragraph{Encyclopedia.}
PLANETARY SPIN-ORBIT OSCILLATOR Canonical Statutory Formula: θ I is a series / summation, written θ i = ω\_i + (k\_0)/(N) ∑ K ij sin(θ\_j - θ\_i) - D\_i θ i + τ tidal. It is expressed as a sum or series over modes or indices, superposing discrete contributions. It is built from θ, τ, k\_0, N, K, j, defining θ i. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
