\section*{ID8810: CONSTRAINT POTENTIAL (MECHANICAL) Canonical Statutory Formula: U\_constraint}
\paragraph{Metadata.}
PiID: 7247162591668 | RTEID: RTE:P34211.1865:T6.1040 | UUID: 4eb83288-9fee-556a-bf44-5190aa14b6c2

\paragraph{Canonical Statement.}
[ID 1126] CONSTRAINT POTENTIAL (MECHANICAL) Canonical Statutory Formula: \$U\_\{constraint\} = \textbackslash{}frac\{K\_\{bolt\}\}\{2\}(d(t)-d\_\{bolt\})\textasciicircum{}\{2\} + V\_\{bearing\}[\textbackslash{}omega\_\{gyro\}]\$ Formal Technical Dissertation: Models the physical limitations of the hardware. \$K\_\{bolt\}\$ represents the stiffness of the connecting mechanism (approx \$10\textasciicircum{}9\$ N/m), and \$V\_\{bearing\}\$ accounts for viscous damping proportional to \$\textbackslash{}omega\textasciicircum{}2\$. Source: [4]

\paragraph{Canonical Equation.}
\[
U_{constraint} = \frac{K_{bolt}}{2}(d(t)-d_{bolt})^{2} + V_{bearing}[\omega_{gyro}]
\]

\paragraph{Dictionary.}
CONSTRAINT POTENTIAL (MECHANICAL) Canonical Statutory Formula: \$U\_constraint = K\_bolt2(d(t)-d\_bolt)\textasciicircum{}2 + V\_bearing[ \_gyro]\$ Formal Technical Dissertation: Models the physical limitations of the hardware.

\paragraph{Encyclopedia.}
CONSTRAINT POTENTIAL (MECHANICAL) Canonical Statutory Formula: U\_constraint is an algebraic definition, written U\_constraint = fracK\_bolt2(d(t)-d\_bolt)\textasciicircum{}2 + V\_bearing[ω\_gyro]. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from K\_bolt, d\_bolt, V\_bearing, g, y, r, defining U\_constraint. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
