\section*{ID6986: Important Inequality / Physical Intuition: (σ\_emN\_e - σ\_abs(N\_d-N\_e))}
\paragraph{Metadata.}
PiID: 1602876496286 | RTEID: RTE:P27128.1894:T0.7166 | UUID: 42de66b1-ef0e-5801-81d6-6bfa3f973b29

\paragraph{Canonical Statement.}
Stimulated gain term sign is controlled by \textbackslash{}((\textbackslash{}sigma\_\textbackslash{}text\{em\}N\_e - \textbackslash{}sigma\_\textbackslash{}text\{abs\}(N\_d-N\_e))\textbackslash{}). If that term becomes **positive**, net stimulated emission > absorption and photons can grow rapidly. For equal cross-sections this requires \textbackslash{}(N\_e > N\_d/2\textbackslash{}) (i.e., inversion), which is typically *not* the mechanism for photon BEC experiments — they instead rely on thermalization + chemical potential effects so you can get macroscopic ground-mode occupation without inversion. So don’t fixate on inversion; instead aim to make thermalization faster than loss (i.e., increase τ\_c or lower loss and/or increase thermalization rates).

\paragraph{Canonical Equation.}
\[
(\sigma_\text{em}N_e - \sigma_\text{abs}(N_d-N_e))
\]

\paragraph{Dictionary.}
Stimulated gain term sign is controlled by \textbackslash{}(( \_emN\_e - \_abs(N\_d-N\_e))\textbackslash{}).

\paragraph{Encyclopedia.}
Important Inequality / Physical Intuition: (σ\_emN\_e - σ\_abs(N\_d-N\_e)) is a symbolic expression, written (σ\_emN\_e - σ\_abs(N\_d-N\_e)). It introduces a symbol or relation used elsewhere in the framework. It is built from N\_e, N\_d. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
