\section*{ID9295: Definition of Res}
\paragraph{Metadata.}
PiID: 4680122482611 | RTEID: RTE:P36094.5492:T2.9240 | UUID: 966edc19-c0d0-5136-ad94-16e61fcf065b

\paragraph{Canonical Statement.}
tistics across quantum and macroscopic systems. Falsifiability / Test Handle: Measure cascade size distributions in candidate systems (e.g., wavefront avalanches, metamaterial transitions); confirm the predicted 3/23/2 exponent and exponential cutoff; deviation from this law would falsify universality. 3.0.47 ID 396: Beat Frequency Resonance and Information Density Type: Structural Constraint Formal Statement: The tripartite channel architecture predicts that resonant beat frequencies occur at \$res=0,fres=f0α,\$ where 0f0 is a base frequency and \$α\$ is the finestructure constant. Each measurement across the channels yields an information density of \$log2(153,600)≈17.23log2(153,600)≈17.23\$ bits. Interpretive Meaning: This constraint links fundamental constants to observable resonances and quantifies the information conveyed per measurement. It ties the DAANSphere’s 153,600point structure to practical Ca

\paragraph{Canonical Equation.}
\[
res=0,fres=f0α,
\]

\paragraph{Dictionary.}
Definition of Res — res=0,fres=f0α

\paragraph{Encyclopedia.}
Definition of Res is an algebraic definition, written res=0,fres=f0α. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from f, r, s, defining res. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
