\section*{ID9131: Definition of S(L,T,B,ρ)}
\paragraph{Metadata.}
PiID: 0766514793942 | RTEID: RTE:P35457.7008:T1.8747 | UUID: 04db2103-8635-5e28-bd2b-e9b6bb831e32

\paragraph{Canonical Statement.}
transformations preserving symplectic structure; informs algorithmic gravitational causation. Falsifiability / Test Handle: Detection of phase space compression or expansion violating symplectic preservation would falsify this constraint. 0.0.96 ID 094: Scaling Functor Between Laboratory and Astrophysical Systems Type: Structural Constraint Formal Statement: The scaling functor SSS maps physical quantities \$(L,T,B,ρ)(L,T,B,\textbackslash{}rho)(L,T,B,ρ)\$ in laboratory systems to astrophysical quantities via \$S(L,T,B,ρ)=(λL,λpT,λqB,λrρ)S(L,T,B,\textbackslash{}rho)=(\textbackslash{}lambda\$ Canonical Registry Vol. 01 32 Trawin Zero Point Contextus Canonicus L,\textbackslash{}lambdaˆp T,\textbackslash{}lambdaˆq B,\textbackslash{}lambdaˆr \$\textbackslash{}rho)S(L,T,B,ρ)=(λL,λpT,λqB,λrρ),\$ where exponents p,q,rp,q,rp,q,r ensure preservation of dimensionless numbers such as the magnetic Reynolds number and Alfvén Mach number. Interpretive Meaning: This defines how to rescale length, time, field strength and density to compare systems across sca

\paragraph{Canonical Equation.}
\[
S(L,T,B,ρ)=(λL,λpT,λqB,λrρ)S(L,T,B,\rho)=(\lambda
\]

\paragraph{Dictionary.}
Definition of S(L,T,B,ρ) — S(L,T,B,ρ)=(λL,λpT,λqB,λrρ)S(L,T,B,ρ)=(λ

\paragraph{Encyclopedia.}
Definition of S(L,T,B,ρ) is an algebraic definition, written S(L,T,B,ρ)=(λL,λpT,λqB,λrρ)S(L,T,B,ρ)=(λ. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from ρ, λ, L, p, T, q, defining S(L,T,B,ρ). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
