\tzpanchor{0014}
\tzpentryheader{0014}{Inter-Modal Transfer Rate}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{5c8266b5-1da5-54ca-aeb9-2932093c3236}}\\
\textbf{PiID} & \tzpcode{3238462643383} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{21}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{54.3651 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.0896 rad}\\
\textbf{TZPID} & \tzpcode{ID0014} & \textbf{Node Dependencies}\quad \tzpidref{0006}\\
\textbf{Registry} & \tzpcode{registry\_id\_0014} & \textbf{Scale}\quad modal-transfer\\
\textbf{LOC Classification} & QC670 modal interaction & QA431 integral operators\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: math-ph, cond-mat.stat-mech & \\
\textbf{Primary Support} & Mode-to-Mode Coupling Integral & Base-Unit Scaling\\
\textbf{Closure Support} & Away-from-TZP Hypersurface Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The inter-modal transfer rate measures how strongly one field mode feeds another when weighted by the Trawinistic Lagrangian density and normalized by the base unit. It is the registry's first explicit bridge between modal decomposition and normalized transport.

\tzpsection{Canonical Equation}
\[
T_{\mathrm{IM}}
=
\frac{1}{u_{T}}
\int_{\Sigma}
\phi_{m_{1}}^{*}\,
\mathcal{L}_{T}\,
\phi_{m_{2}}\,
d\Sigma
\]
\[
\Sigma \cap \{p\} = \varnothing
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $T_{\mathrm{IM}}$: source equation symbol.
    \item $u_{T}$: source equation symbol.
    \item $T$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $m_{1}$: source equation symbol.
    \item $\mathcal{L}_{T}$: source equation symbol.
    \item $m_{2}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0014 generated source Wolfram model *)
ClearAll[K0014, Cr0014, T, R, A, W, I, N];
eq0014$1 = HoldForm[TIM == (1/uT)*IntegralSigma*phiM1*DaggerLT*phiM2dSigma];
eq0014$2 = HoldForm[Sigmacap*{p} == varnothing];
eq0014$3 = HoldForm[IntegralSigma*phiM1*DaggerLTphiM2dSigma];
eq0014$4 = HoldForm[TIM == (1/uT)*IntegralSigma*phiM1*DaggerLTphiM2dSigma];

K0014 = HoldForm[{eq0014$1, eq0014$2, eq0014$3, eq0014$4}];

N = "normalized TRAWIN closure object for Inter-Modal Transfer Rate";
I = "Away-from-TZP Hypersurface Condition integration/comparison layer";
W = "Base-Unit Scaling wave or operator carrier";
A = "Mode-to-Mode Coupling Integral admissible action/amplitude condition";
R = "Base-Unit Scaling rotation/curl preservation layer";
T = "Mode-to-Mode Coupling Integral local source condition";

Cr0014[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0014 = Cr0014[K0014];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Mode-to-Mode Coupling Integral local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Base-Unit Scaling rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Mode-to-Mode Coupling Integral admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Base-Unit Scaling wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Away-from-TZP Hypersurface Condition integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Inter-Modal Transfer Rate.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0014] Inter-Modal Transfer Rate}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
T_{\mathrm{IM}}
=
\frac{1}{u_T}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi_{m_1}$ and $\phi_{m_2}$ be modal states over the hypersurface $\Sigma$.  
Let $\mathcal{L}$ be the transfer operator.

The transfer amplitude from mode $m_2$ into mode $m_1$ is:

\begin{equation}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
\end{equation}

Because the Trawin base unit $u_T$ defines the primitive loop scale of the system, the normalized transfer rate is:

\begin{equation}
\boxed{
T_{\mathrm{IM}}
=
\frac{1}{u_T}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
}
\end{equation}

\paragraph{Interpretation.}
ID 0014 repeats and stabilizes the inter-modal transfer structure introduced earlier, now explicitly as a transfer rate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Inter-Modal Transfer Rate by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Mode-to-Mode Coupling Integral}\par
\[
\int_{\Sigma}
\phi_{m_{1}}^{*}\mathcal{L}_{T}\phi_{m_{2}}\, d\Sigma
\]
\noindent This captures the raw interaction strength between two field modes before any normalization is applied.\par
\noindent\textbf{2. Base-Unit Scaling}\par
\[
T_{\mathrm{IM}}
=
\frac{1}{u_{T}}
\int_{\Sigma}
\phi_{m_{1}}^{*}\mathcal{L}_{T}\phi_{m_{2}}\, d\Sigma
\]
\noindent This turns the interaction strength into a dimensionless transfer rate tied to the internal Trawin scale.\par
\noindent\textbf{3. Away-from-TZP Hypersurface Condition}\par
\[
\Sigma \cap \{p\} = \varnothing
\]
\noindent This closes the progression by ensuring the transfer rate is computed on a regular hypersurface rather than contaminated by unresolved singular contact.\par

\clearpage
\noindent\textbf{[ID 0014] Inter-Modal Transfer Rate}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Inter Modal Transfer Rate label id-014-intermodal-transfer-rate is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} T sub IM = ratio 1 u sub T integral sub Sigma phi sub m sub 1 to the power * L phi sub m sub 2 d Sigma,. \textbf{Contextual meaning:} The entry reads Inter Modal Transfer Rate label id-014-intermodal-transfer-rate as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Mode-to-Mode Coupling Integral; Base-Unit Scaling; Away-from-TZP Hypersurface Condition.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
ID 0014 repeats and stabilizes the inter-modal transfer structure introduced earlier, now explicitly as a transfer rate.

\tzpsection{Equation Grounding}
Equation anchors: T sub IM ;= ; ratio 1 u sub T integral sub Sigma phi sub m sub 1 to the power * , L , phi sub m sub 2 , d Sigma, T sub IM ;= ; ratio 1 u sub T integral sub Sigma phi sub m sub 1 to the power * , L , phi sub m sub 2 , d Sigma,.

\tzpsection{Interpretive Role}
This operator provides a normalized rate for resonance, coupling, and decoherence analyses. It is the natural transport object once fields have been decomposed into coherent modal components.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Inter Modal Transport Rate Label}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Transport Transport Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Transport Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0014]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0014_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0014] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Inter-Modal Transfer Rate}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the inter-modal transfer rate measures how strongly one field mode feeds another when
weighted by the Trawinistic Lagrangian density and normalized...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Inter‑Modal Transfer Rate is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that the inter-modal transfer rate measures how strongly one
field mode feeds another when weighted by the Trawinistic Lagrangian density and
normalized by the base unit. It is the registry's first explicit bridge between modal
decomposition and normalized transport. ID 0014 repeats and stabilizes the inter-modal
transfer structure introduced earlier, now explicitly as a transfer rate.. The CHL
validation treats the equation as the formal anchor and the semantic text as the
interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0014_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
