\section*{ID9230: Relation: Sobs(ω,k)S\_obs(ω,k)Sobs(ω,k)}
\paragraph{Metadata.}
PiID: 8070576561514 | RTEID: RTE:P35842.1398:T2.5082 | UUID: a1702b1b-e45d-591b-bc51-72defe35f1fa

\paragraph{Canonical Statement.}
helicity remains constant despite dynamic evolution, preserving the memory of initial field configurations. (3) Links macroscopic rotations with microscopic KK contributions. Falsifiability / Test Handle: Numerically evolve coupled magnetoacousticKK systems and monitor HtotalH\_\{\textbackslash{}text\{total\}\}Htotal; deviations from conservation indicate nonideal effects or missing contributions. 2.0.168 ID 317: Reverse Harmonic Decomposition Algorithm Type: Operator Formal Statement: Given an observed spectrum \$Sobs(ω,k)S\_\{\textbackslash{}text\{obs\}\}(\textbackslash{}omega,k)Sobs(ω,k),\$ generate a mode table TTT, measure helicity HobsH\_\{\textbackslash{}text\{obs\}\}Hobs, and for each resonance \$ωi\textbackslash{}omega\_iωi:\$ perform Canonical Registry Vol. 01 109 Trawin Zero Point Contextus Canonicus 2 TZP CANONICAL REGISTRY – ENTRIES 150–199 spherical harmonic transform to obtain (ni,i,mi)(n\_i,\textbackslash{}ell\_i,m\_i)(ni,i,mi); solve \$ωiωuncoupled(ni,i,mi)=miKKc/RKK\textbackslash{}omega\_i\$ - \textbackslash{}omega\_\{\textbackslash{}text\{uncoupled\}\}(n\_i,\textbackslash{}ell\_i,m\_i) = m

\paragraph{Canonical Equation.}
\[
Sobs(ω,k)S_{\text{obs}}(\omega,k)Sobs(ω,k),
\]

\paragraph{Dictionary.}
Relation: Sobs(ω,k)S\_obs(ω,k)Sobs(ω,k) — Sobs(ω,k)S\_obs(ω,k)Sobs(ω,k)

\paragraph{Encyclopedia.}
Relation: Sobs(ω,k)S\_obs(ω,k)Sobs(ω,k) is a symbolic expression, written Sobs(ω,k)S\_obs(ω,k)Sobs(ω,k). It introduces a symbol or relation used elsewhere in the framework. It is built from ω, S, o, b, s, k. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
