\tzpanchor{0281}
\tzpentryheader{0281}{Cosmological Entanglement and Information Metric on S\textsuperscript3}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e64feabd-2c3c-563a-b4e0-1761c5b0b222}}\\
\textbf{PiID} & \tzpcode{3393607260249} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{288}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1091.1854 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.7979 rad}\\
\textbf{TZPID} & \tzpcode{ID0281} & \textbf{Node Dependencies}\quad \tzpidref{0280}\\
\textbf{Registry} & \tzpcode{registry\_id\_0281} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Three-Sphere Topology & Entanglement Entropy\\
\textbf{Closure Support} & Information Metric & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A spatial three-sphere topology supports a global entangled state; from this entanglement one can derive an information metric on the DAANSphere that links quantum entanglement entropy to spacetime curvature.

\tzpsection{Canonical Equation}
\[
Sigma \cong S^3
\]
\[
S_{\mathrm{ent}} = -\mathrm{Tr}(\rho \log \rho)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S^3$: three-sphere source domain.
    \item $S_{\mathrm{ent}}$: source equation symbol.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\cong$: source equation symbol.
    \item $S$: source equation symbol.
    \item $T$: source equation symbol.
    \item $r$: global radius, boundary radius, or topological scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0281 generated source Wolfram model *)
ClearAll[K0281, Cr0281, T, R, A, W, I, N];
eq0281$1 = HoldForm[Sigmacong*S^3];
eq0281$2 = HoldForm[SEnt == -Tr[rholog*rho]];
eq0281$3 = HoldForm[g^info*_*ij == PartialI*PartialJ*SEnt];

K0281 = HoldForm[{eq0281$1, eq0281$2, eq0281$3}];

N = "normalized TRAWIN closure object for Cosmological Entanglement and Information Metric on S\textsuperscript3";
I = "Information Metric integration/comparison layer";
W = "Entanglement Entropy wave or operator carrier";
A = "Three-Sphere Topology admissible action/amplitude condition";
R = "Entanglement Entropy rotation/curl preservation layer";
T = "Three-Sphere Topology local source condition";

Cr0281[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0281 = Cr0281[K0281];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Three-Sphere Topology local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Entanglement Entropy rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Three-Sphere Topology admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Entanglement Entropy wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Information Metric integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Cosmological Entanglement and Information Metric on S\textbackslash{}textsuperscript3.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0281] Cosmological Entanglement and Information Metric on S\textsuperscript3}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
Classical emergence occurs when decoherence suppresses interference and pointer states evolve according to effective classical equations derived from the Trawinistic Hamiltonian.

\paragraph{Primary Condition.}
\begin{equation}
\rho_{ij}(t)\rightarrow 0
\qquad
(i\neq j).
\end{equation}

\paragraph{Primary Derivation.}
Let $\rho$ be a density matrix written in a pointer-state basis $\{|i\rangle\}$.  
The off-diagonal entries
\begin{equation}
\rho_{ij}
=
\langle i|\rho|j\rangle,
\qquad i\neq j,
\end{equation}
encode quantum interference between distinct pointer states.

Classical behavior emerges when these off-diagonal terms decay rapidly:
\begin{equation}
\rho_{ij}(t)\rightarrow 0
\qquad
(i\neq j).
\end{equation}

The remaining diagonal entries behave as an effective classical probability distribution:
\begin{equation}
p_i(t)=\rho_{ii}(t).
\end{equation}

Thus the quantum state becomes approximately classical in the pointer basis:
\begin{equation}
\boxed{
\rho(t)
\longrightarrow
\sum_i p_i(t)|i\rangle\langle i|.
}
\end{equation}

\paragraph{Interpretation.}
Classical behavior is obtained when interference is suppressed and the pointer-state probabilities dominate the observable dynamics.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Cosmological Entanglement and Information Metric on S\textbackslash{}textsuperscript3 by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Three-Sphere Topology}\par
\[
Sigma \cong S^3
\]
\noindent This fixes the three-sphere carrier topology used by the cosmological state.\par
\noindent\textbf{2. Entanglement Entropy}\par
\[
S_{\mathrm{ent}} = -\mathrm{Tr}(\rho \log \rho)
\]
\noindent This identifies the entanglement entropy of the global state.\par
\noindent\textbf{3. Information Metric}\par
\[
g^{\mathrm{info}}_{ij} = \partial_i \partial_j S_{\mathrm{ent}}
\]
\noindent This closes the entry by deriving the information metric from entropy variation.\par

\clearpage
\noindent\textbf{[ID 0281] Cosmological Entanglement and Information Metric on S\textsuperscript3}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Cosmological Entanglement and Information Metric on Stextsuperscript3 is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A spatial three-sphere topology supports a global entangled state; from this entanglement one can derive an information metric on the DAANSphere that links quantum entanglement entropy to spacetime curvature. \textbf{Contextual meaning:} The entry reads Cosmological Entanglement and Information Metric on Stextsuperscript3 as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the S3-to-entropy-to-metric chain explicitly, which is the core mathematics of the page. \textbf{Lemma support:} Three-Sphere Topology; Entanglement Entropy; Information Metric.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Classical behavior is obtained when interference is suppressed and the pointer-state probabilities dominate the observable dynamics.

\tzpsection{Equation Grounding}
Equation anchors: Sigma cong S to the power 3; S sub ent = - Tr (rho log rho); and g to the power info sub ij = partial sub i partial sub j S sub ent. Proof route: show that a global entangled state on the three-sphere induces the stated information metric through entropy variation. Formalization route: prove that the entanglement entropy on the S3 carrier yields the stated second-variation information metric.

\tzpsection{Interpretive Role}
The entry now states the S3-to-entropy-to-metric chain explicitly, which is the core mathematics of the page.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Hyperspherical Universe Information Density}: The calculation of the total amount of quantum information that can be encoded in the entire volume of a finite, hyperspherical universe.
\item \textbf{Entropy of Global Spacetime Correlations}: The measurement of how strongly every particle in the universe is quantum mechanically linked to every other particle across cosmic distances.
\item \textbf{Topological Bounding of Cosmic Entanglement}: The theoretical limit dictating that the total quantum entanglement of the universe is strictly capped by the absolute curvature and volume of the cosmos.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0281]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0281_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0281] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Cosmological Entanglement and Information Metric on S\textsuperscript3}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a spatial three-sphere topology supports a global entangled state; from this
entanglement one can derive an information metric on the DAANSphere th...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Cosmological Entanglement and Information Metric on S³ is valid as a tensorial/geometric
statement when the stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0281_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
