\section*{ID8650: Torus Curvature Ratio: in Differential Geometry, Consider a Torus (Doughnut Shape)…}
\paragraph{Metadata.}
PiID: 9748442360800 | RTEID: RTE:P33589.8710:T5.0803 | UUID: f3da8280-fb65-53a4-984d-d4866bc38941

\paragraph{Canonical Statement.}
• Torus Curvature Ratio: In differential geometry, consider a torus (doughnut shape) defined by a major radius \$R\$ (from center of hole to center of tube) and minor radius \$r\$ (tube radius). The Gaussian curvature on the outer equator \$(\$\textbackslash{}backslash phi=0\$)\$ is positive \$\$K\_\{\textbackslash{}backslash text\{outer\}\}=1/[R(R+r)]\$,\$ whereas on the inner equator ( \$(\$\textbackslash{}backslash phi=\textbackslash{}backslash pi\$)\$ it is negative \$K\_\{\textbackslash{}text\{inner\}\}=-1/[R(R-r)]\$. The ratio of magnitudes is \$SUfrac\{|K\_\{\textbackslash{}backslash text\{inner\}\}|\{K\_\{\textbackslash{}backslash text\{outer\}\}=\textbackslash{}backslash frac\{R+r\}\{,R-r,\}S\$. If we set \$\textbackslash{}frac\{R\}\{r\}\textbackslash{}approx2.46\$, this curvature ratio becomes \$\textbackslash{}approx2.37037\$, which is 2x (two times 1.185185). In other words, a torus whose major radius is about 2.46 times its minor radius has an inner/outer curvature contrast of 237.037\%, exactly double the 118.5\% factor. This is a striking geometrical realization of the number: \$\textbackslash{}chi \textbackslash{}approx1.185\$ emerges as a "threshold" ratio distinguishing a moderately thick torus from a near-spherical

\paragraph{Canonical Equation.}
\[
K_{\backslash text{outer}}=1/[R(R+r)]$,$ whereas on the inner equator ( $($\backslash phi=\backslash pi$)$ it is negative $K_{\text{inner}}=-1/[R(R-r)]$. The ratio of magnitudes is $SUfrac{|K_{\backslash text{inner}}|{K_{\backslash text{outer}}=\backslash frac{R+r}{,R-r,}S$. If we set $\frac{R}{r}\approx2.46$, this curvature ratio becomes $\approx2.37037$, which is 2x (two times 1.185185). In other words, a torus whose major radius is about 2.46 times its minor radius has an inner/outer curvature contrast of 237.037%, exactly double the 118.5% factor. This is a striking geometrical realization of the number: $\chi \approx1.185$ emerges as a "threshold" ratio distinguishing a moderately thick torus from a near-spherical torus. (A very thin torus gives a curvature ratio near 1, while 2.37 marks a transition to a much more pronounced donut shape.) • Wave Modes and Half-Phases: The value 1.185 appears tantalizingly close to certain wave phenomena benchmarks. For example, the first zero of the Bessel function $J_0(x)$ occurs at $x\approx2.4048$, which is important in resonance of circular membranes and waveguides. Half of that value is
\]

\paragraph{Dictionary.}
Relation: K\_backslash textouter=1/[R(R+r)], whereas on the inner equator ( (backslash phi=backslash pi) it is negative K\_inner=-1/[R(R-r)]. The ratio of magnitu

\paragraph{Encyclopedia.}
Torus Curvature Ratio: in Differential Geometry, Consider a Torus (Doughnut Shape)… is a scaling / order-of-magnitude relation, written K\_backslash textouter=1/[R(R+r)], whereas on the inner equator ( (backslash phi=. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from χ, R, r, w, h, a, defining K\_backslash textouter. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
