\tzpanchor{0397}
\tzpentryheader{0397}{TZP Operator for Extraction and Collapse}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{8ef58272-4ce8-5d75-96d1-b729bb59e174}}\\
\textbf{PiID} & \tzpcode{0943305727036} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{404}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1541.6392 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.5401 rad}\\
\textbf{TZPID} & \tzpcode{ID0397} & \textbf{Node Dependencies}\quad \tzpidref{0396}\\
\textbf{Registry} & \tzpcode{registry\_id\_0397} & \textbf{Scale}\quad field-dynamical\\
\textbf{LOC Classification} & QC20.7 field theory & QA321 variational structure\\
\textbf{arXiv Classification} & Primary: hep-th & Cross-list: math-ph, gr-qc\\
\textbf{Primary Support} & Unified Density & Euler-Lagrange Flow\\
\textbf{Closure Support} & Stationary Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Define the local operator acting at a Trawin Zero Point by

\tzpsection{Canonical Equation}
\[ H_{\mathrm{TZP}} = \delta(r)\, \lvert \mathrm{TZP}\rangle\langle \mathrm{TZP}\rvert \times \bigl[ \mathrm{ZeroPointExtraction} + \mathrm{DimensionalCollapse} + \mathrm{InfiniteOrderTransition} \bigr]. \] The factor $\delta(r)$ localizes the operator at the singularity, while the bracketed terms govern vacuum-energy extraction, dimensional reduction, and the onset of an infinite-order phase transition.

\[
\mathcal{T}_{\mathrm{TZP}}:\rho\mapsto \Pi_{0}\rho\Pi_{0}
\]
\[
\dot{\rho}=-i[H,\rho]-\lambda(\rho-\Pi_{0}\rho\Pi_{0})
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H_{\mathrm{TZP}}$: source equation symbol.
    \item $\delta(r)$: point-source delta term that anchors the Green-function response.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\rho$: density or measure term used by the entry equation.
    \item $H$: source equation symbol.
    \item $\lambda$: cosmological or lemniscatic branch parameter in the entry relation.
    \item $\mathcal{S}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0397 generated source Wolfram model *)
ClearAll[K0397, Cr0397, T, R, A, W, I, N];
eq0397$1 = HoldForm[HTZP == DiracDelta[r]*KetBra[TZP, TZP]*(ZeroPointExtraction + DimensionalCollapse + InfiniteOrderTransition)];
eq0397$2 = HoldForm[TTZP[rho] -> Pi0rhoPi0];
eq0397$3 = HoldForm[dot[rho] == -i[H, rho] - lambda[rho - Pi0*rhoPi0]];
eq0397$4 = HoldForm[DiracDeltaS/DiracDeltarho == 0];

K0397 = HoldForm[{eq0397$1, eq0397$2, eq0397$3, eq0397$4}];

N = "normalized TRAWIN closure object for TZP Operator for Extraction and Collapse";
I = "Stationary Closure integration/comparison layer";
W = "Euler-Lagrange Flow wave or operator carrier";
A = "Unified Density admissible action/amplitude condition";
R = "Euler-Lagrange Flow rotation/curl preservation layer";
T = "Unified Density local source condition";

Cr0397[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0397 = Cr0397[K0397];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Unified Density local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Euler-Lagrange Flow rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Unified Density admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Euler-Lagrange Flow wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Stationary Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP Operator for Extraction and Collapse.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0397] TZP Operator for Extraction and Collapse}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Bridge Frequency.}
\begin{equation}
f_{\mathrm{bridge}}=\frac{32}{27}f_0.
\end{equation}

\paragraph{Bridge Waveform.}
\begin{equation}
\Psi_{\mathrm{bridge}}(t)
=
G_{\sigma}(t)
\left[
\cos(2\pi f_1t)
-
\cos(2\pi f_2t+\theta)
\right].
\end{equation}

\paragraph{Primary Derivation.}
Let $f_0$ be a shared base frequency.  
The bridge frequency is fixed by:

\begin{equation}
f_{\mathrm{bridge}}=\frac{32}{27}f_0.
\end{equation}

A localized bridge is created by applying a Gaussian window $G_\sigma(t)$ to a flipped and twisted carrier pair:

\begin{equation}
\boxed{
\Psi_{\mathrm{bridge}}(t)
=
G_{\sigma}(t)
\left[
\cos(2\pi f_1t)
-
\cos(2\pi f_2t+\theta)
\right].
}
\end{equation}

\paragraph{Interpretation.}
The flip--twist transform creates a localized beat-and-cancellation bridge from paired carriers.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP Operator for Extraction and Collapse by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Unified Density}\par
\[
\mathcal{T}_{\mathrm{TZP}}:\rho\mapsto \Pi_{0}\rho\Pi_{0}
\]
\noindent This gathers the sectors that the quaternary arc is trying to hold in one variational frame.\par
\noindent\textbf{2. Euler-Lagrange Flow}\par
\[
\dot{\rho}=-i[H,\rho]-\lambda(\rho-\Pi_{0}\rho\Pi_{0})
\]
\noindent This turns the density into an actual field law rather than a formal sum.\par
\noindent\textbf{3. Stationary Closure}\par
\[
\delta\mathcal{S}/\delta\rho=0
\]
\noindent This closes the entry by imposing stationary admissibility on the total action.\par

\clearpage
\noindent\textbf{[ID 0397] TZP Operator for Extraction and Collapse}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP Operator for Extraction and Collapse is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Define the local operator acting at a Trawin Zero Point by H sub TZP = delta(r) lvert TZP TZP rvert times bigl[ ZeroPointExtraction + DimensionalCollapse + InfiniteOrderTransition bigr]. The factor delta(r) localizes the operator at the singularity, while the bracketed terms govern vacuum-energy extraction, dimensional reduction, and the onset of an infinite-order phase transition. \textbf{Contextual meaning:} The entry reads TZP Operator for Extraction and Collapse as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry supplies the book with a true unification density, so later extraction and dynamo pages can be read as sectoral consequences of one action. \textbf{Lemma support:} Unified Density; Euler-Lagrange Flow; Stationary Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The flip--twist transform creates a localized beat-and-cancellation bridge from paired carriers.

\tzpsection{Equation Grounding}
Equation anchors: Port = 8099; Handoff = Join-Path; and Inbox = Join-Path. Proof route: show that the joined density yields a coherent Euler-Lagrange system whose sectoral terms remain admissible under TRAWIN normalization. Formalization route: prove that stationarity of the unified action implies the stated field equation.

\tzpsection{Interpretive Role}
The entry supplies the book with a true unification density, so later extraction and dynamo pages can be read as sectoral consequences of one action.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Target-State Annihilation Mapping}: The mathematical command that completely crushes the complex, evolving system down into a single, inescapable end state.
\item \textbf{Commutator-Driven Phase Drift}: The specific part of the collapse equation driven by the quantum mechanical interference between the system's different moving parts.
\item \textbf{Stationary Action Minimization}: The proof that this extreme collapse represents the system finding its absolute lowest, most stable, and unmoving energy configuration.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0397]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0397_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0397] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP Operator for Extraction and Collapse}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} define the local operator acting at a Trawin Zero Point by \textbackslash{}[ H\_TZP = (r) TZP TZP

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP Operator for Extraction and Collapse is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0397_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
