\section*{ID9431: Definition of Φ𝑛 |𝜕Ω}
\paragraph{Metadata.}
PiID: 4357846878861 | RTEID: RTE:P36622.6674:T3.7942 | UUID: 8cbddedf-c4ed-52da-8f59-4507fe448a36

\paragraph{Canonical Statement.}
cate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0407], [ID 0400] Node registry\_id\_0408 Support Titles Mode Quantization; Dispersion Law; Boundary Condition Test Handle If the resonance pattern cannot be organized into bounded modes with the stated boundary condition, the entry fails. Canonical Equation Links \$Ξcym= ∫ Ω Φ𝑛𝜌vac\$ 𝑑𝑉 \$Φ𝑛 |𝜕Ω=0\$ Aadm \$(Ξcym\$ )=1 [ID 0409] THE SUPERCONDUCTING PAIR CREATION OPERATOR (ℎ𝑎𝑡𝐻𝑆𝐶) TZPID ID0409 UUID 5c6dc21e-7947-5b67-a339-8920af06fb70 Type Operator / Transfer Statement Scale transfer LOC Classification Working routing: QA329 operator theory; QA169 categorical structure arXiv Classification Primary: math.CT; Cross-list: math-ph, cs.LO Canonical Statement This entry develops the superconducting p

\paragraph{Canonical Equation.}
\[
Φ𝑛 |𝜕Ω=0
\]

\paragraph{Dictionary.}
Definition of Φ𝑛 |𝜕Ω — Φ𝑛 |𝜕Ω=0

\paragraph{Encyclopedia.}
Definition of Φ𝑛 |𝜕Ω is an algebraic definition, written Φ𝑛 |𝜕Ω=0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
