\section*{ID7530: Quick Interpretation — What the Results Show: a\_rm DSS}
\paragraph{Metadata.}
PiID: 8607648236341 | RTEID: RTE:P29240.6622:T4.1973 | UUID: 1d4bc430-c54e-522d-81f3-570928adf709

\paragraph{Canonical Statement.}
\# Quick interpretation — what the results show 1. **DAT-GPT Synchronization Sphere (DSS)** - The analytic \textbackslash{}(a\_\{\textbackslash{}rm DSS\}\textbackslash{}) from the DAT-GPT timescale formula has an extremely strong dependence on object radius (\textbackslash{}(R\textasciicircum{}5\textbackslash{})) and distance (\textbackslash{}(a\textasciicircum{}6\textbackslash{})). For **km-scale bodies** the Sun’s DSS is *many orders of magnitude smaller than the asteroid belt or Kuiper belt*. In other words: the Sun cannot tidally synchronize km-sized objects at 2–4 AU (asteroid belt) or at Kuiper distances within typical system lifetimes. This matches the physical intuition we encoded in the model: tidal torque scales like \textbackslash{}(R\textasciicircum{}5/a\textasciicircum{}6\textbackslash{}) and is negligible for small bodies at large distances. - Put plainly: **DDS ≪ belt radii** for small bodies — so tidal synchronizing power from the Sun is not the reason for non-accretion of the belts.

\paragraph{Canonical Equation.}
\[
a_{\rm DSS}
\]

\paragraph{Dictionary.}
Quick interpretation — what the results show 1.

\paragraph{Encyclopedia.}
Quick Interpretation — What the Results Show: a\_rm DSS is a symbolic expression, written a\_rm DSS. It introduces a symbol or relation used elsewhere in the framework. It is built from a\_ DSS. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
