\section*{ID8522: DIPOLE TOPOLOGICAL CONSTRAINT Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 1883999446974 | RTEID: RTE:P33092.8185:T4.2613 | UUID: 4e307763-1feb-507e-bf04-484e508174df

\paragraph{Canonical Statement.}
[ID 1149] DIPOLE TOPOLOGICAL CONSTRAINT Canonical Statutory Formula: \$U(d) \textbackslash{}propto \textbackslash{}frac\{\textbackslash{}mu\textasciicircum{}2\}\{d\textasciicircum{}3\} \textbackslash{}rightarrow \textbackslash{}infty \textbackslash{}text\{ as \} d \textbackslash{}rightarrow 0\$ Formal Technical Dissertation: Theorem 4. The "Dipole Constraint." It asserts that opposing field configurations cannot strictly annihilate due to the divergence of interaction energy at small separations, necessitating the formation of stable toroidal flux topologies. Source: ,

\paragraph{Canonical Equation.}
\[
U(d) \propto \frac{\mu^2}{d^3} \rightarrow \infty \text{ as } d \rightarrow 0
\]

\paragraph{Dictionary.}
DIPOLE TOPOLOGICAL CONSTRAINT Canonical Statutory Formula: \$U(d) \textasciicircum{}2d\textasciicircum{}3 as d 0\$ Formal Technical Dissertation: Theorem 4.

\paragraph{Encyclopedia.}
DIPOLE TOPOLOGICAL CONSTRAINT Canonical Statutory Formula is a scaling / order-of-magnitude relation, written U(d) ∝ (μ\textasciicircum{}2)/(d\textasciicircum{}3) arrow ∞ as d arrow 0. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from μ, U. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
