\tzpanchor{0134}
\tzpentryheader{0134}{Extended Bridge Frequency Sweep}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7d4ef0e3-8d2f-57fc-9873-8c26b86f9f49}}\\
\textbf{PiID} & \tzpcode{2231725359408} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{141}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{520.3518 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.8574 rad}\\
\textbf{TZPID} & \tzpcode{ID0134} & \textbf{Node Dependencies}\quad \tzpidref{0133}\\
\textbf{Registry} & \tzpcode{registry\_id\_0134} & \textbf{Scale}\quad smooth frequency interpolation in the window\\
\textbf{LOC Classification} & QA371 time-dependent oscillators & QC20 wave phenomena\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: nlin.PS, physics.class-ph & \\
\textbf{Primary Support} & Swept Ratio Law & Time-Dependent Bridge Frequency\\
\textbf{Closure Support} & Window Conditions & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Instead of a fixed bridging ratio, define the time-dependent ratio

\tzpsection{Canonical Equation}
\[ r(t) = 1 + (r_0 - 1) h(t) \] within the Gaussian window, where $h(t)$ is a smooth function. This sweeps the bridging frequency across a small range, enabling a continuous mapping between frequency states.

\[
r(t)=1+(r_0-1)h(t)
\]
\[
f_{\mathrm{bridge}}(t)=r(t)\,f_B'
\]
\[
h(t_0)=1,\qquad h(t\to\pm\infty)=0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $r_0$: source equation symbol.
    \item $f_{\mathrm{bridge}}(t)$: source equation symbol.
    \item $f_B$: source equation symbol.
    \item $t_0$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0134 generated source Wolfram model *)
ClearAll[K0134, Cr0134, T, R, A, W, I, N];
eq0134$1 = HoldForm[r[t] == 1 + (r0 - 1)*h[t]];
eq0134$2 = HoldForm[r[t] == 1 + (r0 - 1)*h[t]];
eq0134$3 = HoldForm[fBridge[t] == r[t]*Derivative[1][fB]];
eq0134$4 = HoldForm[TZPSequence[h[t0] == 1, h[t -> PlusMinusInfinity] == 0]];

K0134 = HoldForm[{eq0134$1, eq0134$2, eq0134$3, eq0134$4}];

N = "normalized TRAWIN closure object for Extended Bridge Frequency Sweep";
I = "Window Conditions integration/comparison layer";
W = "Time-Dependent Bridge Frequency wave or operator carrier";
A = "Swept Ratio Law admissible action/amplitude condition";
R = "Time-Dependent Bridge Frequency rotation/curl preservation layer";
T = "Swept Ratio Law local source condition";

Cr0134[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0134 = Cr0134[K0134];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Swept Ratio Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Time-Dependent Bridge Frequency rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Swept Ratio Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Time-Dependent Bridge Frequency wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Window Conditions integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Extended Bridge Frequency Sweep.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0134] Extended Bridge Frequency Sweep}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[ r(t) = 1 + (r_0 - 1) h(t) \] within the Gaussian window, where $h(t)$ is a smooth function. This sweeps the bridging frequency across a small range, enabling a continuous mapping between frequency states.

\[
r(t)=1+(r_0-1)h(t)
\]
\[
f_{\mathrm{bridge}}(t)=r(t)\,f_B'
\]
\[
h(t_0)=1,\qquad h(t\to\pm\infty)=0
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( f_{\mathrm{bridge}}(t)=r(t)\,f_B' \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. Interpreted through TRAWIN, the equation functions as the mapping carrier for the entry’s information content. Under CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Extended Bridge Frequency Sweep by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Swept Ratio Law}\par
\[
r(t)=1+(r_0-1)h(t)
\]
\noindent This turns the bridge ratio into a time-dependent interpolation.\par
\noindent\textbf{2. Time-Dependent Bridge Frequency}\par
\[
f_{\mathrm{bridge}}(t)=r(t)\,f_B'
\]
\noindent This carries the sweep directly into the bridge carrier itself.\par
\noindent\textbf{3. Window Conditions}\par
\[
h(t_0)=1,\qquad h(t\to\pm\infty)=0
\]
\noindent This closes the progression by requiring the sweep to be local and to relax back to the unswept state.\par

\clearpage
\noindent\textbf{[ID 0134] Extended Bridge Frequency Sweep}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Extended Bridge Frequency Sweep is a Operator. Instead of a fixed bridging ratio, define a time dependent ratio r(t) = 1 + (r  -- 1) h(t) within the Gaussian window, where h(t) is a smooth function. This sweeps the bridging frequency across a small range, enabling continuous mapping between frequency states.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Instead of a fixed bridging ratio, define a time dependent ratio r(t) = 1 + (r  -- 1) h(t) within the Gaussian window, where h(t) is a smooth function. This sweeps the bridging frequency across a small range, enabling continuous mapping between frequency states.
\textbf{Contextual meaning:} Sweeping the bridge ratio allows dynamic modulation of the mapping between carriers. It generalizes the bridge operator to a continuum of values.
\textbf{Derivable consequences:} Frequency modulation; adiabatic transitions between states; dynamic domain walls.
\textbf{Lemma support:} Instead of a fixed bridging ratio, define a time dependent ratio r(t) = 1 + (r  -- 1) h(t) within the Gaussian window, where h(t) is a smooth function. This sweeps the bridging frequency across a small range, enabling continuous mapping between frequency states.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Introduce local perturbations to a phase twisted signal and verify that the pattern persists; attempt global modifications to remove the defect. ID 134: Extended Bridge Frequency Sweep

\tzpsection{Equation Grounding}
Instead of a fixed bridging ratio, define a time dependent ratio r(t) = 1 + (r  -- 1) h(t) within the Gaussian window, where h(t) is a smooth function. This sweeps the bridging frequency across a small range, enabling continuous mapping between frequency states.

\tzpsection{Interpretive Role}
Sweeping the bridge ratio allows dynamic modulation of the mapping between carriers. It generalizes the bridge operator to a continuum of values.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Swept Ratio Law}: The conversion of the bridge ratio into a time-dependent interpolation.
\item \textbf{Time-Dependent Bridge Frequency}: The application of the sweep directly into the bridge carrier itself.
\item \textbf{Window Conditions}: The requirement for the sweep to be local and to relax back to the unswept state.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0134]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0134_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0134] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Extended Bridge Frequency Sweep}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} instead of a fixed bridging ratio, define the time-dependent ratio \textbackslash{}[ r(t) = 1 + (r\_0 -
1) h(t) \textbackslash{}] within the Gaussian window, where h(t) is a sm...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Extended Bridge Frequency Sweep is valid as a spectral relation when frequency, phase,
and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0134_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
