\section*{ID9059: Definition of Nˆa\_,bc∫NTa\_bcdnx}
\paragraph{Metadata.}
PiID: 6448246515187 | RTEID: RTE:P35178.1088:T1.4140 | UUID: e839db46-a566-5371-8340-be894ce46edd

\paragraph{Canonical Statement.}
haves; influences torsion localisation; ensures field equations remain covariant; controls regularisation of curvature. Falsifiability / Test Handle: Detection of metric noncompatibility away from the TZP would violate this constraint. 0.0.30 ID 028: Constraint: TZP Torsion Localisation Type: Structural Constraint Formal Statement: The torsion tensor \$T(∇T)T(\textbackslash{}nablaˆ\{\textbackslash{}text\{T\}\})T(∇T)\$ vanishes for all x 6=px \textbackslash{}neq px=p and satisfies \$∫\$ NTa\_bcdnx=Na\_bc\textbackslash{}int \{\textbackslash{}mathcal\{N\}\} T\{a\}\_\{,bc\},\textbackslash{}text\{d\}n x = \$Nˆ\{a\}\_\{,bc\}∫NTa\_bcdnx=Na\_bc\$ for any neighbourhood N\textbackslash{}mathcal\{N\}N containing ppp, where Na\_bcNˆ\{a\}\_\{,bc\}Na\_bc is a fixed finite tensor capturing torsion concentrated at the TZP. Interpretive Meaning: All torsion is localised at the zero point; outside this, spacetime is torsionfree. The integral condition quantifies the net torsion concentrated at ppp. Dependencies: ID 017 Derivable Consequences: Influences spinor transport;

\paragraph{Canonical Equation.}
\[
Nˆ{a}_{,bc}∫NTa_bcdnx=Na_bc
\]

\paragraph{Dictionary.}
Definition of Nˆa\_,bc∫NTa\_bcdnx — Nˆa\_,bc∫NTa\_bcdnx=Na\_bc

\paragraph{Encyclopedia.}
Definition of Nˆa\_,bc∫NTa\_bcdnx is an algebraic definition, written Nˆa\_,bc∫NTa\_bcdnx=Na\_bc. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from N, a\_b, c, defining Nˆa\_,bc∫NTa\_bcdnx. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
