\section*{ID8903: HELICAL TRANSFER FUNCTION (BERRY-SAGNAC) Canonical Statutory Formula: H\_m(Ω, T)}
\paragraph{Metadata.}
PiID: 9647669758318 | RTEID: RTE:P34572.3262:T0.4159 | UUID: 041acc15-2c43-5a1d-8d7a-cfb2325bdbf9

\paragraph{Canonical Statement.}
[ID 933] HELICAL TRANSFER FUNCTION (BERRY-SAGNAC) Canonical Statutory Formula: \$H\_m(\textbackslash{}Omega, t) = \textbackslash{}exp[i(\textbackslash{}omega\_m t + \textbackslash{}Phi\_m\textasciicircum{}\{Berry\} + \textbackslash{}Phi\_m\textasciicircum{}\{Sagnac\}(\textbackslash{}Omega))]\$ Formal Technical Dissertation: Models the phase accumulation of Orbital Angular Momentum (OAM) mode \$m\$ through the rotating helix. It incorporates a geometric Berry phase proportional to the golden ratio logarithm (\$2\textbackslash{}ln\textbackslash{}phi/\textbackslash{}pi\$) and a dynamic Sagnac phase dependent on rotation \$\textbackslash{}Omega\$, enabling mode-dependent multiplexing. Source: [5], [6]

\paragraph{Canonical Equation.}
\[
H_m(\Omega, t) = \exp[i(\omega_m t + \Phi_m^{Berry} + \Phi_m^{Sagnac}(\Omega))]
\]

\paragraph{Dictionary.}
HELICAL TRANSFER FUNCTION (BERRY-SAGNAC) Canonical Statutory Formula: \$H\_m( , t) = [i( \_m t + \_m\textasciicircum{}Berry + \_m\textasciicircum{}Sagnac( ))]\$ Formal Technical Dissertation: Models the phase accumulation of Orbital Angular Momentum (OAM) mode m through the rotating helix.

\paragraph{Encyclopedia.}
HELICAL TRANSFER FUNCTION (BERRY-SAGNAC) Canonical Statutory Formula: H\_m(Ω, T) is an algebraic definition, written H\_m(Ω, t) = exp[i(ω\_m t + Φ\_m\textasciicircum{}Berry + Φ\_m\textasciicircum{}Sagnac(Ω))]. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from Ω, m, B, r, y, S, defining H\_m(Ω, t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
