\section*{Q100 ID9004: Relation: Q\_T in Z}
\paragraph{Metadata.}
PiID: 9706953653494 | RTEID: RTE:P34964.5316:T1.0621 | UUID: 54ef30d6-52ed-5764-9ae5-ad23fb6c61dc

\paragraph{Semantic Queue.}
Status: batch003\_started; class: candidate\_real\_algebra\_segment; role: .

\paragraph{Canonical Statement.}
D 006] does not relax into a lower-energy, non-functional state. Within the Furiene Spindle, this persistence is the prerequisite for maintaining the 310\% Synergetic Gain over indefinite operational timescales. The mathematical core of ID 014 is the quantization of the Trawinistic Winding Number, \$Q\_T\$. This charge is calculated as the integral of the second Chern class (the Pontryagin density) over the entangled toroidal manifold \$T\textasciicircum{}2 \textbackslash{}times T\textasciicircum{}2\$. Because \$Q\_T\$ is restricted to integer values (\$Q\_T \textbackslash{}in \textbackslash{}mathbb\{Z\}\$), any infinitesimal perturbation of the field—such as thermal noise or mechanical vibration—is insufficient to trigger a transition to a different charge state. This "Topological Hard-Stop" creates an energy barrier that effectively "pins" the vacuum fluctuations to the nodal lattice. This is the rigorous proof for the Euler Stability Theorem ( \$\textbackslash{}chi=0\$ ) [ID 352]; since the hypercubic grid

\paragraph{Canonical Equation.}
\[
Q_T \in \mathbb{Z}
\]

\paragraph{Source Truth.}
See ../../tzp\_id/ID9004/ID9004.source\_truth.json and ../../tzp\_id/ID9004/ID9004.tex.
