\section*{ID9027: Relation: Mw∈T\_pM}
\paragraph{Metadata.}
PiID: 5443755890045 | RTEID: RTE:P35053.8457:T1.2093 | UUID: 44ad4402-2eff-54be-aec0-3f39adffaad6

\paragraph{Canonical Statement.}
t backaction; informs information flux calculations. Falsifiability / Test Handle: Observation of field configurations that violate the predicted coherence bounds (e.g., exceeding 1) would falsify this definition. 0.0.15 ID 013: Null Space Projection Type: Operator Formal Statement: The null space projection operator \$P\_null:T\_pM→T\_pMP\_\{\textbackslash{}text\{null\}\}:T\_p\$ M\textbackslash{}to T\_p \$MP\_null:T\_pM→T\_pM\$ is defined by P\_null(v)=vP\_\{\textbackslash{}text\{null\}\}(v)=vP\_null(v)=v if g(v,w)=0g(v,w)=0g(v,w)=0 for all \$w∈T\_pMw\textbackslash{}in\$ T\_p \$Mw∈T\_pM,\$ and P\_null(v)=0P\_\{\textbackslash{}text\{null\}\}(v)=0P\_null(v)=0 otherwise. Interpretive Meaning: This operator extracts the components of a tangent vector that lie in the null space of the degenerate metric at the TZP. It identifies directions in which the metric fails to provide a length. Dependencies: ID 004 Derivable Consequences: Appears in defining the Trawinistic Laplacian; allows decomposition of fields in

\paragraph{Canonical Equation.}
\[
Mw∈T_pM,
\]

\paragraph{Dictionary.}
Relation: Mw∈T\_pM — Mw∈T\_pM

\paragraph{Encyclopedia.}
Relation: Mw∈T\_pM is a symbolic expression, written Mw∈T\_pM. It introduces a symbol or relation used elsewhere in the framework. It is built from M, w, T\_p. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
