\section*{ID9083: Definition of W,PhiH}
\paragraph{Metadata.}
PiID: 4396582533754 | RTEID: RTE:P35271.3061:T1.5676 | UUID: b093ed56-c245-5453-aa18-f567399dc113

\paragraph{Canonical Statement.}
nsionless parameters; constrains parameter spaces in simulations; leads to universality classes. Falsifiability / Test Handle: Discovery of systems that systematically violate the critical value across scales would falsify this universality. 0.0.43 ID 041: Topological Helicity Quantisation Type: Definition Formal Statement: The magnetic helicity H= \$∫\$ VABd3xH=\textbackslash{}int\_\{V\} \textbackslash{}mathbf\{A\}\textbackslash{}cdot \textbackslash{}mathbf\{B\},\textbackslash{}text\{d\}ˆ3xH= \$∫\$ VABd3x is quantised in units of the Trawinistic winding number, i.e., \$H=wΦH\$ = \$w,\textbackslash{}PhiH=wΦ,\$ where \$Φ\textbackslash{}PhiΦ\$ is the magnetic flux through the lemniscatic loop. Interpretive Meaning: Magnetic helicity takes discrete values proportional to the winding number defined around the TZP. This quantisation persists across scales and ensures topological stability. Dependencies: ID 020, ID 037 Derivable Consequences: Constrains dynamo processes; links helicity to angular momentum generation; influe

\paragraph{Canonical Equation.}
\[
w,\PhiH=wΦ,
\]

\paragraph{Dictionary.}
Definition of W,PhiH — w,PhiH=wΦ

\paragraph{Encyclopedia.}
Definition of W,PhiH is an algebraic definition, written w,PhiH=wΦ. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from w, defining w,PhiH. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
