\section*{ID9259: Relation: ρ(r’)|r’|2,d3r’Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3r}
\paragraph{Metadata.}
PiID: 2073883778142 | RTEID: RTE:P35954.7532:T2.6937 | UUID: c652cfbe-461e-5d5b-96ea-28152d42a806

\paragraph{Canonical Statement.}
ility / Test Handle: Compute helicity in experiments or simulations of rotating magnets; verify invariance despite dynamic changes and confirm the contribution of the second term. 2.0.176 ID 325: Gravitomagnetic Coupling Term Type: Definition Formal Statement: In a rapidly rotating gyromagnetic system approaching relativistic tangential velocities, the gravitomagnetic field is \$Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3rB\_\{\textbackslash{}text\{gravitomagnetic\}\}(r)\$ = (2G/cˆ2) (\textbackslash{}omega \textbackslash{}times r)/rˆ3 \textbackslash{}int\_V \$\textbackslash{}rho(r’)|r’|2,d3r’Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3r,\$ where \$ρ(r)\textbackslash{}rho(r)ρ(r)\$ is the mass density. Interpretive Meaning: This term represents the coupling between rotation and gravity, analogous to the magnetic field produced by moving charges. It arises from general relativistic framedragging and indicates that rotating mass distributions can generate gravitomagnetic fields. Dependencies: IDs 322. Derivable Consequences: (1) Suggests that gyromagn

\paragraph{Canonical Equation.}
\[
\rho(r’)|r’|2,d3r’Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3r,
\]

\paragraph{Dictionary.}
Relation: ρ(r’)|r’|2,d3r’Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3r

\paragraph{Encyclopedia.}
Relation: ρ(r’)|r’|2,d3r’Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3r is an algebraic definition, written ρ(r’)|r’|2,d3r’Bgravitomagnetic(r)=(2G/c2)(ω×r)/r3∫Vρ(r)r2d3r. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from G, c, r, V, defining ρ(r’)|r’|2,d3r’Bgravitomagnetic(r). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
