\tzpanchor{0339}
\tzpentryheader{0339}{Weak-Field Flow Dynamics in Static Lattice}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{4d9ab9d9-22e3-5b85-8980-cace77639a74}}\\
\textbf{PiID} & \tzpcode{0917153643678} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{346}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1316.4123 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.1690 rad}\\
\textbf{TZPID} & \tzpcode{ID0339} & \textbf{Node Dependencies}\quad \tzpidref{0338}\\
\textbf{Registry} & \tzpcode{registry\_id\_0339} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Weak-Field Flow Equation & Diffusion Carrier\\
\textbf{Closure Support} & Potential Carrier & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Weak fields propagate through the static metamaterial lattice via diffusion modulated by spatial heterogeneity and pinned potentials.

\tzpsection{Canonical Equation}
\[
\partial_t\psi=-\nabla\cdot\!\left(D(x)\nabla\psi\right)+V(x)\psi
\]
\[
\mathbf{J}=-D(x)\nabla\psi
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $D$: source equation symbol.
    \item $V$: auxiliary target state or comparison variable.
    \item $J$: source equation symbol.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $\psi$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0339 generated source Wolfram model *)
ClearAll[K0339, Cr0339, T, R, A, W, I, N];
eq0339$1 = HoldForm[PartialTpsi == (-Grad)*(D[x]*Gradpsi) + V[x]*psi];
eq0339$2 = HoldForm[J == (-D[x])*Gradpsi];
eq0339$3 = HoldForm[PartialTpsi + Grad*J == V[x]*psi];

K0339 = HoldForm[{eq0339$1, eq0339$2, eq0339$3}];

N = "normalized TRAWIN closure object for Weak-Field Flow Dynamics in Static Lattice";
I = "Potential Carrier integration/comparison layer";
W = "Diffusion Carrier wave or operator carrier";
A = "Weak-Field Flow Equation admissible action/amplitude condition";
R = "Diffusion Carrier rotation/curl preservation layer";
T = "Weak-Field Flow Equation local source condition";

Cr0339[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0339 = Cr0339[K0339];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Weak-Field Flow Equation local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Diffusion Carrier rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Weak-Field Flow Equation admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Diffusion Carrier wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Potential Carrier integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Weak-Field Flow Dynamics in Static Lattice.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0339] Weak-Field Flow Dynamics in Static Lattice}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{\mathbf{B}^2}{2\mu}
=
\frac{1}{2}\rho(\Omega r)^2 .
\end{equation}

\paragraph{Primary Derivation.}
The magnetic energy density is:

\begin{equation}
u_B
=
\frac{\mathbf{B}^2}{2\mu}.
\end{equation}

The rotational kinetic energy density associated with angular velocity $\Omega$ at radius $r$ is:

\begin{equation}
u_{\Omega}
=
\frac{1}{2}\rho v^2 .
\end{equation}

Since tangential velocity is:

\begin{equation}
v=\Omega r,
\end{equation}

we obtain:

\begin{equation}
u_{\Omega}
=
\frac{1}{2}\rho(\Omega r)^2 .
\end{equation}

Equipartition requires:

\begin{equation}
\boxed{
\frac{\mathbf{B}^2}{2\mu}
=
\frac{1}{2}\rho(\Omega r)^2 .
}
\end{equation}

\paragraph{Interpretation.}
Magnetic--Coriolis equipartition identifies the balance point where magnetic field energy and rotational kinetic energy density match.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Weak-Field Flow Dynamics in Static Lattice by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Weak-Field Flow Equation}\par
\[
\partial_t\psi=-\nabla\cdot\!\left(D(x)\nabla\psi\right)+V(x)\psi
\]
\noindent This fixes the weak-field lattice-flow equation carried by the metamaterial background.\par
\noindent\textbf{2. Diffusion Carrier}\par
\[
\mathbf{J}=-D(x)\nabla\psi
\]
\noindent This requires a positive diffusion carrier across the spatially varying lattice.\par
\noindent\textbf{3. Potential Carrier}\par
\[
\partial_t\psi+\nabla\cdot\mathbf{J}=V(x)\psi
\]
\noindent This closes the entry by identifying the potential sector with the imposed meta-bit field profile.\par

\clearpage
\noindent\textbf{[ID 0339] Weak-Field Flow Dynamics in Static Lattice}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Weak-Field Flow Dynamics in Static Lattice is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Weak fields propagate through the static metamaterial lattice via diffusion modulated by spatial heterogeneity and pinned potentials. \textbf{Contextual meaning:} The entry reads Weak-Field Flow Dynamics in Static Lattice as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now presents the lattice-flow dynamics as a clean weak-field PDE instead of a corrupted extracted sentence. \textbf{Lemma support:} Weak-Field Flow Equation; Diffusion Carrier; Potential Carrier.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Magnetic--Coriolis equipartition identifies the balance point where magnetic field energy and rotational kinetic energy density match.

\tzpsection{Equation Grounding}
Equation anchors: partial sub tpsi = - abladot bigl(D(x) ablapsibigr)+V(x)psi; D(x)>0; and V(x)=V sub meta (x). Proof route: show that the stated weak-field lattice dynamics are well posed under positive diffusion and the imposed meta-bit potential. Formalization route: prove that positivity of the diffusion carrier preserves admissible evolution under the stated flow equation.

\tzpsection{Interpretive Role}
The entry now presents the lattice-flow dynamics as a clean weak-field PDE instead of a corrupted extracted sentence.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Isotropic Diffusion Transport}: The mathematical description of particle or energy spread through a uniform grid driven entirely by concentration gradients.
\item \textbf{Potential-Driven Drift}: The addition of a smooth background bias force guiding the overall direction of the random diffusion process.
\item \textbf{Linearized Field Propagation}: The approximation reducing complex, chaotic flow equations into a solvable system valid only for very small amplitudes.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0339]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0339_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0339] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Weak-Field Flow Dynamics in Static Lattice}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} weak fields propagate through the static metamaterial lattice via diffusion modulated by
spatial heterogeneity and pinned potentials

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Weak-Field Flow Dynamics in Static Lattice is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0339_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
