\section*{ID8875: METRIC FLUX DENSITY (GRAVITOMAGNETIC) Canonical Statutory Formula: B M}
\paragraph{Metadata.}
PiID: 5480004480026 | RTEID: RTE:P34463.5959:T0.2367 | UUID: 8ea3cb0a-bc65-52e5-8e69-7a0e7a7f3817

\paragraph{Canonical Statement.}
[ID 1025] METRIC FLUX DENSITY (GRAVITOMAGNETIC) Canonical Statutory Formula: \$\textbackslash{}mathbf\{B\} M = \textbackslash{}nabla \textbackslash{}times (M \{\textbackslash{}mu\textbackslash{}nu\} \textbackslash{}cdot u\textasciicircum{}\textbackslash{}nu) \textbackslash{}cdot \textbackslash{}chi\_T\$ Formal Technical Dissertation: Quantifies the "Metric Curl" or vorticity of spacetime induced by the rotating Furiene Spindle. It governs the conversion of mechanical torque into topological grip on the vacuum plenum. Source: [35]

\paragraph{Canonical Equation.}
\[
\mathbf{B} M = \nabla \times (M {\mu\nu} \cdot u^\nu) \cdot \chi_T
\]

\paragraph{Dictionary.}
METRIC FLUX DENSITY (GRAVITOMAGNETIC) Canonical Statutory Formula: \$B M = (M u\textasciicircum{} ) \_T\$ Formal Technical Dissertation: Quantifies the "Metric Curl" or vorticity of spacetime induced by the rotating Furiene Spindle.

\paragraph{Encyclopedia.}
METRIC FLUX DENSITY (GRAVITOMAGNETIC) Canonical Statutory Formula: B M is a differential equation, written B M = ∇ × (M μν · u\textasciicircum{}ν) · χ\_T. It relates the quantity to its derivatives, governing how the system evolves in space and time. It is built from ∇, μ, ν, M, u, T, defining B M. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
