\section*{ID7532: Quick Interpretation — What the Results Show: a\textasciicircum{}6}
\paragraph{Metadata.}
PiID: 0764823634143 | RTEID: RTE:P29248.4287:T4.2101 | UUID: 0ad3a9f0-f5a7-5039-b919-9e2f121d53c3

\paragraph{Canonical Statement.}
\# Quick interpretation — what the results show 1. **DAT-GPT Synchronization Sphere (DSS)** - The analytic \textbackslash{}(a\_\{\textbackslash{}rm DSS\}\textbackslash{}) from the DAT-GPT timescale formula has an extremely strong dependence on object radius (\textbackslash{}(R\textasciicircum{}5\textbackslash{})) and distance (\textbackslash{}(a\textasciicircum{}6\textbackslash{})). For **km-scale bodies** the Sun’s DSS is *many orders of magnitude smaller than the asteroid belt or Kuiper belt*. In other words: the Sun cannot tidally synchronize km-sized objects at 2–4 AU (asteroid belt) or at Kuiper distances within typical system lifetimes. This matches the physical intuition we encoded in the model: tidal torque scales like \textbackslash{}(R\textasciicircum{}5/a\textasciicircum{}6\textbackslash{}) and is negligible for small bodies at large distances. - Put plainly: **DDS ≪ belt radii** for small bodies — so tidal synchronizing power from the Sun is not the reason for non-accretion of the belts.

\paragraph{Canonical Equation.}
\[
a^6
\]

\paragraph{Dictionary.}
Quick interpretation — what the results show 1 [ID7532]

\paragraph{Encyclopedia.}
Quick Interpretation — What the Results Show: a\textasciicircum{}6 is a symbolic expression, written a\textasciicircum{}6. It introduces a symbol or relation used elsewhere in the framework. It is built from a. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
