\section*{ID9872: Relation: KissingNumber[n] ≡ Lfloor 10\textasciicircum{}n π Rfloor Mod 10}
\paragraph{Metadata.}
PiID: 9459094407046 | RTEID: RTE:P38335.1683:T0.3327 | UUID: ab4d502b-abf4-5cc2-b82d-31752f47fe91

\paragraph{Canonical Statement.}
in the inner torus is the static bubble region: a spherical region defined by \$(x-x\_0)\textasciicircum{}2+(y-y\_0)\textasciicircum{}2+(z-z\_0)\textasciicircum{}2 = r\_\{\textbackslash{}text\{bubble\}\}\textasciicircum{}2\$ that sits inside the volume of the torus. This bubble is not filled with ordinary matter but by the PackingSphere[Hom(S³, ℝ[π])] condition – essentially it contains the abstract sphere of dimension 153600 (S³ generalized) realized within the torus volume. The bubble’s surface acts as a holographic screen where the 4D information from the packing is projected into the 3D torus. It’s also where the kissing number constraints are enforced: on that surface, we impose \$KissingNumber[n] ≡ \textbackslash{}lfloor 10\textasciicircum{}n \textbackslash{}pi \textbackslash{}rfloor \textbackslash{}mod 10\$ for how spheres can pack. This formula ties each tiny sphere in the packing (each representing a state or subspace) to a digit of π, distributing π’s digits across the bubble’s constituents. The entanglement “loci” or operators connect inner and outer tori: we define a quantum entanglement operator \$\textbackslash{}mathcal\{E\}\$ that takes a state on the inner torus coordinates \$(θ\_1\textasciicircum{}, φ\_1\textasciicircum{})\$ and entangles it with a state on the outer torus \$(θ\_2\textasciicircum{}, φ\_2\textasciicircum{})\$. The entanglement entropy of this two-part state is set

\paragraph{Canonical Equation.}
\[
KissingNumber[n] ≡ \lfloor 10^n \pi \rfloor \mod 10
\]

\paragraph{Dictionary.}
Relation: KissingNumber[n] ≡ Lfloor 10\textasciicircum{}n π Rfloor Mod 10 — KissingNumber[n] ≡ lfloor 10\textasciicircum{}n π rfloor mod 10

\paragraph{Encyclopedia.}
Relation: KissingNumber[n] ≡ Lfloor 10\textasciicircum{}n π Rfloor Mod 10 is a symbolic expression, written KissingNumber[n] ≡ lfloor 10\textasciicircum{}n π rfloor mod 10. It introduces a symbol or relation used elsewhere in the framework. It is built from π, K, s, n, g, N. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
