\tzpanchor{0205}
\tzpentryheader{0205}{Kaluza--Klein Harmonic Modes}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{940896b8-f730-5818-837e-f77c6848e1d0}}\\
\textbf{PiID} & \tzpcode{1097566593344} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{212}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{796.0605 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.3117 rad}\\
\textbf{TZPID} & \tzpcode{ID0205} & \textbf{Node Dependencies}\quad \tzpidref{0204}\\
\textbf{Registry} & \tzpcode{registry\_id\_0205} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Mode Decomposition & Frequency Ladder\\
\textbf{Closure Support} & Compact Wavenumber & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The compact circle imposes periodic boundary conditions, quantizing momentum along the extra dimension.

\tzpsection{Canonical Equation}
\[
psi(x,y,t) = \sum_{n}\psi_n(x,t)e^{i n y/R_{\mathrm{KK}}}
\]
\[
omega_n = \frac{n c}{R_{\mathrm{KK}}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $t$: source equation symbol.
    \item $n$: integer mode index.
    \item $R_{\mathrm{KK}}$: source equation symbol.
    \item $c$: speed of light or relativistic conversion factor.
    \item $k_n$: mode-indexed wavenumber.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0205 generated source Wolfram model *)
ClearAll[K0205, Cr0205, T, R, A, W, I, N];
eq0205$1 = HoldForm[psi[x, y, t] == SumNpsiN[x, t]*e^(i*(ny/RKK))];
eq0205$2 = HoldForm[omegaN == (n*c)/RKK];
eq0205$3 = HoldForm[kN == n/RKK];

K0205 = HoldForm[{eq0205$1, eq0205$2, eq0205$3}];

N = "normalized TRAWIN closure object for Kaluza--Klein Harmonic Modes";
I = "Compact Wavenumber integration/comparison layer";
W = "Frequency Ladder wave or operator carrier";
A = "Mode Decomposition admissible action/amplitude condition";
R = "Frequency Ladder rotation/curl preservation layer";
T = "Mode Decomposition local source condition";

Cr0205[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0205 = Cr0205[K0205];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Mode Decomposition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Frequency Ladder rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Mode Decomposition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Frequency Ladder wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Compact Wavenumber integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Kaluza--Klein Harmonic Modes.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0205] Kaluza--Klein Harmonic Modes}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
For any diffeomorphism $\phi:M\to M$ preserving the symmetry group of $M$,

\begin{equation}
\phi(p)=p .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi:M\to M$ be a diffeomorphism preserving the symmetry structure of the manifold. Since $p$ is defined as the unique point where the metric degeneracy occurs,

\begin{equation}
\det(g)\big|_p=0 .
\end{equation}

If $\phi$ preserves the Trawinistic structure, then it must preserve the degeneracy locus:

\begin{equation}
\det(g)\big|_{\phi(p)}=0 .
\end{equation}

Because $p$ is unique, the only point satisfying this condition is $p$ itself. Therefore:

\begin{equation}
\phi(p)=p .
\end{equation}

\paragraph{Interpretation.}
The TZP is invariant under all structure-preserving transformations. It is therefore a fixed point of the system.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Kaluza--Klein Harmonic Modes by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Mode Decomposition}\par
\[
psi(x,y,t) = \sum_{n}\psi_n(x,t)e^{i n y/R_{\mathrm{KK}}}
\]
\noindent This decomposes the carrier field into compact harmonic sectors.\par
\noindent\textbf{2. Frequency Ladder}\par
\[
omega_n = \frac{n c}{R_{\mathrm{KK}}}
\]
\noindent This turns compactification into a discrete frequency ladder.\par
\noindent\textbf{3. Compact Wavenumber}\par
\[
k_n = \frac{n}{R_{\mathrm{KK}}}
\]
\noindent This closes the progression by fixing the matching compact wavenumber.\par

\clearpage
\noindent\textbf{[ID 0205] Kaluza--Klein Harmonic Modes}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Kaluza--Klein Harmonic Modes is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The compact circle imposes periodic boundary conditions, quantizing momentum along the extra dimension. \textbf{Contextual meaning:} The entry reads Kaluza--Klein Harmonic Modes as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads as an actual compact-mode construction, which is the right mathematical bridge between the metric ansatz and the later harmonic transfer pages. \textbf{Lemma support:} Mode Decomposition; Frequency Ladder; Compact Wavenumber.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP is invariant under all structure-preserving transformations. It is therefore a fixed point of the system.

\tzpsection{Equation Grounding}
Equation anchors:
\[
\psi(x,y,t)=\sum_{n\in\mathbb{Z}}\psi_n(x,t)e^{iny/R_{\mathrm{KK}}},
\qquad
\omega_n=\frac{nc}{R_{\mathrm{KK}}},
\qquad
k_n=\frac{n}{R_{\mathrm{KK}}}.
\]
Proof route: show that compact periodicity in the extra dimension forces the stated harmonic decomposition and discrete frequency ladder. Formalization route: prove that periodic compactification implies the stated mode and wavenumber quantization.

\tzpsection{Interpretive Role}
The entry now reads as an actual compact-mode construction, which is the right mathematical bridge between the metric ansatz and the later harmonic transfer pages.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Compact Fourier Wavenumber Assignment}: The quantization of momentum along the compactified fifth dimension into discrete integer steps.
\item \textbf{Transverse Dimensional Periodicity}: The constraint that wavefunctions must perfectly wrap around the microscopic cylindrical dimension.
\item \textbf{High-Frequency Harmonic Truncation}: The effective mass generated in 4D spacetime corresponding to successive excitations of the compactified dimension.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0205]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0205_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0205] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Kaluza--Klein Harmonic Modes}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the compact circle imposes periodic boundary conditions, quantizing momentum along the
extra dimension

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Kaluza--Klein Harmonic Modes is valid as a spectral relation when frequency, phase, and
propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0205_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
