\section*{ID9430: Definition of Ξcym}
\paragraph{Metadata.}
PiID: 5435784687886 | RTEID: RTE:P36618.7842:T3.7878 | UUID: fc8f4524-c957-57e0-ada9-bb00d95c4504

\paragraph{Canonical Statement.}
0408] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0407], [ID 0400] Node registry\_id\_0408 Support Titles Mode Quantization; Dispersion Law; Boundary Condition Test Handle If the resonance pattern cannot be organized into bounded modes with the stated boundary condition, the entry fails. Canonical Equation Links \$Ξcym= ∫ Ω Φ𝑛𝜌vac\$ 𝑑𝑉 \$Φ𝑛 |𝜕Ω=0\$ Aadm \$(Ξcym\$ )=1 [ID 0409] THE SUPERCONDUCTING PAIR CREATION OPERATOR (ℎ𝑎𝑡𝐻𝑆𝐶) TZPID ID0409 UUID 5c6dc21e-7947-5b67-a339-8920af06fb70 Type Operator / Transfer Statement Scale transfer LOC Classification Working routing: QA329 operator theory; QA169 categorical structure arXiv Classification Primary: math.CT; Cross-list: math-ph, cs.LO Canonical Statement This entry develops the su

\paragraph{Canonical Equation.}
\[
Ξcym= ∫ Ω Φ𝑛𝜌vac
\]

\paragraph{Dictionary.}
Definition of Ξcym — Ξcym= ∫ Ω Φ𝑛𝜌vac

\paragraph{Encyclopedia.}
Definition of Ξcym is an algebraic definition, written Ξcym= ∫ Ω Φ𝑛𝜌vac. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from v, a, c, defining Ξcym. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
