\tzpanchor{0301}
\tzpentryheader{0301}{Fibonacci Sphere Parametrization}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{edda8777-aa48-5521-946e-f53b85167dc7}}\\
\textbf{PiID} & \tzpcode{2458700660631} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{308}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1168.8498 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9259 rad}\\
\textbf{TZPID} & \tzpcode{ID0301} & \textbf{Node Dependencies}\quad \tzpidref{0300}\\
\textbf{Registry} & \tzpcode{registry\_id\_0301} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This algorithm uniformly distributes 153,600 addresses over the sphere without polar clustering by using the Fibonacci spiral.

\tzpsection{Canonical Equation}
\[
\varphi = \frac{1+\sqrt{5}}{2}
\]

\[
\theta_i = \frac{2\pi i}{\varphi}
\]

\[
\phi_i = \arccos\!\left(1-\frac{2(i-\tfrac{1}{2})}{n}\right)
\]

\[
\mathbf{p}_i = (\sin\phi_i\cos\theta_i,\ \sin\phi_i\sin\theta_i,\ \cos\phi_i)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\theta_i$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $\phi_i$: flux, phase, or topological map term in the source equation.
    \item $n$: integer mode index.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0301 generated source Wolfram model *)
ClearAll[K0301, Cr0301, T, R, A, W, I, N];
eq0301$1 = HoldForm[phi == (1 + Sqrt[5])/2];
eq0301$2 = HoldForm[thetaI == (2*Pi*i)/phi];
eq0301$3 = HoldForm[phiI == arccos[1 - (2*(i - tfrac[1]*2))/n]];
eq0301$4 = HoldForm[pI == Tuple[SinphiICosthetaI, SinphiISinthetaI, CosphiI]];
eq0301$5 = HoldForm[TZPSequence[thetaI == (2*Pi*i)/phi, phiI == arccos[1 - (2*(i - tfrac[1]*2))/n]]];
eq0301$6 = HoldForm[pI == Tuple[SinphiICosthetaI, SinphiISinthetaI, CosphiI]];

K0301 = HoldForm[{eq0301$1, eq0301$2, eq0301$3, eq0301$4, eq0301$5, eq0301$6}];

N = "normalized TRAWIN closure object for Fibonacci Sphere Parametrization";
I = "Cartesian Point integration/comparison layer";
W = "Spherical Address Angles wave or operator carrier";
A = "Golden Ratio admissible action/amplitude condition";
R = "Spherical Address Angles rotation/curl preservation layer";
T = "Golden Ratio local source condition";

Cr0301[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0301 = Cr0301[K0301];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Golden Ratio local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Spherical Address Angles rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Golden Ratio admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Spherical Address Angles wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Cartesian Point integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Fibonacci Sphere Parametrization.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0301] Fibonacci Sphere Parametrization}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\det(g)\big|_{p}=0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $(M,g)$ be a manifold equipped with metric tensor $g$. Away from the Trawin Zero Point $p$, the metric is assumed nondegenerate:

\begin{equation}
\det(g)\neq 0,
\qquad x\neq p .
\end{equation}

At the TZP, the manifold undergoes a structural collapse of ordinary metric invertibility. This means the inverse metric $g^{-1}$ cannot be defined at $p$.

A metric tensor is invertible if and only if its determinant is nonzero. Therefore, non-invertibility at $p$ implies:

\begin{equation}
\det(g)\big|_{p}=0 .
\end{equation}

\paragraph{Interpretation.}
The TZP is marked by metric degeneracy. This is the first mathematical signature that ordinary geometry fails at the zero point and must be replaced by a Trawinistic structure.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Fibonacci Sphere Parametrization by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Golden Ratio}\par
\[
\varphi = \frac{1+\sqrt{5}}{2}
\]
\noindent This fixes the irrational angular increment used by the Fibonacci spiral.\par
\noindent\textbf{2. Spherical Address Angles}\par
\[
\theta_i = \frac{2\pi i}{\varphi},
\qquad
\phi_i = \arccos\!\left(1-\frac{2(i-\tfrac{1}{2})}{n}\right)
\]
\noindent These angles place the \textbackslash{}(i\textbackslash{})-th address on the unit sphere without polar clustering.\par
\noindent\textbf{3. Cartesian Point}\par
\[
\mathbf{p}_i =
(\sin\phi_i\cos\theta_i,\ \sin\phi_i\sin\theta_i,\ \cos\phi_i)
\]
\noindent This converts the angular address into the point used by the DAANSphere lattice.\par

\clearpage
\noindent\textbf{[ID 0301] Fibonacci Sphere Parametrization}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Fibonacci Sphere Parametrization is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This algorithm uniformly distributes 153,600 addresses over the sphere without polar clustering by using the Fibonacci spiral. \textbf{Contextual meaning:} The entry reads Fibonacci Sphere Parametrization as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Golden Ratio; Spherical Address Angles; Cartesian Point.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP is marked by metric degeneracy. This is the first mathematical signature that ordinary geometry fails at the zero point and must be replaced by a Trawinistic structure.

\tzpsection{Equation Grounding}
Equation anchors: varphi = ratio 1+sqrt 5 2; theta sub i = ratio 2pi i varphi; phi sub i = arccos (1-ratio 2(i-tfrac 1 2 ) n ); and p sub i = (sinphi sub icostheta sub i, sinphi sub isintheta sub i, cosphi sub i). Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Golden Spiral Discretization}: The nearly uniform mapping of discrete points onto a spherical surface using the golden angle.
\item \textbf{Isotropic Spherical Grid Formulation}: The mathematical construction providing equal-area coordinate distribution for stable wave propagation without polar clustering.
\item \textbf{Chiral Surface Tessellation}: The topological projection defining right- and left-handed rotational pathways on a closed manifold.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0301]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0301_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0301] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Fibonacci Sphere Parametrization}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this algorithm uniformly distributes 153,600 addresses over the sphere without polar
clustering by using the Fibonacci spiral

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Fibonacci Sphere Parametrization is valid as a tensorial/geometric statement when the
stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0301_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
