\section*{ID9019: Relation: (Dt’)/(dt)α(t)}
\paragraph{Metadata.}
PiID: 0340216654437 | RTEID: RTE:P35022.7799:T1.1581 | UUID: c0291d61-aed1-56aa-b75b-a7123b4c2bed

\paragraph{Canonical Statement.}
alises other quantities (e.g., temporal displacement factor); serves as scaling factor in Hamiltonians; anchors definitions of physical constants; permits comparison across scales. Falsifiability / Test Handle: If measurements around the TZP produce inconsistent loop integrals, the notion of a unique base unit would be invalid. 0.0.9 ID 007: Temporal Displacement Factor Type: Definition Formal Statement: The temporal displacement factor \$α(t)\textbackslash{}alpha(t)α(t)\$ is defined by \$α(t)=dtdt\textbackslash{}alpha(t)\$ = \$\textbackslash{}frac\{\textbackslash{}text\{d\}t’\}\{\textbackslash{}text\{d\}t\}α(t)\$ = \$dtdt, wherett′tisthelocaltimemeasuredalongageodesicapproachingpppandtttistheglobaltimeparameter.\$ Interpretive Meaning: This factor quantifies how the flow of time near the TZP differs from the global flow of time. It captures temporal dilation or contraction due to the metric degeneracy. Dependencies: ID 001, ID 004 Derivable Consequences: Modifies Hamilton–Jacobi equations; influences phase

\paragraph{Canonical Equation.}
\[
\frac{\text{d}t’}{\text{d}t}α(t)
\]

\paragraph{Dictionary.}
Relation: (Dt’)/(dt)α(t) — (dt’)/(dt)α(t)

\paragraph{Encyclopedia.}
Relation: (Dt’)/(dt)α(t) is a symbolic expression, written (dt’)/(dt)α(t). It introduces a symbol or relation used elsewhere in the framework. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
