\tzpanchor{0080}
\tzpentryheader{0080}{Semiclassical Limits}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{380a6746-7eff-50d0-baa7-65b4c2a20e3b}}\\
\textbf{PiID} & \tzpcode{8628034825342} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{87}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{310.6578 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.5119 rad}\\
\textbf{TZPID} & \tzpcode{ID0080} & \textbf{Node Dependencies}\quad \tzpidref{0032}\\
\textbf{Registry} & \tzpcode{registry\_id\_0080} & \textbf{Scale}\quad mesoscopic-asymptotic\\
\textbf{LOC Classification} & QC174.17 semiclassical methods & QC20 action principles\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: math-ph, hep-th & \\
\textbf{Primary Support} & Trawin Action Functional & Stationary-Phase Condition\\
\textbf{Closure Support} & Semiclassical Propagator & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This entry describes how classical mechanics emerges from quantum theory on curved manifolds; the zero point leaves imprints even in the classical regime.

\tzpsection{Canonical Equation}
\[
\delta S_{\mathrm{T}}[\gamma_{\mathrm{cl}}] = 0
\]
\[
K(x_f,t_f;x_i,t_i)
\approx
\sum_{\gamma_{\mathrm{cl}}}
A_{\gamma}
\exp\!\left(\frac{i}{\hbar}S_{\mathrm{T}}[\gamma_{\mathrm{cl}}]\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\delta$: point-source delta term that anchors the Green-function response.
    \item $S_{\mathrm{T}}$: source equation symbol.
    \item $\gamma_{\mathrm{cl}}$: source equation symbol.
    \item $K$: source equation symbol.
    \item $x_f$: source equation symbol.
    \item $t_f$: source equation symbol.
    \item $x_i$: source equation symbol.
    \item $t_i$: source equation symbol.
    \item $A_{\gamma}$: source equation symbol.
    \item $\gamma$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0080 generated source Wolfram model *)
ClearAll[K0080, Cr0080, T, R, A, W, I, N];
eq0080$1 = HoldForm[DiracDelta*ST[gammaCl] == 0];
eq0080$2 = HoldForm[K[xF, tF; xI, tI] == SumGammaclAGammaexp[(i/hbar)*ST[gammaCl]]];
eq0080$3 = HoldForm[ST[gamma]];

K0080 = HoldForm[{eq0080$1, eq0080$2, eq0080$3}];

N = "normalized TRAWIN closure object for Semiclassical Limits";
I = "Semiclassical Propagator integration/comparison layer";
W = "Stationary-Phase Condition wave or operator carrier";
A = "Trawin Action Functional admissible action/amplitude condition";
R = "Stationary-Phase Condition rotation/curl preservation layer";
T = "Trawin Action Functional local source condition";

Cr0080[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0080 = Cr0080[K0080];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Trawin Action Functional local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Stationary-Phase Condition rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Trawin Action Functional admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Stationary-Phase Condition wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Semiclassical Propagator integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Semiclassical Limits.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0080] Semiclassical Limits}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Limit.}
\begin{equation}
\hbar\rightarrow 0 .
\end{equation}

\paragraph{Stationary-Action Recovery.}
\begin{equation}
\hbar\rightarrow 0
\quad\Longrightarrow\quad
\delta S=0 .
\end{equation}

\paragraph{Primary Derivation.}
The path integral has phase factor:
\begin{equation}
e^{iS/\hbar}.
\end{equation}

As $\hbar\to 0$, non-stationary paths oscillate rapidly and cancel by destructive interference.

The surviving paths satisfy:
\begin{equation}
\delta S=0 .
\end{equation}

Therefore,
\begin{equation}
\boxed{
\hbar\rightarrow 0
\quad\Longrightarrow\quad
\delta S=0 .
}
\end{equation}

\paragraph{Interpretation.}
The semiclassical limit recovers stationary-action classical dynamics from quantum phase cancellation.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Semiclassical Limits by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Trawin Action Functional}\par
\[
S_{\mathrm{T}}[\gamma]
\]
\noindent This identifies the phase-bearing object whose extremals govern the asymptotic regime.\par
\noindent\textbf{2. Stationary-Phase Condition}\par
\[
\delta S_{\mathrm{T}}[\gamma_{\mathrm{cl}}] = 0
\]
\noindent This selects the classical trajectories contributing coherently in the semiclassical limit.\par
\noindent\textbf{3. Semiclassical Propagator}\par
\[
K(x_f,t_f;x_i,t_i)
\approx
\sum_{\gamma_{\mathrm{cl}}}
A_{\gamma}
\exp\!\left(\frac{i}{\hbar}S_{\mathrm{T}}[\gamma_{\mathrm{cl}}]\right)
\]
\noindent This closes the progression by expressing propagation as a sum over stationary Trawinistic histories.\par

\clearpage
\noindent\textbf{[ID 0080] Semiclassical Limits}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Semiclassical Limits is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This entry describes how classical mechanics emerges from quantum theory on curved manifolds; the zero point leaves imprints even in the classical regime. \textbf{Contextual meaning:} The entry reads Semiclassical Limits as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry lets the registry move from full quantum amplitudes to effective classical motion without severing the Trawin zero-point corrections. It provides the hinge between microscopic description and emergent macroscopic law. \textbf{Lemma support:} Trawin Action Functional; Stationary-Phase Condition; Semiclassical Propagator.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The semiclassical limit recovers stationary-action classical dynamics from quantum phase cancellation. \% CANONICAL PDF-ALIGNED VERSION.

\tzpsection{Equation Grounding}
Equation anchors: The semiclassical limit is defined by taking  to0hbarto 0 to0 while holding curvature and TZP contributions fixed; path integrals are approximated by stationary phase contributions from classical paths influenced by the Trawinistic action. The semiclassical limit is defined by taking  to0hbarto 0 to0 while holding curvature and TZP contributions fixed; path integrals are approximated by stationary phase contributions from classical paths influenced by the Trawinistic action.

\tzpsection{Interpretive Role}
This entry lets the registry move from full quantum amplitudes to effective classical motion without severing the Trawin zero-point corrections. It provides the hinge between microscopic description and emergent macroscopic law.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Semiclassical Limits}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Semiclassical Limits Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Limits Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0080]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0080_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0080] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Semiclassical Limits}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this entry describes how classical mechanics emerges from quantum theory on curved
manifolds; the zero point leaves imprints even in the classical...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Semiclassical Limits is valid as a formal dynamical law when the Hamiltonian or energy
operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0080_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
