\tzpanchor{0459}
\tzpentryheader{0459}{Duty Cycle Efficiency}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{6d55f982-4eb4-51d2-bf15-454405e60431}}\\
\textbf{PiID} & \tzpcode{9627495673518} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{466}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1766.8660 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.9113 rad}\\
\textbf{TZPID} & \tzpcode{ID0459} & \textbf{Node Dependencies}\quad \tzpidref{0458}\\
\textbf{Registry} & \tzpcode{registry\_id\_0459} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Aggregate Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 459 establishes the final temporal metric of the generator cycle. The efficiency determines net power relative to the total time required for extraction, reset, measurement, and feedback. This concludes the internal operational specifications for Volume 01. Throughput Calculation: The duty cycle determines the macro shift frequency for persistent flow. System Closure: Final logic for the "Power On" state of the Furiene Turbine.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\eta_{\text{duty}} = \cdots
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{K}_{0459}$: canonical registry object for entry ID 0459.
    \item $\eta_{duty}$: source equation symbol.
    \item $\cdot s$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0459 generated source Wolfram model *)
ClearAll[K0459, Cr0459, T, R, A, W, I, N];
eq0459$1 = HoldForm[eta == Ellipsis];

K0459 = HoldForm[{eq0459$1}];

N = "normalized TRAWIN closure object for Duty Cycle Efficiency";
I = "Duty Cycle Efficiency integration/comparison layer";
W = "Duty Cycle Efficiency wave or operator carrier";
A = "Duty Cycle Efficiency admissible action/amplitude condition";
R = "Duty Cycle Efficiency rotation/curl preservation layer";
T = "Duty Cycle Efficiency local source condition";

Cr0459[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0459 = Cr0459[K0459];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Duty Cycle Efficiency local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Duty Cycle Efficiency rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Duty Cycle Efficiency admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Duty Cycle Efficiency wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Duty Cycle Efficiency integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Duty Cycle Efficiency.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0459] Duty Cycle Efficiency}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
c_i=c_i(\mu,d_{\mathrm{eff}}).
\end{equation}

\paragraph{Flow Equation.}
\begin{equation}
\frac{\mathrm{d}c_i}{\mathrm{d}\ln\mu}
=
f_i(c_j,d_{\mathrm{eff}}).
\end{equation}

\paragraph{Primary Derivation.}
If couplings depend on scale and effective dimension, then derived constants may also become scale-sensitive.

Represent each effective constant as:

\begin{equation}
c_i=c_i(\mu,d_{\mathrm{eff}}).
\end{equation}

The natural flow parameter for scale comparison is $\ln\mu$.  
Differentiating with respect to this parameter gives:

\begin{equation}
\boxed{
\frac{\mathrm{d}c_i}{\mathrm{d}\ln\mu}
=
f_i(c_j,d_{\mathrm{eff}}).
}
\end{equation}

\paragraph{Interpretation.}
Constants are treated as effective parameters that may run under TRAWIN scale and dimension flow.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Duty Cycle Efficiency by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\eta_{\text{duty}} = \cdots
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0459] Duty Cycle Efficiency}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Duty Cycle Efficiency is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 459 establishes the final temporal metric of the generator cycle. The efficiency determines net power relative to the total time required for extraction, reset, measurement, and feedback. This concludes the internal operational specifications for Volume 01. Throughput Calculation: The duty cycle determines the macro shift frequency for persistent flow. System Closure: Final logic for the "Power On" state of the Furiene Turbine.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\eta_{\text{duty}} = \cdots
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 459 establishes the final temporal metric of the generator cycle. The efficiency determines net power relative to the total time required for extraction, reset, measurement, and feedback. This concludes the internal operational specifications for Volume 01. Throughput Calculation: The duty cycle determines the macro shift frequency for persistent flow. System Closure: Final logic for the "Power On" state of the Furiene Turbine.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Duty Cycle Efficiency by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Duty Cycle Efficiency; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0459]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0459].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0459] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Duty Cycle Efficiency}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} eta\textbackslash{}\_\textbackslash{}\textbackslash{} = frac\textbackslash{}\_\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{}\textbackslash{} implies tau\textbackslash{}\_\textbackslash{}\textbackslash{} = sum tau\textbackslash{}\_i

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``DUTY CYCLE EFFICIENCY is valid as a formal registry statement when its source equation
and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that eta\textbackslash{}\_\textbackslash{}\textbackslash{} = frac\textbackslash{}\_\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{}\textbackslash{} implies tau\textbackslash{}\_\textbackslash{}\textbackslash{} = sum tau\textbackslash{}\_i.
Constants are treated as effective parameters that may run under TRAWIN scale and
dimension flow. ------------------------------------------------------------------------
------------------------------------------------. The CHL validation treats the equation
as the formal anchor and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0459].
\par\endgroup
\vfill
\endgroup
\endgroup
