\tzpanchor{0624}
\tzpentryheader{0624}{WEAK MEASUREMENT FEEDBACK LOOP}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{447c5b82-b335-5969-824a-a6bad65ced39}}\\
\textbf{PiID} & \tzpcode{7713427577896} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{631}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2399.8312 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.9542 rad}\\
\textbf{TZPID} & \tzpcode{ID0624} & \textbf{Node Dependencies}\quad \tzpidref{0623}\\
\textbf{Registry} & \tzpcode{registry\_id\_0624} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records weak measurement feedback loop through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\tzpfitmath{\rho_{\mathrm{vac}}^{T} = \frac{1}{u_T^4} \int_{0}^{\omega_{\mathrm{cut}}} \eta(\omega)\, \hbar\omega\, \mathrm{d}\omega.}
\]
\[
\hbar\omega.
\]
\[
\eta(\omega)\hbar\omega.
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\rho_{\mathrm{vac}}$: source equation symbol.
    \item $T$: source equation symbol.
    \item $u_T$: source equation symbol.
    \item $\omega_{\mathrm{cut}}$: angular frequency term in the source equation.
    \item $\omega$: angular frequency term in the source equation.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0624 generated source Wolfram model *)
ClearAll[K0624, Cr0624, T, R, A, W, I, N];
eq0624$1 = HoldForm[TZPFitMath[rhoVac^T == (1/uT^4)*Integral0^omegaCut*eta[omega]*hbaromega*domega]];
eq0624$2 = HoldForm[hbaromega];
eq0624$3 = HoldForm[eta[omega]*hbaromega];

K0624 = HoldForm[{eq0624$1, eq0624$2, eq0624$3}];

N = "normalized TRAWIN closure object for WEAK MEASUREMENT FEEDBACK LOOP";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Canonical Definition admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Canonical Definition local source condition";

Cr0624[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0624 = Cr0624[K0624];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Canonical Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Canonical Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for WEAK MEASUREMENT FEEDBACK LOOP.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0624] WEAK MEASUREMENT FEEDBACK LOOP}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_T^4}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,
\hbar\omega\,
\mathrm{d}\omega .
\end{equation}

\paragraph{Primary Derivation.}
Each vacuum mode of frequency $\omega$ contributes energy proportional to:

\begin{equation}
\hbar\omega .
\end{equation}

The spectral density index $\eta(\omega)$ weights the contribution of each frequency:

\begin{equation}
\eta(\omega)\hbar\omega .
\end{equation}

Integrating over all allowed frequencies up to the cutoff $\omega_{\mathrm{cut}}$ gives the weighted vacuum energy:

\begin{equation}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\hbar\omega\,\mathrm{d}\omega .
\end{equation}

To convert this to a density in Trawin units, divide by the fourth power of the base unit:

\begin{equation}
u_T^4 .
\end{equation}

Therefore,

\begin{equation}
\boxed{
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_T^4}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,
\hbar\omega\,
\mathrm{d}\omega .
}
\end{equation}

\paragraph{Interpretation.}
$\rho_{\mathrm{vac}}^{T}$ defines vacuum energy density as a spectral integral normalized by the four-dimensional Trawin base scale.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors WEAK MEASUREMENT FEEDBACK LOOP by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Canonical Definition}\par
\[
\tzpfitmath{\rho_{\mathrm{vac}}^{T} = \frac{1}{u_T^4} \int_{0}^{\omega_{\mathrm{cut}}} \eta(\omega)\, \hbar\omega\, \mathrm{d}\omega.}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\hbar\omega.
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\eta(\omega)\hbar\omega.
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0624] WEAK MEASUREMENT FEEDBACK LOOP}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
WEAK MEASUREMENT FEEDBACK LOOP is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} hat M sub weak = hat I + sqrt etaepsilon hat O implies dr = sqrt eta langlehat O rangle dt + frac dW sqrt eta. \textbf{Contextual meaning:} The entry reads WEAK MEASUREMENT FEEDBACK LOOP as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub vac to the power T defines vacuum energy density as a spectral integral normalized by the four-dimensional Trawin base scale.

\tzpsection{Equation Grounding}
Equation anchors: mathrm hat M sub weak = hat I + sqrt etaepsilon hat O implies dr = sqrt eta hat O; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Gentle Quantum State Probing}: The incredibly delicate method of observing the system so lightly that you gain useful information without accidentally collapsing the fragile wavefunction.
\item \textbf{Non-Destructive Observational Steering}: The process of taking tiny, incomplete peeks at the data and using those hints to slowly nudge the system back on course without breaking it.
\item \textbf{Continuous Sub-Threshold Monitoring}: The mathematical protocol for constantly listening to the faint quantum whispers of the core without ever triggering a full, chaotic readout event.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0624]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0624_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0624] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont WEAK MEASUREMENT FEEDBACK LOOP}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records weak measurement feedback loop through the Septenary derivation layer,
using the displayed relations as operational anchors for t...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``WEAK MEASUREMENT FEEDBACK LOOP is valid as a formal dynamical law when the Hamiltonian
or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0624_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
