\tzpanchor{0387}
\tzpentryheader{0387}{Triple Resonance Domain Condition}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{db36c1ef-8045-53f2-aa00-8275f2483488}}\\
\textbf{PiID} & \tzpcode{9519415116094} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{394}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1502.8069 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.4762 rad}\\
\textbf{TZPID} & \tzpcode{ID0387} & \textbf{Node Dependencies}\quad \tzpidref{0386}\\
\textbf{Registry} & \tzpcode{registry\_id\_0387} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Triple Resonance Match & Domain Window\\
\textbf{Closure Support} & Normalized Detuning & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Emergent phenomena appear when three characteristic scales satisfy the confluence condition that the quantum length scale is much smaller than the classical scale, which in turn is much smaller than the relativistic scale, and their associated energy scales become comparable. Classical variables include gyroscopic angular momentum and rotation frequencies; quantum variables involve flux quantisation and tunnelling; relativistic variables involve frame-dragging. When these conditions are met, new hybrid phenomena activate.

\tzpsection{Canonical Equation}
\[
\omega_{1}=\omega_{2}=\omega_{3}
\]
\[
\mathcal{D}_{\mathrm{res}}=\{x:\lvert\omega_i(x)-\omega_j(x)\rvert\leq\varepsilon\}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\omega_{1}$: angular frequency term in the source equation.
    \item $\omega_{2}$: angular frequency term in the source equation.
    \item $\omega_{3}$: angular frequency term in the source equation.
    \item $\mathcal{D}_{\mathrm{res}}$: source equation symbol.
    \item $\omega_i(x)$: angular frequency term in the source equation.
    \item $\omega_j(x)$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0387 generated source Wolfram model *)
ClearAll[K0387, Cr0387, T, R, A, W, I, N];
eq0387$1 = HoldForm[omega1 == omega2 == omega3];
eq0387$2 = HoldForm[DRes == {x:Abs[omegaI[x] - omegaJ[x]] <= epsilon}];
eq0387$3 = HoldForm[Inequality[DeltaTri, Equal, maxIjAbs[omegaI - omegaJ]/epsilon, LessEqual, 1]];

K0387 = HoldForm[{eq0387$1, eq0387$2, eq0387$3}];

N = "normalized TRAWIN closure object for Triple Resonance Domain Condition";
I = "Normalized Detuning integration/comparison layer";
W = "Domain Window wave or operator carrier";
A = "Triple Resonance Match admissible action/amplitude condition";
R = "Domain Window rotation/curl preservation layer";
T = "Triple Resonance Match local source condition";

Cr0387[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0387 = Cr0387[K0387];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Triple Resonance Match local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Domain Window rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Triple Resonance Match admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Domain Window wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Detuning integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Triple Resonance Domain Condition.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0387] Triple Resonance Domain Condition}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\dot{\omega}(t)
=
\frac{\tau_{\mathrm{em}}(t)}{I_T}.
\end{equation}

\begin{equation}
\omega(t)
=
\omega(0)
+
\frac{1}{I_T}
\int_0^t
\tau_{\mathrm{em}}(t')
\,\mathrm{d}t' .
\end{equation}

\paragraph{Primary Derivation.}
Let $I_T$ be the Trawinistic moment of inertia.  
Angular momentum is related to angular velocity by:
\begin{equation}
L=I_T\omega .
\end{equation}

Differentiating gives:
\begin{equation}
\dot{L}
=
I_T\dot{\omega},
\end{equation}
assuming $I_T$ is constant over the interval.

Since $\dot{L}=\tau_{\mathrm{em}}$, we obtain:
\begin{equation}
\dot{\omega}(t)
=
\frac{\tau_{\mathrm{em}}(t)}{I_T}.
\end{equation}

Integrating through time gives:
\begin{equation}
\boxed{
\omega(t)
=
\omega(0)
+
\frac{1}{I_T}
\int_0^t
\tau_{\mathrm{em}}(t')
\,\mathrm{d}t' .
}
\end{equation}

\paragraph{Interpretation.}
Rotation is the accumulated response to torque history, scaled by the effective moment of inertia.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Triple Resonance Domain Condition by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Triple Resonance Match}\par
\[
\omega_{1}=\omega_{2}=\omega_{3}
\]
\noindent This fixes the triple-resonance condition aligning the three carrier frequencies.\par
\noindent\textbf{2. Domain Window}\par
\[
\mathcal{D}_{\mathrm{res}}=\{x:\lvert\omega_i(x)-\omega_j(x)\rvert\leq\varepsilon\}
\]
\noindent This identifies the spatial or parameter domain in which the resonance match is admissible.\par
\noindent\textbf{3. Normalized Detuning}\par
\[
\Delta_{\mathrm{tri}}=\max_{i,j}\lvert\omega_i-\omega_j\rvert/\varepsilon\leq1
\]
\noindent This closes the entry with a normalized detuning that measures departure from exact triple resonance.\par

\clearpage
\noindent\textbf{[ID 0387] Triple Resonance Domain Condition}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Triple Resonance Domain Condition is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Emergent phenomena appear when three characteristic scales satisfy the confluence condition that the quantum length scale is much smaller than the classical scale, which in turn is much smaller than the relativistic scale, and their associated energy scales become comparable. Classical variables include gyroscopic angular momentum and rotation frequencies; quantum variables involve flux quantisation and tunnelling; relativistic variables involve frame-dragging. When these conditions are met, new hybrid phenomena activate. \textbf{Contextual meaning:} The entry reads Triple Resonance Domain Condition as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the triple-resonance condition through an actual frequency match, domain window, and detuning measure. \textbf{Lemma support:} Triple Resonance Match; Domain Window; Normalized Detuning.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Rotation is the accumulated response to torque history, scaled by the effective moment of inertia.

\tzpsection{Equation Grounding}
Equation anchors: omega sub 1=omega sub 2=omega sub 3; mathcal D sub res = x: |omega sub i(x)-omega sub j(x)|le varepsilon for all i,j; and Delta sub res =ratio 1 omega sub ast max sub i,j |omega sub i-omega sub j|. Proof route: show that the admissible domain is exactly the set on which the three carrier frequencies remain within the stated resonance window. Formalization route: prove that the normalized detuning vanishes precisely at exact triple resonance.

\tzpsection{Interpretive Role}
The entry now states the triple-resonance condition through an actual frequency match, domain window, and detuning measure.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Perfect Three-Wave Synchronization}: The incredibly rare event where three entirely different oscillating systems happen to hit the exact same frequency at the exact same time.
\item \textbf{Tolerance Window Parameterization}: The mathematical definition of how close the frequencies need to be to 'perfect' before the systems start sharing energy with each other.
\item \textbf{Maximum Detuning Constraint}: The strict upper limit on the allowed frequency mismatch, beyond which the three systems completely ignore one another.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0387]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0387_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0387] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Triple Resonance Domain Condition}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} emergent phenomena appear when three characteristic scales satisfy the confluence
condition that the quantum length scale is much smaller than the...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Triple Resonance Domain Condition is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0387_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
