\tzpanchor{0295}
\tzpentryheader{0295}{Nested Field Topology and Toroidal--Poloidal Decomposition}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{dc1f679c-c245-5016-9632-6a7ec92a06d6}}\\
\textbf{PiID} & \tzpcode{4127372458700} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{302}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1145.5505 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.8875 rad}\\
\textbf{TZPID} & \tzpcode{ID0295} & \textbf{Node Dependencies}\quad \tzpidref{0294}\\
\textbf{Registry} & \tzpcode{registry\_id\_0295} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Nested alternating micro-fields in laboratory permeable enclosures correspond to toroidal--poloidal dynamo decomposition and nested magnetic shells in gas giants, with correlation about 0.82.

\tzpsection{Canonical Equation}
\[
C_{TZP} \approx S_{temp} + S_{atemp} + I_{ent} \approx 17 \text{ bits}
\]
\[
mathcal{O}_{atemp} = {\text{Conformal Fields on } \mathcal{I}^+}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $C_{TZP}$: source equation symbol.
    \item $S_{temp}$: source equation symbol.
    \item $S_{atemp}$: source equation symbol.
    \item $I_{ent}$: source equation symbol.
    \item $O$: source equation symbol.
    \item $\mathcal{I}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0295 generated source Wolfram model *)
ClearAll[K0295, Cr0295, T, R, A, W, I, N];
eq0295$1 = HoldForm[CTZP == STemp + SAtemp + IEnt == 17*Bits];
eq0295$2 = HoldForm[OAtemp == ConformalFieldsOn[IInfinity]];
eq0295$3 = HoldForm[ds2 == 0];

K0295 = HoldForm[{eq0295$1, eq0295$2, eq0295$3}];

N = "normalized TRAWIN closure object for Nested Field Topology and Toroidal--Poloidal Decomposition";
I = "Topological Closure integration/comparison layer";
W = "Compatibility Law wave or operator carrier";
A = "Geometric Carrier admissible action/amplitude condition";
R = "Compatibility Law rotation/curl preservation layer";
T = "Geometric Carrier local source condition";

Cr0295[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0295 = Cr0295[K0295];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Geometric Carrier local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Compatibility Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Geometric Carrier admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Compatibility Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Nested Field Topology and Toroidal--Poloidal Decomposition.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0295] Nested Field Topology and Toroidal--Poloidal Decomposition}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\eta:S\circ F\Rightarrow F\circ S.
\end{equation}

\paragraph{Symplectic Preservation Law.}
\begin{equation}
\eta_X^{*}\omega_{F\circ S(X)}
=
\omega_{S\circ F(X)}.
\end{equation}

\paragraph{Primary Derivation.}
Let $S$ be a scaling functor and $F$ a structure functor.  
There are two routes:

\begin{equation}
S\circ F,
\qquad
F\circ S.
\end{equation}

A natural transformation compares these routes:
\begin{equation}
\eta:S\circ F\Rightarrow F\circ S.
\end{equation}

To preserve dynamics, the bridge must preserve the symplectic form:
\begin{equation}
\boxed{
\eta_X^{*}\omega_{F\circ S(X)}
=
\omega_{S\circ F(X)}.
}
\end{equation}

\paragraph{Interpretation.}
Scaling and structural translation are compatible only when the categorical bridge preserves phase-space geometry.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Nested Field Topology and Toroidal--Poloidal Decomposition by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Geometric Carrier}\par
\[
C_{TZP} \approx S_{temp} + S_{atemp} + I_{ent} \approx 17 \text{ bits}
\]
\noindent This fixes the effective geometry or carrier space named by the entry title.\par
\noindent\textbf{2. Compatibility Law}\par
\[
mathcal{O}_{atemp} = {\text{Conformal Fields on } \mathcal{I}^+}
\]
\noindent This makes the geometry admissible by imposing its internal compatibility law.\par
\noindent\textbf{3. Topological Closure}\par
\[
ds^2=0
\]
\noindent This closes the entry by tying the local structure to a global topological invariant.\par

\clearpage
\noindent\textbf{[ID 0295] Nested Field Topology and Toroidal--Poloidal Decomposition}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Nested Field Topology and Toroidal--Poloidal Decomposition is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Nested alternating micro-fields in laboratory permeable enclosures correspond to toroidal--poloidal dynamo decomposition and nested magnetic shells in gas giants, with correlation about 0.82. \textbf{Contextual meaning:} The entry reads Nested Field Topology and Toroidal--Poloidal Decomposition as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the tertiary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Geometric Carrier; Compatibility Law; Topological Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Scaling and structural translation are compatible only when the categorical bridge preserves phase-space geometry.

\tzpsection{Equation Grounding}
Equation anchors:
\[
C_{\mathrm{TZP}}\approx S_{\mathrm{temp}}+S_{\mathrm{atemp}}+I_{\mathrm{ent}}\approx17\ \mathrm{bits},
\qquad
\mathcal{O}_{\mathrm{atemp}}=\mathrm{ConformalFields}(I^+),
\qquad
ds^2=0.
\]
Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the tertiary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Magnetic Flux Surface Stratification}: The breakdown of a complex magnetic plasma containment field into perfectly nested, non-intersecting layers resembling the skins of an onion.
\item \textbf{Separation of Azimuthal and Meridian Flow}: The mathematical uncoupling of the magnetic field wrapping around the donut (the short way) from the magnetic field wrapping along the donut (the long way).
\item \textbf{Multi-Layer Hierarchical Confinement Structures}: The rigorous geometric proof detailing exactly how the inner, twisted layers of a field protect and stabilize the outer, smoother layers from collapsing.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0295]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0295_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0295] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Nested Field Topology and Toroidal--Poloidal Decomposition}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} nested alternating micro-fields in laboratory permeable enclosures correspond to
toroidal--poloidal dynamo decomposition and nested magnetic shells...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Nested Field Topology and Toroidal--Poloidal Decomposition is valid as a
tensorial/geometric statement when the stated tensor fields are well formed on the
specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0295_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
