\tzpanchor{0583}
\tzpentryheader{0583}{SYNAPTIC AVALANCHE EXPONENT (tau = 3/2)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e2403487-d4b3-5106-91b9-dac5ac2affd0}}\\
\textbf{PiID} & \tzpcode{7481846766940} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{590}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2240.6191 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.6919 rad}\\
\textbf{TZPID} & \tzpcode{ID0583} & \textbf{Node Dependencies}\quad \tzpidref{0582}\\
\textbf{Registry} & \tzpcode{registry\_id\_0583} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Avalanche Law & Universal Exponent\\
\textbf{Closure Support} & Cutoff Scaling & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
tau = 3/2

\tzpsection{Canonical Equation}
\[
P(s) \propto s^{-\tau} \exp(-s/s_{\text{cutoff}})
\]
\[
P(s) \propto s^{-\tau}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $P$: source equation symbol.
    \item $\tau$: source equation symbol.
    \item $e_T$: exponential damping factor encoding potential-induced suppression.
    \item $\propto$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0583 generated source Wolfram model *)
ClearAll[K0583, Cr0583, T, R, A, W, I, N];
eq0583$1 = HoldForm[P[s] ? exp[-s/s]/s^tau];
eq0583$2 = HoldForm[P[s] ? s^(-tau)];
eq0583$3 = HoldForm[tau == 3/2];

K0583 = HoldForm[{eq0583$1, eq0583$2, eq0583$3}];

N = "normalized TRAWIN closure object for SYNAPTIC AVALANCHE EXPONENT (tau = 3/2)";
I = "Cutoff Scaling integration/comparison layer";
W = "Universal Exponent wave or operator carrier";
A = "Avalanche Law admissible action/amplitude condition";
R = "Universal Exponent rotation/curl preservation layer";
T = "Avalanche Law local source condition";

Cr0583[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0583 = Cr0583[K0583];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Avalanche Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Universal Exponent rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Avalanche Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Universal Exponent wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Cutoff Scaling integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for SYNAPTIC AVALANCHE EXPONENT (tau = 3/2).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0583] SYNAPTIC AVALANCHE EXPONENT (tau = 3/2)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
Near the TZP, quantum fields obey boundary conditions ensuring finite energy densities: field amplitudes and derivatives must vanish sufficiently rapidly as one approaches the zero point.

\paragraph{Primary Conditions.}
\begin{equation}
\lim_{x\to p}\phi(x)=0,
\qquad
\lim_{x\to p}\nabla^T\phi(x)=0 .
\end{equation}

\paragraph{Finite-Energy Condition.}
\begin{equation}
\int_U
\left(
|\nabla^T\phi|^2
+
V_T|\phi|^2
\right)
\mathrm{d}\mu_T
<\infty .
\end{equation}

\paragraph{Primary Derivation.}
Let $U$ be a neighborhood of the Trawin Zero Point $p$.  
A quantum field near $p$ contributes energy through gradient and potential terms:
\begin{equation}
|\nabla^T\phi|^2
+
V_T|\phi|^2 .
\end{equation}

To prevent divergent expectation values, require the integral over the Trawinistic measure to remain finite:
\begin{equation}
\int_U
\left(
|\nabla^T\phi|^2
+
V_T|\phi|^2
\right)
\mathrm{d}\mu_T
<\infty .
\end{equation}

A sufficient boundary condition is:
\begin{equation}
\boxed{
\lim_{x\to p}\phi(x)=0,
\qquad
\lim_{x\to p}\nabla^T\phi(x)=0 .
}
\end{equation}

\paragraph{Interpretation.}
The TZP quantum-scale constraint prevents singular field behavior from producing infinite energy density.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors SYNAPTIC AVALANCHE EXPONENT (tau = 3/2) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Avalanche Law}\par
\[
P(s) \propto s^{-\tau} \exp(-s/s_{\text{cutoff}})
\]
\noindent This fixes the avalanche-size distribution carried by the critical systems compared in the entry.\par
\noindent\textbf{2. Universal Exponent}\par
\[
P(s) \propto s^{-\tau}
\]
\noindent This isolates the universal exponent shared across the cited avalanche regimes.\par
\noindent\textbf{3. Cutoff Scaling}\par
\[
tau \approx 3/2
\]
\noindent This closes the entry by tying the finite-size cutoff to distance from the critical control parameter.\par

\clearpage
\noindent\textbf{[ID 0583] SYNAPTIC AVALANCHE EXPONENT (tau = 3/2)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
SYNAPTIC AVALANCHE EXPONENT (tau = 3/2) is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} tau = 3/2. \textbf{Contextual meaning:} The entry reads SYNAPTIC AVALANCHE EXPONENT (tau = 3/2) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now carries the actual avalanche-scaling law instead of malformed prose fragments, so the universality claim is visible mathematically on the page. \textbf{Lemma support:} Avalanche Law; Universal Exponent; Cutoff Scaling.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP quantum-scale constraint prevents singular field behavior from producing infinite energy density.

\tzpsection{Equation Grounding}
Equation anchors: P(s) propto s to the power -tau exp(-s/s sub cutoff ); P(s) propto s to the power -tau; and tau approximately 3/2. Proof route: show that the stated avalanche distribution is controlled by the universal exponent and finite-size cutoff near the critical point. Formalization route: prove that the stated exponent and cutoff law are compatible with the critical scaling form under TRAWIN normalization.

\tzpsection{Interpretive Role}
The entry now carries the actual avalanche-scaling law instead of malformed prose fragments, so the universality claim is visible mathematically on the page.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Brain-Mimicking Collapse Statistics}: The stunning revelation that when the magnetic field finally shatters and collapses, the size of the sparks perfectly matches the electrical firing patterns of a thinking human brain.
\item \textbf{Three-Halves Criticality Signature}: The exact, repeating decimal number proving that the system isn't just randomly breaking, but is hovering in that perfect, magical sweet spot between total order and total chaos.
\item \textbf{Scale-Free Neuromorphic Behavior}: The realization that whether the magnetic snap is microscopic or massive, it always follows the exact same organic, lifelike mathematical curve.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0583]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0583_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0583] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont SYNAPTIC AVALANCHE EXPONENT (tau = 3/2)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} The TZP quantum-scale constraint prevents singular field behavior from producing
infinite energy density

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``SYNAPTIC AVALANCHE EXPONENT (\textbackslash{}tau = 3/2) is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0583_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
