\tzpanchor{0245}
\tzpentryheader{0245}{Daansphere Manifold}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{d01061cf-3e5a-58f5-ba23-fb8c1cc298d3}}\\
\textbf{PiID} & \tzpcode{1909145648566} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{252}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{951.3894 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.5676 rad}\\
\textbf{TZPID} & \tzpcode{ID0245} & \textbf{Node Dependencies}\quad \tzpidref{0244}\\
\textbf{Registry} & \tzpcode{registry\_id\_0245} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Spherical Fibonacci Address & DAANSphere Coordinate Map\\
\textbf{Closure Support} & Antipodal Registry Scale & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The DAANSphere Manifold entry receives the spherical Fibonacci addressing equations from the DAANSphereNavigationProtocol source, fixing the node coordinates and the antipodal registry relation.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
u_i=\frac{i+1/2}{N},\qquad z_i=1-2u_i,\qquad \theta_i=\frac{2\pi i}{\varphi}
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathbf{x}_i=\left(\sqrt{1-z_i^2}\cos\theta_i,\sqrt{1-z_i^2}\sin\theta_i,z_i\right)
$
\end{adjustbox}
\]
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
N=153600,\qquad \mathbf{x}_{i+N/2}\simeq-\mathbf{x}_i
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $u_i$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
    \item $z_i$: source equation symbol.
    \item $\theta_i$: source equation symbol.
    \item $\pi$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0245 generated source Wolfram model *)
ClearAll[K0245, Cr0245, T, R, A, W, I, N];
eq0245$1 = HoldForm[TZPSequence[$uI == (i + 1/2)/N, zI == 1 - 2*uI, thetaI == ((2*Pi*i)/phi)*$]];
eq0245$2 = HoldForm[$xI == Tuple[Sqrt[1 - zI^2]*CosthetaI, Sqrt[1 - zI^2]*SinthetaI, zI]*$];
eq0245$3 = HoldForm[TZPSequence[$N == 153600, SimilarTo[xIN2, eq] - xI$]];

K0245 = HoldForm[{eq0245$1, eq0245$2, eq0245$3}];

N = "normalized TRAWIN closure object for Daansphere Manifold";
I = "Antipodal Registry Scale integration/comparison layer";
W = "DAANSphere Coordinate Map wave or operator carrier";
A = "Spherical Fibonacci Address admissible action/amplitude condition";
R = "DAANSphere Coordinate Map rotation/curl preservation layer";
T = "Spherical Fibonacci Address local source condition";

Cr0245[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0245 = Cr0245[K0245];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Spherical Fibonacci Address local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ DAANSphere Coordinate Map rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Spherical Fibonacci Address admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ DAANSphere Coordinate Map wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Antipodal Registry Scale integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Daansphere Manifold.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0245] Daansphere Manifold}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
g_{\mu}
=
\frac{\mu}
{MR^2\Omega}.
\end{equation}

\paragraph{Primary Derivation.}
Starting from the scaling law:

\begin{equation}
\mu
=
kMR^2\Omega ,
\end{equation}

divide both sides by the natural rotational magnetic scale:

\begin{equation}
MR^2\Omega .
\end{equation}

This gives:

\begin{equation}
\frac{\mu}{MR^2\Omega}=k .
\end{equation}

Define the dimensionless gyromagnetic coupling constant as:

\begin{equation}
\boxed{
g_{\mu}
=
\frac{\mu}
{MR^2\Omega}.
}
\end{equation}

\paragraph{Interpretation.}
$g_{\mu}$ removes ordinary scale factors from the magnetic moment and isolates the dimensionless coupling strength of the rotating system.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Daansphere Manifold by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Spherical Fibonacci Address}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
u_i=\frac{i+1/2}{N},\qquad z_i=1-2u_i,\qquad \theta_i=\frac{2\pi i}{\varphi}
$
\end{adjustbox}
\]
\noindent This records the source indexing law for DAANSphere node addresses.\par
\noindent\textbf{2. DAANSphere Coordinate Map}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
\mathbf{x}_i=\left(\sqrt{1-z_i^2}\cos\theta_i,\sqrt{1-z_i^2}\sin\theta_i,z_i\right)
$
\end{adjustbox}
\]
\noindent This turns the address into an explicit unit-sphere coordinate.\par
\noindent\textbf{3. Antipodal Registry Scale}\par
\[
\begin{adjustbox}{max width=\linewidth}
$\displaystyle
N=153600,\qquad \mathbf{x}_{i+N/2}\simeq-\mathbf{x}_i
$
\end{adjustbox}
\]
\noindent This closes the manifold support page with the operational node count and antipodal pairing rule.\par

\clearpage
\noindent\textbf{[ID 0245] Daansphere Manifold}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
DAANSphere Manifold is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The DAANSphere is a 153600-dimensional manifold serving as a joint state space for physical and informational degrees of freedom in the Trawin framework; it encodes both quantum and classical variables and provides the domain of the TZP emergence operator. \textbf{Contextual meaning:} The entry reads DAANSphere Manifold as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the tertiary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Spherical Fibonacci Address; DAANSphere Coordinate Map; Antipodal Registry Scale.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
\(g_\mu\) removes ordinary scale factors from the magnetic moment and isolates the dimensionless coupling strength of the rotating system.

\tzpsection{Equation Grounding}
Equation anchors: M sub DAANS = Q times C; dim( M sub DAANS )=153600; and E sub TZP : M sub DAANS to T. Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the tertiary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Extremely High-Dimensional Phase Space Representation}: The mapping of a highly complex, multi-variable quantum state into a vastly expanded geometrical framework.
\item \textbf{Topological Closure at D=153600}: The explicit theoretical assertion that the ultimate bounding geometry of this unified framework closes precisely at 153,600 dimensions.
\item \textbf{Multivariant Coordinate Torus Network}: The highly structured conceptual model linking thousands of independent rotational phases into a single, unified topological object.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0245]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0245_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0245] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Daansphere Manifold}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the DAANSphere is a 153600-dimensional manifold serving as a joint state space for
physical and informational degrees of freedom in the Trawin fram...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``DAANSphere Manifold is valid as a synchronization criterion under the coupling
conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0245_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
