\section*{ID8781: Definition of Xi}
\paragraph{Metadata.}
PiID: 9114079073860 | RTEID: RTE:P34098.5731:T5.9185 | UUID: 137273fd-0889-5c91-968b-f35caf1e2adc

\paragraph{Canonical Statement.}
ar that is +1 if the local field is primarily from TZP⁺ branch and -1 if from TZP⁻ branch (or some continuous measure, say \$\textbackslash{}Xi = \textbackslash{}cos\textbackslash{}alpha\$ where \$\textbackslash{}alpha\$ is angle in DAANSspace between local field direction and some reference orientation). A simulation could transport a marker along field lines to label them plus or minus, thereby generating \$\textbackslash{}Xi(x)\$ in space – akin to dyeing the field lines different colors and seeing where those colors go. Initially, at TZP⁺, \$\textbackslash{}Xi=+1\$ and at TZP⁻, \$\textbackslash{}Xi=-1\$ . Along the loop in 4D, \$\textbackslash{}Xi\$ might be +1 until the loop crosses TZP then flips to -1. The simulation might then produce an image where space near TZP⁺ is colored differently than space near TZP⁻, with a gradient or boundary surface where \$\textbackslash{}Xi\$ transitions. That boundary would in fact be the surface where field from both branches meet and cancel or interact – possibly the equatorial plane of

\paragraph{Canonical Equation.}
\[
\Xi=-1
\]

\paragraph{Dictionary.}
Definition of Xi — Xi=-1

\paragraph{Encyclopedia.}
Definition of Xi is an algebraic definition, written Xi=-1. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
