\tzpanchor{0053}
\tzpentryheader{0053}{Quantum Harmonic Oscillator (TZP-Modified)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{2dc867f0-4a57-5138-aff0-410dc73aee32}}\\
\textbf{PiID} & \tzpcode{0974944592307} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{60}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{205.8108 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.3391 rad}\\
\textbf{TZPID} & \tzpcode{ID0053} & \textbf{Node Dependencies}\quad \tzpidref{0030}\\
\textbf{Registry} & \tzpcode{registry\_id\_0053} & \textbf{Scale}\quad oscillator with TZP correction\\
\textbf{LOC Classification} & QC174.17 quantum oscillator models & QC20 curvature corrections\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: hep-th, math-ph & \\
\textbf{Primary Support} & Baseline Oscillator Energy & TZP Correction Term\\
\textbf{Closure Support} & Modified Oscillator Hamiltonian & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This modifies the familiar quantum harmonic oscillator to include effects of the curved manifold and the TZP; frequency and energy levels shift according to curvature.

\tzpsection{Canonical Equation}
\[
H
=
\frac{p^{2}}{2m}
+
\frac{1}{2}m\omega^{2}q^{2}
+
\delta H
\]
\[
\left[a,a^{\dagger}\right] = 1
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
    \item $\delta$: point-source delta term that anchors the Green-function response.
    \item $\dagger$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0053 generated source Wolfram model *)
ClearAll[K0053, Cr0053, T, R, A, W, I, N];
eq0053$1 = HoldForm[H == p^2/(2*m) + (1/2)*momega^2*q^2 + DiracDelta*H];
eq0053$2 = HoldForm[Commutator[a, a^Dagger] == 1];
eq0053$3 = HoldForm[p^2/(2*m) + (1/2)*momega^2*q^2];
eq0053$4 = HoldForm[DiracDelta*H];

K0053 = HoldForm[{eq0053$1, eq0053$2, eq0053$3, eq0053$4}];

N = "normalized TRAWIN closure object for Quantum Harmonic Oscillator (TZP-Modified)";
I = "Modified Oscillator Hamiltonian integration/comparison layer";
W = "TZP Correction Term wave or operator carrier";
A = "Baseline Oscillator Energy admissible action/amplitude condition";
R = "TZP Correction Term rotation/curl preservation layer";
T = "Baseline Oscillator Energy local source condition";

Cr0053[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0053 = Cr0053[K0053];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Baseline Oscillator Energy local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TZP Correction Term rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Baseline Oscillator Energy admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TZP Correction Term wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Modified Oscillator Hamiltonian integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum Harmonic Oscillator (TZP-Modified).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0053] Quantum Harmonic Oscillator (TZP-Modified)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
H
=
\frac{p^2}{2m}
+
\frac{1}{2}m\omega^2 q^2
+
\delta H .
\end{equation}

\paragraph{Ladder Constraint.}
\begin{equation}
[a,a^\dagger]=1 .
\end{equation}

\paragraph{Primary Derivation.}
The ordinary quantum harmonic oscillator has Hamiltonian:

\begin{equation}
H_0
=
\frac{p^2}{2m}
+
\frac{1}{2}m\omega^2 q^2 .
\end{equation}

Near the TZP, curvature-sensitive or zero-point corrections are collected into a perturbative term $\delta H$:

\begin{equation}
H = H_0+\delta H .
\end{equation}

Substituting $H_0$ gives:

\begin{equation}
\boxed{
H
=
\frac{p^2}{2m}
+
\frac{1}{2}m\omega^2 q^2
+
\delta H .
}
\end{equation}

The ladder algebra remains admissible if the correction preserves the oscillator structure:

\begin{equation}
[a,a^\dagger]=1 .
\end{equation}

\paragraph{Interpretation.}
The TZP-modified oscillator keeps the standard oscillator core while adding a curvature-sensitive correction.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum Harmonic Oscillator (TZP-Modified) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Baseline Oscillator Energy}\par
\[
\frac{p^{2}}{2m} + \frac{1}{2}m\omega^{2}q^{2}
\]
\noindent This is the undeformed oscillator energy inherited from the standard model.\par
\noindent\textbf{2. TZP Correction Term}\par
\[
\delta H
\]
\noindent This carries the curvature and zero-point deformation into the Hamiltonian.\par
\noindent\textbf{3. Modified Oscillator Hamiltonian}\par
\[
H
=
\frac{p^{2}}{2m}
+
\frac{1}{2}m\omega^{2}q^{2}
+
\delta H
\]
\noindent This closes the progression by embedding the familiar oscillator inside the TRAWIN-corrected regime.\par

\clearpage
\noindent\textbf{[ID 0053] Quantum Harmonic Oscillator (TZP-Modified)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum Harmonic Oscillator (TZP-Modified) is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This modifies the familiar quantum harmonic oscillator to include effects of the curved manifold and the TZP; frequency and energy levels shift according to curvature. \textbf{Contextual meaning:} The entry reads Quantum Harmonic Oscillator (TZP-Modified) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This model is the compact laboratory for the quantum branch of the canon. It shows how familiar quantized systems are retained while still carrying TRAWIN-specific corrections into their spectrum and operator algebra. \textbf{Lemma support:} Baseline Oscillator Energy; TZP Correction Term; Modified Oscillator Hamiltonian.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP-modified oscillator keeps the standard oscillator core while adding a curvature-sensitive correction.

\tzpsection{Equation Grounding}
Equation anchors: The TZP-modified harmonic oscillator has Hamiltonian H=12m?p2+12momega2(q)2+deltaHH = ratio 1 2m textbackslash,p to the power 2 + ratio 1 2 momegatextsuperscript 2(q) 2 + delta HH=2m1p2+21momega2(q)2+deltaH, where deltaHdelta HdeltaH encodes curvature-dependent corrections and qqq is measured using the Trawin base unit; ladder operators satisfy [ a,a? ] =1 [ a,a to the power dagger ] =1 [ a,a? ] =1 but acquire curvature-dependent phases. The TZP-modified harmonic oscillator has Hamiltonian H=12m?p2+12momega2(q)2+deltaHH = ratio 1 2m textbackslash,p to the power 2 + ratio 1 2 momegatextsuperscript 2(q) 2 + delta HH=2m1p2+21momega2(q)2+deltaH, where deltaHdelta HdeltaH encodes curvature-dependent corrections and qqq is measured using the Trawin base unit; ladder operators satisfy [ a,a? ] =1 [ a,a to the power dagger ] =1 [ a,a? ] =1 but acquire curvature-dependent phases.

\tzpsection{Interpretive Role}
This model is the compact laboratory for the quantum branch of the canon. It shows how familiar quantized systems are retained while still carrying TRAWIN-specific corrections into their spectrum and operator algebra.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{State-Level Modal Oscillator Tzp Modified}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Modal Spectral Analogue}: nearby spectral language for modes, resonant structure, and admissible oscillation.
\item \textbf{Modal Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0053]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0053_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0053] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum Harmonic Oscillator (TZP-Modified)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this modifies the familiar quantum harmonic oscillator to include effects of the curved
manifold and the TZP; frequency and energy levels shift acc...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum Harmonic Oscillator (TZP-Modified) is valid as a synchronization criterion under
the coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0053_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
