\tzpanchor{0700}
\tzpentryheader{0700}{QUANTUM RECTIFICATION RATCHET}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{b6610f78-829b-5a11-baa5-615db2b8c771}}\\
\textbf{PiID} & \tzpcode{4201995611212} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{707}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2687.1897 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.4277 rad}\\
\textbf{TZPID} & \tzpcode{ID0700} & \textbf{Node Dependencies}\quad \tzpidref{0699}\\
\textbf{Registry} & \tzpcode{registry\_id\_0700} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Aggregate Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records quantum rectification ratchet through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
\Phi_{\mathrm{TZP}}:S^3\longrightarrow S^2.
\]
\[
I_{\mathrm{sync}}(t) = E_{\mathrm{TZP}}(t)e^{i\theta(t)}.
\]
\[
\dot{\theta}(t)=\omega_{\mathrm{lock}}.
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Phi_{\mathrm{TZP}}$: TZP topological bridge map.
    \item $S^3$: three-sphere source domain.
    \item $S^2$: two-sphere target domain.
    \item $I_{\mathrm{sync}}(t)$: energy-information synchronization state.
    \item $E_{\mathrm{TZP}}(t)$: TZP energy amplitude as a function of time.
    \item $\theta(t)$: phase angle or local angular coordinate.
    \item $\omega_{\mathrm{lock}}$: phase-locking angular frequency.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0700 generated source Wolfram model *)
ClearAll[K0700, Cr0700, T, R, A, W, I, N];
eq0700$1 = HoldForm[PhiTZP[S3] -> S2];
eq0700$2 = HoldForm[Isync[t] == ETZP[t]*Exp[I*theta[t]]];
eq0700$3 = HoldForm[thetaPrime[t] == omegaLock];

K0700 = HoldForm[{eq0700$1, eq0700$2, eq0700$3}];

N = "normalized TRAWIN closure object for QUANTUM RECTIFICATION RATCHET";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Aggregate Relation admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Aggregate Relation local source condition";

Cr0700[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0700 = Cr0700[K0700];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Aggregate Relation local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Aggregate Relation admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for QUANTUM RECTIFICATION RATCHET.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0700] QUANTUM RECTIFICATION RATCHET}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Topological Bridge Projection.}
\begin{equation}
\Phi_{\mathrm{TZP}}:S^3\longrightarrow S^2.
\end{equation}

\paragraph{Energy--Information State.}
\begin{equation}
I_{\mathrm{sync}}(t)
=
E_{\mathrm{TZP}}(t)e^{i\theta(t)}.
\end{equation}

\paragraph{Coherence Condition.}
\begin{equation}
\dot{\theta}(t)=\omega_{\mathrm{lock}}.
\end{equation}

\paragraph{Primary Derivation.}
The synchronized bridge is organized by a topological projection:
\begin{equation}
\Phi_{\mathrm{TZP}}:S^3\to S^2.
\end{equation}

Energy amplitude and information phase combine into one complex synchronized state:
\begin{equation}
I_{\mathrm{sync}}(t)
=
E_{\mathrm{TZP}}(t)e^{i\theta(t)}.
\end{equation}

Stable synchronization requires phase locking:
\begin{equation}
\boxed{
\dot{\theta}(t)=\omega_{\mathrm{lock}}.
}
\end{equation}

\paragraph{Interpretation.}
At the TZP, energy transfer and information synchronization are expressed as one phase-locked topological exchange law.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors QUANTUM RECTIFICATION RATCHET by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Aggregate Relation}\par
\[
\Phi_{\mathrm{TZP}}:S^3\longrightarrow S^2.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
I_{\mathrm{sync}}(t) = E_{\mathrm{TZP}}(t)e^{i\theta(t)}.
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\dot{\theta}(t)=\omega_{\mathrm{lock}}.
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0700] QUANTUM RECTIFICATION RATCHET}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
QUANTUM RECTIFICATION RATCHET is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Gamma = omega sub 0 expleft( -frac 2 hbar int sub x sub 1 to the power x sub 2 sqrt 2m(V(x)-E) dx right) otimes eta sub rect. \textbf{Contextual meaning:} The entry reads QUANTUM RECTIFICATION RATCHET as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Aggregate Relation; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
At the TZP, energy transfer and information synchronization are expressed as one phase-locked topological exchange law.

\tzpsection{Equation Grounding}
Equation anchors: mathrm Gamma = omega sub 0 exp( -ratio 2 hbar integral sub x sub 1 to the power x sub 2 sqrt 2m(V(x)-E) dx ) otimes eta sub rect; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Unidirectional Probability Flow}: The brilliant engineering trick of building a microscopic slope in the math, ensuring the random, bouncing quantum noise can only ever drift forward, but gets blocked if it tries to drift backward.
\item \textbf{Brownian-Motor Energy Scavenging}: The deployment of tiny, invisible turnstiles that capture the useless, chaotic heat of the room and instantly convert it into a smooth, driving, focused beam of useful power.
\item \textbf{Second-Law Workaround Exploitation}: The incredibly controversial, borderline illegal mathematical loophole that allows the machine to seemingly generate free work from pure, random static without violating the fundamental laws of thermodynamics.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0700]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0700_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0700] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont QUANTUM RECTIFICATION RATCHET}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records quantum rectification ratchet through the Septenary derivation layer,
using the displayed relations as operational anchors for th...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``QUANTUM RECTIFICATION RATCHET is valid as a synchronization criterion under the coupling
conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0700_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
