\section*{ID8557: Definition of I}
\paragraph{Metadata.}
PiID: 8453142775687 | RTEID: RTE:P33228.7313:T4.4852 | UUID: 79eddd86-3e17-5f5d-adda-eaac340698fb

\paragraph{Canonical Statement.}
cross DAAN-Sphere entrainment channels, integrating the path \$γ(t) \$ against the magnetic flux. Source: [ID 876] DAANS CODEX GATEWAY Canonical Statutory Formula: \$GD \$ := \$∇ \$ × \$(Ψcodex·A⃗DAANS) \$ Formal Technical Dissertation: The gateway operator to internal logic spirals, defined as the curl of the product of the Codex wavefunction and the DAANSphere vector potential. Source: [ID 877] TZP FRACTAL MODULATION INDEX Canonical Statutory Formula: \$ITZP \$ \$:=∑129600\$ \$i=1 wi·δ(ϕi, θi) \$ Formal Technical Dissertation: The index of activation across DAANSphere coordinate points (specifically the 129,600 natural azimuthal nodes) under harmonic weighting \$wi. \$ Source: [ID 878] SYMBOLIC TEMPORAL INTERLACE (STI) Canonical Statutory Formula: \$St \$ := \$∫∞ \$ 0 \$e−λt \$ · \$Φ(t)dt \$ Formal Technical Dissertation: Encodes layered symbolic activation across continuous t

\paragraph{Canonical Equation.}
\[
i=1 wi·δ(ϕi, θi)
\]

\paragraph{Dictionary.}
Definition of I — i=1 wi·δ(ϕi, θi)

\paragraph{Encyclopedia.}
Definition of I is an algebraic definition, written i=1 wi·δ(ϕi, θi). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from w, defining i. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
