\section*{ID9419: Relation: |≤𝜀 Δtri=max𝑖}
\paragraph{Metadata.}
PiID: 7142989467154 | RTEID: RTE:P36576.0687:T3.7174 | UUID: 278ff5df-4af8-5b03-99a0-839804aca570

\paragraph{Canonical Statement.}
ertificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0386], [ID 0300] Node registry\_id\_0387 Support Titles Triple Resonance Match; Domain Window; Normalized Detuning Test Handle If the three carrier frequencies cannot be simultaneously aligned within the stated window, the entry fails. Canonical Equation Links 𝜔1=𝜔2=𝜔3 Dres=\{𝑥: |𝜔𝑖 (𝑥 )−𝜔 𝑗 (𝑥 ) \$|≤𝜀\} Δtri=max𝑖,\$ 𝑗 |𝜔𝑖−𝜔 𝑗 \$|/𝜀≤1\$ [ID 0388] Helicity Cascade Operator TZPID ID0388 UUID 8a6c3352-0b64-5d5a-a11d-16bb53d1d804 Type Operator / Transfer Statement Scale transfer LOC Classification Working routing: QA329 operator theory; QA169 categorical structure arXiv Classification Primary: math.CT; Cross-list: math-ph, cs.LO Canonical Statement This entry develops helicity cascade operator inside the field the

\paragraph{Canonical Equation.}
\[
|≤𝜀} Δtri=max𝑖,
\]

\paragraph{Dictionary.}
Relation: |≤𝜀 Δtri=max𝑖 — |≤𝜀 Δtri=max𝑖

\paragraph{Encyclopedia.}
Relation: |≤𝜀 Δtri=max𝑖 is an algebraic definition, written |≤𝜀 Δtri=max𝑖. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from r, m, a, x. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
