\tzpanchor{0491}
\tzpentryheader{0491}{INTEGRATED INFORMATION \$Phi\_TZP\$ SCALING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{14be77c9-b6fb-50ba-9134-aea3842e8d7a}}\\
\textbf{PiID} & \tzpcode{3011949129833} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{498}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1891.1292 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.1160 rad}\\
\textbf{TZPID} & \tzpcode{ID0491} & \textbf{Node Dependencies}\quad \tzpidref{0490}\\
\textbf{Registry} & \tzpcode{registry\_id\_0491} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 491 defines the scaling of integrated information across the full DAANSsphere. As the system moves toward the Unity State, the local information integration at each node (phij ) must synchronize into a global Phitotal. This scaling follows a non linear trajectory, where the crossing of the 1.185 ratio triggers a global state change, transforming the sphere from a collection of nodes into a single coherent information processor. Emergent Coherence: The point at which the 17.23 bits/transition density becomes a globally shared state. Entanglement Mapping: Monitors the density of non local correlations required to sustain the Mediator Channel.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\langle O_1(0)O_2(r)\rangle\propto r^{-(N-1)}
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $O_1(0)$: source equation symbol.
    \item $O_2(r)$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
    \item $\mathcal{K}_{0491}$: canonical registry object for entry ID 0491.
    \item $\propto$: source equation symbol.
    \item $O$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0491 generated source Wolfram model *)
ClearAll[K0491, Cr0491, T, R, A, W, I, N];
eq0491$1 = HoldForm[$Inner[O1[0]*O2[r]] ? $/r^(N - 1)];

K0491 = HoldForm[{eq0491$1}];

N = "normalized TRAWIN closure object for INTEGRATED INFORMATION \$Phi\_TZP\$ SCALING";
I = "INTEGRATED INFORMATION \$Phi\_TZP\$ SCALING integration/comparison layer";
W = "INTEGRATED INFORMATION \$Phi\_TZP\$ SCALING wave or operator carrier";
A = "INTEGRATED INFORMATION \$Phi\_TZP\$ SCALING admissible action/amplitude condition";
R = "INTEGRATED INFORMATION \$Phi\_TZP\$ SCALING rotation/curl preservation layer";
T = "INTEGRATED INFORMATION \$Phi\_TZP\$ SCALING local source condition";

Cr0491[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0491 = Cr0491[K0491];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ INTEGRATED INFORMATION \textbackslash{}\$Phi\textbackslash{}\_TZP\textbackslash{}\$ SCALING local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ INTEGRATED INFORMATION \textbackslash{}\$Phi\textbackslash{}\_TZP\textbackslash{}\$ SCALING rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ INTEGRATED INFORMATION \textbackslash{}\$Phi\textbackslash{}\_TZP\textbackslash{}\$ SCALING admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ INTEGRATED INFORMATION \textbackslash{}\$Phi\textbackslash{}\_TZP\textbackslash{}\$ SCALING wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ INTEGRATED INFORMATION \textbackslash{}\$Phi\textbackslash{}\_TZP\textbackslash{}\$ SCALING integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for INTEGRATED INFORMATION \textbackslash{}\$Phi\textbackslash{}\_TZP\textbackslash{}\$ SCALING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0491] INTEGRATED INFORMATION \$Phi\_TZP\$ SCALING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
P \longrightarrow M,
\qquad
\mathrm{Struct}(P)=SO(3)\times U(1).
\end{equation}

\begin{equation}
\sigma:M\longrightarrow P.
\end{equation}

\paragraph{Primary Derivation.}
Let $M$ be the base manifold of admissible configurations. Rotational orientation is represented by $SO(3)$, while gauge phase is represented by $U(1)$.

A bundle carrying both data has structure group:
\begin{equation}
SO(3)\times U(1).
\end{equation}

Thus,
\begin{equation}
P\to M,
\qquad
\mathrm{Struct}(P)=SO(3)\times U(1).
\end{equation}

A physical configuration is then a section:
\begin{equation}
\boxed{
\sigma:M\to P.
}
\end{equation}

\paragraph{Interpretation.}
Rotational and gauge-phase data are organized into one configuration bundle.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors INTEGRATED INFORMATION \textbackslash{}\$Phi\textbackslash{}\_TZP\textbackslash{}\$ SCALING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\langle O_1(0)O_2(r)\rangle\propto r^{-(N-1)}
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0491] INTEGRATED INFORMATION \$Phi\_TZP\$ SCALING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
INTEGRATED INFORMATION \textbackslash{}\$Phi\textbackslash{}\_TZP\textbackslash{}\$ SCALING is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 491 defines the scaling of integrated information across the full DAANSsphere. As the system moves toward the Unity State, the local information integration at each node (phij ) must synchronize into a global Phitotal. This scaling follows a non linear trajectory, where the crossing of the 1.185 ratio triggers a global state change, transforming the sphere from a collection of nodes into a single coherent information processor. Emergent Coherence: The point at which the 17.23 bits/transition density becomes a globally shared state. Entanglement Mapping: Monitors the density of non local correlations required to sustain the Mediator Channel.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\langle O_1(0)O_2(r)\rangle\propto r^{-(N-1)}
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 491 defines the scaling of integrated information across the full DAANSsphere. As the system moves toward the Unity State, the local information integration at each node (phij ) must synchronize into a global Phitotal. This scaling follows a non linear trajectory, where the crossing of the 1.185 ratio triggers a global state change, transforming the sphere from a collection of nodes into a single coherent information processor. Emergent Coherence: The point at which the 17.23 bits/transition density becomes a globally shared state. Entanglement Mapping: Monitors the density of non local correlations required to sustain the Mediator Channel.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors INTEGRATED INFORMATION \textbackslash{}\$Phi\textbackslash{}\_TZP\textbackslash{}\$ SCALING by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
INTEGRATED INFORMATION \textbackslash{}\$Phi\textbackslash{}\_TZP\textbackslash{}\$ SCALING; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0491]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0491].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0491] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont INTEGRATED INFORMATION \$Phi\_TZP\$ SCALING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} phi\textbackslash{}\_\textbackslash{}\textbackslash{} = sum\textbackslash{}\_=1\textbackslash{}\textasciicircum{}\textbackslash{}153,600\textbackslash{} phi\textbackslash{}\_j otimes mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``INTEGRATED INFORMATION \textbackslash{}Phi\_\{TZP SCALING is well formed when the total space, base
space, structure group, and projection map are compatible.''\\
\textbf{Proof:} The source statement supplies a bundle-style construction. The CHL reading treats the
base as the proposition carrier, the fiber or structure group as the typed parameter,
and the projection as the categorical morphism that preserves local-to-global structure.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- principal-bundle structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0491].
\par\endgroup
\vfill
\endgroup
\endgroup
