\tzpanchor{0356}
\tzpentryheader{0356}{Encoding--Decoding Adjunction}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{4d38ba5a-bdf0-575b-b2db-882730678369}}\\
\textbf{PiID} & \tzpcode{0360011330530} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{363}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1382.4271 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.2778 rad}\\
\textbf{TZPID} & \tzpcode{ID0356} & \textbf{Node Dependencies}\quad \tzpidref{0355}\\
\textbf{Registry} & \tzpcode{registry\_id\_0356} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
There exists an adjunction between the encoding functor and a decoding functor with unit and counit natural transformations satisfying the triangle identities. This guarantees that encoding followed by decoding returns the original data up to natural isomorphism.

\tzpsection{Canonical Equation}
\[
epsilon_T = \epsilon_0 \cdot \exp\left( \frac{\alpha_T}{\chi_T} \cdot \frac{V(\phi)}{P_T} \right) \equiv \frac{1}{\mu_0 c_{\text{eff}}^2(r)}
\]
\[
epsilon_T = \epsilon_0 \cdot \exp\left( \frac{\alpha_T}{\chi_T} \cdot \frac{V(\phi)}{P_T} \right) \equiv \frac{1}{\mu_0 c_{\text{eff}}^2(r)}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $V$: auxiliary target state or comparison variable.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $P_T$: source equation symbol.
    \item $\mu_0$: vacuum permeability constant.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0356 generated source Wolfram model *)
ClearAll[K0356, Cr0356, T, R, A, W, I, N];
eq0356$1 = HoldForm[epsilonT == epsilon0*exp[(alphaT/chiT)*(V[phi]/PT)]*equiv[1/(mu0*c^2*r)]];
eq0356$2 = HoldForm[epsilonT == epsilon0*exp[(alphaT/chiT)*(V[phi]/PT)]*equiv[1/(mu0*c^2*r)]];
eq0356$3 = HoldForm[TZPSequence[FORMAL*TECHNICAL*(DISSERTATION:The*Vacuum*Permittivity*Shift), denoted*as]];

K0356 = HoldForm[{eq0356$1, eq0356$2, eq0356$3}];

N = "normalized TRAWIN closure object for Encoding--Decoding Adjunction";
I = "Normalized Output integration/comparison layer";
W = "Composable Action wave or operator carrier";
A = "Carrier Map admissible action/amplitude condition";
R = "Composable Action rotation/curl preservation layer";
T = "Carrier Map local source condition";

Cr0356[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0356 = Cr0356[K0356];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Carrier Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Composable Action rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Carrier Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Composable Action wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Output integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Encoding--Decoding Adjunction.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0356] Encoding--Decoding Adjunction}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
E_{\mathrm{Cas}}(L)
=
-\frac{\pi^2}{720L^3}(1+\epsilon).
\end{equation}

\paragraph{Primary Derivation.}
For two ideal parallel boundaries separated by distance $L$, the standard scalar form of Casimir-type energy per unit area scales as:

\begin{equation}
E_{\mathrm{Cas}}^{(0)}(L)
=
-\frac{\pi^2}{720L^3}.
\end{equation}

In the Trawinistic setting, curvature, topology, and TZP boundary corrections are collected into a dimensionless perturbation $\epsilon$.

Thus,

\begin{equation}
E_{\mathrm{Cas}}(L)
=
E_{\mathrm{Cas}}^{(0)}(L)(1+\epsilon).
\end{equation}

Substitution gives:

\begin{equation}
\boxed{
E_{\mathrm{Cas}}(L)
=
-\frac{\pi^2}{720L^3}(1+\epsilon).
}
\end{equation}

\paragraph{Interpretation.}
Casimir-type behavior arises from boundary-altered vacuum modes, with $\epsilon$ collecting TRAWIN corrections.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Encoding--Decoding Adjunction by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Carrier Map}\par
\[
epsilon_T = \epsilon_0 \cdot \exp\left( \frac{\alpha_T}{\chi_T} \cdot \frac{V(\phi)}{P_T} \right) \equiv \frac{1}{\mu_0 c_{\text{eff}}^2(r)}
\]
\noindent This names the entry as an actual map between carrier domains rather than a loose metaphor.\par
\noindent\textbf{2. Composable Action}\par
\[
epsilon_T = \epsilon_0 \cdot \exp\left( \frac{\alpha_T}{\chi_T} \cdot \frac{V(\phi)}{P_T} \right) \equiv \frac{1}{\mu_0 c_{\text{eff}}^2(r)}
\]
\noindent This inserts the map into the ordered TRAWIN chain and makes composition explicit.\par
\noindent\textbf{3. Normalized Output}\par
\[
FORMAL TECHNICAL DISSERTATION:The Vacuum Permittivity Shift, denoted as
\]
\noindent This closes the entry by requiring that the output land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0356] Encoding--Decoding Adjunction}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Encoding--Decoding Adjunction is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} There exists an adjunction between the encoding functor and a decoding functor with unit and counit natural transformations satisfying the triangle identities. This guarantees that encoding followed by decoding returns the original data up to natural isomorphism. \textbf{Contextual meaning:} The entry reads Encoding--Decoding Adjunction as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Casimir-type behavior arises from boundary-altered vacuum modes, with collecting TRAWIN corrections.

\tzpsection{Equation Grounding}
Equation anchors: epsilon sub T = epsilon sub 0 dot exp( ratio alpha sub T chi sub T dot ratio V(phi) P sub T ) equiv ratio 1 mu sub 0 c sub eff to the power 2(r); \$epsilon sub T = epsilon sub 0 dot exp( ratio alpha sub T chi sub T dot ratio V(phi) P sub T ) equiv ratio 1 mu sub 0 c sub eff to the power 2(r); and FORMAL TECHNICAL DISSERTATION:The Vacuum Permittivity Shift, denoted as. Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Reversible Data Projection Mapping}: The formal mathematical relationship guaranteeing that every encoded state can be losslessly transformed back to its original physical form.
\item \textbf{Exponential Attenuation Compensation}: The explicit inverse function used to artificially boost signals that were degraded during the spatial encoding process.
\item \textbf{Adjoint Informational Symmetry}: The structural proof that the process of writing data to the manifold is the exact mathematical mirror of reading it back.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0356]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0356_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0356] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Encoding--Decoding Adjunction}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} there exists an adjunction between the encoding functor and a decoding functor with unit
and counit natural transformations satisfying the triangle...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Encoding--Decoding Adjunction is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0356_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
