\section*{ID9397: Relation: =𝑥∈R𝑛 |Φ(𝑥}
\paragraph{Metadata.}
PiID: 4172543709069 | RTEID: RTE:P36490.6379:T3.5767 | UUID: eddc286c-907c-579b-ac84-f7772add5f7a

\paragraph{Canonical Statement.}
1] Isabelle Certificate Lean Certificate Coq Certificate lemmaid0771\_thelemniscatic\_zero\_point\_set:sorry theoremid0771\_thelemniscatic\_zero\_point\_set Theoremid0771\_thelemniscatic\_zero\_point\_set Dependencies and Test Handle Dependencies [ID 0770], [ID 0700] Node registry\_id\_0771 Support Titles Canonical Definition; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links \$=𝑥∈R𝑛 |Φ(𝑥\$ )=0 Jout=· · · Aadm(Jout )=· · · [ID 0772] THE PROTON-GATED MANIFOLD OPERATOR TZPID ID0772 UUID ad5977e6-91c6-59c9-8ba3-fc1316eb6aed Type Geometric / Topological Statement Scale geometric LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math.DG; Cross-list: math-ph, math.AT Canonical Statement This entry develops the pro

\paragraph{Canonical Equation.}
\[
=𝑥∈R𝑛 |Φ(𝑥
\]

\paragraph{Dictionary.}
Relation: =𝑥∈R𝑛 |Φ(𝑥 — =𝑥∈R𝑛 |Φ(𝑥

\paragraph{Encyclopedia.}
Relation: =𝑥∈R𝑛 |Φ(𝑥 is an algebraic definition, written =𝑥∈R𝑛 |Φ(𝑥. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
