\tzpanchor{0207}
\tzpentryheader{0207}{Helicity Transfer Constraint}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{bcec169a-98f5-5847-aeb1-08b61169c38e}}\\
\textbf{PiID} & \tzpcode{9756659334461} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{214}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{803.8270 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.3245 rad}\\
\textbf{TZPID} & \tzpcode{ID0207} & \textbf{Node Dependencies}\quad \tzpidref{0206}\\
\textbf{Registry} & \tzpcode{registry\_id\_0207} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Total Helicity Accounting & Conserved Transfer\\
\textbf{Closure Support} &  & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In the coupled phonon--magnon system, the total helicity H\_total = H\_acoustic + H\_magnetic is conserved.

\tzpsection{Canonical Equation}
\[
H_{\mathrm{total}} = H_{\mathrm{acoustic}} + H_{\mathrm{magnetic}}
\]
\[
\partial_t H_{\mathrm{total}} = 0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H_{\mathrm{total}}$: total helicity conserved in the coupled phonon--magnon system.
    \item $H_{\mathrm{acoustic}}$: acoustic-channel helicity contribution.
    \item $H_{\mathrm{magnetic}}$: magnetic-channel helicity contribution.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0207 generated source Wolfram model *)
ClearAll[K0207, Cr0207, T, R, A, W, I, N];
eq0207$1 = HoldForm[HTotal == HAcoustic + HMagnetic];
eq0207$2 = HoldForm[D[HTotal, t] == 0];

K0207 = HoldForm[{eq0207$1, eq0207$2}];

N = "normalized TRAWIN closure object for Helicity Transfer Constraint";
I = "Helicity Transfer Constraint integration/comparison layer";
W = "Conserved Transfer wave or operator carrier";
A = "Total Helicity Accounting admissible action/amplitude condition";
R = "Conserved Transfer rotation/curl preservation layer";
T = "Total Helicity Accounting local source condition";

Cr0207[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0207 = Cr0207[K0207];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Total Helicity Accounting local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Conserved Transfer rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Total Helicity Accounting admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Conserved Transfer wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Helicity Transfer Constraint integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Helicity Transfer Constraint.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0207] Helicity Transfer Constraint}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
H_{\mathrm{total}}=H_{\mathrm{acoustic}}+H_{\mathrm{magnetic}},\qquad \partial_t H_{\mathrm{total}}=0.
\]
\paragraph{Conservation Derivation.}
Differentiate the total-helicity decomposition with respect to time:
\[
\partial_t H_{\mathrm{total}}=\partial_t H_{\mathrm{acoustic}}+\partial_t H_{\mathrm{magnetic}}.
\]
Applying the stated conservation constraint gives
\[
0=\partial_t H_{\mathrm{acoustic}}+\partial_t H_{\mathrm{magnetic}},\qquad \partial_t H_{\mathrm{acoustic}}=-\partial_t H_{\mathrm{magnetic}}.
\]
\paragraph{Interpretation.}
Within the coupled model, helicity can be transferred between acoustic and magnetic channels while the total remains invariant.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The conserved-sum relation makes any acoustic helicity transfer compensating: within the coupled model, its time variation is balanced by the magnetic helicity variation.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Total Helicity Accounting}\par
\[
H_{\mathrm{total}} = H_{\mathrm{acoustic}} + H_{\mathrm{magnetic}}
\]
\noindent The coupled phonon--magnon system carries a total helicity composed of acoustic and magnetic contributions.\par
\noindent\textbf{2. Conserved Transfer}\par
\[
\partial_t H_{\mathrm{total}}=0
\]
\[
\partial_t H_{\mathrm{acoustic}}=-\partial_t H_{\mathrm{magnetic}}
\]
\noindent Under the stated conservation law, exchange in one channel is balanced by the other.\par

\clearpage
\noindent\textbf{[ID 0207] Helicity Transfer Constraint}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small

\tzpsection{Definition}

A helicity transfer constraint is a conservation law for a coupled phonon--magnon system. It states that acoustic and magnetic contributions may exchange helicity while their combined total remains fixed.

\tzpsection{Contextual Meaning}

In this entry helicity measures twistedness or linking carried by the coupled channels. A change in the acoustic portion is therefore paired with an opposing change in the magnetic portion, rather than interpreted as new helicity being created by the interaction.

\tzpsection{Formal Statement}

\[
H_{\mathrm{total}}=H_{\mathrm{acoustic}}+H_{\mathrm{magnetic}},\qquad
\partial_t H_{\mathrm{total}}=0
\]

\tzpsection{Derivable Consequences}

Differentiating the sum gives \(\partial_t H_{\mathrm{acoustic}}=-\partial_t H_{\mathrm{magnetic}}\) under the conservation condition. The sourced text further identifies controlled opposite-helicity acoustic vortices as a route for testing compensating magnetic-helicity change.

\tzpsection{Lemma Support}

The aligned source names this entry as a conservation law, gives the sum \(H_{\mathrm{total}}=H_{\mathrm{acoustic}}+H_{\mathrm{magnetic}}\), and states that coupling transfers helicity between sound and magnetic fields without creating or destroying it.

\tzpsection{Technical Interpretation}

The equation is an accounting constraint on internal transfer, not by itself an energy-conversion efficiency law. It fixes an invariant quantity against which a phonon--magnon interaction model can be checked.

\tzpsection{Equation Grounding}

\(H_{\mathrm{total}}\) is total helicity of the coupled system; \(H_{\mathrm{acoustic}}\) is the acoustic-channel contribution; and \(H_{\mathrm{magnetic}}\) is the magnetic-channel contribution. The derivative equality expresses the stated conservation.

\tzpsection{Interpretive Role}

This entry carries the tertiary arc from coupling mechanisms to a topological invariant: exchange may occur, but the conserved combined helicity restricts admissible transfer histories.

\tzpsection{TZP Thesaurus}

\noindent \textbf{Helicity}: A measure of twistedness or linking carried by a field configuration. \enspace\textbullet\enspace \textbf{Helicity Transfer}: Redistribution of helicity between acoustic and magnetic channels under coupling. \enspace\textbullet\enspace \textbf{Conservation Constraint}: A relation requiring the combined helicity to remain invariant during transfer.\par

\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0207].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0207] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Helicity Transfer Constraint}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} Within the stated coupled system,
\[
H_{\mathrm{total}}=H_{\mathrm{acoustic}}+H_{\mathrm{magnetic}},\qquad \partial_t H_{\mathrm{total}}=0.
\]
\textbf{Logic Validation:}\\
\textbf{Proposition:} Conservation of total helicity entails balanced transfer between the acoustic and magnetic channels.\\
\textbf{Proof:} Differentiation of the additive decomposition yields \(\partial_t H_{\mathrm{total}}=\partial_t H_{\mathrm{acoustic}}+\partial_t H_{\mathrm{magnetic}}\). Substitution of the sourced conservation condition gives \(\partial_t H_{\mathrm{acoustic}}=-\partial_t H_{\mathrm{magnetic}}\).\\
\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal conservation consequence under the stated model\\
\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL obligation\\
\textbf{Physical Status:} THEORETICAL -- empirical realization remains model-dependent
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0207].
\par\endgroup
\vfill
\endgroup
\endgroup
