\tzpanchor{0359}
\tzpentryheader{0359}{Uniform Base Manifold}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e972acd1-c283-5261-b2c2-012df68943dc}}\\
\textbf{PiID} & \tzpcode{0011330530548} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{366}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1394.0767 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.2970 rad}\\
\textbf{TZPID} & \tzpcode{ID0359} & \textbf{Node Dependencies}\quad \tzpidref{0358}\\
\textbf{Registry} & \tzpcode{registry\_id\_0359} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The DAANSsphere defines a uniform base manifold by generating direction vectors via Fibonacci spiral sampling. Each axis corresponds to a unit direction, an antipodal pair and a depth parameter, giving radial points through an exponential mapping.

\tzpsection{Canonical Equation}
\[
K_{fractal}(\hat{\mathbf{n}}) = \sum_{k=1}^{\infty} s^{-k} G(\hat{\mathbf{n}}, r \cdot s^k) e^{i\phi_k}
\]
\[
r_{i,k} = \exp(t_{i,k})
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $K_{fractal}$: source equation symbol.
    \item $n$: integer mode index.
    \item $G$: source equation symbol.
    \item $\phi_k$: flux, phase, or topological map term in the source equation.
    \item $r_{i,k}$: source equation symbol.
    \item $t_{i,k}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0359 generated source Wolfram model *)
ClearAll[K0359, Cr0359, T, R, A, W, I, N];
eq0359$1 = HoldForm[KFractal[hat[n]] == (SumK1^Infinity*G[hat[n], r*s^k]*Exp[I*phiK])/s^k];
eq0359$2 = HoldForm[rIk == exp[tIk]];

K0359 = HoldForm[{eq0359$1, eq0359$2}];

N = "normalized TRAWIN closure object for Uniform Base Manifold";
I = "Topological Closure integration/comparison layer";
W = "Compatibility Law wave or operator carrier";
A = "Geometric Carrier admissible action/amplitude condition";
R = "Compatibility Law rotation/curl preservation layer";
T = "Geometric Carrier local source condition";

Cr0359[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0359 = Cr0359[K0359];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Geometric Carrier local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Compatibility Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Geometric Carrier admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Compatibility Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Uniform Base Manifold.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0359] Uniform Base Manifold}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
c_i=c_i(\mu,d_{\mathrm{eff}}).
\end{equation}

\paragraph{Flow Equation.}
\begin{equation}
\frac{\mathrm{d}c_i}{\mathrm{d}\ln\mu}
=
f_i(c_j,d_{\mathrm{eff}}).
\end{equation}

\paragraph{Primary Derivation.}
If couplings depend on scale and effective dimension, then derived constants may also become scale-sensitive.

Represent each effective constant as:

\begin{equation}
c_i=c_i(\mu,d_{\mathrm{eff}}).
\end{equation}

The natural flow parameter for scale comparison is $\ln\mu$.  
Differentiating with respect to this parameter gives:

\begin{equation}
\boxed{
\frac{\mathrm{d}c_i}{\mathrm{d}\ln\mu}
=
f_i(c_j,d_{\mathrm{eff}}).
}
\end{equation}

\paragraph{Interpretation.}
Constants are treated as effective parameters that may run under TRAWIN scale and dimension flow.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Uniform Base Manifold by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Geometric Carrier}\par
\[
K_{fractal}(\hat{\mathbf{n}}) = \sum_{k=1}^{\infty} s^{-k} G(\hat{\mathbf{n}}, r \cdot s^k) e^{i\phi_k}
\]
\noindent This fixes the effective geometry or carrier space named by the entry title.\par
\noindent\textbf{2. Compatibility Law}\par
\[
r_{i,k} = \exp(t_{i,k})
\]
\noindent This makes the geometry admissible by imposing its internal compatibility law.\par
\noindent\textbf{3. Topological Closure}\par
\[
K_{fractal}(\hat{\mathbf{n}}) = \sum_{k=1}^{\infty} s^{-k} G(\hat{\mathbf{n}}, r \cdot s^k) e^{i\phi_k}
\]
\noindent This closes the entry by tying the local structure to a global topological invariant.\par

\clearpage
\noindent\textbf{[ID 0359] Uniform Base Manifold}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Uniform Base Manifold is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The DAANSsphere defines a uniform base manifold by generating direction vectors via Fibonacci spiral sampling. Each axis corresponds to a unit direction, an antipodal pair and a depth parameter, giving radial points through an exponential mapping. \textbf{Contextual meaning:} The entry reads Uniform Base Manifold as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Geometric Carrier; Compatibility Law; Topological Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Constants are treated as effective parameters that may run under TRAWIN scale and dimension flow.

\tzpsection{Equation Grounding}
Equation anchors: K sub fractal (hat n ) = sum sub k=1 to the power infinity s to the power -k G(hat n , r dot s to the power k) e to the power iphi sub k; r sub i,k = exp(t sub i,k ); and \$K sub fractal (hat n ) = sum sub k=1 to the power infinity s to the power -k G(hat n , r dot s to the power k) e to the power iphi sub k. Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Isotropic Metric Expansion}: The mathematical series representing a smooth, uniform spatial geometry completely free of localized warping or defects.
\item \textbf{Spherical Harmonic Background}: The use of standardized continuous wavefunctions as the blank canvas upon which more complex, singular structures are built.
\item \textbf{Baseline Geometric Homogeneity}: The property of a space looking and behaving exactly the same in every direction from any given starting point.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0359]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0359_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0359] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Uniform Base Manifold}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the DAANSsphere defines a uniform base manifold by generating direction vectors via
Fibonacci spiral sampling

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Uniform Base Manifold is valid when the stated geometric or topological relation
preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0359_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
