\tzpanchor{0787}
\tzpentryheader{0787}{THZ DENSITY POTENTIAL}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{c21e43aa-3733-581f-8b03-ea784abbd575}}\\
\textbf{PiID} & \tzpcode{3281609631859} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{794}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3017.2636 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.9715 rad}\\
\textbf{TZPID} & \tzpcode{ID0787} & \textbf{Node Dependencies}\quad \tzpidref{0786}\\
\textbf{Registry} & \tzpcode{registry\_id\_0787} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records thz density potential through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0787}}:\mathcal{X}_{\mathrm{id0787}}\longrightarrow\mathcal{Y}_{\mathrm{id0787}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0787}})=\mathcal{O}_{\mathrm{id0787}}
\]
\[
\mathcal{O}_{\mathrm{id0787}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0787}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0787}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0787}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0787 generated source Wolfram model *)
ClearAll[K0787, Cr0787, T, R, A, W, I, N];
eq0787$1 = HoldForm[Oid0787[Xid0787] -> Yid0787];
eq0787$2 = HoldForm[NTRAWIN[OId0787] == OId0787];
eq0787$3 = HoldForm[Element[OId0787[x], YAdm]];

K0787 = HoldForm[{eq0787$1, eq0787$2, eq0787$3}];

N = "normalized TRAWIN closure object for THZ DENSITY POTENTIAL";
I = "THZ DENSITY POTENTIAL integration/comparison layer";
W = "THZ DENSITY POTENTIAL wave or operator carrier";
A = "THZ DENSITY POTENTIAL admissible action/amplitude condition";
R = "THZ DENSITY POTENTIAL rotation/curl preservation layer";
T = "THZ DENSITY POTENTIAL local source condition";

Cr0787[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0787 = Cr0787[K0787];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ THZ DENSITY POTENTIAL local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ THZ DENSITY POTENTIAL rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ THZ DENSITY POTENTIAL admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ THZ DENSITY POTENTIAL wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ THZ DENSITY POTENTIAL integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for THZ DENSITY POTENTIAL.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0787] THZ DENSITY POTENTIAL}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0787}}:\mathcal{X}_{\mathrm{id0787}}\longrightarrow\mathcal{Y}_{\mathrm{id0787}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0787}})=\mathcal{O}_{\mathrm{id0787}}
\]
\[
\mathcal{O}_{\mathrm{id0787}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The expression \( \mathcal{O}_{\mathrm{id0787}}:\mathcal{X}_{\mathrm{id0787}}\longrightarrow\mathcal{Y}_{\mathrm{id0787}} \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. Interpreted through TRAWIN, the equation functions as the integral carrier for the entry’s information content. Within the CHL view, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors THZ DENSITY POTENTIAL by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0787}}:\mathcal{X}_{\mathrm{id0787}}\longrightarrow\mathcal{Y}_{\mathrm{id0787}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0787}})=\mathcal{O}_{\mathrm{id0787}}
\]
\[
\mathcal{O}_{\mathrm{id0787}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0787] THZ DENSITY POTENTIAL}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
THZ DENSITY POTENTIAL is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} rho sub THZ :=langle0|T to the power 00 |0rangle. \textbf{Contextual meaning:} The entry reads THZ DENSITY POTENTIAL as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, THZ DENSITY POTENTIAL is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: rho sub THZ :=0|T to the power 00 lvert 0; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Terahertz Gap Bridging}: The incredible engineering challenge of building electronics that can hum and vibrate fast enough to catch the blindingly quick, high-pitched energy squeaks leaking out of the core.
\item \textbf{Sub-Millimeter Wavelength Confinement}: The terrifying realization that the energy waves are now so incredibly small they can literally slip right through the microscopic gaps between the atoms in the solid metal walls.
\item \textbf{Phonon-Photon High-Frequency Resonance}: The chaotic, buzzing zone where the physical rattling of the metal chamber and the invisible pulses of light are vibrating so fast they become mathematically indistinguishable from each other.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0787]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0787].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0787] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont THZ DENSITY POTENTIAL}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} THZ DENSITY POTENTIAL is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``THZ DENSITY POTENTIAL is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0787].
\par\endgroup
\vfill
\endgroup
\endgroup
