\tzpanchor{0717}
\tzpentryheader{0717}{BIJECTIVE MAPPING VERIFICATION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{5097506a-7920-52e6-8712-a1e136143d8c}}\\
\textbf{PiID} & \tzpcode{9608640344181} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{724}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2749.3212 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.5300 rad}\\
\textbf{TZPID} & \tzpcode{ID0717} & \textbf{Node Dependencies}\quad \tzpidref{0716}\\
\textbf{Registry} & \tzpcode{registry\_id\_0717} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records bijective mapping verification through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0717}}:\mathcal{X}_{\mathrm{id0717}}\longrightarrow\mathcal{Y}_{\mathrm{id0717}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0717}})=\mathcal{O}_{\mathrm{id0717}}
\]
\[
\mathcal{O}_{\mathrm{id0717}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0717}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0717}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0717}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0717 generated source Wolfram model *)
ClearAll[K0717, Cr0717, T, R, A, W, I, N];
eq0717$1 = HoldForm[Oid0717[Xid0717] -> Yid0717];
eq0717$2 = HoldForm[NTRAWIN[OId0717] == OId0717];
eq0717$3 = HoldForm[Element[OId0717[x], YAdm]];

K0717 = HoldForm[{eq0717$1, eq0717$2, eq0717$3}];

N = "normalized TRAWIN closure object for BIJECTIVE MAPPING VERIFICATION";
I = "BIJECTIVE MAPPING VERIFICATION integration/comparison layer";
W = "BIJECTIVE MAPPING VERIFICATION wave or operator carrier";
A = "BIJECTIVE MAPPING VERIFICATION admissible action/amplitude condition";
R = "BIJECTIVE MAPPING VERIFICATION rotation/curl preservation layer";
T = "BIJECTIVE MAPPING VERIFICATION local source condition";

Cr0717[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0717 = Cr0717[K0717];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ BIJECTIVE MAPPING VERIFICATION local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ BIJECTIVE MAPPING VERIFICATION rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ BIJECTIVE MAPPING VERIFICATION admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ BIJECTIVE MAPPING VERIFICATION wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ BIJECTIVE MAPPING VERIFICATION integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for BIJECTIVE MAPPING VERIFICATION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0717] BIJECTIVE MAPPING VERIFICATION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0717}}:\mathcal{X}_{\mathrm{id0717}}\longrightarrow\mathcal{Y}_{\mathrm{id0717}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0717}})=\mathcal{O}_{\mathrm{id0717}}
\]
\[
\mathcal{O}_{\mathrm{id0717}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0717}})=\mathcal{O}_{\mathrm{id0717}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. From the TRAWIN perspective, the equation functions as the mapping carrier for the entry’s information content. According to CHL, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors BIJECTIVE MAPPING VERIFICATION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0717}}:\mathcal{X}_{\mathrm{id0717}}\longrightarrow\mathcal{Y}_{\mathrm{id0717}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0717}})=\mathcal{O}_{\mathrm{id0717}}
\]
\[
\mathcal{O}_{\mathrm{id0717}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0717] BIJECTIVE MAPPING VERIFICATION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
BIJECTIVE MAPPING VERIFICATION is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} forall y in A, exists! x in B : f(x) = y implies |Unique(f(B))| equiv |B|. \textbf{Contextual meaning:} The entry reads BIJECTIVE MAPPING VERIFICATION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, BIJECTIVE MAPPING VERIFICATION is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: H=- i=1 cap64; H sub sub max=log(64)=6; and =R to the power - 3. Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Perfect State-Reversibility Proof}: The mathematical guarantee that every single possible input into the equation produces one, unique output, meaning you can always perfectly run the physics backward to find out where you started.
\item \textbf{Information-Loss Nullification}: The rigorous check ensuring that no two different quantum states ever accidentally blur into the same result, proving that absolutely zero data is destroyed during the process.
\item \textbf{Isomorphic Space Translation}: The mapping that takes a highly complex, impossible-to-solve geometric shape and perfectly translates it, point-for-point, into a simple, flat plane where the math is incredibly easy.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0717]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0717].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0717] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont BIJECTIVE MAPPING VERIFICATION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} BIJECTIVE MAPPING VERIFICATION is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``BIJECTIVE MAPPING VERIFICATION is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0717].
\par\endgroup
\vfill
\endgroup
\endgroup
