\tzpanchor{0023}
\tzpentryheader{0023}{TZP Potential Term}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{1786a77f-3042-596a-ab6d-7ec10b409a08}}\\
\textbf{PiID} & \tzpcode{3383279502884} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{30}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{89.3141 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.1472 rad}\\
\textbf{TZPID} & \tzpcode{ID0023} & \textbf{Node Dependencies}\quad \tzpidref{0001}\\
\textbf{Registry} & \tzpcode{registry\_id\_0023} & \textbf{Scale}\quad potential\\
\textbf{LOC Classification} & QC174.45 potential theory & QC178 gravitation and field energy\\
\textbf{arXiv Classification} & Primary: gr-qc \quad Cross-list: hep-th, math-ph & \\
\textbf{Primary Support} & Geodesic Distance from the Anchor & Exponential Potential Profile\\
\textbf{Closure Support} & Anchor-Value Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The TZP potential term models the energetic influence of proximity to the zero point. It decays exponentially with geodesic distance when measured in units of the Trawin base scale.

\tzpsection{Canonical Equation}
\[
V_{T}(x)
=
\lambda
\exp\!\left(
-\frac{d(x,p)}{u_{T}}
\right)
\]
\[
V_{T}(p)=\lambda
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $V_{T}(x)$: TZP potential or suppression kernel between source and response points.
    \item $T$: source equation symbol.
    \item $\lambda$: cosmological or lemniscatic branch parameter in the entry relation.
    \item $u_{T}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0023 generated source Wolfram model *)
ClearAll[K0023, Cr0023, T, R, A, W, I, N];
eq0023$1 = HoldForm[VT[x] == lambdaexp[-(Tuple[d[x, p]]/uT)]];
eq0023$2 = HoldForm[VT[p] == lambda];
eq0023$3 = HoldForm[d[x, p]];

K0023 = HoldForm[{eq0023$1, eq0023$2, eq0023$3}];

N = "normalized TRAWIN closure object for TZP Potential Term";
I = "Anchor-Value Closure integration/comparison layer";
W = "Exponential Potential Profile wave or operator carrier";
A = "Geodesic Distance from the Anchor admissible action/amplitude condition";
R = "Exponential Potential Profile rotation/curl preservation layer";
T = "Geodesic Distance from the Anchor local source condition";

Cr0023[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0023 = Cr0023[K0023];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Geodesic Distance from the Anchor local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Exponential Potential Profile rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Geodesic Distance from the Anchor admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Exponential Potential Profile wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Anchor-Value Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP Potential Term.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0023] TZP Potential Term}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
V_T(x)
=
\lambda
\exp\left(
-\frac{d(x,p)}{u_T}
\right).
\end{equation}

\paragraph{Primary Derivation.}
Let $d(x,p)$ be the geodesic distance from a point $x$ to the TZP.  
A potential localized around $p$ should be strongest at $x=p$ and decay with distance.

At the zero point:

\begin{equation}
d(p,p)=0 .
\end{equation}

Therefore:

\begin{equation}
V_T(p)=\lambda e^0=\lambda .
\end{equation}

To create exponential decay away from $p$, scale distance by the Trawin base unit $u_T$:

\begin{equation}
\exp\left(-\frac{d(x,p)}{u_T}\right).
\end{equation}

Multiplying by coupling constant $\lambda$ gives:

\begin{equation}
\boxed{
V_T(x)
=
\lambda
\exp\left(
-\frac{d(x,p)}{u_T}
\right).
}
\end{equation}

\paragraph{Interpretation.}
The TZP potential is a localized exponential well or source centered at $p$, controlled by the coupling $\lambda$ and decay scale $u_T$.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP Potential Term by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Geodesic Distance from the Anchor}\par
\[
d(x,p)
\]
\noindent This gives the geometric separation that controls how strongly the zero point should influence the field configuration.\par
\noindent\textbf{2. Exponential Potential Profile}\par
\[
V_{T}(x)
=
\lambda
\exp\!\left(
-\frac{d(x,p)}{u_{T}}
\right)
\]
\noindent This turns anchor distance into a localized energy term scaled by the Trawin base unit.\par
\noindent\textbf{3. Anchor-Value Closure}\par
\[
V_{T}(p)=\lambda
\]
\noindent This closes the progression by fixing the maximum potential strength at the zero point itself.\par

\clearpage
\noindent\textbf{[ID 0023] TZP Potential Term}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP Potential Term is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The TZP potential V sub T(x)Vtextbackslash sub T (x)V sub T(x) is defined near the zero point as V sub T(x)=lambda exp (-d(x,p)u sub T)Vtextbackslash sub T (x)=lambdatextbackslash,textbackslash expbigl(-ratio d(x,p) utextbackslash sub T bigr)V sub T(x)=lambdaexp(-u sub Td(x,p)), where lambda is a coupling constant and d(x,p)d(x,p)d(x,p) is the geodesic distance from xxx to ppp. \textbackslash{}. \textbf{Contextual meaning:} The entry reads TZP Potential Term as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Geodesic Distance from the Anchor; Exponential Potential Profile; Anchor-Value Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The TZP potential is a localized exponential well or source centered at p, controlled by the coupling and decay scale u sub T.

\tzpsection{Equation Grounding}
Equation anchors: The TZP potential V T(x)Vtextbackslash T (x)V T(x) is defined near the zero point as V T(x)=lambda expu2061(-d(x,p)u T)Vtextbackslash T (x)=lambdatextbackslash,textbackslash expbigl(-ratio d(x,p) utextbackslash T bigr)V T(x)=lambdaexp(-u Td(x,p)), where lambda is a coupling constant and d(x,p)d(x,p)d(x,p) is the geodesic distance from xxx to ppp. The TZP potential V T(x)Vtextbackslash T (x)V T(x) is defined near the zero point as V T(x)=lambda expu2061(-d(x,p)u T)Vtextbackslash T (x)=lambdatextbackslash,textbackslash expbigl(-ratio d(x,p) utextbackslash T bigr)V T(x)=lambdaexp(-u Td(x,p)), where lambda is a coupling constant and d(x,p)d(x,p)d(x,p) is the geodesic distance from xxx to ppp.

\tzpsection{Interpretive Role}
This potential supplies the localized energetic term that later Hamiltonians, field equations, and vacuum-density calculations use to represent anchor influence without turning it into a flat background constant.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Tzp Potential Term}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Tzp Potential Term Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Term Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0023]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0023_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0023] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP Potential Term}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the TZP potential term models the energetic influence of proximity to the zero point

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP Potential Term is valid as a synchronization criterion under the coupling conditions
named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0023_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
