\tzpanchor{0091}
\tzpentryheader{0091}{SO(3) $\times$ U(1) Configuration Bundle}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{10b56340-8d92-555e-ab5d-d38e658110c7}}\\
\textbf{PiID} & \tzpcode{4211706798214} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{98}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{353.3732 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.5823 rad}\\
\textbf{TZPID} & \tzpcode{ID0091} & \textbf{Node Dependencies}\quad \tzpidref{0017}\\
\textbf{Registry} & \tzpcode{registry\_id\_0091} & \textbf{Scale}\quad rotation-gauge coupling\\
\textbf{LOC Classification} & QA613 bundles & QC793 gauge symmetry\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: hep-th, physics.class-ph & \\
\textbf{Primary Support} & Base-Manifold Carrier & Bundle Structure Law\\
\textbf{Closure Support} & Physical Configuration Section & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The symmetry structure of the Trawin framework includes both spatial rotations and electromagnetic phases; this combination dictates how fields transform.

\tzpsection{Canonical Equation}
\[
P \longrightarrow M,
\qquad
\mathrm{Struct}(P)=SO(3) \times U(1)
\]
\[
\sigma : M \longrightarrow P
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $P$: source equation symbol.
    \item $M$: source equation symbol.
    \item $U$: auxiliary source state or local chart variable.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0091 generated source Wolfram model *)
ClearAll[K0091, Cr0091, T, R, A, W, I, N];
eq0091$1 = HoldForm[TZPSequence[P -> M, Struct[P] == SO[3]*U[1]]];
eq0091$2 = HoldForm[sigma[M] -> P];
eq0091$3 = HoldForm[M];

K0091 = HoldForm[{eq0091$1, eq0091$2, eq0091$3}];

N = "normalized TRAWIN closure object for SO(3) $\times$ U(1) Configuration Bundle";
I = "Physical Configuration Section integration/comparison layer";
W = "Bundle Structure Law wave or operator carrier";
A = "Base-Manifold Carrier admissible action/amplitude condition";
R = "Bundle Structure Law rotation/curl preservation layer";
T = "Base-Manifold Carrier local source condition";

Cr0091[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0091 = Cr0091[K0091];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Base-Manifold Carrier local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Bundle Structure Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Base-Manifold Carrier admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Bundle Structure Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Physical Configuration Section integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for SO(3) \$\textbackslash{}times\$ U(1) Configuration Bundle.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0091] SO(3) $\times$ U(1) Configuration Bundle}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
P \longrightarrow M,
\qquad
\mathrm{Struct}(P)=SO(3)\times U(1).
\end{equation}

\begin{equation}
\sigma:M\longrightarrow P.
\end{equation}

\paragraph{Primary Derivation.}
Let $M$ be the base manifold of admissible configurations. Rotational orientation is represented by $SO(3)$, while gauge phase is represented by $U(1)$.

A bundle carrying both data has structure group:
\begin{equation}
SO(3)\times U(1).
\end{equation}

Thus,
\begin{equation}
P\to M,
\qquad
\mathrm{Struct}(P)=SO(3)\times U(1).
\end{equation}

A physical configuration is then a section:
\begin{equation}
\boxed{
\sigma:M\to P.
}
\end{equation}

\paragraph{Interpretation.}
Rotational and gauge-phase data are organized into one configuration bundle.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors SO(3) \$\textbackslash{}times\$ U(1) Configuration Bundle by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Base-Manifold Carrier}\par
\[
M
\]
\noindent This identifies the domain over which the system is organized.\par
\noindent\textbf{2. Bundle Structure Law}\par
\[
P \longrightarrow M,
\qquad
\mathrm{Struct}(P)=SO(3) \times U(1)
\]
\noindent This equips the base manifold with combined rotational and gauge symmetry.\par
\noindent\textbf{3. Physical Configuration Section}\par
\[
\sigma : M \longrightarrow P
\]
\noindent This closes the progression by representing a physical state as a section of the full configuration bundle.\par

\clearpage
\noindent\textbf{[ID 0091] SO(3) $\times$ U(1) Configuration Bundle}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
SO(3) times U(1) Configuration Bundle is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The symmetry structure of the Trawin framework includes both spatial rotations and electromagnetic phases; this combination dictates how fields transform. \textbf{Contextual meaning:} The entry reads SO(3) times U(1) Configuration Bundle as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry packages symmetry before dynamics. It supplies the geometric stage on which rotational motion and gauge phase can interact coherently throughout the next few entries. \textbf{Lemma support:} Base-Manifold Carrier; Bundle Structure Law; Physical Configuration Section.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Rotational and gauge-phase data are organized into one configuration bundle.

\tzpsection{Equation Grounding}
Equation anchors: Rotational and gauge symmetries are combined in a configuration bundle with structure group SO(3)times U(1)SO(3)times U(1)SO(3)times U(1); fields are sections of this bundle, and gauge transformations act as SO(3)SO(3)SO(3) rotations combined with U(1)U(1)U(1) phase shifts. Rotational and gauge symmetries are combined in a configuration bundle with structure group SO(3)times U(1)SO(3)times U(1)SO(3)times U(1); fields are sections of this bundle, and gauge transformations act as SO(3)SO(3)SO(3) rotations combined with U(1)U(1)U(1) phase shifts.

\tzpsection{Interpretive Role}
This entry packages symmetry before dynamics. It supplies the geometric stage on which rotational motion and gauge phase can interact coherently throughout the next few entries.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{So 3 Times 1 Configuration}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Fibered Carrier Geometric Analogue}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\item \textbf{Fibered Carrier Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0091]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0091_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0091] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont SO(3) $\times$ U(1) Configuration Bundle}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the symmetry structure of the Trawin framework includes both spatial rotations and
electromagnetic phases; this combination dictates how fields tra...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``SO(3) \textbackslash{}times U(1) Configuration Bundle is well formed when the total space, base
space, structure group, and projection map are compatible.''\\
\textbf{Proof:} The source statement supplies a bundle-style construction. The CHL reading treats the
base as the proposition carrier, the fiber or structure group as the typed parameter,
and the projection as the categorical morphism that preserves local-to-global structure.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- principal-bundle structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0091_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
