\section*{ID9521: Concluding Synthesis: |K\_inner|/K\_outer}
\paragraph{Metadata.}
PiID: 2763478708108 | RTEID: RTE:P36972.1574:T4.3701 | UUID: 223f3b70-7cb1-5363-b295-55e024b2553a

\paragraph{Canonical Statement.}
In classical differential geometry, the ratio 1.185... (32/27) does not emerge as a known fundamental constant for spheres or tori. Spheres have constant intrinsic curvature (Gaussian curvature \$K=1/R\textasciicircum{}2\$ for radius \$R\$) and uniform extrinsic curvature, so no nontrivial dimensionless ratio arises from sphere geometry alone. For a torus, the curvature varies across the surface (positive on the outer bulge, negative on the inner hole). While one can form a ratio of extremal curvatures (e.g. \$|K\_\textbackslash{}text\{inner\}|/K\_\textbackslash{}text\{outer\} = (R+r)/(R-r)\$ for a ring torus of major radius \$R\$ and tube radius \$r\$), this yields a continuum of values depending on \$R/r\$ rather than a unique constant. No special choice of \$R/r\$ produces 32/27 in a canonical way. In short, no intrinsic property of a round sphere or standard torus naturally gives 1.185 – it does not appear in Gauss–Bonnet sums or known curvature integrals. (For comparison, the Euler characteristic of a torus is 0 and of a sphere is 2, neither related to 1.185.) We also did not find any

\paragraph{Canonical Equation.}
\[
|K_\text{inner}|/K_\text{outer} = (R+r)/(R-r)
\]

\paragraph{Dictionary.}
Concluding Synthesis: |K\_inner|/K\_outer — |K\_inner|/K\_outer = (R+r)/(R-r)

\paragraph{Encyclopedia.}
Concluding Synthesis: |K\_inner|/K\_outer is an algebraic definition, written |K\_inner|/K\_outer = (R+r)/(R-r). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R, r, defining |K\_inner|/K\_outer. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
