\tzpanchor{0882}
\tzpentryheader{0882}{TZP HARMONIC LATTICE CONSTANT}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{fad63e2d-b2a4-54d5-bfe2-64d952923e5d}}\\
\textbf{PiID} & \tzpcode{4206171776691} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{889}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3370.6368 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.5538 rad}\\
\textbf{TZPID} & \tzpcode{ID0882} & \textbf{Node Dependencies}\quad \tzpidref{0881}\\
\textbf{Registry} & \tzpcode{registry\_id\_0882} & \textbf{Scale}\quad diagnostic\\
\textbf{LOC Classification} & QA273 dimensionless analysis & QC statistical diagnostics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: nlin.PS, physics.data-an\\
\textbf{Primary Support} & Mode Quantization & Dispersion Law\\
\textbf{Closure Support} & Boundary Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records tzp harmonic lattice constant through a normalized Nonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0882}}:\mathcal{X}_{\mathrm{id0882}}\longrightarrow\mathcal{Y}_{\mathrm{id0882}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0882}})=\mathcal{O}_{\mathrm{id0882}}
\]
\[
\mathcal{O}_{\mathrm{id0882}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0882}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0882}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0882}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0882 generated source Wolfram model *)
ClearAll[K0882, Cr0882, T, R, A, W, I, N];
eq0882$1 = HoldForm[Oid0882[Xid0882] -> Yid0882];
eq0882$2 = HoldForm[NTRAWIN[OId0882] == OId0882];
eq0882$3 = HoldForm[Element[OId0882[x], YAdm]];

K0882 = HoldForm[{eq0882$1, eq0882$2, eq0882$3}];

N = "normalized TRAWIN closure object for TZP HARMONIC LATTICE CONSTANT";
I = "TZP HARMONIC LATTICE CONSTANT integration/comparison layer";
W = "TZP HARMONIC LATTICE CONSTANT wave or operator carrier";
A = "TZP HARMONIC LATTICE CONSTANT admissible action/amplitude condition";
R = "TZP HARMONIC LATTICE CONSTANT rotation/curl preservation layer";
T = "TZP HARMONIC LATTICE CONSTANT local source condition";

Cr0882[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0882 = Cr0882[K0882];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ TZP HARMONIC LATTICE CONSTANT local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TZP HARMONIC LATTICE CONSTANT rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ TZP HARMONIC LATTICE CONSTANT admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TZP HARMONIC LATTICE CONSTANT wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TZP HARMONIC LATTICE CONSTANT integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP HARMONIC LATTICE CONSTANT.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0882] TZP HARMONIC LATTICE CONSTANT}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0882}}:\mathcal{X}_{\mathrm{id0882}}\longrightarrow\mathcal{Y}_{\mathrm{id0882}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0882}})=\mathcal{O}_{\mathrm{id0882}}
\]
\[
\mathcal{O}_{\mathrm{id0882}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0882}})=\mathcal{O}_{\mathrm{id0882}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. Within the TRAWIN framework, the equation functions as the mapping carrier for the entry’s information content. Under CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP HARMONIC LATTICE CONSTANT by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0882}}:\mathcal{X}_{\mathrm{id0882}}\longrightarrow\mathcal{Y}_{\mathrm{id0882}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0882}})=\mathcal{O}_{\mathrm{id0882}}
\]
\[
\mathcal{O}_{\mathrm{id0882}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0882] TZP HARMONIC LATTICE CONSTANT}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP HARMONIC LATTICE CONSTANT is a registry definition in Resonance and Phase Locking with secondary pressure from Biological and Biomolecular Analogies.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} So if you decide theta = 32/27 in the TZP framework, then theta is not just an angle - it becomes the fundamental harmonic of triadic scaling, the root frequency of the repeating geometry we ve been building. \textbf{Contextual meaning:} The entry reads TZP HARMONIC LATTICE CONSTANT as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred. \textbf{Lemma support:} Mode Quantization; Dispersion Law; Boundary Condition.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, TZP HARMONIC LATTICE CONSTANT is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: Then C=153,600/129,600=1; C = 153 , 600 / 129 , 600 = 1; and C=153,600/129,600=1. Proof route: show that bounded carrier geometry forces the stated mode quantization and resonance law. Formalization route: prove that the stated boundary condition yields the stated discrete spectrum.

\tzpsection{Interpretive Role}
The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Fundamental Acoustic Metric}: The single, unchanging numerical value that defines the exact physical distance between the pressure nodes of the standing wave holding the entire machine together.
\item \textbf{Resonant Spatial Discretization}: The mathematical rule proving that inside the chamber, energy cannot exist just anywhere; it is strictly forced into a rigid, invisible 3D grid dictated by the sound waves.
\item \textbf{Piezoelectric Crystal Spacing}: The terrifyingly precise engineering requirement that every single sensor and speaker bolted to the wall must be aligned to within a fraction of a millimeter of this exact mathematical constant.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0882]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0882].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0882] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP HARMONIC LATTICE CONSTANT}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} TZP HARMONIC LATTICE CONSTANT is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP HARMONIC LATTICE CONSTANT is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0882].
\par\endgroup
\vfill
\endgroup
\endgroup
