\section*{ID9293: Definition of TZP}
\paragraph{Metadata.}
PiID: 2246801224826 | RTEID: RTE:P36086.7828:T2.9113 | UUID: 143cc7a9-25f5-5687-9259-291833c658b6

\paragraph{Canonical Statement.}
systems that separately measure the contributions of tunnelling, gravitational coupling, vibrational coupling and superconductivity; verify that their combined evolution matches the predictions of the unified Hamiltonian. Canonical Registry Vol. 01 137 Trawin Zero Point Contextus Canonicus 3 TRAWIN ZERO POINT REGISTRY (IDS 350–399) 3.0.45 ID 394: TZP Bridge–Tunnel Energy–Momentum Tensor Type: Definition Formal Statement: At a Trawin Zero Point, the energy–momentum tensor takes a diagonal form \$TZP=diag(vacuum,topological,topological,topological),TµTZP=diag(ρvacuum,ptopological,ptopological,ptopo-\$ logical), where the vacuum energy density \$vacuumρvacuum\$ diverges following a Besselfunction behaviour, and the pressures topologicalptopological arise from topological terms. Coupling this tensor into Einstein’s equations drives gravitational field generation and constitutes the “bridge–tunnel” mechanism. Interpretive Meaning: This tensor encapsulates how a TZP modifies local energy densiti

\paragraph{Canonical Equation.}
\[
TZP=diag(vacuum,topological,topological,topological),TµTZP=diag(ρvacuum,ptopological,ptopological,ptopo-
\]

\paragraph{Dictionary.}
Definition of TZP — TZP=diag(vacuum,topological,topological,topological),TµTZP=diag(ρvacuum,ptopological,ptopological,ptopo-

\paragraph{Encyclopedia.}
Definition of TZP is an algebraic definition, written TZP=diag(vacuum,topological,topological,topological),TµTZP=diag(ρvacuum,ptopolog. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from a, g, v, c, u, m, defining TZP. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
