\section*{ID9174: Definition of CS}
\paragraph{Metadata.}
PiID: 6733786236256 | RTEID: RTE:P35624.6793:T2.1498 | UUID: 303e4f8c-9352-5f80-8e1e-351ef9ce5d8b

\paragraph{Canonical Statement.}
of vacuum sectors. Dependencies: Primitive Derivable Consequences: Quantization of Chern–Simons levels; discrete classification of vacuum sectors; quantized coupling constants; impetus for topological transitions. Falsifiability / Test Handle: Detection of noninteger or continuous gerbe classes would falsify this classification. 2.0.6 ID 155: Chern–Simons Obstruction Class Type: Definition Formal Statement: The obstruction class for topological unification is given by the Chern–Simons invariant \$CS=14π∫ΣTr[F∧F ]CS\$ = \$\textbackslash{}tfrac\{1\}\{4\textbackslash{}pi\}\textbackslash{}int \{\textbackslash{}Sigma\}\textbackslash{}operatorname\{Tr\}[F\textbackslash{}wedgeF ]CS\$ = \$4π1∫ΣTr[F∧F ], computedfromtheconnectionformAµ= Aµdxµ+Bgravitational\$ + \$CelectromagneticA\_\textbackslash{}mu\$ = Canonical Registry Vol. 01 52 Trawin Zero Point Contextus Canonicus 2 TZP CANONICAL REGISTRY – ENTRIES 150–199 \$A\_\textbackslash{}mudxΘ\{\textbackslash{}mu\}+B\_\{\textbackslash{}text\{gravitational\}\}+ C\_\{\textbackslash{}text\{electromagnetic\}\}Aµ= Aµdxµ+Bgravitational\$ + \$Celectromagnetic.\$ Interp

\paragraph{Canonical Equation.}
\[
CS=14π∫ΣTr[F∧F ]CS
\]

\paragraph{Dictionary.}
Definition of CS — CS=14π∫ΣTr[F∧F ]CS

\paragraph{Encyclopedia.}
Definition of CS is an algebraic definition, written CS=14π∫ΣTr[F∧F ]CS. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from T, r, F, C, S, defining CS. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
