\tzpanchor{0701}
\tzpentryheader{0701}{Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{cdd15e2f-feea-52b8-a801-aca1a8746945}}\\
\textbf{PiID} & \tzpcode{2019956112129} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{708}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2691.0729 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.4341 rad}\\
\textbf{TZPID} & \tzpcode{ID0701} & \textbf{Node Dependencies}\quad \tzpidref{0700}\\
\textbf{Registry} & \tzpcode{registry\_id\_0701} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Configuration Manifold & Kaluza--Klein Sector\\
\textbf{Closure Support} & Gauge Quotient & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records extended phase space for magneto-acoustic--kaluza--klein systems through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0701}}:\mathcal{X}_{\mathrm{id0701}}\longrightarrow\mathcal{Y}_{\mathrm{id0701}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0701}})=\mathcal{O}_{\mathrm{id0701}}
\]
\[
\mathcal{O}_{\mathrm{id0701}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0701}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0701}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0701}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0701 generated source Wolfram model *)
ClearAll[K0701, Cr0701, T, R, A, W, I, N];
eq0701$1 = HoldForm[Oid0701[Xid0701] -> Yid0701];
eq0701$2 = HoldForm[NTRAWIN[OId0701] == OId0701];
eq0701$3 = HoldForm[Element[OId0701[x], YAdm]];

K0701 = HoldForm[{eq0701$1, eq0701$2, eq0701$3}];

N = "normalized TRAWIN closure object for Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems";
I = "Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems integration/comparison layer";
W = "Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems wave or operator carrier";
A = "Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems admissible action/amplitude condition";
R = "Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems rotation/curl preservation layer";
T = "Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems local source condition";

Cr0701[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0701 = Cr0701[K0701];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0701] Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0701}}:\mathcal{X}_{\mathrm{id0701}}\longrightarrow\mathcal{Y}_{\mathrm{id0701}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0701}})=\mathcal{O}_{\mathrm{id0701}}
\]
\[
\mathcal{O}_{\mathrm{id0701}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0701}})=\mathcal{O}_{\mathrm{id0701}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. In the TRAWIN reading, the equation functions as the mapping carrier for the entry’s information content. In CHL terms, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0701}}:\mathcal{X}_{\mathrm{id0701}}\longrightarrow\mathcal{Y}_{\mathrm{id0701}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0701}})=\mathcal{O}_{\mathrm{id0701}}
\]
\[
\mathcal{O}_{\mathrm{id0701}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0701] Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} n 0 = + infty + (- infty)n /. \textbf{Contextual meaning:} The entry reads Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the extended phase space as a clean manifold-plus-sector-plus-gauge structure instead of corrupted product notation. \textbf{Lemma support:} Configuration Manifold; Kaluza--Klein Sector; Gauge Quotient.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: rst, we establish that quantum entangle ment creates non-local correlations characterized by mutual information I(A : B) = S(A) + S(B)   S(AB); ormation density acts as an effective source term in the Einstein equations through the correspondence principle  S/ g   = (c 4/16 G)G  ; and tric down-conversion: |Psi photon = Z domegasdomegai (omegap   omegas   omegai)f(omegas, omegai) a   s (omegas) a   Proof. Proof route: show that the coupled magneto-acoustic and Kaluza--Klein sectors assemble into the stated gauge-quotiented phase-space manifold. Formalization route: prove that the stated gauge group acts admissibly on the extended phase-space carrier and yields the stated quotient structure.

\tzpsection{Interpretive Role}
The entry now states the extended phase space as a clean manifold-plus-sector-plus-gauge structure instead of corrupted product notation.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Compactified Extra-Dimensional Dynamics}: The inclusion of hidden cylindrical spatial dimensions to unify acoustic vibrations with electromagnetic fields.
\item \textbf{Gauge-Invariant Spatialize Integration}: The quotient manifold constructed by removing redundant local phase transformations from the physical degrees of freedom.
\item \textbf{Hybrid Phonon-Photon Carrier Space}: The explicit combined geometric setting where mechanical strain and magnetic flux are treated as one continuous metric.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0701]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0701].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0701] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Extended Phase Space for Magneto-Acoustic--Kaluza--Klein Systems is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0701].
\par\endgroup
\vfill
\endgroup
\endgroup
