\section*{ID9649: Definition of φ\_i}
\paragraph{Metadata.}
PiID: 0736041123735 | RTEID: RTE:P37469.2098:T5.1891 | UUID: 0f745f68-b220-52ce-83a4-539b1743b64e

\paragraph{Canonical Statement.}
\textbackslash{}subsection\{Quantum-to-Holographic-Wavefront Transformation\} Once a quantum state has been prepared corresponding to a particular DAANSphere address, the next stage converts this discrete quantum information into a continuous holographic wavefront suitable for optical propagation. Extract the address index by measuring the quantum state in the computational basis, yielding an integer from 1 to 153,600. Retrieve the corresponding Cartesian coordinates \$\textbackslash{}mathbf\{p\}\_i = (x\_i, y\_i, z\_i)\$ from the pre-computed Fibonacci sphere distribution. Convert to spherical angles \$\textbackslash{}theta\_i = \textbackslash{}arccos(z\_i)\$ and \$\textbackslash{}phi\_i = \textbackslash{}arctan(x\_i, y\_i)\$. Generate the complex wavefront amplitude at this point by evaluating the target intensity function \$I(\textbackslash{}theta, \textbackslash{}phi)\$ and combining with a phase pattern determined by the Gerchberg-Saxton algorithm or another phase retrieval method. The result is a complex number \$A\_i e\textasciicircum{}\{i\textbackslash{}varphi\_i\}\$ representing the holographic field value at address \$i\$. Decompose this complex amplitude into orbital angular momentum modes through Fourier analysis. The OAM spectrum is obtained by computing: \textbackslash{}begin\{equation\} c\_

\paragraph{Canonical Equation.}
\[
\phi_i = \arctan(x_i, y_i)
\]

\paragraph{Dictionary.}
Quantum-to-Holographic-Wavefront Transformation Once a quantum state has been prepared corresponding to a particular DAANSphere address, the next stage converts this discrete quantum information into a continuous holographic wavefront suitable for optical propagation.

\paragraph{Encyclopedia.}
Definition of φ\_i is an algebraic definition, written φ\_i = arctan(x\_i, y\_i). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from x\_i, y\_i, defining φ\_i. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
