\tzpanchor{0493}
\tzpentryheader{0493}{Experimental Deviation Tolerance}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{b163c95f-b376-5aa6-bac7-ec080b8adfc9}}\\
\textbf{PiID} & \tzpcode{1194912983367} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{500}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1898.8956 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.1288 rad}\\
\textbf{TZPID} & \tzpcode{ID0493} & \textbf{Node Dependencies}\quad \tzpidref{0492}\\
\textbf{Registry} & \tzpcode{registry\_id\_0493} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 493 establishes the rigorous error bounds for the Furiene Turbine's operation. To maintain the topological regime, the observed ratio between steps must remain within a 5 Precision Audit: Continuous comparison of SQUID flux data against the weighted surplus criterion. Safety Trigger: Automated decoupling if the error gradient exceeds the Lyapunov persistence limit.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
tolerance = 10^(-12)
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{K}_{0493}$: canonical registry object for entry ID 0493.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0493 generated source Wolfram model *)
ClearAll[K0493, Cr0493, T, R, A, W, I, N];
eq0493$1 = HoldForm[$tolerance == $/10^12];

K0493 = HoldForm[{eq0493$1}];

N = "normalized TRAWIN closure object for Experimental Deviation Tolerance";
I = "Experimental Deviation Tolerance integration/comparison layer";
W = "Experimental Deviation Tolerance wave or operator carrier";
A = "Experimental Deviation Tolerance admissible action/amplitude condition";
R = "Experimental Deviation Tolerance rotation/curl preservation layer";
T = "Experimental Deviation Tolerance local source condition";

Cr0493[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0493 = Cr0493[K0493];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Experimental Deviation Tolerance local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Experimental Deviation Tolerance rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Experimental Deviation Tolerance admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Experimental Deviation Tolerance wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Experimental Deviation Tolerance integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Experimental Deviation Tolerance.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0493] Experimental Deviation Tolerance}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\mathcal{L}_{X_H}\omega=0.
\end{equation}

\begin{equation}
\phi_t^{*}\omega=\omega.
\end{equation}

\paragraph{Primary Derivation.}
Let $\omega$ be the symplectic form and $X_H$ the Hamiltonian vector field.  
Hamiltonian flow preserves the symplectic form when:

\begin{equation}
\mathcal{L}_{X_H}\omega=0.
\end{equation}

Integrating the infinitesimal flow produces the global preservation law:

\begin{equation}
\boxed{
\phi_t^{*}\omega=\omega.
}
\end{equation}

\paragraph{Interpretation.}
Admissible Hamiltonian evolution preserves phase-space topology and Liouville structure.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Experimental Deviation Tolerance by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
tolerance = 10^(-12)
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0493] Experimental Deviation Tolerance}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Experimental Deviation Tolerance is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 493 establishes the rigorous error bounds for the Furiene Turbine's operation. To maintain the topological regime, the observed ratio between steps must remain within a 5 Precision Audit: Continuous comparison of SQUID flux data against the weighted surplus criterion. Safety Trigger: Automated decoupling if the error gradient exceeds the Lyapunov persistence limit.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
tolerance = 10^(-12)
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 493 establishes the rigorous error bounds for the Furiene Turbine's operation. To maintain the topological regime, the observed ratio between steps must remain within a 5 Precision Audit: Continuous comparison of SQUID flux data against the weighted surplus criterion. Safety Trigger: Automated decoupling if the error gradient exceeds the Lyapunov persistence limit.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Experimental Deviation Tolerance by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Experimental Deviation Tolerance; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0493]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0493].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0493] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Experimental Deviation Tolerance}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} sigma\textbackslash{}\_\textbackslash{}\textbackslash{} <= | chi\textbackslash{}\_\textbackslash{}\textbackslash{} - chi\textbackslash{}\_\textbackslash{}\textbackslash{} | <= 0.05

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``EXPERIMENTAL DEVIATION TOLERANCE (\textbackslash{}pm 0.05) is valid as a formal dynamical law when
the Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0493].
\par\endgroup
\vfill
\endgroup
\endgroup
