\section*{ID8525: VACUUM ENERGY MODE SUMMATION Canonical Statutory Formula: ρ\_vac}
\paragraph{Metadata.}
PiID: 3999446974867 | RTEID: RTE:P33104.4682:T4.2805 | UUID: 3ce56c50-67ba-5d42-8450-81200c65f73c

\paragraph{Canonical Statement.}
[ID 1151] VACUUM ENERGY MODE SUMMATION Canonical Statutory Formula: \$\textbackslash{}rho\_\{vac\} = \textbackslash{}frac\{1\}\{2\} \textbackslash{}sum E\_\{modes\}(\textbackslash{}omega\_\{Planck\}) / (2l\_\{Planck\})\textasciicircum{}3\$ Formal Technical Dissertation: A derivation of the Cosmological Constant (\$\textbackslash{}Lambda\$). It proposes that Dark Energy is simply the natural vacuum energy of the spacetime oscillations, which matches observed values when properly time-averaged over the Planck scale. Source:

\paragraph{Canonical Equation.}
\[
\rho_{vac} = \frac{1}{2} \sum E_{modes}(\omega_{Planck}) / (2l_{Planck})^3
\]

\paragraph{Dictionary.}
VACUUM ENERGY MODE SUMMATION Canonical Statutory Formula: \$ \_vac = 12 E\_modes( \_Planck) / (2l\_Planck)\textasciicircum{}3\$ Formal Technical Dissertation: A derivation of the Cosmological Constant (Λ).

\paragraph{Encyclopedia.}
VACUUM ENERGY MODE SUMMATION Canonical Statutory Formula: ρ\_vac is an expectation / trace over state, written ρ\_vac = (1)/(2) ∑ E\_modes(ω\_Planck) / (2l\_Planck)\textasciicircum{}3. It is computed as an expectation value or trace over a quantum state, producing an observable. It is built from E\_modes, P, l, a, n, c, defining ρ\_vac. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
