\tzpanchor{0524}
\tzpentryheader{0524}{WEYL CURVATURE NORMALIZATION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{0de1aeb2-f391-5227-8d10-a2ff8192cb84}}\\
\textbf{PiID} & \tzpcode{1394946395224} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{531}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2015.3923 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.3207 rad}\\
\textbf{TZPID} & \tzpcode{ID0524} & \textbf{Node Dependencies}\quad \tzpidref{0523}\\
\textbf{Registry} & \tzpcode{registry\_id\_0524} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Weyl Curvature & Normalization Map\\
\textbf{Closure Support} & Closure Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
mathcal\{H\}\_\{GR\} supset frac\{hbar\textasciicircum{}2\}\{2m\_\{text\{eff\}\}\} C\_\{munurhosigma\} otimes psi

\tzpsection{Canonical Equation}
\[
text{TopologicalInvariant} \to \text{ToddClass}[T\text{Bundle}[\text{ModuliSpace}[\text{CymaticPatterns}]]]
\]
\[
omega_n \approx \omega_{\text{fund}} \cdot \frac{\text{kissingNumber}[n]}{\pi}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $T$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
    \item $n$: integer mode index.
    \item $\pi$: source equation symbol.
    \item $H$: source equation symbol.
    \item $\delta(r)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0524 generated source Wolfram model *)
ClearAll[K0524, Cr0524, T, R, A, W, I, N];
eq0524$1 = HoldForm[TopologicalInvariant -> ToddClass[TBundle[ModuliSpace[CymaticPatterns]]]];
eq0524$2 = HoldForm[omegaN == omegaFund*(KissingNumber[n]/Pi)];
eq0524$3 = HoldForm[HHatTZP == DiracDelta[r]*Abs[TZP]*Inner[TZP]*TensorProduct[dots]];

K0524 = HoldForm[{eq0524$1, eq0524$2, eq0524$3}];

N = "normalized TRAWIN closure object for WEYL CURVATURE NORMALIZATION";
I = "Closure Condition integration/comparison layer";
W = "Normalization Map wave or operator carrier";
A = "Weyl Curvature admissible action/amplitude condition";
R = "Normalization Map rotation/curl preservation layer";
T = "Weyl Curvature local source condition";

Cr0524[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0524 = Cr0524[K0524];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Weyl Curvature local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Normalization Map rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Weyl Curvature admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Normalization Map wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Condition integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for WEYL CURVATURE NORMALIZATION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0524] WEYL CURVATURE NORMALIZATION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_T^4}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,
\hbar\omega\,
\mathrm{d}\omega .
\end{equation}

\paragraph{Primary Derivation.}
Each vacuum mode of frequency $\omega$ contributes energy proportional to:

\begin{equation}
\hbar\omega .
\end{equation}

The spectral density index $\eta(\omega)$ weights the contribution of each frequency:

\begin{equation}
\eta(\omega)\hbar\omega .
\end{equation}

Integrating over all allowed frequencies up to the cutoff $\omega_{\mathrm{cut}}$ gives the weighted vacuum energy:

\begin{equation}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\hbar\omega\,\mathrm{d}\omega .
\end{equation}

To convert this to a density in Trawin units, divide by the fourth power of the base unit:

\begin{equation}
u_T^4 .
\end{equation}

Therefore,

\begin{equation}
\boxed{
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_T^4}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,
\hbar\omega\,
\mathrm{d}\omega .
}
\end{equation}

\paragraph{Interpretation.}
$\rho_{\mathrm{vac}}^{T}$ defines vacuum energy density as a spectral integral normalized by the four-dimensional Trawin base scale.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors WEYL CURVATURE NORMALIZATION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Weyl Curvature}\par
\[
text{TopologicalInvariant} \to \text{ToddClass}[T\text{Bundle}[\text{ModuliSpace}[\text{CymaticPatterns}]]]
\]
\noindent This fixes the Weyl curvature scalar carried by the entry.\par
\noindent\textbf{2. Normalization Map}\par
\[
omega_n \approx \omega_{\text{fund}} \cdot \frac{\text{kissingNumber}[n]}{\pi}
\]
\noindent This turns that scalar into an explicit normalized curvature observable.\par
\noindent\textbf{3. Closure Condition}\par
\[
hat{H}_{TZP} = \delta(r)|TZP\rangle\langle TZP| \otimes [ \dots ]
\]
\noindent This closes the entry by requiring admissibility of the normalized Weyl sector.\par

\clearpage
\noindent\textbf{[ID 0524] WEYL CURVATURE NORMALIZATION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
WEYL CURVATURE NORMALIZATION is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} mathcal H sub GR supset frac hbar to the power 2 2m sub text eff C sub munurhosigma otimes psi. \textbf{Contextual meaning:} The entry reads WEYL CURVATURE NORMALIZATION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states a clean curvature-normalization chain instead of relying on malformed imported operator composition. \textbf{Lemma support:} Weyl Curvature; Normalization Map; Closure Condition.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub vac to the power T defines vacuum energy density as a spectral integral normalized by the four-dimensional Trawin base scale.

\tzpsection{Equation Grounding}
Equation anchors: text TopologicalInvariant to ToddClass [T Bundle [ ModuliSpace [ CymaticPatterns ]]]; omega sub n approximately omega sub fund dot ratio kissingNumber [n] pi; and hat H sub TZP = delta(r)|TZP TZP| otimes [ dots ]. Proof route: show that the normalized Weyl observable follows from the stated curvature contraction and remains admissible. Formalization route: prove that the normalized Weyl curvature observable satisfies the stated closure condition.

\tzpsection{Interpretive Role}
The entry now states a clean curvature-normalization chain instead of relying on malformed imported operator composition.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Conformal Spacetime Scaling}: The mathematical trick of zooming in or out on the universe to ignore the overall expansion and focus purely on the local twisting and shearing of gravity.
\item \textbf{Traceless Gravitational Tensors}: The isolation of the specific parts of Einstein's equations that describe tidal forces--the stretching of objects--rather than the overall volume changes.
\item \textbf{Metric Distortion Benchmarking}: The process of taking the wild, terrifying relativistic math and forcing it to sit neatly on a scale from 0 to 1 so the engineers can actually read the dials.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0524]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0524_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0524] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont WEYL CURVATURE NORMALIZATION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} mathcal\textbackslash{}\textbackslash{}\_\textbackslash{} supset frac\textasciicircum{}2\textbackslash{}\textbackslash{}2m\textbackslash{}\_\textbackslash{}\textbackslash{}\textbackslash{} C\textbackslash{}\_\textbackslash{} otimes psi

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``WEYL CURVATURE NORMALIZATION is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0524_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
