\tzpanchor{0956}
\tzpentryheader{0956}{TZP Canon ID000}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{47dc8eb8-cde3-5a2a-9c1d-910099b5556a}}\\
\textbf{PiID} & \tzpcode{0532171226806} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{963}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3642.4623 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{06.0017 rad}\\
\textbf{TZPID} & \tzpcode{ID0956} & \textbf{Node Dependencies}\quad \tzpidref{0955}\\
\textbf{Registry} & \tzpcode{registry\_id\_0956} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Hamiltonian Carrier & Transport Output\\
\textbf{Closure Support} & Admissible Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
* **Formal Statement:** The Hamiltonian density /(mathcal\{H\}\_\{mathrm\{T\}\}/) for a field /(phi/) on /(M/) is given by /(mathcal\{H\}\_\{mathrm\{T\}\}=pi/,dot\{phi\}-mathcal\{L\}\_\{mathrm\{T\}\}/), where /(pi=frac\{partial mathcal\{L\}\_\{mathrm\{T\}\}\}\{partial dot\{phi\}\}/) is the canonical momentum and /(mathcal\{L\}\_\{mathrm\{T\}\}/) includes contributions from the degenerate metric and the TZP potential.

\tzpsection{Canonical Equation}
\[
mathcal{H}_{\mathrm{T}}=\pi\,\dot{\phi}-\mathcal{L}_{\mathrm{T}}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $\mathcal{L}_{\mathrm{T}}$: source equation symbol.
    \item $J$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0956 generated source Wolfram model *)
ClearAll[K0956, Cr0956, T, R, A, W, I, N];
eq0956$1 = HoldForm[mathcal[H]*_*T == Pidot[phi] - LT];
eq0956$2 = HoldForm[mathcal[J]*_*out == TTZP[KTZP]];

K0956 = HoldForm[{eq0956$1, eq0956$2}];

N = "normalized TRAWIN closure object for TZP Canon ID000";
I = "TZP Canon ID000 integration/comparison layer";
W = "TZP Canon ID000 wave or operator carrier";
A = "TZP Canon ID000 admissible action/amplitude condition";
R = "TZP Canon ID000 rotation/curl preservation layer";
T = "TZP Canon ID000 local source condition";

Cr0956[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0956 = Cr0956[K0956];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ TZP Canon ID000 local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TZP Canon ID000 rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ TZP Canon ID000 admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TZP Canon ID000 wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TZP Canon ID000 integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP Canon ID000.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0956] TZP Canon ID000}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
mathcal{H}_{\mathrm{T}}=\pi\,\dot{\phi}-\mathcal{L}_{\mathrm{T}}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\paragraph{Primary Derivation.}
The relation is obtained through direct evaluation of the expression. yielding the required identity.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. From the TRAWIN perspective, the equation functions as the generalized carrier for the entry’s information content. According to CHL, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP Canon ID000 by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
mathcal{H}_{\mathrm{T}}=\pi\,\dot{\phi}-\mathcal{L}_{\mathrm{T}}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0956] TZP Canon ID000}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP Canon ID000 is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} * **Formal Statement:** The Hamiltonian density /(mathcal H sub mathrm T /) for a field /(phi/) on /(M/) is given by /(mathcal H sub mathrm T =pi/,dot phi -mathcal L sub mathrm T /), where /(pi=frac partial mathcal L sub mathrm T partial dot phi /) is the canonical momentum and /(mathcal L sub mathrm T /) includes contributions from the degenerate metric and the TZP potential. \textbf{Contextual meaning:} The entry reads TZP Canon ID000 as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states a clean Hamiltonian-transport-admissibility chain instead of malformed source fragments. \textbf{Lemma support:} Hamiltonian Carrier; Transport Output; Admissible Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, TZP Canon ID000 is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: mathcal H sub T =pi dot phi - L sub T; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated Hamiltonian carrier induces the transported output and closes into the admissible TRAWIN sector. Formalization route: prove that the transported Hamiltonian carrier satisfies the stated admissible closure.

\tzpsection{Interpretive Role}
The entry now states a clean Hamiltonian-transport-admissibility chain instead of malformed source fragments.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Primordial System Boot-Code}: The very first, incredibly old, incredibly simple lines of code that wake the supercomputer up and teach it how to read the rest of the software.
\item \textbf{Archival Law Re-Initialization}: The scary process of wiping the computer's memory completely clean and forcefully reminding it of the absolute, basic laws of physics.
\item \textbf{Core-Truth Verification}: The sweeping scan that checks the massive, complicated physics simulations against the simple, basic rules to make sure the computer hasn't gone insane.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0956]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0956].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0956] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP Canon ID000}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} TZP Canon ID000 is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP Canon ID000 is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0956].
\par\endgroup
\vfill
\endgroup
\endgroup
