\tzpanchor{0004}
\tzpentryheader{0004}{Metric Degeneracy Condition}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{4677ae0d-3496-572c-a69f-8ee2c05ea69a}}\\
\textbf{PiID} & \tzpcode{9265358979323} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{11}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{15.5329 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.0256 rad}\\
\textbf{TZPID} & \tzpcode{ID0004} & \textbf{Node Dependencies}\quad \tzpidref{0001}\\
\textbf{Registry} & \tzpcode{registry\_id\_0004} & \textbf{Scale}\quad metric\\
\textbf{LOC Classification} & QA641 pseudo-Riemannian geometry & QC gravitation and relativity\\
\textbf{arXiv Classification} & Primary: gr-qc \quad Cross-list: math.DG, math-ph & \\
\textbf{Primary Support} & Determinant Collapse & Missing Inverse Metric\\
\textbf{Closure Support} & Exterior Regularity & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
At the TZP, the metric tensor satisfies $\det g|_p = 0$ and the inverse metric $g^{-1}|_p$ does not exist; for $x\neq p$, $\det g(x)\neq 0$ and $g^{-1}(x)$ exists.

\tzpsection{Canonical Equation}
\[
\det g\vert_{p}=0
\]
\[
g^{-1}\vert_{p}\ \text{does not exist},
\qquad
\det g(x)\neq 0 \ \text{for}\ x\neq p
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $g(x)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0004 generated source Wolfram model *)
ClearAll[K0004, Cr0004, T, R, A, W, I, N];
eq0004$1 = HoldForm[Det*gP == 0];
eq0004$2 = HoldForm[TZPSequence[(_*p)/g, Det*g[x] != 0 && x != p]];
eq0004$3 = HoldForm[(_*p)/g];
eq0004$4 = HoldForm[Det*g[x] != 0*(x != p)];

K0004 = HoldForm[{eq0004$1, eq0004$2, eq0004$3, eq0004$4}];

N = "normalized TRAWIN closure object for Metric Degeneracy Condition";
I = "Exterior Regularity integration/comparison layer";
W = "Missing Inverse Metric wave or operator carrier";
A = "Determinant Collapse admissible action/amplitude condition";
R = "Missing Inverse Metric rotation/curl preservation layer";
T = "Determinant Collapse local source condition";

Cr0004[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0004 = Cr0004[K0004];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Determinant Collapse local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Missing Inverse Metric rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Determinant Collapse admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Missing Inverse Metric wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Exterior Regularity integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Metric Degeneracy Condition.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0004] Metric Degeneracy Condition}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\det(g)\big|_{p}=0,
\qquad
g^{-1}\big|_{p}\ \text{does not exist},
\qquad
\det(g)\neq 0\ \text{for}\ x\neq p .
\end{equation}

\paragraph{Primary Derivation.}
A metric tensor $g$ admits an inverse $g^{-1}$ precisely when its determinant is nonzero:

\begin{equation}
g^{-1}\ \text{exists}
\iff
\det(g)\neq 0 .
\end{equation}

The Trawinistic manifold is ordinary away from $p$, so:

\begin{equation}
\det(g)(x)\neq 0,
\qquad x\neq p .
\end{equation}

At the TZP, invertibility fails. Hence:

\begin{equation}
g^{-1}\big|_p \ \text{does not exist}.
\end{equation}

By the determinant criterion, this implies:

\begin{equation}
\det(g)\big|_p=0 .
\end{equation}

\paragraph{Interpretation.}
ID 0004 strengthens ID 0001 by explicitly separating the ordinary region from the TZP degeneracy region.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Metric Degeneracy Condition by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Determinant Collapse}\par
\[
\det g\vert_{p}=0
\]
\noindent This identifies the singular metric event that distinguishes the zero point from every ordinary manifold location.\par
\noindent\textbf{2. Missing Inverse Metric}\par
\[
g^{-1}\vert_{p}\ \text{does not exist}
\]
\noindent This strengthens the claim from a scalar determinant statement to a genuine loss of geometric inversion at the anchor.\par
\noindent\textbf{3. Exterior Regularity}\par
\[
\det g(x)\neq 0 \qquad (x\neq p)
\]
\noindent This closes the progression by confining the collapse to the TZP so later dynamics can still be computed on the surrounding manifold.\par

\clearpage
\noindent\textbf{[ID 0004] Metric Degeneracy Condition}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Metric Degeneracy Condition is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} At the TZP, the metric tensor satisfies det g| sub p = 0 and the inverse metric g to the power -1 | sub p does not exist; for xneq p, det g(x)neq 0 and g to the power -1 (x) exists. \textbf{Contextual meaning:} The entry reads Metric Degeneracy Condition as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This condition permits singular curvature behavior without abandoning ordinary geometry away from the anchor. It becomes the gateway for time dilation, field nonlinearity, and generalized measures defined only after normalization. \textbf{Lemma support:} Determinant Collapse; Missing Inverse Metric; Exterior Regularity.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
ID 0004 strengthens ID 0001 by explicitly separating the ordinary region from the TZP degeneracy region.

\tzpsection{Equation Grounding}
Equation anchors: At the TZP, the metric tensor satisfies det g| sub p = 0 and g to the power -1 | sub p does not exist; away from p, det g eq 0. At the TZP, the metric tensor satisfies det g| sub p = 0 and g to the power -1 | sub p does not exist; away from p, det g eq 0.

\tzpsection{Interpretive Role}
This condition permits singular curvature behavior without abandoning ordinary geometry away from the anchor. It becomes the gateway for time dilation, field nonlinearity, and generalized measures defined only after normalization.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Measure Tensor Degeneracy Condition}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\item \textbf{Measure Tensor Geometric Analogue}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\item \textbf{Measure Tensor Terminology}: geometric neighbor term for shape, measure, curvature, or tensor structure.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0004]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0004_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0004] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Metric Degeneracy Condition}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} at the TZP, the metric tensor satisfies  g|\_p = 0 and the inverse metric g\textasciicircum{}-1|\_p
does not exist; for x p,  g(x) 0 and g\textasciicircum{}-1(x) exists

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Metric Degeneracy Condition is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0004_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
