\tzpanchor{0981}
\tzpentryheader{0981}{THZ DENSITY POTENTIAL}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9011b7db-d704-56ae-bafd-f84e6095df1a}}\\
\textbf{PiID} & \tzpcode{6111959092164} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{988}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3739.5429 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{06.1616 rad}\\
\textbf{TZPID} & \tzpcode{ID0981} & \textbf{Node Dependencies}\quad \tzpidref{0980}\\
\textbf{Registry} & \tzpcode{registry\_id\_0981} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Scaling Law\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
rho\_\{mathrm\{ss\}\} = lim\_\{ttoinfinity\} mathrm\{e\}\textasciicircum{}\{mathcal\{L\} t\}rho\_\{0\} = lvert mathrm\{DNA\_\{B\}\} rangle langle mathrm\{DNA\_\{B\}\} rvert,

\tzpsection{Canonical Equation}
\[
rho_{THZ}:=\langle0|T^{00}\lvert 0 \rangle
\]
\[
langle O_1(0) O_2(r) \rangle \propto r^{-(N-1)}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $T$: source equation symbol.
    \item $O_1(0)$: source equation symbol.
    \item $O_2(r)$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0981 generated source Wolfram model *)
ClearAll[K0981, Cr0981, T, R, A, W, I, N];
eq0981$1 = HoldForm[rhoTHZ == Inner[Ket[0], T00, Ket[0]]];
eq0981$2 = HoldForm[langleO1[0]*O2[r] ? r^(-(N - 1))];

K0981 = HoldForm[{eq0981$1, eq0981$2}];

N = "normalized TRAWIN closure object for THZ DENSITY POTENTIAL";
I = "THZ DENSITY POTENTIAL integration/comparison layer";
W = "THZ DENSITY POTENTIAL wave or operator carrier";
A = "THZ DENSITY POTENTIAL admissible action/amplitude condition";
R = "THZ DENSITY POTENTIAL rotation/curl preservation layer";
T = "THZ DENSITY POTENTIAL local source condition";

Cr0981[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0981 = Cr0981[K0981];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ THZ DENSITY POTENTIAL local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ THZ DENSITY POTENTIAL rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ THZ DENSITY POTENTIAL admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ THZ DENSITY POTENTIAL wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ THZ DENSITY POTENTIAL integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for THZ DENSITY POTENTIAL.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0981] THZ DENSITY POTENTIAL}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
rho_{THZ}:=\langle0|T^{00}\lvert 0 \rangle
\]
\[
langle O_1(0) O_2(r) \rangle \propto r^{-(N-1)}
\]

\paragraph{Primary Derivation.}
The expression \( rho_{THZ}:=\langle0|T^{00}\lvert 0 \rangle \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. Interpreted through TRAWIN, the equation functions as the integral carrier for the entry’s information content. According to CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors THZ DENSITY POTENTIAL by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
rho_{THZ}:=\langle0|T^{00}\lvert 0 \rangle
\]
\[
langle O_1(0) O_2(r) \rangle \propto r^{-(N-1)}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0981] THZ DENSITY POTENTIAL}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
THZ DENSITY POTENTIAL is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} rho sub mathrm ss = lim sub ttoinfinity mathrm e to the power mathcal L t rho sub 0 = lvert mathrm DNA sub B rangle langle mathrm DNA sub B rvert,. \textbf{Contextual meaning:} The entry reads THZ DENSITY POTENTIAL as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Scaling Law; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, THZ DENSITY POTENTIAL is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: rho sub THZ :=0|T to the power 00 lvert 0; langle O sub 1(0) O sub 2(r) propto r to the power -(N-1); and rho sub ss = lim sub ttoin fty e to the power L t rho sub 0 = lvert DNA sub B DNA sub B rvert. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Terahertz-Frequency Crowding}: The bizarre physics of blasting the empty vacuum with incredibly high-pitched, invisible light to physically squeeze the space and create imaginary gravity.
\item \textbf{Sub-Millimeter Energy Packing}: The calculation of exactly how much raw, violent electricity you can physically cram into a space smaller than the width of a human hair before it rips reality apart.
\item \textbf{High-Bandwidth Mass Illusion}: The incredible trick of using a massive, screaming radio wave to trick the universe into thinking a heavy, solid object exists where there is actually nothing but empty air.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0981]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0981].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0981] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont THZ DENSITY POTENTIAL}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} THZ DENSITY POTENTIAL is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``THZ DENSITY POTENTIAL is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0981].
\par\endgroup
\vfill
\endgroup
\endgroup
