\section*{ID9836: Relation: H\_binary(π - 3)}
\paragraph{Metadata.}
PiID: 1055924019027 | RTEID: RTE:P38195.3724:T0.1024 | UUID: 1eb8dd51-96b3-5770-901d-de26c32b42e9

\paragraph{Canonical Statement.}
homology on that trajectory (viewing it as a filtered simplicial complex) to get a topological encoding of the signal’s shape. The output of encoding is a triple: the trajectory itself, its topological invariant, and the list of kissing numbers encountered. Transmission (𝒯): The trajectory information modulates a quantum channel that exists between the inner and outer torus. We formalize this channel as a Kissing-Protected Quantum Channel with capacity \$C\_\{\textbackslash{}text\{kissing\}\} = \textbackslash{}log\_2(153600) + H\_\{\textbackslash{}text\{binary\}\}(\textbackslash{}pi - \textbackslash{}lfloor \textbackslash{}pi\textbackslash{}rfloor)\$ qubits. Numerically, \$\textbackslash{}log\_2(153600)\textbackslash{}approx17.2\$ bits and \$H\_\{\textbackslash{}text\{binary\}\}(\textbackslash{}pi - 3)\$ is some entropy of the fractional part of π (a constant \textasciitilde{}\$0.97\$ bits). So roughly \$C \textbackslash{}approx 18\$ qubits per use, indicating our channel can teleport states up to 18 qubits in size per operation (this is extremely high; typical quantum teleports are 1 qubit per entangled pair; our entangled resource is enormously larger, enabling batch teleportation). The channel’s noise model is special: we design Kraus operators \$K\_\{k\}\$ that correspond to errors where a state hops to a different kissing sphere

\paragraph{Canonical Equation.}
\[
H_{\text{binary}}(\pi - 3)
\]

\paragraph{Dictionary.}
Relation: H\_binary(π - 3) — H\_binary(π - 3)

\paragraph{Encyclopedia.}
Relation: H\_binary(π - 3) is a symbolic expression, written H\_binary(π - 3). It introduces a symbol or relation used elsewhere in the framework. It is built from π, H\_. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
