\section*{ID8906: ELECTRON-NEURAL EXCHANGE OPERATOR Canonical Statutory Formula: K Ex}
\paragraph{Metadata.}
PiID: 7669758318327 | RTEID: RTE:P34583.9758:T0.4351 | UUID: cb928b20-5390-5481-b068-fa202b692002

\paragraph{Canonical Statement.}
[ID 937] ELECTRON-NEURAL EXCHANGE OPERATOR Canonical Statutory Formula: \$\textbackslash{}hat\{K\} \{ex\} = -2 \textbackslash{}sum \{i,j\} J\_\{ij\}(L) (\textbackslash{}mathbf\{S\} i \textbackslash{}cdot \textbackslash{}mathbf\{S\} j) \textbackslash{}otimes \textbackslash{}exp(-r \{ij\}/\textbackslash{}xi \{neural\})\$ Formal Technical Dissertation: Governs the momentum transfer for tactile feedback. It models the exchange interaction between the ferrite core's electron spins and the operator's biological spin-density, allowing the user to "feel" the turbine's torque as a proprioceptive extension. Source: [12], [13]

\paragraph{Canonical Equation.}
\[
\hat{K} {ex} = -2 \sum {i,j} J_{ij}(L) (\mathbf{S} i \cdot \mathbf{S} j) \otimes \exp(-r {ij}/\xi {neural})
\]

\paragraph{Dictionary.}
ELECTRON-NEURAL EXCHANGE OPERATOR Canonical Statutory Formula: \$K ex = -2 i,j J\_ij(L) (S i S j) (-r ij/ neural)\$ Formal Technical Dissertation: Governs the momentum transfer for tactile feedback.

\paragraph{Encyclopedia.}
ELECTRON-NEURAL EXCHANGE OPERATOR Canonical Statutory Formula: K Ex is a series / summation, written K ex = -2 ∑ i,j J\_ij(L) (S i · S j) ⊗ exp(-r ij/ξ neural). It is expressed as a sum or series over modes or indices, superposing discrete contributions. It is built from ξ, j, J\_ij, L, S, r, defining K ex. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
