\section*{ID9417: Definition of 𝝎vort}
\paragraph{Metadata.}
PiID: 2571429894671 | RTEID: RTE:P36568.3023:T3.7046 | UUID: 895e2a5d-77f0-5370-9dbf-8a596d66a69c

\paragraph{Canonical Statement.}
tor. Dedicated proof appendix for [ID 0379] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0378], [ID 0300] Node registry\_id\_0379 Support Titles Vorticity Source; Circulation Law; Vortex Operator Test Handle If the velocity carrier cannot generate the stated vortex sector, the entry fails. Canonical Equation Links \$𝝎vort=∇×v Γ= ∮\$ 𝜕𝑆 v·𝑑ℓ Vgen \$(v)=∇×v\$ [ID 0380] Induced Vector Potential Term TZPID ID0380 UUID d004349f-18d1-5a47-92cd-977f15829777 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops induced vector potential term inside th

\paragraph{Canonical Equation.}
\[
𝝎vort=∇×v Γ= ∮
\]

\paragraph{Dictionary.}
Definition of 𝝎vort — 𝝎vort=∇×v Γ= ∮

\paragraph{Encyclopedia.}
Definition of 𝝎vort is an algebraic definition, written 𝝎vort=∇×v Γ= ∮. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from v, defining 𝝎vort. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
