\tzpanchor{0031}
\tzpentryheader{0031}{Hamilton--Jacobi Equation (Trawinistic Form)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{1450e473-0fd6-5784-9045-61d8b17e6334}}\\
\textbf{PiID} & \tzpcode{0288419716939} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{38}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{120.3799 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.1983 rad}\\
\textbf{TZPID} & \tzpcode{ID0031} & \textbf{Node Dependencies}\quad \tzpidref{0006}\\
\textbf{Registry} & \tzpcode{registry\_id\_0031} & \textbf{Scale}\quad classical-dynamics\\
\textbf{LOC Classification} & QC20 classical action methods & QA320 Hamilton--Jacobi theory\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: gr-qc, hep-th & \\
\textbf{Primary Support} & Action Gradient as Momentum & Time-Evolution Term\\
\textbf{Closure Support} & Trawinistic Hamilton--Jacobi Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The action $S$ for a classical trajectory in $M$ satisfies \( \partial S/\partial t + \mathcal{H}_{T}(q,\partial S/\partial q,t)=0 \), where $\mathcal{H}_{T}$ is the Trawinistic Hamiltonian density and $q$ denotes the configuration variables.

\tzpsection{Canonical Equation}
\[
\frac{\partial S}{\partial t}
\;+\;
\mathcal{H}_{\mathrm{T}}
\!\left(
q,\frac{\partial S}{\partial q},t
\right)
=0
\]
\[
p=\frac{\partial S}{\partial q}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S$: source equation symbol.
    \item $t$: source equation symbol.
    \item $\mathcal{H}_{\mathrm{T}}$: source equation symbol.
    \item $\mathcal{K}_{0031}$: canonical registry object for entry ID 0031.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0031 generated source Wolfram model *)
ClearAll[K0031, Cr0031, T, R, A, W, I, N];
eq0031$1 = HoldForm[(Partial*S)/(Partial*t) + HT[q, (Partial*S)/(Partial*q), t] == 0];
eq0031$2 = HoldForm[p == (Partial*S)/(Partial*q)];
eq0031$3 = HoldForm[(Partial*S)/(Partial*t)];

K0031 = HoldForm[{eq0031$1, eq0031$2, eq0031$3}];

N = "normalized TRAWIN closure object for Hamilton--Jacobi Equation (Trawinistic Form)";
I = "Trawinistic Hamilton--Jacobi Closure integration/comparison layer";
W = "Time-Evolution Term wave or operator carrier";
A = "Action Gradient as Momentum admissible action/amplitude condition";
R = "Time-Evolution Term rotation/curl preservation layer";
T = "Action Gradient as Momentum local source condition";

Cr0031[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0031 = Cr0031[K0031];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Action Gradient as Momentum local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Time-Evolution Term rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Action Gradient as Momentum admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Time-Evolution Term wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Trawinistic Hamilton--Jacobi Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Hamilton--Jacobi Equation (Trawinistic Form).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0031] Hamilton--Jacobi Equation (Trawinistic Form)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{\partial S}{\partial t}
+
\mathcal{H}_T
\left(
q,\frac{\partial S}{\partial q},t
\right)
=
0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $S(q,t)$ be the action function for a classical trajectory on the Trawinistic manifold.  
The canonical momentum is obtained from the action by:

\begin{equation}
p_q=\frac{\partial S}{\partial q}.
\end{equation}

The Hamiltonian density or Hamiltonian function in Trawinistic form is:

\begin{equation}
\mathcal{H}_T(q,p_q,t).
\end{equation}

Substituting $p_q=\partial S/\partial q$ into the Hamiltonian gives:

\begin{equation}
\mathcal{H}_T
\left(
q,\frac{\partial S}{\partial q},t
\right).
\end{equation}

The Hamilton--Jacobi condition states that time evolution of the action cancels the Hamiltonian contribution:

\begin{equation}
\boxed{
\frac{\partial S}{\partial t}
+
\mathcal{H}_T
\left(
q,\frac{\partial S}{\partial q},t
\right)
=
0 .
}
\end{equation}

\paragraph{Interpretation.}
This equation translates Trawinistic Hamiltonian dynamics into an action-based evolution law.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Hamilton--Jacobi Equation (Trawinistic Form) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Action Gradient as Momentum}\par
\[
p=\frac{\partial S}{\partial q}
\]
\noindent This replaces canonical momentum by the spatial gradient of the action.\par
\noindent\textbf{2. Time-Evolution Term}\par
\[
\frac{\partial S}{\partial t}
\]
\noindent This supplies the temporal variation needed to balance the Hamiltonian sector.\par
\noindent\textbf{3. Trawinistic Hamilton--Jacobi Closure}\par
\[
\frac{\partial S}{\partial t}
\;+\;
\mathcal{H}_{\mathrm{T}}
\!\left(
q,\frac{\partial S}{\partial q},t
\right)
=0
\]
\noindent This closes the progression by packaging classical evolution into one scalar first-order equation.\par

\clearpage
\noindent\textbf{[ID 0031] Hamilton--Jacobi Equation (Trawinistic Form)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Hamilton--Jacobi Equation (Trawinistic Form) is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The action S for a classical trajectory in M satisfies partial S/partial t + H sub T (q,partial S/partial q,t)=0 , where H sub T is the Trawinistic Hamiltonian density and q denotes the configuration variables. \textbf{Contextual meaning:} The entry reads Hamilton--Jacobi Equation (Trawinistic Form) as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This equation connects the canonical Hamiltonian sector to classical trajectory theory. It is the natural bridge from field-energy language into ray, path, and semiclassical approximations near the anchor. \textbf{Lemma support:} Action Gradient as Momentum; Time-Evolution Term; Trawinistic Hamilton--Jacobi Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This equation translates Trawinistic Hamiltonian dynamics into an action-based evolution law.

\tzpsection{Equation Grounding}
Equation anchors: The action SSS for a classical trajectory in MMM satisfies partialSpartialt+HT(q,partialSpartialq,t)=0ratio partial S partial t + H T bigl(q,ratio partial S partial q ,tbigr)=0partialtpartialS+HT(q,partialqpartialS,t)=0, where HT H T HT is the Trawinistic Hamiltonian density and qqq denotes the configuration variables. The action SSS for a classical trajectory in MMM satisfies partialSpartialt+HT(q,partialSpartialq,t)=0ratio partial S partial t + H T bigl(q,ratio partial S partial q ,tbigr)=0partialtpartialS+HT(q,partialqpartialS,t)=0, where HT H T HT is the Trawinistic Hamiltonian density and qqq denotes the configuration variables.

\tzpsection{Interpretive Role}
This equation connects the canonical Hamiltonian sector to classical trajectory theory. It is the natural bridge from field-energy language into ray, path, and semiclassical approximations near the anchor.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Hamilton Jacobi Equation Trawinistic Form}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Hamilton Jacobi Equation Normalization Analogue}: normalization vocabulary for fixed form, invariant comparison, or TRAWIN admissibility.
\item \textbf{Form Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0031]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0031_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0031] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Hamilton--Jacobi Equation (Trawinistic Form)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the action S for a classical trajectory in M satisfies \textbackslash{}( tial S/ tial t + H\_T(q,
tial S/ tial q,t)=0 \textbackslash{}), where H\_T is the Trawinistic Hamilt...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Hamilton--Jacobi Equation (Trawinistic Form) is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0031_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
