\section*{ID9400: Definition of Φ𝜆𝑛}
\paragraph{Metadata.}
PiID: 2543709069793 | RTEID: RTE:P36502.2875:T3.5959 | UUID: 4b134ce2-0edd-53d9-ab0e-afd86b8359d4

\paragraph{Canonical Statement.}
for [ID 0312] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0311], [ID 0300] Node registry\_id\_0312 Support Titles Variation Law; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links \$Φ𝜆𝑛=R𝜆 (Φ𝑛\$ ) \$R𝜆:𝑇2→𝑇2 I(R𝜆Φ)=I(Φ)\$ [ID 0313] Time as a Toroidal Winding Parameter TZPID ID0313 UUID f1791df6-8d5a-54c5-800e-ee2ea864c611 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops time as a toroidal winding par

\paragraph{Canonical Equation.}
\[
Φ𝜆𝑛=R𝜆 (Φ𝑛
\]

\paragraph{Dictionary.}
Definition of Φ𝜆𝑛 — Φ𝜆𝑛=R𝜆 (Φ𝑛

\paragraph{Encyclopedia.}
Definition of Φ𝜆𝑛 is an algebraic definition, written Φ𝜆𝑛=R𝜆 (Φ𝑛. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R, defining Φ𝜆𝑛. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
