\section*{ID9832: Resulting Entangled Electron–Phonon Kernels: g\_n,σ(q)}
\paragraph{Metadata.}
PiID: 5134105592401 | RTEID: RTE:P38179.8395:T0.0768 | UUID: 4e3b4f05-38b4-5ba1-869d-2bdfaad15a74

\paragraph{Canonical Statement.}
Under suitable approximations (linear response, weak coupling), one can derive effective kernels \textbackslash{}[ K\_\{e,\textbackslash{}mathrm\{ph\}\}(x\_e,x\_\{\textbackslash{}mathrm\{ph\}\};\textbackslash{}theta\_\{e,\textbackslash{}mathrm\{ph\}\}) \textbackslash{}] describing the joint state of an electron at position \$x\_e\$ and a phonon at \$x\_\{\textbackslash{}mathrm\{ph\}\}\$. The design task then becomes to tune \$g\_\{n,\textbackslash{}sigma\}(q)\$, and thus the local geometry and composition parameters, so that \$K\_\{e,\textbackslash{}mathrm\{ph\}\}\$ approximates a desired target kernel, for example one that maximizes a specific entanglement monotone while respecting energy and bandwidth constraints.

\paragraph{Canonical Equation.}
\[
g_{n,\sigma}(q)
\]

\paragraph{Dictionary.}
Under suitable approximations (linear response, weak coupling), one can derive effective kernels describing the joint state of an electron at position x\_e and a phonon at x\_ph.

\paragraph{Encyclopedia.}
Resulting Entangled Electron–Phonon Kernels: g\_n,σ(q) is a symbolic expression, written g\_n,σ(q). It introduces a symbol or relation used elsewhere in the framework. It is built from σ, g\_n, q. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
