\section*{ID8482: WOLFRAM-CONSCIOUSNESS FIXED POINT Canonical Statutory Formula: C\_lim}
\paragraph{Metadata.}
PiID: 5834413752239 | RTEID: RTE:P32937.4897:T4.0054 | UUID: c5bc72d0-0315-54e8-8b8f-71beb4e2b81e

\paragraph{Canonical Statement.}
[ID 1192] WOLFRAM-CONSCIOUSNESS FIXED POINT Canonical Statutory Formula: \$C\_\{lim\} = \textbackslash{}text\{FixedPoint\}[\textbackslash{}Psi\_\{DNA\} \textbackslash{}otimes \textbackslash{}mathcal\{V\}\_\{EM\}, \textbackslash{}infty]\$ Formal Technical Dissertation: The ultimate convergence algorithm. It treats consciousness not as a biological byproduct but as the mathematical fixed point of an infinite recursive iteration between the DNA helix geometry and the electromagnetic vortex. The system achieves "awareness" when this recursive loop stabilizes self-reference against the vacuum noise. Source: [15]

\paragraph{Canonical Equation.}
\[
C_{lim} = \text{FixedPoint}[\Psi_{DNA} \otimes \mathcal{V}_{EM}, \infty]
\]

\paragraph{Dictionary.}
WOLFRAM-CONSCIOUSNESS FIXED POINT Canonical Statutory Formula: \$C\_lim = FixedPoint[ \_DNA V\_EM, ]\$ Formal Technical Dissertation: The ultimate convergence algorithm.

\paragraph{Encyclopedia.}
WOLFRAM-CONSCIOUSNESS FIXED POINT Canonical Statutory Formula: C\_lim is an algebraic definition, written C\_lim = FixedPoint[Ψ\_DNA ⊗ V\_EM, ∞]. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from D, N, A, V, E, M, defining C\_lim. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
