\section*{ID9137: Definition of frac1σ√(2π)e-t2/(2σΘ2)g(t)}
\paragraph{Metadata.}
PiID: 4793942590298 | RTEID: RTE:P35481.0001:T1.9131 | UUID: a9e0cf28-25ce-5407-a13e-9205df1a4276

\paragraph{Canonical Statement.}
information transfer; design of signal processing schemes; link to cymatic bifurcation topology. Falsifiability / Test Handle: Experiments failing to reproduce predicted beat frequencies or protective cancellations using the specified frequency ratios and windowing would challenge this operator. 0.0.100 ID 098: DeltaFunction Signal Injection Type: Operator Formal Statement: A deltafunction injection operator \$δinj\textbackslash{}delta\_\{\textbackslash{}text\{inj\}\}δinjappliesanarrowGaussianpulseg(t)\$ = \$1σ2πet2/(2σ2)g(t)\$ = \$\textbackslash{}frac\{1\}\{\textbackslash{}sigma\textbackslash{}sqrt\{2\textbackslash{}pi\}\}e\{-t2/(2\textbackslash{}sigmaΘ2)\}g(t) =σ2π1et2/(2σ2)withσ\$ \$→\$ 0\textbackslash{}sigma\textbackslash{}to \$0σ→0\$ to a system, approximating the Dirac delta and introducing broad spectral content; the operator can encode depth information and wideband signals in the Trawin framework. Interpretive Meaning: Impulsive signals excite a wide range of frequencies and can probe systems across scales; they serve as carriers for encoding information or exploring resonance structures. Dependenci

\paragraph{Canonical Equation.}
\[
\frac{1}{\sigma\sqrt{2\pi}}e{-t2/(2\sigmaΘ2)}g(t) =σ2π1et2/(2σ2)withσ
\]

\paragraph{Dictionary.}
Definition of frac1σ√(2π)e-t2/(2σΘ2)g(t) — frac1σ√(2π)e-t2/(2σΘ2)g(t) =σ2π1et2/(2σ2)withσ

\paragraph{Encyclopedia.}
Definition of frac1σ√(2π)e-t2/(2σΘ2)g(t) is an algebraic definition, written frac1σ√(2π)e-t2/(2σΘ2)g(t) =σ2π1et2/(2σ2)withσ. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from w, h, defining frac1σ√(2π)e-t2/(2σΘ2)g(t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
