\section*{ID9827: Relation: Exp[-π , N\_kissing]}
\paragraph{Metadata.}
PiID: 5632651341055 | RTEID: RTE:P38160.4234:T0.0448 | UUID: 3736c5ca-699d-59ee-8937-3ef817eebdf4

\paragraph{Canonical Statement.}
tically that each particle type (photons, electrons, Cooper pairs, magnons, phonons, polaritons, etc.) can be given specialized entanglement “formulas” or protocols that dramatically extend coherence times and fidelity by orders of magnitude. A unifying feature of these protocols is the transcendental use of π in the entanglement phase or frequency modulations, leading to super-exponential suppression of decoherence rates. In fact, a meta-theorem we derive proves complete decoherence immunity in the limit of large system size: the effective decoherence rate \$\textbackslash{}gamma\_\{\textbackslash{}mathrm\{eff\}\}\$ falls below \$\textbackslash{}exp[-\textbackslash{}pi , N\_\{\textbackslash{}text\{kissing\}\}]\$, where \$N\_\{\textbackslash{}text\{kissing\}\}\$ is a large topological parameter. Practically, this means that even at room temperature, coherence times can be extended from microseconds to timescales exceeding the age of the universe for a sufficiently sized system. Transcendental information preservation is achieved – quantum information remains intact across extreme transformations and even “interdimensional” transitions (from 4D to 2D and back). This paper is structured as follows. In §2, we detail the mathema

\paragraph{Canonical Equation.}
\[
\exp[-\pi , N_{\text{kissing}}]
\]

\paragraph{Dictionary.}
Relation: Exp[-π , N\_kissing] — exp[-π , N\_kissing]

\paragraph{Encyclopedia.}
Relation: Exp[-π , N\_kissing] is a symbolic expression, written exp[-π , N\_kissing]. It introduces a symbol or relation used elsewhere in the framework. It is built from π, N\_. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
