\section*{ID9088: Definition of g\_µ}
\paragraph{Metadata.}
PiID: 8253375438856 | RTEID: RTE:P35290.7222:T1.5996 | UUID: d35620f9-d4c6-5fb3-b1ca-0f6d337c7552

\paragraph{Canonical Statement.}
ts; ties to gyromagnetic coupling constant; supports rotationinduced magnetism; influences scaling functor. Falsifiability / Test Handle: Empirical data showing significant deviations from the proportionality across diverse systems would disprove this law. Canonical Registry Vol. 01 16 Trawin Zero Point Contextus Canonicus 0.0.47 ID 045: Dimensionless Gyromagnetic Coupling Constant Type: Definition Formal Statement: The dimensionless gyromagnetic coupling constant \$g\_µg\_\{\textbackslash{}mu\}g\_µ\$ is defined by \$g\_µ=µMR2Ωg\_\{\textbackslash{}mu\}=\textbackslash{}frac\{\textbackslash{}mu\}\{M,Rˆ2,\textbackslash{}Omega\}g\_µ=MR2Ωµ,\$ where \$µ\textbackslash{}muµ\$ is the magnetic moment and M,R,ΩM,R,\textbackslash{}OmegaM,R,Ω as in ID 044. In the Trawinistic framework, \$g\_µg\_\{\textbackslash{}mu\}g\_µ\$ is predicted to be O(1)\textbackslash{}mathcal\{O\}(1)O(1) across systems. Interpretive Meaning: This constant quantifies the universality of the relationship between rotation and magnetism. It collapses the scaling law of ID 044 into a single number expected to remain nearly constant. Depen

\paragraph{Canonical Equation.}
\[
g_µ=µMR2Ωg_{\mu}=\frac{\mu}{M,Rˆ2,\Omega}g_µ=MR2Ωµ,
\]

\paragraph{Dictionary.}
Definition of g\_µ — g\_µ=µMR2Ωg\_μ=(μ)/(M,Rˆ2,Ω)g\_µ=MR2Ωµ

\paragraph{Encyclopedia.}
Definition of g\_µ is an algebraic definition, written g\_µ=µMR2Ωg\_μ=(μ)/(M,Rˆ2,Ω)g\_µ=MR2Ωµ. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from μ, Ω, M, R, g\_, g, defining g\_µ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
