\tzpanchor{0311}
\tzpentryheader{0311}{Holographic Encoding and Redundancy}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{db3d0cd5-3189-556e-ac37-f126fa9a6c95}}\\
\textbf{PiID} & \tzpcode{6315588174881} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{318}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1207.6821 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.9899 rad}\\
\textbf{TZPID} & \tzpcode{ID0311} & \textbf{Node Dependencies}\quad \tzpidref{0310}\\
\textbf{Registry} & \tzpcode{registry\_id\_0311} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In the recursive fiber bundle interpretation, every local loop (address) on the sphere encodes the full torus. Consequently, local access implies global access; perturbation of a single loop modifies the global toroidal state; and information is distributed rather than localized.

\tzpsection{Canonical Equation}
\[
\mathcal{E}:\mathcal{H}_{\mathrm{bulk}}\longrightarrow \mathcal{H}_{\partial}
\]
\[
S_{\mathrm{bulk}}\leq \frac{A(\partial\Omega)}{4G\hbar},
\qquad
\mathcal{R}_{\partial}\geq \mathcal{R}_{\mathrm{bulk}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{E}$: source equation symbol.
    \item $\mathcal{H}_{\mathrm{bulk}}$: source equation symbol.
    \item $\mathcal{H}_{\partial}$: source equation symbol.
    \item $S_{\mathrm{bulk}}$: source equation symbol.
    \item $A$: source equation symbol.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
    \item $\mathcal{R}_{\partial}$: source equation symbol.
    \item $\mathcal{R}_{\mathrm{bulk}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0311 generated source Wolfram model *)
ClearAll[K0311, Cr0311, T, R, A, W, I, N];
eq0311$1 = HoldForm[E[Hbulk] -> Hpartial];
eq0311$2 = HoldForm[TZPSequence[SBulk <= A[PartialOmega]/(4*Ghbar), RPartial >= RBulk]];
eq0311$3 = HoldForm[SBulk <= A[PartialOmega]/(4*Ghbar)];
eq0311$4 = HoldForm[RPartial >= RBulk];

K0311 = HoldForm[{eq0311$1, eq0311$2, eq0311$3, eq0311$4}];

N = "normalized TRAWIN closure object for Holographic Encoding and Redundancy";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0311[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0311 = Cr0311[K0311];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Holographic Encoding and Redundancy.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0311] Holographic Encoding and Redundancy}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
I_{\mathrm{CL}}
=
\oint_{\Gamma} A\cdot \mathrm{d}x .
\end{equation}

\paragraph{Primary Derivation.}
Let $\Gamma$ be a closed causal loop passing through or encircling the TZP.  
Let $A$ be a one-form potential defined along the loop.

The infinitesimal contribution of the potential along the path is:

\begin{equation}
A\cdot \mathrm{d}x .
\end{equation}

Integrating this contribution over the full closed loop gives the loop invariant:

\begin{equation}
I_{\mathrm{CL}}
=
\oint_{\Gamma} A\cdot \mathrm{d}x .
\end{equation}

If $\mathrm{d}A=0$ away from $p$ and support is concentrated at the TZP, then the loop integral depends only on the causal winding around $p$.

\paragraph{Interpretation.}
$I_{\mathrm{CL}}$ records the accumulated causal phase around the TZP. It is invariant under deformations of $\Gamma$ that preserve the winding relation to $p$.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Holographic Encoding and Redundancy by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
\mathcal{E}:\mathcal{H}_{\mathrm{bulk}}\longrightarrow \mathcal{H}_{\partial}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
S_{\mathrm{bulk}}\leq \frac{A(\partial\Omega)}{4G\hbar}
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\mathcal{R}_{\partial}\geq \mathcal{R}_{\mathrm{bulk}}
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0311] Holographic Encoding and Redundancy}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Holographic Encoding and Redundancy is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} In the recursive fiber bundle interpretation, every local loop (address) on the sphere encodes the full torus. Consequently, local access implies global access; perturbation of a single loop modifies the global toroidal state; and information is distributed rather than localized. \textbf{Contextual meaning:} The entry reads Holographic Encoding and Redundancy as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
I sub CL records the accumulated causal phase around the TZP. It is invariant under deformations of that preserve the winding relation to p.

\tzpsection{Equation Grounding}
Equation anchors: 600 to 2400 to 9600 to 38400 to 153600; Tjr [L48] u223c= T; and r [L44] The addressed spatial point is:r [L45] pi,k = ri,k nir [L46] , ri,k = er [L47] ti,kr [L48]. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Boundary-Volume Information Bound}: The principle dictating that the total entropy of a 3D region is strictly limited by its 2D enclosing surface area.
\item \textbf{Fault-Tolerant Surface Mapping}: The coding paradigm distributing local bulk data across a globally entangled topological boundary.
\item \textbf{Dimensionally Reduced State Storage}: The physical constraint encoding full field dynamics entirely within the boundary shell metrics.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0311]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0311_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0311] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Holographic Encoding and Redundancy}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in the recursive fiber bundle interpretation, every local loop (address) on the sphere
encodes the full torus

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Holographic Encoding and Redundancy is well formed when the total space, base space,
structure group, and projection map are compatible.''\\
\textbf{Proof:} The source statement supplies a bundle-style construction. The CHL reading treats the
base as the proposition carrier, the fiber or structure group as the typed parameter,
and the projection as the categorical morphism that preserves local-to-global structure.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- principal-bundle structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0311_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
