\tzpanchor{0206}
\tzpentryheader{0206}{Phonon--Magnon Coupling Hamiltonian}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{effa07f7-f254-5420-a685-a4e7a868510a}}\\
\textbf{PiID} & \tzpcode{0975665933446} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{213}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{799.9437 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.3181 rad}\\
\textbf{TZPID} & \tzpcode{ID0206} & \textbf{Node Dependencies}\quad \tzpidref{0205}\\
\textbf{Registry} & \tzpcode{registry\_id\_0206} & \textbf{Scale}\quad field-dynamical\\
\textbf{LOC Classification} & QC20.7 field theory & QA321 variational structure\\
\textbf{arXiv Classification} & Primary: hep-th & Cross-list: math-ph, gr-qc\\
\textbf{Primary Support} & Energy Generator & State Evolution\\
\textbf{Closure Support} & Closure Constraint & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The interaction Hamiltonian for topological phonon--magnon coupling is given by H\_int = g * integral{[}(curl u) dot B{]} dV, where u is the acoustic displacement field, B is the magnetic field and g is the magneto-elastic coupling constant.

\tzpsection{Canonical Equation}
\[
H_{\mathrm{int}} = g\int_V (\nabla\times u)\cdot B\,dV
\]
\[
i\hbar\,\partial_t\psi = H_{\mathrm{int}}\psi
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H_{\mathrm{int}}$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
    \item $\mathcal{N}_{\mathrm{TZP}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0206 generated source Wolfram model *)
ClearAll[K0206, Cr0206, T, R, A, W, I, N];
eq0206$1 = HoldForm[HInt == gIntegralV[Grad*u]*B*dV];
eq0206$2 = HoldForm[ihbar*PartialTpsi == HIntpsi];
eq0206$3 = HoldForm[Commutator[HInt, NTZP] == 0];

K0206 = HoldForm[{eq0206$1, eq0206$2, eq0206$3}];

N = "normalized TRAWIN closure object for Phonon--Magnon Coupling Hamiltonian";
I = "Closure Constraint integration/comparison layer";
W = "State Evolution wave or operator carrier";
A = "Energy Generator admissible action/amplitude condition";
R = "State Evolution rotation/curl preservation layer";
T = "Energy Generator local source condition";

Cr0206[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0206 = Cr0206[K0206];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Energy Generator local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ State Evolution rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Energy Generator admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ State Evolution wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Constraint integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Phonon--Magnon Coupling Hamiltonian.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0206] Phonon--Magnon Coupling Hamiltonian}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
u_T := \int_{\Gamma}\sqrt{|g|}\,\mathrm{d}\ell .
\end{equation}

\paragraph{Primary Derivation.}
Let $\Gamma$ be a fundamental loop encircling the Trawin Zero Point exactly once.  
The infinitesimal line element induced by the metric is:

\begin{equation}
\mathrm{d}s = \sqrt{|g|}\,\mathrm{d}\ell .
\end{equation}

Integrating this metric-weighted length around the loop gives the primitive unit associated with one complete encirclement of the TZP:

\begin{equation}
u_T = \int_{\Gamma}\mathrm{d}s .
\end{equation}

Substituting the line element yields:

\begin{equation}
\boxed{
u_T := \int_{\Gamma}\sqrt{|g|}\,\mathrm{d}\ell .
}
\end{equation}

\paragraph{Interpretation.}
The Trawin base unit $u_T$ is the fundamental geometric unit obtained by completing one metric-weighted loop around the TZP.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Phonon--Magnon Coupling Hamiltonian by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Energy Generator}\par
\[
H_{\mathrm{int}} = g\int_V (\nabla\times u)\cdot B\,dV
\]
\noindent This gathers the free, interaction, and bridge sectors into one energy generator.\par
\noindent\textbf{2. State Evolution}\par
\[
i\hbar\,\partial_t\psi = H_{\mathrm{int}}\psi
\]
\noindent This promotes the generator into the actual carrier of admissible state evolution.\par
\noindent\textbf{3. Closure Constraint}\par
\[
[H_{\mathrm{int}},\mathcal{N}_{\mathrm{TZP}}]=0
\]
\noindent This closes the entry by requiring compatibility with the normalization operator.\par

\clearpage
\noindent\textbf{[ID 0206] Phonon--Magnon Coupling Hamiltonian}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Phonon--Magnon Coupling Hamiltonian is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The interaction Hamiltonian for topological phonon--magnon coupling is given by H sub int = g * integral [ (curl u) dot B ] dV, where u is the acoustic displacement field, B is the magnetic field and g is the magneto-elastic coupling constant. \textbf{Contextual meaning:} The entry reads Phonon--Magnon Coupling Hamiltonian as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry upgrades the surrounding resonance narrative into a full energy generator that can govern evolution rather than merely describe structure. \textbf{Lemma support:} Energy Generator; State Evolution; Closure Constraint.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The Trawin base unit u sub T is the fundamental geometric unit obtained by completing one metric-weighted loop around the TZP.

\tzpsection{Equation Grounding}
Equation anchors: H sub int = gintegral sub V (nablatimes u)dot B dV; ihbar partial sub tpsi = H sub int psi; and [H sub int , N sub TZP ]=0. Proof route: show that the bridge correction preserves admissible Hamiltonian evolution and commutes with the TRAWIN normalization sector. Formalization route: prove that the corrected Hamiltonian yields unitary evolution on the admissible state space.

\tzpsection{Interpretive Role}
The entry upgrades the surrounding resonance narrative into a full energy generator that can govern evolution rather than merely describe structure.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Acoustic-Spintronic Interaction Generator}: The quantum mechanical operator driving the exchange of energy between lattice vibrations and spin waves.
\item \textbf{Magnetoelastic Energy Exchange Term}: The explicit mathematical term capturing how structural strain modifies local magnetic moments.
\item \textbf{Lattice-Spin State Coherence Matrix}: The density matrix tracking the synchronized entanglement between sound quanta and magnetic quanta.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0206]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0206_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0206] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Phonon--Magnon Coupling Hamiltonian}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the interaction Hamiltonian for topological phonon--magnon coupling is given by H\textbackslash{}\_int =
g * integral[(curl u) dot B] dV, where u is the acoustic d...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Phonon--Magnon Coupling Hamiltonian is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0206_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
