\section*{ID9520: Concluding Synthesis: √(64/27)≈1.5396}
\paragraph{Metadata.}
PiID: 0276347870810 | RTEID: RTE:P36968.2742:T4.3637 | UUID: 3fe2fc33-766b-5fab-a7e3-63e0d4826eb2

\paragraph{Canonical Statement.}
One possible point of contact is in cosmological phase transitions: sometimes rational numbers emerge in series expansions or stability criteria. For instance, one recent analysis of axion-like particle oscillations gave a stability limit at \$\textbackslash{}hat\textbackslash{}lambda = -\textbackslash{}sqrt\{64/27\}\$ in scaled units arxiv.org . Here \$\textbackslash{}sqrt\{64/27\}\textbackslash{}approx1.5396\$, so this is not our number but shows how such fractions can arise from algebraic conditions. The specific value 1.185 did not show up in mainstream vacuum energy or cosmological constant resolutions (which typically involve enormous ratios \textasciitilde{}\$10\textasciicircum{}\{120\}\$, not order-1). In short, no connection of 1.185 to vacuum energy or emergent gravity is evident in known research.

\paragraph{Canonical Equation.}
\[
\sqrt{64/27}\approx1.5396
\]

\paragraph{Dictionary.}
One possible point of contact is in cosmological phase transitions: sometimes rational numbers emerge in series expansions or stability criteria [ID9520]

\paragraph{Encyclopedia.}
Concluding Synthesis: √(64/27)≈1.5396 is a scaling / order-of-magnitude relation, written √(64/27)≈1.5396. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
