\tzpanchor{0340}
\tzpentryheader{0340}{Anomalous Transport at Metamaterial Interfaces}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{5f0569d5-7803-5263-8bb9-e32570f0c75d}}\\
\textbf{PiID} & \tzpcode{9171536436789} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{347}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1320.2955 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.1754 rad}\\
\textbf{TZPID} & \tzpcode{ID0340} & \textbf{Node Dependencies}\quad \tzpidref{0339}\\
\textbf{Registry} & \tzpcode{registry\_id\_0340} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Transport Current & Interface Continuity\\
\textbf{Closure Support} & Interface Jump Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
At interfaces between strong and weak metamaterial regions, transport phenomena deviate from simple diffusion due to impedance mismatch and quantum coherence. These anomalies manifest as enhanced or suppressed transmission, resonant tunnelling, and localized mode trapping.

\tzpsection{Canonical Equation}
\[
\mathbf{J}=-D(x)\nabla\psi
\]
\[
[\psi]_{\Sigma}=0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $J$: source equation symbol.
    \item $D$: source equation symbol.
    \item $n$: integer mode index.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $\psi$: source equation symbol.
    \item $\Sigma$: conductivity or coupling coefficient in the source equation.
    \item $\partial_{n}$: source equation symbol.
    \item $\kappa$: source equation symbol.
    \item $S$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0340 generated source Wolfram model *)
ClearAll[K0340, Cr0340, T, R, A, W, I, N];
eq0340$1 = HoldForm[J == (-D[x])*Gradpsi];
eq0340$2 = HoldForm[Jump[psi, Sigma] == 0];
eq0340$3 = HoldForm[Jump[D*PartialN*psi, Sigma] == kappa*psi];

K0340 = HoldForm[{eq0340$1, eq0340$2, eq0340$3}];

N = "normalized TRAWIN closure object for Anomalous Transport at Metamaterial Interfaces";
I = "Interface Jump Law integration/comparison layer";
W = "Interface Continuity wave or operator carrier";
A = "Transport Current admissible action/amplitude condition";
R = "Interface Continuity rotation/curl preservation layer";
T = "Transport Current local source condition";

Cr0340[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0340 = Cr0340[K0340];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Transport Current local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Interface Continuity rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Transport Current admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Interface Continuity wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Interface Jump Law integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Anomalous Transport at Metamaterial Interfaces.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0340] Anomalous Transport at Metamaterial Interfaces}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Lambda_{\mathrm{crit}}\approx 1 .
\end{equation}

\paragraph{Primary Derivation.}
From the Elsasser parameter,

\begin{equation}
\Lambda
=
\frac{\mathbf{B}^2}
{\rho\,\mu\,\Omega^2},
\end{equation}

criticality occurs when magnetic and rotational terms are balanced.

Balance means the numerator and denominator are of the same order:

\begin{equation}
\mathbf{B}^2
\sim
\rho\,\mu\,\Omega^2 .
\end{equation}

Therefore,

\begin{equation}
\frac{\mathbf{B}^2}
{\rho\,\mu\,\Omega^2}
\sim
1 .
\end{equation}

Thus,

\begin{equation}
\boxed{
\Lambda_{\mathrm{crit}}\approx 1 .
}
\end{equation}

\paragraph{Interpretation.}
The critical Elsasser value marks a universal balance architecture across scales: the point where magnetic organization and rotational inertia enter comparable strength.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Anomalous Transport at Metamaterial Interfaces by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Transport Current}\par
\[
\mathbf{J}=-D(x)\nabla\psi
\]
\noindent This fixes the transport current driving propagation across the heterogeneous carrier.\par
\noindent\textbf{2. Interface Continuity}\par
\[
[\psi]_{\Sigma}=0
\]
\noindent This imposes continuity of the transported amplitude across the metamaterial interface.\par
\noindent\textbf{3. Interface Jump Law}\par
\[
[D\partial_{n}\psi]_{\Sigma}=\kappa\psi
\]
\noindent This closes the entry with the interface jump condition that encodes anomalous transmission and trapping.\par

\clearpage
\noindent\textbf{[ID 0340] Anomalous Transport at Metamaterial Interfaces}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Anomalous Transport at Metamaterial Interfaces is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} At interfaces between strong and weak metamaterial regions, transport phenomena deviate from simple diffusion due to impedance mismatch and quantum coherence. These anomalies manifest as enhanced or suppressed transmission, resonant tunnelling, and localized mode trapping. \textbf{Contextual meaning:} The entry reads Anomalous Transport at Metamaterial Interfaces as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states anomalous interface transport through an actual continuity-and-jump system instead of narrative-only prose. \textbf{Lemma support:} Transport Current; Interface Continuity; Interface Jump Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The critical Elsasser value marks a universal balance architecture across scales: the point where magnetic organization and rotational inertia enter comparable strength. \% ========================================================= \% QUATERNARY DERIVATION LAYER -- ID 0341 TO ID 0345 \% =========================================================.

\tzpsection{Equation Grounding}
Equation anchors: J=-D(x) ablapsi; [psi] sub Sigma =0; and [D partial sub npsi] sub Sigma =kappa sub Sigma psivert sub Sigma. Proof route: show that the stated continuity and jump laws organize the anomalous transmission regime at the metamaterial interface. Formalization route: prove that the interface jump law is compatible with the transported current and continuous carrier amplitude.

\tzpsection{Interpretive Role}
The entry now states anomalous interface transport through an actual continuity-and-jump system instead of narrative-only prose.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Discontinuous Interface Jumping}: The non-standard boundary condition where fields experience sudden shifts in phase or amplitude when crossing material boundaries.
\item \textbf{Trapped Surface States}: The accumulation of energy exactly at the border between two different metamaterials due to mismatched impedance.
\item \textbf{Non-Ohmic Current Flow}: The localized regime where transport properties do not follow standard linear resistance, yielding asymmetric transmission.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0340]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0340_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0340] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Anomalous Transport at Metamaterial Interfaces}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} at interfaces between strong and weak metamaterial regions, transport phenomena deviate
from simple diffusion due to impedance mismatch and quantum...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Anomalous Transport at Metamaterial Interfaces is valid as a formal dynamical law when
the Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0340_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
