\section*{ID9341: Definition of ∇𝜈𝑇𝜇𝜈total}
\paragraph{Metadata.}
PiID: 2151375560037 | RTEID: RTE:P36273.1774:T3.2184 | UUID: 37590dfb-c0ae-5e17-89fa-12c501e5bd72

\paragraph{Canonical Statement.}
luded in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0139], [ID 0041] Node registry\_id\_0150 Support Titles Total Tensor Sum; Covariant Conservation; Gravitational Closure Test Handle If the summed total tensor cannot be made divergence-free while still satisfying the stated gravitational closure law, the constraint fails. Canonical Equation Links 𝑇 𝜇𝜈 total=𝑇 𝜇𝜈 vacuum+𝑇 𝜇𝜈 matter+𝑇 𝜇𝜈 grav \$∇𝜈𝑇𝜇𝜈total=0 𝐺𝜇𝜈+Λ𝑔𝜇𝜈=\$ 8𝜋𝐺 𝑐4 𝑇total 𝜇𝜈 Stress–Energy Sectors and Higher Unification Topology This grouping begins by unpacking the conservation closure into explicit vacuum, matter, and gravitational tensor sectors. It then lifts the story into topological gerbe indexing, obstruction classes, higher-force categories, bifurcation functors, dimensional adjunctions, and a final Kan-extension rule for global unification.

\paragraph{Canonical Equation.}
\[
∇𝜈𝑇𝜇𝜈total=0 𝐺𝜇𝜈+Λ𝑔𝜇𝜈=
\]

\paragraph{Dictionary.}
Definition of ∇𝜈𝑇𝜇𝜈total — ∇𝜈𝑇𝜇𝜈total=0 𝐺𝜇𝜈+Λ𝑔𝜇𝜈=

\paragraph{Encyclopedia.}
Definition of ∇𝜈𝑇𝜇𝜈total is an algebraic definition, written ∇𝜈𝑇𝜇𝜈total=0 𝐺𝜇𝜈+Λ𝑔𝜇𝜈=. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
