\tzpanchor{0514}
\tzpentryheader{0514}{ELECTROMAGNETIC STRESS-ENERGY TENSOR}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{483f7f35-d918-575f-af84-20f0da6e3710}}\\
\textbf{PiID} & \tzpcode{5664308602139} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{521}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1976.5600 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.2568 rad}\\
\textbf{TZPID} & \tzpcode{ID0514} & \textbf{Node Dependencies}\quad \tzpidref{0513}\\
\textbf{Registry} & \tzpcode{registry\_id\_0514} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Aggregate Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
"Electromagnetic" -> LineBundle[c\_1 = int\_Sigma F/(2pi)],

\tzpsection{Canonical Equation}
\[
Electromagnetic \to LineBundle[c_1 = \int_\Sigma F/(2\pi)]
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $c_1$: source equation symbol.
    \item $F$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $J$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{J}_{\mathrm{out}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0514 generated source Wolfram model *)
ClearAll[K0514, Cr0514, T, R, A, W, I, N];
eq0514$1 = HoldForm[Electromagnetic -> LineBundle[c1 == (Integral_Sigma)*(F/(2*Pi))]];
eq0514$2 = HoldForm[mathcal[J]*_*out == TTZP[KTZP]];
eq0514$3 = HoldForm[mathcal[A]*_*adm*JOut == 1];

K0514 = HoldForm[{eq0514$1, eq0514$2, eq0514$3}];

N = "normalized TRAWIN closure object for ELECTROMAGNETIC STRESS-ENERGY TENSOR";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Aggregate Relation admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Aggregate Relation local source condition";

Cr0514[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0514 = Cr0514[K0514];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Aggregate Relation local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Aggregate Relation admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for ELECTROMAGNETIC STRESS-ENERGY TENSOR.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0514] ELECTROMAGNETIC STRESS-ENERGY TENSOR}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
T_{\mathrm{IM}}
=
\frac{1}{u_T}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi_{m_1}$ and $\phi_{m_2}$ be modal states over the hypersurface $\Sigma$.  
Let $\mathcal{L}$ be the transfer operator.

The transfer amplitude from mode $m_2$ into mode $m_1$ is:

\begin{equation}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
\end{equation}

Because the Trawin base unit $u_T$ defines the primitive loop scale of the system, the normalized transfer rate is:

\begin{equation}
\boxed{
T_{\mathrm{IM}}
=
\frac{1}{u_T}
\int_{\Sigma}
\phi_{m_1}^{*}
\,\mathcal{L}\,
\phi_{m_2}
\,\mathrm{d}\Sigma .
}
\end{equation}

\paragraph{Interpretation.}
ID 0014 repeats and stabilizes the inter-modal transfer structure introduced earlier, now explicitly as a transfer rate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors ELECTROMAGNETIC STRESS-ENERGY TENSOR by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Aggregate Relation}\par
\[
Electromagnetic \to LineBundle[c_1 = \int_\Sigma F/(2\pi)]
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right)=1
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0514] ELECTROMAGNETIC STRESS-ENERGY TENSOR}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
ELECTROMAGNETIC STRESS-ENERGY TENSOR is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Electromagnetic -> LineBundle[c sub 1 = int sub Sigma F/(2pi)],. \textbf{Contextual meaning:} The entry reads ELECTROMAGNETIC STRESS-ENERGY TENSOR as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Aggregate Relation; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
ID 0014 repeats and stabilizes the inter-modal transfer structure introduced earlier, now explicitly as a transfer rate.

\tzpsection{Equation Grounding}
Equation anchors: Electromagnetic to LineBundle[c sub 1 = integral sub Sigma F/(2pi)]; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spacetime Curvature Sourcing Matrix}: The complete tensor representation of energy density, momentum flux, and shear stress generated by the active electromagnetic fields.
\item \textbf{Electromagnetic Ponderomotive Tensor}: The mathematical tool describing exactly how intense light and magnetic lines of force physically push against their surrounding boundaries.
\item \textbf{Radiation Pressure Manifold Deformation}: The precise calculation of how confined wave interactions physically warp the underlying geometry of the local coordinate system.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0514]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0514_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0514] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont ELECTROMAGNETIC STRESS-ENERGY TENSOR}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} "Electromagnetic" -> LineBundle[c\textbackslash{}\_1 = int\textbackslash{}\_Sigma F/(2pi)],

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ELECTROMAGNETIC STRESS-ENERGY TENSOR (T\textasciicircum{}\{\textbackslash{}mu\textbackslash{}nu is valid as a tensorial/geometric
statement when the stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0514_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
