\section*{ID8808: TOTAL GYROMAGNETIC LAGRANGIAN Canonical Statutory Formula: L Total}
\paragraph{Metadata.}
PiID: 8072471625916 | RTEID: RTE:P34203.4201:T6.0912 | UUID: 9b364377-ef1b-5804-8ab0-92c33a30e678

\paragraph{Canonical Statement.}
[ID 1124] TOTAL GYROMAGNETIC LAGRANGIAN Canonical Statutory Formula: \$\textbackslash{}mathcal\{L\} \{total\} = T \{gyro\} + T\_\{field\} - U\_\{mag\} - U\_\{constraint\} + \textbackslash{}mathcal\{L\}\_\{coupling\}\$ Formal Technical Dissertation: The unified Lagrangian governing the Furiene Spindle dynamics. It sums the rotational kinetic energy, electromagnetic field energy, magnetic potential interaction, mechanical constraint potentials (bolt/bearing), and the gyromagnetic coupling term. Source: [3]

\paragraph{Canonical Equation.}
\[
\mathcal{L} {total} = T {gyro} + T_{field} - U_{mag} - U_{constraint} + \mathcal{L}_{coupling}
\]

\paragraph{Dictionary.}
TOTAL GYROMAGNETIC LAGRANGIAN Canonical Statutory Formula: \$L total = T gyro + T\_field - U\_mag - U\_constraint + L\_coupling\$ Formal Technical Dissertation: The unified Lagrangian governing the Furiene Spindle dynamics.

\paragraph{Encyclopedia.}
TOTAL GYROMAGNETIC LAGRANGIAN Canonical Statutory Formula: L Total is a lagrangian construction, written L total = T gyro + T\_field - U\_mag - U\_constraint + L\_coupling. It defines a Lagrangian density from which the dynamics follow by the principle of least action. It is built from T, g, y, r, o, T\_field, defining L total. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
