\tzpanchor{0103}
\tzpentryheader{0103}{Infinity Hopf Fibration}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7c926607-2c34-5337-b4e5-532a82e2eb85}}\\
\textbf{PiID} & \tzpcode{4808651328230} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{110}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{399.9719 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.6590 rad}\\
\textbf{TZPID} & \tzpcode{ID0103} & \textbf{Node Dependencies}\quad \tzpidref{0102}\\
\textbf{Registry} & \tzpcode{registry\_id\_0103} & \textbf{Scale}\quad Hopf-fibration geometry\\
\textbf{LOC Classification} & QA612.74 fibration and bundle theory & QC174 topology in physics\\
\textbf{arXiv Classification} & Primary: math.AT \quad Cross-list: math-ph, hep-th & \\
\textbf{Primary Support} & Base-to-Bulk Map & Explicit Hopf Coordinates\\
\textbf{Closure Support} & Fiber Identity & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Instead of a mere figure eight, the infinity symbol represents a deep topological map: a three-sphere fibres over a two-sphere with circular fibres, capturing endless cycles of creation and recombination.

\tzpsection{Canonical Equation}
\[
h : S^3 \longrightarrow S^2
\]
\[
h(z_1,z_2)=\left(2 z_1 \overline{z}_2,\ \lvert z_1\rvert^2-\lvert z_2\rvert^2\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S^3$: three-sphere source domain.
    \item $S^2$: two-sphere target domain.
    \item $z_1$: source equation symbol.
    \item $z_2$: source equation symbol.
    \item $S$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0103 generated source Wolfram model *)
ClearAll[K0103, Cr0103, T, R, A, W, I, N];
eq0103$1 = HoldForm[h[S3] -> S2];
eq0103$2 = HoldForm[h[z1, z2] == {2*z1OverBar[z]*_*2, Abs[z1]^2 - Abs[z2]^2}];
eq0103$3 = HoldForm[(x*cong*S^1)/h];

K0103 = HoldForm[{eq0103$1, eq0103$2, eq0103$3}];

N = "normalized TRAWIN closure object for Infinity Hopf Fibration";
I = "Fiber Identity integration/comparison layer";
W = "Explicit Hopf Coordinates wave or operator carrier";
A = "Base-to-Bulk Map admissible action/amplitude condition";
R = "Explicit Hopf Coordinates rotation/curl preservation layer";
T = "Base-to-Bulk Map local source condition";

Cr0103[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0103 = Cr0103[K0103];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Base-to-Bulk Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Explicit Hopf Coordinates rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Base-to-Bulk Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Explicit Hopf Coordinates wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Fiber Identity integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Infinity Hopf Fibration.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0103] Infinity Hopf Fibration}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
h : S^3 \longrightarrow S^2
\]
\[
h(z_1,z_2)=\left(2 z_1 \overline{z}_2,\ \lvert z_1\rvert^2-\lvert z_2\rvert^2\right)
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( h(z_1,z_2)=\left(2 z_1 \overline{z}_2,\ \lvert z_1\rvert^2-\lvert z_2\rvert^2\right) \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. Interpreted through TRAWIN, the equation functions as the mapping carrier for the entry’s information content. Within the CHL view, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Infinity Hopf Fibration by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Base-to-Bulk Map}\par
\[
h : S^3 \longrightarrow S^2
\]
\noindent This identifies the bridge as a map between the circulating total space and its projected boundary image.\par
\noindent\textbf{2. Explicit Hopf Coordinates}\par
\[
h(z_1,z_2)=\left(2 z_1 \overline{z}_2,\ \lvert z_1\rvert^2-\lvert z_2\rvert^2\right)
\]
\noindent This writes the bridge concretely and shows how two complex amplitudes collapse into one projected image.\par
\noindent\textbf{3. Fiber Identity}\par
\[
h^{-1}(x)\cong S^1
\]
\noindent This closes the progression by making each projected point carry a full circulation fiber rather than a single collapsed state.\par

\clearpage
\noindent\textbf{[ID 0103] Infinity Hopf Fibration}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Infinity Hopf Fibration is a Definition. The infinity symbol within the TZP framework is identified with the Hopf fibration h: S  to S  where the pre image of any point in S  is a circle S . This mapping encodes infinite energy--information cycles and provides the topological basis for the dual lobes of the TZP.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The infinity symbol within the TZP framework is identified with the Hopf fibration h: S  to S  where the pre image of any point in S  is a circle S . This mapping encodes infinite energy--information cycles and provides the topological basis for the dual lobes of the TZP.
\textbf{Contextual meaning:} Instead of a mere figure eight, the infinity symbol represents a deep topological map: a three sphere fibres over a two sphere with circular fibres, capturing endless cycles of creation and recombination.
\textbf{Derivable consequences:} Links to spinor fields; connection to universal helices; mot
\textbf{Lemma support:} The infinity symbol within the TZP framework is identified with the Hopf fibration h: S  to S  where the pre image of any point in S  is a circle S . This mapping encodes infinite energy--information cycles and provides the topological basis for the dual lobes of the TZP.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Prepare entangled states encoded in toroidal loops and test resilience against local noise and decoherence. ID 103: Infinity Hopf Fibration

\tzpsection{Equation Grounding}
The infinity symbol within the TZP framework is identified with the Hopf fibration h: S  to S  where the pre image of any point in S  is a circle S . This mapping encodes infinite energy--information cycles and provides the topological basis for the dual lobes of the TZP.

\tzpsection{Interpretive Role}
Instead of a mere figure eight, the infinity symbol represents a deep topological map: a three sphere fibres over a two sphere with circular fibres, capturing endless cycles of creation and recombination.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Base-to-Bulk Map}: The identification of the bridge as a map between the circulating total space and its projected boundary image.
\item \textbf{Explicit Hopf Coordinates}: The concrete bridge showing how two complex amplitudes collapse into one projected image.
\item \textbf{Fiber Identity}: The requirement that each projected point carry a full circulation fiber rather than a single collapsed state.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0103]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0103_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0103] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Infinity Hopf Fibration}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} instead of a mere figure eight, the infinity symbol represents a deep topological map: a
three-sphere fibres over a two-sphere with circular fibres...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Infinity Hopf Fibration is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0103_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
