\section*{ID9401: Definition of R𝜆:𝑇2→𝑇2 I(R𝜆Φ)}
\paragraph{Metadata.}
PiID: 5437090697939 | RTEID: RTE:P36506.1708:T3.6023 | UUID: 39be89d0-51b6-53f0-b9e4-d16bdec60fe0

\paragraph{Canonical Statement.}
sabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0311], [ID 0300] Node registry\_id\_0312 Support Titles Variation Law; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links \$Φ𝜆𝑛=R𝜆 (Φ𝑛\$ ) \$R𝜆:𝑇2→𝑇2 I(R𝜆Φ)=I(Φ)\$ [ID 0313] Time as a Toroidal Winding Parameter TZPID ID0313 UUID f1791df6-8d5a-54c5-800e-ee2ea864c611 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops time as a toroidal winding parameter inside the field th

\paragraph{Canonical Equation.}
\[
R𝜆:𝑇2→𝑇2 I(R𝜆Φ)=I(Φ)
\]

\paragraph{Dictionary.}
Definition of R𝜆:𝑇2→𝑇2 I(R𝜆Φ) — R𝜆:𝑇2→𝑇2 I(R𝜆Φ)=I(Φ)

\paragraph{Encyclopedia.}
Definition of R𝜆:𝑇2→𝑇2 I(R𝜆Φ) is an algebraic definition, written R𝜆:𝑇2→𝑇2 I(R𝜆Φ)=I(Φ). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from I, defining R𝜆:𝑇2→𝑇2 I(R𝜆Φ). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
