\tzpanchor{0028}
\tzpentryheader{0028}{Constraint: TZP Torsion Localisation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e7054e64-47d8-5f5d-82d7-966c10279112}}\\
\textbf{PiID} & \tzpcode{7950288419716} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{35}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{108.7302 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.1792 rad}\\
\textbf{TZPID} & \tzpcode{ID0028} & \textbf{Node Dependencies}\quad \tzpidref{0017}\\
\textbf{Registry} & \tzpcode{registry\_id\_0028} & \textbf{Scale}\quad torsion\\
\textbf{LOC Classification} & QA641 torsion geometry & QC174 spin and transport\\
\textbf{arXiv Classification} & Primary: math.DG \quad Cross-list: gr-qc, hep-th & \\
\textbf{Primary Support} & Exterior Vanishing of Torsion & Localized Integrated Torsion Residue\\
\textbf{Closure Support} & Neighborhood-Independent Localization Rule & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The torsion of the Trawinistic connection vanishes away from the zero point and is allowed only as a finite, localized residue concentrated at the anchor.

\tzpsection{Canonical Equation}
\[
T(\nabla^{\mathrm{T}})=0
\qquad (x\neq p)
\]
\[
\int_{\mathcal N}
T^{a}{}_{bc}\,d^{n}x
=
N^{a}{}_{bc}
\]
for every neighborhood \(\mathcal N\) containing \(p\).

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $T$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $\ni$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0028 generated source Wolfram model *)
ClearAll[K0028, Cr0028, T, R, A, W, I, N];
eq0028$1 = HoldForm[T[Grad^T] == 0*(x != p)];
eq0028$2 = HoldForm[IntegralOver[NRegion, TorsionTensorDensity[a, b, c]*dNx] == TorsionChargeN[a, b, c]];
eq0028$3 = HoldForm[Contains[N, p]];

K0028 = HoldForm[{eq0028$1, eq0028$2, eq0028$3}];

N = "normalized TRAWIN closure object for Constraint: TZP Torsion Localisation";
I = "Neighborhood-Independent Localization Rule integration/comparison layer";
W = "Localized Integrated Torsion Residue wave or operator carrier";
A = "Exterior Vanishing of Torsion admissible action/amplitude condition";
R = "Localized Integrated Torsion Residue rotation/curl preservation layer";
T = "Exterior Vanishing of Torsion local source condition";

Cr0028[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0028 = Cr0028[K0028];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Exterior Vanishing of Torsion local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Localized Integrated Torsion Residue rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Exterior Vanishing of Torsion admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Localized Integrated Torsion Residue wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Neighborhood-Independent Localization Rule integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Constraint: TZP Torsion Localisation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0028] Constraint: TZP Torsion Localisation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
T(\nabla^{\mathrm{T}})=0
\qquad (x\neq p)
\]
\[
\int_{\mathcal N}
T^{a}{}_{bc}\,d^{n}x
=
N^{a}{}_{bc}
\]
for every neighborhood \(\mathcal N\) containing \(p\).

\paragraph{Primary Derivation.}
This condition \( T(\nabla^{\mathrm{T}})=0 \) enforces a normalization. It sets the quantity to a fixed value away from special points and introduces a delta-function source at those points, ensuring that the integral of the quantity equals the specified constant.
\paragraph{Equation Type.}
This statement is classified as a normalization relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. Within the TRAWIN framework, the equation functions as the normalized carrier for the entry’s information content. According to CHL, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Constraint: TZP Torsion Localisation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Exterior Vanishing of Torsion}\par
\[
T(\nabla^{\mathrm{T}})=0
\qquad (x\neq p)
\]
\noindent This forces the regular manifold to behave like an ordinary torsion-free geometry.\par
\noindent\textbf{2. Localized Integrated Torsion Residue}\par
\[
\int_{\mathcal N}
T^{a}{}_{bc}\,d^{n}x
=
N^{a}{}_{bc}
\]
\noindent This replaces distributed torsion with a finite localized residue around the anchor.\par
\noindent\textbf{3. Neighborhood-Independent Localization Rule}\par
\[
\mathcal N \ni p
\]
\noindent This closes the progression by requiring the same finite residue for every enclosing neighborhood, which is the signature of point localization.\par

\clearpage
\noindent\textbf{[ID 0028] Constraint: TZP Torsion Localisation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Constraint: TZP Torsion Localisation is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The torsion tensor T(nablaT)T(nabla T )T(nablaT) vanishes for all xneqpx neq px=p and satisfies intNTa sub bc dnx=Na sub bcintegral sub N Ttextsuperscript a textbackslash sub textbackslash,bc textbackslash, d n x = N a textbackslash sub textbackslash,bc integral\$NTa sub bcdnx=Na sub bc for any neighbourhood N N N containing ppp, where Na sub bcN a textbackslash sub textbackslash,bc Na sub bc is a fixed finite tensor capturing torsion concentrated at the TZP. \textbackslash{}. \textbf{Contextual meaning:} The entry reads Constraint: TZP Torsion Localisation as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This constraint allows the geometry to remain torsion-free almost everywhere while still carrying a finite singular residue at the anchor. It is exactly the kind of localized defect later spinor and phase-shift effects can couple to. \textbf{Lemma support:} Exterior Vanishing of Torsion; Localized Integrated Torsion Residue; Neighborhood-Independent Localization Rule.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technical interpretation remains tied to the local registry and equation witness.

\tzpsection{Equation Grounding}
Equation anchors: The torsion tensor T( ablaT)T( abla to the power T )T( ablaT) vanishes for all x eqpx eq px=p and satisfies intNTa bc dnx=Na bcintegral N Ttextsuperscript a textbackslash textbackslash,bc textbackslash, d n x = N to the power a textbackslash textbackslash,bc intNTa bcdnx=Na bc for any neighbourhood N N N containing ppp, where Na bcN to the power a textbackslash textbackslash,bc Na bc is a fixed finite tensor capturing torsion concentrated at the TZP. The torsion tensor T( ablaT)T( abla to the power T )T( ablaT) vanishes for all x eqpx eq px=p and satisfies intNTa bc dnx=Na bcintegral N Ttextsuperscript a textbackslash textbackslash,bc textbackslash, d n x = N to the power a textbackslash textbackslash,bc intNTa bcdnx=Na bc for any neighbourhood N N N containing ppp, where Na bcN to the power a textbackslash textbackslash,bc Na bc is a fixed finite tensor capturing torsion concentrated at the TZP.

\tzpsection{Interpretive Role}
This constraint allows the geometry to remain torsion-free almost everywhere while still carrying a finite singular residue at the anchor. It is exactly the kind of localized defect later spinor and phase-shift effects can couple to.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Admissibility Condition Tzp Torsion Localisation}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Admissibility Condition Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Admissibility Condition Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0028]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0028_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0028] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Constraint: TZP Torsion Localisation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the torsion of the Trawinistic connection vanishes away from the zero point and is
allowed only as a finite, localized residue concentrated at the...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Constraint: TZP Torsion Localisation is valid as a tensorial/geometric statement when
the stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0028_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
