\section*{ID8901: Definition of Dim}
\paragraph{Metadata.}
PiID: 2896476697583 | RTEID: RTE:P34564.5597:T0.4031 | UUID: 713247b4-4411-5424-9180-356564c639d4

\paragraph{Canonical Statement.}
[ID 931] QUANTUM STATE SPACE DECOMPOSITION Canonical Statutory Formula: \$H\_\{total\} = H\_\{spatial\} \textbackslash{}otimes H\_\{OAM\} \textbackslash{}otimes H\_\{polarization\} \textbackslash{}otimes H\_\{frequency\}\$ Formal Technical Dissertation: Defines the total Hilbert space used for quantum holographic navigation. It factors into four independent subsystems: the spatial address (\$dim = 153,600\$), orbital angular momentum (\$dim = 2m\_\{max\} + 1\$), polarization (\$dim = 2\$), and frequency (\$dim = \textbackslash{}infty\$). This modular decomposition allows for selective entanglement generation and independent CPTP map design. Source: [1], [2]

\paragraph{Canonical Equation.}
\[
dim = 2m_{max} + 1
\]

\paragraph{Dictionary.}
QUANTUM STATE SPACE DECOMPOSITION Canonical Statutory Formula: \$H\_total = H\_spatial H\_OAM H\_polarization H\_frequency\$ Formal Technical Dissertation: Defines the total Hilbert space used for quantum holographic navigation (dim)

\paragraph{Encyclopedia.}
Definition of Dim is an algebraic definition, written dim = 2m\_max + 1. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from m\_max, defining dim. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
