\tzpanchor{0131}
\tzpentryheader{0131}{Gaussian Window Insertion Operator}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9f35b0e3-f4af-5078-bf87-1eb64c034f4f}}\\
\textbf{PiID} & \tzpcode{0582231725359} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{138}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{508.7021 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.8382 rad}\\
\textbf{TZPID} & \tzpcode{ID0131} & \textbf{Node Dependencies}\quad \tzpidref{0130}\\
\textbf{Registry} & \tzpcode{registry\_id\_0131} & \textbf{Scale}\quad time-windowed bridge-tone injection\\
\textbf{LOC Classification} & QA371 signal operators & QC20 wave phenomena\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: nlin.PS, physics.class-ph & \\
\textbf{Primary Support} & Gaussian Envelope & Carrier Mixture\\
\textbf{Closure Support} & Localized Insertion & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Gaussian window insertion operator localizes the bridge-carrier construction in time. Instead of acting globally on the signal, the bridge tone is inserted only inside a smooth envelope centered at \(t_0\), giving a finite event rather than an everywhere-on modulation.

\tzpsection{Canonical Equation}
\[
g(t)=\exp\!\left(-\frac{(t-t_0)^2}{2\sigma^2}\right)
\]
\[
s_{\mathrm{mix}}(t)=f_A'\cos(2\pi f_A' t)+f_B'\cos(2\pi f_B' t)+f_{\mathrm{bridge}}\cos(2\pi f_{\mathrm{bridge}} t)
\]
\[
\mathcal{G}[s](t)=g(t)\,s_{\mathrm{mix}}(t)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $t_0$: source equation symbol.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $s_{\mathrm{mix}}(t)$: source equation symbol.
    \item $f_A$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $t$: source equation symbol.
    \item $f_B$: source equation symbol.
    \item $f_{\mathrm{bridge}}$: source equation symbol.
    \item $\mathcal{G}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0131 generated source Wolfram model *)
ClearAll[K0131, Cr0131, T, R, A, W, I, N];
eq0131$1 = HoldForm[g[t] == exp[-((t - t0)^2/(2*sigma^2))]];
eq0131$2 = HoldForm[sMix[t] == Derivative[1][fA]*Cos[2*Pi*Derivative[1][fA]*t] + Derivative[1][fB]*Cos[2*Pi*Derivative[1][fB]*t] + fBridgeCos[2*Pi*fBridge*t]];
eq0131$3 = HoldForm[G[s]*t == g[t]*sMix[t]];

K0131 = HoldForm[{eq0131$1, eq0131$2, eq0131$3}];

N = "normalized TRAWIN closure object for Gaussian Window Insertion Operator";
I = "Localized Insertion integration/comparison layer";
W = "Carrier Mixture wave or operator carrier";
A = "Gaussian Envelope admissible action/amplitude condition";
R = "Carrier Mixture rotation/curl preservation layer";
T = "Gaussian Envelope local source condition";

Cr0131[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0131 = Cr0131[K0131];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Gaussian Envelope local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Carrier Mixture rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Gaussian Envelope admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Carrier Mixture wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Localized Insertion integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Gaussian Window Insertion Operator.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0131] Gaussian Window Insertion Operator}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
g(t)=\exp\!\left(-\frac{(t-t_0)^2}{2\sigma^2}\right)
\]
\[
s_{\mathrm{mix}}(t)=f_A'\cos(2\pi f_A' t)+f_B'\cos(2\pi f_B' t)+f_{\mathrm{bridge}}\cos(2\pi f_{\mathrm{bridge}} t)
\]
\[
\mathcal{G}[s](t)=g(t)\,s_{\mathrm{mix}}(t)
\]

\paragraph{Primary Derivation.}
The identity \( g(t)=\exp\!\left(-\frac{(t-t_0)^2}{2\sigma^2}\right) \) is an operator relation. Applying the operator to the relevant function and using its algebraic properties (such as linearity, commutators, or derivative rules) leads to the displayed equality.
\paragraph{Equation Type.}
This statement is classified as a operator relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. From the TRAWIN perspective, the equation functions as the operator-level carrier for the entry’s information content. In CHL terms, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Gaussian Window Insertion Operator by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Gaussian Envelope}\par
\[
g(t)=\exp\!\left(-\frac{(t-t_0)^2}{2\sigma^2}\right)
\]
\noindent This defines the smooth time-localization that makes the insertion finite.\par
\noindent\textbf{2. Carrier Mixture}\par
\[
s_{\mathrm{mix}}(t)=f_A'\cos(2\pi f_A' t)+f_B'\cos(2\pi f_B' t)+f_{\mathrm{bridge}}\cos(2\pi f_{\mathrm{bridge}} t)
\]
\noindent This collects the aligned carriers and the bridge tone into one pre-window signal.\par
\noindent\textbf{3. Localized Insertion}\par
\[
\mathcal{G}[s](t)=g(t)\,s_{\mathrm{mix}}(t)
\]
\noindent This closes the progression by expressing the actual insertion as the product of envelope and bridge-bearing signal.\par

\clearpage
\noindent\textbf{[ID 0131] Gaussian Window Insertion Operator}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Gaussian Window Insertion Operator is a Operator. Define a time localized Gaussian envelope g(t) = exp(-[(t -- t ) ]/(2   )). A signal combining scaled carriers and the bridge tone is s(t) = A  sin(2  f\_A' t +   ) + A  sin(2  f\_B' t +   ) + A  g(t) sin(2  f\_bridge t +   ), where   is small relative to the beat period.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Define a time localized Gaussian envelope g(t) = exp(-[(t -- t ) ]/(2   )). A signal combining scaled carriers and the bridge tone is s(t) = A  sin(2  f\_A' t +   ) + A  sin(2  f\_B' t +   ) + A  g(t) sin(2  f\_bridge t +   ), where   is small relative to the beat period.
\textbf{Contextual meaning:} A Gaussian envelope inserts the bridging tone only at specific times, creating a narrow "seam" between carriers.
\textbf{Derivable consequences:} Design of binaural beats; scaling of frequencies to desired difference; foundation for Gaussian insertion and phase manipulation.
\textbf{Lemma support:} Define a time localized Gaussian envelope g(t) = exp(-[(t -- t ) ]/(2   )). A signal combining scaled carriers and the bridge tone is s(t) = A  sin(2  f\_A' t +   ) + A  sin(2  f\_B' t +   ) + A  g(t) sin(2  f\_bridge t +   ), where   is small relative to the beat period.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Implement the scaling and verify that the resulting beat frequency matches the target; test stability of the bridging mapping. ID 131: Gaussian Window Insertion Operator

\tzpsection{Equation Grounding}
Define a time localized Gaussian envelope g(t) = exp(-[(t -- t ) ]/(2   )). A signal combining scaled carriers and the bridge tone is s(t) = A  sin(2  f\_A' t +   ) + A  sin(2  f\_B' t +   ) + A  g(t) sin(2  f\_bridge t +   ), where   is small relative to the beat period.

\tzpsection{Interpretive Role}
A Gaussian envelope inserts the bridging tone only at specific times, creating a narrow "seam" between carriers.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Gaussian Envelope}: The definition of the smooth time-localization that makes the insertion finite.
\item \textbf{Carrier Mixture}: The collection of the aligned carriers and the bridge tone into one pre-window signal.
\item \textbf{Localized Insertion}: The expression of the actual insertion as the product of envelope and bridge-bearing signal.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0131]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0131_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0131] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Gaussian Window Insertion Operator}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the Gaussian window insertion operator localizes the bridge-carrier construction in time

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Gaussian Window Insertion Operator is valid as a spectral relation when frequency,
phase, and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0131_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
