\tzpanchor{0260}
\tzpentryheader{0260}{Asymptotic Series and Zeta Regularization}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7c15252b-db7e-5187-a079-3b7ab7a01b43}}\\
\textbf{PiID} & \tzpcode{3460348610454} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{267}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1009.6377 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.6636 rad}\\
\textbf{TZPID} & \tzpcode{ID0260} & \textbf{Node Dependencies}\quad \tzpidref{0259}\\
\textbf{Registry} & \tzpcode{registry\_id\_0260} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Divergent series at the TZP, such as asymptotic expansions that diverge term by term, can acquire finite values through analytic continuation and zeta-function regularization; resurgent trans-series combine power, exponential and logarithmic terms to capture the full structure.

\tzpsection{Canonical Equation}
\[
\mathcal{K}_{0260} := \operatorname{HoldForm}\!\left(\mathcal{T}_{0260}\right)
\]
\[
\operatorname{Admissible}_{\mathrm{TZP}}\!\left(\mathcal{K}_{0260}\right) \Longleftrightarrow \mathfrak{W}_{\mathrm{TZP}}\!\left(\mathcal{K}_{0260}\right) \not\equiv \varnothing
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{K}_{0260}$: canonical registry object for entry ID 0260.
    \item $\mathcal{T}_{0260}$: source equation symbol.
    \item $W$: source equation symbol.
    \item $v_{\mathrm{A}}$: Alfven velocity or carrier speed.
    \item $\omega_{\mathrm{gyro}}$: gyroscopic angular frequency correction.
    \item $\omega$: angular frequency term in the source equation.
    \item $J_z$: source equation symbol.
    \item $\Phi_Q(f)$: flux, phase, or topological map term in the source equation.
    \item $\mathcal{B}(f)$: magnetic field magnitude.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0260 generated source Wolfram model *)
ClearAll[K0260, Cr0260, T, R, A, W, I, N];
eq0260$1 = HoldForm[K0260 == HoldForm[T0260]];
eq0260$2 = HoldForm[AdmissibleTZP[K0260] == mathfrak[W]*_*TZP*K0260*notequivvarnothing];
eq0260$3 = HoldForm[omega^2 == k^2*vA^2[1 + (omegaGyro/omega)^2]];
eq0260$4 = HoldForm[etaJzcircPhiQ[f] == B[f]*circetaJz];
eq0260$5 = HoldForm[omega^2 == k^2*vA^2[1 + (omegaGyro/omega)^2]];

K0260 = HoldForm[{eq0260$1, eq0260$2, eq0260$3, eq0260$4, eq0260$5}];

N = "normalized TRAWIN closure object for Asymptotic Series and Zeta Regularization";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0260[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0260 = Cr0260[K0260];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Asymptotic Series and Zeta Regularization.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0260] Asymptotic Series and Zeta Regularization}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
C(\phi_1,\phi_2)
=
\frac{
|\langle \phi_1,\phi_2\rangle|
}{
\|\phi_1\|\,\|\phi_2\|
}.
\end{equation}

\paragraph{Decoherence Limit.}
\begin{equation}
C(t)\rightarrow 0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi_1$ and $\phi_2$ be two quantum field states.  
Their normalized overlap is:

\begin{equation}
C(\phi_1,\phi_2)
=
\frac{
|\langle \phi_1,\phi_2\rangle|
}{
\|\phi_1\|\,\|\phi_2\|
}.
\end{equation}

If environmental coupling, curvature noise, or zero-point disturbance destroys phase alignment, then the time-dependent coherence decreases:

\begin{equation}
C(t)
=
C(\phi_1(t),\phi_2(t)).
\end{equation}

Decoherence occurs in the limiting regime:

\begin{equation}
\boxed{
C(t)\rightarrow 0 .
}
\end{equation}

\paragraph{Interpretation.}
Coherence is normalized state overlap; decoherence is the decay of that overlap under admissible disturbance.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Asymptotic Series and Zeta Regularization by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
omega^{2} = k^{2} v_{\mathrm{A}}^{2}\left[1 + \left(\frac{\omega_{\mathrm{gyro}}}{\omega}\right)^{2}\right]
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\eta_{J_z}\circ\Phi_Q(f)=\mathcal{B}(f)\circ\eta_{J_z}
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\omega^{2} = k^{2} v_{\mathrm{A}}^{2}\left[1 + \left(\frac{\omega_{\mathrm{gyro}}}{\omega}\right)^{2}\right]
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0260] Asymptotic Series and Zeta Regularization}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Asymptotic Series and Zeta Regularization is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Divergent series at the TZP, such as asymptotic expansions that diverge term by term, can acquire finite values through analytic continuation and zeta-function regularization; resurgent trans-series combine power, exponential and logarithmic terms to capture the full structure. \textbf{Contextual meaning:} The entry reads Asymptotic Series and Zeta Regularization as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform tertiary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Coherence is normalized state overlap; decoherence is the decay of that overlap under admissible disturbance.

\tzpsection{Equation Grounding}
Equation anchors:
\[
\omega^2=k^2v_A^2\left[1+\left(\frac{\omega_{\mathrm{gyro}}}{\omega}\right)^2\right],
\qquad
\Delta E\approx\frac{\Phi_0^2}{2L}\approx10^{-21}\,\mathrm{J}.
\]
Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform tertiary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Formal Infinity Re-Normalization}: The mathematical trick of treating an infinitely exploding sequence of numbers as a finite, manageable value to make physics equations work.
\item \textbf{Analytic Continuation of Divergent Series}: Extending the domain of a mathematical function so that a sum that usually makes no sense (like 1+2+3+...) yields a specific, usable fraction.
\item \textbf{Zeta-Function Value Assignment}: The specific use of the Riemann Zeta function to assign a precise negative fraction to the sum of all positive integers, a technique vital in string theory and Casimir effects.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0260]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0260_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0260] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Asymptotic Series and Zeta Regularization}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} divergent series at the TZP, such as asymptotic expansions that diverge term by term,
can acquire finite values through analytic continuation and z...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Asymptotic Series and Zeta Regularization is valid when the stated operator maps
admissible inputs into the declared target class.''\\
\textbf{Proof:} The source statement is read as an operator or transformation. The proof obligation is
type preservation: admissible inputs must land in the target object without breaking the
stated constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- operator-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0260_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
