\section*{ID9130: Definition of eˆi(α+β))(R,eiα)(R,eiβ)}
\paragraph{Metadata.}
PiID: 2076651479394 | RTEID: RTE:P35453.8176:T1.8683 | UUID: 47990b64-dc99-5f5b-a93f-41513bec4fb5

\paragraph{Canonical Statement.}
or gauge transformations that cannot be described by SO(3)× U(1)SO(3)\textbackslash{}times U(1)SO(3)× U(1) would refute this definition. 0.0.94 ID 092: SemiDirect Product of Rotation and Gauge Symmetry Type: Structural Constraint Formal Statement: The full symmetry group of gyromagnetic systems is the semidirect product SO(3)U(1)SO(3)\textbackslash{}ltimes U(1)SO(3)U(1), reflecting the fact that gauge phases transform under rotations; mathematically, \$(R,eiα)(R,eiβ)=(RR,ei(α+β))(R,\$ e\{i\textbackslash{}alpha\})\textbackslash{}cdot(R’,e\{i\textbackslash{}beta\}) = (RR’, \$eˆ\{i(\textbackslash{}alpha+\textbackslash{}beta)\})(R,eiα)(R,eiβ)=(RR,ei(α+β))\$ up to an automorphism. Interpretive Meaning: Rotations and gauge phases are intertwined; this structure yields unique conserved quantities and constraints. Dependencies: ID 091 Derivable Consequences: Existence of combined gauge–rotation charges; modifications to conservation laws; topological defects carrying both flux and angular momentum; connection to phase space topology preservation. Falsif

\paragraph{Canonical Equation.}
\[
eˆ{i(\alpha+\beta)})(R,eiα)(R,eiβ)=(RR,ei(α+β))
\]

\paragraph{Dictionary.}
Definition of eˆi(α+β))(R,eiα)(R,eiβ) — eˆi(α+β))(R,eiα)(R,eiβ)=(RR,ei(α+β))

\paragraph{Encyclopedia.}
Definition of eˆi(α+β))(R,eiα)(R,eiβ) is an algebraic definition, written eˆi(α+β))(R,eiα)(R,eiβ)=(RR,ei(α+β)). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from R, defining eˆi(α+β))(R,eiα)(R,eiβ). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
