\section*{ID9296: Definition of ==1(1+InfoDensity[]digit())1/K}
\paragraph{Metadata.}
PiID: 6801224826117 | RTEID: RTE:P36098.4324:T2.9304 | UUID: 15763497-4a41-592a-9efa-1eda464362ba

\paragraph{Canonical Statement.}
ical Information Functor Type: Definition Formal Statement: Introduce a natural transformation \$:InfoCategory[4]→InfoCategory[2], F\$ : \$InfoCategory[4D]→InfoCategory[2D],\$ mapping fourdimensional information states \$4ψ4D\$ to twodimensional states \$2ψ2D.\$ The component map employs an information density defined by von Neumann entropy, Fisher information and Kolmogorov complexity, and a topological charge given by the Chern number, winding number and kissing number. A kissinginvariant factor \$==1(1+InfoDensity[]digit())1/K=n=1N(1+ndigitn(π)InfoDensity[ψ])1/n\$ scales information such that Information[2]=Information[4]× \$Information[ψ2D]\$ = \$Information[ψ4D]×\$ K. Naturality requires (◦)=()◦()F(g◦f)=F(g)◦F(f) for morphisms ,f,g, and information conservation imposes \$ () log()S[F(ψ)]S(ψ)log(πN).\$ Interpretive Meaning: This functor formalises how information compresses when dimensional collapse occurs at a TZP. The kissing number encodes topological com

\paragraph{Canonical Equation.}
\[
==1(1+InfoDensity[]digit())1/K=n=1N(1+ndigitn(π)InfoDensity[ψ])1/n
\]

\paragraph{Dictionary.}
Definition of ==1(1+InfoDensity[]digit())1/K — ==1(1+InfoDensity[]digit())1/K=n=1N(1+ndigitn(π)InfoDensity[ψ])1/n

\paragraph{Encyclopedia.}
Definition of ==1(1+InfoDensity[]digit())1/K is an algebraic definition, written ==1(1+InfoDensity[]digit())1/K=n=1N(1+ndigitn(π)InfoDensity[ψ])1/n. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from n, N, g, I, f, o, defining ==1(1+InfoDensity[]digit())1/K. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
