\section*{ID9920: Definition of τ\_polariton/τ\_bare}
\paragraph{Metadata.}
PiID: 9276457931065 | RTEID: RTE:P38521.5630:T0.6398 | UUID: 3b82f598-7fa6-5b15-bed5-16adb599cbd2

\paragraph{Canonical Statement.}
des across many mini-resonators coupled through kissing topologies. Polaritons – quasiparticles of strongly coupled excitons and photons – are especially interesting: by tailoring the Rabi splitting to \$\textbackslash{}Omega\_\{\textbackslash{}text\{Rabi\}\}' = \textbackslash{}Omega\textbackslash{}sqrt\{1 + N/\textbackslash{}pi\}\$ for mode number \$N\$, we effectively increase the light-matter coupling with system size. Additionally, we choose the operating point away from any non-Hermitian exceptional point by a margin proportional to a “kissing gap,” ensuring the polariton modes do not suffer excess line-broadening. The net result is a polariton lifetime enhancement factor \$\textbackslash{}tau\_\{\textbackslash{}text\{polariton\}\}/\textbackslash{}tau\_\{\textbackslash{}text\{bare\}\} = N/\textbackslash{}pi\$ and nonlinearity (third-order susceptibility) boosted by \$N\textasciicircum{}3\$ in our design. Such giant, scalable nonlinearities could be harnessed for quantum optical switching and amplification at very low power. To summarize this section, our particle-specific entanglement framework mathematically guarantees that information encoded in entangled states will be preserved. Topologically, it does so by embedding the quantum information into a structure with transcendental symmetry (involving π) that conventio

\paragraph{Canonical Equation.}
\[
\tau_{\text{polariton}}/\tau_{\text{bare}} = N/\pi
\]

\paragraph{Dictionary.}
Definition of τ\_polariton/τ\_bare — τ\_polariton/τ\_bare = N/π

\paragraph{Encyclopedia.}
Definition of τ\_polariton/τ\_bare is an algebraic definition, written τ\_polariton/τ\_bare = N/π. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from π, N, defining τ\_polariton/τ\_bare. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
