\tzpanchor{0621}
\tzpentryheader{0621}{MAGNETIC FIELD RAMP-UP}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{d0f20b0c-fae4-55c3-9ea0-de7e7defcf22}}\\
\textbf{PiID} & \tzpcode{7857713427577} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{628}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2388.1816 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.9350 rad}\\
\textbf{TZPID} & \tzpcode{ID0621} & \textbf{Node Dependencies}\quad \tzpidref{0620}\\
\textbf{Registry} & \tzpcode{registry\_id\_0621} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Aggregate Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records magnetic field ramp-up through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
c_T = \left[ \frac{1}{2\pi}F \right] \in H^2(M\setminus\{p\},\mathbb{Z}).
\]
\[
\frac{1}{2\pi}F.
\]
\[
c_T = \left[ \frac{1}{2\pi}F \right].
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $c_T$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $F$: source equation symbol.
    \item $H$: source equation symbol.
    \item $M$: source equation symbol.
    \item $Z$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0621 generated source Wolfram model *)
ClearAll[K0621, Cr0621, T, R, A, W, I, N];
eq0621$1 = HoldForm[Element[cT == TZPGroup[(1/(2*Pi))*F], H^2*Tuple[MsetminusList[p], Z]]];
eq0621$2 = HoldForm[(1/(2*Pi))*F];
eq0621$3 = HoldForm[cT == TZPGroup[(1/(2*Pi))*F]];

K0621 = HoldForm[{eq0621$1, eq0621$2, eq0621$3}];

N = "normalized TRAWIN closure object for MAGNETIC FIELD RAMP-UP";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Aggregate Relation admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Aggregate Relation local source condition";

Cr0621[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0621 = Cr0621[K0621];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Aggregate Relation local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Aggregate Relation admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for MAGNETIC FIELD RAMP-UP.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0621] MAGNETIC FIELD RAMP-UP}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
c_T
=
\left[
\frac{1}{2\pi}F
\right]
\in
H^2(M\setminus\{p\},\mathbb{Z}) .
\end{equation}

\paragraph{Primary Derivation.}
Let $F$ be the curvature two-form of a principal $U(1)$ bundle over the punctured manifold $M\setminus\{p\}$.

For a $U(1)$ bundle, the first characteristic class is obtained by normalizing curvature by $2\pi$:

\begin{equation}
\frac{1}{2\pi}F .
\end{equation}

Taking the cohomology class gives:

\begin{equation}
c_T
=
\left[
\frac{1}{2\pi}F
\right].
\end{equation}

Since the TZP is removed from the base space, the class naturally lives in:

\begin{equation}
H^2(M\setminus\{p\},\mathbb{Z}) .
\end{equation}

Thus,

\begin{equation}
\boxed{
c_T
=
\left[
\frac{1}{2\pi}F
\right]
\in
H^2(M\setminus\{p\},\mathbb{Z}) .
}
\end{equation}

\paragraph{Interpretation.}
The Trawin characteristic class records the topological charge generated by removing the TZP from the manifold.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors MAGNETIC FIELD RAMP-UP by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Aggregate Relation}\par
\[
c_T = \left[ \frac{1}{2\pi}F \right] \in H^2(M\setminus\{p\},\mathbb{Z}).
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\frac{1}{2\pi}F.
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
c_T = \left[ \frac{1}{2\pi}F \right].
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0621] MAGNETIC FIELD RAMP-UP}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
MAGNETIC FIELD RAMP-UP is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} B(t) = int sub 0 to the power t dot B ramp dt implies B target approximately 0.1 text Tesla. \textbf{Contextual meaning:} The entry reads MAGNETIC FIELD RAMP-UP as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Aggregate Relation; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The Trawin characteristic class records the topological charge generated by removing the TZP from the manifold.

\tzpsection{Equation Grounding}
Equation anchors: B(t) = integral sub 0 to the power t dot B ramp dt implies B target approximately 0.1 Tesla; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Controlled Inductive Swelling}: The cautious, stepwise increase of the raw electrical power, slowly inflating the invisible magnetic balloon inside the chamber without popping it.
\item \textbf{Initial Topology Sculpting}: The process of carefully bending and twisting the waking magnetic field lines into the specific, knotted shape required to hold the plasma.
\item \textbf{Pre-Resonance Flux Saturation}: The operational stage where the chamber is completely filled with a dense, heavy magnetic fog, waiting for the spark that will set it spinning.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0621]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0621_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0621] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont MAGNETIC FIELD RAMP-UP}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records magnetic field ramp-up through the Septenary derivation layer, using
the displayed relations as operational anchors for the canon...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``MAGNETIC FIELD RAMP-UP is valid when the stated geometric or topological relation
preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0621_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
