\tzpanchor{0895}
\tzpentryheader{0895}{FIELD ROTATION GRADIENT}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{62327fd0-46ff-5184-88d6-f54a1fbbd21d}}\\
\textbf{PiID} & \tzpcode{4730359825349} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{902}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3421.1187 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.6370 rad}\\
\textbf{TZPID} & \tzpcode{ID0895} & \textbf{Node Dependencies}\quad \tzpidref{0894}\\
\textbf{Registry} & \tzpcode{registry\_id\_0895} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Frequency Lock & Gradient Covector\\
\textbf{Closure Support} & Rotating Field Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records field rotation gradient through a normalized Nonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0895}}:\mathcal{X}_{\mathrm{id0895}}\longrightarrow\mathcal{Y}_{\mathrm{id0895}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0895}})=\mathcal{O}_{\mathrm{id0895}}
\]
\[
\mathcal{O}_{\mathrm{id0895}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0895}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0895}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0895}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0895 generated source Wolfram model *)
ClearAll[K0895, Cr0895, T, R, A, W, I, N];
eq0895$1 = HoldForm[Oid0895[Xid0895] -> Yid0895];
eq0895$2 = HoldForm[NTRAWIN[OId0895] == OId0895];
eq0895$3 = HoldForm[Element[OId0895[x], YAdm]];

K0895 = HoldForm[{eq0895$1, eq0895$2, eq0895$3}];

N = "normalized TRAWIN closure object for FIELD ROTATION GRADIENT";
I = "FIELD ROTATION GRADIENT integration/comparison layer";
W = "FIELD ROTATION GRADIENT wave or operator carrier";
A = "FIELD ROTATION GRADIENT admissible action/amplitude condition";
R = "FIELD ROTATION GRADIENT rotation/curl preservation layer";
T = "FIELD ROTATION GRADIENT local source condition";

Cr0895[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0895 = Cr0895[K0895];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ FIELD ROTATION GRADIENT local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ FIELD ROTATION GRADIENT rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ FIELD ROTATION GRADIENT admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ FIELD ROTATION GRADIENT wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ FIELD ROTATION GRADIENT integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for FIELD ROTATION GRADIENT.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0895] FIELD ROTATION GRADIENT}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0895}}:\mathcal{X}_{\mathrm{id0895}}\longrightarrow \mathcal{Y}_{\mathrm{id0895}},\qquad
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0895}})=\mathcal{O}_{\mathrm{id0895}},\qquad
\mathcal{O}_{\mathrm{id0895}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

\paragraph{Primary Derivation.} Let $x\in \mathcal{X}_{\mathrm{id0895}}$ be the local coordinate or field sample.  The entry transform is\[
y=\mathcal{O}_{\mathrm{id0895}}(x),\qquad \mathcal{O}_{\mathrm{id0895}}:\mathcal{X}_{\mathrm{id0895}}\longrightarrow \mathcal{Y}_{\mathrm{id0895}}.
\]

Its differential transport is represented by the id-local Jacobian\[
J_{0895}(x)=D\mathcal{O}_{\mathrm{id0895}}\big|_x,\qquad \det J_{0895}(x)\neq 0
\]

Compatibility with the Nonary chain is enforced by\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0895}})=\mathcal{O}_{\mathrm{id0895}},\qquad y\in\mathcal{Y}_{\mathrm{adm}}.
\]

Thus the Nonary derivation for [ID 0895] is the three-stage passage
\[
\mathcal{X}_{\mathrm{id0895}}\xrightarrow{\,\mathcal{O}_{\mathrm{id0895}}\,} \mathcal{Y}_{\mathrm{id0895}}\xrightarrow{\,\mathcal{N}_{\mathrm{TRAWIN}}\,} \mathcal{Y}_{\mathrm{adm}},
\]
with the entry title fixing the meaning of the carrier and the TRAWIN normalization fixing the admissibility test.

\paragraph{Interpretation.} FIELD ROTATION GRADIENT is read as a transport rule: it converts local data into an admissible Nonary coordinate while preserving enough differential structure for the following entry to use it.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors FIELD ROTATION GRADIENT by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0895}}:\mathcal{X}_{\mathrm{id0895}}\longrightarrow\mathcal{Y}_{\mathrm{id0895}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0895}})=\mathcal{O}_{\mathrm{id0895}}
\]
\[
\mathcal{O}_{\mathrm{id0895}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0895] FIELD ROTATION GRADIENT}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
FIELD ROTATION GRADIENT is a registry definition in Resonance and Phase Locking with secondary pressure from Biological and Biomolecular Analogies.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} At Lambda << 1: Coriolis dominates -> rotation without field generation. \textbf{Contextual meaning:} The entry reads FIELD ROTATION GRADIENT as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states field rotation gradient as a clean lock-gradient-rotation chain instead of imported prose and script-cap spill. \textbf{Lemma support:} Frequency Lock; Gradient Covector; Rotating Field Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, FIELD ROTATION GRADIENT is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: Deltaomega = 0; dU : M to T to the power * M; and B(r,theta,phi,t)=B(r,theta,phi-omega t). Proof route: show that the zero mismatch condition, manifold gradient map, and rotating-frame field law define one coherent field-rotation carrier. Formalization route: prove that the rotating-frame field law is admissible under the stated gradient map and frequency lock.

\tzpsection{Interpretive Role}
The entry now states field rotation gradient as a clean lock-gradient-rotation chain instead of imported prose and script-cap spill.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Spatial Torsion Differentials}: The exact measurement of how quickly the twisting, violent spin of the magnetic field drops off as you move from the center of the reactor out toward the walls.
\item \textbf{Shear-Stress Magnetic Tearing}: The dangerous mathematical zone where the inside of the field is spinning so much faster than the outside of the field that the invisible lines of force literally snap in half.
\item \textbf{Angular Velocity Mapping}: The creation of a perfect 3D contour map showing not how hot the plasma is, but exactly how fast every single microscopic drop of it is spinning in circles.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0895]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0895].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0895] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont FIELD ROTATION GRADIENT}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} FIELD ROTATION GRADIENT is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``FIELD ROTATION GRADIENT is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0895].
\par\endgroup
\vfill
\endgroup
\endgroup
