\section*{ID8751: Ordinary Spherical Coordinates \$(r,\textbackslash{}theta,\textbackslash{}phi)\$ in \$ℝ\textasciicircum{}3\$ , Any Direction (: θ}
\paragraph{Metadata.}
PiID: 0254947802490 | RTEID: RTE:P33982.0764:T5.7265 | UUID: 7fd4f207-b354-5717-9549-ec8ae4f87d81

\paragraph{Canonical Statement.}
In ordinary spherical coordinates \$(r,\textbackslash{}theta,\textbackslash{}phi)\$ in \$ℝ\textasciicircum{}3\$ , any direction (given by polar angle \$\textbackslash{}theta\$ and azimuthal angle \$\textbackslash{}phi\$ ) is identified with its antipodal direction if one is only concerned with orientation (not pointing). For a dipole-like field, usually one might say “field goes out along \$\textbackslash{}theta=0\$ (north pole) and in along \$\textbackslash{}theta=\textbackslash{}pi\$ (south pole)”. But those two are different directions on the same sphere (just opposite ends of a diameter). There is nothing in the coordinate pair \$(\textbackslash{}theta,\textbackslash{}phi)\$ alone that tells you “this is the outward flux side vs inward flux side”, because if you reversed the actual field direction, the coordinate remains the same but flux orientation flips. We want a way to label points on a sphere wit

\paragraph{Canonical Equation.}
\[
\theta=\pi
\]

\paragraph{Dictionary.}
In ordinary spherical coordinates (r,θ,φ) in ℝ\textasciicircum{}3 , any direction (given by polar angle θ and azimuthal angle φ ) is identified with its antipodal direction if one is only concerned with orientation (not pointing).

\paragraph{Encyclopedia.}
Ordinary Spherical Coordinates \$(r,\textbackslash{}theta,\textbackslash{}phi)\$ in \$ℝ\textasciicircum{}3\$ , Any Direction (: θ is an algebraic definition, written θ=π. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from π, defining θ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
