\section*{ID8497: TOPOLOGICAL GRAVITY SOURCE Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 9683408005355 | RTEID: RTE:P32995.7380:T4.1013 | UUID: 64b25ddf-7cbd-5e78-aade-22c88aba71bb

\paragraph{Canonical Statement.}
[ID 1171] TOPOLOGICAL GRAVITY SOURCE Canonical Statutory Formula: \$\textbackslash{}nabla\textasciicircum{}2 \textbackslash{}Phi\_\{TZP\} \textbackslash{}propto \textbackslash{}frac\{Q\}\{(r-r\_c)\textasciicircum{}3\}\$ Formal Technical Dissertation: Postulates the generation of gravity from pure topology. The scalar field \$\textbackslash{}Phi\_\{TZP\}\$ generates strong spacetime curvature near the singularity (\$r\_c\$) driven solely by the winding number \$Q\$, independent of mass-energy, providing a mechanism for "Topological Gravity." Source: [17], [18]

\paragraph{Canonical Equation.}
\[
\nabla^2 \Phi_{TZP} \propto \frac{Q}{(r-r_c)^3}
\]

\paragraph{Dictionary.}
TOPOLOGICAL GRAVITY SOURCE Canonical Statutory Formula: ∇\textasciicircum{}2 Φ\_TZP ∝ (Q)/((r-r\_c)\textasciicircum{}3) Formal Technical Dissertation: Postulates the generation of gravity from pure topology.

\paragraph{Encyclopedia.}
TOPOLOGICAL GRAVITY SOURCE Canonical Statutory Formula is a differential equation, written ∇\textasciicircum{}2 Φ\_TZP ∝ (Q)/((r-r\_c)\textasciicircum{}3). It relates the quantity to its derivatives, governing how the system evolves in space and time. It is built from ∇, T, Z, P, Q, r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
