\section*{ID8534: COUPLED FOLD-MODE EVOLUTION Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 4867626551658 | RTEID: RTE:P33139.4172:T4.3381 | UUID: ed3fbd6b-5cd3-5143-a34a-80b2583d856e

\paragraph{Canonical Statement.}
[ID 1140] COUPLED FOLD-MODE EVOLUTION Canonical Statutory Formula: \$\textbackslash{}ddot\{q\}\_i + 2\textbackslash{}gamma\_i \textbackslash{}dot\{q\} i + \textbackslash{}omega\_i\textasciicircum{}2 q\_i + \textbackslash{}epsilon \textbackslash{}sum\_j K \{ij\}(\textbackslash{}hat\{n\}(t))q\_j = F\_i(t)\$ Formal Technical Dissertation: The master control equation for the system. It shows how the "Disharmonic Fold" introduces a coupling matrix \$K\_\{ij\}\$ dependent on the axis orientation, allowing the system to pump energy between orthogonal modes (\$q\_i, q\_j\$) by steering the axis. Source: [5]

\paragraph{Canonical Equation.}
\[
\ddot{q}_i + 2\gamma_i \dot{q} i + \omega_i^2 q_i + \epsilon \sum_j K {ij}(\hat{n}(t))q_j = F_i(t)
\]

\paragraph{Dictionary.}
COUPLED FOLD-MODE EVOLUTION Canonical Statutory Formula: \$ q\_i + 2 \_i q i + \_i\textasciicircum{}2 q\_i + \_j K ij(n(t))q\_j = F\_i(t)\$ Formal Technical Dissertation: The master control equation for the system.

\paragraph{Encyclopedia.}
COUPLED FOLD-MODE EVOLUTION Canonical Statutory Formula is a series / summation, written q\_i + 2γ\_i q i + ω\_i\textasciicircum{}2 q\_i + ε ∑\_j K ij(n(t))q\_j = F\_i(t). It is expressed as a sum or series over modes or indices, superposing discrete contributions. It is built from F\_i, defining q\_i + 2γ\_i q i + ω\_i\textasciicircum{}2 q\_i + ε ∑\_j K ij(n(t))q\_j. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
