\section*{ID9896: Relation: P < 1 - 1/π ≈ 0.682}
\paragraph{Metadata.}
PiID: 7001264560016 | RTEID: RTE:P38428.3657:T0.4863 | UUID: a2c0828e-e8fa-5210-a2a6-c49c6da49705

\paragraph{Canonical Statement.}
s is extremely high; typical quantum teleports are 1 qubit per entangled pair; our entangled resource is enormously larger, enabling batch teleportation). The channel’s noise model is special: we design Kraus operators \$K\_\{k\}\$ that correspond to errors where a state hops to a different kissing sphere of the same index (with probability \$p/kissingNumber\_\{max\}\$) or stays put (with probability \$1-p\$). This is like a tailored depolarizing channel that respects the kissing structure. Because of the stabilizer and topological codes (next step), we can correct those specific errors up to a threshold \$p < 1 - 1/\textbackslash{}pi \textbackslash{}approx 0.682\$. Error Correction (𝒞): On the receiving end, we apply a topological error-correcting code native to the kissing graph. In our implementation, we use a surface-code-like approach on a kissing lattice where stabilizers are defined by products of Pauli Z around closed loops of kissing contacts and Pauli X across dual loops. The code distance comes out as \$d = 2\textbackslash{}lfloor\textbackslash{}sqrt\{N\_\{\textbackslash{}max\}\textbackslash{}pi\}\textbackslash{}rfloor + 1\$ (for \$N\_\{\textbackslash{}max\}=153600\$, \$\textbackslash{}sqrt\{153600\textbackslash{}pi\}\textbackslash{}approx 694\$, so \$d\textbackslash{}approx1389\$!). This enormous distance in

\paragraph{Canonical Equation.}
\[
p < 1 - 1/\pi \approx 0.682
\]

\paragraph{Dictionary.}
Relation: P < 1 - 1/π ≈ 0.682 — p < 1 - 1/π ≈ 0.682

\paragraph{Encyclopedia.}
Relation: P < 1 - 1/π ≈ 0.682 is a scaling / order-of-magnitude relation, written p < 1 - 1/π ≈ 0.682. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from π, p. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
