\tzpanchor{0143}
\tzpentryheader{0143}{Spin--Orbit Resonance Proposition}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{5c3180ac-8495-5ca1-a718-e888f1464e3b}}\\
\textbf{PiID} & \tzpcode{9408128481117} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{150}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{555.3008 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.9150 rad}\\
\textbf{TZPID} & \tzpcode{ID0143} & \textbf{Node Dependencies}\quad \tzpidref{0142}\\
\textbf{Registry} & \tzpcode{registry\_id\_0143} & \textbf{Scale}\quad tidal locking and planetary spin-orbit structure\\
\textbf{LOC Classification} & QB355 orbital mechanics & QA371 coupled phase systems\\
\textbf{arXiv Classification} & Primary: astro-ph.EP \quad Cross-list: nlin.AO, physics.class-ph & \\
\textbf{Primary Support} & Resonant Ratio & Tidal Torque Law\\
\textbf{Closure Support} & Torque-Driven Spin Evolution & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
To model actual celestial synchronization phenomena, one must include spin--orbit coupling and tidal dissipation, since they generate specific resonance ratios.

\tzpsection{Canonical Equation}
\[
\frac{\Omega_{\mathrm{spin}}}{\Omega_{\mathrm{orb}}}=\frac{3}{2}
\]
\[
\tau_{\mathrm{tidal}}\propto -\gamma \sin\!\bigl(2\theta-3M\bigr)
\]
\[
\dot{\theta}=\Omega_{\mathrm{spin}}+\tau_{\mathrm{tidal}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Omega_{\mathrm{spin}}$: angular frequency term in the source equation.
    \item $\Omega_{\mathrm{orb}}$: angular frequency term in the source equation.
    \item $\tau_{\mathrm{tidal}}$: source equation symbol.
    \item $\gamma$: source equation symbol.
    \item $\theta$: phase angle or local angular coordinate.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0143 generated source Wolfram model *)
ClearAll[K0143, Cr0143, T, R, A, W, I, N];
eq0143$1 = HoldForm[OmegaSpin/OmegaOrb == 3/2];
eq0143$2 = HoldForm[tauTidal ? (-gamma)*Sin[2*theta - 3*M]];
eq0143$3 = HoldForm[dot[theta] == OmegaSpin + tauTidal];

K0143 = HoldForm[{eq0143$1, eq0143$2, eq0143$3}];

N = "normalized TRAWIN closure object for Spin--Orbit Resonance Proposition";
I = "Torque-Driven Spin Evolution integration/comparison layer";
W = "Tidal Torque Law wave or operator carrier";
A = "Resonant Ratio admissible action/amplitude condition";
R = "Tidal Torque Law rotation/curl preservation layer";
T = "Resonant Ratio local source condition";

Cr0143[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0143 = Cr0143[K0143];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Resonant Ratio local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Tidal Torque Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Resonant Ratio admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Tidal Torque Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Torque-Driven Spin Evolution integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Spin--Orbit Resonance Proposition.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0143] Spin--Orbit Resonance Proposition}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\frac{\Omega_{\mathrm{spin}}}{\Omega_{\mathrm{orb}}}=\frac{3}{2}
\]
\[
\tau_{\mathrm{tidal}}\propto -\gamma \sin\!\bigl(2\theta-3M\bigr)
\]
\[
\dot{\theta}=\Omega_{\mathrm{spin}}+\tau_{\mathrm{tidal}}
\]

\paragraph{Primary Derivation.}
This argument establishes the identity by differentiating and applying the relevant definitions. leading to the displayed result.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. Within the TRAWIN framework, the equation functions as the generalized carrier for the entry’s information content. In CHL terms, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Spin--Orbit Resonance Proposition by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Resonant Ratio}\par
\[
\frac{\Omega_{\mathrm{spin}}}{\Omega_{\mathrm{orb}}}=\frac{3}{2}
\]
\noindent This states the canonical locked frequency relation.\par
\noindent\textbf{2. Tidal Torque Law}\par
\[
\tau_{\mathrm{tidal}}\propto -\gamma \sin\!\bigl(2\theta-3M\bigr)
\]
\noindent This introduces the dissipative forcing responsible for resonance capture.\par
\noindent\textbf{3. Torque-Driven Spin Evolution}\par
\[
\dot{\theta}=\Omega_{\mathrm{spin}}+\tau_{\mathrm{tidal}}
\]
\noindent This closes the progression by placing the torque term directly into the spin dynamics.\par

\clearpage
\noindent\textbf{[ID 0143] Spin--Orbit Resonance Proposition}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Spin--Orbit Resonance Proposition is a Proposition. Real planetary spin--orbit resonances (for example Mercury's 3:2 resonance) arise from star--planet tidal torques that produce terms proportional to sin(phase difference) multiplied by dissipation. These resonances are not captured by phase only Kuramoto models.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Real planetary spin--orbit resonances (for example Mercury's 3:2 resonance) arise from star--planet tidal torques that produce terms proportional to sin(phase difference) multiplied by dissipation. These resonances are not captured by phase only Kuramoto models.
\textbf{Contextual meaning:} To model actual celestial synchronization phenomena, one must include spin--orbit coupling and tidal dissipation, since they generate specific resonance ratios.
\textbf{Derivable consequences:} Need to extend models to include torques; prediction of resonance ratios; improved match with observations.
\textbf{Lemma support:} Real planetary spin--orbit resonances (for example Mercury's 3:2 resonance) arise from star--planet tidal torques that produce terms proportional to sin(phase difference) multiplied by dissipation. These resonances are not captured by phase only Kuramoto models.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Simulate networks with varied frequency distributions and measure how the order parameter responds to coupling changes. ID 143: Spin--Orbit Resonance Proposition

\tzpsection{Equation Grounding}
Real planetary spin--orbit resonances (for example Mercury's 3:2 resonance) arise from star--planet tidal torques that produce terms proportional to sin(phase difference) multiplied by dissipation. These resonances are not captured by phase only Kuramoto models.

\tzpsection{Interpretive Role}
To model actual celestial synchronization phenomena, one must include spin--orbit coupling and tidal dissipation, since they generate specific resonance ratios.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Resonant Ratio}: The statement of the canonical locked frequency relation.
\item \textbf{Tidal Torque Law}: The introduction of the dissipative forcing responsible for resonance capture.
\item \textbf{Torque-Driven Spin Evolution}: The placement of the torque term directly into the spin dynamics.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0143]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0143_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0143] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Spin--Orbit Resonance Proposition}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} to model actual celestial synchronization phenomena, one must include spin--orbit
coupling and tidal dissipation, since they generate specific reso...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Spin--Orbit Resonance Proposition is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0143_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
