\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{isabelle,isabellesym}
\usepackage{amsmath}
\usepackage{url}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}

\title{A Derivation-Order Certificate for a 10,271-Node Registry}
\author{Daniel Alexander Trawin}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This AFP candidate formalizes the derivation-order invariant for a reassembled proof ladder over a 10,271-entry registry. The submitted theory encodes 753 concrete dependency edges as rung pairs and proves that each edge points from an earlier prerequisite rung to a later dependent rung. The result is a small, auditable Isabelle/HOL certificate for acyclicity with respect to the supplied ranking: every materialized dependency respects the strict upward-rung order. The wider registry, graph-topology report, and publication paper are treated as source documentation for the generated edge set; the formal AFP contribution is the checked order invariant itself.
\end{abstract}

\tableofcontents

\section{Overview}

The theory in this entry is generated from the materialized dependency-edge audit of the TZPID proof ladder. Each edge \((d,r)\) means that registry rung \(r\) depends on prerequisite rung \(d\). The intended invariant is therefore \(d < r\).

The formalization deliberately has a narrow scope. It does not attempt to prove the scientific content of the registry entries. It proves that the exported dependency order is non-circular with respect to the reassembled proof ladder.

\section{Sources}

The edge list and informal documentation are derived from the TZPIDProof archive:

\begin{itemize}
  \item \emph{TZPID Reassembled Proof Ladder---All IDs in Derivation Order}.
  \item \emph{TZPID Proof Ladder Graph Topology Report}.
  \item \emph{The DAG Breakthrough: A Derivation-Order Certificate for the TZPID Registry}.
\end{itemize}

Archive DOI: \url{https://doi.org/10.5281/zenodo.20632000}.

\section{Formal Development}

\input{session}

\bibliographystyle{plain}
\begin{thebibliography}{1}

\bibitem{nipkow-paulson-wenzel}
Tobias Nipkow, Lawrence C. Paulson, and Markus Wenzel.
\newblock \emph{Isabelle/HOL: A Proof Assistant for Higher-Order Logic}.
\newblock Springer, 2002.

\bibitem{tzpid-doi}
Daniel Alexander Trawin.
\newblock \emph{TZPID Reassembled Proof Ladder and DAG Certificate}.
\newblock Zenodo, 2026.
\newblock \url{https://doi.org/10.5281/zenodo.20632000}.

\end{thebibliography}

\end{document}
