\tzpanchor{0988}
\tzpentryheader{0988}{q-DEFORMED SYMMETRY GROUP}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{46de18a2-f0ac-553a-bc7b-4afced51f182}}\\
\textbf{PiID} & \tzpcode{0921642019893} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{995}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3762.8422 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{06.2000 rad}\\
\textbf{TZPID} & \tzpcode{ID0988} & \textbf{Node Dependencies}\quad \tzpidref{0987}\\
\textbf{Registry} & \tzpcode{registry\_id\_0988} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
- Composition: Phi\_t circ Phi\_s = Phi\_(t+s) (group property)

\tzpsection{Canonical Equation}
\[
- Composition: \Phi_{\mathrm{t}} \circ \Phi_{\mathrm{s}} = \Phi_(t+s) (group property)
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Phi_{\mathrm{t}}$: flux, phase, or topological map term in the source equation.
    \item $\Phi_{\mathrm{s}}$: flux, phase, or topological map term in the source equation.
    \item $\Phi$: flux, phase, or topological map term in the source equation.
    \item $J$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0988 generated source Wolfram model *)
ClearAll[K0988, Cr0988, T, R, A, W, I, N];
eq0988$1 = HoldForm[-(Composition:PhiTcirc*PhiS == PhiTs[group*property])];
eq0988$2 = HoldForm[mathcal[J]*_*out == TTZP[KTZP]];

K0988 = HoldForm[{eq0988$1, eq0988$2}];

N = "normalized TRAWIN closure object for q-DEFORMED SYMMETRY GROUP";
I = "q-DEFORMED SYMMETRY GROUP integration/comparison layer";
W = "q-DEFORMED SYMMETRY GROUP wave or operator carrier";
A = "q-DEFORMED SYMMETRY GROUP admissible action/amplitude condition";
R = "q-DEFORMED SYMMETRY GROUP rotation/curl preservation layer";
T = "q-DEFORMED SYMMETRY GROUP local source condition";

Cr0988[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0988 = Cr0988[K0988];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ q-DEFORMED SYMMETRY GROUP local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ q-DEFORMED SYMMETRY GROUP rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ q-DEFORMED SYMMETRY GROUP admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ q-DEFORMED SYMMETRY GROUP wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ q-DEFORMED SYMMETRY GROUP integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for q-DEFORMED SYMMETRY GROUP.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0988] q-DEFORMED SYMMETRY GROUP}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
- Composition: \Phi_{\mathrm{t}} \circ \Phi_{\mathrm{s}} = \Phi_(t+s) (group property)
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\paragraph{Primary Derivation.}
One can verify the equality by differentiating and applying the relevant definitions. leading to the displayed result.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. Interpreted through TRAWIN, the equation functions as the generalized carrier for the entry’s information content. According to CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors q-DEFORMED SYMMETRY GROUP by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
- Composition: \Phi_{\mathrm{t}} \circ \Phi_{\mathrm{s}} = \Phi_(t+s) (group property)
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0988] q-DEFORMED SYMMETRY GROUP}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
q-DEFORMED SYMMETRY GROUP is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} - Composition: Phi sub t circ Phi sub s = Phi sub (t+s) (group property). \textbf{Contextual meaning:} The entry reads q-DEFORMED SYMMETRY GROUP as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, q-DEFORMED SYMMETRY GROUP is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: - Composition: Phi sub t compose Phi sub s = Phi sub (t+s) (group property); mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Quantum-Squeezed Geometry}: The bizarre math required to describe a perfectly round, symmetrical magnetic field that has been violently crushed and stretched by the sheer pressure of the quantum void.
\item \textbf{Non-Commutative Rotational Bleed}: The terrifying physics where turning the reactor left and then right results in a completely different, much more dangerous energy state than turning it right and then left.
\item \textbf{Algebraic-Structure Warping}: The realization that the incredibly heavy gravity of the core isn't just bending the metal walls, it's actually bending the abstract, invisible rules of algebra itself.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0988]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0988].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0988] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont q-DEFORMED SYMMETRY GROUP}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} q-DEFORMED SYMMETRY GROUP is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``q-DEFORMED SYMMETRY GROUP is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0988].
\par\endgroup
\vfill
\endgroup
\endgroup
