\tzpanchor{0709}
\tzpentryheader{0709}{TZP Operator for Extraction and Collapse}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{db6f355f-3b2c-5565-9856-ca48f8f8ce8e}}\\
\textbf{PiID} & \tzpcode{1212902196086} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{716}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2722.1387 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.4852 rad}\\
\textbf{TZPID} & \tzpcode{ID0709} & \textbf{Node Dependencies}\quad \tzpidref{0708}\\
\textbf{Registry} & \tzpcode{registry\_id\_0709} & \textbf{Scale}\quad field-dynamical\\
\textbf{LOC Classification} & QC20.7 field theory & QA321 variational structure\\
\textbf{arXiv Classification} & Primary: hep-th & Cross-list: math-ph, gr-qc\\
\textbf{Primary Support} & Unified Density & Euler-Lagrange Flow\\
\textbf{Closure Support} & Stationary Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records tzp operator for extraction and collapse through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0709}}:\mathcal{X}_{\mathrm{id0709}}\longrightarrow\mathcal{Y}_{\mathrm{id0709}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0709}})=\mathcal{O}_{\mathrm{id0709}}
\]
\[
\mathcal{O}_{\mathrm{id0709}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0709}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0709}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0709}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0709 generated source Wolfram model *)
ClearAll[K0709, Cr0709, T, R, A, W, I, N];
eq0709$1 = HoldForm[Oid0709[Xid0709] -> Yid0709];
eq0709$2 = HoldForm[NTRAWIN[OId0709] == OId0709];
eq0709$3 = HoldForm[Element[OId0709[x], YAdm]];

K0709 = HoldForm[{eq0709$1, eq0709$2, eq0709$3}];

N = "normalized TRAWIN closure object for TZP Operator for Extraction and Collapse";
I = "TZP Operator for Extraction and Collapse integration/comparison layer";
W = "TZP Operator for Extraction and Collapse wave or operator carrier";
A = "TZP Operator for Extraction and Collapse admissible action/amplitude condition";
R = "TZP Operator for Extraction and Collapse rotation/curl preservation layer";
T = "TZP Operator for Extraction and Collapse local source condition";

Cr0709[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0709 = Cr0709[K0709];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ TZP Operator for Extraction and Collapse local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TZP Operator for Extraction and Collapse rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ TZP Operator for Extraction and Collapse admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TZP Operator for Extraction and Collapse wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TZP Operator for Extraction and Collapse integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP Operator for Extraction and Collapse.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0709] TZP Operator for Extraction and Collapse}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0709}}:\mathcal{X}_{\mathrm{id0709}}\longrightarrow\mathcal{Y}_{\mathrm{id0709}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0709}})=\mathcal{O}_{\mathrm{id0709}}
\]
\[
\mathcal{O}_{\mathrm{id0709}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The expression \( \mathcal{O}_{\mathrm{id0709}}:\mathcal{X}_{\mathrm{id0709}}\longrightarrow\mathcal{Y}_{\mathrm{id0709}} \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. Within the TRAWIN framework, the equation functions as the integral carrier for the entry’s information content. In CHL terms, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP Operator for Extraction and Collapse by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0709}}:\mathcal{X}_{\mathrm{id0709}}\longrightarrow\mathcal{Y}_{\mathrm{id0709}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0709}})=\mathcal{O}_{\mathrm{id0709}}
\]
\[
\mathcal{O}_{\mathrm{id0709}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0709] TZP Operator for Extraction and Collapse}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP Operator for Extraction and Collapse is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} rangle. \textbf{Contextual meaning:} The entry reads TZP Operator for Extraction and Collapse as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry supplies the book with a true unification density, so later extraction and dynamo pages can be read as sectoral consequences of one action. \textbf{Lemma support:} Unified Density; Euler-Lagrange Flow; Stationary Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, TZP Operator for Extraction and Collapse is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: dissipation = Sigma sub k   sub k ( L sub k rho L sub k  - L sub k  L sub k, rho /2 ) where Jump[L sub k] = ProjectiveMeasurement[ Basis to EigenvectorBasis[Observable[k]], Probability to BornRule[| phi sub k|psi | to the power 2] ]; measurement = -i [M M, rho]/2 + M rho M  where M = Sigma sub omega  ( (omega)) a(omega) otimes  *(omega); and reaction = R[ ] -   where R[ ] =  (mu -   to the power 2)(1 -   to the power 2). Proof route: show that the joined density yields a coherent Euler-Lagrange system whose sectoral terms remain admissible under TRAWIN normalization. Formalization route: prove that stationarity of the unified action implies the stated field equation.

\tzpsection{Interpretive Role}
The entry supplies the book with a true unification density, so later extraction and dynamo pages can be read as sectoral consequences of one action.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Target-State Annihilation Mapping}: The mathematical command that completely crushes the complex, evolving system down into a single, inescapable end state.
\item \textbf{Commutator-Driven Phase Drift}: The specific part of the collapse equation driven by the quantum mechanical interference between the system's different moving parts.
\item \textbf{Stationary Action Minimization}: The proof that this extreme collapse represents the system finding its absolute lowest, most stable, and unmoving energy configuration.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0709]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0709].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0709] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP Operator for Extraction and Collapse}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} TZP Operator for Extraction and Collapse is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP Operator for Extraction and Collapse is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0709].
\par\endgroup
\vfill
\endgroup
\endgroup
