\tzpanchor{0399}
\tzpentryheader{0399}{Information Conservation and Holographic Preservation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{6b928abe-2f12-5b95-80d2-01660cddd01b}}\\
\textbf{PiID} & \tzpcode{4330572703657} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{406}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1549.4056 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.5529 rad}\\
\textbf{TZPID} & \tzpcode{ID0399} & \textbf{Node Dependencies}\quad \tzpidref{0398}\\
\textbf{Registry} & \tzpcode{registry\_id\_0399} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Noether Current & Unitary Preservation\\
\textbf{Closure Support} & Holographic Bound & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Information currents and entropies obey four complementary conservation principles: Noether conservation of an information current $J^{\mu}_{\mathrm{info}}$, Liouville preservation of phase-space volume, unitary conservation of total probability, and the holographic entropy bound limiting information density by boundary area. The holographic preservation theorem asserts that information remains preserved through dimensional collapse at a TZP by topological protection.

\tzpsection{Canonical Equation}
\[
\partial_{\mu}J^{\mu}_{\mathrm{info}}=0
\]
\[
U^{\dagger}U=I
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mu$: source equation symbol.
    \item $U$: auxiliary source state or local chart variable.
    \item $I$: source equation symbol.
    \item $S_{\mathrm{info}}$: source equation symbol.
    \item $A$: source equation symbol.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0399 generated source Wolfram model *)
ClearAll[K0399, Cr0399, T, R, A, W, I, N];
eq0399$1 = HoldForm[PartialMuJ^mu*_*info == 0];
eq0399$2 = HoldForm[U^Dagger*U == I];
eq0399$3 = HoldForm[SInfo <= A/(4*Ghbar)];

K0399 = HoldForm[{eq0399$1, eq0399$2, eq0399$3}];

N = "normalized TRAWIN closure object for Information Conservation and Holographic Preservation";
I = "Holographic Bound integration/comparison layer";
W = "Unitary Preservation wave or operator carrier";
A = "Noether Current admissible action/amplitude condition";
R = "Unitary Preservation rotation/curl preservation layer";
T = "Noether Current local source condition";

Cr0399[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0399 = Cr0399[K0399];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Noether Current local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Unitary Preservation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Noether Current admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Unitary Preservation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Holographic Bound integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Information Conservation and Holographic Preservation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0399] Information Conservation and Holographic Preservation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Carrier Superposition.}
\begin{equation}
\Psi(t)=A\cos(\omega_1t)+B\cos(\omega_2t).
\end{equation}

\paragraph{Envelope--Carrier Decomposition.}
\begin{equation}
\Psi(t)
=
2C
\cos\left(
\frac{\omega_1-\omega_2}{2}t
\right)
\cos\left(
\frac{\omega_1+\omega_2}{2}t
\right).
\end{equation}

\paragraph{Coupling Windows.}
\begin{equation}
t_k=
\frac{2\pi k}{|\omega_1-\omega_2|}.
\end{equation}

\paragraph{Primary Derivation.}
For paired carriers, the raw signal is:
\begin{equation}
\Psi(t)=A\cos(\omega_1t)+B\cos(\omega_2t).
\end{equation}

For equal or normalized amplitudes, the trigonometric sum identity yields:
\begin{equation}
\Psi(t)
=
2C
\cos\left(
\frac{\omega_1-\omega_2}{2}t
\right)
\cos\left(
\frac{\omega_1+\omega_2}{2}t
\right).
\end{equation}

Envelope maxima occur at discrete times:
\begin{equation}
\boxed{
t_k=
\frac{2\pi k}{|\omega_1-\omega_2|}.
}
\end{equation}

\paragraph{Interpretation.}
Beat topology identifies discrete envelope windows where coherent coupling is strongest.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Information Conservation and Holographic Preservation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Noether Current}\par
\[
\partial_{\mu}J^{\mu}_{\mathrm{info}}=0
\]
\noindent This fixes the conserved information current implied by the stated symmetry argument.\par
\noindent\textbf{2. Unitary Preservation}\par
\[
U^{\dagger}U=I
\]
\noindent This identifies unitarity as the algebraic preservation law on the information carrier.\par
\noindent\textbf{3. Holographic Bound}\par
\[
S_{\mathrm{info}}\leq\frac{A}{4G\hbar}
\]
\noindent This closes the entry by imposing the holographic entropy bound on the enclosing surface.\par

\clearpage
\noindent\textbf{[ID 0399] Information Conservation and Holographic Preservation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Information Conservation and Holographic Preservation is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Information currents and entropies obey four complementary conservation principles: Noether conservation of an information current J to the power mu sub info , Liouville preservation of phase-space volume, unitary conservation of total probability, and the holographic entropy bound limiting information density by boundary area. The holographic preservation theorem asserts that information remains preserved through dimensional collapse at a TZP by topological protection. \textbf{Contextual meaning:} The entry reads Information Conservation and Holographic Preservation as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now presents the conservation and holographic-preservation claims as the three complementary equations that actually anchor the page. \textbf{Lemma support:} Noether Current; Unitary Preservation; Holographic Bound.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Beat topology identifies discrete envelope windows where coherent coupling is strongest.

\tzpsection{Equation Grounding}
Equation anchors: partial sub mu J to the power mu sub info =0; U to the power dagger U=mathbb I; and Sleq ratio A 4ell sub P to the power 2. Proof route: show that the conserved current, unitary evolution, and holographic bound jointly preserve information through the TZP collapse. Formalization route: prove that the stated preservation laws are mutually compatible under the admissible evolution.

\tzpsection{Interpretive Role}
The entry now presents the conservation and holographic-preservation claims as the three complementary equations that actually anchor the page.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Zero-Divergence Data Current}: The mathematical proof that, like water in a pipe, the total flow of information through the system is perfectly conserved and never destroyed.
\item \textbf{Unitary Operator Evolution}: The requirement that the rules governing the system's movement over time must preserve the total probability of all possible outcomes.
\item \textbf{Bekenstein Area-Entropy Limit}: The absolute physical law stating that the total amount of data hidden inside the volume cannot exceed the storage capacity of its outer shell.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0399]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0399_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0399] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Information Conservation and Holographic Preservation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} information currents and entropies obey four complementary conservation principles:
Noether conservation of an information current J\textasciicircum{}\_info, Liouv...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Information Conservation and Holographic Preservation is valid when the total tensorial
quantity is conserved under the stated constraint.''\\
\textbf{Proof:} The source statement identifies a conserved balance law. Reading 0399 as a proposition,
validity follows by requiring the full stress, flux, or current contribution to be
included before the divergence or balance condition is evaluated.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conserved total-structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0399_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
