\tzpanchor{0790}
\tzpentryheader{0790}{153,600-DIMENSIONAL TRAJECTORY ENCODING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{ebfa7323-a1f9-52b1-9e98-5b5e967164c9}}\\
\textbf{PiID} & \tzpcode{1609631859502} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{797}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3028.9132 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.9907 rad}\\
\textbf{TZPID} & \tzpcode{ID0790} & \textbf{Node Dependencies}\quad \tzpidref{0789}\\
\textbf{Registry} & \tzpcode{registry\_id\_0790} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records 153,600-dimensional trajectory encoding through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0790}}:\mathcal{X}_{\mathrm{id0790}}\longrightarrow\mathcal{Y}_{\mathrm{id0790}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0790}})=\mathcal{O}_{\mathrm{id0790}}
\]
\[
\mathcal{O}_{\mathrm{id0790}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0790}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0790}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0790}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0790 generated source Wolfram model *)
ClearAll[K0790, Cr0790, T, R, A, W, I, N];
eq0790$1 = HoldForm[Oid0790[Xid0790] -> Yid0790];
eq0790$2 = HoldForm[NTRAWIN[OId0790] == OId0790];
eq0790$3 = HoldForm[Element[OId0790[x], YAdm]];

K0790 = HoldForm[{eq0790$1, eq0790$2, eq0790$3}];

N = "normalized TRAWIN closure object for 153,600-DIMENSIONAL TRAJECTORY ENCODING";
I = "153,600-DIMENSIONAL TRAJECTORY ENCODING integration/comparison layer";
W = "153,600-DIMENSIONAL TRAJECTORY ENCODING wave or operator carrier";
A = "153,600-DIMENSIONAL TRAJECTORY ENCODING admissible action/amplitude condition";
R = "153,600-DIMENSIONAL TRAJECTORY ENCODING rotation/curl preservation layer";
T = "153,600-DIMENSIONAL TRAJECTORY ENCODING local source condition";

Cr0790[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0790 = Cr0790[K0790];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ 153,600-DIMENSIONAL TRAJECTORY ENCODING local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ 153,600-DIMENSIONAL TRAJECTORY ENCODING rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ 153,600-DIMENSIONAL TRAJECTORY ENCODING admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ 153,600-DIMENSIONAL TRAJECTORY ENCODING wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ 153,600-DIMENSIONAL TRAJECTORY ENCODING integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for 153,600-DIMENSIONAL TRAJECTORY ENCODING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0790] 153,600-DIMENSIONAL TRAJECTORY ENCODING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0790}}:\mathcal{X}_{\mathrm{id0790}}\longrightarrow\mathcal{Y}_{\mathrm{id0790}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0790}})=\mathcal{O}_{\mathrm{id0790}}
\]
\[
\mathcal{O}_{\mathrm{id0790}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0790}})=\mathcal{O}_{\mathrm{id0790}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
The statement concerns the variables introduced in the displayed formula. From the TRAWIN perspective, the equation functions as the mapping carrier for the entry’s information content. According to CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors 153,600-DIMENSIONAL TRAJECTORY ENCODING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0790}}:\mathcal{X}_{\mathrm{id0790}}\longrightarrow\mathcal{Y}_{\mathrm{id0790}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0790}})=\mathcal{O}_{\mathrm{id0790}}
\]
\[
\mathcal{O}_{\mathrm{id0790}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0790] 153,600-DIMENSIONAL TRAJECTORY ENCODING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
153,600-DIMENSIONAL TRAJECTORY ENCODING is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} 153,600-dimensional. \textbf{Contextual meaning:} The entry reads 153,600-DIMENSIONAL TRAJECTORY ENCODING as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, 153,600-DIMENSIONAL TRAJECTORY ENCODING is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: frac R r approximately2.46; approx2.37037; and U=exp(ipi ,hat n !dot !tfrac sigma 2 )=-I,. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Infinite-Dimensional Graphing}: The mind-breaking task of trying to draw a map that doesn't just have an X, Y, and Z axis, but has hundreds of thousands of different directions you could possibly move in at the same time.
\item \textbf{Basis-Vector Orthogonality Checks}: The paranoid mathematical proofs running non-stop to guarantee that moving forward in one of those hundred-thousand directions doesn't accidentally move you backward in any of the others.
\item \textbf{State-Vector Ray Projections}: The realization that in this bizarre math, the length of the line you draw doesn't actually matter at all; the only thing that changes the physics is the incredibly specific angle it points.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0790]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0790].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0790] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont 153,600-DIMENSIONAL TRAJECTORY ENCODING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} 153,600-DIMENSIONAL TRAJECTORY ENCODING is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``153,600-DIMENSIONAL TRAJECTORY ENCODING is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0790].
\par\endgroup
\vfill
\endgroup
\endgroup
