\tzpanchor{0238}
\tzpentryheader{0238}{Magnetic Interaction Parameter}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{2f54ac20-5115-59b0-8f7f-ac42f28c38d8}}\\
\textbf{PiID} & \tzpcode{6527120190914} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{245}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{924.2069 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.5228 rad}\\
\textbf{TZPID} & \tzpcode{ID0238} & \textbf{Node Dependencies}\quad \tzpidref{0237}\\
\textbf{Registry} & \tzpcode{registry\_id\_0238} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Unified Density & Euler-Lagrange Flow\\
\textbf{Closure Support} & Stationary Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The magnetic interaction parameter is N = (B\^{}2 L)/(mu\_0 rho v\^{}2 R), characterising the ratio of magnetic to inertial forces in a conductive flow.

\tzpsection{Canonical Equation}
\[
N=\frac{\sigma B^2L}{\rho v}
\]
\[
N\geq1\Rightarrow\text{Lorentz dominated}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $N$: magnetic interaction parameter comparing magnetic and inertial force scales.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $B$: magnetic field magnitude.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $\rho$: density or measure term used by the entry equation.
    \item $v$: velocity, flow speed, or auxiliary comparison variable.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0238 generated source Wolfram model *)
ClearAll[K0238, Cr0238, T, R, A, W, I, N];
eq0238$1 = HoldForm[N == (sigma*B^2*L)/(rho*v)];
eq0238$2 = HoldForm[N >= 1 -> LorentzDominated];

K0238 = HoldForm[{eq0238$1, eq0238$2}];

N = "normalized TRAWIN closure object for Magnetic Interaction Parameter";
I = "Stationary Closure integration/comparison layer";
W = "Euler-Lagrange Flow wave or operator carrier";
A = "Unified Density admissible action/amplitude condition";
R = "Euler-Lagrange Flow rotation/curl preservation layer";
T = "Unified Density local source condition";

Cr0238[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0238 = Cr0238[K0238];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Unified Density local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Euler-Lagrange Flow rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Unified Density admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Euler-Lagrange Flow wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Stationary Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Magnetic Interaction Parameter.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0238] Magnetic Interaction Parameter}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Lambda
=
\frac{\mathbf{B}^2}
{\rho\,\mu\,\Omega^2}.
\end{equation}

\paragraph{Primary Derivation.}
Let $\mathbf{B}$ be magnetic field strength, $\rho$ mass density, $\mu$ magnetic permeability, and $\Omega$ angular rotation rate.

The magnetic contribution is represented by field magnitude squared:

\begin{equation}
\mathbf{B}^2 .
\end{equation}

The inertial-rotational scale is represented by:

\begin{equation}
\rho\,\mu\,\Omega^2 .
\end{equation}

The dimensionless comparison between these two effects defines the Elsasser-type parameter:

\begin{equation}
\boxed{
\Lambda
=
\frac{\mathbf{B}^2}
{\rho\,\mu\,\Omega^2}.
}
\end{equation}

The attractor condition is:

\begin{equation}
\Lambda \approx 1 .
\end{equation}

\paragraph{Interpretation.}
The Elsasser attractor occurs when magnetic and rotational scales enter near-balance, producing a self-organizing critical manifold.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Magnetic Interaction Parameter by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Unified Density}\par
\[
N=\frac{\sigma B^2L}{\rho v}
\]
\noindent This gathers the sectors that the tertiary arc is trying to hold in one variational frame.\par
\noindent\textbf{2. Euler-Lagrange Flow}\par
\[
N\geq1\Rightarrow\text{Lorentz dominated}
\]
\noindent This turns the density into an actual field law rather than a formal sum.\par
\noindent\textbf{3. Stationary Closure}\par
\[
N\geq1\Rightarrow\text{Lorentz dominated}
\]
\noindent This closes the entry by imposing stationary admissibility on the total action.\par

\clearpage
\noindent\textbf{[ID 0238] Magnetic Interaction Parameter}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Magnetic Interaction Parameter is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The magnetic interaction parameter is N = (B 2 L)/(mu sub 0 rho v 2 R), characterising the ratio of magnetic to inertial forces in a conductive flow. \textbf{Contextual meaning:} The entry reads Magnetic Interaction Parameter as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry supplies the book with a true unification density, so later extraction and dynamo pages can be read as sectoral consequences of one action. \textbf{Lemma support:} Unified Density; Euler-Lagrange Flow; Stationary Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The Elsasser attractor occurs when magnetic and rotational scales enter near-balance, producing a self-organizing critical manifold.

\tzpsection{Equation Grounding}
Equation anchors: N=ratio sigma B to the power 2L rho v; N=ratio Ha to the power 2 Re; and Ngeq1Rightarrow Lorentz dominated. Proof route: show that the joined density yields a coherent Euler-Lagrange system whose sectoral terms remain admissible under TRAWIN normalization. Formalization route: prove that stationarity of the unified action implies the stated field equation.

\tzpsection{Interpretive Role}
The entry supplies the book with a true unification density, so later extraction and dynamo pages can be read as sectoral consequences of one action.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Magnetic-to-Kinetic Pressure Ratio}: The dimensionless metric comparing the energy density of the magnetic field to the kinetic energy density of the fluid flow.
\item \textbf{Flow Modification via Lorentz Drag}: The measurement of how severely a strong magnetic field acts to retard and straighten the motion of a conductive fluid.
\item \textbf{Field-Aligned Retardation Coefficient}: The specific quantification of the braking force exerted on a plasma crossing perpendicular to magnetic lines of force.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0238]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0238_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0238] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Magnetic Interaction Parameter}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the magnetic interaction parameter is N = (B\textbackslash{}\textasciicircum{}2 L)/(mu\textbackslash{}\_0 rho v\textbackslash{}\textasciicircum{}2 R), characterising
the ratio of magnetic to inertial forces in a conductive flow

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Magnetic Interaction Parameter is valid when the stated geometric or topological
relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0238_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
