\section*{ID9154: Relation: –(1/ρ)·[∂P\_hydro/∂r+∂P\_electric/∂R]}
\paragraph{Metadata.}
PiID: 9469955657612 | RTEID: RTE:P35547.0149:T2.0219 | UUID: 32902ce6-110e-5df7-9351-7c49ae9065e9

\paragraph{Canonical Statement.}
e. Dependencies: 123 Derivable Consequences: Electrohydrodynamic coupling; design of ionfocusing devices; synergy with charge oscillation. Falsifiability / Test Handle: Measure conductivity distribution in a vortex; observe current focusing and pinch behaviours. 1.0.27 ID 126: Electrohydrodynamic Resonance Operator Type: Operator Formal Statement: Apply a fluctuating negative charge density \$ρ\_e(t)\$ = \$ρ\_0\$ + \$ρ\_1 cos(ω\$ t) to a vortex region. The total radial acceleration becomes a\_total = \$–(1/ρ)·[∂P\_hydro/∂r+∂P\_electric/∂r]\$ + \$(ρ\_e/ρ)E\_r.\$ When \$ω\$ matches the natural vortex frequency, parametric amplification yields a\_total between 5 and 20 times the baseline a\_r. Interpretive Meaning: Oscillating electric charge modifies the pressure field and produces large amplification of vortex strength, defining an electrohydrodynamic resonance. Dependencies: 125 Derivable Consequences: Resonant enhancement of vortex and cu

\paragraph{Canonical Equation.}
\[
–(1/ρ)·[∂P_hydro/∂r+∂P_electric/∂r]
\]

\paragraph{Dictionary.}
Relation: –(1/ρ)·[∂P\_hydro/∂r+∂P\_electric/∂R] — –(1/ρ)·[∂P\_hydro/∂r+∂P\_electric/∂r]

\paragraph{Encyclopedia.}
Relation: –(1/ρ)·[∂P\_hydro/∂r+∂P\_electric/∂R] is a symbolic expression, written –(1/ρ)·[∂P\_hydro/∂r+∂P\_electric/∂r]. It introduces a symbol or relation used elsewhere in the framework. It is built from P\_h, y, r, o, P\_e, l. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
