\section*{ID8799: UNIVERSAL AVALANCHE EXPONENT (\$\textbackslash{}tau\$) Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 2742995818072 | RTEID: RTE:P34168.4711:T6.0336 | UUID: dedf9194-6848-5514-854f-79082c3aadef

\paragraph{Canonical Statement.}
[ID 1179] UNIVERSAL AVALANCHE EXPONENT (\$\textbackslash{}tau\$) Canonical Statutory Formula: \$P(s) \textbackslash{}propto s\textasciicircum{}\{-3/2\} \textbackslash{}exp(-s/s\_\{cutoff\})\$ Formal Technical Dissertation: The statistical signature of the interface. Both the user's neural avalanches and the reactor's quantum decoherence cascades follow this power law with \$\textbackslash{}tau = 3/2\$. This shared criticality allows for the "Metamaterial-Neural Isomorphism" and direct entrainment. Source: [18]

\paragraph{Canonical Equation.}
\[
P(s) \propto s^{-3/2} \exp(-s/s_{cutoff})
\]

\paragraph{Dictionary.}
UNIVERSAL AVALANCHE EXPONENT (τ) Canonical Statutory Formula: P(s) ∝ s\textasciicircum{}-3/2 exp(-s/s\_cutoff) Formal Technical Dissertation: The statistical signature of the interface.

\paragraph{Encyclopedia.}
UNIVERSAL AVALANCHE EXPONENT (\$\textbackslash{}tau\$) Canonical Statutory Formula is a scaling / order-of-magnitude relation, written P(s) ∝ s\textasciicircum{}-3/2 exp(-s/s\_cutoff). It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from P, s, s\_cutoff. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
