\tzpanchor{0231}
\tzpentryheader{0231}{Characteristic Radius of Disharmony}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{87122055-41f3-5212-9ef0-c9b424e505d7}}\\
\textbf{PiID} & \tzpcode{7867831652712} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{238}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{897.0243 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.4780 rad}\\
\textbf{TZPID} & \tzpcode{ID0231} & \textbf{Node Dependencies}\quad \tzpidref{0230}\\
\textbf{Registry} & \tzpcode{registry\_id\_0231} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Characteristic Radius & Bessel Zero\\
\textbf{Closure Support} & Boundary Diagnosis & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The characteristic radius of a localized disturbance in the hyperspherical vacuum is given by r\_0 = 2.405/k, corresponding to the first zero of the spherical Bessel function j\_0(k r).

\tzpsection{Canonical Equation}
\[
r_0 = \frac{2.405}{k}
\]
\[
j_0(k r_0)=0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $r_0$: source equation symbol.
    \item $j_0(kr_0)$: source equation symbol.
    \item $\mathcal{K}_{0231}$: canonical registry object for entry ID 0231.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0231 generated source Wolfram model *)
ClearAll[K0231, Cr0231, T, R, A, W, I, N];
eq0231$1 = HoldForm[r0 == 2.405/k];
eq0231$2 = HoldForm[j0[k*r0] == 0];
eq0231$3 = HoldForm[k*r0 == 2.405];

K0231 = HoldForm[{eq0231$1, eq0231$2, eq0231$3}];

N = "normalized TRAWIN closure object for Characteristic Radius of Disharmony";
I = "Boundary Diagnosis integration/comparison layer";
W = "Bessel Zero wave or operator carrier";
A = "Characteristic Radius admissible action/amplitude condition";
R = "Bessel Zero rotation/curl preservation layer";
T = "Characteristic Radius local source condition";

Cr0231[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0231 = Cr0231[K0231];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Characteristic Radius local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Bessel Zero rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Characteristic Radius admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Bessel Zero wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Boundary Diagnosis integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Characteristic Radius of Disharmony.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0231] Characteristic Radius of Disharmony}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{\partial S}{\partial t}
+
\mathcal{H}_T
\left(
q,\frac{\partial S}{\partial q},t
\right)
=
0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $S(q,t)$ be the action function for a classical trajectory on the Trawinistic manifold.  
The canonical momentum is obtained from the action by:

\begin{equation}
p_q=\frac{\partial S}{\partial q}.
\end{equation}

The Hamiltonian density or Hamiltonian function in Trawinistic form is:

\begin{equation}
\mathcal{H}_T(q,p_q,t).
\end{equation}

Substituting $p_q=\partial S/\partial q$ into the Hamiltonian gives:

\begin{equation}
\mathcal{H}_T
\left(
q,\frac{\partial S}{\partial q},t
\right).
\end{equation}

The Hamilton--Jacobi condition states that time evolution of the action cancels the Hamiltonian contribution:

\begin{equation}
\boxed{
\frac{\partial S}{\partial t}
+
\mathcal{H}_T
\left(
q,\frac{\partial S}{\partial q},t
\right)
=
0 .
}
\end{equation}

\paragraph{Interpretation.}
This equation translates Trawinistic Hamiltonian dynamics into an action-based evolution law.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Characteristic Radius of Disharmony by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Characteristic Radius}\par
\[
r_0 = \frac{2.405}{k}
\]
\noindent This fixes the characteristic disturbance radius.\par
\noindent\textbf{2. Bessel Zero}\par
\[
j_0(k r_0)=0
\]
\noindent This ties the radius to the first spherical Bessel zero.\par
\noindent\textbf{3. Boundary Diagnosis}\par
\[
k r_0 = 2.405
\]
\noindent This closes the entry with the corresponding boundary diagnosis in scaled coordinates.\par

\clearpage
\noindent\textbf{[ID 0231] Characteristic Radius of Disharmony}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Characteristic Radius of Disharmony is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The characteristic radius of a localized disturbance in the hyperspherical vacuum is given by r sub 0 = 2.405/k, corresponding to the first zero of the spherical Bessel function j sub 0(k r). \textbf{Contextual meaning:} The entry reads Characteristic Radius of Disharmony as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the disturbance radius directly through the first Bessel zero. \textbf{Lemma support:} Characteristic Radius; Bessel Zero; Boundary Diagnosis.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This equation translates Trawinistic Hamiltonian dynamics into an action-based evolution law.

\tzpsection{Equation Grounding}
Equation anchors: r sub 0 = ratio 2.405 k; j sub 0(k r sub 0)=0; and k r sub 0 = 2.405. Proof route: show that the first spherical Bessel zero implies the stated characteristic radius. Formalization route: prove that the first nodal radius satisfies the stated scaled Bessel condition.

\tzpsection{Interpretive Role}
The entry now states the disturbance radius directly through the first Bessel zero.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Decoherence Onset Length Scale}: The specific physical distance from the center of a resonant system where phase coherence irreversibly breaks down.
\item \textbf{Critical Disruption Boundary Coordinate}: The geometric threshold marking the separation between an ordered, resonant core and chaotic, unstructured surroundings.
\item \textbf{First-Nodal Breakdown Metric}: The measurement corresponding precisely to the first zero-crossing of the governing Bessel wave equation.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0231]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0231_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0231] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Characteristic Radius of Disharmony}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the characteristic radius of a localized disturbance in the hyperspherical vacuum is
given by r\textbackslash{}\_0 = 2.405/k, corresponding to the first zero of th...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Characteristic Radius of Disharmony is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0231_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
