\tzpanchor{0711}
\tzpentryheader{0711}{POWER EXTRACTION TENSOR}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{a2329771-0aed-5865-9438-850d12b3f3b4}}\\
\textbf{PiID} & \tzpcode{1290219608640} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{718}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2729.9051 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.4980 rad}\\
\textbf{TZPID} & \tzpcode{ID0711} & \textbf{Node Dependencies}\quad \tzpidref{0710}\\
\textbf{Registry} & \tzpcode{registry\_id\_0711} & \textbf{Scale}\quad field-dynamical\\
\textbf{LOC Classification} & QC20.7 field theory & QA321 variational structure\\
\textbf{arXiv Classification} & Primary: hep-th & Cross-list: math-ph, gr-qc\\
\textbf{Primary Support} & Unified Density & Euler-Lagrange Flow\\
\textbf{Closure Support} & Stationary Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records power extraction tensor through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0711}}:\mathcal{X}_{\mathrm{id0711}}\longrightarrow\mathcal{Y}_{\mathrm{id0711}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0711}})=\mathcal{O}_{\mathrm{id0711}}
\]
\[
\mathcal{O}_{\mathrm{id0711}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0711}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0711}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0711}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0711 generated source Wolfram model *)
ClearAll[K0711, Cr0711, T, R, A, W, I, N];
eq0711$1 = HoldForm[Oid0711[Xid0711] -> Yid0711];
eq0711$2 = HoldForm[NTRAWIN[OId0711] == OId0711];
eq0711$3 = HoldForm[Element[OId0711[x], YAdm]];

K0711 = HoldForm[{eq0711$1, eq0711$2, eq0711$3}];

N = "normalized TRAWIN closure object for POWER EXTRACTION TENSOR";
I = "POWER EXTRACTION TENSOR integration/comparison layer";
W = "POWER EXTRACTION TENSOR wave or operator carrier";
A = "POWER EXTRACTION TENSOR admissible action/amplitude condition";
R = "POWER EXTRACTION TENSOR rotation/curl preservation layer";
T = "POWER EXTRACTION TENSOR local source condition";

Cr0711[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0711 = Cr0711[K0711];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ POWER EXTRACTION TENSOR local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ POWER EXTRACTION TENSOR rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ POWER EXTRACTION TENSOR admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ POWER EXTRACTION TENSOR wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ POWER EXTRACTION TENSOR integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for POWER EXTRACTION TENSOR.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0711] POWER EXTRACTION TENSOR}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0711}}:\mathcal{X}_{\mathrm{id0711}}\longrightarrow\mathcal{Y}_{\mathrm{id0711}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0711}})=\mathcal{O}_{\mathrm{id0711}}
\]
\[
\mathcal{O}_{\mathrm{id0711}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The expression \( \mathcal{O}_{\mathrm{id0711}}:\mathcal{X}_{\mathrm{id0711}}\longrightarrow\mathcal{Y}_{\mathrm{id0711}} \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. Within the TRAWIN framework, the equation functions as the integral carrier for the entry’s information content. In CHL terms, the derivation provides a certificate connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors POWER EXTRACTION TENSOR by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0711}}:\mathcal{X}_{\mathrm{id0711}}\longrightarrow\mathcal{Y}_{\mathrm{id0711}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0711}})=\mathcal{O}_{\mathrm{id0711}}
\]
\[
\mathcal{O}_{\mathrm{id0711}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0711] POWER EXTRACTION TENSOR}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
POWER EXTRACTION TENSOR is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} P = int sub S (T to the power munu u sub nu) * dmathbf A implies P sub max \textasciitilde{} frac hbar c to the power 2 a to the power 2. \textbf{Contextual meaning:} The entry reads POWER EXTRACTION TENSOR as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry supplies the book with a true unification density, so later extraction and dynamo pages can be read as sectoral consequences of one action. \textbf{Lemma support:} Unified Density; Euler-Lagrange Flow; Stationary Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, POWER EXTRACTION TENSOR is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: mathcal R sub T = ( R + 2Lambda - ratio 8pi G c to the power 4 T sub topo ) dot exp( ratio Phi sub TZP P sub T ) dot chi sub T; \$ R sub T = ( R + 2Lambda - ratio 8pi G c to the power 4 T sub topo ) dot exp( ratio Phi sub TZP P sub T ) dot chi sub T; and FORMAL TECHNICAL DISSERTATION:The Curvature Tension Invariant, denoted as. Proof route: show that the joined density yields a coherent Euler-Lagrange system whose sectoral terms remain admissible under TRAWIN normalization. Formalization route: prove that stationarity of the unified action implies the stated field equation.

\tzpsection{Interpretive Role}
The entry supplies the book with a true unification density, so later extraction and dynamo pages can be read as sectoral consequences of one action.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Multidimensional Energy Bleed Matrix}: The complex mathematical grid tracking every possible direction and method by which useful power can be drained out of the spinning core.
\item \textbf{Stress-Energy Conversion Rate}: The exact calculation determining how much of the raw, violent spatial curvature can be safely translated into usable, outbound electrical amperage.
\item \textbf{Geometric-to-Kinetic Yield Operator}: The mapping that turns the pure abstract twisting of the mathematical manifold into the real-world physical pushing of a turbine or electron.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0711]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0711].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0711] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont POWER EXTRACTION TENSOR}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} POWER EXTRACTION TENSOR is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``POWER EXTRACTION TENSOR is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0711].
\par\endgroup
\vfill
\endgroup
\endgroup
