\section*{ID9203: Relation: [sum\_n=0ˆ∞J\_n+ 1/2(kr)eΘintheta]⊗[ConstrainedDipole(theta, Varphi)…}
\paragraph{Metadata.}
PiID: 2210327488921 | RTEID: RTE:P35737.2928:T2.3354 | UUID: 6eb622e3-5bab-5ded-8f3f-a4ba860267e6

\paragraph{Canonical Statement.}
cal Registry Vol. 01 71 Trawin Zero Point Contextus Canonicus 2 TZP CANONICAL REGISTRY – ENTRIES 150–199 Falsifiability / Test Handle: Fit measured absorption spectra to the predicted squareroot form; significant discrepancies would falsify this constraint. 2.0.63 ID 212: Gyromagnetic Bessel Interference Operator Type: Operator Formal Statement: The unified propulsion field is defined by the tensor product of a Besselfunction interference pattern and a gyromagnetic field: F(r,theta,varphi,t) = \$[sum\_\{n=0\}ˆ∞J\_\{n+ 1/2\}(kr)eΘ\{intheta\}]⊗[ConstrainedDipole(theta, varphi) ∗GyroscopicPrecession(omega\_gyrot)].\$ Interpretive Meaning: This operator describes how a rotating array of magnetic dipoles generates a Besseltype interference pattern identical to that required for gravity negation. The product structure implies that the gyromagnetic field and the Bessel pattern are inseparable components of the propulsion field. Dependencies: IDs 200 and 206. Derivable Consequences: When subtracted from

\paragraph{Canonical Equation.}
\[
[sum_{n=0}ˆ∞J_{n+ 1/2}(kr)eΘ{intheta}]⊗[ConstrainedDipole(theta, varphi) ∗GyroscopicPrecession(omega_gyrot)].
\]

\paragraph{Dictionary.}
Relation: [sum\_n=0ˆ∞J\_n+ 1/2(kr)eΘintheta]⊗[ConstrainedDipole(theta, varphi) ∗GyroscopicPrecession(omega\_gyrot)].

\paragraph{Encyclopedia.}
Relation: [sum\_n=0ˆ∞J\_n+ 1/2(kr)eΘintheta]⊗[ConstrainedDipole(theta, Varphi)… is an algebraic definition, written [sum\_n=0ˆ∞J\_n+ 1/2(kr)eΘintheta]⊗[ConstrainedDipole(theta, varphi) ∗GyroscopicPr. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from s, u, m\_n=0, J\_n+ 1/2, k, r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
