\tzpanchor{0698}
\tzpentryheader{0698}{Celestial Gyromagnetic Motion Axiom}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{270bcd46-53a7-579f-8e52-24203ff0529a}}\\
\textbf{PiID} & \tzpcode{3542019956112} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{705}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2679.4232 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.4149 rad}\\
\textbf{TZPID} & \tzpcode{ID0698} & \textbf{Node Dependencies}\quad \tzpidref{0697}\\
\textbf{Registry} & \tzpcode{registry\_id\_0698} & \textbf{Scale}\quad magnetofluid\\
\textbf{LOC Classification} & QC809 magnetohydrodynamics & QC6 fluid and plasma dynamics\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph & Cross-list: astro-ph.SR, gr-qc\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records celestial gyromagnetic motion axiom through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
G_{\sigma}(t) = \frac{1}{\sigma\sqrt{2\pi}} \exp\left( -\frac{t^2}{2\sigma^2} \right).
\]
\[
\delta_{\mathrm{inj}} = \lim_{\sigma\to0}G_{\sigma}(t).
\]
\[
\widehat{\delta}_{\mathrm{inj}}(\omega)=1.
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $G_{\sigma}(t)$: source equation symbol.
    \item $\sigma$: conductivity or coupling coefficient in the source equation.
    \item $\pi$: source equation symbol.
    \item $t$: source equation symbol.
    \item $\delta_{\mathrm{inj}}$: source equation symbol.
    \item $\delta$: point-source delta term that anchors the Green-function response.
    \item $\omega$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0698 generated source Wolfram model *)
ClearAll[K0698, Cr0698, T, R, A, W, I, N];
eq0698$1 = HoldForm[GSigma[t] == (1/sigmaSqrt[2*Pi])*exp[-(t^2/(2*sigma^2))]];
eq0698$2 = HoldForm[DiracDeltaInj == LimitSigma0*GSigma[t]];
eq0698$3 = HoldForm[widehat[DiracDelta]*_*inj*omega == 1];

K0698 = HoldForm[{eq0698$1, eq0698$2, eq0698$3}];

N = "normalized TRAWIN closure object for Celestial Gyromagnetic Motion Axiom";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0698[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0698 = Cr0698[K0698];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Celestial Gyromagnetic Motion Axiom.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0698] Celestial Gyromagnetic Motion Axiom}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Gaussian Approximant.}
\begin{equation}
G_{\sigma}(t)
=
\frac{1}{\sigma\sqrt{2\pi}}
\exp\left(
-\frac{t^2}{2\sigma^2}
\right).
\end{equation}

\paragraph{Delta Limit.}
\begin{equation}
\delta_{\mathrm{inj}}
=
\lim_{\sigma\to0}G_{\sigma}(t).
\end{equation}

\paragraph{Spectral Law.}
\begin{equation}
\widehat{\delta}_{\mathrm{inj}}(\omega)=1.
\end{equation}

\paragraph{Primary Derivation.}
A normalized Gaussian pulse becomes increasingly localized as $\sigma\to0$:

\begin{equation}
G_{\sigma}(t)
=
\frac{1}{\sigma\sqrt{2\pi}}
\exp\left(
-\frac{t^2}{2\sigma^2}
\right).
\end{equation}

In the distributional limit,
\begin{equation}
\delta_{\mathrm{inj}}
=
\lim_{\sigma\to0}G_{\sigma}(t).
\end{equation}

The Fourier transform of the delta distribution is constant:
\begin{equation}
\boxed{
\widehat{\delta}_{\mathrm{inj}}(\omega)=1.
}
\end{equation}

\paragraph{Interpretation.}
A sharply localized injection supplies broad spectral content while preserving local bridge architecture.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Celestial Gyromagnetic Motion Axiom by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
G_{\sigma}(t) = \frac{1}{\sigma\sqrt{2\pi}} \exp\left( -\frac{t^2}{2\sigma^2} \right).
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\delta_{\mathrm{inj}} = \lim_{\sigma\to0}G_{\sigma}(t).
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\widehat{\delta}_{\mathrm{inj}}(\omega)=1.
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0698] Celestial Gyromagnetic Motion Axiom}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Celestial Gyromagnetic Motion Axiom is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} gamma-1. \textbf{Contextual meaning:} The entry reads Celestial Gyromagnetic Motion Axiom as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
A sharply localized injection supplies broad spectral content while preserving local bridge architecture.

\tzpsection{Equation Grounding}
Equation anchors: 10/9 approximately 1.111; 32/27 approximately 1.185; and chi approximately 1.185185. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Planetary-Core Dynamo Replication}: The bold claim that the violent, twisting, boiling plasma trapped inside the tiny metal containment vessel is an exact, literal duplicate of the liquid iron storm currently raging in the center of the Earth.
\item \textbf{Stellar-Flare Ejection Modeling}: The use of the laboratory's sudden, violent magnetic snaps to perfectly understand and predict how the Sun occasionally vomits massive, deadly waves of radiation out into the solar system.
\item \textbf{Galactic-Scale Toplogy Sourcing}: The breathtaking idea that the bizarre, impossible shapes forming in the tiny droplets of liquid metal are the exact same shapes forming in the sprawling, million-light-year-wide arms of a spiral galaxy.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0698]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0698_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0698] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Celestial Gyromagnetic Motion Axiom}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records celestial gyromagnetic motion axiom through the Septenary derivation
layer, using the displayed relations as operational anchors...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Celestial Gyromagnetic Motion Axiom is valid as a formal registry statement when its
source equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that the entry records celestial gyromagnetic motion axiom
through the Septenary derivation layer, using the displayed relations as operational
anchors for the canonical equation chain. A sharply localized injection supplies broad
spectral content while preserving local bridge architecture. ---------------------------
----------------------------------------------------------------------------------------
-----. The CHL validation treats the equation as the formal anchor and the semantic text
as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0698_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
