\section*{ID8926: FISHER INFORMATION METRIC (ACQUISITION) Canonical Statutory Formula: g\_ij(θ)}
\paragraph{Metadata.}
PiID: 7029692348896 | RTEID: RTE:P34661.6403:T0.5631 | UUID: 69a02ac2-4136-5c5c-9c93-c1d5a562286a

\paragraph{Canonical Statement.}
[ID 921] FISHER INFORMATION METRIC (ACQUISITION) Canonical Statutory Formula: \$g\_\{ij\}(\textbackslash{}theta) = -E[\textbackslash{}frac\{\textbackslash{}partial\textasciicircum{}2\}\{\textbackslash{}partial \textbackslash{}theta\_i \textbackslash{}partial \textbackslash{}theta\_j\} \textbackslash{}log p(x|\textbackslash{}theta)]\$ Formal Technical Dissertation: The metric used in the data acquisition interface. It quantifies the amount of information the observable random variable carries about the unknown parameter \$\textbackslash{}theta\$, creating a Riemannian geometry of probability distributions [18]. Source: [18]

\paragraph{Canonical Equation.}
\[
g_{ij}(\theta) = -E[\frac{\partial^2}{\partial \theta_i \partial \theta_j} \log p(x|\theta)]
\]

\paragraph{Dictionary.}
FISHER INFORMATION METRIC (ACQUISITION) Canonical Statutory Formula: \$g\_ij( ) = -E[ \textasciicircum{}2 \_i \_j p(x )]\$ Formal Technical Dissertation: The metric used in the data acquisition interface.

\paragraph{Encyclopedia.}
FISHER INFORMATION METRIC (ACQUISITION) Canonical Statutory Formula: g\_ij(θ) is a variational / legendre derivative, written g\_ij(θ) = -E[(∂\textasciicircum{}2)/(∂ θ\_i ∂ θ\_j) log p(x|θ)]. It arises from a variational or Legendre procedure, defining conjugate quantities or stationarity conditions. It is built from ∂, θ, E, j, p, x, defining g\_ij(θ). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
