\section*{ID8539: HELICAL PHASE SPACE PROJECTION Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 2655165827658 | RTEID: RTE:P33158.8333:T4.3701 | UUID: 8a10721d-7914-5a0b-88cc-b2a1f298f751

\paragraph{Canonical Statement.}
[ID 1125] HELICAL PHASE SPACE PROJECTION Canonical Statutory Formula: \$P\_\{helix\} \textbackslash{}in [16\textbackslash{}mathring\{A\}, 24\textbackslash{}mathring\{A\}] \textbackslash{}times [0, 2\textbackslash{}pi n] \textbackslash{}times [0, 3.4\textbackslash{}mathring\{A\} \textbackslash{}cdot 10\textasciicircum{}9]\$ Formal Technical Dissertation: Models the phase space volume of the DNA substrate. It projects the genome into cylindrical coordinates, identifying the active "groove dimensions" (Major/Minor) where quantum coherence can be maintained against thermal noise. Source: [6]

\paragraph{Canonical Equation.}
\[
P_{helix} \in [16\mathring{A}, 24\mathring{A}] \times [0, 2\pi n] \times [0, 3.4\mathring{A} \cdot 10^9]
\]

\paragraph{Dictionary.}
HELICAL PHASE SPACE PROJECTION Canonical Statutory Formula: \$P\_helix [16 A, 24 A] [0, 2 n] [0, 3.4 A 10\textasciicircum{}9]\$ Formal Technical Dissertation: Models the phase space volume of the DNA substrate.

\paragraph{Encyclopedia.}
HELICAL PHASE SPACE PROJECTION Canonical Statutory Formula is a symbolic expression, written P\_helix in [16mathringA, 24mathringA] × [0, 2π n] × [0, 3.4mathringA · 10\textasciicircum{}9]. It introduces a symbol or relation used elsewhere in the framework. It is built from π, P\_helix, A, n. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
