\section*{ID9575: Clarifying Note on the Quantum Tunneling Term: V\_barrier(r,θ,φ)}
\paragraph{Metadata.}
PiID: 0507643100638 | RTEID: RTE:P37181.8514:T4.7156 | UUID: 3ab402b5-3042-564c-8c06-a6917fc6f4bc

\paragraph{Canonical Statement.}
The quantum tunneling contribution in the RNA→DNA transition captures the energetic and geometric asymmetry arising from the presence of the 2\$\textasciicircum{}\{\textbackslash{}prime\}\$-hydroxyl group in RNA. This functional group introduces a torsional barrier in the ribose ring, which is effectively modeled by a potential \$V\_\{\textbackslash{}mathrm\{barrier\}\}(r,\textbackslash{}theta,\textbackslash{}phi)\$. The Laplacian term \$-\textbackslash{}frac\{\textbackslash{}hbar\textasciicircum{}\{2\}\}\{2m\_\{\textbackslash{}mathrm\{eff\}\}\}\textbackslash{}nabla\textasciicircum{}\{2\}\$ describes the quantum delocalization of the ribose configuration along internal coordinates.

\paragraph{Canonical Equation.}
\[
V_{\mathrm{barrier}}(r,\theta,\phi)
\]

\paragraph{Dictionary.}
The quantum tunneling contribution in the RNA→DNA transition captures the energetic and geometric asymmetry arising from the presence of the 2\textasciicircum{}prime-hydroxyl group in RNA [ID9575]

\paragraph{Encyclopedia.}
Clarifying Note on the Quantum Tunneling Term: V\_barrier(r,θ,φ) is a symbolic expression, written V\_barrier(r,θ,φ). It introduces a symbol or relation used elsewhere in the framework. It is built from θ, φ, V\_, r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
