\section*{ID9344: Relation: =⇒ Hol(𝛾)→Mmono}
\paragraph{Metadata.}
PiID: 1375560037279 | RTEID: RTE:P36284.8271:T3.2376 | UUID: c63898be-bb8a-597d-b09c-5ee666ef625c

\paragraph{Canonical Statement.}
included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0161], [ID 0162] Node registry\_id\_0163 Support Titles Total Connection; Holonomy Operator; TZP Monodromy Limit Test Handle If transport around TZP-linking loops does not produce a coherent holonomy limit, the connection-and-holonomy statement fails. Canonical Equation Links \$Ωtot= ∑\$ 𝑖 \$𝑃𝑖⊗𝐴𝑖\$ Hol(𝛾)=P exp \$(∮\$ 𝛾 \$Ωtot\$ ) \$𝛾→𝑆1\$ TZP \$=⇒ Hol(𝛾)→Mmono\$ [ID 0164] Quantum Metric from Hamiltonian TZPID ID0164 UUID 5c3cb89c-b2df-5c2b-9867-5ede89c30d54 Type Metric Construction Scale state-space geometry of TRAWIN Hamiltonian sectors LOC Classification Working routing: QA927 quantum geometry; QC174 quantum Hamiltonians arXiv Classification Primary: quant-ph Cross-list: math-ph, hep-th Canonical Statement The TRAWIN Hamiltonian sectors induce a quantu

\paragraph{Canonical Equation.}
\[
=⇒ Hol(𝛾)→Mmono
\]

\paragraph{Dictionary.}
Relation: =⇒ Hol(𝛾)→Mmono — =⇒ Hol(𝛾)→Mmono

\paragraph{Encyclopedia.}
Relation: =⇒ Hol(𝛾)→Mmono is an algebraic definition, written =⇒ Hol(𝛾)→Mmono. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from H, o, l, M, m, n. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
