\tzpanchor{0467}
\tzpentryheader{0467}{Mutual Information Functional}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f4209f65-6b93-5abc-b093-2a8d687eb238}}\\
\textbf{PiID} & \tzpcode{7351885752724} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{474}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1797.9318 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.9624 rad}\\
\textbf{TZPID} & \tzpcode{ID0467} & \textbf{Node Dependencies}\quad \tzpidref{0466}\\
\textbf{Registry} & \tzpcode{registry\_id\_0467} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Aggregate Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 467 formalizes the mutual information functional for the tripartite system. This equation governs the degree of correlation between temporal, atemporal, and mediator channels. Maintaining this functional is essential for thermodynamic consistency. Entropy Balance: Measures von Neumann entropy across all channels to ensure system closure. Synergy Mapping: Identifies emergent information integration that exceeds individual channel parts.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{I}(A;B;C) = \sum S(X_{\mathrm{i}}) - S(\text{total})
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{I}(A;B;C)$: source equation symbol.
    \item $A$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $C$: speed of light or relativistic conversion factor.
    \item $S$: source equation symbol.
    \item $X_{\mathrm{i}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0467 generated source Wolfram model *)
ClearAll[K0467, Cr0467, T, R, A, W, I, N];
eq0467$1 = HoldForm[$I[A; B; C] == Sum*S[XI] - S[]*$];

K0467 = HoldForm[{eq0467$1}];

N = "normalized TRAWIN closure object for Mutual Information Functional";
I = "Mutual Information Functional integration/comparison layer";
W = "Mutual Information Functional wave or operator carrier";
A = "Mutual Information Functional admissible action/amplitude condition";
R = "Mutual Information Functional rotation/curl preservation layer";
T = "Mutual Information Functional local source condition";

Cr0467[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0467 = Cr0467[K0467];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Mutual Information Functional local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Mutual Information Functional rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Mutual Information Functional admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Mutual Information Functional wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Mutual Information Functional integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Mutual Information Functional.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0467] Mutual Information Functional}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Gamma[\phi] = W[J] - \int J\phi.
\end{equation}

\paragraph{Primary Derivation.}
Effective action is Legendre transform of generating functional.

Thus:
\begin{equation}
\boxed{
\Gamma[\phi] = W[J] - \int J\phi.
}
\end{equation}

\paragraph{Interpretation.}
Encodes full quantum corrections.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Mutual Information Functional by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{I}(A;B;C) = \sum S(X_{\mathrm{i}}) - S(\text{total})
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0467] Mutual Information Functional}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Mutual Information Functional is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 467 formalizes the mutual information functional for the tripartite system. This equation governs the degree of correlation between temporal, atemporal, and mediator channels. Maintaining this functional is essential for thermodynamic consistency. Entropy Balance: Measures von Neumann entropy across all channels to ensure system closure. Synergy Mapping: Identifies emergent information integration that exceeds individual channel parts.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{I}(A;B;C) = \sum S(X_{\mathrm{i}}) - S(\text{total})
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 467 formalizes the mutual information functional for the tripartite system. This equation governs the degree of correlation between temporal, atemporal, and mediator channels. Maintaining this functional is essential for thermodynamic consistency. Entropy Balance: Measures von Neumann entropy across all channels to ensure system closure. Synergy Mapping: Identifies emergent information integration that exceeds individual channel parts.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Mutual Information Functional by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Mutual Information Functional; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0467]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0467].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0467] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Mutual Information Functional}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} mathcal\textbackslash{}(A;B;C) = sum S(X\textbackslash{}\_i) - S(text\textbackslash{})

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``MUTUAL INFORMATION FUNCTIONAL is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0467].
\par\endgroup
\vfill
\endgroup
\endgroup
