\section*{ID9408: Definition of 𝐶, IT}
\paragraph{Metadata.}
PiID: 6979396122571 | RTEID: RTE:P36533.3533:T3.6471 | UUID: f6d5cc43-f5c7-59b8-a5c3-85a65902109b

\paragraph{Canonical Statement.}
malized, and linked forward into the surrounding registry pages. T = 𝐴 \$∪\$ 𝐵 \$∪\$ 𝐶 IT = 𝐼 (𝐴 : 𝐵) + 𝐼 (𝐵 : 𝐶) + 𝐼 (𝐶 : 𝐴) Wolfram Form 𝔚TZP (K0350) \$↦−→ 〈 ΩT, ΨT,\$ 𝜌vac \$〉\$ K0350 := HoldForm(T0350) AdmissibleTZP (K0350) \$⇐⇒𝔚TZP\$ (K0350) . \$∅\$ Wolfram register: canonical symbol lift Title lift: Tripartite Information Architecture Symbol key: \$ΩT:\$ Trawinistic boundary curvature \$ΨT:\$ Trawinistic wavefunction 𝜌vac: vacuum energy density TRAWIN Normalization NormalizeTRAWIN (T = 𝐴 \$∪\$ 𝐵 \$∪\$ 𝐶, IT = 𝐼 (𝐴 : 𝐵) + 𝐼 (𝐵 : 𝐶) + 𝐼 (𝐶 : 𝐴), \$ΔT ≥\$ 0) T: Variation Law is localized within the field theory and action principles arc of the directory. R: Support Relation preserves the operative relation that tripartite information architecture requires. A: Closure Relation fixes the admissible closure condition for the entry. W: Tripartite Information Architecture is rendered as a reusable operator-level statement. I: The informational con

\paragraph{Canonical Equation.}
\[
𝐶, IT = 𝐼 (𝐴 : 𝐵) + 𝐼 (𝐵 : 𝐶) + 𝐼 (𝐶 : 𝐴),
\]

\paragraph{Dictionary.}
Definition of 𝐶, IT — 𝐶, IT = 𝐼 (𝐴 : 𝐵) + 𝐼 (𝐵 : 𝐶) + 𝐼 (𝐶 : 𝐴)

\paragraph{Encyclopedia.}
Definition of 𝐶, IT is an algebraic definition, written 𝐶, IT = 𝐼 (𝐴 : 𝐵) + 𝐼 (𝐵 : 𝐶) + 𝐼 (𝐶 : 𝐴). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
