\tzpanchor{0436}
\tzpentryheader{0436}{London Penetration Depth Tuning}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{28a95264-9e83-5671-aa6a-d13dab1eb394}}\\
\textbf{PiID} & \tzpcode{1179310511854} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{443}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1693.0848 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.7897 rad}\\
\textbf{TZPID} & \tzpcode{ID0436} & \textbf{Node Dependencies}\quad \tzpidref{0435}\\
\textbf{Registry} & \tzpcode{registry\_id\_0436} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 436 establishes the shielding parameters for the superconducting regions of the reactor. Magnetic fields penetrate the superconductor only to the London depth lambdaL, creating regions of high flux density at the interface. The ratio = lambdaL / is tuned to ensure Type II behavior, which permits the flux vortex penetration required for the Energy Channel's operation. Screening Efficiency: Precise control of electron density ns prevents field leakage into the information processing registers. Vortex Arrangement: A field of 0.1 Tesla allows for stable flux quantization without quenching the superconducting state.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\lambda_{\mathrm{L}} = \cdots
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\lambda_{\mathrm{L}}$: source equation symbol.
    \item $\mathcal{K}_{0436}$: canonical registry object for entry ID 0436.
    \item $\cdot s$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0436 generated source Wolfram model *)
ClearAll[K0436, Cr0436, T, R, A, W, I, N];
eq0436$1 = HoldForm[lambdaL == Ellipsis];

K0436 = HoldForm[{eq0436$1}];

N = "normalized TRAWIN closure object for London Penetration Depth Tuning";
I = "London Penetration Depth Tuning integration/comparison layer";
W = "London Penetration Depth Tuning wave or operator carrier";
A = "London Penetration Depth Tuning admissible action/amplitude condition";
R = "London Penetration Depth Tuning rotation/curl preservation layer";
T = "London Penetration Depth Tuning local source condition";

Cr0436[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0436 = Cr0436[K0436];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ London Penetration Depth Tuning local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ London Penetration Depth Tuning rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ London Penetration Depth Tuning admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ London Penetration Depth Tuning wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ London Penetration Depth Tuning integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for London Penetration Depth Tuning.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0436] London Penetration Depth Tuning}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\mathcal{V}_T\phi_{\omega}
=
\sqrt{
\frac{\hbar\omega}{2}
}
\,\phi_{\omega}
\coth\left(
\frac{\omega}{2\omega_0}
\right).
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi_{\omega}$ be a field mode of frequency $\omega$.  
The zero-point amplitude of a harmonic mode is proportional to:

\begin{equation}
\sqrt{\frac{\hbar\omega}{2}} .
\end{equation}

In the TZP setting, this amplitude is modulated by a spectral thermal-like factor:

\begin{equation}
\coth\left(
\frac{\omega}{2\omega_0}
\right),
\end{equation}

where $\omega_0$ is the characteristic frequency determined by the spectral density scale.

Acting on the mode $\phi_{\omega}$ gives:

\begin{equation}
\boxed{
\mathcal{V}_T\phi_{\omega}
=
\sqrt{
\frac{\hbar\omega}{2}
}
\,\phi_{\omega}
\coth\left(
\frac{\omega}{2\omega_0}
\right).
}
\end{equation}

\paragraph{Interpretation.}
The vacuum fluctuation operator assigns each mode a zero-point amplitude corrected by the TZP spectral scale.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors London Penetration Depth Tuning by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\lambda_{\mathrm{L}} = \cdots
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0436] London Penetration Depth Tuning}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
London Penetration Depth Tuning is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 436 establishes the shielding parameters for the superconducting regions of the reactor. Magnetic fields penetrate the superconductor only to the London depth lambdaL, creating regions of high flux density at the interface. The ratio = lambdaL / is tuned to ensure Type II behavior, which permits the flux vortex penetration required for the Energy Channel's operation. Screening Efficiency: Precise control of electron density ns prevents field leakage into the information processing registers. Vortex Arrangement: A field of 0.1 Tesla allows for stable flux quantization without quenching the superconducting state.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\lambda_{\mathrm{L}} = \cdots
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 436 establishes the shielding parameters for the superconducting regions of the reactor. Magnetic fields penetrate the superconductor only to the London depth lambdaL, creating regions of high flux density at the interface. The ratio = lambdaL / is tuned to ensure Type II behavior, which permits the flux vortex penetration required for the Energy Channel's operation. Screening Efficiency: Precise control of electron density ns prevents field leakage into the information processing registers. Vortex Arrangement: A field of 0.1 Tesla allows for stable flux quantization without quenching the superconducting state.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors London Penetration Depth Tuning by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
London Penetration Depth Tuning; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0436]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0436].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0436] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont London Penetration Depth Tuning}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} lambda\textbackslash{}\_L = sqrt\textbackslash{}\_e\textbackslash{}\textbackslash{}\_0 n\textbackslash{}\_s e\textasciicircum{}2\textbackslash{}\textbackslash{} otimes kappa\textbackslash{}\_-L\textbackslash{}\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``LONDON PENETRATION DEPTH TUNING is valid as a formal dynamical law when the Hamiltonian
or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0436].
\par\endgroup
\vfill
\endgroup
\endgroup
