\tzpanchor{0067}
\tzpentryheader{0067}{Topological Quantum States}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{3271f078-92d1-5f36-a34f-2df857c2231f}}\\
\textbf{PiID} & \tzpcode{1640628620899} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{74}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{260.1759 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.4287 rad}\\
\textbf{TZPID} & \tzpcode{ID0067} & \textbf{Node Dependencies}\quad \tzpidref{0065}\\
\textbf{Registry} & \tzpcode{registry\_id\_0067} & \textbf{Scale}\quad nonlocal quantum order\\
\textbf{LOC Classification} & QC174 topological phases & QA612 nonlocal invariants\\
\textbf{arXiv Classification} & Primary: cond-mat.str-el \quad Cross-list: quant-ph, hep-th & \\
\textbf{Primary Support} & Ground-State Degeneracy & Nonlocal Wilson Observable\\
\textbf{Closure Support} & Topological Stability & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A topological quantum state is defined by a ground state degeneracy and excitations that depend solely on global properties of the Trawinistic manifold; its properties are invariant under local perturbations, and it is characterised by non-local order parameters like Wilson loops.

\tzpsection{Canonical Equation}
\[
g_{\mathrm{gs}} > 1
\]
\[
W(C) = \left\langle \psi \middle| \mathcal{P}\exp\!\oint_{C} A \middle| \psi \right\rangle
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $g_{\mathrm{gs}}$: source equation symbol.
    \item $W$: source equation symbol.
    \item $C$: speed of light or relativistic conversion factor.
    \item $\mathcal{P}$: source equation symbol.
    \item $A$: source equation symbol.
    \item $\delta_{\mathrm{local}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0067 generated source Wolfram model *)
ClearAll[K0067, Cr0067, T, R, A, W, I, N];
eq0067$1 = HoldForm[gGs > 1];
eq0067$2 = HoldForm[W[C] == Inner[psi, dleAbs[Pexp*ContourIntegralC*A, dle]*psi]];
eq0067$3 = HoldForm[DiracDeltaLocal*W[C] == 0];

K0067 = HoldForm[{eq0067$1, eq0067$2, eq0067$3}];

N = "normalized TRAWIN closure object for Topological Quantum States";
I = "Topological Stability integration/comparison layer";
W = "Nonlocal Wilson Observable wave or operator carrier";
A = "Ground-State Degeneracy admissible action/amplitude condition";
R = "Nonlocal Wilson Observable rotation/curl preservation layer";
T = "Ground-State Degeneracy local source condition";

Cr0067[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0067 = Cr0067[K0067];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Ground-State Degeneracy local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Nonlocal Wilson Observable rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Ground-State Degeneracy admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Nonlocal Wilson Observable wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Stability integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Topological Quantum States.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0067] Topological Quantum States}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Gamma[\phi] = W[J] - \int J\phi.
\end{equation}

\paragraph{Primary Derivation.}
Effective action is Legendre transform of generating functional.

Thus:
\begin{equation}
\boxed{
\Gamma[\phi] = W[J] - \int J\phi.
}
\end{equation}

\paragraph{Interpretation.}
Encodes full quantum corrections.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Topological Quantum States by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Ground-State Degeneracy}\par
\[
g_{\mathrm{gs}} > 1
\]
\noindent This signals that the phase has nontrivial global structure.\par
\noindent\textbf{2. Nonlocal Wilson Observable}\par
\[
W(C) = \left\langle \psi \middle| \mathcal{P}\exp\!\oint_{C} A \middle| \psi \right\rangle
\]
\noindent This probes the state using a closed nonlocal contour.\par
\noindent\textbf{3. Topological Stability}\par
\[
\delta_{\mathrm{local}} W(C) \approx 0
\]
\noindent This closes the progression by expressing robustness against local perturbations.\par

\clearpage
\noindent\textbf{[ID 0067] Topological Quantum States}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Topological Quantum States is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A topological quantum state is defined by a ground state degeneracy and excitations that depend solely on global properties of the Trawinistic manifold; its properties are invariant under local perturbations, and it is characterised by non-local order parameters like Wilson loops. \textbf{Contextual meaning:} The entry reads Topological Quantum States as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry turns entanglement structure into a topological phase language. It creates a clean route from many-body correlation patterns to nonlocal quantum order and protected degeneracy. \textbf{Lemma support:} Ground-State Degeneracy; Nonlocal Wilson Observable; Topological Stability.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Encodes full quantum corrections.

\tzpsection{Equation Grounding}
Equation anchors: A topological quantum state is defined by a ground state degeneracy and excitations that depend solely on global properties of the Trawinistic manifold; its properties are invariant under local perturbations, and it is characterised by non-local order parameters like Wilson loops. A topological quantum state is defined by a ground state degeneracy and excitations that depend solely on global properties of the Trawinistic manifold; its properties are invariant under local perturbations, and it is characterised by non-local order parameters like Wilson loops.

\tzpsection{Interpretive Role}
This entry turns entanglement structure into a topological phase language. It creates a clean route from many-body correlation patterns to nonlocal quantum order and protected degeneracy.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Shape-Preserving State-Level States}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{Shape-Preserving State-Level Quantum-State Analogue}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{State-Level Terminology}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0067]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0067_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0067] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Topological Quantum States}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a topological quantum state is defined by a ground state degeneracy and excitations that
depend solely on global properties of the Trawinistic mani...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Topological Quantum States is valid as a synchronization criterion under the coupling
conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0067_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
