\tzpanchor{0327}
\tzpentryheader{0327}{Quantum Vortex Circulation Quantization}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7b5b93d1-949b-5f0f-8521-d5bfe6ba0022}}\\
\textbf{PiID} & \tzpcode{9209628292540} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{334}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1269.8136 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.0923 rad}\\
\textbf{TZPID} & \tzpcode{ID0327} & \textbf{Node Dependencies}\quad \tzpidref{0326}\\
\textbf{Registry} & \tzpcode{registry\_id\_0327} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Macroscopic Wavefunction & Circulation Integral\\
\textbf{Closure Support} & Quantized Circulation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In a superfluid or Bose--Einstein condensate, the macroscopic wavefunction Psi(r,t)=n(r,t)eiphi(r,t)Psi(r,t) = sqrt/\{n(r,t)/\} e/\textasciicircum{}\{\}/\{iphi(r,t)/\}Psi(r,t)=n(r,t)eiphi(r,t) exhibits circulation quantization: ointvcdotdell=2pihbarn/mtextbackslash oint v * dell = 2textbackslash pi hbar n/mointvcdotdell=2pihbarn/m, where nnn is the integer winding number and mmm the mass of the constituent particle.

\tzpsection{Canonical Equation}
\[
\Psi(\mathbf{r},t)=\sqrt{n(\mathbf{r},t)}e^{i\phi(\mathbf{r},t)}
\]
\[
\oint \mathbf{v}\cdot d\boldsymbol{\ell}=\frac{h}{m}N
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Psi$: wavefunction or state carrier for the entry equation.
    \item $t$: source equation symbol.
    \item $n$: integer mode index.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $v$: velocity, flow speed, or auxiliary comparison variable.
    \item $Z$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0327 generated source Wolfram model *)
ClearAll[K0327, Cr0327, T, R, A, W, I, N];
eq0327$1 = HoldForm[Psi[r, t] == sqrtTuple[n[r, t]]*eIphirt];
eq0327$2 = HoldForm[ContourIntegral*v*dboldsymbol[ell] == (h/m)*N];
eq0327$3 = HoldForm[Element[N, Z]];

K0327 = HoldForm[{eq0327$1, eq0327$2, eq0327$3}];

N = "normalized TRAWIN closure object for Quantum Vortex Circulation Quantization";
I = "Quantized Circulation integration/comparison layer";
W = "Circulation Integral wave or operator carrier";
A = "Macroscopic Wavefunction admissible action/amplitude condition";
R = "Circulation Integral rotation/curl preservation layer";
T = "Macroscopic Wavefunction local source condition";

Cr0327[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0327 = Cr0327[K0327];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Macroscopic Wavefunction local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Circulation Integral rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Macroscopic Wavefunction admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Circulation Integral wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Quantized Circulation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum Vortex Circulation Quantization.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0327] Quantum Vortex Circulation Quantization}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}

Geometry near the zero point exhibits non‑commutative coordinates due to intrinsic quantum deformation.

\paragraph{Primary Derivation.}

In a non‑commutative extension of the Trawin manifold, coordinate operators $x^a$ satisfy the relation

\begin{equation}
[ x^a , x^b ] = i\,\theta^{ab},
\end{equation}

where $\theta^{ab}$ is a constant antisymmetric matrix encoding the quantum area element.  Ordinary products of functions are replaced by star products, and derivatives are implemented via commutators.

\paragraph{Interpretation.}

Non‑commutativity introduces a minimal area scale near the zero point.  Coordinate uncertainty becomes intrinsic rather than an artefact of measurement.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum Vortex Circulation Quantization by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Macroscopic Wavefunction}\par
\[
\Psi(\mathbf{r},t)=\sqrt{n(\mathbf{r},t)}e^{i\phi(\mathbf{r},t)}
\]
\noindent This fixes the macroscopic condensate wavefunction that carries the quantum vortex phase.\par
\noindent\textbf{2. Circulation Integral}\par
\[
\oint \mathbf{v}\cdot d\boldsymbol{\ell}=\frac{h}{m}N
\]
\noindent This identifies the closed-loop circulation integral around the vortex core.\par
\noindent\textbf{3. Quantized Circulation}\par
\[
N\in\mathbb{Z}
\]
\noindent This closes the entry by stating the quantized circulation carried by the integer winding number.\par

\clearpage
\noindent\textbf{[ID 0327] Quantum Vortex Circulation Quantization}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum Vortex Circulation Quantization is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} In a superfluid or Bose--Einstein condensate, the macroscopic wavefunction Psi(r,t)=n(r,t)eiphi(r,t)Psi(r,t) = sqrt/ n(r,t)/ e/ to the power / iphi(r,t)/ Psi(r,t)=n(r,t)eiphi(r,t) exhibits circulation quantization: ointvcdotdell=2pihbarn/mtextbackslash oint v * dell = 2textbackslash pi hbar n/mointvcdotdell=2pihbarn/m, where nnn is the integer winding number and mmm the mass of the constituent particle. \textbf{Contextual meaning:} The entry reads Quantum Vortex Circulation Quantization as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states quantum-vortex circulation through the actual condensate and loop integral laws instead of unrelated Fibonacci fragments. \textbf{Lemma support:} Macroscopic Wavefunction; Circulation Integral; Quantized Circulation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Non-commutativity introduces a minimal area scale near the zero point. Coordinate uncertainty becomes intrinsic rather than an artefact of measurement.

\tzpsection{Equation Grounding}
Equation anchors: (r,t)=n(r,t)ei (r,t) exhibits circulation quantization:  v dl=2;  n/mtextbackslash oint v textbackslash cdot dtextbackslash ell = 2textbackslash pi textbackslash hbar n/m v dl=2; and  n/m, where nnn is the integer winding number and mmm the mass of the constituent particle. Interpretive Meaning: The circulation of the velocity field around a closed loop in a superfluid is quantized in units of 2. Proof route: show that single-valuedness of the condensate wavefunction forces the stated quantized circulation law. Formalization route: prove that the circulation integral evaluates to the stated integer multiple of h/m.

\tzpsection{Interpretive Role}
The entry now states quantum-vortex circulation through the actual condensate and loop integral laws instead of unrelated Fibonacci fragments.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Discrete Velocity Circulation}: The strict limitation of fluid flow around a topological defect to integer multiples of Planck's constant divided by mass.
\item \textbf{Single-Valued Phase Constraint}: The quantum mechanical requirement forcing the macroscopic wavefunction to perfectly reconnect after a full 360-degree rotation.
\item \textbf{Topological Defect Core Dynamics}: The singularity behavior at the exact center of a vortex where the fluid density drops entirely to zero.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0327]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0327_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0327] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum Vortex Circulation Quantization}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in a superfluid or Bose--Einstein condensate, the macroscopic wavefunction
Psi(r,t)=n(r,t)eiphi(r,t)Psi(r,t) = sqrt/\textbackslash{}n(r,t)/\textbackslash{} e/\textasciicircum{}\textbackslash{}\textbackslash{}/\textbackslash{}iphi(r,t)/\textbackslash{}Psi...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum Vortex Circulation Quantization is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0327_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
