\section*{ID9447: Definition of Hsystem}
\paragraph{Metadata.}
PiID: 5812314593571 | RTEID: RTE:P36684.7990:T3.8966 | UUID: 68977822-8796-5a24-8bbf-7f8baed13f0f

\paragraph{Canonical Statement.}
for [ID 0476] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0475], [ID 0400] Node registry\_id\_0476 Support Titles Variation Law; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links \$Hsystem=Htemporal⊗Hatemporal⊗Hmediating\$ Jout=· · · Aadm(Jout )=· · · [ID 0477] BIOLOGICAL TEMPERATURE RESILIENCE TZPID ID0477 UUID d34fa166-ed93-5940-8954-8b4d1601574e Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops biological temperature resilie

\paragraph{Canonical Equation.}
\[
Hsystem=Htemporal⊗Hatemporal⊗Hmediating
\]

\paragraph{Dictionary.}
Definition of Hsystem — Hsystem=Htemporal⊗Hatemporal⊗Hmediating

\paragraph{Encyclopedia.}
Definition of Hsystem is an algebraic definition, written Hsystem=Htemporal⊗Hatemporal⊗Hmediating. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from H, m, p, o, r, a, defining Hsystem. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
