\tzpanchor{0389}
\tzpentryheader{0389}{Hybrid Eigenmode Spectrum}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{13d6e6fc-2371-5700-b926-f8d5f743cf34}}\\
\textbf{PiID} & \tzpcode{1941511609433} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{396}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1510.5734 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.4890 rad}\\
\textbf{TZPID} & \tzpcode{ID0389} & \textbf{Node Dependencies}\quad \tzpidref{0388}\\
\textbf{Registry} & \tzpcode{registry\_id\_0389} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Hybrid Eigenproblem & Spectral Branches\\
\textbf{Closure Support} & Mode Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The coupled gyro--tunnel--photon system satisfies an eigenvalue problem whose solutions yield three hybrid modes: a super-rotation mode primarily gyroscopic; a quantum--magnetic oscillation mode mixing rotation and tunnelling; and a photon-assisted tunnelling mode. The frequencies depend on the individual mode frequencies and coupling constants.

\tzpsection{Canonical Equation}
\[
\mathcal{L}\psi=\omega\psi
\]
\[
\omega_{\pm}=\frac{\omega_a+\omega_b}{2}\pm\sqrt{\left(\frac{\omega_a-\omega_b}{2}\right)^2+g^2}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{L}$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
    \item $\omega_{\pm}$: angular frequency term in the source equation.
    \item $\omega_a$: angular frequency term in the source equation.
    \item $\omega_b$: angular frequency term in the source equation.
    \item $a_{\pm}$: source equation symbol.
    \item $b_{\pm}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0389 generated source Wolfram model *)
ClearAll[K0389, Cr0389, T, R, A, W, I, N];
eq0389$1 = HoldForm[Lpsi == omegapsi];
eq0389$2 = HoldForm[omegaPlusMinus == ((omegaA + omegaB)/2)*PlusMinusSqrt[((omegaA - omegaB)/2)^2 + g^2]];
eq0389$3 = HoldForm[psiPlusMinus == aPlusMinuspsiA + bPlusMinuspsiB];

K0389 = HoldForm[{eq0389$1, eq0389$2, eq0389$3}];

N = "normalized TRAWIN closure object for Hybrid Eigenmode Spectrum";
I = "Mode Closure integration/comparison layer";
W = "Spectral Branches wave or operator carrier";
A = "Hybrid Eigenproblem admissible action/amplitude condition";
R = "Spectral Branches rotation/curl preservation layer";
T = "Hybrid Eigenproblem local source condition";

Cr0389[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0389 = Cr0389[K0389];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Hybrid Eigenproblem local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Spectral Branches rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Hybrid Eigenproblem admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Spectral Branches wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Mode Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Hybrid Eigenmode Spectrum.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0389] Hybrid Eigenmode Spectrum}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Scale-Translation Functor.}
\begin{equation}
F:\mathrm{LabGyro}\longrightarrow\mathrm{AstroRot}.
\end{equation}

\paragraph{Functorial Composition Law.}
\begin{equation}
F(g\circ f)
=
F(g)\circ F(f).
\end{equation}

\paragraph{Natural Equivalence Witness.}
\begin{equation}
\eta:F\Rightarrow G .
\end{equation}

\paragraph{Primary Derivation.}
Let $\mathrm{LabGyro}$ be a category of laboratory gyromagnetic systems and $\mathrm{AstroRot}$ a category of astrophysical rotating systems.

A scale-translation functor assigns:
\begin{equation}
F:\mathrm{LabGyro}\to\mathrm{AstroRot}.
\end{equation}

To preserve dynamical structure, it must preserve composition:
\begin{equation}
F(g\circ f)=F(g)\circ F(f).
\end{equation}

If two such translations $F$ and $G$ encode the same cross-scale content, a natural transformation witnesses their equivalence:
\begin{equation}
\boxed{
\eta:F\Rightarrow G .
}
\end{equation}

\paragraph{Interpretation.}
FractalNodes supply a categorical bridge between laboratory gyromagnetic behavior and astrophysical rotating systems.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Hybrid Eigenmode Spectrum by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Hybrid Eigenproblem}\par
\[
\mathcal{L}\psi=\omega\psi
\]
\noindent This fixes the hybrid eigenvalue problem governing the coupled mode carrier.\par
\noindent\textbf{2. Spectral Branches}\par
\[
\omega_{\pm}=\frac{\omega_a+\omega_b}{2}\pm\sqrt{\left(\frac{\omega_a-\omega_b}{2}\right)^2+g^2}
\]
\noindent This resolves the split spectral branches produced by the hybrid coupling.\par
\noindent\textbf{3. Mode Closure}\par
\[
\psi_{\pm}=a_{\pm}\psi_a+b_{\pm}\psi_b
\]
\noindent This closes the entry by imposing orthonormal closure on the admissible hybrid eigenmodes.\par

\clearpage
\noindent\textbf{[ID 0389] Hybrid Eigenmode Spectrum}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Hybrid Eigenmode Spectrum is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The coupled gyro--tunnel--photon system satisfies an eigenvalue problem whose solutions yield three hybrid modes: a super-rotation mode primarily gyroscopic; a quantum--magnetic oscillation mode mixing rotation and tunnelling; and a photon-assisted tunnelling mode. The frequencies depend on the individual mode frequencies and coupling constants. \textbf{Contextual meaning:} The entry reads Hybrid Eigenmode Spectrum as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states the hybrid mode spectrum directly, which makes the resonance closure mathematically legible on the page. \textbf{Lemma support:} Hybrid Eigenproblem; Spectral Branches; Mode Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
FractalNodes supply a categorical bridge between laboratory gyromagnetic behavior and astrophysical rotating systems.

\tzpsection{Equation Grounding}
Equation anchors: det (H sub hyb -omega I)=0; omega sub pm =ratio omega sub a+omega sub b 2 pmsqrt (ratio omega sub a-omega sub b 2 ) to the power 2+g to the power 2; and langle psi sub m,psi sub n=delta sub mn. Proof route: show that the coupled hybrid operator resolves into the stated split spectral branches and orthonormal eigenmodes. Formalization route: prove that the stated eigenvalue equation yields the resolved hybrid spectrum under admissible coupling.

\tzpsection{Interpretive Role}
The entry now states the hybrid mode spectrum directly, which makes the resonance closure mathematically legible on the page.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Avoided-Crossing Level Splitting}: The phenomenon where two interacting wave systems that should have the exact same frequency push each other apart into a high and low mode.
\item \textbf{Coupled-Oscillator Diagonalization}: The mathematical trick used to untangle the messy, interacting equations into two clean, independent, and easily solvable vibrations.
\item \textbf{Superposed State Recombination}: The final step of describing the actual physical movement of the system as a mix of the two newly discovered independent modes.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0389]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0389_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0389] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Hybrid Eigenmode Spectrum}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the coupled gyro--tunnel--photon system satisfies an eigenvalue problem whose solutions
yield three hybrid modes: a super-rotation mode primarily g...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Hybrid Eigenmode Spectrum is valid as a synchronization criterion under the coupling
conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0389_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
