\tzpanchor{0348}
\tzpentryheader{0348}{Quantum Tag Injection and Entanglement Tracking Protocol}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{dedb4d07-a367-53fc-893b-7240dc79c293}}\\
\textbf{PiID} & \tzpcode{3678925903600} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{355}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1351.3613 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.2266 rad}\\
\textbf{TZPID} & \tzpcode{ID0348} & \textbf{Node Dependencies}\quad \tzpidref{0347}\\
\textbf{Registry} & \tzpcode{registry\_id\_0348} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Prepare an entangled pair of particles (Alice and Bob). Introduce Alice into a neural or metamaterial system such that she interacts electromagnetically but retains entanglement with Bob. As Alice traverses the system, measure Bob to infer Alice's state evolution. Map each measurement to a DAANSphere address and record the sequence. This sequence encodes the path taken by Alice.

\tzpsection{Canonical Equation}
\[
H_{\mathrm{total}} = H_{\mathrm{spatial}} \otimes H_{\mathrm{OAM}} \otimes H_{\mathrm{polarization}} \otimes H_{\mathrm{frequency}}
\]
\[
dim(H_{\mathrm{spatial}}) = 153{,}600
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H_{\mathrm{total}}$: total quantum state space.
    \item $H_{\mathrm{spatial}}$: spatial address-state factor.
    \item $H_{\mathrm{OAM}}$: orbital-angular-momentum factor.
    \item $H_{\mathrm{polarization}}$: polarization-state factor.
    \item $H_{\mathrm{frequency}}$: frequency-spectrum factor.
    \item $m_{\max}$: maximum retained orbital-angular-momentum mode index.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0348 generated source Wolfram model *)
ClearAll[K0348, Cr0348, T, R, A, W, I, N];
eq0348$1 = HoldForm[HTotal == HSpatial*TensorProduct*HOAM*TensorProduct*HPolarization*TensorProduct*HFrequency];
eq0348$2 = HoldForm[Dim[HSpatial] == 153600];
eq0348$3 = HoldForm[dim[HOAM] == 2*mMax + 1];

K0348 = HoldForm[{eq0348$1, eq0348$2, eq0348$3}];

N = "normalized TRAWIN closure object for Quantum Tag Injection and Entanglement Tracking Protocol";
I = "Normalized Output integration/comparison layer";
W = "Composable Action wave or operator carrier";
A = "Carrier Map admissible action/amplitude condition";
R = "Composable Action rotation/curl preservation layer";
T = "Carrier Map local source condition";

Cr0348[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0348 = Cr0348[K0348];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Carrier Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Composable Action rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Carrier Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Composable Action wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Output integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum Tag Injection and Entanglement Tracking Protocol.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0348] Quantum Tag Injection and Entanglement Tracking Protocol}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
H_{\mathrm{total}} = H_{\mathrm{spatial}} \otimes H_{\mathrm{OAM}} \otimes H_{\mathrm{polarization}} \otimes H_{\mathrm{frequency}}
\]
\[
\dim(H_{\mathrm{spatial}})=153{,}600
\]

\paragraph{Primary Derivation.}
The recovered source passage defines the total state space as a tensor product of spatial address, orbital-angular-momentum, polarization, and frequency factors. The spatial factor is indexed by the 153,600 address states recorded for this protocol.

\paragraph{Interpretation.}
This validates the state-space decomposition used by the tag representation. It does not by itself establish entanglement preservation or a tracking measurement protocol.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The tensor-product equation establishes the composite carrier space, while the support layer records the stated spatial addressing scale.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Carrier Map}\par
\[
H_{\mathrm{total}} = H_{\mathrm{spatial}} \otimes H_{\mathrm{OAM}} \otimes H_{\mathrm{polarization}} \otimes H_{\mathrm{frequency}}
\]
\noindent This names the entry as an actual map between carrier domains rather than a loose metaphor.\par
\noindent\textbf{2. Composable Action}\par
\[
dim(H_{\mathrm{spatial}}) = 153{,}600
\]
\noindent This inserts the map into the ordered TRAWIN chain and makes composition explicit.\par
\noindent\textbf{3. Normalized Output}\par
\[
dim(H_{\mathrm{OAM}}) = 2 m_{\max} + 1
\]
\noindent This closes the entry by requiring that the output land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0348] Quantum Tag Injection and Entanglement Tracking Protocol}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small

\tzpsection{Definition}

Quantum tag injection is represented by a tensor-product organization of total state space. The equation separates spatial address, orbital-angular-momentum, polarization, and frequency degrees of freedom.

\tzpsection{Contextual Meaning}

The protocol does not store information in one undifferentiated variable. Location, orbital structure, polarization, and spectral information contribute distinct factors, allowing a tracking operation to interrogate a component while referring to the composite state.

\tzpsection{Formal Statement}

\[
H_{\mathrm{total}}=H_{\mathrm{spatial}}\otimes H_{\mathrm{OAM}}\otimes H_{\mathrm{polarization}}\otimes H_{\mathrm{frequency}}
\]

\tzpsection{Derivable Consequences}

A total state can be indexed by labels on each factor, distinguishing component operations from full-system operations. A mode cutoff such as \(m_{\max}\) requires its own displayed support.

\tzpsection{Lemma Support}

The approved alignment validates the tensor-product decomposition and identifies its total and constituent spaces. The approved \(m_{\max}\) term is not inferred from the canonical block alone.

\tzpsection{Technical Interpretation}

The tensor product declares coordinate architecture for tagging and tracking, leaving preparation, coupling, and measurement dynamics to later relations.

\tzpsection{Equation Grounding}

\(H_{\mathrm{total}}\) is total quantum state space; \(H_{\mathrm{spatial}}\) is the spatial address-state factor; \(H_{\mathrm{OAM}}\) is the orbital-angular-momentum factor; \(H_{\mathrm{polarization}}\) is the polarization-state factor; and \(H_{\mathrm{frequency}}\) is the frequency-spectrum factor.

\tzpsection{Interpretive Role}

This entry establishes the state-space carrier used to organize tagged information for subsequent tracking equations.

\tzpsection{TZP Thesaurus}

\noindent \textbf{Tensor-Product State Space}: A composite space assembled from separately identifiable physical degrees of freedom. \enspace\textbullet\enspace \textbf{Orbital-Angular-Momentum Factor}: The factor carrying mode information associated with orbital angular momentum. \enspace\textbullet\enspace \textbf{Address-State Factor}: The spatial factor used to assign or track a location-indexed component.\par

\endgroup

\tzpsection{Encyclopedia Mathematica}
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0348_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0348] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum Tag Injection and Entanglement Tracking Protocol}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} prepare an entangled pair of particles (Alice and Bob)

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum Tag Injection and Entanglement Tracking Protocol is valid as a formal dynamical
law when the Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0348_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
