\section*{ID7432: Suggestions / Next Steps (If You Want to Push Further): k\_0}
\paragraph{Metadata.}
PiID: 8115284366795 | RTEID: RTE:P28860.1065:T3.5703 | UUID: 1eddd3cc-7cc0-58bb-a2b2-5ad18d72dac5

\paragraph{Canonical Statement.}
1. **Spin–orbit oscillator pairs**: Include both spin phases and orbital phases in the network and explicitly model star–planet tidal torques (these produce terms ∝ sin(phase difference) * dissipation) — that will naturally allow study of spin–orbit resonances (e.g., Mercury 3:2, possible tidal locking). 2. **Include dissipation**: Add terms that remove energy (tidal damping) so resonant capture can occur in long runs. 3. **Use realistic time-varying distances** (elliptical orbits) rather than |a\_i–a\_j| static approximations. 4. **Study subsystems**: examine inner terrestrial planets separately, and giant planets separately — the dominance of Jupiter–Saturn suggests cluster dynamics may be internal to a subset. 5. **Parameter sweep and visualization**: sweep \textbackslash{}(k\_0\textbackslash{}) and visualize r(t) and phase distributions; look for stable frequency clusters (partial synchronization). 6. **Include moons** (e.g., Earth–Moon tidal coupling) for local effects.

\paragraph{Canonical Equation.}
\[
k_0
\]

\paragraph{Dictionary.}
Suggestions / Next Steps (If You Want to Push Further): k\_0 — k\_0

\paragraph{Encyclopedia.}
Suggestions / Next Steps (If You Want to Push Further): k\_0 is a symbolic expression, written k\_0. It introduces a symbol or relation used elsewhere in the framework. It is built from k\_0. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
