\section*{ID9238: Definition of B\_constraint(r,t)Btotal(r,t)}
\paragraph{Metadata.}
PiID: 6151446320469 | RTEID: RTE:P35873.2056:T2.5593 | UUID: e3882311-0d0d-5185-b98e-48493d8867da

\paragraph{Canonical Statement.}
-d/2)r1=(0,0,d/2) and r2=(0,0,d/2)r\_2=(0,0,d/2)r2=(0,0,d/2). The field produced by a single dipole at position r0r\_0r0 is \$Bdip(r;µ,r0)=(µ0/4π)[3(rr0)(µ(rr0))/rr05µ/rr03]B\_\{\textbackslash{}text\{dip\}\}(r;\textbackslash{}mu,r\_0)\$ = (\textbackslash{}mu\_0/4\textbackslash{}pi)[3(r-r\_0)(\textbackslash{}mu\textbackslash{}cdot(r-r\_0))/|r-r\_0|ˆ5 - \$\textbackslash{}mu/|r-r\_0|ˆ3]Bdip(r;µ,r0)=(µ0/4π)[3(rr0)(µ(rr0))/rr05µ/rr03].\$ The total internal field is \$Btotal(r,t)=Bdip(r;µ1(t),r1)+Bdip(r;µ2(t),r2)+Bconstraint(r,t)B\_\{\textbackslash{}text\{total\}\}(r,t)\$ = B\_\{\textbackslash{}text\{dip\}\}(r;\textbackslash{}mu\_1(t),r\_1) + B\_\{\textbackslash{}text\{dip\}\}(r;\textbackslash{}mu\_2(t),r\_2) + \$B\_\{\textbackslash{}text\{constraint\}\}(r,t)Btotal(r,t)=Bdip(r;µ1(t),r1)+Bdip(r;µ2(t),r2)+Bconstraint(r,t).\$ Interpretive Meaning: A pair of opposing dipoles under mechanical compression generate a localized field configuration that stores magnetic energy and helicity. The total field includes contributions from both dipoles and any selfconsistent constraint field arising from their interaction. Dependencies: ID 200. Derivable Consequences: (1) Forms the local field architecture for the volumetric equil

\paragraph{Canonical Equation.}
\[
B_{\text{constraint}}(r,t)Btotal(r,t)=Bdip(r;µ1(t),r1)+Bdip(r;µ2(t),r2)+Bconstraint(r,t).
\]

\paragraph{Dictionary.}
Definition of B\_constraint(r,t)Btotal(r,t) — B\_constraint(r,t)Btotal(r,t)=Bdip(r;µ1(t),r1)+Bdip(r;µ2(t),r2)+Bconstraint(r,t).

\paragraph{Encyclopedia.}
Definition of B\_constraint(r,t)Btotal(r,t) is an algebraic definition, written B\_constraint(r,t)Btotal(r,t)=Bdip(r;µ1(t),r1)+Bdip(r;µ2(t),r2)+Bconstraint(r,t).. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from B, p, r, c, o, n, defining B\_constraint(r,t)Btotal(r,t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
