\tzpanchor{0082}
\tzpentryheader{0082}{Micro-to-Macro Consistency Conditions}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{4a07d116-40a5-5673-8975-fd3a079b9089}}\\
\textbf{PiID} & \tzpcode{2803482534211} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{89}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{318.4242 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.5247 rad}\\
\textbf{TZPID} & \tzpcode{ID0082} & \textbf{Node Dependencies}\quad \tzpidref{0059}\\
\textbf{Registry} & \tzpcode{registry\_id\_0082} & \textbf{Scale}\quad coarse-grained transfer\\
\textbf{LOC Classification} & QC174.17 scale transitions & Q175 systems consistency\\
\textbf{arXiv Classification} & Primary: quant-ph \quad Cross-list: cond-mat.stat-mech, nlin.AO & \\
\textbf{Primary Support} & Microscopic Observable Layer & Coarse-Graining Map\\
\textbf{Closure Support} & Dynamical Consistency Law & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Consistency between micro and macro descriptions requires that aggregate behaviour derived from quantum rules matches classical laws in the appropriate limit; formally, ensemble averages of quantum observables must satisfy classical conservation laws and equations of motion when decoherence is effective.

\tzpsection{Canonical Equation}
\[
\langle O_{\mathrm{macro}} \rangle
=
\mathcal{C}\!\left(\langle O_{\mathrm{micro}} \rangle\right)
\]
\[
\frac{d}{dt}\langle Q_{\mathrm{macro}} \rangle
=
\mathcal{C}\!\left(\frac{d}{dt}\langle Q_{\mathrm{micro}} \rangle\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $O_{\mathrm{macro}}$: source equation symbol.
    \item $\mathcal{C}$: speed of light or relativistic conversion factor.
    \item $O_{\mathrm{micro}}$: source equation symbol.
    \item $Q_{\mathrm{macro}}$: source equation symbol.
    \item $Q_{\mathrm{micro}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0082 generated source Wolfram model *)
ClearAll[K0082, Cr0082, T, R, A, W, I, N];
eq0082$1 = HoldForm[Inner[OMacro] == C[Inner[OMicro]]];
eq0082$2 = HoldForm[(d/dt)*Inner[QMacro] == C[(d/dt)*Inner[QMicro]]];
eq0082$3 = HoldForm[Inner[OMicro]];

K0082 = HoldForm[{eq0082$1, eq0082$2, eq0082$3}];

N = "normalized TRAWIN closure object for Micro-to-Macro Consistency Conditions";
I = "Dynamical Consistency Law integration/comparison layer";
W = "Coarse-Graining Map wave or operator carrier";
A = "Microscopic Observable Layer admissible action/amplitude condition";
R = "Coarse-Graining Map rotation/curl preservation layer";
T = "Microscopic Observable Layer local source condition";

Cr0082[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0082 = Cr0082[K0082];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Microscopic Observable Layer local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Coarse-Graining Map rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Microscopic Observable Layer admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Coarse-Graining Map wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Dynamical Consistency Law integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Micro-to-Macro Consistency Conditions.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0082] Micro-to-Macro Consistency Conditions}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
Consistency between micro and macro descriptions requires that ensemble averages of quantum observables satisfy classical conservation laws and equations of motion when decoherence is effective.

\paragraph{Primary Equation.}
\begin{equation}
\frac{\mathrm{d}}{\mathrm{d}t}\langle A\rangle
=
\left\langle
\frac{i}{\hbar}[H,A]
+
\frac{\partial A}{\partial t}
\right\rangle .
\end{equation}

\paragraph{Classical Limit Condition.}
\begin{equation}
\langle A\rangle
\longrightarrow
A_{\mathrm{cl}} .
\end{equation}

\paragraph{Primary Derivation.}
For a quantum observable $A$, the expectation value evolves by the Heisenberg equation:
\begin{equation}
\frac{\mathrm{d}}{\mathrm{d}t}\langle A\rangle
=
\left\langle
\frac{i}{\hbar}[H,A]
+
\frac{\partial A}{\partial t}
\right\rangle .
\end{equation}

When decoherence suppresses interference, expectation values behave as classical ensemble variables:
\begin{equation}
\langle A\rangle
\rightarrow
A_{\mathrm{cl}}.
\end{equation}

Macro-consistency requires that these limiting variables satisfy the corresponding classical equations:
\begin{equation}
\boxed{
\mathcal{E}_{\mathrm{macro}}(A_{\mathrm{cl}})=0 .
}
\end{equation}

\paragraph{Interpretation.}
The micro-to-macro bridge is valid when quantum expectation values reproduce classical conservation and motion laws in the decohered limit.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Micro-to-Macro Consistency Conditions by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Microscopic Observable Layer}\par
\[
\langle O_{\mathrm{micro}} \rangle
\]
\noindent This identifies the fine-scale content to be transmitted upward.\par
\noindent\textbf{2. Coarse-Graining Map}\par
\[
\langle O_{\mathrm{macro}} \rangle
=
\mathcal{C}\!\left(\langle O_{\mathrm{micro}} \rangle\right)
\]
\noindent This introduces the admissible transformation from micro description to macro description.\par
\noindent\textbf{3. Dynamical Consistency Law}\par
\[
\frac{d}{dt}\langle Q_{\mathrm{macro}} \rangle
=
\mathcal{C}\!\left(\frac{d}{dt}\langle Q_{\mathrm{micro}} \rangle\right)
\]
\noindent This closes the progression by requiring time evolution to commute with coarse-graining on the relevant quantities.\par

\clearpage
\noindent\textbf{[ID 0082] Micro-to-Macro Consistency Conditions}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Micro-to-Macro Consistency Conditions is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Consistency between micro and macro descriptions requires that aggregate behaviour derived from quantum rules matches classical laws in the appropriate limit; formally, ensemble averages of quantum observables must satisfy classical conservation laws and equations of motion when decoherence is effective. \textbf{Contextual meaning:} The entry reads Micro-to-Macro Consistency Conditions as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry keeps the registry honest when it moves between scales. Any macro claim that cannot be recovered from an admissible microscopic map is excluded from the TRAWIN body of results. \textbf{Lemma support:} Microscopic Observable Layer; Coarse-Graining Map; Dynamical Consistency Law.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The micro-to-macro bridge is valid when quantum expectation values reproduce classical conservation and motion laws in the decohered limit.

\tzpsection{Equation Grounding}
Equation anchors: Consistency between micro and macro descriptions requires that aggregate behaviour derived from quantum rules matches classical laws in the appropriate limit; formally, ensemble averages of quantum observables must satisfy classical conservation laws and equations of motion when decoherence is effective. Consistency between micro and macro descriptions requires that aggregate behaviour derived from quantum rules matches classical laws in the appropriate limit; formally, ensemble averages of quantum observables must satisfy classical conservation laws and equations of motion when decoherence is effective.

\tzpsection{Interpretive Role}
This entry keeps the registry honest when it moves between scales. Any macro claim that cannot be recovered from an admissible microscopic map is excluded from the TRAWIN body of results.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Micro Macro Consistency Conditions}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Micro Macro Consistency Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Conditions Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0082]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0082_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0082] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Micro-to-Macro Consistency Conditions}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} consistency between micro and macro descriptions requires that aggregate behaviour
derived from quantum rules matches classical laws in the appropr...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Micro-to-Macro Consistency Conditions is valid when the total tensorial quantity is
conserved under the stated constraint.''\\
\textbf{Proof:} The source statement identifies a conserved balance law. Reading 0082 as a proposition,
validity follows by requiring the full stress, flux, or current contribution to be
included before the divergence or balance condition is evaluated.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conserved total-structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0082_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
