\section*{ID9227: Definition of HˆKK M)/G GaugeM}
\paragraph{Metadata.}
PiID: 9678070576561 | RTEID: RTE:P35830.4901:T2.4890 | UUID: 18e835fb-2cd1-57c5-b7c0-b2c38305dbfa

\paragraph{Canonical Statement.}
evolution on toroidal fibers. Falsifiability / Test Handle: Analyze dynamical simulations of field configurations and verify that phase trajectories correspond to cycles on a toroidal manifold. 2.0.165 ID 314: Extended Phase Space for MagnetoAcoustic–Kaluza–Klein Systems Type: Definition Formal Statement: The configuration manifold for coupled magnetoacoustic and compactified extradimensional modes is \$M=m=0∞(TSO(3)× R3⊗HmKK)/GgaugeM\$ = \textbackslash{}prod \{m=0\}\{\textbackslash{}infty\}(T*SO(3) \textbackslash{}times \textbackslash{}mathbb\{R\}ˆ3 \textbackslash{}otimes \$Hˆ\{KK\} m)/G \{\textbackslash{}text\{gauge\}\}M=m=0∞(TSO(3)× R3⊗HmKK)/Ggauge,\$ where HmKKHˆ\{KK\} mHmKK denotes the mmmth Kaluza–Klein sector Hilbert space and \$Ggauge=\{:R3→U(1)∇2=0\}G \{\textbackslash{}text\{gauge\}\}\$ = \{\textbackslash{}phi : \textbackslash{}mathbb\{R\}ˆ3 \textbackslash{}to \$U(1),|,\textbackslash{}nablaˆ2\textbackslash{}phi=0\}Ggauge=\{:R3→U(1)∇2=0\}\$ fixes gauge freedom. Interpretive Meaning: This extended phase space captures the degrees of freedom for magnetoacoustic fields coupled to a tower of Kaluza–Klein modes. It includes rotational and translat

\paragraph{Canonical Equation.}
\[
Hˆ{KK} m)/G {\text{gauge}}M=m=0∞(TSO(3)× R3⊗HmKK)/Ggauge,
\]

\paragraph{Dictionary.}
Definition of HˆKK M)/G GaugeM — HˆKK m)/G gaugeM=m=0∞(TSO(3)× R3⊗HmKK)/Ggauge

\paragraph{Encyclopedia.}
Definition of HˆKK M)/G GaugeM is an algebraic definition, written HˆKK m)/G gaugeM=m=0∞(TSO(3)× R3⊗HmKK)/Ggauge. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from m, T, S, O, R, H, defining HˆKK m)/G gaugeM. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
