\section*{ID9471: Definition of 𝑚↦→𝑚+Δ𝑚FD 𝐹thrust}
\paragraph{Metadata.}
PiID: 1605049221242 | RTEID: RTE:P36777.9963:T4.0502 | UUID: 8702977b-f842-5911-80c7-c3899de82dbe

\paragraph{Canonical Statement.}
e Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0217], [ID 0200] Node registry\_id\_0218 Support Titles Carrier Map; Composable Action; Normalized Output Test Handle If the stated map fails to compose or its output leaves the admissible target class, the entry fails. Canonical Equation Links B(𝑟 , 𝜃 \$)=∑\$ 𝑚 𝑎𝑚𝐽𝑚 (𝑘𝑟 )𝑒𝑖𝑚𝜃 \$𝑚↦→𝑚+Δ𝑚FD 𝐹thrust=𝜂shellΔ𝑔\$ [ID 0219] Quantum-Coriolis Operator TZPID ID0219 UUID 0cb02b0e-8e7c-542e-a5fd-2afd92efb34f Type Field / Transport Statement Scale magnetofluid LOC Classification Working routing: QC809 magnetohydrodynamics; QC6 fluid and plasma dynamics arXiv Classification Primary: physics.plasm-ph; Cross-list: astro-ph.SR, gr-qc Canonical Statement This entry develops Quantum-Coriolis Operator inside the inform

\paragraph{Canonical Equation.}
\[
𝑚↦→𝑚+Δ𝑚FD 𝐹thrust=𝜂shellΔ𝑔
\]

\paragraph{Dictionary.}
Definition of 𝑚↦→𝑚+Δ𝑚FD 𝐹thrust — 𝑚↦→𝑚+Δ𝑚FD 𝐹thrust=𝜂shellΔ𝑔

\paragraph{Encyclopedia.}
Definition of 𝑚↦→𝑚+Δ𝑚FD 𝐹thrust is an algebraic definition, written 𝑚↦→𝑚+Δ𝑚FD 𝐹thrust=𝜂shellΔ𝑔. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from s, h, l, defining 𝑚↦→𝑚+Δ𝑚FD 𝐹thrust. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
