\section*{ID9356: Definition of (∇T𝑔)norm}
\paragraph{Metadata.}
PiID: 9839400415297 | RTEID: RTE:P36331.4258:T3.3143 | UUID: 6d03fb7a-00ae-528f-be4f-52a9e78aba43

\paragraph{Canonical Statement.}
Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0017] Node registry\_id\_0027 Support Titles Exterior Metric Compatibility; Anchor Distribution Defect; Normalized Compatibility Split Test Handle If a measurable compatibility defect persists away from the anchor, the localization claim in this constraint fails. Canonical Equation Links \$∇T𝑔=0 (𝑥≠𝑝) ∇T𝑔=𝐶\$ 𝛿 (𝑥,𝑝) (𝑥=𝑝) \$(∇T𝑔)norm=NormalizeTRAWIN(∇T𝑔,\$ 𝐶 𝛿 (𝑥,𝑝) , 𝑔) [ID 0028] Constraint: TZP Torsion Localisation TZPID ID0028 UUID e7054e64-47d8-5f5d-82d7-966c10279112 Type Structural Constraint Scale torsion LOC Classification Working routing: QA641 torsion geometry; QC174 spin and transport arXiv Classification Primary: math.DG Cross-list: gr-qc, hep-th Canonical Statement The torsion of the Trawinistic connection vanishes away from the zero po

\paragraph{Canonical Equation.}
\[
(∇T𝑔)norm=NormalizeTRAWIN(∇T𝑔,
\]

\paragraph{Dictionary.}
Definition of (∇T𝑔)norm — (∇T𝑔)norm=NormalizeTRAWIN(∇T𝑔

\paragraph{Encyclopedia.}
Definition of (∇T𝑔)norm is an algebraic definition, written (∇T𝑔)norm=NormalizeTRAWIN(∇T𝑔. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from N, o, r, m, a, l, defining (∇T𝑔)norm. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
