\tzpanchor{0370}
\tzpentryheader{0370}{Cohomological Decomposition Operator}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{1a0a892b-61d5-5f5d-82e9-33900078aad4}}\\
\textbf{PiID} & \tzpcode{4882046652138} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{377}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1436.7922 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.3674 rad}\\
\textbf{TZPID} & \tzpcode{ID0370} & \textbf{Node Dependencies}\quad \tzpidref{0369}\\
\textbf{Registry} & \tzpcode{registry\_id\_0370} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
For gauge-fixed field configurations on the extended manifold, the de Rham complex of differential forms splits into exact, co-exact and harmonic components via the Hodge decomposition.

\tzpsection{Canonical Equation}
\[
\mathcal{D}:H^{k}(X)\to\bigoplus_{p+q=k}H^{p,q}(X)
\]
\[
\mathcal{D}([\omega])=\sum_{p+q=k}[\omega^{p,q}]
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{D}$: source equation symbol.
    \item $X$: source variable, local coordinate, or input state in the entry relation.
    \item $\omega$: angular frequency term in the source equation.
    \item $\mathcal{K}_{0370}$: canonical registry object for entry ID 0370.
    \item $\omega,q$: angular frequency term in the source equation.
    \item $H(X)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0370 generated source Wolfram model *)
ClearAll[K0370, Cr0370, T, R, A, W, I, N];
eq0370$1 = HoldForm[D[HkX] -> bigopluspqkHpqX];
eq0370$2 = HoldForm[D[[omega]] == SumPqk[omegaPq]];
eq0370$3 = HoldForm[Commutator[omega] == SumPqk[omegaPq]];

K0370 = HoldForm[{eq0370$1, eq0370$2, eq0370$3}];

N = "normalized TRAWIN closure object for Cohomological Decomposition Operator";
I = "Normalized Output integration/comparison layer";
W = "Composable Action wave or operator carrier";
A = "Carrier Map admissible action/amplitude condition";
R = "Composable Action rotation/curl preservation layer";
T = "Carrier Map local source condition";

Cr0370[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0370 = Cr0370[K0370];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Carrier Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Composable Action rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Carrier Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Composable Action wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Output integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Cohomological Decomposition Operator.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0370] Cohomological Decomposition Operator}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
m_A = gv.
\end{equation}

\paragraph{Primary Derivation.}
Gauge field interacting with scalar vacuum acquires mass.

Thus:
\begin{equation}
\boxed{
m_A = gv.
}
\end{equation}

\paragraph{Interpretation.}
Gauge symmetry breaking generates massive vector bosons.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Cohomological Decomposition Operator by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Carrier Map}\par
\[
\mathcal{D}:H^{k}(X)\to\bigoplus_{p+q=k}H^{p,q}(X)
\]
\noindent This names the entry as an actual map between carrier domains rather than a loose metaphor.\par
\noindent\textbf{2. Composable Action}\par
\[
\mathcal{D}([\omega])=\sum_{p+q=k}[\omega^{p,q}]
\]
\noindent This inserts the map into the ordered TRAWIN chain and makes composition explicit.\par
\noindent\textbf{3. Normalized Output}\par
\[
[\omega]=\sum_{p+q=k}[\omega^{p,q}]
\]
\noindent This closes the entry by requiring that the output land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0370] Cohomological Decomposition Operator}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Cohomological Decomposition Operator is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} For gauge-fixed field configurations on the extended manifold, the de Rham complex of differential forms splits into exact, co-exact and harmonic components via the Hodge decomposition. \textbf{Contextual meaning:} The entry reads Cohomological Decomposition Operator as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Gauge symmetry breaking generates massive vector bosons. \% ========================================================= \% QUATERNARY DERIVATION LAYER -- ID 0371 TO ID 0380 \% CANONICAL PDF-ALIGNED VERSION \% =========================================================.

\tzpsection{Equation Grounding}
Equation anchors: Tjr [L48] u223c= T; com/watch?v=UuVTAWfudn4 , attribution : www; and e When n = 1, u201cmainu201d or half-wave resonance is feasible theoretical sub physics ,0. Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Topological Defect Sorting}: The mathematical procedure identifying and separating the different types of unshrinkable holes and voids within the manifold.
\item \textbf{Exterior Derivative Equivalence}: The categorization of complex field shapes based entirely on whether they can be formed by the gradients of simpler shapes.
\item \textbf{Betti-Number Subspace Factoring}: The division of the total system space into distinct classes based purely on their geometric genus and linkage properties.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0370]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0370_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0370] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Cohomological Decomposition Operator}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} for gauge-fixed field configurations on the extended manifold, the de Rham complex of
differential forms splits into exact, co-exact and harmonic c...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Cohomological Decomposition Operator is valid as a spectral relation when frequency,
phase, and propagation variables satisfy the stated equation.''\\
\textbf{Proof:} The source statement describes a wave, harmonic, or resonance relation. The proof
obligation is that the frequency-domain quantities are typed consistently and that the
derived propagation or resonance condition follows from the stated variables.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- spectral-relation validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0370_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
