\section*{ID9086: Definition of µ}
\paragraph{Metadata.}
PiID: 6582533754388 | RTEID: RTE:P35282.9558:T1.5868 | UUID: f66ebf7e-c3dd-5a70-a080-a23f4598c559

\paragraph{Canonical Statement.}
Consequences: Predicts conservation of linking during reconnection; supports invariance of helicity ratio; guides design of laboratory experiments to emulate astrophysical processes; contributes to energy cascades. Falsifiability / Test Handle: Observation of fractional or noninteger linking numbers in magnetic structures would falsify this universality. 0.0.46 ID 044: \$µ\$ M Rš \$ω\$ Universal Scaling Law Type: Definition Formal Statement: The magnetic moment \$µ\textbackslash{}muµ\$ of a rotating body obeys \$µ=kMR2Ω\textbackslash{}mu\$ = \$k,M,Rˆ2,\textbackslash{}Omegaµ=kMR2Ω,\$ where MMM is mass, RRR the characteristic radius, Ω\textbackslash{}OmegaΩ the angular velocity, and kkk a universal proportionality constant determined by the Trawin base unit. Interpretive Meaning: The magnetic moment scales with the product of mass, square of size, and rotation rate across 47 orders of magnitude, indicating a deep link between inertial and magnetic properties. Depen

\paragraph{Canonical Equation.}
\[
µ=kMR2Ω\mu
\]

\paragraph{Dictionary.}
Consequences: Predicts conservation of linking during reconnection; supports invariance of helicity ratio; guides design of laboratory experiments to emulate astrophysical processes; contributes to energy cascades.

\paragraph{Encyclopedia.}
Definition of µ is an algebraic definition, written µ=kMR2Ωμ. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from μ, k, M, R, defining µ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
