\tzpanchor{0513}
\tzpentryheader{0513}{ZERNIKE POLYNOMIAL BASIS MAPPING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{3f178043-1f0a-50dd-b8ad-2d7e7f6d316b}}\\
\textbf{PiID} & \tzpcode{6566430860213} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{520}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1972.6768 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.2504 rad}\\
\textbf{TZPID} & \tzpcode{ID0513} & \textbf{Node Dependencies}\quad \tzpidref{0512}\\
\textbf{Registry} & \tzpcode{registry\_id\_0513} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Zernike polynomial basis maps a circular-aperture field into orthogonal radial and azimuthal modes, preserving the normalized optical carrier through the TRAWIN transfer frame.

\tzpsection{Canonical Equation}
\[
F_{\rm TZP} - F_{\rm background}, \qquad F=-\frac{1}{\beta}\log\mathcal Z
\]
\[
W(\rho,\theta)=\sum_{n,m} a_n^m Z_n^m(\rho,\theta)
\]
\[
\int_{0}^{1}\int_{0}^{2\pi}
Z_n^m(\rho,\theta)Z_{n'}^{m'}(\rho,\theta)\,\rho\,d\theta\,d\rho
=N_n^m\delta_{nn'}\delta_{mm'}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $F_{\mathrm{TZP}}$: source equation symbol.
    \item $F_{\mathrm{background}}$: source equation symbol.
    \item $F$: source equation symbol.
    \item $Z$: source equation symbol.
    \item $W$: source equation symbol.
    \item $\rho$: density or measure term used by the entry equation.
    \item $\theta$: phase angle or local angular coordinate.
    \item $n$: integer mode index.
    \item $a_n$: source equation symbol.
    \item $Z_n$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0513 generated source Wolfram model *)
ClearAll[K0513, Cr0513, T, R, A, W, I, N];
eq0513$1 = HoldForm[TZPSequence[FRmTZP - FRmbackground, F == (-(1/beta))*logmathcal*Z]];
eq0513$2 = HoldForm[W[rho, theta] == SumNm*aN^m*ZN^m[rho, theta]];
eq0513$3 = HoldForm[Integral0^1*Integral0^(2*Pi)*ZN^m[rho, theta]*ZN^Derivative[1][m]*Pair[rho, theta]*rho*dtheta*drho == NN^mDiracDeltaNnDiracDeltaMm];

K0513 = HoldForm[{eq0513$1, eq0513$2, eq0513$3}];

N = "normalized TRAWIN closure object for ZERNIKE POLYNOMIAL BASIS MAPPING";
I = "Normalized Output integration/comparison layer";
W = "Composable Action wave or operator carrier";
A = "Carrier Map admissible action/amplitude condition";
R = "Composable Action rotation/curl preservation layer";
T = "Carrier Map local source condition";

Cr0513[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0513 = Cr0513[K0513];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Carrier Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Composable Action rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Carrier Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Composable Action wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Output integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for ZERNIKE POLYNOMIAL BASIS MAPPING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0513] ZERNIKE POLYNOMIAL BASIS MAPPING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
P_{\mathrm{null}}(v)
=
\begin{cases}
v, & g(v,w)=0\ \text{for all}\ w\in T_pM,\\
0, & \text{otherwise}.
\end{cases}
\end{equation}

\paragraph{Primary Derivation.}
At the TZP, the degenerate metric admits null directions.  
A vector $v\in T_pM$ belongs to the null space if it pairs to zero with every tangent vector $w$:

\begin{equation}
g(v,w)=0
\qquad
\forall w\in T_pM .
\end{equation}

The null projection operator preserves vectors satisfying this condition:

\begin{equation}
P_{\mathrm{null}}(v)=v .
\end{equation}

Vectors not satisfying the null condition are removed by the projection:

\begin{equation}
P_{\mathrm{null}}(v)=0 .
\end{equation}

Thus,

\begin{equation}
\boxed{
P_{\mathrm{null}}(v)
=
\begin{cases}
v, & g(v,w)=0\ \text{for all}\ w\in T_pM,\\
0, & \text{otherwise}.
\end{cases}
}
\end{equation}

\paragraph{Interpretation.}
$P_{\mathrm{null}}$ extracts only those tangent directions annihilated by the degenerate TZP metric.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors ZERNIKE POLYNOMIAL BASIS MAPPING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Carrier Map}\par
\[
F_{\rm TZP} - F_{\rm background}, \qquad F=-\frac{1}{\beta}\log\mathcal Z
\]
\noindent This names the entry as an actual map between carrier domains rather than a loose metaphor.\par
\noindent\textbf{2. Composable Action}\par
\[
W(\rho,\theta)=\sum_{n,m} a_n^m Z_n^m(\rho,\theta)
\]
\noindent This inserts the map into the ordered TRAWIN chain and makes composition explicit.\par
\noindent\textbf{3. Normalized Output}\par
\[
\int_{0}^{1}\int_{0}^{2\pi}
Z_n^m(\rho,\theta)Z_{n'}^{m'}(\rho,\theta)\,\rho\,d\theta\,d\rho
=N_n^m\delta_{nn'}\delta_{mm'}
\]
\noindent This closes the entry by requiring that the output land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0513] ZERNIKE POLYNOMIAL BASIS MAPPING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
ZERNIKE POLYNOMIAL BASIS MAPPING is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Bmag = frac GNewton c to the power 2 left( frac 3(mathbf J *mathbf r )mathbf r r to the power 5 - frac mathbf J r to the power 3 right). \textbf{Contextual meaning:} The entry reads ZERNIKE POLYNOMIAL BASIS MAPPING as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
P sub null extracts only those tangent directions annihilated by the degenerate TZP metric.

\tzpsection{Equation Grounding}
Equation anchors: F sub rm TZP - F sub rm background , ; F=-ratio 1 beta log Z; i) boxed delta rho(vec r ) = delta sub BAO to the power freeze (vec r ) + sum sub m A sub m(r)cos(mphi+phi sub m) + delta rho sub disk-freeze (r,ph; and , n sub KK approximately round Bigg[ ratio (f sub obs - f sub nlm ) 2 pi R sub KK c Bigg]. Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Circular-Aperture Optical Wavefronts}: The standard mathematical language used to describe the exact 3D shape of a beam of light as it passes through a round lens or opening.
\item \textbf{Orthogonal Aberration Decomposition}: The process of breaking down a blurry, distorted image into a neat checklist of specific, correctable errors like 'astigmatism' or 'coma'.
\item \textbf{Radial-Azimuthal Factoring}: The algebraic separation of the light beam's shape into how it changes from the center to the edge, versus how it changes as you spin around the middle.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0513]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0513_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0513] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont ZERNIKE POLYNOMIAL BASIS MAPPING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the Zernike polynomial basis maps a circular-aperture field into orthogonal radial and
azimuthal modes, preserving the normalized optical carrier t...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ZERNIKE POLYNOMIAL BASIS MAPPING is valid as a tensorial/geometric statement when the
stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0513_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
