\section*{ID8798: TEMPORAL TRIGGER MECHANISM Canonical Statutory Formula: T\_trig}
\paragraph{Metadata.}
PiID: 2274299581807 | RTEID: RTE:P34164.5878:T6.0273 | UUID: 97f891e4-2196-5d56-b5b4-fa1ecbaefc3a

\paragraph{Canonical Statement.}
[ID 1178] TEMPORAL TRIGGER MECHANISM Canonical Statutory Formula: \$T\_\{trig\} = \{ t\_\{origin\} \textbackslash{}to t\_\{now\}, t\_\{retrieval\} \textbackslash{}to \textbackslash{}text\{Condition\}[\textbackslash{}text\{Query\}] \}\$ Formal Technical Dissertation: The code structure for embedding a retroactive memory. It links a current timestamp to a future conditional event, creating a "sleeping" quantum correlation that only activates (collapses) when the user queries the system in the future, completing the loop. Source: [17]

\paragraph{Canonical Equation.}
\[
T_{trig} = { t_{origin} \to t_{now}, t_{retrieval} \to \text{Condition}[\text{Query}] }
\]

\paragraph{Dictionary.}
TEMPORAL TRIGGER MECHANISM Canonical Statutory Formula: \$T\_trig = t\_origin t\_now, t\_retrieval Condition[Query] \$ Formal Technical Dissertation: The code structure for embedding a retroactive memory.

\paragraph{Encyclopedia.}
TEMPORAL TRIGGER MECHANISM Canonical Statutory Formula: T\_trig is an algebraic definition, written T\_trig = t\_origin → t\_now, t\_retrieval → Condition[Query]. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from t\_origin, t\_now, t\_retrieval, defining T\_trig. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
