\section*{ID9079: Relation: B22µ(Bˆ2)/(2μ)2µB2}
\paragraph{Metadata.}
PiID: 2184439658253 | RTEID: RTE:P35255.7732:T1.5420 | UUID: b5e8a847-a9d8-5060-b38c-6d2e9c1da761

\paragraph{Canonical Statement.}
sasser criticality; constrains differential rotation; underlies energy equipartition. Canonical Registry Vol. 01 14 Trawin Zero Point Contextus Canonicus Falsifiability / Test Handle: Observation of sustained deviations from \$Λ≈1\textbackslash{}Lambda\textbackslash{}approx1Λ≈1\$ in systems expected to follow the unification theory would falsify this definition. 0.0.41 ID 039: Magnetic–Coriolis Energy Equipartition Type: Conservation Law Formal Statement: In the vicinity of the Elsasser attractor, the magnetic energy density \$B22µ\textbackslash{}frac\{\textbackslash{}mathbf\{B\}ˆ2\}\{2\textbackslash{}mu\}2µB2\$ equals the kinetic energy density associated with differential rotation \$12ρ(Ωr)2\textbackslash{}frac\{1\}\{2\}\textbackslash{}rho, (\textbackslash{}Omega,r)ˆ221ρ(Ωr)2.\$ Interpretive Meaning: Magnetic and rotational energies equilibrate in systems obeying the unification principle. This equipartition explains why \$Λ\textbackslash{}LambdaΛ\$ remains near unity. Dependencies: ID 038 Derivable Consequences: Sets scaling relations between magnetic field and rota

\paragraph{Canonical Equation.}
\[
B22µ\frac{\mathbf{B}ˆ2}{2\mu}2µB2
\]

\paragraph{Dictionary.}
Relation: B22µ(Bˆ2)/(2μ)2µB2 — B22µ(Bˆ2)/(2μ)2µB2

\paragraph{Encyclopedia.}
Relation: B22µ(Bˆ2)/(2μ)2µB2 is a symbolic expression, written B22µ(Bˆ2)/(2μ)2µB2. It introduces a symbol or relation used elsewhere in the framework. It is built from μ, B. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
