\tzpanchor{0545}
\tzpentryheader{0545}{BESSEL MODULATION OF STELLAR AXIS}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{353022ed-8ece-5e20-b583-64c4b86e20fc}}\\
\textbf{PiID} & \tzpcode{2179860943702} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{552}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2093.0567 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.4487 rad}\\
\textbf{TZPID} & \tzpcode{ID0545} & \textbf{Node Dependencies}\quad \tzpidref{0544}\\
\textbf{Registry} & \tzpcode{registry\_id\_0545} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Mode Quantization & Dispersion Law\\
\textbf{Closure Support} & Boundary Condition & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
alpha -> 2pi J\_0[omega\_\{text\{cymatic\}\} t]

\tzpsection{Canonical Equation}
\[
propto 1/R^2
\]
\[
mathcal{H}_{\text{cymatic}} = \int \rho(r,t) \Phi_{\text{acoustic}}[\omega,k,t] d^3r
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $R$: global radius, boundary radius, or topological scale.
    \item $H$: source equation symbol.
    \item $\rho(r,t)$: density or measure term used by the entry equation.
    \item $t$: source equation symbol.
    \item $\Phi$: flux, phase, or topological map term in the source equation.
    \item $\omega$: angular frequency term in the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0545 generated source Wolfram model *)
ClearAll[K0545, Cr0545, T, R, A, W, I, N];
eq0545$1 = HoldForm[propto1/R^2];
eq0545$2 = HoldForm[HCymatic == Integral*rho[r, t]*PhiAcoustic[omega, k, t]*d^3*r];
eq0545$3 = HoldForm[delta -> arcsin[Sin[omegaPrecession*t]]];

K0545 = HoldForm[{eq0545$1, eq0545$2, eq0545$3}];

N = "normalized TRAWIN closure object for BESSEL MODULATION OF STELLAR AXIS";
I = "Boundary Condition integration/comparison layer";
W = "Dispersion Law wave or operator carrier";
A = "Mode Quantization admissible action/amplitude condition";
R = "Dispersion Law rotation/curl preservation layer";
T = "Mode Quantization local source condition";

Cr0545[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0545 = Cr0545[K0545];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Mode Quantization local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Dispersion Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Mode Quantization admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Dispersion Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Boundary Condition integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for BESSEL MODULATION OF STELLAR AXIS.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0545] BESSEL MODULATION OF STELLAR AXIS}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
g_{\mu}
=
\frac{\mu}
{MR^2\Omega}.
\end{equation}

\paragraph{Primary Derivation.}
Starting from the scaling law:

\begin{equation}
\mu
=
kMR^2\Omega ,
\end{equation}

divide both sides by the natural rotational magnetic scale:

\begin{equation}
MR^2\Omega .
\end{equation}

This gives:

\begin{equation}
\frac{\mu}{MR^2\Omega}=k .
\end{equation}

Define the dimensionless gyromagnetic coupling constant as:

\begin{equation}
\boxed{
g_{\mu}
=
\frac{\mu}
{MR^2\Omega}.
}
\end{equation}

\paragraph{Interpretation.}
$g_{\mu}$ removes ordinary scale factors from the magnetic moment and isolates the dimensionless coupling strength of the rotating system.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors BESSEL MODULATION OF STELLAR AXIS by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Mode Quantization}\par
\[
propto 1/R^2
\]
\noindent This fixes the quantized carrier mode indexed by the bounded geometry.\par
\noindent\textbf{2. Dispersion Law}\par
\[
mathcal{H}_{\text{cymatic}} = \int \rho(r,t) \Phi_{\text{acoustic}}[\omega,k,t] d^3r
\]
\noindent This turns the mode index into an actual propagation or resonance law.\par
\noindent\textbf{3. Boundary Condition}\par
\[
delta \to \arcsin(\sin[\omega_{\text{precession}} t])
\]
\noindent This closes the progression by enforcing the boundary or nodal condition that makes the pattern admissible.\par

\clearpage
\noindent\textbf{[ID 0545] BESSEL MODULATION OF STELLAR AXIS}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
BESSEL MODULATION OF STELLAR AXIS is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} alpha -> 2pi J sub 0[omega sub text cymatic t]. \textbf{Contextual meaning:} The entry reads BESSEL MODULATION OF STELLAR AXIS as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred. \textbf{Lemma support:} Mode Quantization; Dispersion Law; Boundary Condition.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
g sub removes ordinary scale factors from the magnetic moment and isolates the dimensionless coupling strength of the rotating system. \% SENARY DERIVATION LAYER -- ID 0546 TO ID 0550.

\tzpsection{Equation Grounding}
Equation anchors: propto 1/R to the power 2; mathcal H sub cymatic = integral rho(r,t) Phi sub acoustic [omega,k,t] d to the power 3r; and delta to arcsin(sin[omega sub precession t]). Proof route: show that bounded carrier geometry forces the stated mode quantization and resonance law. Formalization route: prove that the stated boundary condition yields the stated discrete spectrum.

\tzpsection{Interpretive Role}
The entry is now carried by explicit resonance mathematics, which better matches the wave-and-cymatic story arc of the third hundred.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Cylindrical-Wave Amplitude Decay}: The mathematical function describing exactly how the ripples on the surface of the spinning plasma drop get smaller and smaller as they move away from the equator toward the poles.
\item \textbf{Radial Boundary-Value Solutions}: The strict set of equations that perfectly dictate the exact size and shape of every single splash and wave that can possibly exist on the surface of the fluid star.
\item \textbf{High-Frequency Asymptotic Smoothing}: The proof that if you shake the plasma drop fast enough, the wild, chaotic splashing eventually blurs out into a perfectly smooth, glassy surface.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0545]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0545_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0545] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont BESSEL MODULATION OF STELLAR AXIS}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} g\_ removes ordinary scale factors from the magnetic moment and isolates the
dimensionless coupling strength of the rotating system

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``BESSEL MODULATION OF STELLAR AXIS is valid as a synchronization criterion under the
coupling conditions named by the source.''\\
\textbf{Proof:} The source statement describes coupled-oscillator behavior. The logical claim is
accepted only as a conditional synchronization result: coupling weights, frequency
spread, and order-parameter behavior determine whether coherence is increased, limited,
or dominated by a subset.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional synchronization validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0545_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
