\section*{ID8981: Definition of ∑ ηgas〈σ̂coll〉}
\paragraph{Metadata.}
PiID: 1836090032380 | RTEID: RTE:P34875.2175:T0.9150 | UUID: 38987e43-0ad1-566d-b42f-4bd2d9a6db08

\paragraph{Canonical Statement.}
Helicity Gating: The curved edges provide a topological "gate" that prevents the formation of unwanted micro-singularities at the blade tips. [ID 426] VACUUM CHAMBER EVACUATION \& NOBLE GAS BUFFERING Canonical Statutory Formula \$P (t)\$ = \$P0e −(S/V )t\$ + \$∑ ηgas〈σ̂coll〉 =⇒ Plimit ≈\$ 10−9 Pa (26) Formal Technical Dissertation ID 426 establishes the environmental isolation parameters required to maintain topological protection across the 153,600-node DAANSsphere lattice[cite: 72, 163]. To minimize gas-molecule-induced decoherence and parasitic drag on the rotating ferrite core, the internal chamber must be evacuated to an ultra-high vacuum (UHV) regime of 10−9 Pa or better[cit

\paragraph{Canonical Equation.}
\[
∑ ηgas〈σ̂coll〉 =⇒ Plimit ≈
\]

\paragraph{Dictionary.}
Helicity Gating: The curved edges provide a topological "gate" that prevents the formation of unwanted micro-singularities at the blade tips.

\paragraph{Encyclopedia.}
Definition of ∑ ηgas〈σ̂coll〉 is an algebraic definition, written ∑ ηgas〈σ̂coll〉 =⇒ Plimit ≈. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from P, l, m, defining ∑ ηgas〈σ̂coll〉. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
