\section*{ID9262: Relation: qcritical≈2.8q\_critical≈ 2.8qcritical≈2.8}
\paragraph{Metadata.}
PiID: 3883778142335 | RTEID: RTE:P35966.4029:T2.7129 | UUID: 89cc8982-df57-52f2-bd47-d9cb397ea996

\paragraph{Canonical Statement.}
g sensitive gyroscopes or interferometry; compare observations with predicted magnitude and spatial dependence. Canonical Registry Vol. 01 113 Trawin Zero Point Contextus Canonicus 2 TZP CANONICAL REGISTRY – ENTRIES 150–199 2.0.177 ID 326: Toroidal Field Safety Factor Constraint Type: Structural Constraint Formal Statement: For a nested toroidal magnetic confinement configuration, the safety factor \$q(r)=rB/(R0Bθ)q(r)\$ = r B\_\{\textbackslash{}phi\}/(R\_0 \$B\_\{\textbackslash{}theta\})q(r)=rB/(R0Bθ)\$ must exceed a critical value \$qcritical≈2.8q\_\{\textbackslash{}text\{critical\}\}\textbackslash{}approx 2.8qcritical≈2.8\$ to ensure stability. Interpretive Meaning: The safety factor characterizes the ratio of toroidal to poloidal field components in a toroidal confinement system. Exceeding the critical threshold prevents kink and tearing instabilities, ensuring stable confinement of magnetic flux. Dependencies: ID 323. Derivable Consequences: (1) Provides a design constraint for toroidal magnetic confinement device

\paragraph{Canonical Equation.}
\[
qcritical≈2.8q_{\text{critical}}\approx 2.8qcritical≈2.8
\]

\paragraph{Dictionary.}
Relation: qcritical≈2.8q\_critical≈ 2.8qcritical≈2.8 — qcritical≈2.8q\_critical≈ 2.8qcritical≈2.8

\paragraph{Encyclopedia.}
Relation: qcritical≈2.8q\_critical≈ 2.8qcritical≈2.8 is a scaling / order-of-magnitude relation, written qcritical≈2.8q\_critical≈ 2.8qcritical≈2.8. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from q, c, r, a, l, q\_. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
