\section*{ID8556: Definition of N}
\paragraph{Metadata.}
PiID: 8845314277568 | RTEID: RTE:P33224.8481:T4.4788 | UUID: f14bfeb7-d1ca-5c64-b40e-08c35c31cdc5

\paragraph{Canonical Statement.}
ormal Technical Dissertation: The mapping function from the 2-sphere surface of the DAANSphere to harmonic 3-space geometry. Source: [ID 865] PRIMITIVE ENTANGLEMENT MATRIX Canonical Statutory Formula: \$Πij \$ := \$⟨ψi|EDAANS |ψj⟩ \$ Formal Technical Dissertation: The pairwise quantum entanglement metric encoded within the DAANSphere mappings, defining the connectivity of the 153,600 nodes. Source: [ID 866] HYPERCUBIC GROUP HARMONICS Canonical Statutory Formula: \$GH \$ \$:=⊕8\$ \$n=1 SU(n)cube \$ Formal Technical Dissertation: The decomposition of hyperdimensional rota- tional groups into local symmetry kernels, specifically structured around hypercubic geometries. Source: [ID 867] TRANSCENDENTAL INFORMATION DENSITY Canonical Statutory For-mula: \$ρTI \$ := \$δK \$ \$δV \$ Formal Technical Dissertation: The information density gradient relative to symbolic knowledge \$(K) \$ acro

\paragraph{Canonical Equation.}
\[
n=1 SU(n)cube
\]

\paragraph{Dictionary.}
Definition of N — n=1 SU(n)cube

\paragraph{Encyclopedia.}
Definition of N is an algebraic definition, written n=1 SU(n)cube. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from S, U, c, u, b, defining n. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
