\section*{ID9025: Relation: MP\_null:T\_pM→T\_pM}
\paragraph{Metadata.}
PiID: 6654437558900 | RTEID: RTE:P35046.0792:T1.1965 | UUID: d283038e-895a-52aa-82cf-7ec2af0149cb

\paragraph{Canonical Statement.}
ble Consequences: Provides a quantitative handle on decoherence; enters definitions of entanglement structure; influences measurement backaction; informs information flux calculations. Falsifiability / Test Handle: Observation of field configurations that violate the predicted coherence bounds (e.g., exceeding 1) would falsify this definition. 0.0.15 ID 013: Null Space Projection Type: Operator Formal Statement: The null space projection operator \$P\_null:T\_pM→T\_pMP\_\{\textbackslash{}text\{null\}\}:T\_p\$ M\textbackslash{}to T\_p \$MP\_null:T\_pM→T\_pM\$ is defined by P\_null(v)=vP\_\{\textbackslash{}text\{null\}\}(v)=vP\_null(v)=v if g(v,w)=0g(v,w)=0g(v,w)=0 for all \$w∈T\_pMw\textbackslash{}in\$ T\_p \$Mw∈T\_pM,\$ and P\_null(v)=0P\_\{\textbackslash{}text\{null\}\}(v)=0P\_null(v)=0 otherwise. Interpretive Meaning: This operator extracts the components of a tangent vector that lie in the null space of the degenerate metric at the TZP. It identifies directions in which the metric fails to provide a length. De

\paragraph{Canonical Equation.}
\[
MP_null:T_pM→T_pM
\]

\paragraph{Dictionary.}
Relation: MP\_null:T\_pM→T\_pM — MP\_null:T\_pM→T\_pM

\paragraph{Encyclopedia.}
Relation: MP\_null:T\_pM→T\_pM is a symbolic expression, written MP\_null:T\_pM→T\_pM. It introduces a symbol or relation used elsewhere in the framework. It is built from M, P\_n, u, l, T\_p. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
