\tzpanchor{0567}
\tzpentryheader{0567}{THE NEUTRINO GHOST-FIELD MAPPING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{ab8c6b6a-b39b-5c19-b130-25ca6f8d8fb2}}\\
\textbf{PiID} & \tzpcode{1762931767523} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{574}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2178.4876 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.5895 rad}\\
\textbf{TZPID} & \tzpcode{ID0567} & \textbf{Node Dependencies}\quad \tzpidref{0566}\\
\textbf{Registry} & \tzpcode{registry\_id\_0567} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
hat\{Phi\}\_H

\tzpsection{Canonical Equation}
\[
Delta_{\text{lattice}} = \sqrt{\frac{4\pi R^2}{N_{\text{nodes}}} \cdot \chi_T} \equiv \ell_P \cdot \exp\left( \frac{1}{\alpha_T} \right)
\]
\[
V_{BC} = \{ (\xi_1, \xi_2, \xi_3, \xi_4) : \xi_i \in \{ -1, +1 \} \} \subset \mathbb{R}^4, \quad |V_{BC}| = 16
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\pi$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $V_{BC}$: source equation symbol.
    \item $e_T$: exponential damping factor encoding potential-induced suppression.
    \item $\chi$: source equation symbol.
    \item $\ell$: source equation symbol.
    \item $\xi$: source equation symbol.
    \item $D$: source equation symbol.
    \item $N_{nodes}$: source equation symbol.
    \item $T$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0567 generated source Wolfram model *)
ClearAll[K0567, Cr0567, T, R, A, W, I, N];
eq0567$1 = HoldForm[DeltaLattice == sqrt[((4*Pi*R^2)/NNodes)*chiT]*equiv*ellP*exp[1/alphaT]];
eq0567$2 = HoldForm[VBC == VertexSetBC && VBC Subset Reals4 && Cardinality[VBC] == 16];

K0567 = HoldForm[{eq0567$1, eq0567$2}];

N = "normalized TRAWIN closure object for THE NEUTRINO GHOST-FIELD MAPPING";
I = "Normalized Output integration/comparison layer";
W = "Composable Action wave or operator carrier";
A = "Carrier Map admissible action/amplitude condition";
R = "Composable Action rotation/curl preservation layer";
T = "Carrier Map local source condition";

Cr0567[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0567 = Cr0567[K0567];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Carrier Map local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Composable Action rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Carrier Map admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Composable Action wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Output integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for THE NEUTRINO GHOST-FIELD MAPPING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0567] THE NEUTRINO GHOST-FIELD MAPPING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Gamma[\phi] = W[J] - \int J\phi.
\end{equation}

\paragraph{Primary Derivation.}
Effective action is Legendre transform of generating functional.

Thus:
\begin{equation}
\boxed{
\Gamma[\phi] = W[J] - \int J\phi.
}
\end{equation}

\paragraph{Interpretation.}
Encodes full quantum corrections.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors THE NEUTRINO GHOST-FIELD MAPPING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Carrier Map}\par
\[
Delta_{\text{lattice}} = \sqrt{\frac{4\pi R^2}{N_{\text{nodes}}} \cdot \chi_T} \equiv \ell_P \cdot \exp\left( \frac{1}{\alpha_T} \right)
\]
\noindent This names the entry as an actual map between carrier domains rather than a loose metaphor.\par
\noindent\textbf{2. Composable Action}\par
\[
V_{BC} = \{ (\xi_1, \xi_2, \xi_3, \xi_4) : \xi_i \in \{ -1, +1 \} \} \subset \mathbb{R}^4, \quad |V_{BC}| = 16
\]
\noindent This inserts the map into the ordered TRAWIN chain and makes composition explicit.\par
\noindent\textbf{3. Normalized Output}\par
\[
Delta_{\text{lattice}} = \sqrt{\frac{4\pi R^2}{N_{\text{nodes}}} \cdot \chi_T} \equiv \ell_P \cdot \exp\left( \frac{1}{\alpha_T} \right)
\]
\noindent This closes the entry by requiring that the output land in the admissible target class.\par

\clearpage
\noindent\textbf{[ID 0567] THE NEUTRINO GHOST-FIELD MAPPING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
THE NEUTRINO GHOST-FIELD MAPPING is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} hat Phi sub H. \textbf{Contextual meaning:} The entry reads THE NEUTRINO GHOST-FIELD MAPPING as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc. \textbf{Lemma support:} Carrier Map; Composable Action; Normalized Output.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Encodes full quantum corrections.

\tzpsection{Equation Grounding}
Equation anchors: Delta sub lattice = sqrt ratio 4pi R to the power 2 N sub nodes dot chi sub T equiv ell sub P dot exp( ratio 1 alpha sub T ); V sub BC = (xi sub 1, xi sub 2, xi sub 3, xi sub 4) : xi sub i in -1, +1 subset mathbb R to the power 4, |V sub BC | = 16; and \$Delta sub lattice = sqrt ratio 4pi R to the power 2 N sub nodes dot chi sub T equiv ell sub P dot exp( ratio 1 alpha sub T ). Proof route: show that the composite map lands in the admissible target class once the TRAWIN ordering is respected. Formalization route: prove closure of the stated operator or functor under composition with the TRAWIN chain.

\tzpsection{Interpretive Role}
The entry converts a registry title into a transport map that can be reused by the surrounding transfer arc.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Weak-Interaction Topological Bleed}: The extremely subtle mathematical term accounting for the almost imperceptible amount of energy carried away by practically massless, invisible particles.
\item \textbf{Massless Particle Background Interference}: The process of isolating the faint, background static in the geometry caused by the universe's constant shower of neutrinos.
\item \textbf{Deep-Penetration Energy Loss}: The operator calculating the tiny fraction of the system's total information that completely escapes containment by simply passing through solid matter.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0567]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0567_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0567] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont THE NEUTRINO GHOST-FIELD MAPPING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} Encodes full quantum corrections

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``THE NEUTRINO GHOST-FIELD MAPPING (\textbackslash{}hat\{\textbackslash{}Phi is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0567_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
