\tzpanchor{0124}
\tzpentryheader{0124}{Pull Strength Scaling Law}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7f8c674f-a2fa-57d7-861a-151c3510cf47}}\\
\textbf{PiID} & \tzpcode{4460955058223} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{131}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{481.5195 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.7934 rad}\\
\textbf{TZPID} & \tzpcode{ID0124} & \textbf{Node Dependencies}\quad \tzpidref{0123}\\
\textbf{Registry} & \tzpcode{registry\_id\_0124} & \textbf{Scale}\quad cross-arm to hole area ratio\\
\textbf{LOC Classification} & QA299 scaling analysis & QA911 fluid mechanics\\
\textbf{arXiv Classification} & Primary: physics.flu-dyn \quad Cross-list: math-ph, physics.class-ph & \\
\textbf{Primary Support} & Pull Gain Law & Area Ratio Variable\\
\textbf{Closure Support} & Exponent Form & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The pull strength in a cross-geometry vortex scales as

\tzpsection{Canonical Equation}
\[ \left(\frac{A_{\mathrm{cross}}}{A_{\mathrm{hole}}}\right)^{3/2}, \] where $A_{\mathrm{cross}}$ is the cross-arm area and $A_{\mathrm{hole}}$ is the area of the central opening.

\[
\Pi_{\mathrm{pull}} = \left(\frac{A_{\mathrm{cross}}}{A_{\mathrm{hole}}}\right)^{3/2}
\]
\[
A_{\mathrm{ratio}} = \frac{A_{\mathrm{cross}}}{A_{\mathrm{hole}}}
\]
\[
\Pi_{\mathrm{pull}} = A_{\mathrm{ratio}}^{3/2}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $A_{\mathrm{cross}}$: source equation symbol.
    \item $A_{\mathrm{hole}}$: source equation symbol.
    \item $A_{\mathrm{ratio}}$: source equation symbol.
    \item $\mathcal{K}_{0124}$: canonical registry object for entry ID 0124.
    \item $\Pi_{pull}$: source equation symbol.
    \item $P$: source equation symbol.
    \item $A_{ratio}/2$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0124 generated source Wolfram model *)
ClearAll[K0124, Cr0124, T, R, A, W, I, N];
eq0124$1 = HoldForm[(ACross/AHole)^(3/2)];
eq0124$2 = HoldForm[PiPull == (ACross/AHole)^(3/2)];
eq0124$3 = HoldForm[ARatio == ACross/AHole];
eq0124$4 = HoldForm[PiPull == ARatio^(3/2)];

K0124 = HoldForm[{eq0124$1, eq0124$2, eq0124$3, eq0124$4}];

N = "normalized TRAWIN closure object for Pull Strength Scaling Law";
I = "Exponent Form integration/comparison layer";
W = "Area Ratio Variable wave or operator carrier";
A = "Pull Gain Law admissible action/amplitude condition";
R = "Area Ratio Variable rotation/curl preservation layer";
T = "Pull Gain Law local source condition";

Cr0124[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0124 = Cr0124[K0124];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Pull Gain Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Area Ratio Variable rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Pull Gain Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Area Ratio Variable wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Exponent Form integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Pull Strength Scaling Law.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0124] Pull Strength Scaling Law}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[ \left(\frac{A_{\mathrm{cross}}}{A_{\mathrm{hole}}}\right)^{3/2}, \] where $A_{\mathrm{cross}}$ is the cross-arm area and $A_{\mathrm{hole}}$ is the area of the central opening.

\[
\Pi_{\mathrm{pull}} = \left(\frac{A_{\mathrm{cross}}}{A_{\mathrm{hole}}}\right)^{3/2}
\]
\[
A_{\mathrm{ratio}} = \frac{A_{\mathrm{cross}}}{A_{\mathrm{hole}}}
\]
\[
\Pi_{\mathrm{pull}} = A_{\mathrm{ratio}}^{3/2}
\]

\paragraph{Primary Derivation.}
One can verify the equality by differentiating and applying the relevant definitions. which confirms the stated equality.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. Within the TRAWIN framework, the equation functions as the generalized carrier for the entry’s information content. Under CHL, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Pull Strength Scaling Law by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Pull Gain Law}\par
\[
\Pi_{\mathrm{pull}} = \left(\frac{A_{\mathrm{cross}}}{A_{\mathrm{hole}}}\right)^{3/2}
\]
\noindent This states the main amplification rule for the focused vortex geometry.\par
\noindent\textbf{2. Area Ratio Variable}\par
\[
A_{\mathrm{ratio}} = \frac{A_{\mathrm{cross}}}{A_{\mathrm{hole}}}
\]
\noindent This isolates the governing dimensionless geometry parameter.\par
\noindent\textbf{3. Exponent Form}\par
\[
\Pi_{\mathrm{pull}} = A_{\mathrm{ratio}}^{3/2}
\]
\noindent This closes the progression by restating the law in pure ratio form, ready for comparison and design.\par

\clearpage
\noindent\textbf{[ID 0124] Pull Strength Scaling Law}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Pull Strength Scaling Law is a Structural Constraint. The pull strength in a cross geometry vortex scales as (A\_cross/A\_hole)\textasciicircum{}\{3/2\}, where A\_cross is the cross arm area and A\_hole is the central opening area.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The pull strength in a cross geometry vortex scales as (A\_cross/A\_hole)\textasciicircum{}\{3/2\}, where A\_cross is the cross arm area and A\_hole is the central opening area.
\textbf{Contextual meaning:} Increasing the relative size of the cross arms relative to the hole enhances the radial acceleration by this exponent.
\textbf{Derivable consequences:} Guidelines for optimizing cross geometry; interplay with acceleration field; link to electromagnetic pinch strength.
\textbf{Lemma support:} The pull strength in a cross geometry vortex scales as (A\_cross/A\_hole)\textasciicircum{}\{3/2\}, where A\_cross is the cross arm area and A\_hole is the central opening area.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Measure pressure and acceleration profiles in different geometries and verify the scaling factor. ID 124: Pull Strength Scaling Law

\tzpsection{Equation Grounding}
The pull strength in a cross geometry vortex scales as (A\_cross/A\_hole)\textasciicircum{}\{3/2\}, where A\_cross is the cross arm area and A\_hole is the central opening area.

\tzpsection{Interpretive Role}
Increasing the relative size of the cross arms relative to the hole enhances the radial acceleration by this exponent.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Pull Gain Law}: The statement of the main amplification rule for the focused vortex geometry.
\item \textbf{Area Ratio Variable}: The isolation of the governing dimensionless geometry parameter.
\item \textbf{Exponent Form}: The restatement of the law in pure ratio form, ready for comparison and design.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0124]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0124_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0124] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Pull Strength Scaling Law}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the pull strength in a cross-geometry vortex scales as where A\_cross is the cross-arm
area and A\_hole is the area of the central opening

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Pull Strength Scaling Law is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that the pull strength in a cross-geometry vortex scales as
where A\_cross is the cross-arm area and A\_hole is the area of the central opening.
This entry summarizes the focused flow pages into one dimensionless control law. It is
the tranche's design equation: once the geometry is fixed, the pull gain can be
estimated before electrical or optical forcing is added.. The CHL validation treats the
equation as the formal anchor and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0124_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
