\section*{ID9347: Definition of 𝐺𝜇𝜈+Λ𝑔𝜇𝜈}
\paragraph{Metadata.}
PiID: 5560037279839 | RTEID: RTE:P36296.4768:T3.2568 | UUID: 2b8f6fdb-a1e7-51f5-bb05-5f228a34eb4d

\paragraph{Canonical Statement.}
q Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0150], [ID 0166] Node registry\_id\_0167 Support Titles Einstein-Side Balance; Total Sector Source; Conservation Condition Test Handle If the proposed total-sector sum cannot satisfy the displayed Einstein-side balance while remaining divergence free, the unified field equation fails. Canonical Equation Links \$𝐺𝜇𝜈+Λ𝑔𝜇𝜈=\$ 8𝜋𝐺 𝑐4 𝑇 tot 𝜇𝜈 𝑇 tot 𝜇𝜈=𝑇 grav 𝜇𝜈 +𝑇EM 𝜇𝜈 +𝑇weak 𝜇𝜈 +𝑇strong 𝜇𝜈 +𝑇vac 𝜇𝜈 \$∇𝜈𝑇\$ tot 𝜇𝜈=0 [ID 0168] Field Strength Coherence Condition at TZP TZPID ID0168 UUID faeefb6d-f24d-5524-8197-b1ee94eb10fe Type Coherence Condition Scale TZP localization criterion LOC Classification Working routing: QC20 field coherence; QA299 singular constraints arXiv Classification Primary: hep-th Cross-list: gr-qc, mat

\paragraph{Canonical Equation.}
\[
𝐺𝜇𝜈+Λ𝑔𝜇𝜈=
\]

\paragraph{Dictionary.}
Definition of 𝐺𝜇𝜈+Λ𝑔𝜇𝜈 — 𝐺𝜇𝜈+Λ𝑔𝜇𝜈=

\paragraph{Encyclopedia.}
Definition of 𝐺𝜇𝜈+Λ𝑔𝜇𝜈 is an algebraic definition, written 𝐺𝜇𝜈+Λ𝑔𝜇𝜈=. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
