\tzpanchor{0936}
\tzpentryheader{0936}{INTERACTION LAGRANGIAN COUPLING}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{09d5f4d0-1eb8-5dc2-83ed-0782d28f3871}}\\
\textbf{PiID} & \tzpcode{7875937519577} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{943}\\
\textbf{RTEID} & \textbf{Manifest row}\quad \tzpcode{not listed} & \textbf{Source}\quad \tzpcode{Coordinate Manifest}\\
\textbf{TZPID} & \tzpcode{ID0936} & \textbf{Node Dependencies}\quad \tzpidref{0935}\\
\textbf{Registry} & \tzpcode{registry\_id\_0936} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The interaction Lagrangian coupling binds a scalar field to the local probability density of the state. The Hamiltonian form records the same coupling as a time-dependent interaction term integrated over the active spatial domain.

\tzpsection{Canonical Equation}
\[
\mathcal{L}_{\mathrm{int}}=-g\,\phi(\mathbf{x},t)\,|\Psi|^2
\]
\[
\hat{V}_{\mathrm{int}}(t)=\int_{\Omega} g\,\phi(\mathbf{x},t)|\Psi(\mathbf{x},t)|^2\,d^d x
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{L}_{\mathrm{int}}$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $t$: source equation symbol.
    \item $\Psi$: wavefunction or state carrier for the entry equation.
    \item $V$: auxiliary target state or comparison variable.
    \item $\Omega$: domain, angular, or boundary operator associated with the equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0936 generated source Wolfram model *)
ClearAll[K0936, Cr0936, T, R, A, W, I, N];
eq0936$1 = HoldForm[LInt == (-g)*phi[x, t]*Abs[Psi]^2];
eq0936$2 = HoldForm[hat[V]*_*int*t == IntegralOmega*gphi[x, t]*Abs[Psi[x, t]]^2*d^d*x];

K0936 = HoldForm[{eq0936$1, eq0936$2}];

N = "normalized TRAWIN closure object for INTERACTION LAGRANGIAN COUPLING";
I = "INTERACTION LAGRANGIAN COUPLING integration/comparison layer";
W = "INTERACTION LAGRANGIAN COUPLING wave or operator carrier";
A = "INTERACTION LAGRANGIAN COUPLING admissible action/amplitude condition";
R = "INTERACTION LAGRANGIAN COUPLING rotation/curl preservation layer";
T = "INTERACTION LAGRANGIAN COUPLING local source condition";

Cr0936[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0936 = Cr0936[K0936];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ INTERACTION LAGRANGIAN COUPLING local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ INTERACTION LAGRANGIAN COUPLING rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ INTERACTION LAGRANGIAN COUPLING admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ INTERACTION LAGRANGIAN COUPLING wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ INTERACTION LAGRANGIAN COUPLING integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for INTERACTION LAGRANGIAN COUPLING.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0936] INTERACTION LAGRANGIAN COUPLING}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{L}_{\mathrm{int}}=-g\,\phi(\mathbf{x},t)\,|\Psi|^2
\]
\[
\hat{V}_{\mathrm{int}}(t)=\int_{\Omega} g\,\phi(\mathbf{x},t)|\Psi(\mathbf{x},t)|^2\,d^d x
\]

\paragraph{Primary Derivation.}
The expression \( \mathcal{L}_{\mathrm{int}}=-g\,\phi(\mathbf{x},t)\,|\Psi|^2 \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. Within the TRAWIN framework, the equation functions as the integral carrier for the entry’s information content. Under CHL, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors INTERACTION LAGRANGIAN COUPLING by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{L}_{\mathrm{int}}=-g\,\phi(\mathbf{x},t)\,|\Psi|^2
\]
\[
\hat{V}_{\mathrm{int}}(t)=\int_{\Omega} g\,\phi(\mathbf{x},t)|\Psi(\mathbf{x},t)|^2\,d^d x
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0936] INTERACTION LAGRANGIAN COUPLING}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZPID ENTRY 0936 is a registry definition in Quantum-Classical Transition with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This entry develops tzpid entry 0936 inside the quantum-classical transition arc of the directory. It treats the named object as a TRAWIN-admissible carrier that can be rendered, normalized, and linked forward into the surrounding registry pages. \textbf{Contextual meaning:} The entry reads TZPID ENTRY 0936 as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, TZPID ENTRY 0936 is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: csv,,rendered sub math ::MB sub dc29f2aba114 ,registry sub id sub 1008, L sub int = -g phi( x ,t) |Psi| to the power 2; OLOGICAL COUPLING,rendered sub math sub add sub candidate ,rendered sub math sub to sub registry sub add sub candidates sub deduped, L sub int = -g phi( x ,t) |Psi| to the power 2; and csv,,rendered sub math ::MB sub ef8a1fcf16d3 ,registry sub id sub 1008, hat H(t) = hat H sub 0 + hat V sub rm int + integral d to the power d r. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Classified Algorithmic Vault}: A locked, heavily encrypted line of code that the system is terrified to read, only accessed when the primary containment field begins to catastrophically fail.
\item \textbf{Redacted State Vector}: The deliberate blanking out of a specific set of sensor readings, hiding the true, horrifying speed of the plasma from the lower-level safety systems.
\item \textbf{Quarantine Memory Block}: A completely isolated sector of the computer designed to hold corrupted, mathematically insane equations that would crash the rest of the network.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0936]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0936].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0936] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont INTERACTION LAGRANGIAN COUPLING}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} INTERACTION LAGRANGIAN COUPLING is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``INTERACTION LAGRANGIAN COUPLING is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0936].
\par\endgroup
\vfill
\endgroup
\endgroup
