\section*{ID8491: JACOBIAN SINGULARITY LOCUS Canonical Statutory Formula: Det[J(r\_c)]}
\paragraph{Metadata.}
PiID: 2239709683408 | RTEID: RTE:P32972.4387:T4.0630 | UUID: 967988b1-bdae-5144-aa8d-64b94e98edbd

\paragraph{Canonical Statement.}
[ID 1164] JACOBIAN SINGULARITY LOCUS Canonical Statutory Formula: \$\textbackslash{}text\{Det\}[J(r\_c)] = 0 \textbackslash{}land W = \textbackslash{}frac\{1\}\{2\textbackslash{}pi i\} \textbackslash{}oint \textbackslash{}frac\{d(\textbackslash{}text\{Det\}[J])\}\{\textbackslash{}text\{Det\}[J]\} \textbackslash{}neq 0\$ Formal Technical Dissertation: Defines the mathematical condition for a Trawin Zero Point (TZP). It requires the simultaneous collapse of the Jacobian determinant (dimensional loss) and the preservation of a non-zero topological winding number (\$W\$), distinguishing the stable TZP vortex from a trivial singularity. Source: [1], [2]

\paragraph{Canonical Equation.}
\[
\text{Det}[J(r_c)] = 0 \land W = \frac{1}{2\pi i} \oint \frac{d(\text{Det}[J])}{\text{Det}[J]} \neq 0
\]

\paragraph{Dictionary.}
JACOBIAN SINGULARITY LOCUS Canonical Statutory Formula: \$Det[J(r\_c)] = 0 W = 12 i d(Det[J])Det[J] 0\$ Formal Technical Dissertation: Defines the mathematical condition for a Trawin Zero Point (TZP).

\paragraph{Encyclopedia.}
JACOBIAN SINGULARITY LOCUS Canonical Statutory Formula: Det[J(r\_c)] is a contour integral, written Det[J(r\_c)] = 0 land W = (1)/(2π i) oint (d(Det[J]))/(Det[J]) neq 0. It is evaluated by integrating along a closed contour, capturing global or topological properties of the field. It is built from π, W, J, defining Det[J(r\_c)]. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
