\section*{ID9404: Definition of 𝜇0𝜌 𝑘𝑛}
\paragraph{Metadata.}
PiID: 7090697939612 | RTEID: RTE:P36517.8204:T3.6215 | UUID: 45653127-f0cd-51f0-ae25-49d874d0d696

\paragraph{Canonical Statement.}
cate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0328], [ID 0300] Node registry\_id\_0329 Support Titles Dispersion Law; Standing Quantization; Mode Closure Test Handle If a bounded Alfvén carrier cannot be quantized into admissible standing modes, the hinge law for the third hundred fails. Canonical Equation Links 𝜔𝑛=𝑘𝑛𝑣A , 𝑣A=𝐵/ \$√\$ 𝜇0𝜌 𝑘𝑛=𝑛𝜋/𝐿, \$Ωg=𝑞𝐵/𝑚 𝜔𝑛≈𝑚Ωg\$ [ID 0330] Trawin Zero Point Singularity Conditions TZPID ID0330 UUID e38c5ced-d721-50a6-8da8-614d079efa17 Type Geometric / Topological Statement Scale geometric LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math.DG; Cross-list: math-ph, math.AT Canonical Statement This entry develops trawin zero point s

\paragraph{Canonical Equation.}
\[
𝜇0𝜌 𝑘𝑛=𝑛𝜋/𝐿,
\]

\paragraph{Dictionary.}
Definition of 𝜇0𝜌 𝑘𝑛 — 𝜇0𝜌 𝑘𝑛=𝑛𝜋/𝐿

\paragraph{Encyclopedia.}
Definition of 𝜇0𝜌 𝑘𝑛 is an algebraic definition, written 𝜇0𝜌 𝑘𝑛=𝑛𝜋/𝐿. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
