\section*{ID9816: Relation: C\_kissing ≈ 18}
\paragraph{Metadata.}
PiID: 5020072452256 | RTEID: RTE:P38117.7079:T6.2576 | UUID: 8e5ae417-4caf-58c8-8598-f51e537e7fb2

\paragraph{Canonical Statement.}
the metamaterial fully utilized) is astronomically large, and we are exploiting it in ways that avoid the usual decoherence pitfall. Communication Complexity: Communication in our system takes two main forms: quantum state transfer (teleportation) and classical messaging (needed to coordinate or interpret results). The quantum teleportation we achieve is essentially constant-time across the manifold – it doesn’t scale with distance in any conventional sense because distance in the collapsed manifold is trivial (all points in the 4D space meet at the 2D TZP). The channel capacity we mentioned, \$C\_\{\textbackslash{}text\{kissing\}\} \textbackslash{}approx 18\$ qubits per use, is fixed. If one were to use many entangled pairs in parallel, the throughput could be scaled arbitrarily by replication. More interesting is the complexity of ensuring reliability. Our teleportation scheme has an overhead of error correction and classical communication for decoding. The classical bits needed to send the syndrome and verification results scale with \$\textbackslash{}log(N\_\{\textbackslash{}max\})\$ (for identifying which errors occurred, etc.) – on the order of a few hundred bits even for the la

\paragraph{Canonical Equation.}
\[
C_{\text{kissing}} \approx 18
\]

\paragraph{Dictionary.}
Relation: C\_kissing ≈ 18 — C\_kissing ≈ 18

\paragraph{Encyclopedia.}
Relation: C\_kissing ≈ 18 is a scaling / order-of-magnitude relation, written C\_kissing ≈ 18. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from C\_. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
