\tzpanchor{0403}
\tzpentryheader{0403}{THE JACOBIAN FLOW OPERATOR (JacobianOp)}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{0b689990-df07-586c-a850-3065840faec2}}\\
\textbf{PiID} & \tzpcode{5727036575959} & \textbf{TZPi}\quad \tzpcode{6}\quad \textbf{PiPE}\quad \tzpcode{410}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1564.9385 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.5785 rad}\\
\textbf{TZPID} & \tzpcode{ID0403} & \textbf{Node Dependencies}\quad \tzpidref{0402}\\
\textbf{Registry} & \tzpcode{registry\_id\_0403} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Carrier Map & Composable Action\\
\textbf{Closure Support} & Normalized Output & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
By applying the Jp to the rotating frame metric, we induce a deltagnu.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{O}_{\mathrm{TZP}} : \mathcal{X} \to \mathcal{Y}
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{X}$: local field point or coordinate variable in the canonical equation.
    \item $\mathcal{Y}$: target variable or output state in the entry relation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0403 generated source Wolfram model *)
ClearAll[K0403, Cr0403, T, R, A, W, I, N];
eq0403$1 = HoldForm[$OTZP[X] -> Y$];

K0403 = HoldForm[{eq0403$1}];

N = "normalized TRAWIN closure object for THE JACOBIAN FLOW OPERATOR (JacobianOp)";
I = "THE JACOBIAN FLOW OPERATOR (JacobianOp) integration/comparison layer";
W = "THE JACOBIAN FLOW OPERATOR (JacobianOp) wave or operator carrier";
A = "THE JACOBIAN FLOW OPERATOR (JacobianOp) admissible action/amplitude condition";
R = "THE JACOBIAN FLOW OPERATOR (JacobianOp) rotation/curl preservation layer";
T = "THE JACOBIAN FLOW OPERATOR (JacobianOp) local source condition";

Cr0403[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0403 = Cr0403[K0403];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ THE JACOBIAN FLOW OPERATOR (JacobianOp) local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ THE JACOBIAN FLOW OPERATOR (JacobianOp) rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ THE JACOBIAN FLOW OPERATOR (JacobianOp) admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ THE JACOBIAN FLOW OPERATOR (JacobianOp) wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ THE JACOBIAN FLOW OPERATOR (JacobianOp) integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for THE JACOBIAN FLOW OPERATOR (JacobianOp).\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0403] THE JACOBIAN FLOW OPERATOR (JacobianOp)}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Statement.}
The local topological dimension at the TZP may transition among nearby dimensional states:

\begin{equation}
\dim_p(M)\in\{n,n-1,n+1\}.
\end{equation}

\paragraph{Primary Derivation.}
Let $M$ be an $n$-dimensional manifold away from $p$. For $x\neq p$,

\begin{equation}
\dim_x(M)=n .
\end{equation}

At $p$, however, the metric degeneracy and lemniscatic self-intersection create a local ambiguity: two branches of the manifold meet at one point.

A self-intersection may locally reduce distinguishable dimensional freedom, while bifurcation into two branches may locally increase effective adjacency. Therefore the local dimensional value is not fixed to $n$ alone, but may occupy the set:

\begin{equation}
\dim_p(M)\in\{n-1,n,n+1\}.
\end{equation}

\paragraph{Interpretation.}
The TZP acts as a dimensional seam. It is not merely located inside a dimension; it controls the transition between neighboring effective dimensional states.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors THE JACOBIAN FLOW OPERATOR (JacobianOp) by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{O}_{\mathrm{TZP}} : \mathcal{X} \to \mathcal{Y}
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0403] THE JACOBIAN FLOW OPERATOR (JacobianOp)}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
THE JACOBIAN FLOW OPERATOR (JacobianOp) is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
By applying the Jp to the rotating frame metric, we induce a deltagnu.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathcal{O}_{\mathrm{TZP}} : \mathcal{X} \to \mathcal{Y}
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
By applying the Jp to the rotating frame metric, we induce a deltagnu.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors THE JACOBIAN FLOW OPERATOR (JacobianOp) by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
THE JACOBIAN FLOW OPERATOR (JacobianOp); canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0403]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0403].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0403] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont THE JACOBIAN FLOW OPERATOR (JacobianOp)}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} jacobianOp = nabla otimes FlowVec Big|\textbackslash{}\_\textbackslash{} implies det(JacobianOp) -> 0

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``THE JACOBIAN FLOW OPERATOR (\textbackslash{}JacobianOp) is valid when the stated operator maps
admissible inputs into the declared target class.''\\
\textbf{Proof:} The source statement is read as an operator or transformation. The proof obligation is
type preservation: admissible inputs must land in the target object without breaking the
stated constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- operator-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0403].
\par\endgroup
\vfill
\endgroup
\endgroup
