\section*{ID9441: Definition of (𝑠)∝𝑠1−𝜏}
\paragraph{Metadata.}
PiID: 8614445812314 | RTEID: RTE:P36661.4996:T3.8582 | UUID: 493527c3-454e-5bbb-b990-bfa1e7fea52f

\paragraph{Canonical Statement.}
tificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0460], [ID 0400] Node registry\_id\_0461 Support Titles Carrier Map; Composable Action; Normalized Output Test Handle If the stated map fails to compose or its output leaves the admissible target class, the entry fails. Canonical Equation Links \$𝑣𝑝ℎ𝑎𝑠𝑒≈\$ 𝑐 𝜒 \$≈0.84𝑐\$ OTZP=· · · 𝐼 \$(𝑠)∝𝑠1−𝜏=𝑠−1/2\$ [ID 0462] MEDIATOR CHANNEL ENTANGLEMENT MAINTENANCE TZPID ID0462 UUID f7638b1f-ef6e-5c99-8b56-6d2cf3d1188e Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops mediator channel entanglement maintenance inside th

\paragraph{Canonical Equation.}
\[
(𝑠)∝𝑠1−𝜏=𝑠−1/2
\]

\paragraph{Dictionary.}
Definition of (𝑠)∝𝑠1−𝜏 — (𝑠)∝𝑠1−𝜏=𝑠−1/2

\paragraph{Encyclopedia.}
Definition of (𝑠)∝𝑠1−𝜏 is an algebraic definition, written (𝑠)∝𝑠1−𝜏=𝑠−1/2. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
