\section*{ID9294: Definition of =3/2τ}
\paragraph{Metadata.}
PiID: 2468012248261 | RTEID: RTE:P36090.6660:T2.9177 | UUID: 5e19c111-07ab-5f1c-b261-8a558aeaecce

\paragraph{Canonical Statement.}
effective mass–energy distributions in laboratory analogues (e.g., rotating superfluids); look for pressure anisotropies matching the tensor form; failure to observe divergence at the predicted rate would challenge the definition. 3.0.46 ID 395: Universal Avalanche Scaling Type: Conservation Law Formal Statement: In systems governed by TZP dynamics, the probability distribution of cascade sizes ()P(s) satisfies a universal power law ()3/2exp(/cutoff),P(s)s3/2exp(s/scutoff), where the exponent \$=3/2τ=3/2\$ emerges identically in quantum decoherence cascades, metamaterial avalanches and other scalefree processes. Interpretive Meaning: This entry encodes the scaleinvariant statistics of cascades near TZPs. The exponent 3/23/2 suggests a deep universality connecting seemingly disparate systems. Dependencies: 350, 351 Derivable Consequences: Implies that selforganised criticality is built into the TZP

\paragraph{Canonical Equation.}
\[
=3/2τ=3/2
\]

\paragraph{Dictionary.}
Definition of =3/2τ — =3/2τ=3/2

\paragraph{Encyclopedia.}
Definition of =3/2τ is an algebraic definition, written =3/2τ=3/2. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
