\section*{ID8787: Definition of Det g|\_p}
\paragraph{Metadata.}
PiID: 9073860251522 | RTEID: RTE:P34121.8724:T5.9569 | UUID: bbe7ba55-756c-549e-94ef-4af08cac8f44

\paragraph{Canonical Statement.}
ery computational pipeline must include the **Falsifiability Core Constraint** (ID 048) as a mandatory diagnostic step, evaluating all hypotheses within the **Bayesian Evidence Accumulation Framework** (ID 047). \#\#\#\# 8. Summary of Discretization Constraints Numerical physicists must adhere to the following non-negotiable checklist for DAANSsphere operations: 1. **Resolution:** 153,600-point grid density with **pi-kissing node topology** . 2. **Metric Integrity:** Strict enforcement of \$\textbackslash{}det g|\_p = 0\$ at the TZP bifurcation. 3. **Operator Suite:** Mandatory use of the TRAWIN suite; the 'R' operator must employ null space projections ( \$P\_\{null\}\$ ) at \$p\$ . 4. **Topological Quantization:** Half-integer winding numbers \$w\$ verified by the Trawin Characteristic Class ( \$c\_T\$ ). 5. **Scaling Invariance:** Normalization using the \$u\_T\$ loop integral across all 47 orders of scale. 6. **

\paragraph{Canonical Equation.}
\[
\det g|_p = 0
\]

\paragraph{Dictionary.}
Definition of Det g|\_p — det g|\_p = 0

\paragraph{Encyclopedia.}
Definition of Det g|\_p is an algebraic definition, written det g|\_p = 0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
