\section*{ID9157: Relation: R\_universe / N, Where R\_universe Is the Hubble Radius. for N of Order Unity}
\paragraph{Metadata.}
PiID: 9955657612186 | RTEID: RTE:P35558.6646:T2.0411 | UUID: 529170ea-5376-5e99-8cb2-d65faeabdd36

\paragraph{Canonical Statement.}
ar momentum; universal gyromagnetic ratio; derivation of Newton’s law from toroidal dynamics; predictions for gyromagnetic resonances. Falsifiability / Test Handle: Measure gyromagnetic ratios of astrophysical bodies and test for universality; derive gravitational force from toroidal averages and compare with Newtonian values. 1.0.38 ID 137: Megastructure Formation Theorem Type: Theorem Formal Statement: Standing wave interference across the universe produces filaments with wavelength \$λ\$ = \$π\$ R\_universe / n, where R\_universe is the Hubble radius. For n of order unity, \$λ ≈\$ 150 Mpc. These filaments are flux tubes with Tš topology; the predicted cosmic web spacing matches observations. Canonical Registry Vol. 01 46 Trawin Zero Point Contextus Canonicus 1 TZP CANONICAL REGISTRY – ENTRIES 100–149 Interpretive Meaning: Largescale structures in the universe—filaments and voids—arise from interference patterns of standing waves; the resulting spacing corresponds close

\paragraph{Canonical Equation.}
\[
R_universe / n, where R_universe is the Hubble radius. For n of order unity,
\]

\paragraph{Dictionary.}
Relation: R\_universe / n, where R\_universe is the Hubble radius. For n of order unity

\paragraph{Encyclopedia.}
Relation: R\_universe / N, Where R\_universe Is the Hubble Radius. for N of Order Unity is a symbolic expression, written R\_universe / n, where R\_universe is the Hubble radius. For n of order unity. It introduces a symbol or relation used elsewhere in the framework. It is built from R\_u, n, v, r, s, w. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
