\section*{ID9464: Definition of ∇×mathbf𝐵}
\paragraph{Metadata.}
PiID: 2252847160504 | RTEID: RTE:P36750.8137:T4.0054 | UUID: 7b82e6ec-c984-5514-9d97-18d4c15597a8

\paragraph{Canonical Statement.}
99\_cryogenic\_superconducting\_rail\_ alignment:sorry theoremid0699\_cryogenic\_superconducting\_rail\_ alignment Theoremid0699\_cryogenic\_superconducting\_rail\_ alignment Dependencies and Test Handle Dependencies [ID 0698], [ID 0600] Node registry\_id\_0699 Support Titles Levitation Force; Superconducting Rail Current; Alignment Stiffness Test Handle If the superconducting rail current cannot induce the stated levitation force and alignment stiffness, the entry fails. Canonical Equation Links 𝐹lev=· · · \$∇×mathbf𝐵=𝜇0mathbf𝐽sc\$ 𝑘align= 𝜕𝐹lev 𝜕𝑥 [ID 0700] QUANTUM RECTIFICATION RATCHET TZPID ID0700 UUID b6610f78-829b-5a11-baa5-615db2b8c771 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops quantum rectification ratchet inside the vorte

\paragraph{Canonical Equation.}
\[
∇×mathbf𝐵=𝜇0mathbf𝐽sc
\]

\paragraph{Dictionary.}
Definition of ∇×mathbf𝐵 — ∇×mathbf𝐵=𝜇0mathbf𝐽sc

\paragraph{Encyclopedia.}
Definition of ∇×mathbf𝐵 is an algebraic definition, written ∇×mathbf𝐵=𝜇0mathbf𝐽sc. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from m, a, h, b, f, s, defining ∇×mathbf𝐵. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
