\tzpanchor{0076}
\tzpentryheader{0076}{Fluctuation--Dissipation Relations}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{16019d19-3151-534d-902a-66290c04a7b3}}\\
\textbf{PiID} & \tzpcode{0899862803482} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{83}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{295.1249 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.4863 rad}\\
\textbf{TZPID} & \tzpcode{ID0076} & \textbf{Node Dependencies}\quad \tzpidref{0062}\\
\textbf{Registry} & \tzpcode{registry\_id\_0076} & \textbf{Scale}\quad noise-response coupling\\
\textbf{LOC Classification} & QC174 fluctuation-dissipation & QC311 linear response\\
\textbf{arXiv Classification} & Primary: cond-mat.stat-mech \quad Cross-list: quant-ph, hep-th & \\
\textbf{Primary Support} & Noise Spectrum & Response Function\\
\textbf{Closure Support} & Fluctuation--Dissipation Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Dissipation and fluctuations are related; curvature and the TZP modify the effective temperature and the relationship between noise and response.

\tzpsection{Canonical Equation}
\[
S(\omega)
=
2\hbar\,
\coth\!\left(
\frac{\hbar\omega}{2k_{\mathrm{B}}T_{\mathrm{eff}}}
\right)
\operatorname{Im}R(\omega)
\]
\[
T_{\mathrm{eff}} = T_{\mathrm{eff}}^{\mathrm{th}} + T_{\mathrm{eff}}^{\mathrm{TZP}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
    \item $k_{\mathrm{B}}$: source equation symbol.
    \item $T_{\mathrm{eff}}$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0076 generated source Wolfram model *)
ClearAll[K0076, Cr0076, T, R, A, W, I, N];
eq0076$1 = HoldForm[S[omega] == 2*hbarcoth[hbaromega/(2*kBTEff)]*ImR[omega]];
eq0076$2 = HoldForm[TEff == TEff^th + TEff^TZP];
eq0076$3 = HoldForm[S[omega]];
eq0076$4 = HoldForm[R[omega]];

K0076 = HoldForm[{eq0076$1, eq0076$2, eq0076$3, eq0076$4}];

N = "normalized TRAWIN closure object for Fluctuation--Dissipation Relations";
I = "Fluctuation--Dissipation Relation integration/comparison layer";
W = "Response Function wave or operator carrier";
A = "Noise Spectrum admissible action/amplitude condition";
R = "Response Function rotation/curl preservation layer";
T = "Noise Spectrum local source condition";

Cr0076[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0076 = Cr0076[K0076];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Noise Spectrum local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Response Function rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Noise Spectrum admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Response Function wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Fluctuation--Dissipation Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Fluctuation--Dissipation Relations.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0076] Fluctuation--Dissipation Relations}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
S(\omega)
=
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right)
\operatorname{Im}R(\omega).
\end{equation}

\paragraph{Effective Temperature Split.}
\begin{equation}
T_{\mathrm{eff}}
=
T_{\mathrm{eff}}^{\mathrm{th}}
+
T_{\mathrm{eff}}^{\mathrm{TZP}} .
\end{equation}

\paragraph{Primary Derivation.}
Let $S(\omega)$ be the noise spectrum and $R(\omega)$ the response function.  
Dissipation is encoded by the imaginary part:
\begin{equation}
\operatorname{Im}R(\omega).
\end{equation}

The fluctuation factor is set by the effective thermal and zero-point scale:
\begin{equation}
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right).
\end{equation}

Multiplying the two pieces gives:
\begin{equation}
\boxed{
S(\omega)
=
2\hbar
\coth\left(
\frac{\hbar\omega}{2k_B T_{\mathrm{eff}}}
\right)
\operatorname{Im}R(\omega).
}
\end{equation}

\paragraph{Interpretation.}
Noise and response are coupled through an effective temperature that includes ordinary thermal and TZP contributions.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Fluctuation--Dissipation Relations by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Noise Spectrum}\par
\[
S(\omega)
\]
\noindent This is the observable fluctuation content resolved by frequency.\par
\noindent\textbf{2. Response Function}\par
\[
R(\omega)
\]
\noindent This encodes how the system reacts to perturbation at the same frequency.\par
\noindent\textbf{3. Fluctuation--Dissipation Relation}\par
\[
S(\omega)
=
2\hbar\,
\coth\!\left(
\frac{\hbar\omega}{2k_{\mathrm{B}}T_{\mathrm{eff}}}
\right)
\operatorname{Im}R(\omega)
\]
\noindent This closes the progression by relating fluctuation amplitude to dissipative response.\par

\clearpage
\noindent\textbf{[ID 0076] Fluctuation--Dissipation Relations}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Fluctuation--Dissipation Relations is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Dissipation and fluctuations are related; curvature and the TZP modify the effective temperature and the relationship between noise and response. \textbf{Contextual meaning:} The entry reads Fluctuation--Dissipation Relations as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This law ties the spectral-noise entries directly to linear response and transport. It lets the registry move from observed fluctuations to response coefficients without changing conceptual language. \textbf{Lemma support:} Noise Spectrum; Response Function; Fluctuation--Dissipation Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Noise and response are coupled through an effective temperature that includes ordinary thermal and TZP contributions.

\tzpsection{Equation Grounding}
Equation anchors: The Trawinistic fluctuation--dissipation theorem relates the response function R(omega)R(omega)R(omega) of a system to its noise spectrum S(omega)S(omega)S(omega) via S(omega)=2  cothu2061( omega2kBTeff)Im R(omega)S(omega) = 2hbartextbackslash,textbackslash cothtextbackslash left(ratio hbar omega 2 k B T eff textbackslash right) Im textbackslash,R(omega)S(omega)=2 coth(2kBTeff omega)ImR(omega), where TeffT eff Teff includes contributions from curvature and zero-point fluctuations. The Trawinistic fluctuation--dissipation theorem relates the response function R(omega)R(omega)R(omega) of a system to its noise spectrum S(omega)S(omega)S(omega) via S(omega)=2  cothu2061( omega2kBTeff)Im R(omega)S(omega) = 2hbartextbackslash,textbackslash cothtextbackslash left(ratio hbar omega 2 k B T eff textbackslash right) Im textbackslash,R(omega)S(omega)=2 coth(2kBTeff omega)ImR(omega), where TeffT eff Teff includes contributions from curvature and zero-point fluctuations.

\tzpsection{Interpretive Role}
This law ties the spectral-noise entries directly to linear response and transport. It lets the registry move from observed fluctuations to response coefficients without changing conceptual language.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Fluctuation Dissipation Relations}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Fluctuation Dissipation Relations Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Relations Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0076]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0076_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0076] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Fluctuation--Dissipation Relations}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} dissipation and fluctuations are related; curvature and the TZP modify the effective
temperature and the relationship between noise and response

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Fluctuation--Dissipation Relations is valid as a tensorial/geometric statement when the
stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0076_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
