\section*{ID9442: Definition of ΦTZP}
\paragraph{Metadata.}
PiID: 6144458123145 | RTEID: RTE:P36665.3829:T3.8646 | UUID: a2915fa6-6a30-5ac1-955f-538dbc2d63b6

\paragraph{Canonical Statement.}
D 0463] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0462], [ID 0400] Node registry\_id\_0463 Support Titles Canonical Definition; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links \$ΦTZP=minP\$ I(P) I (𝐴:𝐵)>0 \$ΦTZP≥0\$ [ID 0464] CAUSAL ORDER COLLAPSE LOGIC TZPID ID0464 UUID f560f150-fbb2-5728-9a73-ad31fc498af9 Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops causal order collapse logic inside the m

\paragraph{Canonical Equation.}
\[
ΦTZP=minP
\]

\paragraph{Dictionary.}
Definition of ΦTZP — ΦTZP=minP

\paragraph{Encyclopedia.}
Definition of ΦTZP is an algebraic definition, written ΦTZP=minP. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from m, n, P, defining ΦTZP. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
