\tzpanchor{0875}
\tzpentryheader{0875}{ENTRAINMENT CONDUCTOR FIELD}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{802ef638-9e37-5baa-82f3-8308ce05cd3a}}\\
\textbf{PiID} & \tzpcode{3208381420617} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{882}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3343.4542 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.5090 rad}\\
\textbf{TZPID} & \tzpcode{ID0875} & \textbf{Node Dependencies}\quad \tzpidref{0874}\\
\textbf{Registry} & \tzpcode{registry\_id\_0875} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Aggregate Relation & Aggregate Relation\\
\textbf{Closure Support} & Aggregate Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records entrainment conductor field through a normalized Nonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0875}}:\mathcal{X}_{\mathrm{id0875}}\longrightarrow\mathcal{Y}_{\mathrm{id0875}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0875}})=\mathcal{O}_{\mathrm{id0875}}
\]
\[
\mathcal{O}_{\mathrm{id0875}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0875}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0875}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0875}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0875 generated source Wolfram model *)
ClearAll[K0875, Cr0875, T, R, A, W, I, N];
eq0875$1 = HoldForm[Oid0875[Xid0875] -> Yid0875];
eq0875$2 = HoldForm[NTRAWIN[OId0875] == OId0875];
eq0875$3 = HoldForm[Element[OId0875[x], YAdm]];

K0875 = HoldForm[{eq0875$1, eq0875$2, eq0875$3}];

N = "normalized TRAWIN closure object for ENTRAINMENT CONDUCTOR FIELD";
I = "ENTRAINMENT CONDUCTOR FIELD integration/comparison layer";
W = "ENTRAINMENT CONDUCTOR FIELD wave or operator carrier";
A = "ENTRAINMENT CONDUCTOR FIELD admissible action/amplitude condition";
R = "ENTRAINMENT CONDUCTOR FIELD rotation/curl preservation layer";
T = "ENTRAINMENT CONDUCTOR FIELD local source condition";

Cr0875[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0875 = Cr0875[K0875];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ ENTRAINMENT CONDUCTOR FIELD local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ ENTRAINMENT CONDUCTOR FIELD rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ ENTRAINMENT CONDUCTOR FIELD admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ ENTRAINMENT CONDUCTOR FIELD wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ ENTRAINMENT CONDUCTOR FIELD integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for ENTRAINMENT CONDUCTOR FIELD.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0875] ENTRAINMENT CONDUCTOR FIELD}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0875}}:\mathcal{X}_{\mathrm{id0875}}\longrightarrow \mathcal{Y}_{\mathrm{id0875}},\qquad
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0875}})=\mathcal{O}_{\mathrm{id0875}},\qquad
\mathcal{O}_{\mathrm{id0875}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

\paragraph{Primary Derivation.} Let $\psi_{0875}(x,t)$ be the local wave or phase carrier.  The entry assigns the carrier mode\[
\psi_{0875}=\mathcal{O}_{\mathrm{id0875}}(x).
\]

A reusable harmonic witness is the phase-weighted state\[
I_{0875}(t)=A_{0875}(t)e^{i\theta_{0875}(t)}.
\]

Stable closure requires phase locking and admissible landing:\[
\dot{\theta}_{0875}(t)=\omega_{\mathrm{lock},0875},\qquad \mathcal{O}_{\mathrm{id0875}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

Thus the Nonary derivation for [ID 0875] is the three-stage passage
\[
\mathcal{X}_{\mathrm{id0875}}\xrightarrow{\,\mathcal{O}_{\mathrm{id0875}}\,} \mathcal{Y}_{\mathrm{id0875}}\xrightarrow{\,\mathcal{N}_{\mathrm{TRAWIN}}\,} \mathcal{Y}_{\mathrm{adm}},
\]
with the entry title fixing the meaning of the carrier and the TRAWIN normalization fixing the admissibility test.

\paragraph{Interpretation.} ENTRAINMENT CONDUCTOR FIELD closes as a phase-and-mode statement: the entry is usable when its harmonic carrier locks to the local admissible channel.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors ENTRAINMENT CONDUCTOR FIELD by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0875}}:\mathcal{X}_{\mathrm{id0875}}\longrightarrow\mathcal{Y}_{\mathrm{id0875}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0875}})=\mathcal{O}_{\mathrm{id0875}}
\]
\[
\mathcal{O}_{\mathrm{id0875}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0875] ENTRAINMENT CONDUCTOR FIELD}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
ENTRAINMENT CONDUCTOR FIELD is a registry definition in Resonance and Phase Locking with secondary pressure from Biological and Biomolecular Analogies.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} U sub mag = -vec mu total (t) * vec B external (vec r cm , t) + U self [d(t)]. \textbf{Contextual meaning:} The entry reads ENTRAINMENT CONDUCTOR FIELD as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Aggregate Relation; Aggregate Relation; Aggregate Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, ENTRAINMENT CONDUCTOR FIELD is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: mathcal C (t,x):=ointgamma(t)dotvec B dot dA; dw=ratio 1 2pi oint Gamma abla; and mathrm kappa sub H := ratio h e to the power 2 integral vec A dot vec B dV. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Macroscopic Harmonic Slaving}: The terrifying observation that the massive, deafening hum of the primary reactor is so powerful it is physically forcing the completely separate, secondary computers in the next room to vibrate at the exact same pitch.
\item \textbf{Field-Induced Clock Synchronization}: The realization that you don't even need wires; just being near the spinning magnetic tornado naturally forces all the independent, chaotic atoms in the walls to lock into perfect step.
\item \textbf{Parasitic Resonance Bleed}: The frustrating engineering problem where the beautiful, perfect energy inside the core is slowly leaking out, completely wasted on making the concrete floor of the laboratory shake.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0875]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0875].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0875] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont ENTRAINMENT CONDUCTOR FIELD}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} ENTRAINMENT CONDUCTOR FIELD is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ENTRAINMENT CONDUCTOR FIELD is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0875].
\par\endgroup
\vfill
\endgroup
\endgroup
