\section*{ID8929: ACOUSTIC-MAGNETIC LEVITATION FORCE Canonical Statutory Formula: F\_lev}
\paragraph{Metadata.}
PiID: 9692348896276 | RTEID: RTE:P34673.2899:T0.5823 | UUID: d05e1f53-9318-51a5-a678-38d168c74483

\paragraph{Canonical Statement.}
[ID 924] ACOUSTIC-MAGNETIC LEVITATION FORCE Canonical Statutory Formula: \$F\_\{lev\} = \textbackslash{}frac\{p\_\{rms\}\textasciicircum{}2 A\}\{2 \textbackslash{}rho c\textasciicircum{}2\} + \textbackslash{}frac\{B\textasciicircum{}2 A\}\{2 \textbackslash{}mu\_0\} = mg + F\_\{perturb\}\$ Formal Technical Dissertation: The force balance equation for the levitation system. It combines acoustic radiation pressure and magnetic pressure (Meissner effect) to counteract gravitational acceleration and perturbations, maintaining the 10 \$\textbackslash{}mu\$m gap [21]. Source: [21]

\paragraph{Canonical Equation.}
\[
F_{lev} = \frac{p_{rms}^2 A}{2 \rho c^2} + \frac{B^2 A}{2 \mu_0} = mg + F_{perturb}
\]

\paragraph{Dictionary.}
ACOUSTIC-MAGNETIC LEVITATION FORCE Canonical Statutory Formula: \$F\_lev = p\_rms\textasciicircum{}2 A2 c\textasciicircum{}2 + B\textasciicircum{}2 A2 \_0 = mg + F\_perturb\$ Formal Technical Dissertation: The force balance equation for the levitation system.

\paragraph{Encyclopedia.}
ACOUSTIC-MAGNETIC LEVITATION FORCE Canonical Statutory Formula: F\_lev is an algebraic definition, written F\_lev = fracp\_rms\textasciicircum{}2 A2 ρ c\textasciicircum{}2 + (B\textasciicircum{}2 A)/(2 μ\_0) = mg + F\_perturb. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from ρ, p\_rms, A, c, B, m, defining F\_lev. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
