\section*{ID8904: GERCHBERG-SAXTON HELICAL PROPAGATOR Canonical Statutory Formula: ψ\_n+1}
\paragraph{Metadata.}
PiID: 6476697583183 | RTEID: RTE:P34576.2094:T0.4223 | UUID: 6a4856ad-005d-52a2-a77c-440f3ace676f

\paragraph{Canonical Statement.}
[ID 934] GERCHBERG-SAXTON HELICAL PROPAGATOR Canonical Statutory Formula: \$\textbackslash{}psi\_\{n+1\} = P\textasciicircum{}\{-1\}[\textbackslash{}sqrt\{I\_\{target\}\} e\textasciicircum{}\{i \textbackslash{}cdot \textbackslash{}text\{arg\}(P[\textbackslash{}psi\_n])\}]\$ Formal Technical Dissertation: An iterative phase retrieval algorithm modified for helical media. It alternates between propagation in real space (\$P\$) and intensity constraints in Fourier space to design holographic phase masks that yield specific target intensity distributions after passing through the Blob-Bit coil. Source: [7], [8]

\paragraph{Canonical Equation.}
\[
\psi_{n+1} = P^{-1}[\sqrt{I_{target}} e^{i \cdot \text{arg}(P[\psi_n])}]
\]

\paragraph{Dictionary.}
GERCHBERG-SAXTON HELICAL PROPAGATOR Canonical Statutory Formula: \$ \_n+1 = P\textasciicircum{}-1[ I\_target e\textasciicircum{}i arg(P[ \_n])]\$ Formal Technical Dissertation: An iterative phase retrieval algorithm modified for helical media.

\paragraph{Encyclopedia.}
GERCHBERG-SAXTON HELICAL PROPAGATOR Canonical Statutory Formula: ψ\_n+1 is an algebraic definition, written ψ\_n+1 = P\textasciicircum{}-1[sqrtI\_target e\textasciicircum{}i · arg(P[ψ\_n])]. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from P, I\_target, n, defining ψ\_n+1. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
