\tzpanchor{0024}
\tzpentryheader{0024}{TZP Vacuum Energy Density}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{cea266a9-90df-5dad-9382-b16921324214}}\\
\textbf{PiID} & \tzpcode{3832795028841} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{31}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{93.1973 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.1536 rad}\\
\textbf{TZPID} & \tzpcode{ID0024} & \textbf{Node Dependencies}\quad \tzpidref{0006}\\
\textbf{Registry} & \tzpcode{registry\_id\_0024} & \textbf{Scale}\quad vacuum-energy\\
\textbf{LOC Classification} & QC174.12 vacuum energy & QC178 cosmological energy density\\
\textbf{arXiv Classification} & Primary: hep-th \quad Cross-list: gr-qc, quant-ph & \\
\textbf{Primary Support} & Spectral Weighting Function & Cutoff-Controlled Vacuum Integral\\
\textbf{Closure Support} & Base-Unit Density Scaling & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The TZP vacuum energy density is the finite zero-point energy obtained by weighting vacuum modes with the Trawin spectral index and normalizing by the fourth power of the Trawin base unit.

\tzpsection{Canonical Equation}
\[
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_{T}^{4}}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,\hbar\omega\,d\omega
\]
\[
\omega_{\mathrm{cut}}=\omega_{\mathrm{cut}}(S_{\mathrm{HD}})
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\rho_{\mathrm{vac}}$: source equation symbol.
    \item $T$: source equation symbol.
    \item $u_{T}$: source equation symbol.
    \item $\omega_{\mathrm{cut}}$: angular frequency term in the source equation.
    \item $\omega$: angular frequency term in the source equation.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
    \item $S_{\mathrm{HD}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0024 generated source Wolfram model *)
ClearAll[K0024, Cr0024, T, R, A, W, I, N];
eq0024$1 = HoldForm[rhoVac^T == (1/uT^4)*Integral0^omegaCut*eta[omega]*hbaromega*domega];
eq0024$2 = HoldForm[omegaCut == omegaCut[SHD]];
eq0024$3 = HoldForm[eta[omega]];
eq0024$4 = HoldForm[Integral0^omegaCut*eta[omega]*hbaromega*domega];

K0024 = HoldForm[{eq0024$1, eq0024$2, eq0024$3, eq0024$4}];

N = "normalized TRAWIN closure object for TZP Vacuum Energy Density";
I = "Base-Unit Density Scaling integration/comparison layer";
W = "Cutoff-Controlled Vacuum Integral wave or operator carrier";
A = "Spectral Weighting Function admissible action/amplitude condition";
R = "Cutoff-Controlled Vacuum Integral rotation/curl preservation layer";
T = "Spectral Weighting Function local source condition";

Cr0024[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0024 = Cr0024[K0024];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Spectral Weighting Function local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Cutoff-Controlled Vacuum Integral rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Spectral Weighting Function admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Cutoff-Controlled Vacuum Integral wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Base-Unit Density Scaling integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP Vacuum Energy Density.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0024] TZP Vacuum Energy Density}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_T^4}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,
\hbar\omega\,
\mathrm{d}\omega .
\end{equation}

\paragraph{Primary Derivation.}
Each vacuum mode of frequency $\omega$ contributes energy proportional to:

\begin{equation}
\hbar\omega .
\end{equation}

The spectral density index $\eta(\omega)$ weights the contribution of each frequency:

\begin{equation}
\eta(\omega)\hbar\omega .
\end{equation}

Integrating over all allowed frequencies up to the cutoff $\omega_{\mathrm{cut}}$ gives the weighted vacuum energy:

\begin{equation}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\hbar\omega\,\mathrm{d}\omega .
\end{equation}

To convert this to a density in Trawin units, divide by the fourth power of the base unit:

\begin{equation}
u_T^4 .
\end{equation}

Therefore,

\begin{equation}
\boxed{
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_T^4}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,
\hbar\omega\,
\mathrm{d}\omega .
}
\end{equation}

\paragraph{Interpretation.}
$\rho_{\mathrm{vac}}^{T}$ defines vacuum energy density as a spectral integral normalized by the four-dimensional Trawin base scale.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP Vacuum Energy Density by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Spectral Weighting Function}\par
\[
\eta(\omega)
\]
\noindent This determines how each frequency contributes to the vacuum integral.\par
\noindent\textbf{2. Cutoff-Controlled Vacuum Integral}\par
\[
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,\hbar\omega\,d\omega
\]
\noindent This gathers the weighted zero-point contributions up to the span-controlled ultraviolet cutoff.\par
\noindent\textbf{3. Base-Unit Density Scaling}\par
\[
\rho_{\mathrm{vac}}^{T}
=
\frac{1}{u_{T}^{4}}
\int_{0}^{\omega_{\mathrm{cut}}}
\eta(\omega)\,\hbar\omega\,d\omega
\]
\noindent This closes the progression by converting weighted spectral energy into a density expressed in the framework's own geometric units.\par

\clearpage
\noindent\textbf{[ID 0024] TZP Vacuum Energy Density}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZP Vacuum Energy Density is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The vacuum energy density at the TZP is defined as rho sub vacT=1u sub T4 integral0omega sub cut (omega)  omega domegarhotextbackslash sub vac textsuperscript T =ratio 1 utextbackslash sub T 4 textbackslash,integral sub 0 omegatextbackslash sub cut eta(omega)textbackslash,hbaromegatextbackslash, d omegarho sub vacT=u sub T41integral0omega sub cut (omega) omegadomega, where  (omega)eta(omega) (omega) is the spectral density index from ID 015 and omega sub cutomegatextbackslash sub cut omega sub cut is a high-frequency cutoff determined by HD\$. \textbackslash{}. \textbf{Contextual meaning:} The entry reads TZP Vacuum Energy Density as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Spectral Weighting Function; Cutoff-Controlled Vacuum Integral; Base-Unit Density Scaling.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub vac to the power T defines vacuum energy density as a spectral integral normalized by the four-dimensional Trawin base scale.

\tzpsection{Equation Grounding}
Equation anchors: The vacuum energy density at the TZP is defined as rho vacT=1u T4 integral0omega cuteta(omega)  omega domegarhotextbackslash vac textsuperscript T =ratio 1 utextbackslash T 4 textbackslash,integral 0 to the power omegatextbackslash cut eta(omega)textbackslash,hbaromegatextbackslash, d omegarho vacT=u T41integral0omega cuteta(omega) omegadomega, where eta(omega)eta(omega)eta(omega) is the spectral density index from ID ,015 and omega cutomegatextbackslash cut omega cut is a high-frequency cutoff determined by HD. The vacuum energy density at the TZP is defined as rho vacT=1u T4 integral0omega cuteta(omega)  omega domegarhotextbackslash vac textsuperscript T =ratio 1 utextbackslash T 4 textbackslash,integral 0 to the power omegatextbackslash cut eta(omega)textbackslash,hbaromegatextbackslash, d omegarho vacT=u T41integral0omega cuteta(omega) omegadomega, where eta(omega)eta(omega)eta(omega) is the spectral density index from ID ,015 and omega cutomegatextbackslash cut omega cut is a high-frequency cutoff determined by HD.

\tzpsection{Interpretive Role}
This quantity is the local vacuum reservoir that later cosmological and Hamiltonian entries can draw from. It turns the singularly corrected spectrum into a finite energetic observable rather than a divergent formal sum.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Tzp Ground-State Medium Energy Concentration Field}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{Ground-State Medium Concentration Field Formal Analogue}: quantum-state language for amplitudes, measurement, basis structure, or weak coupling.
\item \textbf{Concentration Field Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0024]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0024_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0024] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP Vacuum Energy Density}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the TZP vacuum energy density is the finite zero-point energy obtained by weighting
vacuum modes with the Trawin spectral index and normalizing by...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZP Vacuum Energy Density is valid as a formal dynamical law when the Hamiltonian or
energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0024_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
