\tzpanchor{0935}
\tzpentryheader{0935}{SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f48f42c0-8926-5fd0-898c-a742ddd5a4ad}}\\
\textbf{PiID} & \tzpcode{3787593751957} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{942}\\
\textbf{RTEID} & \textbf{Manifest row}\quad \tzpcode{not listed} & \textbf{Source}\quad \tzpcode{Coordinate Manifest}\\
\textbf{TZPID} & \tzpcode{ID0935} & \textbf{Node Dependencies}\quad \tzpidref{0934}\\
\textbf{Registry} & \tzpcode{registry\_id\_0935} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The synchronization timescale entry records the inverse-sixth-power orbital scaling for phase locking and the associated relaxation law for the synchronization angle. The equations form a local transfer pair: one fixes the characteristic time, and the other gives the downhill phase-flow rule.

\tzpsection{Canonical Equation}
\[
\tau_{\mathrm{sync}}\approx \frac{\omega I Q}{3k_2GM_P^2R^5}\,a^6
\]
\[
\dot{\theta}=-\frac{\partial V_{\mathrm{sync}}}{\partial\theta}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\tau_{\mathrm{sync}}$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
    \item $I$: source equation symbol.
    \item $Q$: source equation symbol.
    \item $k_2GM$: source equation symbol.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $\theta$: phase angle or local angular coordinate.
    \item $V_{\mathrm{sync}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0935 generated source Wolfram model *)
ClearAll[K0935, Cr0935, T, R, A, W, I, N];
eq0935$1 = HoldForm[tauSync == ((omega*IQ)/(3*k2*(GM_P)^2*R^5))*a^6];
eq0935$2 = HoldForm[dot[theta] == -((Partial*VSync)/Partialtheta)];

K0935 = HoldForm[{eq0935$1, eq0935$2}];

N = "normalized TRAWIN closure object for SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION";
I = "SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION integration/comparison layer";
W = "SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION wave or operator carrier";
A = "SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION admissible action/amplitude condition";
R = "SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION rotation/curl preservation layer";
T = "SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION local source condition";

Cr0935[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0935 = Cr0935[K0935];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0935] SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\tau_{\mathrm{sync}}\approx \frac{\omega I Q}{3k_2GM_P^2R^5}\,a^6
\]
\[
\dot{\theta}=-\frac{\partial V_{\mathrm{sync}}}{\partial\theta}
\]

\paragraph{Primary Derivation.}
The relation is obtained using functional and analytic properties. leading to the displayed result.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. In the TRAWIN reading, the equation functions as the generalized carrier for the entry’s information content. According to CHL, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\tau_{\mathrm{sync}}\approx \frac{\omega I Q}{3k_2GM_P^2R^5}\,a^6
\]
\[
\dot{\theta}=-\frac{\partial V_{\mathrm{sync}}}{\partial\theta}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0935] SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TZPID ENTRY 0935 is a registry definition in Quantum-Classical Transition with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This entry develops tzpid entry 0935 inside the quantum-classical transition arc of the directory. It treats the named object as a TRAWIN-admissible carrier that can be rendered, normalized, and linked forward into the surrounding registry pages. \textbf{Contextual meaning:} The entry reads TZPID ENTRY 0935 as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, TZPID ENTRY 0935 is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: endered sub math sub to sub registry sub add sub candidates sub deduped,tau sub sync approximately ratio omega I Q 3 k sub 2 G M sub P to the power 2 R to the power 5 a to the power 6,sync i q 3 k 2 g m p 2 r 5 a 6,,,30; idate,rendered sub math sub to sub registry sub add sub candidates sub deduped,dottheta = -ratio partial V sub sync partial theta ,v sync,,,30; and csv,,rendered sub math ::MB sub bf8268ce9d72 ,registry sub id sub 0423, tau sub rm sync,i approximately ratio omega sub i I sub i Q sub i 3 k sub 2,i G M sub P to the power 2 R sub i to the power 5. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Registry Null-Space Placeholder}: A highly classified, deliberately blank sector in the database left open to trap rogue data loops and prevent systemic memory overflow.
\item \textbf{Latent Identity Assignment}: The mathematical marking of an object that doesn't quite exist yet, pre-allocating a name and address for a magnetic storm before it physically forms.
\item \textbf{Ghost-File Indexing Protocol}: The process of tracking the echoes of deleted, failed reactor states to ensure the computers don't accidentally try to recreate a past disaster.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0935]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0935].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0935] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``SYNCHRONIZATION TIMESCALE AND PHASE RELAXATION is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0935].
\par\endgroup
\vfill
\endgroup
\endgroup
