\section*{ID9394: Definition of Φn |𝜕Ω}
\paragraph{Metadata.}
PiID: 5564172543709 | RTEID: RTE:P36478.9882:T3.5575 | UUID: 8db6f8d2-8fa2-5533-bb05-6e51c0cea161

\paragraph{Canonical Statement.}
e Lean Certificate Coq Certificate lemmaid0734\_resonance\_peak\_frequency\_sweep:sorry theoremid0734\_resonance\_peak\_frequency\_sweep Theoremid0734\_resonance\_peak\_frequency\_sweep Dependencies and Test Handle Dependencies [ID 0733], [ID 0700] Node registry\_id\_0734 Support Titles Mode Quantization; Dispersion Law; Boundary Condition Test Handle If the resonance pattern cannot be organized into bounded modes with the stated boundary condition, the entry fails. Canonical Equation Links 𝑘n= 𝑛𝜋 𝐿 𝜔n=𝑣 𝑘n \$Φn |𝜕Ω=0\$ [ID 0735] TOROIDAL FLUX-GATING (TRIPARTITE) TZPID ID0735 UUID a45713a6-6e19-5778-b5e2-d5231066ca1e Type Transfer Statement Scale transfer LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math-ph; Cross-list: gr-qc, math.DG Canonical Statement This entry develops toroidal flux-gating (tripartite) inside the vortex and cym

\paragraph{Canonical Equation.}
\[
Φn |𝜕Ω=0
\]

\paragraph{Dictionary.}
Definition of Φn |𝜕Ω — Φn |𝜕Ω=0

\paragraph{Encyclopedia.}
Definition of Φn |𝜕Ω is an algebraic definition, written Φn |𝜕Ω=0. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
