\tzpanchor{0001}
\tzpentryheader{0001}{TZP TRAWIN ZERO POINT}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9e677344-caa2-5920-bb58-a7932d9f1d14}}\\
\textbf{PiID} & \tzpcode{4159265358979} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{8}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{00.0000 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.0000 rad}\\
\textbf{TZPID} & \tzpcode{ID0001} & \textbf{Node Dependencies}\quad \tzpidref{0000}\\
\textbf{Registry} & \tzpcode{registry\_id\_0001} & \textbf{Scale}\quad topological\\
\textbf{LOC Classification} & QA612 algebraic topology & QA641 manifolds\\
\textbf{arXiv Classification} & Primary: math.AT \quad Cross-list: math.DG, gr-qc & \\
\textbf{Primary Support} & Encircling Loop Condition & Lemniscatic Homotopy\\
\textbf{Closure Support} & TZP Self-Intersection & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Lemniscatic Bifurcation Point of Systems At Scale.

\tzpsection{Canonical Equation}
\[
\forall \Gamma \subset M,\;
\Gamma \sim \Lambda
\]
\[
\Lambda(0)=\Lambda(1/2)=p
\]
where $\Gamma$ is any closed loop encircling the TZP and $\Lambda$ is its lemniscatic representative.

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $M$: source equation symbol.
    \item $\Lambda$: lemniscatic representative or canonical branch object.
    \item $\Gamma$: closed loop, path, or admissible trajectory in the entry domain.
    \item $G$: source equation symbol.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $W$: source equation symbol.
    \item $a(0)$: source equation symbol.
    \item $d_{p}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0001 generated source Wolfram model *)
ClearAll[K0001, Cr0001, T, R, A, W, I, N];
eq0001$1 = HoldForm[ForAll[Gamma, Implies[Gamma Subset M, SimilarTo[Gamma, Lambda]]]];
eq0001$2 = HoldForm[Lambda[0] == Lambda[1/2] == p];
eq0001$3 = HoldForm[Gamma Subset TZPSequence[M, WindP[Gamma] == 1]];
eq0001$4 = HoldForm[SimilarTo[Gamma, Lambda]];

K0001 = HoldForm[{eq0001$1, eq0001$2, eq0001$3, eq0001$4}];

N = "normalized TRAWIN closure object for TZP TRAWIN ZERO POINT";
I = "TZP Self-Intersection integration/comparison layer";
W = "Lemniscatic Homotopy wave or operator carrier";
A = "Encircling Loop Condition admissible action/amplitude condition";
R = "Lemniscatic Homotopy rotation/curl preservation layer";
T = "Encircling Loop Condition local source condition";

Cr0001[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0001 = Cr0001[K0001];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Encircling Loop Condition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Lemniscatic Homotopy rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Encircling Loop Condition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Lemniscatic Homotopy wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TZP Self-Intersection integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TZP TRAWIN ZERO POINT.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0001] TZP TRAWIN ZERO POINT}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\det(g)\big|_{p}=0 .
\end{equation}

\paragraph{Primary Derivation.}
Let $(M,g)$ be a manifold equipped with metric tensor $g$. Away from the Trawin Zero Point $p$, the metric is assumed nondegenerate:

\begin{equation}
\det(g)\neq 0,
\qquad x\neq p .
\end{equation}

At the TZP, the manifold undergoes a structural collapse of ordinary metric invertibility. This means the inverse metric $g^{-1}$ cannot be defined at $p$.

A metric tensor is invertible if and only if its determinant is nonzero. Therefore, non-invertibility at $p$ implies:

\begin{equation}
\det(g)\big|_{p}=0 .
\end{equation}

\paragraph{Interpretation.}
The TZP is marked by metric degeneracy. This is the first mathematical signature that ordinary geometry fails at the zero point and must be replaced by a Trawinistic structure.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TZP TRAWIN ZERO POINT by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Encircling Loop Condition}\par
\[
\Gamma \subset M,\qquad \operatorname{Wind}_{p}(\Gamma)=1
\]
\noindent This identifies the class of loops whose topology is sensitive to the zero point rather than ordinary ambient geometry.\par
\noindent\textbf{2. Lemniscatic Homotopy}\par
\[
\Gamma \sim \Lambda
\]
\noindent This pushes the loop into the canonical figure-eight form and makes the topological progression readable instead of merely abstract.\par
\noindent\textbf{3. TZP Self-Intersection}\par
\[
\Lambda(0)=\Lambda(1/2)=p
\]
\noindent This closes the argument by forcing both branches of the lemniscate to meet at the same singular anchor, which later drives dimensional ambiguity.\par

\clearpage
\noindent\textbf{[ID 0001] TZP TRAWIN ZERO POINT}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Trawinistic Manifold label id-001-trawinistic-manifold is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} A Trawinistic manifold is a smooth manifold (M,g) equipped with a Lorentzian metric g such that det g| sub p = 0 at the TZP and g is non-degenerate elsewhere. \textbf{Contextual meaning:} The entry reads Trawinistic Manifold label id-001-trawinistic-manifold as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This axiom is the topological engine for later dimensional branching and winding-based measurement. It is the first place where the registry shows a double-valued local passage rather than a simple smooth loop. \textbf{Lemma support:} Encircling Loop Condition; Lemniscatic Homotopy; TZP Self-Intersection.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The lemniscate is the canonical shape of TZP recurrence: two lobes, one crossing, one central point. This turns the zero point into a geometric crossing rather than a simple endpoint.

\tzpsection{Equation Grounding}
Equation anchors: det(g)biglvert sub p =0 det(g)biglvert sub p =0.

\tzpsection{Interpretive Role}
This axiom is the topological engine for later dimensional branching and winding-based measurement. It is the first place where the registry shows a double-valued local passage rather than a simple smooth loop.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Lemniscatic Self Intersection}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Lemniscatic Self Intersection Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Intersection Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0001]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0001_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0001] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TZP TRAWIN ZERO POINT}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a Trawinistic manifold is a smooth manifold (M,g) equipped with a Lorentzian metric
g such that  g|\_p = 0 at the TZP and g is non-degenerat...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Trawinistic Manifold is valid as a tensorial/geometric statement when the stated tensor
fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0001_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
