\tzpanchor{0361}
\tzpentryheader{0361}{Holographic Redundancy Principle}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e3a53ea4-7e1b-5952-859d-1042756a6f62}}\\
\textbf{PiID} & \tzpcode{1133053054882} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{368}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1401.8432 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.3098 rad}\\
\textbf{TZPID} & \tzpcode{ID0361} & \textbf{Node Dependencies}\quad \tzpidref{0360}\\
\textbf{Registry} & \tzpcode{registry\_id\_0361} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
In the recursive toroidal interpretation, local access to a single projected loop implies global access to the entire toroidal state; perturbing one loop modifies the global torus; and information is distributed holistically rather than stored at specific coordinates.

\tzpsection{Canonical Equation}
\[
\mathcal{E}:\mathcal{H}_{\mathrm{bulk}}\to\mathcal{H}_{\partial}^{\otimes r}
\]
\[
r_{\partial}\geq r_{\min},\qquad S_{\mathrm{bulk}}\leq A/(4G\hbar)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{E}$: source equation symbol.
    \item $\mathcal{H}_{\mathrm{bulk}}$: source equation symbol.
    \item $\mathcal{H}_{\partial}$: source equation symbol.
    \item $r_{\partial}$: source equation symbol.
    \item $r_{\min}$: source equation symbol.
    \item $S_{\mathrm{bulk}}$: source equation symbol.
    \item $\hbar$: reduced Planck constant carrying the quantum scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0361 generated source Wolfram model *)
ClearAll[K0361, Cr0361, T, R, A, W, I, N];
eq0361$1 = HoldForm[E[Hbulk] -> Hpartialotimesr];
eq0361$2 = HoldForm[TZPSequence[rPartial >= rMin, SBulk <= A/(4*Ghbar)]];
eq0361$3 = HoldForm[RecIE == id];

K0361 = HoldForm[{eq0361$1, eq0361$2, eq0361$3}];

N = "normalized TRAWIN closure object for Holographic Redundancy Principle";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Variation Law admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Variation Law local source condition";

Cr0361[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0361 = Cr0361[K0361];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Variation Law local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Variation Law admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Holographic Redundancy Principle.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0361] Holographic Redundancy Principle}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
S_A = -\mathrm{Tr}(\rho_A \log \rho_A).
\end{equation}

\paragraph{Primary Derivation.}
Let $\rho$ be the density matrix of a composite system partitioned into subsystems $A$ and $B$.

The reduced density matrix is:
\begin{equation}
\rho_A = \mathrm{Tr}_B(\rho).
\end{equation}

The entanglement entropy is defined as:
\begin{equation}
S_A = -\mathrm{Tr}(\rho_A \log \rho_A).
\end{equation}

\paragraph{Interpretation.}
Entropy measures quantum correlation between subsystems.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Holographic Redundancy Principle by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Variation Law}\par
\[
\mathcal{E}:\mathcal{H}_{\mathrm{bulk}}\to\mathcal{H}_{\partial}^{\otimes r}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
r_{\partial}\geq r_{\min},\qquad S_{\mathrm{bulk}}\leq A/(4G\hbar)
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\operatorname{Rec}_{i}\mathcal{E}=\operatorname{id}
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0361] Holographic Redundancy Principle}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Holographic Redundancy Principle is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} In the recursive toroidal interpretation, local access to a single projected loop implies global access to the entire toroidal state; perturbing one loop modifies the global torus; and information is distributed holistically rather than stored at specific coordinates. \textbf{Contextual meaning:} The entry reads Holographic Redundancy Principle as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Variation Law; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Entropy measures quantum correlation between subsystems.

\tzpsection{Equation Grounding}
Equation anchors: N = 153 , 600; n sub i sub i=1 to the power 153 , 600 , n sub i in S to the power 2,; and mathbf p sub i,k = r sub i,k , n sub i, r sub i,k = e to the power t sub i,k. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Information Area Saturation Bound}: The absolute thermodynamic limit stating that the total bit capacity of a volume scales only with its outer perimeter, not its internal bulk.
\item \textbf{Non-Local Data Duplication}: The physical mechanism spreading localized quantum states across a wide surface to protect against targeted disruption.
\item \textbf{Bulk-to-Boundary Reconstruction}: The mathematical identity proving that the entire 3D interior can be perfectly calculated just by reading the 2D shell.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0361]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0361_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0361] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Holographic Redundancy Principle}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} in the recursive toroidal interpretation, local access to a single projected loop
implies global access to the entire toroidal state; perturbing on...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Holographic Redundancy Principle is valid as a formal dynamical law when the Hamiltonian
or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0361_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
