\tzpanchor{0632}
\tzpentryheader{0632}{NEURAL TZP SIGNATURE DETECTION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9f58f131-a5d3-5bc3-b364-753955ef4f76}}\\
\textbf{PiID} & \tzpcode{7789609173637} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{639}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2430.8970 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.0054 rad}\\
\textbf{TZPID} & \tzpcode{ID0632} & \textbf{Node Dependencies}\quad \tzpidref{0631}\\
\textbf{Registry} & \tzpcode{registry\_id\_0632} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Frequency Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records neural tzp signature detection through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
S[\phi] = \int_M \mathcal{L}_T \left( \phi,\nabla^T\phi,g \right) \,\mathrm{d}^n x.
\]
\[
\mathcal{L}_T \left( \phi,\nabla^T\phi,g \right).
\]
\[
\boxed{ S[\phi] = \int_M \mathcal{L}_T \left( \phi,\nabla^T\phi,g \right) \,\mathrm{d}^n x. }
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $S$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $\mathcal{L}_T$: source equation symbol.
    \item $T$: source equation symbol.
    \item $n$: integer mode index.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0632 generated source Wolfram model *)
ClearAll[K0632, Cr0632, T, R, A, W, I, N];
eq0632$1 = HoldForm[S[phi] == IntegralMLTTuple[phi, Grad^Tphi, g]*d^n*x];
eq0632$2 = HoldForm[LTTuple[phi, Grad^Tphi, g]];
eq0632$3 = HoldForm[S[phi] == IntegralMLTTuple[phi, Grad^Tphi, g]*d^n*x];

K0632 = HoldForm[{eq0632$1, eq0632$2, eq0632$3}];

N = "normalized TRAWIN closure object for NEURAL TZP SIGNATURE DETECTION";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Frequency Relation admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Frequency Relation local source condition";

Cr0632[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0632 = Cr0632[K0632];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Frequency Relation local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Frequency Relation admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for NEURAL TZP SIGNATURE DETECTION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0632] NEURAL TZP SIGNATURE DETECTION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
S[\phi]
=
\int_M
\mathcal{L}_T
\left(
\phi,\nabla^T\phi,g
\right)
\,\mathrm{d}^n x .
\end{equation}

\paragraph{Primary Derivation.}
Let $\phi$ be a field defined on the Trawinistic manifold $M$.  
The local dynamics are encoded in a Trawinistic Lagrangian density:

\begin{equation}
\mathcal{L}_T
\left(
\phi,\nabla^T\phi,g
\right).
\end{equation}

This density depends on the field, its Trawinistic covariant derivative, and the metric structure.

The total action is obtained by integrating the density over the manifold:

\begin{equation}
\boxed{
S[\phi]
=
\int_M
\mathcal{L}_T
\left(
\phi,\nabla^T\phi,g
\right)
\,\mathrm{d}^n x .
}
\end{equation}

\paragraph{Interpretation.}
The action functional is the master quantity from which the Trawinistic field equations are derived.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors NEURAL TZP SIGNATURE DETECTION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Frequency Relation}\par
\[
S[\phi] = \int_M \mathcal{L}_T \left( \phi,\nabla^T\phi,g \right) \,\mathrm{d}^n x.
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
\mathcal{L}_T \left( \phi,\nabla^T\phi,g \right).
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
\boxed{ S[\phi] = \int_M \mathcal{L}_T \left( \phi,\nabla^T\phi,g \right) \,\mathrm{d}^n x. }
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0632] NEURAL TZP SIGNATURE DETECTION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
NEURAL TZP SIGNATURE DETECTION is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} text Signal = text SQUID output star text EEG phase. \textbf{Contextual meaning:} The entry reads NEURAL TZP SIGNATURE DETECTION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Frequency Relation; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
The action functional is the master quantity from which the Trawinistic field equations are derived.

\tzpsection{Equation Grounding}
Equation anchors: text Signal = SQUID output star EEG phase; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Cognitive Zero-Point Echo}: The search for the incredibly faint, ghostly ripple in the brain waves that proves the biological mind actually briefly touched the terrifying, infinite void of the quantum singularity.
\item \textbf{Macroscopic Singularity Scarring}: The observation of permanent, recognizable damage left behind in the firing patterns of the neurons, serving as undeniable proof that the violent quantum event actually happened.
\item \textbf{Brain-Wave Anomaly Isolation}: The filtering of millions of lines of normal, boring biological data to find the one, impossible, mathematically perfect spike that could only have come from the zero-point core.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0632]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0632_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0632] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont NEURAL TZP SIGNATURE DETECTION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records neural tzp signature detection through the Septenary derivation layer,
using the displayed relations as operational anchors for t...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``NEURAL TZP SIGNATURE DETECTION is valid when the stated operator maps admissible inputs
into the declared target class.''\\
\textbf{Proof:} The source statement is read as an operator or transformation. The proof obligation is
type preservation: admissible inputs must land in the target object without breaking the
stated constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- operator-closure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0632_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
