\tzpanchor{0466}
\tzpentryheader{0466}{17.23 Bit Information Density Tracking}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{2eeab4a9-9199-504c-b398-29a39e0e9a76}}\\
\textbf{PiID} & \tzpcode{6735188575272} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{473}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1794.0486 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.9560 rad}\\
\textbf{TZPID} & \tzpcode{ID0466} & \textbf{Node Dependencies}\quad \tzpidref{0465}\\
\textbf{Registry} & \tzpcode{registry\_id\_0466} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Scaling Law\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 466 establishes the quantification of information density in TZP systems. Each state transition within the 153,600 dimensional manifold encodes approximately 17.23 bits. Tracking this is critical for the "Dual Channel" extraction architecture efficiency. Capacity Monitoring: Ensures the left vortex channel operates near the Bekenstein and Holevo bounds. Transition Logging: Records bits per measurement to maintain information energy balance.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
C = 17 \text{ bits per state transition}
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $C$: speed of light or relativistic conversion factor.
    \item $\delta(x,x')$: point-source delta term that anchors the Green-function response.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $x'$: source point paired with the response point $x$.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0466 generated source Wolfram model *)
ClearAll[K0466, Cr0466, T, R, A, W, I, N];
eq0466$1 = HoldForm[$C == 17*$];

K0466 = HoldForm[{eq0466$1}];

N = "normalized TRAWIN closure object for 17.23 Bit Information Density Tracking";
I = "17.23 Bit Information Density Tracking integration/comparison layer";
W = "17.23 Bit Information Density Tracking wave or operator carrier";
A = "17.23 Bit Information Density Tracking admissible action/amplitude condition";
R = "17.23 Bit Information Density Tracking rotation/curl preservation layer";
T = "17.23 Bit Information Density Tracking local source condition";

Cr0466[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0466 = Cr0466[K0466];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ 17.23 Bit Information Density Tracking local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ 17.23 Bit Information Density Tracking rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ 17.23 Bit Information Density Tracking admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ 17.23 Bit Information Density Tracking wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ 17.23 Bit Information Density Tracking integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for 17.23 Bit Information Density Tracking.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0466] 17.23 Bit Information Density Tracking}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\delta S = 0.
\end{equation}

\paragraph{Primary Derivation.}
Dominant contributions to path integral arise from stationary action paths.

Thus classical trajectories satisfy:
\begin{equation}
\boxed{\delta S = 0.}
\end{equation}

\paragraph{Interpretation.}
Classical paths emerge from quantum stationary phase.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors 17.23 Bit Information Density Tracking by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
C = 17 \text{ bits per state transition}
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0466] 17.23 Bit Information Density Tracking}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
17.23 Bit Information Density Tracking is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 466 establishes the quantification of information density in TZP systems. Each state transition within the 153,600 dimensional manifold encodes approximately 17.23 bits. Tracking this is critical for the "Dual Channel" extraction architecture efficiency. Capacity Monitoring: Ensures the left vortex channel operates near the Bekenstein and Holevo bounds. Transition Logging: Records bits per measurement to maintain information energy balance.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
C = 17 \text{ bits per state transition}
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 466 establishes the quantification of information density in TZP systems. Each state transition within the 153,600 dimensional manifold encodes approximately 17.23 bits. Tracking this is critical for the "Dual Channel" extraction architecture efficiency. Capacity Monitoring: Ensures the left vortex channel operates near the Bekenstein and Holevo bounds. Transition Logging: Records bits per measurement to maintain information energy balance.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors 17.23 Bit Information Density Tracking by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
17.23 Bit Information Density Tracking; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0466]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0466].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0466] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont 17.23 Bit Information Density Tracking}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} mathcal\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} = log\textbackslash{}\_2(153,600) approximately 17.23 text\textbackslash{} bits/state transition\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``17.23 BIT INFORMATION DENSITY TRACKING is valid as a formal dynamical law when the
Hamiltonian or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0466].
\par\endgroup
\vfill
\endgroup
\endgroup
