\tzpanchor{0692}
\tzpentryheader{0692}{Conservation Law: Information Flux Through TZP}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{bfd7dacb-25be-5167-bddd-0785f221d560}}\\
\textbf{PiID} & \tzpcode{9258923542019} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{699}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2656.1239 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.3765 rad}\\
\textbf{TZPID} & \tzpcode{ID0692} & \textbf{Node Dependencies}\quad \tzpidref{0691}\\
\textbf{Registry} & \tzpcode{registry\_id\_0692} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Diagnostic Definition & Scaling Relation\\
\textbf{Closure Support} & Normalized Regime & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records conservation law: information flux through tzp through the Septenary derivation layer, using the displayed relations as operational anchors for the canonical equation chain.

\tzpsection{Canonical Equation}
\[
G=SO(3)\ltimes_{\varphi} U(1).
\]
\[
(R,e^{i\alpha})\cdot(R',e^{i\beta}) = \left( RR', e^{i\alpha}\varphi_R(e^{i\beta}) \right).
\]
\[
\boxed{ (R,e^{i\alpha})\cdot(R',e^{i\beta}) = \left( RR', e^{i\alpha}\varphi_R(e^{i\beta}) \right). }
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $G$: source equation symbol.
    \item $U$: auxiliary source state or local chart variable.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $e_T$: exponential damping factor encoding potential-induced suppression.
    \item $\ltimes_{\varphi}$: source equation symbol.
    \item $\alpha$: source equation symbol.
    \item $\varphi$: source equation symbol.
    \item $\beta$: source equation symbol.
    \item $S$: source equation symbol.
    \item $O(3)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0692 generated source Wolfram model *)
ClearAll[K0692, Cr0692, T, R, A, W, I, N];
eq0692$1 = HoldForm[G == SO[3]*ltimesPhiU[1]];
eq0692$2 = HoldForm[Tuple[R, Exp[I*alpha]]*Tuple[Derivative[1][R], Exp[I*beta]] == Tuple[Derivative[1][RR], Exp[I*alpha]*phiR[Exp[I*beta]]]];
eq0692$3 = HoldForm[Tuple[R, Exp[I*alpha]]*Tuple[Derivative[1][R], Exp[I*beta]] == Tuple[Derivative[1][RR], Exp[I*alpha]*phiR[Exp[I*beta]]]];

K0692 = HoldForm[{eq0692$1, eq0692$2, eq0692$3}];

N = "normalized TRAWIN closure object for Conservation Law: Information Flux Through TZP";
I = "Normalized Regime integration/comparison layer";
W = "Scaling Relation wave or operator carrier";
A = "Diagnostic Definition admissible action/amplitude condition";
R = "Scaling Relation rotation/curl preservation layer";
T = "Diagnostic Definition local source condition";

Cr0692[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0692 = Cr0692[K0692];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Diagnostic Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Scaling Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Diagnostic Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Scaling Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Regime integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Conservation Law: Information Flux Through TZP.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0692] Conservation Law: Information Flux Through TZP}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
G=SO(3)\ltimes_{\varphi} U(1).
\end{equation}

\paragraph{Composition Law.}
\begin{equation}
(R,e^{i\alpha})\cdot(R',e^{i\beta})
=
\left(
RR',
e^{i\alpha}\varphi_R(e^{i\beta})
\right).
\end{equation}

\paragraph{Primary Derivation.}
If rotation and gauge phase compose independently, the group is a direct product.  
If rotations act on gauge phase through an automorphism $\varphi_R$, the coupled group is a semi-direct product:

\begin{equation}
G=SO(3)\ltimes_{\varphi}U(1).
\end{equation}

The product law becomes:
\begin{equation}
\boxed{
(R,e^{i\alpha})\cdot(R',e^{i\beta})
=
\left(
RR',
e^{i\alpha}\varphi_R(e^{i\beta})
\right).
}
\end{equation}

\paragraph{Interpretation.}
Rotation and phase are treated as interacting symmetry sectors rather than merely adjacent labels.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Conservation Law: Information Flux Through TZP by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Diagnostic Definition}\par
\[
G=SO(3)\ltimes_{\varphi} U(1).
\]
\noindent This defines the scalar diagnostic or conversion quantity named by the title.\par
\noindent\textbf{2. Scaling Relation}\par
\[
(R,e^{i\alpha})\cdot(R',e^{i\beta}) = \left( RR', e^{i\alpha}\varphi_R(e^{i\beta}) \right).
\]
\noindent This elevates the quantity into a comparative scaling or correlation law.\par
\noindent\textbf{3. Normalized Regime}\par
\[
\boxed{ (R,e^{i\alpha})\cdot(R',e^{i\beta}) = \left( RR', e^{i\alpha}\varphi_R(e^{i\beta}) \right). }
\]
\noindent This closes the entry by normalizing the diagnostic against a stated reference regime.\par

\clearpage
\noindent\textbf{[ID 0692] Conservation Law: Information Flux Through TZP}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Conservation Law: Information Flux Through TZP is a registry definition in Gyromagnetic and Rotating-Frame Physics with secondary pressure from Vortex and Cymatic Transport.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} integral rho,dV. \textbf{Contextual meaning:} The entry reads Conservation Law: Information Flux Through TZP as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons. \textbf{Lemma support:} Diagnostic Definition; Scaling Relation; Normalized Regime.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Rotation and phase are treated as interacting symmetry sectors rather than merely adjacent labels.

\tzpsection{Equation Grounding}
Equation anchors: oint sub partial Sigma T to the power mu u sub vac n sub mu dSigma sub nu = Res(TZP); V(phi) = ratio lambda 4 (phi to the power 2 - v to the power 2) to the power 2 + V sub lemniscate [r, theta] + sum sub n=1 to the power 153,600 delta(r - r sub n) dot Phi sub nodal; and \$oint sub partial Sigma T to the power mu u sub vac n sub mu dSigma sub nu = Res(TZP). Proof route: show that the named quantity is dimensionless or consistently scaled in the regime stated by the entry. Formalization route: prove that the normalized diagnostic remains invariant under the intended rescaling.

\tzpsection{Interpretive Role}
The entry turns a named scalar quantity into a portable diagnostic that can anchor nearby comparisons.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Event-Horizon Data Scrubbing}: The incredibly controversial, terrifying theory that when information falls into the tiny black hole, the universe literally erases it, permanently violating the most fundamental rule of quantum mechanics.
\item \textbf{Holographic Singularity Bounding}: The counter-theory desperately arguing that the data isn't lost, it's just been perfectly, flawlessly painted onto the invisible 2D wall surrounding the crushed, zero-volume core.
\item \textbf{Null-Space Information Leakage}: The tiny, paranoid calculation checking to see if the precious answers we need are accidentally falling down the drain, completely lost to humanity forever.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0692]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0692_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0692] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Conservation Law: Information Flux Through TZP}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the entry records conservation law: information flux through tzp through the Septenary
derivation layer, using the displayed relations as operation...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Conservation Law: Information Flux Through TZP is valid when the total tensorial
quantity is conserved under the stated constraint.''\\
\textbf{Proof:} The source statement identifies a conserved balance law. Reading 0692 as a proposition,
validity follows by requiring the full stress, flux, or current contribution to be
included before the divergence or balance condition is evaluated.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conserved total-structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0692_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
