\tzpanchor{0643}
\tzpentryheader{0643}{Gauss Linking Number and Topological Invariant}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{ddf3a6f0-142b-5397-8844-3a7bcbdda6d5}}\\
\textbf{PiID} & \tzpcode{3717872146844} & \textbf{TZPi}\quad \tzpcode{2}\quad \textbf{PiPE}\quad \tzpcode{650}\\
\textbf{RTEID} & \textbf{Manifest row}\quad \tzpcode{not listed} & \textbf{Source}\quad \tzpcode{Coordinate Manifest}\\
\textbf{TZPID} & \tzpcode{ID0643} & \textbf{Node Dependencies}\quad \tzpidref{0642}\\
\textbf{Registry} & \tzpcode{registry\_id\_0643} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Variation Law & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Gauss linking number records the topological linking of two closed curves through the double contour integral $Lk=\frac{1}{4\pi}\oint_{C_1}\oint_{C_2}\frac{(\mathbf{r}_1-\mathbf{r}_2)\cdot(\mathrm{d}\mathbf{r}_1\times\mathrm{d}\mathbf{r}_2)}{|\mathbf{r}_1-\mathbf{r}_2|^3}$.

\tzpsection{Canonical Equation}
\[
\tzpfitmath{Lk = \frac{1}{4\pi} \oint_{C_1} \oint_{C_2} \frac{ (\mathbf{r}_1-\mathbf{r}_2) \cdot (\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2) }{ |\mathbf{r}_1-\mathbf{r}_2|^3 }.}
\]
\[
\mathbf{r}_1-\mathbf{r}_2.
\]
\[
\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2.
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $Lk$: Gauss linking number of the two closed curves.
    \item $\pi$: circular constant in the Gauss-integral normalization.
    \item $C_1$: first closed curve or flux-tube path.
    \item $C_2$: second closed curve or flux-tube path.
    \item $r_1$: position vector on the first curve.
    \item $r_2$: position vector on the second curve.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0643 generated source Wolfram model *)
ClearAll[K0643, Cr0643, T, R, A, W, I, N];
eq0643$1 = HoldForm[TZPFitMath[Lk == (1/(4*Pi))*ContourIntegralC1ContourIntegralC2[((r1 - r2)*(dr1*dr2))/Abs[r1 - r2]^3]]];
eq0643$2 = HoldForm[r1 - r2];
eq0643$3 = HoldForm[dr1*dr2];

K0643 = HoldForm[{eq0643$1, eq0643$2, eq0643$3}];

N = "normalized TRAWIN closure object for Gauss Linking Number and Topological Invariant";
I = "Gauss Linking Number and Topological Invariant integration/comparison layer";
W = "Gauss Linking Number and Topological Invariant wave or operator carrier";
A = "Gauss Linking Number and Topological Invariant admissible action/amplitude condition";
R = "Gauss Linking Number and Topological Invariant rotation/curl preservation layer";
T = "Gauss Linking Number and Topological Invariant local source condition";

Cr0643[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0643 = Cr0643[K0643];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Gauss Linking Number and Topological Invariant local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Gauss Linking Number and Topological Invariant rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Gauss Linking Number and Topological Invariant admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Gauss Linking Number and Topological Invariant wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Gauss Linking Number and Topological Invariant integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Gauss Linking Number and Topological Invariant.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0643] Gauss Linking Number and Topological Invariant}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\begingroup\small
\paragraph{Primary Equation.}
\begin{equation}
Lk
=
\frac{1}{4\pi}
\oint_{C_1}
\oint_{C_2}
\frac{
(\mathbf{r}_1-\mathbf{r}_2)
\cdot
(\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2)
}{
|\mathbf{r}_1-\mathbf{r}_2|^3
}.
\end{equation}

\paragraph{Primary Derivation.}
Let $C_1$ and $C_2$ be two closed magnetic flux tubes or field-line loops.  
The Gauss linking integral measures how many times the two loops wind around one another.

For points $\mathbf{r}_1\in C_1$ and $\mathbf{r}_2\in C_2$, the relative displacement is:

\begin{equation}
\mathbf{r}_1-\mathbf{r}_2 .
\end{equation}

The oriented area element generated by the two path differentials is:

\begin{equation}
\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2 .
\end{equation}

Normalizing by the cubic separation gives the universal linking density:

\begin{equation}
\frac{
(\mathbf{r}_1-\mathbf{r}_2)
\cdot
(\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2)
}{
|\mathbf{r}_1-\mathbf{r}_2|^3
}.
\end{equation}

The full linking number is:

\begin{equation}
\boxed{
Lk
=
\frac{1}{4\pi}
\oint_{C_1}
\oint_{C_2}
\frac{
(\mathbf{r}_1-\mathbf{r}_2)
\cdot
(\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2)
}{
|\mathbf{r}_1-\mathbf{r}_2|^3
}.
}
\end{equation}

\paragraph{Wolfram Form.}
\begin{verbatim}
Lk == (1/(4*Pi))*
  Integrate[
    Dot[r1 - r2, Cross[dr1, dr2]]/Norm[r1 - r2]^3,
    {r1, C1}, {r2, C2}
  ]
\end{verbatim}

\paragraph{Interpretation.}
The linking number is integer-valued and topologically stable. It supplies the universal counting rule behind helicity quantisation.
\endgroup

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The double contour integral records oriented linking for the paired closed curves and supplies the invariant used by later topology applications.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\tzpfitmath{Lk = \frac{1}{4\pi} \oint_{C_1} \oint_{C_2} \frac{ (\mathbf{r}_1-\mathbf{r}_2) \cdot (\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2) }{ |\mathbf{r}_1-\mathbf{r}_2|^3 }.}
\]
\[
\mathbf{r}_1-\mathbf{r}_2.
\]
\[
\mathrm{d}\mathbf{r}_1\times \mathrm{d}\mathbf{r}_2.
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0643] Gauss Linking Number and Topological Invariant}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small

\tzpsection{Definition}

The Gauss linking number is an integer-valued invariant measuring oriented winding between two disjoint closed curves. It records linking that cannot be removed through continuous deformation without curve intersection.

\tzpsection{Contextual Meaning}

For closed field-line or flux-tube paths, \(Lk\) counts mutual linking. The curves may bend or move while retaining this number so long as they do not cross; appearance can change while topological connectedness remains fixed.

\tzpsection{Formal Statement}

\[
Lk=\frac{1}{4\pi}\oint_{C_1}\oint_{C_2}\frac{(\mathbf{r}_1-\mathbf{r}_2)\cdot(\mathrm{d}\mathbf{r}_1\times\mathrm{d}\mathbf{r}_2)}{|\mathbf{r}_1-\mathbf{r}_2|^3}
\]

\tzpsection{Derivable Consequences}

Smooth deformations without intersection preserve \(Lk\). Reversing one curve's orientation reverses its sign; topologically unlinked curves have zero linking number under the standard reading.

\tzpsection{Lemma Support}

The approved aligned source supplies the integral and identifies \(Lk\), paths \(C_1\), \(C_2\), and position vectors \(\mathbf{r}_1\), \(\mathbf{r}_2\). Later helicity readings remain applications.

\tzpsection{Technical Interpretation}

The difference vector records separation, the cross product of path differentials records orientation, and cubic distance normalization weights contributions before double integration.

\tzpsection{Equation Grounding}

\(Lk\) is the Gauss linking number of the two closed curves; \(C_1\) and \(C_2\) are the first and second closed curves or flux-tube paths; and \(\mathbf{r}_1\), \(\mathbf{r}_2\) are their respective position vectors.

\tzpsection{Interpretive Role}

This entry anchors topological counting with a precise invariant later pages may apply to linked flux or helicity models.

\tzpsection{TZP Thesaurus}

\noindent \textbf{Gauss Linking Number}: The integer topological count of oriented winding between two closed curves. \enspace\textbullet\enspace \textbf{Closed Curve Pair}: The two paths over which the double contour integral is evaluated. \enspace\textbullet\enspace \textbf{Topological Invariance}: Preservation of linking under deformation that does not allow the curves to cross.\par

\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0643].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0643] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Gauss Linking Number and Topological Invariant}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} TZPID ENTRY 0643 is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TZPID ENTRY 0643 is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0643].
\par\endgroup
\vfill
\endgroup
\endgroup
