\section*{ID8494: HYBRID INFORMATION CAPACITY Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 9709683408005 | RTEID: RTE:P32984.0883:T4.0822 | UUID: bdb66c27-40ba-5927-8ff2-4e730baf87bf

\paragraph{Canonical Statement.}
[ID 1168] HYBRID INFORMATION CAPACITY Canonical Statutory Formula: \$C\_\{TZP\} \textbackslash{}approx S\_\{temp\} + S\_\{atemp\} + I\_\{ent\} \textbackslash{}approx 17 \textbackslash{}text\{ bits\}\$ Formal Technical Dissertation: Establishes the specific information density of a TZP transition. It combines classical measurement capacity (\textasciitilde{}5-7 bits), quantum capacity (\textasciitilde{}5-7 qubits), and entanglement entropy (\textasciitilde{}3-5 bits) to yield the distinct signature of \textasciitilde{}17 bits per state transition, exceeding standard Shannon or Holevo limits. Source: [10], [11], [12]

\paragraph{Canonical Equation.}
\[
C_{TZP} \approx S_{temp} + S_{atemp} + I_{ent} \approx 17 \text{ bits}
\]

\paragraph{Dictionary.}
HYBRID INFORMATION CAPACITY Canonical Statutory Formula: \$C\_TZP S\_temp + S\_atemp + I\_ent 17 bits\$ Formal Technical Dissertation: Establishes the specific information density of a TZP transition.

\paragraph{Encyclopedia.}
HYBRID INFORMATION CAPACITY Canonical Statutory Formula is a scaling / order-of-magnitude relation, written C\_TZP ≈ S\_temp + S\_atemp + I\_ent ≈ 17 bits. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from C\_TZP, S\_temp, S\_atemp, I\_ent. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
