\section*{ID8575: Definition of √ ηϵÔ}
\paragraph{Metadata.}
PiID: 0951702835297 | RTEID: RTE:P33298.6293:T4.6004 | UUID: 510d8fb5-7a99-5427-a21b-f2fc8780b115

\paragraph{Canonical Statement.}
g information registers. Source: [ID 1063] ANGULAR MOMENTUM TRANSFER LOGIC Canonical Statutory For-mula: \$dLsystem \$ \$dt \$ + \$dLfield \$ \$dt \$ = \$τexternal \$ Formal Technical Dissertation: Ensures conservation dur-ing extraction. Angular momentum density is transferred through the TZP coupling, providing the back-torque that stabilizes the turbine against "Metric Wind." Source: [ID 1064] WEAK MEASUREMENT FEEDBACK LOOP Canonical Statutory Formula: \$M̂weak \$ = \$Î \$ + \$√ ηϵÔ =⇒ dr \$ = \$√ η⟨Ô⟩dt+ dW√ \$ \$η \$ Formal Technical Dissertation: Defines the con-tinuous monitoring strategy. Weak measurements extract a record without collapsing the state, enabling real-time feedback control to maximize efficiency while respecting uncertainty limits. Source: [ID 1065] CARNOT EFFICIENCY LIMITS \$(ηtotal) \$ Canonical Statutory Formula: \$ηtotal \$ = \$ηcoupling \$ × \$ηextr

\paragraph{Canonical Equation.}
\[
√ ηϵÔ =⇒ dr
\]

\paragraph{Dictionary.}
Definition of √ ηϵÔ — √ ηϵÔ =⇒ dr

\paragraph{Encyclopedia.}
Definition of √ ηϵÔ is an algebraic definition, written √ ηϵÔ =⇒ dr. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from r, defining √ ηϵÔ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
