\section*{ID9337: Definition of Φ++Φ−}
\paragraph{Metadata.}
PiID: 8883215137556 | RTEID: RTE:P36257.6445:T3.1928 | UUID: 0e3661ae-596c-5689-9eec-6ddaeb47dd56

\paragraph{Canonical Statement.}
n Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0138], [ID 0024] Node registry\_id\_0139 Support Titles Flux Cancellation Law; Cosmological-Density Scaling; Flux-Ratio Residual Test Handle If balanced total flux cannot coexist with a nontrivial residual ratio that feeds the radius law, the emergence statement fails. Canonical Equation Links \$Φ++Φ−=0 𝜌Λ∼\$ ℏ𝑐 𝑅4 \$ΞΦ ΞΦ= Φ+ Φ−\$ [ID 0140] Dipole Energy 1/d4 Scaling Law TZPID ID0140 UUID 962c75ec-f1b2-55d4-b8ba-6d03776ca28e Type Universal Energy Scaling Law Scale Planck-to-cosmic dipole coupling LOC Classification Working routing: QC174 interaction laws; QB981 cosmology arXiv Classification Primary: math-ph Cross-list: gr-qc, hep-th Canonical Statement The dipole energy law closes the cosmic subsecti

\paragraph{Canonical Equation.}
\[
Φ++Φ−=0 𝜌Λ∼
\]

\paragraph{Dictionary.}
Definition of Φ++Φ− — Φ++Φ−=0 𝜌Λ∼

\paragraph{Encyclopedia.}
Definition of Φ++Φ− is an algebraic definition, written Φ++Φ−=0 𝜌Λ∼. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
