\section*{ID8792: TEMPORAL BELL INEQUALITY Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 6025152274299 | RTEID: RTE:P34141.2885:T5.9889 | UUID: 8f0b6309-b564-5f0f-9c4f-4e7cb47d3028

\paragraph{Canonical Statement.}
[ID 1170] TEMPORAL BELL INEQUALITY Canonical Statutory Formula: \$| \textbackslash{}langle A\_0 B\_0 \textbackslash{}rangle + \textbackslash{}langle A\_0 B\_1 \textbackslash{}rangle + \textbackslash{}langle A\_1 B\_0 \textbackslash{}rangle - \textbackslash{}langle A\_1 B\_1 \textbackslash{}rangle | > 2\$ Formal Technical Dissertation: The validation metric for the temporal channel. Here, measurements \$A\$ and \$B\$ are performed not at spacelike separation, but at timelike separation (\$t\_\{then\}\$ and \$t\_\{now\}\$). Violation of the inequality confirms genuine entanglement across time, ruling out classical pre-determination. Source: [9]

\paragraph{Canonical Equation.}
\[
| \langle A_0 B_0 \rangle + \langle A_0 B_1 \rangle + \langle A_1 B_0 \rangle - \langle A_1 B_1 \rangle | > 2
\]

\paragraph{Dictionary.}
TEMPORAL BELL INEQUALITY Canonical Statutory Formula: \$ A\_0 B\_0 + A\_0 B\_1 + A\_1 B\_0 - A\_1 B\_1 2\$ Formal Technical Dissertation: The validation metric for the temporal channel.

\paragraph{Encyclopedia.}
TEMPORAL BELL INEQUALITY Canonical Statutory Formula is an expectation / trace over state, written | ⟨ A\_0 B\_0 ⟩ + ⟨ A\_0 B\_1 ⟩ + ⟨ A\_1 B\_0 ⟩ - ⟨ A\_1 B\_1 ⟩ | > 2. It is computed as an expectation value or trace over a quantum state, producing an observable. It is built from A\_0, B\_0, B\_1, A\_1. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
