\section*{ID9100: Definition of B}
\paragraph{Metadata.}
PiID: 6909411303150 | RTEID: RTE:P35337.3209:T1.6764 | UUID: 1ac71b29-8e46-54b1-8c01-b9a43e055cc7

\paragraph{Canonical Statement.}
evels; boundaryinduced vacuum effects; existence of waveguidelike resonances; relation to Casimirtype phenomena. Falsifiability / Test Handle: Measurements of mode spectra in cavities or waveguides placed in curved settings that differ from predictions would falsify this definition. 0.0.57 ID 055: BoundaryInduced Quantum Effects Type: Operator Formal Statement: The boundary effect operator BBB acts on a field \textbackslash{}phi by modifying its mode expansion coefficients according to the boundary geometry; \$B=nbn(∂Ω)nB\textbackslash{}phi\$ = \$\textbackslash{}sum\_nb\_n(\textbackslash{}partial\textbackslash{}Omega), \textbackslash{}phi\_nB\$ = \$nbn(∂Ω)n,\$ where coefficients bnb\_nbn capture topological and curvature contributions. Interpretive Meaning: Boundaries in the Trawinistic manifold alter quantum fields; the operator encapsulates how edges, surfaces and topological defects influence field configurations and energies. Dependencies: ID 054 Derivable Consequences: Casimir pressures; bounda

\paragraph{Canonical Equation.}
\[
B=nbn(∂Ω)nB\phi
\]

\paragraph{Dictionary.}
Definition of B — B=nbn(∂Ω)nBφ

\paragraph{Encyclopedia.}
Definition of B is an algebraic definition, written B=nbn(∂Ω)nBφ. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from φ, n, b, defining B. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
