\tzpanchor{0092}
\tzpentryheader{0092}{Semi-Direct Product of Rotation and Gauge Symmetry}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{483bff3e-a305-5ea4-9d61-e7848f09c240}}\\
\textbf{PiID} & \tzpcode{2117067982148} & \textbf{TZPi}\quad \tzpcode{7}\quad \textbf{PiPE}\quad \tzpcode{99}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{357.2564 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.5886 rad}\\
\textbf{TZPID} & \tzpcode{ID0092} & \textbf{Node Dependencies}\quad \tzpidref{0045}\\
\textbf{Registry} & \tzpcode{registry\_id\_0092} & \textbf{Scale}\quad group-structured dynamics\\
\textbf{LOC Classification} & QA174 Lie groups & QC793 gauge-rotation coupling\\
\textbf{arXiv Classification} & Primary: math-ph \quad Cross-list: hep-th, math.RT & \\
\textbf{Primary Support} & Separate Symmetry Factors & Semi-Direct Product Group\\
\textbf{Closure Support} & Coupled Composition Rule & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Rotations and gauge phases are intertwined; this structure yields unique conserved quantities and constraints.

\tzpsection{Canonical Equation}
\[
G = SO(3) \ltimes_{\varphi} U(1)
\]
\[
(R,e^{i\alpha})\cdot(R',e^{i\beta})
=
\left(RR', e^{i\alpha}\,\varphi_R(e^{i\beta})\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $G$: source equation symbol.
    \item $U$: auxiliary source state or local chart variable.
    \item $R$: global radius, boundary radius, or topological scale.
    \item $e_T$: exponential damping factor encoding potential-induced suppression.
    \item $\ltimes_{\varphi}$: source equation symbol.
    \item $\alpha$: source equation symbol.
    \item $\varphi$: source equation symbol.
    \item $\beta$: source equation symbol.
    \item $S$: source equation symbol.
    \item $O(3)$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0092 generated source Wolfram model *)
ClearAll[K0092, Cr0092, T, R, A, W, I, N];
eq0092$1 = HoldForm[G == SO[3]*ltimesPhi*U[1]];
eq0092$2 = HoldForm[Tuple[R, Exp[I*alpha]]*Tuple[Derivative[1][R], Exp[I*beta]] == Tuple[Derivative[1][RR], Exp[I*alpha]*phiR[Exp[I*beta]]]];
eq0092$3 = HoldForm[TZPSequence[SO[3], U[1]]];

K0092 = HoldForm[{eq0092$1, eq0092$2, eq0092$3}];

N = "normalized TRAWIN closure object for Semi-Direct Product of Rotation and Gauge Symmetry";
I = "Coupled Composition Rule integration/comparison layer";
W = "Semi-Direct Product Group wave or operator carrier";
A = "Separate Symmetry Factors admissible action/amplitude condition";
R = "Semi-Direct Product Group rotation/curl preservation layer";
T = "Separate Symmetry Factors local source condition";

Cr0092[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0092 = Cr0092[K0092];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Separate Symmetry Factors local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Semi-Direct Product Group rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Separate Symmetry Factors admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Semi-Direct Product Group wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Coupled Composition Rule integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Semi-Direct Product of Rotation and Gauge Symmetry.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0092] Semi-Direct Product of Rotation and Gauge Symmetry}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
G=SO(3)\ltimes_{\varphi} U(1).
\end{equation}

\paragraph{Composition Law.}
\begin{equation}
(R,e^{i\alpha})\cdot(R',e^{i\beta})
=
\left(
RR',
e^{i\alpha}\varphi_R(e^{i\beta})
\right).
\end{equation}

\paragraph{Primary Derivation.}
If rotation and gauge phase compose independently, the group is a direct product.  
If rotations act on gauge phase through an automorphism $\varphi_R$, the coupled group is a semi-direct product:

\begin{equation}
G=SO(3)\ltimes_{\varphi}U(1).
\end{equation}

The product law becomes:
\begin{equation}
\boxed{
(R,e^{i\alpha})\cdot(R',e^{i\beta})
=
\left(
RR',
e^{i\alpha}\varphi_R(e^{i\beta})
\right).
}
\end{equation}

\paragraph{Interpretation.}
Rotation and phase are treated as interacting symmetry sectors rather than merely adjacent labels.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Semi-Direct Product of Rotation and Gauge Symmetry by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Separate Symmetry Factors}\par
\[
SO(3),\qquad U(1)
\]
\noindent This identifies the two symmetry sectors before coupling.\par
\noindent\textbf{2. Semi-Direct Product Group}\par
\[
G = SO(3) \ltimes_{\varphi} U(1)
\]
\noindent This introduces the coupled symmetry object itself.\par
\noindent\textbf{3. Coupled Composition Rule}\par
\[
(R,e^{i\alpha})\cdot(R',e^{i\beta})
=
\left(RR', e^{i\alpha}\,\varphi_R(e^{i\beta})\right)
\]
\noindent This closes the progression by making the rotational action on the gauge sector explicit.\par

\clearpage
\noindent\textbf{[ID 0092] Semi-Direct Product of Rotation and Gauge Symmetry}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Semi-Direct Product of Rotation and Gauge Symmetry is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Rotations and gauge phases are intertwined; this structure yields unique conserved quantities and constraints. \textbf{Contextual meaning:} The entry reads Semi-Direct Product of Rotation and Gauge Symmetry as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This entry sharpens the previous bundle statement by telling us how the combined symmetry composes. It is the algebraic rule needed to model rotation and phase as genuinely interacting rather than merely adjacent symmetries. \textbf{Lemma support:} Separate Symmetry Factors; Semi-Direct Product Group; Coupled Composition Rule.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Rotation and phase are treated as interacting symmetry sectors rather than merely adjacent labels.

\tzpsection{Equation Grounding}
Equation anchors: The full symmetry group of gyromagnetic systems is the semi-direct product SO(3) U(1)SO(3)textbackslash ltimes U(1)SO(3) U(1), reflecting the fact that gauge phases transform under rotations; mathematically, (R,eialpha) (R ,eibeta)=(RR ,ei(alpha+beta))(R, etextsuperscript ialpha )dot(R e ibeta ) = (RR e to the power i(alpha+beta) )(R,eialpha) (R ,eibeta)=(RR ,ei(alpha+beta)) up to an automorphism. The full symmetry group of gyromagnetic systems is the semi-direct product SO(3) U(1)SO(3)textbackslash ltimes U(1)SO(3) U(1), reflecting the fact that gauge phases transform under rotations; mathematically, (R,eialpha) (R ,eibeta)=(RR ,ei(alpha+beta))(R, etextsuperscript ialpha )dot(R e ibeta ) = (RR e to the power i(alpha+beta) )(R,eialpha) (R ,eibeta)=(RR ,ei(alpha+beta)) up to an automorphism.

\tzpsection{Interpretive Role}
This entry sharpens the previous bundle statement by telling us how the combined symmetry composes. It is the algebraic rule needed to model rotation and phase as genuinely interacting rather than merely adjacent symmetries.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Semi Direct Product Rotation Symmetry Freedom}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Symmetry Freedom Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Symmetry Freedom Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0092]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0092_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0092] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Semi-Direct Product of Rotation and Gauge Symmetry}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} rotations and gauge phases are intertwined; this structure yields unique conserved
quantities and constraints

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Semi-Direct Product of Rotation and Gauge Symmetry is valid when the total tensorial
quantity is conserved under the stated constraint.''\\
\textbf{Proof:} The source statement identifies a conserved balance law. Reading 0092 as a proposition,
validity follows by requiring the full stress, flux, or current contribution to be
included before the divergence or balance condition is evaluated.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conserved total-structure validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0092_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
