\tzpanchor{0190}
\tzpentryheader{0190}{Seed Rotation and Magnetic Moment at Emergence}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{d197deea-5a60-57b0-9df5-3bba7093a0a1}}\\
\textbf{PiID} & \tzpcode{5493038196442} & \textbf{TZPi}\quad \tzpcode{8}\quad \textbf{PiPE}\quad \tzpcode{197}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{737.8122 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.2157 rad}\\
\textbf{TZPID} & \tzpcode{ID0190} & \textbf{Node Dependencies}\quad \tzpidref{0189}\\
\textbf{Registry} & \tzpcode{registry\_id\_0190} & \textbf{Scale}\quad cosmic\\
\textbf{LOC Classification} & QB planetary dynamics & QC electromagnetism\\
\textbf{arXiv Classification} & Primary: astro-ph.EP & Cross-list: hep-th, physics.space-ph\\
\textbf{Primary Support} & Seed Rotation & Magnetic Moment\\
\textbf{Closure Support} & Emergence State & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
At a TZP emergence, matter is born with inherent magnetic moment and rotation, seeding later Elsasser number convergence; this accounts for ubiquitous rotation and magnetism in planets and stars.

\tzpsection{Canonical Equation}
\[
\boldsymbol{\mu} \neq 0
\]
\[
\mathbf{\omega} \neq 0
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mu$: source equation symbol.
    \item $\omega$: angular frequency term in the source equation.
    \item $\mathcal{K}_{0190}$: canonical registry object for entry ID 0190.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0190 generated source Wolfram model *)
ClearAll[K0190, Cr0190, T, R, A, W, I, N];
eq0190$1 = HoldForm[mu != 0];
eq0190$2 = HoldForm[omega != 0];
eq0190$3 = HoldForm[TZPNormalizeWrap[mu, omega]];

K0190 = HoldForm[{eq0190$1, eq0190$2, eq0190$3}];

N = "normalized TRAWIN closure object for Seed Rotation and Magnetic Moment at Emergence";
I = "Normalized Closure integration/comparison layer";
W = "Second Support wave or operator carrier";
A = "First Support admissible action/amplitude condition";
R = "Second Support rotation/curl preservation layer";
T = "First Support local source condition";

Cr0190[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0190 = Cr0190[K0190];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ First Support local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Second Support rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ First Support admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Second Support wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Seed Rotation and Magnetic Moment at Emergence.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0190] Seed Rotation and Magnetic Moment at Emergence}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\boldsymbol{\mu} \neq 0
\]
\[
\mathbf{\omega} \neq 0
\]

\paragraph{Primary Derivation.}
To derive the stated relation through direct evaluation of the expression. giving the formula in the first line.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. Within the TRAWIN framework, the equation functions as the generalized carrier for the entry’s information content. Within the CHL view, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Seed Rotation and Magnetic Moment at Emergence by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. First Support}\par
\[
\boldsymbol{\mu} \neq 0
\]
\noindent This support equation moves the entry from the abstract claim toward a concrete first measurable relation.\par
\noindent\textbf{2. Second Support}\par
\[
\mathbf{\omega} \neq 0
\]
\noindent This support equation adds the second structural constraint needed to narrow the admissible TRAWIN reading.\par
\noindent\textbf{3. Normalized Closure}\par
\[
\tzpnormalizewrap{\boldsymbol{\mu},\mathbf{\omega},\text{emergence}}
\]
\noindent This normalized closure ties the support terms together and closes the progression under the TRAWIN frame.\par

\clearpage
\noindent\textbf{[ID 0190] Seed Rotation and Magnetic Moment at Emergence}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Seed Rotation and Magnetic Moment at Emergence is a Derivable Prediction  . At a TZP emergence, matter is born with inherent magnetic moment and rotation, seeding later Elsasser number convergence; this accounts for ubiquitous rotation and magnetism in planets and stars.  

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} At a TZP emergence, matter is born with inherent magnetic moment and rotation, seeding later Elsasser number convergence; this accounts for ubiquitous rotation and magnetism in planets and stars.  
\textbf{Contextual meaning:} Emergent matter inherits spin and magnetic fields from the vacuum fold; these initial conditions drive gyromagnetic dynamics observed across scales.
\textbf{Derivable consequences:} Source evidence records the entry as a reusable object whose consequences should be read from the matched formal statement and local proof route.
\textbf{Lemma support:} At a TZP emergence, matter is born with inherent magnetic moment and rotation, seeding later Elsasser number convergence; this accounts for ubiquitous rotation and magnetism in planets and stars.  \par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Observing a significantly lower binary star formation rate or random pairing inconsistent with the lemniscate prediction would falsify this entry. ID 190: Seed Rotation and Magnetic Moment at Emergence  

\tzpsection{Equation Grounding}
At a TZP emergence, matter is born with inherent magnetic moment and rotation, seeding later Elsasser number convergence; this accounts for ubiquitous rotation and magnetism in planets and stars.  

\tzpsection{Interpretive Role}
Emergent matter inherits spin and magnetic fields from the vacuum fold; these initial conditions drive gyromagnetic dynamics observed across scales.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{First Support}: The nonvanishing condition for the seeded magnetic moment.
\item \textbf{Second Support}: The nonvanishing condition for the seeded rotational velocity.
\item \textbf{Normalized Closure}: The normalization of the emergent seed conditions under the TRAWIN framework.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0190]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0190_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0190] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Seed Rotation and Magnetic Moment at Emergence}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} at a TZP emergence, matter is born with inherent magnetic moment and rotation, seeding
later Elsasser number convergence; this accounts for ubiquit...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Seed Rotation and Magnetic Moment at Emergence is valid as a formal registry statement
when its source equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that at a TZP emergence, matter is born with inherent
magnetic moment and rotation, seeding later Elsasser number convergence; this accounts
for ubiquitous rotation and magnetism in planets and stars. Matter is born with
intrinsic rotation and magnetic moment at emergence.. The CHL validation treats the
equation as the formal anchor and the semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0190_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
