\section*{ID9080: Relation: 12ρ(Ωr)2(1)/(2)ρ, (Ω,r)ˆ221ρ(Ωr)2.}
\paragraph{Metadata.}
PiID: 1844396582533 | RTEID: RTE:P35259.6565:T1.5484 | UUID: e0adcc27-5a93-5341-9e16-1e76b19b9773

\paragraph{Canonical Statement.}
01 14 Trawin Zero Point Contextus Canonicus Falsifiability / Test Handle: Observation of sustained deviations from \$Λ≈1\textbackslash{}Lambda\textbackslash{}approx1Λ≈1\$ in systems expected to follow the unification theory would falsify this definition. 0.0.41 ID 039: Magnetic–Coriolis Energy Equipartition Type: Conservation Law Formal Statement: In the vicinity of the Elsasser attractor, the magnetic energy density \$B22µ\textbackslash{}frac\{\textbackslash{}mathbf\{B\}ˆ2\}\{2\textbackslash{}mu\}2µB2\$ equals the kinetic energy density associated with differential rotation \$12ρ(Ωr)2\textbackslash{}frac\{1\}\{2\}\textbackslash{}rho, (\textbackslash{}Omega,r)ˆ221ρ(Ωr)2.\$ Interpretive Meaning: Magnetic and rotational energies equilibrate in systems obeying the unification principle. This equipartition explains why \$Λ\textbackslash{}LambdaΛ\$ remains near unity. Dependencies: ID 038 Derivable Consequences: Sets scaling relations between magnetic field and rotation rate; informs universal scaling laws; influences stability criteria; ties into helicity quantisation. Falsifiability

\paragraph{Canonical Equation.}
\[
12ρ(Ωr)2\frac{1}{2}\rho, (\Omega,r)ˆ221ρ(Ωr)2.
\]

\paragraph{Dictionary.}
Relation: 12ρ(Ωr)2(1)/(2)ρ, (Ω,r)ˆ221ρ(Ωr)2. — 12ρ(Ωr)2(1)/(2)ρ, (Ω,r)ˆ221ρ(Ωr)2.

\paragraph{Encyclopedia.}
Relation: 12ρ(Ωr)2(1)/(2)ρ, (Ω,r)ˆ221ρ(Ωr)2. is a symbolic expression, written 12ρ(Ωr)2(1)/(2)ρ, (Ω,r)ˆ221ρ(Ωr)2.. It introduces a symbol or relation used elsewhere in the framework. It is built from ρ, Ω, r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
