\section*{ID9858: Numerical Simulation of TZP Vortices: iħ ∂\_t Ψ}
\paragraph{Metadata.}
PiID: 9140359989535 | RTEID: RTE:P38280.8032:T0.2431 | UUID: e920dfd4-b5d1-5cb9-9a45-9ba7bfccb7c1

\paragraph{Canonical Statement.}
Numerical protocols are specified that solve an effective Schrödinger-type equation \textbackslash{}begin\{equation\} i\textbackslash{}hbar \textbackslash{}partial\_t \textbackslash{}Psi = \textbackslash{}Htrawin[\textbackslash{}Psi,t], \textbackslash{}end\{equation\} with boundary conditions encoding Bessel-like radial profiles and azimuthal phase factors corresponding to vortex winding numbers. Spatial discretization schemes (e.g. tensor product grids with pseudo-spectral differentiation) and time-stepping methods (e.g. method of lines) are prescribed to simulate vortex evolution, convergence towards TZP-attractor states, and sensitivity to cymatic or gravitational modulation.

\paragraph{Canonical Equation.}
\[
i\hbar \partial_t \Psi = \Htrawin[\Psi,t],
\]

\paragraph{Dictionary.}
Numerical protocols are specified that solve an effective Schrödinger-type equation with boundary conditions encoding Bessel-like radial profiles and azimuthal phase factors corresponding to vortex winding numbers.

\paragraph{Encyclopedia.}
Numerical Simulation of TZP Vortices: iħ ∂\_t Ψ is a differential equation, written iħ ∂\_t Ψ = Htrawin[Ψ,t]. It relates the quantity to its derivatives, governing how the system evolves in space and time. It is built from Ψ, defining iħ ∂\_t Ψ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
