\tzpanchor{0156}
\tzpentryheader{0156}{Higher Gerbe Structure}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{06ed5405-01b0-5b24-95c8-cb7ab2e75859}}\\
\textbf{PiID} & \tzpcode{4502841027019} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{163}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{605.7826 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.9981 rad}\\
\textbf{TZPID} & \tzpcode{ID0156} & \textbf{Node Dependencies}\quad \tzpidref{0155}\\
\textbf{Registry} & \tzpcode{registry\_id\_0156} & \textbf{Scale}\quad higher-bundle organization of the unified field\\
\textbf{LOC Classification} & QA612 higher cohomology & QA169 higher categories\\
\textbf{arXiv Classification} & Primary: math.AT \quad Cross-list: hep-th, math-ph & \\
\textbf{Primary Support} & Band Definition & Triple-Overlap Cocycle\\
\textbf{Closure Support} & Classifying-Space Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A global geometric object generalizing line bundles encodes nontrivial three-form flux H3H\_3H3 and automorphisms of the Hilbert--tangent bundle.

\tzpsection{Canonical Equation}
\[
\mathrm{Band}(\mathcal{H}_{\mathrm{gerbe}})
=
\operatorname{Aut}\!\left(\mathcal{H}_{\mathrm{Hilbert}}\otimes T\mathcal{M}\right)
\]
\[
g_{ijk}
=
\exp\!\left(2\pi i\int_{U_{ijk}} H_3\right)
\]
\[
B\mathcal{H}_{\mathrm{gerbe}}\simeq K(\mathbb{Z},3)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{H}_{\mathrm{gerbe}}$: source equation symbol.
    \item $\mathcal{H}_{\mathrm{Hilbert}}$: source equation symbol.
    \item $T$: source equation symbol.
    \item $\mathcal{M}$: source equation symbol.
    \item $g_{ijk}$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $U_{ijk}$: source equation symbol.
    \item $H_3$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $K$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0156 generated source Wolfram model *)
ClearAll[K0156, Cr0156, T, R, A, W, I, N];
eq0156$1 = HoldForm[Band[HGerbe] == Aut[HHilbertTensorProduct*TM]];
eq0156$2 = HoldForm[gIjk == exp[2*Pi*iIntegralUijkH3]];
eq0156$3 = HoldForm[SimilarTo[BHGerbe, eq*K[Z, 3]]];

K0156 = HoldForm[{eq0156$1, eq0156$2, eq0156$3}];

N = "normalized TRAWIN closure object for Higher Gerbe Structure";
I = "Classifying-Space Closure integration/comparison layer";
W = "Triple-Overlap Cocycle wave or operator carrier";
A = "Band Definition admissible action/amplitude condition";
R = "Triple-Overlap Cocycle rotation/curl preservation layer";
T = "Band Definition local source condition";

Cr0156[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0156 = Cr0156[K0156];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Band Definition local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Triple-Overlap Cocycle rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Band Definition admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Triple-Overlap Cocycle wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Classifying-Space Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Higher Gerbe Structure.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0156] Higher Gerbe Structure}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathrm{Band}(\mathcal{H}_{\mathrm{gerbe}})
=
\operatorname{Aut}\!\left(\mathcal{H}_{\mathrm{Hilbert}}\otimes T\mathcal{M}\right)
\]
\[
g_{ijk}
=
\exp\!\left(2\pi i\int_{U_{ijk}} H_3\right)
\]
\[
B\mathcal{H}_{\mathrm{gerbe}}\simeq K(\mathbb{Z},3)
\]

\paragraph{Primary Derivation.}
The expression \( \mathrm{Band}(\mathcal{H}_{\mathrm{gerbe}}) \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. In the TRAWIN reading, the equation functions as the integral carrier for the entry’s information content. Within the CHL view, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Higher Gerbe Structure by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Band Definition}\par
\[
\mathrm{Band}(\mathcal{H}_{\mathrm{gerbe}})
=
\operatorname{Aut}\!\left(\mathcal{H}_{\mathrm{Hilbert}}\otimes T\mathcal{M}\right)
\]
\noindent This specifies the automorphism structure carried by the higher gerbe.\par
\noindent\textbf{2. Triple-Overlap Cocycle}\par
\[
g_{ijk}
=
\exp\!\left(2\pi i\int_{U_{ijk}} H_3\right)
\]
\noindent This gives the higher patching data on triple overlaps.\par
\noindent\textbf{3. Classifying-Space Closure}\par
\[
B\mathcal{H}_{\mathrm{gerbe}}\simeq K(\mathbb{Z},3)
\]
\noindent This closes the progression by identifying the homotopy classifying target for the structure.\par

\clearpage
\noindent\textbf{[ID 0156] Higher Gerbe Structure}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Higher Gerbe Structure is a canonical-registry. The unified field includes a higher gerbe with band Aut (VectorBundle[HHilbert TM])\textbackslash{}operatorname\{Aut\}(\textbackslash{}text\{VectorBundle\}[\textbackslash{}mathcal\{H\}\_\{\textbackslash{}text\{H ilbert\}\} \textbackslash{}otimes T\textbackslash{}mathcal\{M\}])Aut(VectorBundle[HHilbert  TM]),  ech 2 cocycle exp (2 i   H3)\textbackslash{}exp(2\textbackslash{}pi i \textbackslash{}int\textbackslash{}int\textbackslash{}int H\_3)exp(2 i   H3 ), and classifying space K(Z,3)K(\textbackslash{}mathbb\{Z\}, 3)K(Z,3).

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The unified field includes a higher gerbe with band Aut (VectorBundle[HHilbert TM])\textbackslash{}operatorname\{Aut\}(\textbackslash{}text\{VectorBundle\}[\textbackslash{}mathcal\{H\}\_\{\textbackslash{}text\{H ilbert\}\} \textbackslash{}otimes T\textbackslash{}mathcal\{M\}])Aut(VectorBundle[HHilbert  TM]),  ech 2 cocycle exp (2 i   H3)\textbackslash{}exp(2\textbackslash{}pi i \textbackslash{}int\textbackslash{}int\textbackslash{}int H\_3)exp(2 i   H3 ), and classifying space K(Z,3)K(\textbackslash{}mathbb\{Z\}, 3)K(Z,3).
\textbf{Contextual meaning:} CS = Tr[F   4  1    F] A =   A dx +     B + gravitational C electromagnetic Aut(VectorBundle[H   Hilbert TM]) exp(2 i H )     3 K(Z, 3) H 3
\textbf{Derivable consequences:} Source evidence records the entry as a reusable object whose consequences should be read from the matched formal statement and local proof route.
\textbf{Lemma support:} The unified field includes a higher gerbe with band Aut (VectorBundle[HHilbert TM])\textbackslash{}operatorname\{Aut\}(\textbackslash{}text\{VectorBundle\}[\textbackslash{}mathcal\{H\}\_\{\textbackslash{}text\{H ilbert\}\} \textbackslash{}otimes T\textbackslash{}mathcal\{M\}])Aut(VectorBundle[HHilbert  TM]),  ech 2 cocycle exp (2 i   H3)\textbackslash{}exp(2\textbackslash{}pi i \textbackslash{}int\textbackslash{}int\textbackslash{}int H\_3)exp(2 i   H3 ), and classifying space K(Z,3)K(\textbackslash{}mathbb\{Z\}, 3)K(Z,3).\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
CS = Tr[F   4  1    F] A =   A dx +     B + gravitational C electromagnetic Aut(VectorBundle[H   Hilbert TM]) exp(2 i H )     3 K(Z, 3) H 3

\tzpsection{Equation Grounding}
The unified field includes a higher gerbe with band Aut (VectorBundle[HHilbert TM])\textbackslash{}operatorname\{Aut\}(\textbackslash{}text\{VectorBundle\}[\textbackslash{}mathcal\{H\}\_\{\textbackslash{}text\{H ilbert\}\} \textbackslash{}otimes T\textbackslash{}mathcal\{M\}])Aut(VectorBundle[HHilbert  TM]),  ech 2 cocycle exp (2 i   H3)\textbackslash{}exp(2\textbackslash{}pi i \textbackslash{}int\textbackslash{}int\textbackslash{}int H\_3)exp(2 i   H3 ), and classifying space K(Z,3)K(\textbackslash{}mathbb\{Z\}, 3)K(Z,3).

\tzpsection{Interpretive Role}
CS = Tr[F   4  1    F] A =   A dx +     B + gravitational C electromagnetic Aut(VectorBundle[H   Hilbert TM]) exp(2 i H )     3 K(Z, 3) H 3
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Band Definition}: The specification of the automorphism structure carried by the higher gerbe.
\item \textbf{Triple-Overlap Cocycle}: The provision of the higher patching data on triple overlaps.
\item \textbf{Classifying-Space Closure}: The identification of the homotopy classifying target for the structure.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0156]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0156_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0156] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Higher Gerbe Structure}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} a global geometric object generalizing line bundles encodes nontrivial three-form flux
H3H\textbackslash{}\_3H3 and automorphisms of the Hilbert--tangent bundle

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Higher Gerbe Structure is valid as a tensorial/geometric statement when the stated
tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0156_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
