\tzpanchor{0435}
\tzpentryheader{0435}{Power Extraction Tensor}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{e0542273-72be-58f3-8e3b-326cee5810ac}}\\
\textbf{PiID} & \tzpcode{6117931051185} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{442}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1689.2016 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.7833 rad}\\
\textbf{TZPID} & \tzpcode{ID0435} & \textbf{Node Dependencies}\quad \tzpidref{0434}\\
\textbf{Registry} & \tzpcode{registry\_id\_0435} & \textbf{Scale}\quad Quantum-Classical Transition\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Unified Density & Euler-Lagrange Flow\\
\textbf{Closure Support} & Stationary Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
ID 435 defines the real time power flow through the torus surface via the stress energy tensor T nu. For centimeter scale devices, the maximum power output is estimated in the microwatt to milliwatt range, scaling inversely with the square of the dimension a. The Poynting vector represents the flux of extracted energy directed into the storage manifold. Flux Density: Energy is concentrated via magnetic field interactions at the superconducting boundaries. Scaling Laws: Parallel arrays are utilized to increase total power output beyond single unit limits.

\tzpsection{Canonical Equation}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathrm{Cl}(T^{\ast}M)=\bigoplus_{k=0}^{\dim M}\Lambda^{k}T^{\ast}M
$
\end{adjustbox}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $M$: source equation symbol.
    \item $\Lambda$: lemniscatic representative or canonical branch object.
    \item $G_{\mathrm{T}}(x,x')$: Trawinistic Green function.
    \item $\Box_{\mathrm{T}}$: Trawinistic wave operator governing propagation on the TZP background.
    \item $\delta(x,x')$: point-source delta term that anchors the Green-function response.
    \item $V_{T}(x,x')$: TZP potential or suppression kernel between source and response points.
    \item $x'$: source point paired with the response point $x$.
    \item $\ast$: source equation symbol.
    \item $C$: speed of light or relativistic conversion factor.
    \item $T^{\ast}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0435 generated source Wolfram model *)
ClearAll[K0435, Cr0435, T, R, A, W, I, N];
eq0435$1 = HoldForm[$Cl[T^ast*M] == bigoplusK0^(Dim*M)*Lambda^k*T^ast*M$];

K0435 = HoldForm[{eq0435$1}];

N = "normalized TRAWIN closure object for Power Extraction Tensor";
I = "Power Extraction Tensor integration/comparison layer";
W = "Power Extraction Tensor wave or operator carrier";
A = "Power Extraction Tensor admissible action/amplitude condition";
R = "Power Extraction Tensor rotation/curl preservation layer";
T = "Power Extraction Tensor local source condition";

Cr0435[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0435 = Cr0435[K0435];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Power Extraction Tensor local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Power Extraction Tensor rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Power Extraction Tensor admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Power Extraction Tensor wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Power Extraction Tensor integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Power Extraction Tensor.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0435] Power Extraction Tensor}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\Box_T G_T(x,x')
=
-\delta(x,x') .
\end{equation}

\paragraph{Primary Derivation.}
Let $G_T(x,x')$ be the Green function or propagator for a scalar field on the Trawinistic background.

The propagator is defined as the response at $x$ to a point source at $x'$.  
The appropriate wave operator is the Trawinistic d'Alembertian:

\begin{equation}
\Box_T .
\end{equation}

For a Green function, applying the wave operator returns the negative delta source:

\begin{equation}
\Box_T G_T(x,x')
=
-\delta(x,x') .
\end{equation}

Thus,

\begin{equation}
\boxed{
\Box_T G_T(x,x')
=
-\delta(x,x') .
}
\end{equation}

Boundary conditions are chosen to remain compatible with the TZP structure and may include exponential suppression induced by $V_T$.

\paragraph{Interpretation.}
The TZP propagator measures how field disturbances travel through a Trawinistic background with degenerate geometry and zero-point boundary structure.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Power Extraction Tensor by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathrm{Cl}(T^{\ast}M)=\bigoplus_{k=0}^{\dim M}\Lambda^{k}T^{\ast}M
$
\end{adjustbox}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0435] Power Extraction Tensor}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Power Extraction Tensor is a registry definition in the active TZPID arc.

\tzpsection{Contextual Meaning}
ID 435 defines the real time power flow through the torus surface via the stress energy tensor T nu. For centimeter scale devices, the maximum power output is estimated in the microwatt to milliwatt range, scaling inversely with the square of the dimension a. The Poynting vector represents the flux of extracted energy directed into the storage manifold. Flux Density: Energy is concentrated via magnetic field interactions at the superconducting boundaries. Scaling Laws: Parallel arrays are utilized to increase total power output beyond single unit limits.

\tzpsection{Formal Statement}
\[
\begin{adjustbox}{max width=\linewidth,center}
$\displaystyle
\mathrm{Cl}(T^{\ast}M)=\bigoplus_{k=0}^{\dim M}\Lambda^{k}T^{\ast}M
$
\end{adjustbox}
\]

\tzpsection{Technical Interpretation}
ID 435 defines the real time power flow through the torus surface via the stress energy tensor T nu. For centimeter scale devices, the maximum power output is estimated in the microwatt to milliwatt range, scaling inversely with the square of the dimension a. The Poynting vector represents the flux of extracted energy directed into the storage manifold. Flux Density: Energy is concentrated via magnetic field interactions at the superconducting boundaries. Scaling Laws: Parallel arrays are utilized to increase total power output beyond single unit limits.

\tzpsection{Equation Grounding}
The equation grounding is carried by the canonical equation and the source Wolfram model on the entry page.

\tzpsection{Interpretive Role}
The canonical equation anchors Power Extraction Tensor by connecting the source condition to the derivation layer and proof certificate.

\tzpsection{TZP Thesaurus}
Power Extraction Tensor; canonical operator; source equation; TRAWIN-normalized relation.
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0435]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0435].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0435] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Power Extraction Tensor}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} p = int\textbackslash{}\_\textbackslash{}\textbackslash{} (T\textasciicircum{}\textbackslash{}\_\textbackslash{}) * dvec\textbackslash{} implies P\textbackslash{}\_\textbackslash{}\textbackslash{} frac c\textasciicircum{}2\textbackslash{}\textasciicircum{}2\textbackslash{}

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``POWER EXTRACTION TENSOR (T\textasciicircum{}\{\textbackslash{}mu\textbackslash{}nuu\_\{\textbackslash{}nu) is valid as a tensorial/geometric statement
when the stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0435].
\par\endgroup
\vfill
\endgroup
\endgroup
