\section*{ID9472: Definition of 𝐻rot}
\paragraph{Metadata.}
PiID: 6050492212424 | RTEID: RTE:P36781.8795:T4.0566 | UUID: b32bd2dc-e889-58ef-b42e-5fdf22854464

\paragraph{Canonical Statement.}
ppendix for [ID 0219] Isabelle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0218], [ID 0200] Node registry\_id\_0219 Support Titles Rotating Hamiltonian; Unitary Evolution; Berry Phase Test Handle If the rotating Hamiltonian does not induce the stated unitary cycle and Berry phase, the entry fails. Canonical Equation Links \$𝐻rot=−ℏΩ·𝐽\$ 𝑈 (𝑡 )=exp(−𝑖𝐻rot𝑡/ℏ) 𝑔𝑎𝑚𝑚𝑎B= \$∫ 2𝜋/Ω\$ 0 \$⟨𝜓\$ (𝑡 ) |𝑖𝜕𝑡 |𝜓 (𝑡 ) \$⟩\$ 𝑑𝑡 [ID 0220] Spin Functor to Hilbert Space TZPID ID0220 UUID 7b7c4c2b-1200-5079-817b-13a7f6f159ae Type Operator / Transfer Statement Scale transfer LOC Classification Working routing: QA329 operator theory; QA169 categorical structure arXiv Classification Primary: math.CT; Cross-list: math-ph, cs.LO Canonical Statement This en

\paragraph{Canonical Equation.}
\[
𝐻rot=−ℏΩ·𝐽
\]

\paragraph{Dictionary.}
Definition of 𝐻rot — 𝐻rot=−ℏΩ·𝐽

\paragraph{Encyclopedia.}
Definition of 𝐻rot is an algebraic definition, written 𝐻rot=−ℏΩ·𝐽. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
