\section*{ID9104: Definition of µdgdµ}
\paragraph{Metadata.}
PiID: 4113031509526 | RTEID: RTE:P35352.8538:T1.7020 | UUID: abf955b0-90d6-5d3d-b6cd-887ec52b0a63

\paragraph{Canonical Statement.}
ential for topological phases. Falsifiability / Test Handle: Observing no critical behaviour where the theory predicts a quantum phase transition would challenge this definition. 0.0.60 ID 058: Renormalization Flow as Dimensional Navigation Type: Structural Constraint Formal Statement: The renormalization group flow on the Trawinistic manifold is interpreted as navigation through effective dimensions defined by the hyperdimensional span; coupling constants \$g(µ)g(\textbackslash{}mu)g(µ)\$ evolve according to \$µdgdµ=β(g,dimeff)\textbackslash{}mu\textbackslash{}frac\{\textbackslash{}text\{d\}g\}\{\textbackslash{}text\{d\}\textbackslash{}mu\}\$ = \$\textbackslash{}beta(g,\textbackslash{}dim \{\textbackslash{}text\{eff\}\})µdµdg=β(g,dimeff),\$ where dimeff\textbackslash{}dim\_\{\textbackslash{}text\{eff\}\}dimeff varies near the TZP. Interpretive Meaning: Changes in scale correspond to moving through spaces of different effective dimension; the zero point provides a pivot for dimensional transitions. Dependencies: ID 009, ID 057 Derivable Consequences: Explanation of dimensional crossovers; predictions of scaledependent

\paragraph{Canonical Equation.}
\[
µdgdµ=β(g,dimeff)\mu\frac{\text{d}g}{\text{d}\mu}
\]

\paragraph{Dictionary.}
Definition of µdgdµ — µdgdµ=β(g,dimeff)μ(dg)/(dμ)

\paragraph{Encyclopedia.}
Definition of µdgdµ is an algebraic definition, written µdgdµ=β(g,dimeff)μ(dg)/(dμ). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from μ, g, m, f, defining µdgdµ. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
