\section*{ID8955: ENTRAINMENT FREQUENCY FIELD Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 7524960357996 | RTEID: RTE:P34774.2537:T0.7486 | UUID: b6e94a7f-18c7-520d-bfe2-5f3b9b54e109

\paragraph{Canonical Statement.}
[ID 870] ENTRAINMENT FREQUENCY FIELD Canonical Statutory Formula: \$F\_e(x, t) := \textbackslash{}frac\{\textbackslash{}partial \textbackslash{}Psi\}\{\textbackslash{}partial t\} + \textbackslash{}nabla \textbackslash{}cdot \textbackslash{}Omega\$ Formal Technical Dissertation: A composite field describing spatiotemporal modulation in resonant entrainment, derived from the wavefunction time derivative and the divergence of the Omega field. Source: [19]

\paragraph{Canonical Equation.}
\[
F_e(x, t) := \frac{\partial \Psi}{\partial t} + \nabla \cdot \Omega
\]

\paragraph{Dictionary.}
ENTRAINMENT FREQUENCY FIELD Canonical Statutory Formula: \$F\_e(x, t) := t + \$ Formal Technical Dissertation: A composite field describing spatiotemporal modulation in resonant entrainment, derived from the wavefunction time derivative and the divergence of the Omega field.

\paragraph{Encyclopedia.}
ENTRAINMENT FREQUENCY FIELD Canonical Statutory Formula is a variational / legendre derivative, written F\_e(x, t) := (∂ Ψ)/(∂ t) + ∇ · Ω. It arises from a variational or Legendre procedure, defining conjugate quantities or stationarity conditions. It is built from ∂, Ψ, ∇, Ω, F\_e, x. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
