\section*{ID8498: BIOLOGICAL COHERENCE PROTECTION Canonical Statutory Formula: τ\_coh > 10\textasciicircum{}3 ×…}
\paragraph{Metadata.}
PiID: 6834080053559 | RTEID: RTE:P32999.6212:T4.1077 | UUID: 11defca8-ddff-53f8-acbb-18e18eb5665d

\paragraph{Canonical Statement.}
[ID 1172] BIOLOGICAL COHERENCE PROTECTION Canonical Statutory Formula: \$\textbackslash{}tau\_\{coh\} > 10\textasciicircum{}3 \textbackslash{}times \textbackslash{}frac\{\textbackslash{}hbar\}\{k\_B T\}\$ Formal Technical Dissertation: Explains quantum effects in warm biological systems. It asserts that "bridge-tunnel" structures at TZP sites (like microtubules) provide topological protection, extending coherence times by orders of magnitude beyond thermal decoherence predictions. Source: [19], [20]

\paragraph{Canonical Equation.}
\[
\tau_{coh} > 10^3 \times \frac{\hbar}{k_B T}
\]

\paragraph{Dictionary.}
BIOLOGICAL COHERENCE PROTECTION Canonical Statutory Formula: τ\_coh 10\textasciicircum{}3 × (ħ)/(k\_B T) Formal Technical Dissertation: Explains quantum effects in warm biological systems.

\paragraph{Encyclopedia.}
BIOLOGICAL COHERENCE PROTECTION Canonical Statutory Formula: τ\_coh > 10\textasciicircum{}3 ×… is an inequality / bound, written τ\_coh > 10\textasciicircum{}3 × (ħ)/(k\_B T). It states an inequality or bound that constrains the admissible range of the quantity. It is built from ħ, c, o, h, k\_B, T. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
