\tzpanchor{0899}
\tzpentryheader{0899}{ENTRAINMENT GRADIENT}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f17b0b59-dcfb-5980-bdf3-c87976e5c618}}\\
\textbf{PiID} & \tzpcode{3598253490428} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{906}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3436.6515 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{05.6625 rad}\\
\textbf{TZPID} & \tzpcode{ID0899} & \textbf{Node Dependencies}\quad \tzpidref{0898}\\
\textbf{Registry} & \tzpcode{registry\_id\_0899} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Geometric Constraint & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records entrainment gradient through a normalized Nonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0899}}:\mathcal{X}_{\mathrm{id0899}}\longrightarrow\mathcal{Y}_{\mathrm{id0899}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0899}})=\mathcal{O}_{\mathrm{id0899}}
\]
\[
\mathcal{O}_{\mathrm{id0899}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0899}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0899}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0899}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0899 generated source Wolfram model *)
ClearAll[K0899, Cr0899, T, R, A, W, I, N];
eq0899$1 = HoldForm[Oid0899[Xid0899] -> Yid0899];
eq0899$2 = HoldForm[NTRAWIN[OId0899] == OId0899];
eq0899$3 = HoldForm[Element[OId0899[x], YAdm]];

K0899 = HoldForm[{eq0899$1, eq0899$2, eq0899$3}];

N = "normalized TRAWIN closure object for ENTRAINMENT GRADIENT";
I = "ENTRAINMENT GRADIENT integration/comparison layer";
W = "ENTRAINMENT GRADIENT wave or operator carrier";
A = "ENTRAINMENT GRADIENT admissible action/amplitude condition";
R = "ENTRAINMENT GRADIENT rotation/curl preservation layer";
T = "ENTRAINMENT GRADIENT local source condition";

Cr0899[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0899 = Cr0899[K0899];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ ENTRAINMENT GRADIENT local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ ENTRAINMENT GRADIENT rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ ENTRAINMENT GRADIENT admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ ENTRAINMENT GRADIENT wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ ENTRAINMENT GRADIENT integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for ENTRAINMENT GRADIENT.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0899] ENTRAINMENT GRADIENT}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0899}}:\mathcal{X}_{\mathrm{id0899}}\longrightarrow \mathcal{Y}_{\mathrm{id0899}},\qquad
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0899}})=\mathcal{O}_{\mathrm{id0899}},\qquad
\mathcal{O}_{\mathrm{id0899}}(x)\in\mathcal{Y}_{\mathrm{adm}}.
\]

\paragraph{Primary Derivation.} Let $x\in \mathcal{X}_{\mathrm{id0899}}$ be the local coordinate or field sample.  The entry transform is\[
y=\mathcal{O}_{\mathrm{id0899}}(x),\qquad \mathcal{O}_{\mathrm{id0899}}:\mathcal{X}_{\mathrm{id0899}}\longrightarrow \mathcal{Y}_{\mathrm{id0899}}.
\]

Its differential transport is represented by the id-local Jacobian\[
J_{0899}(x)=D\mathcal{O}_{\mathrm{id0899}}\big|_x,\qquad \det J_{0899}(x)\neq 0
\]

Compatibility with the Nonary chain is enforced by\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0899}})=\mathcal{O}_{\mathrm{id0899}},\qquad y\in\mathcal{Y}_{\mathrm{adm}}.
\]

Thus the Nonary derivation for [ID 0899] is the three-stage passage
\[
\mathcal{X}_{\mathrm{id0899}}\xrightarrow{\,\mathcal{O}_{\mathrm{id0899}}\,} \mathcal{Y}_{\mathrm{id0899}}\xrightarrow{\,\mathcal{N}_{\mathrm{TRAWIN}}\,} \mathcal{Y}_{\mathrm{adm}},
\]
with the entry title fixing the meaning of the carrier and the TRAWIN normalization fixing the admissibility test.

\paragraph{Interpretation.} ENTRAINMENT GRADIENT is read as a transport rule: it converts local data into an admissible Nonary coordinate while preserving enough differential structure for the following entry to use it.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors ENTRAINMENT GRADIENT by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0899}}:\mathcal{X}_{\mathrm{id0899}}\longrightarrow\mathcal{Y}_{\mathrm{id0899}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0899}})=\mathcal{O}_{\mathrm{id0899}}
\]
\[
\mathcal{O}_{\mathrm{id0899}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0899] ENTRAINMENT GRADIENT}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
ENTRAINMENT GRADIENT is a registry definition in Resonance and Phase Locking with secondary pressure from Biological and Biomolecular Analogies.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} hat H Trawin[psi, t] = hat H tunnel + hat H ER + hat H SC + hat H cymatic + hat H TZP ; hat H tunnel = -hbar to the power 2/(2 m sub eff ) nabla to the power 2 + V sub barrier (r, theta, phi, t) ; hat H ER = integral sqrt |g| R to the power munu T sub munu dSigma ; hat H SC = sum (epsilon sub k - mu)(c to the power dagger sub kuparrow c sub kuparrow + c to the power dagger sub kdownarrow c sub kdownarrow ) + Delta sum (c to the power dagger sub kuparrow c to the power dagger sub -kdownarrow + h.c.). \textbf{Contextual meaning:} The entry reads ENTRAINMENT GRADIENT as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Geometric Constraint.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, ENTRAINMENT GRADIENT is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: PurposefulEvolution := Gradient[; t] = hat H tunnel + hat H ER + hat H SC + hat H cymatic + hat H TZP; and mathrm hat H tunnel = -hbar to the power 2/(2 m sub eff ) abla to the power 2 + V sub barrier (r, theta, phi, t). Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Sympathetic-Vibration Drop-off Rates}: The exact, careful measurement of how the deafening, bone-shaking hum of the reactor slowly fades to a quiet buzz as you walk down the hallway toward the breakroom.
\item \textbf{Phase-Locking Spatial Decay}: The frustrating realization that the magic, synchronizing power of the machine only reaches about 10 feet before the atoms just stop caring and go back to random, chaotic bouncing.
\item \textbf{Contagious-Resonance Mapping}: The creation of a 3D heatmap showing exactly how far the 'infection' of perfect, mathematical order has spread into the messy, chaotic biology of the surrounding city.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0899]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0899].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0899] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont ENTRAINMENT GRADIENT}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} ENTRAINMENT GRADIENT is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ENTRAINMENT GRADIENT is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0899].
\par\endgroup
\vfill
\endgroup
\endgroup
