\tzpanchor{0966}
\tzpentryheader{0966}{ROUND-TRIP FIDELITY METRIC}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{36eccb35-18dc-5e45-b46b-49b58515c5ef}}\\
\textbf{PiID} & \tzpcode{8066130019278} & \textbf{TZPi}\quad \tzpcode{0}\quad \textbf{PiPE}\quad \tzpcode{973}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3681.2945 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{06.0656 rad}\\
\textbf{TZPID} & \tzpcode{ID0966} & \textbf{Node Dependencies}\quad \tzpidref{0965}\\
\textbf{Registry} & \tzpcode{registry\_id\_0966} & \textbf{Scale}\quad geometric\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math.DG & Cross-list: math-ph, math.AT\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
F\_\{RT\} = |langle psi\_\{in\} | mathcal\{D\}(mathcal\{E\}(psi\_\{in\})) rangle|\textasciicircum{}2 > 0.999999

\tzpsection{Canonical Equation}
\[
n=153,600
\]
\[
k=49,152
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $n$: integer mode index.
    \item $\mathcal{K}_{0966}$: canonical registry object for entry ID 0966.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0966 generated source Wolfram model *)
ClearAll[K0966, Cr0966, T, R, A, W, I, N];
eq0966$1 = HoldForm[TZPSequence[n == 153, 600]];
eq0966$2 = HoldForm[TZPSequence[k == 49, 152]];

K0966 = HoldForm[{eq0966$1, eq0966$2}];

N = "normalized TRAWIN closure object for ROUND-TRIP FIDELITY METRIC";
I = "ROUND-TRIP FIDELITY METRIC integration/comparison layer";
W = "ROUND-TRIP FIDELITY METRIC wave or operator carrier";
A = "ROUND-TRIP FIDELITY METRIC admissible action/amplitude condition";
R = "ROUND-TRIP FIDELITY METRIC rotation/curl preservation layer";
T = "ROUND-TRIP FIDELITY METRIC local source condition";

Cr0966[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0966 = Cr0966[K0966];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ ROUND-TRIP FIDELITY METRIC local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ ROUND-TRIP FIDELITY METRIC rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ ROUND-TRIP FIDELITY METRIC admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ ROUND-TRIP FIDELITY METRIC wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ ROUND-TRIP FIDELITY METRIC integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for ROUND-TRIP FIDELITY METRIC.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0966] ROUND-TRIP FIDELITY METRIC}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
n=153,600
\]
\[
k=49,152
\]

\paragraph{Primary Derivation.}
To derive the stated relation by employing standard algebraic manipulations, yielding the required identity.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. Interpreted through TRAWIN, the equation functions as the generalized carrier for the entry’s information content. Within the CHL view, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors ROUND-TRIP FIDELITY METRIC by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
n=153,600
\]
\[
k=49,152
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0966] ROUND-TRIP FIDELITY METRIC}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
ROUND-TRIP FIDELITY METRIC is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} F sub RT = |langle psi sub in | mathcal D (mathcal E (psi sub in )) rangle| to the power 2 > 0.999999. \textbf{Contextual meaning:} The entry reads ROUND-TRIP FIDELITY METRIC as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Geometric Carrier; Compatibility Law; Topological Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, ROUND-TRIP FIDELITY METRIC is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: n=153,600; k=49,152; and A sub total = bigoplus sub v=1 to the power 16 (V sub v otimes S 9600 ). Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the quaternary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Signal-Echo Degradation Tracking}: The careful measurement of exactly how much a command gets distorted and mangled as it travels down the wires, bounces off the plasma, and returns to the computer.
\item \textbf{Closed-Loop Integrity Checking}: The sweeping test that proves the instructions the computer *thought* it sent are exactly the same as the instructions the magnets *actually* received.
\item \textbf{Perfect-Reconstruction Verification}: The absolute mathematical guarantee that if you translate the physics into code, and then translate the code back into physics, you don't lose a single drop of energy.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0966]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0966].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0966] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont ROUND-TRIP FIDELITY METRIC}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} ROUND-TRIP FIDELITY METRIC is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``ROUND-TRIP FIDELITY METRIC is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0966].
\par\endgroup
\vfill
\endgroup
\endgroup
