\section*{ID9266: Relation: 2π/m2πħ/m2π/M.}
\paragraph{Metadata.}
PiID: 7781423356282 | RTEID: RTE:P35981.9358:T2.7385 | UUID: 6aa4364f-e0c6-5bcb-b089-1cb8290c5e8a

\paragraph{Canonical Statement.}
ion Type: Definition Formal Statement: In a superfluid or Bose–Einstein condensate, the macroscopic wavefunction \$Ψ(r,t)=n(r,t)ei(r,t)\textbackslash{}Psi(r,t)\$ = \textbackslash{}sqrt\{n(r,t)\} \$eˆ\{i\textbackslash{}phi(r,t)\}Ψ(r, t)\$ = \$n(r, t)ei(r, t)exhibitscirculationquantization\$ : \$vd\$ = \$2πn/m\textbackslash{}ointv\textbackslash{}cdotd\textbackslash{}ell\$ = \$2\textbackslash{}pi\textbackslash{}hbarn/mvd\$ = \$2πn/m,wherennnistheintegerwindingnumberandmmmthemassoftheconstituentparticle.\$ Interpretive Meaning: The circulation of the velocity field around a closed loop in a superfluid is quantized in units of \$2π/m2\textbackslash{}pi\textbackslash{}hbar/m2π/m.\$ This arises from the singlevaluedness of the condensate wavefunction and underlies the stability of quantized vortices in gyromagnetic BECenhanced systems. Dependencies: IDs 321–324. Derivable Consequences: (1) Implies discrete values for vortex circulation in mercury or helium vortices used in propulsion. (2) Provides a link between macroscopic rotation and microscopic quantum phase. (3) Constra

\paragraph{Canonical Equation.}
\[
2π/m2\pi\hbar/m2π/m.
\]

\paragraph{Dictionary.}
Relation: 2π/m2πħ/m2π/M. — 2π/m2πħ/m2π/m.

\paragraph{Encyclopedia.}
Relation: 2π/m2πħ/m2π/M. is a symbolic expression, written 2π/m2πħ/m2π/m.. It introduces a symbol or relation used elsewhere in the framework. It is built from π, ħ, m. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
