\tzpanchor{0210}
\tzpentryheader{0210}{Dimensional Access Ladder}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{f40541c6-f726-5fd8-8c43-d9d298e14719}}\\
\textbf{PiID} & \tzpcode{6659334461284} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{217}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{815.4766 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.3437 rad}\\
\textbf{TZPID} & \tzpcode{ID0210} & \textbf{Node Dependencies}\quad \tzpidref{0209}\\
\textbf{Registry} & \tzpcode{registry\_id\_0210} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA329 operator theory & QA169 categorical structure\\
\textbf{arXiv Classification} & Primary: math.CT & Cross-list: math-ph, cs.LO\\
\textbf{Primary Support} & Acoustic Harmonic & Compact-Sector Energy\\
\textbf{Closure Support} & Resonance Selection & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
A resonance mapping equates an acoustic harmonic frequency with the frequency associated with a Kaluza--Klein mode energy.

\tzpsection{Canonical Equation}
\[
\omega_n=\frac{E_m}{\hbar},\qquad \omega_n=n f_{\mathrm{fundamental}},\qquad E_m=\frac{m\hbar c}{R_{\mathrm{KK}}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\omega_n$: angular frequency of the acoustic harmonic mode.
    \item $E_m$: energy of the indexed Kaluza--Klein mode.
    \item $\hbar$: reduced Planck constant converting energy to angular frequency.
    \item $n$: acoustic harmonic mode index.
    \item $f_{\mathrm{fundamental}}$: fundamental acoustic frequency.
    \item $c$: speed of light in the compact-mode energy relation.
    \item $R_{\mathrm{KK}}$: compactification radius setting the mode-energy spacing.
    \item $m$: Kaluza--Klein mode index.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0210 generated source Wolfram model *)
ClearAll[K0210, Cr0210, T, R, A, W, I, N];
eq0210$1 = HoldForm[omegaN == n*fFundamental];
eq0210$2 = HoldForm[EM == m*hbar*c/RKK];
eq0210$3 = HoldForm[omegaN == EM/hbar];
eq0210$4 = HoldForm[n*fFundamental == m*c/RKK];

K0210 = HoldForm[{eq0210$1, eq0210$2, eq0210$3, eq0210$4}];

N = "normalized TRAWIN closure object for Dimensional Access Ladder";
I = "Resonance Selection integration/comparison layer";
W = "Compact-Sector Energy wave or operator carrier";
A = "Acoustic Harmonic admissible action/amplitude condition";
R = "Compact-Sector Energy rotation/curl preservation layer";
T = "Acoustic Harmonic local source condition";

Cr0210[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0210 = Cr0210[K0210];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Acoustic Harmonic local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Compact-Sector Energy rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Acoustic Harmonic admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Compact-Sector Energy wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Resonance Selection integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Dimensional Access Ladder.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0210] Dimensional Access Ladder}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\omega_n=\frac{E_m}{\hbar},\qquad \omega_n=n f_{\mathrm{fundamental}},\qquad E_m=\frac{m\hbar c}{R_{\mathrm{KK}}}.
\]
\paragraph{Resonance Derivation.}
Substitute the compact-mode energy into the frequency matching condition:
\[
\omega_n=\frac{1}{\hbar}\frac{m\hbar c}{R_{\mathrm{KK}}}=\frac{m c}{R_{\mathrm{KK}}}.
\]
Equating this with the acoustic harmonic gives
\[
n f_{\mathrm{fundamental}}=\frac{m c}{R_{\mathrm{KK}}},\qquad f_{\mathrm{fundamental}}=\frac{m c}{n R_{\mathrm{KK}}}.
\]
\paragraph{Interpretation.}
The entry supplies a mode-matching condition; transfer remains conditional on a physical coupling mechanism and is not asserted by the algebra alone.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
Combining the acoustic harmonic frequency with the Kaluza--Klein energy spacing gives the resonance selection rule \(n f_{\mathrm{fundamental}}=m c/R_{\mathrm{KK}}\).
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Acoustic Harmonic}\par
\[
\omega_n=n f_{\mathrm{fundamental}}
\]
\noindent The acoustic carrier frequency is indexed by its harmonic mode.\par
\noindent\textbf{2. Compact-Sector Energy}\par
\[
E_m=\frac{m\hbar c}{R_{\mathrm{KK}}}
\]
\noindent The Kaluza--Klein excitation energy is scaled by compactification radius and mode index.\par
\noindent\textbf{3. Resonance Selection}\par
\[
\omega_n=\frac{E_m}{\hbar}
\]
\[
n f_{\mathrm{fundamental}}=\frac{m c}{R_{\mathrm{KK}}}
\]
\noindent Matching the two sectors produces the resonance-selection condition.\par

\clearpage
\noindent\textbf{[ID 0210] Dimensional Access Ladder}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small

\tzpsection{Definition}

The dimensional access ladder is a resonance-matching operator between an acoustic harmonic and a Kaluza--Klein excitation mode. The source relation equates acoustic angular frequency with mode energy measured in frequency units.

\tzpsection{Contextual Meaning}

An acoustic carrier is indexed by \(n\), while a compact-dimension excitation is indexed by \(m\). When their frequency and energy spacing agree, the source describes a resonant channel through which the modeled domains may exchange information or energy.

\tzpsection{Formal Statement}

\[
\omega_n=\frac{E_m}{\hbar},\qquad
\omega_n=n f_{\mathrm{fundamental}},\qquad
E_m=\frac{m\hbar c}{R_{\mathrm{KK}}}
\]

\tzpsection{Derivable Consequences}

Substitution yields \(n f_{\mathrm{fundamental}}=m c/R_{\mathrm{KK}}\). Thus the selected acoustic frequency is conditioned by both mode indices and the compactification radius; decreasing \(R_{\mathrm{KK}}\) raises the matching scale for fixed indices.

\tzpsection{Lemma Support}

The retrieved source explicitly gives all three displayed relations and describes the match as a resonance mapping between acoustic harmonics and Kaluza--Klein modes. It identifies frequency matching as the trigger for the proposed access channel.

\tzpsection{Technical Interpretation}

The equation is a selection condition rather than proof of transfer efficiency. It defines which acoustic excitation is kinematically aligned with a compact-mode energy spacing before any coupling strength is evaluated.

\tzpsection{Equation Grounding}

\(\omega_n\) is the angular frequency of the acoustic harmonic; \(E_m\) is the Kaluza--Klein mode energy; \(f_{\mathrm{fundamental}}\) is the fundamental acoustic frequency; \(R_{\mathrm{KK}}\) is compactification radius; and \(n,m\) identify the corresponding modes.

\tzpsection{Interpretive Role}

This entry connects bounded acoustic harmonics to the compact-sector progression by providing a precise resonance condition rather than a general analogy.

\tzpsection{TZP Thesaurus}

\noindent \textbf{Resonance Mapping}: A matching condition equating the frequencies associated with two modeled sectors. \enspace\textbullet\enspace \textbf{Kaluza--Klein Mode}: An excitation indexed in the compact extra-dimensional sector. \enspace\textbullet\enspace \textbf{Compactification Radius}: The radius scale controlling the spacing of compact-sector mode energies.\par

\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0210].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0210] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Dimensional Access Ladder}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} The source supplies the resonance relations
\[
\omega_n=\frac{E_m}{\hbar},\qquad \omega_n=n f_{\mathrm{fundamental}},\qquad E_m=\frac{m\hbar c}{R_{\mathrm{KK}}}.
\]
\textbf{Logic Validation:}\\
\textbf{Proposition:} A mode pair is selected when its acoustic frequency equals its compact-sector frequency.\\
\textbf{Proof:} Substituting \(E_m=m\hbar c/R_{\mathrm{KK}}\) into \(\omega_n=E_m/\hbar\) gives \(\omega_n=m c/R_{\mathrm{KK}}\). Equating this with \(\omega_n=n f_{\mathrm{fundamental}}\) gives \(n f_{\mathrm{fundamental}}=m c/R_{\mathrm{KK}}\).\\
\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- algebraic resonance selection follows from the displayed relations\\
\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL obligation\\
\textbf{Physical Status:} THEORETICAL -- coupling efficiency remains to be tested
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0210].
\par\endgroup
\vfill
\endgroup
\endgroup
