\section*{ID9402: Definition of 𝑛 · 2.07 × 10−15 Wb, 𝑃ℎ𝑖}
\paragraph{Metadata.}
PiID: 4370906979396 | RTEID: RTE:P36510.0540:T3.6087 | UUID: 62dd4ce8-7bf9-584b-b480-bfdc8ac67c64

\paragraph{Canonical Statement.}
ges. 𝑃ℎ𝑖 = 𝑛 · (ℎ/2𝑒) \$≈\$ 𝑛 · 2.07 × 10−15 Wb 𝑃ℎ𝑖 = 𝑛 · (ℎ/2𝑒) \$≈\$ 𝑛 · 2.07 × 10−15 Wb Wolfram Form 𝔚TZP (K0314) \$↦−→ 〈 Φ𝜏\$ , \$Ω\$ T, \$ΨT 〉\$ K0314 := HoldForm(T0314) AdmissibleTZP (K0314) \$⇐⇒𝔚TZP\$ (K0314) . \$∅\$ Wolfram register: canonical symbol lift Title lift: Extended Phase Space for Magneto-Acoustic Kaluza Klein Systems Symbol key: \$Φ𝜏\$ : phase-time symmetry \$ΩT:\$ Trawinistic boundary curvature \$ΨT:\$ Trawinistic wavefunction TRAWIN Normalization NormalizeTRAWIN( 𝑃ℎ𝑖 = 𝑛 · (ℎ/2𝑒) \$≈\$ 𝑛 · 2.07 × 10−15 Wb, 𝑃ℎ𝑖 = 𝑛 · (ℎ/2𝑒) \$≈\$ 𝑛 · 2.07 × 10−15 Wb, 𝑃ℎ𝑖 = 𝑛 · (ℎ/2𝑒) \$≈\$ 𝑛 · 2.07 × 10−15 Wb ) T: Configuration Manifold is localized within the field the-ory and action principles arc of the directory. R: Kaluza–Klein Sector preserves the operative relation that extended phase space for magneto-acoustic kaluza klein systems requires. A: Gauge Quotient fixes the admissible closure condition for the entry. W: Extended Phase

\paragraph{Canonical Equation.}
\[
𝑛 · 2.07 × 10−15 Wb, 𝑃ℎ𝑖 = 𝑛 · (ℎ/2𝑒)
\]

\paragraph{Dictionary.}
Definition of 𝑛 · 2.07 × 10−15 Wb, 𝑃ℎ𝑖 — 𝑛 · 2.07 × 10−15 Wb, 𝑃ℎ𝑖 = 𝑛 · (ℎ/2𝑒)

\paragraph{Encyclopedia.}
Definition of 𝑛 · 2.07 × 10−15 Wb, 𝑃ℎ𝑖 is an algebraic definition, written 𝑛 · 2.07 × 10−15 Wb, 𝑃ℎ𝑖 = 𝑛 · (ℎ/2𝑒). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
