\tzpanchor{0384}
\tzpentryheader{0384}{Superfluid Vortex Quantisation}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{fa308073-cd08-50f1-a5a3-34c34db42fc5}}\\
\textbf{PiID} & \tzpcode{1469519415116} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{391}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{1491.1573 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{02.4570 rad}\\
\textbf{TZPID} & \tzpcode{ID0384} & \textbf{Node Dependencies}\quad \tzpidref{0383}\\
\textbf{Registry} & \tzpcode{registry\_id\_0384} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Macroscopic Wavefunction & Circulation Integral\\
\textbf{Closure Support} & Quantized Circulation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Incorporating a superfluid condensate into a gyromagnetic system yields a macroscopic wavefunction. The circulation around a closed loop is quantised in integer multiples of Planck's constant divided by the particle mass.

\tzpsection{Canonical Equation}
\[
\Psi(\mathbf{r},t)=\sqrt{n(\mathbf{r},t)}e^{i\phi(\mathbf{r},t)}
\]
\[
\oint \mathbf{v}\cdot d\boldsymbol{\ell}=\frac{h}{m}N
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\Psi$: wavefunction or state carrier for the entry equation.
    \item $t$: source equation symbol.
    \item $n$: integer mode index.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $v$: velocity, flow speed, or auxiliary comparison variable.
    \item $Z$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0384 generated source Wolfram model *)
ClearAll[K0384, Cr0384, T, R, A, W, I, N];
eq0384$1 = HoldForm[Psi[r, t] == sqrtTuple[n[r, t]]*eIphirt];
eq0384$2 = HoldForm[ContourIntegral*v*dboldsymbol[ell] == (h/m)*N];
eq0384$3 = HoldForm[Element[N, Z]];

K0384 = HoldForm[{eq0384$1, eq0384$2, eq0384$3}];

N = "normalized TRAWIN closure object for Superfluid Vortex Quantisation";
I = "Quantized Circulation integration/comparison layer";
W = "Circulation Integral wave or operator carrier";
A = "Macroscopic Wavefunction admissible action/amplitude condition";
R = "Circulation Integral rotation/curl preservation layer";
T = "Macroscopic Wavefunction local source condition";

Cr0384[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0384 = Cr0384[K0384];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Macroscopic Wavefunction local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Circulation Integral rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Macroscopic Wavefunction admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Circulation Integral wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Quantized Circulation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Superfluid Vortex Quantisation.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0384] Superfluid Vortex Quantisation}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equations.}
\begin{equation}
\hbar_{\mathrm{eff}}
=
\hbar(1+\chi_{\mathrm{TZP}}).
\end{equation}

\begin{equation}
\Delta x\,\Delta p
\geq
\frac{\hbar_{\mathrm{eff}}}{2}.
\end{equation}

\begin{equation}
\Delta t\,\Delta E
\geq
\frac{\hbar_{\mathrm{eff}}}{2}.
\end{equation}

\paragraph{Primary Derivation.}
Let $\chi_{\mathrm{TZP}}$ encode the zero-point correction to the operational quantum scale.  
Define:
\begin{equation}
\hbar_{\mathrm{eff}}
=
\hbar(1+\chi_{\mathrm{TZP}}).
\end{equation}

Replacing $\hbar$ by $\hbar_{\mathrm{eff}}$ in the uncertainty relations gives:
\begin{equation}
\Delta x\,\Delta p
\geq
\frac{\hbar_{\mathrm{eff}}}{2},
\qquad
\Delta t\,\Delta E
\geq
\frac{\hbar_{\mathrm{eff}}}{2}.
\end{equation}

Thus no observation protocol can resolve below the effective uncertainty window:
\begin{equation}
\boxed{
\Omega_{\mathrm{obs}}
=
\left\{
(\Delta x,\Delta p,\Delta t,\Delta E):
\Delta x\Delta p\geq \frac{\hbar_{\mathrm{eff}}}{2},
\;
\Delta t\Delta E\geq \frac{\hbar_{\mathrm{eff}}}{2}
\right\}.
}
\end{equation}

\paragraph{Interpretation.}
Observability is bounded by a TZP-corrected effective quantum constant.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Superfluid Vortex Quantisation by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Macroscopic Wavefunction}\par
\[
\Psi(\mathbf{r},t)=\sqrt{n(\mathbf{r},t)}e^{i\phi(\mathbf{r},t)}
\]
\noindent This fixes the macroscopic condensate wavefunction that carries the quantum vortex phase.\par
\noindent\textbf{2. Circulation Integral}\par
\[
\oint \mathbf{v}\cdot d\boldsymbol{\ell}=\frac{h}{m}N
\]
\noindent This identifies the closed-loop circulation integral around the vortex core.\par
\noindent\textbf{3. Quantized Circulation}\par
\[
N\in\mathbb{Z}
\]
\noindent This closes the entry by stating the quantized circulation carried by the integer winding number.\par

\clearpage
\noindent\textbf{[ID 0384] Superfluid Vortex Quantisation}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Superfluid Vortex Quantisation is a registry definition in Field Theory and Action Principles with secondary pressure from Manifold and Metric Dynamics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Incorporating a superfluid condensate into a gyromagnetic system yields a macroscopic wavefunction. The circulation around a closed loop is quantised in integer multiples of Planck s constant divided by the particle mass. \textbf{Contextual meaning:} The entry reads Superfluid Vortex Quantisation as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now states quantum-vortex circulation through the actual condensate and loop integral laws instead of unrelated Fibonacci fragments. \textbf{Lemma support:} Macroscopic Wavefunction; Circulation Integral; Quantized Circulation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Observability is bounded by a TZP-corrected effective quantum constant.

\tzpsection{Equation Grounding}
Equation anchors: (r,t)=n(r,t)ei (r,t) exhibits circulation quantization:  v dl=2;  n/mtextbackslash oint v textbackslash cdot dtextbackslash ell = 2textbackslash pi textbackslash hbar n/m v dl=2; and  n/m, where nnn is the integer winding number and mmm the mass of the constituent particle. Interpretive Meaning: The circulation of the velocity field around a closed loop in a superfluid is quantized in units of 2. Proof route: show that single-valuedness of the condensate wavefunction forces the stated quantized circulation law. Formalization route: prove that the circulation integral evaluates to the stated integer multiple of h/m.

\tzpsection{Interpretive Role}
The entry now states quantum-vortex circulation through the actual condensate and loop integral laws instead of unrelated Fibonacci fragments.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Phase-Gradient Velocity Flow}: The strict rule that the physical speed of the superfluid is driven entirely by how fast the quantum phase angle is changing.
\item \textbf{Planck-Constrained Circulation}: The observation that if you measure the flow around the vortex, the result will always be a perfect, neat multiple of a fundamental constant.
\item \textbf{Integer Winding Number Requirement}: The topological necessity that the wavefunction's phase must spin exactly a whole number of times to avoid breaking the math.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0384]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0384_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0384] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Superfluid Vortex Quantisation}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} incorporating a superfluid condensate into a gyromagnetic system yields a macroscopic
wavefunction

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Superfluid Vortex Quantisation is valid as a formal dynamical law when the Hamiltonian
or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0384_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
