\section*{ID9965: Accumulation Kernel: δ S/δ g\textasciicircum{}μν}
\paragraph{Metadata.}
PiID: 9225695968815 | RTEID: RTE:P38696.3080:T0.9278 | UUID: 24dd5a03-32f2-5d9e-ad89-26ef889296ae

\paragraph{Canonical Statement.}
\textbackslash{}begin\{proof\} The proof proceeds through three steps. First, we establish that quantum entanglement creates non-local correlations characterized by mutual information \$I(A:B) = S(A) + S(B) - S(AB)\$. Second, these correlations evolve under unitary dynamics while experiencing decoherence with characteristic time \$\textbackslash{}tau\_\{\textbackslash{}text\{dec\}\}\$. Third, the accumulated information density acts as an effective source term in the Einstein equations through the correspondence principle \$\textbackslash{}delta S/\textbackslash{}delta g\textasciicircum{}\{\textbackslash{}mu\textbackslash{}nu\} = (c\textasciicircum{}4/16\textbackslash{}pi G)G\_\{\textbackslash{}mu\textbackslash{}nu\}\$. \textbackslash{}end\{proof\}

\paragraph{Canonical Equation.}
\[
\delta S/\delta g^{\mu\nu} = (c^4/16\pi G)G_{\mu\nu}
\]

\paragraph{Dictionary.}
Accumulation Kernel: δ S/δ g\textasciicircum{}μν — δ S/δ g\textasciicircum{}μν = (c\textasciicircum{}4/16π G)G\_μν

\paragraph{Encyclopedia.}
Accumulation Kernel: δ S/δ g\textasciicircum{}μν is an algebraic definition, written δ S/δ g\textasciicircum{}μν = (c\textasciicircum{}4/16π G)G\_μν. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from π, μ, ν, c, G, G\_, defining δ S/δ g\textasciicircum{}μν. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
