\tzpanchor{0010}
\tzpentryheader{0010}{Stochastic Drift Magnitude}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{612817ab-6377-5429-9c27-fe2d003262b2}}\\
\textbf{PiID} & \tzpcode{8979323846264} & \textbf{TZPi}\quad \tzpcode{3}\quad \textbf{PiPE}\quad \tzpcode{17}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{38.8322 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.0640 rad}\\
\textbf{TZPID} & \tzpcode{ID0010} & \textbf{Node Dependencies}\quad \tzpidref{0004}\\
\textbf{Registry} & \tzpcode{registry\_id\_0010} & \textbf{Scale}\quad stochastic\\
\textbf{LOC Classification} & QA274 stochastic processes & QC174.85 fluctuation dynamics\\
\textbf{arXiv Classification} & Primary: math.PR \quad Cross-list: cond-mat.stat-mech, gr-qc & \\
\textbf{Primary Support} & Displacement Variance & Infinitesimal-Time Drift Rate\\
\textbf{Closure Support} & Normalized Stochastic Response & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This quantity captures the intensity of random, Brownian-like motion experienced by degrees of freedom near the zero point.

\tzpsection{Canonical Equation}
\[
\sigma_{\mathrm{SD}}^{2}
=
\lim_{\Delta t \to 0}
\frac{1}{\Delta t}
\left\langle (\Delta x)^{2} \right\rangle
\]
\[
\Delta x = x(t+\Delta t)-x(t)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\sigma_{\mathrm{SD}}$: source equation symbol.
    \item $t$: source equation symbol.
    \item $u_{T}$: source equation symbol.
    \item $x$: local field point or coordinate variable in the canonical equation.
    \item $\Delta$: source equation symbol.
    \item $\sigma_{SD},norm$: source equation symbol.
    \item $S$: source equation symbol.
    \item $D$: source equation symbol.
    \item $N$: normalization, count, or closure parameter in the entry relation.
    \item $R$: global radius, boundary radius, or topological scale.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0010 generated source Wolfram model *)
ClearAll[K0010, Cr0010, T, R, A, W, I, N];
eq0010$1 = HoldForm[sigmaSD^2 == LimitDeltat0[1/(Delta*t)]*Inner[(Delta*x)^2]];
eq0010$2 = HoldForm[Delta*x == x[t + Delta*t] - x[t]];
eq0010$3 = HoldForm[Inner[(Delta*x)^2]];
eq0010$4 = HoldForm[sigmaSD2Norm == NormalizeTRAWIN[LimitDeltat0[Inner[(Delta*x)^2]/(Delta*t)], InnerProduct, uT]];

K0010 = HoldForm[{eq0010$1, eq0010$2, eq0010$3, eq0010$4}];

N = "normalized TRAWIN closure object for Stochastic Drift Magnitude";
I = "Normalized Stochastic Response integration/comparison layer";
W = "Infinitesimal-Time Drift Rate wave or operator carrier";
A = "Displacement Variance admissible action/amplitude condition";
R = "Infinitesimal-Time Drift Rate rotation/curl preservation layer";
T = "Displacement Variance local source condition";

Cr0010[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0010 = Cr0010[K0010];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Displacement Variance local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Infinitesimal-Time Drift Rate rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Displacement Variance admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Infinitesimal-Time Drift Rate wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Stochastic Response integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Stochastic Drift Magnitude.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0010] Stochastic Drift Magnitude}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\sigma_{\mathrm{SD}}^{2}
=
\lim_{\Delta t\to 0}
\frac{1}{\Delta t}
\left\langle
(\Delta x)^2
\right\rangle .
\end{equation}

\paragraph{Primary Derivation.}
Let $\Delta x$ be the displacement of a test particle over a small time interval $\Delta t$ near the TZP.  
The mean-square displacement is:

\begin{equation}
\left\langle(\Delta x)^2\right\rangle .
\end{equation}

A diffusion-like drift magnitude is obtained by measuring the rate at which this mean-square displacement accumulates per unit time:

\begin{equation}
\frac{1}{\Delta t}
\left\langle(\Delta x)^2\right\rangle .
\end{equation}

Taking the infinitesimal-time limit gives the stochastic drift magnitude:

\begin{equation}
\boxed{
\sigma_{\mathrm{SD}}^{2}
=
\lim_{\Delta t\to 0}
\frac{1}{\Delta t}
\left\langle
(\Delta x)^2
\right\rangle .
}
\end{equation}

\paragraph{Interpretation.}
$\sigma_{\mathrm{SD}}^{2}$ measures the infinitesimal drift intensity induced by stochastic fluctuations near the TZP.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Stochastic Drift Magnitude by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Displacement Variance}\par
\[
\left\langle (\Delta x)^{2} \right\rangle
\]
\noindent This captures the raw fluctuation content of a probe trajectory before any rate normalization is imposed.\par
\noindent\textbf{2. Infinitesimal-Time Drift Rate}\par
\[
\sigma_{\mathrm{SD}}^{2}
=
\lim_{\Delta t \to 0}
\frac{1}{\Delta t}
\left\langle (\Delta x)^{2} \right\rangle
\]
\noindent This turns raw variance into a local drift scale by comparing it against vanishing observation time.\par
\noindent\textbf{3. Normalized Stochastic Response}\par
\[
\sigma_{\mathrm{SD}}^{2,\mathrm{norm}}
=
\operatorname{Normalize}_{\mathrm{TRAWIN}}
\!\left(
\lim_{\Delta t \to 0}
\frac{\langle (\Delta x)^2 \rangle}{\Delta t},\,
\langle \cdot \rangle,\,
u_{T}
\right)
\]
\noindent This closes the progression by making the drift scale comparable across admissible TZP neighborhoods rather than tied to one raw sampling scheme.\par

\clearpage
\noindent\textbf{[ID 0010] Stochastic Drift Magnitude}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Stochastic Drift Magnitude is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This quantity captures the intensity of random, Brownian-like motion experienced by degrees of freedom near the zero point. \textbf{Contextual meaning:} The entry reads Stochastic Drift Magnitude as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry preserves the named object as a reusable definition, connects it to the local proof route, and records the consequences implied by the equation chain. \textbf{Lemma support:} Displacement Variance; Infinitesimal-Time Drift Rate; Normalized Stochastic Response.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
sub SD to the power 2 measures the infinitesimal drift intensity induced by stochastic fluctuations near the TZP.

\tzpsection{Equation Grounding}
Equation anchors: The stochastic drift magnitude SigmaSD is defined as sigma SD2=limu2061Deltatto01Deltat (Deltax)2sigmatextbackslash SD to the power 2 = textbackslash lim Delta tto 0 ratio 1 Delta t textbackslash, (Delta x) to the power 2 sigma SD2=limDeltatto0Deltat1(Deltax)2, where DeltaxDelta xDeltax is the displacement of a test particle subject to random fluctuations in the neighbourhood of the TZP and  dot  denotes ensemble averaging. The stochastic drift magnitude SigmaSD is defined as sigma SD2=limu2061Deltatto01Deltat (Deltax)2sigmatextbackslash SD to the power 2 = textbackslash lim Delta tto 0 ratio 1 Delta t textbackslash, (Delta x) to the power 2 sigma SD2=limDeltatto0Deltat1(Deltax)2, where DeltaxDelta xDeltax is the displacement of a test particle subject to random fluctuations in the neighbourhood of the TZP and  dot  denotes ensemble averaging.

\tzpsection{Interpretive Role}
This quantity becomes the registry s basic fluctuation scale for noisy motion near the anchor. It supports later diffusion, coherence-loss, and transport calculations that would be invisible in a purely deterministic reading.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Stochastic Drift Magnitude}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Stochastic Drift Magnitude Formal Analogue}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Magnitude Equivalence}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0010]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0010_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0010] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Stochastic Drift Magnitude}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this quantity captures the intensity of random, Brownian-like motion experienced by
degrees of freedom near the zero point

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Stochastic Drift Magnitude is valid as a formal registry statement when its source
equation and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that this quantity captures the intensity of random,
Brownian-like motion experienced by degrees of freedom near the zero point. \_SD\textasciicircum{}2
measures the infinitesimal drift intensity induced by stochastic fluctuations near the
TZP. This quantity becomes the registry's basic fluctuation scale for noisy motion near
the anchor.. The CHL validation treats the equation as the formal anchor and the
semantic text as the interpretation constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0010_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
