\section*{ID9267: Definition of Rm}
\paragraph{Metadata.}
PiID: 7814233562823 | RTEID: RTE:P35985.8190:T2.7449 | UUID: de472719-ba57-543c-ab01-965573873de1

\paragraph{Canonical Statement.}
macroscopic rotation and microscopic quantum phase. (3) Constrains the possible velocities in superfluid augmentation of gyromagnetic devices. Falsifiability / Test Handle: Observe circulation in superfluid vortices and verify quantization; measure changes with different particle masses. 2.0.179 ID 328: Critical Magnetic Reynolds Number for SelfOrganized Dynamo Type: Conservation Law Formal Statement: A selforganized dynamo and magnetic field generation occur when the magnetic Reynolds number \$Rm=µ0σvLR\_\{\textbackslash{}text\{m\}\}\$ = \textbackslash{}mu\_0 \textbackslash{}sigma v \$LRm=µ0σvL\$ exceeds a critical threshold \$Rm,critical≈103R\_\{\textbackslash{}text\{m,critical\}\}\$ \textbackslash{}approx \$10ˆ3Rm,critical≈103.\$ Interpretive Meaning: The magnetic Reynolds number measures the ratio of magnetic advection to diffusion. Above a critical value, induced currents sustain magnetic fields against resistive dissipation, leading to dynamo action and selforganized magnetic structures. De

\paragraph{Canonical Equation.}
\[
Rm=µ0σvLR_{\text{m}}
\]

\paragraph{Dictionary.}
Definition of Rm — Rm=µ0σvLR\_m

\paragraph{Encyclopedia.}
Definition of Rm is an algebraic definition, written Rm=µ0σvLR\_m. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from v, L, R\_, defining Rm. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
