\tzpanchor{0249}
\tzpentryheader{0249}{Quantum Metamaterial Information Metric}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{9ab45abc-9b9e-5381-a16a-48d8446533da}}\\
\textbf{PiID} & \tzpcode{1456485669234} & \textbf{TZPi}\quad \tzpcode{5}\quad \textbf{PiPE}\quad \tzpcode{256}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{966.9223 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{01.5932 rad}\\
\textbf{TZPID} & \tzpcode{ID0249} & \textbf{Node Dependencies}\quad \tzpidref{0248}\\
\textbf{Registry} & \tzpcode{registry\_id\_0249} & \textbf{Scale}\quad informational\\
\textbf{LOC Classification} & QA76.9 information and coding & QA614 topological data analysis\\
\textbf{arXiv Classification} & Primary: cs.IT & Cross-list: math.AT, math-ph\\
\textbf{Primary Support} & Geometric Carrier & Compatibility Law\\
\textbf{Closure Support} & Topological Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Cosmological entanglement on an S\^{}3 background induces a natural information metric on the DAANSphere, linking quantum entanglement entropy to spacetime curvature; this metric allows information and geometry to co-evolve within the unified framework.

\tzpsection{Canonical Equation}
\[
n_i=(\sqrt{1-z_i^2}\cos a_i,\sqrt{1-z_i^2}\sin a_i,z_i)
\]
\[
|S^2|=4\pi
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $n_i$: source equation symbol.
    \item $z_i$: source equation symbol.
    \item $a_i$: source equation symbol.
    \item $S^2$: two-sphere target domain.
    \item $\pi$: source equation symbol.
    \item $\gamma$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0249 generated source Wolfram model *)
ClearAll[K0249, Cr0249, T, R, A, W, I, N];
eq0249$1 = HoldForm[nI == Tuple[Sqrt[1 - zI^2]*Cos*aI, Sqrt[1 - zI^2]*Sin*aI, zI]];
eq0249$2 = HoldForm[Abs[S^2] == 4*Pi];
eq0249$3 = HoldForm[gamma == Pi[3 - Sqrt[5]]];

K0249 = HoldForm[{eq0249$1, eq0249$2, eq0249$3}];

N = "normalized TRAWIN closure object for Quantum Metamaterial Information Metric";
I = "Topological Closure integration/comparison layer";
W = "Compatibility Law wave or operator carrier";
A = "Geometric Carrier admissible action/amplitude condition";
R = "Compatibility Law rotation/curl preservation layer";
T = "Geometric Carrier local source condition";

Cr0249[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0249 = Cr0249[K0249];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Geometric Carrier local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Compatibility Law rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Geometric Carrier admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Compatibility Law wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Topological Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Quantum Metamaterial Information Metric.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0249] Quantum Metamaterial Information Metric}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\left\langle\phi^2\right\rangle
=
\int_{0}^{\omega_{\mathrm{cut}}}
\frac{\hbar}{2\omega}
\eta(\omega)
\,\mathrm{d}\omega .
\end{equation}

\paragraph{Primary Derivation.}
For a quantum field mode of frequency $\omega$, the vacuum fluctuation contribution scales as:

\begin{equation}
\frac{\hbar}{2\omega}.
\end{equation}

The spectral density index $\eta(\omega)$ weights the contribution of each frequency mode:

\begin{equation}
\frac{\hbar}{2\omega}\eta(\omega).
\end{equation}

Integrating over allowed frequencies from $0$ to the cutoff $\omega_{\mathrm{cut}}$ gives the total zero-point fluctuation variance:

\begin{equation}
\boxed{
\left\langle\phi^2\right\rangle
=
\int_{0}^{\omega_{\mathrm{cut}}}
\frac{\hbar}{2\omega}
\eta(\omega)
\,\mathrm{d}\omega .
}
\end{equation}

\paragraph{Interpretation.}
Zero-point fluctuations are represented as the weighted variance of field amplitudes over the allowed frequency spectrum.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Quantum Metamaterial Information Metric by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Geometric Carrier}\par
\[
n_i=(\sqrt{1-z_i^2}\cos a_i,\sqrt{1-z_i^2}\sin a_i,z_i)
\]
\noindent This fixes the effective geometry or carrier space named by the entry title.\par
\noindent\textbf{2. Compatibility Law}\par
\[
|S^2|=4\pi
\]
\noindent This makes the geometry admissible by imposing its internal compatibility law.\par
\noindent\textbf{3. Topological Closure}\par
\[
\gamma=\pi(3-\sqrt{5})
\]
\noindent This closes the entry by tying the local structure to a global topological invariant.\par

\clearpage
\noindent\textbf{[ID 0249] Quantum Metamaterial Information Metric}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Quantum Metamaterial Information Metric is a registry definition in Information Synchronization with secondary pressure from Field Theory and Action Principles.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Cosmological entanglement on an S 3 background induces a natural information metric on the DAANSphere, linking quantum entanglement entropy to spacetime curvature; this metric allows information and geometry to co-evolve within the unified framework. \textbf{Contextual meaning:} The entry reads Quantum Metamaterial Information Metric as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry stabilizes the geometric side of the tertiary arc, giving the later dynamical laws a carrier on which they can act without ambiguity. \textbf{Lemma support:} Geometric Carrier; Compatibility Law; Topological Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Zero-point fluctuations are represented as the weighted variance of field amplitudes over the allowed frequency spectrum.

\tzpsection{Equation Grounding}
Equation anchors: n sub i=(sqrt 1-z sub i to the power 2 cos a sub i,sqrt 1-z sub i to the power 2 sin a sub i,z sub i); |S to the power 2|=4pi; and gamma=pi(3-sqrt 5 ). Proof route: show that the effective geometry preserves the required compatibility condition while supporting the stated topological invariant. Formalization route: prove that the effective deformation leaves the relevant Euler characteristic or bundle invariant well-defined.

\tzpsection{Interpretive Role}
The entry stabilizes the geometric side of the tertiary arc, giving the later dynamical laws a carrier on which they can act without ambiguity.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Refractive-Index Phase Coherence Distance}: The measurement of how far a quantum signal can propagate through an engineered metamaterial without losing its phase information.
\item \textbf{Sub-Wavelength Information Density}: The calculation of the massive amount of data that can be encoded in the near-field, sub-wavelength structures of a metamaterial lattice.
\item \textbf{Negative-Index Tensor Mapping}: The mathematical representation of how information travels backwards or at negative phase velocities through specialized metamaterials.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0249]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0249_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0249] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Quantum Metamaterial Information Metric}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} cosmological entanglement on an S\textbackslash{}\textasciicircum{}3 background induces a natural information metric on
the DAANSphere, linking quantum entanglement entropy to spa...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Quantum Metamaterial Information Metric is valid as a tensorial/geometric statement when
the stated tensor fields are well formed on the specified domain.''\\
\textbf{Proof:} The source statement gives a metric, curvature, or tensor relation. The CHL reading
validates it by checking that the tensorial objects have compatible domains, indices,
and transformation behavior.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- tensorial well-formedness validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0249_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
