\tzpanchor{0029}
\tzpentryheader{0029}{Trawinistic Hamiltonian Density}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{2f553a0b-a238-5d77-8d6c-e8652414a401}}\\
\textbf{PiID} & \tzpcode{9502884197169} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{36}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{112.6134 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.1856 rad}\\
\textbf{TZPID} & \tzpcode{ID0029} & \textbf{Node Dependencies}\quad \tzpidref{0017}\\
\textbf{Registry} & \tzpcode{registry\_id\_0029} & \textbf{Scale}\quad hamiltonian\\
\textbf{LOC Classification} & QC174 Hamiltonian field theory & QA320 canonical formalism\\
\textbf{arXiv Classification} & Primary: hep-th \quad Cross-list: gr-qc, math-ph & \\
\textbf{Primary Support} & Canonical Momentum & Legendre-Type Energy Density\\
\textbf{Closure Support} & Normalized Hamiltonian Closure & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The Trawinistic Hamiltonian density for a field $\phi$ on $M$ is $\mathcal{H}_{\mathrm{T}}=\pi\dot{\phi}-\mathcal{L}_{\mathrm{T}}$, where $\pi=\partial\mathcal{L}_{\mathrm{T}}/\partial\dot{\phi}$ is the canonical momentum and $\mathcal{L}_{\mathrm{T}}$ contains the degenerate-metric and TZP-potential contributions.

\tzpsection{Canonical Equation}
\[
\mathcal{H}_{\mathrm{T}}
=
\pi\,\dot{\phi}
-\mathcal{L}_{\mathrm{T}}
\]
\[
\pi
=
\frac{\partial \mathcal{L}_{\mathrm{T}}}{\partial \dot{\phi}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{H}_{\mathrm{T}}$: source equation symbol.
    \item $\pi$: source equation symbol.
    \item $\phi$: flux, phase, or topological map term in the source equation.
    \item $\mathcal{L}_{\mathrm{T}}$: source equation symbol.
    \item $V_{T}$: source equation symbol.
    \item $T$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0029 generated source Wolfram model *)
ClearAll[K0029, Cr0029, T, R, A, W, I, N];
eq0029$1 = HoldForm[HT == Pidot[phi] - LT];
eq0029$2 = HoldForm[Pi == (Partial*LT)/Partialdot[phi]];
eq0029$3 = HoldForm[HTNorm == NormalizeTRAWIN[Pidot[phi] - LT, Pi, VT]];

K0029 = HoldForm[{eq0029$1, eq0029$2, eq0029$3}];

N = "normalized TRAWIN closure object for Trawinistic Hamiltonian Density";
I = "Normalized Hamiltonian Closure integration/comparison layer";
W = "Legendre-Type Energy Density wave or operator carrier";
A = "Canonical Momentum admissible action/amplitude condition";
R = "Legendre-Type Energy Density rotation/curl preservation layer";
T = "Canonical Momentum local source condition";

Cr0029[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0029 = Cr0029[K0029];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Canonical Momentum local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Legendre-Type Energy Density rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Canonical Momentum admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Legendre-Type Energy Density wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Normalized Hamiltonian Closure integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Trawinistic Hamiltonian Density.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0029] Trawinistic Hamiltonian Density}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{H}_{\mathrm{T}}
=
\pi\,\dot{\phi}
-\mathcal{L}_{\mathrm{T}}
\]
\[
\pi
=
\frac{\partial \mathcal{L}_{\mathrm{T}}}{\partial \dot{\phi}}
\]

\paragraph{Primary Derivation.}
The expression \( \mathcal{H}_{\mathrm{T}} \) involves an integral. Evaluating the integrand over the indicated domain and applying the definitions of the integrand functions yields the stated identity.
\paragraph{Equation Type.}
This statement is classified as an integral relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. From the TRAWIN perspective, the equation functions as the integral carrier for the entry’s information content. According to CHL, the derivation provides a constructive term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Trawinistic Hamiltonian Density by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Canonical Momentum}\par
\[
\pi
=
\frac{\partial \mathcal{L}_{\mathrm{T}}}{\partial \dot{\phi}}
\]
\noindent This supplies the conjugate variable needed to move from Lagrangian to Hamiltonian description.\par
\noindent\textbf{2. Legendre-Type Energy Density}\par
\[
\mathcal{H}_{\mathrm{T}}
=
\pi\,\dot{\phi}
-\mathcal{L}_{\mathrm{T}}
\]
\noindent This converts the Trawinistic Lagrangian into the corresponding local Hamiltonian density.\par
\noindent\textbf{3. Normalized Hamiltonian Closure}\par
\[
\mathcal{H}_{\mathrm{T}}^{\mathrm{norm}}
=
\operatorname{Normalize}_{\mathrm{TRAWIN}}
\!\left(
\pi\dot{\phi}-\mathcal{L}_{\mathrm{T}},\,
\pi,\,
V_{T}
\right)
\]
\noindent This closes the progression by packaging the canonical energy density together with the singular potential sector into a TRAWIN-normalized operator object.\par

\clearpage
\noindent\textbf{[ID 0029] Trawinistic Hamiltonian Density}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Trawinistic Hamiltonian Density is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} The Trawinistic Hamiltonian density for a field phi on M is H sub T =pidot phi - L sub T , where pi=partial L sub T /partialdot phi is the canonical momentum and L sub T contains the degenerate-metric and TZP-potential contributions. \textbf{Contextual meaning:} The entry reads Trawinistic Hamiltonian Density as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This density is the bridge from geometric and potential structure into dynamics. Once fixed, it generates the canonical equations, the Hamilton--Jacobi form, and the quantum Hamiltonian operator used later in the registry. \textbf{Lemma support:} Canonical Momentum; Legendre-Type Energy Density; Normalized Hamiltonian Closure.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technical interpretation remains tied to the local registry and equation witness.

\tzpsection{Equation Grounding}
Equation anchors: The Hamiltonian density HT H T HT for a field  phi  on MMM is given by HT=pi    -LT H T =textbackslash pitextbackslash,textbackslash dot phi - L T HT=pi   -LT, where pi=partialLTpartial   textbackslash pi=ratio partial L T partial textbackslash dot phi pi=partial   partialLT is the canonical momentum and LT L T LT includes contributions from the degenerate metric and the TZP potential. The Hamiltonian density HT H T HT for a field  phi  on MMM is given by HT=pi    -LT H T =textbackslash pitextbackslash,textbackslash dot phi - L T HT=pi   -LT, where pi=partialLTpartial   textbackslash pi=ratio partial L T partial textbackslash dot phi pi=partial   partialLT is the canonical momentum and LT L T LT includes contributions from the degenerate metric and the TZP potential.

\tzpsection{Interpretive Role}
This density is the bridge from geometric and potential structure into dynamics. Once fixed, it generates the canonical equations, the Hamilton--Jacobi form, and the quantum Hamiltonian operator used later in the registry.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Trawinistic Energy Generator Concentration Field}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Energy Generator Concentration Field Variational Analogue}: variational synonym for action, energy generation, admissible variation, or closure.
\item \textbf{Concentration Field Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0029]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0029_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0029] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Trawinistic Hamiltonian Density}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} the Trawinistic Hamiltonian density for a field  on M is H\_T=-L\_T, where =
tialL\_T/ tial is the canonical momentum and L\_T contains the d...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Trawinistic Hamiltonian Density is valid as a formal dynamical law when the Hamiltonian
or energy operator is well defined on the stated state space.''\\
\textbf{Proof:} The source statement identifies an energy, Hamiltonian, or vacuum-sector mechanism. The
CHL proof reads it as an operator claim: if the state space and localized terms are
defined, then the evolution or extraction channel is formally meaningful.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- formal dynamical-operator validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0029_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
