\tzpanchor{0979}
\tzpentryheader{0979}{TRAWINISTIC OMEGA FIELD}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{bd28f012-e854-5040-b152-e2516f55fd21}}\\
\textbf{PiID} & \tzpcode{7661119590921} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{986}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{3731.7764 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{06.1488 rad}\\
\textbf{TZPID} & \tzpcode{ID0979} & \textbf{Node Dependencies}\quad \tzpidref{0978}\\
\textbf{Registry} & \tzpcode{registry\_id\_0979} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Frequency Relation & Frequency Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
Omega\textasciicircum{}\{top\}=nabla*mathcal\{F\}\_\{t\}

\tzpsection{Canonical Equation}
\[
Omega^{\mathbb{T}}= abla\cdot F_{t}
\]
\[
Omega^{\mathrm{top}}= abla\cdot\mathcal{F}_{t}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $T$: source equation symbol.
    \item $F_{t}$: source equation symbol.
    \item $\mathcal{K}_{0979}$: canonical registry object for entry ID 0979.
    \item $\cdot F_{t}$: source equation symbol.
    \item $O$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0979 generated source Wolfram model *)
ClearAll[K0979, Cr0979, T, R, A, W, I, N];
eq0979$1 = HoldForm[Omega^T == abla*FT];
eq0979$2 = HoldForm[Omega^top == abla*FT];

K0979 = HoldForm[{eq0979$1, eq0979$2}];

N = "normalized TRAWIN closure object for TRAWINISTIC OMEGA FIELD";
I = "TRAWINISTIC OMEGA FIELD integration/comparison layer";
W = "TRAWINISTIC OMEGA FIELD wave or operator carrier";
A = "TRAWINISTIC OMEGA FIELD admissible action/amplitude condition";
R = "TRAWINISTIC OMEGA FIELD rotation/curl preservation layer";
T = "TRAWINISTIC OMEGA FIELD local source condition";

Cr0979[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0979 = Cr0979[K0979];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ TRAWINISTIC OMEGA FIELD local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ TRAWINISTIC OMEGA FIELD rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ TRAWINISTIC OMEGA FIELD admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ TRAWINISTIC OMEGA FIELD wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ TRAWINISTIC OMEGA FIELD integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for TRAWINISTIC OMEGA FIELD.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0979] TRAWINISTIC OMEGA FIELD}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
Omega^{\mathbb{T}}= abla\cdot F_{t}
\]
\[
Omega^{\mathrm{top}}= abla\cdot\mathcal{F}_{t}
\]

\paragraph{Primary Derivation.}
The relation is obtained through direct evaluation of the expression. which confirms the stated equality.
\paragraph{Equation Type.}
This statement is classified as a other relation.

\paragraph{Interpretation.}
The identity governs the objects appearing in the equation. From the TRAWIN perspective, the equation functions as the generalized carrier for the entry’s information content. Under CHL, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors TRAWINISTIC OMEGA FIELD by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
Omega^{\mathbb{T}}= abla\cdot F_{t}
\]
\[
Omega^{\mathrm{top}}= abla\cdot\mathcal{F}_{t}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0979] TRAWINISTIC OMEGA FIELD}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
TRAWINISTIC OMEGA FIELD is a registry definition in Biological and Biomolecular Analogies with secondary pressure from Category Theory and Proof Structure.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} Omega to the power top =nabla*mathcal F sub t. \textbf{Contextual meaning:} The entry reads TRAWINISTIC OMEGA FIELD as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Frequency Relation; Frequency Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, TRAWINISTIC OMEGA FIELD is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: Omega to the power mathbb T = abladot F sub t; Omega to the power top = abladot F sub t; and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Absolute-Rotation Anchoring}: The creation of a massive, theoretical, invisible spinning top that the computer uses as a fixed reference point to measure how fast the rest of the room is moving.
\item \textbf{Global-Spin Density Mapping}: The sweeping calculation of exactly how much pure, dizzying rotational energy is crammed into every single cubic inch of the reactor chamber.
\item \textbf{Omnidirectional-Torsion Sweeping}: The terrifying physics of a magnetic field that doesn't just push the plasma forward, but aggressively tries to violently twist it in every possible direction at once.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0979]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0979].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0979] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont TRAWINISTIC OMEGA FIELD}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} TRAWINISTIC OMEGA FIELD is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``TRAWINISTIC OMEGA FIELD is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0979].
\par\endgroup
\vfill
\endgroup
\endgroup
