\section*{ID9533: Definition of E}
\paragraph{Metadata.}
PiID: 8175450119307 | RTEID: RTE:P37018.7561:T4.4469 | UUID: 813fb86f-2066-540a-98c2-c70e880c3e62

\paragraph{Canonical Statement.}
0,this.featureName,this.ee),n=!1\}))\}),a=(0,x.s)(e=>\{(0,s.p)("newUIEvent",[e],void 0,this.featureName,this.ee),o.observe(document.body,\{attributes:!0,childList:!0,subtree:!0,characterData:!0\})\},100,\{leading:!0\});this.abortHandler=function()\{this.removeOnAbort?.abort(),o.disconnect(),this.abortHandler=void 0\},this.importAggregator(e,()=>i.e(478).then(i.bind(i,4393)),\{domObserver:o\})\}\}var Be=i(7378);const Ve=\{\},Ge=["appendChild","insertBefore","replaceChild"];const ze=\{\};const Ze=\{\},qe="setTimeout",Xe="setInterval",Ye="clearTimeout",Je="-start",Qe=[qe,"setImmediate",Xe,Ye,"clearImmediate"];const \$e=\{\};const\{TZ:et,d3:tt,Kp:rt,\$p:nt,wW:it,e5:ot,tH:at,uP:st,rw:ct,Lc:ut\}=Be;var dt=i(3333);class lt extends E\{static featureName=dt.TZ;constructor(e)\{super(e,dt.TZ);const t=[e.init.page\_action.enabled,e.init.performance.capture\_marks,e.init.performance.capture\_measures,e.init.user\_actions.enabled,e.init.performance.resources.enabled];var r;r=e,p(u.hG,(e,t)=>z(e,t,r),r),function(e)\{p(u.fF,function()\{(0,s.p)(u.Pl+u.fF,[(0,c.t)(),...arguments],void 0,n.K7.genericEvents,e.ee)\},e)\}(e),Se(e),Z(e),function(e)\{p(u.V1,function(t,r)\{co

\paragraph{Canonical Equation.}
\[
e={};const{TZ:et,d3:tt,Kp:rt,
\]

\paragraph{Dictionary.}
Definition of E — e=;constTZ:et,d3:tt,Kp:rt

\paragraph{Encyclopedia.}
Definition of E is an algebraic definition, written e=;constTZ:et,d3:tt,Kp:rt. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from c, o, n, s, T, Z, defining e. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
