\tzpanchor{0740}
\tzpentryheader{0740}{HOLEVO BOUND CHANNEL CAPACITY VERIFICATION}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{4baf4983-0c48-5526-b43f-699455bb3ed0}}\\
\textbf{PiID} & \tzpcode{4771309960518} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{747}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2838.6353 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.6772 rad}\\
\textbf{TZPID} & \tzpcode{ID0740} & \textbf{Node Dependencies}\quad \tzpidref{0739}\\
\textbf{Registry} & \tzpcode{registry\_id\_0740} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Aggregate Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records holevo bound channel capacity verification through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0740}}:\mathcal{X}_{\mathrm{id0740}}\longrightarrow\mathcal{Y}_{\mathrm{id0740}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0740}})=\mathcal{O}_{\mathrm{id0740}}
\]
\[
\mathcal{O}_{\mathrm{id0740}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0740}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0740}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0740}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0740 generated source Wolfram model *)
ClearAll[K0740, Cr0740, T, R, A, W, I, N];
eq0740$1 = HoldForm[Oid0740[Xid0740] -> Yid0740];
eq0740$2 = HoldForm[NTRAWIN[OId0740] == OId0740];
eq0740$3 = HoldForm[Element[OId0740[x], YAdm]];

K0740 = HoldForm[{eq0740$1, eq0740$2, eq0740$3}];

N = "normalized TRAWIN closure object for HOLEVO BOUND CHANNEL CAPACITY VERIFICATION";
I = "HOLEVO BOUND CHANNEL CAPACITY VERIFICATION integration/comparison layer";
W = "HOLEVO BOUND CHANNEL CAPACITY VERIFICATION wave or operator carrier";
A = "HOLEVO BOUND CHANNEL CAPACITY VERIFICATION admissible action/amplitude condition";
R = "HOLEVO BOUND CHANNEL CAPACITY VERIFICATION rotation/curl preservation layer";
T = "HOLEVO BOUND CHANNEL CAPACITY VERIFICATION local source condition";

Cr0740[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0740 = Cr0740[K0740];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ HOLEVO BOUND CHANNEL CAPACITY VERIFICATION local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ HOLEVO BOUND CHANNEL CAPACITY VERIFICATION rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ HOLEVO BOUND CHANNEL CAPACITY VERIFICATION admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ HOLEVO BOUND CHANNEL CAPACITY VERIFICATION wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ HOLEVO BOUND CHANNEL CAPACITY VERIFICATION integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for HOLEVO BOUND CHANNEL CAPACITY VERIFICATION.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0740] HOLEVO BOUND CHANNEL CAPACITY VERIFICATION}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0740}}:\mathcal{X}_{\mathrm{id0740}}\longrightarrow\mathcal{Y}_{\mathrm{id0740}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0740}})=\mathcal{O}_{\mathrm{id0740}}
\]
\[
\mathcal{O}_{\mathrm{id0740}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0740}})=\mathcal{O}_{\mathrm{id0740}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
This relation applies to the quantities defined above. In the TRAWIN reading, the equation functions as the mapping carrier for the entry’s information content. Within the CHL view, the derivation provides a witness morphism connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors HOLEVO BOUND CHANNEL CAPACITY VERIFICATION by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0740}}:\mathcal{X}_{\mathrm{id0740}}\longrightarrow\mathcal{Y}_{\mathrm{id0740}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0740}})=\mathcal{O}_{\mathrm{id0740}}
\]
\[
\mathcal{O}_{\mathrm{id0740}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0740] HOLEVO BOUND CHANNEL CAPACITY VERIFICATION}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
HOLEVO BOUND CHANNEL CAPACITY VERIFICATION is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} chi <= S(rho) - sum p sub i S(rho sub i). \textbf{Contextual meaning:} The entry reads HOLEVO BOUND CHANNEL CAPACITY VERIFICATION as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Aggregate Relation; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, HOLEVO BOUND CHANNEL CAPACITY VERIFICATION is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: chi le S(rho) - sum p sub i S(rho sub i ); mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Absolute Quantum Speed Limit}: The unbreakable law of the universe that slaps a hard ceiling on exactly how much real, classical data you can ever hope to squeeze out of a fuzzy quantum state.
\item \textbf{Entropy-Bottleneck Enforcement}: The frustrating math proving that even if the quantum system contains a million brilliant secrets, the physical laws of nature will only ever let you extract three of them.
\item \textbf{Maximum Observable Truth}: The final, sobering calculation that separates the infinite, swirling magic of the math from the boring, limited, and finite numbers you can actually print on a screen.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0740]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0740].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0740] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont HOLEVO BOUND CHANNEL CAPACITY VERIFICATION}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} HOLEVO BOUND CHANNEL CAPACITY VERIFICATION is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``HOLEVO BOUND CHANNEL CAPACITY VERIFICATION is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0740].
\par\endgroup
\vfill
\endgroup
\endgroup
