\tzpanchor{0042}
\tzpentryheader{0042}{Magnetic Helicity as Scale-Invariant Constraint}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{bf1444a8-f6b0-5ffb-be6d-bec2087b87d7}}\\
\textbf{PiID} & \tzpcode{3993751058209} & \textbf{TZPi}\quad \tzpcode{1}\quad \textbf{PiPE}\quad \tzpcode{49}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{163.0953 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{00.2687 rad}\\
\textbf{TZPID} & \tzpcode{ID0042} & \textbf{Node Dependencies}\quad \tzpidref{0041}\\
\textbf{Registry} & \tzpcode{registry\_id\_0042} & \textbf{Scale}\quad scale-invariant helicity\\
\textbf{LOC Classification} & QC809 helicity constraints & QC20 scaling laws\\
\textbf{arXiv Classification} & Primary: physics.plasm-ph \quad Cross-list: astro-ph.SR, math-ph & \\
\textbf{Primary Support} & Stored Helicity & Scale Weight\\
\textbf{Closure Support} & Scale-Invariant Constraint & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
This constraint states that helicity scales with the square of the magnetic field times the system size, so the dimensionless combination remains constant.

\tzpsection{Canonical Equation}
\[
\chi_{H}
=
\frac{H}{B^{2}L}
\]
\[
\chi_{H} = \mathrm{const.}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $H$: source equation symbol.
    \item $B$: magnetic field magnitude.
    \item $L$: characteristic length scale or Lagrangian carrier in the entry relation.
    \item $\mathcal{K}_{0042}$: canonical registry object for entry ID 0042.
    \item $\chi_{H}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0042 generated source Wolfram model *)
ClearAll[K0042, Cr0042, T, R, A, W, I, N];
eq0042$1 = HoldForm[chiH == H/(B^2*L)];
eq0042$2 = HoldForm[chiH == const];
eq0042$3 = HoldForm[H];
eq0042$4 = HoldForm[B^2*L];
eq0042$5 = HoldForm[chiH == H/(B^2*L) == const];

K0042 = HoldForm[{eq0042$1, eq0042$2, eq0042$3, eq0042$4, eq0042$5}];

N = "normalized TRAWIN closure object for Magnetic Helicity as Scale-Invariant Constraint";
I = "Scale-Invariant Constraint integration/comparison layer";
W = "Scale Weight wave or operator carrier";
A = "Stored Helicity admissible action/amplitude condition";
R = "Scale Weight rotation/curl preservation layer";
T = "Stored Helicity local source condition";

Cr0042[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0042 = Cr0042[K0042];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Stored Helicity local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Scale Weight rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Stored Helicity admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Scale Weight wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Scale-Invariant Constraint integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for Magnetic Helicity as Scale-Invariant Constraint.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0042] Magnetic Helicity as Scale-Invariant Constraint}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\begin{equation}
\frac{H}{\mathbf{B}^2 L}
=
\mathrm{constant}.
\end{equation}

\paragraph{Primary Derivation.}
Magnetic helicity has the characteristic scaling form:

\begin{equation}
H
\sim
\mathbf{B}^2 L .
\end{equation}

Here $\mathbf{B}^2$ captures magnetic field intensity and $L$ captures the characteristic system scale.

To remove scale dependence, divide helicity by this natural scale:

\begin{equation}
\frac{H}{\mathbf{B}^2L}.
\end{equation}

If topology is preserved under scale transformations, then this dimensionless ratio remains invariant:

\begin{equation}
\boxed{
\frac{H}{\mathbf{B}^2 L}
=
\mathrm{constant}.
}
\end{equation}

\paragraph{Interpretation.}
Helicity functions as a scale-independent constraint: the topological content remains stable even when the system size changes.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors Magnetic Helicity as Scale-Invariant Constraint by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Stored Helicity}\par
\[
H
\]
\noindent This is the topological magnetic content imported from the quantized helicity sector.\par
\noindent\textbf{2. Scale Weight}\par
\[
B^{2}L
\]
\noindent This packages the field-amplitude and size dependence that would otherwise distort cross-scale comparison.\par
\noindent\textbf{3. Scale-Invariant Constraint}\par
\[
\chi_{H}
=
\frac{H}{B^{2}L}
=
\mathrm{const.}
\]
\noindent This closes the progression by stating the helicity content in a form that survives admissible changes of system scale.\par

\clearpage
\noindent\textbf{[ID 0042] Magnetic Helicity as Scale-Invariant Constraint}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
Magnetic Helicity as Scale-Invariant Constraint is a registry definition in the active TZPID arc.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} This constraint states that helicity scales with the square of the magnetic field times the system size, so the dimensionless combination remains constant. \textbf{Contextual meaning:} The entry reads Magnetic Helicity as Scale-Invariant Constraint as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} This ratio is the bridge between helicity quantization and large-scale scaling laws. It explains why topological magnetic structure can be compared across systems without renormalizing the definition of helicity at each scale. \textbf{Lemma support:} Stored Helicity; Scale Weight; Scale-Invariant Constraint.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Helicity functions as a scale-independent constraint: the topological content remains stable even when the system size changes.

\tzpsection{Equation Grounding}
Equation anchors: The ratio HB2Lratio H textbackslash mathbf B to the power 2 L B2LH is invariant under changes of the system scale LLL in the unification framework, where HHH is magnetic helicity and Btextbackslash mathbf B B the magnetic field amplitude. The ratio HB2Lratio H textbackslash mathbf B to the power 2 L B2LH is invariant under changes of the system scale LLL in the unification framework, where HHH is magnetic helicity and Btextbackslash mathbf B B the magnetic field amplitude.

\tzpsection{Interpretive Role}
This ratio is the bridge between helicity quantization and large-scale scaling laws. It explains why topological magnetic structure can be compared across systems without renormalizing the definition of helicity at each scale.
\endgroup

\tzpsection{TZP Thesaurus}
\begingroup\footnotesize\sloppy
\begin{enumerate}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
\item \textbf{Magnetized Twist Linkage Scale Conserved Quantity Admissibility Condition}: entry-specific alternate wording for indexing, related literature, and local formal context.
\item \textbf{Magnetized Twist Linkage Conserved Quantity Rotating-Field Analogue}: rotating-field vocabulary for spin, handedness, inertial coupling, or magnetic transport.
\item \textbf{Admissibility Condition Terminology}: entry-specific alternate wording for indexing, related literature, and local formal context.
\end{enumerate}
\endgroup

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0042]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0042_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0042] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont Magnetic Helicity as Scale-Invariant Constraint}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} this constraint states that helicity scales with the square of the magnetic field times
the system size, so the dimensionless combination remains c...

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``Magnetic Helicity as Scale-Invariant Constraint is valid when the stated geometric or
topological relation preserves its invariant.''\\
\textbf{Proof:} The source statement names a geometric/topological carrier. The proof obligation is to
show that deformation, projection, or passage through the stated structure leaves the
relevant invariant or admissible region well defined.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- topological-invariance validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0042_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
