\section*{ID9413: Definition of B}
\paragraph{Metadata.}
PiID: 9612257142989 | RTEID: RTE:P36552.7694:T3.6791 | UUID: 4d6ab4d5-b65e-5a2e-9ad3-8681b8d87646

\paragraph{Canonical Statement.}
Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0367], [ID 0300] Node registry\_id\_0368 Support Titles Variation Law; Support Relation; Closure Relation Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links Hext= \$∫ Ω\$ A·B 𝑑3𝑥+ \$∫ 𝜕Ω\$ 𝛼 𝑑𝑆 \$B=∇×A\$ 𝑑 𝑑𝑡 Hext=0 [ID 0369] Helicity Conservation Law TZPID ID0369 UUID 9c01e38c-cfaf-58f7-9131-476cc2f25831 Type Scaling / Diagnostic Statement Scale diagnostic LOC Classification Working routing: QA273 dimensionless analysis; QC statistical diagnostics arXiv Classification Primary: math-ph; Cross-list: nlin.PS, physics.data-an Canonical Statement This entry develops helicity conservation law inside t

\paragraph{Canonical Equation.}
\[
B=∇×A
\]

\paragraph{Dictionary.}
Definition of B — B=∇×A

\paragraph{Encyclopedia.}
Definition of B is an algebraic definition, written B=∇×A. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from A, defining B. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
