\section*{ID8540: REGULATORY DOMAIN COHERENCE Canonical Statutory Formula: D\_coh ≈ 6.5kb ⟹…}
\paragraph{Metadata.}
PiID: 6551658276584 | RTEID: RTE:P33162.7165:T4.3765 | UUID: f87ed786-9830-5644-b156-ec14bdc7ad5a

\paragraph{Canonical Statement.}
[ID 1126] REGULATORY DOMAIN COHERENCE Canonical Statutory Formula: \$D\_\{coh\} \textbackslash{}approx 6.5kb \textbackslash{}implies \textbackslash{}Psi\_\{domain\}\$ Formal Technical Dissertation: Postulates that the \textasciitilde{}6.5kb functional unit acts as a single coherent quantum domain (\$\textbackslash{}Psi\_\{domain\}\$). This allows the system to treat the genome not as a sequence of discrete bases, but as a macroscopic quantum object with 153,600 addressable "macroscopically distinct" states. Source: [2], [7], [8]

\paragraph{Canonical Equation.}
\[
D_{coh} \approx 6.5kb \implies \Psi_{domain}
\]

\paragraph{Dictionary.}
REGULATORY DOMAIN COHERENCE Canonical Statutory Formula: D\_coh ≈ 6.5kb ⟹ Ψ\_domain Formal Technical Dissertation: Postulates that the \textasciitilde{}6.5kb functional unit acts as a single coherent quantum domain (Ψ\_domain).

\paragraph{Encyclopedia.}
REGULATORY DOMAIN COHERENCE Canonical Statutory Formula: D\_coh ≈ 6.5kb ⟹… is a scaling / order-of-magnitude relation, written D\_coh ≈ 6.5kb ⟹ Ψ\_domain. It expresses a scaling or proportionality, capturing how the quantity grows with its parameters. It is built from D\_coh, k, b, o, m, a. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
