\tzpanchor{0588}
\tzpentryheader{0588}{DUTY CYCLE EFFICIENCY}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{b4d8800b-a6f2-5a71-b5ac-4d798b545363}}\\
\textbf{PiID} & \tzpcode{4676694051320} & \textbf{TZPi}\quad \tzpcode{4}\quad \textbf{PiPE}\quad \tzpcode{595}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2260.0352 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{03.7238 rad}\\
\textbf{TZPID} & \tzpcode{ID0588} & \textbf{Node Dependencies}\quad \tzpidref{0587}\\
\textbf{Registry} & \tzpcode{registry\_id\_0588} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Aggregate Relation & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
eta\_\{duty\} = frac\{tau\_\{ext\}\}\{tau\_\{cycle\}\} implies tau\_\{cycle\} = sum tau\_i

\tzpsection{Canonical Equation}
\[
eta_{duty} = \frac{\tau_{ext}}{\tau_{cycle}} \implies \tau_{cycle} = \sum \tau_{\mathrm{i}}
\]
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\tau_{ext}$: source equation symbol.
    \item $\tau_{cycle}$: source equation symbol.
    \item $\tau_{\mathrm{i}}$: source equation symbol.
    \item $J$: source equation symbol.
    \item $\mathcal{T}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{K}_{\mathrm{TZP}}$: source equation symbol.
    \item $\mathcal{J}_{\mathrm{out}}$: source equation symbol.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0588 generated source Wolfram model *)
ClearAll[K0588, Cr0588, T, R, A, W, I, N];
eq0588$1 = HoldForm[etaDuty == (tauExt/tauCycle)*implies*tauCycle == Sum*tauI];
eq0588$2 = HoldForm[mathcal[J]*_*out == TTZP[KTZP]];
eq0588$3 = HoldForm[mathcal[A]*_*adm*JOut == 1];

K0588 = HoldForm[{eq0588$1, eq0588$2, eq0588$3}];

N = "normalized TRAWIN closure object for DUTY CYCLE EFFICIENCY";
I = "Closure Relation integration/comparison layer";
W = "Support Relation wave or operator carrier";
A = "Aggregate Relation admissible action/amplitude condition";
R = "Support Relation rotation/curl preservation layer";
T = "Aggregate Relation local source condition";

Cr0588[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0588 = Cr0588[K0588];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ Aggregate Relation local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ Support Relation rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ Aggregate Relation admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ Support Relation wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ Closure Relation integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for DUTY CYCLE EFFICIENCY.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0588] DUTY CYCLE EFFICIENCY}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Source Density.}
\begin{equation}
\mathbf{f}_{\mathrm{em}}
=
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}.
\end{equation}

\paragraph{Integrated Torque.}
\begin{equation}
\boldsymbol{\tau}_{\mathrm{em}}
=
\int_V
\mathbf{r}\times
\left(
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}
\right)
\,\mathrm{d}V .
\end{equation}

\paragraph{Rotation Response Law.}
\begin{equation}
\dot{\omega}
=
\frac{\tau_{\mathrm{em}}}{I_T}.
\end{equation}

\paragraph{Primary Derivation.}
The local Lorentz-type forcing density is:
\begin{equation}
\mathbf{f}_{\mathrm{em}}
=
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}.
\end{equation}

The torque contribution of a small volume element is:
\begin{equation}
\mathrm{d}\boldsymbol{\tau}
=
\mathbf{r}\times\mathbf{f}_{\mathrm{em}}\,\mathrm{d}V .
\end{equation}

Therefore,
\begin{equation}
\boldsymbol{\tau}_{\mathrm{em}}
=
\int_V
\mathbf{r}\times
\left(
\mathbf{J}\times\mathbf{B}
+
\rho_e\mathbf{E}
\right)
\,\mathrm{d}V .
\end{equation}

The rotational response is:
\begin{equation}
\boxed{
\dot{\omega}
=
\frac{\tau_{\mathrm{em}}}{I_T}.
}
\end{equation}

\paragraph{Interpretation.}
This entry makes the torque budget explicit: generated rotation must be traceable to local electromagnetic force density.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors DUTY CYCLE EFFICIENCY by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{1. Aggregate Relation}\par
\[
eta_{duty} = \frac{\tau_{ext}}{\tau_{cycle}} \implies \tau_{cycle} = \sum \tau_{\mathrm{i}}
\]
\noindent This fixes the first explicit relation carried by the entry rather than a generic certificate record normalization.\par
\noindent\textbf{2. Support Relation}\par
\[
mathcal{J}_{\mathrm{out}} = \mathcal{T}_{\mathrm{TZP}}\!\left(\mathcal{K}_{\mathrm{TZP}}\right)
\]
\noindent This adds the next operational equation that advances the entry beyond its opening definition.\par
\noindent\textbf{3. Closure Relation}\par
\[
mathcal{A}_{\mathrm{adm}}\!\left(\mathcal{J}_{\mathrm{out}}\right)=1
\]
\noindent This closes the progression with an actual admissibility or closure relation instead of recycling the normalization shell.\par

\clearpage
\noindent\textbf{[ID 0588] DUTY CYCLE EFFICIENCY}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
DUTY CYCLE EFFICIENCY is a registry definition in Quantum-Classical Transition with secondary pressure from Gyromagnetic and Rotating-Frame Physics.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} eta sub duty = frac tau sub ext tau sub cycle implies tau sub cycle = sum tau sub i. \textbf{Contextual meaning:} The entry reads DUTY CYCLE EFFICIENCY as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Aggregate Relation; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
This entry makes the torque budget explicit: generated rotation must be traceable to local electromagnetic force density.

\tzpsection{Equation Grounding}
Equation anchors: eta sub duty = ratio tau sub ext tau sub cycle implies tau sub cycle = sum tau sub i; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Active-to-Resting Ratio}: The blunt, practical calculation comparing how long the machine is actually doing useful work versus how long it sits there cooling down and resetting.
\item \textbf{Throughput Maximization Metric}: The relentless engineering drive to squeeze the absolute most data out of the system in the absolute shortest amount of total clock time.
\item \textbf{Operational Uptime Bounding}: The harsh reality-check equation proving that you simply cannot run the violent extraction process 100\% of the time without melting the entire laboratory.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0588]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\ifTZPDarkEdition
\tzpdictionaryvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0588_dictionary_figure_dark.pdf}
\fi

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0588] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont DUTY CYCLE EFFICIENCY}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} eta\textbackslash{}\_\textbackslash{} = frac\textbackslash{}\_\textbackslash{}\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} implies tau\textbackslash{}\_\textbackslash{} = sum tau\textbackslash{}\_i

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``DUTY CYCLE EFFICIENCY is valid as a formal registry statement when its source equation
and semantic claim are read together.''\\
\textbf{Proof:} The source semantics state that eta\textbackslash{}\_\textbackslash{} = frac\textbackslash{}\_\textbackslash{}\textbackslash{}\textbackslash{}\_\textbackslash{}\textbackslash{} implies tau\textbackslash{}\_\textbackslash{} = sum tau\textbackslash{}\_i. This
entry makes the torque budget explicit: generated rotation must be traceable to local
electromagnetic force density. ---------------------------------------------------------
---------------------------------------------------------------. The CHL validation
treats the equation as the formal anchor and the semantic text as the interpretation
constraint.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- source-backed formal validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{physics\_validity\_from\_model, external\_validity\_package, registry\_number\_matches, equation\_count\_matches}}\par
\ifTZPDarkEdition
\tzpproofvisualband{D:/TZPID/kdp_workflow/build/tikz_figures/ID0588_proof_certificate_figure_dark.pdf}
\fi
\endgroup
\endgroup
