\section*{ID9361: Definition of Δ𝑈}
\paragraph{Metadata.}
PiID: 0041529700287 | RTEID: RTE:P36350.8419:T3.3463 | UUID: 9c43dc9b-632d-5b66-8e11-f600e639179d

\paragraph{Canonical Statement.}
lle Certificate Lean Certificate Coq Certificate Isabelle audit: included in aggregate HOL build. Lean audit: compiled corpus certificate. Rocq audit: compiled corpus certificate. Dependencies and Test Handle Dependencies [ID 0073], [ID 0074] Node registry\_id\_0075 Support Titles Internal-Energy Balance; Entropy Change; TRAWIN Second Law Test Handle If an admissible process violates the corrected entropy bound without compensating zero-point accounting, this entry fails. Canonical Equation Links \$Δ𝑈=𝑄+𝑊 Δ𝑆 Δ𝑆≥\$ 𝑄 𝑇eff \$+ΣTZP\$ [ID 0076] Fluctuation–Dissipation Relations TZPID ID0076 UUID 16019d19-3151-534d-902a-66290c04a7b3 Type Response Law Scale noise-response coupling LOC Classification Working routing: QC174 fluctuation-dissipation; QC311 linear response arXiv Classification Primary: cond-mat.stat-mech Cross-list: quant-ph, hep-th Canonical Statement Fluctuations and dissipation are not independent.

\paragraph{Canonical Equation.}
\[
Δ𝑈=𝑄+𝑊 Δ𝑆 Δ𝑆≥
\]

\paragraph{Dictionary.}
Definition of Δ𝑈 — Δ𝑈=𝑄+𝑊 Δ𝑆 Δ𝑆≥

\paragraph{Encyclopedia.}
Definition of Δ𝑈 is an algebraic definition, written Δ𝑈=𝑄+𝑊 Δ𝑆 Δ𝑆≥. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
