\section*{ID8788: CTC REGION IMPLICIT DEFINITION Canonical Statutory Formula}
\paragraph{Metadata.}
PiID: 0738602515227 | RTEID: RTE:P34125.7556:T5.9633 | UUID: 44215a86-dc32-52c0-8e63-006868f56d97

\paragraph{Canonical Statement.}
[ID 1161] CTC REGION IMPLICIT DEFINITION Canonical Statutory Formula: \$CTC\_\{region\} := \{ (r, \textbackslash{}theta, \textbackslash{}phi, t) \textbackslash{}in \textbackslash{}mathcal\{M\} \textbackslash{}mid g\_\{\textbackslash{}phi\textbackslash{}phi\} < 0 \textbackslash{}land r\_+ < r < r\_\{ergosphere\} \}\$ Formal Technical Dissertation: Defines the spacetime volume where Closed Timelike Curves (CTCs) are topologically permitted. Within this region, the metric component \$g\_\{\textbackslash{}phi\textbackslash{}phi\}\$ becomes negative, allowing the temporal coordinate to behave spatially, facilitating retrocausal trajectory formation within the Kerr-like vortex geometry. Source: [1]

\paragraph{Canonical Equation.}
\[
CTC_{region} := { (r, \theta, \phi, t) \in \mathcal{M} \mid g_{\phi\phi} < 0 \land r_+ < r < r_{ergosphere} }
\]

\paragraph{Dictionary.}
CTC REGION IMPLICIT DEFINITION Canonical Statutory Formula: \$CTC\_region := (r, , , t) M g\_ < 0 r\_+ < r < r\_ergosphere \$ Formal Technical Dissertation: Defines the spacetime volume where Closed Timelike Curves (CTCs) are topologically permitted.

\paragraph{Encyclopedia.}
CTC REGION IMPLICIT DEFINITION Canonical Statutory Formula is an inequality / bound, written CTC\_region := (r, θ, φ, t) in M mid g\_φφ < 0 land r\_+ < r < r\_ergosphere. It states an inequality or bound that constrains the admissible range of the quantity. It is built from θ, φ, C, T, C\_region, r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
