\tzpanchor{0771}
\tzpentryheader{0771}{THELEMNISCATIC ZERO POINT SET}

\begingroup\small
\begingroup\scriptsize
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{0.92}
\noindent\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth}p{0.36\linewidth}X@{}}
\textbf{UUID} & \multicolumn{2}{l@{}}{\tzpcode{7cb8a121-489b-5e40-8335-9f33be6b4f32}}\\
\textbf{PiID} & \tzpcode{9780499510597} & \textbf{TZPi}\quad \tzpcode{9}\quad \textbf{PiPE}\quad \tzpcode{778}\\
\textbf{RTEID} & \textbf{Poloidal $\theta$}\quad \tzpcode{2959.0152 rad} & \textbf{Toroidal $\phi$}\quad \tzpcode{04.8755 rad}\\
\textbf{TZPID} & \tzpcode{ID0771} & \textbf{Node Dependencies}\quad \tzpidref{0770}\\
\textbf{Registry} & \tzpcode{registry\_id\_0771} & \textbf{Scale}\quad transfer\\
\textbf{LOC Classification} & QA641 manifolds and topology & QC174.17 mathematical physics\\
\textbf{arXiv Classification} & Primary: math-ph & Cross-list: gr-qc, math.DG\\
\textbf{Primary Support} & Canonical Definition & Support Relation\\
\textbf{Closure Support} & Closure Relation & \\
\end{tabularx}\par
\endgroup
\endgroup

\tzpsection{Canonical Statement}
The entry records thelemniscatic zero point set through a normalized Octonary TRAWIN operator chain.

\tzpsection{Canonical Equation}
\[
\mathcal{O}_{\mathrm{id0771}}:\mathcal{X}_{\mathrm{id0771}}\longrightarrow\mathcal{Y}_{\mathrm{id0771}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0771}})=\mathcal{O}_{\mathrm{id0771}}
\]
\[
\mathcal{O}_{\mathrm{id0771}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\begin{minipage}[t]{0.49\linewidth}
\tzpsection{Canonical Symbol Key}
\begingroup
\small
\raggedright
\textbf{Source equation symbols.}\par
\begin{itemize}[leftmargin=1.35em,itemsep=1pt,topsep=1pt,parsep=0pt]
    \item $\mathcal{O}_{\mathrm{id0771}}$: canonical operator or carrier map for the entry.
    \item $\mathcal{X}_{\mathrm{id0771}}$: source domain or input state space for the entry map.
    \item $\mathcal{Y}_{\mathrm{id0771}}$: target domain or output state space for the entry map.
    \item $\mathcal{N}_{\mathrm{TRAWIN}}$: TRAWIN normalization operator applied to the entry relation.
    \item $\mathcal{Y}_{\mathrm{adm}}$: admissible output space selected by the source equation.
\end{itemize}
\endgroup
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
\tzpsection{Wolfram Form}
\begingroup
\scriptsize
\raggedright
\textbf{Source Wolfram model.}\par
\begin{Verbatim}[fontsize=\tiny,breaklines=true,breakanywhere=true]
(* TZPID ID0771 generated source Wolfram model *)
ClearAll[K0771, Cr0771, T, R, A, W, I, N];
eq0771$1 = HoldForm[Oid0771[Xid0771] -> Yid0771];
eq0771$2 = HoldForm[NTRAWIN[OId0771] == OId0771];
eq0771$3 = HoldForm[Element[OId0771[x], YAdm]];

K0771 = HoldForm[{eq0771$1, eq0771$2, eq0771$3}];

N = "normalized TRAWIN closure object for THELEMNISCATIC ZERO POINT SET";
I = "THELEMNISCATIC ZERO POINT SET integration/comparison layer";
W = "THELEMNISCATIC ZERO POINT SET wave or operator carrier";
A = "THELEMNISCATIC ZERO POINT SET admissible action/amplitude condition";
R = "THELEMNISCATIC ZERO POINT SET rotation/curl preservation layer";
T = "THELEMNISCATIC ZERO POINT SET local source condition";

Cr0771[expr_] := HoldForm[N[I[W[A[R[T[expr]]]]]]];

Result0771 = Cr0771[K0771];
\end{Verbatim}
\endgroup
\end{minipage}

\par\vspace{0.45\baselineskip}
\noindent\begin{minipage}[t]{\linewidth}
\begingroup
\small
\raggedright
\textbf{TRAWIN Operator Key.}\par
\noindent\textbf{Time/localization operator:} $\mathsf{T}\!\left[\mathrm{local}\right]$ THELEMNISCATIC ZERO POINT SET local source condition.\par
\noindent\textbf{Rotation/curl operator:} $\mathsf{R}\!\left[\nabla\times\right]$ THELEMNISCATIC ZERO POINT SET rotation/curl preservation layer.\par
\noindent\textbf{Action/amplitude operator:} $\mathsf{A}\!\left[\mathrm{admissible}\right]$ THELEMNISCATIC ZERO POINT SET admissible action/amplitude condition.\par
\noindent\textbf{Wave/d'Alembertian operator:} $\mathsf{W}\!\left[\Box\right]$ THELEMNISCATIC ZERO POINT SET wave or operator carrier.\par
\noindent\textbf{Integration operator:} $\mathsf{I}\!\left[\int\right]$ THELEMNISCATIC ZERO POINT SET integration/comparison layer.\par
\noindent\textbf{Normalization operator:} $\mathsf{N}\!\left[\mathrm{normalized}\right]$ normalized TRAWIN closure object for THELEMNISCATIC ZERO POINT SET.\par
\endgroup
\end{minipage}

\clearpage
\noindent\textbf{[ID 0771] THELEMNISCATIC ZERO POINT SET}\par
\vspace{0.35em}
\tzpsection{Derivation Layer}
\paragraph{Primary Equation.}
\[
\mathcal{O}_{\mathrm{id0771}}:\mathcal{X}_{\mathrm{id0771}}\longrightarrow\mathcal{Y}_{\mathrm{id0771}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0771}})=\mathcal{O}_{\mathrm{id0771}}
\]
\[
\mathcal{O}_{\mathrm{id0771}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]

\paragraph{Primary Derivation.}
The first line specifies a map, while the subsequent line provides its explicit form \( \mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0771}})=\mathcal{O}_{\mathrm{id0771}} \). Verifying that the formula satisfies the declared mapping properties confirms that the map is well defined.
\paragraph{Equation Type.}
This statement is classified as a map relation.

\paragraph{Interpretation.}
It pertains to the fields or functions just described. Interpreted through TRAWIN, the equation functions as the mapping carrier for the entry’s information content. Within the CHL view, the derivation provides an explicit term connecting the canonical proposition to its proof certificate.

\par\vspace{0.35em}
\noindent\textbf{Derivable Consequences.}\quad
\begingroup
\footnotesize
\raggedright
The canonical equation anchors THELEMNISCATIC ZERO POINT SET by connecting the source condition to the derivation layer and proof certificate.
\par\endgroup

\tzpsection{Equation Support}
\noindent\textbf{Canonical Support Relation}\par
\[
\mathcal{O}_{\mathrm{id0771}}:\mathcal{X}_{\mathrm{id0771}}\longrightarrow\mathcal{Y}_{\mathrm{id0771}}
\]
\[
\mathcal{N}_{\mathrm{TRAWIN}}(\mathcal{O}_{\mathrm{id0771}})=\mathcal{O}_{\mathrm{id0771}}
\]
\[
\mathcal{O}_{\mathrm{id0771}}(x)\in\mathcal{Y}_{\mathrm{adm}}
\]
\noindent The support equation repeats the canonical relation so the derivation page remains self-contained.\par

\clearpage
\noindent\textbf{[ID 0771] THELEMNISCATIC ZERO POINT SET}\par
\vspace{0.35em}
\tzpsection{Dictionary}
\begingroup\small
\tzpsection{Definition}
THELEMNISCATIC ZERO POINT SET is a registry definition in Vortex and Cymatic Transport with secondary pressure from Resonance and Phase Locking.

% BEGIN TZP CONTEXTUAL MEANING
\tzpsection{Contextual Meaning}
\begingroup\footnotesize\setlength{\emergencystretch}{3em}\sloppy
\textbf{Formal statement:} TZP:= xinmathbb R to the power n |Phi(x)=0. \textbf{Contextual meaning:} The entry reads THELEMNISCATIC ZERO POINT SET as a controlled technical headword whose equation layer, proof route, and registry role are interpreted together. \textbf{Derivable consequences:} The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell. \textbf{Lemma support:} Canonical Definition; Support Relation; Closure Relation.\par
\endgroup
% END TZP CONTEXTUAL MEANING

\tzpsection{Technical Interpretation}
Technically, THELEMNISCATIC ZERO POINT SET is read through the local equation chain and the TRAWIN normalization recorded on the entry page.

\tzpsection{Equation Grounding}
Equation anchors: TZP:= xinmathbb R to the power n |Phi(x)=0; mathcal J sub out = T sub TZP ( K sub TZP ); and mathcal A sub adm ( J sub out )=1. Proof route: show that the stated equations form a coherent progression for the entry and remain compatible under the TRAWIN ordering. Formalization route: prove that the final closure relation follows from the preceding entry-specific equations.

\tzpsection{Interpretive Role}
The entry now reads through actual sourced equations, so its local arc is carried by explicit mathematical relations rather than a uniform quaternary certificate record shell.
\endgroup

\tzpsection{TZP Thesaurus}
\begin{enumerate}[leftmargin=1.6em,itemsep=6pt,topsep=4pt]
\item \textbf{Figure-Eight Singularity Locus}: The realization that the core of the machine isn't a single, crushing dot, but a violently whipping, infinitely thin line crossed perfectly over itself like a glowing infinity symbol.
\item \textbf{Dual-Attractor Orbital Dynamics}: The terrifying math showing that the plasma is constantly, frantically trying to fall down two completely different, competing black holes at the exact same time.
\item \textbf{Central-Node Phase Cancellation}: The exact, mathematically perfect dead-zone right where the two loops of the figure-eight cross, creating a spot of utter, absolute silence in the middle of a roaring star.
\end{enumerate}

\tzpsection{Encyclopedia Mathematica}
\begingroup\footnotesize\sloppy
The visual plate below is reserved for the source-specific equation and progression graphic for [ID 0771]. It is included only as a companion to the canonical equation, not as a substitute for the formal text.
\par\endgroup
\begingroup\footnotesize\itshape
Visual plate pending source-specific approval for [ID 0771].
\par\endgroup

\clearpage
\begingroup\tzpsupportsetup
\noindent\textbf{\fontsize{10.8pt}{12.8pt}\selectfont [ID 0771] Constructive Logic and Proof Certificate}\par
\noindent\textbf{\fontsize{10pt}{12pt}\selectfont THELEMNISCATIC ZERO POINT SET}\par
\vspace{0.45em}
\begingroup
\footnotesize
\setlength{\parskip}{0.22em}
\setlength{\parindent}{0pt}
\noindent\textbf{Curry--Howard--Lambek Interpretation}\par
Under the Curry--Howard--Lambek correspondence, this registry entry is read as a typed proof
object: the stated source condition supplies the proposition, the derivation supplies the
morphism, and the proof certificate records the machine handles needed to check the obligation
in the formal registry.

\vspace{0.45em}
\noindent\textbf{CHL Proof}\par
\textbf{Statement:} THELEMNISCATIC ZERO POINT SET is read as a source-backed proof obligation.

\textbf{Logic Validation:}\\
\textbf{Proposition:} ``THELEMNISCATIC ZERO POINT SET is admissible under the named source equation and derivation.''\\
\textbf{Proof:} The canonical statement supplies the proposition, the derivation supplies the witness, and the TRAWIN operator chain records the normalization path.

\textbf{VERDICT:} \ensuremath{\checkmark}\ \textbf{TRUE} --- conditional registry validation

\textbf{Formal Status:} \ensuremath{\checkmark}\ THEORETICAL -- source-backed CHL proof obligation

\textbf{Physical Status:} THEORETICAL -- requires model-specific empirical interpretation
\par\vspace{0.45em}
\noindent{\tiny\textbf{Isabelle/HOL.} \tzpplaincode{registry\_number\_matches, equation\_count\_matches}}\par
\vfill
\begingroup\footnotesize\itshape
Proof visual pending source-specific approval for [ID 0771].
\par\endgroup
\vfill
\endgroup
\endgroup
