\section*{ID7631: Physical Interpretation (Beat-Frequency View): ω\_rm beat\textasciicircum{}star}
\paragraph{Metadata.}
PiID: 4032659184044 | RTEID: RTE:P29632.8677:T4.8436 | UUID: d418f0d7-e05b-5373-b105-f6f65b198ddd

\paragraph{Canonical Statement.}
\# 3) Physical interpretation (beat-frequency view) - When local oscillators drift relative to the neighborhood, a **beat frequency** forms. If that beat frequency matches the resonant vessel-drop frequency \textbackslash{}(\textbackslash{}omega\_\{\textbackslash{}rm beat\}\textasciicircum{}\textbackslash{}star\textbackslash{}), the vacuum oscillators produce constructive interference of the half-step slips → burst of quasi-particle creation. - Regions of high \textbackslash{}(R\textbackslash{}) (local phase locking) concentrate many oscillators undergoing the same beat → multiplicative effect on \textbackslash{}(\textbackslash{}lambda\textbackslash{}). - This makes creation *spatially localized* where both (a) beat condition holds and (b) coherence exists → seeds of mass density.

\paragraph{Canonical Equation.}
\[
\omega_{\rm beat}^\star
\]

\paragraph{Dictionary.}
Physical Interpretation (Beat-Frequency View): ω\_rm beat\textasciicircum{}star — ω\_rm beat\textasciicircum{}star

\paragraph{Encyclopedia.}
Physical Interpretation (Beat-Frequency View): ω\_rm beat\textasciicircum{}star is a symbolic expression, written ω\_rm beat\textasciicircum{}star. It introduces a symbol or relation used elsewhere in the framework. It is built from b, a. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
