\section*{ID8568: Definition of 3r}
\paragraph{Metadata.}
PiID: 8790029095170 | RTEID: RTE:P33271.4468:T4.5556 | UUID: e4e7a25c-ec0f-5640-9d02-1fe402f7108f

\paragraph{Canonical Statement.}
Statutory Formula: \$Γ̂up \$ = \$lim∆t→tP \$ \$∆I ∆t ⊗ N̂ =⇒ \$ 1043 Hz Formal Technical Dissertation: Defines the fundamental temporal discretization of the manifold. Time is reified as the discrete execution of \$Γ̂up \$ at the singularity. The acoustic carrier must synchronize with a sub-harmonic of this rate to achieve "Causal Phase-Lock." Source: [ID 1036] CYMATIC-VACUUM COUPLING \$(Ξcym) \$ Canonical Statutory Formula: \$Ξcym \$ = \$∫\$ \$L ρ(r, t) \$ · \$Φ̂acoustic[ω, k, t]d \$ \$3r =⇒ δL ∝ ∇ \$ · S Formal Technical Dissertation: Estab-lishes the transduction mechanism between longitudinal acoustic waves (17.2 kHz) and the topo-logical vacuum plenum. The acoustic wave acts as a "Coarse-Graining" tool to twist the vacuum flow near the TZP, creating an "Acoustic Coriolis" effect. Source: [ID 1037] SUPERCONDUCTING PAIR CREATION OPERATOR \$(ĤSC) \$ Canonical Statutory Formula:

\paragraph{Canonical Equation.}
\[
3r =⇒ δL ∝ ∇
\]

\paragraph{Dictionary.}
Statutory Formula: Γ̂up = lim∆t→tP ∆I ∆t ⊗ N̂ =⇒ 1043 Hz Formal Technical Dissertation: Defines the fundamental temporal discretization of the manifold.

\paragraph{Encyclopedia.}
Definition of 3r is an algebraic definition, written 3r =⇒ δL ∝ ∇. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from L, defining 3r. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
