\section*{ID7005: Quick Practical Checklist (Actionable Next Steps)}
\paragraph{Metadata.}
PiID: 7746491599505 | RTEID: RTE:P27201.9707:T0.8382 | UUID: c3db7c96-d947-5f67-ba8c-5a54d81a3c9b

\paragraph{Canonical Statement.}
\# Quick practical checklist (actionable next steps) 1. Decide: optical vs microwave prototyping. For faster lab iteration, optical with dye at room temp is reasonable. For ultimate coherence, microwave superconducting route is easier for very long τ but needs cryo expertise. 2. Simulate EM: run FDTD/FEM for your exact torus geometry to extract precise \textbackslash{}(V\_\{\textbackslash{}text\{eff\}\}, Q,\textbackslash{}) and mode overlap with a dye layer. 3. Run the ODE script above with your simulated \textbackslash{}(V\_\{\textbackslash{}text\{eff\}\}\textbackslash{}), \textbackslash{}(Q\textbackslash{}) and realistic pump coupling efficiency to estimate required pump power and the steady-state N. 4. Prototype a larger-radius ring (e.g., \textbackslash{}(R=200\textbackslash{},\textbackslash{}mu\textbackslash{})m) first — easier to fabricate, easier to couple, slightly lower mode density to observe behavior before scaling down. 5. Instrumentation: prepare spectrometer, confocal microscope, and a time-correlated single-photon module or fast photodiode for lifetime work.

\paragraph{Canonical Equation.}
\[
R=200\,\mu
\]

\paragraph{Dictionary.}
Quick practical checklist (actionable next steps) 1 [ID7005]

\paragraph{Encyclopedia.}
Quick Practical Checklist (Actionable Next Steps) is an algebraic definition, written R=200 μ. It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from μ, defining R. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
