\section*{ID8531: FRACTAL SURFACE FIELD Canonical Statutory Formula: g(θ, φ)}
\paragraph{Metadata.}
PiID: 6974867626551 | RTEID: RTE:P33127.7675:T4.3189 | UUID: 3739fa3e-08af-568b-a6db-319afff0d944

\paragraph{Canonical Statement.}
[ID 1136] FRACTAL SURFACE FIELD Canonical Statutory Formula: \$g(\textbackslash{}theta, \textbackslash{}phi) = \textbackslash{}sum\_k a\_k Re(Y\_\{l\_k m\_k\}(\textbackslash{}theta, \textbackslash{}phi)), \textbackslash{}quad a\_k \textbackslash{}propto l\_k\textasciicircum{}\{-\textbackslash{}alpha\}\$ Formal Technical Dissertation: Defines the "engraving" pattern on the DAANSsphere surface. The field is constructed from spherical harmonics (\$Y\_\{lm\}\$) with amplitudes (\$a\_k\$) following a power law (\$l\_k\textasciicircum{}\{-\textbackslash{}alpha\}\$), ensuring scale-invariant fractal roughness to induce mode mixing. Source: [4]

\paragraph{Canonical Equation.}
\[
g(\theta, \phi) = \sum_k a_k Re(Y_{l_k m_k}(\theta, \phi)), \quad a_k \propto l_k^{-\alpha}
\]

\paragraph{Dictionary.}
FRACTAL SURFACE FIELD Canonical Statutory Formula: \$g( , ) = \_k a\_k Re(Y\_l\_k m\_k( , )), a\_k l\_k\textasciicircum{}- \$ Formal Technical Dissertation: Defines the "engraving" pattern on the DAANSsphere surface.

\paragraph{Encyclopedia.}
FRACTAL SURFACE FIELD Canonical Statutory Formula: g(θ, φ) is a series / summation, written g(θ, φ) = ∑\_k a\_k Re(Y\_l\_k m\_k(θ, φ)), a\_k ∝ l\_k\textasciicircum{}-α. It is expressed as a sum or series over modes or indices, superposing discrete contributions. It is built from θ, φ, α, k, a\_k, R, defining g(θ, φ). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
