\section*{ID8855: COUPLING ACTIVATION RAMP Canonical Statutory Formula: H Int(t)}
\paragraph{Metadata.}
PiID: 3028244186041 | RTEID: RTE:P34385.9315:T0.1088 | UUID: d75fafa8-db5a-51ae-9d55-2b0d014eff49

\paragraph{Canonical Statement.}
[ID 1074] COUPLING ACTIVATION RAMP Canonical Statutory Formula: \$\textbackslash{}hat\{H\} \{int\}(t) = \textbackslash{}lambda(t) \textbackslash{}sum \textbackslash{}hat\{\textbackslash{}Psi\} \{left\} \textbackslash{}otimes \textbackslash{}hat\{\textbackslash{}Psi\}\_\{right\} \textbackslash{}implies \textbackslash{}text\{TZP Ignition\}\$ Formal Technical Dissertation: Marks the "Ignition" of the TZP. Gradually increasing coupling strength between Left (Information) and Right (Energy) vortices initiates the interchange through the lemniscatic crossing point. Source: [43]

\paragraph{Canonical Equation.}
\[
\hat{H} {int}(t) = \lambda(t) \sum \hat{\Psi} {left} \otimes \hat{\Psi}_{right} \implies \text{TZP Ignition}
\]

\paragraph{Dictionary.}
COUPLING ACTIVATION RAMP Canonical Statutory Formula: \$H int(t) = (t) left \_right TZP Ignition\$ Formal Technical Dissertation: Marks the "Ignition" of the TZP.

\paragraph{Encyclopedia.}
COUPLING ACTIVATION RAMP Canonical Statutory Formula: H Int(t) is a hamiltonian construction, written H int(t) = λ(t) ∑ Ψ left ⊗ Ψ\_right ⟹ TZP Ignition. It defines a Hamiltonian that generates the system's time evolution and encodes its energy. It is built from λ, Ψ, l, f, r, g, defining H int(t). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
