\section*{ID9261: Definition of B\_θ)q(r)}
\paragraph{Metadata.}
PiID: 7388377814233 | RTEID: RTE:P35962.5197:T2.7065 | UUID: 1697d782-290a-5782-8039-0f7dd120d6d1

\paragraph{Canonical Statement.}
Test Handle: Attempt to detect gravitomagnetic fields using sensitive gyroscopes or interferometry; compare observations with predicted magnitude and spatial dependence. Canonical Registry Vol. 01 113 Trawin Zero Point Contextus Canonicus 2 TZP CANONICAL REGISTRY – ENTRIES 150–199 2.0.177 ID 326: Toroidal Field Safety Factor Constraint Type: Structural Constraint Formal Statement: For a nested toroidal magnetic confinement configuration, the safety factor \$q(r)=rB/(R0Bθ)q(r)\$ = r B\_\{\textbackslash{}phi\}/(R\_0 \$B\_\{\textbackslash{}theta\})q(r)=rB/(R0Bθ)\$ must exceed a critical value \$qcritical≈2.8q\_\{\textbackslash{}text\{critical\}\}\textbackslash{}approx 2.8qcritical≈2.8\$ to ensure stability. Interpretive Meaning: The safety factor characterizes the ratio of toroidal to poloidal field components in a toroidal confinement system. Exceeding the critical threshold prevents kink and tearing instabilities, ensuring stable confinement of magnetic flux. Dependencies: ID 323. Derivabl

\paragraph{Canonical Equation.}
\[
B_{\theta})q(r)=rB/(R0Bθ)
\]

\paragraph{Dictionary.}
Test Handle: Attempt to detect gravitomagnetic fields using sensitive gyroscopes or interferometry; compare observations with predicted magnitude and spatial dependence.

\paragraph{Encyclopedia.}
Definition of B\_θ)q(r) is an algebraic definition, written B\_θ)q(r)=rB/(R0Bθ). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from r, B, R, defining B\_θ)q(r). Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
