\section*{ID9392: Definition of · · ·}
\paragraph{Metadata.}
PiID: 3455641725437 | RTEID: RTE:P36471.2218:T3.5447 | UUID: 0a42971e-e38f-5090-94c9-d85595f6ba9f

\paragraph{Canonical Statement.}
ficate Lean Certificate Coq Certificate lemmaid0965\_decoding\_lookup\_time\_complexity:sorry theoremid0965\_decoding\_lookup\_time\_complexity Theoremid0965\_decoding\_lookup\_time\_complexity Dependencies and Test Handle Dependencies [ID 0964], [ID 0900] Node registry\_id\_0965 Support Titles Scaling Law; Support Relation; Scaling Law Test Handle If the cited entry equations cannot be made mutually admissible in one TRAWIN-normalized frame, the entry fails. Canonical Equation Links 𝑇𝑑𝑒𝑐 = 𝑂 (log 153600) \$≈\$ · · · = 𝑂 [153600 × 𝐿𝑜𝑔[153600𝐹𝐹𝑇 − 𝑜𝑝𝑡𝑖𝑚𝑖𝑧𝑒𝑑 𝐷 = − log 6 log(27/32) \$≈\$ · · · [ID 0966] ROUND-TRIP FIDELITY METRIC TZPID ID0966 UUID 36eccb35-18dc-5e45-b46b-49b58515c5ef Type Geometric / Topological Statement Scale geometric LOC Classification Working routing: QA641 manifolds and topology; QC174.17 mathematical physics arXiv Classification Primary: math.DG; Cross-list: math-ph, math.AT Canonical Statement This entry develops round-trip fidelity metric inside the bi

\paragraph{Canonical Equation.}
\[
· · · = 𝑂 [153600 × 𝐿𝑜𝑔[153600𝐹𝐹𝑇 − 𝑜𝑝𝑡𝑖𝑚𝑖𝑧𝑒𝑑 𝐷 = − log 6 log(27/32)
\]

\paragraph{Dictionary.}
Definition of · · · — · · · = 𝑂 [153600 × 𝐿𝑜𝑔[153600𝐹𝐹𝑇 − 𝑜𝑝𝑡𝑖𝑚𝑖𝑧𝑒𝑑 𝐷 = − log 6 log(27/32)

\paragraph{Encyclopedia.}
Definition of · · · is an algebraic definition, written · · · = 𝑂 [153600 × 𝐿𝑜𝑔[153600𝐹𝐹𝑇 − 𝑜𝑝𝑡𝑖𝑚𝑖𝑧𝑒𝑑 𝐷 = − log 6 log(27/32). It is an algebraic definition expressing the quantity directly in terms of the variables on its right-hand side. It is built from l, o, g, defining · · ·. Within the Trawin Zero Point registry it serves as one element of the framework's mathematical narrative.
